### 2020-02-06 01-Chp1-Introduction.Rmd
Initial commit

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

# Introduction {#intro-intro}
\minitoc <!-- this will include a mini table of contents-->

<!--
The {#rmd-basics} text after the chapter declaration will allow us to link throughout the document back to the beginning of this chapter. Reference labels will automatically be generated if you don't specify them, as the lowercase title with spaces replaced by hypens (e.g. r-markdown-basics). Look for the reference to this label at the beginning of the next chapter.
-->

This is a test of the bibliography (@Darwin1859)

### 2020-02-06 02-Chp2-Systematic-Review.Rmd
Initial commit

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
There is grandeur in this view of life, with its several powers, having been originally breathed into a few forms or into one; and that, whilst this planet has gone cycling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being, evolved.
```
(ref:darwin-quote) --- Charles Darwin [@Darwin1859]

# Chapter 2: Systematic Review {#chapter-2-headings}
\minitoc <!-- this will include a mini table of contents-->

## Test

### 2020-02-06 _00-introduction.Rmd
Initial commit

--- 2020-02-06 02-Chp2-Systematic-Review.Rmd
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
-There is grandeur in this view of life, with its several powers, having been originally breathed into a few forms or into one; and that, whilst this planet has gone cycling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being, evolved.
-```
-(ref:darwin-quote) --- Charles Darwin [@Darwin1859]
+# Introduction {-}
 
-# Chapter 2: Systematic Review {#chapter-2-headings}
-\minitoc <!-- this will include a mini table of contents-->
+\adjustmtc 
+<!-- For PDF output, we must include this LaTeX command after unnumbered headings, otherwise the numbers in the mini table of contents will be incorrect -->
 
-## Test
+Welcome to my thesis!

### 2020-02-06 index.Rmd
Initial commit

---
#####################
## thesis metadata ##
#####################
title: |
   Lipids and dementia\
   An investigation of their relationship

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
dedication: For Yihui Xie
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

#######################
## bibliography path ##
#######################
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
bibliography-heading-in-pdf: References

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: true   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: true # add as DRAFT mark in the footer?
page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

params:
  corrections: true # set false to stop applying blue background to blocks of corrections

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: none  
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    config:
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    toc: true   
link-citations: true
documentclass: book

---

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
```
<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file scripts/create_chunk_options.R
-->

```{r introduction, child = '_00-introduction.Rmd'}
```

### 2020-02-06 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Updates

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% OXFORD THESIS TEMPLATE

% Use this template to produce a standard thesis that meets the Oxford University requirements for DPhil submission
%
% Originally by Keith A. Gillow (gillow@maths.ox.ac.uk), 1997
% Modified by Sam Evans (sam@samuelevansresearch.org), 2007
% Modified by John McManigle (john@oxfordechoes.com), 2015
% Modified by Ulrik Lyngs (ulrik.lyngs@cs.ox.ac.uk), 2018, for use with R Markdown
%
% Ulrik Lyngs, 25 Nov 2018: Following John McManigle, broad permissions are granted to use, modify, and distribute this software
% as specified in the MIT License included in this distribution's LICENSE file.
%
% John tried to comment this file extensively, so read through it to see how to use the various options.  Remember
% that in LaTeX, any line starting with a % is NOT executed.  Several places below, you have a choice of which line to use
% out of multiple options (eg draft vs final, for PDF vs for binding, etc.)  When you pick one, add a % to the beginning of
% the lines you don't want.

%%%%% CHOOSE PAGE LAYOUT
% The most common choices should be below.  You can also do other things, like replacing "a4paper" with "letterpaper", etc.

% This one will format for two-sided binding (ie left and right pages have mirror margins; blank pages inserted where needed):
%\documentclass[a4paper,twoside]{templates/ociamthesis}
% This one will format for one-sided binding (ie left margin > right margin; no extra blank pages):
%\documentclass[a4paper]{ociamthesis}
% This one will format for PDF output (ie equal margins, no extra blank pages):
%\documentclass[a4paper,nobind]{templates/ociamthesis}
%UL 2 Dec 2018: pass this in from YAML
\documentclass[a4paper, nobind]{templates/ociamthesis}

% UL 30 Nov 2018 pandoc puts lists in 'tightlist' command when no space between bullet points in Rmd file
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% UL 1 Dec 2018, fix to include code in shaded environments

%UL 2 Dec 2018 reduce whitespace around verbatim environments
\usepackage{etoolbox}
\makeatletter
\preto{\@verbatim}{\topsep=0pt \partopsep=0pt }
\makeatother

%UL 26 Mar 2019, enable strikethrough
\usepackage[normalem]{ulem}

%UL 15 Oct 2019, enable link highlighting to be turned off from YAML
\usepackage[colorlinks=false,pdfpagelabels,hidelinks=true]{hyperref}

%%%%% SELECT YOUR DRAFT OPTIONS
% Three options going on here; use in any combination.  But remember to turn the first two off before
% generating a PDF to send to the printer!

% This adds a "DRAFT" footer to every normal page.  (The first page of each chapter is not a "normal" page.)
\fancyfoot[C]{\emph{DRAFT Printed on \today}}

% This highlights (in blue) corrections marked with (for words) \mccorrect{blah} or (for whole
% paragraphs) \begin{mccorrection} . . . \end{mccorrection}.  This can be useful for sending a PDF of
% your corrected thesis to your examiners for review.  Turn it off, and the blue disappears.
\correctionstrue

%%%%% BIBLIOGRAPHY SETUP
% Note that your bibliography will require some tweaking depending on your department, preferred format, etc.
% The options included below are just very basic "sciencey" and "humanitiesey" options to get started.
% If you've not used LaTeX before, I recommend reading a little about biblatex/biber and getting started with it.
% If you're already a LaTeX pro and are used to natbib or something, modify as necessary.
% Either way, you'll have to choose and configure an appropriate bibliography format...

% The science-type option: numerical in-text citation with references in order of appearance.
% \usepackage[style=numeric-comp, sorting=none, backend=biber, doi=false, isbn=false]{biblatex}
% \newcommand*{\bibtitle}{References}

% The humanities-type option: author-year in-text citation with an alphabetical works cited.
% \usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=false, isbn=false]{biblatex}
% \newcommand*{\bibtitle}{Works Cited}

%UL 3 Dec 2018: set this from YAML in index.Rmd
\usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=true, isbn=false, uniquename=false]{biblatex}
\newcommand*{\bibtitle}{Bibliography}

% This makes the bibliography left-aligned (not 'justified') and slightly smaller font.
\renewcommand*{\bibfont}{\raggedright\small}

% Change this to the name of your .bib file (usually exported from a citation manager like Zotero or EndNote).
\addbibresource{bibliography/references.bib}

% Uncomment this if you want equation numbers per section (2.3.12), instead of per chapter (2.18):
%\numberwithin{equation}{subsection}

%%%%% THESIS / TITLE PAGE INFORMATION
% Everybody needs to complete the following:
\title{Lipids and dementia\\
An investigation of their relationship}
\author{Luke A McGuinness}
\college{}

% Master's candidates who require the alternate title page (with candidate number and word count)
% must also un-comment and complete the following three lines:
%\masterssubmissiontrue
%\candidateno{933516}
%\wordcount{28,815}

% Uncomment the following line if your degree also includes exams (eg most masters):
%\renewcommand{\submittedtext}{Submitted in partial completion of the}
% Your full degree name.  (But remember that DPhils aren't "in" anything.  They're just DPhils.)
\degree{Doctor of Philosophy in Population Health Sciences}
% Term and year of submission, or date if your board requires (eg most masters)
\degreedate{TBC}

%%%%% YOUR OWN PERSONAL MACROS
% This is a good place to dump your own LaTeX macros as they come up.

% To make text superscripts shortcuts
	\renewcommand{\th}{\textsuperscript{th}} % ex: I won 4\th place
	\newcommand{\nd}{\textsuperscript{nd}}
	\renewcommand{\st}{\textsuperscript{st}}
	\newcommand{\rd}{\textsuperscript{rd}}

%%%%% THE ACTUAL DOCUMENT STARTS HERE
\begin{document}

%%%%% CHOOSE YOUR LINE SPACING HERE
% This is the official option.  Use it for your submission copy and library copy:
\setlength{\textbaselineskip}{22pt plus2pt}
% This is closer spacing (about 1.5-spaced) that you might prefer for your personal copies:
%\setlength{\textbaselineskip}{18pt plus2pt minus1pt}

% You can set the spacing here for the roman-numbered pages (acknowledgements, table of contents, etc.)
\setlength{\frontmatterbaselineskip}{17pt plus1pt minus1pt}

% UL: You can set the line and paragraph spacing here for the separate abstract page to be handed in to Examination schools
\setlength{\abstractseparatelineskip}{13pt plus1pt minus1pt}
\setlength{\abstractseparateparskip}{0pt plus 1pt}

% UL: You can set the general paragraph spacing here - I've set it to 2pt (was 0) so
% it's less claustrophobic
\setlength{\parskip}{2pt plus 1pt}

% Leave this line alone; it gets things started for the real document.
\setlength{\baselineskip}{\textbaselineskip}

%%%%% CHOOSE YOUR SECTION NUMBERING DEPTH HERE
% You have two choices.  First, how far down are sections numbered?  (Below that, they're named but
% don't get numbers.)  Second, what level of section appears in the table of contents?  These don't have
% to match: you can have numbered sections that don't show up in the ToC, or unnumbered sections that
% do.  Throughout, 0 = chapter; 1 = section; 2 = subsection; 3 = subsubsection, 4 = paragraph...

% The level that gets a number:
\setcounter{secnumdepth}{2}
% The level that shows up in the ToC:
\setcounter{tocdepth}{2}

%%%%% ABSTRACT SEPARATE
% This is used to create the separate, one-page abstract that you are required to hand into the Exam
% Schools.  You can comment it out to generate a PDF for printing or whatnot.
\begin{abstractseparate}
  \textbf{Background}\\
  In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
  by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
  the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
  reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
  between modifiable targets and dementia risk is central to the development of evidence-based prevention
  strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
  levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
  but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
\end{abstractseparate}

% JEM: Pages are roman numbered from here, though page numbers are invisible until ToC.  This is in
% keeping with most typesetting conventions.
\begin{romanpages}

% Title page is created here
\maketitle

%%%%% DEDICATION -- If you'd like one, un-comment the following.
\begin{dedication}
  For Brendan McHugh
\end{dedication}

%%%%% ACKNOWLEDGEMENTS -- Nothing to do here except comment out if you don't want it.
\begin{acknowledgements}
 	This is where you will normally thank your advisor, colleagues, family and friends, as well as funding and institutional support. In our case, we will give our praises to the people who developed the ideas and tools that allow us to push open science a little step forward by writing plain-text, transparent, and reproducible theses in R Markdown.

\begin{flushright}
Luke McGuinness \\
Canynge Hall, Bristol \\
1 December 2021
\end{flushright}
\end{acknowledgements}

%%%%% ABSTRACT -- Nothing to do here except comment out if you don't want it.
\begin{abstract}
	\textbf{Background}\\
In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
between modifiable targets and dementia risk is central to the development of evidence-based prevention
strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
\end{abstract}

%%%%% MINI TABLES
% This lays the groundwork for per-chapter, mini tables of contents.  Comment the following line
% (and remove \minitoc from the chapter files) if you don't want this.  Un-comment either of the
% next two lines if you want a per-chapter list of figures or tables.
  \dominitoc % include a mini table of contents

% This aligns the bottom of the text of each page.  It generally makes things look better.
\flushbottom

% This is where the whole-document ToC appears:
\tableofcontents

\listoffigures
	\mtcaddchapter
  	% \mtcaddchapter is needed when adding a non-chapter (but chapter-like) entity to avoid confusing minitoc

% Uncomment to generate a list of tables:
\listoftables
  \mtcaddchapter
%%%%% LIST OF ABBREVIATIONS
% This example includes a list of abbreviations.  Look at text/abbreviations.tex to see how that file is
% formatted.  The template can handle any kind of list though, so this might be a good place for a
% glossary, etc.
\include{front-and-back-matter/abbreviations}

% The Roman pages, like the Roman Empire, must come to its inevitable close.
\end{romanpages}

%%%%% CHAPTERS
% Add or remove any chapters you'd like here, by file name (excluding '.tex'):
\flushbottom

% all your chapters and appendices will appear here
\hypertarget{introduction}{%
\chapter*{Introduction}\label{introduction}}
\addcontentsline{toc}{chapter}{Introduction}

\adjustmtc

Welcome to my thesis!

\hypertarget{intro-intro}{%
\chapter{Introduction}\label{intro-intro}}

\minitoc

This is a test of the bibliography (\protect\hyperlink{ref-Darwin1859}{1})

\begin{savequote}
There is grandeur in this view of life, with its several powers, having
been originally breathed into a few forms or into one; and that, whilst
this planet has gone cycling on according to the fixed law of gravity,
from so simple a beginning endless forms most beautiful and most
wonderful have been, and are being, evolved.
\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-Darwin1859}{1}}}\end{savequote}

\hypertarget{chapter-2-headings}{%
\chapter{Chapter 2: Systematic Review}\label{chapter-2-headings}}

\minitoc

\hypertarget{test}{%
\section{Test}\label{test}}

\startappendices

\hypertarget{list-of-one-thing}{%
\chapter{List of one thing}\label{list-of-one-thing}}

\hypertarget{list-of-something-else}{%
\chapter{List of something else}\label{list-of-something-else}}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-Darwin1859}{}%
1. Darwin, C. \emph{On the Origin of Species by Means of Natural Selection or the Preservation of Favoured Races in the Struggle for Life}. (John Murray, 1859).

%%%%% REFERENCES

% JEM: Quote for the top of references (just like a chapter quote if you're using them).  Comment to skip.
% \begin{savequote}[8cm]
% The first kind of intellectual and artistic personality belongs to the hedgehogs, the second to the foxes \dots
%   \qauthor{--- Sir Isaiah Berlin \cite{berlin_hedgehog_2013}}
% \end{savequote}

\setlength{\baselineskip}{0pt} % JEM: Single-space References

{\renewcommand*\MakeUppercase[1]{#1}%
\printbibliography[heading=bibintoc,title={\bibtitle}]}

\end{document}

### 2020-02-06 front-and-back-matter/_abstract.Rmd
Updates

--- 2020-02-06 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% OXFORD THESIS TEMPLATE
-
-% Use this template to produce a standard thesis that meets the Oxford University requirements for DPhil submission
-%
-% Originally by Keith A. Gillow (gillow@maths.ox.ac.uk), 1997
-% Modified by Sam Evans (sam@samuelevansresearch.org), 2007
-% Modified by John McManigle (john@oxfordechoes.com), 2015
-% Modified by Ulrik Lyngs (ulrik.lyngs@cs.ox.ac.uk), 2018, for use with R Markdown
-%
-% Ulrik Lyngs, 25 Nov 2018: Following John McManigle, broad permissions are granted to use, modify, and distribute this software
-% as specified in the MIT License included in this distribution's LICENSE file.
-%
-% John tried to comment this file extensively, so read through it to see how to use the various options.  Remember
-% that in LaTeX, any line starting with a % is NOT executed.  Several places below, you have a choice of which line to use
-% out of multiple options (eg draft vs final, for PDF vs for binding, etc.)  When you pick one, add a % to the beginning of
-% the lines you don't want.
-
-%%%%% CHOOSE PAGE LAYOUT
-% The most common choices should be below.  You can also do other things, like replacing "a4paper" with "letterpaper", etc.
-
-% This one will format for two-sided binding (ie left and right pages have mirror margins; blank pages inserted where needed):
-%\documentclass[a4paper,twoside]{templates/ociamthesis}
-% This one will format for one-sided binding (ie left margin > right margin; no extra blank pages):
-%\documentclass[a4paper]{ociamthesis}
-% This one will format for PDF output (ie equal margins, no extra blank pages):
-%\documentclass[a4paper,nobind]{templates/ociamthesis}
-%UL 2 Dec 2018: pass this in from YAML
-\documentclass[a4paper, nobind]{templates/ociamthesis}
-
-% UL 30 Nov 2018 pandoc puts lists in 'tightlist' command when no space between bullet points in Rmd file
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% UL 1 Dec 2018, fix to include code in shaded environments
-
-%UL 2 Dec 2018 reduce whitespace around verbatim environments
-\usepackage{etoolbox}
-\makeatletter
-\preto{\@verbatim}{\topsep=0pt \partopsep=0pt }
-\makeatother
-
-%UL 26 Mar 2019, enable strikethrough
-\usepackage[normalem]{ulem}
-
-%UL 15 Oct 2019, enable link highlighting to be turned off from YAML
-\usepackage[colorlinks=false,pdfpagelabels,hidelinks=true]{hyperref}
-
-%%%%% SELECT YOUR DRAFT OPTIONS
-% Three options going on here; use in any combination.  But remember to turn the first two off before
-% generating a PDF to send to the printer!
-
-% This adds a "DRAFT" footer to every normal page.  (The first page of each chapter is not a "normal" page.)
-\fancyfoot[C]{\emph{DRAFT Printed on \today}}
-
-% This highlights (in blue) corrections marked with (for words) \mccorrect{blah} or (for whole
-% paragraphs) \begin{mccorrection} . . . \end{mccorrection}.  This can be useful for sending a PDF of
-% your corrected thesis to your examiners for review.  Turn it off, and the blue disappears.
-\correctionstrue
-
-%%%%% BIBLIOGRAPHY SETUP
-% Note that your bibliography will require some tweaking depending on your department, preferred format, etc.
-% The options included below are just very basic "sciencey" and "humanitiesey" options to get started.
-% If you've not used LaTeX before, I recommend reading a little about biblatex/biber and getting started with it.
-% If you're already a LaTeX pro and are used to natbib or something, modify as necessary.
-% Either way, you'll have to choose and configure an appropriate bibliography format...
-
-% The science-type option: numerical in-text citation with references in order of appearance.
-% \usepackage[style=numeric-comp, sorting=none, backend=biber, doi=false, isbn=false]{biblatex}
-% \newcommand*{\bibtitle}{References}
-
-% The humanities-type option: author-year in-text citation with an alphabetical works cited.
-% \usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=false, isbn=false]{biblatex}
-% \newcommand*{\bibtitle}{Works Cited}
-
-%UL 3 Dec 2018: set this from YAML in index.Rmd
-\usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=true, isbn=false, uniquename=false]{biblatex}
-\newcommand*{\bibtitle}{Bibliography}
-
-% This makes the bibliography left-aligned (not 'justified') and slightly smaller font.
-\renewcommand*{\bibfont}{\raggedright\small}
-
-% Change this to the name of your .bib file (usually exported from a citation manager like Zotero or EndNote).
-\addbibresource{bibliography/references.bib}
-
-% Uncomment this if you want equation numbers per section (2.3.12), instead of per chapter (2.18):
-%\numberwithin{equation}{subsection}
-
-%%%%% THESIS / TITLE PAGE INFORMATION
-% Everybody needs to complete the following:
-\title{Lipids and dementia\\
-An investigation of their relationship}
-\author{Luke A McGuinness}
-\college{}
-
-% Master's candidates who require the alternate title page (with candidate number and word count)
-% must also un-comment and complete the following three lines:
-%\masterssubmissiontrue
-%\candidateno{933516}
-%\wordcount{28,815}
-
-% Uncomment the following line if your degree also includes exams (eg most masters):
-%\renewcommand{\submittedtext}{Submitted in partial completion of the}
-% Your full degree name.  (But remember that DPhils aren't "in" anything.  They're just DPhils.)
-\degree{Doctor of Philosophy in Population Health Sciences}
-% Term and year of submission, or date if your board requires (eg most masters)
-\degreedate{TBC}
-
-%%%%% YOUR OWN PERSONAL MACROS
-% This is a good place to dump your own LaTeX macros as they come up.
-
-% To make text superscripts shortcuts
-	\renewcommand{\th}{\textsuperscript{th}} % ex: I won 4\th place
-	\newcommand{\nd}{\textsuperscript{nd}}
-	\renewcommand{\st}{\textsuperscript{st}}
-	\newcommand{\rd}{\textsuperscript{rd}}
-
-%%%%% THE ACTUAL DOCUMENT STARTS HERE
-\begin{document}
-
-%%%%% CHOOSE YOUR LINE SPACING HERE
-% This is the official option.  Use it for your submission copy and library copy:
-\setlength{\textbaselineskip}{22pt plus2pt}
-% This is closer spacing (about 1.5-spaced) that you might prefer for your personal copies:
-%\setlength{\textbaselineskip}{18pt plus2pt minus1pt}
-
-% You can set the spacing here for the roman-numbered pages (acknowledgements, table of contents, etc.)
-\setlength{\frontmatterbaselineskip}{17pt plus1pt minus1pt}
-
-% UL: You can set the line and paragraph spacing here for the separate abstract page to be handed in to Examination schools
-\setlength{\abstractseparatelineskip}{13pt plus1pt minus1pt}
-\setlength{\abstractseparateparskip}{0pt plus 1pt}
-
-% UL: You can set the general paragraph spacing here - I've set it to 2pt (was 0) so
-% it's less claustrophobic
-\setlength{\parskip}{2pt plus 1pt}
-
-% Leave this line alone; it gets things started for the real document.
-\setlength{\baselineskip}{\textbaselineskip}
-
-%%%%% CHOOSE YOUR SECTION NUMBERING DEPTH HERE
-% You have two choices.  First, how far down are sections numbered?  (Below that, they're named but
-% don't get numbers.)  Second, what level of section appears in the table of contents?  These don't have
-% to match: you can have numbered sections that don't show up in the ToC, or unnumbered sections that
-% do.  Throughout, 0 = chapter; 1 = section; 2 = subsection; 3 = subsubsection, 4 = paragraph...
-
-% The level that gets a number:
-\setcounter{secnumdepth}{2}
-% The level that shows up in the ToC:
-\setcounter{tocdepth}{2}
-
-%%%%% ABSTRACT SEPARATE
-% This is used to create the separate, one-page abstract that you are required to hand into the Exam
-% Schools.  You can comment it out to generate a PDF for printing or whatnot.
-\begin{abstractseparate}
-  \textbf{Background}\\
+__Background__  
 In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
@@
 but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
-\end{abstractseparate}
-
-% JEM: Pages are roman numbered from here, though page numbers are invisible until ToC.  This is in
-% keeping with most typesetting conventions.
-\begin{romanpages}
-
-% Title page is created here
-\maketitle
-
-%%%%% DEDICATION -- If you'd like one, un-comment the following.
-\begin{dedication}
-  For Brendan McHugh
-\end{dedication}
-
-%%%%% ACKNOWLEDGEMENTS -- Nothing to do here except comment out if you don't want it.
-\begin{acknowledgements}
- 	This is where you will normally thank your advisor, colleagues, family and friends, as well as funding and institutional support.
-In our case, we will give our praises to the people who developed the ideas and tools that allow us to push open science a little step forward by writing plain-text, transparent, and reproducible theses in R Markdown.
-
-\begin{flushright}
-Luke McGuinness \\
-Canynge Hall, Bristol \\
-1 December 2021
-\end{flushright}
-\end{acknowledgements}
-
-%%%%% ABSTRACT -- Nothing to do here except comment out if you don't want it.
-\begin{abstract}
-	\textbf{Background}\\
-In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
-by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
-the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
-reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
-between modifiable targets and dementia risk is central to the development of evidence-based prevention
-strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
-levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
-but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
-\end{abstract}
-
-%%%%% MINI TABLES
-% This lays the groundwork for per-chapter, mini tables of contents.  Comment the following line
-% (and remove \minitoc from the chapter files) if you don't want this.  Un-comment either of the
-% next two lines if you want a per-chapter list of figures or tables.
-  \dominitoc % include a mini table of contents
-
-% This aligns the bottom of the text of each page.  It generally makes things look better.
-\flushbottom
-
-% This is where the whole-document ToC appears:
-\tableofcontents
-
-\listoffigures
-	\mtcaddchapter
-  	% \mtcaddchapter is needed when adding a non-chapter (but chapter-like) entity to avoid confusing minitoc
-
-% Uncomment to generate a list of tables:
-\listoftables
-  \mtcaddchapter
-%%%%% LIST OF ABBREVIATIONS
-% This example includes a list of abbreviations.  Look at text/abbreviations.tex to see how that file is
-% formatted.  The template can handle any kind of list though, so this might be a good place for a
-% glossary, etc.
-\include{front-and-back-matter/abbreviations}
-
-% The Roman pages, like the Roman Empire, must come to its inevitable close.
-\end{romanpages}
-
-%%%%% CHAPTERS
-% Add or remove any chapters you'd like here, by file name (excluding '.tex'):
-\flushbottom
-
-% all your chapters and appendices will appear here
-\hypertarget{introduction}{%
-\chapter*{Introduction}\label{introduction}}
-\addcontentsline{toc}{chapter}{Introduction}
-
-\adjustmtc
-
-Welcome to my thesis!
-
-\hypertarget{intro-intro}{%
-\chapter{Introduction}\label{intro-intro}}
-
-\minitoc
-
-This is a test of the bibliography (\protect\hyperlink{ref-Darwin1859}{1})
-
-\begin{savequote}
-There is grandeur in this view of life, with its several powers, having
-been originally breathed into a few forms or into one; and that, whilst
-this planet has gone cycling on according to the fixed law of gravity,
-from so simple a beginning endless forms most beautiful and most
-wonderful have been, and are being, evolved.
-\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-Darwin1859}{1}}}\end{savequote}
-
-\hypertarget{chapter-2-headings}{%
-\chapter{Chapter 2: Systematic Review}\label{chapter-2-headings}}
-
-\minitoc
-
-\hypertarget{test}{%
-\section{Test}\label{test}}
-
-\startappendices
-
-\hypertarget{list-of-one-thing}{%
-\chapter{List of one thing}\label{list-of-one-thing}}
-
-\hypertarget{list-of-something-else}{%
-\chapter{List of something else}\label{list-of-something-else}}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Darwin1859}{}%
-1. Darwin, C. \emph{On the Origin of Species by Means of Natural Selection or the Preservation of Favoured Races in the Struggle for Life}. (John Murray, 1859).
-
-%%%%% REFERENCES
-
-% JEM: Quote for the top of references (just like a chapter quote if you're using them).  Comment to skip.
-% \begin{savequote}[8cm]
-% The first kind of intellectual and artistic personality belongs to the hedgehogs, the second to the foxes \dots
-%   \qauthor{--- Sir Isaiah Berlin \cite{berlin_hedgehog_2013}}
-% \end{savequote}
-
-\setlength{\baselineskip}{0pt} % JEM: Single-space References
-
-{\renewcommand*\MakeUppercase[1]{#1}%
-\printbibliography[heading=bibintoc,title={\bibtitle}]}
-
-\end{document}

### 2020-02-06 front-and-back-matter/_acknowledgements.Rmd
Updates

--- 2020-02-06 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
@@
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% OXFORD THESIS TEMPLATE
-
-% Use this template to produce a standard thesis that meets the Oxford University requirements for DPhil submission
-%
-% Originally by Keith A. Gillow (gillow@maths.ox.ac.uk), 1997
-% Modified by Sam Evans (sam@samuelevansresearch.org), 2007
-% Modified by John McManigle (john@oxfordechoes.com), 2015
-% Modified by Ulrik Lyngs (ulrik.lyngs@cs.ox.ac.uk), 2018, for use with R Markdown
-%
-% Ulrik Lyngs, 25 Nov 2018: Following John McManigle, broad permissions are granted to use, modify, and distribute this software
-% as specified in the MIT License included in this distribution's LICENSE file.
-%
-% John tried to comment this file extensively, so read through it to see how to use the various options.  Remember
-% that in LaTeX, any line starting with a % is NOT executed.  Several places below, you have a choice of which line to use
-% out of multiple options (eg draft vs final, for PDF vs for binding, etc.)  When you pick one, add a % to the beginning of
-% the lines you don't want.
-
-%%%%% CHOOSE PAGE LAYOUT
-% The most common choices should be below.  You can also do other things, like replacing "a4paper" with "letterpaper", etc.
-
-% This one will format for two-sided binding (ie left and right pages have mirror margins; blank pages inserted where needed):
-%\documentclass[a4paper,twoside]{templates/ociamthesis}
-% This one will format for one-sided binding (ie left margin > right margin; no extra blank pages):
-%\documentclass[a4paper]{ociamthesis}
-% This one will format for PDF output (ie equal margins, no extra blank pages):
-%\documentclass[a4paper,nobind]{templates/ociamthesis}
-%UL 2 Dec 2018: pass this in from YAML
-\documentclass[a4paper, nobind]{templates/ociamthesis}
-
-% UL 30 Nov 2018 pandoc puts lists in 'tightlist' command when no space between bullet points in Rmd file
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-
-% UL 1 Dec 2018, fix to include code in shaded environments
-
-%UL 2 Dec 2018 reduce whitespace around verbatim environments
-\usepackage{etoolbox}
-\makeatletter
-\preto{\@verbatim}{\topsep=0pt \partopsep=0pt }
-\makeatother
-
-%UL 26 Mar 2019, enable strikethrough
-\usepackage[normalem]{ulem}
-
-%UL 15 Oct 2019, enable link highlighting to be turned off from YAML
-\usepackage[colorlinks=false,pdfpagelabels,hidelinks=true]{hyperref}
-
-%%%%% SELECT YOUR DRAFT OPTIONS
-% Three options going on here; use in any combination.  But remember to turn the first two off before
-% generating a PDF to send to the printer!
-
-% This adds a "DRAFT" footer to every normal page.  (The first page of each chapter is not a "normal" page.)
-\fancyfoot[C]{\emph{DRAFT Printed on \today}}
-
-% This highlights (in blue) corrections marked with (for words) \mccorrect{blah} or (for whole
-% paragraphs) \begin{mccorrection} . . . \end{mccorrection}.  This can be useful for sending a PDF of
-% your corrected thesis to your examiners for review.  Turn it off, and the blue disappears.
-\correctionstrue
-
-%%%%% BIBLIOGRAPHY SETUP
-% Note that your bibliography will require some tweaking depending on your department, preferred format, etc.
-% The options included below are just very basic "sciencey" and "humanitiesey" options to get started.
-% If you've not used LaTeX before, I recommend reading a little about biblatex/biber and getting started with it.
-% If you're already a LaTeX pro and are used to natbib or something, modify as necessary.
-% Either way, you'll have to choose and configure an appropriate bibliography format...
-
-% The science-type option: numerical in-text citation with references in order of appearance.
-% \usepackage[style=numeric-comp, sorting=none, backend=biber, doi=false, isbn=false]{biblatex}
-% \newcommand*{\bibtitle}{References}
-
-% The humanities-type option: author-year in-text citation with an alphabetical works cited.
-% \usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=false, isbn=false]{biblatex}
-% \newcommand*{\bibtitle}{Works Cited}
-
-%UL 3 Dec 2018: set this from YAML in index.Rmd
-\usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=true, isbn=false, uniquename=false]{biblatex}
-\newcommand*{\bibtitle}{Bibliography}
-
-% This makes the bibliography left-aligned (not 'justified') and slightly smaller font.
-\renewcommand*{\bibfont}{\raggedright\small}
-
-% Change this to the name of your .bib file (usually exported from a citation manager like Zotero or EndNote).
-\addbibresource{bibliography/references.bib}
-
-% Uncomment this if you want equation numbers per section (2.3.12), instead of per chapter (2.18):
-%\numberwithin{equation}{subsection}
-
-%%%%% THESIS / TITLE PAGE INFORMATION
-% Everybody needs to complete the following:
-\title{Lipids and dementia\\
-An investigation of their relationship}
-\author{Luke A McGuinness}
-\college{}
-
-% Master's candidates who require the alternate title page (with candidate number and word count)
-% must also un-comment and complete the following three lines:
-%\masterssubmissiontrue
-%\candidateno{933516}
-%\wordcount{28,815}
-
-% Uncomment the following line if your degree also includes exams (eg most masters):
-%\renewcommand{\submittedtext}{Submitted in partial completion of the}
-% Your full degree name.  (But remember that DPhils aren't "in" anything.  They're just DPhils.)
-\degree{Doctor of Philosophy in Population Health Sciences}
-% Term and year of submission, or date if your board requires (eg most masters)
-\degreedate{TBC}
-
-%%%%% YOUR OWN PERSONAL MACROS
-% This is a good place to dump your own LaTeX macros as they come up.
-
-% To make text superscripts shortcuts
-	\renewcommand{\th}{\textsuperscript{th}} % ex: I won 4\th place
-	\newcommand{\nd}{\textsuperscript{nd}}
-	\renewcommand{\st}{\textsuperscript{st}}
-	\newcommand{\rd}{\textsuperscript{rd}}
-
-%%%%% THE ACTUAL DOCUMENT STARTS HERE
-\begin{document}
-
-%%%%% CHOOSE YOUR LINE SPACING HERE
-% This is the official option.  Use it for your submission copy and library copy:
-\setlength{\textbaselineskip}{22pt plus2pt}
-% This is closer spacing (about 1.5-spaced) that you might prefer for your personal copies:
-%\setlength{\textbaselineskip}{18pt plus2pt minus1pt}
-
-% You can set the spacing here for the roman-numbered pages (acknowledgements, table of contents, etc.)
-\setlength{\frontmatterbaselineskip}{17pt plus1pt minus1pt}
-
-% UL: You can set the line and paragraph spacing here for the separate abstract page to be handed in to Examination schools
-\setlength{\abstractseparatelineskip}{13pt plus1pt minus1pt}
-\setlength{\abstractseparateparskip}{0pt plus 1pt}
-
-% UL: You can set the general paragraph spacing here - I've set it to 2pt (was 0) so
-% it's less claustrophobic
-\setlength{\parskip}{2pt plus 1pt}
-
-% Leave this line alone; it gets things started for the real document.
-\setlength{\baselineskip}{\textbaselineskip}
-
-%%%%% CHOOSE YOUR SECTION NUMBERING DEPTH HERE
-% You have two choices.  First, how far down are sections numbered?  (Below that, they're named but
-% don't get numbers.)  Second, what level of section appears in the table of contents?  These don't have
-% to match: you can have numbered sections that don't show up in the ToC, or unnumbered sections that
-% do.  Throughout, 0 = chapter; 1 = section; 2 = subsection; 3 = subsubsection, 4 = paragraph...
-
-% The level that gets a number:
-\setcounter{secnumdepth}{2}
-% The level that shows up in the ToC:
-\setcounter{tocdepth}{2}
-
-%%%%% ABSTRACT SEPARATE
-% This is used to create the separate, one-page abstract that you are required to hand into the Exam
-% Schools.  You can comment it out to generate a PDF for printing or whatnot.
-\begin{abstractseparate}
-  \textbf{Background}\\
-  In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
-  by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
-  the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
-  reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
-  between modifiable targets and dementia risk is central to the development of evidence-based prevention
-  strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
-  levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
-  but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
-\end{abstractseparate}
-
-% JEM: Pages are roman numbered from here, though page numbers are invisible until ToC.  This is in
-% keeping with most typesetting conventions.
-\begin{romanpages}
-
-% Title page is created here
-\maketitle
-
-%%%%% DEDICATION -- If you'd like one, un-comment the following.
-\begin{dedication}
-  For Brendan McHugh
-\end{dedication}
-
-%%%%% ACKNOWLEDGEMENTS -- Nothing to do here except comment out if you don't want it.
-\begin{acknowledgements}
 This is where you will normally thank your advisor, colleagues, family and friends, as well as funding and institutional support.
@@
 \end{flushright}
-\end{acknowledgements}
-
-%%%%% ABSTRACT -- Nothing to do here except comment out if you don't want it.
-\begin{abstract}
-	\textbf{Background}\\
-In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
-by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
-the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
-reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
-between modifiable targets and dementia risk is central to the development of evidence-based prevention
-strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
-levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
-but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
-\end{abstract}
-
-%%%%% MINI TABLES
-% This lays the groundwork for per-chapter, mini tables of contents.  Comment the following line
-% (and remove \minitoc from the chapter files) if you don't want this.  Un-comment either of the
-% next two lines if you want a per-chapter list of figures or tables.
-  \dominitoc % include a mini table of contents
-
-% This aligns the bottom of the text of each page.  It generally makes things look better.
-\flushbottom
-
-% This is where the whole-document ToC appears:
-\tableofcontents
-
-\listoffigures
-	\mtcaddchapter
-  	% \mtcaddchapter is needed when adding a non-chapter (but chapter-like) entity to avoid confusing minitoc
-
-% Uncomment to generate a list of tables:
-\listoftables
-  \mtcaddchapter
-%%%%% LIST OF ABBREVIATIONS
-% This example includes a list of abbreviations.  Look at text/abbreviations.tex to see how that file is
-% formatted.  The template can handle any kind of list though, so this might be a good place for a
-% glossary, etc.
-\include{front-and-back-matter/abbreviations}
-
-% The Roman pages, like the Roman Empire, must come to its inevitable close.
-\end{romanpages}
-
-%%%%% CHAPTERS
-% Add or remove any chapters you'd like here, by file name (excluding '.tex'):
-\flushbottom
-
-% all your chapters and appendices will appear here
-\hypertarget{introduction}{%
-\chapter*{Introduction}\label{introduction}}
-\addcontentsline{toc}{chapter}{Introduction}
-
-\adjustmtc
-
-Welcome to my thesis!
-
-\hypertarget{intro-intro}{%
-\chapter{Introduction}\label{intro-intro}}
-
-\minitoc
-
-This is a test of the bibliography (\protect\hyperlink{ref-Darwin1859}{1})
-
-\begin{savequote}
-There is grandeur in this view of life, with its several powers, having
-been originally breathed into a few forms or into one; and that, whilst
-this planet has gone cycling on according to the fixed law of gravity,
-from so simple a beginning endless forms most beautiful and most
-wonderful have been, and are being, evolved.
-\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-Darwin1859}{1}}}\end{savequote}
-
-\hypertarget{chapter-2-headings}{%
-\chapter{Chapter 2: Systematic Review}\label{chapter-2-headings}}
-
-\minitoc
-
-\hypertarget{test}{%
-\section{Test}\label{test}}
-
-\startappendices
-
-\hypertarget{list-of-one-thing}{%
-\chapter{List of one thing}\label{list-of-one-thing}}
-
-\hypertarget{list-of-something-else}{%
-\chapter{List of something else}\label{list-of-something-else}}
-
-\hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Darwin1859}{}%
-1. Darwin, C. \emph{On the Origin of Species by Means of Natural Selection or the Preservation of Favoured Races in the Struggle for Life}. (John Murray, 1859).
-
-%%%%% REFERENCES
-
-% JEM: Quote for the top of references (just like a chapter quote if you're using them).  Comment to skip.
-% \begin{savequote}[8cm]
-% The first kind of intellectual and artistic personality belongs to the hedgehogs, the second to the foxes \dots
-%   \qauthor{--- Sir Isaiah Berlin \cite{berlin_hedgehog_2013}}
-% \end{savequote}
-
-\setlength{\baselineskip}{0pt} % JEM: Single-space References
-
-{\renewcommand*\MakeUppercase[1]{#1}%
-\printbibliography[heading=bibintoc,title={\bibtitle}]}
-
-\end{document}

### 2020-02-06 index.Rmd
Updates

@@
 college: 
-degree: Doctor of Philosophy
+degree: Doctor of Philosophy in Population Health Sciences
 degreedate: TBC
@@
   `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
-dedication: For Yihui Xie
+dedication: For Brendan McHugh
 abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
@@
 csl: bibliography/nature.csl
-bibliography-heading-in-pdf: References
+bibliography-heading-in-pdf: Bibliography
 
@@
     config:
+      toc:
+        before: |
+          <li><a href="./">Thesis - Draft</a></li>
+        after: |
+          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
       sharing:

### 2020-02-07 02-Chp2-Systematic-Review.Rmd
Major updates

@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
-There is grandeur in this view of life, with its several powers, having been originally breathed into a few forms or into one; and that, whilst this planet has gone cycling on according to the fixed law of gravity, from so simple a beginning endless forms most beautiful and most wonderful have been, and are being, evolved.
+Hold
 ```
-(ref:darwin-quote) --- Charles Darwin [@Darwin1859]
+(ref:darwin-quote) --- Charles Darwin [@chang2012a]
 
@@
 
-## Test
+```{r, echo = FALSE}
+knitr::read_chunk("scripts/Chp2-Systematic-Review.R")
+```
+
+## Aims
+
+The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.
+
+## Methods
+
+### Search strategy
+
+We will systematically search electronic bibliographic databases to identify potentially relevant records.
+The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
+The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol.
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened.
+If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.
+
+The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+
+The abstracts list of relevant conferences (e.g.
+the proceedings of the Alzheimer’s Association International Conference, published in the journal Alzheimer’s & Dementia) will be searched.
+Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
+We will also search BioArxiv, a preprint repository, to identify potentially relevant studies.
+Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+
+### Study selection
+
+Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.
+(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016]
+Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+Full-text screening will also be completed in full by the primary author.
+A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
+Reasons for exclusion at this stage will be recorded.
+Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
+A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]
+
+#### Inclusion
+We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
+Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Participants will be free (or assumed to be free) of dementia/MCI at baseline.
+Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+No limits will be placed on the sample size of included studies.
+
+Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l’Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
+an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
+no dementia or dementia/MCI/dementia) based on this definition.
+
+No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods.
+Preprints and unpublished reports will be eligible for inclusion if relevant.
+Multiple publications resulting from the analysis of the same data will be included and grouped.
+
+#### Exclusion
+Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
+Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded.
+Studies that measure change in continuous cognitive measures (e.g.
+MoCA score) without attempt to map these scores to ordinal groups (e.g.
+no dementia/MCI/dementia) will be excluded.
+Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study’s status.
+Studies that are reported in insufficient detail (e.g.
+only in conference abstracts, new, letters, editorials and opinion) will be excluded.
+Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multidomain intervention” where the lipid-regulating agent is included in each arms (e.g.
+for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+below the age of 50) will be excluded.
+
+### Data extraction
+
+### Risk of bias assessment
+
+Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
+Randomised controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomised studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomised studies of exposures were assessed using the ROBINS-E tool.[TBC]
+
+At present, no risk of bias assessment tool for Mendelian randomisation studies is available. Bias in thesee studies was assessed with the help of an expert panel [TBC]
+
+### Patient and public involvement
+
+## Results
+
+```{r prisma-flow, echo = FALSE, warning=FALSE}
+```
+
+## Discussion
+
+## Conclusion

### 2020-02-07 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Get PDF download working
Major updates

@@
 
-This is a test of the bibliography (\protect\hyperlink{ref-Darwin1859}{1})
+This is a test of the bibliography\textsuperscript{{\textbf{???}}}
+
+The following tools were used to perform risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2
 
 \begin{savequote}
-There is grandeur in this view of life, with its several powers, having
-been originally breathed into a few forms or into one; and that, whilst
-this planet has gone cycling on according to the fixed law of gravity,
-from so simple a beginning endless forms most beautiful and most
-wonderful have been, and are being, evolved.
-\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-Darwin1859}{1}}}\end{savequote}
+Hold
+\qauthor{--- Charles Darwin\textsuperscript{{\textbf{???}}}}\end{savequote}
 
@@
 
-\hypertarget{test}{%
-\section{Test}\label{test}}
+\hypertarget{aims}{%
+\section{Aims}\label{aims}}
+
+The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.
+
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
+
+\hypertarget{search-strategy}{%
+\subsection{Search strategy}\label{search-strategy}}
+
+We will systematically search electronic bibliographic databases to identify potentially relevant records.
+The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
+The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol.
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened.
+If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.
+
+The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+
+The abstracts list of relevant conferences (e.g.~the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's \& Dementia) will be searched.
+Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
+We will also search BioArxiv, a preprint repository, to identify potentially relevant studies.
+Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+
+\hypertarget{study-selection}{%
+\subsection{Study selection}\label{study-selection}}
+
+Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{1}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{2}}
+Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+Full-text screening will also be completed in full by the primary author.
+A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
+Reasons for exclusion at this stage will be recorded.
+Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
+A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{3}}
+
+\hypertarget{inclusion}{%
+\subsubsection{Inclusion}\label{inclusion}}
+
+We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
+Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Participants will be free (or assumed to be free) of dementia/MCI at baseline.
+Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+No limits will be placed on the sample size of included studies.
+
+Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{4}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.
+
+No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods.
+Preprints and unpublished reports will be eligible for inclusion if relevant.
+Multiple publications resulting from the analysis of the same data will be included and grouped.
+
+\hypertarget{exclusion}{%
+\subsubsection{Exclusion}\label{exclusion}}
+
+Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
+Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded.
+Studies that measure change in continuous cognitive measures (e.g.~MoCA score) without attempt to map these scores to ordinal groups (e.g.~no dementia/MCI/dementia) will be excluded.
+Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status.
+Studies that are reported in insufficient detail (e.g.~only in conference abstracts, new, letters, editorials and opinion) will be excluded.
+Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a ``multidomain intervention'' where the lipid-regulating agent is included in each arms (e.g.~for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.~below the age of 50) will be excluded.
+
+\hypertarget{data-extraction}{%
+\subsection{Data extraction}\label{data-extraction}}
+
+\hypertarget{risk-of-bias-assessment}{%
+\subsection{Risk of bias assessment}\label{risk-of-bias-assessment}}
+
+Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
+Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{5}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{6}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}
+
+At present, no risk of bias assessment tool for Mendelian randomisation studies is available. Bias in thesee studies was assessed with the help of an expert panel {[}TBC{]}
+
+\hypertarget{patient-and-public-involvement}{%
+\subsection{Patient and public involvement}\label{patient-and-public-involvement}}
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
+
+\includegraphics{_main_files/figure-latex/prisma-flow-1.pdf}
+
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+\hypertarget{conclusion}{%
+\section{Conclusion}\label{conclusion}}
+
+\hypertarget{annotated-bibliography}{%
+\chapter{Annotated Bibliography}\label{annotated-bibliography}}
 
@@
 \hypertarget{refs}{}
-\leavevmode\hypertarget{ref-Darwin1859}{}%
-1. Darwin, C. \emph{On the Origin of Species by Means of Natural Selection or the Preservation of Favoured Races in the Struggle for Life}. (John Murray, 1859).
+\leavevmode\hypertarget{ref-bramer2016}{}%
+1.
+Bramer, W.
+M., Giustini, D., de Jonge, G.
+B., Holland, L.
+\& Bekhuis, T.
+De-duplication of database search results for systematic reviews in EndNote.
+\emph{Journal of the Medical Library Association : JMLA} \textbf{104}, 240--243 (2016).
+
+\leavevmode\hypertarget{ref-ouzzani2016}{}%
+2. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).
+
+\leavevmode\hypertarget{ref-zotero-766}{}%
+3. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.
+
+\leavevmode\hypertarget{ref-petersen1999}{}%
+4. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).
+
+\leavevmode\hypertarget{ref-sterne2019}{}%
+5. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).
+
+\leavevmode\hypertarget{ref-sterne2016}{}%
+6. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).
 

### 2020-02-07 index.Rmd
Major updates

@@
     download: ["pdf"]
+    split_bib: false
     config:
@@
           <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
+
       sharing:

### 2020-02-07 scripts/Chp2-Systematic-Review.R

@@ -1,0 +1,17 @@
+# ---- prisma-flow
+
+PRISMAstatement::prisma(
+  found = 16109,
+  found_other = 16003,
+  no_dupes = 16005,
+  screened = 16000,
+  screen_exclusions = 200,
+  full_text = 14000,
+  full_text_exclusions = 13500,
+  qualitative = 50,
+  quantitative = 2,
+  labels = NULL,
+  extra_dupes_box = FALSE,
+  dpi = 72,
+  font_size = 10
+)

### 2020-02-07 02-Chp2-Systematic-Review.Rmd
Updates

@@
 ```
-(ref:darwin-quote) --- Charles Darwin [@chang2012a]
+(ref:darwin-quote) --- Charles Darwin [@chang2012]
 

### 2020-02-07 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Updates

@@
 
-This is a test of the bibliography\textsuperscript{{\textbf{???}}}
+This is a test of the bibliography\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}
 
@@
 Hold
-\qauthor{--- Charles Darwin\textsuperscript{{\textbf{???}}}}\end{savequote}
+\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}
 
@@
 
-Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{1}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{2}}
+Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{2}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{3}}
 Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
@@
 Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{3}}
+A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{4}}
 
@@
 Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{4}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.
+For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{5}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.
 
@@
 Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{5}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{6}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}
+Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{6}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{7}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}
 
@@
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-chang2012}{}%
+1.
+Chang, C.-C.
+H., Zhao, Y., Lee, C.-W.
+\& Ganguli, M.
+Smoking, death, and Alzheimer's disease: A case of competing risks.
+\emph{Alzheimer Disease and Associated Disorders} \textbf{26}, 300--306 (2012).
+
 \leavevmode\hypertarget{ref-bramer2016}{}%
-1.
+2.
 Bramer, W.
@@
 \leavevmode\hypertarget{ref-ouzzani2016}{}%
-2. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).
+3. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).
 
 \leavevmode\hypertarget{ref-zotero-766}{}%
-3. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.
+4. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.
 
 \leavevmode\hypertarget{ref-petersen1999}{}%
-4. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).
+5. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).
 
 \leavevmode\hypertarget{ref-sterne2019}{}%
-5. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).
+6. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).
 
 \leavevmode\hypertarget{ref-sterne2016}{}%
-6. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).
+7. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).
 

### 2020-02-07 _00-introduction.Rmd
Add word count

@@
 
-# Introduction {-}
+# Covering material {-}
 
@@
 
-Welcome to my thesis!
+```{r word-count, echo=FALSE, warning=FALSE}
+words <-
+  wordcountaddin::word_count("01-Chp1-Introduction.Rmd") +
+  wordcountaddin::word_count("02-Chp2-Systematic-Review.Rmd")
+
+date <- as.character(format(Sys.time(),"%d%m%Y"))
+
+tmpWords <- data.frame(words = words, date = date)
+
+masterWords <- read.csv("words/words.csv", header = TRUE)
+
+masterWords <- rbind(masterWords,tmpWords)
+
+write.csv(file = "words/words.csv", x = masterWords, col.names = FALSE, row.names = FALSE)
+```
+
+Word count: `r words`

### 2020-02-07 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Add word count

@@
 % all your chapters and appendices will appear here
-\hypertarget{introduction}{%
-\chapter*{Introduction}\label{introduction}}
-\addcontentsline{toc}{chapter}{Introduction}
+\hypertarget{covering-material}{%
+\chapter*{Covering material}\label{covering-material}}
+\addcontentsline{toc}{chapter}{Covering material}
 
@@
 
-Welcome to my thesis!
+\begin{verbatim}
+## For information on available language packages for 'koRpus', run
+## 
+##   available.koRpus.lang()
+## 
+## and see ?install.koRpus.lang()
+\end{verbatim}
+
+Word count: 1163
 
@@
 
-The following tools were used to perform risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2
+The following tools were used to perform the risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2
 

### 2020-02-12 03-Ch3-CPRD-Analysis.Rmd
Updates

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:chapter2-quote)'}
A straight line may be the shortest distance between two points, but it is by no means the most interesting
```
(ref:chapter2-quote) --- Third Doctor

# Chapter 3: Primary analysis of lipid regulating agents and dementia
\minitoc <!-- this will include a mini table of contents-->

## Additional ideas

One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(chapter-2-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.

## Aims

## Methods

### Estimation methods

Potential biases included time varying confounding, selection bias due to censoring on death and 
We performed a Cox

### Estimating the value of the time-varying confounders

Mean time from index event to first prescription of statins was 2.4 years. This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.

Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change. This is problematic when the descision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the inital treatment decision, as is likely to be the case for a range of covariates included in the model. For example:

_No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_

In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_.

In practice, this means that the value of the prognostic factor should be regularly captured

However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.

This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).

i.e.
Timepoint 12345678
CVD       00001111
Treatment 00000111

Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point.

Note: this will be harder for things that are not dichotmous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.

### The effect of total cholesterol or LDL-cholesterol on LRA prescription

It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the liklihood of someone being prescribed a statin.

### 2020-02-12 _00-introduction.Rmd
Updates

--- 2020-02-06 _00-introduction.Rmd
@@
 
-Welcome to my thesis!
+```{r word-count, echo=FALSE, warning=FALSE, message=FALSE}
+library(dplyr)
+
+words01 <- as.numeric(wordcountaddin::word_count("01-Chp1-Introduction.Rmd"))
+words02 <- as.numeric(wordcountaddin::word_count("02-Chp2-Systematic-Review.Rmd"))
+words03 <- as.numeric(wordcountaddin::word_count("03-Ch3-CPRD-Analysis.Rmd"))
+
+words <- words01 + words02 + words03
+
+date <- format(Sys.time(),"%Y%m%d")
+
+tmpWords <- data.frame(words = words,
+                       date = date,
+                       days = as.numeric(0),
+                       words_per_day = as.numeric(0),
+                       target = as.numeric(0), stringsAsFactors = FALSE)
+
+masterWords <- read.csv("words/words.csv", header = TRUE)
+
+#masterWords$date <- as.Date(as.character(masterWords$date), "%Y%m%d")
+
+tmpWords$days <- as.numeric(as.Date(tmpWords$date[length(tmpWords$date)],"%Y%m%d")+1 - as.Date(as.character(masterWords$date[1]),"%Y%m%d"))
+
+tmpWords$words_per_day <- as.numeric(masterWords[length(masterWords$words),2])/tmpWords$days
+
+tmpWords$target <- tmpWords[length(tmpWords$days),3]*200
+
+masterWords <- rbind(masterWords,tmpWords)
+
+masterWords <- masterWords %>%
+  group_by(date) %>%
+  filter(words == max(words))
+
+write.csv(file = "words/words.csv", x = masterWords, col.names = FALSE, row.names = FALSE)
+
+change <- masterWords$words[length(masterWords$words)] - masterWords$words[length(masterWords$words)-1]
+
+```
+
+* Word count: `r masterWords$words[length(masterWords$words)]` words
+
+* Change since last day: `r change` words
+
+* Days: `r masterWords$days[length(masterWords$days)]` days
+
+* Words per day: `r masterWords$words_per_day[length(masterWords$words_per_day)]`
+
+```{r, echo = FALSE, warnings = FALSE, message=FALSE}
+library(ggplot2)
+
+masterWords <- read.csv("words/words.csv", header = TRUE)
+
+masterWords$date <- as.numeric(masterWords$date)
+
+ggplot(data = masterWords, aes(x=date))+
+  geom_point(aes(y=words)) +
+  geom_line(aes(y=words)) +
+  geom_point(aes(y=target), colour = "red") +
+  geom_line(aes(y=target), colour = "red")
+
+```

### 2020-02-12 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Updates

@@
 
-\begin{verbatim}
-## For information on available language packages for 'koRpus', run
-## 
-##   available.koRpus.lang()
-## 
-## and see ?install.koRpus.lang()
-\end{verbatim}
+\begin{itemize}
+\item
+  Word count: 1751 words
+\item
+  Change since last day: 0 words
+\item
+  Days: 5 days
+\item
+  Words per day: 350.2
+\end{itemize}
 
-Word count: 1163
+\includegraphics{_main_files/figure-latex/unnamed-chunk-4-1.pdf}
 
@@
 
-This is a test of the bibliography\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}
+\hypertarget{aims-and-objectives-of-the-thesis}{%
+\section{Aims and Objectives of the thesis}\label{aims-and-objectives-of-the-thesis}}
 
-The following tools were used to perform the risk of bias assessments: ROB-2, ROBINS-I and QUADAS-2
+\hypertarget{aim}{%
+\subsection{Aim}\label{aim}}
+
+\hypertarget{objective}{%
+\subsection{Objective}\label{objective}}
+
+\hypertarget{chapter-overview}{%
+\section{Chapter Overview}\label{chapter-overview}}
+
+\begin{itemize}
+\tightlist
+\item
+  Chapter \ref{chapter-2-heading}
+\item
+  Chapter \ref{chapter-3-heading}
+\item
+  Chapter \ref{chapter-3-heading}
+\end{itemize}
+
+\hypertarget{thesis-output}{%
+\section{Thesis Output}\label{thesis-output}}
+
+\hypertarget{peer-reviewed-papers}{%
+\subsection{Peer reviewed papers}\label{peer-reviewed-papers}}
+
+\hypertarget{papers-under-review}{%
+\subsection{Papers under review}\label{papers-under-review}}
+
+\hypertarget{software}{%
+\subsection{Software}\label{software}}
+
+\hypertarget{talks}{%
+\subsection{Talks}\label{talks}}
+
+\hypertarget{summary}{%
+\section{Summary}\label{summary}}
+
+\begin{itemize}
+\item
+\item
+\item
+\end{itemize}
 
@@
 
-\hypertarget{chapter-2-headings}{%
-\chapter{Chapter 2: Systematic Review}\label{chapter-2-headings}}
+\hypertarget{chapter-2-heading}{%
+\chapter{Chapter 2: Systematic Review}\label{chapter-2-heading}}
 
 \minitoc
+
+\hypertarget{additional-ideas}{%
+\section{Additional ideas}\label{additional-ideas}}
+
+\begin{itemize}
+\tightlist
+\item
+  Evidence map - show the distribution of the different studies population across the world.
+\item
+  Living systematic review approach - update weekly based on medRxiv
+\end{itemize}
 
@@
 
+\begin{savequote}
+A straight line may be the shortest distance between two points, but it
+is by no means the most interesting
+\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}
+
+\hypertarget{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}{%
+\chapter{Chapter 3: Analysis of the relationship between lipid regulating agent use and dementia outcomes in the Clinical Practice Research Datalink}\label{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}}
+
+\minitoc
+
+\hypertarget{additional-ideas-1}{%
+\section{Additional ideas}\label{additional-ideas-1}}
+
+One of the problems I'll point out with the trials in the systematic review chapter (Chapter \ref{chapter-2-heading}) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+
+\hypertarget{aims-1}{%
+\section{Aims}\label{aims-1}}
+
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
+
+\hypertarget{estimation-methods}{%
+\subsection{Estimation methods}\label{estimation-methods}}
+
+Potential biases included time varying confounding, selection bias due to censoring on death and
+We performed a Cox
+
+\hypertarget{estimating-the-value-of-the-time-varying-confounders}{%
+\subsection{Estimating the value of the time-varying confounders}\label{estimating-the-value-of-the-time-varying-confounders}}
+
+Mean time from index event to first prescription of statins was 2.4 years.
+This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
+
+Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
+This is problematic when the descision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the inital treatment decision, as is likely to be the case for a range of covariates included in the model.
+For example:
+
+\emph{No CVD (t=0) -\textgreater{} No LRA (t=0) -\textgreater{} CVD (t=1) -\textgreater{} LRA (t=1) -\textgreater{} Dementia (t=2)}
+
+In this case, the decision to move to LRA use is influenced by CVD status at \emph{Time 1}, which will not be captured by adjusting only for CVD status at \emph{Time 0}.
+
+In practice, this means that the value of the prognostic factor should be regularly captured
+
+However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
+
+This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
+
+i.e.
+Timepoint 12345678
+CVD 00001111
+Treatment 00000111
+
+Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point.
+
+Note: this will be harder for things that are not dichotmous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
+
+\hypertarget{the-effect-of-total-cholesterol-or-ldl-cholesterol-on-lra-prescription}{%
+\subsection{The effect of total cholesterol or LDL-cholesterol on LRA prescription}\label{the-effect-of-total-cholesterol-or-ldl-cholesterol-on-lra-prescription}}
+
+It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the liklihood of someone being prescribed a statin.
+
 \hypertarget{annotated-bibliography}{%

### 2020-02-12 index.Rmd
Updates

--- 2020-02-06 index.Rmd
@@
     download: ["pdf"]
+    output_dir: "docs/5abd0cd3e96bf9459398f146495c15129ee56682"
+    split_bib: false
     config:

### 2020-02-19 01-Chp1-Introduction.Rmd
Major updates
Updates
Add word count
Major changes

@@
 
-This is a test of the bibliography (@Darwin1859)
+## Aims and Objectives of the thesis
+
+### Aim
+
+### Objective
+
+## Chapter Overview
+
+* Chapter \@ref(sys-rev-heading)
+* Chapter \@ref(chapter-3-heading)
+* Chapter \@ref(chapter-3-heading)
+
+## Thesis Output
+
+### Peer reviewed papers
+
+### Papers under review
+
+### Software
+
+* `robvis`: An R package and associted `shiny` web application that allows users to easily visualise the results of risk of bias graphs.
+
+* `medrxvir`: An R package
+
+### Talks
+
+## Summary
+
+*
+* 
+*

### 2020-02-19 012-Chp-Systematic-Review-Tools.Rmd
Major changes

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
Why are open source statistical programming  
languages the best?

Because they R.
```
(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# Creating new systematic review tools in R
\minitoc <!-- this will include a mini table of contents-->

```{r setup, include=FALSE}
library(medrxivr)
knitr::opts_chunk$set(echo = TRUE)
```

## Background

R is a pro
Below I introduce two R packages that I created to faciliate some aspects of the systematic review process.

## `robvis`

### Introduction

### Installation

A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:

```{r, eval = FALSE}
install.packages("robvis")
```

As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version. The most recent development version can be install from GitHub using:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/robvis")
```

### Reception and Future Plans

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )

robvis_downloads <- plyr::round_any(sum(robvisstats$count),100, f = floor)

date <- format(Sys.Date(),"%d %B, %Y")

```

As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times. It ha

It has also been intergrated with a suite of new online platforms for performing risk of bias assessments online.

In this thesis, `robvis` is used to present the results of the risk of bias assessments conducted as part of the systematic review and

While `robvis` currently provides a stable, future development work is planned.

## `medrxivr`

### Introduction

Searching pre-print repositories is becoming an increasingly important part of a systematic review. However, while several of the main repositories (e.g. arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse, this is not true for medRxiv, an offspring of bioRxiv which hosts preprints in the medical, clinical, and related health sciences.

At present, medRxiv allows only simple search queries, as opposed to the often complex boolean logic that information specialists use to query other major databases. Additionally, record details must be downloaded individually, rather than in batches, making the export of relevant records for title and abstract screening a time consuming task.

Im order to facilitate the searching

### Installation

To install `medrxivr` from CRAN:

```{r, eval = FALSE}
# Currently doesn't work as not on CRAN

install.packages("medrxivr")
```

To install the development version from GitHub:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/medrxivr")
```

### Methods

The `medrxivr` project is split into two parts:

* A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
* A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.

The webscraper is a straightforward R script built in R using `rvest`[cite] and a range of text processing packages[cite]. To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:

```{r,eval=FALSE}
# Include and highly comment code.

```

Using Windows Task Scheduler, the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file. Following quality control checks, the updated dataset is automatically uploaded to a cloud server, and immediately becomes available to the main `medrxivr` package functions.

The functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:

* `mx_search()` [main]: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.

```{r, eval = FALSE}
topic1  <- c("dementia","vascular","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins","cholesterol")     # Combined with OR

myquery <- list(topic1, topic2)                    # Combined with AND

results <- mx_search(myquery)
```

* `mx_download()` [main]: Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.

```{r, eval = FALSE}
mx_download(results,        # Object returned by mx_search
            "pdf/")         # Directory to save PDFs to 
```

* `mx_crosscheck()` [helper]: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.

```{r}
mx_crosscheck()
```

### Reception and Future Plans

`medrxivr`

Published paper,

## Dicussion

## Summary

*In this Chapter, I have introduced two new tools for facilitating evidence syntheses in R: `robvis` and `medrxivr`

* I have

* The impact of these packages to date, and a roadmap for their future development, has been discussed.

### 2020-02-19 03-Ch3-CPRD-Analysis.Rmd
Major changes

@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:chapter2-quote)'}
-A straight line may be the shortest distance between two points, but it is by no means the most interesting
+"When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin"
 ```
-(ref:chapter2-quote) --- Third Doctor
+(ref:chapter2-quote) --- Harold F. Dorn, 1953 [@dorn1953]
 
@@
 
-One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(chapter-2-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
 
@@
 It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the liklihood of someone being prescribed a statin.
+
+However, this is not the case.
+Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
+Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent.
+However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months.
+[Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
+Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.]
+
+As expected, in a confirmatory analysis using lipid levels, there was no association between <span color="red">the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required.
+*</span>

### 2020-02-19 _00-introduction.Rmd
Major changes

@@
 
-# Covering material {-}
+# Preface {-}
 
@@
 words03 <- as.numeric(wordcountaddin::word_count("03-Ch3-CPRD-Analysis.Rmd"))
+words04 <- as.numeric(wordcountaddin::word_count("011-Chp2-Background.Rmd"))
+words05 <- as.numeric(wordcountaddin::word_count("012-Chp-Systematic-Review-Tools.Rmd"))
+words06 <- as.numeric(wordcountaddin::word_count("20-Discussion.Rmd"))
 
-words <- words01 + words02 + words03
+words <- words01 + words02 + words03 + words04 + words05 + words06
 

### 2020-02-19 docs/5abd0cd3e96bf9459398f146495c15129ee56682/_main.tex
Major changes

@@
 % UL 1 Dec 2018, fix to include code in shaded environments
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+%UL 2 Dec 2018 add a bit of white space before and after code blocks
+\renewenvironment{Shaded}
+{
+  \vspace{4pt}%
+  \begin{snugshade}%
+}{%
+  \end{snugshade}%
+  \vspace{4pt}%
+}
 
@@
 % all your chapters and appendices will appear here
-\hypertarget{covering-material}{%
-\chapter*{Covering material}\label{covering-material}}
-\addcontentsline{toc}{chapter}{Covering material}
+\hypertarget{preface}{%
+\chapter*{Preface}\label{preface}}
+\addcontentsline{toc}{chapter}{Preface}
 
@@
 \item
-  Word count: 1751 words
+  Word count: 2544 words
 \item
@@
 \item
-  Days: 5 days
+  Days: 13 days
 \item
-  Words per day: 350.2
+  Words per day: 195.6923077
 \end{itemize}
 
-\includegraphics{_main_files/figure-latex/unnamed-chunk-4-1.pdf}
+\includegraphics{_main_files/figure-latex/unnamed-chunk-14-1.pdf}
 
@@
 \item
-  Chapter \ref{chapter-2-heading}
+  Chapter \ref{sys-rev-heading}
 \item
@@
 
+\begin{itemize}
+\item
+  \texttt{robvis}: An R package and associted \texttt{shiny} web application that allows users to easily visualise the results of risk of bias graphs.
+\item
+  \texttt{medrxvir}: An R package
+\end{itemize}
+
 \hypertarget{talks}{%
@@
 
+\hypertarget{background}{%
+\chapter{Background}\label{background}}
+
+\hypertarget{dementia}{%
+\section{Dementia}\label{dementia}}
+
+\hypertarget{history}{%
+\subsection{History}\label{history}}
+
+\hypertarget{economic-impact}{%
+\subsection{Economic impact}\label{economic-impact}}
+
+\hypertarget{risk-factors}{%
+\subsection{Risk factors}\label{risk-factors}}
+
+\hypertarget{treatments}{%
+\subsection{Treatments}\label{treatments}}
+
+\hypertarget{preventative-measures}{%
+\subsection{Preventative measures}\label{preventative-measures}}
+
+\hypertarget{serum-lipids}{%
+\section{Serum lipids}\label{serum-lipids}}
+
+\hypertarget{range-of-lipids}{%
+\subsection{Range of lipids}\label{range-of-lipids}}
+
+\hypertarget{hdl-c}{%
+\subsection{HDL-c}\label{hdl-c}}
+
+\hypertarget{ldl-c}{%
+\subsection{LDL-c}\label{ldl-c}}
+
+\hypertarget{triglycerides}{%
+\subsection{Triglycerides}\label{triglycerides}}
+
+\hypertarget{total-cholesterol}{%
+\subsection{Total cholesterol}\label{total-cholesterol}}
+
+\hypertarget{summary-1}{%
+\section{Summary}\label{summary-1}}
+
+\begin{savequote}
+Why are open source statistical programming\\
+languages the best?
+
+Because they R.
+\qauthor{--- Bealy, 2013\textsuperscript{\protect\hyperlink{ref-bealy2013}{1}}}\end{savequote}
+
+\hypertarget{creating-new-systematic-review-tools-in-r}{%
+\chapter{Creating new systematic review tools in R}\label{creating-new-systematic-review-tools-in-r}}
+
+\minitoc
+
+\hypertarget{background-1}{%
+\section{Background}\label{background-1}}
+
+R is a pro
+Below I introduce two R packages that I created to faciliate some aspects of the systematic review process.
+
+\hypertarget{robvis}{%
+\section{\texorpdfstring{\texttt{robvis}}{robvis}}\label{robvis}}
+
+\hypertarget{introduction}{%
+\subsection{Introduction}\label{introduction}}
+
+\hypertarget{installation}{%
+\subsection{Installation}\label{installation}}
+
+A stable version of \texttt{robvis} is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{install.packages}\NormalTok{(}\StringTok{"robvis"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+As development of \texttt{robvis} is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version.
+The most recent development version can be install from GitHub using:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"mcguinlu/robvis"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{reception-and-future-plans}{%
+\subsection{Reception and Future Plans}\label{reception-and-future-plans}}
+
+As of 19 February, 2020, \texttt{robvis} has been downloaded more than 1200 times. It has been accepted
+
+It has also been intergrated with a suite of new online platforms for performing risk of bias assessments online.
+
+In this thesis, \texttt{robvis} is used to present the results of the risk of bias assessments conducted as part of the systematic review and
+
+While \texttt{robvis} currently provides a stable, future development work is planned.
+
+\hypertarget{medrxivr}{%
+\section{\texorpdfstring{\texttt{medrxivr}}{medrxivr}}\label{medrxivr}}
+
+\hypertarget{introduction-1}{%
+\subsection{Introduction}\label{introduction-1}}
+
+Searching pre-print repositories is becoming an increasingly important part of a systematic review.
+However, while several of the main repositories (e.g.~arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse, this is not true for medRxiv, an offspring of bioRxiv which hosts preprints in the medical, clinical, and related health sciences.
+
+At present, medRxiv allows only simple search queries, as opposed to the often complex boolean logic that information specialists use to query other major databases.
+Additionally, record details must be downloaded individually, rather than in batches, making the export of relevant records for title and abstract screening a time consuming task.
+
+Im order to facilitate the searching
+
+\hypertarget{installation-1}{%
+\subsection{Installation}\label{installation-1}}
+
+To install \texttt{medrxivr} from CRAN:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Currently doesn't work as not on CRAN}
+
+\KeywordTok{install.packages}\NormalTok{(}\StringTok{"medrxivr"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+To install the development version from GitHub:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{devtools}\OperatorTok{::}\KeywordTok{install_github}\NormalTok{(}\StringTok{"mcguinlu/medrxivr"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{methods}{%
+\subsection{Methods}\label{methods}}
+
+The \texttt{medrxivr} project is split into two parts:
+
+\begin{itemize}
+\tightlist
+\item
+  A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
+\item
+  A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.
+\end{itemize}
+
+The webscraper is a straightforward R script built in R using \texttt{rvest}{[}cite{]} and a range of text processing packages{[}cite{]}.
+To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# Include and highly comment code. }
+\end{Highlighting}
+\end{Shaded}
+
+Using Windows Task Scheduler, the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file.
+Following quality control checks, the updated dataset is automatically uploaded to a cloud server, and immediately becomes available to the main \texttt{medrxivr} package functions.
+
+The functions in the \texttt{medrxivr} package then facilitate users in working with this dataset. There are two main functions and a helper function:
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{mx\_search()} {[}main{]}: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.
+\end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{topic1  <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"dementia"}\NormalTok{,}\StringTok{"vascular"}\NormalTok{,}\StringTok{"alzheimer's"}\NormalTok{)  }\CommentTok{# Combined with OR}
+\NormalTok{topic2  <-}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"lipids"}\NormalTok{,}\StringTok{"statins"}\NormalTok{,}\StringTok{"cholesterol"}\NormalTok{)     }\CommentTok{# Combined with OR}
+
+\NormalTok{myquery <-}\StringTok{ }\KeywordTok{list}\NormalTok{(topic1, topic2)                    }\CommentTok{# Combined with AND}
+
+\NormalTok{results <-}\StringTok{ }\KeywordTok{mx_search}\NormalTok{(myquery)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{mx\_download()} {[}main{]}: Takes the output from \texttt{mx\_search()} and retrieves the full text PDF for each record, saving it to a folder specified by the user.
+\end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{mx_download}\NormalTok{(results,        }\CommentTok{# Object returned by mx_search}
+            \StringTok{"pdf/"}\NormalTok{)         }\CommentTok{# Directory to save PDFs to }
+\end{Highlighting}
+\end{Shaded}
+
+\begin{itemize}
+\tightlist
+\item
+  \texttt{mx\_crosscheck()} {[}helper{]}: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.
+\end{itemize}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{mx_crosscheck}\NormalTok{()}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Using medRxiv DataDump - 2020-02-19 10:38
+\end{verbatim}
+
+\begin{verbatim}
+## 2 new record(s) added to medRxiv since last data dump
+\end{verbatim}
+
+\hypertarget{reception-and-future-plans-1}{%
+\subsection{Reception and Future Plans}\label{reception-and-future-plans-1}}
+
+\texttt{medrxivr}
+
+Published paper,
+
+\hypertarget{dicussion}{%
+\section{Dicussion}\label{dicussion}}
+
+\hypertarget{summary-2}{%
+\section{Summary}\label{summary-2}}
+
+*In this Chapter, I have introduced two new tools for facilitating evidence syntheses in R: \texttt{robvis} and \texttt{medrxivr}
+
+\begin{itemize}
+\item
+  I have
+\item
+  The impact of these packages to date, and a roadmap for their future development, has been discussed.
+\end{itemize}
+
 \begin{savequote}
 Hold
-\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}
+\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{2}}}\end{savequote}
 
-\hypertarget{chapter-2-heading}{%
-\chapter{Chapter 2: Systematic Review}\label{chapter-2-heading}}
+\hypertarget{sys-rev-heading}{%
+\chapter{Chapter 2: Systematic Review}\label{sys-rev-heading}}
 
@@
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+\hypertarget{methods-1}{%
+\section{Methods}\label{methods-1}}
 
@@
 
-Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{2}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{3}}
+Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.~(2016).\textsuperscript{\protect\hyperlink{ref-bramer2016}{3}} Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.\textsuperscript{\protect\hyperlink{ref-ouzzani2016}{4}}
 Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
@@
 Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{4}}
+A PRIMSA flow diagram will be produced to document how records moved through the review.\textsuperscript{\protect\hyperlink{ref-zotero-766}{5}}
 
@@
 Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{5}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.
+For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.~an adapted version of the Petersen criteria\textsuperscript{\protect\hyperlink{ref-petersen1999}{6}}) and create ordinal groups of patients (e.g.~no dementia or dementia/MCI/dementia) based on this definition.
 
@@
 Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{6}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{7}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}
+Randomised controlled trials were assessed using the RoB2 tool,\textsuperscript{\protect\hyperlink{ref-sterne2019}{7}}, non-randomised studies of interventions were assessed using the ROBINS-I tool,\textsuperscript{\protect\hyperlink{ref-sterne2016}{8}} and non-randomised studies of exposures were assessed using the ROBINS-E tool.{[}TBC{]}
 
@@
 \begin{savequote}
-A straight line may be the shortest distance between two points, but it
-is by no means the most interesting
-\qauthor{--- Charles Darwin\textsuperscript{\protect\hyperlink{ref-chang2012}{1}}}\end{savequote}
+``When dealing with human beings controlled experiments frequently prove
+to be impracticable, so for a scientific basis for our assumptions we
+turn to past history to reconstruct the suspected causal chain of events
+- and then our statistical troubles may begin''
+\qauthor{--- Harold F. Dorn, 1953\textsuperscript{\protect\hyperlink{ref-dorn1953}{9}}}\end{savequote}
 
-\hypertarget{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}{%
-\chapter{Chapter 3: Analysis of the relationship between lipid regulating agent use and dementia outcomes in the Clinical Practice Research Datalink}\label{chapter-3-analysis-of-the-relationship-between-lipid-regulating-agent-use-and-dementia-outcomes-in-the-clinical-practice-research-datalink}}
+\hypertarget{chapter-3-primary-analysis-of-lipid-regulating-agents-and-dementia}{%
+\chapter{Chapter 3: Primary analysis of lipid regulating agents and dementia}\label{chapter-3-primary-analysis-of-lipid-regulating-agents-and-dementia}}
 
@@
 
-One of the problems I'll point out with the trials in the systematic review chapter (Chapter \ref{chapter-2-heading}) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+One of the problems I'll point out with the trials in the systematic review chapter (Chapter \ref{sys-rev-heading}) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
 
@@
 
-\hypertarget{methods-1}{%
-\section{Methods}\label{methods-1}}
+\hypertarget{methods-2}{%
+\section{Methods}\label{methods-2}}
 
@@
 
-\emph{No CVD (t=0) -\textgreater{} No LRA (t=0) -\textgreater{} CVD (t=1) -\textgreater{} LRA (t=1) -\textgreater{} Dementia (t=2)}
+\begin{verbatim}
+_No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_
+\end{verbatim}
 
@@
 
-i.e.
-Timepoint 12345678
-CVD 00001111
+i.e.\\
+Timepoint 12345678\\
+CVD 00001111\\
 Treatment 00000111
@@
 
+However, this is not the case.
+Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,\textsuperscript{\protect\hyperlink{ref-hippisley-cox2008}{10}} which estimates a patients' 10-year risk of a cardiovascular event.
+Current NICE guidelines state that those with a QRISK score of 10\% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent.
+However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months.
+{[}Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
+Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.{]}
+
+As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required.
+*
+
+\hypertarget{references}{%
+\chapter{References}\label{references}}
+
 \hypertarget{annotated-bibliography}{%
@@
 
-\hypertarget{list-of-one-thing}{%
-\chapter{List of one thing}\label{list-of-one-thing}}
+\hypertarget{by-chapter}{%
+\chapter{By Chapter}\label{by-chapter}}
 
-\hypertarget{list-of-something-else}{%
-\chapter{List of something else}\label{list-of-something-else}}
+\hypertarget{chapter-1}{%
+\section{Chapter 1}\label{chapter-1}}
+
+\hypertarget{chapter-2}{%
+\section{Chapter 2}\label{chapter-2}}
+
+\hypertarget{other-appendix}{%
+\chapter{Other Appendix}\label{other-appendix}}
 
 \hypertarget{refs}{}
+\leavevmode\hypertarget{ref-bealy2013}{}%
+1. Bealy, C. R Programming Humour. \emph{Cross Validated} (2013).
+
 \leavevmode\hypertarget{ref-chang2012}{}%
-1.
+2.
 Chang, C.-C.
@@
 \leavevmode\hypertarget{ref-bramer2016}{}%
-2.
+3.
 Bramer, W.
@@
 \leavevmode\hypertarget{ref-ouzzani2016}{}%
-3. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).
+4. Ouzzani, M., Hammady, H., Fedorowicz, Z. \& Elmagarmid, A. Rayyan-a web and mobile app for systematic reviews. \emph{Systematic Reviews} \textbf{5}, 210 (2016).
 
 \leavevmode\hypertarget{ref-zotero-766}{}%
-4. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.
+5. The PRISMA statement for reporting systematic reviews and meta-analyses of studies that evaluate healthcare interventions: Explanation and elaboration \textbar{} The BMJ.
 
 \leavevmode\hypertarget{ref-petersen1999}{}%
-5. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).
+6. Petersen, R. C. \emph{et al.} Mild cognitive impairment: Clinical characterization and outcome. \emph{Archives of Neurology} \textbf{56}, 303--308 (1999).
 
 \leavevmode\hypertarget{ref-sterne2019}{}%
-6. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).
+7. Sterne, J. A. C. \emph{et al.} RoB 2: A revised tool for assessing risk of bias in randomised trials. \emph{BMJ} \textbf{366}, (2019).
 
 \leavevmode\hypertarget{ref-sterne2016}{}%
-7. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).
+8. Sterne, J. A. \emph{et al.} ROBINS-I: A tool for assessing risk of bias in non-randomised studies of interventions. \emph{BMJ} \textbf{355}, (2016).
+
+\leavevmode\hypertarget{ref-dorn1953}{}%
+9. Dorn, H. F. Philosophy of Inferences from Retrospective Studies. \emph{American Journal of Public Health and the Nations Health} \textbf{43}, 677--683 (1953).
+
+\leavevmode\hypertarget{ref-hippisley-cox2008}{}%
+10. Hippisley-Cox, J. \emph{et al.} Predicting cardiovascular risk in England and Wales: Prospective derivation and validation of QRISK2. \emph{BMJ} \textbf{336}, 1475--1482 (2008).
 

### 2020-11-25 01-Chp1-Introduction.Rmd
This time for sure

--- 2020-02-06 01-Chp1-Introduction.Rmd
@@
 
-This is a test of the bibliography (@Darwin1859)
+## Aims and Objectives of the thesis
+
+### Aim
+
+```{r}
+f <- flextable::flextable(robvis::data_rob2)
+
+f <- flextable::autofit(f)
+
+f
+```
+
+### Objective
+
+## Chapter Overview
+
+* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels.
+This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
+* __Chapter \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`.
+The motivation for, development and impact of, and future plans for these tools are outlined.
+* __Chapter \@ref(sys-rev-heading)__ This Chapter describes the
+* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regaulting agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+* __Chapter \@ref():__ This Chapter seeks
+
+## Thesis Output
+
+The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools, and . . .
+
+### Peer reviewed papers
+
+__Include other papers I have been involved in?__
+
+### Papers under review
+
+* McGuinness et al.
+
+### Software
+
+* `robvis`: An R package and associated `shiny` web application that allows users to easily visualise the results of risk of bias graphs.
+
+* `medrxvir`: An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv^[https://www.medrxiv.org/] preprint repository.
+
+### Talks
+
+* Talk at Cochrane on medrxivr
+* Webinar to Evidence Synthesis Ireland on Risk of Bias test
+
+## Summary
+
+*
+* 
+*

### 2020-11-25 02-Chp2-Background.Rmd
This time for sure

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

# Background {#background-heading}

## Dementia

### Definition and Subtypes
Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory. The most common causes of dementia are Alzheimer’s disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively. The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia) or by progression of other neurological diseases (e.g. Parkinson’s disease).

###	Diagnosis
Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition. Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g. the Mini-Mental State Examination), to clinical tests (e.g. Magnetic Resonance Imaging (MRI) scans).

###	Public Health Importance
Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,6 an ageing population looks set to create a dementia epidemic, particularly in Westernised countries. In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.

###	Challenges in the study of dementia using traditional study designs

Speak to the

Historically, studies on dementia have faced a range of challenges. As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect. Therefore, the statistical power need to detect these associations will often require sample sizes that are unfeasible using primary data collection. 
This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up. Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g. the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10

Fortunately, these limitations may potentially be addressed through the use of routinely collected health data, and the electronic health record databases in which they are stored.

Include CIND definition here

And MCI

And different scales

### History

> Two major clinical trials are often cited as providing
evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER)5
and the Medical Research
Council/British Heart Foundation Heart Protection Study27
; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate. Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript. In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences. In the MRC/BHF HPS trial,27
similar percentages ofparticipants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period. The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
*Taken from Cramer 2008 - included in review*

### Economic impact

### Risk factors

### Treatments

### Preventative measures

## Serum lipids

### Range of lipids

### HDL-c

### LDL-c

### Triglycerides

### Total cholesterol

## Serum lipid interventions

### Statins

#### Lipophilic

#### Hydrophilic

## Summary

### 2020-11-25 03-Chp2-Systematic-Review.Rmd
This time for sure

--- 2020-02-07 02-Chp2-Systematic-Review.Rmd
@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
+  bookdown::word_document2:  
+      toc: false
+      toc_depth: 3
+      reference_docx: word-styles-reference-01.docx
   bookdown::html_document2: default
-  bookdown::word_document2: default
   bookdown::pdf_document2:
@@
 
-# Chapter 2: Systematic Review {#chapter-2-headings}
+# Chapter 2: Systematic Review {#sys-rev-heading}
 \minitoc <!-- this will include a mini table of contents-->
 
-```{r, echo = FALSE}
-knitr::read_chunk("scripts/Chp2-Systematic-Review.R")
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+knitr::read_chunk("R/Chp2-Systematic-Review.R")
 ```
+
+## Additional ideas
+
+* Evidence map - show the distribution of the different studies population across the world.
+* Living systematic review approach - update weekly based on medRxiv
 
@@
 Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multidomain intervention” where the lipid-regulating agent is included in each arms (e.g.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multi-domain intervention” where the lipid-regulating agent is included in each arms (e.g.
 for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
@@
 
+Excluded studies performing autopsy unless it was done under accepted criteria
+Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
+
 ### Data extraction
+
+Harmonisation of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
 
@@
 
-```{r prisma-flow, echo = FALSE, warning=FALSE}
+### Screening results
+
+#### Inter-rater reliability
+
+Inter- and intra-rater reliability was asssessed for a 10% subsample of records at the title and abstract screening stage.
+Intra-rater reliability involved a sinlge reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
+
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
+[@cohen1960: [@gwet2008; @wongpakaran2013]
+
+How to interpret agreement co-efficients is widely debated.
+Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:kappa-table).
+
+Gwet's AC1 is calculated using the following:
+
+-> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
+
+```{r gwet-table, echo = FALSE}
 ```
+
+```{r agreement-table-inter, echo = FALSE}
+```
+
+```{r agreement-table-intra, echo = FALSE}
+```
+
+For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).
+
+The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]
+
+Those records which were excluded in the inital screening , but were included either by the same reviewer on their second vieweing (n=4), or by the second reviewer (n=29), were investigated.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.
+
+#### PRISMA flowchart
+
+```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review."}
+```
+
+Following deduplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened.
+
+A breakdown of records by
+
+## Included studies
+
+XXXX studies met the criteria for inclusion in the review
+
+####
 

### 2020-11-25 04-Ch3-CPRD-Analysis.Rmd
This time for sure

--- 2020-02-19 03-Ch3-CPRD-Analysis.Rmd
@@
 
-# Chapter 3: Primary analysis of lipid regulating agents and dementia
+# Primary analysis of lipid regulating agents and dementia {#cprd-analysis}
 \minitoc <!-- this will include a mini table of contents-->
@@
 One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+
+Might be able to get around this by pointing
 
@@
 Potential biases included time varying confounding, selection bias due to censoring on death and 
-We performed a Cox
+We performed a Cox  test this si to addd some words.
 

### 2020-11-25 05-Chp-Systematic-Review-Tools.Rmd
This time for sure

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: word-styles-reference-01.docx
  bookdown::html_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
Why are open source statistical programming  
languages the best?

Because they R.
```
(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# Creating new systematic review tools in R {#sys-rev-tools-heading}
\minitoc <!-- this will include a mini table of contents-->

```{r setup, include=FALSE}
source("R/doc_options.R")
```

<!----------------------------------------------------------------------------->

## Background

Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced. A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as title and abstract screening, - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.

Below I introduce two new R packages created to faciliate some aspects of the systematic review process.

<!----------------------------------------------------------------------------->
## Producing risk-of-bias visualisation with `robvis`

### Introduction

Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews. A convenient plot in many reviews is a “traffic light” plot, which tabulates the judgement for each study in each domain. For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]

Researchers can face a number of barriers in creating these plots. While some evidence synthesis platforms, such as Cochrane’s Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone. Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review. Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process. For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.

Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily. Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.

The tool is open-source and available to use free of charge. Users can download a stable version of the R package from CRAN ([https://cran.r-project.org/package=robvis](https://cran.r-project.org/package=robvis)); or access and contribute to the development version via GitHub ([https://github.com/mcguinlu/robvis](https://github.com/mcguinlu/robvis)).

### Development

Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies. Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback. This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019. The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness;@simillis2020; @tanneru2020]

### Installation

A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:

```{r, eval = FALSE}
install.packages("robvis")
```

As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version. The most recent development version can be install from GitHub using:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/robvis")
```

### Usage

`robvis` contains two main functions. The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment. The second, `rob_summary()`, creates a weighted bar plot  showing the proportion of information with each judgement for each domain in the assessment tool specified.

A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`. A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)

Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:

-> NEED TO ADD DATA HERE!

&nbsp;

``` {r, eval = FALSE}

rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  psize = 15)
```

``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", out.height = "100%", fig.align = "centre"}

plotdata <- robvis::data_rob2

tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15)

ggplot2::ggsave(
          filename = "figures/sys-rev-tools/example-rob-traffic-light-plot.png",
          plot = tfplot,
          width = 7,
          height = 8,
          dpi = 400
          )

knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png")
```

Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:

```{r, eval = FALSE}

rob_summary(data = data_rob2,
            tool = "ROB2", 
            overall = TRUE)

```

``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%", out.height = "100%"}

sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black"),
                  axis.text.y = ggplot2::element_text(size = 6)
                  )

ggplot2::ggsave(
          filename = "figures/sys-rev-tools/example-rob-summary-barplot.png",
          plot = sumplot,
          width = 8,
          height = 2.41,
          dpi = 400
          )

knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")

```

A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)

`r br`

``` {r robvisarguments, echo = FALSE, eval = TRUE}

arguments <- data.frame(stringsAsFactors=FALSE,
              argument = c("data", "tool", "colour", "overall", "weighted",
                           "psize"),
     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
           rob_summary = c("X", "X", "X", "X", "X", ""),
           Description = c(
"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
"Defines the risk of bias assessment tool used. The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported. Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
"Defines the colour scheme for the plot. The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`). Alternatively, users can specify their own colour scheme e.g. `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))

if(doc.type == "docx"){

  knitr::kable(arguments,escape = T,
             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",

             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))

}else{

  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
             align = c("l","c","c","l"),
             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
  column_spec(4,"5cm") %>%
  kable_styling(font_size = 9, 
                bootstrap_options = c("striped", "hover"),
                latex_options = c("repeat_header", "striped"))
}

```

`r br`

### Reception and Future Plans

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )

robvis_downloads <- plyr::round_any(sum(robvisstats$count),100, f = floor)

date <- format(Sys.Date(),"%B %Y")

```

As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times. It has been well recieved but the systematic review community, and has been cited frequently in the published literature. A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods. A chapter on the tool has been incorporated in to the “Doing Meta-Analysis in R” online textbook.[@mathias_harrer_2019_2551803]

While `robvis` is a stable package, a range of additional functionality could be added. At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority. For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments. However, following user-driven demand, this functionality is in development and will be available in the near future. Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis. The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.

<!----------------------------------------------------------------------------->
## Searching for health-related preprints with `medrxivr`

### Introduction

Searching pre-print repositories is becoming an increasingly important part of a systematic review. Preprints - unpublished versions of manuscripts, frequently uploaded to a repository at the same time they are submitted to a journal for peer review - represent an important source of grey literature.

However, while several of the main repositories (e.g. arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse,^[https://arxiv.org/help/api] this is not true for medRxiv, a repository launched in June 2019 to host preprints in the medical, clinical, and related health sciences.

At present, medRxiv allows only simple search queries, as opposed to the often complex Boolean logic that information specialists use to query other major databases. Additionally, record metadata (titles/abstracts/author lists) must be accessed individually, rather than in batches, meaning that downloading relevant records for title and abstract screening a time consuming task.

The `medrxivr` R package was created in order to facilitate the searching of this data source, allow

### Usage

To install `medrxivr` from CRAN:

```{r, eval = FALSE}
# Currently doesn't work as not on CRAN

install.packages("medrxivr")
```

To install the development version from GitHub:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/medrxivr")
```

### Methods

The `medrxivr` project is split into two parts:

* A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
* A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.

The webscraper is a straightforward R script built in R using `rvest` and a range of text processing packages[@wickham2019; @wickham2019a; @wickham2020]. To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:

```{r,eval=FALSE}

# Perform a search for "*" (defined by %252A), which acts as a wildcard  
# This approach will capture all records
url <- "https://www.medrxiv.org/search/%252A"

# Read the HTML from this link
page <- read_html(url)

# Extract the text (html_text()) value of the CSS node of interest, in this
# case, the "#page-title" node

results <- page %>%
  html_nodes("#page-title") %>%
  html_text()

# Remove any commas from the results (e.g. 1,500 become 1500)
results <- gsub(",","",results)

# Convert it from a character string to a numeric
results <- as.numeric(word(results))

```

Using Windows Task Scheduler,[@zotero-880] the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file. Following a quality control pipeline, which checks the completeness of the new records and ensures that all records have been captured, the updated dataset is automatically uploaded to a cloud server and immediately becomes available to the `medrxivr` package functions.

The functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:

* `mx_search()` [main]: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.

```{r, eval = FALSE}
topic1  <- c("dementia","vascular","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins","cholesterol")     # Combined with OR

myquery <- list(topic1, topic2)                    # Combined with AND

results <- mx_search(myquery)
```

* `mx_download()` [main]: Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.

```{r, eval = FALSE}
mx_download(results,        # Object returned by mx_search
            "pdf/")         # Directory to save PDFs to 
```

* `mx_crosscheck()` [helper]: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.

```{r, eval = FALSE}
mx_crosscheck()

## Using medRxiv snapshot - 2020-03-04 10:55
## No new records added to medRxiv since last snapshot.
```

### Reception and Future Plans

The tool has be well received by the community, and several use cases have been reported. The tool was primarily created to faciliate the searching performed as part of the review in Chapter \@ref(sys-rev-heading). However, several other use cases have emerged for the tool. It has been used to visalise the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], etc, etc

Following peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.

The tool has also

<!----------------------------------------------------------------------------->
## Dicussion

Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. [EXPAND]

By implementing the tools described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R.  These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `robvis`, it is likely that several other evidence synthesists have written scripts to produce similar risk-of-bias plots to those presented here - in fact, in the course of its development, I identified one other research group that has done so. This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency. Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short timeframe, expanding the potential pool of users of the package to anyone with an internet connection.

Creating a package using R has a number of particular advantages. R provides access to a range of powerful tools including the `ggplot` infrastructure as demonstrated above, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages. Recently, the `metaverse` project,[@variousauthors2020] of which `robvis` and `medrivr` are a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager. Key offerings in this suite of packages include litsearcher, which facilitates systematic search strategy development, revtools, a package for managing the review process and performing title and abstract screening, metaDigitise, a package for automatic extraction of data from figures in research papers, and metafor, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]

<!----------------------------------------------------------------------------->
## Summary

* In this Chapter, I have introduced two new tools for facilitating evidence syntheses: `robvis`, a tool for producing publication quality risk of bias assessments, and `medrxivr`, a tool for performing complex searches in the medRxiv preprint repository.

* I have outlined the motivation for developing these tools in relation to this thesis - more specifically, that they were used extensively to the conduct the comprehensive systematic review described in Chapter \@ref(sys-rev-heading)

* The impact of these packages to date, their place in the broader evidence synthesis in R ecosystem, and a roadmap for their future development has been discussed.

### 2020-11-25 97-Discussion.Rmd
This time for sure

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

# Discussion

## Summary of findings

## Strengths and Limitations

## Reproducible research

Reproducible science has been a key theme running through this thesis. An open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.

## Public involvement and engagement

Involving and engaging the public and patients has been a central theme to this thesis.

Public engagement activities included

Public involvement also steered the creation of the topic

## Future work

## Conclusions

### 2020-11-25 front-and-back-matter/_00-introduction.Rmd
This time for sure

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

# Covering material {-}

\adjustmtc 
<!-- For PDF output, we must include this LaTeX command after unnumbered headings, otherwise the numbers in the mini table of contents will be incorrect -->

```{r word-count, echo=FALSE, warning=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)

get_words <- function(){

files <- list.files(pattern = "\\.Rmd$")

files <- files[which(files != "index.Rmd")]

words_v <- c()

for (file in 1:length(files)) {
  tmp <- wordcountaddin::word_count(files[file])
  words_v <- c(words_v, tmp)
}

words <- sum(words_v)

date <- as.character(format(Sys.time(),"%Y%m%d"))
time <- as.character(format(Sys.time(),"%H%M"))

tmpWords <- data.frame(words = words,
                       date = date,
                       time = time)

masterWords <- read.csv(here::here("data","words","words.csv"),
                        header = TRUE)

masterWords <- rbind(masterWords,
                     tmpWords) %>%
  dplyr::group_by(date) %>%
  dplyr::filter(time == max(time))

return(masterWords)

}

words <- get_words()

write.csv(file = here::here("data","words","words.csv"),
          x = words,
          col.names = FALSE,
          row.names = FALSE)

start_date <- as.Date("20201124", format="%Y%m%d")

max_date <- as.Date(max(words$date), format="%Y%m%d")

date_diff <- as.numeric((max_date) - start_date)

target <- (date_diff*200)+5580

words_behind <- target - words$words[which(words$date == max(words$date))]

target_df <- data.frame(date = c(start_date,max_date),
                           words = c(5580, target))

words$date <- as.Date(words$date, format="%Y%m%d")

```

Word count: `r words$words`

Days: `r date_diff`

Words behind: `r words_behind`

```{r word-count-fig, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(mapping = aes(x=date,y=words)) +
  geom_line(data = target_df, colour = "blue") +
  geom_step(data = words, colour = "red")

```

### 2020-11-25 front-and-back-matter/_acknowledgements.Rmd
This time for sure

@@
-This is where you will normally thank your advisor, colleagues, family and friends, as well as funding and institutional support.
-In our case, we will give our praises to the people who developed the ideas and tools that allow us to push open science a little step forward by writing plain-text, transparent, and reproducible theses in R Markdown.
+Additionally, I would like to thank Sharen O’Keefe.
 
 \begin{flushright}
-Luke McGuinness \\
 Canynge Hall, Bristol \\

### 2020-11-25 front-and-back-matter/_declaration.Rmd
This time for sure

I declare that the work in this dissertation was carried out in accordance with the requirements of the University's Regulations and Code of Practice for Research Degree Programmes and that it has not been submitted for any other academic award. Except where indicated by specific reference in the text, the work is the candidate's own work. Work done in collaboration with, or with the assistance of, others, is indicated as such. Any views expressed in the dissertation are those of the author.

\begin{flushright}
SIGNED: ...................... \\
Luke McGuinness \\
Canynge Hall, Bristol \\
1 December 2021
\end{flushright}

### 2020-11-25 index.Rmd
Major changes
This time for sure

--- 2020-02-07 index.Rmd
@@
   `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
+declaration: |
+  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
 dedication: For Brendan McHugh
@@
 abstractseparate: true  # include front page w/ abstract for examination schools?
-bib-humanities: true   #set to true if you want in-text references formatted as author-year
+bib-humanities: false   #set to true if you want in-text references formatted as author-year
 doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
-draft: true # add as DRAFT mark in the footer?
+draft: false # add as DRAFT mark in the footer?
 page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
@@
     download: ["pdf"]
+    output_dir: "docs"
     split_bib: false
@@
           <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
-
       sharing:
@@
   bookdown::word_document2:
+    output_dir: "docs"
     toc: true
+    toc_depth: 2
+    reference_docx: templates/word-styles-reference-01.docx   
 link-citations: true
@@
 This will include code to create additional chunk options (e.g. for adding author references to savequotes)
-If you need to create your own additional chunk options, edit the file scripts/create_chunk_options.R
+If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
 -->
 
-```{r introduction, child = '_00-introduction.Rmd'}
+```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
 ```

### 2020-11-25 02-Chp2-Background.Rmd
Small starter fixes

@@
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-documentclass: book
----
-
 # Background {#background-heading}
+\minitoc <!-- this will include a mini table of contents-->
 

### 2020-11-25 03-Chp2-Systematic-Review.Rmd
Small starter fixes

@@
 ---
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
+#########################################
+# options for knitting a single chapter #
+#########################################
 output:
-  bookdown::word_document2:  
-      toc: false
-      toc_depth: 3
-      reference_docx: word-styles-reference-01.docx
   bookdown::html_document2: default
+  bookdown::word_document2: default
   bookdown::pdf_document2:
@@
 
-# Chapter 2: Systematic Review {#sys-rev-heading}
+# Systematic Review {#sys-rev-heading}
 \minitoc <!-- this will include a mini table of contents-->

### 2020-11-25 index.Rmd
Small starter fixes

@@
     keep_tex: true
-    citation_package: none 
+    citation_package: default 
     pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections

### 2020-11-26 01-Chp1-Introduction.Rmd
Small starter fixes
Clean-up for today - ahead!

@@
 
-```{r}
-f <- flextable::flextable(robvis::data_rob2)
-
-f <- flextable::autofit(f)
-
-f
-```
-
 ### Objective
@@
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-* __Chapter \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`.
+* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between  
+* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+* __Chapter \@ref():__ This Chapter seeks
+
+* __Appendix \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`.
 The motivation for, development and impact of, and future plans for these tools are outlined.
-* __Chapter \@ref(sys-rev-heading)__ This Chapter describes the
-* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regaulting agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
-* __Chapter \@ref():__ This Chapter seeks
 
@@
 * Talk at Cochrane on medrxivr
-* Webinar to Evidence Synthesis Ireland on Risk of Bias test
+* Presentation to the 
+* Webinar to Evidence Synthesis Ireland on Risk of Bias
 

### 2020-11-26 03-Chp2-Systematic-Review.Rmd
Clean-up for today - ahead!

@@
 
+Data will be visualized using a paired forest and risk of bias plot
+
 ### Patient and public involvement
@@
 
-Those records which were excluded in the inital screening , but were included either by the same reviewer on their second vieweing (n=4), or by the second reviewer (n=29), were investigated.
+Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.
@@
 
-```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review."}
+```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review.", out.width="100%"}
 ```
 
-Following deduplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened.
+Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility.
+387 were deemed potentially eligible and the full text records for these were requested and screened.
+[**CROSS-REF to PRISMA flow here**]
 
@@
 
-XXXX studies met the criteria for inclusion in the review
+XXXX studies met the criteria for inclusion in the review.
 
-####
+Include here:
+
+* PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
+
+* Summary of types of study
+
+* Summary of locations
+
+* Summary of diagnostic criteria used
+
+* Summary of risk of bias
+
+* Long table, horizontally. Newer version of flextable (GH) allows for PDF output
+
+## Publication bias
+
+* Check if there are protocols available for any of the published reports, and whether there were
+* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st
+
+### Triangualtion across evidence sources
+
+One key question for which multiple distinct sources of evidence were available were those looking at Laz
+
+A key limitiation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use
 
@@
 
+Of note, as part of the review, we identified serveral previous systematic reviews of this topic. However, this review is the firest to
+
 ## Conclusion

### 2020-11-26 04-Ch3-CPRD-Analysis.Rmd
Clean-up for today - ahead!

@@
 
-Might be able to get around this by pointing
+Might be able to get around this by pointing out
+
+## Things we tried
+
+- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than.
+Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
+Need total number of those starting and average time to start.
+- Positive controls. Need to be able to explain why these controls have such wildly increased results.
+- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
+- Allowing for time-varying confounders for binary covariates.
+- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+
+## Things we could try
+
+- Work through data using positive control to see if the way it is being added is what is causing the issues.
+- Examine Cramer et al. thesis and see what they did
+- Marginal structural models approach (a la J. Sterne)
 
 ## Aims
+
+In this
 
@@
 
-It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the liklihood of someone being prescribed a statin.
+It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.
 

### 2020-11-26 05-Chp-Systematic-Review-Tools.Rmd
Clean-up for today - ahead!

@@
 
-``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", out.height = "100%", fig.align = "centre"}
+``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
 
@@
 
-tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 15)
+tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)
 
-ggplot2::ggsave(
-          filename = "figures/sys-rev-tools/example-rob-traffic-light-plot.png",
-          plot = tfplot,
-          width = 7,
-          height = 8,
-          dpi = 400
-          )
+robvis::rob_save(tfplot, 
+                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")
 
-knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png")
+knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
 ```
@@
 
-``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%", out.height = "100%"}
+``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
 
-sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE) +
-   ggplot2::theme(plot.background = ggplot2::element_rect(colour = "black"),
-                  axis.text.y = ggplot2::element_text(size = 6)
-                  )
+sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)
 
-ggplot2::ggsave(
-          filename = "figures/sys-rev-tools/example-rob-summary-barplot.png",
-          plot = sumplot,
-          width = 8,
-          height = 2.41,
-          dpi = 400
-          )
+robvis::rob_save(sumplot,
+                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")
 

### 2020-11-26 front-and-back-matter/_00-introduction.Rmd
Clean-up for today - ahead!

@@
 
-files <- list.files(pattern = "\\.Rmd$")
+files <- list.files(path = here::here(), pattern = "\\.Rmd$")
 
-files <- files[which(files != "index.Rmd")]
+files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]
 
@@
 for (file in 1:length(files)) {
-  tmp <- wordcountaddin::word_count(files[file])
+  tmp <- wordcountaddin::word_count(here::here(files[file]))
   words_v <- c(words_v, tmp)
@@
 
+words_today <- words$words[which(as.Date(words$date, format="%Y%m%d")==max_date)]
+
 date_diff <- as.numeric((max_date) - start_date)
@@
 
-words_behind <- target - words$words[which(words$date == max(words$date))]
+words_behind <- words$words[which(words$date == max(words$date))] - target
 
@@
 
-Word count: `r words$words`
+Word count: `r words_today`
 
@@
 Words behind: `r words_behind`
+
+&nbsp;
+
+&nbsp;
 

### 2020-11-26 index.Rmd
Clean-up for today - ahead!

@@
 draft: false # add as DRAFT mark in the footer?
-page-layout: nobind #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
+page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
 hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print

### 2020-11-30 01-Chp1-Introduction.Rmd
End of day - ahead!
Closes #1

@@
 
+```{r load_helper_scripts, include=FALSE}
+source("R/citations.R")
+```
+
 ## Aims and Objectives of the thesis
@@
 
-### Objective
+### Objectives
+
+   * To review the published literature with respect to the effec tof lipids and lipid regulating agents  
+   * To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
+   * To meta-analyze the
 
@@
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between  
+* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid 
 * __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
@@
 
+A lot of packages were used in this project`r gen_rmd_citation()`
+
 * `robvis`: An R package and associated `shiny` web application that allows users to easily visualise the results of risk of bias graphs.

### 2020-11-30 02-Chp2-Background.Rmd
End of day - ahead!
Closes #1

@@
+---
+output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::word_document2: default
+  bookdown::html_document2: default
+documentclass: book
+---
+
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
+Science knows it doesn't know everything; otherwise, it'd stop
+```
+(ref:dara-quote) --- Dara O'Briain
+
 # Background {#background-heading}
@@
 
+A further clinical subtype that is of particular import the
+
 And MCI
@@
 ### History
-
-> Two major clinical trials are often cited as providing
-evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER)5
-and the Medical Research
-Council/British Heart Foundation Heart Protection Study27
-; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
+> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research
+Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
 Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
@@
 In the MRC/BHF HPS trial,27
-similar percentages ofparticipants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period.
+similar percentages of participants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period.
 The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
 *Taken from Cramer 2008 - included in review*
+
+There exist only two large scale randomized controlled trials - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
+Both showed no effect of
+
+Queries around how the data were collected, along
 
@@
 
+## Methods used in the thesis
+
+## Evidence synthesis
+
+### Triangulation
+
+### Individual patient data meta-analyis
+
 ## Summary

### 2020-11-30 03-Chp2-Systematic-Review.Rmd
End of day - ahead!
Closes #1

@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
 output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
   bookdown::pdf_document2:
     template: templates/brief_template.tex
+  bookdown::word_document2: default
+  bookdown::html_document2: default
 documentclass: book
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:darwin-quote)'}
-Hold
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
+Science knows it doesn't know everything; otherwise, it'd stop
 ```
-(ref:darwin-quote) --- Charles Darwin [@chang2012]
+(ref:dara-quote) --- Dara O'Briain
 
@@
 
+Based on the review of prev, no previous
+
+Literature con
+
 ## Methods
@@
 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
-We will also search BioArxiv, a preprint repository, to identify potentially relevant studies.
+We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
 Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
@@
 
-Harmonisation of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
+Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
 
@@
 
+Following screening, XXX studies were included.
+
+The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.
+
+Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]
+
+*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
+Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
+This analysis was performed by extracting the citing articles from Google Scholar on XXXX and screening them manually.
+The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*
+
+As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
+
 #### Inter-rater reliability
@@
 How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:kappa-table).
+Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
 

### 2020-11-30 05-Chp-Systematic-Review-Tools.Rmd
End of day - ahead!
Closes #1

@@
       toc_depth: 3
-      reference_docx: word-styles-reference-01.docx
+      reference_docx: templates/word-styles-reference-01.docx
   bookdown::html_document2: default
@@
 
-The `medrxivr` R package was created in order to facilitate the searching of this data source, allow
+This source of information is particularly important to this thesis, in that one of the primary types of evidence that I planned to use in the triangulation exercise (Mendelian randomization (MR)) is still developing and many MR studies that look at the clinical question that this project aims to investigate are posted as preprints on the bioRxiv, and more recently medRxiv, preprint servers.
+Being able to systematically search these records for the purpose of the systematic review described in Chapter \@(ref:sys-rev-heading) was a necessity.
+In light of the above, the `medrxivr` R package was created in order to facilitate the searching of this data source.
+
+### Development
+
+Early versions of the tool
 
@@
 ```{r, eval = FALSE}
-# Currently doesn't work as not on CRAN
-
 install.packages("medrxivr")
@@
 ```{r, eval = FALSE}
-devtools::install_github("mcguinlu/medrxivr")
+devtools::install_github("ropensci/medrxivr")
 ```
@@
 
+## Export
+
+One of the key
+
+## Data visualisation and reporter functions
+
+**TBC**
+
 ### Reception and Future Plans
@@
 The tool has be well received by the community, and several use cases have been reported.
-The tool was primarily created to faciliate the searching performed as part of the review in Chapter \@ref(sys-rev-heading).
 However, several other use cases have emerged for the tool.
@@
 
-The tool has also
+A short paper describing the tool has been published in the Journal of Open Source Software following formal peer-review of the package and associated documentation and tutorials as part of the rOpenSci onboarding process.
+The entire review discussion can be viewed online.^[https://github.com/ropensci/software-review/issues/380]
+
+The tool has been used reasonably widely, included in the systematic reviews, but also to extract data to facilitate the compare the behavior of researchers under two different journal policies by comparing the preprint paper with the published journal paper.
+
+Feedback from the systematic review community has been positive.
+
+### Package infrastructure
+
+The `medrxvir` package was written in R using RStudio, and followed development best practices, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced reviewers.
+
+The medRxiv snapshot is taken every morning using GitHub Actions, an automated system fo repetitive tasks.
+
+## Shiny app
+
+Part of the key theme of accessibility meant creating a web-application that l
 
@@
 Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. [EXPAND]
+
+As
 

### 2020-11-30 97-Discussion.Rmd
Clean-up for today - ahead!
End of day - ahead!
Closes #1

@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
 output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
+  bookdown::word_document2: 
+      reference_docx: templates/word-styles-reference-01.docx   
   bookdown::pdf_document2:
     template: templates/brief_template.tex
+  bookdown::html_document2: default
 documentclass: book
@@
 
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
+Science knows it doesn't know everything; otherwise, it'd stop
+```
+(ref:dara-quote) --- Dara O'Briain
+
 # Discussion
 
-## Summary of findings
+## Summary of findings (and implications for policy makers)
 
@@
 
+There are several strengths and limitations to the work presented in this thesis.
+One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
+
 ## Reproducible research
 
-Reproducible science has been a key theme running through this thesis.
-An open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
+In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+
+Containerisation was used to ensure that the code is reproducible, in line iwht best practices
+
+Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the)
+
+One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
+IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis).
+However, access is dependency on an ISAC application to the managing body of the CPRD.
 

### 2020-11-30 front-and-back-matter/abbreviations.tex
End of day - ahead!
Closes #1

% do not edit by hand - add to abbreviations.csv instead
% First parameter can be changed eg to "Glossary" or something.
% Second parameter is the max length of bold terms.
\begin{mclistof}{List of Abbreviations}{3.2cm}
\item[DOI] Digitial object identifier
\item[HDL] High Density Lipoprotein
\item[MR] Mendelian randomization
\end{mclistof}

### 2020-11-30 index.Rmd
End of day - ahead!
Closes #1

@@
 #######################
-bibliography: bibliography/references.bib
+bibliography: 
+  - bibliography/references.bib
+  - bibliography/pkg-refs.bib
 csl: bibliography/nature.csl
@@
 source('scripts_and_filters/create_chunk_options.R')
+source("R/citations.R")
 ```
+
 <!--

### 2020-11-30 R/Chp2-Systematic-Review.R

@@ -24,8 +24,14 @@ knitr::include_graphics("figures/sys-rev/prismaflow.png",
 
 kappa.table <- data.frame(
   stringsAsFactors = FALSE,
-  Kappa = c("0–.20", ".21–.39", ".40–.59", ".60–.79",
-            ".80–.90", "Above.90"),
+  Kappa = c(
+    "0 – 0.20",
+    "0.21 – 0.39",
+    "0.40 –.59",
+    "0.60 –0.79",
+    "0.80–0.90",
+    "> 0.90"
+  ),
   Interpretation = c(
     "None",
     "Minimal",
@@ -33,10 +39,14 @@ kappa.table <- data.frame(
     "Moderate",
     "Strong",
     "Almost perfect"
-  ))
+  )
+)
 
-knitr::kable(kappa.table,
-             caption = "Guidelines for a stricter interpretation of Cohen's kappa, presented in McHugh (2012)" )
+mal::aca_simple_table(kappa.table,
+                      autofit = FALSE,
+                      fontsize = 10) %>%
+  flextable::width(j = 1:2, 1.5) %>%
+  flextable::set_caption("Test")   
 
 # ---- agreement-table-inter
 
@@ -46,6 +56,8 @@ agreement.table.1 <- data.frame(group = rep("Second reviewer decision",3),
                                 Include = c(9,22,31), 
                                 Total = c(1253, 48,1301))
 
+
+# mal::aca_simple_table(agreement.table.1)
 
 knitr::kable(agreement.table.1, col.names = c("","","Exclude", "Include","Total"),  caption = 'Inter-rater reliability') %>%
   kable_styling("striped") %>%

### 2020-11-30 R/abbreviations.R

@@ -1,0 +1,21 @@
+abbr <-
+  dplyr::arrange(read.csv(
+    here::here("data", "abbreviations", "abbreviations.csv"),
+    stringsAsFactors = FALSE
+  ), Acronym)
+
+acron <- abbr$Acronym
+def <- abbr$Definition
+
+abbr_text <- c(
+  "% do not edit by hand - add to abbreviations.csv instead",
+  "% First parameter can be changed eg to \"Glossary\" or something.",
+  "% Second parameter is the max length of bold terms.",
+  "\\begin{mclistof}{List of Abbreviations}{3.2cm}",
+  unlist(lapply(1:length(acron), function(i) {
+    glue::glue("\\item[{acron[i]}] {def[i]}")
+  })),
+  "\\end{mclistof}"
+)
+
+writeLines(abbr_text, here::here("front-and-back-matter","abbreviations.tex"))

### 2020-12-09 01-Chp1-Introduction.Rmd
Double-saving

@@
 ```
+
+## Additional ideas
+
+* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published.
+Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished.
+* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.
 

### 2020-12-09 03-Chp-Systematic-Review-Tools.Rmd
Double-saving

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
Why are open source statistical programming  
languages the best?

Because they R.
```
(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# medrxivr: an R package for searching medRxiv and bioRxiv preprint data {#sys-rev-tools-heading}
\minitoc <!-- this will include a mini table of contents-->

```{r setup, include=FALSE}
source("R/doc_options.R")
```

<!----------------------------------------------------------------------------->

## Lay summary

Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal. 
They represent an important source of scientific literature.
A new software program called `medrxivr` was created as part of this thesis to allow researchers to find preprints related to their research in a transparent and reproducible way. 
Development of this tool was required as part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.

<!----------------------------------------------------------------------------->
## Introduction

Preprints represent an increasingly important source of scientific information. Authors can use preprint servers for several purposes - to establish primacy when submitting to a journal where a the peer-review process may take several months; to post complete manuscripts that will never be formally published,[CITE] such as those reporting updated case reports during the COVID-19 pandemic;[CITE] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias, or the "file-drawer" effect.

As a result, preprint repositories should be considered an distinct but complementary information source when reviewing the evidence base as part of a systematic review. The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]

Preprints represent a particularly important to this thesis, ias one of the primary types of evidence that I planned to use in the triangulation exercise (Mendelian randomization (MR)) is still developing and many MR studies that look at the clinical question that this project aims to investigate are posted as preprints on the bioRxiv, and more recently medRxiv, preprint servers. Being able to systematically search these records for the purpose of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity. In light of the above, the `medrxivr` R package was created in order to facilitate the searching of this data source.

<!----------------------------------------------------------------------------->

In addition the

Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced. A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as running searches and extracting records, title and abstract screening, and data extraction - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.

In addition, we need to focus on developing tools that allow systematic, reproducible access to more informal sources of scientific material. One key emerging source

Searching pre-print repositories is becoming an increasingly important part of a systematic review. Preprints - unpublished versions of manuscripts, frequently uploaded to a repository at the same time they are submitted to a journal for peer review - represent an important source of grey literature. As the barriers and time to publication are both lower, they also represent an important source of information that may be either currently tied up in the peer-review process

At present, medRxiv allows only simple search queries, as opposed to the often complex Boolean logic that information specialists use to query other major databases. Additionally, record metadata (titles/abstracts/author lists) must be accessed individually, rather than in batches, meaning that downloading relevant records for title and abstract screening a time consuming task.

This chapter outlines the development and key functionality of `medrxivr (version 0.2)`. The motivating factors that necessitated the development of this tool as part of this thesis are discussed. The use of medrxivr in external projects and by other researchers is discussed. As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary. The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.

Current extraction mechanisms for extracting the results of searches from medRxiv are to go through each record, one-by-one, downloading individual citations. As the scale of the medRxiv database increases, particularly in light of the massive expansion as a result of COVID, this alreay time-consuming and error-prone method is not longer feasible.

<!----------------------------------------------------------------------------->
## Development

Work on this element began in Summer 2019, and initially existed as a collection of scripts built to allow for searching medRxiv and bioRxiv as part of the systematic search outline in Chapter \@ref(sys-rev-heading). Following interest from other researchers in using the ad-hoc web-scraping scripts, the initial version of the `medrxivr` package was released in February 2020. Additional development work took place, allowing for improved searching and exporting function

The updates to the systematic search to capture new literature published since the last search was performed with the fully developed package.

Early versions of the tool had a reliance on web-scraping data directly from the medRxiv website. Web-scraping is a fragile, or brittle, way to extract data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992].

However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the medrxivr package to engage in "fault prevention" and work towards a more robust interface with the available data.

Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible required expansion to the bioRxiv repository, so that both can now be searched from a single tool. However, the introductory examples given below apply are taken from searches performed in the medRxiv repository.

Developed to meet three criteria:

1. reproducible and transparent search functionality, with Boolean operator logic;  
2. support for bulk export of references returned by the search;  
3. automated access full-text records of relevant records.

<!-----------------------------------------------------------------------------> 
## Installation

`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code

To install the stable `medrxivr` from CRAN:

&nbsp;

```{r, eval = FALSE}
install.packages("medrxivr")
```

&nbsp;

Alternatively, the  install the development version from GitHub:

```{r, eval = FALSE}
# install.packages("devtools") 
devtools::install_github("ropensci/medrxivr")
```

The `medrxivr` R package is split into two component parts:

* An interface to the Cold Springs Harbor Laboratory API, which allows the wholesale import of the medRxiv and bioRxiv metadata
* A collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.

The standard workflow is to download a copy of the preprint repository metadata, and then run your searchers locally. This is a workaround as the Cold Springs Harbor Labratory API does not provide any functionality to search the database.

<!----------------------------------------------------------------------------->
## Importing preprint meta data

`medrixvr` provides two ways to access medRxiv data.

`mx_api_content(server = "medrxiv")` creates a local copy of all data available from the medRxiv API at the time the function is run.

``` {r, eval = FALSE}
# Get a copy of the database from the live medRxiv API endpoint
preprint_data <- mx_api_content()  
```

As an alternative to downloading a copy fo the database from the API in realtime, the `mx_snapshot()` function provides access to a maintained static snapshot of the database. The snapshot is created each morning at 6am. This method, which doet not rely on the API, was created as during development e unavailable during peak usage times) and has the additional advantage of being faster, as it reads data from a comma-seperated file rather than having to re-extract it from the API.

The relationship between the two methods for accessing the data conatined in the medRxiv database is summarized in the figure below:

(ref:medrxivr-data-sources-cap) __Overview of `medrxivr` data sources:__ Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function. Note: due to the size of bioRxiv, a maintained snapshot of medrxiv is available via `mx_snapshot()`.

(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources

```{r medrxivr-data-sources, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
```

<!----------------------------------------------------------------------------->
## Creating a search

Once a local copy of the database has been created, the functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:

* `mx_search()`: Enables users to search the preprint data, using regular expressions and Boolean logic.

&nbsp;

```{r, eval = FALSE}
topic1  <- c("dementia","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins")        # Combined with OR

myquery <- list(topic1, topic2)         # Combined with AND

results <- mx_search(myquery)
```

&nbsp;

Additional functionality allowing common syntax used by systematic reviewers and health librarians, including the use of NEAR statements (which allows for ),

<!----------------------------------------------------------------------------->
## Further functionality

<!----------------------------------------------------------------------------->
### Exporting to bibliography

One of the key features of the `medrxivr` is the ability for users to export the results of their

For example, the results of our simple search above can be exported using the following code:

``` {r, eval = FALSE}
mx_export(results, 
          file = "medrxiv_export.bib")
```

<!----------------------------------------------------------------------------->
### PDF download

A second key use of the medrxivr package:

* `mx_download()` Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.

```{r, eval = FALSE}
mx_download(results,        # Object returned by mx_search()
            "pdf/")         # Directory to save PDFs to 
```

<!----------------------------------------------------------------------------->
### Search reporter

One additional function creates a formatted output table with each search strategy presented on an individual line and the number of records associated with this strategy.

```{r, eval = FALSE}
mx_report(results)
```

This allows users to discover which aspects of their

### Data visualisation

<!----------------------------------------------------------------------------->
### Shiny app

Part of the key theme of accessibility meant creating a web-application that allowed those without any knowledge of the R programming environment to benefit from it's functionality. 
The app is readily available and has

<!----------------------------------------------------------------------------->
## Reception and future plans

```{r, echo = FALSE}
medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )

medrxivr_downloads <- plyr::round_any(sum(medstats$count), 100, f = floor)

date <- format(Sys.Date(),"%B %Y")
```

The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times, and the medRxivr app has been visited more than ????), and several use cases have been reported. It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in a number of other systematic reviews,[@noone2020] in addition to forming a platform for an analysis of researcher's differing data-sharing tendencies under two different journal models (preprint server vs formal publication).[CITE]

Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.^[https://github.com/ropensci/software-review/issues/380]

Lobbying of the cold springs harbour labratory has been ongoing. This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for.

<!----------------------------------------------------------------------------->
## Comparison with other search options

During development of the package, there were several alternative considered as part of a audit of existing tools. However, development of a new custom tool was preferred as none met the three criteria required: 1) reproducible and transparent search functionality, with Boolean operator logic; 2) support for bulk export of references returned by the search; 3) automated access full-text records of relevant records.

Some previous tools exist while allowed for robust searching of preprint repositories, such as `search.bioPreprint` [@iwema2016]- however, these tools were aimed more at those looking to keep up to date with recent developments rather than systematically assess the entirety . As such, they did not support needed functionality such as bulk export of records matching a search term, unlimited return of records (c.f. `search.bioPreprint` which is limited to the most recent 1000 records matching a user search).

<!----------------------------------------------------------------------------->
## Package infrastructure

The `medrxvir` package was written in R using RStudio, and followed development best practices, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced reviewers.

The medRxiv snapshot is still taken every morning using GitHub Actions, an automated system for repetitive tasks.

An automatically generated documentation website is also generated on each update to the code-base ^[https://docs.ropensci.org/medrxivr/]

<!----------------------------------------------------------------------------->
## Discussion

Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. []

While searching of the medRxiv database was crucical for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading)

**Need to also touch on the biases involved in search preprint literature, in that the authors of those in the **

it is too early to see if preprint reps

There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]

As

By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified. This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency. Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.

Creating a package using R has a number of advantages unique to the R programming environment. R provides access to a range of powerful tools including the `ggplot` infrastructure for creating publication-quality plots, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages. Recently, the `metaverse` project,[@variousauthors2020] of `medrivr` is a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager. Key offerings in this suite of packages include `litsearcher`, which facilitates systematic search strategy development, `revtools`, a package for managing the review process and performing title and abstract screening, `metaDigitise`, a package for automatic extraction of data from figures in research papers, and `metafor`, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]

<!----------------------------------------------------------------------------->
## Summary

* In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex searches in the medRxiv and bioRxiv preprint repositories.

* I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature source used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).

* The impact of this tool to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development has been discussed.

### 2020-12-09 04-Chp2-Systematic-Review.Rmd
Double-saving

--- 2020-11-30 03-Chp2-Systematic-Review.Rmd
@@
 ```
+
+## Lay summary
 
@@
 How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwettable).
 
-Gwet's AC1 is calculated using the following:
+In a two by two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
+
+$$AC1 = \frac{p-e(\gamma)}{1-e(\gamma)}$$
+Here, $p = \frac{A+D}{N}$ and $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where $q = \frac{(A+C)+(A+B)}{2N}$
 
@@
 
-```{r gwet-table, echo = FALSE}
+```{r agreementtableinter, echo = FALSE}
 ```
 
-```{r agreement-table-inter, echo = FALSE}
-```
-
-```{r agreement-table-intra, echo = FALSE}
+```{r agreementtableintra, echo = FALSE}
 ```
@@
 #### PRISMA flowchart
-
-```{r prisma-flow, echo = FALSE, warning=FALSE, message=FALSE, fig.cap="PRISMA flow diagram, detailing the movement of studies through the systematic review.", out.width="100%"}
-```
 

### 2020-12-09 05-Ch3-CPRD-Analysis.Rmd
Double-saving

--- 2020-11-30 04-Ch3-CPRD-Analysis.Rmd
@@
 
-Note: this will be harder for things that are not dichotmous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
+Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
 
@@
 Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should recieved a lipid regulation agent.
+Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should received a lipid regulation agent.
 However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months.
 [Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that acutally did what they should.]
+Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.]
 
-As expected, in a confirmatory analysis using lipid levels, there was no association between <span color="red">the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, incdicating that adjusting for this variable was not required.
-*</span>
+As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*
+
+### Replicating the analysis
+
+**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of differnet code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]

### 2020-12-09 front-and-back-matter/99-appendices.Rmd
Double-saving

--- 2020-11-26 05-Chp-Systematic-Review-Tools.Rmd
@@
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: word-styles-reference-01.docx
-  bookdown::html_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-documentclass: book
----
+`r if(knitr:::is_latex_output()) '\\startappendices'`
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
-Why are open source statistical programming  
-languages the best?
+`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
 
-Because they R.
-```
-(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
+<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
 
-# Creating new systematic review tools in R {#sys-rev-tools-heading}
-\minitoc <!-- this will include a mini table of contents-->
+# By Chapter
 
-```{r setup, include=FALSE}
-source("R/doc_options.R")
-```
+## Chapter 1
 
-<!----------------------------------------------------------------------------->
+## Chapter 2
 
-## Background
-
-Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced.
-A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as title and abstract screening, - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.
-
-Below I introduce two new R packages created to faciliate some aspects of the systematic review process.
+# Other Appendix
 
@@
 The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
-
-<!----------------------------------------------------------------------------->
-## Searching for health-related preprints with `medrxivr`
-
-### Introduction
-
-Searching pre-print repositories is becoming an increasingly important part of a systematic review.
-Preprints - unpublished versions of manuscripts, frequently uploaded to a repository at the same time they are submitted to a journal for peer review - represent an important source of grey literature.
-
-However, while several of the main repositories (e.g.
-arXiv, bioRxiv) have existing methods by which records can be searched and downloaded en masse,^[https://arxiv.org/help/api] this is not true for medRxiv, a repository launched in June 2019 to host preprints in the medical, clinical, and related health sciences.
-
-At present, medRxiv allows only simple search queries, as opposed to the often complex Boolean logic that information specialists use to query other major databases.
-Additionally, record metadata (titles/abstracts/author lists) must be accessed individually, rather than in batches, meaning that downloading relevant records for title and abstract screening a time consuming task.
-
-The `medrxivr` R package was created in order to facilitate the searching of this data source, allow
-
-### Usage
-
-To install `medrxivr` from CRAN:
-
-```{r, eval = FALSE}
-# Currently doesn't work as not on CRAN
-
-install.packages("medrxivr")
-```
-
-To install the development version from GitHub:
-
-```{r, eval = FALSE}
-devtools::install_github("mcguinlu/medrxivr")
-```
-
-### Methods
-
-The `medrxivr` project is split into two parts:
-
-* A webscraper that runs once a day which collects and cleans new records uploaded to medRxiv, and adds them to a machine readable database.
-* A lightweight R package that provides an interface for this database, allowing users to search for relevant records, and easily retieve the associated full tex PDFs.
-
-The webscraper is a straightforward R script built in R using `rvest` and a range of text processing packages[@wickham2019; @wickham2019a; @wickham2020].
-To quickly illustrate the process, the code to retrieve the total number of records on medRxiv is included below:
-
-```{r,eval=FALSE}
-
-# Perform a search for "*" (defined by %252A), which acts as a wildcard  
-# This approach will capture all records
-url <- "https://www.medrxiv.org/search/%252A"
-
-# Read the HTML from this link
-page <- read_html(url)
-
-# Extract the text (html_text()) value of the CSS node of interest, in this
-# case, the "#page-title" node
-
-results <- page %>%
-  html_nodes("#page-title") %>%
-  html_text()
-
-# Remove any commas from the results (e.g. 1,500 become 1500)
-results <- gsub(",","",results)
-
-# Convert it from a character string to a numeric
-results <- as.numeric(word(results))
-
-```
-
-Using Windows Task Scheduler,[@zotero-880] the script is scheduled to automatically run every morning, adding new records uploaded to medRxiv since the last run of the webscraper to a local comma-seperated-values (CSV) file.
-Following a quality control pipeline, which checks the completeness of the new records and ensures that all records have been captured, the updated dataset is automatically uploaded to a cloud server and immediately becomes available to the `medrxivr` package functions.
-
-The functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:
-
-* `mx_search()` [main]: Enables users to search the medrxivr data dump, using regular expressions and boolean logic.
-
-```{r, eval = FALSE}
-topic1  <- c("dementia","vascular","alzheimer's")  # Combined with OR
-topic2  <- c("lipids","statins","cholesterol")     # Combined with OR
-
-myquery <- list(topic1, topic2)                    # Combined with AND
-
-results <- mx_search(myquery)
-```
-
-* `mx_download()` [main]: Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.
-
-```{r, eval = FALSE}
-mx_download(results,        # Object returned by mx_search
-            "pdf/")         # Directory to save PDFs to 
-```
-
-* `mx_crosscheck()` [helper]: Provides information on the version of the data dump that the user is searching, and checks whether any new records have been uploaded to medRxiv since the last run of the webscraper.
-
-```{r, eval = FALSE}
-mx_crosscheck()
-
-## Using medRxiv snapshot - 2020-03-04 10:55
-## No new records added to medRxiv since last snapshot.
-```
-
-### Reception and Future Plans
-
-The tool has be well received by the community, and several use cases have been reported.
-The tool was primarily created to faciliate the searching performed as part of the review in Chapter \@ref(sys-rev-heading).
-However, several other use cases have emerged for the tool.
-It has been used to visalise the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], etc, etc
-
-Following peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.
-
-The tool has also
-
-<!----------------------------------------------------------------------------->
-## Dicussion
-
-Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. [EXPAND]
-
-By implementing the tools described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R.
-These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `robvis`, it is likely that several other evidence synthesists have written scripts to produce similar risk-of-bias plots to those presented here - in fact, in the course of its development, I identified one other research group that has done so.
-This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
-Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short timeframe, expanding the potential pool of users of the package to anyone with an internet connection.
-
-Creating a package using R has a number of particular advantages.
-R provides access to a range of powerful tools including the `ggplot` infrastructure as demonstrated above, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages.
-Recently, the `metaverse` project,[@variousauthors2020] of which `robvis` and `medrivr` are a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager.
-Key offerings in this suite of packages include litsearcher, which facilitates systematic search strategy development, revtools, a package for managing the review process and performing title and abstract screening, metaDigitise, a package for automatic extraction of data from figures in research papers, and metafor, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]
-
-<!----------------------------------------------------------------------------->
-## Summary
-
-* In this Chapter, I have introduced two new tools for facilitating evidence syntheses: `robvis`, a tool for producing publication quality risk of bias assessments, and `medrxivr`, a tool for performing complex searches in the medRxiv preprint repository.
-
-* I have outlined the motivation for developing these tools in relation to this thesis - more specifically, that they were used extensively to the conduct the comprehensive systematic review described in Chapter \@ref(sys-rev-heading)
-
-* The impact of these packages to date, their place in the broader evidence synthesis in R ecosystem, and a roadmap for their future development has been discussed.

### 2020-12-09 03-Chp-Systematic-Review-Tools.Rmd
Updates end-of-day

@@
 
-In addition the
-
-Developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced.
+More generally, developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced.
 A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as running searches and extracting records, title and abstract screening, and data extraction - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.
@@
 
-One of the key features of the `medrxivr` is the ability for users to export the results of their
+One of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
+While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is
 
@@
 By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R.
-These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified.
+These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified (xxxx xxxx, author of the `rbiorxiv` pacakge).[@rbiorxiv]
+
+``` {r, eval = TRUE, echo = FALSE}
+
+t<-rbiorxiv::biorxiv_summary()
+
+```
+
 This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
@@
 * The impact of this tool to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development has been discussed.
+
+test

### 2020-12-09 04-Chp2-Systematic-Review.Rmd
Updates end-of-day

@@
 
+Consideration of the potential impact of the magnitude and direct of unaddressed confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+Wihtin GRADE the overall quality of evidence can be upgraded when there is deemed to be **will need to confirm this.l** [@guyatt2011]
+
 ## Conclusion

### 2020-12-10 04-Chp-Systematic-Review.Rmd
Fix fancy headers in template file and update other files

--- 2020-12-09 04-Chp2-Systematic-Review.Rmd
@@
 ```
-(ref:dara-quote) --- Dara O'Briain
 
@@
 knitr::read_chunk("R/Chp2-Systematic-Review.R")
+knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwettable).
+Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+
+<!----------------------------------------------------------------------------->
+``` {r gwet-setup, results="hide", message=FALSE}
+```
+
+```{r gwet-table, message=FALSE, results="asis"}
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
+``` {r chunkname_setup, results="hide", message=FALSE}
+```
+
+```{r chunkname_table, message=FALSE, results="asis"}
+```
+<!----------------------------------------------------------------------------->
+
 #### PRISMA flowchart
@@
 
+<!----------------------------------------------------------------------------->
 Include here:

### 2020-12-10 index.Rmd
Fix fancy headers in template file and update other files

@@
 source('scripts_and_filters/create_chunk_options.R')
-source("R/citations.R")
+source("R/helper.R")
+source
 ```

### 2020-12-10 R/helper.R

@@ -1,0 +1,56 @@
+# Generates an line pandoc citation string for all packages used in the 
+
+gen_rmd_citation <- function(filename = "pkg-refs.bib") {
+  
+  # Read in bib file
+  pkgs <- readLines(here::here("bibliography",filename))
+  
+  # Extract bibtex keys to a string
+  pkg_names <- unique(pkgs[which(grepl("@",pkgs))])
+  
+  pkg_names <- unique(gsub(
+    "\\{|,", "", stringr::str_extract(pkg_names, "\\{.+")
+  ))
+
+  # Read in list of packages that I need to have a citation for, but shouldn't
+  # go in here, and exclude these from the vector
+  extra_packages <- readLines(file.path("data","extra_packages.txt"))
+  
+  pkg_names <- pkg_names[which(!(pkg_names %in% extra_packages))]
+  
+  # Format string as pandoc citation
+  pkg_cit <- paste0("[@", paste(pkg_names, collapse = "; @"),"]")
+  
+  return(pkg_cit)
+  
+}
+
+# Place comma at thousand position
+# Taken from https://github.com/thomasbattram/thesis
+comma <- function(x){format(x, digits = 2, big.mark = ",")}
+
+# Apply comma to all values in a table
+# Taken from https://github.com/thomasbattram/thesis
+tidy_nums <- function(df) 
+{
+  df[] <- lapply(df, comma)
+  return(df)
+}
+
+# Convert nub
+# Taken from https://github.com/thomasbattram/thesis
+num_to_text <- function(x, start_of_sentence = FALSE)
+{
+  if (!x%%1 == 0) warning("X is not an integer")
+  if (start_of_sentence) {
+    out <- xfun::numbers_to_words(x)
+    out <- stringr::str_to_sentence(out)
+  } else {
+    if (x < 11 & x > -1) {
+      out <- xfun::numbers_to_words(x)
+    } else {
+      out <- x
+    }
+  }
+  return(out)
+}

### 2020-12-10 01-Chp-Introduction.Rmd
Fix fancy headers in template file and update other files
End of day: -700

--- 2020-12-09 01-Chp1-Introduction.Rmd
@@
 
-# Introduction {#intro-intro}
+# Introduction {#intro-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-```{r load_helper_scripts, include=FALSE}
-source("R/citations.R")
-```
+First I provide a background to the central concepts and themes of this thesis, and justify the motivations for this piece of work.
+I introduce a tool that allows for systematic searching of preprint literature, which is then used in a systematic review of all available evidence on my central research question.
 
@@
 
+## Theoretical framework
+The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.
+
+All elements of this thesis are based around this framework.
+
 ## Chapter Overview
@@
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid 
-* __Chapter \@ref(cprd-analysis):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
-* __Chapter \@ref():__ This Chapter seeks
-
-* __Appendix \@ref(sys-rev-tools-heading)__ This Chapter introduces new evidence synthesis two tools built in R: `robvis` and `medrixvr`.
-The motivation for, development and impact of, and future plans for these tools are outlined.
+* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
+* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
+* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
 
@@
 
+  * McGuinness, Luke A., and Lena Schmidt.
+"medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 (2020): 2651.
+DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)
+
+  * McGuinness, Luke A., and Julian PT Higgins.
+"Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Methods (2020).
+DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)
+
 ### Papers under review
 
-* McGuinness et al.
+  *
 
@@
 
-A lot of packages were used in this project`r gen_rmd_citation()`
+* `medrxvir`: An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv^[https://www.medrxiv.org/] and bioRxiv^[https://www.biorxiv.org/] preprint repositories.
+See Chapter \@ref(sys-rev-tools-heading) for more details.
+Install a stable version of the package from CRAN with `install.packages("medrxivr")` or alternatively install the development version from GitHub using `devtools::install_github("mcguinlu/medrxivr")`.
+Link: [https://ropensci.github.io/medrxivr/](https://ropensci.github.io/medrxivr/)
 
-* `robvis`: An R package and associated `shiny` web application that allows users to easily visualise the results of risk of bias graphs.
-
-* `medrxvir`: An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv^[https://www.medrxiv.org/] preprint repository.
+* `robvis`: An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
+See Appendix \@ref(appendix-robvis) for more details.
+Install a stable version of the package from CRAN using `install.packages("robvis")` or alternatively install the development version from GitHub using `devtools::install_github("mcguinlu/robvis")`.
+Link: [https://mcguinlu.github.io/robvis/](https://mcguinlu.github.io/robvis/)
 
@@
 
-* Talk at Cochrane on medrxivr
 * Presentation to the 
 * Webinar to Evidence Synthesis Ireland on Risk of Bias
+* Presentation(s) to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
 

### 2020-12-10 03-Chp-Systematic-Review-Tools.Rmd
Update to cite rbiorxiv
Fix fancy headers in template file and update other files
End of day: -700

@@
 
-<!----------------------------------------------------------------------------->
-
 More generally, developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced.
@@
 <!----------------------------------------------------------------------------->
+
+(ref:medrxivr-sr-cap) __Role of `medrxivr` in a systematic review workflow:__ `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
+Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to faciliate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
+
+(ref:medrxivr-sr-scap) Role of `medrxivr` in a systematic review workflow
+
+```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
+knitr::include_graphics(file.path("figures/UoBcrest.pdf"))
+```
+
+<!----------------------------------------------------------------------------->
+
 ## Development
+
+Development of the package followed the
+
+### Success crtieria
+
+Defining success criteria
+
+The tool was developed to meet three success criteria,[@wateridge1995] created both from the list of functionality needed to perform the systematic searches as part of the review in Chapter \@ref(sys-rev-heading) and from an informal survey of colleagues and the evidence synthesis and health librarians on Twitter.
+These criteria were as follows:
+
+1. reliable, reproducible and transparent search functionality, allowing for similar Boolean (AND/OR/NOT) operator logic as that available from other literature search platforms such as OvidSP;  
+2. support for bulk export of references returned by the search to a file type that can be imported into a reference manager (e.g., .bib  or .ris);  
+3. automated retrieval of the full-text PDFs of relevant records.
+
+<!----------------------------------------------------------------------------->
+
+### Early version
 
@@
 Early versions of the tool had a reliance on web-scraping data directly from the medRxiv website.
-Web-scraping is a fragile, or brittle, way to extract data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992].
+Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992].
+In the case of early versions of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the medRxiv website was regularly updated.
 
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the medrxivr package to engage in "fault prevention" and work towards a more robust interface with the available data.
+However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the medrxivr package to engage in "fault prevention" and work towards a more robust interface with the available data.[@laprie1992]
 
-Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible required expansion to the bioRxiv repository, so that both can now be searched from a single tool.
-However, the introductory examples given below apply are taken from searches performed in the medRxiv repository.
-
-Developed to meet three criteria:
-
-1. reproducible and transparent search functionality, with Boolean operator logic;  
-2. support for bulk export of references returned by the search;  
-3. automated access full-text records of relevant records.
+Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible papers for the review detailed in Chapter \@ref(sys-rev-heading) required expansion to allow for similar searching of the bioRxiv repository.
 
 <!----------------------------------------------------------------------------->
-## Installation
+## Package infrastructure
 
-`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code
+The `medrxvir` package was written in R using RStudio, and followed development best-practice, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced, independent reviewers.
 
-To install the stable `medrxivr` from CRAN:
+An automatically generated documentation website is also generated on each update to the code-base. ^[https://docs.ropensci.org/medrxivr/]
 
-&nbsp;
-
-```{r, eval = FALSE}
-install.packages("medrxivr")
-```
-
-&nbsp;
-
-Alternatively, the  install the development version from GitHub:
-
-```{r, eval = FALSE}
-# install.packages("devtools") 
-devtools::install_github("ropensci/medrxivr")
-```
+<!-----------------------------------------------------------------------------> 
+## Usage
 
@@
 <!----------------------------------------------------------------------------->
-## Importing preprint meta data
+
+## Installation
+
+`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code:
+
+&nbsp;
+
+```{r, eval = FALSE}
+install.packages("medrxivr")
+```
+
+&nbsp;
+
+Alternatively, the development version of the pacakage can be installed from GitHub:
+
+```{r, eval = FALSE}
+# install.packages("devtools") 
+devtools::install_github("ropensci/medrxivr")
+```
+
+<!----------------------------------------------------------------------------->
+### Importing preprint metadata
 
@@
 <!----------------------------------------------------------------------------->
-## Creating a search
+### Performing a search
 
@@
 <!----------------------------------------------------------------------------->
-## Further functionality
+### Exporting to a bibliography file
 
-<!----------------------------------------------------------------------------->
-### Exporting to bibliography
-
-One of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
+In line with the second success criteria, one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
 While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is
@@
 <!----------------------------------------------------------------------------->
-### PDF download
+### Downloading the PDFs of relevant records
 
@@
 <!----------------------------------------------------------------------------->
-### Search reporter
+### Reporting your results
 
@@
 
-### Data visualisation
+### Visualising your results
 
@@
 <!----------------------------------------------------------------------------->
-## Comparison with other search options
+### Comparison with other bioRxiv/medRxiv interfaces
 
-During development of the package, there were several alternative considered as part of a audit of existing tools.
-However, development of a new custom tool was preferred as none met the three criteria required: 1) reproducible and transparent search functionality, with Boolean operator logic; 2) support for bulk export of references returned by the search; 3) automated access full-text records of relevant records.
+Prior development of `medrxivr`, several alternative search tools were considered as part of a audit of existing tools for accessing the metadata of records stored on the medRxiv and bioRxiv servers.
 
-Some previous tools exist while allowed for robust searching of preprint repositories, such as `search.bioPreprint` [@iwema2016]- however, these tools were aimed more at those looking to keep up to date with recent developments rather than systematically assess the entirety .
-As such, they did not support needed functionality such as bulk export of records matching a search term, unlimited return of records (c.f.
-`search.bioPreprint` which is limited to the most recent 1000 records matching a user search).
+Two key examples are useful to consider to highlight the additional functionality that `medrxivr` contributes.
 
-<!----------------------------------------------------------------------------->
-## Package infrastructure
+The first, a platform called Rxivist [@abdill2019], Similar to `medrxivr`, this tool previously scrapped data straight from the bioRxiv.
+(at the time of development, Rxvist , but as of November 2020, Rxivist also provides access to
 
-The `medrxvir` package was written in R using RStudio, and followed development best practices, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced reviewers.
+However, this platform is focused more on exploring the number of times a preprint has been downloaded and/r shared on Twitter, to allow researchers to find the most popular papers related to their topic.
+The search interface^[Available at https://rxivist.org/] does not allow for either complex search strategies or
+The second `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues such as F1000Research.
+[@iwema2016].
+However, this tool is aimed more at those looking to keep up to date with recent developments rather than systematically assessing the entirety of the available literature, and as such, only returns the most recent `r comma(1000)` records by publication date.
 
-The medRxiv snapshot is still taken every morning using GitHub Actions, an automated system for repetitive tasks.
+Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records.
 
-An automatically generated documentation website is also generated on each update to the code-base ^[https://docs.ropensci.org/medrxivr/]
+. As such, this tool does not meet the second success did not meet the success criteria laid out in the introduction to this Chapter.
 
@@
 
-it is too early to see if preprint reps
-
-There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]
-
-As
+There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE] It is likely too early, (and too difficult) to tell whether.
+**The additional contribution of searching these repositories to the systematic review element of this thesis is explored in Chapter \@ref(sys-rev-heading)**
 
@@
 These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified (xxxx xxxx, author of the `rbiorxiv` pacakge).[@rbiorxiv]
-
-``` {r, eval = TRUE, echo = FALSE}
-
-t<-rbiorxiv::biorxiv_summary()
-
-```
 
@@
 * The impact of this tool to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development has been discussed.
-
-test

### 2020-12-10 04-Chp-Systematic-Review.Rmd
End of day: -700

@@
 
-# Systematic Review {#sys-rev-heading}
+# Systematic review and triangulation of available evidence {#sys-rev-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 ```
+
+## To Do
+
+* Examine how many times a primary study was included in a review  
+* Look at wether searching preprints made any difference to my results
 
@@
 
-#### Inclusion
+#### Inclusion criteria
 We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
@@
 
-#### Exclusion
+#### Exclusion criteria
 Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
@@
 
-Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorising lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
+Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
 
@@
 Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomised controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomised studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomised studies of exposures were assessed using the ROBINS-E tool.[TBC]
+Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
 
-At present, no risk of bias assessment tool for Mendelian randomisation studies is available. Bias in thesee studies was assessed with the help of an expert panel [TBC]
+At present, no risk of bias assessment tool for Mendelian randomization studies is available.
+Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE]
 
-Data will be visualized using a paired forest and risk of bias plot
+Data will be visualized using a paired forest and risk of bias plot, created using the `robvis` tool.
+This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]
 
@@
 As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
-
-#### Inter-rater reliability
 
@@
 <!----------------------------------------------------------------------------->
-``` {r chunkname_setup, results="hide", message=FALSE}
+``` {r prisma-flow-setup, results="hide", message=FALSE}
 ```
 
-```{r chunkname_table, message=FALSE, results="asis"}
+(ref:prisma-flow-cap) __PRISMA Flowchart:__ Overview of how records moved through the systematic review process
+
+(ref:prisma-flow-scap) PRISMA Flowchart
+
+```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
 ```
@@
 
-#### PRISMA flowchart
-
 Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility.
 387 were deemed potentially eligible and the full text records for these were requested and screened.
-[**CROSS-REF to PRISMA flow here**]
+\@ref(fig:prisma-flow-fig)
 
-A breakdown of records by
-
-## Included studies
+### Characteristics of included studies
 
@@
 
-## Publication bias
+### Risk of bias {#risk-of-bias-subheading}
+
+### Publication bias
 
@@
 
-### Triangualtion across evidence sources
+## Triangualtion across evidence sources
 
@@
 
-A key limitiation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use
+A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use.
+In addition, there was limited literature available - as discussed in CHapter \@ref()
+
+Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
+For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
+[@guyatt2011]
+
+Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test  test
 
@@
 
-Of note, as part of the review, we identified serveral previous systematic reviews of this topic. However, this review is the firest to
+### Comparison with other reviews
 
-Consideration of the potential impact of the magnitude and direct of unaddressed confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Wihtin GRADE the overall quality of evidence can be upgraded when there is deemed to be **will need to confirm this.l** [@guyatt2011]
+Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
+
+__The duplication of work across reviews (including, ironically, by this review) is substantial.
+In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
+However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.__
+
+### Strenghts and limitations
 

### 2020-12-10 06-Chp-IPD-Analysis.Rmd
End of day: -700

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:ipd-quote)'}
Science knows it doesn't know everything; otherwise, it'd stop
```
(ref:ipd-quote) --- Bealy, 2013 [@bealy2013]

# Individual participant data meta-analysis {#ipd-heading}
\minitoc <!-- this will include a mini table of contents-->

## Data sources

As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.

Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get

Each should have:

* Description (including period,numbers, numbers with outcome, etc)
*
*

```{r tests, }

```

### 2020-12-10 front-and-back-matter/99-appendices.Rmd
End of day: -700

@@
 
-# By Chapter
+# By Chapter {#chapter-appendix-heading}
 
-## Chapter 1
+## Chapter 1 {#appendix-chapter-1}
 
-## Chapter 2
-
-# Other Appendix
+## Chapter 2 {#appendix-chapter-2}
 
 <!----------------------------------------------------------------------------->
-## Producing risk-of-bias visualisation with `robvis`
+# Other Appendix {#other-appendix-heading}
+
+## Software used to create this thesis
+
+This thesis was written in RMarkdown.
+Several R packages were used as part of this project.`r gen_rmd_citation()`
+
+## Producing risk-of-bias visualisation with `robvis` {#appendix-robvis}
 

### 2020-12-10 R/Chp2-Systematic-Review.R

@@ -1,26 +1,5 @@
-# ---- prismaflow
+# ---- prisma-flow-setup
 
-# png(file = "figures/sys-rev/prismaflow.png", bg = "transparent")
-# PRISMAstatement::prisma(
-#   found = 16109,
-#   found_other = 0,
-#   no_dupes = 16109,
-#   screened = 16109,
-#   screen_exclusions = 15722,
-#   full_text = 387,
-#   full_text_exclusions = 0,
-#   qualitative = 0,
-#   quantitative = 0,
-#   labels = NULL,
-#   extra_dupes_box = FALSE,
-#   dpi = 72,
-#   font_size = 10)
-# dev.off()
-# 
-# knitr::include_graphics("figures/sys-rev/prismaflow.png", 
-#                         )
-
- 
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- gwet-setup

### 2020-12-11 02-Chp-Background.Rmd
End of day: -621

--- 2020-11-30 02-Chp2-Background.Rmd
@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
-Science knows it doesn't know everything; otherwise, it'd stop
+Science knows it doesn't know everything; otherwise, it'd stop.
 ```

### 2020-12-11 03-Chp-Systematic-Review-Tools.Rmd
End of day: -621

@@
 
-# medrxivr: an R package for searching medRxiv and bioRxiv preprint data {#sys-rev-tools-heading}
+# medrxivr: an R package for performing systematic searches of health-related preprints {#sys-rev-tools-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.^[https://github.com/ropensci/software-review/issues/380]
+Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
+^[https://github.com/ropensci/software-review/issues/380]
 
-Lobbying of the cold springs harbour labratory has been ongoing.
-This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for.
+Lobbying of the cold springs harbour laboratory has been ongoing.
+This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for performing searches (for example, as of December 2020, downloading a copy of the bioRxiv database takes approximately an hour.)
 
 <!----------------------------------------------------------------------------->
-### Comparison with other bioRxiv/medRxiv interfaces
+### Comparison with other medRxiv/bioRxiv interfaces
 
-Prior development of `medrxivr`, several alternative search tools were considered as part of a audit of existing tools for accessing the metadata of records stored on the medRxiv and bioRxiv servers.
+Prior development of `medrxivr`, an informal audit of comparable tools search tools were considered as part of a audit of existing tools for accessing the metadata of records stored on the medRxiv and bioRxiv servers.
+Two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
 
-Two key examples are useful to consider to highlight the additional functionality that `medrxivr` contributes.
+The first, a platform called Rxivist [@abdill2019], allows users to search preprints from the using keywords.
+Similar to `medrxivr`, this tool previously scrapped data straight from the medRxiv and bioRxiv websites but as of November 2020, Rxivist also provides access to Cold Spring Harbour API.
+However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
+The search interface^[Available at https://rxivist.org/] does not allow for complex search strategies, and there is no option to batch-export the results of a search.
 
-The first, a platform called Rxivist [@abdill2019], Similar to `medrxivr`, this tool previously scrapped data straight from the bioRxiv.
-(at the time of development, Rxvist , but as of November 2020, Rxivist also provides access to
+The second, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues using post-publication peer-review such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
+As such, the platform only returns the most recent `r comma(1000)` records by publication date.
 
-However, this platform is focused more on exploring the number of times a preprint has been downloaded and/r shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface^[Available at https://rxivist.org/] does not allow for either complex search strategies or
-The second `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues such as F1000Research.
-[@iwema2016].
-However, this tool is aimed more at those looking to keep up to date with recent developments rather than systematically assessing the entirety of the available literature, and as such, only returns the most recent `r comma(1000)` records by publication date.
-
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records.
-
-. As such, this tool does not meet the second success did not meet the success criteria laid out in the introduction to this Chapter.
+Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records which is required for the full-text screening stage of a systematic review.
 
 <!----------------------------------------------------------------------------->
-## Discussion
+## Discussion ^[Some of the arguments presented here are repeated in a paper introducing second R package developed during this thesis, but not directly related to it.[@mcguinness] A summary of this second tool, `robvis` is presented in Appendix \@ref(appendix-robvis).]
 
-Packaging and sharing R scripts should be a fundamental part of evidence synthesis process. []
+The development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis process.
 
-While searching of the medRxiv database was crucical for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading)
-
-**Need to also touch on the biases involved in search preprint literature, in that the authors of those in the **
-
-There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE] It is likely too early, (and too difficult) to tell whether.
-**The additional contribution of searching these repositories to the systematic review element of this thesis is explored in Chapter \@ref(sys-rev-heading)**
+While searching of the medRxiv database was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+As key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords).
+There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - studies or analysis that are not published for a range of reasons, including results that are not deemed "novel" or are not statistically significant.
+This is because simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]
+It is likely too early, (and too difficult) to tell whether the popularity of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+**Of particular interest to this thesis is whether including unpublished preprints in the systematic review and meta-analysis is worthwhile.
+To this end, the additional contribution of searching these repositories to the systematic review element of this thesis is explored in Chapter \@ref(sys-rev-heading) [CROSS].**
 
 By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. 
-These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] In the case of `medrxivr`, it is likely that several other evidence synthesists had written scripts that have a similar functionality - in fact, in the course of its development, one other researcher that has done so was identified (xxxx xxxx, author of the `rbiorxiv` pacakge).[@rbiorxiv]
+These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] 
+In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts scripts that have a similar, or related, functionality - in fact, in the course of its development, one other researcher that has done so was identified (Nicholas Fraser, author of the `rbiorxiv` package).[@rbiorxiv]
+If these scripts continue to be developed in private and never shared or publicised, this leads to inevitable harm to the evidence synthesis community, not only in terms of duplication of time and effort, but also due to lost collaboration opportunities.
 
-This duplication of time and effort is inefficient, and creating and sharing well-documented R packages represents one way to reduce this inefficiency.
-Taking this approach one step further, `Shiny` apps represent a straightforward way to provide a user-friendly GUI for a newly created R package within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.
+Creating and sharing well-documented packages, the recognised standard for sharing reproducible and useful code, represents one way to reduce this inefficiency.
+Progressing this argument further, `Shiny` apps represent a efficient way to provide a user-friendly interface for newly created R packages within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.
 
+[**The next section needs to be reduced and fit a bit better to this Chapter - it was taken from the robvis paper, but the issues it raises are important and potentially relevant here.**]{.correction}
+
+In addition
 Creating a package using R has a number of advantages unique to the R programming environment.
@@
 
-* I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature source used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
+* I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
 
-* The impact of this tool to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development has been discussed.
+* I have contrasted `medrxivr` with other other platforms to highlight the added functionality it offers.
+I have also discussed its reception to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development.

### 2020-12-11 04-Chp-Systematic-Review.Rmd
End of day: -621

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
-Science knows it doesn't know everything; otherwise, it'd stop
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)'}
+"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
 ```
+(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]
 
@@
 * Examine how many times a primary study was included in a review  
-* Look at wether searching preprints made any difference to my results
+* Look at whether searching preprints made any difference to my results
 
@@
 
+[This is a test]{.correction}
+
 XXXX studies met the criteria for inclusion in the review.
@@
 
+Test
+
 ## Conclusion
+
+Test

### 2020-12-11 05-Chp-CPRD-Analysis.Rmd
End of day: -700
End of day: -621

--- 2020-12-09 05-Ch3-CPRD-Analysis.Rmd
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:chapter2-quote)'}
-"When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin"
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprd-quote)'}
+When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
 ```
-(ref:chapter2-quote) --- Harold F. Dorn, 1953 [@dorn1953]
+(ref:cprd-quote) --- Harold F. Dorn, 1953 [@dorn1953]
 
-# Primary analysis of lipid regulating agents and dementia {#cprd-analysis}
+# Primary analysis of lipid regulating agents and dementia {#cprd-analysis-heading}
 \minitoc <!-- this will include a mini table of contents-->

### 2020-12-11 06-Chp-IPD-Analysis.Rmd
End of day: -621

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:ipd-quote)'}
-Science knows it doesn't know everything; otherwise, it'd stop
-```
-(ref:ipd-quote) --- Bealy, 2013 [@bealy2013]
-
 # Individual participant data meta-analysis {#ipd-heading}
@@
 
-* Description (including period,numbers, numbers with outcome, etc)
+* Description (including observation period, numbers, numbers with outcome, etc)
 *

### 2020-12-11 97-Discussion.Rmd
End of day: -700
End of day: -621

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
-Science knows it doesn't know everything; otherwise, it'd stop
-```
-
-# Discussion
+# Discussion {#discussion-heading}
 
@@
 One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis).
+IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
 However, access is dependency on an ISAC application to the managing body of the CPRD.

### 2020-12-11 front-and-back-matter/_00-introduction.Rmd
End of day: -700
End of day: -621

@@
 library(ggplot2)
+
+get_words_short <- function(){
+
+files <- list.files(path = here::here(), pattern = "\\.Rmd$")
+
+files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]
+
+words_v <- c()
+
+for (file in 1:length(files)) {
+  tmp <- wordcountaddin::word_count(here::here(files[file]))
+  words_v <- c(words_v, tmp)
+}
+
+words <- sum(words_v)
+
+return(words)
+
+}
 
@@
   dplyr::group_by(date) %>%
-  dplyr::filter(time == max(time))
+  slice(which.max(time)) %>%
+  dplyr::ungroup()
 
@@
 
+words_new_today <- words$words[which(words$date == max(words$date))] - words$words[length(words$words)-1]
+
 target_df <- data.frame(date = c(start_date,max_date),
@@
 
+Words today: `r words_new_today`
+
 &nbsp;

### 2020-12-11 index.Rmd
End of day: -621

--- 2020-11-30 index.Rmd
@@
 title: |
-   Lipids and dementia\
+   Lipids and dementia:\
    An investigation of their relationship
@@
 source('scripts_and_filters/create_chunk_options.R')
-source("R/citations.R")
+source("R/helper.R")
 ```

### 2021-01-05 03-Chp-Systematic-Review-Tools.Rmd
End of day: -3533

@@
 output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
   bookdown::word_document2: 
@@
       reference_docx: templates/word-styles-reference-01.docx
+  bookdown::html_document2: default
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
 documentclass: book
@@
 source("R/doc_options.R")
+source("R/helper.R")
 ```
@@
 They represent an important source of scientific literature.
-A new software program called `medrxivr` was created as part of this thesis to allow researchers to find preprints related to their research in a transparent and reproducible way. 
-Development of this tool was required as part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
+A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way. 
+Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
 
@@
 
-Development of the package followed the
-
-### Success crtieria
-
-Defining success criteria
+### Success criteria
 
@@
 
-### Early version
+### Early versions
 
@@
 <!----------------------------------------------------------------------------->
-## Package infrastructure
+### Package infrastructure
 
@@
 
-## Installation
+### Installation
 
@@
 
-A second key use of the medrxivr package:
-
-* `mx_download()` Takes the output from `mx_search()` and retrieves the full text PDF for each record, saving it to a folder specified by the user.
+A second key use of `medrxivr` is to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
+`mx_download()` takes the list of records included following title and abstract screening, and saves the PDF for each to a folder specified by the user.
+This funcationality is similar to the "Find Full Text" feature offered by EndNote.
 
 ```{r, eval = FALSE}
-mx_download(results,        # Object returned by mx_search()
+mx_download(results,        # Object returned by search, less excluded records
             "pdf/")         # Directory to save PDFs to 
@@
 <!----------------------------------------------------------------------------->
-### Reporting your results
+### Refining your search
 
-One additional function creates a formatted output table with each search strategy presented on an individual line and the number of records associated with this strategy.
+An important argument of the `mx_search()` is XXXX, which creates a formatted output table with each search strategy presented on an individual line and the number of records associated with this strategy.
 
 ```{r, eval = FALSE}
-mx_report(results)
+mx_reporter(results)
 ```
 
-This allows users to discover which aspects of their
+This allows users to discover which aspects of their search is contributing most to the total results returned.
+
+This is crucial as part of developing a search strategy [@bramer2018], as it allows for the key terms related to each topic to be discovered.
 
@@
 
-<!----------------------------------------------------------------------------->
-### Shiny app
+A final part of this tool is the ability to visualise the growth of popularity of a particular topic.
 
-Part of the key theme of accessibility meant creating a web-application that allowed those without any knowledge of the R programming environment to benefit from it's functionality. 
-The app is readily available and has
+**Need to include figures produced by this function here- use the simple search described above**
 
 <!----------------------------------------------------------------------------->
-## Reception and future plans
+## Discussion
+
+Intro text
+
+<!----------------------------------------------------------------------------->
+### Reception and future plans
 
 ```{r, echo = FALSE}
-medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )
+medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d"))
 
@@
 The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times, and the medRxivr app has been visited more than ????), and several use cases have been reported.
-It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in a number of other systematic reviews,[@noone2020] in addition to forming a platform for an analysis of researcher's differing data-sharing tendencies under two different journal models (preprint server vs formal publication).[CITE]
+It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in a number of other systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
 
 Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-^[https://github.com/ropensci/software-review/issues/380]
+^[https://github.com/ropensci/software-review/issues/380] The tool has also been well recieved by the open-source community, demonstrated by the engagement of other developers in contributing to important functionality and suggesting bug-fixes.
 
-Lobbying of the cold springs harbour laboratory has been ongoing.
-This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for performing searches (for example, as of December 2020, downloading a copy of the bioRxiv database takes approximately an hour.)
+Lobbying of the Cold Springs Harbour Laboratory has been ongoing to develop the API further to allow for direct searching of the database.
+This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for performing searches (for example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour).
 
@@
 <!----------------------------------------------------------------------------->
-## Discussion ^[Some of the arguments presented here are repeated in a paper introducing second R package developed during this thesis, but not directly related to it.[@mcguinness] A summary of this second tool, `robvis` is presented in Appendix \@ref(appendix-robvis).]
+### Role of open source tools in evidence synthesis ^[Some of the arguments presented here are repeated in a paper introducing second R package developed during this thesis, but not directly related to the thesis content.[@mcguinness] A summary of this second tool, `robvis`, which creates publication quality risk-of-bias plots, is presented in Appendix \@ref(appendix-robvis).]
 
@@
 As key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords).
-There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - studies or analysis that are not published for a range of reasons, including results that are not deemed "novel" or are not statistically significant.
-This is because simply lowering the barriers to publication may encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]
-It is likely too early, (and too difficult) to tell whether the popularity of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant.
+This is because simply lowering the barriers to publication may well encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]
+It is likely too early (and too difficult) to tell whether the popularity of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 **Of particular interest to this thesis is whether including unpublished preprints in the systematic review and meta-analysis is worthwhile.
@@
 These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] 
-In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts scripts that have a similar, or related, functionality - in fact, in the course of its development, one other researcher that has done so was identified (Nicholas Fraser, author of the `rbiorxiv` package).[@rbiorxiv]
-If these scripts continue to be developed in private and never shared or publicised, this leads to inevitable harm to the evidence synthesis community, not only in terms of duplication of time and effort, but also due to lost collaboration opportunities.
+In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts scripts that have a similar, or related, functionality - in fact, in the course of developing the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package).[@rbiorxiv]
+If these useful scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost collaboration opportunities.
 
@@
 
-[**The next section needs to be reduced and fit a bit better to this Chapter - it was taken from the robvis paper, but the issues it raises are important and potentially relevant here.**]{.correction}
+```{block type='correction'}
+**The next section needs to be reduced and fit a bit better to this Chapter - it was taken from the robvis paper, but the issues it raises are important and potentially relevant here.**
+```
 
@@
 
-* In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex searches in the medRxiv and bioRxiv preprint repositories.
+* In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
 
@@
 
-* I have contrasted `medrxivr` with other other platforms to highlight the added functionality it offers.
+* I have contrasted `medrxivr` with other interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
 I have also discussed its reception to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development.

### 2021-01-05 05-Chp-CPRD-Analysis.Rmd
End of day: -3533

@@
 
+### Study design and protocol
+
+We performed a prospective cohort study using data from the CPRD.
+Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
+All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
+
+An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
+This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).[@vonelm2008]
+
+&nbsp;
+
+### Study Cohort
+
+Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4mmol/L; or an LDL-c test result of >2mmol/L.
+
+These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
+This approach was employed in an attempt to reduce confounding by indication that we would expect to observe in the full cohort, because individuals not prescribed lipid-regulating agents likely be less healthy across a range of variables than those prescribed lipid-regulating agents, leading to a biased association been lipid-regulating agent use and dementia.
+Conditioning entry into the study into the study on being either “at-risk” or already diagnosed with hypercholesterolemia attempts to mitigate this bias.
+
+The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
+Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+
+&nbsp;
+
+### Exposures
+
+We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF)[@wishart2017], namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
+
+A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
+We did however examine how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
+
+&nbsp;
+
+### Outcomes
+
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
+When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1).
+The diagnosis date of the outcome was determined by the first record of a relevant code.
+
+&nbsp;
+
+## Covariates
+
+The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+All
+covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+
+&nbsp;
+
 ### Estimation methods
@@
 Potential biases included time varying confounding, selection bias due to censoring on death and 
-We performed a Cox  test this si to addd some words.
+We performed a Cox
 
@@
 
-**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of differnet code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]
+**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]
+
+In order to
+
+As part of our exploration of the, we chose to explore whether our results were comparable with
+
+As discussed in
+
+## Discussion
+
+## Main findings
+
+Lipid-regulating agents had no effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
+For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+
+&nbsp;
+
+## Comparison to other literature
+
+Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.
+
+&nbsp;
+
+__Statins and all-cause dementia__
+
+A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016a] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
+A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]
+
+These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia.
+However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to a artifical protective effect of statins on all-cause dementia
+
+&nbsp;
+
+__Statins and Alzheimer's disease__
+
+Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80), though the reduction was more extreme than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings, but could not rule out no effect (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
+
+An additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis.[@chu2018]
+
+&nbsp;
+
+__Statins and non-Alzheimer's disease dementia__
+
+Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
+A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis.
+An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
+
+&nbsp;
+
+__Other drug classes__
+
+Apart from statins, few studies examining a lipid-regulating agent have been reported.
+One of the few classes for which data was available were fibrates, which were shown to have no effect on all-cause dementia, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
+
+To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
+
+&nbsp;
+
+## Strengths and Limitations
+
+A major strength of our analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
+In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
+
+However, the findings of our analysis are subject to several limitations.
+There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
+
+Our study may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
+We attempted to address this by limiting inclusion to those either prescribed or “at risk” of being prescribed, which was determined using an elevated test result.
+We also adjusted for several additional potential confounding variables.
+However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that our findings may be biased by residual confounding.
+Important confounding variables for which we have not adjusted could include genetic factors.
+A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of unspecified Alzheimer’s and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020] This finding, combined with the potential for differential misclassification between Alzheimer’s disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.
+
+Finally, there is also the potential for reverse causation in this analysis.
+Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
+
+## Conclusions
+
+We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+We found use of lipid-regulating agents not associated with probable or possible Alzheimer’s disease, but were associated with an increased risk of all-cause, vascular and other dementias.
+In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
+
+We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature.
+However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.

### 2021-01-06 02-Chp-Background.Rmd
End of day: -3533
End of day: -3403

@@
 
+This Chapter will provide an overview of the key exposures, outcomes and methods used throughout this thesis.
+
 ## Dementia
@@
 ###	Diagnosis
-Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
+Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition (is this true, or would it be better to say that there is no gold standard test without an autopsy).
 Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
@@
 Magnetic Resonance Imaging (MRI) scans).
+
+### Criteria
+
+Several scales are commonly used to diagnose dementia and associated diseases for research purposes.
+Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke–Alzheimer Disease and Related Disorders (NINCDS–ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM- **]
+
+**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter \@ref(sys-rev-heading)**
 
@@
 In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
+
+``` {r}
+library(gt)
+library(dplyr)
+
+gt(data = mtcars) %>%
+  tab_style(
+    style = cell_text(weight = "bold"),
+    locations = list(cells_body(
+      columns = vars(mpg)),
+      cells_column_labels(columns = vars(mpg))))
+
+```
 
@@
 As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect.
-Therefore, the statistical power need to detect these associations will often require sample sizes that are unfeasible using primary data collection.
+Therefore, the statistical power need to detect these associations will often require sample sizes that are **unfeasible** using primary data collection.
 This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up.
@@
 
-Include CIND definition here
+*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitivie impairment but who fall below the diagnostic criteria for dementia.
 
@@
 
+The blood profile has a range of lipid fractions to it.
+However, for the sake of this thesis, we will only consider the three most important fractions, namely total cholesterol, low density lipoprotein cholesterol (LDLc), high density lipoprotein cholesterol (HDLc) and trigylcerides (TG).
+
 ### HDL-c
@@
 ### LDL-c
+
+Include formula for working out total cholesterol and the ranges.
+
+LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the :
+
+$$LDLc \approx TC - HDLc - kTG$$
+where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
+
+Limitations to the method include a requirement to fast for 12-14hrs prior to measures, an inability to estimate LDLc if TG levels are high
+
+``` {block type='correction'}
+Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
+```
 
@@
 
-## Evidence synthesis
+### Evidence synthesis
+
+### Primary cohort analysis
 

### 2021-01-06 04-Chp-Systematic-Review.Rmd
End of day: -3533
End of day: -3403

@@
 
+### Sources of heterogeneity
+
+Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
+
 ### Publication bias
 
-* Check if there are protocols available for any of the published reports, and whether there were
+* Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
 * Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st
@@
 
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [ALSO CITE WILKINSON AND MCGUINNESS HERE].
+
+In addition, the a
+
 ### Comparison with other reviews

### 2021-01-13 01-Chp-Introduction.Rmd
End of day: -621
End of day: -3533
End of day

@@
 ---
+
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)'}
+Hold
+```
+(ref:intro-quote) --- Hold
 
@@
 ## Theoretical framework
-The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.
+The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.
 
@@
 
-### Papers under review
+### Papers under review/Preprints
 
@@
 
+### Peer review
+
+* 2 papers for Systematic Reviews
+* 1 paper for Environment International
+* 1 paper for Journal of Clinical Epidemiology
+
 ## Summary

### 2021-01-13 04-Chp-Systematic-Review.Rmd
End of day

@@
 Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
-[@cohen1960: [@gwet2008; @wongpakaran2013]
+[@cohen1960: @gwet2008; @wongpakaran2013]
 
@@
 <!----------------------------------------------------------------------------->
-``` {r gwet-setup, results="hide", message=FALSE}
-```
-
-```{r gwet-table, message=FALSE, results="asis"}
-```
+<!-- # ``` {r gwet-setup, results="hide", message=FALSE} -->
+<!-- # ``` -->
+<!-- # -->
+<!-- # ```{r gwet-table, message=FALSE, results="asis"} -->
+<!-- # ``` -->
 <!----------------------------------------------------------------------------->
@@
 
-```{r agreementtableinter, echo = FALSE}
-```
-
-```{r agreementtableintra, echo = FALSE}
-```
+<!-- # ```{r agreementtableinter, echo = FALSE} -->
+<!-- # ``` -->
+<!-- # ```{r agreementtableintra, echo = FALSE} -->
+<!-- # ``` -->
 
@@
 ### Characteristics of included studies
-
-[This is a test]{.correction}
 
@@
 A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use.
-In addition, there was limited literature available - as discussed in CHapter \@ref()
+In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)
 

### 2021-01-13 reviews/year_2/report.Rmd
End of day

---
output:
  bookdown::word_document2:
    reference_docx: ../../templates/word-styles-reference-01.docx
---

```{r include=FALSE}
## packages
library(tidyverse)
library(kableExtra)
library(flextable)
```

# Annual Review - Year 2 {-}

**Title**:

&nbsp;

**Supervisors**:

* Julian Higgins (Primary)
* Yoav Ben-Shlomo
* Liz Coulthard
* George Davey-Smith

&nbsp;

**Current date**: 19/01/2021

&nbsp;

**PhD Start date**: 01/01/2019

&nbsp;

**Expected submission date**: 01/01/2022

&nbsp;

**Maximum submission date**: 01/01/2023

&nbsp;

**Note:** The content of this report represents a more comprehensive version of that entered into the STaR University of Bristol PGR reporting system.

\newpage

# Overview of PhD
I am on a 3 year PhD funded by an NIHR Doctoral Research Fellowship. I have just entered my third year and expect to finish in January 2021.

&nbsp;

## Rationale

Several existing studies exist. However, there has been no attempt to review the entirity of information related to this research question, regardless of source.

&nbsp;

## Theoretical framework
The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research can address questions that have yet to be answered, or explore existing questions in a way that increases our confidence in the result.

The primary evidence generation aspects of this thesis are performed with the primary intention of providing a further source of evidence for the evidence synthesis/triangulation.

## Aim {#aim}
The central aim of this thesis is to: <br>

* **To investigate the relationship between blood lipid levels and dementia outcomes using **

&nbsp;

## Objectives {#objectives}
In order to achieve this aim this thesis will:

1. Identify all existing on the relationship between blood lipid levels (and interventions that affect blood lipid levels) and dementia
    * The review will include all types of study design including randomised controlled trials, Mendelian randomisation analyses, and non-randomised studies of exposures and interventions.

&nbsp;

2. Examine the relationship between lipid-regulating agents and dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink

&nbsp;

3. To integrate the existing evidence from the review with the primary evidence produced as part of this thesis in a triangulation framewok.

\newpage

# Chapter progress

The thesis is laid out in a similar manner to that successfully defended by Sam Abbott of the MRC IEU ([https://www.samabbott.co.uk/thesis](https://www.samabbott.co.uk/thesis)). Each chapter is self-contained in that it presents the relevant methods and results for that particular analysis, as opposed to having the Methods and Results of an analysis presented in distinct chapters.

The exact order in which chapters are presented is yet to be confirmed - advice on the best way to present this would be appreciated!

**Include Gantt chart here**

## Chapter 1: Introduction

**Overview**

This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis output.

**Progress**

A preliminary draft of this chapter is complete. Additional outputs and  .

&nbsp;

<!----------------------------------------------------------------->
## Chapter 2: Background

**Overview**

This chapter provides an overview of the main topics covered in the thesis, including dementia (prevalence and impact, clinical presentation, diagnostic criteria, treatments), blood lipids fractions (fractions of interest (TC, HDL, LDL, TG), accepted ranges for each), and lipid regulating agents (type (statin vs non-statin), mechanism of action, indications for use).

**Progress**

This chapter is approximately 70% complete.

&nbsp;

<!----------------------------------------------------------------->
## Chapter 3: Tool for systematically searching health-related preprints (medrxiv)
**Overview**
This chapter introduces a tool built to allow for systematic searching of the medRxiv and preprint repositories. The development of this tool was necessitated by the fact that preprints represent an important source of grey literature.

**Progress**

Paper: 100% (Published)
Chapter: 100%

&nbsp;

<!----------------------------------------------------------------->
## Chapter 4: Systematic review

**Overview**

This chapter presents the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/statins and dementia subtypes.

**Progress**

The data extraction stage is complete, and I am in the midst of finalising the few remaining risk-of-bias assessments.

Paper: 80%  
Chapter: 70%

&nbsp;

<!----------------------------------------------------------------->
## Chapter 5: Observational analyses

**Overview**

This chapter uses data from the Clinical Practice Research Datalink (CPRD) to investigate the relationship between statin use and dementia.

This analysis has two motivations: firstly that the availability of the data and secondly, the opportunity to use a separate analytical technique to many of the studies included in the systematic review. As an example, the Hippsley-Cox BMJ paper examining the effect of statins likely suffers from immortal time bias, as exposed and unexposed participants were not followed up from a common point. [CITE].

This analysis has proven challenging likely due to the presence of confounding by indication. The suggestion has been to write up the corresponding paper as an example of the dangers of EHR in cases where strong confounding by indication is likely.

While this limitation is important, it presents a nice opportunity to compare the effect of different analytical strategies with competing directions (immortal time makes statins look better, condounding by indication makes statins look worse) of bias on the same question.

**Progress**

Paper: 80%
Chapter: 80%

&nbsp;

<!----------------------------------------------------------------->
## Chapter 6: Individual patient data meta-analysis

**Overview**

This chapter will use data from several Dementia Platform cohorts (plus some of the cohorts identified through the systematic review) to investigate the relationship between blood lipids levels and dementia outcomes. This analysis has not yet started, but data access has been secured.

**Progress**

This analysis has not yet formally started. Cohorts identified through the systematic review have been invited to participate (though I am sceptical about the chance of response), but regardless I have access to the CPRD data in addition to several DPUK cohorts

&nbsp;

<!----------------------------------------------------------------->
## Chapter 8: Triangulation

**Overview**

This chapter will draw together different sources of information (including the primary analysis performed as part of this thesis) in a triangulation framework, along with a consideration of the key sources/direction of bias in each, to inform.

**Progress**

Not started, though several of the key data sources included the systema

&nbsp;

<!----------------------------------------------------------------->
## Chapter 10: Discussion/limitations/conclusion
**Overview**

This chapter a summary of the main findings of the thesis, a discussion of the strengths and limitations, a roadmap for future work, and a conclusion.

**Progress**

Not started.

\newpage

<!----------------------------------------------------------------->
# Other
## Courses

All training courses planned for the past year have either been cancelled or postponed due to the pandemic. As a resutl, in the review period, I have not taken part in any courses related to my thesis.

&nbsp;

<!----------------------------------------------------------------->
## Conferences/ presentations

In the review period, I have not presented work related to my thesis.

&nbsp;

<!----------------------------------------------------------------->
## Teaching

In the review period, I have taught on the following courses:

* MSc Epidemiology/Public Health "Clinical Epidemiology" module
    * Tutored a small group of several weeks
    * Marked the end-of-module assessments
* Introduction to R short course for new PhD students, Bristol Medical School short course
    * Presented a lecture on advanced R topics (data visualisation, literate programming and web applications)
* Introduction to data visualisation and web applications using R, Bristol Medical School short course
    * Designed and delivered the web applications aspects of the course
    * Tutor helping on practicals on data visualisations and literate programming with Rmarkdown

I also hosted a drop-in "Intro to R" session each Friday in the autumn term to help new students with questions about R.

&nbsp;

<!----------------------------------------------------------------->
## Other work

__COVID-related work__

* *Living review:* As part of national team, I developed and deployed an integrated literature searching and screening pipeline to help a team of national experts produce the first iteration of a living systematic review on the impact of COVID-19 on suicide and self-harm (now published: [https://doi.org/10.12688/f1000research.24274.1](https://doi.org/10.12688/f1000research.24274.1))

* *Rapid review of symptoms:* Through my work on the medrxivr (the preprint search tool described in Chapter 2), I was involved in developing and running preprint searches for a rapid systematic review of COVID-19 symptoms (now published: [https://dx.doi.org/10.2139/ssrn.3582819](https://dx.doi.org/10.2139/ssrn.3582819))

__Evidence synthesis methods__

* *robvis:* A paper describing the risk-of-bias visualisation tool that I developed was published as part of special issue of "Research Synthesis Methods". The tool has now been used ~100 published reviews.

* *PRISMA2020:* I contributed to the updated PRISMA2020 guidelines on the preferred reporting items for systematic reviews and meta-analyses, and am a co-author on two papers describing the new version of this reporting checklist which have been accepted for publication in the BMJ.

__Primary research__

* *Comparison of data availability statements:*
Using medrxivr (the preprint search tool described in Chapter 2), myself and a fellow PhD student compared the

* *Making primary research synthesis-ready:* I acted as last author on a commentary describing the best practice and advatnages for primary researchers in the field of prevention science to ensure that their research is "synthesis-ready" (i.e. can be easily found and integrated into an evidence synthesis project). This commentary is under consideration at "Prevention Science".

\newpage

## References

### 2021-01-13 reviews/year_2/star.Rmd
End of day

---
output:
  bookdown::word_document2:
    reference_docx: ../../templates/word-styles-reference-01.docx
---

```{r include=FALSE}
## packages
library(tidyverse)
library(kableExtra)
library(flextable)
```

# STaR report {#star-report}
## Introduction

**Title**

**Maximum submission date**
01/01/2022

## Looking back
### Research progress

* Chapter 1: Introduction
  * This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis output.

* Chapter 2: Background
  * This is a small introductory chapter to put the thesis into context, lay out the aims and objectives and to propose the idea of a pipeline for MR studies using metabolomics data. I have almost completed this chapter.

* Chapter 3: medrxivr tool for searching preprints
  * A short chapter describing the motivation, development and reception of medrxivr, a tool built to facilitate the systematic searching of the medRxiv and bioRxiv preprint servers. This chapter represents a more comprehensive version of a published manuscript [https://doi.org/10.21105/joss.02651](https://doi.org/10.21105/joss.02651).

* Chapter 4: Comprehensive systematic review
  * This Chapter presents the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/statins and dementia subtypes.
  * Data extraction is complete and I am in the midst of finishing the risk-of-bias assessments.

* Chapter 5: observational analysis: adiposity -> metabolites
  * This chapter uses data from the Clinical Practice Research Datalink (CPRD) to investigate the relationship between statin use and dementia. 
  * This analysis has proven challenging likely due to the presence of confounding by indication. The suggestion has been to write up the corresponding paper as an example of the dangers of EHR in cases where strong confounding by indication is likely.

* chapter 6: Individual patient data meta-analysis
  * This chapter will use data from several Dementia Platform cohorts (plus some of the cohorts identified through the systematic review) to investigate the relationship between blood lipids levels and dementia outcomes. This analysis has not yet started, but data access has been secured.

* Chapter 7: Triangulation
  * This short chapter will draw together different sources of information (including the primary analysis performed as part of this thesis) in a triangulation framework.

* Chapter 8: Discussion
  * This chapter a summary of the main findings of the thesis, a discussion of the strengths and limitations, a roadmap for future work, and a conclusion.

### Training

Due to the pandemic, the majority of the training courses and workshops I had planned to attend during the review period were cancelled. However, I plan to attend the next iteration of each event in the coming year, and have confirmed with my funder that this is possible.

### Presenting your research

In the review period, I have not presented work related to my thesis.

### Public engagement and outreach

### Teaching
I have taught on the following:

* MSc Epi/Public Health "Clinical Epidemiology" module
    * Tutored a small group of several weeks
    * Marked the end-of-module presentations
* Introduction to R short course for new PhD students, Bristol Medical School short course
    * Presented a lecture on the 
    * Tutor helping participants on a data manipulation practical
* Introduction to data visualisation and web applications using R, Bristol Medical School short course
    * Designed and delivered the web applications aspects of the course.
    * Tutor helping on practicals on data visualisations and Rmarkdown.

I also ran an open-door "Intro to R" session each Friday in the autumn term to help new students with questions about R.

### Summary / further comments

None

## Planning ahead
### Research objectives

January-April:

1. Finish systematic review data extraction
1. Complete replication of chapter 5 analysis in INTERVAL and complete write-up of chapter and manuscript
1. Finish chapter 1
1. Finish chapter 3
1. Finish chapter 6

April-June:

1. Finish chapter 2 - systematic review chapter
1. Finish chapter 4 - complete observational analysis and write-up of chapter 4
1. Complete one clustering analysis and begin work on a second and third (chapters 7 and 8)

July-October:

1. Finish chapter 7 second and third clustering analyses
1. Begin writing chapter 8 rules for instrumenting clusters

November-December:

1. Finish chapter 7 and 8
1. Begin final analysis for chapter 9
1. Finish write-up of chapter 9

1. finishing touches to thesis
1. finish outstanding manuscripts
1. Submit

### Planned training and development

I am booked onto the Mendelian Randomisation (17th-19 March) and Advanced Methods for Multiple Imputation (2nd March).

In addition, as per my Fellowship training scheme, I plan to attend the Royal Society "Writing about your research" course.

### Communicating your research

I plan on producing the following outputs from the coming 12 months:

* Comprehensive systematic review
  * preprint/publication
  * poster/presentation at the Alzheimer's Association International Conference (deadline 25th January)
* Primary analysis of the CPRD
  * preprint/publication

## Further comments

None.

### 2021-01-14 reviews/year_2/report.Rmd
End of day

@@
     reference_docx: ../../templates/word-styles-reference-01.docx
+bibliography: ../../bibliography/references.bib
+csl: ../../bibliography/nature.csl
 ---
@@
 library(flextable)
+
+x = 0
 ```
@@
 # Overview of PhD
-I am on a 3 year PhD funded by an NIHR Doctoral Research Fellowship. I have just entered my third year and expect to finish in January 2021.
+<!-- ## Rationale -->
+
+<!-- Several primary studies and systematic reviews exist that seek to examine the relationship between blood lipid levels, or interventions which modify blood lipid levels such as statins, and the subsequent risk of dementia.
+However, as yet, there has been no systematic attempt to find and integrate all available sources of evidence from distinct study designs to address this research question using a triangulation framework.[@lawlor2016a] -->
+
+<!-- This thesis aims to find, critically appraise and synthesize the available evidence related to this research question, and then integrate this with the primary evidence produced as part of this thesis.
+-->
+
+<!-- &nbsp; -->
+
+## Aim {#aim}
+The central aim of this thesis is to: <br>
+
+* **To investigate the relationship between blood lipid levels, and interventions that modify blood lipid levels, and dementia outcomes**
 
@@
 
-## Rationale
+## Objectives {#objectives}
+To achieve this aim, there are several smaller objectives, which map to the proposed chapters of my PhD outline in Section \@ref(chapter-progress):
 
-Several existing studies exist. However, there has been no attempt to review the entirity of information related to this research question, regardless of source.
+1.
+Identify all existing on the relationship between blood lipid levels (and interventions that affect blood lipid levels) and dementia, regardless of study design, and including studies available solely as a preprint.
+
+&nbsp;
+
+2. Examine the relationship between lipid-regulating agents and dementia in a large scale population-based cohort, the Clinical Practice Research Datalink.
+
+&nbsp;
+
+3. Examine the relationship between blood lipid levels and dementia risk in several cohorts as part of a individual participant data meta-analysis.
+
+&nbsp;
+
+4. Integrate the existing evidence from the review with the primary evidence produced as part of this thesis as part of a qualitative triangulation exercise.
 
@@
 ## Theoretical framework
-The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research can address questions that have yet to be answered, or explore existing questions in a way that increases our confidence in the result.
+The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research can address questions that have yet to be answered, or can re-examine existing questions in a way that increases our confidence in the result.
 
-The primary evidence generation aspects of this thesis are performed with the primary intention of providing a further source of evidence for the evidence synthesis/triangulation.
-
-## Aim {#aim}
-The central aim of this thesis is to: <br>
-
-* **To investigate the relationship between blood lipid levels and dementia outcomes using **
+The primary evidence generation aspects of this thesis are performed with the primary intention of providing a further source of evidence for the evidence synthesis/triangulation aspect.
 
@@
 
-## Objectives {#objectives}
-In order to achieve this aim this thesis will:
+\newpage
 
-1. Identify all existing on the relationship between blood lipid levels (and interventions that affect blood lipid levels) and dementia
-    * The review will include all types of study design including randomised controlled trials, Mendelian randomisation analyses, and non-randomised studies of exposures and interventions.
+# Chapter progress {#chapter-progress}
+
+The thesis is laid out in a similar manner to that successfully defended by [Sam Abbott of the MRC IEU](https://www.samabbott.co.uk/thesis).
+Each chapter is self-contained in that it presents the relevant methods and results for that particular analysis, and so there are no dedicated methods chapters.
+
+An overview of the proposed thesis chapters and the way they link together is shown in Figure 1.
+The exact order in which chapters should be presented (particularly Chapters 4, 5 & 6) is yet to be confirmed.
+Any advice from reviewers on this would be appreciated.
 
@@
 
-2. Examine the relationship between lipid-regulating agents and dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
+![](../../figures/chapter_overview.png)
+&nbsp;
+
+__Figure `r (x <- x + 1)`: Overview of thesis chapters and the relationship between them.__
 
@@
 
-3. To integrate the existing evidence from the review with the primary evidence produced as part of this thesis in a triangulation framewok.
+**Include Gantt chart here**
 
-\newpage
-
-# Chapter progress
-
-The thesis is laid out in a similar manner to that successfully defended by Sam Abbott of the MRC IEU ([https://www.samabbott.co.uk/thesis](https://www.samabbott.co.uk/thesis)).
-Each chapter is self-contained in that it presents the relevant methods and results for that particular analysis, as opposed to having the Methods and Results of an analysis presented in distinct chapters.
-
-The exact order in which chapters are presented is yet to be confirmed - advice on the best way to present this would be appreciated!
-
-**Include Gantt chart here**
+&nbsp;
+&nbsp;
 
@@
 
-This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis output.
+This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis outputs (papers/software).
 
@@
 
-A preliminary draft of this chapter is complete. Additional outputs and  .
+A preliminary draft of this chapter is complete. Additional outputs will be added if/when they arise.
 
+&nbsp;
 &nbsp;
@@
 
-This chapter is approximately 70% complete.
+This descriptive chapter is approximately 70% complete.
+
+&nbsp;
+&nbsp;
+
+<!----------------------------------------------------------------->
+## Chapter 3: Tool for systematically searching health-related preprints (medrxivr)
+
+**Overview**
+
+This chapter introduces a tool built in R to allow for systematic searching of the [medRxiv](https://www.medrxiv.org/) and [bioRxiv](https://www.biorxiv.org/) preprint repositories.
+
+Preprints represent an important source of grey literature and so should be included as part of a systematic review, and searching these repositories.
+However, the native search interface on the preprint websites do not allow for complex search strategies (e.g.
+using Boolean operators or wildcards) and are not transparent or repeatable, with the same search producing wildly different numbers of records over time.
+
+To allow for easy systematic searching of this literature souce as part of the systematic review described in Chapter 4, the `medrxivr` tool was developed.
 
@@
 
-<!----------------------------------------------------------------->
-## Chapter 3: Tool for systematically searching health-related preprints (medrxiv)
-**Overview**
-This chapter introduces a tool built to allow for systematic searching of the medRxiv and preprint repositories.
-The development of this tool was necessitated by the fact that preprints represent an important source of grey literature.
-
 **Progress**
 
-Paper: 100% (Published)
-Chapter: 100%
+* Paper: 100% (published)
+* Chapter: 100% (draft)
 
+The code underlying the tool underwent stringent peer review via the rOpenSci review process (you can see the discussion between myself and the reviewers [here](https://github.com/ropensci/software-review/issues/380)), following which a short paper describing the tool was [published in the Journal of Open Source Software](https://joss.theoj.org/papers/10.21105/joss.02651).
+
+This chapter represents an expanded version of the published paper, expanding on the motivation, key functionality, reception and planned future development of the tool.
+A  draft of this chapter is complete.
+
+&nbsp;
+
+__Note:__ evidence synthesis software development has been a key component of my work during my Fellowship.
+At my last APR, Tom Gaunt flagged in his comments that I should consider including some of this work as a chapter in my thesis, if I could tie it in with the thesis as whole.
+Based on this, I am keen to include the medrxivr tool, as it was designed and developed specifically to help with the review described in Chapter 4.
+However, I would be very glad to hear your opinion on whether the inclusion of this work as a chapter makes sense in terms of the thesis as a whole.
+
+<!----------------------------------------------------------------------------->
+
+![](../../figures/sys-rev-tools/medrxiv-role.png)
+
+__Figure `r (x <- x + 1)` - Role of medrxivr in the systematic review process:__ medrxivr contributes to the review process at two key stages: (i) searching of literature sources, and (ii) accessing full text records.
+
+&nbsp;
 &nbsp;
@@
 This chapter presents the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/statins and dementia subtypes.
+The review included all types of study design including randomised controlled trials, Mendelian randomisation analyses, and non-randomised studies of exposures and interventions.
 
@@
 
-The data extraction stage is complete, and I am in the midst of finalising the few remaining risk-of-bias assessments.
+* Literature search (100%)
+* Title and abstract/Full-text screening (100%)
+* Data extraction (100%)
+* Risk of bias assessment (75%)
+* Writing (50%)
 
-Paper: 80%  
-Chapter: 70%
+<!----------------------------------------------------------------->
 
+![](../../figures/sys-rev/prisma_flow.png)
+
+__Figure `r (x <- x + 1)` - PRISMA flow diagram showing the movement of records through the systematic review.__
+
+&nbsp;
+<!----------------------------------------------------------------->
+
+The review .
+Using other published reviews to verify the results demonstrated that the search was sufficiently comprehensive to capture all previously identified studies, plus some studies that had not been included in any previous review.
+
+Data extraction has been completed for the 1-5 studies included in the review and
+
+As dual screening and extraction is recommended for systematic reviews, this element of my thesis has involved a number of external researchers.
+I have found the people-management aspect of the review challenging, but it has provided good experience in terms of leading a review team.
+
+For space, and to illustrate the proposed triangulation below
+
+&nbsp;
+
+**Added value**
+
+One of the take-aways from my last APR was to make the "added value" of this work beyond existing review clear.
+I believe there are two aspects where this review adds value above what is already available in the published literature:
+
+* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
+As part of this review, I have not only performed a original search of primary literature databases, but have also searched the reference lists of comparable reviews to ensure no study has been omitted.
+* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.ROBINS-I/E).
+This is important area in which this thesis can add value, as based on the risk of bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
+
+&nbsp;
 &nbsp;
@@
 
-This analysis has two motivations: firstly that the availability of the data and secondly, the opportunity to use a separate analytical technique to many of the studies included in the systematic review.
-As an example, the Hippsley-Cox BMJ paper examining the effect of statins likely suffers from immortal time bias, as exposed and unexposed participants were not followed up from a common point.
-[CITE].
-
-This analysis has proven challenging likely due to the presence of confounding by indication.
-The suggestion has been to write up the corresponding paper as an example of the dangers of EHR in cases where strong confounding by indication is likely.
-
-While this limitation is important, it presents a nice opportunity to compare the effect of different analytical strategies with competing directions (immortal time makes statins look better, condounding by indication makes statins look worse) of bias on the same question.
+Rather than reproduce the methods/findings here, I have attached the initial draft of the paper this chapter is based on at the end of this report.
 
@@
 
-Paper: 80%
-Chapter: 80%
+* Paper: 80%
+* Chapter: 80%
 
+In relation to the results presented in the attached paper, there are two key discussion points.
+The first is that while statins are associated with a slight reduction in the risk of probable AD (HR: 0.91, 95%CI: 0.88-0.95) and possible AD (HR: 0.95, 95%CI: 0.92-0.99), we still see an increased risk of vascular dementia (HR: 1.7, 95%CI: 1.62-1.77) and other dementia (HR: 1.7, 95%CI: 1.62-1.77) in those using statins.
+This reflects the initial findings of this analysis presented at the last APR, and was not attenuated even after using multiple imputation to account for potential selection bias caused by the original complete case analysis and accounting for several potentially important confounders.
+
+Secondly, following a recommendation by a co-author to use the same analysis strategy with a known control (coronary heart disease; CHD), we found that statins appeared to increase the risk of CHD, in contrast to the the results of large RCTs.
+This finding suggests the presence of substantial confounding by indication, in that those who go on to take a statin are fundamentally different from those who do not, and has been replicated in other standard mulitvariable HR analyses.[@danaei2013a] A suggested approach to frame this (possible insurmountable) issue has been to rewrite the paper as an example of the dangers of using EHR in cases where strong confounding by indication is likely.
+However, it would be particularly useful to get reviewers feedback on any further analytical strategies we could attempt to address this issue.
+
+In terms of the broader thesis, while this limitation is important, it presents a good opportunity to compare the effect of different analytical strategies with competing directions of bias (immortal time bias makes statins look better, confounding by indication makes statins look worse) of bias on the same underlying question.
+
+Finally, in an attempt to assess whether these (likely spurious) findings for vascular dementia are a product of the CPRD data or our analytical strategy, we recently attempted to replicate an analysis performed by Smeeth et al.
+in the THIN EHR database which found a protective effect of statins on dementia risk (HR 0.81, 99% CI 0.69-0.96).[@smeeth2009a] However, following correspondence with the author team to acquire the code-list they used to define dementia cases, we confirmed that it was substantially different from that used in our study.
+This fact, coupled with concerns over their analytical strategy (which seemed to adjust for covariates on the causal pathway), limited the value of this attempted replication.
+
+&nbsp;
+
+**Added value**
+
+Similar to the systematic review, feedback from my last APR suggested that the "added value" of this study above those that already exist should be made clearer.
+
+There are two particular:
+* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies included in the review, this CPRD analysis would be one of the largest studies of this research question.
+* _Addressing the limitations of other observational analyses:_ Analysing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
+
+&nbsp;
 &nbsp;
@@
 
-This analysis has not yet formally started.
-Cohorts identified through the systematic review have been invited to participate (though I am sceptical about the chance of response), but regardless I have access to the CPRD data in addition to several DPUK cohorts
+This analysis has not yet formally started, though access to several DPUK cohorts has been secured.
+Cohorts identified through the systematic review have also been invited to participate (though I am sceptical about the chance of response).[@nevitt2017]
 
+&nbsp;
 &nbsp;
@@
 <!----------------------------------------------------------------->
-## Chapter 8: Triangulation
+## Chapter 7: Triangulation
 
@@
 
+As flagged in my last APR, this chapter will make clear that "triangulation" in the context of my thesis is a qualitative integration of the distinct evidence sources available (systematic review, CPRD study, IPD meta-analysis).
+
 **Progress**
 
-Not started, though several of the key data sources included the systema
+Not started.
 
+&nbsp;
 &nbsp;
@@
 <!----------------------------------------------------------------->
-## Chapter 10: Discussion/limitations/conclusion
+## Chapter 8: Discussion/limitations/conclusion
 **Overview**
 
-This chapter a summary of the main findings of the thesis, a discussion of the strengths and limitations, a roadmap for future work, and a conclusion.
+This chapter a summary of the main findings of the thesis, a discussion of the strengths and limitations of the work presented, a roadmap for future work, and a conclusion.
 
@@
 All training courses planned for the past year have either been cancelled or postponed due to the pandemic.
-As a resutl, in the review period, I have not taken part in any courses related to my thesis.
+As a result, in the review period, I have not taken part in any courses related to my thesis.
+
+However, in the coming year, I plan to attend the "Mendelian randomisation" and "Advanced methods for multiple imputation" short courses at the University of Bristol, in addition to the "Causal Inference in Epidemiology: Recent Methodological Developments" short course at LSHTM and the "Writing about your research" course at the Royal Society.
 
@@
 
-In the review period, I have not presented work related to my thesis.
+In the review period, I presented on the preprint search tool described in Chapter 3 at the Bristol  "Autosynthesis Club" and "Methods in Evidence Synthesis" seminars.
+
+It's only in writing this report that I realised that I am yet to present on the other parts of my thesis, and so this is a particular aspect of my PhD that I would like to develop further in the coming year.
+As such, I aim to present at more diverse events in the coming year, including at an IEU monthly meeting and the Faculty of Health Sciences research showcase.
+
+In addition, I plan to submit an abstract to the Alzheimer's Association International Conference in July (deadline 25th January).
 
@@
 
-In the review period, I have taught on the following courses:
+In the review period, I have gained the following teaching experience:
 
@@
     * Tutor helping on practicals on data visualisations and literate programming with Rmarkdown
+* Drop-in "Intro to R" sessions
+    * Organised and ran an hour long session each Friday in the autumn term to help answer new PGR students' questions about R.
 
-I also hosted a drop-in "Intro to R" session each Friday in the autumn term to help new students with questions about R.
+I have also submitted a proposal to supervise an MSc student for the summer term.
+The project aims to examine the overlap between the set of primary studies included in the several existing systematic reviews of blood lipid levels and dementia (as mentioned in the description of Chapter 4, above).
 
-&nbsp;
+\newpage
 
 <!----------------------------------------------------------------->
-## Other work
+# Other work
 
@@
 
-* *Living review:* As part of national team, I developed and deployed an integrated literature searching and screening pipeline to help a team of national experts produce the first iteration of a living systematic review on the impact of COVID-19 on suicide and self-harm (now published: [https://doi.org/10.12688/f1000research.24274.1](https://doi.org/10.12688/f1000research.24274.1))
+* *Living review:* In early March, I developed and deployed an integrated literature searching and screening pipeline to help a team of national experts produce the first iteration of a living systematic review on the impact of COVID-19 on suicide and self-harm (now published: [https://doi.org/10.12688/f1000research.24274.1](https://doi.org/10.12688/f1000research.24274.1)).
+Maintenance of this pipeline took up a lot of my time - however, following discussions with my primary supervisory, in late summer, I handed over responsibility to another member of the team.
 
-* *Rapid review of symptoms:* Through my work on the medrxivr (the preprint search tool described in Chapter 2), I was involved in developing and running preprint searches for a rapid systematic review of COVID-19 symptoms (now published: [https://dx.doi.org/10.2139/ssrn.3582819](https://dx.doi.org/10.2139/ssrn.3582819))
+* *Rapid review of symptoms:* Through my work on medrxivr (the preprint search tool described in Chapter 2), I was involved in developing and running preprint searches for a rapid systematic review of COVID-19 symptoms (now published: [https://dx.doi.org/10.2139/ssrn.3582819](https://dx.doi.org/10.2139/ssrn.3582819))
 
@@
 
-* *robvis:* A paper describing the risk-of-bias visualisation tool that I developed was published as part of special issue of "Research Synthesis Methods".
+* *robvis:* A paper describing the risk-of-bias visualisation tool I developed was published as part of special issue of "Research Synthesis Methods" ([https://doi.org/10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)).
 The tool has now been used ~100 published reviews.
@@
 * *Comparison of data availability statements:*
-Using medrxivr (the preprint search tool described in Chapter 2), myself and a fellow PhD student compared the
+Using medrxivr (the preprint search tool described in Chapter 2), myself and a fellow PhD student compared the availability of data for the same manuscript when published under two different data-sharing policies (i.e.
+that of the preprint repository vs.
+the peer-reviewed journal).
+The preprint of the study is available [here](https://doi.org/10.31222/osf.io/p75xe).
 
@@
 can be easily found and integrated into an evidence synthesis project).
-This commentary is under consideration at "Prevention Science".
+This commentary is under consideration at "Prevention Science" and a preprint is available [here](https://doi.org/10.31222/osf.io/ptg9j).
 
@@
 
-## References
+## Report references
+
+<div id="refs"></div>
+
+\newpage
+
+## Draft of CPRD paper

### 2021-03-10 01-Chp-Introduction.Rmd
All working again after the update to Pandoc

@@
 output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::html_document2: default
   bookdown::word_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
 documentclass: book
@@
 \minitoc <!-- this will include a mini table of contents-->
-
-<!--
-The {#rmd-basics} text after the chapter declaration will allow us to link throughout the document back to the beginning of this chapter.
-Reference labels will automatically be generated if you don't specify them, as the lowercase title with spaces replaced by hypens (e.g.
-r-markdown-basics).
-Look for the reference to this label at the beginning of the next chapter.
--->
 

### 2021-03-10 02-Chp-Background.Rmd
End of day
All working again after the update to Pandoc

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)'}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
 Science knows it doesn't know everything; otherwise, it'd stop.
@@
 \minitoc <!-- this will include a mini table of contents-->
+
+## Lay summary
+
+## Introduction
+
+> This chapter provides the context of the thesis.
+It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality.
+The chapter briefly explores different measures of increased adiposity and potential hypotheses for underlying aetiology of diseases associated with increased adiposity.
+Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed.
+*From Matt Lee's thesis.*
 
@@
 As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect.
-Therefore, the statistical power need to detect these associations will often require sample sizes that are **unfeasible** using primary data collection.
+Therefore, the statistical power need to detect these associations will often require sample sizes that are unfeasible using primary data collection.
 This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up.

### 2021-03-10 03-Chp-Systematic-Review-Tools.Rmd
All working again after the update to Pandoc

@@
 output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::word_document2: 
@@
   bookdown::html_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
 documentclass: book
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)'}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = TRUE}
 Why are open source statistical programming  
@@
 
-# medrxivr: an R package for performing systematic searches of health-related preprints {#sys-rev-tools-heading}
+# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 source("R/helper.R")
+library(medrxivr)
 ```
@@
 <!----------------------------------------------------------------------------->
+
+## Main points (to be removed)
+
+The main points I want to get across in this Chapter are:
+
+* Why searching preprints is important
+
+* Why existing methods are not sufficient
+
+* What the medrxivr tool adds
 
@@
 Preprints represent an increasingly important source of scientific information.
-Authors can use preprint servers for several purposes - to establish primacy when submitting to a journal where a the peer-review process may take several months; to post complete manuscripts that will never be formally published,[CITE] such as those reporting updated case reports during the COVID-19 pandemic;[CITE] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias, or the "file-drawer" effect.
+Defined by the The Committee on Publication Ethics (COPE) as ‘a scholarly manuscript posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process’[@committeeonpublicationethicscope2018], preprints serve several purposes.
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
-As a result, preprint repositories should be considered an distinct but complementary information source when reviewing the evidence base as part of a systematic review.
+As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
 The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]
 
-Preprints represent a particularly important to this thesis, ias one of the primary types of evidence that I planned to use in the triangulation exercise (Mendelian randomization (MR)) is still developing and many MR studies that look at the clinical question that this project aims to investigate are posted as preprints on the bioRxiv, and more recently medRxiv, preprint servers.
-Being able to systematically search these records for the purpose of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity.
-In light of the above, the `medrxivr` R package was created in order to facilitate the searching of this data source.
+Being able to systematically search these preprints for the purpose of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
 
-More generally, developing new tools for facilitating evidence synthesis will benefit patients by speeding up the speed with which systematic reviews are produced.
-A recent study put the mean duration of a systematic review project, from date of registration to date of publication is 67.3 weeks.[@borah2017] A large proportion of this time will be spent on manual tasks such as running searches and extracting records, title and abstract screening, and data extraction - therefore, efforts to increase the efficiency of the process should focus on process that can be automated.
+At present, the medRxiv website allows only simple search queries as opposed to the often complex Boolean logic that information specialists use to query other major databases.
+Additionally, previous extraction mechanisms for obtaining the results of searches from medRxiv were to go through each record, one-by-one, downloading individual citations.
+As the scale of the medRxiv database increases, particularly in light of the massive expansion of the repository as a result of COVID, this already time-consuming and error-prone method is not longer feasible.
 
-In addition, we need to focus on developing tools that allow systematic, reproducible access to more informal sources of scientific material. One key emerging source
-
-Searching pre-print repositories is becoming an increasingly important part of a systematic review.
-Preprints - unpublished versions of manuscripts, frequently uploaded to a repository at the same time they are submitted to a journal for peer review - represent an important source of grey literature.
-As the barriers and time to publication are both lower, they also represent an important source of information that may be either currently tied up in the peer-review process
-
-At present, medRxiv allows only simple search queries, as opposed to the often complex Boolean logic that information specialists use to query other major databases.
-Additionally, record metadata (titles/abstracts/author lists) must be accessed individually, rather than in batches, meaning that downloading relevant records for title and abstract screening a time consuming task.
-
-This chapter outlines the development and key functionality of `medrxivr (version 0.2)`.
-The motivating factors that necessitated the development of this tool as part of this thesis are discussed.
-The use of medrxivr in external projects and by other researchers is discussed.
+This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv preprints.
+The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
 As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
-
-Current extraction mechanisms for extracting the results of searches from medRxiv are to go through each record, one-by-one, downloading individual citations.
-As the scale of the medRxiv database increases, particularly in light of the massive expansion as a result of COVID, this alreay time-consuming and error-prone method is not longer feasible.
+The GitHub repository^[Available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
 
@@
 (ref:medrxivr-sr-cap) __Role of `medrxivr` in a systematic review workflow:__ `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
-Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to faciliate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
+Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
 
@@
 ```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
-knitr::include_graphics(file.path("figures/UoBcrest.pdf"))
+knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
 ```
@@
 
-### Success criteria
+### Success criteria {#success-criteria}
 
-The tool was developed to meet three success criteria,[@wateridge1995] created both from the list of functionality needed to perform the systematic searches as part of the review in Chapter \@ref(sys-rev-heading) and from an informal survey of colleagues and the evidence synthesis and health librarians on Twitter.
+The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform the systematic searches as part of the review in Chapter \@ref(sys-rev-heading) and from an informal survey of colleagues and the evidence synthesis and health librarian community on Twitter.
 These criteria were as follows:
 
-1. reliable, reproducible and transparent search functionality, allowing for similar Boolean (AND/OR/NOT) operator logic as that available from other literature search platforms such as OvidSP;  
-2. support for bulk export of references returned by the search to a file type that can be imported into a reference manager (e.g., .bib  or .ris);  
+1. reliable, reproducible and transparent search functionality, allowing for Boolean (AND/OR/NOT) operator logic;
+
+2. support for bulk export of references returned by the search to a file type that can be imported into a reference manager (e.g., _.bib_  or _.ris_); and
+
 3. automated retrieval of the full-text PDFs of relevant records.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+### Alternative medRxiv/bioRxiv interfaces
+
+Prior development of this tool, an informal audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted.
+While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
+
+The first, a platform called Rxivist [@abdill2019], allows users to search preprints from the using keywords.
+Similar to `medrxivr`, this tool previously scrapped data straight from the medRxiv and bioRxiv websites but as of November 2020, Rxivist also provided access to Cold Spring Harbor API.
+However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
+The search interface^[Available at https://rxivist.org/] does not allow for complex search strategies using Boolean operators, and there is no option to batch-export the results of a search.
+
+The second, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues using post-publication peer-review such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
+As such, the platform only returns the most recent `r comma(1000)` records by publication date.
+
+Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records which is required for the full-text screening stage of a systematic review.
+
+&nbsp;
 
@@
 
-Work on this element began in Summer 2019, and initially existed as a collection of scripts built to allow for searching medRxiv and bioRxiv as part of the systematic search outline in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the ad-hoc web-scraping scripts, the initial version of the `medrxivr` package was released in February 2020.
-Additional development work took place, allowing for improved searching and exporting function
-
-The updates to the systematic search to capture new literature published since the last search was performed with the fully developed package.
+Work on this tool began in Summer 2019, which initially existed as a collection of scripts built to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
+Following interest from other researchers in using the _ad-hoc_ web-scraping scripts, the initial version of the `medrxivr` package was released in February 2020.
+Additional development work took place in 2019/2020, allowing for improved searching and exporting functionality.
 
@@
 Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992].
-In the case of early versions of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the medRxiv website was regularly updated.
+In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the medRxiv website was regularly updated.
 
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the medrxivr package to engage in "fault prevention" and work towards a more robust interface with the available data.[@laprie1992]
+However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data.[@laprie1992]
 
 Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible papers for the review detailed in Chapter \@ref(sys-rev-heading) required expansion to allow for similar searching of the bioRxiv repository.
+
+&nbsp;
 
@@
 
-The `medrxvir` package was written in R using RStudio, and followed development best-practice, including complete and information documentation, a robust unit testing framework (99% of all code lines within the package are formally tested under this framework) across multiple platforms including Windows, MacOS, and Linux, and in-depth code review by two experienced, independent reviewers.
+The `medrxvir` package was written in R using RStudio,[@rcoreteam2019] and followed development best-practice, including detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
 
-An automatically generated documentation website is also generated on each update to the code-base. ^[https://docs.ropensci.org/medrxivr/]
+&nbsp;
 
@@
 
-* An interface to the Cold Springs Harbor Laboratory API, which allows the wholesale import of the medRxiv and bioRxiv metadata
+* An interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
 * A collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
 
-The standard workflow is to download a copy of the preprint repository metadata, and then run your searchers locally.
-This is a workaround as the Cold Springs Harbor Labratory API does not provide any functionality to search the database.
+The standard workflow is to download a copy of the metadata, and then run your searchers locally.
+This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.
+
+&nbsp;
 
@@
 
-Alternatively, the development version of the pacakage can be installed from GitHub:
+Alternatively, the development version of the package can be installed from GitHub:
+&nbsp;
 
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
@@
 
-`medrixvr` provides two ways to access medRxiv data.
+`medrixvr` provides two ways to access medRxiv data. The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
 
-`mx_api_content(server = "medrxiv")` creates a local copy of all data available from the medRxiv API at the time the function is run.
+&nbsp;
 
@@
 # Get a copy of the database from the live medRxiv API endpoint
-preprint_data <- mx_api_content()  
+mx_data <- mx_api_content()  
 ```
 
-As an alternative to downloading a copy fo the database from the API in realtime, the `mx_snapshot()` function provides access to a maintained static snapshot of the database.
-The snapshot is created each morning at 6am.
-This method, which doet not rely on the API, was created as during development e unavailable during peak usage times) and has the additional advantage of being faster, as it reads data from a comma-seperated file rather than having to re-extract it from the API.
+&nbsp;
 
-The relationship between the two methods for accessing the data conatined in the medRxiv database is summarized in the figure below:
-
-(ref:medrxivr-data-sources-cap) __Overview of `medrxivr` data sources:__ Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
-Note: due to the size of bioRxiv, a maintained snapshot of medrxiv is available via `mx_snapshot()`.
-
-(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources
-
-```{r medrxivr-data-sources, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
-```
-
-<!----------------------------------------------------------------------------->
-### Performing a search
-
-Once a local copy of the database has been created, the functions in the `medrxivr` package then facilitate users in working with this dataset. There are two main functions and a helper function:
-
-* `mx_search()`: Enables users to search the preprint data, using regular expressions and Boolean logic.
+The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am.
+This method removes the dependency on the API which can become unavailable during peak usage times.
+The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
 
@@
 ```{r, eval = FALSE}
+# Import a copy of the medRxiv data from the snapshot
+mx_data <- mx_snapshot()
+```
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+(ref:medrxivr-data-sources-cap) __Overview of `medrxivr` data sources:__ Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
+Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
+
+(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources
+
+```{r medrxivr-data-sources, fig.pos="!h", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
+```
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Performing a search
+
+The first step is to create your search strategy. Terms to be combined with the OR operator are contained in vectors, while topics to be combined with the AND operator are contained in lists.
+
+&nbsp;
+
+```{r, eval = TRUE}
+# Create the search query
 topic1  <- c("dementia","alzheimer's")  # Combined with OR
@@
 myquery <- list(topic1, topic2)         # Combined with AND
-
-results <- mx_search(myquery)
 ```
@@
 
-Additional functionality allowing common syntax used by systematic reviewers and health librarians, including the use of NEAR statements (which allows for ),
+For example, the search above written in standard syntax would be: "((dementia __OR__ alzheimer's) __AND__ (lipids __OR__ statins))".
+
+Once a local copy of the database has been created and your search strategy has been defined, both are passed to the `mx_search()` function.
+
+&nbsp;
+
+```{r, eval = FALSE}
+# Run the search
+results <- mx_search(mx_data,
+                     myquery)
+```
+
+&nbsp;
+
+The search also supports common syntax used by systematic reviewers and health librarians, including the use of NEAR statements (which allows for identification of co-localised terms) and wildcards (which allow for alternate spellings, e.g.
+"randomi*s*ation" vs "randomi*z*ation").
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+### Refining your search
+
+An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.
+
+&nbsp;
+
+```{r, eval = FALSE}
+results  <- mx_search(mx_data,
+                      c("dementia", "alzheimer's"),
+                      report = TRUE)
+```
+
+```{r, eval = FALSE}
+## Found 203 record(s) matching your search.
+## Total topic 1 records: 203
+## dementia: 203
+## Total topic 2 records: 0
+## alzheimer’s: 0
+```
+
+&nbsp;
+
+This allows users to discover which aspects of their search is contributing most to the total results returned.
+This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
+
+&nbsp;
 
@@
 
-In line with the second success criteria, one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
+In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
 While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is
@@
 mx_export(results, 
-          file = "medrxiv_export.bib")
+          file = "medrxiv_export.bib",
+          report = TRUE)
 ```
+
+&nbsp;
 
@@
 
-A second key use of `medrxivr` is to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
-`mx_download()` takes the list of records included following title and abstract screening, and saves the PDF for each to a folder specified by the user.
-This funcationality is similar to the "Find Full Text" feature offered by EndNote.
+Finally, `medrxivr` allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
+`mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
+This functionality is similar to the "Find Full Text" feature offered by EndNote.
+
+&nbsp;
 
 ```{r, eval = FALSE}
-mx_download(results,        # Object returned by search, less excluded records
+mx_download(results,  # Object containing included records
             "pdf/")   # Directory to save PDFs to 
@@
 
-<!----------------------------------------------------------------------------->
-### Refining your search
-
-An important argument of the `mx_search()` is XXXX, which creates a formatted output table with each search strategy presented on an individual line and the number of records associated with this strategy.
-
-```{r, eval = FALSE}
-mx_reporter(results)
-```
-
-This allows users to discover which aspects of their search is contributing most to the total results returned.
-
-This is crucial as part of developing a search strategy [@bramer2018], as it allows for the key terms related to each topic to be discovered.
-
-### Visualising your results
-
-A final part of this tool is the ability to visualise the growth of popularity of a particular topic.
-
-**Need to include figures produced by this function here- use the simple search described above**
+&nbsp;
 
@@
 
-Intro text
-
-<!----------------------------------------------------------------------------->
 ### Reception and future plans
@@
 
-The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times, and the medRxivr app has been visited more than ????), and several use cases have been reported.
-It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in a number of other systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
+The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
+It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
 
 Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-^[https://github.com/ropensci/software-review/issues/380] The tool has also been well recieved by the open-source community, demonstrated by the engagement of other developers in contributing to important functionality and suggesting bug-fixes.
+^[https://github.com/ropensci/software-review/issues/380] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
 
-Lobbying of the Cold Springs Harbour Laboratory has been ongoing to develop the API further to allow for direct searching of the database.
-This would negate the current need to download a full copy of the relevant preprint database before searching it locally, which is currently the rate limiting step for performing searches (for example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour).
+Lobbying of the Cold Springs Harbor Laboratoryto develop the API to allow for direct searching of the database has been ongoing.
+This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
+For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.
+
+&nbsp;
 
 <!----------------------------------------------------------------------------->
-### Comparison with other medRxiv/bioRxiv interfaces
+### Limitations of `medrxivr`
 
-Prior development of `medrxivr`, an informal audit of comparable tools search tools were considered as part of a audit of existing tools for accessing the metadata of records stored on the medRxiv and bioRxiv servers.
-Two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
+While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
+However, this approach ethos other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
+A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
 
-The first, a platform called Rxivist [@abdill2019], allows users to search preprints from the using keywords.
-Similar to `medrxivr`, this tool previously scrapped data straight from the medRxiv and bioRxiv websites but as of November 2020, Rxivist also provides access to Cold Spring Harbour API.
-However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface^[Available at https://rxivist.org/] does not allow for complex search strategies, and there is no option to batch-export the results of a search.
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 
-The second, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues using post-publication peer-review such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
-As such, the platform only returns the most recent `r comma(1000)` records by publication date.
-
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records which is required for the full-text screening stage of a systematic review.
+&nbsp;
 
 <!----------------------------------------------------------------------------->
-### Role of open source tools in evidence synthesis ^[Some of the arguments presented here are repeated in a paper introducing second R package developed during this thesis, but not directly related to the thesis content.[@mcguinness] A summary of this second tool, `robvis`, which creates publication quality risk-of-bias plots, is presented in Appendix \@ref(appendix-robvis).]
+### Role of open source tools in evidence synthesis
 
-The development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis process.
+_Not sure where this should go, but keen to include it_
 
-While searching of the medRxiv database was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-As key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords).
-There is the potential that the cross-section of literature posted on medrxiv would be substantially different from the true grey literature - studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant.
-This is because simply lowering the barriers to publication may well encourage authors to published "null" results,[CITE] but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[CITE]
-It is likely too early (and too difficult) to tell whether the popularity of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-**Of particular interest to this thesis is whether including unpublished preprints in the systematic review and meta-analysis is worthwhile.
-To this end, the additional contribution of searching these repositories to the systematic review element of this thesis is explored in Chapter \@ref(sys-rev-heading) [CROSS].**
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b;@mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 
-By implementing the tool described above as both as an R package and a `Shiny` web app, the functionality is available to evidence synthesists with varying levels of ability in R. 
-These tools serve as an example of the advantages of “packaging” the R scripts that evidence synthesists often create for personal use.[@wickham2015r] 
-In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts scripts that have a similar, or related, functionality - in fact, in the course of developing the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package).[@rbiorxiv]
-If these useful scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost collaboration opportunities.
-
-Creating and sharing well-documented packages, the recognised standard for sharing reproducible and useful code, represents one way to reduce this inefficiency.
-Progressing this argument further, `Shiny` apps represent a efficient way to provide a user-friendly interface for newly created R packages within a very short time-frame, expanding the potential pool of users of the package to anyone with an internet connection.
-
-```{block type='correction'}
-**The next section needs to be reduced and fit a bit better to this Chapter - it was taken from the robvis paper, but the issues it raises are important and potentially relevant here.**
-```
-
-In addition
-Creating a package using R has a number of advantages unique to the R programming environment.
-R provides access to a range of powerful tools including the `ggplot` infrastructure for creating publication-quality plots, and RMarkdown, which enables creation of documents that can be rendered in a range of formats such as PDF, HTML, or Word.[@xie2018r] Furthermore, and focusing specifically on evidence synthesis, building new tools as packages in R allows for easy integration with the range of existing evidence synthesis packages.
-Recently, the `metaverse` project,[@variousauthors2020] of `medrivr` is a part, has begun to curate a collection of R packages that cover different aspects of the systematic review and meta-analysis process which, when taken together, form a coherent end-to-end open-source alternative to commercial offerings such as Covidence or Review Manager.
-Key offerings in this suite of packages include `litsearcher`, which facilitates systematic search strategy development, `revtools`, a package for managing the review process and performing title and abstract screening, `metaDigitise`, a package for automatic extraction of data from figures in research papers, and `metafor`, a package for conducting meta-analyses in R.[@grames2019automated; @metaforref; @pick2018; @westgate2019revtools]
+&nbsp;
 
@@
 
-* I have contrasted `medrxivr` with other interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed its reception to date, its place in the broader evidence synthesis in R ecosystem, and a roadmap for its future development.
+* I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
+I have also discussed the tools reception to date, a roadmap for its future development and its place in the broader evidence synthesis in R ecosystem.

### 2021-03-10 04-Chp-Systematic-Review.Rmd
All working again after the update to Pandoc

@@
 
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)'}
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = TRUE}
 "It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
@@
 
-# Systematic review and triangulation of available evidence {#sys-rev-heading}
+# Systematic review of all available evidence {#sys-rev-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 * Look at whether searching preprints made any difference to my results
+* Could apply ROBIS to previous reviews to see how they stack-up?
 
@@
 ## Results
+
+### Previous reviews
+
+__Will need to include something in the methods section on this__
+
+As part of this analysis, we examined the overlap between different published reviews on this topic.
+
+Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
+
+Put upSet plot here.
+
+An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
+
+Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
+So for example, XXXX records were captured both by the XXXX review and the XXXX review.
+
+Where the matrix has just a single point highlighted, this shows the records unique to that review.
+
+The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
+
+Our review is presented as the last point on this plot, and captured XXXX records
+
+The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
+The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
 

### 2021-03-10 05-Chp-CPRD-Analysis.Rmd
All working again after the update to Pandoc

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprd-quote)'}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = TRUE}
 When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
 ```
-(ref:cprd-quote) --- Harold F. Dorn, 1953 [@dorn1953]
+(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]
 
 # Primary analysis of lipid regulating agents and dementia {#cprd-analysis-heading}
+
 \minitoc <!-- this will include a mini table of contents-->

### 2021-03-10 06-Chp-IPD-Analysis.Rmd
End of day: -3533
All working again after the update to Pandoc

@@
 * Description (including observation period, numbers, numbers with outcome, etc)
+* Whether they are a known genetically at-risk cohort
 *
-*
+
+### Epic Norfolk
+
+The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]
 
@@
 ```
+
+Different approaches to combining subgroups. [@fisher2017]
+
+## Discussion
+
+Letters sent to
+
+This is likely due to my junior position as a ECR
+
+Range of reasons why

### 2021-03-10 front-and-back-matter/99-appendices.Rmd
End of day: -3533
All working again after the update to Pandoc

@@
 <!----------------------------------------------------------------------------->
+
 # Other Appendix {#other-appendix-heading}
@@
 This thesis was written in RMarkdown.
-Several R packages were used as part of this project.`r gen_rmd_citation()`
+Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]
 
-## Producing risk-of-bias visualisation with `robvis` {#appendix-robvis}
+## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
 
@@
 Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
-A convenient plot in many reviews is a “traffic light” plot, which tabulates the judgement for each study in each domain.
+A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain.
 For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
@@
 Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane’s Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
+While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
 Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
@@
 The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN ([https://cran.r-project.org/package=robvis](https://cran.r-project.org/package=robvis)); or access and contribute to the development version via GitHub ([https://github.com/mcguinlu/robvis](https://github.com/mcguinlu/robvis)).
+Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).
 
@@
 This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
-The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness;@simillis2020; @tanneru2020]
+The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]
 
@@
 
--> NEED TO ADD DATA HERE!
+-\> NEED TO ADD DATA HERE!
 
-&nbsp;
-
-``` {r, eval = FALSE}
+```{r, eval = FALSE}
 
@@
 
-``` {r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
+```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
 
@@
 
-``` {r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
+```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
 
@@
 
-``` {r robvisarguments, echo = FALSE, eval = TRUE}
+```{r robvisarguments, echo = FALSE, eval = TRUE}
 
@@
 
-robvis_downloads <- plyr::round_any(sum(robvisstats$count),100, f = floor)
+robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)
 
@@
 As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times.
-It has been well recieved but the systematic review community, and has been cited frequently in the published literature.
+It has been well received but the systematic review community, and has been cited frequently in the published literature.
 A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods.
-A chapter on the tool has been incorporated in to the “Doing Meta-Analysis in R” online textbook.[@mathias_harrer_2019_2551803]
+A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]
 

### 2021-03-10 index.Rmd
All working again after the update to Pandoc

@@
 bibliography: 
-  - bibliography/references.bib
-  - bibliography/pkg-refs.bib
+    - "bibliography/references.bib"
 csl: bibliography/nature.csl

### 2021-03-10 reviews/year_2/report.Rmd
All working again after the update to Pandoc

@@
 x = 0
+y = 0
 ```
@@
 
-**Title**:
+**Title**: Investigating the relationship between blood lipids levels, and interventions that modify blood lipid levels, and dementia outcomes.
 
@@
 
-**Current date**: 19/01/2021
-
-&nbsp;
-
-**PhD Start date**: 01/01/2019
+**PhD start date**: 01/01/2019
 
@@
 # Overview of PhD
-<!-- ## Rationale -->
-
-<!-- Several primary studies and systematic reviews exist that seek to examine the relationship between blood lipid levels, or interventions which modify blood lipid levels such as statins, and the subsequent risk of dementia.
-However, as yet, there has been no systematic attempt to find and integrate all available sources of evidence from distinct study designs to address this research question using a triangulation framework.[@lawlor2016a] -->
-
-<!-- This thesis aims to find, critically appraise and synthesize the available evidence related to this research question, and then integrate this with the primary evidence produced as part of this thesis.
--->
-
-<!-- &nbsp; -->
 
 ## Aim {#aim}
-The central aim of this thesis is to: <br>
+The central aim of this thesis is: <br>
 
-* **To investigate the relationship between blood lipid levels, and interventions that modify blood lipid levels, and dementia outcomes**
+* **To investigate the relationship between blood lipid levels, and interventions that modify blood lipid levels, and dementia outcomes.**
 
@@
 ## Objectives {#objectives}
-To achieve this aim, there are several smaller objectives, which map to the proposed chapters of my PhD outline in Section \@ref(chapter-progress):
+To achieve this aim, there are several smaller objectives, which map to the proposed chapters of my thesis outlined in Section \@ref(chapter-progress):
 
 1.
-Identify all existing on the relationship between blood lipid levels (and interventions that affect blood lipid levels) and dementia, regardless of study design, and including studies available solely as a preprint.
-
-&nbsp;
+Identify all existing evidence on the effect of blood lipid levels (and interventions that affect blood lipid levels) on dementia risk, regardless of study design and including studies available solely as a preprint.
 
@@
 
-&nbsp;
-
 3. Examine the relationship between blood lipid levels and dementia risk in several cohorts as part of a individual participant data meta-analysis.
 
-&nbsp;
-
-4. Integrate the existing evidence from the review with the primary evidence produced as part of this thesis as part of a qualitative triangulation exercise.
+4. Integrate the existing evidence identified by the review with the primary evidence produced as part of this thesis in a qualitative triangulation exercise.
 
@@
 ## Theoretical framework
-The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research can address questions that have yet to be answered, or can re-examine existing questions in a way that increases our confidence in the result.
+The main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.
 
-The primary evidence generation aspects of this thesis are performed with the primary intention of providing a further source of evidence for the evidence synthesis/triangulation aspect.
+While this thesis does include a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspects.
 
@@
 The thesis is laid out in a similar manner to that successfully defended by [Sam Abbott of the MRC IEU](https://www.samabbott.co.uk/thesis).
-Each chapter is self-contained in that it presents the relevant methods and results for that particular analysis, and so there are no dedicated methods chapters.
+Each chapter is self-contained, presenting the relevant methods and results for that particular analysis, and so there are no dedicated methods chapters.
 
@@
 
-**Include Gantt chart here**
+![](../../figures/gantt.png){width=450}
+&nbsp;
 
+__Figure `r (x <- x + 1)`: Gantt chart showing research milestones, training courses and conferences for the last 12 months of my PhD thesis.__ 
 &nbsp;
@@
 This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis outputs (papers/software).
+
+&nbsp;
 
@@
 
+&nbsp;
+
 **Progress**
@@
 This chapter introduces a tool built in R to allow for systematic searching of the [medRxiv](https://www.medrxiv.org/) and [bioRxiv](https://www.biorxiv.org/) preprint repositories.
+Preprints represent an important source of grey literature and so should be included as part of a systematic review.
+However, the native search interface on preprint websites do not allow for complex search strategies (e.g.
+those using Boolean operators or wildcards) and are not transparent or reproducible, with the same search producing wildly different numbers of records over time.
 
-Preprints represent an important source of grey literature and so should be included as part of a systematic review, and searching these repositories.
-However, the native search interface on the preprint websites do not allow for complex search strategies (e.g.
-using Boolean operators or wildcards) and are not transparent or repeatable, with the same search producing wildly different numbers of records over time.
+To allow for easy systematic searching of this literature source as part of the systematic review described in Chapter 4, the `medrxivr` tool was developed.
 
-To allow for easy systematic searching of this literature souce as part of the systematic review described in Chapter 4, the `medrxivr` tool was developed.
+__Note:__ Evidence synthesis software development has been a key component of my work during my Fellowship.
+At my last progress review, Tom Gaunt (PGR Director) flagged in his comments that I should consider including some of this work as a chapter in my thesis, if I could tie it in with the thesis as whole.
+Based on this, I am keen to include the medrxivr tool, as it was designed and developed specifically to help with the review described in Chapter 4.
+However, I would be very glad to hear your opinion on whether the inclusion of this work as a chapter makes sense in terms of the thesis as a whole.
 
@@
 
-The code underlying the tool underwent stringent peer review via the rOpenSci review process (you can see the discussion between myself and the reviewers [here](https://github.com/ropensci/software-review/issues/380)), following which a short paper describing the tool was [published in the Journal of Open Source Software](https://joss.theoj.org/papers/10.21105/joss.02651).
+The code underlying the tool underwent peer review via the rOpenSci review process (you can see the discussion between myself and the reviewers [here](https://github.com/ropensci/software-review/issues/380)), following which a short paper describing the tool was [published in the Journal of Open Source Software](https://joss.theoj.org/papers/10.21105/joss.02651).
 
-This chapter represents an expanded version of the published paper, expanding on the motivation, key functionality, reception and planned future development of the tool.
+This chapter represents an expanded version of the published paper, discussing the motivation, key functionality, reception and planned future development of the tool.
 A draft of this chapter is complete.
@@
 
-__Note:__ evidence synthesis software development has been a key component of my work during my Fellowship.
-At my last APR, Tom Gaunt flagged in his comments that I should consider including some of this work as a chapter in my thesis, if I could tie it in with the thesis as whole.
-Based on this, I am keen to include the medrxivr tool, as it was designed and developed specifically to help with the review described in Chapter 4.
-However, I would be very glad to hear your opinion on whether the inclusion of this work as a chapter makes sense in terms of the thesis as a whole.
-
 <!----------------------------------------------------------------------------->
 
-![](../../figures/sys-rev-tools/medrxiv-role.png)
+![](../../figures/sys-rev-tools/medrxiv-role.png){width=350}
 
@@
 
-This chapter presents the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/statins and dementia subtypes.
-The review included all types of study design including randomised controlled trials, Mendelian randomisation analyses, and non-randomised studies of exposures and interventions.
+This chapter will present the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/blood lipids interventions (e.g.
+statins) and dementia.
+The review included all types of study design including randomised controlled trials, Mendelian randomization analyses, and non-randomised studies of exposures and interventions (NRSI/NRSE).
+
+&nbsp;
 
@@
 
-* Literature search (100%)
-* Title and abstract/Full-text screening (100%)
-* Data extraction (100%)
-* Risk of bias assessment (75%)
-* Writing (50%)
+In terms of the different stages of the review, progress currently stands as:
+
+* Literature search: 100%
+* Title and abstract/Full-text screening: 100%
+* Data extraction: 100%
+* Risk of bias assessment: 75%
+* Analysis: 60%
+* Writing: 50%
+
+&nbsp;
+&nbsp;
 
@@
 
-![](../../figures/sys-rev/prisma_flow.png)
+![](../../figures/sys-rev/prisma_flow.png){width=350}
 
@@
 
-The review .
-Using other published reviews to verify the results demonstrated that the search was sufficiently comprehensive to capture all previously identified studies, plus some studies that had not been included in any previous review.
+First, in response to issues flagged at last year's progress review (comprehensiveness of search/is screening a 10% sample in duplicate sufficient if inter-rater reliability is low), searching the bibliographies of published reviews on this topic demonstrated that the search was sufficiently comprehensive to capture all previously identified studies in addition some studies that had not been included in any previous review.
+Additionally, inter-rater agreement on a random 10% subsample of records was high for both the title/abstract and full-text screening stages of the review.
 
-Data extraction has been completed for the 1-5 studies included in the review and
+For the sake of space, the full methods and results of the review are not presented here, but the protocol is [available online](https://doi.org/10.17605/OSF.IO/VTW5Y).
+As a short summary, 127 reports describing 105 primary studies were included in the review (see the PRISMA flow diagram above for an overview of the movement of records through the review).
+The majority of studies identified by the review are non-randomised studies, with only two randomised controlled trails and eight Mendelian randomization studies identified.
+Data extraction has been completed for all studies, and risk-of-bias assessments for each are almost complete.
 
-As dual screening and extraction is recommended for systematic reviews, this element of my thesis has involved a number of external researchers.
-I have found the people-management aspect of the review challenging, but it has provided good experience in terms of leading a review team.
+To enable comparison with the results of the observational analysis presented as part of Chapter 5, the results of a meta-analysis examining the effect of statins on dementia outcomes in included NRSI is presented.
+Statin use was associated with a reduced risk of all-cause dementia (HR: 0.86, 95%CI 0.83-0.88) and Alzheimer's disease (HR: 0.78, 95%CI 0.69-0.89), but were not found to have an effect on the risk of vascular dementia (HR: 0.93, 95%CI 0.76-1.14).
 
-For space, and to illustrate the proposed triangulation below
+![](../../figures/forestplot_acd.png){width=350}
+
+__Figure `r (x <- x + 1)` - Results of a random-effects meta-analysis of non-randomised studies examining the effect of statin use on the risk of all-cause dementia.__
+
+![](../../figures/forestplot_ad.png){width=350}
+
+__Figure `r (x <- x + 1)` - Results of a random-effects meta-analysis of non-randomised studies examining the effect of statin use on the risk of Alzheimer's disease.__
+
+![](../../figures/forestplot_vad.png){width=350}
+
+__Figure `r (x <- x + 1)` - Results of a random-effects meta-analysis of non-randomised studies examining the effect of statin use on the risk of vascular dementia.__
+
+&nbsp;
+
+In terms of the meta-analysis of the non-intervention studies, this was complicated by the different ways in which lipid fractions were quantified in different studies (e.g.
+grouped based on clinical guidelines or quantiles, or dichotomized into a hypercholesterolemia variable).
+However, following discussion with my supervisors who pointed me towards useful material on this subject, this element of the analysis is almost complete.
+
+One interesting discussion point highlighted by the review is the absence of data on vascular dementia as an outcome.
+As illustrated in the meta-analysis above, there were substantially fewer non-randomised studies reporting vascular dementia as an outcome compared with those reporting all-cause dementia or Alzheimer's disease outcomes.
+This is reflected in the available randomised controlled trials and Mendelian randomization studies (as no genetic consortia data are available for the vascular dementia outcome, MR studies of this condition are precluded).
+This will restrict the triangulation exercise for this outcome, as it will have to rely on different analytical strategies within a single study design (non-randomised studies) rather than incorporating fundamentally different study designs.
+
+A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review.
+I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.
 
@@
 
-One of the take-aways from my last APR was to make the "added value" of this work beyond existing review clear.
-I believe there are two aspects where this review adds value above what is already available in the published literature:
+One of the take-aways from my last progress review was to make the "added value" of this work beyond existing reviews clear.
+I believe there are three aspects where this review is distinct from those reviews already available in the published literature:
 
 * _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also searched the reference lists of comparable reviews to ensure no study has been omitted.
-* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk of bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
+As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
+ROBINS-I/E).
+This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
+* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature.
+As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
 
@@
 <!----------------------------------------------------------------->
-## Chapter 5: Observational analyses
+## Chapter 5: Observational analysis
 
@@
 
-Rather than reproduce the methods/findings here, I have attached the initial draft of the paper this chapter is based on at the end of this report.
+Rather than reproduce the methods/findings of this chapter here, I have attached the initial draft of the paper this chapter is based on at the end of this report.
+
+&nbsp;
 
@@
 In relation to the results presented in the attached paper, there are two key discussion points.
-The first is that while statins are associated with a slight reduction in the risk of probable AD (HR: 0.91, 95%CI: 0.88-0.95) and possible AD (HR: 0.95, 95%CI: 0.92-0.99), we still see an increased risk of vascular dementia (HR: 1.7, 95%CI: 1.62-1.77) and other dementia (HR: 1.7, 95%CI: 1.62-1.77) in those using statins.
-This reflects the initial findings of this analysis presented at the last APR, and was not attenuated even after using multiple imputation to account for potential selection bias caused by the original complete case analysis and accounting for several potentially important confounders.
+The first is that while statins are associated with a slight reduction in the risk of probable (HR: 0.91, 95%CI: 0.88-0.95) and possible Alzheimer's Disease (HR: 0.95, 95%CI: 0.92-0.99), there is an increased risk of vascular dementia (HR: 1.7, 95%CI: 1.62-1.77) and other dementia (HR: 1.13, 95%CI: 1.09-1.18) in those using statins.
+This reflects the initial findings of this analysis presented at the last progress review, and was not attenuated even after using multiple imputation to account for potential selection bias caused by the original complete case analysis and after accounting for several potentially important confounders.
 
-Secondly, following a recommendation by a co-author to use the same analysis strategy with a known control (coronary heart disease; CHD), we found that statins appeared to increase the risk of CHD, in contrast to the the results of large RCTs.
-This finding suggests the presence of substantial confounding by indication, in that those who go on to take a statin are fundamentally different from those who do not, and has been replicated in other standard mulitvariable HR analyses.[@danaei2013a] A suggested approach to frame this (possible insurmountable) issue has been to rewrite the paper as an example of the dangers of using EHR in cases where strong confounding by indication is likely.
-However, it would be particularly useful to get reviewers feedback on any further analytical strategies we could attempt to address this issue.
+Secondly, following circulation of the draft, a co-author recommended that I use the same analysis strategy with a known control (coronary heart disease; CHD).
+However, when running this analysis, I found that statins appeared to increase the risk of CHD, in contrast to the results of published large RCTs.
+This finding suggests the presence of substantial confounding by indication in this analysis, in that those who go on to take a statin are fundamentally different from those who do not, and this has been seen in other standard multivariable HR analyses of the effect of statins on CHD.[@danaei2013a] A suggested approach to frame this (possible insurmountable) issue has been to rewrite the paper as an example of the dangers of using EHR in cases where strong confounding by indication is likely.
+However, it would be particularly useful to get reviewers feedback on any further analytical strategies I could attempt to address this issue.
 
-In terms of the broader thesis, while this limitation is important, it presents a good opportunity to compare the effect of different analytical strategies with competing directions of bias (immortal time bias makes statins look better, confounding by indication makes statins look worse) of bias on the same underlying question.
+In terms of the broader thesis, while these concerns mean I have low confidence in the accuracy of the result, it presents a good opportunity for comparison with other published papers that used different analytical strategies where the source and direction of bias is different (e.g.
+confounding by indication in our analysis likely makes statin use look worse but immortal time bias in other papers likely makes statin use look better).
 
-Finally, in an attempt to assess whether these (likely spurious) findings for vascular dementia are a product of the CPRD data or our analytical strategy, we recently attempted to replicate an analysis performed by Smeeth et al.
-in the THIN EHR database which found a protective effect of statins on dementia risk (HR 0.81, 99% CI 0.69-0.96).[@smeeth2009a] However, following correspondence with the author team to acquire the code-list they used to define dementia cases, we confirmed that it was substantially different from that used in our study.
+Finally, in an attempt to assess whether these unexpected findings for vascular dementia are a product of the CPRD data or our analytical strategy, I recently attempted to replicate an analysis performed by Smeeth et al.
+which used the THIN EHR database and found a protective effect of statins on dementia risk (HR 0.81, 99% CI 0.69-0.96).[@smeeth2009a] However, following correspondence with the author team to acquire the code-list they used to define dementia cases, I confirmed that it was substantially different from that used in our study.
 This fact, coupled with concerns over their analytical strategy (which seemed to adjust for covariates on the causal pathway), limited the value of this attempted replication.
@@
 
-Similar to the systematic review, feedback from my last APR suggested that the "added value" of this study above those that already exist should be made clearer.
+Similar to the systematic review presented in Chapter 4, feedback from my last progress review suggested that the "added value" of this study above those that already exist should be made clearer.
+There are two particular motivations for this analysis above those already available in the published literature:
 
-There are two particular:
-* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies included in the review, this CPRD analysis would be one of the largest studies of this research question.
-* _Addressing the limitations of other observational analyses:_ Analysing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
+* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
+* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
 
@@
 This analysis has not yet started, but data access has been secured.
+
+&nbsp;
 
@@
 
-This chapter will draw together different sources of information (including the primary analysis performed as part of this thesis) in a triangulation framework, along with a consideration of the key sources/direction of bias in each, to inform.
+This chapter will draw together different sources of information (including the primary analysis performed as part of this thesis), along with a consideration of the key sources/direction of bias in each, in a qualitative triangulation framework.[@lawlor2016a]
 
-As flagged in my last APR, this chapter will make clear that "triangulation" in the context of my thesis is a qualitative integration of the distinct evidence sources available (systematic review, CPRD study, IPD meta-analysis).
+As flagged in my last progress review, this chapter will make very clear that "triangulation" in the context of my thesis is a qualitative integration of the distinct evidence sources available (systematic review, CPRD study, IPD meta-analysis).
+
+&nbsp;
 
@@
 
-However, in the coming year, I plan to attend the "Mendelian randomisation" and "Advanced methods for multiple imputation" short courses at the University of Bristol, in addition to the "Causal Inference in Epidemiology: Recent Methodological Developments" short course at LSHTM and the "Writing about your research" course at the Royal Society.
+However, in the coming year, I have secured places on the  "Mendelian randomization" and "Advanced methods for multiple imputation" short courses at the University of Bristol, in addition to the "Causal Inference in Epidemiology: Recent Methodological Developments" short course at LSHTM and the "Writing about your research" course at the Royal Society.
 
@@
 
-In the review period, I presented on the preprint search tool described in Chapter 3 at the Bristol  "Autosynthesis Club" and "Methods in Evidence Synthesis" seminars.
+In the review period, I presented on the preprint search tool described in Chapter 3 at the Bristol  "Auto-synthesis Club" and "Methods in Evidence Synthesis" seminars.
 
-It's only in writing this report that I realised that I am yet to present on the other parts of my thesis, and so this is a particular aspect of my PhD that I would like to develop further in the coming year.
+It's only in writing this report that I realized that I am yet to present on the other parts of my thesis, and so this is a particular aspect of my PhD that I would like to develop further in the coming year.
 As such, I aim to present at more diverse events in the coming year, including at an IEU monthly meeting and the Faculty of Health Sciences research showcase.
@@
 * MSc Epidemiology/Public Health "Clinical Epidemiology" module
-    * Tutored a small group of several weeks
+    * Tutored a small group for several weeks
     * Marked the end-of-module assessments
-* Introduction to R short course for new PhD students, Bristol Medical School short course
+* "Introduction to R" short course for new PhD students, Bristol Medical School short course
     * Presented a lecture on advanced R topics (data visualisation, literate programming and web applications)
-* Introduction to data visualisation and web applications using R, Bristol Medical School short course
+* "Introduction to Data Visualisation and Web Applications using R", Bristol Medical School short course
     * Designed and delivered the web applications aspects of the course
@@
 
-I have also submitted a proposal to supervise an MSc student for the summer term.
+I have also had a proposal accepted to supervise an MSc student for the summer term.
 The project aims to examine the overlap between the set of primary studies included in the several existing systematic reviews of blood lipid levels and dementia (as mentioned in the description of Chapter 4, above).
@@
 * *Comparison of data availability statements:*
-Using medrxivr (the preprint search tool described in Chapter 2), myself and a fellow PhD student compared the availability of data for the same manuscript when published under two different data-sharing policies (i.e.
+Using medrxivr (the preprint search tool described in Chapter 2), fellow PhD student and I compared the availability of data for the same manuscript when published under two different data-sharing policies (i.e.
 that of the preprint repository vs.
@@
 
-* *Making primary research synthesis-ready:* I acted as last author on a commentary describing the best practice and advatnages for primary researchers in the field of prevention science to ensure that their research is "synthesis-ready" (i.e.
+* *Making primary research synthesis-ready:* I am last author on a commentary describing the best practice and advantages for primary researchers in the field of prevention science to ensure that their research is "synthesis-ready" (i.e.
 can be easily found and integrated into an evidence synthesis project).

### 2021-03-10 reviews/year_2/star.Rmd
All working again after the update to Pandoc

@@
   * This short chapter presents the aims and objectives of the thesis, an overview of each chapter, an introduction to evidence synthesis as the theoretical framework underlying the thesis, and a summary of thesis output.
+  * A draft of this chapter is complete.
 
 * Chapter 2: Background
-  * This is a small introductory chapter to put the thesis into context, lay out the aims and objectives and to propose the idea of a pipeline for MR studies using metabolomics data.
-I have almost completed this chapter.
+  * This chapter will provide an overview of the main topics covered in the thesis, including dementia, blood lipids fractions, and lipid regulating agents.
+  * This chapter is ~70% complete.
 
@@
 This chapter represents a more comprehensive version of a published manuscript [https://doi.org/10.21105/joss.02651](https://doi.org/10.21105/joss.02651).
+  * A draft of this chapter is complete.
 
@@
   * This chapter uses data from the Clinical Practice Research Datalink (CPRD) to investigate the relationship between statin use and dementia. 
-  * This analysis has proven challenging likely due to the presence of confounding by indication.
+  * This analysis has proven challenging, likely due to the presence of unaddressed confounding by indication.
 The suggestion has been to write up the corresponding paper as an example of the dangers of EHR in cases where strong confounding by indication is likely.
 
-* chapter 6: Individual patient data meta-analysis
+* Chapter 6: Individual patient data meta-analysis
   * This chapter will use data from several Dementia Platform cohorts (plus some of the cohorts identified through the systematic review) to investigate the relationship between blood lipids levels and dementia outcomes.
@@
 * Chapter 7: Triangulation
-  * This short chapter will draw together different sources of information (including the primary analysis performed as part of this thesis) in a triangulation framework.
+  * This short chapter will draw together different sources of information (including the primary analyses performed as part of this thesis) as part of a qualitative triangulation exercise.
+  * This aspect of my thesis has not started.
 
@@
 
-In the review period, I have not presented work related to my thesis.
+In the review period, I presented on the preprint search tool described in Chapter 3 at the Bristol “Auto-synthesis Club” and “Methods in Evidence Synthesis” seminars.
 
@@
 
-1. Finish systematic review data extraction
-1. Complete replication of chapter 5 analysis in INTERVAL and complete write-up of chapter and manuscript
-1. Finish chapter 1
-1. Finish chapter 3
-1. Finish chapter 6
+1. Finish risk of bias assessments for systematic review
+1. Draft systematic review manuscript
+1. Finish Chapter 4 - Systematic review
+1. Finish Chapter 2 - Background
+1. Clean datasets from DPUK and begin IPD analysis
 
@@
 
-1. Finish chapter 2 - systematic review chapter
-1. Finish chapter 4 - complete observational analysis and write-up of chapter 4
-1. Complete one clustering analysis and begin work on a second and third (chapters 7 and 8)
+1. Perform IPD analyses
+1. Plan triangulation exercise
 
@@
 
-1. Finish chapter 7 second and third clustering analyses
-1. Begin writing chapter 8 rules for instrumenting clusters
+1. Finish Chapter 6 - IPD analysis
+1. Perform triangulation exercise
 
@@
 
-1. Finish chapter 7 and 8
-1. Begin final analysis for chapter 9
-1. Finish write-up of chapter 9
-
-1. finishing touches to thesis
-1. finish outstanding manuscripts
-1. Submit
+1. Finish Chapter 7 - Triangulation
+1. Make final changes to thesis
+1. Produce final drafts of remaining manuscripts and submit as preprints
+1. Submit thesis
 
@@
 
-In addition, as per my Fellowship training scheme, I plan to attend the Royal Society "Writing about your research" course.
+In addition, as per my Fellowship training scheme, I plan to attend the Royal Society "Writing about your research" course and the “Causal Inference in Epidemiology: Recent Methodological Developments” short course at LSHTM.
 
@@
   * preprint/publication
-  * poster/presentation at the Alzheimer's Association International Conference (deadline 25th January)
 * Primary analysis of the CPRD
   * preprint/publication
+
+It’s only in writing this report that I realized that I am yet to publicly present on the some parts of my thesis, and so this is a particular aspect of my PhD that I would like to develop.
+As such, I aim to present at more diverse events in the coming year, including at an IEU monthly meeting and the Faculty of Health Sciences research showcase.
+In addition, I plan to submit an abstract to the Alzheimer’s Association International Conference in July (deadline 25th January).
 

### 2021-03-12 03-Chp-Systematic-Review-Tools.Rmd
Send draft of Chapter 2 to Ciara

@@
 output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::word_document2: 
@@
       reference_docx: templates/word-styles-reference-01.docx
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 ```
+
 (ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
@@
 # medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-* Why searching preprints is important
+-   Why searching preprints is important
 
-* Why existing methods are not sufficient
+-   Why existing methods are not sufficient
 
-* What the medrxivr tool adds
+-   What the `medrxivr` tool adds
 
@@
 <!----------------------------------------------------------------------------->
+
 ## Introduction
@@
 Preprints represent an increasingly important source of scientific information.
-Defined by the The Committee on Publication Ethics (COPE) as ‘a scholarly manuscript posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process’[@committeeonpublicationethicscope2018], preprints serve several purposes.
+Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
 They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
@@
 
-Being able to systematically search these preprints for the purpose of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
+Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
+At the time of writing, however, the bioRxiv.medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
+As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
 
-At present, the medRxiv website allows only simple search queries as opposed to the often complex Boolean logic that information specialists use to query other major databases.
-Additionally, previous extraction mechanisms for obtaining the results of searches from medRxiv were to go through each record, one-by-one, downloading individual citations.
-As the scale of the medRxiv database increases, particularly in light of the massive expansion of the repository as a result of COVID, this already time-consuming and error-prone method is not longer feasible.
+This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv and bioRxiv preprints.
+The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
+As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary of the work done on this project.
+The GitHub repository[^chp-systematic-review-tools-1] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
 
-This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv preprints.
-The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
-As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary.
-The GitHub repository^[Available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
+[^chp-systematic-review-tools-1]: Available at <https://github.com/ropensci/medrxivr>
+
+&nbsp;
 
@@
 
-(ref:medrxivr-sr-cap) __Role of `medrxivr` in a systematic review workflow:__ `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
+(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
 Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
@@
 
-The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform the systematic searches as part of the review in Chapter \@ref(sys-rev-heading) and from an informal survey of colleagues and the evidence synthesis and health librarian community on Twitter.
-These criteria were as follows:
+The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
+The criteria were as follows:
 
@@
 
-2. support for bulk export of references returned by the search to a file type that can be imported into a reference manager (e.g., _.bib_  or _.ris_); and
+2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
 
-3. automated retrieval of the full-text PDFs of relevant records.
+3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.
 
@@
 <!----------------------------------------------------------------------------->
+
 ### Alternative medRxiv/bioRxiv interfaces
 
-Prior development of this tool, an informal audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted.
+Prior development of this tool, an audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted.
 While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
 
-The first, a platform called Rxivist [@abdill2019], allows users to search preprints from the using keywords.
-Similar to `medrxivr`, this tool previously scrapped data straight from the medRxiv and bioRxiv websites but as of November 2020, Rxivist also provided access to Cold Spring Harbor API.
+The first, a platform called Rxivist [@abdill2019], allows users to search preprints using keywords.
 However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface^[Available at https://rxivist.org/] does not allow for complex search strategies using Boolean operators, and there is no option to batch-export the results of a search.
+The search interface[^chp-systematic-review-tools-2] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
 
-The second, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv, bioRxiv, but also publishing venues using post-publication peer-review such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
+[^chp-systematic-review-tools-2]: Available at <https://rxivist.org/>
+
+The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
 As such, the platform only returns the most recent `r comma(1000)` records by publication date.
 
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant records which is required for the full-text screening stage of a systematic review.
+Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.
 
@@
 
-Work on this tool began in Summer 2019, which initially existed as a collection of scripts built to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the _ad-hoc_ web-scraping scripts, the initial version of the `medrxivr` package was released in February 2020.
-Additional development work took place in 2019/2020, allowing for improved searching and exporting functionality.
+Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
+Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and the initial version of the `medrxivr` R package was released in February 2020.
 
-Early versions of the tool had a reliance on web-scraping data directly from the medRxiv website.
-Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002;@laprie1992].
-In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the medRxiv website was regularly updated.
+Early versions of the tool had a reliance on scraping data directly from the repository website.
+Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
+In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the repository website was regularly updated.
 
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was released in early 2020, allowing for a newer version of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data.[@laprie1992]
-
-Finally, while initial versions of the tool focused primarily on the medRxiv repository, discovery of some eligible papers for the review detailed in Chapter \@ref(sys-rev-heading) required expansion to allow for similar searching of the bioRxiv repository.
-
-&nbsp;
+However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
+This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]
 
 <!----------------------------------------------------------------------------->
+
 ### Package infrastructure
@@
 <!----------------------------------------------------------------------------->
+
 ## Usage
@@
 
-* An interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
-* A collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
+-   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
+-   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
 
-The standard workflow is to download a copy of the metadata, and then run your searchers locally.
+The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy.
 This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.
+
+While the package allows for users to search both medRxiv and bioRxiv, as the process is identical for both, the examples in the sections are limited to the medRxiv repository.
 
@@
 Alternatively, the development version of the package can be installed from GitHub:
+
 &nbsp;
@@
 <!----------------------------------------------------------------------------->
+
 ### Importing preprint metadata
@@
 
-``` {r, eval = FALSE}
+```{r, eval = FALSE}
 # Get a copy of the database from the live medRxiv API endpoint
@@
 
-The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am.
-This method removes the dependency on the API which can become unavailable during peak usage times.
+The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`.
+Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
 The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
@@
 
-(ref:medrxivr-data-sources-cap) __Overview of `medrxivr` data sources:__ Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
+(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
 Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
@@
 
-The first step is to create your search strategy. Terms to be combined with the OR operator are contained in vectors, while topics to be combined with the AND operator are contained in lists.
+Once a local copy of the metadata is created, the first step in searching it is to create a search strategy.
+Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(…)`).
 
@@
 
-For example, the search above written in standard syntax would be: "((dementia __OR__ alzheimer's) __AND__ (lipids __OR__ statins))".
+For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
+There is now limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
+Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
+"randomi*s*ation" vs "randomi*z*ation".
 
-Once a local copy of the database has been created and your search strategy has been defined, both are passed to the `mx_search()` function.
+Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.
 
@@
 
-The search also supports common syntax used by systematic reviewers and health librarians, including the use of NEAR statements (which allows for identification of co-localised terms) and wildcards (which allow for alternate spellings, e.g.
-"randomi*s*ation" vs "randomi*z*ation").
+<!----------------------------------------------------------------------------->
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
 ### Refining your search
@@
 results  <- mx_search(mx_data,
-                      c("dementia", "alzheimer's"),
+                      c("dementia", "alzheimer's"), # Combined with OR
                       report = TRUE)
@@
 
-This allows users to discover which aspects of their search is contributing most to the total results returned.
+This allows users to discover which terms in their search are contributing most to the total number of results returned.
 This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
+It also aids in identifying misspelled search terms, which will frequently return no results.
 
@@
 <!----------------------------------------------------------------------------->
+
 ### Exporting to a bibliography file
@@
 In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
-While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` - as it was built with systematic reviews specifically in mind, it is
+While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
 
-For example, the results of our simple search above can be exported using the following code:
+For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
 
-``` {r, eval = FALSE}
+```{r, eval = FALSE}
 mx_export(results, 
@@
 <!----------------------------------------------------------------------------->
+
 ### Downloading the PDFs of relevant records
 
-Finally, `medrxivr` allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
+`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
 `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
@@
 ```{r, eval = FALSE}
-mx_download(results,  # Object containing included records
+mx_download(results,  # Search results, less excluded records
             "pdf/")   # Directory to save PDFs to 
@@
 <!----------------------------------------------------------------------------->
+
 ## Discussion
@@
 
-The tool has be well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak ^[https://twitter.com/L_Brierley/status/1233109086444695553], perform systematic searches in systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
+The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
+It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
 
-Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web", and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-^[https://github.com/ropensci/software-review/issues/380] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
+[^chp-systematic-review-tools-3]: <https://twitter.com/L_Brierley/status/1233109086444695553>
 
-Lobbying of the Cold Springs Harbor Laboratoryto develop the API to allow for direct searching of the database has been ongoing.
+Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web",[CITE] and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
+[^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
+
+[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>
+
+[Add bit about the benefits of the rOpenSci review process]
+
+Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing.
 This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
@@
 <!----------------------------------------------------------------------------->
+
 ### Limitations of `medrxivr`
@@
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+(This disagress with the use cases listed in the intro!)
 
@@
 <!----------------------------------------------------------------------------->
+
 ### Role of open source tools in evidence synthesis
 
-_Not sure where this should go, but keen to include it_
+*Not sure where this should go, but keen to include it*
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b;@mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
-
-&nbsp;
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 
 <!----------------------------------------------------------------------------->
+
 ## Summary
 
-* In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
+-   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
 
-* I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
+-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
 
-* I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
+-   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
 I have also discussed the tools reception to date, a roadmap for its future development and its place in the broader evidence synthesis in R ecosystem.

### 2021-03-15 02-Chp-Background.Rmd
Send draft of Chapter 2 to Ciara
End of day

@@
 ## Lay summary
+
+This thesis is
+
+Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement P
 
@@
 
-``` {r}
-library(gt)
-library(dplyr)
-
-gt(data = mtcars) %>%
-  tab_style(
-    style = cell_text(weight = "bold"),
-    locations = list(cells_body(
-      columns = vars(mpg)),
-      cells_column_labels(columns = vars(mpg))))
-
-```
-
 ###	Challenges in the study of dementia using traditional study designs
@@
 
-*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitivie impairment but who fall below the diagnostic criteria for dementia.
+*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia.
 
@@
 
-There exist only two large scale randomized controlled trials - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
+There exist only two large scale randomized controlled trials of the effect of statins on dementia risk - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
 Both showed no effect of
+
+However, while being widely cited,
 
@@
 ### Economic impact
+
+The economic impact of dementia is enormous, but in terms of the direct care required
+
+Patients with dementia stay in hospital for longer,[@mollers2019]
+
+Patients are more prone to falls and other con
 
@@
 
+he main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.
+
+While this thesis does include a research tool (Chapter 2 - systematic searching of preprint) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
+
 ### Primary cohort analysis

### 2021-03-15 04-Chp-Systematic-Review.Rmd
End of day

@@
 
+### Comments on the process
+
+Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
+Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
+
+Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.
+
+A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review.
+I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.
+
+### Original contribution to research
+
+I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by [CITE]):
+
+* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
+As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
+ROBINS-I/E).
+This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
+* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature.
+As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
+
 ### Comparison with other reviews

### 2021-03-15 05-Chp-CPRD-Analysis.Rmd
End of day

@@
 
-## Covariates
+### Covariates
 
@@
 Potential biases included time varying confounding, selection bias due to censoring on death and 
-We performed a Cox
+We use a Cox proportional hazards model with a time-varying treatment indicator.
 
@@
 
-### Replicating the analysis
+### Replicating other analytical strategies
 
@@
 
-As part of our exploration of the, we chose to explore whether our results were comparable with
+As part of our exploration of the unexpected results,
 
-As discussed in
+]
 
@@
 
-## Main findings
+### Main findings
 
@@
 
-## Comparison to other literature
+### Comparison to other literature
 
@@
 
-## Strengths and Limitations
+### Original contribution to research
+
+There are two primary ways in which this research adds to the topic:
+
+* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
+* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
+
+### Strengths and Limitations
 
@@
 
-## Conclusions
+### Conclusions
 

### 2021-03-15 97-Discussion.Rmd
End of day: -3533
End of day

@@
 
+## Additional topics for the discussion
+
+There are several addition topics I would like to cover:
+
+* The difference between the peer review of the software vs.
+the peer review of papers.
+A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
+Essentially, a more transparent and open
+
+* The management of
+
+Doing systematic reviews as a
+
 ## Summary of findings (and implications for policy makers)
@@
 One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
+
+Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
 

### 2021-03-23 01-Chp-Introduction.Rmd
End of day
Updates

@@
 
-## Aims and Objectives of the thesis
-
-### Aim
-
-### Objectives
-
-   * To review the published literature with respect to the effec tof lipids and lipid regulating agents  
-   * To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
-   * To meta-analyze the
-
-## Theoretical framework
-The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.
-
-All elements of this thesis are based around this framework.
-
-## Chapter Overview
-
-* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
-* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
-* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
-* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
-
-## Thesis Output
+## Thesis Output {#thesis-output}
 
@@
 
+  * McGuinness & Sheppard.
+
+  * PRISMA papers and software
+
+  * Discursive paper on open source in Evidence Synthesis
+
+<!-- Essentially, look at the Trello   -->
+
 ### Papers under review/Preprints
 
-  *
+  * MSc Paper
 
@@
 * 1 paper for Journal of Clinical Epidemiology
-
-## Summary
-
-*
-* 
-*

### 2021-03-23 02-Chp-Background.Rmd
Updates

@@
 ```
+
 (ref:dara-quote) --- Dara O'Briain
@@
 # Background {#background-heading}
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement P
-
 ## Introduction
 
-> This chapter provides the context of the thesis.
+<!-- This chapter provides the context of the thesis.
 It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality.
@@
 Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed.
-*From Matt Lee's thesis.*
+*From Matt Lee's thesis.* -->
 
 This Chapter will provide an overview of the key exposures, outcomes and methods used throughout this thesis.
+
+This Chapter will provide an overview of the thesis, introducing the core concepts used throughout and providing some background context on each.
+It will briefly discuss the natural history of dementia, it's public health importance and the .IN this context it will highlihg the importance of identifying easily modified treatment
+
+It will also introduce the primary exp, covering their biological role, measurement and
+
+Finally, it will outline the theoretical framework used in this thesis.
+
+<!-- Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer’s disease (AD) and vascular dementia (VaD) [1].
+Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease [2].
+Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative intervention due to the availability of lipid-modifying treatments.
+In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
+-->
+
+<!-- A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
+The generation of the amyloid plaques found in the brains of Alzheimer’s patients is cholesterol dependent [3,4], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
+Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [5-7].
+-->
+
+<!-- Despite these encouraging results, the evidence from epidemiological studies to date has been contradictory.
+Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer’s disease and vascular dementia and reported widely different results.
+A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
+With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
+-->
+
+<!--  Observational studies do not represent the only source of evidence examining the link between lipid levels and dementia.
+A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk [23].
+However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia [24,25].
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
+-->
+
+<!-- The use of newer methodological approaches, such as Mendelian randomisation (MR), has also produced contradictory results.
+In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
+A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk [27].
+However, this study was criticised as it did not exclude the region surrounding the ApoE gene, meaning the risk reduction observed could be driven by variants in this region.
+-->
+
+<!-- In short, each individual epidemiological approach taken to examine this research question is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk.
+However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
+If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk [26].
+In this context, systematically identifying, assessing and integrating all available evidence in a triangulation framework, regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
+-->
+
+<!-- Finally, if lipids have a causal role in development of dementia, evidence-based preventative strategies would be informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.
+Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28].
+Meta-analyses of trial-level data often have limited ability to examine exposure-covariate interactions.
+An individual participant data (IPD) meta-analysis is therefore  -->
+
+<!-- Consider sex as a biological variable -->
 
@@
 ### Definition and Subtypes
+
 Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory.
-The most common causes of dementia are Alzheimer’s disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively.
+The most common causes of dementia are Alzheimer's disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively.
 The remaining 10-30% of cases are caused other dementia subtypes (e.g.
 Lewy Body dementia) or by progression of other neurological diseases (e.g.
-Parkinson’s disease).
+Parkinson's disease).
+
+Two important considerations ont he
 
 ### Diagnosis
-Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition (is this true, or would it be better to say that there is no gold standard test without an autopsy).
-Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
+
+Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
+<!-- (is this true, or would it be better to say that there is no gold standard test without an autopsy?)--> Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
 the Mini-Mental State Examination), to clinical tests (e.g.
@@
 Several scales are commonly used to diagnose dementia and associated diseases for research purposes.
-Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke–Alzheimer Disease and Related Disorders (NINCDS–ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM- **]
+Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS--ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM-IV citations**
 
-**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter \@ref(sys-rev-heading)**
+**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter** \@ref(sys-rev-heading)
 
 ### Public Health Importance
+
 Dementia is quickly becoming a critically important public health issue.
@@
 ### History
-> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research
-Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
+
+> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
 Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
 In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences.
-In the MRC/BHF HPS trial,27
-similar percentages of participants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period.
+In the MRC/BHF HPS trial,27 similar percentages of participants (0.3% in each---statin vs placebo---group) developed dementia during the 5-year follow-up period.
 The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
@@
 
-There exist only two large scale randomized controlled trials of the effect of statins on dementia risk - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
+There exist only two large scale randomized controlled trials of the effect of statins on dementia risk [CITE] - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
 Both showed no effect of
 
-However, while being widely cited,
+However, while being widely cited, these studies have major limitations that limiti their utility
+
+in assessing the impact of lipid-lowering treatment on dementia risk.
 
@@
 
+Risk factors for dementia
+
 ### Treatments
@@
 ### Preventative measures
+
+At present fe
 
@@
 
-$$LDLc \approx TC - HDLc - kTG$$
-where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
+$$LDLc \approx TC - HDLc - kTG$$ where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
 
@@
 
-``` {block type='correction'}
+```{block type='correction'}
 Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
@@
 
+Statins are the primary
+
+<!----------------------------------------------------------------------------->
+
+(ref:statin-mechanisam-cap) **Statin mechanism of action:**
+
+(ref:statin-mechanisam-scap) Statin mechanism of action
+
+```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
+```
+
+<!----------------------------------------------------------------------------->
+
 #### Lipophilic
@@
 
-## Methods used in the thesis
+### Other lipid regulating agents (LRA)
+
+## Theoretical framework
+
+The main theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered, or explores the same question in a way that increases our confidence in the result.
+
+All elements of this thesis are based around this framework.
 
@@
 
-he main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.
+The main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.
 
@@
 
-### Primary cohort analysis
+More specifically this includes the accurate searching of sources of grey literature (as enabled by the too presented in Chapter \@ref(sys-rev-tools-heading)) and risk of bias assessment.
 
-### Triangulation
+### Involvement of patients and the public
 
-### Individual patient data meta-analyis
+Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
 
-## Summary
+## Chapter overview
+
+* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels.
+This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
+* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
+* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
+* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+
+## Aims and Objectives of the thesis
+
+### Hypothesis
+
+### Aim
+
+### Objectives
+
+-   To review the published literature with respect to the effec tof lipids and lipid regulating agents\
+-   To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
+-   To meta-analyze the

### 2021-03-23 03-Chp-Systematic-Review-Tools.Rmd
Updates

@@
 The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (preprint server versus journal).[CITE]
+It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (see \@ref(thesis-output)).[CITE]
 

### 2021-03-23 04-Chp-Systematic-Review.Rmd
Updates

@@
 ```
+
 (ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]
@@
 # Systematic review of all available evidence {#sys-rev-heading}
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 knitr::read_chunk("R/Chp2-Systematic-Review.R")
-knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 
-* Examine how many times a primary study was included in a review  
-* Look at whether searching preprints made any difference to my results
-* Could apply ROBIS to previous reviews to see how they stack-up?
+-   Examine how many times a primary study was included in a review\
+-   Look at whether searching preprints made any difference to my results
+-   Could apply ROBIS to previous reviews to see how they stack-up?
 
@@
 
-* Evidence map - show the distribution of the different studies population across the world.
-* Living systematic review approach - update weekly based on medRxiv
+-   Evidence map - show the distribution of the different studies population across the world.
+-   Living systematic review approach - update weekly based on medRxiv
 
@@
 The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer’s Association International Conference, published in the journal Alzheimer’s & Dementia) will be searched.
+the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
 Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
@@
 
+<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
+
+The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).
+
 ### Study selection
@@
 Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016]
-Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
 If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
@@
 #### Inclusion criteria
+
 We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
@@
 
-Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l’Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
 For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
@@
 #### Exclusion criteria
+
 Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
@@
 no dementia/MCI/dementia) will be excluded.
-Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study’s status.
+Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status.
 Studies that are reported in insufficient detail (e.g.
@@
 Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a “multi-domain intervention” where the lipid-regulating agent is included in each arms (e.g.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
 for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
@@
 
-Excluded studies performing autopsy unless it was done under accepted criteria
-Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
+Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
 
@@
 
+The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020]
+
+A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.
+
 ### Patient and public involvement
@@
 
-__Will need to include something in the methods section on this__
+**Will need to include something in the methods section on this**
 
@@
 Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
-This analysis was performed by extracting the citing articles from Google Scholar on XXXX and screening them manually.
+This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually.
 The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*
+
+<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
 
@@
 
-<!----------------------------------------------------------------------------->
-<!-- # ``` {r gwet-setup, results="hide", message=FALSE} -->
-<!-- # ``` -->
-<!-- # -->
-<!-- # ```{r gwet-table, message=FALSE, results="asis"} -->
-<!-- # ``` -->
-<!----------------------------------------------------------------------------->
+<!-- ------------------------------------------------------------------------- -->
+
+```{r gwet-setup, results="hide", message=FALSE}
+```
+
+```{r gwet-table, message=FALSE, results="asis"}
+```
+
+<!-- ------------------------------------------------------------------------- -->
 
@@
 
-$$AC1 = \frac{p-e(\gamma)}{1-e(\gamma)}$$
-Here, $p = \frac{A+D}{N}$ and $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where $q = \frac{(A+C)+(A+B)}{2N}$
+$$AC1 = \frac{p-e(\gamma)}{1-e(\gamma)}$$ Here, $p = \frac{A+D}{N}$ and $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where $q = \frac{(A+C)+(A+B)}{2N}$
 
--> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
+-\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
 
 <!-- # ```{r agreementtableinter, echo = FALSE} -->
+
 <!-- # ``` -->
+
 <!-- # ```{r agreementtableintra, echo = FALSE} -->
+
 <!-- # ``` -->
@@
 <!----------------------------------------------------------------------------->
-``` {r prisma-flow-setup, results="hide", message=FALSE}
+
+```{r prisma-flow-setup, results="hide", message=FALSE}
 ```
 
-(ref:prisma-flow-cap) __PRISMA Flowchart:__ Overview of how records moved through the systematic review process
+(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process
 
@@
 ```
+
 <!----------------------------------------------------------------------------->
@@
 
-<!----------------------------------------------------------------------------->
 Include here:
 
-* PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
+-   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
 
-* Summary of types of study
+-   Summary of types of study
 
-* Summary of locations
+-   Summary of locations
 
-* Summary of diagnostic criteria used
+-   Summary of diagnostic criteria used
 
-* Summary of risk of bias
+-   Summary of risk of bias
 
-* Long table, horizontally. Newer version of flextable (GH) allows for PDF output
+-   Long table, horizontally. Newer version of flextable (GH) allows for PDF output
+
+A common theme across the studies was a lack of data on vascular dementia.
+This is particularly interesting as lipids and statins are primarily a vascular disease.
+There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
+For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of
+
+One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4.
+As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.
+
+In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
+
+### Converting risk ratios to odds ratios
+
+Include formulae and informed assumptions
+
+### Hazard ratios vs risk/odds ratios
+
+Not interchangeable in the context of systematic review.
+If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
+
+Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
+
+The likely effect of this is that the overall effect measures are biased towards . . . . ?
+
+Can you predict the direction of effect from a
+
+Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
+
+<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
+
+Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
 
@@
 
-* Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
-* Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st
+-   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
+-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st
 
@@
 Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test
+
+### Added evidental value of including preprints
+
+<!-- Will to get actual numbers for this section -->
+
+There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
+While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
+
+Of interest,
+
+<!-- Triple check whether any of the studies have yet to be published -->
+
+This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
+It also means that searches are current - if the aim of systematic reviews is to
+
+While the total number of relevant studies found using this method was
+
+<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
+
+<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
+
+While these preprint have subsequently
 
@@
 
-* _Comprehensiveness:_ While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
+-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
+-   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
 ROBINS-I/E).
 This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-* _Inclusion of preprints:_ Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched  preprinted health-related manuscripts as a source of grey literature.
+-   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
 As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
@@
 
-__The duplication of work across reviews (including, ironically, by this review) is substantial.
+**The duplication of work across reviews (including, ironically, by this review) is substantial.
 In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.__
+However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
+
+<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->
+
+### Reviewing Mendelian randomisations studies
+
+While
+
+This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.
+
+Recent updates, such as a guide to reading and interpreting.
+However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
+
+Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for
+
+Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.
 
 ### Strenghts and limitations
+
+Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy.
+An example is Larsson et al.
+2017[@larsson2017a], where the study examined the association between lipid fractions
+
+Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
 

### 2021-03-23 97-Discussion.Rmd
Updates

@@
 
+## Triangulation
+
+Summary table of different studies and results
+
+## Discussion of E-values
+
+How strong unmeasured confounding would have to be in order to explain the observed effect.
+
+Heavily criticised in a range of papers.
+
+## Use of concensus panel to bring everything together
+
 ## Additional topics for the discussion
@@
 
-* The management of
-
-Doing systematic reviews as a
+* That systematic review should no be
 
@@
 
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the)
+Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
 
@@
 
+P
+
 ## Future work

### 2021-03-23 front-and-back-matter/99-appendices.Rmd
Updates

@@
 
-## Chapter 1 {#appendix-chapter-1}
+## Chapter \@ref(intro-heading) {#appendix-into}
 
-## Chapter 2 {#appendix-chapter-2}
+## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
+
+### Search strategy {#appendix-search-strategy}
+
+### Code to search preprints {#appendix-medrxivr-code}
+
+<!-- Double check this is the final code used -->
+
+```{r, eval = FALSE}
+
+library(medrxivr)
+
+mx_data <- mx_api_content(to_date = "2019-09-01")
+
+bx_data <- mx_api_content(server = "biorxiv",
+                                    to_date = "2019-09-01")
+
+topic1 <- c("statin",
+            mx_caps("ldl"),
+            mx_caps("hdl"),
+            mx_caps("TG"),
+            paste0("\\b",mx_caps("TC"),"\\b"),
+            "ezetim",
+            "lipoprotein",
+            "lipid",
+            "cholesterol")
+
+topic2 <- c(mx_caps("dementia"),
+            mx_caps("alzheim"),
+            mx_caps("MCI"),
+            mx_caps("mild cognitive"))
+
+query <- list(
+  topic1,
+  topic2
+)
+
+test <- mx_search(bx_data, query)
+
+test2 <- mx_search(mx_data, query)
+
+```
+
+### MR risk of bias tool {#appendix-mr-rob}
+
+## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
 

### 2021-04-07 01-Chp-Introduction.Rmd
End of day: 0

@@
 
-## Thesis Output {#thesis-output}
-
-The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools, and . . .
-
-### Peer reviewed papers
-
-__Include other papers I have been involved in?__
-
-  * McGuinness, Luke A., and Lena Schmidt.
-"medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 (2020): 2651.
-DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)
-
-  * McGuinness, Luke A., and Julian PT Higgins.
-"Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Methods (2020).
-DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)
-
-  * McGuinness & Sheppard.
-
-  * PRISMA papers and software
-
-  * Discursive paper on open source in Evidence Synthesis
-
-<!-- Essentially, look at the Trello   -->
-
-### Papers under review/Preprints
-
-  * MSc Paper
-
-### Software
-
-* `medrxvir`: An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv^[https://www.medrxiv.org/] and bioRxiv^[https://www.biorxiv.org/] preprint repositories.
-See Chapter \@ref(sys-rev-tools-heading) for more details.
-Install a stable version of the package from CRAN with `install.packages("medrxivr")` or alternatively install the development version from GitHub using `devtools::install_github("mcguinlu/medrxivr")`.
-Link: [https://ropensci.github.io/medrxivr/](https://ropensci.github.io/medrxivr/)
-
-* `robvis`: An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
-See Appendix \@ref(appendix-robvis) for more details.
-Install a stable version of the package from CRAN using `install.packages("robvis")` or alternatively install the development version from GitHub using `devtools::install_github("mcguinlu/robvis")`.
-Link: [https://mcguinlu.github.io/robvis/](https://mcguinlu.github.io/robvis/)
-
-### Talks
-
-* Presentation to the 
-* Webinar to Evidence Synthesis Ireland on Risk of Bias
-* Presentation(s) to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
-
-### Peer review
-
-* 2 papers for Systematic Reviews
-* 1 paper for Environment International
-* 1 paper for Journal of Clinical Epidemiology
+&nbsp;

### 2021-04-07 02-Chp-Background.Rmd
End of day: 0

@@
 
-# Background {#background-heading}
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+knitr::read_chunk("R/background.R")
+```
+
+# Background & Objectives {#background-heading}
 
@@
 
-This thesis is
+Around __[NUMBER]__ people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
+No cure for dementia exists, so researchers are trying to find ways to prevent the condition.
+This involves finding risk factors for dementia that we can change.
+Risk factors increase a person's risk of developing a disease.
+Avoiding a risk factor does not guarantee that a person will not develop dementia, but makes it less likely.
+A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood.
+However, researchers remain unsure, as studies disagree on whether a role for lipids in dementia exists.
+
+Additionally, because of problems in the design of previous studies, a cause and effect link between lipids and dementia could not be confirmed.
+
+The research contained in this thesis will sum up what we know about the relationship between lipids and dementia.
+
+I will use all available evidence, including that preprinted by authors (i.e.
+not formally reviewed by others in their field to assess the accuracry of their claims) to assess whether lipid levels cause dementia.
+
+Finally, I will attempt to find the groups of patients that might benefit most from treatment to change their lipid levels.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-This Chapter will provide an overview of the key exposures, outcomes and methods used throughout this thesis.
+This Chapter will provide an overview of the thesis, introducing the core concepts used throughout and providing some background context on each.
+It will briefly discuss the natural history of dementia, it's public health importance and the
 
-This Chapter will provide an overview of the thesis, introducing the core concepts used throughout and providing some background context on each.
-It will briefly discuss the natural history of dementia, it's public health importance and the .IN this context it will highlihg the importance of identifying easily modified treatment
+In this context it will highlight the importance of identifying easily modified risk factors, and introduce blood lipids, and blood lipid-modifying treatements such as statins, as the primary exposures e
 
-It will also introduce the primary exp, covering their biological role, measurement and
+It will also introduce the primary exposures used in this thesis, covering the biological role, measurement and. It will cover the mechanism of common lipid regulating agents.
 
@@
 
-<!-- Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer’s disease (AD) and vascular dementia (VaD) [1].
-Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease [2].
-Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative intervention due to the availability of lipid-modifying treatments.
-In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
--->
-
-<!-- A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer’s patients is cholesterol dependent [3,4], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [5-7].
--->
-
-<!-- Despite these encouraging results, the evidence from epidemiological studies to date has been contradictory.
-Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer’s disease and vascular dementia and reported widely different results.
-A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
-With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
--->
-
-<!--  Observational studies do not represent the only source of evidence examining the link between lipid levels and dementia.
-A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk [23].
-However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia [24,25].
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
--->
-
-<!-- The use of newer methodological approaches, such as Mendelian randomisation (MR), has also produced contradictory results.
-In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
-A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk [27].
-However, this study was criticised as it did not exclude the region surrounding the ApoE gene, meaning the risk reduction observed could be driven by variants in this region.
--->
-
-<!-- In short, each individual epidemiological approach taken to examine this research question is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk.
-However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
-If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk [26].
-In this context, systematically identifying, assessing and integrating all available evidence in a triangulation framework, regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
--->
-
-<!-- Finally, if lipids have a causal role in development of dementia, evidence-based preventative strategies would be informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.
-Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28].
-Meta-analyses of trial-level data often have limited ability to examine exposure-covariate interactions.
-An individual participant data (IPD) meta-analysis is therefore  -->
-
-<!-- Consider sex as a biological variable -->
+<!----------------------------------------------------------------------------->
 
@@
 
-### Definition and Subtypes
+Dementia is a progressive neurocognitive disorder, characterised by impaired memory, reduced executive function and
+
+A
+
+The most common types of which are Alzheimer's disease (AD) and vascular dementia (VaD) [1].
+
+Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative intervention due to the availability of lipid-modifying treatments.
+In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
 
@@
 
-Two important considerations ont he
-
-### Diagnosis
+Two important considerations on the
 
 Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
-<!-- (is this true, or would it be better to say that there is no gold standard test without an autopsy?)--> Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
+<!-- is this true, or would it be better to say that there is no gold standard test without an autopsy?--> Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
 the Mini-Mental State Examination), to clinical tests (e.g.
@@
 
-### Criteria
-
-Several scales are commonly used to diagnose dementia and associated diseases for research purposes.
-Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS--ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM-IV citations**
-
-**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter** \@ref(sys-rev-heading)
-
-### Public Health Importance
+### Public Health importance
 
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,6 an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
-In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
+While approximately have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Despite the increasing number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
 
-### Challenges in the study of dementia using traditional study designs
+### Chronic underfunding
+
+Despite it's
+
+Statistic comparison
+
+Given all of this, the systematic assessment of easily modifiable targets (such as blood lipid levels) for their utility in the prevention of dementia should be considered.
+
+<!----------------------------------------------------------------------------->
+
+### Natural history
+
+Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease [2]. Progression from onset is an average
+
+<!----------------------------------------------------------------------------->
+
+### Alzheimer's disease
+
+Named after Aloi
+
+### Vascular dementia
+
+Second largest underlying pathology of dementia
+
+Diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
+
+<!----------------------------------------------------------------------------->
+
+### Diagnostis criteria
+
+There exist several diagnostic criteria for dementia and related disease, many of which have existed for quite some time and have more recently been updated to reflect current understanding in deme.
+
+In all cases, dementia is diagnosed on the basis of behavioural.
+
+it is a inherently subjective diagnosis made by an experience clinican.
+This means the potential for misclassification both of dementia vs no-dementia and between the different underlying conditions is extremely likely.
+
+<!----------------------------------------------------------------------------->
+
+```{r diagnosticCriteria-setup, results="hide", message=FALSE, echo = FALSE}
+```
+
+```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+
+Several sets of criteria are commonly used to diagnose dementia, and the underlying diseases for research purposes.
+Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS-ADRDA).[@dubois2007]
+
+[**Need first NINCDS-ADRDA citation and DSM-IV citations**]
+
+While these criteria define the, they are informed using practical scales to measure patients cognitive health.
+
+One of the best known of thes scales is the
+
+A further sclae is the MoCA
+
+Also touch on aspects of each, such as the clock-drawing and whether or not they need to validated with input from another person.
+
+<!-- Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in systematic review -->
+
+The distinction between memory scales and dementia diagnosis scales should be noted, and the common confluence of the two addressed.
+
+For example MMSE scores is a tool for assessing cognitive impairment, but does not by itself indicate the absence or presence of dementia.
+A low score on the MMSE should feed into the diagnostic process, potentiall as a screenign tool to help identify which patients require further assessment by a trained clinican.
+Studies that use it alone are likely to be biased.
+
+Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available.
+
+### Differing risk by sex
+
+Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t
+
+Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
+
+Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28].
+
+<!----------------------------------------------------------------------------->
+
+## Challenges in the study of dementia using traditional study designs
 
@@
 
-And different scales
+hr
 
-### History
+<!-- I -->
 
-> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
-Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
-In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences.
-In the MRC/BHF HPS trial,27 similar percentages of participants (0.3% in each---statin vs placebo---group) developed dementia during the 5-year follow-up period.
-The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
-*Taken from Cramer 2008 - included in review*
+<!-- Consider sex as a biological variable -->
 
-There exist only two large scale randomized controlled trials of the effect of statins on dementia risk [CITE] - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
-Both showed no effect of
-
-However, while being widely cited, these studies have major limitations that limiti their utility
-
-in assessing the impact of lipid-lowering treatment on dementia risk.
-
-Queries around how the data were collected, along
+<!----------------------------------------------------------------------------->
 
@@
 
-### Risk factors
+Costs can be categorised as direct and indirect, in terms of direct costs of hospitalisations an, but alos in terms of caring responsibilities for those re
 
-Risk factors for dementia
+<!----------------------------------------------------------------------------->
 
@@
 
-### Preventative measures
+At present, there are no known curative treatments for dementia, though several
 
-At present fe
+Development treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceultical world, given the overall lack of success of multiple promining therapeutics.
+
+<!----------------------------------------------------------------------------->
+
+### Risk factors and Preventative measures
+
+Given the lack of available treatments, a strong focus has landed on preventative measures for dementia.
+
+Several elements are considered to be risk factors for subsequent dementia risk.
+
+These
+
+<!----------------------------------------------------------------------------->
 
 ## Serum lipids
+
+Cholestorol
+
+Basic cholesterol structure is a  steroid nucleus
+
+Cholesterol is a fat soluble molecule, meaning that
+
+<!----------------------------------------------------------------------------->
 
@@
 
+Range of other higher and lower density (VLDL, etc)
+
+<!--- Will need to explain why I am focusing on these fractions rather that looking at others include VLDL, etc --->
+
+<!----------------------------------------------------------------------------->
+
+### Total cholesterol
+
+Total serum cholesterol is a summary measures, derived from the measure c
+
+<!--- Include formula for working out total cholesterol and a table detailing the acceptable ranges. --->
+
+Total cholesterol can be measured directly. Minimal clinical difference in measurements between fasting and non-fasting states.
+
+<!----------------------------------------------------------------------------->
+
+### Triglycerides
+
+These are the smallest/simplest type of lipids and so should go first, then build up to more complex phospholipids like LDL-c, HDL-c.
+
+Triglycerides are a simple molecule
+
+<!----------------------------------------------------------------------------->
+
 ### HDL-c
+
+Cholesterol ratio
+
+<!----------------------------------------------------------------------------->
 
@@
 
-Include formula for working out total cholesterol and the ranges.
-
-LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the :
+LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the:
 
@@
 
-```{block type='correction'}
-Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
-```
-
-### Triglycerides
-
-### Total cholesterol
-
-## Serum lipid interventions
+<!-- Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters. -->
 
@@
 
-Statins are the primary
+Statins are by far away the most common method of modufthe primary
+
+Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid,  by compeitivlely binding with HMG-CoA Reductase (HMG-CoA-R).
+This conversion is the key rate limiting step in the biochemical pathway that produces cholesterol (see Figure \ref()), allowing statins to reduce prevention of cholesterol
 
@@
 
+Lipophic
+
+Lipophilic statins are particularly important in the context of dementia, as they are able to cross the blood-brain barrier.
+
 #### Hydrophilic
@@
 
-## Theoretical framework
+There are a range of other interventions that can be used to modify a persons lipid profile, though each act is slightly different want
+
+For example, ezetimibe
+
+<!----------------------------------------------------------------------------->
+
+## Evidence synthesis
+
+From a brief scoping literature search, Systematic reviews of the literature exist, with two main caveats: __[CITATION NEEDED - REFER to MSc project]__
+
+Firstly, the majority of reviews
+
+<!----------------------------------------------------------------------------->
+
+## Thesis focus: Integrating diverse sources of evidence
 
@@
 
-### Evidence synthesis
+And the aim to integrate diverse sources of evidence. By diverse here,
+
+Of particular interest is the synthesis of evidence from a range of diverse soources,
 
@@
 
-While this thesis does include a research tool (Chapter 2 - systematic searching of preprint) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
+While this thesis does include a research tool Chapter \@ref(sys-rev-tools) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
 
@@
 
-### Involvement of patients and the public
+<!----------------------------------------------------------------------------->
 
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
+### Study designs and sources of bias
 
-## Chapter overview
+<!-- Need to talk about biases here? Or have a different section: Diverse sources of evidence: different underlying biases -->
 
-* __Chapter \@ref(background-heading):__ Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-* __Chapter \@ref(sys-rev-tools-heading)__ This CHhapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the bioRxiv and medRxiv preprint repositories.
-* __Chapter \@ref(sys-rev-heading)__ This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids and lipid. 
-* __Chapter \@ref(cprd-analysis-heading):__ This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
-* __Chapter \@ref(ipd-heading):__ This Chapter describes an individual patient data analysis of several longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+Meta-analyses of randomised controlled trials are commonly seen as the gold standard in the
+
+Indeed in the "evidence pyramid", meta-analysis of trials sit proudly on top. However, there included several potential limitations to this trial-only approach.
+
+RCTs may be unfeasible if the outcome of interest is one with a long prodomal period, such as dementia, <!--- Cross link here to section on presentation of dementia ---> as they would require exteremely long and costly follow-up.[@ritchie2015] <!--- Check citation --->
+
+Additionally randomised trials require clinical equipoise - something that is unlikely in the case of statins, as while equipose may exist, it would be unethical to randomised patients to statins or not given their proven protective effect against coronary disease.
+
+It is no surprise then that the two know existing trials of statins for the prevention of dementia are in fact trials of statins for the prevention of coronary related outcomes.[@mcguinness2016a] The Prospective Study of Pravastatin in the Elderly (PROSPER) examined the protective effect of pravastating on coronary outcomes,
+
+However, while being widely cited and indeed included in a Cochrane review on this topic (ironically, the lead author on this Cochrane review is ), these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
+
+Firstly, there was no clinical cognitive evaluation of patients to .
+In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years.
+As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome.
+
+The second trial, the Medical Research Council/British Health Foundation Protection Study
+
+Additionally, there two trials, whiel putatively examining all cause dementia subject to the limitation described above, do not make any effort to assign an underlying pathogy to each case.
+
+As discussed in Section
+
+<!-- > Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study of Pravastatin in the Elderly (PROSPER) and the Medical Research Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
+Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
+In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences.
+In the MRC/BHF HPS trial,27 similar percentages of participants (0.3% in each---statin vs placebo---group) developed dementia during the 5-year follow-up period.
+The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
+*Taken from Cramer 2008 - included in review* -->
+
+__Maybe take a stand here - and in the systematic review, and say that you are not going to __
+
+There exist only two large scale randomized controlled trials of the effect of statins on dementia risk [CITE] - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
+Both showed no effect of
+
+Queries around how the data were collected, along
+
+A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
+The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent [CITE], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
+Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [CITE].
+
+Despite these encouraging results, evidence from epidemiological studies to date has been anecdotally been contradictory.
+
+Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported widely different results.
+A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
+With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
+
+Observational studies do not represent the only source of evidence examining the link between lipid levels and dementia.
+A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk [23].
+However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia [24,25].
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
+
+Comment here on the use of MR studies as a different approach - one that is growing and commonly preprinted.
+
+The use of newer methodological approaches, such as Mendelian randomisation (MR), has also produced contradictory results.
+In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
+A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk [27].
+However, this study was criticised as it did not exclude the region surrounding the ApoE gene, meaning the risk reduction observed could be driven by variants in this region.
+
+n short, each individual epidemiological approach taken to examine this research question is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk.
+However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
+If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk [26].
+In this context, systematically identifying, assessing and integrating all available evidence in a triangulation framework, regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
+
+This thesis aims to find all exisiting evidence on the relationship between lipids/statins and dementia, critically assess it using a domain based tool
+
+And then triangulate the different sources of evidence along with the primary analyses performed in this thesis.
+
+<!----------------------------------------------------------------------------->
+
+### Different sources of bias
+
+While we can expect different study designs, this thesis also considers diverse sources of evidence in terms of the methodological approaches taken within a
+
+The term "observational study", unlike RCT, belies wide range of analytical approaches,[@thiese2014] each with it's own limitations which can
+
+Of particular interest in the context of interventional research is immortal time bias.
+
+#### Misclassification bias
+
+Incredibly hard to diagnose dementia, and even if diagnosed dementia, how to distinguish between different subtypes.
+
+When using code lists to define outcomes in large, population scale electronic health databases, evidence exists that there is wild misclassification between the
+
+<!--- Be careful here, as you don't account for misclassification in your CPRD study --->
+
+Misclassification can also affect studies of interventions through the intorudction of immortal time. Several high profile observational studies of the effect of statins on dementi.
+
+#### Reverse causation
+
+Reverse causation is where the assumed exposure in an analytical framework is actually the outcome.
+**[CITATION NEEDED]** In the case of lipids and dementia, a reverse casaul relationship would be observed by the early prodomal effects of dementia influencing a change
+
+#### Ascertainment bias
+
+When examining the effect of treatment on low-lying diseases, number of consultations has an impact.
+
+In this context, evidence synthesis exercises must account for these threats to internal validity as part of the synthesis. However, many previous highly cited systematic reviews have now done so.
+
+<!--- This is a key advantage of this study, as we account for . --->
+
+Given the range of biases that can be expected to effect studies into dementia, any evidence synthesis effort must take account of these and perform a robust risk of bias assessment to assess the internal validity.
+
+A key issues here, particularly in the context of using statins as a proxy for blood lipid levels, is that there is a key distinction between internal validity and generalisability.
+One can be called the wrong answer to the right question, the other, the right answer to the wrong question.
+
+Having identified a gap in the literature in the systematic review, both in terms of an absence of observational studies using the specific deisng and in an absence of data related to vascular dementia, in Chapter \@ref(cprd-analysis-heading), I aim to address this evidence gap and provide a further source of information for the triangulation in Chapter \@ref(discussion-heading)
+
+<!----------------------------------------------------------------------------->
+
+### Preprints versus peer-reviewed articles
+
+Preprints
+
+Preprints have existed in several fields, such as the aRxiv in the field of physics and mathematics, but more recently.
+Preprint repositories exist for everything from ecology (EcoEvoRxiv) to meta-research (metaArXiv)
+
+Preprints can
+
+Comment on good concordance between preprinted and published versions
+
+There is much ongoing debate in, particulary in light of the explosion of prep
+
+The outlook on this topic has shifted noticeab
+
+One of the major criticisms of preprints is that they have not yet undergone formal peer review. Some researchers recommend treating
+
+However, t
+
+Additionally, in the context of systematic review.
+This however, substantially increases the need for thourough and detailed risk-of-bias assessment as part of a systematic review.
+In theory this should be donw anyways, but several of the existing highly cited reviews of observationsal studies of the relationship between tstatins and dementia did not perform a risk-of-bias assessment, or used
+
+Checklists for risk of bias domains
+
+However, the a noticeable s
+
+One of the major current limitations for inclusion of data from preprint repositories in systematic reviews is the absence of a replicable and transparent search tool for performing systematic searches.
+The tool presented in Chapter \@ref(sys-rev-tools) aims to address this.
+
+<!----------------------------------------------------------------------------->
+
+### Summary level results vs existing un-analysed datasets
+
+Analysis of summary level data, that is the data extracted from publications describing primary studies, can only take investigations so far.
+
+We are limited to the question that the original investigators wanted to ask, and the summar statistics they choose to present (see Section , which contributed to a discursive piece on present summary statistics of prevention reasearch for eacy inclusion in systematic reviews).
+
+However, requesting the individual patient-level data from relevant cohorts is error prone. A commonly cited example is the editor of Molecular Brain, who require
+
+As such, portals
+
+There has recently been a push to acknowledge the systematic differences between the sexes in terms of the life course and propensity for different diseases. As discussed above in Section
+
+If lipids have a causal role in development of dementia, evidence-based preventative strategies would be informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.
+
+This thesis will request raw data from primary studies identified by the systematic review and through other means, including the DPUK Portal, describe how it could be made more readily available in the first place and
+
+However, due to a lack of primary studies readily presenting this data, meta-analyses of patient-level data often have limited ability to examine exposure-covariate interactions.
+An individual participant data (IPD) meta-analysis is therefore the best (/only) option to examine the modification of dementia risk by individual-level covariates.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-### Aim
+Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the risk of subsequent dementia.
 
-### Objectives
+### Aims and Objectives
 
--   To review the published literature with respect to the effec tof lipids and lipid regulating agents\
--   To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink
--   To meta-analyze the
+The specific research questions that this thesis seeks to address are:
+
+* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
+* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
+* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
+* To meta-analyse previously unexplored dataset as part of a
+
+### Thesis Structure
+
+Chapters are self-contained, presenting the methods and results of that specific research project.
+The are bookended by introductory and discussion sections which place the methods and results in context.
+Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appedix-ppi) for more detail on the group).
+
+-   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
+This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
+-   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+-   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids, and interventions that modified blood lipids, and dementia.
+-   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+-   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several previously unanalysed longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+
+## Outputs from this thesis {#thesis-output}
+
+The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools.
+
+### Contributions to the scientific literature
+
+During the course of this thesis,
+
+See Appendix \@ref
+
+&nbsp;
+
+_McGuinness, L.
+A., and L Schmidt.
+"medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 (2020): 2651.
+DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
+
+A short paper introducing the open source preprint search tool described in Chapter \@ref(sys-rev-tools).
+<!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience.
+--->
+
+&nbsp;
+
+_Hennessy, E.
+A., Acabchuk, R., Arnold, P.
+A., Dunn, A.
+G., Foo, Y.
+Z., Johnson, B.
+T., Geange, S.
+R., Haddaway, N.
+R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
+Welch, V.,  McGuinness L.
+A.
+(2020).
+Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
+MetaArXiv.DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_
+
+The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers in prevention science is currently under review at Prevention Science.
+
+I co-wrote the discursive piece with Emily Hennessy (see author declarations).
+
+&nbsp;
+
+_McGuinness, L.
+A., and J.
+P.
+T.
+Higgins.
+"Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Methods (2020).
+DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
+
+The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
+See Appendix \@ref(appendix-robvis) for more details on this tool.
+
+For information on the additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
+
+&nbsp;
+
+### Software
+**`medrxvir`**
+
+An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
+See Chapter \@ref(sys-rev-tools-heading) for more details.
+Install a stable version of the package from CRAN or alternatively install the development version from GitHub using:
+
+```{r, eval = FALSE}
+# CRAN version
+install.packages("medrxivr")
+
+# Development version
+devtools::install_github("mcguinlu/medrxivr")
+```
+
+&nbsp;
+
+**`robvis`**
+
+An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
+See Appendix \@ref(appendix-robvis) for more details.
+Install a stable version of the package from CRAN or alternatively install the development version from GitHub using:
+
+``` {r, eval = FALSE}
+# CRAN version
+install.packages("robvis")
+
+# Development version
+devtools::install_github("mcguinlu/robvis")
+```
+
+&nbsp;
+
+### Presentations/Talks
+
+* Abstract accepted to the Cochrane Colloquium 2019
+* ARUK abstract on systematic review <!--- I hope! --->
+* Presentations to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
+* Risk of bias webinars for Evidence Synthesis Ireland
+* Presentations to internal department wide seminar series, including the Methods in Evidence Synthesis Salon (MESS) and the MRC-IEU seminar series.
+
+## Summary
+
+This Chapter has provided background information on the core elements of the central research question, framed the research in the context of a specific theoretical framework, and described the contributions of the research in this thesis to the scientific literature.

### 2021-04-07 02-Chp-Background.tex
End of day: 0

--- 2021-04-07 02-Chp-Background.Rmd
@@
----
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% BRIEF VERSION OF OXFORD THESIS TEMPLATE FOR CHAPTER PREVIEWS
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
+%%%%% CHOOSE PAGE LAYOUT
+% format for PDF output (ie equal margins, no extra blank pages):
+\documentclass[a4paper,nobind]{templates/ociamthesis}
+
+% UL 30 Nov 2018 pandoc puts lists in 'tightlist' command when no space between bullet points in Rmd file
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\usepackage{float}
+
+% UL 1 Dec 2018, fix to include code in shaded environments
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+
+%UL 2 Dec 2018 add a bit of white space before and after code blocks
+\renewenvironment{Shaded}
+{
+  \vspace{4pt}%
+  \begin{snugshade}%
+}{%
+  \end{snugshade}%
+  \vspace{4pt}%
+}
+%UL 2 Dec 2018 reduce whitespace around verbatim environments
+\usepackage{etoolbox}
+\makeatletter
+\preto{\@verbatim}{\topsep=0pt \partopsep=0pt }
+\makeatother
+
+%UL 28 Mar 2019, enable strikethrough
+\usepackage[normalem]{ulem}
+
+%UL 3 Nov 2019, avoid mysterious error from not having hyperref included
+\usepackage{hyperref}
+
+%%%%% SELECT YOUR DRAFT OPTIONS
+% Three options going on here; use in any combination.  But remember to turn the first two off before
+% generating a PDF to send to the printer!
+
+% This adds a "DRAFT" footer to every normal page.  (The first page of each chapter is not a "normal" page.)
+
+% This highlights (in blue) corrections marked with (for words) \mccorrect{blah} or (for whole
+% paragraphs) \begin{mccorrection} . . . \end{mccorrection}.  This can be useful for sending a PDF of
+% your corrected thesis to your examiners for review.  Turn it off, and the blue disappears.
+
+%%%%% BIBLIOGRAPHY SETUP
+% Note that your bibliography will require some tweaking depending on your department, preferred format, etc.
+% The options included below are just very basic "sciencey" and "humanitiesey" options to get started.
+% If you've not used LaTeX before, I recommend reading a little about biblatex/biber and getting started with it.
+% If you're already a LaTeX pro and are used to natbib or something, modify as necessary.
+% Either way, you'll have to choose and configure an appropriate bibliography format...
+
+% The science-type option: numerical in-text citation with references in order of appearance.
+% \usepackage[style=numeric-comp, sorting=none, backend=biber, doi=false, isbn=false]{biblatex}
+% \newcommand*{\bibtitle}{References}
+
+% The humanities-type option: author-year in-text citation with an alphabetical works cited.
+% \usepackage[style=authoryear, sorting=nyt, backend=biber, maxcitenames=2, useprefix, doi=false, isbn=false]{biblatex}
+% \newcommand*{\bibtitle}{Works Cited}
+
+%UL 3 Dec 2018: set this from YAML in index.Rmd
+\usepackage[style=numeric-comp, sorting=none, backend=biber, doi=false, isbn=false]{biblatex}
+\newcommand*{\bibtitle}{References}
+
+% This makes the bibliography left-aligned (not 'justified') and slightly smaller font.
+\renewcommand*{\bibfont}{\raggedright\small}
+
+% Change this to the name of your .bib file (usually exported from a citation manager like Zotero or EndNote).
+\addbibresource{}
+
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{CSLReferences}%
+  {}%
+  {\par}
+
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+
+\usepackage{calc}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+
+%%%%% YOUR OWN PERSONAL MACROS
+% This is a good place to dump your own LaTeX macros as they come up.
+
+% To make text superscripts shortcuts
+	\renewcommand{\th}{\textsuperscript{th}} % ex: I won 4\th place
+	\newcommand{\nd}{\textsuperscript{nd}}
+	\renewcommand{\st}{\textsuperscript{st}}
+	\newcommand{\rd}{\textsuperscript{rd}}
+
+%%%%% THE ACTUAL DOCUMENT STARTS HERE
+\begin{document}
+
+%%%%% CHOOSE YOUR LINE SPACING HERE
+% This is the official option.  Use it for your submission copy and library copy:
+\setlength{\textbaselineskip}{22pt plus2pt}
+% This is closer spacing (about 1.5-spaced) that you might prefer for your personal copies:
+%\setlength{\textbaselineskip}{18pt plus2pt minus1pt}
+
+% UL: You can set the general paragraph spacing here - I've set it to 2pt (was 0) so
+% it's less claustrophobic
+\setlength{\parskip}{2pt plus 1pt}
+
+% Leave this line alone; it gets things started for the real document.
+\setlength{\baselineskip}{\textbaselineskip}
+
+% all your chapters and appendices will appear here
+\begin{savequote}
 Science knows it doesn't know everything; otherwise, it'd stop.
-```
+\end{savequote}
 
-(ref:dara-quote) --- Dara O'Briain
+\hypertarget{background-heading}{%
+\chapter{Background \& Objectives}\label{background-heading}}
 
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-knitr::read_chunk("R/background.R")
-```
+\minitoc
 
-# Background & Objectives {#background-heading}
+\hypertarget{lay-summary}{%
+\section{Lay summary}\label{lay-summary}}
 
-\minitoc <!-- this will include a mini table of contents-->
-
-## Lay summary
-
-Around __[NUMBER]__ people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
+Around \textbf{{[}NUMBER{]}} people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
 No cure for dementia exists, so researchers are trying to find ways to prevent the condition.
@@
 
-I will use all available evidence, including that preprinted by authors (i.e.
-not formally reviewed by others in their field to assess the accuracry of their claims) to assess whether lipid levels cause dementia.
+I will use all available evidence, including that preprinted by authors (i.e.~not formally reviewed by others in their field to assess the accuracry of their claims) to assess whether lipid levels cause dementia.
 
@@
 
-<!----------------------------------------------------------------------------->
-
-## Introduction
-
-<!-- This chapter provides the context of the thesis.
-It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality.
-The chapter briefly explores different measures of increased adiposity and potential hypotheses for underlying aetiology of diseases associated with increased adiposity.
-Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed.
-*From Matt Lee's thesis.* -->
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-## Dementia
+\hypertarget{dementia}{%
+\section{Dementia}\label{dementia}}
 
@@
 
-The most common types of which are Alzheimer's disease (AD) and vascular dementia (VaD) [1].
+The most common types of which are Alzheimer's disease (AD) and vascular dementia (VaD) {[}1{]}.
 
@@
 Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory.
-The most common causes of dementia are Alzheimer's disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively.
-The remaining 10-30% of cases are caused other dementia subtypes (e.g.
-Lewy Body dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).
+The most common causes of dementia are Alzheimer's disease and vascular dementia, accounting for \textasciitilde60-80\% and \textasciitilde10\% of cases respectively.
+The remaining 10-30\% of cases are caused other dementia subtypes (e.g.~Lewy Body dementia) or by progression of other neurological diseases (e.g.~Parkinson's disease).
 
@@
 Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
-<!-- is this true, or would it be better to say that there is no gold standard test without an autopsy?--> Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
-the Mini-Mental State Examination), to clinical tests (e.g.
-Magnetic Resonance Imaging (MRI) scans).
+Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.~the Mini-Mental State Examination), to clinical tests (e.g.~Magnetic Resonance Imaging (MRI) scans).
 
-### Public Health importance
+\hypertarget{public-health-importance}{%
+\subsection{Public Health importance}\label{public-health-importance}}
 
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
-While approximately have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Despite the increasing number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,{[}@prince2016{]} an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
+While approximately have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.{[}@baker2019{]} Globally, the prevalence of dementia is expected to reach 75 million by 2030.{[}@prince2016{]} Despite the increasing number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
 
-### Chronic underfunding
+\hypertarget{chronic-underfunding}{%
+\subsection{Chronic underfunding}\label{chronic-underfunding}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\hypertarget{natural-history}{%
+\subsection{Natural history}\label{natural-history}}
 
-### Natural history
+Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease {[}2{]}.
+Progression from onset is an average
 
-Much remains unknown about dementia pathogenesis, despite research implicating amyloid plaques and neurofibrillary tangles as potential mechanisms of disease [2]. Progression from onset is an average
-
-<!----------------------------------------------------------------------------->
-
-### Alzheimer's disease
+\hypertarget{alzheimers-disease}{%
+\subsection{Alzheimer's disease}\label{alzheimers-disease}}
 
@@
 
-### Vascular dementia
+\hypertarget{vascular-dementia}{%
+\subsection{Vascular dementia}\label{vascular-dementia}}
 
@@
 
-Diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
+Diagnosed using the NINCDS-AIREN criteria.{[}@roman1993vascular{]}
 
-<!----------------------------------------------------------------------------->
-
-### Diagnostis criteria
+\hypertarget{diagnostis-criteria}{%
+\subsection{Diagnostis criteria}\label{diagnostis-criteria}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\begin{table}[!h]
 
-```{r diagnosticCriteria-setup, results="hide", message=FALSE, echo = FALSE}
-```
-
-```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
-```
-
-<!----------------------------------------------------------------------------->
+\caption{\label{tab:diagnosticCriteria-table}Diagnostic criteria used to diagnose different types of dementia}
+\centering
+\begin{tabular}[t]{lll}
+\toprule
+Disease & Criteria & Summary\\
+\midrule
+AD & NINCDS-ADRDA & Lorem ipsum\\
+VaD & NINCDS-AIREN & Lorem ipsum 2\\
+\bottomrule
+\end{tabular}
+\end{table}
 
 Several sets of criteria are commonly used to diagnose dementia, and the underlying diseases for research purposes.
-Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS-ADRDA).[@dubois2007]
+Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS-ADRDA).{[}@dubois2007{]}
 
-[**Need first NINCDS-ADRDA citation and DSM-IV citations**]
+{[}\textbf{Need first NINCDS-ADRDA citation and DSM-IV citations}{]}
 
@@
 
-<!-- Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in systematic review -->
-
 The distinction between memory scales and dementia diagnosis scales should be noted, and the common confluence of the two addressed.
@@
 
-### Differing risk by sex
+\hypertarget{differing-risk-by-sex}{%
+\subsection{Differing risk by sex}\label{differing-risk-by-sex}}
 
@@
 
-Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
+Rate of dementia/AD differs in men and women
 
-Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28].
+Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex {[}16,28{]}.
 
-<!----------------------------------------------------------------------------->
-
-## Challenges in the study of dementia using traditional study designs
+\hypertarget{challenges-in-the-study-of-dementia-using-traditional-study-designs}{%
+\section{Challenges in the study of dementia using traditional study designs}\label{challenges-in-the-study-of-dementia-using-traditional-study-designs}}
 
@@
 This fact is further complicated by the long latency of dementia, which necessitates a costly long-term approach to patient follow-up.
-Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g.
-the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10
+Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g.~the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10
 
@@
 
-*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia.
+\emph{Cognitive impairment not dementia} (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia.
 
@@
 
-<!-- I -->
-
-<!-- Consider sex as a biological variable -->
-
-<!----------------------------------------------------------------------------->
-
-### Economic impact
+\hypertarget{economic-impact}{%
+\subsection{Economic impact}\label{economic-impact}}
 
@@
 
-Patients with dementia stay in hospital for longer,[@mollers2019]
+Patients with dementia stay in hospital for longer,{[}@mollers2019{]}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### Treatments
+\hypertarget{treatments}{%
+\subsection{Treatments}\label{treatments}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### Risk factors and Preventative measures
+\hypertarget{risk-factors-and-preventative-measures}{%
+\subsection{Risk factors and Preventative measures}\label{risk-factors-and-preventative-measures}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-## Serum lipids
+\hypertarget{serum-lipids}{%
+\section{Serum lipids}\label{serum-lipids}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### Range of lipids
+\hypertarget{range-of-lipids}{%
+\subsection{Range of lipids}\label{range-of-lipids}}
 
@@
 
-Range of other higher and lower density (VLDL, etc)
+Range of other higher and lower density
 
-<!--- Will need to explain why I am focusing on these fractions rather that looking at others include VLDL, etc --->
-
-<!----------------------------------------------------------------------------->
-
-### Total cholesterol
+\hypertarget{total-cholesterol}{%
+\subsection{Total cholesterol}\label{total-cholesterol}}
 
@@
 
-<!--- Include formula for working out total cholesterol and a table detailing the acceptable ranges. --->
-
 Total cholesterol can be measured directly. Minimal clinical difference in measurements between fasting and non-fasting states.
 
-<!----------------------------------------------------------------------------->
-
-### Triglycerides
+\hypertarget{triglycerides}{%
+\subsection{Triglycerides}\label{triglycerides}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### HDL-c
+\hypertarget{hdl-c}{%
+\subsection{HDL-c}\label{hdl-c}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\hypertarget{ldl-c}{%
+\subsection{LDL-c}\label{ldl-c}}
 
-### LDL-c
+LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,{[}@friedewald1972{]} where the:
 
-LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the:
-
-$$LDLc \approx TC - HDLc - kTG$$ where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
+\[LDLc \approx TC - HDLc - kTG\] where \(k\) is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
 
@@
 
-<!-- Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters. -->
-
-### Statins
+\hypertarget{statins}{%
+\subsection{Statins}\label{statins}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\begin{figure}
+\includegraphics[width=1\linewidth]{figures/sys-rev/prisma_flow} \caption[Statin mechanism of action]{\textbf{Statin mechanism of action:}}\label{fig:statin-mechanisam}
+\end{figure}
 
-(ref:statin-mechanisam-cap) **Statin mechanism of action:**
-
-(ref:statin-mechanisam-scap) Statin mechanism of action
-
-```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-#### Lipophilic
+\hypertarget{lipophilic}{%
+\subsubsection{Lipophilic}\label{lipophilic}}
 
@@
 
-#### Hydrophilic
+\hypertarget{hydrophilic}{%
+\subsubsection{Hydrophilic}\label{hydrophilic}}
 
-### Other lipid regulating agents (LRA)
+\hypertarget{other-lipid-regulating-agents-lra}{%
+\subsection{Other lipid regulating agents (LRA)}\label{other-lipid-regulating-agents-lra}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\hypertarget{evidence-synthesis}{%
+\section{Evidence synthesis}\label{evidence-synthesis}}
 
-## Evidence synthesis
-
-From a brief scoping literature search, Systematic reviews of the literature exist, with two main caveats: __[CITATION NEEDED - REFER to MSc project]__
+From a brief scoping literature search, Systematic reviews of the literature exist, with two main caveats: \textbf{{[}CITATION NEEDED - REFER to MSc project{]}}
 
@@
 
-<!----------------------------------------------------------------------------->
-
-## Thesis focus: Integrating diverse sources of evidence
+\hypertarget{thesis-focus-integrating-diverse-sources-of-evidence}{%
+\section{Thesis focus: Integrating diverse sources of evidence}\label{thesis-focus-integrating-diverse-sources-of-evidence}}
 
@@
 
-While this thesis does include a research tool Chapter \@ref(sys-rev-tools) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
+While this thesis does include a research tool Chapter \ref{sys-rev-tools} and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
 
-More specifically this includes the accurate searching of sources of grey literature (as enabled by the too presented in Chapter \@ref(sys-rev-tools-heading)) and risk of bias assessment.
+More specifically this includes the accurate searching of sources of grey literature (as enabled by the too presented in Chapter \ref{sys-rev-tools-heading}) and risk of bias assessment.
 
-<!----------------------------------------------------------------------------->
-
-### Study designs and sources of bias
-
-<!-- Need to talk about biases here? Or have a different section: Diverse sources of evidence: different underlying biases -->
+\hypertarget{study-designs-and-sources-of-bias}{%
+\subsection{Study designs and sources of bias}\label{study-designs-and-sources-of-bias}}
 
@@
 
-Indeed in the "evidence pyramid", meta-analysis of trials sit proudly on top. However, there included several potential limitations to this trial-only approach.
+Indeed in the ``evidence pyramid'', meta-analysis of trials sit proudly on top. However, there included several potential limitations to this trial-only approach.
 
-RCTs may be unfeasible if the outcome of interest is one with a long prodomal period, such as dementia, <!--- Cross link here to section on presentation of dementia ---> as they would require exteremely long and costly follow-up.[@ritchie2015] <!--- Check citation --->
+RCTs may be unfeasible if the outcome of interest is one with a long prodomal period, such as dementia, as they would require exteremely long and costly follow-up.{[}@ritchie2015{]}
 
@@
 
-It is no surprise then that the two know existing trials of statins for the prevention of dementia are in fact trials of statins for the prevention of coronary related outcomes.[@mcguinness2016a] The Prospective Study of Pravastatin in the Elderly (PROSPER) examined the protective effect of pravastating on coronary outcomes,
+It is no surprise then that the two know existing trials of statins for the prevention of dementia are in fact trials of statins for the prevention of coronary related outcomes.{[}@mcguinness2016a{]} The Prospective Study of Pravastatin in the Elderly (PROSPER) examined the protective effect of pravastating on coronary outcomes,
 
@@
 In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome.
+As highlighted in Section @() , change in scores alone is insufficient to diagnose a dementia outcome.
 
@@
 
-<!-- > Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study of Pravastatin in the Elderly (PROSPER) and the Medical Research Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
-Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
-In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences.
-In the MRC/BHF HPS trial,27 similar percentages of participants (0.3% in each---statin vs placebo---group) developed dementia during the 5-year follow-up period.
-The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
-*Taken from Cramer 2008 - included in review* -->
+\textbf{Maybe take a stand here - and in the systematic review, and say that you are not going to }
 
-__Maybe take a stand here - and in the systematic review, and say that you are not going to __
-
-There exist only two large scale randomized controlled trials of the effect of statins on dementia risk [CITE] - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
+There exist only two large scale randomized controlled trials of the effect of statins on dementia risk {[}CITE{]} - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane {[}@mcguinness2016b{]}.
 Both showed no effect of
@@
 A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent [CITE], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [CITE].
+The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent {[}CITE{]}, while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
+Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility {[}CITE{]}.
 
@@
 Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported widely different results.
-A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
-With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
+A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD {[}8-13{]}, though other studies have shown no association {[}14-17{]}, or a reduced susceptibility {[}18,19{]}.
+With regards VaD, decreased levels of HDL-c appear to be associated with increased risk {[}18,20,21{]}, while for LDL-c, studies have reported both positive and negative association {[}18,22{]}.
 
 Observational studies do not represent the only source of evidence examining the link between lipid levels and dementia.
-A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk [23].
-However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia [24,25].
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
+A recent Cochrane review identified two large randomised controlled trials (RCTs) of statins for the prevention of dementia, indicating that assignment to late-life lipid modifying treatment, as a proxy for lower lipid levels, does not reduce dementia risk {[}23{]}.
+However, both RCTs were limited, primarily by the relatively short follow-up period examined, while one failed to report the criteria used to diagnose dementia {[}24,25{]}.
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited {[}23{]}.
 
@@
 The use of newer methodological approaches, such as Mendelian randomisation (MR), has also produced contradictory results.
-In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
-A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk [27].
+In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference {[}26{]}.
+A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk {[}27{]}.
 However, this study was criticised as it did not exclude the region surrounding the ApoE gene, meaning the risk reduction observed could be driven by variants in this region.
@@
 However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
-If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk [26].
+If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk {[}26{]}.
 In this context, systematically identifying, assessing and integrating all available evidence in a triangulation framework, regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
@@
 
-<!----------------------------------------------------------------------------->
-
-### Different sources of bias
+\hypertarget{different-sources-of-bias}{%
+\subsection{Different sources of bias}\label{different-sources-of-bias}}
 
@@
 
-The term "observational study", unlike RCT, belies wide range of analytical approaches,[@thiese2014] each with it's own limitations which can
+The term ``observational study'', unlike RCT, belies wide range of analytical approaches,{[}@thiese2014{]} each with it's own limitations which can
 
@@
 
-#### Misclassification bias
+\hypertarget{misclassification-bias}{%
+\subsubsection{Misclassification bias}\label{misclassification-bias}}
 
@@
 
-<!--- Be careful here, as you don't account for misclassification in your CPRD study --->
-
 Misclassification can also affect studies of interventions through the intorudction of immortal time. Several high profile observational studies of the effect of statins on dementi.
 
-#### Reverse causation
+\hypertarget{reverse-causation}{%
+\subsubsection{Reverse causation}\label{reverse-causation}}
 
 Reverse causation is where the assumed exposure in an analytical framework is actually the outcome.
-**[CITATION NEEDED]** In the case of lipids and dementia, a reverse casaul relationship would be observed by the early prodomal effects of dementia influencing a change
+\textbf{{[}CITATION NEEDED{]}} In the case of lipids and dementia, a reverse casaul relationship would be observed by the early prodomal effects of dementia influencing a change
 
-#### Ascertainment bias
+\hypertarget{ascertainment-bias}{%
+\subsubsection{Ascertainment bias}\label{ascertainment-bias}}
 
@@
 In this context, evidence synthesis exercises must account for these threats to internal validity as part of the synthesis. However, many previous highly cited systematic reviews have now done so.
-
-<!--- This is a key advantage of this study, as we account for . --->
 
@@
 
-Having identified a gap in the literature in the systematic review, both in terms of an absence of observational studies using the specific deisng and in an absence of data related to vascular dementia, in Chapter \@ref(cprd-analysis-heading), I aim to address this evidence gap and provide a further source of information for the triangulation in Chapter \@ref(discussion-heading)
+Having identified a gap in the literature in the systematic review, both in terms of an absence of observational studies using the specific deisng and in an absence of data related to vascular dementia, in Chapter \ref{cprd-analysis-heading}, I aim to address this evidence gap and provide a further source of information for the triangulation in Chapter \ref{discussion-heading}
 
-<!----------------------------------------------------------------------------->
-
-### Preprints versus peer-reviewed articles
+\hypertarget{preprints-versus-peer-reviewed-articles}{%
+\subsection{Preprints versus peer-reviewed articles}\label{preprints-versus-peer-reviewed-articles}}
 
@@
 One of the major current limitations for inclusion of data from preprint repositories in systematic reviews is the absence of a replicable and transparent search tool for performing systematic searches.
-The tool presented in Chapter \@ref(sys-rev-tools) aims to address this.
+The tool presented in Chapter \ref{sys-rev-tools} aims to address this.
 
-<!----------------------------------------------------------------------------->
-
-### Summary level results vs existing un-analysed datasets
+\hypertarget{summary-level-results-vs-existing-un-analysed-datasets}{%
+\subsection{Summary level results vs existing un-analysed datasets}\label{summary-level-results-vs-existing-un-analysed-datasets}}
 
@@
 
-<!----------------------------------------------------------------------------->
+\hypertarget{aims-and-objectives-of-the-thesis}{%
+\section{Aims and Objectives of the thesis}\label{aims-and-objectives-of-the-thesis}}
 
-## Aims and Objectives of the thesis
-
-### Hypothesis
+\hypertarget{hypothesis}{%
+\subsection{Hypothesis}\label{hypothesis}}
 
@@
 
-### Aims and Objectives
+\hypertarget{aims-and-objectives}{%
+\subsection{Aims and Objectives}\label{aims-and-objectives}}
 
@@
 
-* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
-* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
-* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
-* To meta-analyse previously unexplored dataset as part of a
+\begin{itemize}
+\tightlist
+\item
+  To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
+\item
+  To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
+\item
+  To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
+\item
+  To meta-analyse previously unexplored dataset as part of a
+\end{itemize}
 
-### Thesis Structure
+\hypertarget{thesis-structure}{%
+\subsection{Thesis Structure}\label{thesis-structure}}
 
@@
 The are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appedix-ppi) for more detail on the group).
+Each chapter is prefaced by a ``Lay'' or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \ref{disc-PPI} for a discussion of the group's involvement and Appendix \ref{appedix-ppi} for more detail on the group).
 
--   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
+\begin{itemize}
+\tightlist
+\item
+  \textbf{Chapter \ref{background-heading}:} Background information on dementia and blood lipid levels.
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids, and interventions that modified blood lipids, and dementia.
--   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
--   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several previously unanalysed longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+\item
+  \textbf{Chapter \ref{sys-rev-tools-heading}:} This Chapter introduces a new tool, the \texttt{medrxivr} R package, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+\item
+  \textbf{Chapter \ref{sys-rev-heading}:} This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids, and interventions that modified blood lipids, and dementia.
+\item
+  \textbf{Chapter \ref{cprd-analysis-heading}:} This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+\item
+  \textbf{Chapter \ref{ipd-heading}:} This Chapter describes an individual patient data analysis of several previously unanalysed longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+\end{itemize}
 
-## Outputs from this thesis {#thesis-output}
+\hypertarget{thesis-output}{%
+\section{Outputs from this thesis}\label{thesis-output}}
 
@@
 
-### Contributions to the scientific literature
+\hypertarget{contributions-to-the-scientific-literature}{%
+\subsection{Contributions to the scientific literature}\label{contributions-to-the-scientific-literature}}
 
@@
 
-See Appendix \@ref
+See Appendix @ref
 
-&nbsp;
+~
+
+\usepackage{hanging}
+\begin{hangparas}{.25in}{1}
 
@@
 DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
+\end{hangparas}
 
-A short paper introducing the open source preprint search tool described in Chapter \@ref(sys-rev-tools).
-<!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience.
---->
+A short paper introducing the open source preprint search tool described in Chapter \ref{sys-rev-tools}.
 
-&nbsp;
+~
 
-_Hennessy, E.
+\emph{Hennessy, E.
 A., Acabchuk, R., Arnold, P.
@@
 Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
-MetaArXiv.DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_
+MetaArXiv.DOI: \href{https://doi.org/10.31222/osf.io/ptg9j}{10.31222/osf.io/ptg9j}}
 
-The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers in prevention science is currently under review at Prevention Science.
+The experience of extracting data for the systematic review in Chapter \ref{sys-rev-heading} inspired a practical guide for researchers in prevention science is currently under review at Prevention Science.
 
@@
 
-&nbsp;
+~
 
-_McGuinness, L.
+\emph{McGuinness, L.
 A., and J.
@@
 Higgins.
-"Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Methods (2020).
-DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
+``Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments.'' Research Synthesis Methods (2020).
+DOI: \href{https://doi.org/10.1002/jrsm.1411}{10.1002/jrsm.1411}}
 
-The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
-See Appendix \@ref(appendix-robvis) for more details on this tool.
+The tool used to visualise the risk-of-bias assessments in Chapter \ref{sys-rev-heading} has been published in Research Synthesis Methods.
+See Appendix \ref{appendix-robvis} for more details on this tool.
 
-For information on the additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
+For information on the additional contributions to the scientific literature not directly related to this thesis, see Appendix \ref{appendix-publications}.
 
-&nbsp;
+~
 
-### Software
-**`medrxvir`**
+\hypertarget{software}{%
+\subsection{Software}\label{software}}
 
-An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
-See Chapter \@ref(sys-rev-tools-heading) for more details.
+\textbf{\texttt{medrxvir}}
+
+An R package and associated \texttt{shiny} web application that allows users to easily search and retrieve bibliographic data from the medRxiv{[}@rawlinson2019{]} and bioRxiv{[}@sever2019{]} preprint repositories.
+See Chapter \ref{sys-rev-tools-heading} for more details.
 Install a stable version of the package from CRAN or alternatively install the development version from GitHub using:
 
-```{r, eval = FALSE}
-# CRAN version
-install.packages("medrxivr")
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# CRAN version}
+\FunctionTok{install.packages}\NormalTok{(}\StringTok{"medrxivr"}\NormalTok{)}
 
-# Development version
-devtools::install_github("mcguinlu/medrxivr")
-```
+\CommentTok{\# Development version}
+\NormalTok{devtools}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{"mcguinlu/medrxivr"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
-&nbsp;
+~
 
-**`robvis`**
+\textbf{\texttt{robvis}}
 
-An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
-See Appendix \@ref(appendix-robvis) for more details.
+An R package and associated \texttt{shiny} web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
+See Appendix \ref{appendix-robvis} for more details.
 Install a stable version of the package from CRAN or alternatively install the development version from GitHub using:
 
-``` {r, eval = FALSE}
-# CRAN version
-install.packages("robvis")
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# CRAN version}
+\FunctionTok{install.packages}\NormalTok{(}\StringTok{"robvis"}\NormalTok{)}
 
-# Development version
-devtools::install_github("mcguinlu/robvis")
-```
+\CommentTok{\# Development version}
+\NormalTok{devtools}\SpecialCharTok{::}\FunctionTok{install\_github}\NormalTok{(}\StringTok{"mcguinlu/robvis"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
 
-&nbsp;
+~
 
-### Presentations/Talks
+\hypertarget{presentationstalks}{%
+\subsection{Presentations/Talks}\label{presentationstalks}}
 
-* Abstract accepted to the Cochrane Colloquium 2019
-* ARUK abstract on systematic review <!--- I hope! --->
-* Presentations to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
-* Risk of bias webinars for Evidence Synthesis Ireland
-* Presentations to internal department wide seminar series, including the Methods in Evidence Synthesis Salon (MESS) and the MRC-IEU seminar series.
+\begin{itemize}
+\tightlist
+\item
+  Abstract accepted to the Cochrane Colloquium 2019
+\item
+  ARUK abstract on systematic review
+\item
+  Presentations to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
+\item
+  Risk of bias webinars for Evidence Synthesis Ireland
+\item
+  Presentations to internal department wide seminar series, including the Methods in Evidence Synthesis Salon (MESS) and the MRC-IEU seminar series.
+\end{itemize}
 
-## Summary
+\hypertarget{summary}{%
+\section{Summary}\label{summary}}
 
 This Chapter has provided background information on the core elements of the central research question, framed the research in the context of a specific theoretical framework, and described the contributions of the research in this thesis to the scientific literature.
+
+%%%%% REFERENCES
+
+% JEM: Quote for the top of references (just like a chapter quote if you're using them).  Comment to skip.
+% \begin{savequote}[8cm]
+% The first kind of intellectual and artistic personality belongs to the hedgehogs, the second to the foxes \dots
+%   \qauthor{--- Sir Isaiah Berlin \cite{berlin_hedgehog_2013}}
+% \end{savequote}
+
+\setlength{\baselineskip}{0pt} % JEM: Single-space References
+
+{\renewcommand*\MakeUppercase[1]{#1}%
+\printbibliography[heading=bibintoc,title={\bibtitle}]}
+
+\end{document}

### 2021-04-07 04-Chp-Systematic-Review.Rmd
End of day: 0

@@
 
-### Risk of bias assessment
+### Risk of bias assessment {#risk-of-bias}
 
@@
 
+I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.
+
+Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
+
 At present, no risk of bias assessment tool for Mendelian randomization studies is available.
-Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE]
+Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob).
+Advance results from this review were obtained from contact with the authors.
 
-Data will be visualized using a paired forest and risk of bias plot, created using the `robvis` tool.
+Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
 This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]
-
-The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020]
-
-A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review were obtained from contact with the authors.
 
@@
 
-## Triangualtion across evidence sources
+### Triangualtion across evidence sources
 
@@
 
-While these preprint have subsequently
+On further investigation, the argument that .
+
+It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
+
+However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
+
+While concerns have been raised that
+
+Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
+
+A common criticism of preprinted articles is that they have not formally been peer-reviewed.
+__[CITATION NEEDED]__ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
+
+> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
+
+References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
+
+The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
+
+While [__some__] preprint have subsequently been published, this does not cause any major issues.
 
@@
 
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [ALSO CITE WILKINSON AND MCGUINNESS HERE].
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.
 
@@
 
-I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by [CITE]):
+I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):
 

### 2021-04-07 06-Chp-IPD-Analysis.Rmd
Updates
End of day: 0

@@
 
-## Data sources
+## Methods
+
+### Data sources
+
+Several cohort studies were approach
+
+<!-- Need exact number approach -->
 
@@
 
+## Risk of bias assessment
+
+Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
+
+<!--- Inlcude CPRD analysis here, but dou --->
+
+## Data cleaning
+
 ## Discussion
 
-Letters sent to
+Letters sent to all cohorts identified through the
 
-This is likely due to my junior position as a ECR
+This is likely due to my junior position as a early a
 
-Range of reasons why
+Range of reasons why data is not made available.
+
+Unfortunately,
+
+As part of this,
+
+As part of this, an analysis of
+
+## Discussion
+
+Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.

### 2021-04-07 front-and-back-matter/99-appendices.Rmd
End of day: 0

@@
 ## Chapter \@ref(intro-heading) {#appendix-into}
+
+### Publications beyond the scope of this thesis {#appendix-publications}
+
+__Peer reviewed__
+
+  * McGuinness & Sheppard. Comparison of pairwise
+
+  * PRISMA main paper
+
+  * PRISMA E&E
+
+  * PRISMA 2020 software
+
+  * COVID Suicide Living Review
+
+  * Data extraction tools systematic review
+
+<!-- Essentially, look at the Trello -->
+__Under review/Preprints__
+
+  * MSc Paper on systematic reviews of this thesis topic
+
+  *
+
+### Involvement of patients and the public {#appendix-ppi}
+
+Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.
+
+Additionally,
+
+Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
 
@@
 
+Note
+
 ### MR risk of bias tool {#appendix-mr-rob}
@@
 ## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
+
+## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
+
+### Code lists
 
@@
 Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]
+
+All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
 
@@
 
--\> NEED TO ADD DATA HERE!
+__NEED TO ADD DATA HERE!__
 

### 2021-04-07 front-and-back-matter/_acknowledgements.Rmd
Small starter fixes
Clean-up for today - ahead!
End of day
All working again after the update to Pandoc
End of day: 0

@@
 Additionally, I would like to thank Sharen O’Keefe.
+
+Thanks to the creator of the oxfordown which was used
+
+There are so many people without whom this would not have been possible:
+
+[**Check all name spellings**]
+
+Sharen O'Keffe
+Neal Haddaway
+Martin Westgate
+
+robvis contributors
+
+Annual reviewersLn Rupert Payne and Emma Anderson
+
+<!-- I am a Wellcome Trust Funded PhD student with grant code 102432/Z/13/Z.
+The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.
+-->
+
+Statistical support:
+
+All authors who volunteered time and effort
 

### 2021-04-08 01-Chp-Introduction.Rmd
End of day: 2490

@@
 
-First I provide a background to the central concepts and themes of this thesis, and justify the motivations for this piece of work.
-I introduce a tool that allows for systematic searching of preprint literature, which is then used in a systematic review of all available evidence on my central research question.
-
 ## Additional ideas

### 2021-04-08 02-Chp-Background.Rmd
End of day: 2490

--- 2021-03-15 02-Chp-Background.Rmd
@@
 output:
+  bookdown::word_document2: default
   bookdown::pdf_document2:
     template: templates/brief_template.tex
-  bookdown::word_document2: default
   bookdown::html_document2: default
@@
 ```
+
 (ref:dara-quote) --- Dara O'Briain
 
-# Background {#background-heading}
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+knitr::read_chunk("R/background.R")
+
+knitr::opts_chunk$set(
+  include = FALSE
+)
+```
+
+# Background, Theoretical framework, Aims & Objectives {#background-heading}
+
 \minitoc <!-- this will include a mini table of contents-->
 
-## Lay summary
+<!-- ## Lay summary -->
 
-This thesis is
+<!-- Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
+Despite many promising candidates, no cure for dementia currently exists, so the focus is now on figuring out ways to prevent the condition by finding risk factors (characteristics that influence a person's chance of developing a disease) that we can easily change.
+Avoiding a risk factor does not guarantee that a person will not develop dementia, but makes it less likely.
+A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood.
+-->
 
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement P
+<!-- This Chapter provides background information on dementia and lipids. It also provides a description. -->
+
+<!-- Evidence synthesis involves drawing on multiple sources of information to obtain the best possible to a research question, in this case, do lipids influence dementia risk.  -->
+
+<!----------------------------------------------------------------------------->
 
@@
 
-> This chapter provides the context of the thesis.
-It briefly gives the background on the problem of increased adiposity, the biology of adipose tissue, and diseases linking increased body mass index and mortality.
-The chapter briefly explores different measures of increased adiposity and potential hypotheses for underlying aetiology of diseases associated with increased adiposity.
-Finally, the potential application of metabolites and Mendelian randomization in the context of understanding underlying aetiology are discussed.
-*From Matt Lee's thesis.*
+This Chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background context on each.
+It will briefly discuss the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention therapeutics.
 
-This Chapter will provide an overview of the key exposures, outcomes and methods used throughout this thesis.
+In this context, it will highlight the importance of identifying easily modified risk factors and introduce blood lipids, and blood lipid-modifying treatments such as statins, as the primary exposures considered by this research.
+
+The central theoretical framework used - the synthesis of diverse sources of evidence - is introduced, and the research presented in this thesis is then framed in terms of three types of diverse evidence, with opposing viewpoints for each being discussed.
+
+Finally, it will outline the aims, objectives and structure of this thesis, and briefly summarise the contributions to the scientific literature that arose from this research.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-### Definition and Subtypes
 Dementia is major neurocognitive disorder, with symptoms including impairment of executive cognitive functions such as speech, judgement and memory.
-The most common causes of dementia are Alzheimer’s disease and vascular dementia, accounting for ~60-80% and ~10% of cases respectively.
-The remaining 10-30% of cases are caused other dementia subtypes (e.g.
-Lewy Body dementia) or by progression of other neurological diseases (e.g.
-Parkinson’s disease).
 
-###	Diagnosis
-Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition (is this true, or would it be better to say that there is no gold standard test without an autopsy).
-Information from multiple diagnostic tools are utilised, from medical history examination, through assessment of patients mental ability (e.g.
-the Mini-Mental State Examination), to clinical tests (e.g.
-Magnetic Resonance Imaging (MRI) scans).
+<!----------------------------------------------------------------------------->
 
-### Criteria
+### Underlying pathologies
 
-Several scales are commonly used to diagnose dementia and associated diseases for research purposes.
-Two of the most commonly used include the criteria of the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR)1 and the National Institute of Neurological Disorders and Stroke–Alzheimer Disease and Related Disorders (NINCDS–ADRDA).[@dubois2007] [**Need first NINCDS-ADRDA citation and DSM- **]
+Dementia is a collective umbrella term for a range of conditions each with different clinical presentations and disease courses, and is generally defined as "". <!--- Cite --->
 
-**Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in Chapter \@ref(sys-rev-heading)**
+Alzheimer's disease, named after Dr.
+Alois Alzheimer who presented the first recorded case in 1907, is the most common cause of dementia, accounting for approximately 60-80% of cases.
+Characterised by substantial cognitive impairment and diffculty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.
+Much remains unknown unknown about Alzheimer's pathogenesis, despite research implicating the accumluation of amyloid plaques and neurofibrillary tangles, or alternatively the cholingeric nervous system, <!--- check ---> as potential mechanisms of disease.
 
-###	Public Health Importance
-Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,6 an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
-In the UK, there are estimated to be 800,000 people currently living with dementia, with this figure expected to double by 2040.7 Globally, the prevalence of dementia is expected to reach 75 million by 2030.8 Despite the number of dementia cases and decades of research, there remains much unknown about the pathogenesis and progression of the disease.
+<!-- [__Need a bit more here__] -->
 
-###	Challenges in the study of dementia using traditional study designs
+Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases and is caused by a range of cerebrovascular disorders.
+Presentation can vary widely based on the underlying cause, and due to the varied underlying  pathopysiology, VaD can onset quite rapidly following a cerbrovascular event such as a stroke or over a long period due to series of small infarcts.
+VaD is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
 
-Speak to the
+The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).
 
-Historically, studies on dementia have faced a range of challenges.
+Where more than one underlying dementia pathologies co-occur, this is termed mixed dementia.
+It is common for patients to present with mixed dementia, as the occurrence of one underlying cause weakens overall brain health and increases the likeliness of occurrence of the other.
+<!--- Double check this --->
+
+<!-- __MCI__ and difference between MCI and dementia, MCI as a stepping stone to dementia, etc. -->
+
+<!----------------------------------------------------------------------------->
+
+### Diagnostic criteria
+
+Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
+<!-- is this true, or would it be better to say that there is no gold standard test without an autopsy?--> There exist several diagnostic criteria for dementia and related disease, many of which have existed for quite some time and have more recently been updated to reflect current understanding in dementia pathology.
+In all cases, dementia is diagnosed on the basis of behavioural and congitive changes as assessed by an experience clinician.
+<!-- This means the potential for misclassification both of dementia versus no-dementia and between the different underlying conditions is extremely likely. -->
+
+<!----------------------------------------------------------------------------->
+
+```{r diagnosticCriteria-setup, results="hide", message=FALSE, echo = FALSE}
+```
+
+```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+
+Two of the most commonly used criteria include the the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR) <!-- __[CITATION NEEDED]__ --> criteria and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS-ADRDA) criteria.[@dubois2007]
+
+<!-- [**Need first NINCDS-ADRDA citation and DSM-IV citations**] -->
+
+While these define the overall parameters for a assinging a dementia diagnosis, they are informed using practical scales to measure patients cognitive health, with two of the best known of these scales being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
+
+<!-- Also touch on aspects of each, such as the clock-drawing and whether or not they need to validated with input from another person. -->
+
+<!-- Note important differences between the scales and whether they affect results. Could cross-reference with an exploratory analysis in systematic review -->
+
+The distinction between these memory scales and diagnostic criteria presented above should be noted.
+For example, the MMSE is a tool for assessing cognitive impairment, but does not by itself indicate the absence or presence of dementia, instead merely indicating congitive impairment which could be due to another cause (for example, temporary delerium as a result of an infection or surgery).
+<!--- Check --->
+ A low score on the MMSE should feed into the diagnostic process, potentially as a screening tool to help identify which patients require further assessment by a trained clinician.
+Studies that use a memory scale alone are likely to be biased.
+
+<!-- Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available.
+-->
+
+<!-- ### Differing risk by sex -->
+
+<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->
+
+<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
+
+<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->
+
+<!----------------------------------------------------------------------------->
+
+<!-- ## Challenges in the study of dementia using traditional study designs -->
+
+<!-- Speak to the -->
+
+<!-- Historically, studies on dementia have faced a range of challenges.
 As a range of determinants (genetic, environmental and lifestyle) are thought to jointly influence the risk, progression and outcomes of dementia, any individual association is likely to have only a small effect.
@@
 Furthermore, dementia studies often have limited generalisability to the target population, as certain subgroups (e.g.
-the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10
+the very old) are frequently under-represented in study cohorts due to difficulties associated with their recruitment.9 Finally, studies employing a case-control design are further limited by the high potential for differential recall bias between those who have and have not developed dementia.10 -->
 
-Fortunately, these limitations may potentially be addressed through the use of routinely collected health data, and the electronic health record databases in which they are stored.
+<!-- Fortunately, these limitations may potentially be addressed through the use of routinely collected health data, and the electronic health record databases in which they are stored. -->
 
-*Cognitive impairment not dementia* (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia.
+<!-- *Cognitive impairment not dementia* (CIND) is another term used to described those with cognitive impairment but who fall below the diagnostic criteria for dementia. -->
 
-A further clinical subtype that is of particular import the
+<!-- A further clinical subtype that is of particular import the -->
 
-And MCI
+<!-- And MCI -->
 
-And different scales
+<!-- hr -->
 
-### History
-> Two major clinical trials are often cited as providing evidence that statins do not have an effect on the incidence ofdementia: the Prospective Study ofPravastatin in the Elderly (PROSPER) and the Medical Research
-Council/British Heart Foundation Heart Protection Study; however, because of methodologic limitations in relation to dementia outcomes in these two trials, the results of these trials are difficult to evaluate.
-Dementia incidence or cognitive outcomes were not preplanned endpoints in either of them, neither study included a clinical cognitive evaluation, and numbers of patients with follow-up information for cognitive evaluations were not reported in either study manuscript.
-In PROSPER a post hoc analysis compared changes in cognitive scores over a 3-year period between statintreated and placebo patients and found no significant differences.
-In the MRC/BHF HPS trial,27
-similar percentages of participants (0.3% in each—statin vs placebo—group) developed dementia during the 5-year follow-up period.
-The report did not state how the outcome of dementia was determined (e.g., reported as an adverse event or by follow-up phone interview).
-*Taken from Cramer 2008 - included in review*
+<!-- I -->
 
-There exist only two large scale randomized controlled trials of the effect of statins on dementia risk - in fact these studies are the only two trials included in a 2016 review of statins for the prevention of dementia produced by the Cochrane [@mcguinness2016b].
-Both showed no effect of
+<!-- Consider sex as a biological variable -->
 
-However, while being widely cited,
+<!----------------------------------------------------------------------------->
 
-Queries around how the data were collected, along
+### Public Health Importance
 
-### Economic impact
+Dementia is quickly becoming a critically important public health issue.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
+While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016]
 
-The economic impact of dementia is enormous, but in terms of the direct care required
+<!--- Talk about chronic underfunding here --->
+<!--- Talk about impact on health systems and  --->
 
-Patients with dementia stay in hospital for longer,[@mollers2019]
+Dementia also has a substantial economic impact.
+In 2015, the estimated total cost of dementia in England was £24.2 billion.
+Health care costs alone were £3.8 billion.[@wittenberg2019] <!--- Cross check against old data on cost to NHS --->.
+Based on the implications of a dementia diagnosis, this is perhaps unsurprising.
+Patients living with dementia are more prone to falls and other conditions that necessitate admission to hospital.
+Once admitted, patients with dementia are more likely to be stay in hospital for longer.[@mollers2019]
 
-Patients are more prone to falls and other con
+<!-- For the same period, unpaid care was estimated at .[@wittenberg2019] -->
+<!-- While the burden of dementia on patients themselves...
+comment here on the economic strain of unpaid care and the emotional strain of lookign after someone who has dementia - part.
+related to emotional and personality changes.
+-->
 
-### Risk factors
+The urgent need to reduce the burden of dementia, both at the personal and system (national health systemic) level, is clear.
+As such, the systematic assessment of easily modifiable targets (such as blood lipid levels) for their utility in the prevention of dementia should be prioritized.
+
+<!----------------------------------------------------------------------------->
+
+<!-- ### Risk factors -->
+
+<!-- Dyslipidemia (see Section \@ref(evidence-association) for a fuller dicussion). -->
 
@@
 
-### Preventative measures
+Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics, such as BACE inhibitors, being regularly abandoned due to futility.[@cummings2020].
+At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several therapeutics can help alleviate the symptoms of Alzheimer's disease.
+
+The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
+Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memeory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors are only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.
+
+Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative treatment due to the availability of lipid-modifying treatments.
+In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
+The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-### Range of lipids
+<!----------------------------------------------------------------------------->
 
-The blood profile has a range of lipid fractions to it.
-However, for the sake of this thesis, we will only consider the three most important fractions, namely total cholesterol, low density lipoprotein cholesterol (LDLc), high density lipoprotein cholesterol (HDLc) and trigylcerides (TG).
+### Lipid fractions
 
-### HDL-c
+The blood lipid profile contains a range of fractions.
+However, for the sake of this thesis, we will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorded from food (exogenouse lipids) or produced internally (endogenous lipids).
 
-### LDL-c
+Triglycerides are the simplest and most common type of lipids found across the body.
+They are used to store unused calories from food, and to move energy around the body.
+In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.
+As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
+Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells.
+In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.
+<!-- Need to also touch on the interplay between the different subcategories of lipids Does lowering one fraction affect the other(s)?
+Are there feedback loops?
+This is important because if not, statins can only be used to triangulate with findings for LDL-c.
+May also need to standardise in terms of -->
 
-Include formula for working out total cholesterol and the ranges.
+<!--- Will need to explain why I am focusing on these fractions rather that looking at others include VLDL, etc --->
 
-LDL-c levels are not directly measured but instead are estimated from using the Friedewald formula,[@friedewald1972] where the :
+<!----------------------------------------------------------------------------->
 
-$$LDLc \approx TC - HDLc - kTG$$
-where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
+<!-- Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters. -->
 
-Limitations to the method include a requirement to fast for 12-14hrs prior to measures, an inability to estimate LDLc if TG levels are high
+Total serum cholesterol is a commonly used summary measure to estimate the total lipid burden in a patients blood, and  derived from the HDL-c, LDL-c and TG fractions using the Friedewald formula:[@friedewald1972]
 
-``` {block type='correction'}
-Measurement error is a big deal for this thesis, as will discuss measurement error regarding how  different codelists/measurement of AD vs vascular dementia affect results in later chapters.
-```
+$$TC \approx LDLc - HDLc - kTG$$ where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
 
-### Triglycerides
+<!--- Include formula for working out total cholesterol and a table detailing the acceptable ranges. --->
 
-### Total cholesterol
+Elevated cholesterol in the bloodstream via high LDL-c levels leads to atherosclerosis, the build-up of fatty deposits in the blood vessels, which constrict blood flow and can lead to vascular complications.
+Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.
+Globally, the prevalence of elevated total cholesterol, or hypercholestoreolemia, was estimated by the World Health Organisation to be approximately 40%.
 
-## Serum lipid interventions
+<!----------------------------------------------------------------------------->
+
+<!-- ### Hypercholesterolemia -->
+
+<!-- Clinical diagnosisof cholesterol above a certain level - moves from a continuous . realtively improtant in EHR where blood lipid levels may not be measured, but the formal diag -->
+
+<!-- Scales for Hypercholesterolemia in UK - see NICE guidance -->
+
+<!-- Can also be familial Hypercholesterolemia - -->
 
@@
 
-#### Lipophilic
+Statins are by far the most common method of lipid regulation currently prescribed.
+Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid,  by compeitivlely binding with HMG-CoA Reductase (HMG-CoA-R).
+This conversion is the key rate limiting step in the biochemical pathway that produces cholesterol (see Figure \ref(), allowing statins to reduce the production of LDL cholesterol.
 
-#### Hydrophilic
+<!----------------------------------------------------------------------------->
 
-## Methods used in the thesis
+(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the
 
-### Evidence synthesis
+(ref:statin-mechanisam-scap) Statin mechanism of action
 
-he main theoretical framework used in this thesis is evidence synthesis - the identification, critical assessment, and integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question; or b) highlight gaps in the existing evidence base.
+```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
 
-While this thesis does include a research tool (Chapter 2 - systematic searching of preprint) and a primary evidence generation element (Chapter 5 - observational analysis of CPRD data), this was performed with the intention of providing a further source of evidence for the evidence synthesis/triangulation aspect of the thesis.
+<!----------------------------------------------------------------------------->
 
-### Primary cohort analysis
+Statins can either be lipophilic or hydrophilic, with several of the common brands falling into each category.
+The distinction between the two is of particular importance in the assessment of their impact on dementia, as only lipophilic statins can cross the blood brain barrier.
+However, this is only applicable if the relationship between statins and dementia risk is independent of their impact on circulating blood levels.
 
-### Triangulation
+### Other lipid regulating agents (LRA)
 
-### Individual patient data meta-analyis
+There are a range of other interventions that can be used to modify a persons lipid profile, though each act is slightly different ways.
+Most commonly though, these treatments are either used as adjunct (additional) treatments with statins therapy, or are used in situations where statins are contra-indicated or not tolerated.
+
+<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->
+
+The most commonly used non-statin therapeutic is ezetimbibe, which prevents intestinal absorption of cholesterol.
+However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimbe therapies (both compounds contained in a single pill, as opposed to complimentary treatemnts).
+
+A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
+They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
+
+Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.
+
+<!----------------------------------------------------------------------------->
+
+## Evidence for the association between blood lipids and dementia {#evidence-association}
+
+In this section I provide an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
+
+<!----------------------------------------------------------------------------->
+### Basic science
+
+A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
+The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent [CITE], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
+Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [CITE].
+
+<!--- might need some more here --->
+
+Despite these encouraging results, evidence from the diverse range of epidemiological studies on this topic has to date been been contradictory.
+
+<!----------------------------------------------------------------------------->
+### Observational studies
+
+Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported widely different results.
+A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
+With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
+
+<!--- Will need more here - particularly on the --->
+
+<!-- Need to talk about biases here? Or have a different section: Diverse sources of evidence: different underlying biases -->
+
+<!----------------------------------------------------------------------------->
+### Randomised controlled trials
+
+Meta-analyses of randomised controlled trials are commonly seen as the gold standard in terms of epidemiological evidence.
+Indeed in the "evidence pyramid", meta-analysis of trials sit proudly on top.
+However, there included several potential limitations to this trial-only approach.
+In terms of the central research of this theis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
+
+<!----------------------------------------------------------------------------->
+(ref:evidence-pyramid-cap) __The "evidence pyramid":__ Overview of the widely accepted relative ranking of different sources of evidence, with meta-analyses of RCTS being considered the best form of evidence.
+
+(ref:evidence-pyramid-scap) The "evidence pyramid"
+
+```{r evidence-pyramid, echo = FALSE, results="asis", fig.cap='(ref:evidence-pyramid-cap)', out.width='100%', fig.scap='(ref:evidence-pyramid-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+<!----------------------------------------------------------------------------->
+
+However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@()), <!--- Cross link here to section on presentation of dementia ---> as they would require extremely long and costly follow-up.[@ritchie2015] <!--- Check citation --->Additionally randomised trials require clinical equipoise - something that is unlikely in the case of statins, as while equipose may exist, it would be unethical to randomised patients to statins or not given their proven protective effect against coronary disease.
+It is no surprise then that the two know existing trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a]  are in fact trials of statins for the prevention of coronary related outcomes.
+The Prospective Study of Pravastatin in the Elderly (PROSPER) examined the protective effect of pravastatin on coronary outcomes.
+
+While being widely cited and indeed included in a Cochrane review on this topic (ironically, the lead author on this Cochrane review is ), these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
+Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
+In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years.
+As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome.
+The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r mal::mal_estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
+
+Additionally, the two trials, while putatively examining all-cause dementia subject to the limited applicability of change in cognitive scores as described above, do not make any effort to assign an underlying pathology to each case.
+As discussed in Section \@ref(), <!--- Cross to section on difference disease courses in Ad vs VaD vs other ---> the different underlying pathology of dementia have different mechanisms of action, and so it is not given that the effect of statins would be consistent across them.
+
+Additionally, both trials were limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia [24,25].
+The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+Given the long leg time between non-symptomatic onset of dementia and clinical presentation.
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
+
+<!----------------------------------------------------------------------------->
+
+### Mendelian randomisation
+
+Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
+In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
+The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] as shown in Figure \@ref(fig:mr-overview), namely that:
+
+1. the IV is associated with the exposure of interest (the relevance assumption);
+2. the IV and outcome do not share a common cause (the independence assumption); and
+3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).
+
+This approach relies on the results of genome wide association studies (GWAS) to identify appropriate instruments, and as such, analysis of this type are restricted by the availability of relevant GWAS.
+As the cost of genome sequence falls, more and more GWAS are being performed, and so number of MR studies had increased in tandem.
+
+<!--- Can you compare the frequency of terms between PubMed and medRxiv to show that it is overrepresented --->
+
+<!----------------------------------------------------------------------------->
+(ref:mr-overview-cap) __Overview of Mendelian randomisation study design:__ Shows the central assumptions of the Mendelian randomisation study design, using the example of lipids and dementia.
+
+(ref:mr-overview-scap) Overview of Mendelian randomisation study design
+
+```{r mr-overview, echo = FALSE, results="asis", fig.cap='(ref:mr-overview-cap)', out.width='100%', fig.scap='(ref:mr-overview-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+<!----------------------------------------------------------------------------->
+
+A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk.[27] However, this study was widely criticised as it did not exclude the region surrounding the ApoE gene, the strongest know risk factor for Alzheimer's disease.
+This invalidated the exclusion exclusion restriction criteria (Assumption 3, above), as the risk reduction observed in this study could be driven by variants in this region via a pathway independent of lipid levels.
+<!--- Need more on MR here --->
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+In summary, multiple sources of evidence exist on the relationship between statins and dementia. In the next section, I introduce the theoretical framework used in this thesis.
+
+<!----------------------------------------------------------------------------->
+
+## Theoretical framework: Evidence synthesis
+
+The central theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered or explores the same question in a way that increases our confidence in the result.
+
+This thesis applies seeks to use an evidence synthesis framework to assess the relationship between lipids/statins and dementia.
+Of particular interest is the synthesis of evidence from a range of diverse sources.
+This thesis considers three sources of diversity in the evidence base:
+
+* Diverse study designs (and sources of bias)
+* Diverse publication status (preprints vs published articles)
+* Diverse sources of data (summary level data vs individual-level data)
+
+These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.
+
+<!----------------------------------------------------------------------------->
+
+### Study designs
+
+<!----------------------------------------------------------------------------->
+As illustrated in Section \@ref(evidence-association), each individual epidemiological approach taken to examine the central research question of this thesis is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk.
+
+However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
+If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk.[26] In this context, systematically identifying, assessing and integrating all available evidence in a "aetiological triangulation" framework,[@lawlor2016a] regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
+
+<!--- May need an extra bit here about how the different types of research apply to different time scales --->
+
+<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias --->
+
+As such, this thesis aims to find all existing evidence on the relationship between lipids/statins and dementia via the comprehensive review in Chapter \@ref(sys-rev-heading), and then triangulate the different sources of evidence along with the primary analyses performed in this thesis (Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)) in Chapter \@ref(dicussion-heading).
+
+<!----------------------------------------------------------------------------->
+
+<!-- ### Different sources of bias -->
+
+<!-- While we can expect different study designs to be subject to different inherent sources of bias - for example, issues with the randomisation procedure will only apply to randomised controlled trials - this thesis also considers diverse sources of evidence in terms of the methodological approaches taken within study type.
+-->
+
+<!-- The term "observational study", unlike RCT, belies wide range of analytical approaches,[@thiese2014] each with it's own limitations which can  -->
+
+<!-- #### Misclassification bias -->
+
+<!-- Incredibly hard to diagnose dementia, and even if diagnosed dementia,  distinguishing between the different subtypes. -->
+
+<!-- When using code lists to define outcomes in large, population scale electronic health databases, evidence exists that there is wild misclassification between the  -->
+
+<!-- Given the diagnostic criteria for vascular dementia, it adds a particular difficulty to  -->
+
+<!-- <!--- Be careful here, as you don't account for misclassification in your CPRD study --->
+
+<!-- Misclassification can also affect studies of interventions through the introduction of immortal time. Several high profile observational studies of the effect of statins on dementia. -->
+
+<!-- #### Reverse causation -->
+
+<!-- Reverse causation is where the assumed exposure in an analytical framework is actually the outcome, reversing the direction of the assumed causal diagram.
+__[CITATION NEEDED]__ In the case of lipids and dementia, a reverse casual relationship would be observed by the early prodomal effects of dementia influencing a change in blood lipids.
+-->
+
+<!-- In this context, evidence synthesis exercises must account for these threats to internal validity as part of the synthesis.
+However, many previous highly cited systematic reviews have now done so.
+-->
+
+<!-- <!--- This is a key advantage of this study, as we account for . --->
+
+<!-- Given the range of biases that can be expected to effect studies into dementia, any evidence synthesis effort must take account of these and perform a robust risk of bias assessment to assess the internal validity.
+-->
+
+<!-- A key issues here, particularly in the context of using statins as a proxy for blood lipid levels, is that there is a key distinction between internal validity and generalisability.
+One can be called the wrong answer to the right question, the other, the right answer to the wrong question.
+-->
+
+<!-- Having identified a gap in the literature in the systematic review, both in terms of an absence of observational studies using the specific deisng and in an absence of data related to vascular dementia, in Chapter \@ref(cprd-analysis-heading), I aim to address this evidence gap and provide a further source of information for the triangulation in Chapter \@ref(discussion-heading) -->
+
+<!----------------------------------------------------------------------------->
+
+### Preprints versus peer-reviewed articles {#diverse-sources-preprints}
+
+Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+
+Preprint repositories have existed in certain fields for many years, such as the aRxiv for preprints in physics and mathematics, but have recently expanded into other fields.
+Repositories now exist for everything from ecology (EcoEvoRxiv) to meta-research (metaArXiv).
+There is much ongoing debate, particularly in light of the explosion of preprints following their widespread use to disseminate research related to the COVID-19 pandemic, about how preprints should be handled in the context of an evidence synthesis.
+
+<!----------------------------------------------------------------------------->
+(ref:medrxiv-growth-cap) __Growth of the medRxiv and bioRxiv repositories over time:__ Additional caption info here.
+
+(ref:medrxiv-growth-scap) Growth of the medRxiv and bioRxiv repositories over time
+
+```{r medrxiv-growth, echo = FALSE, results="asis", fig.cap='(ref:medrxiv-growth-cap)', out.width='100%', fig.scap='(ref:medrxiv-growth-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+<!----------------------------------------------------------------------------->
+
+One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.
+Some researchers recommend treating preprints as a separate category to peer-reviewed publication, using a flag or marker to indicate that certain evidence was sourced from.
+However, this approach assigns a lot of weight to peer-review as a indicator of "quality".
+Given the rise of predatory journals, and the (anecdotally) variable quality of peer-review across legitimate journals depending on the reviewer selected for a paper, peer-review is not always a reliable indicator.
+
+Meta-studies of the concordance between preprints and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the overwhelming majority of cases.[@shi2021a] This indicates that preprints should be considered a reliable reflection of the study, though these analyses are by necessity limited to preprinted studies that were subsequently published - the effect of peer review in limiting the publication of poorly design or executed studies is harder to assess.
+However, in the absence of any information on the subsequent publication, the preprint contains the best available evidence on a given research study, and so should be included in the review.
+
+The inclusion of non-peer-reviewed preprints substantially increases the need for thorough and detailed risk-of-bias assessment as part of the systematic review, in lieu of formal peer review.
+Risk-of-bias assessments provide a structured and transparent way to assess the internal validity of a study across several domains of bias.
+In theory, risk-of-bias assessments should be performed as part of systematic reviews, regardless of whether they included preprints,<!--- cite PRISMA and ROB2 paper here ---> but several of the existing highly cited reviews of observational studies of the relationship between statins and dementia did not perform any risk-of-bias assessment.
+<!-- __[CITATION NEEDED]__ -->
+
+Accepting that preprints represent an import source of information, their inclusion in systematic reviews is limited in practical terms by the absence of a replicable and transparent search tool for performing systematic searches in preprint repositories.
+The tool presented in Chapter \@ref(sys-rev-tools) aims to address this, and enables the inclusion of health-related preprints as evidence sources in the systematic review presented in Chapter \@ref(sys-rev-heading).
+
+<!--- Talk a bit more about studification, and link to how medrxivr allows you to do this --->
+
+<!----------------------------------------------------------------------------->
+
+### Summary level results vs individual patient data
+
+If lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.
+
+Analysis of summary level data, that is the data extracted from publications describing primary studies, can only take investigators so far in this regard.
+Due to a lack of primary studies readily presenting results stratified by covariates of interests, for example sex and ethnicity (see Section \@ref()), meta-analyses of summary-level data often have limited ability to examine exposure-covariate interactions (for example, sex and ethnicity.
+
+An individual participant data (IPD) meta-analysis is therefore the best option to examine the modification of dementia risk by individual-level covariates.
+This analytical approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.
+It also allows for the incorporation of relevant, previously un-analysed datasets, available via new initiatives such as the Dementia Portal UK,<!--- Cite this ---> which aim to provide access to several dementia-related datasets via a single simplified application process.
+
+This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading) and combine this with previously unanalysed data from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading).
+
+<!----------------------------------------------------------------------------->
+
+## Aims and Objectives of the thesis
+
+### Hypothesis
+
+Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the risk of subsequent dementia.
+
+### Aims and Objectives
+
+The specific research objectives that this thesis seeks to address are:
+
+* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
+* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
+* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
+* To meta-analyse previously unexplored datasets as part of a individual participant data (IPD meta-analysis)
+
+### Thesis Structure
+
+Chapters are self-contained, presenting the methods and results of that specific research project.
+The are bookended by introductory and discussion sections which place the methods and results in context.
+Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appedix-ppi) for more detail on the group).
+
+-   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
+This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
+-   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+-   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids, and interventions that modified blood lipids, and dementia.
+-   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database, based in England.
+-   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several previously unanalysed longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+
+## Outputs from this thesis {#thesis-output}
+
+The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools.
+
+### Contributions to the scientific literature
+
+During the course of this thesis, I have made several contributions to the scienitfic literature. Those arising from or directly related to the contents of this submission are presented below.
+
+&nbsp;
+
+_**McGuinness, L.
+A.**, and L Schmidt.
+(2020) "medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651.
+DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
+
+A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools).
+<!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience.
+--->
+
+&nbsp;
+
+_Hennessy, E.
+A., Acabchuk, R., Arnold, P.
+A., Dunn, A.
+G., Foo, Y.
+Z., Johnson, B.
+T., Geange, S.
+R., Haddaway, N.
+R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
+Welch, V.,  **McGuinness L.
+A.** (2020).
+Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
+MetaArXiv.
+DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_
+
+The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers in prevention science is currently under review at Prevention Science.
+This piece was co-written with Dr.
+Emily Hennessy (see author declarations).
+<!--- Will need to cross-reference this bit!
+--->
+
+&nbsp;
+
+_**McGuinness, L.
+A.**, and Higgins J.
+P.
+T.
+(2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method).
+DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
+
+The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
+See Appendix \@ref(appendix-robvis) for more details on this tool.
+
+&nbsp;
+
+_**McGuinness, L.
+A.**, and Sheppard A.
+L.
+2020.
+“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv.
+DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_
+
+Using the tool described in Chapter \@ref(sys-rev-tools), I performed a "research-on-research" study, comparing the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
+
+&nbsp;
+
+For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
+
+&nbsp;
+
+### Presentations/Talks
+
+* Abstract accepted to the Cochrane Colloquium 2019
+* ARUK abstract on systematic review (I hope!)
+* Presentation to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
+* Invited seminar series on the RoB2 risk-of-bias assessment tool for randomised controlled trials to for Evidence Synthesis Ireland
+* Presentations to internal department wide seminar series, including the Methods in Evidence Synthesis Salon (MESS) and the MRC-IEU seminar series.
+
+### Software {#outputs-software}
+**`medrxvir`**
+
+An R package and associated `shiny` web application that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
+See Chapter \@ref(sys-rev-tools-heading) for more details.
+Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:
+
+```{r, eval = FALSE}
+# CRAN version
+install.packages("medrxivr")
+
+# Development version
+devtools::install_github("mcguinlu/medrxivr")
+```
+
+&nbsp;
+
+**`robvis`**
+
+An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
+See Appendix \@ref(appendix-robvis) for more details.
+Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:
+
+``` {r, eval = FALSE}
+# CRAN version
+install.packages("robvis")
+
+# Development version
+devtools::install_github("mcguinlu/robvis")
+```
+
+&nbsp;
 
 ## Summary
+
+This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of the research in this thesis to the scientific literature.

### 2021-04-08 03-Chp-Systematic-Review-Tools.Rmd
End of day: 0
End of day: 2490

@@
       reference_docx: templates/word-styles-reference-01.docx
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 
+[Need to include bit on linking to published version via the tool]{.correction}
+
 ## Main points (to be removed)
@@
 
-Preprints represent an increasingly important source of scientific information.
-Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
-
+Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)).
 As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
@@
 The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
-As the majority of work on this aspect of this thesis is represented by lines of code, this Chapter is a high-level summary of the work done on this project.
-The GitHub repository[^chp-systematic-review-tools-1] for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
-
-[^chp-systematic-review-tools-1]: Available at <https://github.com/ropensci/medrxivr>
+As the majority of work on this aspect of this thesis is represented by lines of code (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)) this Chapter is an intentionally short, high-level summary of the work done on this project.
+The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
 
@@
 An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.
+__[CITATION NEEDED - PRISMA-S]__
 

### 2021-04-08 tmp.Rmd
End of day: 2490

Chapter 1. Introduction
1.1. Summary
This chapter presents the problem that the research conducted in this thesis seeks to
address and an outline of the main output of this thesis: new evidence concerning
repurposing antihypertensives for dementia prevention using genetic and non-genetic
instrumental variable analyses. This chapter then introduces three issues that arose and
have been addressed during the conduct of this research. They are: how to calculate
power for instrumental variable analyses in pharmacoepidemiology; how to use
Mendelian randomization to predict drug repurposing opportunities; and what factors
have effected prescribing of existing dementia drugs. This chapter concludes with the
aims and objectives of this thesis, a summary of its organization and a list of the
associated outputs.
1.2. Statement of the problem
There is a substantial unmet clinical need for treatments for dementia where significant
benefits to patients, society and the public purse can be gained. Despite this, some drug
companies have recently withdrawn from this therapy area due to failed and costly efforts
to find new treatments. (1,2) Drug repurposing, the identification of properties in existing
or abandoned compounds for other clinical conditions, offers significant advantages over
traditional drug discovery approaches. This includes immediate access to human safety
data from the original clinical development work, which can accelerate testing in clinical
trials, saving both time and money. (3–5)
Many antihypertensive medications have been proposed as drug repurposing candidates
for the prevention of dementia. In part, because of research to better understand several
reports of observed associations between midlife hypertension and later-life risk of
Alzheimer’s disease and vascular dementia. (5–8) There is also increasing recognition
that one of the earliest pathological events in the development of Alzheimer’s disease is
vascular dysregulation. (9) As well as suggestions that some antihypertensives,
specifically those that block angiotensin receptor and calcium channel signalling, may
have other neurological benefits. (9–11)
2
Several observational studies have investigated repurposing antihypertensives for
dementia prevention. (12–19) However, these studies have typically used case-control
designs with logistic regression and cohort designs with survival analysis, both of which
are observational study designs that may be subject to unmeasured or residual
confounding and reverse causation. Specific concerns of observational studies are
confounding by indication, where the reasons that a patient receives a treatment relate to
the reasons that the patient is at an increased risk of the outcome; and healthy adherer
bias, where patients initiating or adhering to a drug for prevention of a condition are
more likely to be healthy. There is also potential for reverse causation due to preclinical
or early stages of the disease, which could lead to more frequent contacts with general
practitioners (GPs) and lead to raised blood pressure being more likely to be detected.
This, in turn, could lead to the prescription of an antihypertensive drug in advance of
dementia being formally diagnosed. Consequently, current evidence concerning
repurposing antihypertensives for dementia prevention is considered inconclusive.
1.3. New evidence concerning repurposing antihypertensives for dementia prevention
using instrumental variable analysis
Instrumental variable analysis, which estimates the causal effect of an exposure on an
outcome by using a third variable (the instrument), can be robust to confounding and
reverse causation if certain assumptions are met. That is:
  IV1. The instrument must associate with the exposure
IV2. The instrument must only affect the outcome through the exposure
IV3. The instrument and the outcome must have no common causes
These assumptions can be represented on a directed acyclic graph, as shown in Figure
1.1. Instrumental variable analysis, with other sources of evidence, can be used in a
triangulation framework to obtain a reliable answer concerning the potential repurposing
of antihypertensives for dementia prevention. (20) This thesis presents two forms of
instrumental variable analysis to provide new evidence concerning this hypothesis. The
first uses physicians’ prescribing preference as a non-genetic instrument in electronic
health record data obtained from the United Kingdom (UK) Clinical Practice Research
Datalink (CPRD). The second uses single nucleotide polymorphisms (SNPs) i.e.
differences in the deoxyribonucleic acid (DNA) nucleotides between individuals, which
have been selected to mimic the biological function of the protein targets of 
3
antihypertensive drug classes, as a genetic instrument in an approach more commonly
known as Mendelian randomization. The results of both these instrumental variable
analyses have been made available via the following references. (21,22)
1.4. Calculating power for instrumental variable analysis in pharmacoepidemiology
Instrumental variable analysis is an increasingly popular method in the field of
pharmacoepidemiology. (23–28) However, the power calculators that were available for
studies using instrumental variable analysis at the start of my PhD – such as Mendelian
randomisation power calculators – did not allow for the structure of research questions
using non-genetic instruments (for example, physicians’ prescribing preference) in this
field. (29,30) This is because analysis using non-genetic instruments in pharmacoepidemiology will typically have stronger instruments and so can detect smaller causal
effects. Consequently, there was a need for dedicated power calculators for these type of
research questions in pharmacoepidemiology. In this thesis, I investigate how to conduct
Figure 1.1: A directed acyclic graph illustrating the basic instrumental variable analysis model.
Directed acyclic graphs are a visual representation of a model, which represent variables by ‘nodes’
and the relationships between them by ‘directed edges’. (68) The graphs are defined as acyclic
because edges cannot form ‘cycles’, whereby the edges all act in the same direction. This prevents a
variable from being both a cause and a consequence of itself. Directed acyclic graphs are a common
tool in epidemiology and, more specifically, causal inference when edges are given a causal
interpretation, as they allow researchers to depict their model and its assumptions using a common
graphing scheme. (69)
4
power calculations for pharmacoepidemiological studies, which use a single binary
instrument to analyse the causal effect of a binary exposure on a continuous outcome. I
also provide an online calculator, as well as packages in both R and Stata, for the
implementation of the formula by others (https://github.com/venexia/PharmIV). This
work has been published in the International Journal of Epidemiology. (31)
1.5. Using Mendelian randomization to predict drug repurposing opportunities
Identification of drug repurposing opportunities can maximize the benefit of a drug.
However, as highlighted before, the more traditional observational research methods
used to investigate these opportunities are subject to several biases. These include
confounding by indication, reverse causality, and missing data. In this thesis, I propose
Mendelian randomization as a novel approach that can be used for the prediction of drug
repurposing opportunities. Mendelian randomization addresses some of the limitations
associated with the existing methods in this field. Furthermore, it can be applied either
pre- or post-approval of the drug and could therefore prevent the potentially harmful
exposure of patients in clinical trials and beyond. This thesis includes discussion of
examples from the literature that have used Mendelian randomization to predict drug
repurposing opportunities and covers the strengths and limitations associated with using
this method for this purpose. There was relatively little discussion focussed on using
Mendelian randomization for drug repurposing when I commenced my PhD and I have
since published on this topic. (32)
1.6. Factors effecting existing dementia drug prescribing
Drugs for dementia have been available in England from 1997. However, since their
launch, there have been several changes to national guidelines and initiatives that may
have influenced prescribing. These include changes in National Institute for Health and
Care Excellence (NICE) guidance; several government dementia strategies; the addition
of dementia to the Quality and Outcomes Framework (QOF); and the expiry of drug
patents. Despite this, little research had been conducted prior to my PhD into the effect
of these events on prescribing. (33,34) In this thesis, I investigate prescribing trends in
England since the launch of these drugs up to 1st January 2016 using data from the
CPRD to address this gap in the literature. The key motivation for this analysis was to 
5
identify factors that have affected prescriptions of existing treatments that may also
influence repurposed drug candidates in the future. However, the results from this
analysis could also be used to identify breaks in the prescription of these drugs that could
be exploited as natural experiments for progression studies. For example, if these drugs
were not prescribed when the NICE guidelines stopped recommending their use between
2006 and 2011, the progression of people diagnosed during this time who did not access
the drugs could be compared with the progression of people diagnosed before and after
this time who did have access to the drugs. The results presented in this chapter have
been published in Alzheimer’s Research & Therapy. (35)
1.7. Aims and objectives
The objective of this thesis was to use instrumental variable analysis methods, in existing
data sources, to triangulate evidence for repurposing antihypertensive drugs for the
prevention of dementia.
The specific aims were as follows:
  1. Develop a power calculator for non-genetic instrumental variable analysis studies
in the context of pharmacoepidemiology.
2. Describe the use of genetic instrumental variable analysis, namely Mendelian
randomization, for predicting drug repurposing opportunities.
3. Examine the impact of regulatory guidance and patent expiry on dementia drug
prescribing.
4. Investigate whether antihypertensive drugs have a causal effect on incident
dementia using instrumental variable analysis with electronic health record data.
5. Investigate whether antihypertensive drugs have a causal effect on incident
dementia using instrumental variable analysis with genetic data.
1.8. Organization of this thesis
Chapter 2 provides the background necessary for the rest of this thesis through the
introduction of dementia, the concept of drug repurposing, and discussion of the existing
evidence regarding antihypertensive drugs for dementia prevention. It also covers the 
6
strengths and limitations of observational pharmacoepidemiology and explains why it
might be preferable over ‘gold standard’ randomized controlled trials for some
hypotheses. Chapter 3 describes instrumental variable analysis, the method utilized
throughout this thesis, and documents the development of a power calculator for this
method in the context of pharmacoepidemiology (Aim 1). Chapter 4 introduces the idea
of using Mendelian randomization, a form of instrumental variable analysis that uses
genetic variants as instruments, for drug repurposing and covers the strengths and
limitations of this approach (Aim 2). Chapter 5 describes the CPRD and my use of this
data source. Chapter 6 covers the current treatments available for dementia and factors
affecting their prescription in England based on data from the CPRD (Aim 3). Chapter 7
presents an assessment of the effects of antihypertensive drugs on dementia prevention
using instrumental variable analysis with data from the CPRD (Aim 4); while Chapter 8
presents an assessment of the effects of antihypertensive drugs on dementia prevention
using instrumental variable analysis with genetic data (Aim 5). The thesis concludes with
a discussion in Chapter 9 that brings together all the elements of this thesis and discusses
their implications.
1.9. Outputs from this thesis
1.9.1. Contributions to scientific literature
Contributions to scientific literature arising from this thesis are detailed below and
provided in Appendix A.
The protocol for the observational work using CPRD data to investigate drug
repurposing opportunities is published in the BMJ Open. (36) Its contents are referenced
in several places throughout this thesis, particularly Chapter 5:
  Walker VM, Davies NM, Jones T, Kehoe PG, Martin RM. Can commonly prescribed
drugs be repurposed for the prevention or treatment of Alzheimer’s and other
neurodegenerative diseases? Protocol for an observational cohort study in the UK
Clinical Practice Research Datalink. BMJ Open. 2016 Dec 1;6(12):e012044.
7
The power calculator for instrumental variable analysis in pharmacoepidemiology,
described in Chapter 3, is published in the International Journal of Epidemiology (31):
  Walker VM, Davies NM, Windmeijer F, Burgess S, Martin RM. Power calculator for
instrumental variable analysis in pharmacoepidemiology. Int J Epidemiol. 2017 Oct
1;46(5):1627–32.
Also published in the International Journal of Epidemiology is an article discussing
Mendelian randomization as a novel approach for the prediction of adverse drug events
and drug repurposing opportunities (32), which formed the basis of Chapter 4:
  Walker VM, Davey Smith G, Davies NM, Martin RM. Mendelian randomization: a
novel approach for the prediction of adverse drug events and drug repurposing
opportunities. Int J Epidemiol. 2017 Dec 1;46(6):2078–89.
The trend analysis examining prescribing practice for drugs for dementia in the CPRD,
presented in Chapter 6, is available from Alzheimer’s Research & Therapy (35):
  Walker VM, Davies NM, Kehoe PG, Martin RM. What is the impact of regulatory
guidance and expiry of drug patents on dementia drug prescriptions in England? A trend
analysis in the Clinical Practice Research Datalink. Alzheimer’s Research & Therapy.
2018 May 29;10:51.
The assessment of antihypertensives for dementia prevention using electronic health
record data, reported in Chapter 7, is currently under peer review and available from
bioRxiv (21):
  Walker VM, Davies NM, Martin RM, Kehoe PG. Comparison of antihypertensive drug
classes for dementia prevention. bioRxiv. 2019 Jan 12;517482.
The assessment of antihypertensives for dementia prevention using genetic data, reported
in Chapter 8, has been made available as an advance article from the International
Journal of Epidemiology (22):
  8
Walker VM, Kehoe PG, Martin RM, Davies NM. Repurposing antihypertensive drugs
for the prevention of Alzheimer’s disease: a Mendelian Randomization study. Int J
Epidemiol. 2019 Jul 4; Advance article.
1.9.2. Contributions to scientific meetings
I presented the paper “Power calculator for instrumental variable analysis in
pharmacoepidemiology”, described in Chapter 3, at the UK Administrative Data
Research Network Annual Research Conference 2017 in Edinburgh, UK.
I presented the paper “Mendelian randomization: a novel approach for the prediction of
adverse drug events and drug repurposing opportunities”, which formed the basis of
Chapter 4, at the University of Bristol Population Health Symposium 2016 in Bristol, UK
and at the International Society for Pharmacoepidemiology mid-year meeting 2018 in
Toronto, Canada.
I presented posters, based on the paper “What is the impact of regulatory guidance and
expiry of drug patents on dementia drug prescriptions in England?” detailed in Chapter
6, at the Alzheimer’s Research UK Research Conference 2016 in Aberdeen, UK and at
the University of Bristol brain research showcase and networking day 2018 in Bristol,
UK.
I presented “Can treatments for hypertension be repurposed for the treatment of
dementia?” at the Society of Epidemiologic Research annual conference 2018 in
Baltimore, United States of America (USA); at the European Congress of Epidemiology
2018 in Lyon, France and the International Society for Pharmacoepidemiology annual
meeting 2018 in Prague, Czech Republic. These presentations combined results from
Chapters 7 and 8.

### 2021-04-08 R/helper.R

@@ -57,3 +57,35 @@ num_to_text <- function(x, start_of_sentence = FALSE)
   return(out)
 }
 
+add_words <- function(words = 100){
+  
+  t <- wordcountaddin::text_stats()
+  w <- as.numeric(stringr::str_extract(t[3], "[0-9]+"))
+  n <- w + words
+  
+  message("Start:   ",format(Sys.time(),"%H:%M"),"\nNext:    ", n," <------\n")
+}
+
+
+check_words <- function(fp){
+  
+  i <- 0
+  
+  while (i < 26) {
+    
+    t <- wordcountaddin::text_stats(filename = fp)
+    
+    w <- as.numeric(stringr::str_extract(t[3], "[0-9]+"))
+    
+    message(i," - Current: ",w)
+    
+    i <- i +1
+    
+    Sys.sleep(60)
+  }
+  
+  beepr::beep(sound = "fanfare")
+  
+  rstudioapi::showDialog("Pomodoro done!", "Take a break . . . ")
+
+}

### 2021-04-09 02-Chp-Background.Rmd
End of day: -2681

@@
 source("R/doc_options.R")
+source("R/helper.R")
 knitr::read_chunk("R/background.R")
@@
 
-### Diagnostic criteria
+### Diagnostic criteria {#diagnostic-criteria}
 
@@
 As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r mal::mal_estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
+The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
 
@@
 
-### Study designs
+### Study designs and sources of bias
 
@@
 
-<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias --->
+<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias
+
+In this context, assessment of
+
+even within certain study designs, underlying biases are different
+
+In some cases, synthesis across evidence required the
+
+--->
 
@@
 
-A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools).
+A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
 <!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience.
@@
 This piece was co-written with Dr.
-Emily Hennessy (see author declarations).
+Emily Hennessy (see Author Declarations in the front materials).
 <!--- Will need to cross-reference this bit!

### 2021-04-09 04-Chp-Systematic-Review.Rmd
End of day: -2681

@@
 
+<!--- Take a stand here! --->
+
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
+While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
+While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
+
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+
+Does it also cause issues in terms of self-report?
+
 ### Screening results
@@
 
-*As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
+As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
 Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
@@
 -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
--   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published st
+-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult
 
@@
 
-### Added evidental value of including preprints
+### Added evidental value of including preprints {}
 
@@
 
+### Inclusion of preprints
+
+As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted.
+Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.
+
+The added evidental value of including these preprints was highlighted in Section
+
+On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
+While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.
+
 ### Original contribution to research

### 2021-04-09 05-Chp-CPRD-Analysis.Rmd
Updates
End of day: 0
End of day: -2681

@@
 \minitoc <!-- this will include a mini table of contents-->
+
+<!-- Include the early analysis we did here, that did not work as a result of limited scope.
+Could include some of the genetic work also.
+Will additionally need to put the relevant materials from the paper in the  -->
 
@@
 We use a Cox proportional hazards model with a time-varying treatment indicator.
+
+Expand on use of age as the time scale, but describe the problems this introduced
+
+Expand on post estimation analyses, which showed that nothing except age had an effect.
 
@@
 
+### Enabling easy synthesis
+
+In light of my own experiences in attempting to extract information for papers assessing prevantive measures, I attempted to document
+
+Study was reported in line with the [CHECK] reporting guidelines, and
+
 ### Conclusions

### 2021-04-09 06-Chp-IPD-Analysis.Rmd
End of day: -2681

@@
 
-Letters sent to all cohorts identified through the
+Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all.
+Will also need to comment on the additional tactics used.
 
@@
 
-Range of reasons why data is not made available.
+Range of reasons why data is not readily available.
 
 Unfortunately,
-
-As part of this,
 

### 2021-04-09 front-and-back-matter/_00-introduction.Rmd
All working again after the update to Pandoc
End of day: 0
End of day: -2681

@@
 
-files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]
+files <- files[which(!(files %in% c("_main.Rmd","index.Rmd", "tmp.Rmd")))]
 
@@
 
-target <- (date_diff*200)+5580
+target <- (date_diff*97) + 5580
 
@@
 
-target_df <- data.frame(date = c(start_date,max_date),
-                           words = c(5580, target))
+target_df <- data.frame(date = c(start_date,as.Date("20211116", format="%Y%m%d")),
+                           words = c(5580, 40000))
 
@@
 
-Words behind: `r words_behind`
+Words behind: `r format(words_behind, scientific = F)`
 
@@
 ggplot(mapping = aes(x=date,y=words)) +
-  geom_line(data = target_df, colour = "blue") +
+  geom_line(data = target_df, colour = "black", linetype = 2) +
+  geom_hline(yintercept = 40000, colour = "black", linetype = 2) +
+  geom_vline(xintercept = as.numeric(as.Date("20211116", format="%Y%m%d")), colour = "black", linetype = 2) +
+  geom_vline(xintercept = as.numeric(as.Date("20211216", format="%Y%m%d")), colour = "red") +
+  scale_x_date(limits = c(as.Date("20201124", format="%Y%m%d"),as.Date("20211231", format="%Y%m%d"))) +
   geom_step(data = words, colour = "red")

### 2021-04-12 04-Chp-Systematic-Review.Rmd
End of day: -3686

@@
 -   Could apply ROBIS to previous reviews to see how they stack-up?
+
+## Extra studies to include:
+
+* Smeet et al. reference in the CPRD analysis
 
@@
 Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob).
-Advance results from this review were obtained from contact with the authors.
+Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
 
 Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as part of this thesis to aid in creating standard risk-of-bias figures, and is summarized in Appendix \@ref(appendix-robvis).[@mcguinness2019]
+This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
+
+Many reviews use reporting guidelines instead - this is bad![@costa2011]
 
@@
 
-Inter- and intra-rater reliability was asssessed for a 10% subsample of records at the title and abstract screening stage.
-Intra-rater reliability involved a sinlge reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
+Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
 
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliabilty was chosen over other methods of assessing inter-rater reliability such as percent agreeement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
 [@cohen1960: @gwet2008; @wongpakaran2013]
@@
 How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpreation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
 
@@
 Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline vs mild cognitive impairment and the definition of eligible lipids.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
+
+<!--- Cross check this with the actual numbers included --->
 
@@
 -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult
+
+One particularly interesting meta-bias potentially applicable in this review is the definition
 
@@
 
+### Open data sharing {#sys-rev-open-data}
+
+<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->
+
 ### Original contribution to research
@@
 However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
+
+__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
 

### 2021-04-12 05-Chp-CPRD-Analysis.Rmd
End of day: -3686

@@
 Will additionally need to put the relevant materials from the paper in the  -->
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/Chp2-Systematic-Review.R")
+```
 
@@
 
-## Aims
+## Lay summary
 
-In this
+The CPR
+
+## Introduction
+
+Lack of evidence for the association of statins on vascular dementia risk
 
 ## Methods
+
+### Data source
+
+The Clinical Practice Research Datalink (CPRD) is a large, population-based, electronic health record database.[@herrett2015] It contains the primary care records for
+
+Originally termed the GPRD (General Practice Research Database),
+
+The
+
+Data completeness and collection of certain disease are heavily influenced by exercises that reward doctors for capturing certain diagnoses, such as the Quality and Outcomes Framework.
+However, these drives can oftern have unintended consequences [@liu2019]
 
@@
 This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).[@vonelm2008]
+
+_Note: If protocol was written by Venexia, how do I reference this?_
 
@@
 
+<!--- Need a lot more here - see other thesis for example of how covariates are described --->
+
 The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
@@
 
+$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
+
+where:
+
+* $t$ is the survival time;
+* $h(t)$ is the hazard function; and
+* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
+* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
+
+As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
+
+__Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__
+
+Hazard rations are
+
+Test for non-proportionality are therefore very important, as models which fail
+
+Problems with testing for non-proportional hazards when
+
+<!----------------------------------------------------------------------------->
+(ref:cprd-dag-1-cap) __Directed acyclic graph showing assumed relationship between exposure and covariate:__
+
+(ref:cprd-dag-1-scap) Directed acyclic graph showing assumed relationship between exposure and covariate
+
+```{r cprd-dag-1, echo = FALSE, results="asis", fig.cap='(ref:cprd-dag-1-cap)', out.width='100%', fig.scap='(ref:cprd-dag-1-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
+```
+<!----------------------------------------------------------------------------->
+
 ### Estimating the value of the time-varying confounders
@@
 Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
-This is problematic when the descision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the inital treatment decision, as is likely to be the case for a range of covariates included in the model.
+This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
 For example:
@@
 Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modifcation is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins precription levels at 6 months.
-[Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.]
+Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
+However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
+
+<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
+Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
+-->
 
@@
 
-**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c]
+**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This highlights a particular challenge in comparing research across different time-periods and coding systems.
+Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
 
@@
 
-As part of our exploration of the unexpected results,
+As part of my exploration of the unexpected results, I attempted to replicate the analyses of another paper that used a different approach to
 
-]
+Having contacted the authors to address these concerns, it was noted that
+
+Propensity scores are based on a range of baseline variables, and provide an estimates of the
+
+They used propensity scores to attempt to matcch patients equally likely to recieve the vaccine
+
+In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
+Fortunately, the authors kindly shared their
+
+<!--- Show comparison of code lists here --->
+
+<!----------------------------------------------------------------------------->
+``` {r smeeth-comparison-setup, results="hide", message=FALSE}
+```
+
+```{r smeeth-comparison-table, message=FALSE, results="asis"}
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+### Coding quality in the CPRD
+
+Lots of things influence prevalence: historic trends, availability of good codes
+
+There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]
+
 ### Strengths and Limitations
@@
 
-Study was reported in line with the [CHECK] reporting guidelines, and
+This study was reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
+
+Reporting
 

### 2021-04-12 04-Chp-Systematic-Review.Rmd
Test

@@
 * Smeet et al. reference in the CPRD analysis
+* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Characteristics of included studies
@@
 
+### Searching for/including Mendelian randomisation studies
+
+As a form of analysis that lends itself to multiple comparison, there is a strong
+
+Through snowballing and other measurse, we identified [@larsson2017b]
+
+Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
+
 ### Comments on the process

### 2021-04-12 tmp.Rmd
Test

@@
-Chapter 1. Introduction
-1.1. Summary
-This chapter presents the problem that the research conducted in this thesis seeks to
-address and an outline of the main output of this thesis: new evidence concerning
-repurposing antihypertensives for dementia prevention using genetic and non-genetic
-instrumental variable analyses. This chapter then introduces three issues that arose and
-have been addressed during the conduct of this research. They are: how to calculate
-power for instrumental variable analyses in pharmacoepidemiology; how to use
-Mendelian randomization to predict drug repurposing opportunities; and what factors
-have effected prescribing of existing dementia drugs. This chapter concludes with the
-aims and objectives of this thesis, a summary of its organization and a list of the
-associated outputs.
-1.2. Statement of the problem
-There is a substantial unmet clinical need for treatments for dementia where significant
-benefits to patients, society and the public purse can be gained. Despite this, some drug
-companies have recently withdrawn from this therapy area due to failed and costly efforts
-to find new treatments. (1,2) Drug repurposing, the identification of properties in existing
-or abandoned compounds for other clinical conditions, offers significant advantages over
-traditional drug discovery approaches. This includes immediate access to human safety
-data from the original clinical development work, which can accelerate testing in clinical
-trials, saving both time and money. (3–5)
-Many antihypertensive medications have been proposed as drug repurposing candidates
-for the prevention of dementia. In part, because of research to better understand several
-reports of observed associations between midlife hypertension and later-life risk of
-Alzheimer’s disease and vascular dementia. (5–8) There is also increasing recognition
-that one of the earliest pathological events in the development of Alzheimer’s disease is
-vascular dysregulation. (9) As well as suggestions that some antihypertensives,
-specifically those that block angiotensin receptor and calcium channel signalling, may
-have other neurological benefits. (9–11)
-2
-Several observational studies have investigated repurposing antihypertensives for
-dementia prevention. (12–19) However, these studies have typically used case-control
-designs with logistic regression and cohort designs with survival analysis, both of which
-are observational study designs that may be subject to unmeasured or residual
-confounding and reverse causation. Specific concerns of observational studies are
-confounding by indication, where the reasons that a patient receives a treatment relate to
-the reasons that the patient is at an increased risk of the outcome; and healthy adherer
-bias, where patients initiating or adhering to a drug for prevention of a condition are
-more likely to be healthy. There is also potential for reverse causation due to preclinical
-or early stages of the disease, which could lead to more frequent contacts with general
-practitioners (GPs) and lead to raised blood pressure being more likely to be detected.
-This, in turn, could lead to the prescription of an antihypertensive drug in advance of
-dementia being formally diagnosed. Consequently, current evidence concerning
-repurposing antihypertensives for dementia prevention is considered inconclusive.
-1.3. New evidence concerning repurposing antihypertensives for dementia prevention
-using instrumental variable analysis
-Instrumental variable analysis, which estimates the causal effect of an exposure on an
-outcome by using a third variable (the instrument), can be robust to confounding and
-reverse causation if certain assumptions are met. That is:
-  IV1. The instrument must associate with the exposure
-IV2. The instrument must only affect the outcome through the exposure
-IV3. The instrument and the outcome must have no common causes
-These assumptions can be represented on a directed acyclic graph, as shown in Figure
-1.1. Instrumental variable analysis, with other sources of evidence, can be used in a
-triangulation framework to obtain a reliable answer concerning the potential repurposing
-of antihypertensives for dementia prevention. (20) This thesis presents two forms of
-instrumental variable analysis to provide new evidence concerning this hypothesis. The
-first uses physicians’ prescribing preference as a non-genetic instrument in electronic
-health record data obtained from the United Kingdom (UK) Clinical Practice Research
-Datalink (CPRD). The second uses single nucleotide polymorphisms (SNPs) i.e.
-differences in the deoxyribonucleic acid (DNA) nucleotides between individuals, which
-have been selected to mimic the biological function of the protein targets of 
-3
-antihypertensive drug classes, as a genetic instrument in an approach more commonly
-known as Mendelian randomization. The results of both these instrumental variable
-analyses have been made available via the following references. (21,22)
-1.4. Calculating power for instrumental variable analysis in pharmacoepidemiology
-Instrumental variable analysis is an increasingly popular method in the field of
-pharmacoepidemiology. (23–28) However, the power calculators that were available for
-studies using instrumental variable analysis at the start of my PhD – such as Mendelian
-randomisation power calculators – did not allow for the structure of research questions
-using non-genetic instruments (for example, physicians’ prescribing preference) in this
-field. (29,30) This is because analysis using non-genetic instruments in pharmacoepidemiology will typically have stronger instruments and so can detect smaller causal
-effects. Consequently, there was a need for dedicated power calculators for these type of
-research questions in pharmacoepidemiology. In this thesis, I investigate how to conduct
-Figure 1.1: A directed acyclic graph illustrating the basic instrumental variable analysis model.
-Directed acyclic graphs are a visual representation of a model, which represent variables by ‘nodes’
-and the relationships between them by ‘directed edges’. (68) The graphs are defined as acyclic
-because edges cannot form ‘cycles’, whereby the edges all act in the same direction. This prevents a
-variable from being both a cause and a consequence of itself. Directed acyclic graphs are a common
-tool in epidemiology and, more specifically, causal inference when edges are given a causal
-interpretation, as they allow researchers to depict their model and its assumptions using a common
-graphing scheme. (69)
-4
-power calculations for pharmacoepidemiological studies, which use a single binary
-instrument to analyse the causal effect of a binary exposure on a continuous outcome. I
-also provide an online calculator, as well as packages in both R and Stata, for the
-implementation of the formula by others (https://github.com/venexia/PharmIV). This
-work has been published in the International Journal of Epidemiology. (31)
-1.5. Using Mendelian randomization to predict drug repurposing opportunities
-Identification of drug repurposing opportunities can maximize the benefit of a drug.
-However, as highlighted before, the more traditional observational research methods
-used to investigate these opportunities are subject to several biases. These include
-confounding by indication, reverse causality, and missing data. In this thesis, I propose
-Mendelian randomization as a novel approach that can be used for the prediction of drug
-repurposing opportunities. Mendelian randomization addresses some of the limitations
-associated with the existing methods in this field. Furthermore, it can be applied either
-pre- or post-approval of the drug and could therefore prevent the potentially harmful
-exposure of patients in clinical trials and beyond. This thesis includes discussion of
-examples from the literature that have used Mendelian randomization to predict drug
-repurposing opportunities and covers the strengths and limitations associated with using
-this method for this purpose. There was relatively little discussion focussed on using
-Mendelian randomization for drug repurposing when I commenced my PhD and I have
-since published on this topic. (32)
-1.6. Factors effecting existing dementia drug prescribing
-Drugs for dementia have been available in England from 1997. However, since their
-launch, there have been several changes to national guidelines and initiatives that may
-have influenced prescribing. These include changes in National Institute for Health and
-Care Excellence (NICE) guidance; several government dementia strategies; the addition
-of dementia to the Quality and Outcomes Framework (QOF); and the expiry of drug
-patents. Despite this, little research had been conducted prior to my PhD into the effect
-of these events on prescribing. (33,34) In this thesis, I investigate prescribing trends in
-England since the launch of these drugs up to 1st January 2016 using data from the
-CPRD to address this gap in the literature. The key motivation for this analysis was to 
-5
-identify factors that have affected prescriptions of existing treatments that may also
-influence repurposed drug candidates in the future. However, the results from this
-analysis could also be used to identify breaks in the prescription of these drugs that could
-be exploited as natural experiments for progression studies. For example, if these drugs
-were not prescribed when the NICE guidelines stopped recommending their use between
-2006 and 2011, the progression of people diagnosed during this time who did not access
-the drugs could be compared with the progression of people diagnosed before and after
-this time who did have access to the drugs. The results presented in this chapter have
-been published in Alzheimer’s Research & Therapy. (35)
-1.7. Aims and objectives
-The objective of this thesis was to use instrumental variable analysis methods, in existing
-data sources, to triangulate evidence for repurposing antihypertensive drugs for the
-prevention of dementia.
-The specific aims were as follows:
-  1. Develop a power calculator for non-genetic instrumental variable analysis studies
-in the context of pharmacoepidemiology.
-2. Describe the use of genetic instrumental variable analysis, namely Mendelian
-randomization, for predicting drug repurposing opportunities.
-3. Examine the impact of regulatory guidance and patent expiry on dementia drug
-prescribing.
-4. Investigate whether antihypertensive drugs have a causal effect on incident
-dementia using instrumental variable analysis with electronic health record data.
-5. Investigate whether antihypertensive drugs have a causal effect on incident
-dementia using instrumental variable analysis with genetic data.
-1.8. Organization of this thesis
-Chapter 2 provides the background necessary for the rest of this thesis through the
-introduction of dementia, the concept of drug repurposing, and discussion of the existing
-evidence regarding antihypertensive drugs for dementia prevention. It also covers the 
-6
-strengths and limitations of observational pharmacoepidemiology and explains why it
-might be preferable over ‘gold standard’ randomized controlled trials for some
-hypotheses. Chapter 3 describes instrumental variable analysis, the method utilized
-throughout this thesis, and documents the development of a power calculator for this
-method in the context of pharmacoepidemiology (Aim 1). Chapter 4 introduces the idea
-of using Mendelian randomization, a form of instrumental variable analysis that uses
-genetic variants as instruments, for drug repurposing and covers the strengths and
-limitations of this approach (Aim 2). Chapter 5 describes the CPRD and my use of this
-data source. Chapter 6 covers the current treatments available for dementia and factors
-affecting their prescription in England based on data from the CPRD (Aim 3). Chapter 7
-presents an assessment of the effects of antihypertensive drugs on dementia prevention
-using instrumental variable analysis with data from the CPRD (Aim 4); while Chapter 8
-presents an assessment of the effects of antihypertensive drugs on dementia prevention
-using instrumental variable analysis with genetic data (Aim 5). The thesis concludes with
-a discussion in Chapter 9 that brings together all the elements of this thesis and discusses
-their implications.
-1.9. Outputs from this thesis
-1.9.1. Contributions to scientific literature
-Contributions to scientific literature arising from this thesis are detailed below and
-provided in Appendix A.
-The protocol for the observational work using CPRD data to investigate drug
-repurposing opportunities is published in the BMJ Open. (36) Its contents are referenced
-in several places throughout this thesis, particularly Chapter 5:
-  Walker VM, Davies NM, Jones T, Kehoe PG, Martin RM. Can commonly prescribed
-drugs be repurposed for the prevention or treatment of Alzheimer’s and other
-neurodegenerative diseases? Protocol for an observational cohort study in the UK
-Clinical Practice Research Datalink. BMJ Open. 2016 Dec 1;6(12):e012044.
-7
-The power calculator for instrumental variable analysis in pharmacoepidemiology,
-described in Chapter 3, is published in the International Journal of Epidemiology (31):
-  Walker VM, Davies NM, Windmeijer F, Burgess S, Martin RM. Power calculator for
-instrumental variable analysis in pharmacoepidemiology. Int J Epidemiol. 2017 Oct
-1;46(5):1627–32.
-Also published in the International Journal of Epidemiology is an article discussing
-Mendelian randomization as a novel approach for the prediction of adverse drug events
-and drug repurposing opportunities (32), which formed the basis of Chapter 4:
-  Walker VM, Davey Smith G, Davies NM, Martin RM. Mendelian randomization: a
-novel approach for the prediction of adverse drug events and drug repurposing
-opportunities. Int J Epidemiol. 2017 Dec 1;46(6):2078–89.
-The trend analysis examining prescribing practice for drugs for dementia in the CPRD,
-presented in Chapter 6, is available from Alzheimer’s Research & Therapy (35):
-  Walker VM, Davies NM, Kehoe PG, Martin RM. What is the impact of regulatory
-guidance and expiry of drug patents on dementia drug prescriptions in England? A trend
-analysis in the Clinical Practice Research Datalink. Alzheimer’s Research & Therapy.
-2018 May 29;10:51.
-The assessment of antihypertensives for dementia prevention using electronic health
-record data, reported in Chapter 7, is currently under peer review and available from
-bioRxiv (21):
-  Walker VM, Davies NM, Martin RM, Kehoe PG. Comparison of antihypertensive drug
-classes for dementia prevention. bioRxiv. 2019 Jan 12;517482.
-The assessment of antihypertensives for dementia prevention using genetic data, reported
-in Chapter 8, has been made available as an advance article from the International
-Journal of Epidemiology (22):
-  8
-Walker VM, Kehoe PG, Martin RM, Davies NM. Repurposing antihypertensive drugs
-for the prevention of Alzheimer’s disease: a Mendelian Randomization study. Int J
-Epidemiol. 2019 Jul 4; Advance article.
-1.9.2. Contributions to scientific meetings
-I presented the paper “Power calculator for instrumental variable analysis in
-pharmacoepidemiology”, described in Chapter 3, at the UK Administrative Data
-Research Network Annual Research Conference 2017 in Edinburgh, UK.
-I presented the paper “Mendelian randomization: a novel approach for the prediction of
-adverse drug events and drug repurposing opportunities”, which formed the basis of
-Chapter 4, at the University of Bristol Population Health Symposium 2016 in Bristol, UK
-and at the International Society for Pharmacoepidemiology mid-year meeting 2018 in
-Toronto, Canada.
-I presented posters, based on the paper “What is the impact of regulatory guidance and
-expiry of drug patents on dementia drug prescriptions in England?” detailed in Chapter
-6, at the Alzheimer’s Research UK Research Conference 2016 in Aberdeen, UK and at
-the University of Bristol brain research showcase and networking day 2018 in Bristol,
-UK.
-I presented “Can treatments for hypertension be repurposed for the treatment of
-dementia?” at the Society of Epidemiologic Research annual conference 2018 in
-Baltimore, United States of America (USA); at the European Congress of Epidemiology
-2018 in Lyon, France and the International Society for Pharmacoepidemiology annual
-meeting 2018 in Prague, Czech Republic. These presentations combined results from
-Chapters 7 and 8.
+---
+output: html_document
+bibliography: bib/library.bib
+csl: csl/nature.csl
+space_betwee_paragraphs: true
+fig_caption: true
+always_allow_html: yes
+link-citations: true
+---
+
+```{r include=FALSE}
+# word count = 
+doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # this will tell the .Rmd file what output you are knitting to (word, pdf, html) so that you cna use if else statements when making tables - html/pdf output tables do not work well in word.
+For word we need to use the 'flextable' packaged to make tables.
+## packages
+library(dplyr)
+library(kableExtra)
+library(flextable)
+```
+
+# Data visualisation {#chapter6}
+
+<style>
+body {
+text-align: justify}
+</style>
+
+### *EpiViz: a tool to visualise large metabolomic association analyses* {-}
+
+In Chapters \@ref(chapter4) and \@ref(chapter5) we observed large metabolic shifts as a result of increased adiposity.
+These results were presented using Circos plots.
+Production of the first stage of these plots was inefficient.
+This chapter details the development and implementation of a web application and `R` package that efficiently creates Circos plots that can be used by the community for similar analyses.
+The `R` package was used to re-make the plots presented in Chapters \@ref(chapter4) and \@ref(chapter5) and make those in subsequent chapters.
+<br>
+
+\newpage
+
+## Introduction
+The metabolome (briefly discussed in Section \@ref(metabolites)) is a complex biological system comprised of the bodies entire small molecules.
+These small molecules, metabolites, take many forms and act in a multitude of pathways[@Griffin2006].
+Metabolites are expressed differentially among cell types and carry information from genetic and non-genetic factors[@Johnson2016; @Wishart2019].
+They are the ultimate end-point of a biological process and are therefore seen as the link between genotype and phenotype[@Griffin2006; @Su2014; @Chu2019; @Wishart2019].
+<br>
+
+There are potentially many thousands of metabolites[@Griffin2006] across different cell types, with expression associated with traits and diseases[@Guasch-Ferre2016; @Liesenfeld2013; @Johnson2016; @Moore2014; @Cirulli2019; @Wishart2018].
+However, assigning individual metabolite changes to diseases is difficult[@Su2014; @Fearnley2016; @Chu2019] because of the complexity of their interrelationships.
+The metabolome is made up of many feedback and feed-forward loops, meaning metabolic products of one pathway will likely influence those of another.
+The intercorrelated nature of metabolites[@Rosato2018] is further complicated by the wide degree of genetic correlation[@Gallois2019] and shared genetic architecture[@Shin2014; @Kettunen2016; @Long2017; @Gallois2019].
+Gaining global overview of association analyses will likely aid interpretation of results.
+Global overview is of particular importance in MR studies where robust selection of instrumental variables is required to meet methodological assumptions[@DaveySmith2003].
+<br>
+
+Forest plots are widely used in metabolomic association analyses[@May-Wilson2017; @Taylor2019; @Soares2019; @SantosFerreira2019; @Hartley2020; @Borges2017] to visualise and interpret results.
+They can be easily made, with a number of `R` packages, such as [`ggforestplot`](https://github.com/nightingalehealth/ggforestplot) and [`TwoSampleMR`](https://mrcieu.github.io/TwoSampleMR/#to-many-forest-plot)[@Hemani2018], available.
+However, when presenting more than 50 data points forest plots are cumbersome and many separate plots are needed.
+This makes gaining global overview difficult.
+<br>
+
+An alternative approach is to compress information into a circular rather than vertical/horizontal form (see Figures 3 and 2 from [@Shin2014] and [@Kettunen2016] respectively).
+Circos plots[@Krzywinski2009], as implemented in many genetics studies, condense large amounts of information into informative visualisations (see Figure 1A from [@Saben2014]).
+However, Circos software is designed for genomic data and written in programming languages unfamiliar to many epidemiologists.
+The `R` package [`circlize`](https://jokergoo.github.io/circlize_book/book/index.html)[@Gu2014] provides most of the functionality of the Circos software but is designed for genomic information and requires an advanced understanding of `R`.
+Here I present `EpiViz`, a web application and `R` package, that builds on the [`circlize`](https://jokergoo.github.io/circlize_book/book/index.html)[@Gu2014] and [`ComplexHeatmap`](https://jokergoo.github.io/ComplexHeatmap-reference/book/)[@Gu2016] `R` packages.
+`EpiViz` enables epidemiologists with little programming experience to efficiently create Circos plots with hundreds of variables and gain global overview.
+
+## Methods
+### Circos plots for association analyses
+`EpiViz` adapts and builds on the `Circlize` foundation to create Circos plots compatible with association analysis data.
+Circos plots are composed of six elements: template, plotting space, tracks, sections, data, legend (Figure \@ref(fig:annotated-circos-plot)).
+The template element is a square of defined proportions within which information is plotted.
+Each additional element is layered onto the template one after the other.
+The plotting space element is an empty circle which is layered and centred on top of the template.
+Data is plotted on to the plotting space.
+An optional extra of the Circos plot, the legend element takes the dimensions of the template and creates a separate plotting space that can be layered on to the bottom of the template element.
+<br>
+
+The plotting space is separated into tracks and sections.
+Tracks are laid down as rings within the plotting space.
+Each track represents a single element of information such as an exposure.
+Tracks are numbered from the outside to the centre of the circle and coloured separately.
+Sections divide the plotting space into distinct areas, much like a pie chart.
+Sections are defined by the data and usually represent groups of outcomes such as metabolite classes.
+A section track is laid at the outside of the tracks to give a header for each section.
+The header is referenced in the legend element.
+<br>
+
+Once the template, plotting space, tracks and sections are laid down, coordinates for each section and track location can be called to plot the data element.
+Each track and section coordinate, e.g.
+track 2 section 3, is treated as an individual plotting space.
+As such, data can be plotted based on the following coordinates: track, section, $X$, $Y$.
+The $X$ axis of each track is defined by the number of rows in the data frame, i.e a data frame with 100 rows will have an $X$ axis of length 100 with each row given an $X$ axis coordinate from 1:100.
+The $Y$ axis is defined by the minimum and maximum of the data for that track.
+As such, each track and section coordinate, e.g.
+track 2 section 3, can be considered an individual plot with a $Y$ axis that is shared by all of the sections in that track.
+For each position on the $X$ axis the label element of each row is plotted outside of the section header.
+<br>
+
+```{r annotated-circos-plot, echo=FALSE, out.width='100%', fig.cap="Annotated Circos plot highlighting elements of the Circos plot"}
+knitr::include_graphics("data/chapter6/figures/annotated_circos_plot.pdf")
+```
+
+### Implementation
+`EpiViz` is a `Shiny` web application and `R` package.
+`R` (version 3.6.2)[@r2019] and `Shiny`[@Chang2019] (version 1.4.0) were used to develop the web application and `R` (version 3.6.2) was used to develop the `R` package.
+`Shiny` is an `R` package that enables development and deployment of web applications written in the `R` programming language.
+Development of `EpiViz` was progressive and feedback from colleagues (see Section \@ref(epiviz-acknowledgements)) was vital in this process.
+
+### Operation
+The [web application](http://mrcieu.mrsoftware.org/EpiViz/) is publicly accessible -- [http://mrcieu.mrsoftware.org/EpiViz/](http://mrcieu.mrsoftware.org/EpiViz/) -- and held under an [MIT license](https://github.com/mattlee821/EpiViz/blob/master/LICENSE.txt).
+[Docker](https://www.docker.com/) was used to containerise the application.
+The [Medical Research Council Integrative Epidemiology Unit](http://mrcieu.mrsoftware.org/EpiViz/) at the University of Bristol `Shiny` server hosts the web application.
+The web application has been tested on computers running macOS (version 10.14) and Windows (version 10) using: Internet Explorer (version 11; Windows), Google Chrome (version 79; macOS and Windows), Safari (version 13; macOS).
+<br>
+
+The [`R` package](https://github.com/mattlee821/EpiViz/tree/master/R_package) is publicly accessible through GitHub -- https://github.com/mattlee821/EpiViz/tree/master/R_package --  and held under an[MIT license](https://github.com/mattlee821/EpiViz/blob/master/LICENSE.txt).
+The `R` package is accessible on all computers with `R` version 3.3.0 or higher and has been tested on macOS (version 10.14) and Windows (version 10) running `R` version 3.3.0 or higher.
+<br>
+
+A legend function is available for both the web application and `R` package and is implemented using functions from the [`ComplexHeatmap`](https://jokergoo.github.io/ComplexHeatmap-reference/book/)[@Gu2016] `R` package.
+By default the colours used for the Circos plot in both the web-application and `R` package are accessible colours identified using [i want hue](https://medialab.github.io/iwanthue/).
+Example data is provided on the web application *Home* tab and with the `R` package using the function `EpiViz::EpiViz_data*()` where `*` is 1-3.
+Example data can be produced for use with the web-application and `R` package using code on [GitHub](https://github.com/mattlee821/EpiViz/blob/master/R_package/data-raw/example_data_simulation.R).
+<br>
+
+#### `Shiny` web application
+In order to use the [web application](http://mrcieu.mrsoftware.org/EpiViz/) a web-browser and an internet connection of at least 1Mbps is required.
+No other system requirements are needed.
+Upon opening the web application, users are shown a number of example Circos plots created with the application and are directed towards the [*Home*]() tab.
+The *Home* tab (Figure \@ref(fig:web-app-home)) provides users with a short summary of the application, link to the `R` package, and example data for use with the app.
+<br>
+
+```{r web-app-home, echo=FALSE, out.width='100%', fig.cap="Screenshot of the EpiViz web application Home page"}
+knitr::include_graphics("data/chapter6/figures/web_app_home.png")
+```
+
+The [*How to*]() provides instructions for using the application and is split into three: Step 1 deals with the preparation of data to be used with the application, step 2 deals with how to use the application, and step 3 provides information on potential next steps.
+Users are instructed to upload one data frame per track of the Circos plot.
+Each data frame should be a tab delimited text file and `R` code is provided for users to achieve this.
+The user is guided through an example utilising the example data provided with the application and downloadable on the *Home* tab.
+<br>
+
+Having prepared their data as instructed in Step 1, users select the [*Analysis*]() tab and upload one data frame for each track of the Circos plot.
+If formatted as described in the *How to* tab, descriptive information including a volcano plot will be produced automatically (Figure \@ref(fig:web-app-analysis-step1)).
+<br>
+
+```{r web-app-analysis-step1, echo=FALSE, out.width='100%', fig.cap="Screenshot of the EpiViz web application Analysis page, showing Step 1"}
+knitr::include_graphics("data/chapter6/figures/web_app_analysis_data.png")
+```
+
+If the data frame appears as expected to the user the Circos plot can then be produced by selecting the [*Plot*]() tab.
+A series of drop down lists are presented which auto-populate with the column names from the first uploaded data frame.
+The following column information is required for the Circos plot: label, group, estimate, p-value, lower confidence interval, upper confidence interval (Figure \@ref(fig:web-app-analysis-step2)).
+Users can select one, two, or three tracks for their Circos plot, with data for the respective track coming from the upload data section.
+<br>
+
+```{r web-app-analysis-step2, echo=FALSE, out.width='100%', fig.cap="Screenshot of the EpiViz web application Analysis page, showing Step 2"}
+knitr::include_graphics("data/chapter6/figures/web_app_analysis_plot.png")
+```
+
+A p-value threshold (default 0.05) can be provided to indicate a significance threshold.
+On the Circos plot a solid point is indicated as reaching the significance threshold and an open point indicates not reaching the threshold.
+An optional legend function is provided and users can choose the labels for the legend points.
+The legend is auto-populated using the levels in the `group` column of the up-loaded data frame.
+Finally, users can select to use *Accessible colours* (default) or *Not accessible colours* for the colours of the points on the Circos plot.
+<br>
+
+#### `R` package
+The `EpiViz` `R` package is accessed using `R` version 3.3.0 or above.
+Documentation for using the package to create Circos plots is available as a README on [GitHub](https://github.com/mattlee821/EpiViz/tree/master/R_package) and includes use cases and troubleshooting.
+The `R` package can be installed directly from GitHub into `R` with the following `R` code: <br>
+
+```{r eval=FALSE}
+# Install devtools
+install.packages("devtools")
+library(devtools)
+
+# Install directly from GitHub
+devtools::install_github("mattlee821/EpiViz/R_package")
+library(EpiViz)
+```
+
+Once installed, users can use the example data provided with the package to produce Figure \@ref(fig:r-package-3-track-type-plot), which illustrates the three different types of track available (point, line, bar), using the following `R` code: <br>
+
+```{r eval=FALSE}
+circos_plot(track_number = 3,
+            track1_data = EpiViz::EpiViz_data1,
+            track2_data = EpiViz::EpiViz_data2,
+            track3_data = EpiViz::EpiViz_data3,
+            track1_type = "points",
+            track2_type = "lines",
+            track3_type = "bar",
+            label_column = 1,
+            section_column = 9,
+            estimate_column = 2,
+            pvalue_column = 3,
+            pvalue_adjustment = 1,
+            lower_ci = 4,
+            upper_ci = 5,
+            lines_column = 2,
+            lines_type = "o",
+            bar_column = 2)
+```
+
+```{r r-package-3-track-type-plot, echo=FALSE, out.width='100%', fig.cap="Circos plot prduced using EpiViz R package and example data"}
+knitr::include_graphics("data/chapter6/figures/r_package_3_track_type_plot.pdf")
+```
+
+These Circos plots are designed to be viewed on a screen rather than on paper.
+As such the plots are created at a larger scale compared to traditional plots made in `R`.
+This means that when viewing the Circos plot in an viewer such as the `R` Studio Viewer pane the plot appears squashed.
+Viewers like this should be used only as a guide when making the plot.
+Instead, plots should saved as `PDF` using the below code -- `PDF` files can be converted to other image formats.
+<br>
+
+```{r eval=FALSE}
+pdf("my_circos_plot.pdf",
+    width = 30, height = 30, pointsize = 35)
+circos_plot(...
+            circle_size = 25)
+dev.off()
+```
+
+`R` sets default height, width and pointsize parameters and users should iterate the sizing of the plot adjusting the `width` and `height` functions to get the desired plot size.
+They should then adjust the `pointsize` function to increase and decrease the size of all information in the plot (labels, points, lines etc.).
+The numbers provided work with most plots and were used for all examples.
+In addition, users can adjust the size of the Circos plot directly using the argument `circle_size`.
+The default for `circle_size` is 25 and smaller numbers increase the size of the circle and larger numbers decrease the size.
+Finally, users can adjust the height of tracks individually using `track*_height` where `*` refers to the track number (see below code).
+The default for each track is 20 percent of the total size of the circle (the section track is fixed at 5 percent).
+<br>
+
+```{r eval=FALSE}
+circos_plot(...
+            track1_height = 0.2,
+            track2_height = 0.2,
+            track3_height = 0.2)
+```
+
+In order to minimise the time required to maintain the `R` package further customisation is achieved by the users themselves.
+The function is written to aid this customisation with *Default parameters* and *Customisable parameters* located at the top of the `circos_plot()` function script.
+Guidance and code is provided on [GitHub](https://github.com/mattlee821/EpiViz/tree/master/R_package) to aid user customisation, for example changing track colours requires users navigating to the *Customisable parameters* section and then to the *Colours* section and replacing the following lines with their desired colours: <br>
+
+```{r eval=FALSE}
+discrete_palette <- c("#00378f", # track 1 colour
+                      "#ffc067", # track 2 colour
+                      "#894300") # track 3 colour
+```
+
+## Discussion
+Circos plots have been used to visualise and provide overview of large association analyses both in the literature[@Shin2014; @Kettunen2016] and this thesis (see Chapters \@ref(chapter4), \@ref(chapter5) and \@ref(chapter9)).
+This has been time consuming and cumbersome.
+Requiring bespoke code these plots have been challenging to work with when using multiple data sets (see [GitHub](https://github.com/mattlee821/000_thesis/tree/master/index/data/chapter6/code/circos_example.R) for example bespoke code).
+<br>
+
+`EpiViz` provides an efficient way to produce Circos plots for association analyses and can be implemented with little up-front cost.
+The web application is intended for researchers with limited to no experience of `R`, while those with some experience can gain added functionality from the `R` package.
+The application of Circos plots to comparing and gaining global overview of association analyses is presented in Chapters \@ref(chapter4), \@ref(chapter5) and \@ref(chapter9), as well as by colleagues[@Taylor2019].
+<br>
+
+Though intended to be low maintenance, there is scope for further development of both the web application and `R` package.
+Of broad appeal to both is the inclusion of new plotting methods such as the chord diagram which shows relatedness between two nodes.
+In the case of metabolites a chord diagram would provide greater understanding about the relationship between different sections.
+In addition, the ability to filter and choose specific sections to display would simplify the plot and highlight potentially meaningful results.
+<br>
+
+The web application is less flexible than the `R` package, however there are specific extensions of interest.
+Firstly interactive plots would provide users the ability to expand sections of interest and display additional information.
+Rather than a final presentation of the data this would primarily focus on exploration of data.
+Additionally, introducing features from the `R` package such as different plot types will broaden the appeal of the web application.
+These additions are likely to increase the costs of maintenance however.
+<br>
+
+The `R` package has extensive scope for enhancement and presents a more efficient investment of time for extensions over the web application due to the flexibility of `R`.
+Currently, only a single data point can be plotted on each track at each $X$ axis coordinate.
+This is to prevent over-crowding.
+However, if a data set has 50 points for example, adding a second point to each $X$ axis coordinate of the track would not overcrowd the plot.
+<br>
+
+The current limited customisation afforded with the web application and the `R` package is designed to reduce the maintenance costs of the author.
+As a result, functions that users may wish to use, such as multiple point estimates on a single track, must be coded by the user in `R`.
+Though guidance is provided on GitHub for such customisations, this additional effort may reduce the utility of the tool, especially among users with little experience of `R` but very specific requirements.
+Similarly, although designed to be efficient, users must provide data in a specific format in order to use the web application and `R` package.
+`R` code is provided to aid this effort but the requirement for users with no `R` experience to create a specific data frame will be off-putting for some.
+<br>
+
+In order to achieve the desired goal of providing global overview of large association analyses Circos plots must be much larger than traditional plots such as forest plots.
+As such, Circos plots are best utilised as a tool for the user rather than a reader of a print journal.
+Circos plots are best viewed using a screen with the ability to zoom in to sections where more detail is required.
+This fact will reduce the utility of this type of Circos plot in publications as fixed margins will limit the size and resolution of the plot.
+Resolution can be improved by saving the Circos plots as a `PDF` file.
+Many journals do not accept `PDF` images and will convert these into lossless formats such as `PNG` or `JPEG`.
+This will reduce the resolution provided for readers.
+<br>
+
+`EpiViz` is simple and efficient to use.
+There is potential for `EpiViz` to become widely used among the community.
+To pre-empt popularity and provide a stable environment the web application was containerized using Docker and hosted on a server with provision for multiple-users.
+With popularity it is hoped that a community will help to develop `EpiViz` further.
+<br>
+
+## Acknowledgements {#epiviz-acknowledgements}
+`EpiViz` was greatly aided by the `R` packages [`Circlize`](https://jokergoo.github.io/circlize_book/book/index.html)[@Gu2014] and [`ComplexHeatmap`](https://jokergoo.github.io/ComplexHeatmap-reference/book/)[@Gu2016], whose code is freely available and was used as a reference point.
+The following contributed to the development of `EpiViz`: Luke McGuinness, Osama Mahmoud, Sam Neaves.
+The following colleagues provided feedback in the development of `EpiViz`: Caroline Bull, Charlie Hatcher, Kurt Taylor, Nancy Mcbride, Neil Goulding, Steph Suddell.
+
+\newpage

### 2021-04-12 03-Chp-Systematic-Review-Tools.Rmd
End of day-2592

@@
 bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
+csl: bibliography/bmj.csl
 output:
@@
 
-`medrixvr` provides two ways to access medRxiv data. The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
+`medrixvr` provides two ways to access medRxiv data, as shown in Figure \@ref(fig:medrxivr-data-sources).
+The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
 
@@
 The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`.
-Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
-The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
 
@@
 
+Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
+The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
+
+&nbsp;
+
 <!----------------------------------------------------------------------------->
 
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx-api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
+(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
 Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
@@
 <!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
-There is now limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
+There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
 Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
@@
 results  <- mx_search(mx_data,
-                      c("dementia", "alzheimer's"), # Combined with OR
+                      myquery, # Combined with OR
                       report = TRUE)
@@
 ```{r, eval = FALSE}
-## Found 203 record(s) matching your search.
-## Total topic 1 records: 203
-## dementia: 203
-## Total topic 2 records: 0
-## alzheimer’s: 0
+## Found 1 record(s) matching your search.
+## 
+## Total topic 1 records: 224
+## dementia: 224
+## alzheimer's: 0
+## 
+## Total topic 2 records: 119
+## lipids: 90
+## statins: 33
 ```
@@
 This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
-It also aids in identifying misspelled search terms, which will frequently return no results.
+It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results.
+As an example, in the search presented above, the term "alzheimer's" returns no records.
+This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
 

### 2021-04-12 04-Chp-Systematic-Review.Rmd
End of day-2592

@@
 
-```{r gwet-setup, results="hide", message=FALSE}
+```{r gwet-setup, results="hide", message=FALSE, echo = FALSE}
 ```
 
-```{r gwet-table, message=FALSE, results="asis"}
+```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
 ```
@@
 
-In a two by two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
+<!--- Need example table here, showing relevant cells --->
 
-$$AC1 = \frac{p-e(\gamma)}{1-e(\gamma)}$$ Here, $p = \frac{A+D}{N}$ and $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where $q = \frac{(A+C)+(A+B)}{2N}$
+In a two-by-two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
+
+$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
+
+where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
+
+$$q = \frac{(A+C)+(A+B)}{2N}$$
 
@@
 
-Through snowballing and other measurse, we identified [@larsson2017b]
+Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
 

### 2021-04-13 02-Chp-Background.Rmd
End of day-2592
End of day: -2405

@@
 ---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
-  bookdown::word_document2: default
   bookdown::pdf_document2:
     template: templates/brief_template.tex
+  bookdown::word_document2: default
   bookdown::html_document2: default
@@
 knitr::read_chunk("R/background.R")
-
-knitr::opts_chunk$set(
-  include = FALSE
-)
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
@@
 
-<!-- ## Lay summary -->
+## Figures/Tables To
 
-<!-- Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
-Despite many promising candidates, no cure for dementia currently exists, so the focus is now on figuring out ways to prevent the condition by finding risk factors (characteristics that influence a person's chance of developing a disease) that we can easily change.
+* Diagnostic criteria
+* Statin mechanism of action 
+* Evidence pyramid
+* Overview of MR studies
+
+## Lay summary
+
+Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
+Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition.
+The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change.
 Avoiding a risk factor does not guarantee that a person will not develop dementia, but makes it less likely.
-A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood.
--->
+A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all available research agrees.
+The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
 
-<!-- This Chapter provides background information on dementia and lipids. It also provides a description. -->
-
-<!-- Evidence synthesis involves drawing on multiple sources of information to obtain the best possible to a research question, in this case, do lipids influence dementia risk.  -->
+This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them.
+It introduces the combination of evidence from different sources as the key framework used to guide the research presented in the remaining chapters.
+It then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
+Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.
 
@@
 
-This Chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background context on each.
+This Chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
 It will briefly discuss the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention therapeutics.
 
-In this context, it will highlight the importance of identifying easily modified risk factors and introduce blood lipids, and blood lipid-modifying treatments such as statins, as the primary exposures considered by this research.
+This chapter will highlight the importance of identifying easily modified risk factors and introduce blood lipids, and blood lipid-modifying treatments such as statins, as the primary exposures considered by this research.
 
-The central theoretical framework used - the synthesis of diverse sources of evidence - is introduced, and the research presented in this thesis is then framed in terms of three types of diverse evidence, with opposing viewpoints for each being discussed.
+The central theoretical framework used throughout this thesis will be the synthesis of diverse sources of evidence.
+This framework is introduced, and the research presented in this thesis is then framed in terms of three types of diverse evidence, with opposing viewpoints for each being discussed.
 
@@
 
-Dementia is a collective umbrella term for a range of conditions each with different clinical presentations and disease courses, and is generally defined as "". <!--- Cite --->
+Dementia is a collective umbrella term for a range of conditions each with different clinical presentations and disease courses, and is generally __defined as ""__. <!--- Cite --->
 
@@
 Characterised by substantial cognitive impairment and diffculty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.
-Much remains unknown unknown about Alzheimer's pathogenesis, despite research implicating the accumluation of amyloid plaques and neurofibrillary tangles, or alternatively the cholingeric nervous system, <!--- check ---> as potential mechanisms of disease.
+Despite research implicating the accumulation of amyloid plaques and neurofibrillary tangles, or alternatively the cholingeric nervous system, <!--- check ---> as potential mechanisms of disease, much remains unknown unknown about Alzheimer's pathogenesi
 
@@
 Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases and is caused by a range of cerebrovascular disorders.
-Presentation can vary widely based on the underlying cause, and due to the varied underlying  pathopysiology, VaD can onset quite rapidly following a cerbrovascular event such as a stroke or over a long period due to series of small infarcts.
-VaD is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
+Presentation can vary widely based on the underlying cause.
+Due to the varied underlying  pathophysiology, VaD can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.
+VaD is diagnosed using the __NINCDS-AIREN__ criteria.[@roman1993vascular]
 
@@
 
-Where more than one underlying dementia pathologies co-occur, this is termed mixed dementia.
-It is common for patients to present with mixed dementia, as the occurrence of one underlying cause weakens overall brain health and increases the likeliness of occurrence of the other.
+The term mixed dementia is used when more than one underlying dementia pathologies co-occur.
+This is a  common presentation of dementia because the presence  of one underlying condition  weakens overall brain health and increases the likelihood  of another condition developing.
 <!--- Double check this --->
@@
 Dementia is difficult to diagnose, primarily due to the absence of a gold standard test for the condition.
-<!-- is this true, or would it be better to say that there is no gold standard test without an autopsy?--> There exist several diagnostic criteria for dementia and related disease, many of which have existed for quite some time and have more recently been updated to reflect current understanding in dementia pathology.
-In all cases, dementia is diagnosed on the basis of behavioural and congitive changes as assessed by an experience clinician.
+<!-- is this true, or would it be better to say that there is no gold standard test without an autopsy?--> There exist several diagnostic criteria for dementia and related disease.
+In all cases, dementia is diagnosed on the basis of behavioural and cognitive changes as assessed by an experience clinician.
 <!-- This means the potential for misclassification both of dementia versus no-dementia and between the different underlying conditions is extremely likely. -->
@@
 
-Two of the most commonly used criteria include the the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR) <!-- __[CITATION NEEDED]__ --> criteria and the National Institute of Neurological Disorders and Stroke--Alzheimer Disease and Related Disorders (NINCDS-ADRDA) criteria.[@dubois2007]
+Two of the most commonly used criteria include those found in the Diagnostic and Statistical Manual of Mental Disorders, fourth edition (DSM-IV-TR) <!-- __[CITATION NEEDED]__ --> criteria and the National Institute of Neurological Disorders and those developed by the Stroke-Alzheimer's Disease and Related Disorders Association (NINCDS-ADRDA).[@dubois2007]
 
@@
 
-### Public Health Importance
+### Public health importance
 
@@
 
-Total serum cholesterol is a commonly used summary measure to estimate the total lipid burden in a patients blood, and  derived from the HDL-c, LDL-c and TG fractions using the Friedewald formula:[@friedewald1972]
+Total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood.
+The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
 
-$$TC \approx LDLc - HDLc - kTG$$ where $k$ is 0.20 if measurements are in mg/dl and 0.45 if in mmol/l.
+$$TC \approx LDLc - HDLc - kTG$$
+where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
 
-<!--- Include formula for working out total cholesterol and a table detailing the acceptable ranges. --->
+Widely used criteria for assessing the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
 
-Elevated cholesterol in the bloodstream via high LDL-c levels leads to atherosclerosis, the build-up of fatty deposits in the blood vessels, which constrict blood flow and can lead to vascular complications.
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+(ref:lipidLevels-caption) Classificaion of lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
+
+```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+Elevated cholesterol in the bloodstream via high LDL-c levels leads to atherosclerosis, the build-up of fatty deposits in the blood vessels.
+These deposits constrict blood flow and can lead to vascular complications.
 Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.
-Globally, the prevalence of elevated total cholesterol, or hypercholestoreolemia, was estimated by the World Health Organisation to be approximately 40%.
+Globally, the prevalence of elevated total cholesterol, or hypercholesterolemia, was estimated by the World Health Organisation to be approximately 40%.
 
@@
 Statins are by far the most common method of lipid regulation currently prescribed.
-Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid,  by compeitivlely binding with HMG-CoA Reductase (HMG-CoA-R).
-This conversion is the key rate limiting step in the biochemical pathway that produces cholesterol (see Figure \ref(), allowing statins to reduce the production of LDL cholesterol.
+Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid,  by competitively binding with HMG-CoA Reductase (HMG-CoA-R).
+This conversion limits the rate at which cholesterol (see Figure \ref(), can be produced, enabling statins to effectively reduce the production of LDL cholesterol.
 
@@
 
-There are a range of other interventions that can be used to modify a persons lipid profile, though each act is slightly different ways.
-Most commonly though, these treatments are either used as adjunct (additional) treatments with statins therapy, or are used in situations where statins are contra-indicated or not tolerated.
+There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways.
+However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
 
@@
 
-The most commonly used non-statin therapeutic is ezetimbibe, which prevents intestinal absorption of cholesterol.
-However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimbe therapies (both compounds contained in a single pill, as opposed to complimentary treatemnts).
+The most commonly used non-statin therapeutic is ezetimibe, which prevents intestinal absorption of cholesterol.
+However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.
+
+```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 <!----------------------------------------------------------------------------->
@@
 
-In this section I provide an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
+This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
 
@@
 The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent [CITE], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be robustly associated with increased AD susceptibility [CITE].
+Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility [CITE].
 
@@
 
-Despite these encouraging results, evidence from the diverse range of epidemiological studies on this topic has to date been been contradictory.
+Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.
 
@@
 
-Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported widely different results.
-A high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], though other studies have shown no association [14-17], or a reduced susceptibility [18,19].
+Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
+In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], however others have shown no association [14-17], or a reduced susceptibility [18,19].
 With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
@@
 
-### Summary level results vs individual patient data
+### Summary level results versus individual patient data
 
@@
 
-## Aims and Objectives of the thesis
+## Thesis overview
 
@@
 
-### Aims and Objectives
+### Aims and objectives
 
@@
 
-### Thesis Structure
+### Structure
 

### 2021-04-13 03-Chp-Systematic-Review-Tools.Rmd
End of day: -2405

@@
 bibliography: bibliography/references.bib
-csl: bibliography/bmj.csl
+csl: bibliography/nature.csl
 output:

### 2021-04-13 index.Rmd
End of day: 0
End of day: -2405

@@
 mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
+mini-toc-depth: 1
 mini-lot: false  # mini-list of tables by start of each chapter?
@@
     reference_docx: templates/word-styles-reference-01.docx
+    number_sections: false   
 link-citations: true

### 2021-04-13 R/helper.R

@@ -137,10 +137,25 @@ estimate <- function(estimate, lci, uci, type = "OR", sep = ",", to = "-"){
 }
 
 
-end_of_day <- function(words = NULL) {
+make <- function(arg = "pdf") {
+  system(paste0("make ", arg))
+}
 
+covering <- function(){
+  rmarkdown::render("front-and-back-matter/_00-introduction.Rmd")
+  browseURL("front-and-back-matter/_00-introduction.html")
+}
+
+end_of_day <- function(words = NULL) {
+  
+  # Make PDF and Word, and clean
+  system("make pdf-quiet")
+  system("make word")
+  system("make clean")
+  system("make clean-knits")
+  
   gert::git_add(files = ".")
-  gert::git_commit(paste0("End of day", words))
+  gert::git_commit(paste0("End of day: ", words))
   gert::git_push()
   
 }

### 2021-04-15 02-Chp-Background.Rmd
End of day: -2625

@@
 
+__Do I need another section on why the relationship is unclear?__
+
 ## Figures/Tables To
@@
 Avoiding a risk factor does not guarantee that a person will not develop dementia, but makes it less likely.
-A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all available research agrees.
+A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
 The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
@@
 This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them.
-It introduces the combination of evidence from different sources as the key framework used to guide the research presented in the remaining chapters.
-It then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
+It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
 Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.
@@
 
-This Chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
-It will briefly discuss the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention therapeutics.
+This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
+It briefly discussed the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention therapeutics.
 
-This chapter will highlight the importance of identifying easily modified risk factors and introduce blood lipids, and blood lipid-modifying treatments such as statins, as the primary exposures considered by this research.
+This chapter then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.
 
-The central theoretical framework used throughout this thesis will be the synthesis of diverse sources of evidence.
-This framework is introduced, and the research presented in this thesis is then framed in terms of three types of diverse evidence, with opposing viewpoints for each being discussed.
+It introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters. I will outline the aims, objectives and structure of this thesis, and
 
-Finally, it will outline the aims, objectives and structure of this thesis, and briefly summarise the contributions to the scientific literature that arose from this research.
+Finally, it briefly summarises the contributions to the scientific literature that arose from this research.
 
@@
 
-### Underlying pathologies
+### Underlying pathologies {#underlying-pathologies}
 
@@
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population looks set to create a dementia epidemic, particularly in Westernised countries.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.
 While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016]
-
-<!--- Talk about chronic underfunding here --->
-<!--- Talk about impact on health systems and  --->
 
@@
 
-Several cardiovascular elements have been identified as potential risk factors for dementia, and of these, lipid levels represent a promising target for preventative treatment due to the availability of lipid-modifying treatments.
-In this context, determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
-The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them.
+### Risk factors
+
+Given the substantial burden that dementia represents and the absence of any curative therapies, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019] The most commonly studied are cardiovascular factors, including hypertension,[@hughes2020association], stroke[@kuzma2018] and hyperlipidaemia.
+In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
+
+The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the evidence for an association between lipids and dementia outcomes.
 
@@
 The blood lipid profile contains a range of fractions.
-However, for the sake of this thesis, we will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorded from food (exogenouse lipids) or produced internally (endogenous lipids).
+However, for the sake of this thesis, we will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
 
@@
 In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.
+
 <!-- Need to also touch on the interplay between the different subcategories of lipids Does lowering one fraction affect the other(s)?
@@
 
-(ref:lipidLevels-caption) Classificaion of lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
+(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
+
+(ref:lipidLevels-scaption) Classification of blood lipid levels
 
@@
 &nbsp;
+&nbsp;
 
@@
 
-A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
+The core underlying biological cause of demetnia,
+
+A role for lipids in the aetiology of the disease is supported by both genetic linkage studies and functional cell biology studies.
+
 The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent [CITE], while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
@@
 Several observational studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], however others have shown no association [14-17], or a reduced susceptibility [18,19].
+In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD [8-13], however others have shown no association [14-17], or a reduced susceptibility [@mielke2005; @reitz2004a].
 With regards VaD, decreased levels of HDL-c appear to be associated with increased risk [18,20,21], while for LDL-c, studies have reported both positive and negative association [18,22].
@@
 
-Meta-analyses of randomised controlled trials are commonly seen as the gold standard in terms of epidemiological evidence.
-Indeed in the "evidence pyramid", meta-analysis of trials sit proudly on top.
-However, there included several potential limitations to this trial-only approach.
-In terms of the central research of this theis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
+In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
 
-<!----------------------------------------------------------------------------->
-(ref:evidence-pyramid-cap) __The "evidence pyramid":__ Overview of the widely accepted relative ranking of different sources of evidence, with meta-analyses of RCTS being considered the best form of evidence.
+However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.
 
-(ref:evidence-pyramid-scap) The "evidence pyramid"
+While being widely cited, these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
+Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
+One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
+As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
+The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
 
-```{r evidence-pyramid, echo = FALSE, results="asis", fig.cap='(ref:evidence-pyramid-cap)', out.width='100%', fig.scap='(ref:evidence-pyramid-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-<!----------------------------------------------------------------------------->
+Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
+As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not given that the effect of statins would be consistent across them.
 
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@()), <!--- Cross link here to section on presentation of dementia ---> as they would require extremely long and costly follow-up.[@ritchie2015] <!--- Check citation --->Additionally randomised trials require clinical equipoise - something that is unlikely in the case of statins, as while equipose may exist, it would be unethical to randomised patients to statins or not given their proven protective effect against coronary disease.
-It is no surprise then that the two know existing trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a]  are in fact trials of statins for the prevention of coronary related outcomes.
-The Prospective Study of Pravastatin in the Elderly (PROSPER) examined the protective effect of pravastatin on coronary outcomes.
-
-While being widely cited and indeed included in a Cochrane review on this topic (ironically, the lead author on this Cochrane review is ), these studies have major limitations that their utility to provide evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
-In fact, the PROSPER trial reported not on dementia outcomes, but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@() <!--- Cross with section on how scores alone are insufficient --->, change in scores alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
-
-Additionally, the two trials, while putatively examining all-cause dementia subject to the limited applicability of change in cognitive scores as described above, do not make any effort to assign an underlying pathology to each case.
-As discussed in Section \@ref(), <!--- Cross to section on difference disease courses in Ad vs VaD vs other ---> the different underlying pathology of dementia have different mechanisms of action, and so it is not given that the effect of statins would be consistent across them.
-
-Additionally, both trials were limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia [24,25].
-The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
-Given the long leg time between non-symptomatic onset of dementia and clinical presentation.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited [23].
+Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+Given the long lag time between non-symptomatic onset of dementia and clinical presentation.
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]
 
@@
 
-Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
-In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference [26].
-The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] as shown in Figure \@ref(fig:mr-overview), namely that:
+Newer methodological approaches,such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.
+In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] as shown in Figure \@ref(fig:mr-overview), namely that:
 
@@
 
-This approach relies on the results of genome wide association studies (GWAS) to identify appropriate instruments, and as such, analysis of this type are restricted by the availability of relevant GWAS.
-As the cost of genome sequence falls, more and more GWAS are being performed, and so number of MR studies had increased in tandem.
+Several Mendelian randomisations studies have examined the effect of blood lipid levels on dementia outcomes, finding <!--- Finish --->
 
-<!--- Can you compare the frequency of terms between PubMed and medRxiv to show that it is overrepresented --->
+A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk.
+However, this study was widely criticised as it did not exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.
+This invalidated the exclusion exclusion restriction criteria (Assumption 3, above), as the risk reduction observed in this study could be driven by variants in this region via a pathway independent of lipid levels.
 
-<!----------------------------------------------------------------------------->
-(ref:mr-overview-cap) __Overview of Mendelian randomisation study design:__ Shows the central assumptions of the Mendelian randomisation study design, using the example of lipids and dementia.
-
-(ref:mr-overview-scap) Overview of Mendelian randomisation study design
-
-```{r mr-overview, echo = FALSE, results="asis", fig.cap='(ref:mr-overview-cap)', out.width='100%', fig.scap='(ref:mr-overview-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A recent MR study indicated that low levels of LDL-c may cause a reduction in AD risk.[27] However, this study was widely criticised as it did not exclude the region surrounding the ApoE gene, the strongest know risk factor for Alzheimer's disease.
-This invalidated the exclusion exclusion restriction criteria (Assumption 3, above), as the risk reduction observed in this study could be driven by variants in this region via a pathway independent of lipid levels.
 <!--- Need more on MR here --->
@@
 
+Multiples forms of evidenc
+
 <!----------------------------------------------------------------------------->
@@
 
-The central theoretical framework used in this thesis is evidence synthesis - the discovery and critical integration of all available evidence on a research question in order to either: a) provide a more definitive answer to that question or; b) highlight gaps in the existing evidence base, so that future research address questions that have yet to be answered or explores the same question in a way that increases our confidence in the result.
+Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a]
 
-This thesis applies seeks to use an evidence synthesis framework to assess the relationship between lipids/statins and dementia.
-Of particular interest is the synthesis of evidence from a range of diverse sources.
-This thesis considers three sources of diversity in the evidence base:
+The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
+The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
 
-* Diverse study designs (and sources of bias)
-* Diverse publication status (preprints vs published articles)
-* Diverse sources of data (summary level data vs individual-level data)
+This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
+Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:
+
+* Triangulation
+* Inclusion of grey literature
+* Individual patient data meta-analysis
 
@@
 
-### Study designs and sources of bias
-
-<!----------------------------------------------------------------------------->
-As illustrated in Section \@ref(evidence-association), each individual epidemiological approach taken to examine the central research question of this thesis is subject to distinct biases and short-comings that limit our ability to infer a causal relationship between blood lipids and subsequent dementia risk.
-
-However, as each approach will be subject to distinct biases, these differences in design can be advantageous.
-If all approaches point, or triangulate, towards the same answer, this strengthens the evidence of a causal link between lipid levels and dementia risk.[26] In this context, systematically identifying, assessing and integrating all available evidence in a "aetiological triangulation" framework,[@lawlor2016a] regardless of study design or approach taken, may help to increase our confidence that a causal relationship truly exists.
-
-<!--- May need an extra bit here about how the different types of research apply to different time scales --->
-
-<!--- May need a bit about the differeny sources of bias, and why this lead me to do the CPRD analysis, which has a distinct source of bias
-
-In this context, assessment of
-
-even within certain study designs, underlying biases are different
-
-In some cases, synthesis across evidence required the
-
---->
-
-As such, this thesis aims to find all existing evidence on the relationship between lipids/statins and dementia via the comprehensive review in Chapter \@ref(sys-rev-heading), and then triangulate the different sources of evidence along with the primary analyses performed in this thesis (Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)) in Chapter \@ref(dicussion-heading).
+### Triangulating across study designs
 
@@
 
-<!-- ### Different sources of bias -->
+As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
+However, each method is limited by its own unique biases.
+Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results provides us with a middleground, between the directions of bias.
+A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.
 
-<!-- While we can expect different study designs to be subject to different inherent sources of bias - for example, issues with the randomisation procedure will only apply to randomised controlled trials - this thesis also considers diverse sources of evidence in terms of the methodological approaches taken within study type.
--->
+In order to triangulate across different evidence sources, all available evidence on a research question must first be identified.
+This requirement motivates the conduct of the comprehensive systematic review presented in Chapter \@ref(sys-rev-heading).
 
-<!-- The term "observational study", unlike RCT, belies wide range of analytical approaches,[@thiese2014] each with it's own limitations which can  -->
+Due to the fact triangulation exercises revolve around integral biases, it is necessary to assess the direction and magnitude of bias in a study.
+Risk-of-bias assessment tools provide a structured and transparent way to evaluate the internal validity of a study across several domains of bias.
+Tools now exist for a range of study designs including:
 
-<!-- #### Misclassification bias -->
+* randomised controlled trials;[@sterne2019] 
+* non-randomised studies of interventions;[@sterne2016robins] and
+* diagnostic accuracy studies.[@whiting2011quadas]
 
-<!-- Incredibly hard to diagnose dementia, and even if diagnosed dementia,  distinguishing between the different subtypes. -->
+Risk-of-bias assessment using a domain-based tool is a recommended part of the systematic review process.
+[@Pagen71; @sterne2019a; @mcguinness2018] In spite of this, several of the existing highly-cited systematic reviews of observational studies of the relationship between statins and dementia did not perform any risk-of-bias assessment[@chu2018b] or used an outdated tool.[@anstey;@poly2020c] As such, a core component of the systematic review presented in Chapter \@ref(sys-rev-heading) is a comprehensive domain-based risk-of-bias assessment for all included studies.
 
-<!-- When using code lists to define outcomes in large, population scale electronic health databases, evidence exists that there is wild misclassification between the  -->
-
-<!-- Given the diagnostic criteria for vascular dementia, it adds a particular difficulty to  -->
-
-<!-- <!--- Be careful here, as you don't account for misclassification in your CPRD study --->
-
-<!-- Misclassification can also affect studies of interventions through the introduction of immortal time. Several high profile observational studies of the effect of statins on dementia. -->
-
-<!-- #### Reverse causation -->
-
-<!-- Reverse causation is where the assumed exposure in an analytical framework is actually the outcome, reversing the direction of the assumed causal diagram.
-__[CITATION NEEDED]__ In the case of lipids and dementia, a reverse casual relationship would be observed by the early prodomal effects of dementia influencing a change in blood lipids.
--->
-
-<!-- In this context, evidence synthesis exercises must account for these threats to internal validity as part of the synthesis.
-However, many previous highly cited systematic reviews have now done so.
--->
-
-<!-- <!--- This is a key advantage of this study, as we account for . --->
-
-<!-- Given the range of biases that can be expected to effect studies into dementia, any evidence synthesis effort must take account of these and perform a robust risk of bias assessment to assess the internal validity.
--->
-
-<!-- A key issues here, particularly in the context of using statins as a proxy for blood lipid levels, is that there is a key distinction between internal validity and generalisability.
-One can be called the wrong answer to the right question, the other, the right answer to the wrong question.
--->
-
-<!-- Having identified a gap in the literature in the systematic review, both in terms of an absence of observational studies using the specific deisng and in an absence of data related to vascular dementia, in Chapter \@ref(cprd-analysis-heading), I aim to address this evidence gap and provide a further source of information for the triangulation in Chapter \@ref(discussion-heading) -->
+The findings from the review will then be triangulated with the primary analyses performed in this thesis (Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)) in Chapter \@ref(dicussion-heading).
 
@@
 
-### Preprints versus peer-reviewed articles {#diverse-sources-preprints}
+### Inclusion of grey literature {#diverse-sources-preprints}
 
+The importance of including grey (or gray) literature in systematic reviews is widely acknowledged.
+Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]
+
+A important developing source of grey literature are preprints.
 Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months;[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic;[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
-Preprint repositories have existed in certain fields for many years, such as the aRxiv for preprints in physics and mathematics, but have recently expanded into other fields.
-Repositories now exist for everything from ecology (EcoEvoRxiv) to meta-research (metaArXiv).
-There is much ongoing debate, particularly in light of the explosion of preprints following their widespread use to disseminate research related to the COVID-19 pandemic, about how preprints should be handled in the context of an evidence synthesis.
+One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns a lot of weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints is further strengthened by evidence that the results from preprinted studies seldom change following peer review.
+Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the overwhelming majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
 
-<!----------------------------------------------------------------------------->
-(ref:medrxiv-growth-cap) __Growth of the medRxiv and bioRxiv repositories over time:__ Additional caption info here.
-
-(ref:medrxiv-growth-scap) Growth of the medRxiv and bioRxiv repositories over time
-
-```{r medrxiv-growth, echo = FALSE, results="asis", fig.cap='(ref:medrxiv-growth-cap)', out.width='100%', fig.scap='(ref:medrxiv-growth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-<!----------------------------------------------------------------------------->
-
-One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.
-Some researchers recommend treating preprints as a separate category to peer-reviewed publication, using a flag or marker to indicate that certain evidence was sourced from.
-However, this approach assigns a lot of weight to peer-review as a indicator of "quality".
-Given the rise of predatory journals, and the (anecdotally) variable quality of peer-review across legitimate journals depending on the reviewer selected for a paper, peer-review is not always a reliable indicator.
-
-Meta-studies of the concordance between preprints and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the overwhelming majority of cases.[@shi2021a] This indicates that preprints should be considered a reliable reflection of the study, though these analyses are by necessity limited to preprinted studies that were subsequently published - the effect of peer review in limiting the publication of poorly design or executed studies is harder to assess.
-However, in the absence of any information on the subsequent publication, the preprint contains the best available evidence on a given research study, and so should be included in the review.
-
-The inclusion of non-peer-reviewed preprints substantially increases the need for thorough and detailed risk-of-bias assessment as part of the systematic review, in lieu of formal peer review.
-Risk-of-bias assessments provide a structured and transparent way to assess the internal validity of a study across several domains of bias.
-In theory, risk-of-bias assessments should be performed as part of systematic reviews, regardless of whether they included preprints,<!--- cite PRISMA and ROB2 paper here ---> but several of the existing highly cited reviews of observational studies of the relationship between statins and dementia did not perform any risk-of-bias assessment.
-<!-- __[CITATION NEEDED]__ -->
-
-Accepting that preprints represent an import source of information, their inclusion in systematic reviews is limited in practical terms by the absence of a replicable and transparent search tool for performing systematic searches in preprint repositories.
-The tool presented in Chapter \@ref(sys-rev-tools) aims to address this, and enables the inclusion of health-related preprints as evidence sources in the systematic review presented in Chapter \@ref(sys-rev-heading).
-
-<!--- Talk a bit more about studification, and link to how medrxivr allows you to do this --->
+In this thesis, preprints are considered an important source of evidence.
+However, as with many sources of grey literature, there are several logistical issues with carrying out systematic searches in preprint repositories.[@mahood2014] As such, to enable their inclusion in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
 
@@
 
-### Summary level results versus individual patient data
+### Individual patient data meta-analysis
 
@@
 
-Analysis of summary level data, that is the data extracted from publications describing primary studies, can only take investigators so far in this regard.
+Analysis of summary-level data, that is the data extracted from publications describing primary studies, can only take investigators so far in this regard.
 Due to a lack of primary studies readily presenting results stratified by covariates of interests, for example sex and ethnicity (see Section \@ref()), meta-analyses of summary-level data often have limited ability to examine exposure-covariate interactions (for example, sex and ethnicity.
@@
 
-This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading) and combine this with previously unanalysed data from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading).
+This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
+Any data contained will be combined with previously unanalysed data from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading).
 
@@
 The are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appedix-ppi) for more detail on the group).
+Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
 
@@
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, the `medrxivr` R package, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+-   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
 -   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the relationship between blood lipids, and interventions that modified blood lipids, and dementia.
@@
 -   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several previously unanalysed longitudinal cohort studies, to describe the relationship between blood serum lipids and dementia outcomes.
+-   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified and produced as part of this thesis.
+The overall strengths and weaknesses of this project are discussed in detail, and further work is suggested.
+
+An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)
+
+\blandscape
+<!----------------------------------------------------------------------------->
+(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading).
+Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
+
+```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+\elandscape
 
@@
 
-The outputs of this thesis are detailed below, and include published peer review papers, presentations at conferences, open source evidence synthesis tools.
+The outputs of this thesis are detailed below, and include published peer review papers, presentations, and open-source evidence synthesis tools.
 
@@
 
-During the course of this thesis, I have made several contributions to the scienitfic literature. Those arising from or directly related to the contents of this submission are presented below.
+During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.
 
@@
 
-A short paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
-<!--- need a bit here on why it is short - better to have documentation online, describe it as a lesson learned from the robvis paper, showing personal growth and improved experience.
---->
+A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
+As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).
 
@@
 Emily Hennessy (see Author Declarations in the front materials).
-<!--- Will need to cross-reference this bit!
---->
 
@@
 
-Using the tool described in Chapter \@ref(sys-rev-tools), I performed a "research-on-research" study, comparing the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
+Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
 
@@
 
-* Abstract accepted to the Cochrane Colloquium 2019
-* ARUK abstract on systematic review (I hope!)
-* Presentation to the Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf)
-* Invited seminar series on the RoB2 risk-of-bias assessment tool for randomised controlled trials to for Evidence Synthesis Ireland
-* Presentations to internal department wide seminar series, including the Methods in Evidence Synthesis Salon (MESS) and the MRC-IEU seminar series.
+<!--- Include links here for slides for each talk/poster --->
+
+_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_ Accepted poster abstract, Alzheimer's Association International Conference 2021.
+
+&nbsp;
+
+_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_
+Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
+
+&nbsp;
+
+_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_ Presentation to the  Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.
+
+_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_ Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
 

### 2021-04-15 03-Chp-Systematic-Review-Tools.Rmd
End of day: -2625

@@
 
-## Introduction
+## Introduction {#sys-rev-tools-intro}
 
@@
 Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
-At the time of writing, however, the bioRxiv.medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
+At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
 As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
@@
 
-```{r medrxivr-data-sources, fig.pos="!h", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
+```{r medrxivr-data-sources, fig.pos="H", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
 knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
@@
 ```{r, echo = FALSE}
-medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d"))
+
+medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = "2021-12-01")
 
@@
 
-date <- format(Sys.Date(),"%B %Y")
+date <- format(as.Date("2021-12-01"),"%B %Y")
 ```
@@
 The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to visualize the growing number of preprints related to the 2019 coronavirus outbreak [^chp-systematic-review-tools-3], perform searches of preprints as part of systematic reviews,[@noone2020] and examine how data-sharing behaviour is affected by different publication policies (see \@ref(thesis-output)).[CITE]
+It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]
 
-[^chp-systematic-review-tools-3]: <https://twitter.com/L_Brierley/status/1233109086444695553>
-
-Following rigorous peer-review, it has been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web",[CITE] and an associated article published in the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
+The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
 [^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
@@
 [^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>
-
-[Add bit about the benefits of the rOpenSci review process]
 
@@
 A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
-However, this approach ethos other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
+However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
 A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv would be substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-(This disagress with the use cases listed in the intro!)
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 
@@
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably lead to harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 
@@
 -   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed the tools reception to date, a roadmap for its future development and its place in the broader evidence synthesis in R ecosystem.
+I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.

### 2021-04-15 04-Chp-Systematic-Review.Rmd
End of day: -2625

@@
 
+<!--- Findings from this chapter are used throughout the later chapters of this thesis.
+In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.
+From Sam abbotts--->
+
 Test

### 2021-04-26 01-Chp-Background.Rmd
End of day: -2835

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
Science knows it doesn't know everything; otherwise, it'd stop.
```

(ref:dara-quote) --- Dara O'Briain

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/background.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

# Background, Theoretical framework, Aims & Objectives {#background-heading}

\minitoc <!-- this will include a mini table of contents-->

## Lay summary

[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]

Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition. Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition. The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change. Avoiding a risk factor does not guarantee that a person will not develop dementia but makes it less likely. A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees. The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.

This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them. It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis. Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.

<!----------------------------------------------------------------------------->

## Introduction

This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each. It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research. It then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.

The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters. Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.

<!----------------------------------------------------------------------------->

## Dementia

<!----------------------------------------------------------------------------->

### Definition and underlying pathologies {#underlying-pathologies}

Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]

Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases. Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease. Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]

Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases. Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]

The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease). [@burns2009]

<!----------------------------------------------------------------------------->

### Diagnostic criteria {#diagnostic-criteria}

Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]

(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.

```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.

Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale. The distinction between these memory scales and diagnostic criteria presented above should be noted. For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table). Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).

Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available (see Section \@ref(intro-treatments)). Cause-specific criteria exist for the diagnosis of dementia sub-types. For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]

<!-- ### Differing risk by sex -->

<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->

<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->

<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->

<!----------------------------------------------------------------------------->

### Public health importance

Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only once without a proven treatment.

Dementia also has a substantial economic impact. In 2015, the estimated total cost of dementia in England was £24.2 billion. Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]

As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.

<!----------------------------------------------------------------------------->

### Treatments {#intro-treatments}

Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020]. At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.

The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme. Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]

### Risk factors

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @ansteya]

The benefits of a prevention-based approach based on addressing these risk factors are well-studied. Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]

In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.

This thesis will focus on blood lipids as the primary risk factor of interest. The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the existing evidence for an association between lipids and dementia outcomes.

<!----------------------------------------------------------------------------->

## Serum lipids

<!----------------------------------------------------------------------------->

### Lipid fractions

The blood lipid profile contains a range of component parts, or fractions. However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]

Triglycerides are the simplest and most common type of lipids found across the body. They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities. Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor. In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]

In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood. The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]

$$TC \approx LDLc - HDLc - kTG$$
where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).

&nbsp;

<!----------------------------------------------------------------------------->

(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]

(ref:lipidLevels-scaption) Classification of blood lipid levels

```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels. These deposits constrict blood flow and can lead to vascular complications. Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.

<!----------------------------------------------------------------------------->

### Statins

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R). This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.

<!----------------------------------------------------------------------------->

(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the

(ref:statin-mechanisam-scap) Statin mechanism of action

```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

<!----------------------------------------------------------------------------->

### Other lipid regulating agents (LRA)

There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)). However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.

<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->

The most commonly used non-statin therapeutic is ezetimibe,[@kosoglou2005] which prevents intestinal absorption of cholesterol. However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).[@genest2006]

A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver. They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.

Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.

Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.

```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;
&nbsp;

<!----------------------------------------------------------------------------->

## Evidence for the association between blood lipids and dementia {#evidence-association}

This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.

<!----------------------------------------------------------------------------->
### Basic science

A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies. The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport. Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]

Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.

<!----------------------------------------------------------------------------->
### Observational studies

By far the largest source of evidence on the relationship between comes from observational designs. Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results. In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a]. With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]

Several previous systematic review of observational studies examining the effect of lipids[@anstey] and lipid-regulating agents[@chu2018b;@poly2020c] on dementia outcomes have been performed. However, these reviews have several limitations. Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)). Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey;@poly2020c]

<!----------------------------------------------------------------------------->

### Randomised controlled trials

In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.

However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.

While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk. Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome. One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years. As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome. The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.

Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome. As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.

Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up. Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia. Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]

<!----------------------------------------------------------------------------->

### Mendelian randomisation

Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:

1. the IV is associated with the exposure of interest (the relevance assumption);
2. the IV and outcome do not share a common cause (the independence assumption); and
3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).

Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels. This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]

Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.

<!----------------------------------------------------------------------------->

&nbsp;

In summary, multiple sources of evidence exist on the relationship between statins and dementia. In the next section, I introduce the synthesis of diverse sources of evidence as the theoretical framework used in this thesis.

Multiples forms of evidenc

<!----------------------------------------------------------------------------->

## Theoretical framework: Evidence synthesis

Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]

The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base. The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.

This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:

* Inclusion of grey literature
* Triangulation across evidence sources
* Individual patient data meta-analysis

These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.

<!----------------------------------------------------------------------------->

### Inclusion of grey literature {#diverse-sources-preprints}

The importance of including grey (or gray) literature in systematic reviews is widely acknowledged. Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]

A important developing source of grey literature are preprints. Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes. They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]

One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review. Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.

In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic. However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories. As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).

<!----------------------------------------------------------------------------->
### Triangulating across study designs

As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk. However, each method is limited by its own unique biases. Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result. The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias. A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.

This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.

All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading). Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise. [@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.

Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).

<!----------------------------------------------------------------------------->

### Individual patient data meta-analysis

Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]

In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]

An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]

Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a]. Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]

In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop. The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.

This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
<!----------------------------------------------------------------------------->

## Thesis overview

### Hypothesis

Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.

### Aims and objectives

The specific research objectives that this thesis seeks to address are:

* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions

### Structure {#thesis-structure}

Chapters are self-contained, presenting the methods and results of that specific research project. They are bookended by introductory and discussion sections which place the methods and results in context. Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).

-   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
-   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
-   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
-   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
-   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis. The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.

An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)

\blandscape
<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading). Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.

```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
\elandscape

## Outputs from this thesis {#thesis-output}

The outputs of this thesis are detailed below, and include peer-reviewed papers, presentations, and open-source evidence synthesis tools.

### Contributions to the scientific literature

During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.

&nbsp;

_**McGuinness, L. A.**, and L Schmidt. (2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651. DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_

A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading). As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).

&nbsp;

_Hennessy, E. A., Acabchuk, R., Arnold, P. A., Dunn, A. G., Foo, Y. Z., Johnson, B. T., Geange, S. R., Haddaway, N. R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A. Welch, V.,  **McGuinness L. A.** (2020). Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact. MetaArXiv. DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers. This piece was co-written with Dr. Emily Hennessy (see Author Declarations in the front materials). [Under 2nd round of review at Prevention Science]

&nbsp;

_**McGuinness, L. A.**, and Higgins J. P. T. (2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method). DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_

The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods. See Appendix \@ref(appendix-robvis) for more details on this tool.

&nbsp;

_**McGuinness, L. A.**, and Sheppard A. L. 2020. “A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv. DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_

Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts. [Accepted to PLOS One - need to update the citation]

&nbsp;

For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).

&nbsp;

### Presentations/Talks

<!--- Include links here for slides for each talk/poster --->

_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Accepted poster abstract, Alzheimer's Association International Conference 2021.

&nbsp;

_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_:
Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)

&nbsp;

_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.

_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.

### Software {#outputs-software}
**`medrxvir`**

An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories. See Chapter \@ref(sys-rev-tools-heading) for more details. Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:

```{r, eval = FALSE}
# CRAN version
install.packages("medrxivr")

# Development version
devtools::install_github("ropensci/medrxivr")
```

&nbsp;

**`robvis`**

An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review. See Appendix \@ref(appendix-robvis) for more details. Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:

``` {r, eval = FALSE}
# CRAN version
install.packages("robvis")

# Development version
devtools::install_github("mcguinlu/robvis")
```

&nbsp;

## Summary

This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.

\newpage

## References

### 2021-04-26 02-Chp-Systematic-Review-Tools.Rmd
End of day: -2835

--- 2021-04-15 03-Chp-Systematic-Review-Tools.Rmd
@@
       reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
   bookdown::html_document2: default
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = TRUE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
 Why are open source statistical programming  
@@
 library(medrxivr)
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
@@
 <!----------------------------------------------------------------------------->
-
-[Need to include bit on linking to published version via the tool]{.correction}
-
-## Main points (to be removed)
-
-The main points I want to get across in this Chapter are:
-
--   Why searching preprints is important
-
--   Why existing methods are not sufficient
-
--   What the `medrxivr` tool adds
 
@@
 Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[\@bramer2018a;\@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
+At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
 As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, warning=FALSE}
 
@@
 
-*Not sure where this should go, but keen to include it*
-
 Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
@@
 I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
+
+\newpage
+
+## References

### 2021-04-26 05-Chp-CPRD-Analysis.Rmd
End of day: -2835

@@
 ---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
@@
     template: templates/brief_template.tex
-  bookdown::word_document2: default
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
   bookdown::html_document2: default
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = TRUE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
 When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
@@
 source("R/helper.R")
-knitr::read_chunk("R/Chp2-Systematic-Review.R")
+knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
@@
 
-Might be able to get around this by pointing out
+Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?)
 
-## Things we tried
+__Things we tried__
 
-- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than.
+- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
 Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
 Need total number of those starting and average time to start.
-- Positive controls. Need to be able to explain why these controls have such wildly increased results.
+- Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper.
 - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
 - Allowing for time-varying confounders for binary covariates.
-- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
 
-## Things we could try
+__Things we could try__
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ## Lay summary
+Large scale database such as this are often called population level, and studies that make use of them have a number of advantages.
 
-The CPR
+This analysis uses one of these databases, the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of XXXXXX people from YYYYYY general practices across England.
+
+Using this data, I have analysed the ...
+
+<!----------------------------------------------------------------------------->
 
@@
 
+Large scale databases advantages over other means
+
+Cross reference here aswell re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
+
+<!----------------------------------------------------------------------------->
+
 ## Methods
 
-### Data source
+### Data source {#cprd-data-source}
 
@@
 
+The CPRD uses a coding system called Read code <!--- check capitalisation --->
+
 ### Study design and protocol
@@
 
-_Note: If protocol was written by Venexia, how do I reference this?_
+<!-- Note: If protocol was written by Venexia, how do I reference this? -->
 
@@
 
-### Study Cohort
+### Study cohort
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4mmol/L; or an LDL-c test result of >2mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
 
@@
 
+<!--- Include short bit on follow-up here, describing how and why it was defined --->
+
 We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
@@
 
+A range of additional variables were included in the analysis, intended to address differential distributions of potnetial confounding variables between those who had a
+
 <!--- Need a lot more here - see other thesis for example of how covariates are described --->
 
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-All
-covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
+
+Charlson co-morbidity index,
+
+Index of Multiple Deprivation (IMD),
+
+consultation rate,
+
+alcohol (current, former,  never),
+
+smoking (current, former,  never),
+
+BMI,
+
+baseline total cholesterol,
+
+and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+
+All covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+
+### Missing data
+
+Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and
+
+Binary variables were modelled using a
+
+continuo
+
+As per best practice, all other variables, including the out
+
+The MICE command in Stata was used
+
+### Time axis
+
+In Cox models, there is the option to
+
+Age vs time-since entry
+
+Expand on use of age as the time scale, but describe the problems this introduced
 
@@
 We use a Cox proportional hazards model with a time-varying treatment indicator.
-
-Expand on use of age as the time scale, but describe the problems this introduced
 
@@
 
+### Immortal time bias and time-varying treatment indicators
+
+Immortal time bias is a type of misclassification bias. It occurs when
+
+One potential way to address this is the use of a time-varying treatment indicator, a factor which modi
+
+In the case of this analysis, this treatment indicator is statin use. Using codes for statins (see Appendix \@ref())
+
+<!----------------------------------------------------------------------------->
+
 ### Estimating the value of the time-varying confounders
@@
 
+<!----------------------------------------------------------------------------->
+
 ### The effect of total cholesterol or LDL-cholesterol on LRA prescription
@@
 As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*
+
+<!--- This hasn't been done! --->
 
@@
 
-<!--- Show comparison of code lists here --->
+However, there was a large difference in the case mix of dementia diagnoses between the two analyses.
+
+However, as shown in Table \@ref(tab:smeethComparison-table), there is substantial divergence between the two sets of code-lists.
+
+The reason for the discrepancy in terms of the number of Alzheimer cases as a percentage of total dementia cases between our study and the Smeeth 2010 paper is due to two things:
+•	While all of the codes used to define Alzheimer’s in the Smeeth paper are included in our “Probable Alzheimer’s” code-list, we also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
+•	Several of the codes in our “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
+
+Using the Smeeth code-list, we get a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
+<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth.
+-->
+
+Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+
+&nbsp;
 
 <!----------------------------------------------------------------------------->
-``` {r smeeth-comparison-setup, results="hide", message=FALSE}
-```
+(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
 
-```{r smeeth-comparison-table, message=FALSE, results="asis"}
+(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
+
+```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
 ```
 <!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
+A further limitation is the possibility of time-varying confounding <!--- Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
+
 Finally, there is also the potential for reverse causation in this analysis.
@@
 
-Reporting
+Reporting guidelines do not always work, but help to guide
+
+All code and summary statistics (i.e.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.
+
+&nbsp;
 
@@
 Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
+
+\newpage
+
+## References

### 2021-04-26 R/Chp3-CPRD-Analysis.R

@@ -1,15 +1,12 @@
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- smeeth-comparison-setup
+# ---- smeethComparison-table
 
-smeeth-comparison_table <- mtcars
+smeethComparison_table <- mtcars[1:4,1:3]
 
-smeeth-comparison_caption <- "Caption"
-
-# ---- smeeth-comparison-table
-
-knitr::kable(
-  smeeth - comparison_table,
-  format = "latex",
-  caption = smeeth - comparison_caption,
-  booktabs = TRUE
-) %>% kable_styling(latex_options = c("striped", "hold_position"))
+if(doc_type == "docx"){
+knitr::kable(smeethComparison_table,caption = "(ref:smeethComparison-caption)")
+}else{
+knitr::kable(smeethComparison_table, format = "latex", caption = "(ref:smeethComparison-caption)", caption.short = "(ref:smeethComparison-scaption)", booktabs = TRUE) %>% 
+row_spec(0, bold = TRUE) %>%
+kable_styling(latex_options = c("HOLD_position"))
+}

### 2021-04-26 R/helper.R

@@ -64,8 +64,7 @@ check_words <- function(fp, words = 100){
     message("File: ",fp)
   }
   
-  t <- wordcountaddin::text_stats(fp)
-  w <- as.numeric(stringr::str_extract(t[3], "[0-9]+"))
+  w <- wordcountaddin::word_count(fp)
   n <- w + words
   
   message("Start:   ",format(Sys.time(),"%H:%M"),"\nCurrent: ",w,"\nNext:    ", n," <------\n")
@@ -82,9 +81,7 @@ pomodoro <- function(fp){
   
   while (i < 26) {
     
-    t <- wordcountaddin::text_stats(filename = fp)
-    
-    w <- as.numeric(stringr::str_extract(t[3], "[0-9]+"))
+    w <- wordcountaddin::word_count(filename = fp)
     
     message(i," - Current: ",w)
     
@@ -134,9 +131,9 @@ estimate <- function(estimate, lci, uci, type = "OR", sep = ",", to = "-"){
     stop("Lower CI is greater than upper CI")
   }
   
-  estimate <- stringr::str_trim(sprintf("%7.1f", estimate))
-  lci <- stringr::str_trim(sprintf("%7.1f", lci))
-  uci <- stringr::str_trim(sprintf("%7.1f", uci))
+  estimate <- stringr::str_trim(sprintf("%7.2f", estimate))
+  lci <- stringr::str_trim(sprintf("%7.2f", lci))
+  uci <- stringr::str_trim(sprintf("%7.2f", uci))
   z <- paste0(type, estimate, start, "95% CI: ", lci, to, uci, end)
   return(z)
 }

### 2021-04-27 05-Chp-CPRD-Analysis.Rmd
End of day: -2767

@@
 
-Originally termed the GPRD (General Practice Research Database),
+Originally termed the General Practice Research Database,
 
@@
 
+<!--- Insert flow-chart here --->
+
 &nbsp;
@@
 
+Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up ( <!--- Get date here ---> )
+
+_As a positive control outcome, we included cornonary artery disease. Statins have a known effect on this outcome on the basis of randomised controlled trials._
+
+We also used a negative control of backpain to investigate the potential for residual confounding.
+
 &nbsp;
@@
 
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
+The analysis was adjusted for a range of baseline covariates including sex,
+
+grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
 
@@
 
-All covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!--- link to Zenodo here --->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+<!--- Review materials from multiple imputation course --->
+
 Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and
 
-Binary variables were modelled using a
+<!-- Binary variables were modelled using a -->
 
-continuo
+<!-- continuos -->
 
-As per best practice, all other variables, including the out
+<!-- As per best practice, all other variables, including the out  -->
 
-The MICE command in Stata was used
+<!-- The MICE command in Stata was used -->
+
+In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.
+All covariates included in the analytic model were also included in the imputation model.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
-In Cox models, there is the option to
+<!-- In Cox models, there is the option to -->
 
-Age vs time-since entry
+<!-- Age vs time-since entry -->
 
-Expand on use of age as the time scale, but describe the problems this introduced
+<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
+
+To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
+Additional analyses stratified by outcome and drug class were also performed.
 
 &nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-Hazard rations are
+Hazard ratios are
 
@@
 
-<!--- This hasn't been done! --->
+<!--- This hasn't been done! Plus I do not think this is the case --->
 
@@
 
+## Results
+
 &nbsp;
+<!----------------------------------------------------------------------------->
+
+### Patient characteristics
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Missing data
+
+### Primary analysis
+
+### Sensitivity analyses
+
+By pregnancy
+
+By age-at-entry
+
+By statin type (lipo vs hydrophilic)
+
+### Controls
+
+Backpain
+
+Coronary artery disease
 
@@
 All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting (i.e.
+as comma separated values, or CSV, files) from the Github repository for this project.
+<!--- Will need to cite this, and may need to archive on Zenodo.
+--->
 

### 2021-04-27 R/helper.R

@@ -72,28 +72,43 @@ check_words <- function(fp, words = 100){
 
 pomodoro <- function(fp){
   
+  # Get file path ----
+    
   if (!hasArg(fp)) {
     fp <- rstudioapi::getSourceEditorContext()$path
     message("File: ",fp)
   }
+
+  # Fail early if wrong file type
+  sink <- wordcountaddin::word_count(filename = fp)
   
+  # Add job
+  # job_id <- rstudioapi::jobAdd("Long Pomodoro", progressUnits = 25L)   
+      
   i <- 0
+  
+  # rstudioapi::jobAddOutput(job_id, paste0("File: ",fp))
+  
+  # Run Long Pomodoro
   
   while (i < 26) {
     
     w <- wordcountaddin::word_count(filename = fp)
+    
+    # rstudioapi::jobAddOutput(job_id, paste0(i," - Current: ",w,"\n"))
     
     message(i," - Current: ",w)
     
     i <- i +1
     
     Sys.sleep(60)
+    
+    # rstudioapi::jobSetProgress(job_id, i-1)
   }
   
   beepr::beep(sound = "fanfare")
   
-  rstudioapi::showDialog("Pomodoro done!", "Take a break . . . ")
-
+  rstudioapi::showDialog("Pomodoro done!", paste0("Take a break . . . \n Final count: ", w))
 }
 
 
@@ -161,3 +176,4 @@ end_of_day <- function(words = NULL) {
   gert::git_push()
   
 }
+

### 2021-05-04 05-Chp-CPRD-Analysis.Rmd
End of day: -2856

@@
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
+```{r load-files, echo = FALSE}
 ```
@@
 
-Cross reference here aswell re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
+Cross reference here as well re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
 
@@
 
-<!--- Insert flow-chart here --->
-
-&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 &nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 -->
+IN addition, this analysis used propensity s. IN addition, an analytical approach which appeared to adjust for key variables likely to be on the analytical pathway between
 
@@
 
+### Patient sample
+
+<!----------------------------------------------------------------------------->
+(ref:cprdFlowchart-cap) __Attrition of CPRD participants as the eligibility criteria were applied:__
+
+(ref:cprdFlowchart-scap) Attrition of CPRD participants
+
+```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!--- Add some text here about the fact highlighting the key criteria that excluded participants --->
+
+&nbsp;
+
 ### Patient characteristics
 
+```{r characteristics, echo = FALSE}
+```
+
+Of the `r format(attrition[1,1], big.mark = ",")` participants included in our extract, `r format(attrition[14,1], big.mark = ",")` met the inclusion criteria (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of 11,091,437 patient years at risk.
+The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
+During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia; see Supplementary Figure 1).
+The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+
+<!--- Table 1 is missing type 2 diabetes --->
+
 &nbsp;
+
+\blandscape
+<!----------------------------------------------------------------------------->
+(ref:cprdCharacteristics-caption) Patient characteristics by drug class
+
+(ref:cprdCharacteristics-scaption) Patient characteristics by drug class
+
+```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+\elandscape
+
+&nbsp;
+
+A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
+We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
+The "Ezetimibe and statins" treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently.
+
+&nbsp;
+
 <!----------------------------------------------------------------------------->
@@
 
+```{r missing-data, echo = FALSE}
+```
+
+```{r azd-text, echo = FALSE}
+```
+
+Full covariate information was available for `r missingtext`.
+Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`, and baseline total cholesterol was missing for `r choltext`.
+
 ### Primary analysis
+
+All results described below are from the fully adjusted model.
+The results of the age-only model are presented in Supplementary Figure 3, and demonstrate that adjustment for additional covariates had a minimal effect.
+
+&nbsp;
+
+__Alzheimer's disease__
+
+As shown in Figure \@ref(fig:fig-results), our results show no effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+
+&nbsp;
+
+__Non-Alzheimer's disease dementias__
+
+In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
+Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+
+&nbsp;
+
+__All-cause dementia__
+
+For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
 
@@
 
-By pregnancy
+When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Appendix XXX).
+Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Appendix XXX).
 
-By age-at-entry
+<!-- For our negative control, there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (r sens_bp_text), suggesting there may be some residual confounding (Appendix XXX).
+-->
 
-By statin type (lipo vs hydrophilic)
+<!--- I actually think it would be better to include these results not in the appendix --->
+
+<!-- By pregnancy -->
+
+<!-- By age-at-entry -->
+
+<!-- By statin type (lipo vs hydrophilic) -->
 
@@
 
-Backpain
+<!-- Backpain -->
 
-Coronary artery disease
+<!-- Coronary artery disease -->
+
+_TBC - supervisors to email about it_
 
 ## Discussion
+
+<!--- To what extent should I cross-reference with the other literature here? --->
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Comparison to other literature
@@
 Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.
+
+Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. __[CITATION NEEDED]__
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Original contribution to research
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Coding quality in the CPRD
@@
 There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]
+
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Enabling easy synthesis
 
-In light of my own experiences in attempting to extract information for papers assessing prevantive measures, I attempted to document
+In light of my own experiences in attempting to extract information for papers assessing preventative measures, as documented in Section \@ref(), the outputs from this analysis are described in detail in both.
+IN line with this, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
 
-This study was reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
-
-Reporting guidelines do not always work, but help to guide
+Reporting guidelines do not always work, but help to guide accurate rep
 
 All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting (i.e.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
 as comma separated values, or CSV, files) from the Github repository for this project.
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Conclusions
 
-We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-We found use of lipid-regulating agents not associated with probable or possible Alzheimer’s disease, but were associated with an increased risk of all-cause, vascular and other dementias.
+This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+It found use of lipid-regulating agents associated with a small reduction in probable or possible Alzheimer’s disease, and were associated with an increased risk of all-cause, vascular and other dementias.
 In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
 
-We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature.
+This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
 However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+
+Given the observed increased association of statins in other
+
+While these
+
 Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.

### 2021-05-04 R/Chp3-CPRD-Analysis.R

@@ -10,3 +10,329 @@ knitr::kable(smeethComparison_table, format = "latex", caption = "(ref:smeethCom
 row_spec(0, bold = TRUE) %>%
 kable_styling(latex_options = c("HOLD_position"))
 }
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- load-files
+
+attrition <- read.csv(here::here("data","cprd","cohort_attrition.csv"))
+
+p1 <- read.csv(here::here("data","cprd","regression_results_p1.csv")) %>%
+  filter(drug == "Any") %>%
+  select(outcome, N_fail) %>%
+  unique()
+
+p1$outcome <- factor(p1$outcome, levels = c("Any dementia", "Probable AD", "Possible AD", "Vascular dementia", "Other dementia"))
+p1 <- p1[order(p1$outcome),]
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- cprdCharacteristics-table
+
+table1 <- read.csv(here::here("data","cprd","table1.csv"),header=FALSE)
+table1 <- data.table::transpose(table1)
+colnames(table1) <- as.character(unlist(table1[1,]))
+table1 = table1[-1, ]
+
+colnames(table1)[1] <- " "
+
+table1[1,1] <- "Sample size"
+table1[2,1] <- "Index year \\newline(median)"
+table1[3,1] <- "Female"
+table1[4,1] <- "Age"
+table1[5,1] <- "CAD"
+table1[6,1] <- "CBS"
+table1[7,1] <- "CVD"
+table1[8,1] <- "Charlson (ever > 0)"
+table1[9,1] <- "IMD-2010 (median)"
+table1[10,1] <-"Consulation rate (mean/SD)"
+table1[11,1] <-"Alcohol (ever)"
+table1[12,1] <-"Smoking (ever)"
+table1[13,1] <-"BMI (mean/SD)"
+table1[14,1] <-"PAD"
+table1[15,1] <-"Hypertension"
+table1[16,1] <-"Total cholesterol (mean/SD)"
+table1[17,1] <-"CKD"
+table1[18,1] <-"Type 1 Diabetes"
+
[…]

### 2021-05-04 R/helper.R

@@ -70,6 +70,10 @@ check_words <- function(fp, words = 100){
   message("Start:   ",format(Sys.time(),"%H:%M"),"\nCurrent: ",w,"\nNext:    ", n," <------\n")
 }
 
+pomodoro_bg <- function(){
+  job::job({pomodoro()},import = c(pomodoro))  
+}
+
 pomodoro <- function(fp){
   
   # Get file path ----
@@ -177,3 +181,7 @@ end_of_day <- function(words = NULL) {
   
 }
 
+
+hold <- function(){
+  "**PLACEHOLDER**"
+}

### 2021-05-11 01-Chp-Background.Rmd
End of day: -2767
End of day: -3892

@@
 output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::word_document2:
@@
     number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 <!----------------------------------------------------------------------------->
+
+<!--- May need small bit here on converting from one measurement to the other i.e.
+mg/dL to mmol/L--->
 

### 2021-05-11 04-Chp-CPRD-Analysis.Rmd
End of day: -3892

--- 2021-05-04 05-Chp-CPRD-Analysis.Rmd
@@
       number_sections: false 
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 
-## Additional ideas
+<!-- ## Additional ideas -->
 
-One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+-->
 
-Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?)
+<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
 
-__Things we tried__
+<!-- __Things we tried__ -->
 
-- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
+<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
 Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
 Need total number of those starting and average time to start.
-- Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper.
-- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
-- Allowing for time-varying confounders for binary covariates.
+-->
+<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
+<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
+<!-- - Allowing for time-varying confounders for binary covariates. -->
 
-__Things we could try__
+<!-- __Things we could try__ -->
 
-- Work through data using positive control to see if the way it is being added is what is causing the issues.
-- Examine Cramer et al. thesis and see what they did
-- Marginal structural models approach (a la J. Sterne)
+<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
+<!-- - Examine Cramer et al. thesis and see what they did -->
+<!-- - Marginal structural models approach (a la J. Sterne) -->
 
@@
 ## Lay summary
-Large scale database such as this are often called population level, and studies that make use of them have a number of advantages.
+Large-scale electronic health record (EHR) databases are created through the routine collection of information from patients.
+Under this system, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
+These databases have substantial advantages for research studies, including the number of people they contain and the length of time for which participants are followed.
+This is particulary important when studying diseases such as dementia, which may begin to develop long before symptoms are seen.
 
-This analysis uses one of these databases, the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of XXXXXX people from YYYYYY general practices across England.
+This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across England.
+Using this data, I examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
 
-Using this data, I have analysed the ...
+Lipid regulating agents were found to have no or minimal effect on Alzheimer's disease, but increased the risk of vascular dementia.
+This increase is very likely to be due to the presence of bias in the analysis despite best efforts to address it.
+However, this analysis still provides important sources of information which will be used in later chapters.
 
@@
 
+&nbsp;
+
 ## Introduction
 
-Lack of evidence for the association of statins on vascular dementia risk
+This chapter details an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent use and dementia outcomes.
+The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
 
-Large scale databases advantages over other means
+In the first instance, it explicitly examines vascular dementia as an outcome.
+This is particular important to the thesis as a whole, as the systematic review identified an absence of information on the effect of lipids on dementia risk.
 
-Cross reference here as well re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
+In the second instance, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia.
+This approach was taken to provide a further distinct evidence source for the triangulation exercise presented in Chapter \@ref(discussion-heading).
 
@@
 
+&nbsp;
+
 ## Methods
+
+### Study protocol
+
+An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-The Clinical Practice Research Datalink (CPRD) is a large, population-based, electronic health record database.[@herrett2015] It contains the primary care records for
+Previously know as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collected primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
-Originally termed the General Practice Research Database,
+To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD collects data use a predefined coding system known as Read codes.[@booth1994] All clinical events can be identified by a specific code.
+The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
+Eu...
+- Mental and behavioural disorders), while subsequent digits provide addition information on the specific condition diagnosed (e.g.
+Eu001 - Dementia in Alzheimer's disease with late onset).
 
-The
+&nbsp;
 
-Data completeness and collection of certain disease are heavily influenced by exercises that reward doctors for capturing certain diagnoses, such as the Quality and Outcomes Framework.
-However, these drives can oftern have unintended consequences [@liu2019]
+<!----------------------------------------------------------------------------->
+(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" is nested under the top-level of "Mental disorders".
+Broad topics are specified using the initial two bytes, while subsequent bytes are used to define specific conditions and context.
 
-The CPRD uses a coding system called Read code <!--- check capitalisation --->
+(ref:readExample-scaption) Example of CPRD Read code hierarchy
 
-### Study design and protocol
+```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+Using this system, lists of relevant codes for each of the index events, exposures and outcomes described in the sections below were created.
+
+&nbsp;
+
+### Cohort definition
 
@@
 Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
-
-An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
-This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).[@vonelm2008]
+All events of interest were identified using predetermined code lists, which are available for inspection.
 
 <!-- Note: If protocol was written by Venexia, how do I reference this? -->
-
-&nbsp;
-
-### Study cohort
 
@@
 
+&nbsp;
+
 ### Exposures
@@
 
-&nbsp;
+<!--- TODO this table doesn't exist anywhere as it has been cut off the bottom of Table 1 --->
 
@@
 
+&nbsp;
+
 ### Outcomes
 
-<!--- Include short bit on follow-up here, describing how and why it was defined --->
+<!--- TODO Include short bit on follow-up here, describing how and why it was defined --->
 
@@
 
-Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up ( <!--- Get date here ---> )
+Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up ( <!--- TODO Get date here ---> )
 
-_As a positive control outcome, we included cornonary artery disease. Statins have a known effect on this outcome on the basis of randomised controlled trials._
+As a positive control outcome, we included cornonary artery disease.
+Statins have a known effect on this outcome on the basis of randomised controlled trials.
+__[CITATION NEEDED]__ We also used a negative control of back pain to investigate the potential for residual confounding.
 
-We also used a negative control of backpain to investigate the potential for residual confounding.
+<!--- TODO need more information on how the controls were modelled - e.g. using the same covariates as in the main model or not? --->
+
+<!--- TODO Will also need some more here on why there were chosen --->
 
@@
 
-A range of additional variables were included in the analysis, intended to address differential distributions of potnetial confounding variables between those who had a
+A range of additional variables were included in the analysis, intended to address differential distributions of potential confounding variables between those who had were prescribed an LRA and those who were not.
 
-<!--- Need a lot more here - see other thesis for example of how covariates are described --->
+<!--- TODO Need a lot more here - see other thesis for example of how covariates are described --->
 
-The analysis was adjusted for a range of baseline covariates including sex,
+The analysis was adjusted for a range of baseline covariates including sex,grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
 
-grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
+All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!--- TODO link to Zenodo here --->
 
-Charlson co-morbidity index,
-
-Index of Multiple Deprivation (IMD),
-
-consultation rate,
-
-alcohol (current, former,  never),
-
-smoking (current, former,  never),
-
-BMI,
-
-baseline total cholesterol,
-
-and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-
-All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!--- link to Zenodo here --->
+We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
+Additional analyses stratified by outcome and drug class were also performed.
 
@@
 
+Given that they contain an administrative data, collected for the purposes of patient management and care rather than academic research, missing data are a recognised issue in electronic health records databases.[@wells2013strategies]
+
+<!--- TODO Need to complete paragraph below --->
+
+<!--- Failing to adjust for missing data can. . .  --->
+
+<!-- Complete case analyses are limited by . . . -->
+
 <!--- Review materials from multiple imputation course --->
 
-Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed dataset.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
 
-<!-- Binary variables were modelled using a -->
+Missing data was only considered an issue for variables where a numerical test result was expected, (e.g.
+BMI) or where a code existed for the absence of the condition (e.g.
+categorical smoking status).
+This approach was necessary, as absence of a code for other conditions (e.g.
+statin use or dementia) is used to define a negative value of binary variables indicating the presence or absence of the condition, and so had no missing data at the point of imputation.[@wells2013strategies]
 
-<!-- continuos -->
-
-<!-- As per best practice, all other variables, including the out  -->
-
-<!-- The MICE command in Stata was used -->
-
-In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.
-All covariates included in the analytic model were also included in the imputation model.
+To investigate the impact of multiple imputation versus a complete case analysis,[@pigott2001review] where participants missing any covariate are dropped from the dataset, we preformed and compared the results of both approaches.[@hughes2019a]
 
@@
 
+<!--- TODO Finish paragraph from fragments below --->
+
 <!-- In Cox models, there is the option to -->
@@
 
-To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
-Additional analyses stratified by outcome and drug class were also performed.
+As part of a Cox proportional hazard model, there is the option to use either absolute time or participants age as the time scale of interest.
+A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
+
+In order to compare and contrast between the two approaches, we ran two simple model, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
+
+<!--- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! --->
 
@@
 
-Potential biases included time varying confounding, selection bias due to censoring on death and 
-We use a Cox proportional hazards model with a time-varying treatment indicator.
+To estimate the effect of statins on dementia outcomes, we used a Cox proportional hazards model, defined as:
 
-Expand on post estimation analyses, which showed that nothing except age had an effect.
+<!-- TODO Expand on post estimation analyses, which showed that nothing except age had an effect. -->
 
@@
 
-__Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__
+<!-- TODO __Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__ -->
 
-Hazard ratios are
+<!-- Hazard ratios are -->
 
-Test for non-proportionality are therefore very important, as models which fail
+<!-- Test for non-proportionality are therefore very important, as models which fail -->
 
-Problems with testing for non-proportional hazards when
+<!-- Problems with testing for non-proportional hazards when  -->
 
@@
 
-Immortal time bias is a type of misclassification bias. It occurs when
+<!-- Potential biases included time varying confounding, selection bias due to censoring on death and  -->
+<!-- We use a Cox proportional hazards model with a time-varying treatment indicator. -->
 
-One potential way to address this is the use of a time-varying treatment indicator, a factor which modi
+Immortal time bias covers two distinct but related types of bias.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to exposure is excluded, leading to the exposed and control groups being followed up from different time points.[@levesque2010a] In this case, events that occur prior to the exposure event are missing from the analysis.
 
-In the case of this analysis, this treatment indicator is statin use. Using codes for statins (see Appendix \@ref())
+The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
+It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
+This second presentation appears to be common in the existing literature, as many of the studies included in the review in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(#risk-of-bias-subheading))
+
+To address the potential for immortal time bias in our analysis, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
+
+<!--- TODO Discuss problems introduced by censoring on death --->
 
 <!----------------------------------------------------------------------------->
+(ref:immortalTimeBias-cap) __shortcap:__
 
-### Estimating the value of the time-varying confounders
+(ref:immortalTimeBias-scap) shortcap
 
-Mean time from index event to first prescription of statins was 2.4 years.
-This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
-
-Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
-This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
-For example:
-
-    _No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_
-
-In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_.
-
-In practice, this means that the value of the prognostic factor should be regularly captured
-
-However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
-
-This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
-
-i.e.  
-Timepoint 12345678  
-CVD       00001111  
-Treatment 00000111
-
-Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point.
-
-Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
-
+```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
+```
 <!----------------------------------------------------------------------------->
 
-### The effect of total cholesterol or LDL-cholesterol on LRA prescription
+<!-- ### Sensitivity analyses -->
 
-It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.
+<!--- Described sensitivity analyses reported below here --->
 
-However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*
-
-<!--- This hasn't been done! Plus I do not think this is the case --->
-
-### Replicating other analytical strategies
-
-**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This highlights a particular challenge in comparing research across different time-periods and coding systems.
-Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
-
-In order to
-
-As part of my exploration of the unexpected results, I attempted to replicate the analyses of another paper that used a different approach to
-
-Having contacted the authors to address these concerns, it was noted that
-
-Propensity scores are based on a range of baseline variables, and provide an estimates of the
-
-They used propensity scores to attempt to matcch patients equally likely to recieve the vaccine
-
-In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
-Fortunately, the authors kindly shared their
-
-However, there was a large difference in the case mix of dementia diagnoses between the two analyses.
-
-However, as shown in Table \@ref(tab:smeethComparison-table), there is substantial divergence between the two sets of code-lists.
-
-The reason for the discrepancy in terms of the number of Alzheimer cases as a percentage of total dementia cases between our study and the Smeeth 2010 paper is due to two things:
-•	While all of the codes used to define Alzheimer’s in the Smeeth paper are included in our “Probable Alzheimer’s” code-list, we also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
-•	Several of the codes in our “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
-
-Using the Smeeth code-list, we get a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
-<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth.
--->
-IN addition, this analysis used propensity s. IN addition, an analytical approach which appeared to adjust for key variables likely to be on the analytical pathway between
-
-Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+<!--- Make sure to include age as a sensitivity analysis, given that that is the purpose of the IPD analysis --->
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
-
-(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
-
-```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
 ## Results
 
+### Patient characteristics
+
+```{r characteristics, echo = FALSE}
+```
+
+Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of 11,091,437 <!--- TODO make this reactive!
+---> patient years at risk.
+
 &nbsp;
-<!----------------------------------------------------------------------------->
-
-### Patient sample
 
@@
 (ref:cprdFlowchart-scap) Attrition of CPRD participants
+
+<!--- This figure needs to have comma seperated numbers in order to agree with text. --->
 
@@
 
-<!--- Add some text here about the fact highlighting the key criteria that excluded participants --->
-
-&nbsp;
-
-### Patient characteristics
-
-```{r characteristics, echo = FALSE}
-```
-
-Of the `r format(attrition[1,1], big.mark = ",")` participants included in our extract, `r format(attrition[14,1], big.mark = ",")` met the inclusion criteria (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of 11,091,437 patient years at risk.
 The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia; see Supplementary Figure 1).
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia; <!--- see Supplementary Figure 1 --->).
 The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-
-<!--- Table 1 is missing type 2 diabetes --->
-
-&nbsp;
 
@@
 
-&nbsp;
+<!--- Table 1 is missing type 2 diabetes --->
 
@@
 
+&nbsp;
+
 ### Primary analysis
@@
 
+<!----------------------------------------------------------------------------->
+(ref:cprdPrimary-cap) __Results from primary analyses of CPRD data:__
+
+(ref:cprdPrimary-scap) Results from primary analyses of CPRD data
+
+```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_p1.jpeg"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;
@@
 
-As shown in Figure \@ref(fig:fig-results), our results show no effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+As shown in Figure \@ref(fig:cprdPrimary), the results of the analysis do not support an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 
+&nbsp;
+
 ### Sensitivity analyses
 
-When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Appendix XXX).
-Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Appendix XXX).
+When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(hold)).
+Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Figure \@ref(hold)).
+
+<!--- TODO Actually run this analysis --->
+
+<!--- TODO Sort out the mess that is below --->
 
@@
 <!--- I actually think it would be better to include these results not in the appendix --->
+
+<!--- By multiple imputation versus complete case analysis --->
 
@@
 
-### Controls
+<!--- By time varying confounder --->
+
+<!-- ### Estimating the value of the time-varying confounders -->
+
+<!-- Mean time from index event to first prescription of statins was 2.4 years.
+This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
+-->
+
+<!-- Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
+This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
+For example: -->
+
+<!--     _No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_ -->
+
+<!-- In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_. -->
+
+<!-- In practice, this means that the value of the prognostic factor should be regularly captured -->
+
+<!-- However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
+-->
+
+<!-- This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
+-->
+
+<!-- i.e.   -->
+<!-- Timepoint 12345678   -->
+<!-- CVD       00001111   -->
+<!-- Treatment 00000111   -->
+
+<!-- Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point. -->
+
+<!-- Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.  -->
+
+<!-- ### Controls  -->
+
+<!--- TODO I think this is maybe dealth with at the end of the "Exposures" section, but better to have it here? --->
 
@@
 
-_TBC - supervisors to email about it_
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 <!--- To what extent should I cross-reference with the other literature here? --->
+
+<!--- Maybe it would be better to signpost towards the triangulation chapter where the different evidence streams are combined --->
 
@@
 For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+
+<!--- TODO Why are fibrates different? --->
+
+<!--- TODO Be explicit here about the possibility of publication bias in the vascular dementia results --->
 
@@
 
-Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. __[CITATION NEEDED]__
+Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. <!--- TODO citation needed --->
 
@@
 
+<!----------------------------------------------------------------------------->
 &nbsp;
 
-<!----------------------------------------------------------------------------->
+### Strengths and limitations
 
-### Original contribution to research
+<!--- TODO I actually don't think Strengths and Limitations are the best way to describe this! --->
 
-There are two primary ways in which this research adds to the topic:
+<!-- TODO A major strength of this analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
+In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
+-->
 
-* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
+There are two primary strenghts to this analysis compared to others available in the literature:
+
+* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest studies of this research question.
 * _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
 
-<!----------------------------------------------------------------------------->
-
-### Coding quality in the CPRD
-
-Lots of things influence prevalence: historic trends, availability of good codes
-
-There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]
-
-<!----------------------------------------------------------------------------->
-
-### Strengths and Limitations
-
-A major strength of our analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
-In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
-
-However, the findings of our analysis are subject to several limitations.
+However, the findings of this analysis are subject to several limitations.
 There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
@@
 
-Our study may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
+This analysis may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
 We attempted to address this by limiting inclusion to those either prescribed or “at risk” of being prescribed, which was determined using an elevated test result.
 We also adjusted for several additional potential confounding variables.
-However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that our findings may be biased by residual confounding.
+However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that this findings may be biased by residual confounding.
 Important confounding variables for which we have not adjusted could include genetic factors.
@@
 
-A further limitation is the possibility of time-varying confounding <!--- Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
+<!--- TODO A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
 
@@
 <!----------------------------------------------------------------------------->
+&nbsp;
 
-### Enabling easy synthesis
+### Replicating other analytical strategies
 
-In light of my own experiences in attempting to extract information for papers assessing preventative measures, as documented in Section \@ref(), the outputs from this analysis are described in detail in both.
-IN line with this, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
+<!--- TODO I will definitely have to mention this earlier in the chapter, as it is bad for to try and spring methods on people --->
 
-Reporting guidelines do not always work, but help to guide accurate rep
+Misclassification of outcomes, as discussed in the section above, is not the only issue introduced by the use of EHR codes to define outcomes.
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This is a particular challenge in comparing research across different time-periods and coding systems.
+Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
 
-All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the Github repository for this project.
-<!--- Will need to cite this, and may need to archive on Zenodo.
---->
+As part of my exploration of the unexpected results, I attempted to replicate the analyses of another research group (Smeeth et al.)__[CITATION NEEDED]__ that employed a different approach to explore the effect of statin use on dementia outcomes.
+
+<!-- Having contacted the authors to address these concerns, it was noted that  -->
+
+<!-- Propensity scores are based on a range of baseline variables, and provide an estimates of the  -->
+
+<!-- They used propensity scores to attempt to matcch patients equally likely to receive the vaccine -->
+
+<!-- In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
+Fortunately, the authors kindly shared their -->
+
+However, there was a large difference in the dementia "case mix", or proportion of different dementia diagnoses, between the two analyses, particularly in terms of the number of Alzheimer cases as a percentage of total dementia cases.
+The reason for this discrepancy between this analysis study and the previous paper is due to two things.
+While all of the codes used to define Alzheimer’s in the Smeeth paper are included in my “Probable Alzheimer’s” code-list (see Appendix \@ref(hold)), I also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
+Several of the codes in my “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
+
+Using the Smeeth code-list, I obtained a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
+
+<!--- TODO check that this is actually the case, that when you use the codelist from Smeeth, you get a different case-mix. Present it as a table. --->
+<!--- Will need to present the results for this! --->
+<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth. -->
+<!-- IN addition, this analysis used propensity s. IN addition, an analytical approach which appeared to adjust for key variables likely to be on the analytical pathway between   -->
+
+<!-- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+-->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
+
+(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
+
+```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
+
+<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
+
+<!-- However, this is not the case.
+Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
+Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
+However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
+-->
+
+<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
+Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
+-->
+
+<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
+-->
+
+<!--- This hasn't been done! Plus I do not think this is the case --->
+
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+<!-- &nbsp; -->
+
+<!-- ### Issues with large-scale EHR databases -->
+
+<!-- __Missclassification__ -->
+
+<!-- __Coding quality in the CPRD__ -->
+
+<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
+
+<!-- There is the possibility of ascertainment bias -  -->
+
+<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Enabling easy synthesis of this analysis
+
+In light of my own experiences in attempting to extract information for papers assessing preventative measures, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are described in detail in both.
+IN line with this, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
+<!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
+
+<!-- TODO Reporting guidelines do not always work, but help to guide accurate rep -->
+
+All code and summary statistics (i.e.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
+as comma separated values, or CSV, files) from the Github repository for this project.
+<!--- TODO Will need to cite this, and may need to archive on Zenodo.
+--->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Conclusions
@@
 This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It found use of lipid-regulating agents associated with a small reduction in probable or possible Alzheimer’s disease, and were associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
+It found that the use of lipid-regulating agents was associated with a small reduction in probable or possible Alzheimer’s disease, and with an increased risk of all-cause, vascular and other dementias.
+In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in this cohort.
 
@@
 However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-
-Given the observed increased association of statins in other
-
-While these
+<!-- TODO Finish This is supported by our findings for the negative and positive controls used.
+-->
 
 Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
+
+<!--- TODO In my most recent discussion with --->
+
+<!--- TODO Need better linkage with next chapter and triangulation --->
 

### 2021-05-11 front-and-back-matter/99-appendices.Rmd
End of day: -2625
End of day: -3892

@@
 
+### Amendments to protocol {#appendix-cprd-amendments}
+
 ### Code lists
+
+## Chapter \@ref(discussion-heading)
+
+### Catalogue of failures
+
+Short section detailing the things I tried to do but which did not work.
 
@@
 ```{r, echo = FALSE}
-robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = format(Sys.Date(),"%Y-%m-%d") )
+robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
 
@@
 
-date <- format(Sys.Date(),"%B %Y")
+date <- format(as.Date("2021-12-01"),"%B %Y")
 

### 2021-05-11 index.Rmd
End of day: -3892

@@
 source("R/helper.R")
+options(scipen=999)
 ```

### 2021-05-11 R/helper.R

@@ -29,7 +29,11 @@ gen_rmd_citation <- function(filename = "pkg-refs.bib") {
 
 # Place comma at thousand position
 # Taken from https://github.com/thomasbattram/thesis
-comma <- function(x){format(x, digits = 2, big.mark = ",")}
+comma <- function(x){
+  
+  format(x, digits = 2, big.mark = ",")
+  
+  }
 
 # Apply comma to all values in a table
 # Taken from https://github.com/thomasbattram/thesis
@@ -184,4 +188,15 @@ end_of_day <- function(words = NULL) {
 
 hold <- function(){
   "**PLACEHOLDER**"
+}
+
+todo <- function(fp){
+  
+  if (!hasArg(fp)) {
+    fp <- rstudioapi::getSourceEditorContext()$path
+    message("File: ",fp)
+  }
+  
+  todor::todor_file(fp)
+  
 }

### 2021-05-12 04-Chp-CPRD-Analysis.Rmd
End of day: -3964

@@
       number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 source("R/helper.R")
+options(scipen = 99)
 knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
@@
 
-<!-- Note: If protocol was written by Venexia, how do I reference this? -->
+<!-- NOTE If protocol was written by Venexia, how do I reference this? -->
 
@@
 We did however examine how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
-
-<!--- TODO this table doesn't exist anywhere as it has been cut off the bottom of Table 1 --->
 
@@
 
-Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of 11,091,437 <!--- TODO make this reactive!
+Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` <!--- TODO make this reactive!
 ---> patient years at risk.
@@
 The "Ezetimibe and statins" treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently.
+
+<!--- TODO Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? --->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:cprdSSA-caption) Participants who stopped, switched or added treatements by initial treatment type
+
+(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
+
+```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-<!--- TODO In my most recent discussion with --->
+<!--- TODO In my most recent discussion with supervisors, I discussed that a long term RCT isn't encouraged by the results --->
 

### 2021-05-12 R/Chp3-CPRD-Analysis.R

@@ -133,6 +133,43 @@ if(doc_type == "docx") {
     table
   
 }
+
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- cprdSSA-table
+
+cprdSSA_table <- table1[19:21,-3]
+
+if(doc_type == "docx") {
+  knitr::kable(cprdSSA_table, caption = "(ref:cprdSSA-caption)")
+} else{
+  knitr::kable(
+    cprdSSA_table,
+    format = "latex",
+    caption = "(ref:cprdSSA-caption)",
+    caption.short = "(ref:cprdSSA-scaption)",
+    booktabs = TRUE,
+    row.names = FALSE,
+    align = "lccccccccc"
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    column_spec(1, width = paste0(5,"em"), bold = TRUE) %>%
+    column_spec(2:9, width = paste0(4.225,"em")) %>%
+    row_spec(2:nrow(cprdSSA_table)-1, hline_after = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"), font_size = 7) %>%
+    kableExtra::footnote(
+      threeparttable = TRUE,
+      general_title = "Definitions:",
+      general = paste(
+        "Stopped - last prescription of the primary drug class followed by at least six months of observation with no further prescriptions;",
+        "Added - second drug class prescribed before the last prescription of the initial class;",
+        "Switched - second drug class being prescribed after the last prescription of the initial class."
+      )
+    )
+}
+
+
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- missing-data
 
@@ -170,7 +207,7 @@ choltext <- paste0(format(chol, big.mark = ","), " participants (", cholpercent,
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- characteristics
 
-characteristics <- read.csv(here::here("data","cprd","characteristics.csv"),header=TRUE)
+characteristics <- read.csv(here::here("data","cprd","characteristics.csv"), header=TRUE)
 
 # Median and IQR for follow-up
[…]

### 2021-05-20 03-Chp-Systematic-Review.Rmd
End of day: -3892
End of day: -4243

--- 2021-04-15 04-Chp-Systematic-Review.Rmd
@@
 * Larsson - 10.1136/bmj.j5375 [@larsson2017b]
+* Statins and the risk of dementia Jick
 
@@
 Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
+
+Following guidance for a dose response meta-analysis, we picked m
+
+<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->
 
@@
 
+<!--- Comment here on issues involved in extracting data --->
+
 ### Original contribution to research

### 2021-05-20 04-Chp-CPRD-Analysis.Rmd
End of day: -4243

@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
+<!-- TODO Add amendments to Appendix -->
+
+<!--------------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" is nested under the top-level of "Mental disorders".
-Broad topics are specified using the initial two bytes, while subsequent bytes are used to define specific conditions and context.
+Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
 
@@
 ```
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 
@@
 
-Using this system, lists of relevant codes for each of the index events, exposures and outcomes described in the sections below were created.
+Using this system, lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created.
 
@@
 
-We performed a prospective cohort study using data from the CPRD.
-Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-All events of interest were identified using predetermined code lists, which are available for inspection.
+This analysis was a prospective cohort study using data from the CPRD.
+It included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
+Records pre-dating the 1995 cutoff were included in the original CPRD extract but were excluded from the analysis as records are expected to be more complete and reliable after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort the 1st January 1996.
 
-<!-- NOTE If protocol was written by Venexia, how do I reference this? -->
+All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
+
+<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
 
@@
 
-<!--- TODO Include short bit on follow-up here, describing how and why it was defined --->
-
 We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1).
+When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure ).
 The diagnosis date of the outcome was determined by the first record of a relevant code.
 
-Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up ( <!--- TODO Get date here ---> )
+Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up (29th February 2016).
 
-As a positive control outcome, we included cornonary artery disease.
+As a positive outcome control, we included ishemic heart disease.
 Statins have a known effect on this outcome on the basis of randomised controlled trials.
-__[CITATION NEEDED]__ We also used a negative control of back pain to investigate the potential for residual confounding.
+__[CITATION NEEDED]__ We also used a negative outcome control of back pain to investigate the potential for residual confounding.
 
-<!--- TODO need more information on how the controls were modelled - e.g. using the same covariates as in the main model or not? --->
+<!-- TODO need more information on how the controls were modelled - e.g.
+using the same covariates as in the main model or not?
+I.e.
+should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis?
+-->
 
-<!--- TODO Will also need some more here on why there were chosen --->
+<!-- TODO Will also need some more here on why there were chosen -->
+
+The inclusion of control outcomes are a useful technique to assess the strength of uncontrolled confounding in an analysis.[@lipsitch2010] Despite observational analyses suggesting a link between statins and muscle pain, systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
+As such, muscular backpain was used as a negative control outcome in this analysis.
+
+<!----------------------------------------------------------------------------->
+(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure [X], outcome [Y], confounders (measured [C] and unmeasured [U]) and an ideal negative outcome [N]:
+
+(ref:negativeOutcome-scap) DAG of ideal negative outcome
+
+```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
+library(dagitty)
+library(ggdag)
+
+ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
+  dagitty::dagitty("dag {
+    U -> N
+    C -> N
+    X <- U -> Y
+    X <- C -> Y
+    X -> Y
+    bb =\"-2.368,-2.972,2.597,2.726\"
+    C [pos=\"-0.3,0\"]
+    N [pos=\"0.5,1\"]
+    U [pos=\"-0.15,1.5\"]
+    X [exposure,pos=\"0,-1\"]
+    Y [outcome,pos=\"0.5,-1\"]
+  }"
+) %>% ggdag_classic() +
+  theme_dag()
+
+,
+height = 3
+)
+
+knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))
+
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-<!--- TODO Need a lot more here - see other thesis for example of how covariates are described --->
+<!-- TODO Need a lot more here - see other thesis for example of how covariates are described -->
 
@@
 
-All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!--- TODO link to Zenodo here --->
+All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!-- TODO link to Zenodo here -->
 
@@
 
-<!--- TODO Need to complete paragraph below --->
+<!-- TODO Need to complete paragraph below -->
 
-<!--- Failing to adjust for missing data can. . .  --->
+<!-- Failing to adjust for missing data can. . .  -->
 
@@
 
-<!--- Review materials from multiple imputation course --->
+<!-- Review materials from multiple imputation course -->
 
@@
 
-<!--- TODO Finish paragraph from fragments below --->
+<!-- TODO Finish paragraph from fragments below -->
 
@@
 
-<!--- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! --->
+<!-- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! -->
 
 &nbsp;
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:cprd-dag-1-cap) __Directed acyclic graph showing assumed relationship between exposure and covariate:__
-
-(ref:cprd-dag-1-scap) Directed acyclic graph showing assumed relationship between exposure and covariate
-
-```{r cprd-dag-1, echo = FALSE, results="asis", fig.cap='(ref:cprd-dag-1-cap)', out.width='100%', fig.scap='(ref:cprd-dag-1-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
-```
-<!----------------------------------------------------------------------------->
-
 ### Immortal time bias and time-varying treatment indicators
@@
 
-<!--- TODO Discuss problems introduced by censoring on death --->
+<!-- TODO Discuss problems introduced by censoring on death -->
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:immortalTimeBias-cap) __shortcap:__
@@
 ```
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->  
+### Sensitivity analyses
 
-<!-- ### Sensitivity analyses -->
+<!-- TODO Described sensitivity analyses reported below here -->
 
-<!--- Described sensitivity analyses reported below here --->
+In addition to the primary analysis
 
-<!--- Make sure to include age as a sensitivity analysis, given that that is the purpose of the IPD analysis --->
+Statins are contra-indicated in pregnant patients, and so I preformed a sensitivity analysis in patients aged 55 and coded as female.
+
+We also prod
+
+<!-- Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
 
@@
 
-Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` <!--- TODO make this reactive!
----> patient years at risk.
+```{r attritionFigure, include = FALSE}
+```
+
+Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
 
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:cprdFlowchart-cap) __Attrition of CPRD participants as the eligibility criteria were applied:__
@@
 
-<!--- This figure needs to have comma seperated numbers in order to agree with text. --->
+<!-- This figure needs to have comma seperated numbers in order to agree with text. -->
 
 ```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
+knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition_test.png"))
 ```
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 
@@
 The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia; <!--- see Supplementary Figure 1 --->).
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia; <!-- see Supplementary Figure 1 -->).
 The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
@@
 \blandscape
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:cprdCharacteristics-caption) Patient characteristics by drug class
@@
 ```
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 \elandscape
 
-<!--- Table 1 is missing type 2 diabetes --->
+<!-- Table 1 is missing type 2 diabetes -->
 
@@
 
-<!--- TODO Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? --->
+<!-- TODO Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
+
+<!-- TODO Described the average length of time between patients being diagnosed with  -->
 
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:cprdSSA-caption) Participants who stopped, switched or added treatements by initial treatment type
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:cprdPrimary-cap) __Results from primary analyses of CPRD data:__
@@
 
-For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
 There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
@@
 
-When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(hold)).
-Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Figure \@ref(hold)).
+When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(hold)).
+Removing participants coded as female and aged 55 and under at index from our analysis had minimal effect on our estimates (Figure \@ref(hold)).
 
-<!--- TODO Actually run this analysis --->
+<!-- TODO Actually run this analysis -->
 
-<!--- TODO Sort out the mess that is below --->
+<!-- TODO Sort out the mess that is below -->
 
@@
 
-<!--- I actually think it would be better to include these results not in the appendix --->
+<!-- I actually think it would be better to include these results not in the appendix -->
 
-<!--- By multiple imputation versus complete case analysis --->
+<!-- By multiple imputation versus complete case analysis -->
 
@@
 
-<!--- By time varying confounder --->
+<!-- By time varying confounder -->
 
@@
 
-<!-- This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
+<!-- This means I can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
 -->
@@
 
-<!-- ### Controls  -->
-
-<!--- TODO I think this is maybe dealth with at the end of the "Exposures" section, but better to have it here? --->
-
-<!-- Backpain -->
-
-<!-- Coronary artery disease -->
-
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 &nbsp;
@@
 
-<!--- To what extent should I cross-reference with the other literature here? --->
+<!-- To what extent should I cross-reference with the other literature here? -->
 
-<!--- Maybe it would be better to signpost towards the triangulation chapter where the different evidence streams are combined --->
+<!-- Maybe it would be better to signpost towards the triangulation chapter where the different evidence streams are combined -->
 
@@
 
-<!--- TODO Why are fibrates different? --->
+<!-- TODO Why are fibrates different? -->
 
-<!--- TODO Be explicit here about the possibility of publication bias in the vascular dementia results --->
+<!-- TODO Be explicit here about the possibility of publication bias in the vascular dementia results -->
+
+<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
+
+<!-- TODO Discuss impact of sensitivity analysis results, particularly -->
+
+The effect estimate seems to increase as the casemix ratio of Alzheimers:vascular dementia decreases.
+
+The fact that a similar increased risk of IHD is observed in those taking statins likely means that those who end up taking statins (or another lipid regulating agent) are inherently different from those who do not in some way that this analysis does not account for.
+
+Likely confounding by indication
+
+Confounding by indication occurs when an unobserved variable both prompts exposure to the intervention and modifies a participants risk of the outcome.
+In this case, this confounder would prompt prescription of statins (or another lipid regultating agent) but also represent a vascular risk factor that contributes to the development of the control outcome (ischemic heart disease) and also dementia outcomes with an increasing casemix of vascular origin (e.g.
+the vascular dementia and other dementia endpoints)
+
+In causal inference language, statins and dementia are said to be d-connected (see Figure \@ref(fig:indicationBias)), as there is an open "backdoor" path between them, via the
+
+Alternatively, rather than a single variable, it is likely that those that take statins are different in a myriad of ways, each of which contributes a
+
+A common example of this bias
+
+While this analysis has attempted to adjust for several baseline variables that my prompt
+
+Possible further analysis techniques would be the use of
+
+<!----------------------------------------------------------------------------->
+(ref:indicationBias-cap) __Confounding by indication directed acyclic graph:__
+
+(ref:indicationBias-scap) Confounding by indication directed acyclic graph
+
+```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
+
+ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
+dagitty::dagitty("dag {
+  Statin [exposure,pos=\"0.000,0.000\"]
+  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
+  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
+  \"Uncontrolled variable\" -> Statin
+  \"Uncontrolled variable\" -> \"Vascular outcomes\"
+}") %>% ggdag_classic(size = 6) +
+  xlim(-0.5,3) +
+  geom_text(data = data.frame(x = 0.316392393234329,
+                              y = 0.537705383514239,
+                              label = "Prompts"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "red",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_text(data = data.frame(x = 1.65891420807966,
+                              y = 0.537705383514239,
+                              label = "Causes"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "red",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_curve(data = data.frame(x = 0.220612676359188,
+                               y = -0.000788829298738025,
+                               xend = 1.45,
+                               yend = -0.00157828084913909),
+             mapping = aes(x = x,
+                           y = y,
+                           xend = xend,
+                           yend = yend),
+             linetype = "dashed",
+             angle = 0L,
+             size = 0.6,
+             colour = "black",
+             curvature = 0,
+             arrow = structure(list(angle = 0,
+                                    length = structure(0,
+                                                       class = "unit",
+                                                       valid.unit = 2L,
+                                                       unit = "inches"),
+                                    ends = 2L,
+                                    type = 2L),
+                               class = "arrow"),
+             inherit.aes = FALSE,
+             show.legend = FALSE) +
+
+  theme_dag(),
+width = 8,
+height = 3)
+
+knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Similar suprising findings for the effect of statins on
+
+In essence, this
 
@@
 
-Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. <!--- TODO citation needed --->
+Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. <!-- TODO citation needed -->
 
@@
 
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
+To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so I cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 &nbsp;
@@
 
-<!--- TODO I actually don't think Strengths and Limitations are the best way to describe this! --->
+<!-- TODO I actually don't think Strengths and Limitations are the best way to describe this! -->
 
 <!-- TODO A major strength of this analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
-In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
+In addition, I followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
 -->
@@
 However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that this findings may be biased by residual confounding.
-Important confounding variables for which we have not adjusted could include genetic factors.
+Important confounding variables for which I have not adjusted could include genetic factors.
 A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of unspecified Alzheimer’s and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020] This finding, combined with the potential for differential misclassification between Alzheimer’s disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.
 
-<!--- TODO A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
+<!-- TODO A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
 
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 &nbsp;
@@
 
-<!--- TODO I will definitely have to mention this earlier in the chapter, as it is bad for to try and spring methods on people --->
+<!-- TODO I will definitely have to mention this earlier in the chapter, as it is bad for to try and spring methods on people -->
 
@@
 
-<!--- TODO check that this is actually the case, that when you use the codelist from Smeeth, you get a different case-mix. Present it as a table. --->
-<!--- Will need to present the results for this! --->
+<!-- TODO check that this is actually the case, that when you use the codelist from Smeeth, you get a different case-mix. Present it as a table. -->
+<!-- Will need to present the results for this! -->
 <!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth. -->
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 (ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
@@
 
-<!--- This hasn't been done! Plus I do not think this is the case --->
+<!-- This hasn't been done! Plus I do not think this is the case -->
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 <!-- &nbsp; -->
@@
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 &nbsp;
 
-### Enabling easy synthesis of this analysis
+### Enabling easy synthesis of this analysis {#cprd-data-avail}
 
 In light of my own experiences in attempting to extract information for papers assessing preventative measures, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are described in detail in both.
-IN line with this, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
+
+All code, Read codelist and summary statistics (i.e.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
+as comma separated values, or CSV, files) from the archived repository for this project.
+<!-- TODO Will need to cite this, and may need to archive on Zenodo.
+-->
+
+The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
+Interested researchers can apply directly to the  In this scenario, sharing the code represents a <!-- TODO CITATION NEEDED: Goldarce BMJ opinion -->
+
+As such, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
+<!-- Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
 
@@
 
-All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the Github repository for this project.
-<!--- TODO Will need to cite this, and may need to archive on Zenodo.
---->
-
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
 &nbsp;
@@
 <!-- TODO Finish This is supported by our findings for the negative and positive controls used.
--->
+A slight increas-->
 
@@
 
-<!--- TODO In my most recent discussion with supervisors, I discussed that a long term RCT isn't encouraged by the results --->
+<!-- TODO In my most recent discussion with supervisors, I discussed that a long term RCT isn't encouraged by the results -->
 
-<!--- TODO Need better linkage with next chapter and triangulation --->
+<!-- TODO Need better linkage with next chapter and triangulation -->
 

### 2021-05-21 04-Chp-CPRD-Analysis.Rmd
End of day: -3799

@@
 
-As a positive outcome control, we included ishemic heart disease.
-Statins have a known effect on this outcome on the basis of randomised controlled trials.
-__[CITATION NEEDED]__ We also used a negative outcome control of back pain to investigate the potential for residual confounding.
+In addition to our primary outcomes of interest, we created two additional control outcomes.
+The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding.[@lipsitch2010] Negative outcomes are those without a likely causal pathway between the exposure and outcome (see Figure \@ref()).
+Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
+Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, our confidence in the result for the outcome of interest is increased.
 
-<!-- TODO need more information on how the controls were modelled - e.g.
-using the same covariates as in the main model or not?
-I.e.
-should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis?
--->
+Muscular backpain was used as a negative control outcome in this analysis.
+Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy), systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
 
-<!-- TODO Will also need some more here on why there were chosen -->
+Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment on the risk of this condition.[@collins2016a]
 
-The inclusion of control outcomes are a useful technique to assess the strength of uncontrolled confounding in an analysis.[@lipsitch2010] Despite observational analyses suggesting a link between statins and muscle pain, systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
-As such, muscular backpain was used as a negative control outcome in this analysis.
+<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
 
 <!----------------------------------------------------------------------------->
-(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure [X], outcome [Y], confounders (measured [C] and unmeasured [U]) and an ideal negative outcome [N]:
+(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
+Note the absence of an arrow between $X$ and $N$.
+In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders (assuming $C$ has been adjusted for).
 
@@
 
-<!-- TODO Need a lot more here - see other thesis for example of how covariates are described -->
+The analysis was adjusted for a range of baseline covariates.
+Demographic covariates included age and gender.
+Age was calculated at date of entry into the cohort.
+Socioeconomic status was proxied using the Index of Multiple Deprivation, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
+Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
 
-The analysis was adjusted for a range of baseline covariates including sex,grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+Body mass index (calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
+A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
+To assess healthcare utilisation, I calculated the average annual number of consultations between the beginning of a patients data and their entry into the cohort
 
-All covariates were determined at index and definitions for each can be found in the archived data repository reflecting this study <!-- TODO link to Zenodo here -->
+Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
+The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new]
 
-We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
-Additional analyses stratified by outcome and drug class were also performed.
+Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
 
@@
 
-<!-- TODO Need to complete paragraph below -->
+<!-- IDEA Add more detail here on the missing data approach -->
 
@@
 categorical smoking status).
-This approach was necessary, as absence of a code for other conditions (e.g.
-statin use or dementia) is used to define a negative value of binary variables indicating the presence or absence of the condition, and so had no missing data at the point of imputation.[@wells2013strategies]
+This approach was necessary, as absence of a code for other treatments or conditions (e.g.
+statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
 
 To investigate the impact of multiple imputation versus a complete case analysis,[@pigott2001review] where participants missing any covariate are dropped from the dataset, we preformed and compared the results of both approaches.[@hughes2019a]
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Time axis
-
-<!-- TODO Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time or participants age as the time scale of interest.
-A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
-
-In order to compare and contrast between the two approaches, we ran two simple model, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
-
-<!-- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! -->
 
@@
 To estimate the effect of statins on dementia outcomes, we used a Cox proportional hazards model, defined as:
-
-<!-- TODO Expand on post estimation analyses, which showed that nothing except age had an effect. -->
 
@@
 
+<!-- TODO Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
+
+### Time axis
+
+<!-- TODO Finish paragraph from fragments below -->
+
+<!-- In Cox models, there is the option to -->
+
+<!-- Age vs time-since entry -->
+
+<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
+
+As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship.
+The main analyses presented all used age as the time axis.
+
+In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
+
+<!-- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! -->
+
+&nbsp;
+<!--------------------------------------------------------------------------->
+
 ### Immortal time bias and time-varying treatment indicators
@@
 <!--------------------------------------------------------------------------->
-(ref:immortalTimeBias-cap) __shortcap:__
+(ref:immortalTimeBias-cap) Diagram illustrating immortal time bias
 
@@
 <!--------------------------------------------------------------------------->
+
 ### Sensitivity analyses
 
+To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
+
+<!-- TODO Re-run this analysis -->
+
+Sensitivity cohorts were also created, stratifying first by year of entry into the cohort and second by remiving participants who may have been pregnant (as statins are contraindicated in pregnancy).
+
+Additional analyses stratified by outcome and drug class were also performed.
+
 <!-- TODO Described sensitivity analyses reported below here -->
-
-In addition to the primary analysis
-
-Statins are contra-indicated in pregnant patients, and so I preformed a sensitivity analysis in patients aged 55 and coded as female.
-
-We also prod
 
@@
 &nbsp;
+
+Exploring the results when using a different codelist
 
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) __Attrition of CPRD participants as the eligibility criteria were applied:__
+(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied
 
@@
 The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia; <!-- see Supplementary Figure 1 -->).
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia).
 The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
@@
 
-<!-- Table 1 is missing type 2 diabetes -->
+<!-- FIX Table 1 is missing type 2 diabetes -->
 
@@
 
-<!-- TODO Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
+<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
 
@@
 Full covariate information was available for `r missingtext`.
-Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`, and baseline total cholesterol was missing for `r choltext`.
+Six key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`
 
@@
 
+```{r p1Figure, include = FALSE}
+```
+
 ```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
@@
 &nbsp;
+
+<!-- TODO Cross-check with the decision flowchart to ensure that  -->
+
+<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
 
@@
 
+__Choice of time axis__
+
+__Complete case versus imputed data__
+
+__Unadjusted versus full adjusted models__
+
+<!-- TODO Expand on post estimation analyses, which showed that nothing except age had an effect. -->
+
+__Sensitivity cohorts__
+
 When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(hold)).
@@
 
+__By statin type__
+
+As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lip
+
+__Control outcomes__
+
+Using the fully adjusted model, the for the backpain negative control outcome was `r hold()` and the ischemic heart disease was `r hold()`
+
 <!-- TODO Actually run this analysis -->
 
-<!-- TODO Sort out the mess that is below -->
+<!-- TODO Sort out the mess that is **below** -->
 
@@
 <!-- I actually think it would be better to include these results not in the appendix -->
-
-<!-- By multiple imputation versus complete case analysis -->
-
-<!-- By pregnancy -->
-
-<!-- By age-at-entry -->
-
-<!-- By statin type (lipo vs hydrophilic) -->
-
-<!-- By time varying confounder -->
 
@@
 
-<!-- To what extent should I cross-reference with the other literature here? -->
+<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
 
@@
 
-Lipid-regulating agents had no effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+Lipid-regulating agents had a small effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
 The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
@@
 <!-- TODO Discuss impact of sensitivity analysis results, particularly -->
+
+<!-- TODO Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
+However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
 
@@
 <!----------------------------------------------------------------------------->
-(ref:indicationBias-cap) __Confounding by indication directed acyclic graph:__
+(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication
 
-(ref:indicationBias-scap) Confounding by indication directed acyclic graph
+(ref:indicationBias-scap) Confounding by indication causal diagram
 
@@
             vjust = 0.5,
-            colour = "red",
+            colour = "black",
             family = "sans",
@@
 
-### Replicating other analytical strategies
+### Use of alternative code lists
+
+WHen using the Smeeth et al codelists were `r hold()` for Alzheimer's disease and `r hold()` for
+
+However, direct comparison between the results is difficul
 
@@
 The reason for this discrepancy between this analysis study and the previous paper is due to two things.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in my “Probable Alzheimer’s” code-list (see Appendix \@ref(hold)), I also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
+While all of the codes used to define Alzheimer’s in the Smeeth paper are included in my “Probable Alzheimer’s” code-list, I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
 Several of the codes in my “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
@@
 <!-- TODO check that this is actually the case, that when you use the codelist from Smeeth, you get a different case-mix. Present it as a table. -->
+
 <!-- Will need to present the results for this! -->
+
 <!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth. -->
+
 <!-- IN addition, this analysis used propensity s. IN addition, an analytical approach which appeared to adjust for key variables likely to be on the analytical pathway between   -->
@@
 
-<!--------------------------------------------------------------------------->
-(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
+<!----------------------------------------------------------------------------->
+(ref:smeethComparison-cap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
 
-(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
+(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
 
-```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
+```{r sankeydiagram, include=FALSE}
 ```
-<!--------------------------------------------------------------------------->
+
+```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-<!-- TODO Finish This is supported by our findings for the negative and positive controls used.
-A slight increas-->
+However, there is a strong potential for unmeasured confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+This is supported by our findings for the negative and positive control outcomes used.
+Future research using large scale electronic health records should aim to address these potential biases, potentially using a analytical design that more closely emulates a trial.[@danaei2013b]
 
-Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
+The unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted by the previous chapter (see Section \@ref(sys-rev-pub-bias)) .
+It is possible that previous research identified a similar effect and via a publication bias mechanism, these results did not make it into the evidence base.
 
-<!-- TODO In my most recent discussion with supervisors, I discussed that a long term RCT isn't encouraged by the results -->
+Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
 
-<!-- TODO Need better linkage with next chapter and triangulation -->
+In the following Chapter, the dataset described here is incorporated along with several other datasets
 

### 2021-05-28 04-Chp-CPRD-Analysis.Rmd
Submission of Chapter 4 to supervisors

@@
 
-# Primary analysis of lipid regulating agents and dementia {#cprd-analysis-heading}
+# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}
 
@@
 
+<!-- TODO Check lipid-regulating vs lipid regulating -->
+
+<!-- TODO Check all fig/table cross-references evaluate -->
+
 ## Lay summary
-Large-scale electronic health record (EHR) databases are created through the routine collection of information from patients.
-Under this system, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
-These databases have substantial advantages for research studies, including the number of people they contain and the length of time for which participants are followed.
-This is particulary important when studying diseases such as dementia, which may begin to develop long before symptoms are seen.
 
-This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across England.
-Using this data, I examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
+Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
+Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
+These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
+This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
 
-Lipid regulating agents were found to have no or minimal effect on Alzheimer's disease, but increased the risk of vascular dementia.
-This increase is very likely to be due to the presence of bias in the analysis despite best efforts to address it.
-However, this analysis still provides important sources of information which will be used in later chapters.
+This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
+Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
+
+No evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
+In contrast, I found an increased risk of vascular and other (i.e.
+non-Alzheimer's) dementia with lipid regulating agent use.
+
+This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
+This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
+However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
 
@@
 
-This chapter details an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent use and dementia outcomes.
-The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
+In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
 
-In the first instance, it explicitly examines vascular dementia as an outcome.
-This is particular important to the thesis as a whole, as the systematic review identified an absence of information on the effect of lipids on dementia risk.
+The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
 
-In the second instance, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia.
-This approach was taken to provide a further distinct evidence source for the triangulation exercise presented in Chapter \@ref(discussion-heading).
+Firstly, it explicitly examines vascular dementia as an outcome.
+The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
+As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
+
+Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
+Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
+This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
 
@@
 
+<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
+
 <!-- TODO Add amendments to Appendix -->
@@
 
-Previously know as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collected primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD collects data use a predefined coding system known as Read codes.[@booth1994] All clinical events can be identified by a specific code.
+To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
 The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
 Eu...
-- Mental and behavioural disorders), while subsequent digits provide addition information on the specific condition diagnosed (e.g.
+- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
 Eu001 - Dementia in Alzheimer's disease with late onset).
@@
 <!--------------------------------------------------------------------------->
-(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" is nested under the top-level of "Mental disorders".
+(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
 Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
@@
 
-Using this system, lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created.
+Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
 
@@
 
-This analysis was a prospective cohort study using data from the CPRD.
-It included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were included in the original CPRD extract but were excluded from the analysis as records are expected to be more complete and reliable after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort the 1st January 1996.
+This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
+Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
+However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
+
+Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
+These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
 
@@
 
-<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
-
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
-
-These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-This approach was employed in an attempt to reduce confounding by indication that we would expect to observe in the full cohort, because individuals not prescribed lipid-regulating agents likely be less healthy across a range of variables than those prescribed lipid-regulating agents, leading to a biased association been lipid-regulating agent use and dementia.
-Conditioning entry into the study into the study on being either “at-risk” or already diagnosed with hypercholesterolemia attempts to mitigate this bias.
-
 The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+had less than one full day of follow-up).
 
@@
 
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF)[@wishart2017], namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
+We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
 
 A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
+We did however examine how often the initial drug class altered according to one of three criteria:
+
+- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
+- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
+- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.
 
@@
 
-### Outcomes
+### Outcomes {#cprd-outcomes}
 
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure ).
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
+When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
 The diagnosis date of the outcome was determined by the first record of a relevant code.
 
-Participants were followed up, and were censored at the earliest of date of diagnosis, death, date of transfer out of the study cohort or end of follow-up (29th February 2016).
+<!----------------------------------------------------------------------------->
+(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
+Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
 
-In addition to our primary outcomes of interest, we created two additional control outcomes.
-The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding.[@lipsitch2010] Negative outcomes are those without a likely causal pathway between the exposure and outcome (see Figure \@ref()).
+(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes
+
+```{r decisionTree, include = FALSE}
+```
+
+```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
+
+&nbsp;
+
+### Covariates
+
+A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
+
+Demographic covariates adjusted for included age and gender.
+Age was calculated at date of entry into the cohort.
+Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
+To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
+Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
+
+Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
+A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
+To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
+
+Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
+The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
+
+Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+
+### Missing data
+
+Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
+
+<!-- IDEA Add more detail here on the missing data approach -->
+
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
+
+Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
+BMI), or where a code existed for the absence of the condition (e.g.
+categorical smoking status).
+This approach was necessary, as absence of a code for other treatments or conditions (e.g.
+statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
+
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019a] to investigate the impact of multiple imputation on the results.
+
+&nbsp;
+<!--------------------------------------------------------------------------->
+
+### Estimation methods
+
+A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
+
+$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
+
+where:
+
+* $t$ is the survival time;
+* $h(t)$ is the hazard function; and
+* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
+* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
+
+As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
+
+A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
+Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
+This is discussed in detail in the following section.
+
+<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
+
+<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}
+
+Immortal time bias covers two distinct but related types of bias.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010a] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
+
+The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
+It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
+This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
+
+This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
+To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
+
+Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
+Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
+they enter the cohort and move into the exposed group on the same day).
+
+<!--------------------------------------------------------------------------->
+(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
+
+(ref:immortalTimeBias-scap) shortcap
+
+```{r, immortalTime, include = FALSE}
+```
+
+```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
+```
+<!--------------------------------------------------------------------------->
+
+### Time axis
+
+<!-- IDEA Finish paragraph from fragments below -->
+
+<!-- In Cox models, there is the option to -->
+
+<!-- Age vs time-since entry -->
+
+<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
+
+As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship.
+The main analyses presented all used age as the time axis.
+
+<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
+-->
+
+&nbsp;
+<!--------------------------------------------------------------------------->
+
+### Sensitivity analyses
+
+The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
+To assess the robustness of the results, a number of sensitivity analyses were performed.
+These are described in the following sections.
+
+#### Control outcomes
+
+In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
+The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
+Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
+
 Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
-Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, our confidence in the result for the outcome of interest is increased.
+Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
 
-Muscular backpain was used as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy), systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
+Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
+Muscular backpain was chosen as a negative control outcome in this analysis.
+Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
+As such, if no evidence of an effect of statins on backpain is found in the analysis, then confidence in the results for the dementia outcomes is increased.
 
-Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment on the risk of this condition.[@collins2016a]
+Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
 
@@
 (ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
-Note the absence of an arrow between $X$ and $N$.
-In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders (assuming $C$ has been adjusted for).
+Note the absence of any arrow between $X$ and $N$.
+In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).
 
@@
 
-&nbsp;
+#### Impact of additional covariates
 
-### Covariates
-
-A range of additional variables were included in the analysis, intended to address differential distributions of potential confounding variables between those who had were prescribed an LRA and those who were not.
-
-The analysis was adjusted for a range of baseline covariates.
-Demographic covariates included age and gender.
-Age was calculated at date of entry into the cohort.
-Socioeconomic status was proxied using the Index of Multiple Deprivation, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
-Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
-
-Body mass index (calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
-A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
-To assess healthcare utilisation, I calculated the average annual number of consultations between the beginning of a patients data and their entry into the cohort
-
-Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
-The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new]
-
-Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
+To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
 
@@
 
-<!--------------------------------------------------------------------------->
+#### Sensitivity cohorts
 
-### Missing data
+Two sensitivity cohorts were also created.
+The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
+The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
 
-Given that they contain an administrative data, collected for the purposes of patient management and care rather than academic research, missing data are a recognised issue in electronic health records databases.[@wells2013strategies]
-
-<!-- IDEA Add more detail here on the missing data approach -->
-
-<!-- Failing to adjust for missing data can. . .  -->
-
-<!-- Complete case analyses are limited by . . . -->
-
-<!-- Review materials from multiple imputation course -->
-
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed dataset.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
-
-Missing data was only considered an issue for variables where a numerical test result was expected, (e.g.
-BMI) or where a code existed for the absence of the condition (e.g.
-categorical smoking status).
-This approach was necessary, as absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
-
-To investigate the impact of multiple imputation versus a complete case analysis,[@pigott2001review] where participants missing any covariate are dropped from the dataset, we preformed and compared the results of both approaches.[@hughes2019a]
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Estimation methods
-
-To estimate the effect of statins on dementia outcomes, we used a Cox proportional hazards model, defined as:
-
-$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
-
-where:
-
-* $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
-* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
-
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
-<!-- TODO __Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__ -->
-
-<!-- Hazard ratios are -->
-
-<!-- Test for non-proportionality are therefore very important, as models which fail -->
-
-<!-- Problems with testing for non-proportional hazards when  -->
-
-<!-- TODO Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
-
-### Time axis
-
-<!-- TODO Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship.
-The main analyses presented all used age as the time axis.
-
-In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
-
-<!-- TODO Need to actually run these models, but the important things is that they can be run on the unimputed data! -->
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Immortal time bias and time-varying treatment indicators
-
-<!-- Potential biases included time varying confounding, selection bias due to censoring on death and  -->
-<!-- We use a Cox proportional hazards model with a time-varying treatment indicator. -->
-
-Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to exposure is excluded, leading to the exposed and control groups being followed up from different time points.[@levesque2010a] In this case, events that occur prior to the exposure event are missing from the analysis.
-
-The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
-This second presentation appears to be common in the existing literature, as many of the studies included in the review in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(#risk-of-bias-subheading))
-
-To address the potential for immortal time bias in our analysis, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-<!-- TODO Discuss problems introduced by censoring on death -->
-
-<!--------------------------------------------------------------------------->
-(ref:immortalTimeBias-cap) Diagram illustrating immortal time bias
-
-(ref:immortalTimeBias-scap) shortcap
-
-```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
-```
-<!--------------------------------------------------------------------------->
-
-### Sensitivity analyses
-
-To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
-
-<!-- TODO Re-run this analysis -->
-
-Sensitivity cohorts were also created, stratifying first by year of entry into the cohort and second by remiving participants who may have been pregnant (as statins are contraindicated in pregnancy).
-
-Additional analyses stratified by outcome and drug class were also performed.
-
-<!-- TODO Described sensitivity analyses reported below here -->
-
-<!-- Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
+<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
 
@@
 
-Exploring the results when using a different codelist
+#### Statin properties
+
+As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).
+
+To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
+
+&nbsp;
+
+#### Impact of dementia code lists
+
+As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
+
+This previous study used a propensity matching approach to estimate the effect of statins on a range of outcomes, and a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but no evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+
+The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
+
+&nbsp;
 
@@
 
-Of the `r comma(attrition[1,1])` participants included in our extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
+Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
 
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied
+(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
 
@@
 
-The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
+The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
 During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia).
-The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
 
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdCharacteristics-caption) Patient characteristics by drug class
+(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
 
@@
 
-<!-- FIX Table 1 is missing type 2 diabetes -->
-
 A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
-The "Ezetimibe and statins" treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently.
+I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
+Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
 
@@
 
-<!-- TODO Described the average length of time between patients being diagnosed with  -->
+<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
 
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdSSA-caption) Participants who stopped, switched or added treatements by initial treatment type
+(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
 
@@
 &nbsp;
+
+The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
 
@@
 Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`
+Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`
 
@@
 
-All results described below are from the fully adjusted model.
-The results of the age-only model are presented in Supplementary Figure 3, and demonstrate that adjustment for additional covariates had a minimal effect.
+The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
+
+For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
+
+&nbsp;
 
 <!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) __Results from primary analyses of CPRD data:__
+(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
 
@@
 
-<!-- TODO Cross-check with the decision flowchart to ensure that  -->
-
 <!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
@@
 
-As shown in Figure \@ref(fig:cprdPrimary), the results of the analysis do not support an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+No evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 
-__Choice of time axis__
+The results of the series of sensitivity analyses performed are described in the following sections.
 
-__Complete case versus imputed data__
+#### Complete case versus imputed data
 
-__Unadjusted versus full adjusted models__
+In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
+It should be noted that due to the large amount of missing data (e.g.
+`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
+In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009b]
 
-<!-- TODO Expand on post estimation analyses, which showed that nothing except age had an effect. -->
+&nbsp;
 
-__Sensitivity cohorts__
+<!----------------------------------------------------------------------------->
+(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
 
-When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(hold)).
-Removing participants coded as female and aged 55 and under at index from our analysis had minimal effect on our estimates (Figure \@ref(hold)).
+(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
 
-__By statin type__
+```{r completeCase, include= FALSE}
+```
 
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lip
+```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_complete_case.jpeg"))
+```
+<!----------------------------------------------------------------------------->
 
-__Control outcomes__
+&nbsp;
 
-Using the fully adjusted model, the for the backpain negative control outcome was `r hold()` and the ischemic heart disease was `r hold()`
+#### Control outcomes
 
-<!-- TODO Actually run this analysis -->
+```{r controlOutcomes, echo = FALSE, message = FALSE}
+```
 
-<!-- TODO Sort out the mess that is **below** -->
+Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
+The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
 
-<!-- For our negative control, there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (r sens_bp_text), suggesting there may be some residual confounding (Appendix XXX).
--->
+For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
+However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
 
-<!-- I actually think it would be better to include these results not in the appendix -->
+&nbsp;
 
-<!-- ### Estimating the value of the time-varying confounders -->
+<!----------------------------------------------------------------------------->
+(ref:controlOutcomeFig-cap) Results of control outcome analysis.
 
-<!-- Mean time from index event to first prescription of statins was 2.4 years.
-This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
--->
+(ref:controlOutcomeFig-scap) Results of control outcome analysis
 
-<!-- Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
-This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
-For example: -->
+```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_control_outcomes.jpeg"))
+```
+<!----------------------------------------------------------------------------->
 
-<!--     _No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_ -->
+&nbsp;
 
-<!-- In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_. -->
+#### Impact of additional covariates
 
-<!-- In practice, this means that the value of the prognostic factor should be regularly captured -->
+The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
 
-<!-- However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
--->
+These models were used to estimate the impact of adjustment for additional covariates.
+Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
 
-<!-- This means I can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
--->
+Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
+In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
 
-<!-- i.e.   -->
-<!-- Timepoint 12345678   -->
-<!-- CVD       00001111   -->
-<!-- Treatment 00000111   -->
+&nbsp;
 
-<!-- Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point. -->
+<!----------------------------------------------------------------------------->
+(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
 
-<!-- Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.  -->
+(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
 
-<!--------------------------------------------------------------------------->
+```{r unadjustedComparison, include=FALSE}
+```
+
+```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_unadjusted.jpeg"))
+```
+<!----------------------------------------------------------------------------->
+
+#### Sensitivity cohorts: Entry year
+
+When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
+
+(ref:diagnosisTypeFig-scap) Sensitivty analus
+
+```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/fp_cohort_entry.jpeg"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
+While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
+
+(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
+
+```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Sensitivity cohorts: Pregnancy
+
+In the second sensitivity cohort, removing participants coded as female and aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
+
+(ref:pregnancyFig-scap) Comparison of pregnancy analysis
+
+```{r pregnancy, include = FALSE}
+```
+
+```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_pregnancy.jpeg"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Statin properties
+
+In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
+Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
+
+(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
+
+```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
+Additionally, in the AD outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
+
+(ref:statinTypeFig-scap) Analysis stratified by statin properties
+
+```{r statinType, include = FALSE}
+
+```
+
+```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","fp_sta_type.jpeg"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Comparing codelists
+
+```{r smeethText, include = FALSE}
+```
+
+When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
+
+However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
+While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
+Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
+The joining lines showing the overlap between the categories in the two analyses.
+
+(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
+
+```{r sankeydiagram, include=FALSE}
+```
+
+```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
+```
+<!----------------------------------------------------------------------------->
+
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
+
 &nbsp;
@@
 
-<!-- Maybe it would be better to signpost towards the triangulation chapter where the different evidence streams are combined -->
+### Summary of findings
 
-### Main findings
-
-Lipid-regulating agents had a small effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+Lipid-regulating agents showed no evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
 The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
@@
 
-<!-- TODO Why are fibrates different? -->
+The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
+When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
 
-<!-- TODO Be explicit here about the possibility of publication bias in the vascular dementia results -->
+<!-- QUESTION Why are fibrates different? -->
 
@@
 
-<!-- TODO Discuss impact of sensitivity analysis results, particularly -->
-
-<!-- TODO Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
+<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
 However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
 
-The effect estimate seems to increase as the casemix ratio of Alzheimers:vascular dementia decreases.
+&nbsp;
 
-The fact that a similar increased risk of IHD is observed in those taking statins likely means that those who end up taking statins (or another lipid regulating agent) are inherently different from those who do not in some way that this analysis does not account for.
+<!--------------------------------------------------------------------------->
 
-Likely confounding by indication
+### Interpretation of results
 
-Confounding by indication occurs when an unobserved variable both prompts exposure to the intervention and modifies a participants risk of the outcome.
-In this case, this confounder would prompt prescription of statins (or another lipid regultating agent) but also represent a vascular risk factor that contributes to the development of the control outcome (ischemic heart disease) and also dementia outcomes with an increasing casemix of vascular origin (e.g.
-the vascular dementia and other dementia endpoints)
+This section will expand on a potential explanation for the observed results detailed above.
+However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
+For a comparison of the result presented above with those from the systematic review (Chapter \@ref(hold)) and the individual patient data analysis (Chapter \@ref(hold)), see Section \@ref(hold).
 
-In causal inference language, statins and dementia are said to be d-connected (see Figure \@ref(fig:indicationBias)), as there is an open "backdoor" path between them, via the
-
-Alternatively, rather than a single variable, it is likely that those that take statins are different in a myriad of ways, each of which contributes a
-
-A common example of this bias
-
-While this analysis has attempted to adjust for several baseline variables that my prompt
-
-Possible further analysis techniques would be the use of
+A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
+While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
+In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
 
 <!----------------------------------------------------------------------------->
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication
+(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
 
@@
 
-Similar suprising findings for the effect of statins on
+In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
 
-In essence, this
+Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
+The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
+This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
 
-&nbsp;
+A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
 
-<!--------------------------------------------------------------------------->
+Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
+I also adjusted for several additional potential baseline variables.
+However, important confounding variables for which I have not adjusted could include genetic factors.
+A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
 
-### Comparison to other literature
+On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
+It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
 
-Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.
+<!-- IDEA talk about time-varying confounding here -->
 
-Several previous studies have demonstrated that statins are the overwhelmingly favoured methods of cholesterol control. <!-- TODO citation needed -->
-
-&nbsp;
-
-__Statins and all-cause dementia__
-
-A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016a] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
-A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]
-
-These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia.
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to a artifical protective effect of statins on all-cause dementia
-
-&nbsp;
-
-__Statins and Alzheimer's disease__
-
-Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80), though the reduction was more extreme than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings, but could not rule out no effect (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
-
-An additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis.[@chu2018]
-
-&nbsp;
-
-__Statins and non-Alzheimer's disease dementia__
-
-Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
-A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis.
-An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
-
-&nbsp;
-
-__Other drug classes__
-
-Apart from statins, few studies examining a lipid-regulating agent have been reported.
-One of the few classes for which data was available were fibrates, which were shown to have no effect on all-cause dementia, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
-
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so I cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
+In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
 
@@
 
-<!-- TODO I actually don't think Strengths and Limitations are the best way to describe this! -->
-
-<!-- TODO A major strength of this analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
-In addition, I followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
--->
-
-There are two primary strenghts to this analysis compared to others available in the literature:
-
-* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest studies of this research question.
-* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
+The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
+Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
+Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
+This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
 
 However, the findings of this analysis are subject to several limitations.
-There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
+There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
+As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
 
-This analysis may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
-We attempted to address this by limiting inclusion to those either prescribed or “at risk” of being prescribed, which was determined using an elevated test result.
-We also adjusted for several additional potential confounding variables.
-However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that this findings may be biased by residual confounding.
-Important confounding variables for which I have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of unspecified Alzheimer’s and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020] This finding, combined with the potential for differential misclassification between Alzheimer’s disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.
+Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
+This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
 
-<!-- TODO A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
+<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
 
-Finally, there is also the potential for reverse causation in this analysis.
+<!-- IDEA there is also the potential for reverse causation in this analysis.
 Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Use of alternative code lists
-
-WHen using the Smeeth et al codelists were `r hold()` for Alzheimer's disease and `r hold()` for
-
-However, direct comparison between the results is difficul
-
-<!-- TODO I will definitely have to mention this earlier in the chapter, as it is bad for to try and spring methods on people -->
-
-Misclassification of outcomes, as discussed in the section above, is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This is a particular challenge in comparing research across different time-periods and coding systems.
-Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
-
-As part of my exploration of the unexpected results, I attempted to replicate the analyses of another research group (Smeeth et al.)__[CITATION NEEDED]__ that employed a different approach to explore the effect of statin use on dementia outcomes.
-
-<!-- Having contacted the authors to address these concerns, it was noted that  -->
-
-<!-- Propensity scores are based on a range of baseline variables, and provide an estimates of the  -->
-
-<!-- They used propensity scores to attempt to matcch patients equally likely to receive the vaccine -->
-
-<!-- In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
-Fortunately, the authors kindly shared their -->
-
-However, there was a large difference in the dementia "case mix", or proportion of different dementia diagnoses, between the two analyses, particularly in terms of the number of Alzheimer cases as a percentage of total dementia cases.
-The reason for this discrepancy between this analysis study and the previous paper is due to two things.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in my “Probable Alzheimer’s” code-list, I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
-Several of the codes in my “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
-
-Using the Smeeth code-list, I obtained a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
-
-<!-- TODO check that this is actually the case, that when you use the codelist from Smeeth, you get a different case-mix. Present it as a table. -->
-
-<!-- Will need to present the results for this! -->
-
-<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth. -->
-
-<!-- IN addition, this analysis used propensity s. IN addition, an analytical approach which appeared to adjust for key variables likely to be on the analytical pathway between   -->
-
-<!-- Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
 -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-```{r sankeydiagram, include=FALSE}
-```
-
-```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
 
@@
 
-<!-- ### Issues with large-scale EHR databases -->
+<!-- IDEA Issues with large-scale EHR databases -->
 
@@
 
-In light of my own experiences in attempting to extract information for papers assessing preventative measures, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are described in detail in both.
+In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
 
-All code, Read codelist and summary statistics (i.e.
+All code, Read codelists and summary statistics (i.e.
 the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project.
-<!-- TODO Will need to cite this, and may need to archive on Zenodo.
+as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
+<!-- TODO Archive on Zenodo.
 -->
@@
 The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-Interested researchers can apply directly to the  In this scenario, sharing the code represents a <!-- TODO CITATION NEEDED: Goldarce BMJ opinion -->
+In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
 
-As such, this analyses has been reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!-- Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
+Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
+<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
 
-<!-- TODO Reporting guidelines do not always work, but help to guide accurate rep -->
+This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
 
@@
 This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It found that the use of lipid-regulating agents was associated with a small reduction in probable or possible Alzheimer’s disease, and with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in this cohort.
+It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
+
+It found no evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
+However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
+In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
 
 This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for unmeasured confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-This is supported by our findings for the negative and positive control outcomes used.
-Future research using large scale electronic health records should aim to address these potential biases, potentially using a analytical design that more closely emulates a trial.[@danaei2013b]
-
-The unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted by the previous chapter (see Section \@ref(sys-rev-pub-bias)) .
-It is possible that previous research identified a similar effect and via a publication bias mechanism, these results did not make it into the evidence base.
+However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
+Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
 
 Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-In the following Chapter, the dataset described here is incorporated along with several other datasets
+In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
 

### 2021-05-28 R/background.R

@@ -103,6 +103,7 @@ if(doc_type == "docx"){
     thesisOverview_table,
     format = "latex",
     caption = "(ref:thesisOverview-caption)",
+    caption.short = "(ref:thesisOverview-scaption)",
     booktabs = TRUE
   ) %>%
     column_spec(1, width = paste0(6,"em")) %>%

### 2021-06-01 01-Chp-Background.Rmd
End of day: -4243
Submission of Chapter 4 to supervisors
End of day: -3464

@@
 source("R/helper.R")
-knitr::read_chunk("R/background.R")
+knitr::read_chunk("R/01-Code-Background.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
@@
 Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).
-[@burns2009]
+Parkinson's disease).[@burns2009]
 
@@
 
+(ref:thesisOverview-scaption) Summary of studies included in this thesis
+
 ```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}

### 2021-06-01 03-Chp-Systematic-Review.Rmd
End of day: -3799
End of day: -3464

@@
 
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = TRUE}
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
 "It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
@@
 source("R/doc_options.R")
-knitr::read_chunk("R/Chp2-Systematic-Review.R")
+source("R/helper.R")
+knitr::read_chunk("R/03-Code-Systematic-Review.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
@@
 -   Look at whether searching preprints made any difference to my results
--   Could apply ROBIS to previous reviews to see how they stack-up?
+-   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)
 
@@
 
-Based on the review of prev, no previous
+Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
+
+Only by looking across all available evidence can
 
@@
 
-Following guidance for a dose response meta-analysis, we picked m
+Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
+
+This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.
 
@@
 
+<!-- TODO Cite release version of this tool, and just use domain based approach -->
+
 Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
+
+<!-- TODO This next bit is not true -->
 
@@
 
+<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->
+
 Many reviews use reporting guidelines instead - this is bad![@costa2011]
+
+<!----------------------------------------------------------------------------->
+
+## Studification
+
+In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+<!----------------------------------------------------------------------------->
+
+## Following up with authors
+
+As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man
+
+<!-- TODO move to results, and keep just a short bit here -->
+
+<!----------------------------------------------------------------------------->
+
+### Statistical analysis methods
+
+<!----------------------------------------------------------------------------->
+
+Meta-analysis is an important method of . . .
+
+Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.
+
+This anal
+
+Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.
+
+### Visualisation of results
+
+Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)
+
+A summary of this tool is contained in Appendix \@ref (), .
+
+### Assessment of added value of including preprint
+
+Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew
+
+Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
+
+I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
+
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ## Results
+
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Screening results
@@
 
-<!-- ------------------------------------------------------------------------- -->
+&nbsp;
 
-```{r gwet-setup, results="hide", message=FALSE, echo = FALSE}
-```
+<!----------------------------------------------------------------------------->
+(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
+
+(ref:gwet-scaption) Ranges for Gwet's AC1
 
@@
 ```
+<!----------------------------------------------------------------------------->
 
-<!-- ------------------------------------------------------------------------- -->
-
-<!--- Need example table here, showing relevant cells --->
+&nbsp;
 
@@
 -\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
+
+<!--- TODO Need example table here, showing relevant cells --->
 
@@
 <!----------------------------------------------------------------------------->
+
+<!-- TODO This needs to use the PRISMA2020 package -->
 
@@
 
-### Publication bias
+### Publication bias {#sys-rev-pub-bias}
 
@@
 
-One particularly interesting meta-bias potentially applicable in this review is the definition
+One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across
 
@@
 
+As part of the reflective element of this thesis,
+
 Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
 Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
+
+Average time to complete a s
+
+However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
 
@@
 
-## Conclusion
-
-Test
+## References

### 2021-06-01 04-Chp-CPRD-Analysis.Rmd
End of day: -3464

@@
 options(scipen = 99)
-knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
+knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
@@
 The main analyses presented all used age as the time axis.
+
+<!-- TODO Will need to expand on choice of time axis here -->
 

### 2021-06-01 97-Discussion.Rmd
End of day: 0
End of day: -2681
End of day: -3464

@@
 
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
+
 # Discussion {#discussion-heading}
+\minitoc <!-- this will include a mini table of contents-->
 
-## Triangulation
+## Triangulation across exisiting evidence and evidence produced in this thesis
+
+Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
 
@@
 Essentially, a more transparent and open
-
-* That systematic review should no be
 
@@
 
-## Public involvement and engagement
+## Public involvement and engagement {#disc-PPI}
 
@@
 
-## Conclusions
+## Overall conclusions

### 2021-06-01 _main.Rmd
End of day: -3464

---
#####################
## thesis metadata ##
#####################
title: |
   Lipids and dementia:\
   An investigation of their relationship

author: Luke A McGuinness
college: 
degree: Doctor of Philosophy in Population Health Sciences
degreedate: TBC
abstract: |
  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
acknowledgements: |
  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
declaration: |
  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
dedication: For Brendan McHugh
abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

#######################
## bibliography path ##
#######################
bibliography: 
    - "bibliography/references.bib"
csl: bibliography/nature.csl
bibliography-heading-in-pdf: Bibliography

#####################
## PDF formatting  ##
#####################
abstractseparate: true  # include front page w/ abstract for examination schools?
bib-humanities: false   #set to true if you want in-text references formatted as author-year
doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
draft: false # add as DRAFT mark in the footer?
page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
toc-depth: 2 # depth of heading to include in table of contents
lof: true # list of figures in front matter?
lot: true # list of tables in front matter?
mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
mini-toc-depth: 1
mini-lot: false  # mini-list of tables by start of each chapter?
mini-lof: false  # mini-list of figures by start of each chapter?

params:
  corrections: true # set false to stop applying blue background to blocks of corrections

#####################
## output options  ##
#####################
output:
  bookdown::pdf_book:
    template: templates/template.tex
    keep_tex: true
    citation_package: default 
    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
  bookdown::gitbook:
    css: templates/style.css
    download: ["pdf"]
    output_dir: "docs"
    split_bib: false
    config:
      toc:
        before: |
          <li><a href="./">Thesis - Draft</a></li>
        after: |
          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
      sharing:
        facebook: false
        twitter: yes
        all: false
  bookdown::word_document2:
    output_dir: "docs"
    toc: true
    toc_depth: 2
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false   
link-citations: true
documentclass: book

---

```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
source('scripts_and_filters/create_chunk_options.R')
source("R/helper.R")
options(scipen=999)
```

<!--
Include the create_chunk_options chunk above at the top of your index.Rmd file
This will include code to create additional chunk options (e.g. for adding author references to savequotes)
If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
-->

```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
```

<!--chapter:end:index.Rmd-->

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
  bookdown::word_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

# Introduction {#intro-heading}
\minitoc <!-- this will include a mini table of contents-->

## Additional ideas

### General

* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published. Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished.

* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.

*

### Background

### medrxivr

###

&nbsp;

<!--chapter:end:00-Chp-Introduction.Rmd-->

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2:
    reference_docx: templates/word-styles-reference-01.docx
    number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
Science knows it doesn't know everything; otherwise, it'd stop.
```

(ref:dara-quote) --- Dara O'Briain

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/01-Code-Background.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

# Background, Theoretical framework, Aims & Objectives {#background-heading}

\minitoc <!-- this will include a mini table of contents-->

## Lay summary

[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]

Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition. Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition. The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change. Avoiding a risk factor does not guarantee that a person will not develop dementia but makes it less likely. A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees. The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.

This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them. It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis. Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.

<!----------------------------------------------------------------------------->

## Introduction

This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each. It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research. It then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.

The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters. Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.

<!----------------------------------------------------------------------------->

## Dementia

<!----------------------------------------------------------------------------->

### Definition and underlying pathologies {#underlying-pathologies}

Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]

Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases. Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease. Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]

Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases. Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]

The remaining 10-30% of cases are caused other dementia subtypes (e.g. Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g. Parkinson's disease).[@burns2009]

<!----------------------------------------------------------------------------->

### Diagnostic criteria {#diagnostic-criteria}

Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]

(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.

```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.

Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale. The distinction between these memory scales and diagnostic criteria presented above should be noted. For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table). Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).

Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available (see Section \@ref(intro-treatments)). Cause-specific criteria exist for the diagnosis of dementia sub-types. For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]

<!-- ### Differing risk by sex -->

<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->

<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->

<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->

<!----------------------------------------------------------------------------->

### Public health importance

Dementia is quickly becoming a critically important public health issue. Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only once without a proven treatment.

Dementia also has a substantial economic impact. In 2015, the estimated total cost of dementia in England was £24.2 billion. Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]

As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.

<!----------------------------------------------------------------------------->

### Treatments {#intro-treatments}

Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020]. At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.

The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme. Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]

### Risk factors

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @ansteya]

The benefits of a prevention-based approach based on addressing these risk factors are well-studied. Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]

In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.

This thesis will focus on blood lipids as the primary risk factor of interest. The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the existing evidence for an association between lipids and dementia outcomes.

<!----------------------------------------------------------------------------->

## Serum lipids

<!----------------------------------------------------------------------------->

<!--- May need small bit here on converting from one measurement to the other i.e.
mg/dL to mmol/L--->

### Lipid fractions

The blood lipid profile contains a range of component parts, or fractions. However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]

Triglycerides are the simplest and most common type of lipids found across the body. They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities. Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor. In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]

In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood. The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]

$$TC \approx LDLc - HDLc - kTG$$
where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).

&nbsp;

<!----------------------------------------------------------------------------->

(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]

(ref:lipidLevels-scaption) Classification of blood lipid levels

```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels. These deposits constrict blood flow and can lead to vascular complications. Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.

<!----------------------------------------------------------------------------->

### Statins

Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R). This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.

<!----------------------------------------------------------------------------->

(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the

(ref:statin-mechanisam-scap) Statin mechanism of action

```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

<!----------------------------------------------------------------------------->

### Other lipid regulating agents (LRA)

There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)). However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.

<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->

The most commonly used non-statin therapeutic is ezetimibe,[@kosoglou2005] which prevents intestinal absorption of cholesterol. However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).[@genest2006]

A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver. They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.

Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.

Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.

```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;
&nbsp;

<!----------------------------------------------------------------------------->

## Evidence for the association between blood lipids and dementia {#evidence-association}

This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.

<!----------------------------------------------------------------------------->
### Basic science

A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies. The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport. Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]

Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.

<!----------------------------------------------------------------------------->
### Observational studies

By far the largest source of evidence on the relationship between comes from observational designs. Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results. In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a]. With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]

Several previous systematic review of observational studies examining the effect of lipids[@anstey] and lipid-regulating agents[@chu2018b;@poly2020c] on dementia outcomes have been performed. However, these reviews have several limitations. Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)). Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey;@poly2020c]

<!----------------------------------------------------------------------------->

### Randomised controlled trials

In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.

However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.

While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk. Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome. One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years. As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome. The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.

Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome. As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.

Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up. Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia. Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]

<!----------------------------------------------------------------------------->

### Mendelian randomisation

Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:

1. the IV is associated with the exposure of interest (the relevance assumption);
2. the IV and outcome do not share a common cause (the independence assumption); and
3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).

Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels. This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]

Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.

<!----------------------------------------------------------------------------->

&nbsp;

In summary, multiple sources of evidence exist on the relationship between statins and dementia. In the next section, I introduce the synthesis of diverse sources of evidence as the theoretical framework used in this thesis.

Multiples forms of evidenc

<!----------------------------------------------------------------------------->

## Theoretical framework: Evidence synthesis

Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]

The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base. The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.

This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:

* Inclusion of grey literature
* Triangulation across evidence sources
* Individual patient data meta-analysis

These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.

<!----------------------------------------------------------------------------->

### Inclusion of grey literature {#diverse-sources-preprints}

The importance of including grey (or gray) literature in systematic reviews is widely acknowledged. Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]

A important developing source of grey literature are preprints. Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes. They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]

One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review. Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.

In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic. However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories. As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).

<!----------------------------------------------------------------------------->
### Triangulating across study designs

As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk. However, each method is limited by its own unique biases. Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result. The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias. A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.

This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.

All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading). Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise. [@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.

Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).

<!----------------------------------------------------------------------------->

### Individual patient data meta-analysis

Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]

In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]

An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]

Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a]. Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]

In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop. The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.

This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading). Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
<!----------------------------------------------------------------------------->

## Thesis overview

### Hypothesis

Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.

### Aims and objectives

The specific research objectives that this thesis seeks to address are:

* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions

### Structure {#thesis-structure}

Chapters are self-contained, presenting the methods and results of that specific research project. They are bookended by introductory and discussion sections which place the methods and results in context. Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).

-   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels. This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
-   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
-   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
-   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
-   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
-   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis. The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.

An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)

\blandscape
<!----------------------------------------------------------------------------->
(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading). Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.

(ref:thesisOverview-scaption) Summary of studies included in this thesis

```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->
\elandscape

## Outputs from this thesis {#thesis-output}

The outputs of this thesis are detailed below, and include peer-reviewed papers, presentations, and open-source evidence synthesis tools.

### Contributions to the scientific literature

During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.

&nbsp;

_**McGuinness, L. A.**, and L Schmidt. (2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651. DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_

A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading). As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).

&nbsp;

_Hennessy, E. A., Acabchuk, R., Arnold, P. A., Dunn, A. G., Foo, Y. Z., Johnson, B. T., Geange, S. R., Haddaway, N. R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A. Welch, V.,  **McGuinness L. A.** (2020). Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact. MetaArXiv. DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_

The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers. This piece was co-written with Dr. Emily Hennessy (see Author Declarations in the front materials). [Under 2nd round of review at Prevention Science]

&nbsp;

_**McGuinness, L. A.**, and Higgins J. P. T. (2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method). DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_

The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods. See Appendix \@ref(appendix-robvis) for more details on this tool.

&nbsp;

_**McGuinness, L. A.**, and Sheppard A. L. 2020. “A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv. DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_

Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts. [Accepted to PLOS One - need to update the citation]

&nbsp;

For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).

&nbsp;

### Presentations/Talks

<!--- Include links here for slides for each talk/poster --->

_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Accepted poster abstract, Alzheimer's Association International Conference 2021.

&nbsp;

_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_:
Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)

&nbsp;

_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.

_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.

### Software {#outputs-software}
**`medrxvir`**

An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories. See Chapter \@ref(sys-rev-tools-heading) for more details. Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:

```{r, eval = FALSE}
# CRAN version
install.packages("medrxivr")

# Development version
devtools::install_github("ropensci/medrxivr")
```

&nbsp;

**`robvis`**

An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review. See Appendix \@ref(appendix-robvis) for more details. Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:

``` {r, eval = FALSE}
# CRAN version
install.packages("robvis")

# Development version
devtools::install_github("mcguinlu/robvis")
```

&nbsp;

## Summary

This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.

\newpage

## References

<!--chapter:end:01-Chp-Background.Rmd-->

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
Why are open source statistical programming  
languages the best?

Because they R.
```

(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]

# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}

\minitoc <!-- this will include a mini table of contents-->

```{r setup, include=FALSE}
source("R/doc_options.R")
source("R/helper.R")
library(medrxivr)
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

<!----------------------------------------------------------------------------->

## Lay summary

Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal. They represent an important source of scientific literature. A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way. Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.

<!----------------------------------------------------------------------------->

## Introduction {#sys-rev-tools-intro}

Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)). As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review. The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]

Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature. At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations. As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.

This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv and bioRxiv preprints. The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed. As the majority of work on this aspect of this thesis is represented by lines of code (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)) this Chapter is an intentionally short, high-level summary of the work done on this project. The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.

&nbsp;

<!----------------------------------------------------------------------------->

(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching. Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).

(ref:medrxivr-sr-scap) Role of `medrxivr` in a systematic review workflow

```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
```

<!----------------------------------------------------------------------------->

## Development

### Success criteria {#success-criteria}

The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter. The criteria were as follows:

1.  reliable, reproducible and transparent search functionality, allowing for Boolean (AND/OR/NOT) operator logic;

2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and

3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.

&nbsp;

<!----------------------------------------------------------------------------->

### Alternative medRxiv/bioRxiv interfaces

Prior development of this tool, an audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted. While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.

The first, a platform called Rxivist [@abdill2019], allows users to search preprints using keywords. However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic. The search interface[^chp-systematic-review-tools-2] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.

[^chp-systematic-review-tools-2]: Available at <https://rxivist.org/>

The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature. As such, the platform only returns the most recent `r comma(1000)` records by publication date.

Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.

&nbsp;

<!----------------------------------------------------------------------------->

### Early versions

Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading). Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and the initial version of the `medrxivr` R package was released in February 2020.

Early versions of the tool had a reliance on scraping data directly from the repository website. Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992]. In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the repository website was regularly updated.

However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory. This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]

&nbsp;

<!----------------------------------------------------------------------------->

### Package infrastructure

The `medrxvir` package was written in R using RStudio,[@rcoreteam2019] and followed development best-practice, including detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.

&nbsp;

<!----------------------------------------------------------------------------->

## Usage

The `medrxivr` R package is split into two component parts:

-   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
-   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.

The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy. This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.

While the package allows for users to search both medRxiv and bioRxiv, as the process is identical for both, the examples in the sections are limited to the medRxiv repository.

&nbsp;

<!----------------------------------------------------------------------------->

### Installation

`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code:

&nbsp;

```{r, eval = FALSE}
install.packages("medrxivr")
```

&nbsp;

Alternatively, the development version of the package can be installed from GitHub:

&nbsp;

```{r, eval = FALSE}
# install.packages("devtools") 
devtools::install_github("ropensci/medrxivr")
```

&nbsp;

<!----------------------------------------------------------------------------->

### Importing preprint metadata

`medrixvr` provides two ways to access medRxiv data, as shown in Figure \@ref(fig:medrxivr-data-sources). The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.

&nbsp;

```{r, eval = FALSE}
# Get a copy of the database from the live medRxiv API endpoint
mx_data <- mx_api_content()  
```

&nbsp;

The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`.

&nbsp;

```{r, eval = FALSE}
# Import a copy of the medRxiv data from the snapshot
mx_data <- mx_snapshot()
```

&nbsp;

Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times. The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).

&nbsp;

<!----------------------------------------------------------------------------->

(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function. Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.

(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources

```{r medrxivr-data-sources, fig.pos="H", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
```

&nbsp;

<!----------------------------------------------------------------------------->

&nbsp;

### Performing a search

Once a local copy of the metadata is created, the first step in searching it is to create a search strategy. Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(…)`).

&nbsp;

```{r, eval = TRUE}
# Create the search query
topic1  <- c("dementia","alzheimer's")  # Combined with OR
topic2  <- c("lipids","statins")        # Combined with OR

myquery <- list(topic1, topic2)         # Combined with AND
```

&nbsp;

For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))". There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for. Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g. "randomi*s*ation" vs "randomi*z*ation".

Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.

&nbsp;

```{r, eval = FALSE}
# Run the search
results <- mx_search(mx_data,
                     myquery)
```

&nbsp;

<!----------------------------------------------------------------------------->

### Refining your search

An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy. __[CITATION NEEDED - PRISMA-S]__

&nbsp;

```{r, eval = FALSE}
results  <- mx_search(mx_data,
                      myquery, # Combined with OR
                      report = TRUE)
```

```{r, eval = FALSE}
## Found 1 record(s) matching your search.
## 
## Total topic 1 records: 224
## dementia: 224
## alzheimer's: 0
## 
## Total topic 2 records: 119
## lipids: 90
## statins: 33
```

&nbsp;

This allows users to discover which terms in their search are contributing most to the total number of results returned. This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered. It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results. As an example, in the search presented above, the term "alzheimer's" returns no records. This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.

&nbsp;

<!----------------------------------------------------------------------------->

### Exporting to a bibliography file

In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager. While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.

For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:

```{r, eval = FALSE}
mx_export(results, 
          file = "medrxiv_export.bib",
          report = TRUE)
```

&nbsp;

<!----------------------------------------------------------------------------->

### Downloading the PDFs of relevant records

`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)). `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user. This functionality is similar to the "Find Full Text" feature offered by EndNote.

&nbsp;

```{r, eval = FALSE}
mx_download(results,  # Search results, less excluded records
            "pdf/")   # Directory to save PDFs to 
```

&nbsp;

<!----------------------------------------------------------------------------->

## Discussion

### Reception and future plans

```{r, echo = FALSE, warning=FALSE}

medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = "2021-12-01")

medrxivr_downloads <- plyr::round_any(sum(medstats$count), 100, f = floor)

date <- format(as.Date("2021-12-01"),"%B %Y")
```

The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported. It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]

The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online. [^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.

[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>

Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing. This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches. For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.

&nbsp;

<!----------------------------------------------------------------------------->

### Limitations of `medrxivr`

While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here. A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed. However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity). A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]

There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.

&nbsp;

<!----------------------------------------------------------------------------->

### Role of open source tools in evidence synthesis

Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]

<!----------------------------------------------------------------------------->

## Summary

-   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.

-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).

-   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers. I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.

\newpage

## References

<!--chapter:end:02-Chp-Systematic-Review-Tools.Rmd-->

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
```

(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]

# Systematic review of all available evidence {#sys-rev-heading}

\minitoc <!-- this will include a mini table of contents-->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
knitr::read_chunk("R/03-Code-Systematic-Review.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

## To Do

-   Examine how many times a primary study was included in a review\
-   Look at whether searching preprints made any difference to my results
-   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)

## Extra studies to include:

* Smeet et al. reference in the CPRD analysis
* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
* Statins and the risk of dementia Jick

## Lay summary

## Additional ideas

-   Evidence map - show the distribution of the different studies population across the world.
-   Living systematic review approach - update weekly based on medRxiv

## Aims

The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.

Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.

Only by looking across all available evidence can

Literature con

## Methods

### Search strategy

We will systematically search electronic bibliographic databases to identify potentially relevant records. The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist. The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed. An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol. To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened. If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.

The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection. We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.

The abstracts list of relevant conferences (e.g. the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched. Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal. We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies. Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).

<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->

The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).

### Study selection

Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al. (2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria. If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened. Full-text screening will also be completed in full by the primary author. A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria. Reasons for exclusion at this stage will be recorded. Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague. A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]

#### Inclusion criteria

We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI. Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.

Participants will be free (or assumed to be free) of dementia/MCI at baseline. Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression. No limits will be placed on the sample size of included studies.

Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria. For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g. an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g. no dementia or dementia/MCI/dementia) based on this definition.

No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods. Preprints and unpublished reports will be eligible for inclusion if relevant. Multiple publications resulting from the analysis of the same data will be included and grouped.

#### Exclusion criteria

Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded. Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded. Studies that measure change in continuous cognitive measures (e.g. MoCA score) without attempt to map these scores to ordinal groups (e.g. no dementia/MCI/dementia) will be excluded. Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status. Studies that are reported in insufficient detail (e.g. only in conference abstracts, new, letters, editorials and opinion) will be excluded. Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles. Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g. for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e. below the age of 50) will be excluded.

Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of

### Data extraction

Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.

Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)

This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.

<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->

### Risk of bias assessment {#risk-of-bias}

Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design. Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]

I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.

<!-- TODO Cite release version of this tool, and just use domain based approach -->

Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.

<!-- TODO This next bit is not true -->

At present, no risk of bias assessment tool for Mendelian randomization studies is available. Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob). Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.

Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool. This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).

<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->

Many reviews use reporting guidelines instead - this is bad![@costa2011]

<!----------------------------------------------------------------------------->

## Studification

In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.

<!----------------------------------------------------------------------------->

## Following up with authors

As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man

<!-- TODO move to results, and keep just a short bit here -->

<!----------------------------------------------------------------------------->

### Statistical analysis methods

<!----------------------------------------------------------------------------->

Meta-analysis is an important method of . . .

Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.

This anal

Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.

### Visualisation of results

Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)

A summary of this tool is contained in Appendix \@ref (), .

### Assessment of added value of including preprint

Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew

Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.

I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.

<!----------------------------------------------------------------------------->

### Patient and public involvement

<!----------------------------------------------------------------------------->

## Results

<!----------------------------------------------------------------------------->

### Previous reviews

**Will need to include something in the methods section on this**

As part of this analysis, we examined the overlap between different published reviews on this topic.

Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,

Put upSet plot here.

An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.

Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews. So for example, XXXX records were captured both by the XXXX review and the XXXX review.

Where the matrix has just a single point highlighted, this shows the records unique to that review.

The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies

Our review is presented as the last point on this plot, and captured XXXX records

The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews. The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.

<!--- Take a stand here! --->

Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes. While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up. While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)

This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.

Does it also cause issues in terms of self-report?

<!----------------------------------------------------------------------------->

### Screening results

Following screening, XXX studies were included.

The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.

Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]

As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis. Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness. This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually. The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*

<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->

As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.

Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage. Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.

Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does. [@cohen1960: @gwet2008; @wongpakaran2013]

How to interpret agreement co-efficients is widely debated. Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).

&nbsp;

<!----------------------------------------------------------------------------->
(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric

(ref:gwet-scaption) Ranges for Gwet's AC1

```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

In a two-by-two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:

$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$

where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where

$$q = \frac{(A+C)+(A+B)}{2N}$$

-\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]

<!--- TODO Need example table here, showing relevant cells --->

<!-- # ```{r agreementtableinter, echo = FALSE} -->

<!-- # ``` -->

<!-- # ```{r agreementtableintra, echo = FALSE} -->

<!-- # ``` -->

For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).

The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]

Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated. This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.

<!--- Cross check this with the actual numbers included --->

<!----------------------------------------------------------------------------->

<!-- TODO This needs to use the PRISMA2020 package -->

```{r prisma-flow-setup, results="hide", message=FALSE}
```

(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process

(ref:prisma-flow-scap) PRISMA Flowchart

```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
```

<!----------------------------------------------------------------------------->

Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility. 387 were deemed potentially eligible and the full text records for these were requested and screened. \@ref(fig:prisma-flow-fig)

<!----------------------------------------------------------------------------->

### Characteristics of included studies

XXXX studies met the criteria for inclusion in the review.

Include here:

-   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)

-   Summary of types of study

-   Summary of locations

-   Summary of diagnostic criteria used

-   Summary of risk of bias

-   Long table, horizontally. Newer version of flextable (GH) allows for PDF output

A common theme across the studies was a lack of data on vascular dementia. This is particularly interesting as lipids and statins are primarily a vascular disease. There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading). For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of

One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4. As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.

In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review

### Converting risk ratios to odds ratios

Include formulae and informed assumptions

### Hazard ratios vs risk/odds ratios

Not interchangeable in the context of systematic review. If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.

Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.

The likely effect of this is that the overall effect measures are biased towards . . . . ?

Can you predict the direction of effect from a

Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis

<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->

Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.

### Risk of bias {#risk-of-bias-subheading}

### Sources of heterogeneity

Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**

### Publication bias {#sys-rev-pub-bias}

-   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
-   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult

One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across

### Triangualtion across evidence sources

One key question for which multiple distinct sources of evidence were available were those looking at Laz

A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use. In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)

Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework. Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the. For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated. [@guyatt2011]

Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test

### Added evidental value of including preprints {}

<!-- Will to get actual numbers for this section -->

There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)). While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available

Of interest,

<!-- Triple check whether any of the studies have yet to be published -->

This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy. It also means that searches are current - if the aim of systematic reviews is to

While the total number of relevant studies found using this method was

<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->

<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->

On further investigation, the argument that .

It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .

However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.

While concerns have been raised that

Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]

A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.

> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review

References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]

The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed

While [__some__] preprint have subsequently been published, this does not cause any major issues.

## Discussion

Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.

In addition, the a

### Searching for/including Mendelian randomisation studies

As a form of analysis that lends itself to multiple comparison, there is a strong

Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]

Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->

### Comments on the process

As part of the reflective element of this thesis,

Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed. Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.

Average time to complete a s

However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->

Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.

A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review. I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.

### Inclusion of preprints

As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted. Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.

The added evidental value of including these preprints was highlighted in Section

On further investigation, X of these preprints were subsequently published since the search was performed in 2019. While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.

### Open data sharing {#sys-rev-open-data}

<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->

<!--- Comment here on issues involved in extracting data --->

### Original contribution to research

I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):

-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%. As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g. ROBINS-I/E). This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature. As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.

### Comparison with other reviews

Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.

Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,

**The duplication of work across reviews (including, ironically, by this review) is substantial. In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews. However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**

__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic. Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.

<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->

### Reviewing Mendelian randomisations studies

While

This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.

Recent updates, such as a guide to reading and interpreting. However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.

Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for

Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.

### Strenghts and limitations

Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy. An example is Larsson et al. 2017[@larsson2017a], where the study examined the association between lipid fractions

Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the

<!--- Findings from this chapter are used throughout the later chapters of this thesis. In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model. From Sam abbotts--->

Test

## References

<!--chapter:end:03-Chp-Systematic-Review.Rmd-->

---
bibliography: bibliography/references.bib
csl: bibliography/nature.csl
output:
  bookdown::word_document2: 
      toc: false
      toc_depth: 3
      reference_docx: templates/word-styles-reference-01.docx
      number_sections: false 
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
```
(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]

# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}

\minitoc <!-- this will include a mini table of contents-->

<!-- Include the early analysis we did here, that did not work as a result of limited scope. Could include some of the genetic work also. Will additionally need to put the relevant materials from the paper in the  -->

```{r, echo = FALSE, warning=FALSE, message=FALSE}
source("R/doc_options.R")
source("R/helper.R")
options(scipen = 99)
knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
```

```{r load-files, echo = FALSE}
```

<!-- ## Additional ideas -->

<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event. -->

<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->

<!-- __Things we tried__ -->

<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by . Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly. Need total number of those starting and average time to start. -->
<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
<!-- - Allowing for time-varying confounders for binary covariates. -->

<!-- __Things we could try__ -->

<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
<!-- - Examine Cramer et al. thesis and see what they did -->
<!-- - Marginal structural models approach (a la J. Sterne) -->

<!--------------------------------------------------------------------------->

<!-- TODO Check lipid-regulating vs lipid regulating -->

<!-- TODO Check all fig/table cross-references evaluate -->

## Lay summary

Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care. Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes. These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed. This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.

This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK. Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.

No evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates. In contrast, I found an increased risk of vascular and other (i.e. non-Alzheimer's) dementia with lipid regulating agent use.

This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis. This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful. However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.

<!--------------------------------------------------------------------------->

&nbsp;

## Introduction

In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.

The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).

Firstly, it explicitly examines vascular dementia as an outcome. The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia. As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.

Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review). Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator. This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).

<!--------------------------------------------------------------------------->

&nbsp;

## Methods

### Study protocol

An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]

<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->

<!-- TODO Add amendments to Appendix -->

<!--------------------------------------------------------------------------->

&nbsp;

### Data source {#cprd-data-source}

Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]

To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code. The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g. Eu... - Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g. Eu001 - Dementia in Alzheimer's disease with late onset).

&nbsp;

<!--------------------------------------------------------------------------->
(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._). Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.

(ref:readExample-scaption) Example of CPRD Read code hierarchy

```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
```
<!--------------------------------------------------------------------------->

&nbsp;

Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.

&nbsp;

### Cohort definition

This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data. Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis. However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.

Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L. These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.

All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).

The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice. Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e. had less than one full day of follow-up).

<!--------------------------------------------------------------------------->

&nbsp;

### Exposures

We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.

A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach. We did however examine how often the initial drug class altered according to one of three criteria:

- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.

<!--------------------------------------------------------------------------->

&nbsp;

### Outcomes {#cprd-outcomes}

We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome. When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)). The diagnosis date of the outcome was determined by the first record of a relevant code.

<!----------------------------------------------------------------------------->
(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record. Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.

(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes

```{r decisionTree, include = FALSE}
```

```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
```
<!----------------------------------------------------------------------------->

Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).

&nbsp;

### Covariates

A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.

Demographic covariates adjusted for included age and gender. Age was calculated at date of entry into the cohort. Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England. To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.  Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.

Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date. A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort. To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.

Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes. In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant. The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.

Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).

&nbsp;

<!--------------------------------------------------------------------------->

### Missing data

Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.

<!-- IDEA Add more detail here on the missing data approach -->

In this analysis, missing data were handled using a multiple imputation approach. Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression. As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.

Missing data was only considered an issue for variables where a numerical test result was expected (e.g. BMI), or where a code existed for the absence of the condition (e.g. categorical smoking status). This approach was necessary, as absence of a code for other treatments or conditions (e.g. statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]

Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset. As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019a] to investigate the impact of multiple imputation on the results.

&nbsp;
<!--------------------------------------------------------------------------->

### Estimation methods

A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:

$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$

where:

* $t$ is the survival time;
* $h(t)$ is the hazard function; and
* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.

As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.

A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group. Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias. This is discussed in detail in the following section.

<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->

<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->

<!----------------------------------------------------------------------------->
&nbsp;

### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}

Immortal time bias covers two distinct but related types of bias. The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010a] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.

The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)). It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group. This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).

This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription). To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]

Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group. Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e. they enter the cohort and move into the exposed group on the same day).

<!--------------------------------------------------------------------------->
(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).

(ref:immortalTimeBias-scap) shortcap

```{r, immortalTime, include = FALSE}
```

```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
```
<!--------------------------------------------------------------------------->

### Time axis

<!-- IDEA Finish paragraph from fragments below -->

<!-- In Cox models, there is the option to -->

<!-- Age vs time-since entry -->

<!-- Expand on use of age as the time scale, but describe the problems this introduced -->

As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship. The main analyses presented all used age as the time axis.

<!-- TODO Will need to expand on choice of time axis here -->

<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age. -->

&nbsp;
<!--------------------------------------------------------------------------->

### Sensitivity analyses

The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class. To assess the robustness of the results, a number of sensitivity analyses were performed. These are described in the following sections.

#### Control outcomes

In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes. The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes. Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).

Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials. Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.

Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class. Muscular backpain was chosen as a negative control outcome in this analysis. Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect. As such, if no evidence of an effect of statins on backpain is found in the analysis, then confidence in the results for the dementia outcomes is increased.

Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.

<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->

<!----------------------------------------------------------------------------->
(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$. Note the absence of any arrow between $X$ and $N$. In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).

(ref:negativeOutcome-scap) DAG of ideal negative outcome

```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
library(dagitty)
library(ggdag)

ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
  dagitty::dagitty("dag {
    U -> N
    C -> N
    X <- U -> Y
    X <- C -> Y
    X -> Y
    bb =\"-2.368,-2.972,2.597,2.726\"
    C [pos=\"-0.3,0\"]
    N [pos=\"0.5,1\"]
    U [pos=\"-0.15,1.5\"]
    X [exposure,pos=\"0,-1\"]
    Y [outcome,pos=\"0.5,-1\"]
  }"
) %>% ggdag_classic() +
  theme_dag()

,
height = 3
)

knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))

```
<!----------------------------------------------------------------------------->

#### Impact of additional covariates

To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.

&nbsp;

#### Sensitivity cohorts

Two sensitivity cohorts were also created. The first stratified by year of entry into the cohort in an attempt to assess for time period effects. The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]

<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->

&nbsp;

#### Statin properties

As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).

To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.

&nbsp;

#### Impact of dementia code lists

As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]

This previous study used a propensity matching approach to estimate the effect of statins on a range of outcomes, and a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but no evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).

The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).

&nbsp;

## Results

### Patient characteristics

```{r characteristics, echo = FALSE}
```

```{r attritionFigure, include = FALSE}
```

Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.

&nbsp;

<!--------------------------------------------------------------------------->
(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.

(ref:cprdFlowchart-scap) Attrition of CPRD participants

<!-- This figure needs to have comma seperated numbers in order to agree with text. -->

```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition_test.png"))
```
<!--------------------------------------------------------------------------->

&nbsp;

The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`. During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia). The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).

\blandscape
<!--------------------------------------------------------------------------->
(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.

(ref:cprdCharacteristics-scaption) Patient characteristics by drug class

```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
```
<!--------------------------------------------------------------------------->
\elandscape

A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin. I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)). Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.

<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->

<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->

&nbsp;

<!--------------------------------------------------------------------------->
(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.

(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type

```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
```
<!--------------------------------------------------------------------------->

&nbsp;

The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).

&nbsp;

<!--------------------------------------------------------------------------->

### Missing data

```{r missing-data, echo = FALSE}
```

```{r azd-text, echo = FALSE}
```

Full covariate information was available for `r missingtext`. Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`

&nbsp;

### Primary analysis

The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).

For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.

&nbsp;

<!--------------------------------------------------------------------------->
(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.

(ref:cprdPrimary-scap) Results from primary analyses of CPRD data

```{r p1Figure, include = FALSE}
```

```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_p1.jpeg"))
```
<!--------------------------------------------------------------------------->

&nbsp;

<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->

__Alzheimer's disease__

No evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).

&nbsp;

__Non-Alzheimer's disease dementias__

In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`). Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.

&nbsp;

__All-cause dementia__

For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup. There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).

&nbsp;

### Sensitivity analyses

The results of the series of sensitivity analyses performed are described in the following sections.

#### Complete case versus imputed data

In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis. It should be noted that due to the large amount of missing data (e.g. `r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data. In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009b]

&nbsp;

<!----------------------------------------------------------------------------->
(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.

(ref:completeCaseFig-scap) Complete case vs. imputed data analysis

```{r completeCase, include= FALSE}
```

```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_complete_case.jpeg"))
```
<!----------------------------------------------------------------------------->

&nbsp;

#### Control outcomes

```{r controlOutcomes, echo = FALSE, message = FALSE}
```

Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive). The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).

For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding. However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).

&nbsp;

<!----------------------------------------------------------------------------->
(ref:controlOutcomeFig-cap) Results of control outcome analysis.

(ref:controlOutcomeFig-scap) Results of control outcome analysis

```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_control_outcomes.jpeg"))
```
<!----------------------------------------------------------------------------->

&nbsp;

#### Impact of additional covariates

The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).

These models were used to estimate the impact of adjustment for additional covariates. Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.

Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome. In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.

(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates

```{r unadjustedComparison, include=FALSE}
```

```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_unadjusted.jpeg"))
```
<!----------------------------------------------------------------------------->

#### Sensitivity cohorts: Entry year

When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).

&nbsp;

<!----------------------------------------------------------------------------->
(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.

(ref:diagnosisTypeFig-scap) Sensitivty analus

```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
knitr::include_graphics(file.path("figures/cprd-analysis/fp_cohort_entry.jpeg"))
```
<!----------------------------------------------------------------------------->

&nbsp;

On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)). While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry

(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry

```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

#### Sensitivity cohorts: Pregnancy

In the second sensitivity cohort, removing participants coded as female and aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).

<!----------------------------------------------------------------------------->
(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.

(ref:pregnancyFig-scap) Comparison of pregnancy analysis

```{r pregnancy, include = FALSE}
```

```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_pregnancy.jpeg"))
```
<!----------------------------------------------------------------------------->

&nbsp;

#### Statin properties

In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)). Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.

(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).

```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)). Additionally, in the AD outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)

(ref:statinTypeFig-scap) Analysis stratified by statin properties

```{r statinType, include = FALSE}

```

```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
knitr::include_graphics(file.path("figures","cprd-analysis","fp_sta_type.jpeg"))
```
<!----------------------------------------------------------------------------->

&nbsp;

#### Comparing codelists

```{r smeethText, include = FALSE}
```

When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.

However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used. While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”). Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.

&nbsp;

<!----------------------------------------------------------------------------->
(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure). The joining lines showing the overlap between the categories in the two analyses.

(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper

```{r sankeydiagram, include=FALSE}
```

```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
```
<!----------------------------------------------------------------------------->

This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).

&nbsp;

## Discussion

<!-- QUESTION To what extent should I cross-reference with the other literature here? -->

### Summary of findings

Lipid-regulating agents showed no evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis. The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants. For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.

The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed. When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.

<!-- QUESTION Why are fibrates different? -->

<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->

<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins. However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->

&nbsp;

<!--------------------------------------------------------------------------->

### Interpretation of results

This section will expand on a potential explanation for the observed results detailed above. However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point. For a comparison of the result presented above with those from the systematic review (Chapter \@ref(hold)) and the individual patient data analysis (Chapter \@ref(hold)), see Section \@ref(hold).

A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication. While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)). In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]

<!----------------------------------------------------------------------------->
(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.

(ref:indicationBias-scap) Confounding by indication causal diagram

```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}

ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
dagitty::dagitty("dag {
  Statin [exposure,pos=\"0.000,0.000\"]
  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
  \"Uncontrolled variable\" -> Statin
  \"Uncontrolled variable\" -> \"Vascular outcomes\"
}") %>% ggdag_classic(size = 6) +
  xlim(-0.5,3) +
  geom_text(data = data.frame(x = 0.316392393234329,
                              y = 0.537705383514239,
                              label = "Prompts"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_text(data = data.frame(x = 1.65891420807966,
                              y = 0.537705383514239,
                              label = "Causes"),
            mapping = aes(x = x,
                          y = y,
                          label = label),
            angle = 0L,
            lineheight = 1L,
            hjust = 0.5,
            vjust = 0.5,
            colour = "black",
            family = "sans",
            fontface = "bold",
            inherit.aes = FALSE,
            show.legend = FALSE) +
  geom_curve(data = data.frame(x = 0.220612676359188,
                               y = -0.000788829298738025,
                               xend = 1.45,
                               yend = -0.00157828084913909),
             mapping = aes(x = x,
                           y = y,
                           xend = xend,
                           yend = yend),
             linetype = "dashed",
             angle = 0L,
             size = 0.6,
             colour = "black",
             curvature = 0,
             arrow = structure(list(angle = 0,
                                    length = structure(0,
                                                       class = "unit",
                                                       valid.unit = 2L,
                                                       unit = "inches"),
                                    ends = 2L,
                                    type = 2L),
                               class = "arrow"),
             inherit.aes = FALSE,
             show.legend = FALSE) +

  theme_dag(),
width = 8,
height = 3)

knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
```
<!----------------------------------------------------------------------------->

In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.

Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses. The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors. This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase. This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).

A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual. Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.

Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful. I also adjusted for several additional potential baseline variables. However, important confounding variables for which I have not adjusted could include genetic factors. A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]

On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)). It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.

<!-- IDEA talk about time-varying confounding here -->

In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.

<!--------------------------------------------------------------------------->
&nbsp;

### Strengths and limitations

The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up. Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question. Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups. This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.

However, the findings of this analysis are subject to several limitations. There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure. As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents. Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019b]

Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes. Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis. This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.

<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->

<!-- IDEA there is also the potential for reverse causation in this analysis. Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent. -->

<!--------------------------------------------------------------------------->

<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->

<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->

<!-- However, this is not the case. Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event. Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent. However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.  -->

<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months. Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should. -->

<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required. -->

<!-- This hasn't been done! Plus I do not think this is the case -->

<!--------------------------------------------------------------------------->

<!--------------------------------------------------------------------------->
<!-- &nbsp; -->

<!-- IDEA Issues with large-scale EHR databases -->

<!-- __Missclassification__ -->

<!-- __Coding quality in the CPRD__ -->

<!-- Lots of things influence prevalence: historic trends, availability of good codes -->

<!-- There is the possibility of ascertainment bias -  -->

<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->

<!--------------------------------------------------------------------------->
&nbsp;

### Enabling easy synthesis of this analysis {#cprd-data-avail}

In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.

All code, Read codelists and summary statistics (i.e. the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e. as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX). <!-- TODO Archive on Zenodo. -->

The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee. In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]

Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist). <!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->

This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.

<!--------------------------------------------------------------------------->
&nbsp;

### Conclusions

This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia. It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.

It found no evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease. However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias. In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.

This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading). However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use. This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia. Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]

Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading). In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.

\newpage

## References

<!--chapter:end:04-Chp-CPRD-Analysis.Rmd-->

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::html_document2: default
  bookdown::word_document2: default
  bookdown::pdf_document2:
    template: templates/brief_template.tex
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

# Individual participant data meta-analysis {#ipd-heading}
\minitoc <!-- this will include a mini table of contents-->

## Methods

### Data sources

Several cohort studies were approach

<!-- Need exact number approach -->

As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.

Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get

Each should have:

* Description (including observation period, numbers, numbers with outcome, etc)
* Whether they are a known genetically at-risk cohort
*

### Epic Norfolk

The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]

```{r tests, }

```

Different approaches to combining subgroups. [@fisher2017]

## Risk of bias assessment

Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).

<!--- Inlcude CPRD analysis here, but dou --->

## Data cleaning

## Discussion

Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all. Will also need to comment on the additional tactics used.

This is likely due to my junior position as a early a

Range of reasons why data is not readily available.

Unfortunately,

As part of this, an analysis of

## Discussion

Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.

<!--chapter:end:05-Chp-IPD-Analysis.Rmd-->

---
output:
  bookdown::word_document2: 
      reference_docx: templates/word-styles-reference-01.docx   
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

# Discussion {#discussion-heading}
\minitoc <!-- this will include a mini table of contents-->

## Triangulation across exisiting evidence and evidence produced in this thesis

Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .

Summary table of different studies and results

## Discussion of E-values

How strong unmeasured confounding would have to be in order to explain the observed effect.

Heavily criticised in a range of papers.

## Use of concensus panel to bring everything together

## Additional topics for the discussion

There are several addition topics I would like to cover:

* The difference between the peer review of the software vs. the peer review of papers. A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.  Essentially, a more transparent and open

## Summary of findings (and implications for policy makers)

## Strengths and Limitations

There are several strengths and limitations to the work presented in this thesis. One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide

Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]

## Reproducible research

Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata. In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.

Containerisation was used to ensure that the code is reproducible, in line iwht best practices

Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).

One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset. IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading). However, access is dependency on an ISAC application to the managing body of the CPRD.

## Public involvement and engagement {#disc-PPI}

Involving and engaging the public and patients has been a central theme to this thesis.

Public engagement activities included

Public involvement also steered the creation of the topic

P

## Future work

## Overall conclusions

<!--chapter:end:97-Discussion.Rmd-->

`r if(!knitr:::is_latex_output()) '# Bibliography {-}'`

<!-- If you're outputting to LaTeX, the heading and references will be generated by the OxThesis LaTeX template. This .Rmd file serves only to add the References headline to gitbook output before the references are added by pandoc -->

```{block type='savequote', include=knitr::is_latex_output(), echo = TRUE}
Lasciate ogne speranza, voi ch'intrate. . .
```

# Bibliography

<div id="refs"></div>

<!--chapter:end:front-and-back-matter/98-references.Rmd-->

`r if(knitr:::is_latex_output()) '\\startappendices'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`

<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->

# By Chapter {#chapter-appendix-heading}

## Chapter \@ref(intro-heading) {#appendix-into}

### Publications beyond the scope of this thesis {#appendix-publications}

__Peer reviewed__

  * McGuinness & Sheppard. Comparison of pairwise

  * PRISMA main paper

  * PRISMA E&E

  * PRISMA 2020 software

  * COVID Suicide Living Review

  * Data extraction tools systematic review

<!-- Essentially, look at the Trello -->
__Under review/Preprints__

  * MSc Paper on systematic reviews of this thesis topic

  *

### Involvement of patients and the public {#appendix-ppi}

Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.

Additionally,

Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary

## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}

### Search strategy {#appendix-search-strategy}

### Code to search preprints {#appendix-medrxivr-code}

<!-- Double check this is the final code used -->

```{r, eval = FALSE}

library(medrxivr)

mx_data <- mx_api_content(to_date = "2019-09-01")

bx_data <- mx_api_content(server = "biorxiv",
                                    to_date = "2019-09-01")

topic1 <- c("statin",
            mx_caps("ldl"),
            mx_caps("hdl"),
            mx_caps("TG"),
            paste0("\\b",mx_caps("TC"),"\\b"),
            "ezetim",
            "lipoprotein",
            "lipid",
            "cholesterol")

topic2 <- c(mx_caps("dementia"),
            mx_caps("alzheim"),
            mx_caps("MCI"),
            mx_caps("mild cognitive"))

query <- list(
  topic1,
  topic2
)

test <- mx_search(bx_data, query)

test2 <- mx_search(mx_data, query)

```

Note

### MR risk of bias tool {#appendix-mr-rob}

## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}

## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}

### Amendments to protocol {#appendix-cprd-amendments}

### Code lists

## Chapter \@ref(discussion-heading)

### Catalogue of failures

Short section detailing the things I tried to do but which did not work.

<!----------------------------------------------------------------------------->

# Other Appendix {#other-appendix-heading}

## Software used to create this thesis

This thesis was written in RMarkdown. Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]

All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}

### Introduction

Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews. A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain. For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]

Researchers can face a number of barriers in creating these plots. While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone. Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review. Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process. For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.

Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily. Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.

The tool is open-source and available to use free of charge. Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).

### Development

Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies. Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback. This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019. The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]

### Installation

A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:

```{r, eval = FALSE}
install.packages("robvis")
```

As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version. The most recent development version can be install from GitHub using:

```{r, eval = FALSE}
devtools::install_github("mcguinlu/robvis")
```

### Usage

`robvis` contains two main functions. The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment. The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.

A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`. A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)

Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:

__NEED TO ADD DATA HERE!__

```{r, eval = FALSE}

rob_traffic_light(data = data_rob2,
                  tool = "ROB2",
                  psize = 15)
```

```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}

plotdata <- robvis::data_rob2

tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)

robvis::rob_save(tfplot, 
                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")

knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
```

Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:

```{r, eval = FALSE}

rob_summary(data = data_rob2,
            tool = "ROB2", 
            overall = TRUE)

```

```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}

sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)

robvis::rob_save(sumplot,
                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")

knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")

```

A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)

`r br`

```{r robvisarguments, echo = FALSE, eval = TRUE}

arguments <- data.frame(stringsAsFactors=FALSE,
              argument = c("data", "tool", "colour", "overall", "weighted",
                           "psize"),
     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
           rob_summary = c("X", "X", "X", "X", "X", ""),
           Description = c(
"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
"Defines the risk of bias assessment tool used. The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported. Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
"Defines the colour scheme for the plot. The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`). Alternatively, users can specify their own colour scheme e.g. `colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))

if(doc.type == "docx"){

  knitr::kable(arguments,escape = T,
             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",

             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))

}else{

  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
             align = c("l","c","c","l"),
             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
  column_spec(4,"5cm") %>%
  kable_styling(font_size = 9, 
                bootstrap_options = c("striped", "hover"),
                latex_options = c("repeat_header", "striped"))
}

```

`r br`

### Reception and Future Plans

```{r, echo = FALSE}
robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")

robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)

date <- format(as.Date("2021-12-01"),"%B %Y")

```

As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times. It has been well received but the systematic review community, and has been cited frequently in the published literature. A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods. A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]

While `robvis` is a stable package, a range of additional functionality could be added. At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority. For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments. However, following user-driven demand, this functionality is in development and will be available in the near future. Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis. The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.

<!--chapter:end:front-and-back-matter/99-appendices.Rmd-->

### 2021-06-01 R/background.R

@@ -1,119 +1,0 @@
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- diagnosticCriteria-table
-
-diagnosticCriteria_table <- read.csv("data/background/dementiaCriteria.csv") %>%
-  mutate("Major neurocognitive event (previously dementia)" = Dementia) %>%
-  select(Criterion, "Major neurocognitive event (previously dementia)")
-
-col_widths <- 32/ncol(diagnosticCriteria_table)
-
-if(doc_type == "docx") {
-  knitr::kable(diagnosticCriteria_table, caption = "(ref:diagnosticCriteria-caption)")
-} else{
-  table <- knitr::kable(
-    diagnosticCriteria_table,
-    format = "latex",
-    caption = "(ref:diagnosticCriteria-caption)",
-    caption.short = "(ref:diagnosticCriteria-scaption)",
-    align = "cl",
-    booktabs = TRUE
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    column_spec(2, width = paste0(27,"em")) %>%
-    column_spec(1, bold = TRUE,  width = paste0(5,"em")) %>%
-    row_spec(2:nrow(diagnosticCriteria_table)-1, hline_after = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position")) %>%
-    kableExtra::footnote(threeparttable = TRUE, symbol = "From DSM: Evidence of decline is based on concern of the individual, a knowledgeable informant, or the clinician that there has been a significant decline in cognitive function and a substantial impairment in cognitive performance, preferably documented by standardized neuropsychological testing or, in its absence, another quantified clinical assessment.")
-  
-  table <- gsub("textbackslash\\{\\}newline","\\newline",table)
-  
-  table
-}
-
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- lipidLevels-table
-
-lipidLevels_table <- read.csv("data/background/lipidLevels.csv") %>%
-  mutate("Measure (mg/dL)" = Measure) %>%
-  select("Fraction","Measure (mg/dL)","Classification")
-
[…]

### 2021-06-02 03-Chp-Systematic-Review.Rmd
End of day: -3432

@@
 
-## To Do
+<!-- ## To Do -->
 
--   Examine how many times a primary study was included in a review\
--   Look at whether searching preprints made any difference to my results
--   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)
+<!-- -   TODO Examine how many times a primary study was included in a review\ -->
+<!-- -   TODO Look at whether searching preprints made any difference to my results -->
+<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->
 
-## Extra studies to include:
+<!-- TODO Extra studies to include: -->
 
-* Smeet et al. reference in the CPRD analysis
-* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
-* Statins and the risk of dementia Jick
+<!-- * Smeet et al. reference in the CPRD analysis -->
+<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
+<!-- * Statins and the risk of dementia Jick -->
 
@@
 
-## Additional ideas
+As introduced in previous chapters,
 
--   Evidence map - show the distribution of the different studies population across the world.
--   Living systematic review approach - update weekly based on medRxiv
+<!-- IDEA Evidence map - show the distribution of the different studies population across the world.
+Distribution will have to be of participants, not primary authors.
+Though could use to show how data is being used globally -->
 
-## Aims
+## Introduction {#sys-rev-intro}
 
@@
 
-Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
+Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
 
-Only by looking across all available evidence can
+Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).
 
@@
 
+<!-- TODO Look at citation chaser for this, but have a cut-off publication date of  -->
+
 <!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
@@
 The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).
+A summary by topic is presented in Table
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:searchOverview-caption) Summary of systematic search by topic. For a full list of search terms, see Appendix \@ref()
+
+(ref:searchOverview-scaption) searchOverview
+
+```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
+<!-- TODO Expand on rationale for exclusion of cross-sectional studies.
+Dementia is a disease severly at risk of differential recall, leading to misclassification bias.
+By using prospective studies, the potential for this bias is reduced.
+-->
+
 ### Data extraction
@@
 
-This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.
+This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.
+
+A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.
 
@@
 
+#### Randomised controlled trials
+
 Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
 Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
+
+#### Non-randomised studies of interventions
 
@@
 
-<!-- TODO This next bit is not true -->
+#### Mendelian randomisation studies
+
+<!-- TODO This next bit is not all true -->
 
@@
 
-## Studification
+### Studification
 
@@
 
-## Following up with authors
+### Following up with authors
 
@@
 
-A summary of this tool is contained in Appendix \@ref (), .
+This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->
+
+A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using
+
+.
 
@@
 
-```{r prisma-flow-setup, results="hide", message=FALSE}
+```{r prisma-flow-setup, include = FALSE}
 ```
@@
 
-(ref:prisma-flow-scap) PRISMA Flowchart
+(ref:prisma-flow-scap) PRISMA Flow Diagram
 
@@
 
-Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility.
-387 were deemed potentially eligible and the full text records for these were requested and screened.
+Following de-duplication, the titles and abstracts of `r hold()` records were assessed for eligibility.
+`r hold()` were deemed potentially eligible and the full text records for these were requested and screened.
 \@ref(fig:prisma-flow-fig)
@@
 
+As shown in
+
 Include here:
 
--   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
+-   PRISMA Flowchart
 
@@
 
+Many studies did not report the codelists used to run the analysis,
+
 ### Triangualtion across evidence sources
@@
 One key question for which multiple distinct sources of evidence were available were those looking at Laz
+
+<!-- TODO Have a look at this -->
 
@@
 
-<!-- Will to get actual numbers for this section -->
+<!-- TODO Will have to get actual numbers for this section -->
 
@@
 
+Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).
+
 Of interest,
 
-<!-- Triple check whether any of the studies have yet to be published -->
+<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->
 
@@
 In addition, the a
-
-### Searching for/including Mendelian randomisation studies
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
-
-Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
 
@@
 
+#### Inclusion of Mendelian randomisation studies
+
+As a form of analysis that lends itself to multiple comparison, there is a strong
+
+Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
+
+Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
+
 Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy.
 An example is Larsson et al.
-2017[@larsson2017a], where the study examined the association between lipid fractions
+2017[@larsson2017a], where the study examined the association between lipid fractions with Azlheimer's disease.
+
+Potentially the use of methods such as snowballing (forwards and backwards citation chasing) should attenuate the bias introduced by this method.
+
+However, in future reviews, a dedicated search for "risk factors" and "dementia" and "
+
+#### Inclusion of preprints
 
 Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
+cut-off point for the search (e.g. they would not have been captured by the search fot published papers)
 
@@
 
-Test
+### Use in other chapters
+
+Findings from this review are used though out the subsequent chapters.
+
+For example,
 

### 2021-06-02 front-and-back-matter/99-appendices.Rmd
End of day: -3432

@@
 
+<!----------------------------------------------------------------------------->
 # By Chapter {#chapter-appendix-heading}
 
+<!----------------------------------------------------------------------------->
 ## Chapter \@ref(intro-heading) {#appendix-into}
 
+<!----------------------------------------------------------------------------->
 ### Publications beyond the scope of this thesis {#appendix-publications}
@@
 
+<!----------------------------------------------------------------------------->
+
 ### Involvement of patients and the public {#appendix-ppi}
@@
 
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
+<!----------------------------------------------------------------------------->
+
+## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-tools}
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
 ### Code to search preprints {#appendix-medrxivr-code}
@@
 
-topic1 <- c("statin",
+topic1 <- c(mx_caps("statin"),
             mx_caps("ldl"),
@@
             mx_caps("TG"),
+            mx_caps("triglycer"),
             paste0("\\b",mx_caps("TC"),"\\b"),
-            "ezetim",
-            "lipoprotein",
-            "lipid",
-            "cholesterol")
+            mx_caps("ezetim"),
+            mx_caps("fibrate"),
+            mx_caps("bile acid"),
+            mx_caps("lipoprotein"),
+            mx_caps("lipid"),
+            mx_caps("cholesterol"))
 
@@
 
-test <- mx_search(bx_data, query)
+bx_results <- mx_search(bx_data, query)
 
-test2 <- mx_search(mx_data, query)
+mx_results <- mx_search(mx_data, query)
 
@@
 
+<!----------------------------------------------------------------------------->
 ### MR risk of bias tool {#appendix-mr-rob}
 
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
-
+<!----------------------------------------------------------------------------->
 ## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-
+<!----------------------------------------------------------------------------->
 ### Amendments to protocol {#appendix-cprd-amendments}
 
+<!----------------------------------------------------------------------------->
 ### Code lists
 
+## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
+<!----------------------------------------------------------------------------->
+### Section 1
+
+<!----------------------------------------------------------------------------->
+### Section 2
+
+<!----------------------------------------------------------------------------->
 ## Chapter \@ref(discussion-heading)
 
+<!----------------------------------------------------------------------------->
 ### Catalogue of failures
@@
 <!----------------------------------------------------------------------------->
-
 # Other Appendix {#other-appendix-heading}
@@
 
+<!----------------------------------------------------------------------------->
 ## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
@@
 The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
+
+## Creating

### 2021-06-02 front-and-back-matter/_acknowledgements.Rmd
End of day: -3432

@@
+<!-- TODO CHECK ALL NAME SPELLINGS -->
+
 Additionally, I would like to thank Sharen O’Keefe.
-
-Thanks to the creator of the oxfordown which was used
 
@@
 
-robvis contributors
+robvis contributors: (there are at least 3)
 
-Annual reviewersLn Rupert Payne and Emma Anderson
+Annual reviewers: Rupert Payne and Emma Anderson
 
-<!-- I am a Wellcome Trust Funded PhD student with grant code 102432/Z/13/Z.
+Those who contributed their time to dual marking papers and code with me,
+
+I am a NIHR Doctoral Research Fellow with grant code **TBC**.
 The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.
--->
 
-Statistical support:
+Statistical support: check emails!
 
-All authors who volunteered time and effort
+All authors who volunteered time and effort to provided
+
+A special thanks goes out to Mark Newbury of the
+
+Finally, thanks to parents and Ciara Gardiner.
 

### 2021-06-02 R/03-Code-Systematic-Review.R

@@ -1,3 +1,18 @@
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- searchOverview-table
+
+searchOverview_table <- mtcars
+
+if(doc_type == "docx"){
+knitr::kable(searchOverview_table,caption = "(ref:searchOverview-caption)")
+}else{
+knitr::kable(searchOverview_table, format = "latex", caption = "(ref:searchOverview-caption)", caption.short = "(ref:searchOverview-scaption)", booktabs = TRUE) %>% 
+row_spec(0, bold = TRUE) %>%
+kable_styling(latex_options = c("HOLD_position"))
+}
+
+
+
 # ---- prisma-flow-setup
 
 
@@ -42,6 +57,7 @@ if(doc_type == "docx") {
     kable_styling(latex_options = c("HOLD_position"))
 }
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- agreementtableinter
 
 agreement.table.1 <- data.frame(group = rep("Second reviewer decision",3),
@@ -59,6 +75,7 @@ knitr::kable(agreement.table.1, booktabs = TRUE, col.names = c("","","Exclude", 
   kableExtra::collapse_rows(columns = 1, valign ="middle") %>%
   kableExtra::row_spec(2,extra_css = "border-bottom: 1px solid")
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- agreementtableintra
 
 agreement.table.2 <- data.frame(group = rep("Same reviewer decision",3),

### 2021-06-02 R/helper.R

@@ -28,7 +28,7 @@ gen_rmd_citation <- function(filename = "pkg-refs.bib") {
 }
 
 # Place comma at thousand position
-# Taken from https://github.com/thomasbattram/thesis
+# Copied from https://github.com/thomasbattram/thesis
 comma <- function(x){
   
   format(x, digits = 2, big.mark = ",")
@@ -36,7 +36,7 @@ comma <- function(x){
   }
 
 # Apply comma to all values in a table
-# Taken from https://github.com/thomasbattram/thesis
+# Copied from https://github.com/thomasbattram/thesis
 tidy_nums <- function(df) 
 {
   df[] <- lapply(df, comma)
@@ -44,7 +44,7 @@ tidy_nums <- function(df)
 }
 
 # Convert nub
-# Taken from https://github.com/thomasbattram/thesis
+# Copied from https://github.com/thomasbattram/thesis
 num_to_text <- function(x, start_of_sentence = FALSE)
 {
   if (!x%%1 == 0) warning("X is not an integer")
@@ -61,6 +61,8 @@ num_to_text <- function(x, start_of_sentence = FALSE)
   return(out)
 }
 
+
+# Get word count for a given file, and set new target
 check_words <- function(fp, words = 100){
   
   if (!hasArg(fp)) {
@@ -74,52 +76,8 @@ check_words <- function(fp, words = 100){
   message("Start:   ",format(Sys.time(),"%H:%M"),"\nCurrent: ",w,"\nNext:    ", n," <------\n")
 }
 
-pomodoro_bg <- function(){
-  job::job({pomodoro()},import = c(pomodoro))  
-}
 
-pomodoro <- function(fp){
-  
-  # Get file path ----
-    
-  if (!hasArg(fp)) {
-    fp <- rstudioapi::getSourceEditorContext()$path
-    message("File: ",fp)
-  }
-
-  # Fail early if wrong file type
-  sink <- wordcountaddin::word_count(filename = fp)
-  
-  # Add job
-  # job_id <- rstudioapi::jobAdd("Long Pomodoro", progressUnits = 25L)   
-      
-  i <- 0
-  
-  # rstudioapi::jobAddOutput(job_id, paste0("File: ",fp))
-  
-  # Run Long Pomodoro
-  
-  while (i < 26) {
-    
-    w <- wordcountaddin::word_count(filename = fp)
-    
[…]

### 2021-06-04 03-Chp-Systematic-Review.Rmd
End of day: -3311

@@
 
+### Protocol
+
+A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]
+
 ### Search strategy
 
-We will systematically search electronic bibliographic databases to identify potentially relevant records.
-The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened.
-If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.
-
-The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-
-The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
-Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
-We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
-
-<!-- TODO Look at citation chaser for this, but have a cut-off publication date of  -->
-
-<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
-
-The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).
-A summary by topic is presented in Table
+I systematically search electronic bibliographic databases to identify potentially relevant records.
+The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
+The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+<!-- TODO Need to actually attach each search strategy, and detail the specific databases used.
+See search strategy results.
+-->
 
@@
 
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 14" in Table \@ref(tab:searchOverview-table)) was screened.
+If any potentially relevant studies are identified, their titles and abstracts were searched for key terms that can be incorporated into the filters to improve search sensitivity.
+
+<!-- TODO need to comment on this feed-back process, or remove -->
+
+The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the Univeristy ).
+We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
+
+The abstracts list of relevant conferences (e.g.
+the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
+<!-- TODO how were these searched?
+-->
+ Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
+We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
+Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+
+<!-- TODO Look at citationchaser for this, but have a cut-off publication date of  -->
+
+<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
+
 ### Study selection
 
-Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+Records weree imported into Endnote and deduplicated using the method outlined in Bramer et al.
+(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
+those matched based on the "Title" field alone).
+
+Screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+
 Full-text screening will also be completed in full by the primary author.
@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Assessment of inter-rater reliability
+
+Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
+
+If this approach demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
+[@cohen1960: @gwet2008; @wongpakaran2013]
+
+Gwet's AC1 is defined as
+
+$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
+
+In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
+
+$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
+
+where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
+
+$$q = \frac{(A+C)+(A+B)}{2N}$$
+
+<!-- TODO Need to be sure of how to calculate. -->
+
+How to interpret agreement co-efficients is widely debated.
+Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
+
+(ref:gwet-scaption) Ranges for Gwet's AC1
+
+```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 ### Data extraction
@@
 
+Given the focus on triangulating different sources of evidence at risk of a diverse range of bias, a detailed and structured risk of bias assessment formed an important part of this review.
+
+There has been a recent moved from
+
+Talk about move from checklist tools to more domain based methods
+
+Many reviews use reporting guidelines instead - this is bad![@costa2011]
+
+Described here how tools work and how you get an overall judgement -. algorithm
+
+<!----------------------------------------------------------------------------->
+
 #### Randomised controlled trials
@@
 Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
+Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019],
+The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
 
-#### Non-randomised studies of interventions
+<!----------------------------------------------------------------------------->
+#### Non-randomised studies of interventions/exposures
 
+For non-randomised studies of interventions, I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
+Similar to the RoB 2, it has a number of prompting questions per domain, with judgements includeing.
+Ideally, obs studies assesed in reference to an idealised randomised controlled trial.
+Futher, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
+
+For non-randomised studies o
 I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.
+
+non-randomized studies of interventions were assessed using the ROBINS-I tool, and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
 
@@
 
-Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
+Secondly, as mentioned in the introduction to this section, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
+
+<!----------------------------------------------------------------------------->
 
@@
 At present, no risk of bias assessment tool for Mendelian randomization studies is available.
-Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob).
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies.
+A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
 Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
 
-Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
-
 <!-- TODO Cite MR tool here from malmuk, see info from Francesca -->
-
-Many reviews use reporting guidelines instead - this is bad![@costa2011]
 
@@
 
+Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
+This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
+
 .
@@
 
-Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew
+Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
 
@@
 
+### Search results
+
+Detail
+
 ### Previous reviews
+
+<!-- TODO Not sure this is the best place for this -->
 
@@
 As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
-
-Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
-[@cohen1960: @gwet2008; @wongpakaran2013]
-
-How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In a two-by-two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
-
-$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-$$q = \frac{(A+C)+(A+B)}{2N}$$
-
--\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
 
@@
 
--   Long table, horizontally. Newer version of flextable (GH) allows for PDF output
+-   Long table, horizontally.
 
@@
 
+###
+
 ### Comments on the process
@@
 Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
-cut-off point for the search (e.g. they would not have been captured by the search fot published papers)
+cut-off point for the search (e.g. they would not have been captured by the search for published papers)
 

### 2021-06-04 front-and-back-matter/99-appendices.Rmd
End of day: -3311

@@
 
+### Web of Science Databases Searched {#appendix-wos-databases}
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:wosDatabases-caption) Summary of Web of Science databases searched.
+
+(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
+
+```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
+
+wosDatabases_table <- read.csv(here::here("data/sys-rev/wosDatabases.csv"))
+
+if(doc_type == "docx") {
+  knitr::kable(wosDatabases_table, caption = "(ref:wosDatabases-caption)")
+} else{
+  knitr::kable(
+    wosDatabases_table,
+    format = "latex",
+    caption = "(ref:wosDatabases-caption)",
+    caption.short = "(ref:wosDatabases-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    column_spec(column = 1, width = paste0(18,"em")) %>%
+    column_spec(column = 2, width = paste0(8,"em")) %>%
+    column_spec(column = 3, width = paste0(6,"em")) %>%
+    row_spec(2:nrow(wosDatabases_table)-1, hline_after = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"))
+}
+
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 <!----------------------------------------------------------------------------->
@@
 ### MR risk of bias tool {#appendix-mr-rob}
+
+<!----------------------------------------------------------------------------->
+(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
+
+(ref:mrTool-scaption) Mendelian randomisation risk-of-bias assessment tool
+
+```{r mrTool-table, message=FALSE, results="asis", echo = FALSE}
+
+mrTool_table <- read.csv(here::here("data/sys-rev/mrRobTool.csv")) %>%
+  select(1:5) %>%
+  rename("Bias domain" = Bias.domain)
+
+if(doc_type == "docx") {
+  knitr::kable(mrTool_table, caption = "(ref:mrTool-caption)")
+} else{
+  knitr::kable(
+    mrTool_table,
+    format = "latex",
+    caption = "(ref:mrTool-caption)",
+    caption.short = "(ref:mrTool-scaption)",
+    longtable = TRUE,
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    column_spec(column = 1:5, width = paste0(32/5,"em")) %>%
+    row_spec(2:nrow(mrTool_table)-1, hline_after = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position","repeat_header"))
+}
+
+```
 

### 2021-06-04 front-and-back-matter/_acknowledgements.Rmd
End of day: -3311

@@
+__Professional__
+
 <!-- TODO CHECK ALL NAME SPELLINGS -->
-
-Additionally, I would like to thank Sharen O’Keefe.
 
@@
 
+Thanks to Francesca for sharing advance copy of review of Mendelian randomisation studies, to inform choice of tool.
+
 I am a NIHR Doctoral Research Fellow with grant code **TBC**.
 The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.
+
+Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
+<<github>>
 
@@
 
+__Personal__
+
 Finally, thanks to parents and Ciara Gardiner.
@@
 \begin{flushright}
-Canynge Hall, Bristol \\
+Canynge Hall, Bristol \\\
 1 December 2021

### 2021-06-04 index.Rmd
End of day: -3311

@@
 acknowledgements: |
-  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
+  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
 declaration: |

### 2021-06-04 R/03-Code-Systematic-Review.R

@@ -1,19 +1,34 @@
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- searchOverview-table
 
-searchOverview_table <- mtcars
+searchOverview_table <- read.csv(here::here("data","sys-rev","searchOverview.csv"))
 
-if(doc_type == "docx"){
-knitr::kable(searchOverview_table,caption = "(ref:searchOverview-caption)")
-}else{
-knitr::kable(searchOverview_table, format = "latex", caption = "(ref:searchOverview-caption)", caption.short = "(ref:searchOverview-scaption)", booktabs = TRUE) %>% 
-row_spec(0, bold = TRUE) %>%
-kable_styling(latex_options = c("HOLD_position"))
-}
-
-
+  if(doc_type == "docx") {
+    knitr::kable(searchOverview_table, caption = "(ref:searchOverview-caption)")
+  } else{
+    knitr::kable(
+      searchOverview_table,
+      format = "latex", 
+      caption = "(ref:searchOverview-caption)",
+      caption.short = "(ref:searchOverview-scaption)",
+      booktabs = TRUE,
+      align = "cl"
+    ) %>%
+      row_spec(0, bold = TRUE) %>%
+      row_spec(2:nrow(searchOverview_table)-1, hline_after = TRUE) %>%
+      kableExtra::column_spec(1, bold= FALSE) %>%
+      kable_styling(latex_options = c("HOLD_position"), font_size = 10)  %>%
+      kableExtra::footnote(
+        threeparttable = TRUE,
+        general_title = "",
+        general = paste("For all topics, search queries were comprised",
+                        "of relevant free text & controlled vocabulary terms."
+        )
+      )
+  }
 
 # ---- prisma-flow-setup
+
 
 
 

### 2021-06-04 R/abbreviations.R

@@ -1,3 +1,5 @@
+# IMport, sort and arragn
+
 abbr <-
   dplyr::arrange(read.csv(
     here::here("data", "abbreviations", "abbreviations.csv"),
@@ -19,3 +21,17 @@ abbr_text <- c(
 )
 
 writeLines(abbr_text, here::here("front-and-back-matter","abbreviations.tex"))
+
+# Render the acknowledgements section from Rmd to Md and paste in the output of
+# github_thanks()
+
+source(here::here("R","helper.R"))
+
+writeLines(glue::glue(
+  paste(c("<!-- do not edit by hand - make changes to _acknowledgements.Rmd instead -->\n",
+          readLines("front-and-back-matter/_acknowledgements.Rmd")),collapse = "\n"),
+  github = github_thanks(),
+  .open = "<<",
+  .close = ">>"
+),
+here::here("front-and-back-matter","_acknowledgements.md"))

### 2021-06-07 01-Chp-Background.Rmd
End of day: -2964

@@
 
-### Lipid fractions
+### Lipid fractions {#intro-lipid-fractions}
 
@@
 <!----------------------------------------------------------------------------->
-### Triangulating across study designs
+### Triangulating across study designs {#intro-triangulation}
 
@@
 
+<!-- TODO Ideally the two preprints for the CPRD and systematic review papers will go here -->
+
 &nbsp;
@@
 A.**, and L Schmidt.
-(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651.
+(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R.
+Journal of Open Source Software 5.54 2651.
 DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
@@
 A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
-As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).
+As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see Section \@ref(sys-rev-tools-intro) for more details).
 
@@
 Emily Hennessy (see Author Declarations in the front materials).
+<!-- TODO Need to create author declarations section -->
  [Under 2nd round of review at Prevention Science]
@@
 2020.
-“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv.
-DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_
+“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887.
+DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_
 
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
-[Accepted to PLOS One - need to update the citation]
+Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
 
@@
 _"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.
+
+&nbsp;
 

### 2021-06-07 02-Chp-Systematic-Review-Tools.Rmd
End of day: -3464
End of day: -3311
End of day: -2964

@@
 
+<!-- TODO I might need to make it clearer thatthe tool was always intended to search both databases, as medRxiv grew out of bioRxiv categories, and no relevant records identified by the search in medRxiv -->
+
 ## Lay summary
@@
 
+<!-- IDEA Could remake this using Diagrammr? -->
+
 (ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
@@
 ## Development
+
+<!-- IDEA Add timeline chart as seen here: https://bookdown.org/alecri/thesis/4-methods.html#sec:dosresmeta -->
 

### 2021-06-07 03-Chp-Systematic-Review.Rmd
End of day: -2964

@@
 
-(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]
+(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane20001931]
 
@@
 
+Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
+
+$$
+mg/dL = mmol/L \times{} Z
+$$
+where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
+For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+
 ### Risk of bias assessment {#risk-of-bias}
 
-Given the focus on triangulating different sources of evidence at risk of a diverse range of bias, a detailed and structured risk of bias assessment formed an important part of this review.
+A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation).
+To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.
 
-There has been a recent moved from
+There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018a; @sterne2016] and thus directly evaluating the internal validity of a study.
+Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
 
-Talk about move from checklist tools to more domain based methods
+This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.
 
-Many reviews use reporting guidelines instead - this is bad![@costa2011]
+As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
 
-Described here how tools work and how you get an overall judgement -. algorithm
+Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
+For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up.
+missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up.
+In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.
+
+In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
+The study design-specific tools are introduced and discussed in more detail in the following sections.
 
@@
 
-Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
+Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
 Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019],
 The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
+Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
+Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
+
+One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to
 
@@
 
-For non-randomised studies of interventions, I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to the RoB 2, it has a number of prompting questions per domain, with judgements includeing.
-Ideally, obs studies assesed in reference to an idealised randomised controlled trial.
-Futher, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
+Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including.
+Ideally, obs studies assessed in reference to an idealised randomised controlled trial.
+Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
 
-For non-randomised studies o
-I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.
+For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.
 
-non-randomized studies of interventions were assessed using the ROBINS-I tool, and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
-
-<!-- TODO Cite release version of this tool, and just use domain based approach -->
-
-Secondly, as mentioned in the introduction to this section, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
+Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] The motivation for this decision was two-fold.
+In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
+In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.
 
@@
 
-At present, no risk of bias assessment tool for Mendelian randomization studies is available.
+At present, no risk-of-bias assessment tool for Mendelian randomization studies is available.
 Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies.
@@
 
+Use the example of getting the cut-off points from the
+
 <!-- TODO move to results, and keep just a short bit here -->
@@
 
-### Statistical analysis methods
+### Analysis methods
 
-<!----------------------------------------------------------------------------->
+#### Simple meta-analysis
 
 Meta-analysis is an important method of . . .
+
+Both a fixed-effect and random-effects meta-analysis model was.
+
+For
 
@@
 Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.
+
+#### Dose-response analyses
+
+<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs > 3 categories -->
+
+Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
+for example, highest vs lowest quartile).
+while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
+
+Where possible, data for all exposure groups was extracted, and this.
+Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
+if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L)
+
+Note that
+
+#### Sensitivity analyses
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-.
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+### Dose response meta-analysis
+
+<!-- TODO Cite excluded studies and  -->
+
+Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls be
+
+<!-- TODO Include image -->
+
 ### Sources of heterogeneity
@@
 
+<!-- TODO Have a look at this - potentially move to triangulation chapter -->
+
 One key question for which multiple distinct sources of evidence were available were those looking at Laz
-
-<!-- TODO Have a look at this -->
 

### 2021-06-07 07-Discussion.Rmd
End of day: -2964

--- 2021-06-01 _main.Rmd
@@
----
-#####################
-## thesis metadata ##
-#####################
-title: |
-   Lipids and dementia:\
-   An investigation of their relationship
-
-author: Luke A McGuinness
-college: 
-degree: Doctor of Philosophy in Population Health Sciences
-degreedate: TBC
-abstract: |
-  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
-acknowledgements: |
-  `r paste(readLines("front-and-back-matter/_acknowledgements.Rmd"), collapse = '\n  ')`
-declaration: |
-  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
-dedication: For Brendan McHugh
-abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
-
-#######################
-## bibliography path ##
-#######################
-bibliography: 
-    - "bibliography/references.bib"
-csl: bibliography/nature.csl
-bibliography-heading-in-pdf: Bibliography
-
-#####################
-## PDF formatting  ##
-#####################
-abstractseparate: true  # include front page w/ abstract for examination schools?
-bib-humanities: false   #set to true if you want in-text references formatted as author-year
-doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
-draft: false # add as DRAFT mark in the footer?
-page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
-hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
-toc-depth: 2 # depth of heading to include in table of contents
-lof: true # list of figures in front matter?
-lot: true # list of tables in front matter?
-mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
-mini-toc-depth: 1
-mini-lot: false  # mini-list of tables by start of each chapter?
-mini-lof: false  # mini-list of figures by start of each chapter?
-
-params:
-  corrections: true # set false to stop applying blue background to blocks of corrections
-
-#####################
-## output options  ##
-#####################
-output:
-  bookdown::pdf_book:
-    template: templates/template.tex
-    keep_tex: true
-    citation_package: default 
-    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
-  bookdown::gitbook:
-    css: templates/style.css
-    download: ["pdf"]
-    output_dir: "docs"
-    split_bib: false
-    config:
-      toc:
-        before: |
-          <li><a href="./">Thesis - Draft</a></li>
-        after: |
-          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
-      sharing:
-        facebook: false
-        twitter: yes
-        all: false
-  bookdown::word_document2:
-    output_dir: "docs"
-    toc: true
-    toc_depth: 2
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false   
-link-citations: true
-documentclass: book
-
----
-
-```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
-source('scripts_and_filters/create_chunk_options.R')
-source("R/helper.R")
-options(scipen=999)
-```
-
-<!--
-Include the create_chunk_options chunk above at the top of your index.Rmd file
-This will include code to create additional chunk options (e.g. for adding author references to savequotes)
-If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
--->
-
-```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
-```
-
-<!--chapter:end:index.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Introduction {#intro-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-## Additional ideas
-
-### General
-
-* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published.
-Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished.
-
-* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.
-
-*
-
-### Background
-
-### medrxivr
-
-###
-
-&nbsp;
-
-<!--chapter:end:00-Chp-Introduction.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2:
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
-Science knows it doesn't know everything; otherwise, it'd stop.
-```
-
-(ref:dara-quote) --- Dara O'Briain
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/01-Code-Background.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-# Background, Theoretical framework, Aims & Objectives {#background-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-## Lay summary
-
-[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]
-
-Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
-Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition.
-The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change.
-Avoiding a risk factor does not guarantee that a person will not develop dementia but makes it less likely.
-A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
-The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
-
-This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them.
-It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
-Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction
-
-This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
-It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research.
-It then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.
-
-The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
-Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
-
-<!----------------------------------------------------------------------------->
-
-## Dementia
-
-<!----------------------------------------------------------------------------->
-
-### Definition and underlying pathologies {#underlying-pathologies}
-
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
-
-Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.
-Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
-Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
-
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
-
-The remaining 10-30% of cases are caused other dementia subtypes (e.g.
-Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).[@burns2009]
-
-<!----------------------------------------------------------------------------->
-
-### Diagnostic criteria {#diagnostic-criteria}
-
-Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]
-
-(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.
-
-```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
-
-Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
-The distinction between these memory scales and diagnostic criteria presented above should be noted.
-For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
-Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
-
-Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available (see Section \@ref(intro-treatments)).
-Cause-specific criteria exist for the diagnosis of dementia sub-types.
-For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
-
-<!-- ### Differing risk by sex -->
-
-<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->
-
-<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
-
-<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->
-
-<!----------------------------------------------------------------------------->
-
-### Public health importance
-
-Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only once without a proven treatment.
-
-Dementia also has a substantial economic impact.
-In 2015, the estimated total cost of dementia in England was £24.2 billion.
-Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]
-
-As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.
-
-<!----------------------------------------------------------------------------->
-
-### Treatments {#intro-treatments}
-
-Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020].
-At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.
-
-The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
-Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]
-
-### Risk factors
-
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @ansteya]
-
-The benefits of a prevention-based approach based on addressing these risk factors are well-studied.
-Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
-
-In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
-
-This thesis will focus on blood lipids as the primary risk factor of interest.
-The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the existing evidence for an association between lipids and dementia outcomes.
-
-<!----------------------------------------------------------------------------->
-
-## Serum lipids
-
-<!----------------------------------------------------------------------------->
-
-<!--- May need small bit here on converting from one measurement to the other i.e.
-mg/dL to mmol/L--->
-
-### Lipid fractions
-
-The blood lipid profile contains a range of component parts, or fractions.
-However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
-
-Triglycerides are the simplest and most common type of lipids found across the body.
-They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
-Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
-In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
-
-In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood.
-The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
-
-$$TC \approx LDLc - HDLc - kTG$$
-where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
-
-Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
-
-(ref:lipidLevels-scaption) Classification of blood lipid levels
-
-```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
-These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.
-
-<!----------------------------------------------------------------------------->
-
-### Statins
-
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R).
-This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.
-
-<!----------------------------------------------------------------------------->
-
-(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the
-
-(ref:statin-mechanisam-scap) Statin mechanism of action
-
-```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-### Other lipid regulating agents (LRA)
-
-There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
-However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
-
-<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->
-
-The most commonly used non-statin therapeutic is ezetimibe,[@kosoglou2005] which prevents intestinal absorption of cholesterol.
-However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).[@genest2006]
-
-A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
-They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
-
-Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.
-
-Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.
-
-```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Evidence for the association between blood lipids and dementia {#evidence-association}
-
-This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
-
-<!----------------------------------------------------------------------------->
-### Basic science
-
-A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]
-
-Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.
-
-<!----------------------------------------------------------------------------->
-### Observational studies
-
-By far the largest source of evidence on the relationship between comes from observational designs.
-Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a].
-With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]
-
-Several previous systematic review of observational studies examining the effect of lipids[@anstey] and lipid-regulating agents[@chu2018b;@poly2020c] on dementia outcomes have been performed.
-However, these reviews have several limitations.
-Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey;@poly2020c]
-
-<!----------------------------------------------------------------------------->
-
-### Randomised controlled trials
-
-In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.
-
-While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
-One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
-
-Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
-As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
-
-Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
-Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]
-
-<!----------------------------------------------------------------------------->
-
-### Mendelian randomisation
-
-Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
-
-1. the IV is associated with the exposure of interest (the relevance assumption);
-2. the IV and outcome do not share a common cause (the independence assumption); and
-3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).
-
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]
-
-Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In summary, multiple sources of evidence exist on the relationship between statins and dementia.
-In the next section, I introduce the synthesis of diverse sources of evidence as the theoretical framework used in this thesis.
-
-Multiples forms of evidenc
-
-<!----------------------------------------------------------------------------->
-
-## Theoretical framework: Evidence synthesis
-
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
-
-The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.
-
-This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
-Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:
-
-* Inclusion of grey literature
-* Triangulation across evidence sources
-* Individual patient data meta-analysis
-
-These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.
-
-<!----------------------------------------------------------------------------->
-
-### Inclusion of grey literature {#diverse-sources-preprints}
-
-The importance of including grey (or gray) literature in systematic reviews is widely acknowledged.
-Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]
-
-A important developing source of grey literature are preprints.
-Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
-
-One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
-Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
-
-In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic.
-However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
-
-<!----------------------------------------------------------------------------->
-### Triangulating across study designs
-
-As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own unique biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.
-
-This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.
-
-All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading).
-Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
-
-Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Individual patient data meta-analysis
-
-Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]
-
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
-
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]
-
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
-Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
-
-In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop.
-The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.
-
-This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
-<!----------------------------------------------------------------------------->
-
-## Thesis overview
-
-### Hypothesis
-
-Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.
-
-### Aims and objectives
-
-The specific research objectives that this thesis seeks to address are:
-
-* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
-* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
-* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
-* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
-
-### Structure {#thesis-structure}
-
-Chapters are self-contained, presenting the methods and results of that specific research project.
-They are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
-
--   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
--   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
--   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis.
-The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.
-
-An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)
-
-\blandscape
-<!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading).
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
-
-(ref:thesisOverview-scaption) Summary of studies included in this thesis
-
-```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape
-
-## Outputs from this thesis {#thesis-output}
-
-The outputs of this thesis are detailed below, and include peer-reviewed papers, presentations, and open-source evidence synthesis tools.
-
-### Contributions to the scientific literature
-
-During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and L Schmidt.
-(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R." Journal of Open Source Software 5.54 2651.
-DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
-
-A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
-As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see \@ref(sys-rev-tools-intro) for more details).
-
-&nbsp;
-
-_Hennessy, E.
-A., Acabchuk, R., Arnold, P.
-A., Dunn, A.
-G., Foo, Y.
-Z., Johnson, B.
-T., Geange, S.
-R., Haddaway, N.
-R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
-Welch, V.,  **McGuinness L.
-A.** (2020).
-Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
-MetaArXiv.
-DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_
-
-The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers.
-This piece was co-written with Dr.
-Emily Hennessy (see Author Declarations in the front materials).
-[Under 2nd round of review at Prevention Science]
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Higgins J.
-P.
-T.
-(2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method).
-DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
-
-The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
-See Appendix \@ref(appendix-robvis) for more details on this tool.
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Sheppard A.
-L.
-2020.
-“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv.
-DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_
-
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
-[Accepted to PLOS One - need to update the citation]
-
-&nbsp;
-
-For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
-
-&nbsp;
-
-### Presentations/Talks
-
-<!--- Include links here for slides for each talk/poster --->
-
-_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Accepted poster abstract, Alzheimer's Association International Conference 2021.
-
-&nbsp;
-
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_:
-Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
-
-&nbsp;
-
-_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.
-
-_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
-
-### Software {#outputs-software}
-**`medrxvir`**
-
-An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
-See Chapter \@ref(sys-rev-tools-heading) for more details.
-Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:
-
-```{r, eval = FALSE}
-# CRAN version
-install.packages("medrxivr")
-
-# Development version
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-**`robvis`**
-
-An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
-See Appendix \@ref(appendix-robvis) for more details.
-Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:
-
-``` {r, eval = FALSE}
-# CRAN version
-install.packages("robvis")
-
-# Development version
-devtools::install_github("mcguinlu/robvis")
-```
-
-&nbsp;
-
-## Summary
-
-This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.
-
-\newpage
-
-## References
-
-<!--chapter:end:01-Chp-Background.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
-Why are open source statistical programming  
-languages the best?
-
-Because they R.
-```
-
-(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
-
-# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r setup, include=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-library(medrxivr)
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!----------------------------------------------------------------------------->
-
-## Lay summary
-
-Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal.
-They represent an important source of scientific literature.
-A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way.
-Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction {#sys-rev-tools-intro}
-
-Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)).
-As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
-The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]
-
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
-As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
-
-This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv and bioRxiv preprints.
-The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
-As the majority of work on this aspect of this thesis is represented by lines of code (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)) this Chapter is an intentionally short, high-level summary of the work done on this project.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
-Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
-
-(ref:medrxivr-sr-scap) Role of `medrxivr` in a systematic review workflow
-
-```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-## Development
-
-### Success criteria {#success-criteria}
-
-The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
-The criteria were as follows:
-
-1.  reliable, reproducible and transparent search functionality, allowing for Boolean (AND/OR/NOT) operator logic;
-
-2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
-
-3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Alternative medRxiv/bioRxiv interfaces
-
-Prior development of this tool, an audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted.
-While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
-
-The first, a platform called Rxivist [@abdill2019], allows users to search preprints using keywords.
-However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface[^chp-systematic-review-tools-2] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
-
-[^chp-systematic-review-tools-2]: Available at <https://rxivist.org/>
-
-The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
-As such, the platform only returns the most recent `r comma(1000)` records by publication date.
-
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Early versions
-
-Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and the initial version of the `medrxivr` R package was released in February 2020.
-
-Early versions of the tool had a reliance on scraping data directly from the repository website.
-Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the repository website was regularly updated.
-
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
-This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Package infrastructure
-
-The `medrxvir` package was written in R using RStudio,[@rcoreteam2019] and followed development best-practice, including detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Usage
-
-The `medrxivr` R package is split into two component parts:
-
--   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
--   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
-
-The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy.
-This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.
-
-While the package allows for users to search both medRxiv and bioRxiv, as the process is identical for both, the examples in the sections are limited to the medRxiv repository.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Installation
-
-`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code:
-
-&nbsp;
-
-```{r, eval = FALSE}
-install.packages("medrxivr")
-```
-
-&nbsp;
-
-Alternatively, the development version of the package can be installed from GitHub:
-
-&nbsp;
-
-```{r, eval = FALSE}
-# install.packages("devtools") 
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Importing preprint metadata
-
-`medrixvr` provides two ways to access medRxiv data, as shown in Figure \@ref(fig:medrxivr-data-sources).
-The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Get a copy of the database from the live medRxiv API endpoint
-mx_data <- mx_api_content()  
-```
-
-&nbsp;
-
-The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Import a copy of the medRxiv data from the snapshot
-mx_data <- mx_snapshot()
-```
-
-&nbsp;
-
-Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
-The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
-Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
-
-(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources
-
-```{r medrxivr-data-sources, fig.pos="H", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Performing a search
-
-Once a local copy of the metadata is created, the first step in searching it is to create a search strategy.
-Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(…)`).
-
-&nbsp;
-
-```{r, eval = TRUE}
-# Create the search query
-topic1  <- c("dementia","alzheimer's")  # Combined with OR
-topic2  <- c("lipids","statins")        # Combined with OR
-
-myquery <- list(topic1, topic2)         # Combined with AND
-```
-
-&nbsp;
-
-For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
-There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
-Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
-"randomi*s*ation" vs "randomi*z*ation".
-
-Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Run the search
-results <- mx_search(mx_data,
-                     myquery)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Refining your search
-
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.
-__[CITATION NEEDED - PRISMA-S]__
-
-&nbsp;
-
-```{r, eval = FALSE}
-results  <- mx_search(mx_data,
-                      myquery, # Combined with OR
-                      report = TRUE)
-```
-
-```{r, eval = FALSE}
-## Found 1 record(s) matching your search.
-## 
-## Total topic 1 records: 224
-## dementia: 224
-## alzheimer's: 0
-## 
-## Total topic 2 records: 119
-## lipids: 90
-## statins: 33
-```
-
-&nbsp;
-
-This allows users to discover which terms in their search are contributing most to the total number of results returned.
-This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
-It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results.
-As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Exporting to a bibliography file
-
-In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
-While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
-
-For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
-
-```{r, eval = FALSE}
-mx_export(results, 
-          file = "medrxiv_export.bib",
-          report = TRUE)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Downloading the PDFs of relevant records
-
-`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
-`mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
-This functionality is similar to the "Find Full Text" feature offered by EndNote.
-
-&nbsp;
-
-```{r, eval = FALSE}
-mx_download(results,  # Search results, less excluded records
-            "pdf/")   # Directory to save PDFs to 
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-### Reception and future plans
-
-```{r, echo = FALSE, warning=FALSE}
-
-medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = "2021-12-01")
-
-medrxivr_downloads <- plyr::round_any(sum(medstats$count), 100, f = floor)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-```
-
-The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]
-
-The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-[^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
-
-[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>
-
-Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing.
-This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
-For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Limitations of `medrxivr`
-
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
-However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
-A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
-
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Role of open source tools in evidence synthesis
-
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
-
-<!----------------------------------------------------------------------------->
-
-## Summary
-
--   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
-
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
-
--   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
-
-\newpage
-
-## References
-
-<!--chapter:end:02-Chp-Systematic-Review-Tools.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
-```
-
-(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]
-
-# Systematic review of all available evidence {#sys-rev-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-## To Do
-
--   Examine how many times a primary study was included in a review\
--   Look at whether searching preprints made any difference to my results
--   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)
-
-## Extra studies to include:
-
-* Smeet et al. reference in the CPRD analysis
-* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
-* Statins and the risk of dementia Jick
-
-## Lay summary
-
-## Additional ideas
-
--   Evidence map - show the distribution of the different studies population across the world.
--   Living systematic review approach - update weekly based on medRxiv
-
-## Aims
-
-The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.
-
-Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
-
-Only by looking across all available evidence can
-
-Literature con
-
-## Methods
-
-### Search strategy
-
-We will systematically search electronic bibliographic databases to identify potentially relevant records.
-The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened.
-If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.
-
-The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-
-The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
-Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
-We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
-
-<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
-
-The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).
-
-### Study selection
-
-Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
-Full-text screening will also be completed in full by the primary author.
-A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
-Reasons for exclusion at this stage will be recorded.
-Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]
-
-#### Inclusion criteria
-
-We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
-Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants will be free (or assumed to be free) of dementia/MCI at baseline.
-Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits will be placed on the sample size of included studies.
-
-Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
-an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
-no dementia or dementia/MCI/dementia) based on this definition.
-
-No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods.
-Preprints and unpublished reports will be eligible for inclusion if relevant.
-Multiple publications resulting from the analysis of the same data will be included and grouped.
-
-#### Exclusion criteria
-
-Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
-Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded.
-Studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/MCI/dementia) will be excluded.
-Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status.
-Studies that are reported in insufficient detail (e.g.
-only in conference abstracts, new, letters, editorials and opinion) will be excluded.
-Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) will be excluded.
-
-Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
-
-### Data extraction
-
-Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
-
-Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
-
-This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.
-
-<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->
-
-### Risk of bias assessment {#risk-of-bias}
-
-Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
-
-I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.
-
-<!-- TODO Cite release version of this tool, and just use domain based approach -->
-
-Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
-
-<!-- TODO This next bit is not true -->
-
-At present, no risk of bias assessment tool for Mendelian randomization studies is available.
-Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob).
-Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
-
-Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
-
-<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->
-
-Many reviews use reporting guidelines instead - this is bad![@costa2011]
-
-<!----------------------------------------------------------------------------->
-
-## Studification
-
-In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-<!----------------------------------------------------------------------------->
-
-## Following up with authors
-
-As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man
-
-<!-- TODO move to results, and keep just a short bit here -->
-
-<!----------------------------------------------------------------------------->
-
-### Statistical analysis methods
-
-<!----------------------------------------------------------------------------->
-
-Meta-analysis is an important method of . . .
-
-Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.
-
-This anal
-
-Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.
-
-### Visualisation of results
-
-Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)
-
-A summary of this tool is contained in Appendix \@ref (), .
-
-### Assessment of added value of including preprint
-
-Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
-
-I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
-
-<!----------------------------------------------------------------------------->
-
-### Patient and public involvement
-
-<!----------------------------------------------------------------------------->
-
-## Results
-
-<!----------------------------------------------------------------------------->
-
-### Previous reviews
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, we examined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
-
-Put upSet plot here.
-
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
-
-<!----------------------------------------------------------------------------->
-
-### Screening results
-
-Following screening, XXX studies were included.
-
-The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.
-
-Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]
-
-As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
-Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
-This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually.
-The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*
-
-<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
-
-As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
-
-Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
-[@cohen1960: @gwet2008; @wongpakaran2013]
-
-How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In a two-by-two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
-
-$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-$$q = \frac{(A+C)+(A+B)}{2N}$$
-
--\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
-
-<!--- TODO Need example table here, showing relevant cells --->
-
-<!-- # ```{r agreementtableinter, echo = FALSE} -->
-
-<!-- # ``` -->
-
-<!-- # ```{r agreementtableintra, echo = FALSE} -->
-
-<!-- # ``` -->
-
-For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).
-
-The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]
-
-Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
-
-<!--- Cross check this with the actual numbers included --->
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO This needs to use the PRISMA2020 package -->
-
-```{r prisma-flow-setup, results="hide", message=FALSE}
-```
-
-(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process
-
-(ref:prisma-flow-scap) PRISMA Flowchart
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility.
-387 were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig)
-
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies
-
-XXXX studies met the criteria for inclusion in the review.
-
-Include here:
-
--   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
-
--   Summary of types of study
-
--   Summary of locations
-
--   Summary of diagnostic criteria used
-
--   Summary of risk of bias
-
--   Long table, horizontally. Newer version of flextable (GH) allows for PDF output
-
-A common theme across the studies was a lack of data on vascular dementia.
-This is particularly interesting as lipids and statins are primarily a vascular disease.
-There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
-For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of
-
-One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4.
-As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.
-
-In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
-
-### Converting risk ratios to odds ratios
-
-Include formulae and informed assumptions
-
-### Hazard ratios vs risk/odds ratios
-
-Not interchangeable in the context of systematic review.
-If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
-
-Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-
-The likely effect of this is that the overall effect measures are biased towards . . . . ?
-
-Can you predict the direction of effect from a
-
-Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
-
-<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
-
-Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
-
-### Risk of bias {#risk-of-bias-subheading}
-
-### Sources of heterogeneity
-
-Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
-
-### Publication bias {#sys-rev-pub-bias}
-
--   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
--   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult
-
-One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across
-
-### Triangualtion across evidence sources
-
-One key question for which multiple distinct sources of evidence were available were those looking at Laz
-
-A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use.
-In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)
-
-Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
-For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011]
-
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test
-
-### Added evidental value of including preprints {}
-
-<!-- Will to get actual numbers for this section -->
-
-There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
-While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
-
-Of interest,
-
-<!-- Triple check whether any of the studies have yet to be published -->
-
-This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
-It also means that searches are current - if the aim of systematic reviews is to
-
-While the total number of relevant studies found using this method was
-
-<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
-
-<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
-
-On further investigation, the argument that .
-
-It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
-
-However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
-
-While concerns have been raised that
-
-Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
-
-A common criticism of preprinted articles is that they have not formally been peer-reviewed.
-__[CITATION NEEDED]__ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
-
-> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
-
-References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
-
-The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
-
-While [__some__] preprint have subsequently been published, this does not cause any major issues.
-
-## Discussion
-
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.
-
-In addition, the a
-
-### Searching for/including Mendelian randomisation studies
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
-
-Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
-
-### Comments on the process
-
-As part of the reflective element of this thesis,
-
-Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
-
-Average time to complete a s
-
-However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
-
-Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.
-
-A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.
-
-### Inclusion of preprints
-
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted.
-Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.
-
-The added evidental value of including these preprints was highlighted in Section
-
-On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
-While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.
-
-### Open data sharing {#sys-rev-open-data}
-
-<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->
-
-<!--- Comment here on issues involved in extracting data --->
-
-### Original contribution to research
-
-I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
--   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
-As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
-
-### Comparison with other reviews
-
-Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->
-
-### Reviewing Mendelian randomisations studies
-
-While
-
-This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.
-
-Recent updates, such as a guide to reading and interpreting.
-However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
-
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for
-
-Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.
-
-### Strenghts and limitations
-
-Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy.
-An example is Larsson et al.
-2017[@larsson2017a], where the study examined the association between lipid fractions
-
-Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
-
-<!--- Findings from this chapter are used throughout the later chapters of this thesis.
-In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.
-From Sam abbotts--->
-
-Test
-
-## References
-
-<!--chapter:end:03-Chp-Systematic-Review.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
-When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
-```
-(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]
-
-# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-<!-- Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-options(scipen = 99)
-knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-```{r load-files, echo = FALSE}
-```
-
-<!-- ## Additional ideas -->
-
-<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
--->
-
-<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
-
-<!-- __Things we tried__ -->
-
-<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
-Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
-Need total number of those starting and average time to start.
--->
-<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
-<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
-<!-- - Allowing for time-varying confounders for binary covariates. -->
-
-<!-- __Things we could try__ -->
-
-<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
-<!-- - Examine Cramer et al. thesis and see what they did -->
-<!-- - Marginal structural models approach (a la J. Sterne) -->
-
-<!--------------------------------------------------------------------------->
-
-<!-- TODO Check lipid-regulating vs lipid regulating -->
-
-<!-- TODO Check all fig/table cross-references evaluate -->
-
-## Lay summary
-
-Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
-Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
-These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
-This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
-
-This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
-Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
-
-No evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
-In contrast, I found an increased risk of vascular and other (i.e.
-non-Alzheimer's) dementia with lipid regulating agent use.
-
-This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
-This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
-However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Introduction
-
-In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
-
-The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
-
-Firstly, it explicitly examines vascular dementia as an outcome.
-The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
-As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
-
-Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
-This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Methods
-
-### Study protocol
-
-An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
-
-<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
-
-<!-- TODO Add amendments to Appendix -->
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Data source {#cprd-data-source}
-
-Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
-The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
-Eu...
-- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
-Eu001 - Dementia in Alzheimer's disease with late onset).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
-Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
-
-(ref:readExample-scaption) Example of CPRD Read code hierarchy
-
-```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
-
-&nbsp;
-
-### Cohort definition
-
-This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
-However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
-
-Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
-These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-
-All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
-
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
-had less than one full day of follow-up).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Exposures
-
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
-
-A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class altered according to one of three criteria:
-
-- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
-- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
-- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Outcomes {#cprd-outcomes}
-
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
-The diagnosis date of the outcome was determined by the first record of a relevant code.
-
-<!----------------------------------------------------------------------------->
-(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
-Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
-
-(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes
-
-```{r decisionTree, include = FALSE}
-```
-
-```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
-
-&nbsp;
-
-### Covariates
-
-A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
-
-Demographic covariates adjusted for included age and gender.
-Age was calculated at date of entry into the cohort.
-Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
-To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
-Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
-
-Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
-A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
-To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
-
-Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
-The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
-
-Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
-
-<!-- IDEA Add more detail here on the missing data approach -->
-
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
-
-Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
-BMI), or where a code existed for the absence of the condition (e.g.
-categorical smoking status).
-This approach was necessary, as absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
-
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019a] to investigate the impact of multiple imputation on the results.
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Estimation methods
-
-A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
-
-$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
-
-where:
-
-* $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
-* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
-
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
-A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
-Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
-This is discussed in detail in the following section.
-
-<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
-
-<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}
-
-Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010a] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
-
-The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
-This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
-
-This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
-To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
-Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
-they enter the cohort and move into the exposed group on the same day).
-
-<!--------------------------------------------------------------------------->
-(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
-
-(ref:immortalTimeBias-scap) shortcap
-
-```{r, immortalTime, include = FALSE}
-```
-
-```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
-```
-<!--------------------------------------------------------------------------->
-
-### Time axis
-
-<!-- IDEA Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship.
-The main analyses presented all used age as the time axis.
-
-<!-- TODO Will need to expand on choice of time axis here -->
-
-<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
--->
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Sensitivity analyses
-
-The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
-To assess the robustness of the results, a number of sensitivity analyses were performed.
-These are described in the following sections.
-
-#### Control outcomes
-
-In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
-The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
-Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
-
-Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
-Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-
-Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
-Muscular backpain was chosen as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
-As such, if no evidence of an effect of statins on backpain is found in the analysis, then confidence in the results for the dementia outcomes is increased.
-
-Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
-
-<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
-
-<!----------------------------------------------------------------------------->
-(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
-Note the absence of any arrow between $X$ and $N$.
-In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).
-
-(ref:negativeOutcome-scap) DAG of ideal negative outcome
-
-```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
-library(dagitty)
-library(ggdag)
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
-  dagitty::dagitty("dag {
-    U -> N
-    C -> N
-    X <- U -> Y
-    X <- C -> Y
-    X -> Y
-    bb =\"-2.368,-2.972,2.597,2.726\"
-    C [pos=\"-0.3,0\"]
-    N [pos=\"0.5,1\"]
-    U [pos=\"-0.15,1.5\"]
-    X [exposure,pos=\"0,-1\"]
-    Y [outcome,pos=\"0.5,-1\"]
-  }"
-) %>% ggdag_classic() +
-  theme_dag()
-
-,
-height = 3
-)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))
-
-```
-<!----------------------------------------------------------------------------->
-
-#### Impact of additional covariates
-
-To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
-
-&nbsp;
-
-#### Sensitivity cohorts
-
-Two sensitivity cohorts were also created.
-The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
-The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
-
-<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
-
-&nbsp;
-
-#### Statin properties
-
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).
-
-To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
-
-&nbsp;
-
-#### Impact of dementia code lists
-
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
-
-This previous study used a propensity matching approach to estimate the effect of statins on a range of outcomes, and a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but no evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
-
-The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-## Results
-
-### Patient characteristics
-
-```{r characteristics, echo = FALSE}
-```
-
-```{r attritionFigure, include = FALSE}
-```
-
-Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
-
-(ref:cprdFlowchart-scap) Attrition of CPRD participants
-
-<!-- This figure needs to have comma seperated numbers in order to agree with text. -->
-
-```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition_test.png"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia).
-The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-
-\blandscape
-<!--------------------------------------------------------------------------->
-(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
-
-(ref:cprdCharacteristics-scaption) Patient characteristics by drug class
-
-```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-\elandscape
-
-A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
-Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
-
-<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
-
-<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
-
-(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
-
-```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-```{r missing-data, echo = FALSE}
-```
-
-```{r azd-text, echo = FALSE}
-```
-
-Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`
-
-&nbsp;
-
-### Primary analysis
-
-The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
-
-For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
-
-(ref:cprdPrimary-scap) Results from primary analyses of CPRD data
-
-```{r p1Figure, include = FALSE}
-```
-
-```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_p1.jpeg"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
-
-__Alzheimer's disease__
-
-No evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
-
-&nbsp;
-
-__Non-Alzheimer's disease dementias__
-
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
-Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
-
-&nbsp;
-
-__All-cause dementia__
-
-For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
-There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
-
-&nbsp;
-
-### Sensitivity analyses
-
-The results of the series of sensitivity analyses performed are described in the following sections.
-
-#### Complete case versus imputed data
-
-In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
-It should be noted that due to the large amount of missing data (e.g.
-`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
-In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009b]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
-
-(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
-
-```{r completeCase, include= FALSE}
-```
-
-```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_complete_case.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Control outcomes
-
-```{r controlOutcomes, echo = FALSE, message = FALSE}
-```
-
-Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
-The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
-
-For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
-However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:controlOutcomeFig-cap) Results of control outcome analysis.
-
-(ref:controlOutcomeFig-scap) Results of control outcome analysis
-
-```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_control_outcomes.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Impact of additional covariates
-
-The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
-
-These models were used to estimate the impact of adjustment for additional covariates.
-Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
-
-Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
-In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
-
-(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
-
-```{r unadjustedComparison, include=FALSE}
-```
-
-```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_unadjusted.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity cohorts: Entry year
-
-When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
-
-(ref:diagnosisTypeFig-scap) Sensitivty analus
-
-```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/fp_cohort_entry.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
-While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
-
-(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
-
-```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Sensitivity cohorts: Pregnancy
-
-In the second sensitivity cohort, removing participants coded as female and aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
-
-(ref:pregnancyFig-scap) Comparison of pregnancy analysis
-
-```{r pregnancy, include = FALSE}
-```
-
-```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_pregnancy.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Statin properties
-
-In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
-Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
-
-(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
-
-```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
-Additionally, in the AD outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
-
-(ref:statinTypeFig-scap) Analysis stratified by statin properties
-
-```{r statinType, include = FALSE}
-
-```
-
-```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_sta_type.jpeg"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Comparing codelists
-
-```{r smeethText, include = FALSE}
-```
-
-When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
-
-However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
-Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
-The joining lines showing the overlap between the categories in the two analyses.
-
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-```{r sankeydiagram, include=FALSE}
-```
-
-```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
-```
-<!----------------------------------------------------------------------------->
-
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
-
-&nbsp;
-
-## Discussion
-
-<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
-
-### Summary of findings
-
-Lipid-regulating agents showed no evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
-
-The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
-When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
-
-<!-- QUESTION Why are fibrates different? -->
-
-<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
-
-<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
-However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Interpretation of results
-
-This section will expand on a potential explanation for the observed results detailed above.
-However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(hold)) and the individual patient data analysis (Chapter \@ref(hold)), see Section \@ref(hold).
-
-A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
-While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
-
-<!----------------------------------------------------------------------------->
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
-
-(ref:indicationBias-scap) Confounding by indication causal diagram
-
-```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
-dagitty::dagitty("dag {
-  Statin [exposure,pos=\"0.000,0.000\"]
-  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
-  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
-  \"Uncontrolled variable\" -> Statin
-  \"Uncontrolled variable\" -> \"Vascular outcomes\"
-}") %>% ggdag_classic(size = 6) +
-  xlim(-0.5,3) +
-  geom_text(data = data.frame(x = 0.316392393234329,
-                              y = 0.537705383514239,
-                              label = "Prompts"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 1.65891420807966,
-                              y = 0.537705383514239,
-                              label = "Causes"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_curve(data = data.frame(x = 0.220612676359188,
-                               y = -0.000788829298738025,
-                               xend = 1.45,
-                               yend = -0.00157828084913909),
-             mapping = aes(x = x,
-                           y = y,
-                           xend = xend,
-                           yend = yend),
-             linetype = "dashed",
-             angle = 0L,
-             size = 0.6,
-             colour = "black",
-             curvature = 0,
-             arrow = structure(list(angle = 0,
-                                    length = structure(0,
-                                                       class = "unit",
-                                                       valid.unit = 2L,
-                                                       unit = "inches"),
-                                    ends = 2L,
-                                    type = 2L),
-                               class = "arrow"),
-             inherit.aes = FALSE,
-             show.legend = FALSE) +
-
-  theme_dag(),
-width = 8,
-height = 3)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
-```
-<!----------------------------------------------------------------------------->
-
-In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
-
-Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
-The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
-This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
-
-A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
-
-Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-I also adjusted for several additional potential baseline variables.
-However, important confounding variables for which I have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
-
-On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
-It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
-
-<!-- IDEA talk about time-varying confounding here -->
-
-In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Strengths and limitations
-
-The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
-Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
-Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
-This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
-
-However, the findings of this analysis are subject to several limitations.
-There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
-As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
-
-Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
-This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
-
-<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
-
-<!-- IDEA there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
--->
-
-<!--------------------------------------------------------------------------->
-
-<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
-
-<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
-
-<!-- However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
--->
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
--->
-
-<!-- This hasn't been done! Plus I do not think this is the case -->
-
-<!--------------------------------------------------------------------------->
-
-<!--------------------------------------------------------------------------->
-<!-- &nbsp; -->
-
-<!-- IDEA Issues with large-scale EHR databases -->
-
-<!-- __Missclassification__ -->
-
-<!-- __Coding quality in the CPRD__ -->
-
-<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
-
-<!-- There is the possibility of ascertainment bias -  -->
-
-<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Enabling easy synthesis of this analysis {#cprd-data-avail}
-
-In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
-
-All code, Read codelists and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
-<!-- TODO Archive on Zenodo.
--->
-
-The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
-
-Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
-
-This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Conclusions
-
-This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
-
-It found no evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
-However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
-
-This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
-Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
-
-Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
-
-\newpage
-
-## References
-
-<!--chapter:end:04-Chp-CPRD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Individual participant data meta-analysis {#ipd-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-## Methods
-
-### Data sources
-
-Several cohort studies were approach
-
-<!-- Need exact number approach -->
-
-As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.
-
-Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get
-
-Each should have:
-
-* Description (including observation period, numbers, numbers with outcome, etc)
-* Whether they are a known genetically at-risk cohort
-*
-
-### Epic Norfolk
-
-The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]
-
-```{r tests, }
-
-```
-
-Different approaches to combining subgroups. [@fisher2017]
-
-## Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-<!--- Inlcude CPRD analysis here, but dou --->
-
-## Data cleaning
-
-## Discussion
-
-Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all.
-Will also need to comment on the additional tactics used.
-
-This is likely due to my junior position as a early a
-
-Range of reasons why data is not readily available.
-
-Unfortunately,
-
-As part of this, an analysis of
-
-## Discussion
-
-Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.
-
-<!--chapter:end:05-Chp-IPD-Analysis.Rmd-->
-
 ---
@@
 
+<!----------------------------------------------------------------------------->
 ## Triangulation across exisiting evidence and evidence produced in this thesis
+
+### Overview of triangulation {#triangulation-overview}
 
@@
 Summary table of different studies and results
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Use of concensus panel to bring everything together
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Summary of findings (and implications for policy makers)
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Public involvement and engagement {#disc-PPI}
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Future work
 
-## Overall conclusions
-
-<!--chapter:end:97-Discussion.Rmd-->
-
-`r if(!knitr:::is_latex_output()) '# Bibliography {-}'`
-
-<!-- If you're outputting to LaTeX, the heading and references will be generated by the OxThesis LaTeX template.
-This .Rmd file serves only to add the References headline to gitbook output before the references are added by pandoc -->
-
-```{block type='savequote', include=knitr::is_latex_output(), echo = TRUE}
-Lasciate ogne speranza, voi ch'intrate. . .
-```
-
-# Bibliography
-
-<div id="refs"></div>
-
-<!--chapter:end:front-and-back-matter/98-references.Rmd-->
-
-`r if(knitr:::is_latex_output()) '\\startappendices'`
-
-`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
-
-<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
-
-# By Chapter {#chapter-appendix-heading}
-
-## Chapter \@ref(intro-heading) {#appendix-into}
-
-### Publications beyond the scope of this thesis {#appendix-publications}
-
-__Peer reviewed__
-
-  * McGuinness & Sheppard. Comparison of pairwise
-
-  * PRISMA main paper
-
-  * PRISMA E&E
-
-  * PRISMA 2020 software
-
-  * COVID Suicide Living Review
-
-  * Data extraction tools systematic review
-
-<!-- Essentially, look at the Trello -->
-__Under review/Preprints__
-
-  * MSc Paper on systematic reviews of this thesis topic
-
-  *
-
-### Involvement of patients and the public {#appendix-ppi}
-
-Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.
-
-Additionally,
-
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
-
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
-
-### Search strategy {#appendix-search-strategy}
-
-### Code to search preprints {#appendix-medrxivr-code}
-
-<!-- Double check this is the final code used -->
-
-```{r, eval = FALSE}
-
-library(medrxivr)
-
-mx_data <- mx_api_content(to_date = "2019-09-01")
-
-bx_data <- mx_api_content(server = "biorxiv",
-                                    to_date = "2019-09-01")
-
-topic1 <- c("statin",
-            mx_caps("ldl"),
-            mx_caps("hdl"),
-            mx_caps("TG"),
-            paste0("\\b",mx_caps("TC"),"\\b"),
-            "ezetim",
-            "lipoprotein",
-            "lipid",
-            "cholesterol")
-
-topic2 <- c(mx_caps("dementia"),
-            mx_caps("alzheim"),
-            mx_caps("MCI"),
-            mx_caps("mild cognitive"))
-
-query <- list(
-  topic1,
-  topic2
-)
-
-test <- mx_search(bx_data, query)
-
-test2 <- mx_search(mx_data, query)
-
-```
-
-Note
-
-### MR risk of bias tool {#appendix-mr-rob}
-
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
-
-## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-
-### Amendments to protocol {#appendix-cprd-amendments}
-
-### Code lists
-
-## Chapter \@ref(discussion-heading)
-
-### Catalogue of failures
-
-Short section detailing the things I tried to do but which did not work.
-
+&nbsp;
 <!----------------------------------------------------------------------------->
 
-# Other Appendix {#other-appendix-heading}
-
-## Software used to create this thesis
-
-This thesis was written in RMarkdown.
-Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]
-
-All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
-
-## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
-
-### Introduction
-
-Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
-A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
-
-Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
-Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
-Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
-For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.
-
-Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
-Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
-
-The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).
-
-### Development
-
-Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
-Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback.
-This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
-The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]
-
-### Installation
-
-A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:
-
-```{r, eval = FALSE}
-install.packages("robvis")
-```
-
-As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version.
-The most recent development version can be install from GitHub using:
-
-```{r, eval = FALSE}
-devtools::install_github("mcguinlu/robvis")
-```
-
-### Usage
-
-`robvis` contains two main functions.
-The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
-The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.
-
-A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
-A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)
-
-Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
-
-__NEED TO ADD DATA HERE!__
-
-```{r, eval = FALSE}
-
-rob_traffic_light(data = data_rob2,
-                  tool = "ROB2",
-                  psize = 15)
-```
-
-```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
-
-plotdata <- robvis::data_rob2
-
-tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)
-
-robvis::rob_save(tfplot, 
-                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
-```
-
-Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
-
-```{r, eval = FALSE}
-
-rob_summary(data = data_rob2,
-            tool = "ROB2", 
-            overall = TRUE)
-
-```
-
-```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
-
-sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)
-
-robvis::rob_save(sumplot,
-                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-```
-
-A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)
-
-`r br`
-
-```{r robvisarguments, echo = FALSE, eval = TRUE}
-
-arguments <- data.frame(stringsAsFactors=FALSE,
-              argument = c("data", "tool", "colour", "overall", "weighted",
-                           "psize"),
-     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
-           rob_summary = c("X", "X", "X", "X", "X", ""),
-           Description = c(
-"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
-"Defines the risk of bias assessment tool used.
-The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
-Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
-"Defines the colour scheme for the plot.
-The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`).
-Alternatively, users can specify their own colour scheme e.g.
-`colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
-"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
-"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
-"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
-
-if(doc.type == "docx"){
-
-  knitr::kable(arguments,escape = T,
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))
-
-}else{
-
-  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-             align = c("l","c","c","l"),
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
-  column_spec(4,"5cm") %>%
-  kable_styling(font_size = 9, 
-                bootstrap_options = c("striped", "hover"),
-                latex_options = c("repeat_header", "striped"))
-}
-
-```
-
-`r br`
-
-### Reception and Future Plans
-
-```{r, echo = FALSE}
-robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
-
-robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-
-```
-
-As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times.
-It has been well received but the systematic review community, and has been cited frequently in the published literature.
-A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods.
-A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]
-
-While `robvis` is a stable package, a range of additional functionality could be added.
-At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
-However, following user-driven demand, this functionality is in development and will be available in the near future.
-Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
-The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
-
-<!--chapter:end:front-and-back-matter/99-appendices.Rmd-->
+## Overall conclusions

### 2021-06-07 front-and-back-matter/99-appendices.Rmd
End of day: -2964

@@
 <!----------------------------------------------------------------------------->
-## Chapter \@ref(intro-heading) {#appendix-into}
+## Chapter \@ref(background-heading) {#appendix-into}
 
@@
 __Peer reviewed__
-
-  * McGuinness & Sheppard. Comparison of pairwise
 
@@
 
-<!-- Essentially, look at the Trello -->
+<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->
+
 __Under review/Preprints__
@@
 
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-tools}
+## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
 <!----------------------------------------------------------------------------->
@@
 ### Search strategy {#appendix-search-strategy}
+
+Impor
 
@@
 
-<!-- Double check this is the final code used -->
+<!-- TODO Double check this is the final code used -->
 

### 2021-06-13 01-Chp-Background.Rmd
End of day: -3162

@@
 
-$$TC \approx LDLc - HDLc - kTG$$
+$$TC \approx LDLc + HDLc + kTG$$
 where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

### 2021-06-13 03-Chp-Systematic-Review.Rmd
End of day: -3162

@@
 
-The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the Univeristy ).
+The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
 We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
@@
 -->
+
  Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
@@
 
-### Following up with authors
+### Following up with authors {#contacting-authors}
 
@@
 
-#### Simple meta-analysis
+#### Standard meta-analysis
 
@@
 
-Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.
+Need formula here, and description of different methods and quarrels regarding disctinction fixed effect vs random effects meta-analyses.
 
-This anal
-
-Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.
+This analytical approach was used for
 
@@
 
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs > 3 categories -->
+<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
+<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.  -->
 
@@
 for example, highest vs lowest quartile).
+<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
+-->
  while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
@@
 Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L)
+if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).
 
-Note that
+<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
+A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
+Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
+Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
+
+Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
+Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).
 
 #### Sensitivity analyses
+
+I conducted a leave one out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED -->
+
+In addition,
 
@@
 <!----------------------------------------------------------------------------->
+
+### Deviations from the protocol
+
+A dose response meta-analysis was not planned, marking a departure from the register protocol. <!-- TODO Check this is accurate -->
 
@@
 
-<!-- TODO This needs to use the PRISMA2020 package -->
-
 ```{r prisma-flow-setup, include = FALSE}
@@
 
-(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process
+(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
+The different contributions of databases and preprint servers to the review are indicated.
 
-(ref:prisma-flow-scap) PRISMA Flow Diagram
+(ref:prisma-flow-scap) PRISMA flow diagram
 
@@
 
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] shown in Figure \@ref(prisma-flow-fig), shows the movement of articles through the review.
+To illustrate the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
+
+Of note, preprints and published papers reporting the same study were not considered duplicate records.
+Instead, they were considered as different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+
 ### Characteristics of included studies
@@
 
--   Summary of locations
+-   Summary of locations (use evidence map)
 
@@
 
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019d; @wilkinson2018b]
 

### 2021-06-13 05-Chp-IPD-Analysis.Rmd
End of day: -3464
End of day: -3162

--- 2021-04-09 06-Chp-IPD-Analysis.Rmd
@@
 
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
+
 # Individual participant data meta-analysis {#ipd-heading}
@@
 
+Is there a good way to visualise input of cohorts into an IPD analysis?
+
 ## Methods
+
+Talk about how different covariates were managed across cohorts,
+
+Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
 
@@
 
-This is likely due to my junior position as a early a
+This is likely due to my junior position as a early career research combined with the impact
 
 Range of reasons why data is not readily available.
+Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
+primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
 
@@
 
-Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.
+### Reflections on data access
+
+Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and

### 2021-06-14 01-Chp-Background.Rmd
End of day: -2951

@@
 It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research.
-It then provides background on blood lipids and lipid-modifying treatments, and summarises the existing evidence on the effect of these exposures on dementia outcomes.
+It then provides background on blood lipids and lipid-modifying treatments, and summarises the types of evidence used to examine the effect of these exposures on dementia outcomes.
 
@@
 Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
+Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
 
-The remaining 10-30% of cases are caused other dementia subtypes (e.g.
-Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
+The remaining 10-30% of cases are caused by other dementia subtypes (e.g.
+Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
 Parkinson's disease).[@burns2009]
@@
 
-Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expect progression and potential treatment options available (see Section \@ref(intro-treatments)).
+Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
 Cause-specific criteria exist for the diagnosis of dementia sub-types.
@@
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only once without a proven treatment.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only one without a proven cure.
 
@@
 
-<!--- May need small bit here on converting from one measurement to the other i.e.
-mg/dL to mmol/L--->
-
 ### Lipid fractions {#intro-lipid-fractions}
@@
 They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
-Low-Density-Lipoprotein-cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
-In contrast, High Density-Lipoprotein-cholestel (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
+Low-density-lipoprotein cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
+In contrast, High density-lipoprotein cholesterol (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
 
@@
 These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.
+Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.
 
@@
 
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R).
-This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.
+<!-- TODO Need more on this: maybe a diagram of the pathway -->
+
+<!-- REVIEW [JH] This section seems very short for such a key entity in your thesis.
+I don’t know exactly what else there is to say about statins, but I recommend expanding it a bit, The second sentence is gobbledygook to me.
+-->
+
+Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
+This conversion limits the rate at which cholesterol can be produced, enabling statins to reduce effectively the production of LDL cholesterol.
 
@@
 
-```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
+knitr::include_graphics(file.path("figures/background/statinPath.png"))
 ```
@@
 
-There are a range of other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
+There are several other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
 However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
@@
 
-A second example are fibrates, used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
+Fibrates provide a second example of non-statin therapy.
+They are used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
 They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
@@
 
-Multiples forms of evidenc
-
 <!----------------------------------------------------------------------------->
@@
 The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.
+The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
 
 This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
-Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:
+Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:
 
-* Inclusion of grey literature
+* Inclusion of preprints
 * Triangulation across evidence sources
@@
 
-### Inclusion of grey literature {#diverse-sources-preprints}
+### Inclusion of preprints  {#diverse-sources-preprints}
+
+<!-- TODO Incorporate Julian's comments below -->
+
+<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
+Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
+It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
+Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
+We have no clear and widely used definition of grey literature.
+-->
 
@@
 As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own unique biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.
+However, each method is limited by its own biases.
+Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
+A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
 
@@
 
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
+In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
 
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]
+An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
 
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
+Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
 Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
@@
 
-This thesis will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
+I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
 Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
@@
 
-### Hypothesis
+### Aims and objectives
 
-Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.
-
-### Aims and objectives
+The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes
 

### 2021-06-14 03-Chp-Systematic-Review.Rmd
End of day: -2951

@@
 
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
-[@cohen1960: @gwet2008; @wongpakaran2013]
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.
 
-Gwet's AC1 is defined as
+Gwet's AC1 is defined as:
 
@@
 
-How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
 
@@
 
-As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man
+Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
+This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
+
+This was particular important for the dose response meta-analysis, we
 
@@
 
+<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
+
 <!-- TODO Do I initially want to fit a linear relationship across categories and  -->
@@
 Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).
+
+When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it.
+Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
+
+we assumed the width of the category to be the same as the adjacent category.
+When the lowest category was open ended, we set the lower boundary to zero.
 
@@
 
-<!-- # ```{r agreementtableinter, echo = FALSE} -->
+&nbsp;
 
-<!-- # ``` -->
+<!----------------------------------------------------------------------------->
+(ref:agreeInter-caption) Inter-rater agreement on a subset of ~10% of records, illustrating high accuracy.
 
-<!-- # ```{r agreementtableintra, echo = FALSE} -->
+<!-- TODO Include AC1 result in caption above -->
 
-<!-- # ``` -->
+(ref:agreeInter-scaption) Inter-rater agreement
 
-For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).
+```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
 
-The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]
+&nbsp;
 
-Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated.
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
+
+(ref:agreeIntra-scaption) Inter-rater agreement
+
+```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
+Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
+The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
+
+Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`) were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
+
+Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
 
@@
 
-### Added evidental value of including preprints {}
+### Added evidental value of including preprints {sys-rev-including-preprints}
 
@@
 
+<!-- TODO This section will be informed by the review published as a preprint -->
+
 Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.

### 2021-06-14 05-Chp-IPD-Analysis.Rmd
End of day: -2951

@@
 
+## Lay Summary
+
+## Introduction
+
 Is there a good way to visualise input of cohorts into an IPD analysis?
@@
 ## Methods
+
+As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man
 
@@
 
-## Risk of bias assessment
+Several DPUK cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
+
+See
+
+### Risk of bias assessment
 
@@
 
-## Data cleaning
+### Data cleaning
 
@@
 
-Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all.
+Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responded if at all.
 Will also need to comment on the additional tactics used.
@@
 
-## Discussion
-
 ### Reflections on data access
@@
 Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
+
+### Study within a review
+
+In future, it could have been worth running a "study within a review", such as that used to examine whe
+
+https://bmjopen.bmj.com/content/9/1/e025273

### 2021-06-14 index.Rmd
End of day: -2951

@@
 dedication: For Brendan McHugh
+covidStatment: |
+  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
 abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations

### 2021-06-15 01-Chp-Background.Rmd
End of day: -2772

@@
 output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::word_document2:
@@
     number_sections: false 
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 
-### Statins
+### Statins {#intro-statins}
 
-<!-- TODO Need more on this: maybe a diagram of the pathway -->
+Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
+This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
 
-<!-- REVIEW [JH] This section seems very short for such a key entity in your thesis.
-I don’t know exactly what else there is to say about statins, but I recommend expanding it a bit, The second sentence is gobbledygook to me.
--->
-
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
-This conversion limits the rate at which cholesterol can be produced, enabling statins to reduce effectively the production of LDL cholesterol.
+&nbsp;
 
@@
 
-(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the
+(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.
 
@@
 
-```{r statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
+```{r statin-mechanisam, echo = FALSE, results="asis",fig.pos = "H", fig.align = 'center', fig.cap='(ref:statin-mechanisam-cap)', out.width='50%', fig.scap='(ref:statin-mechanisam-scap)'}
 knitr::include_graphics(file.path("figures/background/statinPath.png"))
 ```
+
+&nbsp;
+
+Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)).
+Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g.
+ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
+rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+<!-- TODO Review the look and feel of this table -->
+
+(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.
+
+(ref:statinOverview-scaption) Overview of common statins
+
+```{r statinOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-&nbsp;
 &nbsp;

### 2021-06-15 02-Chp-Systematic-Review-Tools.Rmd
End of day: -2772

@@
 
-```{r medrxivr-sr, echo = FALSE, results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='100%', fig.scap='(ref:medrxivr-sr-scap)'}
+```{r medrxivr-sr, echo = FALSE, fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
 knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))

### 2021-06-15 03-Chp-Systematic-Review.Rmd
End of day: -2772

@@
 ---
-
 ```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
@@
 
-As introduced in previous chapters,
+The importance of
 
-<!-- IDEA Evidence map - show the distribution of the different studies population across the world.
-Distribution will have to be of participants, not primary authors.
-Though could use to show how data is being used globally -->
+I found that
 
+The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
+
+<!----------------------------------------------------------------------------->
 ## Introduction {#sys-rev-intro}
@@
 An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
-<!-- TODO Need to actually attach each search strategy, and detail the specific databases used.
+<!-- TODO Need to actually attach each search strategy.
 See search strategy results.
@@
 <!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic. For a full list of search terms, see Appendix \@ref()
+(ref:searchOverview-caption) Summary of systematic search by topic.
+The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
 
@@
 
-The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
+The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
 We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
@@
 The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
+the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
 <!-- TODO how were these searched?
--->
+Date and other range -->
 
- Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
+ Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
 We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
 
-<!-- TODO Look at citationchaser for this, but have a cut-off publication date of  -->
+<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->
 
@@
 
-Records weree imported into Endnote and deduplicated using the method outlined in Bramer et al.
+Records were imported into Endnote and deduplicated using the method outlined in Bramer et al.
 (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
@@
 Full-text screening will also be completed in full by the primary author.
-A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
-Reasons for exclusion at this stage will be recorded.
-Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
+A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
+Reasons for exclusion at this stage were recorded.
+Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
 A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]
@@
 
-Participants will be free (or assumed to be free) of dementia/MCI at baseline.
-Studies of any duration will be included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+Participants were free (or assumed to be free) of dementia/MCI at baseline.
+Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
 No limits will be placed on the sample size of included studies.
 
-Eligible studies will define dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+<!-- TODO do i actually want to include MCI?
+-->
  For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
@@
 
-No limitations will be imposed on publication status, publication date, venue or language, although we will require sufficiently detailed reports of the studies to be able to examine their methods.
-Preprints and unpublished reports will be eligible for inclusion if relevant.
-Multiple publications resulting from the analysis of the same data will be included and grouped.
+No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
 
@@
 
-Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
+Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
 
@@
 
+Multiple publications resulting from the analysis of the same data will be included and grouped ().
+
 In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
@@
 
-we assumed the width of the category to be the same as the adjacent category.
-When the lowest category was open ended, we set the lower boundary to zero.
+I assumed the width of the category to be the same as the adjacent category.
+When the lowest category was open ended, I set the lower boundary to zero.
 
@@
 
-### Search results
+### Search and screening results
 
-Detail
+`r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.
 
-### Previous reviews
-
-<!-- TODO Not sure this is the best place for this -->
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, we examined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
-
-Put upSet plot here.
-
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
+<!--- Cross check this with the actual numbers included --->
 
@@
 
-### Screening results
+```{r prisma-flow-setup, include = FALSE}
+```
+
+(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
+The different contributions of databases and preprint servers to the review are indicated.
+
+(ref:prisma-flow-scap) PRISMA flow diagram
+
+```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+
+<!----------------------------------------------------------------------------->
+
+Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
+`r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened.
+\@ref(fig:prisma-flow-fig)
+
+<!----------------------------------------------------------------------------->
+
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] shown in Figure \@ref(prisma-flow-fig), shows the movement of articles through the review.
+To illustrate the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
 
@@
 
-As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
+As part of our our forward snowballing exercise (where articles citing an included study are cited), Irecorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
 Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
@@
 
+<!-- TODO Actually do this! -->
+
 <!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
 
-As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
+As a summary of the duplication of work in this area, Ilooked at how many reviews a single included study had previously been included in.
 
@@
 
-&nbsp;
-
-&nbsp;
-
 <!----------------------------------------------------------------------------->
@@
 For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
+Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
 The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
@@
 Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
-
-<!--- Cross check this with the actual numbers included --->
-
-<!----------------------------------------------------------------------------->
-
-```{r prisma-flow-setup, include = FALSE}
-```
-
-(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
-The different contributions of databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-Following de-duplication, the titles and abstracts of `r hold()` records were assessed for eligibility.
-`r hold()` were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig)
-
-<!----------------------------------------------------------------------------->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] shown in Figure \@ref(prisma-flow-fig), shows the movement of articles through the review.
-To illustrate the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
 
@@
 
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test
+Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test
 
@@
 
-###
+### Previous reviews
+
+<!-- TODO Not sure this is the best place for this -->
+
+**Will need to include something in the methods section on this**
+
+As part of this analysis, Iexamined the overlap between different published reviews on this topic.
+
+Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
+
+<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
+
+An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
+
+Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
+So for example, XXXX records were captured both by the XXXX review and the XXXX review.
+
+Where the matrix has just a single point highlighted, this shows the records unique to that review.
+
+The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
+
+Our review is presented as the last point on this plot, and captured XXXX records
+
+The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
+The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
+
+<!--- Take a stand here! --->
+
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
+While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
+While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
+
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+
+Does it also cause issues in terms of self-report?
+
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
 ### Inclusion of preprints
@@
 
+<!----------------------------------------------------------------------------->
 ### Open data sharing {#sys-rev-open-data}
@@
 
+<!----------------------------------------------------------------------------->
 ### Original contribution to research
@@
 
+<!----------------------------------------------------------------------------->
 ### Comparison with other reviews
@@
 
-Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
 
@@
 
-<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->
+<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
 
+<!----------------------------------------------------------------------------->
 ### Reviewing Mendelian randomisations studies
@@
 
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for
+Problems with overlapping samples in reviews of Mendelian randomisation studies in that Imay be double counting participants - for
 
@@
 
+<!----------------------------------------------------------------------------->
 ### Strenghts and limitations
@@
 
+<!-- TODO Maybe need to integrate with the section immediately above.
+Best option probably to move the section above to the end of this section, highlighting that while these studies were included, it was not easy given a lack of resources for MR studies -->
+
 As a form of analysis that lends itself to multiple comparison, there is a strong
 
-Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
+Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
+[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
+The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
+Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
+This may bias reviews as the analysising multiple risk factors at a time becomes more common.
 
-Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
+<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
 
-Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy.
-An example is Larsson et al.
-2017[@larsson2017a], where the study examined the association between lipid fractions with Azlheimer's disease.
+Is it a big issue that the studies have the same underlying datasets? <!--- TODO check discussion from Matt Lee thesis, in email --->
 
-Potentially the use of methods such as snowballing (forwards and backwards citation chasing) should attenuate the bias introduced by this method.
-
-However, in future reviews, a dedicated search for "risk factors" and "dementia" and "
+Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
+However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
 

### 2021-06-15 04-Chp-CPRD-Analysis.Rmd
End of day: -2772

@@
 
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).
+As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
 
 To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
+
+<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
 

### 2021-06-15 R/01-Code-Background.R

@@ -89,28 +89,33 @@ if(doc_type == "docx"){
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- statinsPath
 library(DiagrammeR)
+
 graph <- grViz(diagram = "digraph flowchart {
       # define node aesthetics
       node [fontname = Arial, color = 'grey90',shape = oval, style = filled, fontcolor = black]        
-      tab1 [label = 'Acetyl-CoA']
-      tab5 [label = 'Statins', shape = 'line',fillcolor = 'black',fontcolor = 'white']
-      tabinvis [shape=point, fillcolor = 'black']
-      tab6 [label = 'HMG-CoA reductase']
-      tab2 [label = 'HMG-CoA']
+      tab0 [label = 'Acetly-CoA']
+      tab1 [label = 'HMG-CoA']
+      tab5 [label = 'Statins',shape = 'line', fillcolor = 'black',fontcolor = 'white']
+      tabinvis [style = 'invis',shape=point, width = 0]
+      tab6 [label = 'HMG-CoA reductase', shape = 'line',fillcolor = 'white']
       tab3 [label = 'Mevalonate']
       tab4 [label = 'Cholesterol']
       tab7 [label = 'Several intermediate compounds', color = 'white', fillcolor = 'white']
       
+      
       subgraph {
-          rank = same; tab5;tabinvis; tab6
+          rank = same; tab5;tab1
+      }
+      subgraph {
+          rank = same; tabinvis; tab6
       }
       
 # set up node layout
+      tab0 -> tab1
       tab1 -> tabinvis [arrowhead = 'none']
-      tabinvis -> tab6 [arrowtail = 'curve', dir = back];
-      tab5 -> tabinvis [arrowhead = 'tee']
-      tabinvis -> tab2 
-      tab2 -> tab3;
+      tabinvis -> tab6 [arrowtail = 'curve', dir = back, minlen = 2];
+      tab5 -> tab6 [arrowhead = 'tee']
+      tabinvis -> tab3
       tab3 -> tab7 [arrowhead = 'none', style = 'dashed']
       tab7 -> tab4 [style = 'dashed']
       
@@ -122,7 +127,7 @@ htmltools::html_print(DiagrammeR::add_mathjax(graph), viewer = NULL) %>%
[…]

### 2021-06-15 04-Chp-CPRD-Analysis.Rmd
End of day: -2722

@@
 ```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition_test.png"))
+knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
 ```
@@
 Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`, and baseline LDL cholesterol was missing for `r ldltext`
+Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
 

### 2021-06-15 manuscripts/cprd/manuscript.Rmd
End of day: -2722

--- 2021-04-26 05-Chp-CPRD-Analysis.Rmd
@@
 ---
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
+title: 
+date: "Maunscript last updated: `r format(Sys.time(), '%d %B, %Y')`"
+bibliography: references.bib
+csl: vancouver.csl
+pandoc_args: [       "-F", "./pandoc-word-pagebreak"     ]
 output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::word_document2:
@@
       toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
       number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
+      reference_docx: "../../templates/word-styles-reference-01.docx"
 ---
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
-When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
-```
-(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]
+```{r setup, include=FALSE, warning=FALSE, message=FALSE}
+knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
+options(scipen = 999)
+source(here::here("R/doc_options.R"))
+source(here::here("R/helper.R"))
 
-# Primary analysis of lipid regulating agents and dementia {#cprd-analysis-heading}
+#Load relevant libraries and datasets from the 'outputs' folder
 
-\minitoc <!-- this will include a mini table of contents-->
+knitr::read_chunk(here::here("R/04-Code-CPRD-Analysis.R"))
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
 
-<!-- Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
 
-## Additional ideas
+# Front matter
 
-One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+__Type of manuscript:__
 
-Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?)
+Original Research Article
 
-__Things we tried__
+&nbsp;
 
-- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
-Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
-Need total number of those starting and average time to start.
-- Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper.
-- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
-- Allowing for time-varying confounders for binary covariates.
+__Title: __
 
-__Things we could try__
+Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the CPRD
 
-- Work through data using positive control to see if the way it is being added is what is causing the issues.
-- Examine Cramer et al. thesis and see what they did
-- Marginal structural models approach (a la J. Sterne)
+&nbsp;
 
-<!----------------------------------------------------------------------------->
+__Authors and affiliations:__
 
-## Lay summary
-Large scale database such as this are often called population level, and studies that make use of them have a number of advantages.
+Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2^, Venexia M Walker^1,2^, Neil M Davies^1,2^, Richard M Martin^1,2^,  Elizabeth Coulthard^3^, George Davey-Smith^1,2^,  Patrick G Kehoe^3,4^ and Yoav Ben-Shlomo^2^
 
-This analysis uses one of these databases, the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of XXXXXX people from YYYYYY general practices across England.
+(1) MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
+(2) Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
+(3) Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
+(4) Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK
 
-Using this data, I have analysed the ...
+&nbsp;
 
-<!----------------------------------------------------------------------------->
+__Corresponding author:__
 
-## Introduction
+Luke McGuinness; Bristol Medical School, University of Bristol,
+Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; luke.mcguinness@bristol.ac.uk
 
-Lack of evidence for the association of statins on vascular dementia risk
+&nbsp;
 
-Large scale databases advantages over other means
+__Conflict of interest statement__
+None declared.
 
-Cross reference here aswell re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
+&nbsp;
 
-<!----------------------------------------------------------------------------->
+__Sources of funding__
 
-## Methods
+LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+JPTH and GDS are supported by NIHR Bristol Biomedical Research Centre at University Hospitals Bristol NHS Foundation Trust and the University of Bristol.
+YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
+LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol.
+JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
+The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.
 
-### Data source {#cprd-data-source}
+&nbsp;
 
-The Clinical Practice Research Datalink (CPRD) is a large, population-based, electronic health record database.[@herrett2015] It contains the primary care records for
+__Data/code availability__
+This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
+The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on Github (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of submission on Zenodo (DOI: __TBC__).
 
-Originally termed the GPRD (General Practice Research Database),
+\newpage
 
-The
+```{r load-files, echo = FALSE}
+```
 
-Data completeness and collection of certain disease are heavily influenced by exercises that reward doctors for capturing certain diagnoses, such as the Quality and Outcomes Framework.
-However, these drives can oftern have unintended consequences [@liu2019]
+```{r attrition, echo = FALSE}
+```
 
-The CPRD uses a coding system called Read code <!--- check capitalisation --->
+```{r missing-data, echo = FALSE}
+```
 
-### Study design and protocol
+```{r characteristics, echo = FALSE}
+```
+
+```{r azd-text, echo = FALSE}
+```
+
+# Abstract
+
+__Introduction:__ There is some evidence that circulating blood lipids play a role in the development of of Alzheimer's disease and dementia.
+As a result, these readily modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
+Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in over <!-- TODO replace -->
+ participants.
+
+__Methods:__ Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease) in a prospective cohort study design using routinely collected data from the Clinical Practice Research Datalink.
+
+__Results:__ We analyzed `r totaltext` with a average follow-up of `r fu_ab_text`.
+Lipid-regulating agents were found to have no effect on risk of Alzheimer's disease (probable AD `r probad_text`; possible AD `r possad_text`), but an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+
+__Discussion:__ We found lipid-regulating agents had no effect on Alzheimer's disease risk, but increased the risk of all-cause, vascular and other dementia.
+However, this analysis is likely subject to residual confounding by indication and bias due to outcome misclassification.
+
+__Keywords:__ Dementia; Alzheimer's disease; Lipids; Statins; Cohort study; Observational study
+
+\newpage
+
+# Introduction
+
+Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer’s disease (AD) and vascular dementia (VaD).[@prince2016] Despite an increasing number of cases globally and decades of research, there remains much unknown about the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or reverse the cognitive decline associated with the condition.[@jobke2018] Drug repurposing, the identification of new applications for previously approved drugs, may provide an efficient mechanism to discover effective preventative and therapeutic treatments for dementia.[@ashburn2004; @pushpakom2019]
+
+Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2019a] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments.
+In this context, determining whether lipid-regulating agents could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy.
+Several existing prospective studies have examined the association of lipid-regulating agent use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.
+
+The use of electronic health data for epidemiological research has several advantages.[@casey2016] As the data are collected through the routine care of a large cohort, they allow for nested prospective studies using sample sizes and time-scales which would be unfeasible using traditional methods.
+In addition, data are collected for care provision and without a specific research question in mind,  providing a holistic picture of a patient and their health experience.
+This provides vital data on a range of potential confounders which can be incorporated into an analysis.
+
+We therefore aim to examine the association between several major classes of lipid-regulating agents and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
+
+\newpage
+
+# Methods {#methods}
+
+## Study design and protocol
 
@@
 
-<!-- Note: If protocol was written by Venexia, how do I reference this? -->
-
 &nbsp;
 
-### Study cohort
+## Study Cohort
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4mmol/L; or an LDL-c test result of >2mmol/L.
 
@@
 
-### Exposures
+## Exposures
 
@@
 
-### Outcomes
+## Outcomes
 
-<!--- Include short bit on follow-up here, describing how and why it was defined --->
-
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
 When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1).
@@
 
-### Covariates
+## Covariates
 
-A range of additional variables were included in the analysis, intended to address differential distributions of potnetial confounding variables between those who had a
-
-<!--- Need a lot more here - see other thesis for example of how covariates are described --->
-
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
-
-Charlson co-morbidity index,
-
-Index of Multiple Deprivation (IMD),
-
-consultation rate,
-
-alcohol (current, former,  never),
-
-smoking (current, former,  never),
-
-BMI,
-
-baseline total cholesterol,
-
-and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-
-All covariates were determined at index and definitions for each can be found in Supplementary Table 1.
-
-### Missing data
-
-Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and
-
-Binary variables were modelled using a
-
-continuo
-
-As per best practice, all other variables, including the out
-
-The MICE command in Stata was used
-
-### Time axis
-
-In Cox models, there is the option to
-
-Age vs time-since entry
-
-Expand on use of age as the time scale, but describe the problems this introduced
+The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+All
+covariates were determined at index and definitions for each can be found in Supplementary Table 1.
 
@@
 
-### Estimation methods
+## Analysis plan
 
-Potential biases included time varying confounding, selection bias due to censoring on death and 
-We use a Cox proportional hazards model with a time-varying treatment indicator.
+All analyses were performed in STATA 15.
+Cox proportional hazard models were used to estimate the hazard ratio and corresponding 95% confidence intervals, allowing for the potential for clustering by practice.
+To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
+Additional analyses stratified by outcome and drug class were also performed.
 
-Expand on post estimation analyses, which showed that nothing except age had an effect.
-
-$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
-
-where:
-
-* $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
-* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
-
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
-__Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__
-
-Hazard rations are
-
-Test for non-proportionality are therefore very important, as models which fail
-
-Problems with testing for non-proportional hazards when
-
-<!----------------------------------------------------------------------------->
-(ref:cprd-dag-1-cap) __Directed acyclic graph showing assumed relationship between exposure and covariate:__
-
-(ref:cprd-dag-1-scap) Directed acyclic graph showing assumed relationship between exposure and covariate
-
-```{r cprd-dag-1, echo = FALSE, results="asis", fig.cap='(ref:cprd-dag-1-cap)', out.width='100%', fig.scap='(ref:cprd-dag-1-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
-```
-<!----------------------------------------------------------------------------->
-
-### Immortal time bias and time-varying treatment indicators
-
-Immortal time bias is a type of misclassification bias. It occurs when
-
-One potential way to address this is the use of a time-varying treatment indicator, a factor which modi
-
-In the case of this analysis, this treatment indicator is statin use. Using codes for statins (see Appendix \@ref())
-
-<!----------------------------------------------------------------------------->
-
-### Estimating the value of the time-varying confounders
-
-Mean time from index event to first prescription of statins was 2.4 years.
-This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
-
-Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
-This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
-For example:
-
-    _No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_
-
-In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_.
-
-In practice, this means that the value of the prognostic factor should be regularly captured
-
-However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
-
-This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
-
-i.e.  
-Timepoint 12345678  
-CVD       00001111  
-Treatment 00000111
-
-Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point.
-
-Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
-
-<!----------------------------------------------------------------------------->
-
-### The effect of total cholesterol or LDL-cholesterol on LRA prescription
-
-It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.
-
-However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*
-
-<!--- This hasn't been done! --->
-
-### Replicating other analytical strategies
-
-**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This highlights a particular challenge in comparing research across different time-periods and coding systems.
-Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
-
-In order to
-
-As part of my exploration of the unexpected results, I attempted to replicate the analyses of another paper that used a different approach to
-
-Having contacted the authors to address these concerns, it was noted that
-
-Propensity scores are based on a range of baseline variables, and provide an estimates of the
-
-They used propensity scores to attempt to matcch patients equally likely to recieve the vaccine
-
-In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
-Fortunately, the authors kindly shared their
-
-However, there was a large difference in the case mix of dementia diagnoses between the two analyses.
-
-However, as shown in Table \@ref(tab:smeethComparison-table), there is substantial divergence between the two sets of code-lists.
-
-The reason for the discrepancy in terms of the number of Alzheimer cases as a percentage of total dementia cases between our study and the Smeeth 2010 paper is due to two things:
-•	While all of the codes used to define Alzheimer’s in the Smeeth paper are included in our “Probable Alzheimer’s” code-list, we also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
-•	Several of the codes in our “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
-
-Using the Smeeth code-list, we get a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
-<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth.
--->
-
-Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.
+All covariates included in the analytic model were also included in the imputation model.
+The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
+## Additional analyses
 
-(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
-
-```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
+We performed a number of sensitivity analysis.
+We stratified the analysis by grouped year of entry to explore the potential for a time period effect.
+As statins are contraindicated in pregnancy,[@nationalinstituteforhealthandcareexcellence]  we ran the models described above but excluding participants coded as female below the age of 55.
+We also further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
+Finally, we performed a negative control analysis, using the fully adjusted model to investigate the association between lipid-regulating agents and back pain.
 
@@
 
-## Discussion
+\newpage
 
-### Main findings
+# Results {#results}
+
+## Patient characteristics
+
+Of the `r format(attrition[1,1], big.mark = ",")` participants included in our extract, `r format(attrition[14,1], big.mark = ",")` met the inclusion criteria (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of 11,091,437 patient years at risk.
+The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
+During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia; see Supplementary Figure 1).
+The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+
+A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
+We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
+The "Ezetimibe and statins" treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently.
+
+&nbsp;
+
+## Missing data
+
+Full covariate information was available for `r missingtext`.
+Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
+
+&nbsp;
+
+## Primary analysis
+
+&nbsp;
+
+All results described below are from the fully adjusted model.
+The results of the model adjusted only for age and for age and sex are presented in Supplementary Figure 3.
+Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
+In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
+
+&nbsp;
+
+__Alzheimer's disease__
+
+As shown in Figure \@ref(fig:cprdPrimary), our results show no effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+
+&nbsp;
+
+__Non-Alzheimer's disease dementias__
+
+In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
+Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+
+&nbsp;
+
+__All-cause dementia__
+
+For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
+
+&nbsp;
+
+## Sensitivity analyses
+
+```{r sens-text, echo = FALSE}
+```
+
+When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Supplementary Figure 4).
+Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Supplementary Figure 5).
+
+For our negative control, there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (`r sens_bp_text`), suggesting there may be some residual confounding (Supplementary Figure 6).
+
+\newpage
+
+# Discussion {#discussion}
+
+## Main findings
+
+<!--- Is this true - no effect? Is it not a small reduction rather than no effect? --->
 
@@
 
-### Comparison to other literature
+## Comparison to other literature
 
@@
 
-These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia.
+These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
 However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to a artifical protective effect of statins on all-cause dementia
@@
 Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
-A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis.
+A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis (`r vasdem_text`).
 An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
@@
 
-### Original contribution to research
-
-There are two primary ways in which this research adds to the topic:
-
-* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
-* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
-
-### Coding quality in the CPRD
-
-Lots of things influence prevalence: historic trends, availability of good codes
-
-There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]
-
-### Strengths and Limitations
+## Strengths and Limitations
 
@@
 
-A further limitation is the possibility of time-varying confounding <!--- Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
-
 Finally, there is also the potential for reverse causation in this analysis.
@@
 
-### Enabling easy synthesis
+\newpage
 
-In light of my own experiences in attempting to extract information for papers assessing prevantive measures, I attempted to document
-
-This study was reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
-
-Reporting guidelines do not always work, but help to guide
-
-All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.
-
-&nbsp;
-
-### Conclusions
+# Conclusions {#conclusion}
 
@@
 
-## References
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
+
+```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
+
+```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
+knitr::include_graphics(here::here("figures","cprd-analysis","fp_p1.jpeg"))
+```
+<!--------------------------------------------------------------------------->
+
+\newpage
+
+# Bibliography

### 2021-06-15 manuscripts/cprd/supp-materials.Rmd
End of day: -2722

---
title: 
date: "Supplementary Files updated: `r format(Sys.time(), '%d %B, %Y')`"
bibliography: references.bib
csl: vancouver.csl
pandoc_args: [       "-F", "./pandoc-word-pagebreak"     ]
output:
  bookdown::word_document2:
      toc: true
      number_sections: false
      toc_depth: 2
      reference_docx: "../../templates/word-styles-reference-01-no_line_num.docx"
---

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
options(scipen = 999)
source(here::here("R/doc_options.R"))
source(here::here("R/helper.R"))

#Load relevant libraries and datasets from the 'outputs' folder

knitr::read_chunk(here::here("R/04-Code-CPRD-Analysis.R"))
doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
```

\newpage

# Supplementary Materials {#supp-mat}

## Supplementary Material 1: Changes to protocol {#supp-mat-protocol}

Main changes include:

  * Use of a time-varying treatment indicator, to correctly classify time-at-risk.
  * Inclusion of additional covariates that are adjusted for in the main model.

\newpage

# Supplementary tables {#supp-tab}

## Supplementary Table 1: Definition of exposures and covariates

&nbsp;

<!----------------------------------------------------------------------------->
(ref:covariateDef-caption) Definition of covariates

```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

\newpage

## Supplementary Table 2: Adherence and switching by drug class

&nbsp;

<!----------------------------------------------------------------------------->
(ref:cprdSSA-caption) cprdSSA

```{r cprdCharacteristics-table, message=FALSE, results="asis", include = FALSE}
```

```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

\newpage

## Supplementary Table 3: STROBE Reporting Guidelines {#supp-tab-strobe}

```{r child = 'supplementary_files/STROBE-Checklist.Rmd', eval = FALSE}
```

__To be completed__

\newpage

## Supplementary Table 4: Statin type prescribing by year {#supp-tab-sta-type}

&nbsp;

<!----------------------------------------------------------------------------->
(ref:statinTypeTable-caption) Statin prescription by year

```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
```
<!----------------------------------------------------------------------------->

&nbsp;

\newpage

# Supplementary figures {#supp-fig}
## Supplementary Figure 1 {#supp-fig-outcome-decision}

```{r supp-fig-decision-tree,echo = FALSE, fig.cap="The algorithm used to choose between two diagnosis. This decision tree is adapted with permission from Walker _et al_ (2019).[@walker2019a]"}
knitr::include_graphics(here::here("figures/cprd-analysis/decision_tree.png"))
```

\newpage

## Supplementary Figure 2 {#supp-fig-attrition}
```{r supp-fig-attrition,echo = FALSE, fig.cap="Attrition of participants as the eligibility criteria were applied.", fig.width="60%"}
knitr::include_graphics(here::here("figures/cprd-analysis/cohort_attrition.png"))
```

\newpage

## Supplementary Figure 3 {#supp-fig-unadjusted}
```{r supp-fig-comparison,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, adjusted only for age."}
knitr::include_graphics(here::here("figures/cprd-analysis/fp_unadjusted.jpeg"))
```

\newpage

## Supplementary Figure 4 {#supp-fig-entry}
```{r supp-fig-entry,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, stratified by year of entry into the cohort. {Note: Venexia reccomend including some info on average length of follow-up for each group beside the HR - will be done before submission.}"}
knitr::include_graphics(here::here("figures/cprd-analysis/fp_cohort_entry.jpeg"))
```

\newpage

## Supplementary Figure 5 {#supp-fig-pregnancy}
```{r supp-fig-pregnancy,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, removing women who were less than 55 years of age at index."}
knitr::include_graphics(here::here("figures/cprd-analysis/fp_pregnancy.jpeg"))
```

\newpage

## Supplementary Figure 6 {#supp-fig-sta-type}
```{r supp-fig-sta-type, echo = FALSE, fig.cap="Association of statins with a dementia or related outcome, stratified by statin lipophilic/hydrophilic properties."}
knitr::include_graphics(here::here("figures/cprd-analysis/fp_sta_type.jpeg"))
```

\newpage

## Supplementary Figure 7 {#supp-fig-backpain}
```{r supp-fig-backpain,echo = FALSE, fig.cap="Association of any lipid regulating agent with backpain and ischemic heart disease (IHD)."}
knitr::include_graphics(here::here("figures/cprd-analysis/fp_control_outcomes.jpeg"))
```

\newpage

# References for supplementary materials

### 2021-06-15 R/doc_options.R

@@ -5,6 +5,7 @@ library(medrxivr)
 library(kableExtra)
 library(dplyr)
 library(flextable)
+library(ggplot2)
 
 doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
 

### 2021-07-12 03-Chp-Systematic-Review.Rmd
End of day:

@@
 Literature con
+
+Systematic reviews aim to transparently and reproducibly identift
+
+<!-- TODO Need to seriously improve this -->
+
+&nbsp;
 
@@
 <!-- TODO Need to actually attach each search strategy.
-See search strategy results.
+Should be able to loop through search strategy results.
 -->
@@
 
-$$
+\begin{equation} 
   mg/dL = mmol/L \times{} Z
-$$
+  (\#eq:lipidConversion)
+\end{equation}
+
 where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
 For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+
+<!----------------------------------------------------------------------------->
 
@@
 
-<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->
+#### Risk of bias due to missing evidence
+
+A recent shift towards the assessment of missing evidence due to selective non-reporting (as distinct from the selective reporting of a single result from multiple planned - handled in Domain 5 of the RoB 2 tool for example).
+
+As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualise
 
@@
 
-Multiple publications resulting from the analysis of the same data will be included and grouped ().
+Multiple publications resulting from the analysis of the same data were included and grouped ().
 
 In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
+Instead, they were considered as different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
 
@@
 
-Where possible, data for all exposure groups was extracted, and this.
+Where possible, data for all exposure groups was extracted, and this <!-- TODO ??? -->
+.
 Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
@@
 Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
-
+s
 Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
@@
 
+Patient and
+
 <!----------------------------------------------------------------------------->
@@
 
-A dose response meta-analysis was not planned, marking a departure from the register protocol. <!-- TODO Check this is accurate -->
+A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->
 
@@
 
+\blandscape{}
+
+&nbsp;
+
 (ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
@@
 
+\elandscape{}
+
 <!----------------------------------------------------------------------------->
@@
 `r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig)
+\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
 
@@
 
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] shown in Figure \@ref(prisma-flow-fig), shows the movement of articles through the review.
-To illustrate the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> shown in Figure \@ref(prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
 
@@
 Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
-
-Of note, preprints and published papers reporting the same study were not considered duplicate records.
-Instead, they were considered as different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
 
@@
 
-<!-- TODO Cite excluded studies and  -->
+<!-- TODO Cite excluded studies and list exclusion reasons  -->
 
@@
 
-As part of the reflective element of this thesis,
+As part of the reflective element of this thesis, I collated my experiences on performing a systematic review.
 
@@
 
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted.
-Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.
+As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses, predominantly preprinted vs published.
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
 
-The added evidental value of including these preprints was highlighted in Section
+The added evidential value of including these preprints was highlighted in Section \ref()
 
 On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
-While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.
+While this provides some additional evidence that the quality of the research described by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavailable at the time the search was conducted.
 
@@
 ### Open data sharing {#sys-rev-open-data}
+
+As evidenced by the issues involved in obtaining
+
+Building in part on the research, I co-wrote an guidance piece for pre
+
+Similarly, a substanital amount of time and effort has gone into making the data obtained by this review openly available to
 
@@
 
-I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):
+I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
 
@@
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+
 -   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
@@
 This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
+
 -   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
 As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
+
+- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
+This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
+IN addition this review was used to pilot an upcoming risk of bias tool
 
@@
 
+<!-- Three things to cover: No good tools for dealing with MR studies yet (particularly search filters, as terminology is hard + no risk of bias tool); Is double counting of studies an issue (maybe speak to George, particularly if you can find an example)  -->
+
+<!-- TODO Email George with query on dual counting, following review of email with Julian -->
+
 While
@@
 
-Recent updates, such as a guide to reading and interpreting.
+Recent updates, such as a guide to reading and interpreting Mendelian .
+
 However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
 
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that Imay be double counting participants - for
+Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants
+
+Double-counting of other -
 
 Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.
+
+In short, given the recent developments in the production of studies and results from Mendelian randomisation
+
+This is particularly relevant to missing evidence, as new methods in MR studies allow for the anlysis of many exposures/outcomes concurrently.
+In this scenario, missing evidence is likely to be an issue as onyl those of particular interest to the authors/those reaching statistical significance will be reported in the paper
+
+This is highlighted by the identification of studies relevant to the review though coincidental reading and citation searhcing, that were not identified by the search as they reported many results and only the statistically significant ones were included in searchable fields
+
+This is particularly troubling given the comprehensiveness of the search (~17,000 records screened).
+In retrospect, a mitigating approach may have been to have an additional search for topics related to risk factors, dementia and MR studies, and screened t
+
+<!-- TODO Best option probably to highlight that while these studies were included, it was not easy given a lack of resources for MR studies -->
+
+As a form of analysis that lends itself to multiple comparison, there is a strong
+
+Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
+[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
+
+The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
+Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
+This may bias reviews as the analysising multiple risk factors at a time becomes more common.
+
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's"),
+
+<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
+
+Is it a big issue that the studies have the same underlying datasets? <!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
+
+Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
+However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
 
@@
 
-<!-- TODO Maybe need to integrate with the section immediately above.
-Best option probably to move the section above to the end of this section, highlighting that while these studies were included, it was not easy given a lack of resources for MR studies -->
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
-[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
-Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
-This may bias reviews as the analysising multiple risk factors at a time becomes more common.
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Is it a big issue that the studies have the same underlying datasets? <!--- TODO check discussion from Matt Lee thesis, in email --->
-
-Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
-However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
-
 #### Inclusion of preprints
@@
 
-<!--- Findings from this chapter are used throughout the later chapters of this thesis.
+<!--- IDEA Findings from this chapter are used throughout the later chapters of this thesis.
 In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.

### 2021-07-12 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 title: 
-date: "Maunscript last updated: `r format(Sys.time(), '%d %B, %Y')`"
+date: "Manuscript last updated: `r format(Sys.time(), '%d %B, %Y')`"
 bibliography: references.bib
@@
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
-
 ```
@@
 
-Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the CPRD
+Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the Clinical Practice Research Datalink
 
@@
 
-Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2^, Venexia M Walker^1,2^, Neil M Davies^1,2^, Richard M Martin^1,2^,  Elizabeth Coulthard^3^, George Davey-Smith^1,2^,  Patrick G Kehoe^3,4^ and Yoav Ben-Shlomo^2^
+Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2,3^, Venexia M Walker^1,2,4^, Neil M Davies^1,2^, Richard M Martin^1,2,3^,  Elizabeth Coulthard^5^, George Davey-Smith^1,2,3^,  Patrick G Kehoe^5,6^ and Yoav Ben-Shlomo^2^
 
@@
 (2)	Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
-(3) Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
-(4) Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK
+(3)	NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
+(4)	Department of Surgery, University of Pennsylvania Perelman School of Medicine, Philadelphia, USA
+(5)	Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
+(6)	Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK
 
@@
 LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
-JPTH and GDS are supported by NIHR Bristol Biomedical Research Centre at University Hospitals Bristol NHS Foundation Trust and the University of Bristol.
+JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
+The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care.
 YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
-LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol.
+LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1).
 JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
@@
 
+__Word counts__
+
+* Main text word count (max 3000): 2999
+* Abstract word count (max 250): 244
+
+&nbsp;
+
 __Data/code availability__
 This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
-The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on Github (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of submission on Zenodo (DOI: __TBC__).
+The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of submission on Zenodo (DOI: __TBC__).
 
@@
 
+```{r controlOutcomesText, echo = FALSE, message = FALSE}
+```
+
+<!-- TODO Check scale in figures -->
+<!-- TODO Check cross link between supplementary tables and text -->
+
 # Abstract
 
-__Introduction:__ There is some evidence that circulating blood lipids play a role in the development of of Alzheimer's disease and dementia.
+__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease and dementia.
 As a result, these readily modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
-Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in over <!-- TODO replace -->
- participants.
+Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.
 
-__Methods:__ Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease) in a prospective cohort study design using routinely collected data from the Clinical Practice Research Datalink.
+__Methods:__ A retrospective cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
+Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).
 
-__Results:__ We analyzed `r totaltext` with a average follow-up of `r fu_ab_text`.
-Lipid-regulating agents were found to have no effect on risk of Alzheimer's disease (probable AD `r probad_text`; possible AD `r possad_text`), but an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+__Results:__ We analyzed `r totaltext` with a median follow-up of `r fu_ab_text`.
+We found little evidence that lipid-regulating agents were associated with risk of Alzheimer’s disease  (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+Evidence for an increased risk of one of the control outcomes, ischemic heart disease (`r ihd_text`), indicated the presence of substantial residual confounding related to vascular factors.
 
-__Discussion:__ We found lipid-regulating agents had no effect on Alzheimer's disease risk, but increased the risk of all-cause, vascular and other dementia.
-However, this analysis is likely subject to residual confounding by indication and bias due to outcome misclassification.
+__Conclusion:__ We found little evidence that lipid-regulating agents had any effect on Alzheimer’s disease risk.
+There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.
 
-__Keywords:__ Dementia; Alzheimer's disease; Lipids; Statins; Cohort study; Observational study
+__Keywords:__ Dementia; Alzheimer's disease; Lipids; Statins; Cohort study; Observational study; Electronic health records
+
+\newpage
+
+# Key messages
+
+* A large cohort of patients from the Clinical Practice Research Datalink electronic health record database was assembled to examine the effect of lipid-regulating agents, such as statins, on dementia outcomes.
+
+* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia.
+In all cases, the estimated associations were driven by the statin subgroup, which comprised the majority of participants in our cohort.
+
+* However, evidence from the control outcome analyses indicated strong residual confounding by indication, mostly likely related to vascular factors.
 
@@
 Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2019a] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments.
-In this context, determining whether lipid-regulating agents could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy.
-Several existing prospective studies have examined the association of lipid-regulating agent use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.
+In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy.
+Several existing prospective studies have examined the association of LRA use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.
 
-The use of electronic health data for epidemiological research has several advantages.[@casey2016] As the data are collected through the routine care of a large cohort, they allow for nested prospective studies using sample sizes and time-scales which would be unfeasible using traditional methods.
+The use of electronic health data for epidemiological research has several advantages.[@casey2016] As the data are collected through the routine care of a large cohort, they allow for nested cohort studies using sample sizes and time-scales which would be infeasible using traditional methods.
 In addition, data are collected for care provision and without a specific research question in mind,  providing a holistic picture of a patient and their health experience.
@@
 
-We therefore aim to examine the association between several major classes of lipid-regulating agents and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
+We therefore aim to examine the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
 
@@
 
-We performed a prospective cohort study using data from the CPRD.
+We performed a cohort study using data from the CPRD.
 Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
@@
 
-An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
-This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).[@vonelm2008]
+An *a priori* protocol for this study was published,[@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
+This study was reported in line with the RECORD guidelines (Supplementary Table 1).[@nicholls2016record]
 
@@
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4mmol/L; or an LDL-c test result of >2mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a LRA (such as statins); a total cholesterol test result of >4mmol/L; or an low density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
 
-These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-This approach was employed in an attempt to reduce confounding by indication that we would expect to observe in the full cohort, because individuals not prescribed lipid-regulating agents likely be less healthy across a range of variables than those prescribed lipid-regulating agents, leading to a biased association been lipid-regulating agent use and dementia.
-Conditioning entry into the study into the study on being either “at-risk” or already diagnosed with hypercholesterolemia attempts to mitigate this bias.
+These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL-c test results, or had already been diagnosed with it, as indicated by a diagnostic code or related prescription.
+This approach, conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia, was employed in an attempt to reduce confounding by indication that we would expect to observe in a general population cohort.
 
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+The index date for a participant was defined as the date where the first relevant code or test result (as detailed above) was recorded on their clinical record.
+Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
+Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
 
@@
 A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
+We did however tabulate how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
 
@@
 
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-All
-covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+All covariates were determined at index and definitions for each can be found in Supplementary Table 2.
 
@@
 Cox proportional hazard models were used to estimate the hazard ratio and corresponding 95% confidence intervals, allowing for the potential for clustering by practice.
-To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] We ran two models, one unadjusted except for age, which was captured by using the participant's age as the time axis for the model,[@lamarca1998; @gail2009; @pencina2007] and a second adjusted for the additional covariates described above.
+Participant's age was used as the time axis for all models.[@lamarca1998; @gail2009; @pencina2007] To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] To observe the effect of adjusting for additional covariates, we compared models adjusted for age only and age and sex to the fully adjusted model.
 Additional analyses stratified by outcome and drug class were also performed.
 
-In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.
-All covariates included in the analytic model were also included in the imputation model.
-The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).
+In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.[@sterne2009a] All covariates included in the analytic model were also included in the imputation model.[@moons2006using] The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).
 
@@
 We performed a number of sensitivity analysis.
-We stratified the analysis by grouped year of entry to explore the potential for a time period effect.
-As statins are contraindicated in pregnancy,[@nationalinstituteforhealthandcareexcellence]  we ran the models described above but excluding participants coded as female below the age of 55.
+As statins are contraindicated in pregnancy,[@nationalinstituteforhealthandcareexcellence]  we ran the models described above but excluding participants below the age of 55.
 We also further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
-Finally, we performed a negative control analysis, using the fully adjusted model to investigate the association between lipid-regulating agents and back pain.
+Finally, we included three control outcomes with known associations with statin use.[@collins2016a; @herrett2021] Using the fully adjusted model, we investigated the association between LRA and back pain (negative control), ischemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
 
@@
 
-Of the `r format(attrition[1,1], big.mark = ",")` participants included in our extract, `r format(attrition[14,1], big.mark = ",")` met the inclusion criteria (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of 11,091,437 patient years at risk.
+A total of `r format(attrition[14,1], big.mark = ",")` participants met the inclusion criteria for our cohort (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of `r comma(total_followup)` patient years at risk.
+The majority of participants were included in the cohort on the basis of an elevated test result (`r index_event_text`).
 The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia; see Supplementary Figure 1).
+During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia).
 The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
@@
 We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
-The "Ezetimibe and statins" treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently.
+The stopping, addition and switching of drug classes was common across all exposure groups (Supplementary Table 3).
 
@@
 
-&nbsp;
-
-All results described below are from the fully adjusted model.
-The results of the model adjusted only for age and for age and sex are presented in Supplementary Figure 3.
-Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
-In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
-
-&nbsp;
-
 __Alzheimer's disease__
 
-As shown in Figure \@ref(fig:cprdPrimary), our results show no effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+As shown in Figure \@ref(fig:cprdPrimary), our results show little evidence of an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 
-When stratifying based on year of entry to the cohort, we observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Supplementary Figure 4).
-Removing participants coded as female aged 55 and under at index from our analysis had minimal effect on our estimates (Supplementary Figure 5).
+Adjustment for additional covariates beyond age and sex had a limited impact (Supplementary Figure 3), with the exception of the Probable AD outcome, where the full adjustment attenuated to the null the protective effect observed when adjusting only for age and sex.
 
-For our negative control, there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (`r sens_bp_text`), suggesting there may be some residual confounding (Supplementary Figure 6).
+Removing participants aged 55 and under at index from our analysis had minimal effect on our estimates (Supplementary Figure 4).
+When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Supplementary Figure 5).
+Additionally, in the Alzheimer's disease outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.
+
+For our control outcomes (Supplementary Figure 6), there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (`r backpain_text`).
+However, LRA prescription was also associated with an increased risk of ischemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
 
@@
 
-<!--- Is this true - no effect? Is it not a small reduction rather than no effect? --->
-
-Lipid-regulating agents had no effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+There was little evidence that lipid-regulating agents had any observed effect on probable and possible Alzheimer's when compared with no treatment, but some evidence they were associated with an increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
 The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+For the other drug classes, there was limited evidence of an association with any outcome, with two exceptions.
+Ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increased risk of all-cause dementia and probable Alzheimer's disease.
 
@@
 
-Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.
+Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] echoing the distribution of participants in our analysis.
 
@@
 These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to a artifical protective effect of statins on all-cause dementia
+However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to an artificial protective effect of statins on all-cause dementia.
 
@@
 Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80), though the reduction was more extreme than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings, but could not rule out no effect (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
 
@@
 Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
-A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis (`r vasdem_text`).
+A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis (`r vasdem_text`).
 An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
@@
 Apart from statins, few studies examining a lipid-regulating agent have been reported.
-One of the few classes for which data was available were fibrates, which were shown to have no effect on all-cause dementia, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
+One of the few classes for which data was available were fibrates, for minimal evidence of an effect on all-cause dementia was identified, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
 
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
+To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding for that treatment.
 
@@
 However, the findings of our analysis are subject to several limitations.
-There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contained prescriptions for lipid-regulating agents.
 Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
 
-Our study may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
-We attempted to address this by limiting inclusion to those either prescribed or “at risk” of being prescribed, which was determined using an elevated test result.
-We also adjusted for several additional potential confounding variables.
-However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that our findings may be biased by residual confounding.
-Important confounding variables for which we have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of unspecified Alzheimer’s and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020] This finding, combined with the potential for differential misclassification between Alzheimer’s disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.
+Our study may also be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use.
+Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
+The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is not know to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible AD to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of vascular cases in the outcome definition increases.
+A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]
 
 Finally, there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
+Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.
 
@@
 We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-We found use of lipid-regulating agents not associated with probable or possible Alzheimer’s disease, but were associated with an increased risk of all-cause, vascular and other dementias.
+We found limited evidence to support the use of lipid-regulating agents for the prevention of  probable or possible Alzheimer’s disease, but they were associated with an increased risk of all-cause, vascular and other dementias.
 In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
@@
 We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature.
-However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which may relate to the unexpected increase in risk of vascular dementia associated with statin use.
 Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
@@
 
-&nbsp;
+# Main table
 
@@
 
-&nbsp;
+\newpage
+
+# Main figure
 
 <!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
-
-```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
+```{r cprdPrimary, echo = FALSE, fig.cap="Test"}
 knitr::include_graphics(here::here("figures","cprd-analysis","fp_p1.jpeg"))
@@
 
+_Figure 1: Results from the primary analyses of CPRD data, stratified by dementia outcome and drug class.
+All results were obtained using the fully adjusted model and participant age as the time scale._
+
 \newpage

### 2021-07-12 manuscripts/cprd/manuscript.tex
End of day:

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\author{}
\date{\vspace{-2.5em}Manuscript last updated: 16 June, 2021}

\begin{document}

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\hypertarget{front-matter}{%
\section{Front matter}\label{front-matter}}

\textbf{Type of manuscript:}

Original Research Article

~

\textbf{Title: }

Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the CPRD

~

\textbf{Authors and affiliations:}

Luke A McGuinness\textsuperscript{1,2,*}, Julian PT Higgins\textsuperscript{1,2,3}, Venexia M Walker\textsuperscript{1,2,4}, Neil M Davies\textsuperscript{1,2}, Richard M Martin\textsuperscript{1,2,3}, Elizabeth Coulthard\textsuperscript{5}, George Davey-Smith\textsuperscript{1,2,3}, Patrick G Kehoe\textsuperscript{5,6} and Yoav Ben-Shlomo\textsuperscript{2}

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\tightlist
\item
  MRC University of Bristol Integrative Epidemiology Unit, Bristol, UK
\item
  Bristol Medical School: Population Health Sciences, University of Bristol, Bristol, UK
\item
  NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
\item
  Department of Surgery, University of Pennsylvania Perelman School of Medicine, Philadelphia, USA
\item
  Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
\item
  Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK
\end{enumerate}

~

\textbf{Corresponding author:}

Luke McGuinness; Bristol Medical School, University of Bristol,
Canynge Hall, 39 Whatley Road, Bristol, BS8 2PS, United Kingdom.; \href{mailto:luke.mcguinness@bristol.ac.uk}{\nolinkurl{luke.mcguinness@bristol.ac.uk}}

~

\textbf{Conflict of interest statement}
None declared.

~

\textbf{Sources of funding}

LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048). JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol. The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care. YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust. LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC\_UU\_00011/1). JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.

~

\textbf{Word counts}

\begin{itemize}
\tightlist
\item
  Main text word count (max 3000): 3021
\item
  Abstract word count (max 250): 203
\end{itemize}

~

\textbf{Data/code availability}
This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15\_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee. The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (\url{https://github.com/mcguinlu/CPRD-LRA}), and were archived at the time of submission on Zenodo (DOI: \textbf{TBC}).

\newpage

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

\textbf{Background:} There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease and dementia. As a result, these readily modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia. Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large scale electronic health record database.

\textbf{Methods:} A retrospective cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed. Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).

\textbf{Results:} We analyzed 1,695,683 participants with a median follow-up of 5.8 participant-years. We found little evidence that lipid-regulating agents were associated with risk of Alzheimer's disease (probable AD HR: 0.98, 95\%CI: 0.94-1.01; possible AD HR: 0.97, 95\%CI: 0.93-1.01), but there was evidence of an increased risk of all-cause (HR: 1.17, 95\%CI: 1.14-1.19), vascular (HR: 1.81, 95\%CI: 1.73-1.89) and other dementia (HR: 1.19, 95\%CI: 1.15-1.24). Evidence for an increased risk of the control outcome, ischemic heart disease (\texttt{r}ihd\_text`), indicated the presence of substantial residual confounding.

\textbf{Conclusion:} We found little evidence that lipid-regulating agents had any effect on Alzheimer's disease risk. There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.

\textbf{Keywords:} Dementia; Alzheimer's disease; Lipids; Statins; Cohort study; Observational study; Electronic health records

\newpage

\hypertarget{key-messages}{%
\section{Key messages}\label{key-messages}}

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer's disease (AD) and vascular dementia (VaD).(1) Despite an increasing number of cases globally and decades of research, there remains much unknown about the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or reverse the cognitive decline associated with the condition.(2) Drug repurposing, the identification of new applications for previously approved drugs, may provide an efficient mechanism to discover effective preventative and therapeutic treatments for dementia.(3,4)

Several cardiovascular factors have been identified as potential risk factors for dementia,(5) and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments. In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy. Several existing prospective studies have examined the association of LRA use with dementia.(6--10) However, many of these studies are small, record few outcomes, and have limited follow-up.

The use of electronic health data for epidemiological research has several advantages.(11) As the data are collected through the routine care of a large cohort, they allow for nested prospective studies using sample sizes and time-scales which would be unfeasible using traditional methods. In addition, data are collected for care provision and without a specific research question in mind, providing a holistic picture of a patient and their health experience. This provides vital data on a range of potential confounders which can be incorporated into an analysis.

We therefore aim to examine the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.(12)

\newpage

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{study-design-and-protocol}{%
\subsection{Study design and protocol}\label{study-design-and-protocol}}

We performed a cohort study using data from the CPRD. Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for ``research quality'' data. All events of interest were identified using predetermined code lists, which are available for inspection (see \protect\hyperlink{data-code-avail}{Data/code availability}).

An \emph{a priori} protocol for this study was published, (13) and amendments to this are recorded in Supplementary Materials 1. This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).(14)

~

\hypertarget{study-cohort}{%
\subsection{Study Cohort}\label{study-cohort}}

Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a LRA (such as statins); a total cholesterol test result of \textgreater4mmol/L; or an low density lipoprotein cholesterol (LDL-c) test result of \textgreater2mmol/L.

These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL-c test results, or had already been diagnosed with it, as indicated by a diagnostic code or related prescription. This approach was employed in an attempt to reduce confounding by indication that we would expect to observe in a general population cohort. Conditioning entry into the study on being either ``at-risk'' or already diagnosed with hypercholesterolemia attempts to mitigate this potential bias.

The index date for a participant was defined as the date where the first relevant code or test result (as detailed above) was recorded on their clinical record. Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice. Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of ``research quality'' data, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.

~

\hypertarget{exposures}{%
\subsection{Exposures}\label{exposures}}

We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF)(15), namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.

A participant's drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach. We did however tabulate how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).

~

\hypertarget{outcomes}{%
\subsection{Outcomes}\label{outcomes}}

We considered five outcomes as part of this analysis: probable Alzheimer's disease, possible Alzheimer's disease, vascular dementia, other dementia, and a composite all-cause dementia outcome. When two or more outcomes were coded in a participant's clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1). The diagnosis date of the outcome was determined by the first record of a relevant code.

~

\hypertarget{covariates}{%
\subsection{Covariates}\label{covariates}}

The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (\textless2000, 2000-2004, 2005-2009, \textgreater2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former, never), smoking (current, former, never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes. All
covariates were determined at index and definitions for each can be found in Supplementary Table 1.

~

\hypertarget{analysis-plan}{%
\subsection{Analysis plan}\label{analysis-plan}}

All analyses were performed in STATA 15. Cox proportional hazard models were used to estimate the hazard ratio and corresponding 95\% confidence intervals, allowing for the potential for clustering by practice. To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.(16) To observe the effect of adjusting for additional covariates, we compared models adjusted for age only (captured by using the participant's age as the time axis for the model(17--19)) and age and sex to the fully adjusted model. Additional analyses stratified by outcome and drug class were also performed.

In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets. All covariates included in the analytic model were also included in the imputation model. The full imputation model is available for inspection (See \protect\hyperlink{data-code-avail}{Data/Code availability} section).

~

\hypertarget{additional-analyses}{%
\subsection{Additional analyses}\label{additional-analyses}}

We performed a number of sensitivity analysis. We stratified the analysis by grouped year of entry to explore the potential for a time period effect. As statins are contraindicated in pregnancy,(20) we ran the models described above but excluding participants below the age of 55. We also further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins. Finally, we include two control outcomes, using the fully adjusted model to investigate the association between LRA and both back pain (negative control) and ischemic heart disease (postive control).

~

\newpage

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{patient-characteristics}{%
\subsection{Patient characteristics}\label{patient-characteristics}}

A total of participants included in our extract, 1,684,564 met the inclusion criteria (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of 10800903 patient years at risk. The majority of participants were included in the cohort on the basis of an elevated test result (\texttt{r}index\_event\_text`). The median age at index was 57 years (Inter quartile range (IQR):48-68) and participants were followed up for a median of 5.8 years (IQR:2.7-9.7). During follow-up, an all-cause dementia diagnosis was recorded for 41,830 patients (12,647 probable AD, 9,954 possible AD, 8,466 vascular dementia, 10,763 other dementia; see Supplementary Figure 1). The distribution of baseline characteristics across the drug classes can be seen in Table \ref{tab:cprdCharacteristics-table}.

A substantial majority (98.1\%) of participants prescribed a lipid-regulating agent were prescribed a statin. We excluded the ``Ezetimibe and statins'' and ``Nicotinic acid groups'' classes from subsequent analysis based on the extremely small number of participants in these groups (Table \ref{tab:cprdCharacteristics-table}). The ``Ezetimibe and statins'' treatment group represent those prescribed a treatment containing both ezetimibe and statins, rather than those where the two treats were prescribed concurrently. The stopping, addition and switching of drug classes was common across all exposure groups (Supplementary Table 2).

~

\hypertarget{missing-data}{%
\subsection{Missing data}\label{missing-data}}

Full covariate information was available for 451,897 participants (26.6\%). Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for 630,439 participants (37.2\%), because it is only recorded for English practices; alcohol status was missing for 272,745 participants (16.1\%); smoking status was missing for 85,267 participants (5\%); BMI, or a calculated BMI from height and weight measurements, was missing for 270,122 participants (15.9\%); baseline total cholesterol was missing for 121,101 participants (7.1\%); and baseline LDL cholesterol was missing for 793,720 participants (46.8\%).

~

\hypertarget{primary-analysis}{%
\subsection{Primary analysis}\label{primary-analysis}}

~

All results described below are from the fully adjusted model. The results of the model adjusted only for age and for age and sex are presented in Supplementary Figure 3. Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome. In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.

~

\textbf{Alzheimer's disease}

As shown in Figure \ref{fig:cprdPrimary}, our results show little evidence of an effect of lipid-regulating agents on probable (HR: 0.98, 95\%CI: 0.94-1.01) and possible (HR: 0.97, 95\%CI: 0.93-1.01) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (HR: 1.28, 95\%CI: 1.08-1.52).

~

\textbf{Non-Alzheimer's disease dementias}

In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (HR: 1.81, 95\%CI: 1.73-1.89) or other dementia (HR: 1.19, 95\%CI: 1.15-1.24). Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (HR: 2.33, 95\%CI: 1.11-4.89) and other (HR: 1.88, 95\%CI: 1.01-3.5) dementia.

~

\textbf{All-cause dementia}

For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (HR: 1.17, 95\%CI: 1.14-1.19), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup. There was also some evidence that fibrates were associated with increased risk of all-cause dementia (HR: 1.28, 95\%CI: 1.08-1.52).

~

\hypertarget{sensitivity-analyses}{%
\subsection{Sensitivity analyses}\label{sensitivity-analyses}}

Removing participants aged 55 and under at index from our analysis had minimal effect on our estimates (Supplementary Figure 4).

For our control outcomes (Supplementary Figure 6), there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (HR: 1.04, 95\% CI: 1.03-1.05). However, LRA prescription was also associated with a substantially increased risk of ischemic heart disease (HR: 1.62, 95\% CI: 1.59-1.64), suggesting substantial uncontrolled confounding related to vascular factors.

\newpage

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{main-findings}{%
\subsection{Main findings}\label{main-findings}}

There was little evidence that lipid-regulating agents on probable and possible Alzheimer's when compared with no treatment, but some evidence they were associated with an increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis. The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants. For the other drug classes, there was limited evidence of an association with any outcome, with two exceptions. Ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increased risk of all-cause dementia and probable Alzheimer's disease.

~

\hypertarget{comparison-to-other-literature}{%
\subsection{Comparison to other literature}\label{comparison-to-other-literature}}

Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as ``non-statin cholesterol-lowering drugs.''(8) This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.

~

\textbf{Statins and all-cause dementia}

A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.(21) This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00, 95\%CI:0.61-1.65),(22) but concerns were raised over the diagnostic criteria used. A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95\%CI: 0.79--0.87).(23)

These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (HR: 1.17, 95\%CI: 1.14-1.19). However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,(24) which may lead to an artificial protective effect of statins on all-cause dementia

~

\textbf{Statins and Alzheimer's disease}

Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease. No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95\% CI 0.60--0.80), though the reduction was more extreme than observed in our analysis.(23) In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer's disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95\%CI: 0.63-1.31).(25)

An additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis.(6)

~

\textbf{Statins and non-Alzheimer's disease dementia}

Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia. A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95\% CI 0.74--1.16).(23) This contrasts with the increased effect found in our analysis (HR: 1.81, 95\%CI: 1.73-1.89). An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.

~

\textbf{Other drug classes}

Apart from statins, few studies examining a lipid-regulating agent have been reported. One of the few classes for which data was available were fibrates, for miminal evidence of an effect on all-cause dementia was identified, (8) inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.

To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.

~

\hypertarget{strengths-and-limitations}{%
\subsection{Strengths and Limitations}\label{strengths-and-limitations}}

A major strength of our analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed. In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.

However, the findings of our analysis are subject to several limitations. There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents. Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.(26,27)

Our study may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome. We attempted to address this by limiting inclusion to those either prescribed or ``at risk'' of being prescribed, which was determined using an elevated test result. We also adjusted for several additional potential confounding variables. However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicating that our findings may be biased by residual confounding. Important confounding variables for which we have not adjusted could include genetic factors. A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer's disease polygenic risk score was associated with an increased risk of unspecified Alzheimer's and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.(28) This finding, combined with the potential for differential misclassification between Alzheimer's disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.

Finally, there is also the potential for reverse causation in this analysis. Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.

\newpage

\hypertarget{conclusion}{%
\section{Conclusions}\label{conclusion}}

We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer's disease, vascular dementia, and other dementia. We found limited evidence to support the use of lipid-regulating agents for the prevention of probable or possible Alzheimer's disease, but were associated with an increased risk of all-cause, vascular and other dementias. In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.

We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature. However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which may relate to the unexpected increase in risk of vascular dementia associated with statin use. Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.

\newpage

~

\begin{table}[H]

\caption[(ref:cprdCharacteristics-scaption)]{\label{tab:cprdCharacteristics-table}Patient characteristics by drug class. Summary statistics are presented as ``\% (N)'' unless otherwise specified in the variable name.}
\centering
\fontsize{5}{7}\selectfont
\begin{threeparttable}
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}>{\centering\arraybackslash}p{6em}}
\toprule
\textbf{ } & \textbf{Whole Sample} & \textbf{None} & \textbf{Statins} & \textbf{Bile acid sequestrants} & \textbf{Ezetimibe} & \textbf{Ezetimibe \& Statins} & \textbf{Fibrates} & \textbf{Nicotinic acid groups} & \textbf{Omega-3 Fatty Acid Groups}\\
\midrule
\textbf{Sample size (N)} & 1695683 & 1095857 & 588455 & 5417 & 766 & 127 & 3896 & 168 & 997\\
\midrule
\textbf{Index year \newline(median)} & 2006 & 2007 & 2004 & 2005 & 2004 & 2005 & 2001 & 2001 & 2005\\
\midrule
\textbf{Female} & 53.1\% (900847) & 56.3\% (616801) & 47.2\% (277841) & 66.4\% (3598) & 54.6\% (418) & 52.8\% (67) & 38.6\% (1505) & 54.8\% (92) & 52.7\% (525)\\
\midrule
\textbf{Age} & 57 & 54 & 62 & 57 & 60 & 57 & 58 & 62 & 56\\
\midrule
\textbf{CAD} & 0.4\% (7180) & 0.1\% (614) & 1.1\% (6487) & 0.1\% (6) & 0.9\% (7) & 0.0\% (0) & 1.4\% (53) & 0.0\% (0) & 1.3\% (13)\\
\midrule
\addlinespace
\textbf{CBS} & 0.3\% (5739) & 0.1\% (701) & 0.8\% (4947) & 0.1\% (4) & 0.4\% (3) & 0.0\% (0) & 2.0\% (78) & 0.0\% (0) & 0.6\% (6)\\
\midrule
\textbf{CVD} & 2.2\% (36680) & 1.2\% (12803) & 4.0\% (23567) & 1.7\% (90) & 2.6\% (20) & 2.4\% (3) & 4.4\% (171) & 4.8\% (8) & 1.8\% (18)\\
\midrule
\textbf{Charlson (ever > 0)} & 31.0\% (525566) & 25.5\% (279520) & 40.9\% (240925) & 42.6\% (2308) & 41.8\% (320) & 24.4\% (31) & 50.9\% (1983) & 44.6\% (75) & 40.5\% (404)\\
\midrule
\textbf{IMD-2010 (median)} & 9 & 8 & 9 & 8 & 9 & 13 & 10 & 11 & 10\\
\midrule
\textbf{Consulation rate (mean/SD)} & 5.4 (5.5) & 5.0 (5.0) & 6.3 (6.1) & 8.6 (7.4) & 7.4 (6.6) & 4.8 (4.3) & 7.1 (6.2) & 9.3 (7.7) & 8.0 (8.0)\\
\midrule
\addlinespace
\textbf{Alcohol (ever)} & 85.8\% (1455443) & 86.5\% (947716) & 84.7\% (498304) & 82.8\% (4487) & 83.9\% (643) & 87.4\% (111) & 82.8\% (3226) & 82.7\% (139) & 81.9\% (817)\\
\midrule
\textbf{Smoking (ever)} & 51.1\% (866207) & 47.0\% (515192) & 58.5\% (344540) & 55.2\% (2990) & 57.4\% (440) & 60.6\% (77) & 60.1\% (2342) & 53.6\% (90) & 53.8\% (536)\\
\midrule
\textbf{BMI (mean/SD)} & 27.0 (5.3) & 26.7 (5.2) & 27.7 (5.3) & 26.8 (5.8) & 28.1 (5.7) & 28.1 (4.9) & 29.0 (5.2) & 26.4 (5.0) & 26.8 (5.5)\\
\midrule
\textbf{PAD} & 0.8\% (12879) & 0.4\% (4204) & 1.4\% (8524) & 0.9\% (47) & 0.9\% (7) & 0.8\% (1) & 1.9\% (75) & 6.5\% (11) & 1.0\% (10)\\
\midrule
\textbf{Hypertension} & 16.1\% (273011) & 11.6\% (126891) & 24.5\% (144010) & 12.9\% (697) & 23.9\% (183) & 25.2\% (32) & 25.8\% (1006) & 21.4\% (36) & 15.6\% (156)\\
\midrule
\addlinespace
\textbf{Total cholesterol (mean/SD)} & 5.7 (12.4) & 5.5 (10.8) & 6.2 (15.3) & 5.3 (1.3) & 7.1 (26.5) & 6.7 (1.5) & 6.4 (5.6) & 5.4 (1.5) & 5.6 (1.7)\\
\midrule
\textbf{LDL cholesterol (mean/SD)} & 3.6 (4.8) & 3.4 (5.2) & 4.0 (3.6) & 3.1 (1.0) & 3.9 (1.1) & 4.2 (1.0) & 3.3 (1.8) & 3.4 (0.9) & 3.2 (1.0)\\
\midrule
\textbf{CKD} & 0.1\% (1391) & 0.1\% (814) & 0.1\% (566) & 0.1\% (7) & 0.1\% (1) & 0.0\% (0) & 0.0\% (0) & 0.0\% (0) & 0.3\% (3)\\
\midrule
\textbf{Type 1 Diabetes} & 0.2\% (4057) & 0.1\% (795) & 0.5\% (3206) & 0.3\% (14) & 1.0\% (8) & 0.8\% (1) & 0.8\% (31) & 0.6\% (1) & 0.1\% (1)\\
\midrule
\textbf{Type 2 Diabetes} & 2.9\% (49381) & 1.1\% (12376) & 6.1\% (36182) & 2.3\% (124) & 5.4\% (41) & 4.7\% (6) & 15.8\% (617) & 4.2\% (7) & 2.8\% (28)\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item \textit{Abbreviations:} 
\item LRA - Lipid regulating agent; IMD - Index of Multiple Deprivation; BMI - Body Mass Index; CAD - Coronary Arterial Disease; CBS - Coronary Bypass Surgery; CVD - Cardiovascular disease; PAD - Peripheral arterial disease; CKD - Chronic Kidney Disease; SD - Standard deviation.
\end{tablenotes}
\end{threeparttable}
\end{table}

~

\begin{figure}
\includegraphics[width=103.33in]{C:/Users/lm16564/OneDrive - University of Bristol/Documents/rrr/thesis/figures/cprd-analysis/fp_p1} \caption{Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.}\label{fig:cprdPrimary}
\end{figure}

\newpage

\hypertarget{bibliography}{%
\section*{Bibliography}\label{bibliography}}
\addcontentsline{toc}{section}{Bibliography}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\hypertarget{ref-prince2016}{}%
\CSLLeftMargin{1. }
\CSLRightInline{Prince M, Ali G-C, Guerchet M, Prina AM, Albanese E, Wu Y-T. Recent global trends in the prevalence and incidence of dementia, and survival with dementia. Alzheimer's Research \& Therapy. 2016 Jul;8. }

\leavevmode\hypertarget{ref-jobke2018}{}%
\CSLLeftMargin{2. }
\CSLRightInline{Jobke B, McBride T, Nevin L, Peiperl L, Ross A, Stone C, et al. Setbacks in {Alzheimer} research demand new strategies, not surrender. PLoS medicine. 2018 Feb;15(2):e1002518. }

\leavevmode\hypertarget{ref-ashburn2004}{}%
\CSLLeftMargin{3. }
\CSLRightInline{Ashburn TT, Thor KB. Drug repositioning: Identifying and developing new uses for existing drugs. Nature Reviews Drug Discovery. 2004;3(8):673. }

\leavevmode\hypertarget{ref-pushpakom2019}{}%
\CSLLeftMargin{4. }
\CSLRightInline{Pushpakom S, Iorio F, Eyers PA, Escott KJ, Hopper S, Wells A, et al. Drug repurposing: Progress, challenges and recommendations. Nature Reviews Drug Discovery. 2019;18(1):41. }

\leavevmode\hypertarget{ref-walker2019a}{}%
\CSLLeftMargin{5. }
\CSLRightInline{Walker VM, Davies NM, Martin RM, Kehoe PG. Comparison of antihypertensive drug classes for dementia prevention. bioRxiv. 2019 Jan;517482. }

\leavevmode\hypertarget{ref-chu2018}{}%
\CSLLeftMargin{6. }
\CSLRightInline{Chu C-S, Tseng P-T, Stubbs B, Chen T-Y, Tang C-H, Li D-J, et al. Use of statins and the risk of dementia and mild cognitive impairment: {A} systematic review and meta-analysis. Scientific Reports. 2018 Apr;8(1):5804. }

\leavevmode\hypertarget{ref-larsson2018}{}%
\CSLLeftMargin{7. }
\CSLRightInline{Larsson SC, Markus HS. Does {Treating Vascular Risk Factors Prevent Dementia} and {Alzheimer}'s {Disease}? {A Systematic Review} and {Meta}-{Analysis}. Journal of Alzheimer's Disease. 2018 Jan;64(2):657--68. }

\leavevmode\hypertarget{ref-ancelin2012}{}%
\CSLLeftMargin{8. }
\CSLRightInline{Ancelin M-L, Carrière I, Barberger-Gateau P, Auriacombe S, Rouaud O, Fourlanos S, et al. Lipid lowering agents, cognitive decline, and dementia: The three-city study. Journal of Alzheimer's Disease. 2012 Jan;30(3):629--37. }

\leavevmode\hypertarget{ref-bettermann2012}{}%
\CSLLeftMargin{9. }
\CSLRightInline{Bettermann K, Arnold AM, Williamson J, Rapp S, Sink K, Toole JF, et al. Statins, {Risk} of {Dementia}, and {Cognitive Function}: {Secondary Analysis} of the {Ginkgo Evaluation} of {Memory Study}. Journal of Stroke and Cerebrovascular Diseases. 2012 Aug;21(6):436--44. }

\leavevmode\hypertarget{ref-rea2005}{}%
\CSLLeftMargin{10. }
\CSLRightInline{Rea TD, Breitner JC, Psaty BM, Fitzpatrick AL, Lopez OL, Newman AB, et al. Statin {Use} and the {Risk} of {Incident Dementia}: {The Cardiovascular Health Study}. Archives of Neurology. 2005 Jul;62(7):1047--51. }

\leavevmode\hypertarget{ref-casey2016}{}%
\CSLLeftMargin{11. }
\CSLRightInline{Casey JA, Schwartz BS, Stewart WF, Adler NE. Using {Electronic Health Records} for {Population Health Research}: {A Review} of {Methods} and {Applications}. Annual Review of Public Health. 2016 Mar;37(1):61--81. }

\leavevmode\hypertarget{ref-herrett2015}{}%
\CSLLeftMargin{12. }
\CSLRightInline{Herrett E, Gallagher AM, Bhaskaran K, Forbes H, Mathur R, van Staa T, et al. Data {Resource Profile}: {Clinical Practice Research Datalink} ({CPRD}). International Journal of Epidemiology. 2015 Jun;44(3):827--36. }

\leavevmode\hypertarget{ref-walker2016a}{}%
\CSLLeftMargin{13. }
\CSLRightInline{Walker VM, Davies NM, Jones T, Kehoe PG, Martin RM. Can commonly prescribed drugs be repurposed for the prevention or treatment of {Alzheimers} and other neurodegenerative diseases? {Protocol} for an observational cohort study in the {UK Clinical Practice Research Datalink}. BMJ Open. 2016;6(12). }

\leavevmode\hypertarget{ref-vonelm2008}{}%
\CSLLeftMargin{14. }
\CSLRightInline{von Elm E, Altman DG, Egger M, Pocock SJ, Gøtzsche PC, Vandenbroucke JP. The {Strengthening} the {Reporting} of {Observational Studies} in {Epidemiology} ({STROBE}) statement: Guidelines for reporting observational studies. Journal of Clinical Epidemiology. 2008 Apr;61(4):344--9. }

\leavevmode\hypertarget{ref-wishart2017}{}%
\CSLLeftMargin{15. }
\CSLRightInline{Wishart DS, Feunang YD, Guo AC, Lo EJ, Marcu A, Grant JR, et al. {DrugBank} 5.0: A major update to the {DrugBank} database for 2018. Nucleic Acids Research. 2017;46(D1):D1074--82. }

\leavevmode\hypertarget{ref-levesque2010}{}%
\CSLLeftMargin{16. }
\CSLRightInline{Lévesque LE, Hanley JA, Kezouh A, Suissa S. Problem of immortal time bias in cohort studies: Example using statins for preventing progression of diabetes. BMJ. 2010 Mar;340. }

\leavevmode\hypertarget{ref-lamarca1998}{}%
\CSLLeftMargin{17. }
\CSLRightInline{Lamarca R, Alonso J, Gomez G, Munoz A. Left-truncated {Data With Age} as {Time Scale}: {An Alternative} for {Survival Analysis} in the {Elderly Population}. The Journals of Gerontology Series A: Biological Sciences and Medical Sciences. 1998 Sep;53A(5):M337--43. }

\leavevmode\hypertarget{ref-gail2009}{}%
\CSLLeftMargin{18. }
\CSLRightInline{Gail MH, Graubard B, Williamson DF, Flegal KM. Comments on {`{Choice} of time scale and its effect on significance of predictors in longitudinal studies'} by {Michael J}. {Pencina}, {Martin G}. {Larson} and {Ralph B}. {D}'{Agostino}, {\emph{Statistics}}{ \emph{in} }{\emph{Medicine}} 2007; {\textbf{26}} :1343-1359. Statistics in Medicine. 2009 Apr;28(8):1315--7. }

\leavevmode\hypertarget{ref-pencina2007}{}%
\CSLLeftMargin{19. }
\CSLRightInline{Pencina MJ, Larson MG, D'Agostino RB. Choice of time scale and its effect on significance of predictors in longitudinal studies. Statistics in Medicine. 2007 Mar;26(6):1343--59. }

\leavevmode\hypertarget{ref-nationalinstituteforhealthandcareexcellence}{}%
\CSLLeftMargin{20. }
\CSLRightInline{National Institute for Health and Care Excellence. Cardiovascular disease: Risk assessment and reduction, including lipid modification. https://www.nice.org.uk/guidance/cg181/ifp/chapter/Drug-treatments-to-lower-your-cholesterol; {NICE}; }

\leavevmode\hypertarget{ref-mcguinness2016a}{}%
\CSLLeftMargin{21. }
\CSLRightInline{McGuinness B, Craig D, Bullock R, Passmore P. Statins for the prevention of dementia. Cochrane Database of Systematic Reviews. 2016;(1). }

\leavevmode\hypertarget{ref-heartprotectionstudycollaborativegroup2002}{}%
\CSLLeftMargin{22. }
\CSLRightInline{Heart Protection Study Collaborative Group. {MRC}/{BHF Heart Protection Study} of cholesterol lowering with simvastatin in 20 536 high-risk individuals: A randomised placebocontrolled trial. The Lancet. 2002 Jul;360(9326):7--22. }

\leavevmode\hypertarget{ref-poly2020}{}%
\CSLLeftMargin{23. }
\CSLRightInline{Poly TN, Islam MM, Walther BA, Yang H-C, Wu C-C, Lin M-C, et al. Association between {Use} of {Statin} and {Risk} of {Dementia}: {A Meta}-{Analysis} of {Observational Studies}. Neuroepidemiology. 2020;54(3):214--26. }

\leavevmode\hypertarget{ref-chao2015}{}%
\CSLLeftMargin{24. }
\CSLRightInline{Chao T-F, Liu C-J, Chen S-J, Wang K-L, Lin Y-J, Chang S-L, et al. Statins and the risk of dementia in patients with atrial fibrillation: {A} nationwide population-based cohort study. International Journal of Cardiology. 2015 Oct;196:91--7. }

\leavevmode\hypertarget{ref-williams}{}%
\CSLLeftMargin{25. }
\CSLRightInline{Williams DM, Finan C, Schmidt AF, Burgess S, Hingorani AD. Lipid lowering and {Alzheimer}'s disease risk: A {Mendelian} randomization study. Annals of Neurology. 2019;n/a(n/a). }

\leavevmode\hypertarget{ref-wilkinson2018}{}%
\CSLLeftMargin{26. }
\CSLRightInline{Wilkinson T, Ly A, Schnier C, Rannikmäe K, Bush K, Brayne C, et al. Identifying dementia cases with routinely collected health data: {A}~systematic review. Alzheimer's \& Dementia. 2018 Aug;14(8):1038--51. }

\leavevmode\hypertarget{ref-mcguinness2019b}{}%
\CSLLeftMargin{27. }
\CSLRightInline{McGuinness LA, Warren-Gash C, Moorhouse LR, Thomas SL. The validity of dementia diagnoses in routinely collected electronic health records in the {United Kingdom}: {A} systematic review. Pharmacoepidemiology and Drug Safety. 2019 Feb;28(2):244--55. }

\leavevmode\hypertarget{ref-korologou-linden2020}{}%
\CSLLeftMargin{28. }
\CSLRightInline{Korologou-Linden R, Anderson EL, Howe LD, Millard LAC, Ben-Shlomo Y, Williams DM, et al. The causes and consequences of {Alzheimer}'s disease: Phenome-wide evidence from {Mendelian} randomization. medRxiv. 2020 Mar;2019.12.18.19013847. }

\end{CSLReferences}

\end{document}

### 2021-07-12 manuscripts/cprd/supp-materials.Rmd
End of day:

@@
       toc: true
+      toc_depth: 2
       number_sections: false
-      toc_depth: 2
-      reference_docx: "../../templates/word-styles-reference-01-no_line_num.docx"
+      reference_docx: "../../templates/word-styles-reference-01.docx"
 ---
@@
 
+Any changes made to the approved procotol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".
+
 Main changes include:
@@
 
-## Supplementary Table 1: Definition of exposures and covariates
+## Supplementary Table 1: STROBE Reporting Guidelines {#supp-tab-strobe}
+
+```{r child = 'supplementary_files/STROBE-Checklist.Rmd', eval = FALSE}
+```
+
+A copy of the RECORD Checklist[@nicholls2016record] is provided below.
+
+__To be copied in__
+
+\newpage
+
+## Supplementary Table 2: Definition of exposures and covariates
+
+(ref:covariateDef-caption) Definition of covariates adjusted for in the Cox PR model.
+
+The code lists used to define covariates adjusted for in the fully-adjusted model (see Supplementary Table \@ref(tab:covariateDef-table)) were originally created for use in a previous analysis.[@walker2020] Some code lists were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017] and these are noted in the table.
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:covariateDef-caption) Definition of covariates
-
-```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
+```{r covariateDef-table, echo = FALSE}
 ```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
 
@@
 
-## Supplementary Table 2: Adherence and switching by drug class
+## Supplementary Table 3: Adherence and switching by drug class
 
-&nbsp;
+(ref:cprdSSA-caption) Adherence and switching by drug class.
 
 <!----------------------------------------------------------------------------->
-(ref:cprdSSA-caption) cprdSSA
 
@@
 
-```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-\newpage
-
-## Supplementary Table 3: STROBE Reporting Guidelines {#supp-tab-strobe}
-
-```{r child = 'supplementary_files/STROBE-Checklist.Rmd', eval = FALSE}
+```{r cprdSSA-table, message=FALSE, echo = FALSE}
 ```
 
-__To be completed__
-
-\newpage
-
-## Supplementary Table 4: Statin type prescribing by year {#supp-tab-sta-type}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeTable-caption) Statin prescription by year
-
-```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
-```
 <!----------------------------------------------------------------------------->
@@
 
-```{r supp-fig-decision-tree,echo = FALSE, fig.cap="The algorithm used to choose between two diagnosis. This decision tree is adapted with permission from Walker _et al_ (2019).[@walker2019a]"}
+```{r supp-fig-decision-tree,echo = FALSE, fig.cap="The algorithm used to choose between two diagnosis. This decision tree is adapted with permission from Walker _et al_ (2020).[@walker2020]"}
 knitr::include_graphics(here::here("figures/cprd-analysis/decision_tree.png"))
@@
 ## Supplementary Figure 2 {#supp-fig-attrition}
-```{r supp-fig-attrition,echo = FALSE, fig.cap="Attrition of participants as the eligibility criteria were applied.", fig.width="60%"}
+
+```{r supp-fig-attrition,echo = FALSE, fig.cap="Attrition of participants as the eligibility criteria were applied.", out.width='60%'}
 knitr::include_graphics(here::here("figures/cprd-analysis/cohort_attrition.png"))
@@
 ## Supplementary Figure 3 {#supp-fig-unadjusted}
-```{r supp-fig-comparison,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, adjusted only for age."}
+```{r supp-fig-comparison,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome using three models adjusted for age, age and sex, and all covariates respectively."}
 knitr::include_graphics(here::here("figures/cprd-analysis/fp_unadjusted.jpeg"))
@@
 
-## Supplementary Figure 4 {#supp-fig-entry}
-```{r supp-fig-entry,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, stratified by year of entry into the cohort.
-{Note: Venexia reccomend including some info on average length of follow-up for each group beside the HR - will be done before submission.}"}
-knitr::include_graphics(here::here("figures/cprd-analysis/fp_cohort_entry.jpeg"))
-```
-
-\newpage
-
-## Supplementary Figure 5 {#supp-fig-pregnancy}
-```{r supp-fig-pregnancy,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, removing women who were less than 55 years of age at index."}
+## Supplementary Figure 4 {#supp-fig-pregnancy}
+```{r supp-fig-pregnancy,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, removing participants who were less than 55 years of age at index."}
 knitr::include_graphics(here::here("figures/cprd-analysis/fp_pregnancy.jpeg"))
@@
 
-## Supplementary Figure 6 {#supp-fig-sta-type}
+## Supplementary Figure 5 {#supp-fig-sta-type}
 ```{r supp-fig-sta-type, echo = FALSE, fig.cap="Association of statins with a dementia or related outcome, stratified by statin lipophilic/hydrophilic properties."}
@@
 
-## Supplementary Figure 7 {#supp-fig-backpain}
-```{r supp-fig-backpain,echo = FALSE, fig.cap="Association of any lipid regulating agent with backpain and ischemic heart disease (IHD)."}
+## Supplementary Figure 6 {#supp-fig-backpain}
+```{r supp-fig-backpain,echo = FALSE, fig.cap="Association of any lipid regulating agent with backpain, ischemic heart disease (IHD), and Type 2 diabetes."}
 knitr::include_graphics(here::here("figures/cprd-analysis/fp_control_outcomes.jpeg"))

### 2021-07-12 R/04-Code-CPRD-Analysis.R

@@ -98,7 +98,17 @@ if(t[1]-sum(t[2:9]) != 0){
 cprdCharacteristics_table <- table1_disp
 
 if(doc_type == "docx") {
-  apply_flextable(cprdCharacteristics_table, caption = "(ref:cprdCharacteristics-caption)")
+  apply_flextable(cprdCharacteristics_table, caption = "(ref:cprdCharacteristics-caption)") %>%
+    flextable::add_footer_row(colwidths = 10,
+                          values = paste("LRA - Lipid regulating agent;",
+                                              "IMD - Index of Multiple Deprivation;",
+                                              "BMI - Body Mass Index;",
+                                              "CAD - Coronary Arterial Disease;",
+                                              "CBS - Coronary Bypass Surgery;",
+                                              "CVD - Cardiovascular disease;",
+                                              "PAD - Peripheral arterial disease;",
+                                              "CKD - Chronic Kidney Disease;",
+                                         "SD - Standard deviation."))
 } else{
   table <- knitr::kable(
     cprdCharacteristics_table,
@@ -125,7 +135,8 @@ if(doc_type == "docx") {
         "CBS - Coronary Bypass Surgery;",
         "CVD - Cardiovascular disease;",
         "PAD - Peripheral arterial disease;",
-        "CKD - Chronic Kidney Disease"
+        "CKD - Chronic Kidney Disease;",
+        "SD - Standard deviation."
       )
     )
     
@@ -227,7 +238,7 @@ fu_ab_text <- paste0(round(characteristics$c1[1],1),
 
 # Median and IQR for age at index
 age_text <- paste0(characteristics$c1[4],
-                   " years (IQR:",
+                   " years (Inter quartile range (IQR):",
                    characteristics$c1[5],
                    "-",
                    characteristics$c1[6],
@@ -246,6 +257,26 @@ t1$V2 <- as.numeric(t1$V2)
 percentage.statins <-
[…]

### 2021-07-16 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane20001931]
+(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
 
@@
 Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]
+A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]
 
@@
 
-There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018a; @sterne2016] and thus directly evaluating the internal validity of a study.
+There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
 Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
@@
 
-Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] The motivation for this decision was two-fold.
+Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold.
 In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
@@
 Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
+This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
 
@@
 
-Patient and
+Patient and public memebers were intended to be involved at this poit
 
@@
 
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019d; @wilkinson2018b]
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
 
@@
 
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
+-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.

### 2021-07-16 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
 <!-- ## Additional ideas -->
+
+<!-- TODO Need to add some information on the generation and use of propensity scores -->
 
@@
 <!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
+
+<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->
 
@@
 ```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_p1.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_p1.png"))
 ```
@@
 ```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_complete_case.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_complete_case.png"))
 ```
@@
 #### Control outcomes
+
+```{r controlOutcomesText, echo = FALSE, message = FALSE}
+```
 
@@
 ```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_control_outcomes.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_control_outcomes.png"))
 ```
@@
 ```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_unadjusted.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_unadjusted.png"))
 ```
@@
 
+```{r cohortEntry, include=FALSE}
+```
+
 <!----------------------------------------------------------------------------->
@@
 ```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/fp_cohort_entry.jpeg"))
+knitr::include_graphics(file.path("figures/cprd-analysis/forester_cohort_entry.png"))
 ```
@@
 
-In the second sensitivity cohort, removing participants coded as female and aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
+In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
 
@@
 ```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_pregnancy.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_pregnancy.png"))
 ```
@@
 ```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","fp_sta_type.jpeg"))
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_sta_type.png"))
 ```

### 2021-07-16 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 
-Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2,3^, Venexia M Walker^1,2,4^, Neil M Davies^1,2^, Richard M Martin^1,2,3^,  Elizabeth Coulthard^5^, George Davey-Smith^1,2,3^,  Patrick G Kehoe^5,6^ and Yoav Ben-Shlomo^2^
+Luke A McGuinness^1,2,\*^, Julian PT Higgins^1,2,3^, Venexia M Walker^1,2,4^, Neil M Davies^1,2^, Richard M Martin^1,2,3^,  Elizabeth Coulthard^5^, George Davey-Smith^1,2,3^,  Patrick G Kehoe^5^ and Yoav Ben-Shlomo^2^
 
@@
 (5)	Bristol Medical School: Translational Health Sciences, University of Bristol, Bristol, UK
-(6)	Dementia Research Group, Bristol Medical School, University of Bristol, Bristol, UK
 
@@
 YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
-LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1).
+LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1, MC_UU_00011/4).
 JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
 The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.
+NMD is supported by a Norwegian Research Council Grant number 295989.
 
@@
 
-__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease and dementia.
-As a result, these readily modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
-Here, we assess the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.
+__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia.
+As a result, these modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
+Here, we test the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.
 
-__Methods:__ A retrospective cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
-Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).
+__Methods:__ A cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
+Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible AD).
 
-__Results:__ We analyzed `r totaltext` with a median follow-up of `r fu_ab_text`.
-We found little evidence that lipid-regulating agents were associated with risk of Alzheimer’s disease  (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
-Evidence for an increased risk of one of the control outcomes, ischemic heart disease (`r ihd_text`), indicated the presence of substantial residual confounding related to vascular factors.
+__Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` participant-years (median: `r fu_text`).
+We found little evidence that lipid-regulating agents were associated with risk of AD (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+Evidence from a number of control outcomes (ischeamic heart disease `r ihd_text`; backpain `r backpain_text` and diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding related to vascular factors.
 
-__Conclusion:__ We found little evidence that lipid-regulating agents had any effect on Alzheimer’s disease risk.
+__Conclusion:__ We found little evidence that lipid-regulating agents were associated with reduced on Alzheimer’s disease risk.
 There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.
@@
 * Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia.
-In all cases, the estimated associations were driven by the statin subgroup, which comprised the majority of participants in our cohort.
+In all cases, the estimated associations were driven by the statin subgroup, which comprised most participants in our cohort.
 
-* However, evidence from the control outcome analyses indicated strong residual confounding by indication, mostly likely related to vascular factors.
+* Evidence from the control outcome analyses indicated strong residual confounding by indication, mostly likely related to vascular factors.
 
@@
 
-Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2019a] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments.
+Several cardiovascular factors have been identified as potential risk factors for dementia,[@walker2020] and of these, circulating lipid levels represent a promising target for intervention due to the ready availability of lipid-modifying treatments.
 In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy.
@@
 Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
+Records pre-dating the 1995 cutoff were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
 
-An *a priori* protocol for this study was published,[@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
+An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Supplementary Materials 1.
 This study was reported in line with the RECORD guidelines (Supplementary Table 1).[@nicholls2016record]
@@
 
-In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.[@sterne2009a] All covariates included in the analytic model were also included in the imputation model.[@moons2006using] The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).
+In the case of missing data, we used multiple imputation by chained equations (MICE) in STATA to create 20 imputed datasets.[@sterne2009] All covariates included in the analytic model were also included in the imputation model.[@moons2006using] The full imputation model is available for inspection (See [Data/Code availability](#data-code-avail) section).
 
@@
 
+<!-- TODO Need a little bit here on comparison with Smeeth -->
+
 Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] echoing the distribution of participants in our analysis.
@@
 
-A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016a] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
+A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
 A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]
@@
 Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams2020]
 
@@
 There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contained prescriptions for lipid-regulating agents.
-Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
+Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 
-Our study may also be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use.
+Our study is likely to be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use.
 Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
@@
 ```{r cprdPrimary, echo = FALSE, fig.cap="Test"}
-knitr::include_graphics(here::here("figures","cprd-analysis","fp_p1.jpeg"))
+knitr::include_graphics(here::here("figures","cprd-analysis","forester_p1.png"))
 ```
@@
 
-_Figure 1: Results from the primary analyses of CPRD data, stratified by dementia outcome and drug class.
+_Figure 1: Hazard ratios produced by the primary analyses of CPRD data, stratified by dementia outcome and drug class.
 All results were obtained using the fully adjusted model and participant age as the time scale._

### 2021-07-16 R/04-Code-CPRD-Analysis.R

@@ -1,35 +1,54 @@
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- smeethComparison-table
 
-smeethComparison_table <- mtcars[1:4,1:3]
+smeethComparison_table <- mtcars[1:4, 1:3]
 
-if(doc_type == "docx"){
-apply_flextable(smeethComparison_table,caption = "(ref:smeethComparison-caption)")
-}else{
-knitr::kable(smeethComparison_table, format = "latex", caption = "(ref:smeethComparison-caption)", caption.short = "(ref:smeethComparison-scaption)", booktabs = TRUE) %>% 
-row_spec(0, bold = TRUE) %>%
-kable_styling(latex_options = c("HOLD_position"))
+if (doc_type == "docx") {
+  apply_flextable(smeethComparison_table, caption = "(ref:smeethComparison-caption)")
+} else{
+  knitr::kable(
+    smeethComparison_table,
+    format = "latex",
+    caption = "(ref:smeethComparison-caption)",
+    caption.short = "(ref:smeethComparison-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"))
 }
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- load-files
 
-attrition <- read.csv(here::here("data","cprd","cohort_attrition.csv"))
+attrition <-
+  read.csv(here::here("data", "cprd", "cohort_attrition.csv"))
 
-p1 <- read.csv(here::here("data","cprd","regression_results_p1.csv")) %>%
+p1 <-
+  read.csv(here::here("data", "cprd", "regression_results_p1.csv")) %>%
   filter(drug == "Any") %>%
   select(outcome, N_fail) %>%
   unique()
 
-p1$outcome <- factor(p1$outcome, levels = c("Any dementia", "Probable AD", "Possible AD", "Vascular dementia", "Other dementia"))
-p1 <- p1[order(p1$outcome),]
+p1$outcome <-
+  factor(
+    p1$outcome,
+    levels = c(
+      "Any dementia",
+      "Probable AD",
+      "Possible AD",
+      "Vascular dementia",
[…]

### 2021-07-16 R/forester.R

@@ -1,0 +1,524 @@
+#' Create a forest plot column in a table
+#'
+#' Creates an png image with the forest plot column inserted in the supplied data frame.
+#'
+#' @param left_side_data Data frame (required). The information to be displayed to the left of the forest plot.
+#' @param estimate Vector. The point estimates to be displayed in the forest plot.
+#' @param ci_low Vector. The lower confidence bounds.
+#' @param ci_high Vector. The upper confidence bounds.
+#' @param right_side_data Data frame (optional). Information to be displayed on the right side of the table. If not supplied, an Estimate column is generated automatically.
+#' @param estimate_precision Integer. The number of decimal places on the estimate (default 1)
+#' @param ggplot_width Integer. The width of forest plot in characters (default 30)
+#' @param null_line_at Numeric. Default 0. Change to 1 if using relative measures such as OR, RR.
+#' @param file_path String. Where to save the image, default "forestable_plot.png" in the current working directory.
+#' @param dpi Numeric. The image resolution in dpi, default 600
+#' @param display Logical. Show the table in RStudio viewer? Default TRUE. If you're using forester inside of RMarkdown, change to false and display the generated images using standard markdown syntax (See file_path).
+#' @param blank_na Logical. Should missing values in the left side table be displayed as blank? Default TRUE, if FALSE, NA values will be shown
+#' @param font_family String. The font to use for the ggplot and table. Default "mono".
+#' @param estimate_col_name String. The name for the generated estimate column. Default "Estimate"
+#' @param stripe_colour Hex String. Colour to use for the table stripes, default "#eff3f2"
+#' @param x_scale_linear Logical. Default TRUE, change to FALSE for log scale
+#' @param xlim Vector. Manually specify limits for the x axis as a vector length 2, i.e. c(low, high)
+#' @param xbreaks Vector. X axis breaks to label. Specify limits in xlim if using this option.
+#' @param nudge_x Numeric. Nudge the alignment horizontally. Default 1. Higher values make the entire plot wider and consequently space out the elements of the figure.
[…]

### 2021-07-16 R/helper.R

@@ -1,4 +1,5 @@
 library(magrittr)
+source(here::here("R/forester.R"))
 
 # Generates an line pandoc citation string for all packages used in the 
 
@@ -178,7 +179,7 @@ todo <- function(fp){
 
 chapter_edit <- function(N){
   
-    # Open Chapter RMarkdown file
+  # Open Chapter RMarkdown file
   chapters <- list.files(pattern = ".Rmd")
   
   chapter <- chapters[which(data.table::like(chapters, N))]
@@ -245,13 +246,13 @@ apply_flextable <- function(data, caption = NULL) {
   
   ft <- flextable::flextable(data)  %>%
     flextable::bg(bg = "#A6A6A6", part = "header") %>%
-    bold(part = "header") %>%
-    bold(j=1, part = "body") %>%
-    align(align = "center", part = "all" ) %>%
-    align(j = 1, align = "left") %>%
-    bg(i = ~ seq(from = 1, to = nrow(data)) %% 2 == 0, bg = "#DDDDDD", part = "body") %>%
-    fontsize(size = 9, part = "all") %>%
-    set_table_properties(layout = "autofit")
+    flextable::bold(part = "header") %>%
+    flextable::bold(j=1, part = "body") %>%
+    flextable::align(align = "center", part = "all" ) %>%
+    flextable::align(j = 1, align = "left") %>%
+    flextable::bg(i = ~ seq(from = 1, to = nrow(data)) %% 2 == 0, bg = "#DDDDDD", part = "body") %>%
+    flextable::fontsize(size = 9, part = "all") %>%
+    flextable::set_table_properties(layout = "autofit")
   
   if (!is.null(caption)) {
     ft <- flextable::set_caption(ft, caption)
@@ -259,3 +260,177 @@ apply_flextable <- function(data, caption = NULL) {
   
   return(ft)
 }
+
+
+create_title_row <- function(top_title = "Any dementia", first_col, title) {
+  if (title == top_title) {
+    temp <- data.frame(
+      tmp = title,
+      HR = NA,
+      ci_lower = NA,
+      ci_upper = NA,
+      N_sub = NA,
+      N_fail = NA
+    )
+  } else{
+    temp <- data.frame(
+      tmp = c(" ", title),
+      HR = c(NA, NA),
+      ci_lower = c(NA, NA),
+      ci_upper = c(NA, NA),
+      N_sub = c(NA, NA),
+      N_fail = c(NA, NA)
+    )
[…]

### 2021-07-20 01-Chp-Background.Rmd
End of day

@@
 
-$$TC \approx LDLc + HDLc + kTG$$
+\begin{equation}
+  TC \approx LDLc + HDLc + kTG
+  (\#eq:total-cholesterol-formula)
+\end{equation}
+
 where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).

### 2021-07-20 03-Chp-Systematic-Review.Rmd
End of day

@@
 
-<!-- -   TODO Examine how many times a primary study was included in a review\ -->
+<!-- -   TODO Examine how many times a primary study was included in a review -->
 <!-- -   TODO Look at whether searching preprints made any difference to my results -->
@@
 A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]
+
+### Contributions
+
+This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.
+
+<!-- TODO Double check this list at the end of the project. -->
 
@@
 
-$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
+\begin{equation}
+  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
+  (\#eq:AC1-main)
+\end{equation}
 
@@
 
-$$q = \frac{(A+C)+(A+B)}{2N}$$
+\begin{equation}
+  q = \frac{(A+C)+(A+B)}{2N}
+  (\#eq:AC1-supp)
+\end{equation}
 
@@
 The study design-specific tools are introduced and discussed in more detail in the following sections.
+
+In addition, the tool also aim to capture the potential direction of bias for each given domain.
+An optional question at the end of each domain, e.g.
+for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included
+
+* Not applicable 
+* Favours experimental 
+* Favours comparator
+* Towards null 
+* Away from null 
+* Unpredictable
 
@@
 
-Need formula here, and description of different methods and quarrels regarding disctinction fixed effect vs random effects meta-analyses.
+Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
 
 This analytical approach was used for
+
+\begin{equation}
+  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
+  (\#eq:meta-analysis-fixed)
+\end{equation}
+
+where ...
+
+<!-- TODO Need equation for random effects too -->
 
@@
 
+Following the search
+
 `r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.
@@
 <!--- Cross check this with the actual numbers included --->
+
+No eligible records were identified in the screening of the 500 records excluded by the search. Many of these were basic science studies <!-- TODO text -->
 
@@
 
-Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]
+&nbsp;
 
-As part of our our forward snowballing exercise (where articles citing an included study are cited), Irecorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
+As part of our our forward snowballing exercise (where articles citing an included study are cited), I recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
 Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Characteristics of included studies
@@
 XXXX studies met the criteria for inclusion in the review.
+
+Table \@ref(tab:incl-studies-character) shows the characteristics
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:studyCharacteristics-caption) studyCharacteristics
+
+(ref:studyCharacteristics-scaption) studyCharacteristics
+
+```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Risk of bias {#risk-of-bias-subheading}
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Meta-n
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Sources of heterogeneity
@@
 Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 Many studies did not report the codelists used to run the analysis,
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Previous reviews
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Inclusion of preprints
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Open data sharing {#sys-rev-open-data}
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Original contribution to research
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Comparison with other reviews
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Reviewing Mendelian randomisations studies
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+
 ### Strenghts and limitations
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 #### Inclusion of preprints
 
-Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
-cut-off point for the search (e.g. they would not have been captured by the search for published papers)
+Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
+they would not have been captured by the search for published papers)
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Use in other chapters
 
@@
 
-### Use in other chapters
-
 Findings from this review are used though out the subsequent chapters.
@@
 
+## Conclusions
+
+\newpage
+
 ## References

### 2021-07-20 04-Chp-CPRD-Analysis.Rmd
End of day

@@
 source("R/helper.R")
+library(dplyr)
 options(scipen = 99)
@@
 
-$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
+\begin{equation}
+  h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)
+  (\#eq:cox-model)
+\end{equation}
 

### 2021-07-20 front-and-back-matter/99-appendices.Rmd
End of day:
End of day

@@
 <!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+knitr::read_chunk(here::here("R/appendix.R"))
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
 
@@
 
-Impor
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:searchHits-caption) Overview of the full Medline search strategy.
+
+(ref:searchHits-scaption) searchHits
+
+```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 ```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
-
-wosDatabases_table <- read.csv(here::here("data/sys-rev/wosDatabases.csv"))
-
-if(doc_type == "docx") {
-  knitr::kable(wosDatabases_table, caption = "(ref:wosDatabases-caption)")
-} else{
-  knitr::kable(
-    wosDatabases_table,
-    format = "latex",
-    caption = "(ref:wosDatabases-caption)",
-    caption.short = "(ref:wosDatabases-scaption)",
-    booktabs = TRUE
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    column_spec(column = 1, width = paste0(18,"em")) %>%
-    column_spec(column = 2, width = paste0(8,"em")) %>%
-    column_spec(column = 3, width = paste0(6,"em")) %>%
-    row_spec(2:nrow(wosDatabases_table)-1, hline_after = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position"))
-}
 
@@
 ## Creating
+
+## Copies of papers arising from this thesis
+
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}

### 2021-07-20 R/03-Code-Systematic-Review.R

@@ -162,4 +162,78 @@ if(doc_type == "docx") {
     kableExtra::row_spec(2, extra_css = "border-bottom: 1px solid")
 }
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- chunkname-table
 
+chunkname_table <- mtcars
+
+if(doc_type == "docx"){
+apply_flextable(chunkname_table,caption = "(ref:chunkname-caption)")
+}else{
+knitr::kable(chunkname_table, format = "latex", caption = "(ref:chunkname-caption)", caption.short = "(ref:chunkname-scaption)", booktabs = TRUE) %>% 
+row_spec(0, bold = TRUE) %>%
+kable_styling(latex_options = c("HOLD_position"))
+}
+
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# primaryFigures----
+
+test <- rio::import("data/sys-rev/data_extraction_reviewer1.xlsx") %>%
+  janitor::clean_names() %>%
+  dplyr::filter(done == "Y",
+         !is.na(point_estimate), 
+         measure == "HR", 
+         outcome == "Dementia", 
+         exposure %like% "[Ss]tatin", 
+         !grepl(pattern = "[Ll]ipo|[Hh]ydro", x = .$exposure)) %>%
+  mutate(point = log(point_estimate), 
+         SE = (log(lower_95_percent) - log(upper_95_percent))/3.92) %>%
+  arrange(author, year)
+
+t <- metafor::rma.uni(data = test,
+                      yi = point,
+                      sei = SE)
+
+png(file = 'forestplot_acd.png') 
+metafor::forest(t, transf=exp, slab = paste(test$author, test$year), refline =1, xlab = "HR for any dementia")
+dev.off() 
+
+
+
+test <- rio::import("data/sys-rev/data_extraction_reviewer1.xlsx") %>%
+  janitor::clean_names() %>%
+  filter(done == "Y",
+         !is.na(point_estimate), 
+         measure == "HR", 
+         outcome %like% "VaD", 
+         exposure %like% "[Ss]tatin", 
+         !grepl(pattern = "[Ll]ipo|[Hh]ydro", x = .$exposure)) %>%
+  mutate(point = log(point_estimate), 
[…]

### 2021-07-20 R/appendix.R

@@ -1,0 +1,63 @@
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- searchHits-table
+
+test <-
+  # Read in all sheets
+  read_excel_allsheets(here::here("data/sys-rev/searchResults_19_06_03.xlsx"))[2] %>%
+  
+  # Filter columns and clean names
+  lapply(
+    function(x)
+      x %>% select(1:3) %>% rename(
+        "#" = x1,
+        "Search term" = x2,
+        "Hits" = x3
+      )
+  )
+
+
+searchHits_table <- test$Medline
+
+if (doc_type == "docx") {
+  apply_flextable(searchHits_table, caption = "(ref:searchHits-caption)")
+} else{
+  knitr::kable(
+    searchHits_table,
+    format = "latex",
+    caption = "(ref:searchHits-caption)",
+    caption.short = "(ref:searchHits-scaption)",
+    longtable = TRUE,
+    booktabs = TRUE,
+    align = "lll",
+    linesep = ""
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    row_spec(c(18,36,73:76,78,84,96,97,100,107,108,118:123), bold= T, italic = T) %>%
+    column_spec(column = 1, width = paste0(2,"em")) %>%
+    column_spec(column = 2, width = paste0(26,"em")) %>%
+    column_spec(column = 3, width = paste0(4,"em")) %>%
+    kable_styling(latex_options = c("HOLD_position","repeat_header"))
+}
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- wosDatabases-table
+
+wosDatabases_table <- read.csv(here::here("data/sys-rev/wosDatabases.csv"))
+
+if(doc_type == "docx") {
+  knitr::kable(wosDatabases_table, caption = "(ref:wosDatabases-caption)")
+} else{
+  knitr::kable(
+    wosDatabases_table,
+    format = "latex",
+    caption = "(ref:wosDatabases-caption)",
+    caption.short = "(ref:wosDatabases-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
[…]

### 2021-07-20 R/helper.R

@@ -1,4 +1,6 @@
 library(magrittr)
+
+# Load forester function
 source(here::here("R/forester.R"))
 
 # Generates an line pandoc citation string for all packages used in the 
@@ -434,3 +436,20 @@ generate_forester_plot <-
     )
     
   }
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+
+read_excel_allsheets <- function(filename, tibble = FALSE, col_names = FALSE) {
+  # I prefer straight data.frames
+  # but if you like tidyverse tibbles (the default with read_excel)
+  # then just pass tibble = TRUE
+  
+  sheets <- readxl::excel_sheets(filename)
+  
+  
+  
+  x <- lapply(sheets, function(X) readxl::read_excel(filename, sheet = X, col_names = col_names) %>% janitor::clean_names())
+  if(!tibble) x <- lapply(x, as.data.frame)
+  names(x) <- sheets
+  x
+}

### 2021-07-23 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-Table \@ref(tab:incl-studies-character) shows the characteristics
+Table \@ref(tab:studyCharacteristics-table) shows the characteristics
 
 &nbsp;
+
+\blandscape{}
 
@@
 
+\elandscape{}
+
 As shown in
 
-Include here:
+<!--- TODO Figures and tables to include here:
 
--   PRISMA Flowchart
+-   PRISMA Flowchart (done)
 
--   Summary of types of study
+-   Summary of types of study (half done)
 
--   Summary of locations (use evidence map)
+-   Summary of locations (half done)
 
--   Summary of diagnostic criteria used
+-   Summary of diagnostic criteria used (done)
 
--   Summary of risk of bias
+-   Summary of risk of bias (not done)
 
--   Long table, horizontally.
+--->
+
+<!----------------------------------------------------------------------------->
+
+```{r cohortLocationsSetup, include = FALSE}
+
+```
+
+(ref:cohortLocations-cap) Geographical distribution of study cohorts
+
+(ref:cohortLocations-scap) Geographical distribution of study cohorts
+
+```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Many of the included studies were conducted in European countries (Figure \@ref(fig:cohortLocations).
 
@@
 There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
-For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of
+For vascular dementia, few studies examined this outcome, primarily because of the absence (until recently) of
 
@@
 
+<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
+
 In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
+
+<!----------------------------------------------------------------------------->
 
@@
 Include formulae and informed assumptions
-
-### Hazard ratios vs risk/odds ratios
 
@@
 
-### Meta-n
+### Meta-analysis of statin use and hypercholesteroleamia
+
+Straight-forward random effects meta-analysis of
+
+```{r primaryFigures, include = FALSE}
+
+```
+
+<!----------------------------------------------------------------------------->
+(ref:fpStatins-cap) __Forest plot showing effect of statins:__
+
+(ref:fpStatins-scap) Forest plot showing effect of statins
+
+```{r fpStatins, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpStatins-cap)', out.width='100%', fig.scap='(ref:fpStatins-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-### Dose response meta-analysis
+### Dose response meta-analysis of lipid levels
 

### 2021-07-23 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
+An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
 
@@
 In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009a] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
 As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
@@
 Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019a] to investigate the impact of multiple imputation on the results.
+As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
 
@@
 Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010a] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
 
@@
 `r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
-In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009b]
+In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]
 
@@
 As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
+Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 

### 2021-07-23 R/03-Code-Systematic-Review.R

@@ -163,77 +163,217 @@ if(doc_type == "docx") {
 }
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- chunkname-table
+# ---- studyCharacteristics-table
 
-chunkname_table <- mtcars
+toc_df <- rio::import("data/sys-rev/Book1.xlsx",which = 1) %>%
+  janitor::clean_names() %>%
+  select(study_id, author, year, location, data_source) %>%
+  dplyr::filter(study_id == "9429")
 
-if(doc_type == "docx"){
-apply_flextable(chunkname_table,caption = "(ref:chunkname-caption)")
-}else{
-knitr::kable(chunkname_table, format = "latex", caption = "(ref:chunkname-caption)", caption.short = "(ref:chunkname-scaption)", booktabs = TRUE) %>% 
-row_spec(0, bold = TRUE) %>%
-kable_styling(latex_options = c("HOLD_position"))
+toc_df2 <- rio::import("data/sys-rev/Book1.xlsx",which = 2) %>%
+  janitor::clean_names() %>%
+  group_by(study_id) %>% 
+  summarize(Criteria = paste0(unique(diagnostic_criteria), collapse = "; "),
+            Exposures = paste0(unique(exposure), collapse = "; "), 
+            Outcomes = paste0(unique(outcome), collapse = "; ")) %>%
+  ungroup()
+
+studyCharacteristics_table <- left_join(toc_df, toc_df2) %>%
+  mutate(Study = paste(author, year)) %>%
+  select(Study, location, data_source, Exposures, Outcomes, Criteria, -c(study_id,author, year)) %>%
+  rename("Location" = location,
+         "Data source" = data_source, 
+         "Diagnostic criteria" = Criteria)
+
+if(doc_type == "docx") {
+  apply_flextable(studyCharacteristics_table, caption = "(ref:studyCharacteristics-caption)")
+} else{
+  knitr::kable(
+    studyCharacteristics_table,
+    format = "latex",
+    caption = "(ref:studyCharacteristics-caption)",
+    caption.short = "(ref:studyCharacteristics-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"))
 }
 
 
[…]

### 2021-07-23 R/doc_options.R

@@ -7,6 +7,8 @@ library(dplyr)
 library(data.table)
 library(flextable)
 library(ggplot2)
+library(patchwork)
+library(sf)
 
 doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
 

### 2021-07-27 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
+<!----------------------------------------------------------------------------->
+
 &nbsp;
@@
 
-### Search strategy
+### Search strategy and and study selection
 
@@
 
-### Study selection
+#### Study selection
 
@@
 
+#### Studification
+
+Multiple publications resulting from the analysis of the same data were included and grouped ().
+
+In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
+Instead, they were considered as different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+
+<!----------------------------------------------------------------------------->
+
+#### Following up with authors {#contacting-authors}
+
+Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
+This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
+
+This was particular important for the dose response meta-analysis, we
+
+Use the example of getting the cut-off points from the
+
+<!-- TODO move to results, and keep just a short bit here -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Converting between different
+
+Include formulae and informed assumptions
+
+Not interchangeable in the context of systematic review.
+If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
+
+Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
+
+The likely effect of this is that the overall effect measures are biased towards . . . . ?
+
+Can you predict the direction of effect from a
+
+Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
+
+<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
+
+Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
+
+WHile the analysis of change scores is feasible, as they were explicityl
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Risk of bias assessment {#risk-of-bias}
@@
 <!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 <!----------------------------------------------------------------------------->
+&nbsp;
+
 #### Non-randomised studies of interventions/exposures
@@
 
+&nbsp;
+
 #### Mendelian randomisation studies
@@
 
+&nbsp;
+
 #### Risk of bias due to missing evidence
@@
 
-As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualise
-
-<!----------------------------------------------------------------------------->
-
-### Studification
-
-Multiple publications resulting from the analysis of the same data were included and grouped ().
-
-In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
-Instead, they were considered as different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
-<!----------------------------------------------------------------------------->
-
-### Following up with authors {#contacting-authors}
-
-Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
-
-This was particular important for the dose response meta-analysis, we
-
-Use the example of getting the cut-off points from the
-
-<!-- TODO move to results, and keep just a short bit here -->
+As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualised
 
@@
 
+Studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies).
+
 #### Standard meta-analysis
@@
 This analytical approach was used for
+
+$u$
+
+\begin{equation}
+  \theta_i = \mu + u_i
+  (\#eq:meta-analysis-random)
+\end{equation}
 
@@
 
-<!-- TODO Need equation for random effects too -->
+<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
+
+This analytical approach was used for cases where the exposure was dichotomous (e.g. statin use or not, hypercholesterolemia or not).
 
@@
 
-### Visualisation of results
+#### Visualisation of results
 
@@
 This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
+
+Also, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a
+
+As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
 
@@
 
+<!-- TODO List here that one of the key reasons for building the tool was to . Reference back to  -->
+
 <!----------------------------------------------------------------------------->
@@
 
-Patient and public memebers were intended to be involved at this poit
+Patient and public members were intended to be involved at this poit
 
@@
 A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->
+
+Similarly, there was initially no intention to try and examine the risk of bias due to missing evidence.
 
@@
 
+<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
+
 One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4.
@@
 <!----------------------------------------------------------------------------->
-
-### Converting risk ratios to odds ratios
-
-Include formulae and informed assumptions
-
-Not interchangeable in the context of systematic review.
-If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
-
-Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-
-The likely effect of this is that the overall effect measures are biased towards . . . . ?
-
-Can you predict the direction of effect from a
-
-Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
-
-<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
-
-Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-Straight-forward random effects meta-analysis of
+Straight-forward random effects meta-analysis of binary exposures
 
@@
 Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
+
+Important here to examine effect of risk of bias (due to immortal time in observational studies).
+
+Also important to examine the effect of:
+
+* age at baseline
+* sex (percentage)
+* education
+* baseline cognitive scores (how to group)
 
@@
 
-A common criticism of preprinted articles is that they have not formally been peer-reviewed.
-__[CITATION NEEDED]__ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
+A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ <!-- TODO See Chapter 1 for reference for this quote. -->
+ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
 
@@
 
-While [__some__] preprint have subsequently been published, this does not cause any major issues.
+While `r hold()` preprint have subsequently been published, this does not cause any major issues.
+
+### Risk of bias due to missing evidence
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 <!----------------------------------------------------------------------------->
+
+### Summary of findings
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
+<!-- TODO This section will be informed by the review published as a preprint -->
+
+Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
+
+**The duplication of work across reviews (including, ironically, by this review) is substantial.
+In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
+However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
+
+__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
+
+<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
+
+In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
+In these studies, the unit of analysis are systematic reviews rather than the
+
+However, a comparative analysis between indicates
+
 &nbsp;
@@
 
-### Original contribution to research
+### Strenghts and limitations
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### Comparison with other reviews
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
+#### Limitations
 
@@
 
-### Strenghts and limitations
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-#### Inclusion of Mendelian randomisation studies
+### Strengths and limitations
 
@@
 
+In this chapter I have
+
+This work built on the tool introduced in the preceeding chapter, and the results from the systematic review are used in further chapters.
+
+In Chapter \@ref(cprd-analysis-heading), 
+A summary of the evidence guided the
+
+In Chapter \@ref(ipd-heading),
+
+<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of -->
+
+A
+
 \newpage

### 2021-07-27 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 __Methods:__ A cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
-Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible AD).
+Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
+no drug) and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).
 
 __Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` participant-years (median: `r fu_text`).
-We found little evidence that lipid-regulating agents were associated with risk of AD (probable AD `r probad_text`; possible AD `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
-Evidence from a number of control outcomes (ischeamic heart disease `r ihd_text`; backpain `r backpain_text` and diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding related to vascular factors.
+We found little evidence that lipid-regulating agents were associated with risk of Alzheimer's disease (probable `r probad_text`; possible `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+Evidence from a number of control outcomes (ischaemic heart disease `r ihd_text`; backpain `r backpain_text` and diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding related to vascular factors.
 
@@
 * Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia.
-In all cases, the estimated associations were driven by the statin subgroup, which comprised most participants in our cohort.
+In all cases, the estimated associations were driven by the any statin subgroup, which comprised most participants in our cohort.
 
@@
 
-Dementia is a major neurocognitive disorder, the most common types of which are Alzheimer’s disease (AD) and vascular dementia (VaD).[@prince2016] Despite an increasing number of cases globally and decades of research, there remains much unknown about the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or reverse the cognitive decline associated with the condition.[@jobke2018] Drug repurposing, the identification of new applications for previously approved drugs, may provide an efficient mechanism to discover effective preventative and therapeutic treatments for dementia.[@ashburn2004; @pushpakom2019]
+Dementia is a major progressive neurocognitive disorder, the most common types of which are Alzheimer’s disease, vascular dementia and Lewy Body dementia.[@prince2016] Despite an increasing number of cases globally and decades of research, there remains much unknown about the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest, slow or reverse the cognitive decline associated with the condition.[@jobke2018] Drug repurposing, the identification of new applications for previously approved drugs, may provide an efficient mechanism to discover new effective preventative and therapeutic treatments for dementia.[@ashburn2004; @pushpakom2019]
 
@@
 
-We therefore aim to examine the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
+We therefore aimed to test the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
 
@@
 Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
+Records pre-dating the 1995 cut-off were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
 
@@
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a LRA (such as statins); a total cholesterol test result of >4mmol/L; or an low density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a LRA (such as statins); a total cholesterol test result of >4mmol/L; or a low density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
 
 These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL-c test results, or had already been diagnosed with it, as indicated by a diagnostic code or related prescription.
-This approach, conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia, was employed in an attempt to reduce confounding by indication that we would expect to observe in a general population cohort.
+This approach, conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia, was employed to reduce confounding by indication that we would expect to observe in a general population cohort.
 
 The index date for a participant was defined as the date where the first relevant code or test result (as detailed above) was recorded on their clinical record.
-Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); last registration date with their GP practice; last CPRD collection date for their practice.
+Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data prior to their index date, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
 
@@
 
-A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
+To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] Under this model, all participants entered the unexposed group on their index date and were moved into the exposed group on the date they were first prescribed an eligible LRA.
+Participants whose index event was a LRA prescription entered the study and the exposed group on the same day, and so contributed no time-at-risk to the unexposed group.
+
+A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored to mimic an intention-to-treat approach.
 We did however tabulate how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
@@
 All analyses were performed in STATA 15.
-Cox proportional hazard models were used to estimate the hazard ratio and corresponding 95% confidence intervals, allowing for the potential for clustering by practice.
-Participant's age was used as the time axis for all models.[@lamarca1998; @gail2009; @pencina2007] To address the potential for immortal time bias, we employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] To observe the effect of adjusting for additional covariates, we compared models adjusted for age only and age and sex to the fully adjusted model.
+Cox proportional hazard models with a time-varying treatment indicator were used to estimate the hazard ratio and corresponding 95% confidence intervals, allowing for potential clustering of outcomes by practice.
+Participant's age was used as the time axis for all models.[@lamarca1998; @gail2009; @pencina2007] To observe the effect of adjusting for additional covariates, we compared models adjusted for age only and age and sex to the fully adjusted model.
 Additional analyses stratified by outcome and drug class were also performed.
@@
 
-## Additional analyses
+## Sensitivity analyses
 
-We performed a number of sensitivity analysis.
+We performed several sensitivity analyses.
 As statins are contraindicated in pregnancy,[@nationalinstituteforhealthandcareexcellence]  we ran the models described above but excluding participants below the age of 55.
-We also further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
-Finally, we included three control outcomes with known associations with statin use.[@collins2016a; @herrett2021] Using the fully adjusted model, we investigated the association between LRA and back pain (negative control), ischemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
+Given the different ability of lipophilic statins to cross the blood-brain barrier,[@sierra2011] we further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
+Finally, we included three control outcomes with known associations with statin use.[@collins2016a; @herrett2021] Using the fully adjusted model, we investigated the association between LRA and back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
 
@@
 A total of `r format(attrition[14,1], big.mark = ",")` participants met the inclusion criteria for our cohort (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of `r comma(total_followup)` patient years at risk.
-The majority of participants were included in the cohort on the basis of an elevated test result (`r index_event_text`).
+Most participants were included in the cohort due to an elevated test result (`r index_event_text`).
 The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable AD, `r format(p1[3,2], big.mark = ",")` possible AD, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia).
+During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable Alzheimer's disease, `r format(p1[3,2], big.mark = ",")` possible Alzheimer's disease, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia).
 The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
 
-A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
+Most participants (`r percentage.statins`) prescribed a lipid-regulating agent were prescribed a statin.
 We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
@@
 
-As shown in Figure \@ref(fig:cprdPrimary), our results show little evidence of an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+As shown in Figure \@ref(fig:cprdPrimary), our results show little evidence of an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, except for fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
-Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+Again, this effect was driven mainly by the any statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
 
@@
 
-Adjustment for additional covariates beyond age and sex had a limited impact (Supplementary Figure 3), with the exception of the Probable AD outcome, where the full adjustment attenuated to the null the protective effect observed when adjusting only for age and sex.
+Adjustment for additional covariates beyond age and sex had a limited impact (Supplementary Figure 3), except for the Probable Alzheimer's disease outcome, where the full adjustment attenuated to the null the protective effect observed when adjusting only for age and sex.
 
@@
 
-For our control outcomes (Supplementary Figure 6), there was some evidence that treatment with a lipid-regulating agent was associated with an increased risk of back pain (`r backpain_text`).
-However, LRA prescription was also associated with an increased risk of ischemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
+For our control outcomes (Supplementary Figure 6), there was some evidence that patients prescribed a lipid-regulating agent had increased risks of back pain (`r backpain_text`), ischaemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
 
@@
 There was little evidence that lipid-regulating agents had any observed effect on probable and possible Alzheimer's when compared with no treatment, but some evidence they were associated with an increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
+The effect observed in each case was driven by the any statin subgroup, which included a substantial majority of participants.
 For the other drug classes, there was limited evidence of an association with any outcome, with two exceptions.
@@
 These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to an artificial protective effect of statins on all-cause dementia.
+However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to an artificial protective effect of statins on all-cause dementia and limit the ability for comparison between studies.
 
@@
 Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings (OR: 0.91, 95%CI: 0.63-1.31).[@williams2020]
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was not inconsistent with our results.[@williams2020]
 
-An additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis.[@chu2018]
+Our additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
 
@@
 
-Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
+Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementia.
 A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis (`r vasdem_text`).
@@
 Apart from statins, few studies examining a lipid-regulating agent have been reported.
-One of the few classes for which data was available were fibrates, for minimal evidence of an effect on all-cause dementia was identified, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
+One of the few classes for which data was available were fibrates, minimal evidence of an effect on all-cause dementia was identified,[@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
 
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding for that treatment.
+A previous Mendelian randomization study provided an estimate of the effect of ezetimibe on Alzheimer's disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with the finding from our analyses.
+To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on risk of vascular dementia, and so we cannot compare our unexpected finding for that comparison.
 
+<!----------------------------------------------------------------------------->
 &nbsp;
@@
 However, the findings of our analysis are subject to several limitations.
-There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contained prescriptions for lipid-regulating agents.
+There was a  possibility of differential outcome misclassification based on the exposure, as we cannot exclude the possibility that for people with memory complaints, a diagnosis of vascular dementia might be made more frequently than Alzheimer’s disease if their medical records contain prescriptions for lipid-regulating agents.
+
 Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
@@
 Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
-The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is not know to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible AD to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of vascular cases in the outcome definition increases.
+The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischaemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is unlikely to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible Alzheimer's disease to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of cases with a vascular component increases.
 A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]
 
@@
 
-We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+We have provided new evidence on the association of lipid-regulating agent prescription with all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
 We found limited evidence to support the use of lipid-regulating agents for the prevention of  probable or possible Alzheimer’s disease, but they were associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
+In all cases, the estimated associations were driven by those observed in the any statin subgroup, which comprised the majority of participants in our cohort.
 
@@
 
+<!-- TODO 11,119 participants removed because their endate was . This explains the discrepancy between the total number in this figure and the table above. -->
+
 <!--------------------------------------------------------------------------->

### 2021-07-27 manuscripts/cprd/supp-materials.Rmd
End of day:

@@
 
-  * Use of a time-varying treatment indicator, to correctly classify time-at-risk.
-  * Inclusion of additional covariates that are adjusted for in the main model.
+-   Use of a time-varying treatment indicator, to correctly classify time-at-risk.
+-   Inclusion of additional covariates that are adjusted for in the main model.
 
@@
 
-## Supplementary Table 1: STROBE Reporting Guidelines {#supp-tab-strobe}
+## Supplementary Table 1: RECORD Reporting Guidelines {#supp-tab-strobe}
 
@@
 
-__To be copied in__
+**To be copied in**
 
@@
 The code lists used to define covariates adjusted for in the fully-adjusted model (see Supplementary Table \@ref(tab:covariateDef-table)) were originally created for use in a previous analysis.[@walker2020] Some code lists were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017] and these are noted in the table.
-
-&nbsp;
 
@@
 
-&nbsp;
-
 \newpage
@@
 # Supplementary figures {#supp-fig}
+
 ## Supplementary Figure 1 {#supp-fig-outcome-decision}
@@
 
+```{r unadjustedComparison, include = FALSE}
+```
+
+```{r pregnancy, include = FALSE}
+```
+
+```{r statinType, include = FALSE}
+```
+
+```{r controlOutcomesText, include = FALSE}
+```
+
+```{r controlOutcomes, include = FALSE}
+```
+
 ## Supplementary Figure 3 {#supp-fig-unadjusted}
+
 ```{r supp-fig-comparison,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome using three models adjusted for age, age and sex, and all covariates respectively."}
-knitr::include_graphics(here::here("figures/cprd-analysis/fp_unadjusted.jpeg"))
+knitr::include_graphics(here::here("figures/cprd-analysis/forester_unadjusted.png"))
 ```
@@
 ## Supplementary Figure 4 {#supp-fig-pregnancy}
+
 ```{r supp-fig-pregnancy,echo = FALSE, fig.cap="Association of any lipid regulating agent with a dementia or related outcome, removing participants who were less than 55 years of age at index."}
-knitr::include_graphics(here::here("figures/cprd-analysis/fp_pregnancy.jpeg"))
+knitr::include_graphics(here::here("figures/cprd-analysis/forester_pregnancy.png"))
 ```
@@
 ## Supplementary Figure 5 {#supp-fig-sta-type}
+
 ```{r supp-fig-sta-type, echo = FALSE, fig.cap="Association of statins with a dementia or related outcome, stratified by statin lipophilic/hydrophilic properties."}
-knitr::include_graphics(here::here("figures/cprd-analysis/fp_sta_type.jpeg"))
+knitr::include_graphics(here::here("figures/cprd-analysis/forester_sta_type.png"))
 ```
@@
 ## Supplementary Figure 6 {#supp-fig-backpain}
+
 ```{r supp-fig-backpain,echo = FALSE, fig.cap="Association of any lipid regulating agent with backpain, ischemic heart disease (IHD), and Type 2 diabetes."}
-knitr::include_graphics(here::here("figures/cprd-analysis/fp_control_outcomes.jpeg"))
+knitr::include_graphics(here::here("figures/cprd-analysis/forester_control_outcomes.png"))
 ```

### 2021-07-27 R/03-Code-Systematic-Review.R

@@ -167,11 +167,11 @@ if(doc_type == "docx") {
 
 toc_df <- rio::import("data/sys-rev/Book1.xlsx",which = 1) %>%
   janitor::clean_names() %>%
-  select(study_id, author, year, location, data_source) %>%
-  dplyr::filter(study_id == "9429")
+  select(study_id, author, year, location, data_source)
 
 toc_df2 <- rio::import("data/sys-rev/Book1.xlsx",which = 2) %>%
   janitor::clean_names() %>%
+  filter(!is.na(study_id)) %>%
   group_by(study_id) %>% 
   summarize(Criteria = paste0(unique(diagnostic_criteria), collapse = "; "),
             Exposures = paste0(unique(exposure), collapse = "; "), 
@@ -183,7 +183,9 @@ studyCharacteristics_table <- left_join(toc_df, toc_df2) %>%
   select(Study, location, data_source, Exposures, Outcomes, Criteria, -c(study_id,author, year)) %>%
   rename("Location" = location,
          "Data source" = data_source, 
-         "Diagnostic criteria" = Criteria)
+         "Diagnostic criteria" = Criteria) %>%
+  arrange(Study) %>%
+  filter(!is.na(Location))
 
 if(doc_type == "docx") {
   apply_flextable(studyCharacteristics_table, caption = "(ref:studyCharacteristics-caption)")
@@ -213,8 +215,6 @@ world <- toc_df %>%
 
 p1 <- ggplot(data = world) +
   geom_sf(aes(fill = n, geometry = geometry), legend = "none") +
-  scale_fill_gradient(low = "grey95",
-                      high = "grey10") +
   geom_rect(
     xmax = 36,
     xmin = -10,
@@ -239,12 +239,8 @@ p1 <- ggplot(data = world) +
   theme_void() +
   theme(panel.border = element_rect(colour = "black", fill = "transparent"))
 
-
-
 p2 <- ggplot(data = world) +
   geom_sf(aes(fill = n, geometry = geometry)) +
-  scale_fill_gradient(low = "grey95",
-                      high = "grey10") +
   xlab("Longitude") + ylab("Latitude") +
   coord_sf(xlim = c(36,-12),
            ylim = c(70, 35),
@@ -283,6 +279,8 @@ p3 <- p2 + plot_space + p1 + plot_layout(
   widths = c(1, 1, 1),
   heights = c(5, 0.1, 10)
 )  & labs(fill="No. of\ncohorts") &
[…]

### 2021-08-03 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test
+Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
 

### 2021-08-03 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
+<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
+
 As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
@@
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(hold)) and the individual patient data analysis (Chapter \@ref(hold)), see Section \@ref(hold).
+For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
 

### 2021-08-03 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 
-* Main text word count (max 3000): 2999
-* Abstract word count (max 250): 244
+* Main text word count (max 4000): 3104
+* Abstract word count (max 250): 250
 
@@
 
+__Check TODOs!__
+
+<!-- TODO Fix total length of follow-up between text and table 2 -->
+
 __Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia.
 As a result, these modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
-Here, we test the association between lipid-regulating agents and subsequent risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a large-scale electronic health record database.
+Here, we test the association between lipid-regulating agents and risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), an electronic health record database.
 
-__Methods:__ A cohort study design using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
-Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
+__Methods:__ A cohort study using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
+Multivariable Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
 no drug) and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).
@@
 __Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` participant-years (median: `r fu_text`).
-We found little evidence that lipid-regulating agents were associated with risk of Alzheimer's disease (probable `r probad_text`; possible `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
-Evidence from a number of control outcomes (ischaemic heart disease `r ihd_text`; backpain `r backpain_text` and diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding related to vascular factors.
+We found little evidence that lipid-regulating agents were associated with Alzheimer's disease (probable `r probad_text`; possible `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
+Evidence from a number of control outcomes (ischaemic heart disease `r ihd_text`; backpain `r backpain_text`; and Type 2 diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding by indication.
 
-__Conclusion:__ We found little evidence that lipid-regulating agents were associated with reduced on Alzheimer’s disease risk.
-There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely the result of residual confounding by indication.
+__Conclusion:__ We found little evidence that lipid-regulating agents were associated with reduced Alzheimer’s disease risk.
+There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely due to residual confounding by indication.
 
@@
 In addition, data are collected for care provision and without a specific research question in mind,  providing a holistic picture of a patient and their health experience.
-This provides vital data on a range of potential confounders which can be incorporated into an analysis.
+While they may not contain information on all potentially important confounders,[@farmer2018] electronic health records provide routine data on common covariates for millions of participants.
 
@@
 The index date for a participant was defined as the date where the first relevant code or test result (as detailed above) was recorded on their clinical record.
-Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); last registration date with their GP practice; last CPRD collection date for their practice.
+Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); last registration date with their GP practice; or the last CPRD collection date for their practice.
 Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data prior to their index date, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
@@
 
-A total of `r format(attrition[14,1], big.mark = ",")` participants met the inclusion criteria for our cohort (See Supplementary Figure 2 for the attrition flowchart), with a total follow-up of `r comma(total_followup)` patient years at risk.
+A total of `r format(attrition[14,1], big.mark = ",")` participants met the inclusion criteria for our cohort (see Supplementary Figure 2 for the attrition flowchart), with a total follow-up of `r comma(total_followup)` patient years at risk.
 Most participants were included in the cohort due to an elevated test result (`r index_event_text`).
@@
 
-For our control outcomes (Supplementary Figure 6), there was some evidence that patients prescribed a lipid-regulating agent had increased risks of back pain (`r backpain_text`), ischaemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
+For our control outcomes (Supplementary Figure 6), there was some evidence that patients prescribed a lipid-regulating agent had an increased risk of back pain (`r backpain_text`), ischaemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
 
@@
 A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
-A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]
+A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020] This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
+However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with the results of this analysis.
 
-These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to an artificial protective effect of statins on all-cause dementia and limit the ability for comparison between studies.
+Additionally, a previous analysis of the THIN EHR database using a propensity score matching analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96),[@smeeth2009].
+Differences in dementia coding over time, in addition to a different set of covariates adjusted for in the analysis, may go someway to explaining the discrepancy.
 
@@
 
+<!-- TODO Need to cite Smeeth paper and discuss -->
+
 &nbsp;
 
-__Statins and non-Alzheimer's disease dementia__
+__Statins and vascular/other dementia__
 
@@
 A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b]
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication in that study through use of a trial emulation analysis, the expected protective effect of statins was observed.
 
@@
 However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which may relate to the unexpected increase in risk of vascular dementia associated with statin use.
-Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
+Other analytical methods.
+Future research should aim to address these biases, potentially via a trial emulation analysis.
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary of person-time at risk and number of events by exposure group.
+
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 # Main figure
@@
 
-_Figure 1: Hazard ratios produced by the primary analyses of CPRD data, stratified by dementia outcome and drug class.
+_Figure 1: Results from the primary analyses of CPRD data comparing prescription of an lipid-regulating drug with no prescription, stratified by dementia outcome and drug class.
 All results were obtained using the fully adjusted model and participant age as the time scale._

### 2021-08-03 R/03-Code-Systematic-Review.R

@@ -317,19 +317,6 @@ point_colour <-
          "black",
          "grey50")
 
-
-test2 <- data.frame(x = c(1, 1.25, 1, 0.75),
-                    y = c(
-                      last(t$conf.low),
-                      last(t$estimate),
-                      last(t$conf.high),
-                      last(t$estimate)
-                    ))
-
-ggplot() +
-  geom_polygon(aes(x=x,y=y))
-
-
 forester_thesis(
   t[,1],
   t$estimate,

### 2021-08-03 R/04-Code-CPRD-Analysis.R

@@ -77,15 +77,15 @@ table1 = table1[-1,]
 colnames(table1)[1] <- " "
 
 table1[1, 1] <- "Sample size (N)"
-table1[2, 1] <- "Index year \\newline(median)"
+table1[2, 1] <- "Year of \\newline cohort entry \\newline (median)"
 table1[3, 1] <- "Female"
-table1[4, 1] <- "Age"
+table1[4, 1] <- "Age at \\newline cohort entry \\newline (median)"
 table1[5, 1] <- "CAD"
 table1[6, 1] <- "CBS"
 table1[7, 1] <- "CVD"
 table1[8, 1] <- "Charlson (ever > 0)"
 table1[9, 1] <- "IMD-2010 (median)"
-table1[10, 1] <- "Consulation rate (mean/SD)"
+table1[10, 1] <- "Consultation rate (mean/SD)"
 table1[11, 1] <- "Alcohol (ever)"
 table1[12, 1] <- "Smoking (ever)"
 table1[13, 1] <- "BMI (mean/SD)"
@@ -105,18 +105,21 @@ table1[24, 1] <- "Follow up \\newline(years; median)"
 table1.copy <- table1
 
 table1 <- table1[, c(1, 10, 7, 9, 2:6, 8)]
-table1_disp <- table1[c(1:16, 22, 17:18, 23, 24), ]
+table1_disp <- table1[c(1:16, 22, 17:18, 23), ]
 
 # Quick check to ensure data quality
 t <- table1_disp[1, 2:10]
 t <- as.numeric(table1_disp[1, 2:10])
 
+
 if (t[1] - sum(t[2:9]) != 0) {
   stop("cprdCharacteristics-table: Sum of subgroups != Total sample size")
 }
 
+table1_disp[1,2:9] <- stringr::str_trim(comma(as.numeric(table1_disp[1,2:9])))
+
 # Create display table using kable
-cprdCharacteristics_table <- table1_disp
+cprdCharacteristics_table <- comma(table1_disp)
 
 if (doc_type == "docx") {
   apply_flextable(cprdCharacteristics_table, caption = "(ref:cprdCharacteristics-caption)") %>%
@@ -370,9 +373,9 @@ probad <- results %>%
   filter(outcome == "Probable AD" & drug == "Any")
 
 probad_text <- paste0(
-  "HR: ",
+  "HR:",
   round(probad$HR, 2),
-  ", 95%CI: ",
+  ", 95%CI:",
   round(probad$ci_lower, 2),
   "-",
[…]

### 2021-08-06 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]
+A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.
+This systematic review was performed in conjunction with a team of secondary reviewer, These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.
 
 <!-- TODO Double check this list at the end of the project. -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
-We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
 As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
@@
 
- Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
+Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
+I also searched bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
 Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 #### Study selection
 
-Records were imported into Endnote and deduplicated using the method outlined in Bramer et al.
+Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
 (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
@@
 A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-#### Converting between different
-
-Include formulae and informed assumptions
+#### Converting between different exposure measures
+
+<!-- TODO Include formulae and informed assumptions  -->
 
@@
 
-WHile the analysis of change scores is feasible, as they were explicityl
+While the analysis of change scores is feasible, as they were explicityl
 
@@
 
+This additional appraisal marks a departure from the protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
+This is because the tool did not exist when the protocol was originally registered.
+
 <!----------------------------------------------------------------------------->
@@
 
-In addition,
+In addition, I where available, I presented results stratified by sex and age.
 
@@
 
-Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)
-
-This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->
-
-A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using
-
-Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
-
-Also, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a
-
-As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Assessment of added value of including preprint
+Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).
+This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.^[https://github.com/mcguinlu/robvis/issues/102] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
+
+Additionally, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Assessment of added value of including preprints
 
 Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
-s
+
 Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
@@
 Patient and public members were intended to be involved at this poit
-
-<!----------------------------------------------------------------------------->
-
-### Deviations from the protocol
-
-A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->
-
-Similarly, there was initially no intention to try and examine the risk of bias due to missing evidence.
 
@@
 
-Straight-forward random effects meta-analysis of binary exposures
-
+Straight-forward random effects meta-analysis of binary exposures, using study defined meaures of each.
+
+<!----------------------------------------------------------------------------->
 ```{r primaryFigures, include = FALSE}
-
-```
-
-<!----------------------------------------------------------------------------->
+```
+
 (ref:fpStatins-cap) __Forest plot showing effect of statins:__
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Triangualtion across evidence sources
+<!----------------------------------------------------------------------------->
+(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia
+
+(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
+```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/funnel_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Added evidental value of including preprints {#sys-rev-including-preprints}
+
+<!-- TODO Will have to get actual numbers for this section -->
+
+As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching, was not substantial (bioRxiv = , medRxiv = ) .
+
+However, this is largely due to the timing of the preprint searches
+
+Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.
+
+This does speak to the over-representation of certain study designs in the preprint literature
+
+Regardless, some studies were identified
+
+There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
+While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
+
+Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).
+
+Of interest,
+
+<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->
+
+This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
+It also means that searches are current - if the aim of systematic reviews is to
+
+While the total number of relevant studies found using this method was
+
+<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
+
+<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
+
+On further investigation, the argument that .
+
+It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
+
+However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
+
+While concerns have been raised that
+
+Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
+
+A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ <!-- TODO See Chapter 1 for reference for this quote. -->
+ However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
+
+> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
+
+References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
+
+The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
+
+While `r hold()` preprint have subsequently been published, this does not cause any major issues.
+
+### Risk of bias due to missing evidence
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Discussion
+
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
+
+In addition, the a
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Summary of findings
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Previous reviews
+
+<!-- TODO Not sure this is the best place for this -->
+
+**Will need to include something in the methods section on this**
+
+As part of this analysis, Iexamined the overlap between different published reviews on this topic.
+
+Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
+
+<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
+
+An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
+
+Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
+So for example, XXXX records were captured both by the XXXX review and the XXXX review.
+
+Where the matrix has just a single point highlighted, this shows the records unique to that review.
+
+The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
+
+Our review is presented as the last point on this plot, and captured XXXX records
+
+The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
+The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
+
+<!--- Take a stand here! --->
+
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
+While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
+While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
+
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+
+Does it also cause issues in terms of self-report?
+
+<!-- TODO This section will be informed by the review published as a preprint -->
+
+Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
+
+**The duplication of work across reviews (including, ironically, by this review) is substantial.
+In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
+However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
+
+__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
+
+<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
+
+In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
+In these studies, the unit of analysis are systematic reviews rather than the
+
+However, a comparative analysis between indicates
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Triangulation across evidence sources
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Added evidental value of including preprints {sys-rev-including-preprints}
-
-<!-- TODO Will have to get actual numbers for this section -->
-
-There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
-While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
-
-Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).
-
-Of interest,
-
-<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->
-
-This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
-It also means that searches are current - if the aim of systematic reviews is to
-
-While the total number of relevant studies found using this method was
-
-<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
-
-<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
-
-On further investigation, the argument that .
-
-It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
-
-However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
-
-While concerns have been raised that
-
-Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
-
-A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ <!-- TODO See Chapter 1 for reference for this quote. -->
- However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
-
-> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
-
-References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
-
-The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
-
-While `r hold()` preprint have subsequently been published, this does not cause any major issues.
-
-### Risk of bias due to missing evidence
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion
-
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
-
-In addition, the a
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Summary of findings
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Previous reviews
-
-<!-- TODO Not sure this is the best place for this -->
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, Iexamined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
-
-<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
-
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
-
-In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
-In these studies, the unit of analysis are systematic reviews rather than the
-
-However, a comparative analysis between indicates
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 As part of the reflective element of this thesis, I collated my experiences on performing a systematic review.
+
+#### Protocol registration
+
+While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecodotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
+In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
+
+#### Workload
 
@@
 
+#### People management
+
 Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.
@@
 
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses, predominantly preprinted vs published.
+As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
+published).
 Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
 
-The added evidential value of including these preprints was highlighted in Section \ref()
+The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).
 
@@
 
-### Strenghts and limitations
+### Strengths and limitations
+
+<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
+
+#### Strengths
 
@@
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+<!-- TODO Though this could -->
 
@@
 
+<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
+they would not have been captured by the search for published papers) -->
+
 - *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
@@
 
+<!----------------------------------------------------------------------------->
 &nbsp;
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+However, this review also has several limitations.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Strengths and limitations
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-#### Inclusion of preprints
-
-Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
-they would not have been captured by the search for published papers)
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Use in other chapters
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Conclusions
 
@@
 
-Findings from this review are used though out the subsequent chapters.
-
-For example,
-
-## Conclusions
-
-In this chapter I have
-
-This work built on the tool introduced in the preceeding chapter, and the results from the systematic review are used in further chapters.
-
-In Chapter \@ref(cprd-analysis-heading), 
-A summary of the evidence guided the
-
-In Chapter \@ref(ipd-heading),
+In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
+
+This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref()
 

### 2021-08-06 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 
-This thesis was written in RMarkdown.
-Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]
+```{r, include = FALSE}
+knitr::write_bib(c(.packages(), "bookdown", "knitr"), here::here("bibliography/packages.bib"))
+```
 
+This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
 All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

### 2021-08-06 index.Rmd
End of day:

--- 2021-06-04 index.Rmd
@@
 college: 
-degree: Doctor of Philosophy in Population Health Sciences
-degreedate: TBC
+degree: Doctor of Philosophy
+degreedate: 2022
+word-count: |
+  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
 abstract: |
@@
 #######################
-bibliography: 
-    - "bibliography/references.bib"
+bibliography: [bibliography/references.bib, bibliography/packages.bib]
 csl: bibliography/nature.csl

### 2021-08-06 R/03-Code-Systematic-Review.R

@@ -198,7 +198,10 @@ if(doc_type == "docx") {
     booktabs = TRUE
   ) %>%
     row_spec(0, bold = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position"))
+    kable_styling(latex_options = c("HOLD_position")) %>%
+    kableExtra::column_spec(0:1, width = "5em") %>%
+    kableExtra::column_spec(2:6, width = "10em")
+    
 }
 
 
@@ -214,7 +217,7 @@ world <- toc_df %>%
   tidyr::replace_na(list(n = 0))
 
 p1 <- ggplot(data = world) +
-  geom_sf(aes(fill = n, geometry = geometry), legend = "none") +
+  geom_sf(aes(fill = n, geometry = geometry), size = 0.1, legend = "none") +
   geom_rect(
     xmax = 36,
     xmin = -10,
@@ -222,7 +225,7 @@ p1 <- ggplot(data = world) +
     ymin = 35,
     fill = "transparent",
     color = "black",
-    size = 1
+    size = 0.5
   ) +
   xlab("Longitude") + ylab("Latitude") +
   coord_sf(ylim = c(-60, 85),
@@ -240,7 +243,7 @@ p1 <- ggplot(data = world) +
   theme(panel.border = element_rect(colour = "black", fill = "transparent"))
 
 p2 <- ggplot(data = world) +
-  geom_sf(aes(fill = n, geometry = geometry)) +
+  geom_sf(aes(fill = n, geometry = geometry), size = 0.1) +
   xlab("Longitude") + ylab("Latitude") +
   coord_sf(xlim = c(36,-12),
            ylim = c(70, 35),
@@ -257,17 +260,17 @@ plot_space <- ggplot() +
   ) +
   annotate(
     "segment",
-    x = -110,
+    x = -160,
     xend = -1180,
-    y = -1040,
+    y = -720,
     yend = 71,
     colour = "black",
   ) +
   annotate(
     "segment",
-    x = 440,
+    x = 625,
     xend = 1210,
-    y = -1040,
+    y = -720,
     yend = 71,
     colour = "black",
   ) +
@@ -287,8 +290,8 @@ p3 <- p2 + plot_space + p1 + plot_layout(
 ggsave(
   here::here("figures/sys-rev/cohortLocations.png"),
   p3,
-  height = 10,
-  width = 9
+  height = 6,
+  width = 8
 )
 
[…]

### 2021-08-06 R/forester.R

@@ -42,7 +42,7 @@ forester_thesis <- function(left_side_data,
                      ci_low,
                      ci_high,
                      right_side_data = NULL,
-                     estimate_precision = 1,
+                     estimate_precision = 2,
                      ggplot_width = 30,
                      null_line_at = 0,
                      file_path = here::here("forester_plot.png"),

### 2021-08-10 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 
-The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-[^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
-
-[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>
+The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
 
@@
 &nbsp;
+
+### Use case
+
+In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
+For example, I led a descriptive analysis of the change data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
+
+We found <!-- TODO complete -->
+
+This study has since been published in PLOS One, and a copy is included in Appendix \@ref() .
 

### 2021-08-10 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-<!-- -   TODO Examine how many times a primary study was included in a review -->
 <!-- -   TODO Look at whether searching preprints made any difference to my results -->
-<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->
 
 <!-- TODO Extra studies to include: -->
-
 <!-- * Smeet et al. reference in the CPRD analysis -->
@@
 
-The importance of
-
-I found that
+Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
+They do this by finding and combining the results from many related primary research studies.
+Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
+
+This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
+
+There were 127 primary studies <!-- TODO check this -->that contained information on this relationship.
+I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
+Lipids were not associated with any outcome.
+The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
+
+The use of the results of this review in subsequent chapters is dicussed.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+## Introduction {#sys-rev-intro}
+
+In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
+This analysis sought to address two specific aims.
+
+Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
+These include randomised controlled trials, observational studies of different analytical design (cohort, case-control, etc), and Mendelian randomisation studies.
+However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
+Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
+As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.
+
+Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence syntheists but may contain important unpublished studies.
+As an adjunct analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
+This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
 
@@
 &nbsp;
-
-<!----------------------------------------------------------------------------->
-## Introduction {#sys-rev-intro}
-
-The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.
-
-Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
-
-Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).
-
-Literature con
-
-Systematic reviews aim to transparently and reproducibly identift
-
-<!-- TODO Need to seriously improve this -->
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-This systematic review was performed in conjunction with a team of secondary reviewer, These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.
+In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
+Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewer.
+These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.
+In addition, Sarah Dawson, and information specialist, provided input to the design of the search strategy.
 
@@
 
-### Search strategy and and study selection
-
-I systematically search electronic bibliographic databases to identify potentially relevant records.
+### Search strategy
+
+I systematically search electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
 The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+The strategy included terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
 <!-- TODO Need to actually attach each search strategy.
@@
 
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 14" in Table \@ref(tab:searchOverview-table)) was screened.
-If any potentially relevant studies are identified, their titles and abstracts were searched for key terms that can be incorporated into the filters to improve search sensitivity.
+When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
 
@@
 
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
+The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+As the contents of the Web of Science Core Collection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
 I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-
-The abstracts list of relevant conferences (e.g.
+
+In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
+
+Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
+In addition, the abstracts list of relevant conferences (e.g.
 the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
 <!-- TODO how were these searched?
-Date and other range -->
-
-Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-I also searched bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
 
@@
 
-<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Study selection
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Study selection
 
@@
 
-Screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-
-Full-text screening will also be completed in full by the primary author.
-A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
+Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+
+Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer.
+In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
 Reasons for exclusion at this stage were recorded.
 Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]
+A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
+
+The criteria used to assess eligibility are presented in the subsequent sections.
 
@@
 
-We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
-Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants were free (or assumed to be free) of dementia/MCI at baseline.
+I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
+<!-- TODO Do I actually want to include MCI?
+--> Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Participants were free (or assumed to be free) of dementia/MCI <!-- TODO Do I actually want to include MCI?
+-->  at baseline.
 Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits will be placed on the sample size of included studies.
+No limits were placed on the sample size of included studies.
 
 Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-<!-- TODO do i actually want to include MCI?
--->
- For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
+<!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI?
+--> For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
 an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
@@
 
-No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
+No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
 
@@
 
-Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
-Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded.
+Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews were excluded.
+Studies which present no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
 Studies that measure change in continuous cognitive measures (e.g.
 MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/MCI/dementia) will be excluded.
-Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status.
+no dementia/MCI/dementia) were excluded.
+Conference abstracts with no corresponding full-text publication were examined, and I contacted authors to obtain information on the study's status.
 Studies that are reported in insufficient detail (e.g.
-only in conference abstracts, new, letters, editorials and opinion) will be excluded.
-Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) will be excluded.
-
-Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
-
+only in conference abstracts, new, letters, editorials and opinion) were excluded.
+Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
 <!-- TODO Expand on rationale for exclusion of cross-sectional studies.
@@
 
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Assessment of inter-rater reliability
-
-Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
-
-If this approach demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
+for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+below the age of 50) were excluded.
+Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
+Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Validation of screening process
+
+Inter- and intra-rater reliability during the screening stage were assessed for a 10% sub-sample of records at the title and abstract screening stage.
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
+assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
+assessment of accuracy).
 
 Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
 
@@
 
+If this assessment demonstrated issues with the screening process, a larger proportion of records would have been dual-screened.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ### Data extraction
 
+Data extraction was performed using a piloted data extraction form.
+Extracted items included: article metadata (year of publication, author list, journal), study characteristics (location, cohort name, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
+All data was extracted the data in the first instance and was checked for accuracy by a second member of the review team.
+
+#### Harmonisation of cholesterol measures
+
 Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
-
-Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
-
-This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.
-
-A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.
-
-<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->
-
-Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
+<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
+not providing qratile cut-off values, not poviding numbers per group, etc.
+--> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
 
@@
 
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Studification
-
-Multiple publications resulting from the analysis of the same data were included and grouped ().
-
-In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+#### Study-fication
+
+As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
+This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
+Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
 
@@
 
-This was particular important for the dose response meta-analysis, we
-
-Use the example of getting the cut-off points from the
+This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
+
+<!-- TODO Use the example of getting the cut-off points from the  -->
 
@@
 
-Not interchangeable in the context of systematic review.
-If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
-
-Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-
-The likely effect of this is that the overall effect measures are biased towards . . . . ?
-
-Can you predict the direction of effect from a
-
-Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
+The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
+If the outcome is rare, odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account time-to-event in each treatment group.
+
+Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
+In adddition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
+Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
+
+<!-- TODO Need to really fix this -->
+
+<!-- The likely effect of this is that the overall effect measures are biased towards . . . . ? -->
+
+<!-- Can you predict the direction of effect from a  -->
+
+<!-- Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis  -->
 
@@
 
-Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
-
-While the analysis of change scores is feasible, as they were explicityl
-
 &nbsp;
@@
 
-A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation).
+A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
 To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.
@@
 This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.
-
 As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
@@
 The study design-specific tools are introduced and discussed in more detail in the following sections.
-
-In addition, the tool also aim to capture the potential direction of bias for each given domain.
-An optional question at the end of each domain, e.g.
-for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included
-
-* Not applicable 
-* Favours experimental 
-* Favours comparator
-* Towards null 
-* Away from null 
-* Unpredictable
+In addition, the tool also aim to capture the potential direction of bias for each result.
+Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
 
@@
 Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019],
+Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019]
+
 The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
@@
 Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
-
-One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to
+Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
 
@@
 
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including.
-Ideally, obs studies assessed in reference to an idealised randomised controlled trial.
-Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
-
-For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.
-
-Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold.
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
+Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
+Ideally, observationals studies should be assessed in reference to an idealised randomised controlled trial.
+Further, the rare overall judgement of "Low" is considered equivalent to a randomised controlled trial.
+
+For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool.[@morganr2020] The tool is still in development, but while the signalling questions for each domain are yet to be confirmed, the overarching risk-of-bias domains have been finalised.
+The motivation for this using this tool above other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
 In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
-In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.
-
-<!----------------------------------------------------------------------------->
-
+<!-- TODO CITATION NEEDED --> In addition, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
+
+<!----------------------------------------------------------------------------->
 &nbsp;
@@
 
-<!-- TODO This next bit is not all true -->
-
-At present, no risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies.
-A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
-Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
-
+At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies (advance results from this review were obtained from contact with the authors.).
+<!-- TODO CITATION NEEDED --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
+
+<!----------------------------------------------------------------------------->
 &nbsp;
@@
 
-A recent shift towards the assessment of missing evidence due to selective non-reporting (as distinct from the selective reporting of a single result from multiple planned - handled in Domain 5 of the RoB 2 tool for example).
-
-As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualised
-
-This additional appraisal marks a departure from the protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
+A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.
+<!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+<!-- TODO CITATION NEEDED -->
+
+This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
 This is because the tool did not exist when the protocol was originally registered.
@@
 
-Studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies).
+An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies across
+
+Where individual studies were deemed comparable, they were incoroporated into a quantitative analysis or "meta-analysis".
+<!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
+
+Of note, studies were not combined across different study designs (i.e.
+RCTs were not combined in a meta-analysis with results from observational studies).
+The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-Meta-analysis is an important method of . . .
-
-Both a fixed-effect and random-effects meta-analysis model was.
-
-For
-
-Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
-
-This analytical approach was used for
-
-$u$
+<!-- Where both the outcome and the exposure were dichotmous, or the -->
+
+Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
+<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
+--> The fixed-effect method was implemented as:
 
@@
 
-where ...
+<!-- where ... -->
 
 <!-- TODO Need equation for random effects too. See Sean's thesis here. -->
-
-This analytical approach was used for cases where the exposure was dichotomous (e.g. statin use or not, hypercholesterolemia or not).
 
@@
 <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
--->
- while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-
-Where possible, data for all exposure groups was extracted, and this <!-- TODO ??? -->
-.
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
+--> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
+
+Where possible, data for all exposure groups was extracted.
+<!-- TODO ???
+--> Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
 if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).
@@
 <!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
-
 <!-- TODO Do I initially want to fit a linear relationship across categories and  -->
-A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
+A <!-- TODO confirm type of spline --> spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
 Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
@@
 
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it.
+When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the higest category was the same as the one immediately below it.
 Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
 
-I assumed the width of the category to be the same as the adjacent category.
-When the lowest category was open ended, I set the lower boundary to zero.
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-I conducted a leave one out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED -->
-
-In addition, I where available, I presented results stratified by sex and age.
+I conducted a leave-one-out analysis in order to explore the impact of any given study on the results.
+<!-- TODO CITATION NEEDED --> In addition, where available, I performed meta-regression to assess whether the results varied by age or sex.
+
+<!-- TODO Need more here -->
 
@@
 
-Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.^[https://github.com/mcguinlu/robvis/issues/102] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
-
-Additionally, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
+The use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
+
+Further, given the importance of visualising the potential biases of a result alongside the result itself, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).
+<!-- TODO CITATION NEEDED --> This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
 
@@
 
-Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
-
-I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
-
-<!-- TODO List here that one of the key reasons for building the tool was to . Reference back to  -->
-
-<!----------------------------------------------------------------------------->
-
-### Patient and public involvement
-
-Patient and public members were intended to be involved at this poit
+Preprints are a valuable evidence source (see Introduction, Section \@ref()) but their inclusion in a systematic reivew.
+As part of a study within this larger review, I also to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
+
+Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
-
-### Search and screening results
-
-Following the search
-
-`r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.
-
-<!--- Cross check this with the actual numbers included --->
-
-No eligible records were identified in the screening of the 500 records excluded by the search. Many of these were basic science studies <!-- TODO text -->
-
-<!----------------------------------------------------------------------------->
+### Initial search and validation of search filters
+
+`r num_to_text(23447,T)` records were identified through database searches.
+
+<!--- TODO Cross check this with the actual numbers included --->
+
+Of the 500 random records screened to ensure the accuracy of the study design filters, no eligible records were identified.
+Many of those excluded by the filters were basic science studies, commentaries or educational articles.
+<!-- TODO CITATION NEEDED -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Screening results
+
+Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
+`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
+\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
+
+The PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
+
+<!----------------------------------------------------------------------------->
+
+<!-- TODO PRISMA must include reasons for exclusion - extract from  -->
 
@@
 
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
-
-<!----------------------------------------------------------------------------->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> shown in Figure \@ref(prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Following screening, XXX studies were included.
-
-The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.
-
-&nbsp;
-
-As part of our our forward snowballing exercise (where articles citing an included study are cited), I recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
-Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
-This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually.
-The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*
-
-<!-- TODO Actually do this! -->
+<!-- TODO Show bar chart by date of publication? -->
 
@@
 
-As a summary of the duplication of work in this area, Ilooked at how many reviews a single included study had previously been included in.
-
-<!--- TODO Need example table here, showing relevant cells --->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of ~10% of records, illustrating high accuracy.
+```{r agree-setup, include = FALSE}
+```
+
+The values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
+Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
+The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
 
@@
 
-For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`) were investigated.
+Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab: agreeInter-table)) were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
 
-Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
-
-&nbsp;
-
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 
-XXXX studies met the criteria for inclusion in the review.
-
-Table \@ref(tab:studyCharacteristics-table) shows the characteristics
+Following ful-text screening, 127 studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
 
@@
 \blandscape{}
-
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-
 \elandscape{}
 
-As shown in
+<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
+
+<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
 
@@
 
-<!----------------------------------------------------------------------------->
-
+As shown in Figure \@ref(fig:cohortLocations), the majority of study cohorts were based in the developed world.
+
+<!----------------------------------------------------------------------------->
 ```{r cohortLocationsSetup, include = FALSE}
@@
 
-Many of the included studies were conducted in European countries (Figure \@ref(fig:cohortLocations).
-
-A common theme across the studies was a lack of data on vascular dementia.
-This is particularly interesting as lipids and statins are primarily a vascular disease.
-There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
-For vascular dementia, few studies examined this outcome, primarily because of the absence (until recently) of
-
-<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
-
-One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4.
-As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.
-
-<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
-
-In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias {#risk-of-bias-subheading}
-
-&nbsp;
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- TODO ### Risk of bias {#risk-of-bias-subheading} -->
+
+<!-- &nbsp; -->
 
@@
 
-Straight-forward random effects meta-analysis of binary exposures, using study defined meaures of each.
-
+<!-- Straight-forward random effects meta-analysis of binary exposures, using study defined measures of each. -->
+
+Statin use was associated with a reduce risk of all-cause dementia (`r estimate(0.76,0.66,0.88)`, Figure \@ref(fig:fpStatins)).
+
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Dose response meta-analysis of lipid levels
+&nbsp;
+
+### Dose response meta-analysis of lipid levels {#dose-response-results}
 
@@
 
-Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls be
+Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
+The results from the dose response analysis can be seen in Figure \@ref(fig:dose-response).
 
@@
 &nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Sources of heterogeneity
-
-Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
-
-Important here to examine effect of risk of bias (due to immortal time in observational studies).
-
-Also important to examine the effect of:
-
-* age at baseline
-* sex (percentage)
-* education
-* baseline cognitive scores (how to group)
-
-&nbsp;
-
+<!----------------------------------------------------------------------------->
+
+<!-- ### Sources of heterogeneity -->
+
+<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->
+
+<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->
+
+<!-- Also important to examine the effect of: -->
+
+<!-- * age at baseline -->
+<!-- * sex (percentage) -->
+<!-- * education -->
+<!-- * baseline cognitive scores (how to group) -->
+
+<!-- ### Sensitivity analyses -->
+
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 
--   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
--   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult
-
-One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across
-
-Many studies did not report the codelists used to run the analysis,
-
+<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
+<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
+
+There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
+
+<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
+
+<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
+Depsite attempts to obtain this additional information through contact with a -->
+
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
 &nbsp;
@@
 
-As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching, was not substantial (bioRxiv = , medRxiv = ) .
-
-However, this is largely due to the timing of the preprint searches
-
-Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.
-
-This does speak to the over-representation of certain study designs in the preprint literature
-
-Regardless, some studies were identified
-
-There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
-While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
-
-Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).
-
-Of interest,
-
-<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->
-
-This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
-It also means that searches are current - if the aim of systematic reviews is to
-
-While the total number of relevant studies found using this method was
-
-<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
-
-<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
-
-On further investigation, the argument that .
-
-It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
-
-However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
-
-While concerns have been raised that
-
-Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
-
-A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ <!-- TODO See Chapter 1 for reference for this quote. -->
- However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
-
-> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
-
-References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
-
-The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
-
-While `r hold()` preprint have subsequently been published, this does not cause any major issues.
+As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching, was not substantial (bioRxiv = 256, medRxiv = 0). <!-- TODO check -->
+
+<!-- QUESTION Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
+This is discussed further in Section \@ref(rev-discussion-MR).
+
 <!----------------------------------------------------------------------------->
@@
 
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
-
-In addition, the a
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
 ### Summary of findings
 
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Previous reviews
-
-<!-- TODO Not sure this is the best place for this -->
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, Iexamined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
+This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+
+A common theme across the evidence base was a lack of data on the association of vascular dementia.
+This is particularly interesting given that lipids and statins are primarily related to vascular disease.
+There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".
+<!-- TODO CITATION NEEDED --> For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.
+
+One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
+As covered in the discussion, ApoE4 genotype is the major risk factor for Alzheimer's disease, but is also involved in cholesterol transport.
+
+<!--- 
+QUESTION
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+- No these studies should not be included, as not recognised criteria.
+-->
+
+<!-- __Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
+-->
+
+This review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and is regularly held up as  providing no evidence for an effect of the statin on dementia outcomes.
+While widely cited and included in the Cochrane review on this topic,[@mcguinness2016] only reported the mean change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test, etc.) over follow-up rather than incident.
+While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using a , as cognitive tests should feed into a broader diagnostic pathway (see section \@ref(diagnostic-criteria)).
+As such, this trial did not met the inclusion criteria for this review.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Previous reviews {#rev-previous-reviews}
+
+<!-- TODO This section will be informed by the review published as a preprint -->
+
+__This section will be completed once Georgia has completed her analysis, and can also be cross-references with the meta-meta analysis published is Brain Sciences recently.__
+
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.
+<!-- TODO CITATION NEEDED -->
+
+However, despite these differences in methodology, the duplication of work across reviews (including this review) is substantial.
+In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
+Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.
+This approach would have enable more efficient identification of relevant primary studies, to which the methods which sets this review apart from other published reviews could have been applied.
 
@@
 
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
+<!-- An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot.
+For example, the XXXX review includes XXXX studies.
 The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
 The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
-
-In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
-In these studies, the unit of analysis are systematic reviews rather than the
-
-However, a comparative analysis between indicates
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Triangulation across evidence sources
+-->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- ### Triangulation across evidence sources -->
 
@@
 
-One key question for which multiple distinct sources of evidence were available were those looking at Laz
-
-A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use.
-In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)
-
-Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
+
+<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
 Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
 For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011]
-
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+[@guyatt2011] -->
+
+<!-- Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+-->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Inclusion of preprints
+
+As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
+published).
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
+There were several relevant preprints captured by the search.
+The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).
+
+The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:test)) is due to the timing of the preprint searches.
+The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
+As such, at the point it was searched, the medRxiv database contained only a small number of records.
+
+While none of the preprints contributed uniquely to the review, this is again.
+Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
+The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
+This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
+
+Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
+However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
+
+<!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->
+
+<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
+
+<!-- Regardless, some studies were identified -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Reviewing Mendelian randomisations studies {#rev-discussion-MR}
+
+Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
+
+Firstly, as this study design is relatively new, particularly when compared to randomised trials or cohort studies, the process and tools for systematically assessing them are not as well developed.
+A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
+This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application.
+
+Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
+A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
+While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref().
+Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool, which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not access the additional methodological considerations of the analysis of the Mendelian randomisation analysis itself.
+<!-- TODO Read this tool.
+--> For this review, I utilised the best available author-devised tool, sourced on a recent review of systematic reviews of Mendelian randomisation studies.
+
+<!-- TODO Need to add some text to the ROB section of this chapter on distinction between reporting and quality -->
+
+<!-- Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants -->
+<!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
+<!-- TODO Email George with query on dual counting, following review of email with Julian -->
+
+As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
+This is particularly relevant to the consideration of bias due to missing evidence.
+As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
+The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
+Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
+This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
+
+Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
+This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`).
+Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
+Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substanital benefit.
+
+<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
 #### Protocol registration
 
-While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecodotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
+While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
 In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
 
-#### Workload
-
-Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
+&nbsp;
+
+<!-- #### Workload -->
+
+<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
 Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
-
-Average time to complete a s
-
-However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
+-->
+
+<!-- Average time to complete a s -->
+
+<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
+
+&nbsp;
 
@@
 
-Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.
-
-A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of preprints
-
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
-
-The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).
-
-On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
-While this provides some additional evidence that the quality of the research described by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavailable at the time the search was conducted.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As evidenced by the issues involved in obtaining
-
-Building in part on the research, I co-wrote an guidance piece for pre
-
-Similarly, a substanital amount of time and effort has gone into making the data obtained by this review openly available to
-
-<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->
-
-<!--- Comment here on issues involved in extracting data --->
-
-&nbsp;
-
+This review provide an excellent opportunity to gain experience in managing a team of researchers.
+However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
+I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+<!-- ### Validation against recent umbrella review -->
+
+<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
+
+<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
+
+<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
+In fields where there is a lot of existing reviews, they -->
+
+<!-- All studies identified by reviews included in te -->
+
+<!-- In hindsight, this approach ma -->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+#### Open data sharing {#sys-rev-open-data}
+
+As discussed in Section \@ref(dose-response-results), many primary studies did not report important elements, and so these could not be extracted.
+This limiation was compounded by the expected low response rate to requests for further information from primary authors (although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019]).
+
+While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
+
+Based on my experience of extracting data for this review, I co-wrote an guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021]
+
+Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. <!-- TODO Cite the Zenodo repo here! -->
+
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could -->
+<!-- TODO Though this could --> In addition
 
@@
 
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
+-   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related manuscripts as a source of grey literature.
 As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
@@
 This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
-IN addition this review was used to pilot an upcoming risk of bias tool
+In addition this review was used to pilot an upcoming risk of bias tool
 
@@
 
-However, this review also has several limitations.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Reviewing Mendelian randomisations studies
-
-<!-- Three things to cover: No good tools for dealing with MR studies yet (particularly search filters, as terminology is hard + no risk of bias tool); Is double counting of studies an issue (maybe speak to George, particularly if you can find an example)  -->
-
-<!-- TODO Email George with query on dual counting, following review of email with Julian -->
-
-While
-
-This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.
-
-Recent updates, such as a guide to reading and interpreting Mendelian .
-
-However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
-
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants
-
-Double-counting of other -
-
-Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.
-
-In short, given the recent developments in the production of studies and results from Mendelian randomisation
-
-This is particularly relevant to missing evidence, as new methods in MR studies allow for the anlysis of many exposures/outcomes concurrently.
-In this scenario, missing evidence is likely to be an issue as onyl those of particular interest to the authors/those reaching statistical significance will be reported in the paper
-
-This is highlighted by the identification of studies relevant to the review though coincidental reading and citation searhcing, that were not identified by the search as they reported many results and only the statistically significant ones were included in searchable fields
-
-This is particularly troubling given the comprehensiveness of the search (~17,000 records screened).
-In retrospect, a mitigating approach may have been to have an additional search for topics related to risk factors, dementia and MR studies, and screened t
-
-<!-- TODO Best option probably to highlight that while these studies were included, it was not easy given a lack of resources for MR studies -->
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
-[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
-
-The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
-Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
-This may bias reviews as the analysising multiple risk factors at a time becomes more common.
-
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's"),
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Is it a big issue that the studies have the same underlying datasets? <!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
-
-Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
-However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
+The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
+An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
+
+In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
+However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
 
@@
 
-<!--- IDEA Findings from this chapter are used throughout the later chapters of this thesis.
-In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.
-From Sam abbotts--->
-
 In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
 
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref()
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of -->
-
-A
+This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
+
+<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
 

### 2021-08-10 R/03-Code-Systematic-Review.R

@@ -87,8 +87,9 @@ if(doc_type == "docx") {
 }
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- agreeInter-table
+# ---- agree-setup
 
+# Inter
 agreeInter_table <- data.frame(group = rep("Second reviewer decision",3),
                                reviewer = c("Exclude", "Include", "Total"), 
                                Exclude = c(1244,26,1270), 
@@ -103,6 +104,25 @@ agreeInter_coeff_table <- agreeInter_coeff_table[-1]
 
 agreeInter_coeff <- unlist(c(comma(irrCAC::gwet.ac1.table(agreeInter_coeff_table)[2]),
                              comma(irrCAC::kappa2.table(agreeInter_coeff_table)[2])))
+
+# Intra
+agreeIntra_table <- data.frame(group = rep("Same reviewer decision",3),
+                               reviewer = c("Exclude", "Include", "Total"), 
+                               Exclude = c(1266,4,1270), 
+                               Include = c(14,17,31), 
+                               Total = c(1280,21,1301))
+
+discrepancy_Intra <- agreeIntra_table$Exclude[2]
+
+agreeIntra_coeff_table <- agreeIntra_table[1:2,2:4]
+rownames(agreeIntra_coeff_table) <- agreeIntra_coeff_table[,1]
+agreeIntra_coeff_table <- agreeIntra_coeff_table[-1]
+
+agreeIntra_coeff <- unlist(c(comma(irrCAC::gwet.ac1.table(agreeIntra_coeff_table)[2]),
+                             comma(irrCAC::kappa2.table(agreeIntra_coeff_table)[2])))
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- agreeInter-table
 
 if(doc_type == "docx") {
   knitr::kable(agreeInter_table, caption = "(ref:agreeInter-caption)")
@@ -126,21 +146,6 @@ if(doc_type == "docx") {
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- agreeIntra-table
-
[…]

### 2021-08-13 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
-For example, I led a descriptive analysis of the change data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
+For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
 
-We found <!-- TODO complete -->
+medRxiv requires that authors complete a data availability statement, but do not police
 
-This study has since been published in PLOS One, and a copy is included in Appendix \@ref() .
+We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
+
+This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
 

### 2021-08-13 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-Following ful-text screening, 127 studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+Following full-text screening, __XXXX__ studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
 
@@
 
-<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
+The majority of studies were non-randomised, with only one included randomised controlled trials (the Heart Protection Study) and a relative small number of Mendelian randomisation studies.
+Of the non-randomised studies, many were assessments of the relationship with statis use.
+
+Of the studies examining lipid levels, by far the most common fraction assessed was total cholesterol. The association with triglycerides levels was not consider in many papers.
+<!-- TODO Check this is actually true-->
+
+The vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia.
+
+Many studies using electronic health records as their data source did not accurately report the diagnostic criteria used to identify cases, and of those that did, none sought to validate the accuracy of their defined code lists.
+
+<!-- TODO Check this, and do I actually want to say this, as I don't validate my codelist in the CPRD analysis? -->
+
+Many of the studies were conducted in electronic health record databases, which have a number of advantages over smaller more traditional cohort studies.
 
@@
 --->
+
+<!-- TODO Also need to extract the codes used in each study -->
 
@@
 
-<!-- TODO ### Risk of bias {#risk-of-bias-subheading} -->
-
-<!-- &nbsp; -->
-
+### Risk of bias {#risk-of-bias-subheading}
+
+Many of the included studies were at high-risk of bias.
+
+The one randomised controllled trial was deemed to be a low risk of bias,
+
+&nbsp;
 <!----------------------------------------------------------------------------->
@@
 This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+
+The distribution of evidence between analytical designs is to be expected.
+Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
+Similarly, Mendelian randomisation is a relatively new study design, and so only appears in the literature in recent years, driven by the growth of dementia GWASs (Figure \@ref(fig:typeByYear)).
+
+<!----------------------------------------------------------------------------->
+(ref:typeByYear-cap) __Study designs by year of publication__ -
+
+(ref:typeByYear-scap) Study designs by year of publication
+
+```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+<!----------------------------------------------------------------------------->
+```{r preprintGrowthSetup, include=FALSE}
+```
+
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.
+
+(ref:preprintGrowth-scap) Growth of preprint repositories over time
+
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
+```
+<!----------------------------------------------------------------------------->
 <!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->
@@
 
+One particular limitiation with regards to the risk of bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
+This meant that there were no signalling questions to guide the domain-level risk of bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
+However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
+In fact, low agreement was common across the tools, though this is expected based on the available literature.
+<!-- TODO CITATION NEEDED -->
+
+One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
+Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
+
 <!----------------------------------------------------------------------------->

### 2021-08-13 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
+<!-- TODO The rates shown are per days at risk not years-->
+
+Crude rate ratios were calculated for each outcome and class of interest and are presented in Table \@ref(tab: )
+
 The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
@@
 
-#### Comparing codelists
+#### Comparing codelists {#comparing-codelists}
 
@@
 
+<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->
+
 <!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
@@
 ### Interpretation of results
+
+<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
 

### 2021-08-13 05-Chp-IPD-Analysis.Rmd
End of day
End of day:

@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ## Introduction
@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ## Methods
+
+As part
 
@@
 Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-### Epic Norfolk
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Epic Norfolk
 
@@
 
+#### BRACE
+
+#### CaPS
+
+#### ELSA
+
+#### EPIC Norfolk
+
+#### Generation Scotland
+
+#### Memento
+
+#### NICOLA
+
+#### TRACK HD
+
+#### Whitehall II
+
+_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
+Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
+
+included in previous IPD meta-analysis (Endnote ID: 2140)
+
 Different approaches to combining subgroups. [@fisher2017]
@@
 See
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Data cleaning
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 

### 2021-08-13 R/03-Code-Systematic-Review.R

@@ -172,7 +172,7 @@ if(doc_type == "docx") {
 
 toc_df <- rio::import("data/sys-rev/Book1.xlsx",which = 1) %>%
   janitor::clean_names() %>%
-  select(study_id, author, year, location, data_source)
+  select(study_id, author, year, type, location, data_source)
 
 toc_df2 <- rio::import("data/sys-rev/Book1.xlsx",which = 2) %>%
   janitor::clean_names() %>%
@@ -182,6 +182,14 @@ toc_df2 <- rio::import("data/sys-rev/Book1.xlsx",which = 2) %>%
             Exposures = paste0(unique(exposure), collapse = "; "), 
             Outcomes = paste0(unique(outcome), collapse = "; ")) %>%
   ungroup()
+
+p_type <- toc_df %>%
+  group_by(year) %>%
+  count(type) %>%
+  ggplot(aes(x = year, y = n, fill = type)) +
+  geom_bar(stat = "identity")
+
+ggsave(here::here("figures/sys-rev/type_by_year.png"), p_type)
 
 studyCharacteristics_table <- left_join(toc_df, toc_df2) %>%
   mutate(Study = paste(author, year)) %>%
@@ -216,7 +224,7 @@ if(doc_type == "docx") {
 world <- toc_df %>%
   count(location) %>%
   right_join(
-    rnaturalearth::ne_countries(scale = "medium", returnclass = "sf"),
+    rnaturalearth::ne_countries(scale = "medium", returnclass = "sf") %>% filter(type != "Dependency"),
     by = c("location" = "name")
   ) %>%
   tidyr::replace_na(list(n = 0))
@@ -286,10 +294,10 @@ p3 <- p2 + plot_space + p1 + plot_layout(
   guides = 'collect',
   widths = c(1, 1, 1),
   heights = c(5, 0.1, 10)
-)  & labs(fill="No. of\ncohorts") &
-  scale_fill_gradient(low = "grey95",
-                      high = "grey10") &
-  theme(legend.position = "left", 
+)  & labs(fill="No. of\nstudies") &
+  scale_fill_gradient(low = "#ffffff",
+                      high = "#000000", guide = guide_legend(reverse = TRUE)) &
+  theme(legend.position = "left",
         legend.box.margin=margin(0,20,0,0))
 
 ggsave(
@@ -386,3 +394,82 @@ dev.off()
 # t <- metafor::rma.uni(data = test,
[…]

### 2021-08-13 R/04-Code-CPRD-Analysis.R

@@ -1609,7 +1609,7 @@ clean_stata_output <- function(data){
     janitor::clean_names() %>%
     data.table::transpose() %>%
     mutate(V4 = comma(as.numeric(V4)/365.25)) %>%
-    select(V2,V4,V5) %>%
+    select(V2,V4,V6,V5) %>%
     filter(!V2 %in% c("hc_eze_~a", "hc_nag")) %>%
     arrange(match(V2, c("None","hc_sta","hc_om3", "hc_fib","hc_eze","hc_bas"))) %>%
     mutate(V2 = case_when(V2 == "None" ~ "No LRA (unexposed)",
@@ -1621,60 +1621,66 @@ clean_stata_output <- function(data){
                           T ~ "Total"))
 }
 
-main <- readLines(here::here("data/cprd/mylog.txt"))[c(19:26,28)] %>%
-  clean_stata_output()
+options(scipen=999)
 
-main[,4] <- readLines(here::here("data/cprd/mylog_adprob.txt"))[c(15:22,24)] %>%
+main <- readLines(here::here("data/cprd/rate_table.txt"))[c(19:26,28)] %>%
   clean_stata_output() %>%
-  pull(V5)
+  select(V2,V5,V4,V6)
 
-main[,5] <- readLines(here::here("data/cprd/mylog_adposs.txt"))[c(15:22,24)] %>%
+main <- cbind(main,readLines(here::here("data/cprd/rate_table_adprob.txt"))[c(15:22,24)] %>%
   clean_stata_output() %>%
-  pull(V5)
+  select(V5,V4,V6))
 
-main[,6] <- readLines(here::here("data/cprd/mylog_vasdem.txt"))[c(15:22,24)] %>%
+main <- cbind(main,readLines(here::here("data/cprd/rate_table_adposs.txt"))[c(15:22,24)] %>%
   clean_stata_output() %>%
-  pull(V5)
+  select(V5,V4,V6))
 
-main[,7] <- readLines(here::here("data/cprd/mylog_othdem.txt"))[c(15:22,24)] %>%
+main <- cbind(main,readLines(here::here("data/cprd/rate_table_vasdem.txt"))[c(15:22,24)] %>%
   clean_stata_output() %>%
-  pull(V5)
+  select(V5,V4,V6))
+
+main <- cbind(main,readLines(here::here("data/cprd/rate_table_othdem.txt"))[c(15:22,24)] %>%
+  clean_stata_output() %>%
[…]

### 2021-08-17 01-Chp-Background.Rmd
End of day:

--- 2021-06-15 01-Chp-Background.Rmd
@@
 Welch, V.,  **McGuinness L.
-A.** (2020).
+A.** (2021).
 Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
-MetaArXiv.
-DOI: [10.31222/osf.io/ptg9j](https://doi.org/10.31222/osf.io/ptg9j)_
+Prevention Science .
+DOI: [10.1007/s11121-021-01279-8](https://doi.org/10.1007/s11121-021-01279-8)_
 
@@
 <!-- TODO Need to create author declarations section -->
- [Under 2nd round of review at Prevention Science]
 
@@
 
-_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Accepted poster abstract, Alzheimer's Association International Conference 2021.
-
+_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Poster presentation, Alzheimer's Association International Conference 2021.
 &nbsp;
 
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_:
-Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
+_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
 

### 2021-08-17 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
-The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]
+The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which launched in 2019 and was designed to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv.[@rawlinson2019]
 
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
+Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
 At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
@@
 
-This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool created to facilitate the searching of medRxiv and bioRxiv preprints.
-The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in external projects and by other researchers is discussed.
-As the majority of work on this aspect of this thesis is represented by lines of code (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr)) this Chapter is an intentionally short, high-level summary of the work done on this project.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.
+This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool I created to facilitate the systematic searching of medRxiv and bioRxiv preprints.
+The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in my own projects and by other researchers is discussed.
+As the majority of work on this aspect of my thesis is represented by lines of code or online documentation (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr) and [https://docs.ropensci.org/medrxivr/](https://docs.ropensci.org/medrxivr/) respectively), this chapter is an intentionally short, high-level summary of my work on this project.
+The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.[@zotero-15029]
 
@@
 
-(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow:** `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
+(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow** - `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
 Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
@@
 
-The tool was developed to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
+I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
 The criteria were as follows:
@@
 
-Prior development of this tool, an audit of existing tools for accessing medRxiv and bioRxiv metadata was conducted.
+Prior to development of this tool, I conducted an audit of existing tools for accessing medRxiv and bioRxiv metadata.
 While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
 
-The first, a platform called Rxivist [@abdill2019], allows users to search preprints using keywords.
+The first, a platform called Rxivist[@abdill2019], allows users to search preprints using keywords.
 However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface[^chp-systematic-review-tools-2] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
-
-[^chp-systematic-review-tools-2]: Available at <https://rxivist.org/>
+The search interface[@zotero-15027] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
 
@@
 Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and the initial version of the `medrxivr` R package was released in February 2020.
+Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and I released the initial version of the `medrxivr` R package in February 2020.
 
@@
 Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, constant maintenance work was required to ensure the web-scraping script performed as expected, as the repository website was regularly updated.
+In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required me to regularly update or fix the script.
 
@@
 
-The `medrxvir` package was written in R using RStudio,[@rcoreteam2019] and followed development best-practice, including detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
+I wrote the `medrxvir` package in R using RStudio,[@rcoreteam2019] and followed development best-practice, including development of detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
 
@@
 
-While the package allows for users to search both medRxiv and bioRxiv, as the process is identical for both, the examples in the sections are limited to the medRxiv repository.
+While the package allows users to interact with and search both medRxiv and bioRxiv metadata, as the process is identical for both, searching the medRxiv database is used as an illustrative example throughout this chapter.
 
@@
 
-`medrixvr` provides two ways to access medRxiv data, as shown in Figure \@ref(fig:medrxivr-data-sources).
-The first, via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
+<!-- TODO Clean up this section -->
+
+<!-- REVIEW Not clear why there are two, or what are advantages or disadvantages of each. There’s a hint below (“can become unavailable during peak usage times”), but perhaps add some more -->
+
+Prior to searching the metadata, it must first be imported in R.
+In `medrixvr`, I have provided two separate but related methods for users to import the data (Figure \@ref(fig:medrxivr-data-sources)).
+The first of these methods, accessed via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
 
@@
 
-The second, via the `mx_snapshot()` function, provides access to a maintained static snapshot of the database, created each morning at 6am using `mx_api_content()`.
+This provides an up-to-the-minute reflection of the medRxiv preprint repository.
+However, this approach has two limitations.
+Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database  <!-- TODO Get numbers here, at a given date --> requires a time-intensive process of cycling through multiple pages.
+Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
+
+To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
 
@@
 
-Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
-The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
+This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file to an online server (Figure \@ref(fig:medrxivr-data-sources)).
+Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
+
+The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
+However, given that the number of records added each day is relatively low, this should pose minor issues.
 
@@
 
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
+(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources** - Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
 Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
@@
 Once a local copy of the metadata is created, the first step in searching it is to create a search strategy.
-Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(…)`).
+Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(...)`).
 
@@
 
-### Refining your search
+### Refining a search
 
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.
-__[CITATION NEEDED - PRISMA-S]__
+An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.[@rethlefsen2021prisma]
 
@@
 results  <- mx_search(mx_data,
-                      myquery, # Combined with OR
+                      myquery,
                       report = TRUE)
@@
 
+<!-- TODO Add some text to this section about the challenges of defaults, and the fact that the autocaps option exists -->
+
+<!-- REVIEW Can you not just make the search case insensitive?
+It means you often need to include capitalized and non-capitalized versions in case a word appears at the start of a sentence or is capitalized for some other reason?
+(I find a lot of people these days pseudo-randomly capitalize words for no good reason (like you did in “Application Programming Interface” on page 4 above!!)) -->
+
 &nbsp;
@@
 
-In line with the second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
+In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
 While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
@@
 For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
+
+&nbsp;
 
@@
 
-The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
+The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
 
@@
 
-medRxiv requires that authors complete a data availability statement, but do not police
+By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two differnt publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
+We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
+This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
+Author contributions are discussed in the
 
-We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
-
-This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
+In short, this use case illustrates that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints as a part of evidence synthesis exercises.
 
@@
 
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
 A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
@@
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
+
+<!-- TODO Clean-up this section -->
+
+<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
+
+Allowing for a two year lag, previous work has found that two-thirds of bioRxiv preprints were published in a peer-reviewed journal,[@abdill2019b] indicating that s not-insignificant number of preprints are never publishe but are accessible as preprints.
+
+It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 
@@
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably harm to the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 

### 2021-08-17 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-# Systematic review of all available evidence {#sys-rev-heading}
+# Systematic review of all evidence available on the association between blood lipids (and treatment) and dementia outcomes {#sys-rev-heading}
 
@@
 
-<!-- TODO PRISMA must include reasons for exclusion - extract from  -->
+<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
 
@@
 ### Summary of findings
+
+some evidence that age has impact on observed lipid-dementia relationship - use to link
 
@@
 The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).
+
+medRxiv grew out of the Epidemiology and Clinical Trials categories of the 
+<!-- TODO Complete above paragraph -->
 

### 2021-08-17 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
     template: templates/brief_template.tex
+    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
   bookdown::word_document2: 
@@
 The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia).
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia: Table \@ref(tab:followUp-table)).
 The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
@@
 
-<!-- TODO The rates shown are per days at risk not years-->
-
-Crude rate ratios were calculated for each outcome and class of interest and are presented in Table \@ref(tab: )
+Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
+
+\blandscape
+
+<!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary
+
+(ref:followUp-scaption) followUp
+
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+\elandscape
 
@@
 &nbsp;
+
+<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
+
+<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
 

### 2021-08-17 05-Chp-IPD-Analysis.Rmd
End of day:

@@
 output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
   bookdown::pdf_document2:
     template: templates/brief_template.tex
+  bookdown::word_document2: default
+  bookdown::html_document2: default
 documentclass: book
@@
 
-Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
+<!-- TODO Read this[@riley2020] -->
 
@@
 
-Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get
+These data source
 
@@
 
+#### CPRD
+
+The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+
+The CPRD is introduced more fully in . Briefly, a similar approach to the cohort definition as used in Chapter
+
 #### ELSA
@@
 
-Several DPUK cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
 
-See
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Cohorts provided data but ultimately excluded
+
+Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Cohorts identified the systematic review but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+Electronic health record co
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Cohorts approach but received no answer
+
+Maybe discuss here t
+
+This was particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
+Despite multiple attempts to contact the team, there was no response received.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Data cleaning
+
+Across all cohorts, data cle
+
+For all cohorts, the first lipid measurement was used for the exposure method,
+
+For heterogeneity across the cohorts, the total time at risk was investigated.
+
+<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Missing data
+
+Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
 
@@
 
-### Data cleaning
+### Analysis
+
+All analysis were standardised by changes in 1-SD of the exposure variable.
+
+This was done to
+
+CLustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+
+Stratified by age-at-entry and sex, and ethnicity where possible.
+
+## Results
 
@@
 
-Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responded if at all.
+### Limitations
+
+#### Low response rate to request for data
+
+This review had a low response rate to requests for data access.
+
+While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.
+
+There are likely several reasons for this.
+
+* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
+
+* While there is no
+
+For many other reasons also - if
+
+A potential further reason was highlighted during my attendance at the
+
+Letters sent to all cohorts identified through the systematic review <!-- TODO will need quite a bit here on the numbers approached and how they responded if at all.
 Will also need to comment on the additional tactics used.
+-->
 
@@
 
-As part of this, an analysis of
+The low response rate and the
+
+Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
+
+<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
+The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
+Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
+However, analysis combining individual and study level data may mitigate these effects [3, 21].
+from [@ventresca2020a] -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
+Even with the guaranteed data access afforded by the DPUK, accessing sufficient data was
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Study within a review
 
-In future, it could have been worth running a "study within a review", such as that used to examine whe
+In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a]
 
-https://bmjopen.bmj.com/content/9/1/e025273
+\newpage
+
+## References

### 2021-08-17 front-and-back-matter/_00-introduction.Rmd
End of day: -3799
End of day: -2951
End of day:

@@
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-documentclass: book
----
-
 # Covering material {-}
@@
 library(ggplot2)
+
+options(scipen=999)
 
@@
 
-words <- sum(words_v)
+# TODO Work out what an appropriate number of words for tables is
+# Sum words and add number of words in tables
+words <- sum(words_v) + 250
 

### 2021-09-13 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
+#### Combining across groups
+
+Following best practice, where summary data was presented across two groups (e.g.
+age at baseline stratified by hypercholesterolemai status), the following approach was used to combine the groups <!-- TODO Cite cochrane handbook here -->
+
+<!-- TODO Insert equations here -->
+
+\begin{equation}
+N = N_1 + N_2
+  (\#eq:combiningGroups1)
+\end{equation}
+
+\begin{equation}
+Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
+  (\#eq:combiningGroups2)
+\end{equation}
+
+\begin{equation}
+SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
+  (\#eq:combiningGroups3)
+\end{equation}
+
+This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis. where more than one group
+
 #### Harmonisation of cholesterol measures
@@
 --> The fixed-effect method was implemented as:
+
+<!-- TODO Check these against those in Ben's thesis paper -->
 
@@
 Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
+<!-- TODO Each bracket should have an upper and lower end -->
 
@@
 
-Further, given the importance of visualising the potential biases of a result alongside the result itself, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).
-<!-- TODO CITATION NEEDED --> This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
+Further, given the importance of visualising the potential biases of a result alongside the result itself, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
 
@@
 
-Preprints are a valuable evidence source (see Introduction, Section \@ref()) but their inclusion in a systematic reivew.
+Preprints are a valuable evidence source (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
+
 As part of a study within this larger review, I also to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
@@
 ## Results
+
+<!-- TODO Compare findings for two papers from Rantanen -->
 
@@
 The PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+
+<!-- TODO Finish PRISMA -->
 
@@
 
+Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
+
 &nbsp;
@@
 <!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) studyCharacteristics
-
-(ref:studyCharacteristics-scaption) studyCharacteristics
+(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
+
+(ref:studyCharacteristics-scaption) Characteristics of included studies
 
@@
 
-Many of the included studies were at high-risk of bias.
-
-The one randomised controllled trial was deemed to be a low risk of bias,
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Meta-analysis of statin use and hypercholesteroleamia
+Many of the included results were assessed to be at high risk of bias.
+
+The one randomised controlled trial was deemed to be a low risk of bias,
+
+Several synthesis were also assessed to be at risk of bias due to missing evidence.
+
+A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
+This is discussed further in Section \@ref(rev-discussion-MR).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Statins
+
+```{r primaryFigures, include = FALSE, message=FALSE,warning=FALSE}
+```
 
@@
 
-Statin use was associated with a reduce risk of all-cause dementia (`r estimate(0.76,0.66,0.88)`, Figure \@ref(fig:fpStatins)).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-```{r primaryFigures, include = FALSE}
-```
-
-(ref:fpStatins-cap) __Forest plot showing effect of statins:__
-
-(ref:fpStatins-scap) Forest plot showing effect of statins
-
-```{r fpStatins, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpStatins-cap)', out.width='100%', fig.scap='(ref:fpStatins-scap)'}
+In the two included RCTs, statin use was not associated with dementia outcomes
+
+<!----------------------------------------------------------------------------->
+(ref:statinsRCT-cap) __Random effects meta-analysis of statins on all-cause dementia:__
+
+(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r statinsRCT, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forest_statins_rct.png"))
+```
+<!----------------------------------------------------------------------------->
+
+In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r estimate(0.76,0.66,0.88)`, Figure \@ref(fig:statinsNRSI)).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+(ref:statinsNRSI-cap) __Forest plot showing effect of statins:__
+
+(ref:statinsNRSI-scap) Forest plot showing effect of statins
+
+```{r statinsNRSI, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsNRSI-cap)', out.width='100%', fig.scap='(ref:statinsNRSI-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
@@
 <!----------------------------------------------------------------------------->
+
+In Mendelian randomisation studies, a similar blah blah blah
+
+<!----------------------------------------------------------------------------->
+
+(ref:statinsMR-cap) __Forest plot showing effect of statins:__
+
+(ref:statinsMR-scap) Forest plot showing effect of statins
+
+```{r statinsMR, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsMR-cap)', out.width='100%', fig.scap='(ref:statinsMR-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
+
+### Hypercholesterolemia and lipid levels
+
+<!----------------------------------------------------------------------------->
+
+(ref:hypercholNRSE-cap) __Forest plot showing effect of statins:__
+
+(ref:hypercholNRSE-scap) Forest plot showing effect of statins
+
+```{r hypercholNRSE, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:hypercholNRSE-cap)', out.width='100%', fig.scap='(ref:hypercholNRSE-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Several studies presented results per SD change in a lipid fraction.
+
+<!----------------------------------------------------------------------------->
+
+(ref:lipidsNRSE-cap) __Forest plot showing effect of statins:__
+
+(ref:lipidsNRSE-scap) Forest plot showing effect of statins
+
+```{r lipidsNRSE, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidsNRSE-cap)', out.width='100%', fig.scap='(ref:lipidsNRSE-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;
@@
 Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
-The results from the dose response analysis can be seen in Figure \@ref(fig:dose-response).
-
-<!-- TODO Include image -->
+The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
+
+<!----------------------------------------------------------------------------->
+
+(ref:lipidsDoseResponse-cap) __Forest plot showing effect of statins:__
+
+(ref:lipidsDoseResponse-scap) Forest plot showing effect of statins
+
+```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidsDoseResponse-cap)', out.width='100%', fig.scap='(ref:lipidsDoseResponse-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 <!-- ### Sources of heterogeneity -->
+
+Planned to investigate effect of sex and age at baseline.
+
+Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
 
@@
 
-As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching, was not substantial (bioRxiv = 256, medRxiv = 0). <!-- TODO check -->
+I had intended to assess the added evidental value of including preprints as a literautre source.
+
+As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0). <!-- TODO check numbers -->
+
+No unique preprints were identified as part of this review, with the published version of the few/sole <!-- TODO check which --> relevant preprint(s) being captured by the main search.
 
@@
 
-### Risk of bias due to missing evidence
-
-A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
-This is discussed further in Section \@ref(rev-discussion-MR).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
 ## Discussion
@@
 
-some evidence that age has impact on observed lipid-dementia relationship - use to link
+There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
+This finding was not supported by evidence from the single available RCT, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings are a
+
+In addition,  there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of
+
+Some evidence that age has impact on observed lipid-dementia relationship - use to link
 
@@
 
+<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
+The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
+from Anstey 2017 -->
+
+Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] Tie this in with
+
 <!----------------------------------------------------------------------------->
@@
 
+<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
+
 <!----------------------------------------------------------------------------->
@@
 
+Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
+This point is important given one of the core assumptions of
+
+<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
+
 Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
 
-Firstly, as this study design is relatively new, particularly when compared to randomised trials or cohort studies, the process and tools for systematically assessing them are not as well developed.
+Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
+Figure \@ref(fig:typeByYear) demonstrates that MR studies only begin to appear in the evidence base much later than NRSE/NRSI.
+As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
 A key example of this is in the absence of validated search filters for Mendelian randomisations studies.

### 2021-09-13 04-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-No evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
+Little evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
 In contrast, I found an increased risk of vascular and other (i.e.
@@
 
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounded of the exposure-outcome relationship.
-The main analyses presented all used age as the time axis.
+As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
+As such, the main analyses presented all used age as the time axis.
 
@@
 Muscular backpain was chosen as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the effect of statin use on muscle pain[@herrett2021] have found no evidence of an effect.
-As such, if no evidence of an effect of statins on backpain is found in the analysis, then confidence in the results for the dementia outcomes is increased.
+Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
+As such, if statins are not associated with backpain in this analysis, then confidence in the results for the dementia outcomes is increased.
 
@@
 
-To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
+To explore whether any observed associations in the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
 
@@
 
-This previous study used a propensity matching approach to estimate the effect of statins on a range of outcomes, and a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but no evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+This previous study used a propensity matching approach to estimate the association of statins with a range of outcomes, and found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
 
@@
 
-No evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
-Additionally, in the AD outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.
+Additionally, in the AD outcomes, hydrophilic statins were associated with a small reduction in risk, compared to the weak evidence for an effect for lipophilic statins.
 
@@
 
-Lipid-regulating agents showed no evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+Lipid-regulating agents showed little evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
 The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
@@
 
-It found no evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
+It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
 However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.

### 2021-09-13 05-Chp-IPD-Analysis.Rmd
End of day:

@@
 
+Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
+
 <!----------------------------------------------------------------------------->
@@
 Talk about how different covariates were managed across cohorts, 
-
+c
 <!-- TODO Read this[@riley2020] -->
@@
 * Description (including observation period, numbers, numbers with outcome, etc)
-* Whether they are a known genetically at-risk cohort
 *
@@
 
+Has only 8 events
+
 ```{r tests, }
@@
 ```
-
-#### BRACE
 
@@
 
-#### ELSA
+Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
+
+Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
+
+the
 
@@
 #### Generation Scotland
-
-#### Memento
 
@@
 
+#### BRACE
+
+Likley had dementia at baseline
+
+#### Memento
+Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
+
+#### Generation Scotland
+
+Cross-sectional data only
+
+#### NICOLA
+
+NICOLA study - only had cross-sectional data
+
+#### ELSA
+
+Data provided but only had ever high cholesterol as a binary variable. Not compatible with
+
 <!----------------------------------------------------------------------------->
@@
 Electronic health record co
+
+LBC - 1936
+
+Taiwan etc,
 
@@
 
+<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
+
 <!----------------------------------------------------------------------------->
@@
 
-Across all cohorts, data cle
+Across all cohorts, data cleaning was performed in a similary manner, using commonly named variables, so that a single model could be applied using functional programming.
+
+The one exception to this is the CPRD data, which was held in a different system to the rest.
+
+The advantage of this approach is that it reduces the liklihood of errors in model mis-speciication if needing to change variables names from cohort to cohort.
 
@@
 
-For heterogeneity across the cohorts, the total time at risk was investigated.
+For heterogeneity across the cohorts, the total time-at-risk was investigated.
 
@@
 
+There is some concerns about performing risk of bias assessments on your own analysis, and so
+
 <!--- Inlcude CPRD analysis here, but dou --->
@@
 
+<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
+
 All analysis were standardised by changes in 1-SD of the exposure variable.
 
-This was done to
+This was done to aid interpretability of the outcome.
 
-CLustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+Similary,
+
+Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
 
@@
 
+Hazard ratios were utilised to
+
+In order to investigate the interaction of sex with
+
+A two-stage model was used out of necessity, with the one-stage model being recluded by the different datasets being in protected data silos.
+
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
+
+<!-- TODO Figure showing the outline of interval censored studies. -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ## Results
+
+Data
 
@@
 
+Useful citation for discussion[@levis2021]
+
 ### Limitations
@@
 
+<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
+
+<!-- TODO text -->
+
 This review had a low response rate to requests for data access.
@@
 While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.
-
+test
 There are likely several reasons for this.
@@
 
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a]
+In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
+
+Previous SWARs have
 

### 2021-09-13 _main.Rmd
End of day:

@@
 Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can either onset quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
-
-The remaining 10-30% of cases are caused other dementia subtypes (e.g.
-Lewy Body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
+Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
+
+The remaining 10-30% of cases are caused by other dementia subtypes (e.g.
+Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
 Parkinson's disease).[@burns2009]
@@
 
-<!--- May need small bit here on converting from one measurement to the other i.e.
-mg/dL to mmol/L--->
-
-### Lipid fractions
+### Lipid fractions {#intro-lipid-fractions}
 
@@
 
-$$TC \approx LDLc - HDLc - kTG$$
+\begin{equation}
+  TC \approx LDLc + HDLc + kTG
+  (\#eq:total-cholesterol-formula)
+\end{equation}
+
 where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
@@
 These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organisation to be approximately 40%.
-
-<!----------------------------------------------------------------------------->
-
-### Statins
-
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-Hydroxy-3-Methylglutaryl-Coenzyme-A (HMG-CoA) into mevalonic acid, by competitively binding with HMG-CoA Reductase (HMG-CoA-R).
-This conversion limits the rate at which cholesterol can be produced, enabling statins to effectively reduce the production of LDL cholesterol.
-
-<!----------------------------------------------------------------------------->
-
-(ref:statin-mechanisam-cap) **Statin mechanism of action:** Overview of the
+Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.
+
+<!----------------------------------------------------------------------------->
+
+### Statins {#intro-statins}
+
+Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
+This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.
 
@@
 
-```{r eval = FALSE, statin-mechanisam, echo = FALSE, results="asis", fig.cap='(ref:statin-mechanisam-cap)', out.width='100%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
+```{r statin-mechanisam, echo = FALSE, results="asis",fig.pos = "H", fig.align = 'center', fig.cap='(ref:statin-mechanisam-cap)', out.width='50%', fig.scap='(ref:statin-mechanisam-scap)'}
+knitr::include_graphics(file.path("figures/background/statinPath.png"))
+```
+
+&nbsp;
+
+Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)).
+Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g.
+ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
+rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+<!-- TODO Review the look and feel of this table -->
+
+(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.
+
+(ref:statinOverview-scaption) Overview of common statins
+
+```{r statinOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered, or to provide an additional source of evidence for an existing question.
+The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
 
 This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
-Specifically, this thesis considers three methodologies within the umbrella term of evidence synthesis:
-
-* Inclusion of grey literature
+Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:
+
+* Inclusion of preprints
 * Triangulation across evidence sources
@@
 <!----------------------------------------------------------------------------->
-### Triangulating across study designs
+### Triangulating across study designs {#intro-triangulation}
 
 As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own unique biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about a exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, one expected to increased the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.
+However, each method is limited by its own biases.
+Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
+A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
 
@@
 
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not presenting results stratified by covariates of interests, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
-
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all dataset, potentially eliminating some important sources of heterogeneity.[@stewart2002]
-
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies is frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
+In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
+
+An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
+
+Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
 Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
@@
 
-### Hypothesis
-
-Circulating blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, affect the subsequent risk of dementia and related outcomes.
-
 ### Aims and objectives
+
+The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes
 
@@
 Emily Hennessy (see Author Declarations in the front materials).
-[Under 2nd round of review at Prevention Science]
+<!-- TODO Need to create author declarations section -->
 
@@
 2020.
-“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.” MetaArXiv.
-DOI: [10.31222/osf.io/p75xe](https://doi.org/10.31222/osf.io/p75xe)_
-
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
-[Accepted to PLOS One - need to update the citation]
+“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887.
+DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_
+
+Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
 
@@
 
-_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Accepted poster abstract, Alzheimer's Association International Conference 2021.
-
-&nbsp;
-
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_:
-Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
+_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Poster presentation, Alzheimer's Association International Conference 2021.
+&nbsp;
+
+_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
 
@@
 
-(ref:sys-rev-quote) --- Archie Cochrane, 2000 [@cochrane20001931]
+(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
 
@@
 
-## To Do
-
--   Examine how many times a primary study was included in a review\
--   Look at whether searching preprints made any difference to my results
--   Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project)
-
-## Extra studies to include:
-
-* Smeet et al. reference in the CPRD analysis
-* Larsson - 10.1136/bmj.j5375 [@larsson2017b]
-* Statins and the risk of dementia Jick
+<!-- ## To Do -->
+
+<!-- -   TODO Examine how many times a primary study was included in a review -->
+<!-- -   TODO Look at whether searching preprints made any difference to my results -->
+<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->
+
+<!-- TODO Extra studies to include: -->
+
+<!-- * Smeet et al. reference in the CPRD analysis -->
+<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
+<!-- * Statins and the risk of dementia Jick -->
 
@@
 
-## Additional ideas
-
--   Evidence map - show the distribution of the different studies population across the world.
--   Living systematic review approach - update weekly based on medRxiv
-
-## Aims
+The importance of
+
+I found that
+
+The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+## Introduction {#sys-rev-intro}
 
@@
 
-Based on the review of prev, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
-
-Only by looking across all available evidence can
+Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
+
+Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).
 
@@
 
+Systematic reviews aim to transparently and reproducibly identift
+
+<!-- TODO Need to seriously improve this -->
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 ## Methods
 
-### Search strategy
-
-We will systematically search electronic bibliographic databases to identify potentially relevant records.
-The search strategy used in each database will be developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE) terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and will be designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table 3.2 below and the full draft search strategies for each database are attached to this protocol.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as Line 7 NOT Line 13 in Table 3.2) will be screened.
-If any potentially relevant studies are identified, their titles and abstracts will be searched for key terms that can be incorporated into the filters to improve search sensitivity.
-
-The following databases will be searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+### Protocol
+
+A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]
+
+### Contributions
+
+This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.
+
+<!-- TODO Double check this list at the end of the project. -->
+
+### Search strategy and and study selection
+
+I systematically search electronic bibliographic databases to identify potentially relevant records.
+The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
+The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+<!-- TODO Need to actually attach each search strategy.
+Should be able to loop through search strategy results.
+-->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:searchOverview-caption) Summary of systematic search by topic.
+The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
+
+(ref:searchOverview-scaption) searchOverview
+
+```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 14" in Table \@ref(tab:searchOverview-table)) was screened.
+If any potentially relevant studies are identified, their titles and abstracts were searched for key terms that can be incorporated into the filters to improve search sensitivity.
+
+<!-- TODO need to comment on this feed-back process, or remove -->
+
+The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
 We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
 
 The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) will be searched.
-Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses will be accessed using the Open Access Theses and Dissertations portal.
+the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
+<!-- TODO how were these searched?
+Date and other range -->
+
+ Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
 We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies will be searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
+
+<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->
 
@@
 
-The full search strategy for the Medline search, which was designed first and subsequently translated into the syntax for other databases is presented in Appendix \@ref(appendix-search-strategy).
-
-### Study selection
-
-Records will be imported into Endnote and deduplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] Screening (both title/abstract and full-text) will be performed using a combination of Endnote and Rayyan, a web based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records will be performed by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-If this demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+#### Study selection
+
+Records were imported into Endnote and deduplicated using the method outlined in Bramer et al.
+(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
+those matched based on the "Title" field alone).
+
+Screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+
 Full-text screening will also be completed in full by the primary author.
-A second reviewer will screen a random sample of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
-Reasons for exclusion at this stage will be recorded.
-Disagreements occurring during either stage of the screening process will be resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.[@zotero-766]
+A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
+Reasons for exclusion at this stage were recorded.
+Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
+A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]
 
@@
 
+<!-- TODO Expand on rationale for exclusion of cross-sectional studies.
+Dementia is a disease severly at risk of differential recall, leading to misclassification bias.
+By using prospective studies, the potential for this bias is reduced.
+-->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Assessment of inter-rater reliability
+
+Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
+
+If this approach demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
+
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.
+
+Gwet's AC1 is defined as:
+
+$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
+
+In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
+
+\begin{equation}
+  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
+  (\#eq:AC1-main)
+\end{equation}
+
+where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
+
+\begin{equation}
+  q = \frac{(A+C)+(A+B)}{2N}
+  (\#eq:AC1-supp)
+\end{equation}
+
+<!-- TODO Need to be sure of how to calculate. -->
+
+How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
+
+(ref:gwet-scaption) Ranges for Gwet's AC1
+
+```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 ### Data extraction
@@
 
-Following guidance for a dose response meta-analysis, we picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
-
-This analysis was unusual, as multiple methods of intergration and analysis were required with data spannign many forms.
+Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
+
+This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.
+
+A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.
 
@@
 
+Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
+
+\begin{equation} 
+  mg/dL = mmol/L \times{} Z
+  (\#eq:lipidConversion)
+\end{equation}
+
+where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
+For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+
+<!----------------------------------------------------------------------------->
+
+#### Studification
+
+Multiple publications resulting from the analysis of the same data were included and grouped ().
+
+In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
+Instead, they were considered as different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+
+<!----------------------------------------------------------------------------->
+
+#### Following up with authors {#contacting-authors}
+
+Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
+This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
+
+This was particular important for the dose response meta-analysis, we
+
+Use the example of getting the cut-off points from the
+
+<!-- TODO move to results, and keep just a short bit here -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Converting between different
+
+Include formulae and informed assumptions
+
+Not interchangeable in the context of systematic review.
+If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
+
+Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
+
+The likely effect of this is that the overall effect measures are biased towards . . . . ?
+
+Can you predict the direction of effect from a
+
+Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
+
+<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
+
+Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
+
+WHile the analysis of change scores is feasible, as they were explicityl
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Risk of bias assessment {#risk-of-bias}
 
-Risk of bias assessment was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019], non-randomized studies of interventions were assessed using the ROBINS-I tool,[@sterne2016] and non-randomized studies of exposures were assessed using the ROBINS-E tool.[CITE]
-
-I opted to use the ROBINS-E tool, despite it still being in development,[@morganr2020] in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000newcastle] There are two primary reasons for this: firstly, current thinking in assessing internal validity has moved away from scales.
-
-<!-- TODO Cite release version of this tool, and just use domain based approach -->
-
-Secondly, using a domain based to assess the risk of bias in studies of exposure allowed for better comparison and consistency across the tool used for different study designs, as they are all domain based.
-
-<!-- TODO This next bit is not true -->
-
-At present, no risk of bias assessment tool for Mendelian randomization studies is available.
-Bias in these studies was assessed with the help of an expert panel drawn from my supervisors and other external invited researchers.[CITE] The risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation, as identified by a review of risk of bias assessments in systematic reviews of MR studies.[@mamluk2020] A copy of the is available in Appendix \@ref(appendix-mr-rob).
+A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation).
+To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.
+
+There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
+Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
+
+This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.
+
+As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+
+Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
+For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up.
+missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up.
+In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.
+
+In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
+The study design-specific tools are introduced and discussed in more detail in the following sections.
+
+In addition, the tool also aim to capture the potential direction of bias for each given domain.
+An optional question at the end of each domain, e.g.
+for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included
+
+* Not applicable 
+* Favours experimental 
+* Favours comparator
+* Towards null 
+* Away from null 
+* Unpredictable
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Randomised controlled trials
+
+Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
+Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019],
+The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
+Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
+Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
+
+One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Non-randomised studies of interventions/exposures
+
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
+Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including.
+Ideally, obs studies assessed in reference to an idealised randomised controlled trial.
+Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
+
+For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.
+
+Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold.
+In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
+In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Mendelian randomisation studies
+
+<!-- TODO This next bit is not all true -->
+
+At present, no risk-of-bias assessment tool for Mendelian randomization studies is available.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies.
+A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
 Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
 
-Results from the risk-of-bias assessment will be visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2019] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
-
-<!-- TODO Cite MR tool here from malmuk, see info from Francesca -->
-
-Many reviews use reporting guidelines instead - this is bad![@costa2011]
-
-<!----------------------------------------------------------------------------->
-
-## Studification
-
-In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-<!----------------------------------------------------------------------------->
-
-## Following up with authors
-
-As part of the IPD analysis, relevant cohort studies were identified and approached. In the first instance, the corresponding author on the main man
-
-<!-- TODO move to results, and keep just a short bit here -->
-
-<!----------------------------------------------------------------------------->
-
-### Statistical analysis methods
-
-<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Risk of bias due to missing evidence
+
+A recent shift towards the assessment of missing evidence due to selective non-reporting (as distinct from the selective reporting of a single result from multiple planned - handled in Domain 5 of the RoB 2 tool for example).
+
+As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualised
+
+<!----------------------------------------------------------------------------->
+
+### Analysis methods
+
+Studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies).
+
+#### Standard meta-analysis
 
@@
 
-Need formula here, and description of different methods and quarrels re fixed effect vs random effects meta-analyses.
-
-This anal
-
-Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.
-
-### Visualisation of results
+Both a fixed-effect and random-effects meta-analysis model was.
+
+For
+
+Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
+
+This analytical approach was used for
+
+$u$
+
+\begin{equation}
+  \theta_i = \mu + u_i
+  (\#eq:meta-analysis-random)
+\end{equation}
+
+\begin{equation}
+  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
+  (\#eq:meta-analysis-fixed)
+\end{equation}
+
+where ...
+
+<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
+
+This analytical approach was used for cases where the exposure was dichotomous (e.g. statin use or not, hypercholesterolemia or not).
+
+#### Dose-response analyses
+
+<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
+<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.  -->
+
+Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
+for example, highest vs lowest quartile).
+<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
+-->
+ while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
+
+Where possible, data for all exposure groups was extracted, and this <!-- TODO ??? -->
+.
+Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
+if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).
+
+<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
+
+<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
+A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
+Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
+Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
+
+Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
+Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).
+
+When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it.
+Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
+
+I assumed the width of the category to be the same as the adjacent category.
+When the lowest category was open ended, I set the lower boundary to zero.
+
+#### Sensitivity analyses
+
+I conducted a leave one out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED -->
+
+In addition,
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Visualisation of results
 
@@
 
-A summary of this tool is contained in Appendix \@ref (), .
+This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->
+
+A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using
+
+Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
+This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
+
+Also, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a
+
+As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
 
@@
 
-Preprints are a valuable vidence source (see Introduction) but their inclusion in a systematic reivew
-
+Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
+s
 Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
@@
 
-<!----------------------------------------------------------------------------->
+Patient and public members were intended to be involved at this poit
+
+<!----------------------------------------------------------------------------->
+
+### Deviations from the protocol
+
+A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->
+
+Similarly, there was initially no intention to try and examine the risk of bias due to missing evidence.
 
@@
 
-### Previous reviews
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, we examined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
-
-Put upSet plot here.
-
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
-
-<!----------------------------------------------------------------------------->
-
-### Screening results
+### Search and screening results
+
+Following the search
+
+`r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.
+
+<!--- Cross check this with the actual numbers included --->
+
+No eligible records were identified in the screening of the 500 records excluded by the search. Many of these were basic science studies <!-- TODO text -->
+
+<!----------------------------------------------------------------------------->
+
+```{r prisma-flow-setup, include = FALSE}
+```
+
+\blandscape{}
+
+&nbsp;
+
+(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
+The different contributions of databases and preprint servers to the review are indicated.
+
+(ref:prisma-flow-scap) PRISMA flow diagram
+
+```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+
+\elandscape{}
+
+<!----------------------------------------------------------------------------->
+
+Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
+`r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened.
+\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
+
+<!----------------------------------------------------------------------------->
+
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> shown in Figure \@ref(prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
 
@@
 
-Table \@ref(tab:incl-studies-character) shows the characteristics [**Include column here that says whether it was included in a systematic review - see below**]
-
-As part of our our forward snowballing exercise (where articles citing an included study are cited), we recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
+&nbsp;
+
+As part of our our forward snowballing exercise (where articles citing an included study are cited), I recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
 Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
@@
 
+<!-- TODO Actually do this! -->
+
 <!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
 
-As a summary of the duplication of work in this area, we looked at how many reviews a single included study had previously been included in.
-
-Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments) as i account for chance agreement between reviewers but does not suffer from severely imbalanced marginal totals in the same way that Cohen's kappa value does.
-[@cohen1960: @gwet2008; @wongpakaran2013]
-
-How to interpret agreement co-efficients is widely debated.
-Here we use guidelines based on a stricter interpretation of the Cohen's Kappa coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In a two-by-two table with cells A, B, C and D, Gwet's AC1 is calculated using the following:
-
-$$AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}$$
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-$$q = \frac{(A+C)+(A+B)}{2N}$$
-
--\> Insert formula here. Need to be sure of how to calculate. [@gwet2008; @sim2005]
+As a summary of the duplication of work in this area, Ilooked at how many reviews a single included study had previously been included in.
 
@@
 
-<!-- # ```{r agreementtableinter, echo = FALSE} -->
-
-<!-- # ``` -->
-
-<!-- # ```{r agreementtableintra, echo = FALSE} -->
-
-<!-- # ``` -->
-
-For the inter-rater reliability, percentage agreement was 97.3% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)), while for the intra-rater reliability, agreement was 98.6% (AC1 = XXXX, Table \@ref(tab:agreement-table-intra)).
-
-The discrepancy between the percent agreement and the associated value of AC is expected, due to the heavy imbalance in this sample towards exclusion.[@feinstein1990]
-
-Those records which were excluded in the initial screening, but were included either by the same reviewer on their second viewing (n=4), or by the second reviewer (n=29), were investigated.
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:agreeInter-caption) Inter-rater agreement on a subset of ~10% of records, illustrating high accuracy.
+
+<!-- TODO Include AC1 result in caption above -->
+
+(ref:agreeInter-scaption) Inter-rater agreement
+
+```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
+
+(ref:agreeIntra-scaption) Inter-rater agreement
+
+```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
+Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
+The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
+
+Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`) were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
 
-<!--- Cross check this with the actual numbers included --->
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO This needs to use the PRISMA2020 package -->
-
-```{r prisma-flow-setup, results="hide", message=FALSE}
-```
-
-(ref:prisma-flow-cap) **PRISMA Flowchart:** Overview of how records moved through the systematic review process
-
-(ref:prisma-flow-scap) PRISMA Flowchart
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-Following de-duplication, the titles and abstracts of 16109 records were assessed for eligibility.
-387 were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig)
+Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
+
+&nbsp;
 
@@
 
-Include here:
-
--   PRISMA Flowchart (use PRISMA2020 from GitHub - depending on level of involvement, could refer to the Appendix here too.)
-
--   Summary of types of study
-
--   Summary of locations
-
--   Summary of diagnostic criteria used
-
--   Summary of risk of bias
-
--   Long table, horizontally. Newer version of flextable (GH) allows for PDF output
+Table \@ref(tab:studyCharacteristics-table) shows the characteristics
+
+&nbsp;
+
+\blandscape{}
+
+<!----------------------------------------------------------------------------->
+(ref:studyCharacteristics-caption) studyCharacteristics
+
+(ref:studyCharacteristics-scaption) studyCharacteristics
+
+```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+\elandscape{}
+
+As shown in
+
+<!--- TODO Figures and tables to include here:
+
+-   PRISMA Flowchart (done)
+
+-   Summary of types of study (half done)
+
+-   Summary of locations (half done)
+
+-   Summary of diagnostic criteria used (done)
+
+-   Summary of risk of bias (not done)
+
+--->
+
+<!----------------------------------------------------------------------------->
+
+```{r cohortLocationsSetup, include = FALSE}
+
+```
+
+(ref:cohortLocations-cap) Geographical distribution of study cohorts
+
+(ref:cohortLocations-scap) Geographical distribution of study cohorts
+
+```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Many of the included studies were conducted in European countries (Figure \@ref(fig:cohortLocations).
 
@@
 There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
-For vascular dementia, few studies exmined this outcome, primarily because of the absence (until recently) of
+For vascular dementia, few studies examined this outcome, primarily because of the absence (until recently) of
+
+<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
 
@@
 
+<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
+
 In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
 
-### Converting risk ratios to odds ratios
-
-Include formulae and informed assumptions
-
-### Hazard ratios vs risk/odds ratios
-
-Not interchangeable in the context of systematic review.
-If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
-
-Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-
-The likely effect of this is that the overall effect measures are biased towards . . . . ?
-
-Can you predict the direction of effect from a
-
-Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
-
-<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
-
-Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Meta-analysis of statin use and hypercholesteroleamia
+
+Straight-forward random effects meta-analysis of binary exposures
+
+```{r primaryFigures, include = FALSE}
+
+```
+
+<!----------------------------------------------------------------------------->
+(ref:fpStatins-cap) __Forest plot showing effect of statins:__
+
+(ref:fpStatins-scap) Forest plot showing effect of statins
+
+```{r fpStatins, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpStatins-cap)', out.width='100%', fig.scap='(ref:fpStatins-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Dose response meta-analysis of lipid levels
+
+<!-- TODO Cite excluded studies and list exclusion reasons  -->
+
+Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls be
+
+<!-- TODO Include image -->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Sources of heterogeneity
@@
 Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
+
+Important here to examine effect of risk of bias (due to immortal time in observational studies).
+
+Also important to examine the effect of:
+
+* age at baseline
+* sex (percentage)
+* education
+* baseline cognitive scores (how to group)
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+Many studies did not report the codelists used to run the analysis,
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Triangualtion across evidence sources
+
+<!-- TODO Have a look at this - potentially move to triangulation chapter -->
 
@@
 
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), we test test
-
-### Added evidental value of including preprints {}
-
-<!-- Will to get actual numbers for this section -->
+Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Added evidental value of including preprints {sys-rev-including-preprints}
+
+<!-- TODO Will have to get actual numbers for this section -->
 
@@
 
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] __[ALSO CITE WILKINSON AND MCGUINNESS HERE]__.
+Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
 
@@
 
-### Searching for/including Mendelian randomisation studies
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, we identified at least one Mendelian randomisation studi [@larsson2017b]
-
-Is it a big issue that the studies have the same underlying datasets? <!--- see discussion from Matt Lee thesis, in email --->
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Summary of findings
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Previous reviews
+
+<!-- TODO Not sure this is the best place for this -->
+
+**Will need to include something in the methods section on this**
+
+As part of this analysis, Iexamined the overlap between different published reviews on this topic.
+
+Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
+
+<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
+
+An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
+
+Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
+So for example, XXXX records were captured both by the XXXX review and the XXXX review.
+
+Where the matrix has just a single point highlighted, this shows the records unique to that review.
+
+The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
+
+Our review is presented as the last point on this plot, and captured XXXX records
+
+The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
+The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
+
+<!--- Take a stand here! --->
+
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
+While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
+While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
+
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+
+Does it also cause issues in terms of self-report?
+
+<!-- TODO This section will be informed by the review published as a preprint -->
+
+Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
+
+**The duplication of work across reviews (including, ironically, by this review) is substantial.
+In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
+However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
+
+__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
+
+<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
+
+In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
+In these studies, the unit of analysis are systematic reviews rather than the
+
+However, a comparative analysis between indicates
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
 ### Inclusion of preprints
 
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis sought to syntheze evidence across different publication statuses, predominantly preprinted.
-Using the tool described in Chapter \@ref(), two preprint serves related to health and biomedical sciences were search as part of this review.
-
-The added evidental value of including these preprints was highlighted in Section
+As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses, predominantly preprinted vs published.
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
+
+The added evidential value of including these preprints was highlighted in Section \ref()
 
 On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
-While this provides some additional evidence that the quality of the research desribed by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavaialble at the time the search was conducted.
+While this provides some additional evidence that the quality of the research described by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavailable at the time the search was conducted.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
+As evidenced by the issues involved in obtaining
+
+Building in part on the research, I co-wrote an guidance piece for pre
+
+Similarly, a substanital amount of time and effort has gone into making the data obtained by this review openly available to
+
 <!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->
@@
 
-### Original contribution to research
-
-I believe there are three aspects where this review is distinct from those reviews already available in the published literature (as identified by __[CITATION NEEDED]__):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018b; @yang2020; @muangpaisan2010; @poly2020b] the overlap between the list of studies included in each is not 100%.
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Strenghts and limitations
+
+I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
+
+-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+
 -   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
@@
 This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
+
 -   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
@@
 
-### Comparison with other reviews
-
-Of note, as part of the review, we identified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- Will hopefully be able to cite MSc review here to give details of other reviews -->
+- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
+This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
+IN addition this review was used to pilot an upcoming risk of bias tool
+
+&nbsp;
+
+#### Limitations
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 
@@
 
-Recent updates, such as a guide to reading and interpreting.
+Recent updates, such as a guide to reading and interpreting Mendelian .
+
 However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
 
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that we may be double counting participants - for
+Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants
+
+Double-counting of other -
 
@@
 
-### Strenghts and limitations
-
-Potentially missing other Mendelian randomisation studies, as we identified some through our snowball searching that were not captured by the search strategy.
-An example is Larsson et al.
-2017[@larsson2017a], where the study examined the association between lipid fractions
-
-Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the
-
-<!--- Findings from this chapter are used throughout the later chapters of this thesis.
+In short, given the recent developments in the production of studies and results from Mendelian randomisation
+
+This is particularly relevant to missing evidence, as new methods in MR studies allow for the anlysis of many exposures/outcomes concurrently.
+In this scenario, missing evidence is likely to be an issue as onyl those of particular interest to the authors/those reaching statistical significance will be reported in the paper
+
+This is highlighted by the identification of studies relevant to the review though coincidental reading and citation searhcing, that were not identified by the search as they reported many results and only the statistically significant ones were included in searchable fields
+
+This is particularly troubling given the comprehensiveness of the search (~17,000 records screened).
+In retrospect, a mitigating approach may have been to have an additional search for topics related to risk factors, dementia and MR studies, and screened t
+
+<!-- TODO Best option probably to highlight that while these studies were included, it was not easy given a lack of resources for MR studies -->
+
+As a form of analysis that lends itself to multiple comparison, there is a strong
+
+Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
+[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
+
+The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
+Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
+This may bias reviews as the analysising multiple risk factors at a time becomes more common.
+
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's"),
+
+<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
+
+Is it a big issue that the studies have the same underlying datasets? <!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
+
+Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
+However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Strengths and limitations
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+#### Inclusion of preprints
+
+Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
+they would not have been captured by the search for published papers)
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Use in other chapters
+
+<!--- IDEA Findings from this chapter are used throughout the later chapters of this thesis.
 In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.
@@
 
-Test
+Findings from this review are used though out the subsequent chapters.
+
+For example,
+
+## Conclusions
+
+In this chapter I have
+
+This work built on the tool introduced in the preceeding chapter, and the results from the systematic review are used in further chapters.
+
+In Chapter \@ref(cprd-analysis-heading), 
+A summary of the evidence guided the
+
+In Chapter \@ref(ipd-heading),
+
+<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of -->
+
+A
+
+\newpage
 
@@
 
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(hold) in the Introductory Chapter).
+<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
+
+As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
 
 To explore whether any observed effect for the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
+
+<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
 
@@
 
+## Lay Summary
+
+## Introduction
+
+Is there a good way to visualise input of cohorts into an IPD analysis?
+
 ## Methods
+
+As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man
+
+Talk about how different covariates were managed across cohorts,
+
+Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-## Risk of bias assessment
+Several DPUK cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
+
+See
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Risk of bias assessment
 
@@
 
-## Data cleaning
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Data cleaning
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responsed if at all.
+Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responded if at all.
 Will also need to comment on the additional tactics used.
 
-This is likely due to my junior position as a early a
+This is likely due to my junior position as a early career research combined with the impact
 
 Range of reasons why data is not readily available.
+Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
+primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
 
@@
 
-## Discussion
-
-Describe your experience of trying to access the DPUK - while a great resources, furstrating at times.
+### Reflections on data access
+
+Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
+
+### Study within a review
+
+In future, it could have been worth running a "study within a review", such as that used to examine whe
+
+https://bmjopen.bmj.com/content/9/1/e025273
 
@@
 
+<!----------------------------------------------------------------------------->
 ## Triangulation across exisiting evidence and evidence produced in this thesis
 
+### Overview of triangulation {#triangulation-overview}
+
 Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Discussion of E-values
@@
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Future work
 
+&nbsp;
+<!----------------------------------------------------------------------------->
+
 ## Overall conclusions
 
-<!--chapter:end:97-Discussion.Rmd-->
+<!--chapter:end:07-Discussion.Rmd-->
 
@@
 
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+knitr::read_chunk(here::here("R/appendix.R"))
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
+<!----------------------------------------------------------------------------->
 # By Chapter {#chapter-appendix-heading}
 
-## Chapter \@ref(intro-heading) {#appendix-into}
-
+<!----------------------------------------------------------------------------->
+## Chapter \@ref(background-heading) {#appendix-into}
+
+<!----------------------------------------------------------------------------->
 ### Publications beyond the scope of this thesis {#appendix-publications}
@@
 
-  * McGuinness & Sheppard. Comparison of pairwise
-
   * PRISMA main paper
@@
 
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
+<!----------------------------------------------------------------------------->
+
+## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
+<!----------------------------------------------------------------------------->
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:searchHits-caption) Overview of the full Medline search strategy.
+
+(ref:searchHits-scaption) searchHits
+
+```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+### Web of Science Databases Searched {#appendix-wos-databases}
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:wosDatabases-caption) Summary of Web of Science databases searched.
+
+(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
+
+```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
+
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
 ### Code to search preprints {#appendix-medrxivr-code}
 
-<!-- Double check this is the final code used -->
+<!-- TODO Double check this is the final code used -->
 
@@
 
-test <- mx_search(bx_data, query)
-
-test2 <- mx_search(mx_data, query)
+bx_results <- mx_search(bx_data, query)
+
+mx_results <- mx_search(mx_data, query)
 
@@
 
+<!----------------------------------------------------------------------------->
 ### MR risk of bias tool {#appendix-mr-rob}
 
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
-
+<!----------------------------------------------------------------------------->
+(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
+
+(ref:mrTool-scaption) Mendelian randomisation risk-of-bias assessment tool
+
+```{r mrTool-table, message=FALSE, results="asis", echo = FALSE}
+
+mrTool_table <- read.csv(here::here("data/sys-rev/mrRobTool.csv")) %>%
+  select(1:5) %>%
+  rename("Bias domain" = Bias.domain)
+
+if(doc_type == "docx") {
+  knitr::kable(mrTool_table, caption = "(ref:mrTool-caption)")
+} else{
+  knitr::kable(
+    mrTool_table,
+    format = "latex",
+    caption = "(ref:mrTool-caption)",
+    caption.short = "(ref:mrTool-scaption)",
+    longtable = TRUE,
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    column_spec(column = 1:5, width = paste0(32/5,"em")) %>%
+    row_spec(2:nrow(mrTool_table)-1, hline_after = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position","repeat_header"))
+}
+
+```
+
+<!----------------------------------------------------------------------------->
 ## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-
+<!----------------------------------------------------------------------------->
 ### Amendments to protocol {#appendix-cprd-amendments}
 
+<!----------------------------------------------------------------------------->
 ### Code lists
 
+## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
+<!----------------------------------------------------------------------------->
+### Section 1
+
+<!----------------------------------------------------------------------------->
+### Section 2
+
+<!----------------------------------------------------------------------------->
 ## Chapter \@ref(discussion-heading)
 
+<!----------------------------------------------------------------------------->
 ### Catalogue of failures
@@
 
+## Creating
+
+## Copies of papers arising from this thesis
+
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
+
 <!--chapter:end:front-and-back-matter/99-appendices.Rmd-->

### 2021-09-13 tmp.Rmd
End of day:

--- 2021-04-08 tmp.Rmd
@@
-Chapter 1. Introduction
-1.1. Summary
-This chapter presents the problem that the research conducted in this thesis seeks to
-address and an outline of the main output of this thesis: new evidence concerning
-repurposing antihypertensives for dementia prevention using genetic and non-genetic
-instrumental variable analyses. This chapter then introduces three issues that arose and
-have been addressed during the conduct of this research. They are: how to calculate
-power for instrumental variable analyses in pharmacoepidemiology; how to use
-Mendelian randomization to predict drug repurposing opportunities; and what factors
-have effected prescribing of existing dementia drugs. This chapter concludes with the
-aims and objectives of this thesis, a summary of its organization and a list of the
-associated outputs.
-1.2. Statement of the problem
-There is a substantial unmet clinical need for treatments for dementia where significant
-benefits to patients, society and the public purse can be gained. Despite this, some drug
-companies have recently withdrawn from this therapy area due to failed and costly efforts
-to find new treatments. (1,2) Drug repurposing, the identification of properties in existing
-or abandoned compounds for other clinical conditions, offers significant advantages over
-traditional drug discovery approaches. This includes immediate access to human safety
-data from the original clinical development work, which can accelerate testing in clinical
-trials, saving both time and money. (3–5)
-Many antihypertensive medications have been proposed as drug repurposing candidates
-for the prevention of dementia. In part, because of research to better understand several
-reports of observed associations between midlife hypertension and later-life risk of
-Alzheimer’s disease and vascular dementia. (5–8) There is also increasing recognition
-that one of the earliest pathological events in the development of Alzheimer’s disease is
-vascular dysregulation. (9) As well as suggestions that some antihypertensives,
-specifically those that block angiotensin receptor and calcium channel signalling, may
-have other neurological benefits. (9–11)
-2
-Several observational studies have investigated repurposing antihypertensives for
-dementia prevention. (12–19) However, these studies have typically used case-control
-designs with logistic regression and cohort designs with survival analysis, both of which
-are observational study designs that may be subject to unmeasured or residual
-confounding and reverse causation. Specific concerns of observational studies are
-confounding by indication, where the reasons that a patient receives a treatment relate to
-the reasons that the patient is at an increased risk of the outcome; and healthy adherer
-bias, where patients initiating or adhering to a drug for prevention of a condition are
-more likely to be healthy. There is also potential for reverse causation due to preclinical
-or early stages of the disease, which could lead to more frequent contacts with general
-practitioners (GPs) and lead to raised blood pressure being more likely to be detected.
-This, in turn, could lead to the prescription of an antihypertensive drug in advance of
-dementia being formally diagnosed. Consequently, current evidence concerning
-repurposing antihypertensives for dementia prevention is considered inconclusive.
-1.3. New evidence concerning repurposing antihypertensives for dementia prevention
-using instrumental variable analysis
-Instrumental variable analysis, which estimates the causal effect of an exposure on an
-outcome by using a third variable (the instrument), can be robust to confounding and
-reverse causation if certain assumptions are met. That is:
-  IV1. The instrument must associate with the exposure
-IV2. The instrument must only affect the outcome through the exposure
-IV3. The instrument and the outcome must have no common causes
-These assumptions can be represented on a directed acyclic graph, as shown in Figure
-1.1. Instrumental variable analysis, with other sources of evidence, can be used in a
-triangulation framework to obtain a reliable answer concerning the potential repurposing
-of antihypertensives for dementia prevention. (20) This thesis presents two forms of
-instrumental variable analysis to provide new evidence concerning this hypothesis. The
-first uses physicians’ prescribing preference as a non-genetic instrument in electronic
-health record data obtained from the United Kingdom (UK) Clinical Practice Research
-Datalink (CPRD). The second uses single nucleotide polymorphisms (SNPs) i.e.
-differences in the deoxyribonucleic acid (DNA) nucleotides between individuals, which
-have been selected to mimic the biological function of the protein targets of 
-3
-antihypertensive drug classes, as a genetic instrument in an approach more commonly
-known as Mendelian randomization. The results of both these instrumental variable
-analyses have been made available via the following references. (21,22)
-1.4. Calculating power for instrumental variable analysis in pharmacoepidemiology
-Instrumental variable analysis is an increasingly popular method in the field of
-pharmacoepidemiology. (23–28) However, the power calculators that were available for
-studies using instrumental variable analysis at the start of my PhD – such as Mendelian
-randomisation power calculators – did not allow for the structure of research questions
-using non-genetic instruments (for example, physicians’ prescribing preference) in this
-field. (29,30) This is because analysis using non-genetic instruments in pharmacoepidemiology will typically have stronger instruments and so can detect smaller causal
-effects. Consequently, there was a need for dedicated power calculators for these type of
-research questions in pharmacoepidemiology. In this thesis, I investigate how to conduct
-Figure 1.1: A directed acyclic graph illustrating the basic instrumental variable analysis model.
-Directed acyclic graphs are a visual representation of a model, which represent variables by ‘nodes’
-and the relationships between them by ‘directed edges’. (68) The graphs are defined as acyclic
-because edges cannot form ‘cycles’, whereby the edges all act in the same direction. This prevents a
-variable from being both a cause and a consequence of itself. Directed acyclic graphs are a common
-tool in epidemiology and, more specifically, causal inference when edges are given a causal
-interpretation, as they allow researchers to depict their model and its assumptions using a common
-graphing scheme. (69)
-4
-power calculations for pharmacoepidemiological studies, which use a single binary
-instrument to analyse the causal effect of a binary exposure on a continuous outcome. I
-also provide an online calculator, as well as packages in both R and Stata, for the
-implementation of the formula by others (https://github.com/venexia/PharmIV). This
-work has been published in the International Journal of Epidemiology. (31)
-1.5. Using Mendelian randomization to predict drug repurposing opportunities
-Identification of drug repurposing opportunities can maximize the benefit of a drug.
-However, as highlighted before, the more traditional observational research methods
-used to investigate these opportunities are subject to several biases. These include
-confounding by indication, reverse causality, and missing data. In this thesis, I propose
-Mendelian randomization as a novel approach that can be used for the prediction of drug
-repurposing opportunities. Mendelian randomization addresses some of the limitations
-associated with the existing methods in this field. Furthermore, it can be applied either
-pre- or post-approval of the drug and could therefore prevent the potentially harmful
-exposure of patients in clinical trials and beyond. This thesis includes discussion of
-examples from the literature that have used Mendelian randomization to predict drug
-repurposing opportunities and covers the strengths and limitations associated with using
-this method for this purpose. There was relatively little discussion focussed on using
-Mendelian randomization for drug repurposing when I commenced my PhD and I have
-since published on this topic. (32)
-1.6. Factors effecting existing dementia drug prescribing
-Drugs for dementia have been available in England from 1997. However, since their
-launch, there have been several changes to national guidelines and initiatives that may
-have influenced prescribing. These include changes in National Institute for Health and
-Care Excellence (NICE) guidance; several government dementia strategies; the addition
-of dementia to the Quality and Outcomes Framework (QOF); and the expiry of drug
-patents. Despite this, little research had been conducted prior to my PhD into the effect
-of these events on prescribing. (33,34) In this thesis, I investigate prescribing trends in
-England since the launch of these drugs up to 1st January 2016 using data from the
-CPRD to address this gap in the literature. The key motivation for this analysis was to 
-5
-identify factors that have affected prescriptions of existing treatments that may also
-influence repurposed drug candidates in the future. However, the results from this
-analysis could also be used to identify breaks in the prescription of these drugs that could
-be exploited as natural experiments for progression studies. For example, if these drugs
-were not prescribed when the NICE guidelines stopped recommending their use between
-2006 and 2011, the progression of people diagnosed during this time who did not access
-the drugs could be compared with the progression of people diagnosed before and after
-this time who did have access to the drugs. The results presented in this chapter have
-been published in Alzheimer’s Research & Therapy. (35)
-1.7. Aims and objectives
-The objective of this thesis was to use instrumental variable analysis methods, in existing
-data sources, to triangulate evidence for repurposing antihypertensive drugs for the
-prevention of dementia.
-The specific aims were as follows:
-  1. Develop a power calculator for non-genetic instrumental variable analysis studies
-in the context of pharmacoepidemiology.
-2. Describe the use of genetic instrumental variable analysis, namely Mendelian
-randomization, for predicting drug repurposing opportunities.
-3. Examine the impact of regulatory guidance and patent expiry on dementia drug
-prescribing.
-4. Investigate whether antihypertensive drugs have a causal effect on incident
-dementia using instrumental variable analysis with electronic health record data.
-5. Investigate whether antihypertensive drugs have a causal effect on incident
-dementia using instrumental variable analysis with genetic data.
-1.8. Organization of this thesis
-Chapter 2 provides the background necessary for the rest of this thesis through the
-introduction of dementia, the concept of drug repurposing, and discussion of the existing
-evidence regarding antihypertensive drugs for dementia prevention. It also covers the 
-6
-strengths and limitations of observational pharmacoepidemiology and explains why it
-might be preferable over ‘gold standard’ randomized controlled trials for some
-hypotheses. Chapter 3 describes instrumental variable analysis, the method utilized
-throughout this thesis, and documents the development of a power calculator for this
-method in the context of pharmacoepidemiology (Aim 1). Chapter 4 introduces the idea
-of using Mendelian randomization, a form of instrumental variable analysis that uses
-genetic variants as instruments, for drug repurposing and covers the strengths and
-limitations of this approach (Aim 2). Chapter 5 describes the CPRD and my use of this
-data source. Chapter 6 covers the current treatments available for dementia and factors
-affecting their prescription in England based on data from the CPRD (Aim 3). Chapter 7
-presents an assessment of the effects of antihypertensive drugs on dementia prevention
-using instrumental variable analysis with data from the CPRD (Aim 4); while Chapter 8
-presents an assessment of the effects of antihypertensive drugs on dementia prevention
-using instrumental variable analysis with genetic data (Aim 5). The thesis concludes with
-a discussion in Chapter 9 that brings together all the elements of this thesis and discusses
-their implications.
-1.9. Outputs from this thesis
-1.9.1. Contributions to scientific literature
-Contributions to scientific literature arising from this thesis are detailed below and
-provided in Appendix A.
-The protocol for the observational work using CPRD data to investigate drug
-repurposing opportunities is published in the BMJ Open. (36) Its contents are referenced
-in several places throughout this thesis, particularly Chapter 5:
-  Walker VM, Davies NM, Jones T, Kehoe PG, Martin RM. Can commonly prescribed
-drugs be repurposed for the prevention or treatment of Alzheimer’s and other
-neurodegenerative diseases? Protocol for an observational cohort study in the UK
-Clinical Practice Research Datalink. BMJ Open. 2016 Dec 1;6(12):e012044.
-7
-The power calculator for instrumental variable analysis in pharmacoepidemiology,
-described in Chapter 3, is published in the International Journal of Epidemiology (31):
-  Walker VM, Davies NM, Windmeijer F, Burgess S, Martin RM. Power calculator for
-instrumental variable analysis in pharmacoepidemiology. Int J Epidemiol. 2017 Oct
-1;46(5):1627–32.
-Also published in the International Journal of Epidemiology is an article discussing
-Mendelian randomization as a novel approach for the prediction of adverse drug events
-and drug repurposing opportunities (32), which formed the basis of Chapter 4:
-  Walker VM, Davey Smith G, Davies NM, Martin RM. Mendelian randomization: a
-novel approach for the prediction of adverse drug events and drug repurposing
-opportunities. Int J Epidemiol. 2017 Dec 1;46(6):2078–89.
-The trend analysis examining prescribing practice for drugs for dementia in the CPRD,
-presented in Chapter 6, is available from Alzheimer’s Research & Therapy (35):
-  Walker VM, Davies NM, Kehoe PG, Martin RM. What is the impact of regulatory
-guidance and expiry of drug patents on dementia drug prescriptions in England? A trend
-analysis in the Clinical Practice Research Datalink. Alzheimer’s Research & Therapy.
-2018 May 29;10:51.
-The assessment of antihypertensives for dementia prevention using electronic health
-record data, reported in Chapter 7, is currently under peer review and available from
-bioRxiv (21):
-  Walker VM, Davies NM, Martin RM, Kehoe PG. Comparison of antihypertensive drug
-classes for dementia prevention. bioRxiv. 2019 Jan 12;517482.
-The assessment of antihypertensives for dementia prevention using genetic data, reported
-in Chapter 8, has been made available as an advance article from the International
-Journal of Epidemiology (22):
-  8
-Walker VM, Kehoe PG, Martin RM, Davies NM. Repurposing antihypertensive drugs
-for the prevention of Alzheimer’s disease: a Mendelian Randomization study. Int J
-Epidemiol. 2019 Jul 4; Advance article.
-1.9.2. Contributions to scientific meetings
-I presented the paper “Power calculator for instrumental variable analysis in
-pharmacoepidemiology”, described in Chapter 3, at the UK Administrative Data
-Research Network Annual Research Conference 2017 in Edinburgh, UK.
-I presented the paper “Mendelian randomization: a novel approach for the prediction of
-adverse drug events and drug repurposing opportunities”, which formed the basis of
-Chapter 4, at the University of Bristol Population Health Symposium 2016 in Bristol, UK
-and at the International Society for Pharmacoepidemiology mid-year meeting 2018 in
-Toronto, Canada.
-I presented posters, based on the paper “What is the impact of regulatory guidance and
-expiry of drug patents on dementia drug prescriptions in England?” detailed in Chapter
-6, at the Alzheimer’s Research UK Research Conference 2016 in Aberdeen, UK and at
-the University of Bristol brain research showcase and networking day 2018 in Bristol,
-UK.
-I presented “Can treatments for hypertension be repurposed for the treatment of
-dementia?” at the Society of Epidemiologic Research annual conference 2018 in
-Baltimore, United States of America (USA); at the European Congress of Epidemiology
-2018 in Lyon, France and the International Society for Pharmacoepidemiology annual
-meeting 2018 in Prague, Czech Republic. These presentations combined results from
-Chapters 7 and 8.
+---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
+output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
+  bookdown::html_document2: default
+documentclass: book
+---
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/03-Code-Systematic-Review.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
+```{r primaryFigure1, include = FALSE}
+```
+
+<!-- Straight-forward random effects meta-analysis of binary exposures, using study defined measures of each. -->
+
+In RCTs statin use was not associated
+
+<!----------------------------------------------------------------------------->
+(ref:statinsRCT-cap) __Random effects meta-analysis of statins on all-cause dementia:__
+
+(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r statinsRCT, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/forest_statins_rct.png"))
+```

### 2021-09-13 R/03-Code-Systematic-Review.R

@@ -27,24 +27,33 @@ searchOverview_table <- read.csv(here::here("data","sys-rev","searchOverview.csv
       )
   }
 
+
+
 # ---- prisma-flow-setup
 
-prisma_df <- read.csv(here::here("data/sys-rev/PRISMAflow.csv"), stringsAsFactors = F)
+prisma_df <-
+  read.csv(here::here("data/sys-rev/PRISMAflow.csv"),
+           stringsAsFactors = F)
 
-prisma_full <- read.csv(system.file("extdata", "PRISMA.csv", package= "PRISMA2020"), stringsAsFactors = F)[,c(1:4,6:7)] %>%
+prisma_full <-
+  read.csv(system.file("extdata", "PRISMA.csv", package = "PRISMA2020"),
+           stringsAsFactors = F)[, c(1:4, 6:7)] %>%
   dplyr::left_join(prisma_df, by = "description") %>%
   PRISMA2020::read_PRISMAdata()
 
 attach(prisma_full)
-PRISMA2020::PRISMA_save(plotobj = PRISMA2020::PRISMA_flowdiagram(
-  prisma_full,
-  interactive = F,
-  previous = F,
-  other = T,
-  fontsize = 12
-),
-"figures/sys-rev/prismaflow.png")
+PRISMA2020::PRISMA_save(
+  plotobj = PRISMA2020::PRISMA_flowdiagram(
+    prisma_full,
+    interactive = F,
+    previous = F,
+    other = T,
+    fontsize = 12
+  ),
+  "figures/sys-rev/prismaflow.png"
+)
 detach("prisma_full")
+
 
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
@@ -170,11 +179,19 @@ if(doc_type == "docx") {
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- studyCharacteristics-table
 
-toc_df <- rio::import("data/sys-rev/Book1.xlsx",which = 1) %>%
+toc_df <- rio::import("data/sys-rev/data_extraction_main.xlsx",which = 1) %>%
   janitor::clean_names() %>%
-  select(study_id, author, year, type, location, data_source)
+  filter(is.na(exclude)) %>%
[…]

### 2021-09-13 R/05-Code-IPD-Analysis.R

@@ -1,0 +1,32 @@
+tmp <-
+  read.csv(
+    "data/ipd/ipd_age_sex.csv",
+    strip.white = T,
+    stringsAsFactors = F,
+    header = T
+  ) %>%
+  filter(cohort != "MEMENTO") %>%
+  nest_by(lipid)
+
+library(metafor)
+
+forest_save <- function(data, lipid) {
+  png(paste0("figures/ipd/", lipid, ".png"),
+      width = 700,
+      height = 220)
+  
+  # metafor::rma(yi = estimate, vi = se, data = data, slab = cohort, method = "DL", measure = "OR") %>%
+  #   forest(showweights = T, refline = 1, annotate = T, header = c(lipid,"Estimate [95%CI]"), transf=exp)
+  
+  meta::metagen(
+    TE = estimate,
+    seTE = se,
+    studlab = cohort,
+    data = data
+  ) %>% meta::forest(overall = FALSE,
+                     xlab = paste("LogOR per 1-SD change in", lipid))
+  
+  dev.off()
+}
+
+purrr::map2(.x = tmp$data, .y = tmp$lipid, ~ forest_save(.x, .y))

### 2021-09-13 R/helper.R

@@ -1,4 +1,10 @@
 library(magrittr)
+library(dplyr)
+library(ggplot2)
+library(patchwork)
+
+conflicted::conflict_prefer("filter", "dplyr")
+conflicted::conflict_prefer("last", "data.table")
 
 # Register fonts with R
 library(grDevices)
@@ -11,12 +17,12 @@ source(here::here("R/forester.R"))
 
 
 # Clean output of metafor using sensible defaults
-broom_ma <- function(metafor_obj) {
+broom_ma <- function(metafor_obj, exp = TRUE) {
   return(broom::tidy(
     metafor_obj,
     conf.int = TRUE,
     include_studies = TRUE,
-    exponentiate = TRUE
+    exponentiate = exp
   ) %>%
     rename("Study" = term) %>%
     mutate(Study = ifelse(Study == "overall", "Overall",Study),
@@ -488,4 +494,57 @@ read_excel_allsheets <- function(filename, tibble = FALSE, col_names = FALSE) {
   if(!tibble) x <- lapply(x, as.data.frame)
   names(x) <- sheets
   x
+}
+
+
+combine_age <- function(age, group_size) {
+  
+  age <- stringr::str_remove_all(age, " ")
+  age <- stringr::str_remove_all(group_size, " ")
+  
+  # Find parentheses
+  re <- "\\(([^()]+)\\)"
+  
+  # Extract sd
+  sd <- c(stringr::str_extract_all(age,re, simplify = T))
+  sd <- as.numeric(substring(sd, 2, nchar(sd)-1))
+  
+  mean <- c(stringr::str_split(age,"\\|", simplify = T))
+  mean <- as.numeric(stringr::str_remove_all(mean,re))
+  
+  n <- as.numeric(stringr::str_split(group_size,"\\|", simplify = T))
+  
+  t <- utilities::sample.decomp(
+    n = n,
+    sample.mean = mean,
+    sample.sd = sd,
+    include.sd = TRUE
+  ) %>%
+    slice_tail() %>%
+    tidy_nums()
+  
+  return(paste0(t$sample.mean," (",t$sample.sd,")"))
+  
+}
+
+
+combine_female <- function(female, group_size) {
+  
+  age <- stringr::str_remove_all(female, " ")
+  age <- stringr::str_remove_all(group_size, " ")
+  
+  percentages <- as.numeric(stringr::str_split(female,"\\|", simplify = T))
+  
[…]

### 2021-09-15 03-Chp-Systematic-Review.Rmd
Still copying data across to new format

@@
 <!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI?
---> For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
+-->
+
+__Bit on inclusion of EHR, where it is unclear how dementia diagnosed.__
+
+<!-- TODO Any study using EHR - go back and extract codelists -->
+
+For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
 an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
@@
 
+##
+
+\begin{equation}
+N = N_1 + N_2
+  (\#eq:combiningGroups1)
+\end{equation}
+
 #### Harmonisation of cholesterol measures
@@
 
+<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
+
+Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
+
 &nbsp;
@@
 ## Discussion
+
+<!-- TODO Check inclusion of Rockwood 2002:  -->
 
@@
 
-Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
-This point is important given one of the core assumptions of
-
-<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
+One of the strenghts of this review is it's inclusion of MR studies as a source of evidence.
 
@@
 Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substanital benefit.
+Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.
 
 <!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
+
+Talk about problem with studies sharing underlying datasets in two sample MR frameworks - c.f.
+EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, MR analysis can be multiple studies using the exact same summary statistics from the same cohorts
+
+Introduce assumptions underlying MR (with image).
+Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
+Note the region must be quite wide - talk about controversy surrounding Benn paper
+
+Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
+This point is important given one of the core assumptions of
+
+<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
+
+MR are limited by the need for SNP to be present in both datasets (for TSMR).
+
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of exisitng GWASes to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
+-->
 

### 2021-09-15 R/helper.R

@@ -548,3 +548,25 @@ combine_female <- function(female, group_size) {
   return(t$percentage)
   
 }
+
+
+
+get_confidence_from_p<- function(est, p) {
+  
+  # From https://www.bmj.com/content/343/bmj.d2090
+  
+  z = -0.862 + sqrt(0.743 - 2.404 * log(p))
+  
+  log_est = log(est)
+  
+  log_SE = abs(log_est / z)
+  
+  list(
+    lower = exp(log_est - 1.96 * log_SE),
+    upper = exp(log_est + 1.96 * log_SE)
+  ) %>%
+    tidy_nums() %>%
+  return()
+  
+
+}

### 2021-09-20 tmp.Rmd
Working again - thankfully!

@@
 ```
-
-```{r primaryFigure1, include = FALSE}
-```
-
-<!-- Straight-forward random effects meta-analysis of binary exposures, using study defined measures of each. -->
-
-In RCTs statin use was not associated
-
-<!----------------------------------------------------------------------------->
-(ref:statinsRCT-cap) __Random effects meta-analysis of statins on all-cause dementia:__
-
-(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
-
-```{r statinsRCT, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forest_statins_rct.png"))
-```

### 2021-09-20 R/helper.R

@@ -2,7 +2,9 @@ library(magrittr)
 library(dplyr)
 library(ggplot2)
 library(patchwork)
+library(metafor)
 
+conflicted::conflict_prefer("summarize", "dplyr")
 conflicted::conflict_prefer("filter", "dplyr")
 conflicted::conflict_prefer("last", "data.table")
 
@@ -500,7 +502,7 @@ read_excel_allsheets <- function(filename, tibble = FALSE, col_names = FALSE) {
 combine_age <- function(age, group_size) {
   
   age <- stringr::str_remove_all(age, " ")
-  age <- stringr::str_remove_all(group_size, " ")
+  group_size <- stringr::str_remove_all(group_size, " ")
   
   # Find parentheses
   re <- "\\(([^()]+)\\)"
@@ -569,4 +571,55 @@ get_confidence_from_p<- function(est, p) {
   return()
   
 
+}
+
+save_fp <- function(data) {
+  
+  # Don't perform meta-analysis if only one result
+  
+  if (nrow(data)==1) {
+    return()
+  }
+  
+  fp <- paste0("fp_", data$exposure_category[1],"_",data$exposure[1],"_", data$outcome[1],".png")
+  
+  png(here::here("figures","sys-rev",fp), height = 300, width = 800)
+  
+  metafor::rma(data = data,
+               yi = point,
+               sei = SE,
+               slab = paste(study_id, author,year)) %>%
+    metafor::forest(transf = exp,
+                    refline = 1,
+                    xlab = "Hazard ratio",
+                    header = "Author(s) and Year",
+                    annotate = TRUE)
+  
+  dev.off()
+}
+
+
+meta_grouped <- function(data) {
+  
+  # Don't perform meta-analysis if only one result
+  
+  t <- metafor::rma(data = data,
+               yi = point,
+               sei = SE,
+               slab = paste(study_id, author,year)) 
+  
+ 
+  details <- data.frame(stringsAsFactors = FALSE,
+                        exposure = data$exposure[1],
+                        outcome = data$outcome[1],
+                        studies = length(unique(data$study_id)),
+                        bias = data$bias[1], 
+                        I2 = t$I2
+  )
+  
+  results <- predict.rma(t,transf=exp)
+
+  return(cbind(details,results))
+  
+  
 }

### 2021-09-20 01-Chp-Background.Rmd
End of day:

@@
 
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @ansteya]
+Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
 
@@
 
-Several previous systematic review of observational studies examining the effect of lipids[@anstey] and lipid-regulating agents[@chu2018b;@poly2020c] on dementia outcomes have been performed.
+Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020c] on dementia outcomes have been performed.
 However, these reviews have several limitations.
 Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey;@poly2020c]
+Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey2015;@poly2020c]
 

### 2021-09-20 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 
-### Limitations of `medrxivr`
+### Limitations of `medrxivr` {#medrxivr-limitations}
 
@@
 
-Allowing for a two year lag, previous work has found that two-thirds of bioRxiv preprints were published in a peer-reviewed journal,[@abdill2019b] indicating that s not-insignificant number of preprints are never publishe but are accessible as preprints.
+```{r, include=FALSE}
+med_res <-
+  # Use snapshot from July 2021
+  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
+                      "*",
+                      from_date = "2019-07-01",
+                      to_date = "2019-08-01") %>%
+mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
+  group_by(pub_ind) %>%
+  count()
+
+published <- med_res$n[2]
+publication_n <- sum(med_res$n)
+publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
+```
+
+Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
+`r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
+allowing for a two-year lag between preprint posting and publication).
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
+
+<!-- TODO replicate this analysis -->
 

### 2021-09-20 03-Chp-Systematic-Review.Rmd
End of day:

@@
 <!-- TODO Extra studies to include: -->
-<!-- * Smeet et al. reference in the CPRD analysis -->
 <!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
@@
 The use of the results of this review in subsequent chapters is dicussed.
+
+<!-- TODO Search for MCI -->
 
@@
 
-Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-<!-- TODO CITATION NEEDED --> <!-- TODO do i actually want to include MCI?
--->
+Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD), National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
+<!-- TODO CITATION NEEDED -->
 
@@
 
-The use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a systematic review.<!-- TODO CITATION NEEDED --> As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
+Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
 
@@
 Many of those excluded by the filters were basic science studies, commentaries or educational articles.
-<!-- TODO CITATION NEEDED -->
 
@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Hypercholesterolemia and lipid levels
@@
 This is particularly interesting given that lipids and statins are primarily related to vascular disease.
-There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".
-<!-- TODO CITATION NEEDED --> For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.
+There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.
 
@@
 While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.
-<!-- TODO CITATION NEEDED -->
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
 
@@
 
-<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
-
-<!-- An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot.
-For example, the XXXX review includes XXXX studies.
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
--->
-
 <!----------------------------------------------------------------------------->
@@
 ### Inclusion of preprints
+
+```{r preprintGrowthSetup, include=FALSE}
+```
 
@@
 
-medRxiv grew out of the Epidemiology and Clinical Trials categories of the 
-<!-- TODO Complete above paragraph -->
-
-The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:test)) is due to the timing of the preprint searches.
+Three relevant preprints were identified
+
+medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
+The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
 The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a small number of records.
+As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
+
+Of the three identified preprints, two were subsequently published as of September 2020.
+This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
 
@@
 <!----------------------------------------------------------------------------->
-```{r preprintGrowthSetup, include=FALSE}
-```
-
 (ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.
@@
 <!----------------------------------------------------------------------------->
-<!-- TODO Include figure here showing growth of preprint database size, and cite studies detailing increasing acceptance as a valid form of evidence.  -->
+<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
 
@@
 
-One of the strenghts of this review is it's inclusion of MR studies as a source of evidence.
+One of the strengths of this review is it's inclusion of MR studies as a source of evidence.
 
@@
 
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
+<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
 
@@
 However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.
-<!-- TODO CITATION NEEDED -->
+In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
 

### 2021-09-20 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 <!----------------------------------------------------------------------------->
+
+## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
+<!----------------------------------------------------------------------------->
+
+### Code for publication rate analysis
+
+```{r, eval=FALSE}
+med_res <-
+  # Use snapshot of published status from July 2021
+  medrxivr::mx_search(
+    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
+    query = "*",
+    from_date = "2019-07-01",
+    to_date = "2019-08-01"
+  ) %>%
+  # Create indicator to show which records have been published
+  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
+  # Group by indicator variable and count
+  group_by(pub_ind) %>%
+  count()
+
+```
 
@@
 
-__NEED TO ADD DATA HERE!__
+<!-- TODO __NEED TO ADD DATA HERE!__ -->
 
@@
 
-## Copies of papers arising from this thesis
+## Copies of papers arising from this thesis {#published-papers}
 

### 2021-09-20 R/03-Code-Systematic-Review.R

@@ -195,6 +195,10 @@ toc_df <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which
          age_combo = case_when(age_combo=="74.900000000000006"~"74.9", T ~ age_combo))
 
 
+# toc_df %>%
+#   filter(is.na(exclude)) %>%
+#   distinct(study_id,.keep_all = T) %>%
+#   count()
 
 toc_df2 <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which = 2) %>%
   janitor::clean_names() %>%
@@ -277,7 +281,7 @@ if(doc_type == "docx") {
     kableExtra::group_rows(
       group_label = "MR",
       start_row = 75,
-      end_row = 79,
+      end_row = 81,
       hline_after = T,
       extra_latex_after = "\\addlinespace"
     )
@@ -493,10 +497,10 @@ rct_tri_res <- data.frame(
   predict.rma(res, transf = exp)
 )
 
-# Update with proper ROB assessments
+# TODO Update with proper ROB assessments
 dat_rob <- robvis::data_rob2[1:2,]
 dat_rob[,1] <- res$slab
-dat_rob[2,2:7] <- "No information"
+dat_rob[2,2:7] <- "Low"
 
 try(dev.off(),silent = T)
 png(here::here("figures/sys-rev/fp_statins_any_rct.png"), height = 300, width = 800)

### 2021-09-24 03-Chp-Systematic-Review.Rmd
Back to a working version

@@
 
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication of MR studies which used similar data from the Global Lipid
+
+(ref:mrDuplication-scap) Summary of duplication of MR studies
+
+```{r mrDuplicationSetup, include=FALSE}
+```
+
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
+```
+<!----------------------------------------------------------------------------->
+
 Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of exisitng GWASes to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
 -->
+
+A key example of the importance of pleiotropy in Mendelian randomisations studies is ill.
+In almost all cases, MR studies examine.
+A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
 

### 2021-09-24 forest flexi.R

@@ -1,0 +1,362 @@
+forest_strata_rob <- function(dat, dat_rob, rob_tool = "ROB2"){
+
+### calculate log risk ratios and corresponding sampling variances (and use
+### the 'slab' argument to store study labels as part of the data frame)
+
+dat_rob <- dat_rob %>%
+  mutate(Overall = factor(Overall ,levels =c("Low","Moderate","Serious","Critical"))) %>%
+  arrange(Overall)
+
+dat <- left_join(dat, dat_rob) %>%
+  arrange(Overall)
+
+dat_rob_vec <- dat_rob %>%
+  mutate(row_n = 1:n()) %>%
+  group_by(Overall) %>%
+  summarise(n=n(),max = max(row_n), min = min(row_n)) %>%
+  mutate(offset = seq(1,length(unique(.$Overall))*3,by=3)) %>%
+  
+  mutate(min = min+offset, max =max+offset, heading = max+1, stats = min-1.25) %>%
+  mutate(min = ifelse(n==1,min-1,min),
+         max = ifelse(n==1,max-1,max),
+         heading = ifelse(n==1,heading-1,heading))
+
+rows <- c()
+
+for (i in 1:nrow(dat_rob_vec)) {
+  
+  rows <-c(rows, dat_rob_vec$min[i]:dat_rob_vec$max[i])
+  
+}
+
+
+x_min = -12
+x_max = 4.6
+textpos <- c(x_min, x_max-1)
+y_max <- max(rows)+4
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# Deal with adding rob data
+
+max_domain_column <- ifelse(rob_tool == "ROB2",7,9)
+
+rob_data <-
+  cbind(dat_rob[, 1], data.frame(lapply(dat_rob[, 2:max_domain_column], robvis:::clean_data),
+                                  stringsAsFactors = F))
+
+
+x_pos <- seq(x_max, by = 0.55, length.out = max_domain_column - 2)
+
+x_overall_pos <- max(x_pos) + 1
+
+# Convenience vector, specifying x-axis positions for all risk of bias columns
+header_row <- c(x_pos, x_overall_pos)
+
+legend_pos <- x_max+(max(header_row)-min(header_row))/2
+
+# New right-hand x-axis limit
[…]

### 2021-09-24 test-forest-strata.R

@@ -1,0 +1,27 @@
+library(metafor)
+
+### copy BCG vaccine meta-analysis data into 'dat'
+dat <- dat.bcg[6:12,]
+
+dat_rob <- robvis::data_robins[3:9,]
+
+
+dat <-
+  escalc(
+    measure = "RR",
+    ai = tpos,
+    bi = tneg,
+    ci = cpos,
+    di = cneg,
+    data = dat,
+    slab = paste(author, year, sep = ", ")
+  )
+
+dat$id <- 1:nrow(dat)
+dat_rob$id <- 1:nrow(dat_rob)
+
+forest_strata_rob(dat,dat_rob)
+
+png("test.png", width = 800, height = 500)
+forest_strata_rob(dat, dat_rob)
+dev.off()

### 2021-09-24 06-Chp-Triangulation.Rmd
Back to a working version

---
#########################################
# options for knitting a single chapter #
#########################################
output:
  bookdown::pdf_document2:
    template: templates/brief_template.tex
  bookdown::word_document2: default
  bookdown::html_document2: default
documentclass: book
---

```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
Hold
```
(ref:intro-quote) --- Hold

<!-- TODO Add this to the Chapter summary in the introduction and  -->

# Triangulation {#tri-heading}

## Lay Summary

<!----------------------------------------------------------------------------->
&nbsp;

## Introduction

This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)

### Definition of the causal question

<!-- TODO See ROBINS-E for this, as to how to think about exposures -->

### Summary of triangulation

Need to check how much I talk about this in the introduction

Describe in detail

<!----------------------------------------------------------------------------->

## Graphical representation

For the graphs, the direction of bias is important.

Where the direction of bias was unclear/could not be determined from the

A different approach was taken for the confounding versus other domains, as confounding will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g. non-differential misclassification). In this case, the program accounted for the position of the effect estimate when assigning a directional arrow to the

These graphs were built using the risk of bias tool described in Appendix \ref()

<!----------------------------------------------------------------------------->

## Results

Compare bias-adjusted and

See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.

<!----------------------------------------------------------------------------->

## Discussion

I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain

Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.

### 2021-09-24 03-Chp-Systematic-Review.Rmd
Back to a working version
End of day:

@@
 
+<!-- TODO text -->
+
 &nbsp;
@@
 Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
-These include randomised controlled trials, observational studies of different analytical design (cohort, case-control, etc), and Mendelian randomisation studies.
+These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
 However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
@@
 
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence syntheists but may contain important unpublished studies.
-As an adjunct analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
+Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies.
+As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
 This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
@@
 In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewer.
-These included Alexandra MacAleenan, Athena Sheppard, Matthew Lee and Lena Schmidt.
-In addition, Sarah Dawson, and information specialist, provided input to the design of the search strategy.
+Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration).
+<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
+In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
 
@@
 
-I systematically search electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
+I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
+The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
 The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy included terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
 An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
@@
 
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-I also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-
+I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
 In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
 
-Grey literature was also searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
+Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
 In addition, the abstracts list of relevant conferences (e.g.
@@
 
-<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->
-
 &nbsp;
@@
 
-Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.
 
@@
 
-I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
-<!-- TODO Do I actually want to include MCI?
---> Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants were free (or assumed to be free) of dementia/MCI <!-- TODO Do I actually want to include MCI?
--->  at baseline.
+I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
+Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Participants were screened for dementia at baseline and prevalent cases excluded.
+Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
 Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
@@
 
-Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD), National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-<!-- TODO CITATION NEEDED -->
-
-__Bit on inclusion of EHR, where it is unclear how dementia diagnosed.__
+Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.
+
+<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
 
@@
 
-For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
-an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
-no dementia or dementia/MCI/dementia) based on this definition.
-
 No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
@@
 
-Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews were excluded.
-Studies which present no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
+Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded.
+Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
 Studies that measure change in continuous cognitive measures (e.g.
 MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/MCI/dementia) were excluded.
-Conference abstracts with no corresponding full-text publication were examined, and I contacted authors to obtain information on the study's status.
-Studies that are reported in insufficient detail (e.g.
-only in conference abstracts, new, letters, editorials and opinion) were excluded.
+no dementia/dementia) were excluded.
+Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status.
 Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
-<!-- TODO Expand on rationale for exclusion of cross-sectional studies.
-Dementia is a disease severly at risk of differential recall, leading to misclassification bias.
-By using prospective studies, the potential for this bias is reduced.
--->
-
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
+
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
 for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
@@
 
-Inter- and intra-rater reliability during the screening stage were assessed for a 10% sub-sample of records at the title and abstract screening stage.
+Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
 Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
@@
 
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
 [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
@@
 
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
 Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
@@
 
-If this assessment demonstrated issues with the screening process, a larger proportion of records would have been dual-screened.
+Intra- and inter-rater reliability was assessed against these cut-offs.
+If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.
 
@@
 Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author list, journal), study characteristics (location, cohort name, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
-All data was extracted the data in the first instance and was checked for accuracy by a second member of the review team.
+Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
+I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
+
+#### Study-fication
+
+As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
+This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
+Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 Following best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemai status), the following approach was used to combine the groups <!-- TODO Cite cochrane handbook here -->
-
-<!-- TODO Insert equations here -->
+age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups.
+[@higgins2019]
 
@@
 
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis. where more than one group
-
-##
-
-\begin{equation}
-N = N_1 + N_2
-  (\#eq:combiningGroups1)
-\end{equation}
+This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
 <!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
@@
 
-#### Study-fication
-
-As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
-Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
-Instead, they were considered as different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
 <!----------------------------------------------------------------------------->
@@
 
-Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
-
-This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
-<!-- TODO Use the example of getting the cut-off points from the  -->
-
-<!-- TODO move to results, and keep just a short bit here -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Converting between different exposure measures
+Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
+This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Analysis of varying effect measures
 
@@
 The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-If the outcome is rare, odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account time-to-event in each treatment group.
+If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group.
+As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]
 
 Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-In adddition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
+In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
 Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
-
 <!-- TODO Need to really fix this -->
 
-<!-- The likely effect of this is that the overall effect measures are biased towards . . . . ? -->
-
-<!-- Can you predict the direction of effect from a  -->
-
-<!-- Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis  -->
-
-<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Risk of bias assessment {#risk-of-bias}
+In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Risk-of-bias assessment {#risk-of-bias}
 
 A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
-To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.
+To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
 
@@
 
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.
-As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-
-Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
-For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up.
-missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up.
-In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.
+This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools.
+<!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
+For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
+In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.
 
@@
 The study design-specific tools are introduced and discussed in more detail in the following sections.
-In addition, the tool also aim to capture the potential direction of bias for each result.
-Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
 
@@
 
-Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019]
-
-The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
+Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
 Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
@@
 Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
-Ideally, observationals studies should be assessed in reference to an idealised randomised controlled trial.
-Further, the rare overall judgement of "Low" is considered equivalent to a randomised controlled trial.
-
-For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool.[@morganr2020] The tool is still in development, but while the signalling questions for each domain are yet to be confirmed, the overarching risk-of-bias domains have been finalised.
-The motivation for this using this tool above other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
-In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
-<!-- TODO CITATION NEEDED --> In addition, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
+Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial.
+Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
+
+While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
+Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level.
+The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
+In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
+Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
 
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies (advance results from this review were obtained from contact with the authors.).
-<!-- TODO CITATION NEEDED --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
+<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
 
@@
 
-A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.
-<!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
-<!-- TODO CITATION NEEDED -->
+A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
 
 This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
-This is because the tool did not exist when the protocol was originally registered.
+This is largely because the tool did not exist when the protocol was originally registered.
 
@@
 
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies across
-
-Where individual studies were deemed comparable, they were incoroporated into a quantitative analysis or "meta-analysis".
+An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design
+
+Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
 <!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
@@
 <!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
+
 <!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
+
+This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
+
+<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
 
@@
 --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-
-Where possible, data for all exposure groups was extracted.
-<!-- TODO ???
---> Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).
-
-<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
-<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
-A <!-- TODO confirm type of spline --> spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
+In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
+
+Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
+if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
+
+A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
+The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
 Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
 Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
-<!-- TODO Each bracket should have an upper and lower end -->
 
 Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the higest category was the same as the one immediately below it.
+
+Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
+
+When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
 Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
@@
 
-I conducted a leave-one-out analysis in order to explore the impact of any given study on the results.
-<!-- TODO CITATION NEEDED --> In addition, where available, I performed meta-regression to assess whether the results varied by age or sex.
-
+I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
+<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
+_A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
 <!-- TODO Need more here -->
@@
 
-Further, given the importance of visualising the potential biases of a result alongside the result itself, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication).[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other reserachers to design a modular method for creating these plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using this tool.
+One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
+
+In response to this criticism, I develope a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
-Preprints are a valuable evidence source (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
-
-As part of a study within this larger review, I also to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
+Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
+
+As a sensitivity analysis, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+
+Additionally, I followedpreprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
 
@@
 
-<!-- TODO Compare findings for two papers from Rantanen -->
+<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
 
@@
 
-`r num_to_text(23447,T)` records were identified through database searches.
+The database search identified `r num_to_text(23447)` records, of which
 
@@
 
-Of the 500 random records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were basic science studies, commentaries or educational articles.
+Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
+Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected.
+<!-- TODO include some example citations here -->
 
@@
 `r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
-
-The PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-
-<!-- TODO Finish PRISMA -->
-
+<!-- TODO Check these figures & Finish PRISMA -->
+
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
 To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
 
+Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
+change in cognitive scores).
+
+### Validation of screening
+
 <!----------------------------------------------------------------------------->
@@
 
-(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
-The different contributions of databases and preprint servers to the review are indicated.
+(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
+The different contributions of standarad bibliographic databases and preprint servers to the review are indicated.
 
@@
 
-<!-- TODO Show bar chart by date of publication? -->
-
-<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
-
 ```{r agree-setup, include = FALSE}
@@
 
-The values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
 For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
 Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
+The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
 
@@
 
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab: agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
+Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline/MCI versus dementia, and the definition of eligible lipids fractions.
 
@@
 
-Following full-text screening, __XXXX__ studies met the criteria for inclusion in the review. Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+Following full-text screening, __XXXX__ studies met the criteria for inclusion in the review.
+
+Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of studies were non-randomised, with only two included randomised controlled trials, both of which examined all-cause dementia.
+
+Similarly, the majority of the few included  and a relative small number of Mendelian randomisation studies. Of the non-randomised studies, many were assessments of the relationship with statis use.
+
+The vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
 
@@
 
+Of the studies examining lipid levels, by far the most common fraction assessed was total cholesterol. The association with triglyceride levels was not consider in many papers.
+<!-- TODO Check this is actually true-->
+
+Many studies using electronic health records as their data source did not accurately report the diagnostic criteria used to identify cases.
+
+Midlife cholesterol levels were of particular interest, with several studies examining this age-range.
+
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterik), one of which had subsequently been published and was captured by the primary literature serachr.
+All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
+
+Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
+As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
+-->.
+As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
+
+<!--- TODO Figures and tables to include here:
+
+-   PRISMA Flowchart (done)
+
+-   Summary of types of study (half done)
+
+-   Summary of locations (half done)
+
+-   Summary of diagnostic criteria used (done)
+
+-   Summary of risk of bias (not done)
+
+--->
+
+<!-- TODO Also need to extract the codes used in each study -->
+
+<!-- TODO Need to add asterik denoting preprints to table, and add a column on whether codes repoted for EHR -->
+
 &nbsp;
@@
 
-The majority of studies were non-randomised, with only one included randomised controlled trials (the Heart Protection Study) and a relative small number of Mendelian randomisation studies.
-Of the non-randomised studies, many were assessments of the relationship with statis use.
-
-Of the studies examining lipid levels, by far the most common fraction assessed was total cholesterol. The association with triglycerides levels was not consider in many papers.
-<!-- TODO Check this is actually true-->
-
-The vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia.
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic criteria used to identify cases, and of those that did, none sought to validate the accuracy of their defined code lists.
-
-<!-- TODO Check this, and do I actually want to say this, as I don't validate my codelist in the CPRD analysis? -->
-
-Many of the studies were conducted in electronic health record databases, which have a number of advantages over smaller more traditional cohort studies.
-
-<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
-
-<!--- TODO Figures and tables to include here:
-
--   PRISMA Flowchart (done)
-
--   Summary of types of study (half done)
-
--   Summary of locations (half done)
-
--   Summary of diagnostic criteria used (done)
-
--   Summary of risk of bias (not done)
-
---->
-
-<!-- TODO Also need to extract the codes used in each study -->
-
-As shown in Figure \@ref(fig:cohortLocations), the majority of study cohorts were based in the developed world.
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of study cohorts were based in the developed world.
 
@@
 
-Many of the included results were assessed to be at high risk of bias.
-
-The one randomised controlled trial was deemed to be a low risk of bias,
-
-Several synthesis were also assessed to be at risk of bias due to missing evidence.
-
+As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
+
+However, as a brief summary of the biases at play:
+
+Both randomised controlled trials were considered to be at low risk of bias.
+
+For NRSI
+For NRSE
+
+For MR studies
+
+Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
 A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
@@
 
-<!-- Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
 -->
@@
 
-### Reviewing Mendelian randomisations studies {#rev-discussion-MR}
-
-One of the strengths of this review is it's inclusion of MR studies as a source of evidence.
+### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
+
+One of the strengths of this review is it's inclusion of Mendelian randomisation studies as a source of evidence.
 
@@
 Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that MR studies only begin to appear in the evidence base much later than NRSE/NRSI.
+Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI.
 As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
@@
 
-Talk about problem with studies sharing underlying datasets in two sample MR frameworks - c.f.
-EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, MR analysis can be multiple studies using the exact same summary statistics from the same cohorts
-
-Introduce assumptions underlying MR (with image).
+Talk about problem with studies sharing underlying datasets in two sample Mendelian randomisation frameworks - c.f.
+EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, Mendelian randomisation analysis can be multiple studies using the exact same summary statistics from the same cohorts
+
+Introduce assumptions underlying Mendelian randomisation (with image).
 Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
@@
 <!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of MR studies which used similar data from the Global Lipid
-
-(ref:mrDuplication-scap) Summary of duplication of MR studies
+(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used similar data from the Global Lipid
+
+(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
 
@@
 
-A key example of the importance of pleiotropy in Mendelian randomisations studies is ill.
-In almost all cases, MR studies examine.
+A key example of the importance of .
+In almost all cases, Mendelian randomisation studies examine.
 A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
@@
 
-### Comments on the process
-
-As part of the reflective element of this thesis, I collated my experiences on performing a systematic review.
-
-&nbsp;
-
-#### Protocol registration
-
-While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
+<!-- ### Comments on the process -->
+
+<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
+
+<!-- &nbsp; -->
+
+<!-- #### Protocol registration -->
+
+<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
 In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
-
-&nbsp;
+-->
+
+<!-- &nbsp; -->
 
@@
 <!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
+Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
 -->
@@
 
-&nbsp;
-
-#### People management
-
-This review provide an excellent opportunity to gain experience in managing a team of researchers.
+<!-- &nbsp; -->
+
+<!-- #### People management -->
+
+<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
 However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
 I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
-
-&nbsp;
+-->
+
+<!-- &nbsp; -->
 <!----------------------------------------------------------------------------->
@@
 
-#### Open data sharing {#sys-rev-open-data}
+### Open data sharing {#sys-rev-open-data}
 
@@
 
--   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
+-   *Structured risk-of-bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
 ROBINS-I/E).
@@
 
-One particular limitiation with regards to the risk of bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk of bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
+One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
+This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
 However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.

### 2021-09-28 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-There were 127 primary studies <!-- TODO check this -->that contained information on this relationship.
+There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
 I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
@@
 
-<!-- Where both the outcome and the exposure were dichotmous, or the -->
-
 Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
@@
 
+Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
+<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
+
 &nbsp;
@@
 
-In response to this criticism, I develope a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
+__[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]__
+
 Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
@@
 
-Additionally, I followedpreprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
+Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
 
@@
 
-<!--- TODO Cross check this with the actual numbers included --->
+<!-- TODO Cross check this with the actual numbers included -->
 
@@
 (ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standarad bibliographic databases and preprint servers to the review are indicated.
+The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
 
@@
 
-Following full-text screening, __XXXX__ studies met the criteria for inclusion in the review.
-
-Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of studies were non-randomised, with only two included randomised controlled trials, both of which examined all-cause dementia.
-
-Similarly, the majority of the few included  and a relative small number of Mendelian randomisation studies. Of the non-randomised studies, many were assessments of the relationship with statis use.
-
-The vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
+Following full-text screening, 87 reports describing 78 unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
+Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
+
+Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
+For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
+
+In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
+Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
 
@@
 
-Of the studies examining lipid levels, by far the most common fraction assessed was total cholesterol. The association with triglyceride levels was not consider in many papers.
-<!-- TODO Check this is actually true-->
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic criteria used to identify cases.
-
-Midlife cholesterol levels were of particular interest, with several studies examining this age-range.
-
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterik), one of which had subsequently been published and was captured by the primary literature serachr.
+Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
+
+Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
+
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
 All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
@@
 
--   PRISMA Flowchart (done)
-
--   Summary of types of study (half done)
-
--   Summary of locations (half done)
-
--   Summary of diagnostic criteria used (done)
-
 -   Summary of risk of bias (not done)
@@
 
-<!-- TODO Need to add asterik denoting preprints to table, and add a column on whether codes repoted for EHR -->
-
-&nbsp;
+<!-- TODO Need to add abbreviations to table -->
 
@@
 (ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
+Note that three studies reported on multiple study designs, and these have been duplicated across the relevant sub-sections.
 
@@
 
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of study cohorts were based in the developed world.
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
 
@@
 ```{r cohortLocationsSetup, include = FALSE}
-
 ```
@@
 
-### Risk of bias {#risk-of-bias-subheading}
+### Risk of bias {#risk-of-bias-res}
 
@@
 &nbsp;
-<!----------------------------------------------------------------------------->
-
-### Statins
-
-```{r primaryFigures, include = FALSE, message=FALSE,warning=FALSE}
-```
-
-<!-- Straight-forward random effects meta-analysis of binary exposures, using study defined measures of each. -->
-
-In the two included RCTs, statin use was not associated with dementia outcomes
-
-<!----------------------------------------------------------------------------->
-(ref:statinsRCT-cap) __Random effects meta-analysis of statins on all-cause dementia:__
+
+<!----------------------------------------------------------------------------->
+
+### All-cause dementia
+
+__Statins__
+
+```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+
+(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
 
@@
 
-```{r statinsRCT, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forest_statins_rct.png"))
-```
-<!----------------------------------------------------------------------------->
-
-In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r estimate(0.76,0.66,0.88)`, Figure \@ref(fig:statinsNRSI)).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-(ref:statinsNRSI-cap) __Forest plot showing effect of statins:__
-
-(ref:statinsNRSI-scap) Forest plot showing effect of statins
-
-```{r statinsNRSI, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsNRSI-cap)', out.width='100%', fig.scap='(ref:statinsNRSI-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-
-In Mendelian randomisation studies, a similar blah blah blah
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsMR-cap) __Forest plot showing effect of statins:__
-
-(ref:statinsMR-scap) Forest plot showing effect of statins
-
-```{r statinsMR, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsMR-cap)', out.width='100%', fig.scap='(ref:statinsMR-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Hypercholesterolemia and lipid levels
-
-<!----------------------------------------------------------------------------->
-
-(ref:hypercholNRSE-cap) __Forest plot showing effect of statins:__
-
-(ref:hypercholNRSE-scap) Forest plot showing effect of statins
-
-```{r hypercholNRSE, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:hypercholNRSE-cap)', out.width='100%', fig.scap='(ref:hypercholNRSE-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
+```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+
+(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
+
+__Lipids__
+
+* NRSE
+
+* MR studies per 1-SD
+
+In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
+
+&nbsp;
 
@@
 
-<!----------------------------------------------------------------------------->
-
-(ref:lipidsNRSE-cap) __Forest plot showing effect of statins:__
-
-(ref:lipidsNRSE-scap) Forest plot showing effect of statins
-
-```{r lipidsNRSE, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidsNRSE-cap)', out.width='100%', fig.scap='(ref:lipidsNRSE-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
+In Mendelian randomisation studies, a similar
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Alzheimer's disease
+
+There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+
+(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease
+
+```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
+The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+__Lipids__
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Vascular dementia
+
+__Statins__
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
+
+(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia
+
+```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+__Lipids__
 
@@
 
-<!----------------------------------------------------------------------------->
-
-(ref:lipidsDoseResponse-cap) __Forest plot showing effect of statins:__
-
-(ref:lipidsDoseResponse-scap) Forest plot showing effect of statins
-
-```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidsDoseResponse-cap)', out.width='100%', fig.scap='(ref:lipidsDoseResponse-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Sources of heterogeneity -->
-
-Planned to investigate effect of sex and age at baseline.
-
+### Sources of heterogeneity
+
+Data on another potentially important source of heterogeneity
 Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
@@
 
-### Publication bias {#sys-rev-pub-bias}
+### Sensitivity analysis
+
+Given that the majority of the studies included in the review were of
+
+### Small study effects {#sys-rev-pub-bias}
 
@@
 &nbsp;
+
 <!----------------------------------------------------------------------------->
@@
 (ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
+
 ```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/funnel_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Added evidental value of including preprints {#sys-rev-including-preprints}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Added evidental value of including preprints {#sys-rev-including-preprints-res}
 
@@
 
-I had intended to assess the added evidental value of including preprints as a literautre source.
-
-As show in Figure \@ref(prisma-flow-fig), the number of results returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0). <!-- TODO check numbers -->
-
-No unique preprints were identified as part of this review, with the published version of the few/sole <!-- TODO check which --> relevant preprint(s) being captured by the main search.
-
-<!-- QUESTION Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
+As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
+From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
+
+For the analysis of XX on YYY, preprints added ...
+
+Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
+
+<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
 
@@
 <!-- TODO Check inclusion of Rockwood 2002:  -->
+This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+
+The discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
+A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise (Chapter \@ref(tri-heading)).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the single available RCT, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings are a
-
-In addition,  there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of
+This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogenity in exposure (e.g.
+mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
 
@@
 
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-
-The distribution of evidence between analytical designs is to be expected.
+The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
+This distribution of evidence between analytical designs is to be expected.
 Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a relatively new study design, and so only appears in the literature in recent years, driven by the growth of dementia GWASs (Figure \@ref(fig:typeByYear)).
+Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
 
@@
 This is particularly interesting given that lipids and statins are primarily related to vascular disease.
-There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of genome wide association studies, which are used in two sample summary Mendelian randomisation studies.
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the discussion, ApoE4 genotype is the major risk factor for Alzheimer's disease, but is also involved in cholesterol transport.
+__Can't look forward to other chapter__ There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of GWAS of this outcome.
 
@@
 
-This review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and is regularly held up as  providing no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic,[@mcguinness2016] only reported the mean change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test, etc.) over follow-up rather than incident.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using a , as cognitive tests should feed into a broader diagnostic pathway (see section \@ref(diagnostic-criteria)).
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk,[@shepherd2002a] reporting on cognitive outcomes as one of several secondary outcomes.
+While widely cited in relation to the effect of statins on dementia and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial only reported on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
 As such, this trial did not met the inclusion criteria for this review.
@@
 
-Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] Tie this in with
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Previous reviews {#rev-previous-reviews}
+Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Comparison with previous reviews {#rev-previous-reviews}
 
@@
 
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
 Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
 
-However, despite these differences in methodology, the duplication of work across reviews (including this review) is substantial.
+Similar the on previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease was conducted prior to the majority of MR studies included in this review being published, and extracted results including SNPs in APoE4 (see the following section for a discussion of the bias this introduces).
+
+However, despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
 In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.
-This approach would have enable more efficient identification of relevant primary studies, to which the methods which sets this review apart from other published reviews could have been applied.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-<!-- ### Triangulation across evidence sources -->
-
-<!-- TODO Have a look at this - potentially move to triangulation chapter -->
-
-<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
-
-<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
-For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011] -->
-
-<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
--->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of preprints
-
-```{r preprintGrowthSetup, include=FALSE}
-```
-
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
-There were several relevant preprints captured by the search.
-The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints).
-
-Three relevant preprints were identified
-
-medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
-The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
-
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
-
-While none of the preprints contributed uniquely to the review, this is again.
-Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
-The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
-This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
-However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
-
-<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
-
-<!-- Regardless, some studies were identified -->
+Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
 
@@
 
+One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
+As covered in the introduction (see Section \@ref()), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria of .
+
 Introduce assumptions underlying Mendelian randomisation (with image).
@@
 <!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used similar data from the Global Lipid
+(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
 
@@
 
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of exisitng GWASes to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
+<!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
+
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
 -->
@@
 A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Inclusion of preprints
+
+```{r preprintGrowthSetup, include=FALSE}
+```
+
+As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
+published).
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
+There were several relevant preprints captured by the search.
+The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).
+
+Three relevant preprints were identified
+
+medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
+The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
+The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
+As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
+
+Of the three identified preprints, two were subsequently published as of September 2020.
+This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
+
+While none of the preprints contributed uniquely to the review, this is again.
+Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
+The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
+This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
+
+Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
+However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
+
+<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
+
+<!----------------------------------------------------------------------------->
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.
+
+(ref:preprintGrowth-scap) Growth of preprint repositories over time
+
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
+```
+<!----------------------------------------------------------------------------->
+<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
+
+<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
+
+<!-- Regardless, some studies were identified -->
 

### 2021-09-28 06-Chp-Triangulation.Rmd
End of day:

@@
 
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- ### Triangulation across evidence sources -->
+
+<!-- TODO Have a look at this - potentially move to triangulation chapter -->
+
+<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
+
+<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
+For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
+[@guyatt2011] -->
+
+<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+-->
+
 # Triangulation {#tri-heading}
@@
 
+### Data sources
+
+This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
+
+<!----------------------------------------------------------------------------->
+
+### Background to the causal question
+
+Following best practice guidance, three
+
+Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
+
+This was also guideded by the forthcoming ROBINS-E tool, which has
+
+<!----------------------------------------------------------------------------->
+
 ### Definition of the causal question
@@
 
+### Risk of bias tool
+
+In addition, the tool also aim to capture the potential direction of bias for each result.
+Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
+Highlight that this is slightly different for the confounding domain in non-randomised studies.
+
+These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
+
 <!----------------------------------------------------------------------------->
+&nbsp;
 
-## Graphical representation
+### Graphical representation
 
@@
 
-Where the direction of bias was unclear/could not be determined from the
+Where the direction of bias was unclear/could not be determined from the report, this is indicated
 
-A different approach was taken for the confounding versus other domains, as confounding will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
+In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
+The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
+
+Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
+Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
 non-differential misclassification).
-In this case, the program accounted for the position of the effect estimate when assigning a directional arrow to the
+In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
+For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
+In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
+If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
 
 These graphs were built using the risk of bias tool described in Appendix \ref()
+
+<!-- TODO Does immortal time bias not also have a consistent effect -->
+
+<!----------------------------------------------------------------------------->
+
+### Standardisation across study designs
+
+Standardising across different measures of ex
+
+Want best information across lipids, and so standardised across differnt measures
+
+Fixing directions of effect - get everything pointing the same way
+
+<!----------------------------------------------------------------------------->
+### Analyses
+
+Bias-adjusted meta-analysis [@higgins2008a]
 
@@
 
+Summary of risk-of-bias/triangulation results
+
+Percentage of domains for which a direction of bias could be assigned?
+
 Compare bias-adjusted and
@@
 See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
+
+Applicability/indirectness as an issue 
+Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
 
@@
 
+### Challenges of real-life data
+
 Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
+ALso highlight the issue with assigning a direct of bias in many studies
+
+### Need for new methods
+
+Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?

### 2021-09-28 R/helper.R

@@ -16,6 +16,7 @@ grDevices::windowsFonts("Fira Sans" = grDevices::windowsFont("Fira Sans"))
 
 # Load forester function
 source(here::here("R/forester.R"))
+source(here::here("R/forest flexi.R"))
 
 try(dev.off())
 
@@ -111,7 +112,7 @@ word_check <- function(fp, words = 100){
 
 
 # Create nice estimate with consistent handling across thesis
-estimate <- function(estimate, lci, uci, type = "OR", sep = ",", to = "-"){
+estimate <- function(estimate, lci, uci, type = "OR", sep = ",", to = "-", exp = F){
   
   if (!hasArg(estimate)) {
     stop("Estimate missing")
@@ -123,6 +124,12 @@ estimate <- function(estimate, lci, uci, type = "OR", sep = ",", to = "-"){
   
   if (!hasArg(uci)) {
     stop("UCI missing")
+  }
+  
+  if (exp == TRUE) {
+    estimate <- exp(estimate)
+    lci <- exp(lci)
+    uci <- exp(uci)
   }
   
   if (type != "") {
@@ -574,27 +581,34 @@ get_confidence_from_p<- function(est, p) {
 
 }
 
-save_fp <- function(data) {
+save_fp <- function(dat, design = "obs",...) {
   
   # Don't perform meta-analysis if only one result
   
-  if (nrow(data)==1) {
+  if (nrow(dat)==1) {
     return()
   }
   
-  fp <- paste0("fp_", data$exposure_category[1],"_",data$exposure[1],"_", data$outcome[1],".png")
+  height <- max(nrow(dat)*70,500)
   
-  png(here::here("figures","sys-rev",fp), height = 300, width = 800)
+  dat_rob <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"), which = 3) %>%
+    janitor::clean_names() %>%
+    filter(result_id %in% dat$result_id)
+    
+    if (design == "obs") {
+      tool <- "ROBINS-I"
+      dat_rob <- select(dat_rob, -c(result,summary_of_biases, comments))
+    } else {
+      tool <- "ROB2"
+      dat_rob <- select(dat_rob, -c(d6,d7,result,summary_of_biases, comments))
+      
+    }  
+    
+  fp <- stringr::str_remove_all(paste0("fp_", design,"_",dat$exposure[1],"_", dat$outcome[1],".png")," ")
   
-  metafor::rma(data = data,
-               yi = point,
[…]

### 2021-09-28 forest flexi.R

@@ -1,362 +1,0 @@
-forest_strata_rob <- function(dat, dat_rob, rob_tool = "ROB2"){
-
-### calculate log risk ratios and corresponding sampling variances (and use
-### the 'slab' argument to store study labels as part of the data frame)
-
-dat_rob <- dat_rob %>%
-  mutate(Overall = factor(Overall ,levels =c("Low","Moderate","Serious","Critical"))) %>%
-  arrange(Overall)
-
-dat <- left_join(dat, dat_rob) %>%
-  arrange(Overall)
-
-dat_rob_vec <- dat_rob %>%
-  mutate(row_n = 1:n()) %>%
-  group_by(Overall) %>%
-  summarise(n=n(),max = max(row_n), min = min(row_n)) %>%
-  mutate(offset = seq(1,length(unique(.$Overall))*3,by=3)) %>%
-  
-  mutate(min = min+offset, max =max+offset, heading = max+1, stats = min-1.25) %>%
-  mutate(min = ifelse(n==1,min-1,min),
-         max = ifelse(n==1,max-1,max),
-         heading = ifelse(n==1,heading-1,heading))
-
-rows <- c()
-
-for (i in 1:nrow(dat_rob_vec)) {
-  
-  rows <-c(rows, dat_rob_vec$min[i]:dat_rob_vec$max[i])
-  
-}
-
-
-x_min = -12
-x_max = 4.6
-textpos <- c(x_min, x_max-1)
-y_max <- max(rows)+4
-
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# Deal with adding rob data
-
-max_domain_column <- ifelse(rob_tool == "ROB2",7,9)
-
-rob_data <-
-  cbind(dat_rob[, 1], data.frame(lapply(dat_rob[, 2:max_domain_column], robvis:::clean_data),
-                                  stringsAsFactors = F))
-
-
-x_pos <- seq(x_max, by = 0.55, length.out = max_domain_column - 2)
-
-x_overall_pos <- max(x_pos) + 1
-
-# Convenience vector, specifying x-axis positions for all risk of bias columns
-header_row <- c(x_pos, x_overall_pos)
-
-legend_pos <- x_max+(max(header_row)-min(header_row))/2
-
-# New right-hand x-axis limit
[…]

### 2021-09-28 03-Chp-Systematic-Review.Rmd
End of day:

@@
 <!-- ## To Do -->
-
-<!-- -   TODO Look at whether searching preprints made any difference to my results -->
 
@@
 
-Following full-text screening, 87 reports describing 78 unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
+```
+
+Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
 
@@
 
+of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
+
 ### Risk of bias {#risk-of-bias-res}
@@
 The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
+
+&nbsp;
 
@@
 <!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the relative number of hits returned by each is expected.
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
 

### 2021-09-28 05-Chp-IPD-Analysis.Rmd
Back to a working version
End of day:

@@
 
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/05-Code-IPD-Analysis.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
 ## Lay Summary
+
+As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
 
@@
 
+### Applying for data access
+
+__Systematic review__
+
 As part
 
-As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man
+As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
+In the first instance, the corresponding author on the main man
+
+__Dementia platform UK__
+
+In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
+In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
 
 Talk about how different covariates were managed across cohorts,
-c
+
+### Eligibility criteria
+
+Lipids reported/available as a continuous measure, and were not cross-sectional.
+
+Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
+The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
+
 <!-- TODO Read this[@riley2020] -->
+
+### Missing data
+
+Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
 
@@
 
-### Data sources
+### Risk of bias assessment
 
-Several cohort studies were approach
+Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
 
-<!-- Need exact number approach -->
+There is some concerns about performing risk of bias assessments on your own analysis, and so
 
-As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
 
-These data source
+&nbsp;<!----------------------------------------------------------------------->
 
-Each should have:
+### Analysis
 
-* Description (including observation period, numbers, numbers with outcome, etc)
-*
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
+<!-- TODO Figure showing the outline of interval censored studies. -->
+
+All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
+
+Similary,
+
+Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+
+Stratified by age-at-entry and sex, and ethnicity where possible.
+
+Hazard ratios were utilised to
+
+In order to investigate the interaction of sex with
+
+A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
+
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
+
+In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
+These were extracted and synthesised using a random effects meta-analysis.
+
+Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.
+
+The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]
+
+__Replicating published findings__
+
+Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Results
+
+### Data access
+
+<!-- Need exact number from each approach, plus detailed exclusion reasons -->
+
+Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
+Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
+
+In addition, the reasons for cohorts not being included in the analysis are presented.
+In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+
+For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th
 
 <!----------------------------------------------------------------------------->
+```{r cohortFlowchartSetup, include = FALSE}
+```
+
+(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
+
+(ref:cohortFlowchart-scap) Flowchart
+
+```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
+knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.
+
+I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
+
+As highlighted in the
+
+### Included data sources
+
+The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
+
+Of note, all data sources included in the analysis were based in the United Kingdom.
+This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.
+
 &nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:cohortOverview-caption) Summary of cohorts for which data were available
+
+(ref:cohortOverview-scaption) Summary of included cohorts
+
+```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->
+
+<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Caerphilly Prospective Study
+
+The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
+
+Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
+As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### CPRD
+
+The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+
+The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
+
+Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
+
+Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
+
+the
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-#### CaPS
-
-#### CPRD
-
-The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-The CPRD is introduced more fully in . Briefly, a similar approach to the cohort definition as used in Chapter
-
-Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
-
-Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
-
-the
-
-#### EPIC Norfolk
-
-#### Generation Scotland
-
-#### NICOLA
-
-#### TRACK HD
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-included in previous IPD meta-analysis (Endnote ID: 2140)
+This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]
 
-Different approaches to combining subgroups. [@fisher2017]
+This gave
 
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
+
 Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
 
-#### BRACE
+The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+
+__BRACE__
 
@@
 
-#### Memento
+__Memento__
+
 Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
 
-#### Generation Scotland
+__Generation Scotland__
 
@@
 
-#### NICOLA
+__NICOLA__
 
@@
 
-#### ELSA
+__ELSA__
 
@@
 
+&nbsp;
+
 <!----------------------------------------------------------------------------->
+(ref:dataExcluded-caption) dataExcluded
+
+(ref:dataExcluded-scaption) dataExcluded
+
+```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;
@@
 
-Maybe discuss here t
-
-This was particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
+A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
 Despite multiple attempts to contact the team, there was no response received.
@@
 
-### Data cleaning
+### Data cleaning and harmonisation
 
-Across all cohorts, data cleaning was performed in a similary manner, using commonly named variables, so that a single model could be applied using functional programming.
+Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
 
@@
 
-### Missing data
-
-Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-There is some concerns about performing risk of bias assessments on your own analysis, and so
-
-<!--- Inlcude CPRD analysis here, but dou --->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Analysis
-
-<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
-
-All analysis were standardised by changes in 1-SD of the exposure variable.
-
-This was done to aid interpretability of the outcome.
-
-Similary,
-
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Stratified by age-at-entry and sex, and ethnicity where possible.
-
-Hazard ratios were utilised to
-
-In order to investigate the interaction of sex with
-
-A two-stage model was used out of necessity, with the one-stage model being recluded by the different datasets being in protected data silos.
-
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
-
-<!-- TODO Figure showing the outline of interval censored studies. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Results
-
-Data
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
 ## Discussion
@@
 
-<!-- TODO text -->
-
 This review had a low response rate to requests for data access.
 
-While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.
+While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
 test
@@
 
-Letters sent to all cohorts identified through the systematic review <!-- TODO will need quite a bit here on the numbers approached and how they responded if at all.
-Will also need to comment on the additional tactics used.
--->
+Letters sent to all cohorts identified through the systematic review 
+<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
 
@@
 
-&nbsp;
-<!----------------------------------------------------------------------------->
+For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
 
-### Reflections on data access
+On a personal level, given the
+
+In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Resources
+
+While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
+
+Given the resource intensity of data cleaning and harmonisation,
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Data access
+
+Couple of sections
+
+* Problems with getting data from studies
+*
+
+Sharing data has several legal, ethical and logistical challenges, and can often
+
+This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
 
@@
 
-Even with the guaranteed data access afforded by the DPUK, accessing sufficient data was
+Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
+
+Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
 
@@
 
-Previous SWARs have
+Options could include
+
+Previous SWARs have been registered as protocols, but have not yet reported!
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reflections on the process
+
+May have been overly ambitious
 

### 2021-09-28 _main.Rmd
End of day:

@@
 As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
-The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which evolved to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv, which launched in 2019.[@rawlinson2019]
-
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of grey literature.
+The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which launched in 2019 and was designed to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv.[@rawlinson2019]
+
+Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
 At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
@@
 
-Allowing users of `medrxivr` to access a maintained snapshot removes any dependency on the API, which can become unavailable during peak usage times.
-The relationship between the two methods for accessing the data contained in the medRxiv database is summarized in Figure \@ref(fig:medrxivr-data-sources).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources:** Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
+This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file to an online server (Figure \@ref(fig:medrxivr-data-sources)).
+Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
+
+The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
+However, given that the number of records added each day is relatively low, this should pose minor issues.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources** - Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
 Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
@@
 
-### Refining your search
-
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.
-__[CITATION NEEDED - PRISMA-S]__
+### Refining a search
+
+An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.[@rethlefsen2021prisma]
 
@@
 
-The package was been onboarded into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.
-[^chp-systematic-review-tools-4] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
-
-[^chp-systematic-review-tools-4]: <https://github.com/ropensci/software-review/issues/380>
+The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Limitations of `medrxivr`
-
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of this thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Use case
+
+In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
+For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
+
+By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two differnt publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
+We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
+This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
+Author contributions are discussed in the
+
+In short, this use case illustrates that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints as a part of evidence synthesis exercises.
+
+<!----------------------------------------------------------------------------->
+
+### Limitations of `medrxivr` {#medrxivr-limitations}
+
+While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
 A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
@@
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different from the true grey literature (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979] It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
+
+<!-- TODO Clean-up this section -->
+
+<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
+
+```{r, include=FALSE}
+med_res <-
+  # Use snapshot from July 2021
+  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
+                      "*",
+                      from_date = "2019-07-01",
+                      to_date = "2019-08-01") %>%
+mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
+  group_by(pub_ind) %>%
+  count()
+
+published <- med_res$n[2]
+publication_n <- sum(med_res$n)
+publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
+```
+
+<!-- TODO Need to finish this bit and move it to the use-case section! -->
+
+Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
+`r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
+allowing for a two-year lag between preprint posting and publication).
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
+
+<!-- TODO replicate this analysis -->
+
+It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 
@@
 <!--chapter:end:02-Chp-Systematic-Review-Tools.Rmd-->
+
+---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
+output:
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::html_document2: default
+documentclass: book
+---
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
+"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
+```
+
+(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
+
+# Systematic review of all evidence available on the association between blood lipids (and treatment) and dementia outcomes {#sys-rev-heading}
+
+\minitoc <!-- this will include a mini table of contents-->
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/03-Code-Systematic-Review.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
+<!-- ## To Do -->
+
+<!-- TODO Extra studies to include: -->
+<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
+<!-- * Statins and the risk of dementia Jick -->
+
+## Lay summary
+
+Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
+They do this by finding and combining the results from many related primary research studies.
+Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
+
+This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
+
+There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
+I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
+Lipids were not associated with any outcome.
+The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
+
+The use of the results of this review in subsequent chapters is dicussed.
+
+<!-- TODO Search for MCI -->
+
+<!-- TODO text -->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+## Introduction {#sys-rev-intro}
+
+In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
+This analysis sought to address two specific aims.
+
+Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
+These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
+However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
+Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
+As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.
+
+Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies.
+As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
+This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
+
+The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Methods
+
+### Protocol
+
+A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Contributions
+
+In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
+Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration).
+<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
+In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
+
+<!-- TODO Double check this list at the end of the project. -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Search strategy
+
+I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
+The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
+The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
+The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
+An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+<!-- TODO Need to actually attach each search strategy.
+Should be able to loop through search strategy results.
+-->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:searchOverview-caption) Summary of systematic search by topic.
+The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
+
+(ref:searchOverview-scaption) searchOverview
+
+```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
+To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
+
+<!-- TODO need to comment on this feed-back process, or remove -->
+
+I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
+
+Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
+In addition, the abstracts list of relevant conferences (e.g.
+the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
+<!-- TODO how were these searched?
+Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Study selection
+
+Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
+(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
+those matched based on the "Title" field alone).
+
+Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.
+
+Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer.
+In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
+Reasons for exclusion at this stage were recorded.
+Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
+A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
+
+The criteria used to assess eligibility are presented in the subsequent sections.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Inclusion criteria
+
+I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
+Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Participants were screened for dementia at baseline and prevalent cases excluded.
+Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
+Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+No limits were placed on the sample size of included studies.
+
+Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.
+
+<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
+
+<!-- TODO Any study using EHR - go back and extract codelists -->
+
+No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Exclusion criteria
+
+Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded.
+Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
+Studies that measure change in continuous cognitive measures (e.g.
+MoCA score) without attempt to map these scores to ordinal groups (e.g.
+no dementia/dementia) were excluded.
+Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status.
+Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
+
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
+for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+below the age of 50) were excluded.
+Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
+Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Validation of screening process
+
+Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
+assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
+assessment of accuracy).
+
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
+
+Gwet's AC1 is defined as:
+
+$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
+
+In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
+
+\begin{equation}
+  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
+  (\#eq:AC1-main)
+\end{equation}
+
+where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
+
+\begin{equation}
+  q = \frac{(A+C)+(A+B)}{2N}
+  (\#eq:AC1-supp)
+\end{equation}
+
+<!-- TODO Need to be sure of how to calculate. -->
+
+How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
+
+(ref:gwet-scaption) Ranges for Gwet's AC1
+
+```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+Intra- and inter-rater reliability was assessed against these cut-offs.
+If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Data extraction
+
+Data extraction was performed using a piloted data extraction form.
+Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
+I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
+
+#### Study-fication
+
+As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
+This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
+Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+
+This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
+This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Combining across groups
+
+Following best practice, where summary data was presented across two groups (e.g.
+age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups.
+[@higgins2019]
+
+\begin{equation}
+N = N_1 + N_2
+  (\#eq:combiningGroups1)
+\end{equation}
+
+\begin{equation}
+Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
+  (\#eq:combiningGroups2)
+\end{equation}
+
+\begin{equation}
+SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
+  (\#eq:combiningGroups3)
+\end{equation}
+
+This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Harmonisation of cholesterol measures
+
+<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
+not providing qratile cut-off values, not poviding numbers per group, etc.
+--> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
+
+\begin{equation} 
+  mg/dL = mmol/L \times{} Z
+  (\#eq:lipidConversion)
+\end{equation}
+
+where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
+For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Following up with authors {#contacting-authors}
+
+Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
+This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Analysis of varying effect measures
+
+<!-- TODO Include formulae and informed assumptions  -->
+
+The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
+If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group.
+As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]
+
+Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
+In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
+Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
+<!-- TODO Need to really fix this -->
+
+In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Risk-of-bias assessment {#risk-of-bias}
+
+A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
+To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
+
+There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
+Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
+
+This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools.
+<!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
+For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
+In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.
+
+In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
+The study design-specific tools are introduced and discussed in more detail in the following sections.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Randomised controlled trials
+
+Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
+Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
+Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
+Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Non-randomised studies of interventions/exposures
+
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
+Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
+Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial.
+Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
+
+While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
+Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level.
+The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
+In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
+Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Mendelian randomisation studies
+
+At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
+<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Risk of bias due to missing evidence
+
+A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
+
+This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
+This is largely because the tool did not exist when the protocol was originally registered.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Analysis methods
+
+An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design
+
+Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
+<!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
+
+Of note, studies were not combined across different study designs (i.e.
+RCTs were not combined in a meta-analysis with results from observational studies).
+The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Standard meta-analysis
+
+Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
+<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
+--> The fixed-effect method was implemented as:
+
+<!-- TODO Check these against those in Ben's thesis paper -->
+
+\begin{equation}
+  \theta_i = \mu + u_i
+  (\#eq:meta-analysis-random)
+\end{equation}
+
+\begin{equation}
+  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
+  (\#eq:meta-analysis-fixed)
+\end{equation}
+
+<!-- where ... -->
+
+<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
+
+#### Dose-response analyses
+
+<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
+
+<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
+
+This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
+
+<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
+
+Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
+for example, highest vs lowest quartile).
+<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
+--> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
+In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
+
+Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
+if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
+
+A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
+The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
+Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
+Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
+
+Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
+
+Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
+
+When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
+Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Sensitivity analyses
+
+I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
+<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
+_A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
+<!-- TODO Need more here -->
+
+Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
+<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Visualisation of results
+
+Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
+
+One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
+
+In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Assessment of added value of including preprints
+
+__[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]__
+
+Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
+
+As a sensitivity analysis, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+
+Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Results
+
+<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
+
+### Initial search and validation of search filters
+
+The database search identified `r num_to_text(23447)` records, of which
+
+<!-- TODO Cross check this with the actual numbers included -->
+
+Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
+Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected.
+<!-- TODO include some example citations here -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Screening results
+
+Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
+`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
+<!-- TODO Check these figures & Finish PRISMA -->
+
+A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
+
+Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
+change in cognitive scores).
+
+### Validation of screening
+
+<!----------------------------------------------------------------------------->
+
+<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
+
+```{r prisma-flow-setup, include = FALSE}
+```
+
+\blandscape{}
+
+&nbsp;
+
+(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
+The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
+
+(ref:prisma-flow-scap) PRISMA flow diagram
+
+```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
+```
+
+\elandscape{}
+
+<!----------------------------------------------------------------------------->
+
+```{r agree-setup, include = FALSE}
+```
+
+For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
+Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
+The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
+
+<!-- TODO Include AC1 result in caption above -->
+
+(ref:agreeInter-scaption) Inter-rater agreement
+
+```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
+
+(ref:agreeIntra-scaption) Inter-rater agreement
+
+```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline/MCI versus dementia, and the definition of eligible lipids fractions.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Characteristics of included studies
+
+```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
+```
+
+Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
+Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
+
+Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
+For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
+
+In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
+Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
+
+Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
+
+Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
+
+Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
+
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
+All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
+
+Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
+As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
+-->.
+As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
+
+<!--- TODO Figures and tables to include here:
+
+-   Summary of risk of bias (not done)
+
+--->
+
+<!-- TODO Also need to extract the codes used in each study -->
+
+<!-- TODO Need to add abbreviations to table -->
+
+\blandscape{}
+<!----------------------------------------------------------------------------->
+(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
+Note that three studies reported on multiple study designs, and these have been duplicated across the relevant sub-sections.
+
+(ref:studyCharacteristics-scaption) Characteristics of included studies
+
+```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+\elandscape{}
+
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
+
+<!----------------------------------------------------------------------------->
+```{r cohortLocationsSetup, include = FALSE}
+```
+
+(ref:cohortLocations-cap) Geographical distribution of study cohorts
+
+(ref:cohortLocations-scap) Geographical distribution of study cohorts
+
+```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
+```
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
+
+### Risk of bias {#risk-of-bias-res}
+
+As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
+
+However, as a brief summary of the biases at play:
+
+Both randomised controlled trials were considered to be at low risk of bias.
+
+For NRSI
+For NRSE
+
+For MR studies
+
+Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
+A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
+This is discussed further in Section \@ref(rev-discussion-MR).
+
+<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
+
+Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### All-cause dementia
+
+__Statins__
+
+```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+
+(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
+
+(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+
+(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
+
+__Lipids__
+
+* NRSE
+
+* MR studies per 1-SD
+
+In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
+
+&nbsp;
+
+Several studies presented results per SD change in a lipid fraction.
+
+In Mendelian randomisation studies, a similar
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Alzheimer's disease
+
+There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+
+(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease
+
+```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
+The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+__Lipids__
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Vascular dementia
+
+__Statins__
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
+
+(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia
+
+```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+__Lipids__
+
+### Dose response meta-analysis of lipid levels {#dose-response-results}
+
+<!-- TODO Cite excluded studies and list exclusion reasons -->
+
+Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
+The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
+
+&nbsp;
+
+### Sources of heterogeneity
+
+Data on another potentially important source of heterogeneity
+Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
+
+<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->
+
+<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->
+
+<!-- Also important to examine the effect of: -->
+
+<!-- * age at baseline -->
+<!-- * sex (percentage) -->
+<!-- * education -->
+<!-- * baseline cognitive scores (how to group) -->
+
+<!-- ### Sensitivity analyses -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Sensitivity analysis
+
+Given that the majority of the studies included in the review were of
+
+### Small study effects {#sys-rev-pub-bias}
+
+<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
+<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
+
+There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
+
+<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
+
+<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
+Depsite attempts to obtain this additional information through contact with a -->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia
+
+(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
+
+```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Added evidental value of including preprints {#sys-rev-including-preprints-res}
+
+<!-- TODO Will have to get actual numbers for this section -->
+
+As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
+From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
+
+For the analysis of XX on YYY, preprints added ...
+
+Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
+
+<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Discussion
+
+<!-- TODO Check inclusion of Rockwood 2002:  -->
+This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+
+The discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
+A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise (Chapter \@ref(tri-heading)).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Summary of findings
+
+There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
+This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogenity in exposure (e.g.
+mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
+
+Some evidence that age has impact on observed lipid-dementia relationship - use to link
+
+The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
+This distribution of evidence between analytical designs is to be expected.
+Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
+Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
+
+<!----------------------------------------------------------------------------->
+(ref:typeByYear-cap) __Study designs by year of publication__ -
+
+(ref:typeByYear-scap) Study designs by year of publication
+
+```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
+```
+<!----------------------------------------------------------------------------->
+
+A common theme across the evidence base was a lack of data on the association of vascular dementia.
+This is particularly interesting given that lipids and statins are primarily related to vascular disease.
+__Can't look forward to other chapter__ There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of GWAS of this outcome.
+
+<!--- 
+QUESTION
+This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
+- No these studies should not be included, as not recognised criteria.
+-->
+
+<!-- __Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
+Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
+-->
+
+Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk,[@shepherd2002a] reporting on cognitive outcomes as one of several secondary outcomes.
+While widely cited in relation to the effect of statins on dementia and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial only reported on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
+As such, this trial did not met the inclusion criteria for this review.
+
+<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
+The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
+from Anstey 2017 -->
+
+Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Comparison with previous reviews {#rev-previous-reviews}
+
+<!-- TODO This section will be informed by the review published as a preprint -->
+
+__This section will be completed once Georgia has completed her analysis, and can also be cross-references with the meta-meta analysis published is Brain Sciences recently.__
+
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
+Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
+
+Similar the on previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease was conducted prior to the majority of MR studies included in this review being published, and extracted results including SNPs in APoE4 (see the following section for a discussion of the bias this introduces).
+
+However, despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
+In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
+Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
+
+One of the strengths of this review is it's inclusion of Mendelian randomisation studies as a source of evidence.
+
+Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
+
+Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
+Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI.
+As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
+A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
+This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application.
+
+Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
+A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
+While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref().
+Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool, which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not access the additional methodological considerations of the analysis of the Mendelian randomisation analysis itself.
+<!-- TODO Read this tool.
+--> For this review, I utilised the best available author-devised tool, sourced on a recent review of systematic reviews of Mendelian randomisation studies.
+
+<!-- TODO Need to add some text to the ROB section of this chapter on distinction between reporting and quality -->
+
+<!-- Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants -->
+<!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
+<!-- TODO Email George with query on dual counting, following review of email with Julian -->
+
+As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
+This is particularly relevant to the consideration of bias due to missing evidence.
+As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
+The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
+Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
+This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
+
+Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
+This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`).
+Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
+Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.
+
+<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
+
+Talk about problem with studies sharing underlying datasets in two sample Mendelian randomisation frameworks - c.f.
+EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, Mendelian randomisation analysis can be multiple studies using the exact same summary statistics from the same cohorts
+
+One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
+As covered in the introduction (see Section \@ref()), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria of .
+
+Introduce assumptions underlying Mendelian randomisation (with image).
+Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
+Note the region must be quite wide - talk about controversy surrounding Benn paper
+
+Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
+This point is important given one of the core assumptions of
+
+<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
+
+MR are limited by the need for SNP to be present in both datasets (for TSMR).
+
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
+
+(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
+
+```{r mrDuplicationSetup, include=FALSE}
+```
+
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
+
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
+-->
+
+A key example of the importance of .
+In almost all cases, Mendelian randomisation studies examine.
+A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Inclusion of preprints
+
+```{r preprintGrowthSetup, include=FALSE}
+```
+
+As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
+published).
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
+There were several relevant preprints captured by the search.
+The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).
+
+Three relevant preprints were identified
+
+medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
+The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
+The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
+As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
+
+Of the three identified preprints, two were subsequently published as of September 2020.
+This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
+
+While none of the preprints contributed uniquely to the review, this is again.
+Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
+The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
+This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
+
+Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
+However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
+
+<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
+
+<!----------------------------------------------------------------------------->
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
+
+(ref:preprintGrowth-scap) Growth of preprint repositories over time
+
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
+```
+<!----------------------------------------------------------------------------->
+<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
+
+<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
+
+<!-- Regardless, some studies were identified -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+<!-- ### Comments on the process -->
+
+<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
+
+<!-- &nbsp; -->
+
+<!-- #### Protocol registration -->
+
+<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
+In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
+-->
+
+<!-- &nbsp; -->
+
+<!-- #### Workload -->
+
+<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
+Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
+-->
+
+<!-- Average time to complete a s -->
+
+<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
+
+<!-- &nbsp; -->
+
+<!-- #### People management -->
+
+<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
+However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
+I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
+-->
+
+<!-- &nbsp; -->
+<!----------------------------------------------------------------------------->
+
+<!-- ### Validation against recent umbrella review -->
+
+<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
+
+<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
+
+<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
+In fields where there is a lot of existing reviews, they -->
+
+<!-- All studies identified by reviews included in te -->
+
+<!-- In hindsight, this approach ma -->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+
+### Open data sharing {#sys-rev-open-data}
+
+As discussed in Section \@ref(dose-response-results), many primary studies did not report important elements, and so these could not be extracted.
+This limiation was compounded by the expected low response rate to requests for further information from primary authors (although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019]).
+
+While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
+
+Based on my experience of extracting data for this review, I co-wrote an guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021]
+
+Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. <!-- TODO Cite the Zenodo repo here! -->
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Strengths and limitations
+
+<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
+
+#### Strengths
+
+I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
+
+-   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
+As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
+<!-- TODO Though this could --> In addition
+
+-   *Structured risk-of-bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
+ROBINS-I/E).
+This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
+
+-   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related manuscripts as a source of grey literature.
+As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
+
+<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
+they would not have been captured by the search for published papers) -->
+
+- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
+This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
+In addition this review was used to pilot an upcoming risk of bias tool
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Limitations
+
+The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
+An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
+
+In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
+However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
+
+One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
+This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
+However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
+In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
+
+One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
+Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Conclusions
+
+In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
+
+This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
+
+<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
+
+\newpage
+
+## References
+
+<!--chapter:end:03-Chp-Systematic-Review.Rmd-->
 
@@
 ---
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
-```
-
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
-
-# Systematic review of all available evidence {#sys-rev-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!-- ## To Do -->
-
-<!-- -   TODO Examine how many times a primary study was included in a review -->
-<!-- -   TODO Look at whether searching preprints made any difference to my results -->
-<!-- -  TODO Could apply ROBIS to previous reviews to see how they stack-up? (This may be done as part of Georgia's summer project) -->
-
-<!-- TODO Extra studies to include: -->
-
-<!-- * Smeet et al. reference in the CPRD analysis -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-<!-- * Statins and the risk of dementia Jick -->
-
-## Lay summary
-
-The importance of
-
-I found that
-
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-## Introduction {#sys-rev-intro}
-
-The aim of this chapter is to systematically review all available literature on the association between blood levels of total cholesterol and it's constituent parts (HDL-c,LDL-c and triglycerides) on the subsequent risk of dementia.
-
-Based on the review of existing literature, no previous evidence synthesis exercise attempted to examine all available literature simultaneously.
-
-Only by looking across all available evidence can the true, given the often limited use of one type of evidence (RCTs are hard to do, obs studies are biased).
-
-Literature con
-
-Systematic reviews aim to transparently and reproducibly identift
-
-<!-- TODO Need to seriously improve this -->
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-## Methods
-
-### Protocol
-
-A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020]
-
-### Contributions
-
-This systematic review was performed in conjunction with a team of secondary reviewer, all of whom . These included Alexandra MacAleenana, Athena Sheppard, Matthew Lee and Lena Schmidt.
-
-<!-- TODO Double check this list at the end of the project. -->
-
-### Search strategy and and study selection
-
-I systematically search electronic bibliographic databases to identify potentially relevant records.
-The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy will include terms related to lipids, lipid modifying treatments, and dementia and its sub-types, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full draft search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
-<!-- TODO Need to actually attach each search strategy.
-Should be able to loop through search strategy results.
--->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic.
-The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
-
-(ref:searchOverview-scaption) searchOverview
-
-```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 14" in Table \@ref(tab:searchOverview-table)) was screened.
-If any potentially relevant studies are identified, their titles and abstracts were searched for key terms that can be incorporated into the filters to improve search sensitivity.
-
-<!-- TODO need to comment on this feed-back process, or remove -->
-
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection (for the specific databases available thi via the University).
-We will also search clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-As the contents of the Web of Science Core COllection can vary by institution, the specific database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-
-The abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
-<!-- TODO how were these searched?
-Date and other range -->
-
- Grey literature will also be searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-We will also search bioRxiv and medRxiv, preprint repositories using a tool built as part of this thesis, to identify potentially relevant studies.
-Finally, the reference lists of included studies were searched by hand while studies citing included studies will be examined using Google Scholar (forward and reverse citation searching).
-
-<!-- TODO Look at citationchaser for this, but have a cut-off publication date of July 2019 - better than searching by hand/Google Scholar -->
-
-<!-- Include table with overview of search strategy here: summarise topics and how they were combined -->
-
-#### Study selection
-
-Records were imported into Endnote and deduplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
-those matched based on the "Title" field alone).
-
-Screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by the primary author, with a random selection of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-
-Full-text screening will also be completed in full by the primary author.
-A second reviewer screened a random sample (approx 10%) of included and excluded records, in addition to any records identified by the first reviewer as being difficult to assess against the inclusion criteria.
-Reasons for exclusion at this stage were recorded.
-Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram will be produced to document how records moved through the review.[@page2021]
-
-#### Inclusion criteria
-
-We will seek studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia/MCI.
-Eligible study designs include randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants were free (or assumed to be free) of dementia/MCI at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits will be placed on the sample size of included studies.
-
-Eligible studies defined dementia according to recognised criteria, for example the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN), International Classification of Diseases (ICD), or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.
-<!-- TODO do i actually want to include MCI?
--->
- For MCI, eligible studies are those that attempted state a definition for diagnoses of MCI (e.g.
-an adapted version of the Petersen criteria [@petersen1999]) and create ordinal groups of patients (e.g.
-no dementia or dementia/MCI/dementia) based on this definition.
-
-No limitations will be imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
-
-#### Exclusion criteria
-
-Case-control studies, cross-sectional studies, qualitative studies, case reports/series and narrative reviews will be excluded.
-Studies which present no evidence of attempting to exclude prevalent cases from their analyses will also be excluded.
-Studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/MCI/dementia) will be excluded.
-Conference abstracts with no corresponding full-text publication will be examined, and we will contact authors to obtain information on the study's status.
-Studies that are reported in insufficient detail (e.g.
-only in conference abstracts, new, letters, editorials and opinion) will be excluded.
-Previous systematic reviews will not be eligible, but their reference lists will be screened to identify any potentially relevant articles.
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where the lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) will be excluded.
-
-Excluded studies performing autopsy unless it was done under accepted criteria Exclude studies using a dietary intervention, for example omega-3 fatty acid enriched diet, as it hard to disentangle the effect of other elements contained within te diet, vs simple tablet based supplements of
-
-<!-- TODO Expand on rationale for exclusion of cross-sectional studies.
-Dementia is a disease severly at risk of differential recall, leading to misclassification bias.
-By using prospective studies, the potential for this bias is reduced.
--->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Assessment of inter-rater reliability
-
-Inter- and intra-rater reliability was assessed for a 10% sub-sample of records at the title and abstract screening stage.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions, while inter-rater reliability involved two reviewers independently screening the same set of records.
-
-If this approach demonstrates a significant level of erroneous exclusion by the primary author a larger proportion will be dual-screened.
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure of inter-rater reliability was chosen over other methods of assessing inter-rater reliability such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review, this is an important characteristic.
-
-Gwet's AC1 is defined as:
-
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
-
-In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
-
-\begin{equation}
-  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
-  (\#eq:AC1-main)
-\end{equation}
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-\begin{equation}
-  q = \frac{(A+C)+(A+B)}{2N}
-  (\#eq:AC1-supp)
-\end{equation}
-
-<!-- TODO Need to be sure of how to calculate. -->
-
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
-Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Data extraction
-
-Harmonization of cholesterol measures across studies was performed, as different studies used different methods to quantify exposure, including comparing differing risks in the highest vs lowest quartiles of a lipid, using a binary classification of patients into a hypercholesterolaemia or not, categorizing lipid levels into high, middle, and low groups according to study-defined criteria, and simply treating the exposure as a continuous variable.
-
-Following guidance for a dose response meta-analysis, I picked midpoint for all studies where bands were provided (extremely common in the case of lipids)
-
-This analysis was unusual, as multiple methods of integration and analysis were required with data spanning many forms.
-
-A piloted data extraction for was used. I extracted the data in the first instance and subset was checked by a colleague for accuracy.
-
-<!-- TODO Cross reference with the data extraction issues here - i.e. not providing qratile cut-off values, not poviding numbers per group, etc. -->
-
-Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
-
-\begin{equation} 
-  mg/dL = mmol/L \times{} Z
-  (\#eq:lipidConversion)
-\end{equation}
-
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
-
-<!----------------------------------------------------------------------------->
-
-#### Studification
-
-Multiple publications resulting from the analysis of the same data were included and grouped ().
-
-In the advent of multiple papers reporting results on the same cohort, but say, at different time points, I used a process of studifiction to build out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered duplicate records.
-Instead, they were considered as different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
-<!----------------------------------------------------------------------------->
-
-#### Following up with authors {#contacting-authors}
-
-Where data points required either for the analysis or risk-of-bias assessment but were not reported, the primary authors of the study were contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review,[@reynders2019]
-
-This was particular important for the dose response meta-analysis, we
-
-Use the example of getting the cut-off points from the
-
-<!-- TODO move to results, and keep just a short bit here -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Converting between different
-
-Include formulae and informed assumptions
-
-Not interchangeable in the context of systematic review.
-If outcome is rare, odds and risk ratios approximate each other, but the hazard ratio is measuring something completely different, by taking into account time-to-event in each treatment group.
-
-Several existing reviews do not distinguish between the two types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-
-The likely effect of this is that the overall effect measures are biased towards . . . . ?
-
-Can you predict the direction of effect from a
-
-Best practice methods for dealing with disparate effect measures in included studies is to not perform a meta-analysis
-
-<!-- See the third row of the table here; https://training.cochrane.org/handbook/current/chapter-12#section-12-1 -->
-
-Some evidence of manipulation of effect estimates in previous reviews,(e.g. Chou, Sci Reports - at least one study disagrees with) but not documented in review text.
-
-WHile the analysis of change scores is feasible, as they were explicityl
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Risk of bias assessment {#risk-of-bias}
-
-A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) and Section \@ref(triangulation-overview) for an overview of triangulation).
-To enable this triangulation exercise, a detailed and structured risk of bias assessment formed an important part of this review.
-
-There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
-Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
-
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as, and challenges in the comparison of results from different tools.
-
-As part of this, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-
-Additionally, results should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
-For example, a study may report on the efficacy of an intervention at 6 months and two years follow-up.
-missing outcome data that is not an issues at 6 months may introduce bias at 2 year follow-up.
-In this case, assigning a bias judgement to the study as a whole hides this differential biases for each result.
-
-In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
-The study design-specific tools are introduced and discussed in more detail in the following sections.
-
-In addition, the tool also aim to capture the potential direction of bias for each given domain.
-An optional question at the end of each domain, e.g.
-for Domain 1 of the RoB2 tool: "What is the predicted direction of bias arising from the randomization process?", possible responses included
-
-* Not applicable 
-* Favours experimental 
-* Favours comparator
-* Towards null 
-* Away from null 
-* Unpredictable
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Randomised controlled trials
-
-Risk of bias assessment in randomised controlled trials was performed using the domain-based risk-of-bias assessment tool appropriate to the study design.
-Randomized controlled trials were assessed using the RoB2 tool,[@sterne2019],
-The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
-Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
-Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
-
-One a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Non-randomised studies of interventions/exposures
-
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk of bias in non-randomised studies - of interventions) <!-- TODO Capitalise appropriately --> tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to the RoB 2, it has a number of prompting questions per domain, with judgements including.
-Ideally, obs studies assessed in reference to an idealised randomised controlled trial.
-Further, the rare overall judgement of Low should be considered equivalent to a randomised controlled trial.
-
-For non-randomised studies of exposures (NRSE), I opted to use a preliminary version of the ROBINS-E tool, despite it still being in development.[@morganr2020] While the signalling questions for each domain are yet to be confirmed, the overarching domains have been finalised.
-
-Despite these limitations, I chose this approach in place of other existing published tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] The motivation for this decision was two-fold.
-In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools such as the NOS.
-In addition, using a domain-based tool enabled better comparison with risk-of-bias assessments performed for the other study designs.
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Mendelian randomisation studies
-
-<!-- TODO This next bit is not all true -->
-
-At present, no risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk of bias assessments in systematic reviews of MR studies.
-A copy of this tool is available in Appendix \@ref(appendix-mr-rob).
-Advance results from this review of bias assessment in MR studies were obtained from contact with the authors.
-
-&nbsp;
-
-#### Risk of bias due to missing evidence
-
-A recent shift towards the assessment of missing evidence due to selective non-reporting (as distinct from the selective reporting of a single result from multiple planned - handled in Domain 5 of the RoB 2 tool for example).
-
-As part of this review, I piloted the RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool. <!-- TODO CITATION NEEDED --> Results were visualised
-
-<!----------------------------------------------------------------------------->
-
-### Analysis methods
-
-Studies were not combined across different study designs (i.e. RCTs were not combined in a meta-analysis with results from observational studies).
-
-#### Standard meta-analysis
-
-Meta-analysis is an important method of . . .
-
-Both a fixed-effect and random-effects meta-analysis model was.
-
-For
-
-Need formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
-
-This analytical approach was used for
-
-$u$
-
-\begin{equation}
-  \theta_i = \mu + u_i
-  (\#eq:meta-analysis-random)
-\end{equation}
-
-\begin{equation}
-  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
-  (\#eq:meta-analysis-fixed)
-\end{equation}
-
-where ...
-
-<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
-
-This analytical approach was used for cases where the exposure was dichotomous (e.g. statin use or not, hypercholesterolemia or not).
-
-#### Dose-response analyses
-
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
-<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on.  -->
-
-Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
-for example, highest vs lowest quartile).
-<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
--->
- while this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-
-Where possible, data for all exposure groups was extracted, and this <!-- TODO ??? -->
-.
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not presented (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands in mmol/L).
-
-<!-- Taken from another paper: "A potential non-linear association was evaluated using a restricted cubic spline model with three knots at the 10th, 50th and 90th percentile of frequency of the exposure [@orsini2012meta]" -->
-
-<!-- TODO Do I initially want to fit a linear relationship across categories and  -->
-A XXXX spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of an exposure can have an effect versus the "normal" reference dose.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
-Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
-
-Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the widht of the higest category was the same as the one immediately below it.
-Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
-
-I assumed the width of the category to be the same as the adjacent category.
-When the lowest category was open ended, I set the lower boundary to zero.
-
-#### Sensitivity analyses
-
-I conducted a leave one out analysis in order to explore the impact of any given study on the results. <!-- TODO CITATION NEEDED -->
-
-In addition,
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Visualisation of results
-
-Given the importance of visualising the potential biases alongside the results of any given study, a new visualisation tool was designed to allow for "paired" forest plots (as recommended by the ROB2 publication)
-
-This tool grew out of a collaboration with other reserachers to design a modular method for creating these plots <!-- Apparently collaboration is a big thing they want to see -->
-
-A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this analysis were created using
-
-Results from the risk-of-bias assessment were visualized using a paired forest/risk-of-bias blobbogram, created using the `robvis` tool.
-This tool was developed as an adjunct to this thesis to aid in creating standard risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of the tool is provided in Appendix \@ref(appendix-robvis).
-
-Also, the use of evidence maps is becoming increasingly common to explore the distibution of research cohorts included in a
-
-As such, each individual cohort contibuting to the evidence base was quantified and visualised on a world map.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Assessment of added value of including preprint
-
-Preprints are a valuable evidence source (see Introduction) but their inclusion in a systematic reivew
-s
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints give you a look into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a different.
-
-I also sought to explore the additional evidental value of including preprints in the meta-analysis, assessed using the fixed effect weight from a standard meta-analysis.
-
-<!-- TODO List here that one of the key reasons for building the tool was to . Reference back to  -->
-
-<!----------------------------------------------------------------------------->
-
-### Patient and public involvement
-
-Patient and public members were intended to be involved at this poit
-
-<!----------------------------------------------------------------------------->
-
-### Deviations from the protocol
-
-A dose response meta-analysis was not planned, marking a departure from the registered protocol. <!-- TODO Check this is accurate -->
-
-Similarly, there was initially no intention to try and examine the risk of bias due to missing evidence.
-
-## Results
-
-<!----------------------------------------------------------------------------->
-
-### Search and screening results
-
-Following the search
-
-`r num_to_text(23447,T)` records were identified through database searches. Following depulication, `r num_to_text(16109)` unique records remained.
-
-<!--- Cross check this with the actual numbers included --->
-
-No eligible records were identified in the screening of the 500 records excluded by the search. Many of these were basic science studies <!-- TODO text -->
-
-<!----------------------------------------------------------------------------->
-
-```{r prisma-flow-setup, include = FALSE}
-```
-
-\blandscape{}
-
-&nbsp;
-
-(ref:prisma-flow-cap) PRISMA Flow diagram illustrating how records moved through the systematic review process.
-The different contributions of databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-\elandscape{}
-
-<!----------------------------------------------------------------------------->
-
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible and the full text records for these were requested and screened.
-\@ref(fig:prisma-flow-fig) <!-- TODO Check these figures -->
-
-<!----------------------------------------------------------------------------->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> shown in Figure \@ref(prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Following screening, XXX studies were included.
-
-The distribution of included studies over time demonstrates that despite the conduct of several previous reviews of different types of literature surrounding this question, primary studies continue to the published as these reviews have yet to provide a definite answer.
-
-&nbsp;
-
-As part of our our forward snowballing exercise (where articles citing an included study are cited), I recorded whether a study included in our review had been included in any previous evidence synthesis attempt in an attempt to qualify the added value of this analysis.
-Additionally, if an included article was subsequently cited by a review, all studies in that review were screened for inclusion for the sake of completeness.
-This analysis was performed by extracting the citing articles from Google Scholar on [DATE] and screening them manually.
-The DOI of articles extracted from this analysis are included in the appendix, as the Google Scholar search functionality is not readily reproducible.*
-
-<!-- TODO Actually do this! -->
-
-<!-- For the snowballing exercise - make sure you don't include studies published after review date: ~ June 2019 -->
-
-As a summary of the duplication of work in this area, Ilooked at how many reviews a single included study had previously been included in.
-
-<!--- TODO Need example table here, showing relevant cells --->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of ~10% of records, illustrating high accuracy.
-
-<!-- TODO Include AC1 result in caption above -->
-
-(ref:agreeInter-scaption) Inter-rater agreement
-
-```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
-
-(ref:agreeIntra-scaption) Inter-rater agreement
-
-```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-For the inter-rater reliability, agreement was very high ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Agreement was similary high for intra-rater reliability ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a heavy imbalance  towards exclusion.[@feinstein1990]
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline versus mild cognitive impairment, and the definition of eligible lipids fractions.
-
-Additionally, records I excluded on my second viewing (n=`r discrepancy_Intra`) were investigated. All were . . .
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies
-
-XXXX studies met the criteria for inclusion in the review.
-
-Table \@ref(tab:studyCharacteristics-table) shows the characteristics
-
-&nbsp;
-
-\blandscape{}
-
-<!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) studyCharacteristics
-
-(ref:studyCharacteristics-scaption) studyCharacteristics
-
-```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-\elandscape{}
-
-As shown in
-
-<!--- TODO Figures and tables to include here:
-
--   PRISMA Flowchart (done)
-
--   Summary of types of study (half done)
-
--   Summary of locations (half done)
-
--   Summary of diagnostic criteria used (done)
-
--   Summary of risk of bias (not done)
-
---->
-
-<!----------------------------------------------------------------------------->
-
-```{r cohortLocationsSetup, include = FALSE}
-
-```
-
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
-
-(ref:cohortLocations-scap) Geographical distribution of study cohorts
-
-```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Many of the included studies were conducted in European countries (Figure \@ref(fig:cohortLocations).
-
-A common theme across the studies was a lack of data on vascular dementia.
-This is particularly interesting as lipids and statins are primarily a vascular disease.
-There is the potential that they studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading).
-For vascular dementia, few studies examined this outcome, primarily because of the absence (until recently) of
-
-<!-- IDEA Could include a second evidence synthesis map here to summarise Table 1, highlighting the lack of vascular dementia outcomes and the massive amount of observational data -->
-
-One item of particular interest in the absence of studies examining Mendelian randomisation studies is the absence of any effect following the adjustment for Apoe4.
-As covered in the discussion, ApoE4 genotype is the mjor risk factor for Alzheimer's disease.
-
-<!-- TODO Could extract before and after adjusted for ApoE4 to illustrate -->
-
-In addition, there was quite a spread in terms fo the effect estimates used to th. Previous systematic review
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias {#risk-of-bias-subheading}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Meta-analysis of statin use and hypercholesteroleamia
-
-Straight-forward random effects meta-analysis of binary exposures
-
-```{r primaryFigures, include = FALSE}
-
-```
-
-<!----------------------------------------------------------------------------->
-(ref:fpStatins-cap) __Forest plot showing effect of statins:__
-
-(ref:fpStatins-scap) Forest plot showing effect of statins
-
-```{r fpStatins, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpStatins-cap)', out.width='100%', fig.scap='(ref:fpStatins-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/forester_statins_any.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Dose response meta-analysis of lipid levels
-
-<!-- TODO Cite excluded studies and list exclusion reasons  -->
-
-Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls be
-
-<!-- TODO Include image -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Sources of heterogeneity
-
-Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]**
-
-Important here to examine effect of risk of bias (due to immortal time in observational studies).
-
-Also important to examine the effect of:
-
-* age at baseline
-* sex (percentage)
-* education
-* baseline cognitive scores (how to group)
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Publication bias {#sys-rev-pub-bias}
-
--   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were
--   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult
-
-One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across
-
-Many studies did not report the codelists used to run the analysis,
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Triangualtion across evidence sources
-
-<!-- TODO Have a look at this - potentially move to triangulation chapter -->
-
-One key question for which multiple distinct sources of evidence were available were those looking at Laz
-
-A key limitation for other types of dementia, in particularly vascular, is that there has yet to be a GWAS identifying relevant SNPS that could then be used in a MR study with SNPS for lipids to estimates the causal effect of lipids on vascular dementia [**Is this true?**] This rules out the use.
-In addition, there was limited literature available - as discussed in CHapter \@ref(sys-rev)
-
-Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
-For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011]
-
-Without our framework and as part of the risk of bias assessments reported in \@ref(risk-of-bias-subheading), Itest test
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Added evidental value of including preprints {sys-rev-including-preprints}
-
-<!-- TODO Will have to get actual numbers for this section -->
-
-There were several relevant preprints captured by the search run using the tool presented in Chapter \@ref(sys-rev-tools-heading) (see Appendix \@ref(appendix-medrxivr-code)).
-While many of the preprints included were subsequently published by the time of submission of this thesis, at the time of the search they were only available
-
-Good example is [https://doi.org/10.1101/168674](https://doi.org/10.1101/168674), which was subsequently published in Nature Comms but in 2020, following peer-review (found no impact of LDL-c on AD following removal of APOE4).
-
-Of interest,
-
-<!-- TODO Triple check whether any of the studies have yet to be published. Chose a given date and go from there -->
-
-This likely reflects a bias in the type of study that is submitted, but indicates the additional evidential value of include preprints in the search strategy.
-It also means that searches are current - if the aim of systematic reviews is to
-
-While the total number of relevant studies found using this method was
-
-<!-- Can I explore the amount of information added by the preprints quantiatively using the weights in the meta-analysis -->
-
-<!-- Add bit on comparison of preprints and published papers, demonstrating the preprints are a good reflection of -->
-
-On further investigation, the argument that .
-
-It is not so much that they provide a source of unpublished grey-literature, more so that they provide a "future" look at .
-
-However, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a requirement.
-
-While concerns have been raised that
-
-Previous meta-studies have found high concordance between the main interpretations and other study design details in preprint-journal article pairs,[@shi2021] though quality of reporting was slightly better in formally published articles.[@carneiro2020]
-
-A common criticism of preprinted articles is that they have not formally been peer-reviewed. __[CITATION NEEDED]__ <!-- TODO See Chapter 1 for reference for this quote. -->
- However, I believe this criticism is less warranted in the context of inclusion of preprints in a systematic review, given a formal assessment of risk of bias, which provides a structured approach to assessing the internal validity of a study.
-
-> Anyone who can't assess a study to the level of peer review shouldn't do a systematic review
-
-References included in the review were also searched for on PubPeer, a platform which enables post-publication peer review of published journal articles.[@hunter2012]
-
-The added value of peer-review to papers that is questionable and difficult to quantify for a number of reasons, including the fact that most peer reviews are closed
-
-While `r hold()` preprint have subsequently been published, this does not cause any major issues.
-
-### Risk of bias due to missing evidence
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion
-
-Major limitation is that several included studies used data from electronic health databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018]
-
-In addition, the a
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Summary of findings
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Previous reviews
-
-<!-- TODO Not sure this is the best place for this -->
-
-**Will need to include something in the methods section on this**
-
-As part of this analysis, Iexamined the overlap between different published reviews on this topic.
-
-Several primary studies were captured in multiple systematic reviews. However, some studies were not captured by any previous review,
-
-<!-- IDEA Put upSet plot here - though this will likely now be in Georgia's dissertation -->
-
-An upset plot shows the total size of each set (in this case, the set of included studies in each review) in the bottom left hand bar plot. For example, the XXXX review includes XXXX studies.
-
-Where a line joins two points in the matrix, the main barchart shows the number of records shared by these reviews.
-So for example, XXXX records were captured both by the XXXX review and the XXXX review.
-
-Where the matrix has just a single point highlighted, this shows the records unique to that review.
-
-The reviews are ordered by date, to attempt to show the increasing overlap and total number of studies
-
-Our review is presented as the last point on this plot, and captured XXXX records
-
-The alternative is to have a barplot showing the total cumulative number of records over the years, using our set as the master, with the bars coloured by the number of records included in 1/2/3/4 reviews.
-The information below the bar axis could then show the number of reviews published in that year, or alternative, you could have an upsidedown bar to show cumulative number of reviews on this topic.
-
-<!--- Take a stand here! --->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk and putatively provides no evidence for an effect of the statin on dementia outcomes.
-While widely cited and included in the Cochrane review on this topic, it has not been included here, for the reason that it only reported the change from cognitive score (as measured using the [CHECK] scale) over a mean follow-up.
-While this is a useful indicator of general cognitive decline, it is not equivalent to a dementia outcome, as cogntive scales should feed into a broader diagnostic pathway - See section \@ref(diagnostic-criteria)
-
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-
-Does it also cause issues in terms of self-report?
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-Of note, as part of the review, Iidentified several previous systematic reviews of this topic.[CITE] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools. Newcastle-Ottowa scale,
-
-**The duplication of work across reviews (including, ironically, by this review) is substantial.
-In Section XXXX, I demonstrated that the each primary study included in this review was also included in other review so this topic, but that not all studies were included in all reviews.
-However, by creating a comprehensive review that attempted to draw together all available evidence from across the full range of study types.**
-
-__Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
-
-<!-- TODO Will hopefully be able to cite MSc review here to give details of other reviews -->
-
-In retrospective, an alternative approach to the one taken could have been employed, performing an review of reviews, also known as an umbrella review.
-In these studies, the unit of analysis are systematic reviews rather than the
-
-However, a comparative analysis between indicates
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Comments on the process
-
-As part of the reflective element of this thesis, I collated my experiences on performing a systematic review.
-
-Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk of bias assessments, inclusion of all literature, searching for other reviews) is foolish.
-
-Average time to complete a s
-
-However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. <!-- TODO CITATION NEEDED - Cite Triccios new paper here -->
-
-Great learning experience in terms of managing a team, but due to a rotating schedule of people, much harder to do that expected.
-
-A final point on the progress of the review is that, due to the need for dual screening and data extraction, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging and could definitely have improved the process through better communication of deadlines, but it has provided good experience of leading a review team.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Inclusion of preprints
-
-As highlighted in Section \@ref(diverse-sources-preprints), this thesis explicitly sought to synthesize evidence across different publication statuses, predominantly preprinted vs published.
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
-
-The added evidential value of including these preprints was highlighted in Section \ref()
-
-On further investigation, X of these preprints were subsequently published since the search was performed in 2019.
-While this provides some additional evidence that the quality of the research described by included preprints was sufficiently high to pass peer-review, it does not invalidate the approach, as the future publication status was unavailable at the time the search was conducted.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As evidenced by the issues involved in obtaining
-
-Building in part on the research, I co-wrote an guidance piece for pre
-
-Similarly, a substanital amount of time and effort has gone into making the data obtained by this review openly available to
-
-<!--- How many of the included studies accurately reported the diagnostic criteria for EHR? Cross link with section in CPRD analysis --->
-
-<!--- Comment here on issues involved in extracting data --->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Strenghts and limitations
-
-I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-
--   *Structured risk of bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter 3, this review systematically searched preprinted health-related manuscripts as a source of grey literature.
-As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
-
-- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
-This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
-IN addition this review was used to pilot an upcoming risk of bias tool
-
-&nbsp;
-
-#### Limitations
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Reviewing Mendelian randomisations studies
-
-<!-- Three things to cover: No good tools for dealing with MR studies yet (particularly search filters, as terminology is hard + no risk of bias tool); Is double counting of studies an issue (maybe speak to George, particularly if you can find an example)  -->
-
-<!-- TODO Email George with query on dual counting, following review of email with Julian -->
-
-While
-
-This may be because Mendelian randomisation studies have yet to reach a critical mass in terms of requiring a systematic review.
-
-Recent updates, such as a guide to reading and interpreting Mendelian .
-
-However, this guide includes reporting items in their quality checklist - reporting quality while important, is unrelated to internal validity.
-
-Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants
-
-Double-counting of other -
-
-Methods for reviews of Mendelian randomisation studies are not well developed to account for the consideration above.
-
-In short, given the recent developments in the production of studies and results from Mendelian randomisation
-
-This is particularly relevant to missing evidence, as new methods in MR studies allow for the anlysis of many exposures/outcomes concurrently.
-In this scenario, missing evidence is likely to be an issue as onyl those of particular interest to the authors/those reaching statistical significance will be reported in the paper
-
-This is highlighted by the identification of studies relevant to the review though coincidental reading and citation searhcing, that were not identified by the search as they reported many results and only the statistically significant ones were included in searchable fields
-
-This is particularly troubling given the comprehensiveness of the search (~17,000 records screened).
-In retrospect, a mitigating approach may have been to have an additional search for topics related to risk factors, dementia and MR studies, and screened t
-
-<!-- TODO Best option probably to highlight that while these studies were included, it was not easy given a lack of resources for MR studies -->
-
-As a form of analysis that lends itself to multiple comparison, there is a strong
-
-Through snowballing and other measures, I identified at least one Mendelian randomisation study that had not been identified by the search strategy.
-[@larsson2017b] On review of this paper, the search would not have been expected to find it, given the absence of any lipid-related keywords in the title and abstract.
-
-The study examined the association between lipid fractions with Azlheimer's disease, as one of many risk factors for AzD.
-Studies such as this can introduce bias, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by systematic reviews of the topic.
-This may bias reviews as the analysising multiple risk factors at a time becomes more common.
-
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's"),
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Is it a big issue that the studies have the same underlying datasets? <!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
-
-Potentially the use of methods such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should cpature similar studies. 
-However, in future better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Strengths and limitations
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-#### Inclusion of preprints
-
-Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
-they would not have been captured by the search for published papers)
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Use in other chapters
-
-<!--- IDEA Findings from this chapter are used throughout the later chapters of this thesis.
-In particular, Chapter 6 uses statistical modelling to exploring the impact of BCG vaccination on TB outcomes in greater detail, Chapter 7 explores the impact of the change in BCG vaccination policy on TB incidence rates using the incidence rate estimates from this chapter, Chapter 8 uses the understanding of the ETS gained from this chapter to parameterise a dynamic TB transmission model, and Chapter 9 uses the insights gained into the date variables in the ETS to fit a dynamic TB transmission model.
-From Sam abbotts--->
-
-Findings from this review are used though out the subsequent chapters.
-
-For example,
-
-## Conclusions
-
-In this chapter I have
-
-This work built on the tool introduced in the preceeding chapter, and the results from the systematic review are used in further chapters.
-
-In Chapter \@ref(cprd-analysis-heading), 
-A summary of the evidence guided the
-
-In Chapter \@ref(ipd-heading),
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of -->
-
-A
-
-\newpage
-
-## References
-
-<!--chapter:end:03-Chp-Systematic-Review.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
 
@@
 
+Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
+
+\blandscape
+
+<!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary
+
+(ref:followUp-scaption) followUp
+
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+\elandscape
+
 The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
@@
 
+<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
+
+<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
+
 ## Discussion
@@
 
+<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
+
 This section will expand on a potential explanation for the observed results detailed above.
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(hold)) and the individual patient data analysis (Chapter \@ref(hold)), see Section \@ref(hold).
+For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
 
@@
 
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/05-Code-IPD-Analysis.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
 ## Lay Summary
 
+As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ## Introduction
@@
 
+Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ## Methods
 
-As part of the IPD analysis, relevant cohort studies were identified from the sty and approached. In the first instance, the corresponding author on the main man
+### Applying for data access
+
+__Systematic review__
+
+As part
+
+As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
+In the first instance, the corresponding author on the main man
+
+__Dementia platform UK__
+
+In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
+In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
 
@@
 
-Talk about missing data was handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Data sources
-
-Several cohort studies were approach
-
-<!-- Need exact number approach -->
-
-As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.
-
-Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get
-
-Each should have:
-
-* Description (including observation period, numbers, numbers with outcome, etc)
-* Whether they are a known genetically at-risk cohort
-*
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+### Eligibility criteria
+
+Lipids reported/available as a continuous measure, and were not cross-sectional.
+
+Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
+The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
+
+<!-- TODO Read this[@riley2020] -->
+
+### Missing data
+
+Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Risk of bias assessment
+
+Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
+
+There is some concerns about performing risk of bias assessments on your own analysis, and so
+
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Analysis
+
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
+<!-- TODO Figure showing the outline of interval censored studies. -->
+
+All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
+
+Similary,
+
+Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+
+Stratified by age-at-entry and sex, and ethnicity where possible.
+
+Hazard ratios were utilised to
+
+In order to investigate the interaction of sex with
+
+A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
+
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
+
+In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
+These were extracted and synthesised using a random effects meta-analysis.
+
+Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.
+
+The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]
+
+__Replicating published findings__
+
+Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Results
+
+### Data access
+
+<!-- Need exact number from each approach, plus detailed exclusion reasons -->
+
+Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
+Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
+
+In addition, the reasons for cohorts not being included in the analysis are presented.
+In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+
+For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th
+
+<!----------------------------------------------------------------------------->
+```{r cohortFlowchartSetup, include = FALSE}
+```
+
+(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
+
+(ref:cohortFlowchart-scap) Flowchart
+
+```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
+knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.
+
+I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
+
+As highlighted in the
+
+### Included data sources
+
+The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
+
+Of note, all data sources included in the analysis were based in the United Kingdom.
+This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:cohortOverview-caption) Summary of cohorts for which data were available
+
+(ref:cohortOverview-scaption) Summary of included cohorts
+
+```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->
+
+<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Caerphilly Prospective Study
+
+The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
+
+Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
+As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### CPRD
+
+The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+
+The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
+
+Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
+
+Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
+
+the
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Different approaches to combining subgroups. [@fisher2017]
-
-Several DPUK cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
-
-See
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-<!--- Inlcude CPRD analysis here, but dou --->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Data cleaning
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Whitehall II
+
+_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
+Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
+
+This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]
+
+This gave
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Cohorts provided data but ultimately excluded
+
+As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
+
+Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
+
+The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+
+__BRACE__
+
+Likley had dementia at baseline
+
+__Memento__
+
+Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
+
+__Generation Scotland__
+
+Cross-sectional data only
+
+__NICOLA__
+
+NICOLA study - only had cross-sectional data
+
+__ELSA__
+
+Data provided but only had ever high cholesterol as a binary variable. Not compatible with
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:dataExcluded-caption) dataExcluded
+
+(ref:dataExcluded-scaption) dataExcluded
+
+```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+### Cohorts identified the systematic review but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+Electronic health record co
+
+LBC - 1936
+
+Taiwan etc,
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Cohorts approach but received no answer
+
+A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
+Despite multiple attempts to contact the team, there was no response received.
+
+<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Data cleaning and harmonisation
+
+Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
+
+The one exception to this is the CPRD data, which was held in a different system to the rest.
+
+The advantage of this approach is that it reduces the liklihood of errors in model mis-speciication if needing to change variables names from cohort to cohort.
+
+For all cohorts, the first lipid measurement was used for the exposure method,
+
+For heterogeneity across the cohorts, the total time-at-risk was investigated.
+
+<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
 
@@
 
-Letters sent to all cohorts identified through the systematic review - will need quite a bit here on the numbers approached and how they responded if at all.
-Will also need to comment on the additional tactics used.
+Useful citation for discussion[@levis2021]
+
+### Limitations
+
+#### Low response rate to request for data
+
+<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
+
+This review had a low response rate to requests for data access.
+
+While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
+test
+There are likely several reasons for this.
+
+* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
+
+* While there is no
+
+For many other reasons also - if
+
+A potential further reason was highlighted during my attendance at the
+
+Letters sent to all cohorts identified through the systematic review 
+<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
 
@@
 
-As part of this, an analysis of
-
-### Reflections on data access
+The low response rate and the
+
+Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
+
+<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
+The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
+Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
+However, analysis combining individual and study level data may mitigate these effects [3, 21].
+from [@ventresca2020a] -->
+
+For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
+
+On a personal level, given the
+
+In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Resources
+
+While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
+
+Given the resource intensity of data cleaning and harmonisation,
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Data access
+
+Couple of sections
+
+* Problems with getting data from studies
+*
+
+Sharing data has several legal, ethical and logistical challenges, and can often
+
+This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
 
@@
 
+Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
+
+Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Study within a review
 
-In future, it could have been worth running a "study within a review", such as that used to examine whe
-
-https://bmjopen.bmj.com/content/9/1/e025273
+In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
+
+Options could include
+
+Previous SWARs have been registered as protocols, but have not yet reported!
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reflections on the process
+
+May have been overly ambitious
+
+\newpage
+
+## References
 
 <!--chapter:end:05-Chp-IPD-Analysis.Rmd-->
+
+---
+#########################################
+# options for knitting a single chapter #
+#########################################
+output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::word_document2: default
+  bookdown::html_document2: default
+documentclass: book
+---
+
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
+
+<!-- TODO Add this to the Chapter summary in the introduction and  -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- ### Triangulation across evidence sources -->
+
+<!-- TODO Have a look at this - potentially move to triangulation chapter -->
+
+<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
+
+<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
+For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
+[@guyatt2011] -->
+
+<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+-->
+
+# Triangulation {#tri-heading}
+
+## Lay Summary
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Introduction
+
+This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)
+
+### Data sources
+
+This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
+
+<!----------------------------------------------------------------------------->
+
+### Background to the causal question
+
+Following best practice guidance, three
+
+Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
+
+This was also guideded by the forthcoming ROBINS-E tool, which has
+
+<!----------------------------------------------------------------------------->
+
+### Definition of the causal question
+
+<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
+
+### Summary of triangulation
+
+Need to check how much I talk about this in the introduction
+
+Describe in detail
+
+### Risk of bias tool
+
+In addition, the tool also aim to capture the potential direction of bias for each result.
+Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
+Highlight that this is slightly different for the confounding domain in non-randomised studies.
+
+These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Graphical representation
+
+For the graphs, the direction of bias is important.
+
+Where the direction of bias was unclear/could not be determined from the report, this is indicated
+
+In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
+The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
+
+Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
+Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
+non-differential misclassification).
+In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
+For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
+In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
+If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
+
+These graphs were built using the risk of bias tool described in Appendix \ref()
+
+<!-- TODO Does immortal time bias not also have a consistent effect -->
+
+<!----------------------------------------------------------------------------->
+
+### Standardisation across study designs
+
+Standardising across different measures of ex
+
+Want best information across lipids, and so standardised across differnt measures
+
+Fixing directions of effect - get everything pointing the same way
+
+<!----------------------------------------------------------------------------->
+### Analyses
+
+Bias-adjusted meta-analysis [@higgins2008a]
+
+<!----------------------------------------------------------------------------->
+
+## Results
+
+Summary of risk-of-bias/triangulation results
+
+Percentage of domains for which a direction of bias could be assigned?
+
+Compare bias-adjusted and
+
+See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
+
+Applicability/indirectness as an issue 
+Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
+
+<!----------------------------------------------------------------------------->
+
+## Discussion
+
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+
+### Challenges of real-life data
+
+Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
+ALso highlight the issue with assigning a direct of bias in many studies
+
+### Need for new methods
+
+Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
+
+<!--chapter:end:06-Chp-Triangulation.Rmd-->
 
@@
 
-&nbsp;
-<!----------------------------------------------------------------------------->
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Qualitative vs qunatitative triangulation
+
+### Researcher positionality statement
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-&nbsp;
-<!----------------------------------------------------------------------------->
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
+---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
+output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
+  bookdown::html_document2: default
+documentclass: book
+---
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/doc_options.R")
+source("R/helper.R")
+knitr::read_chunk("R/03-Code-Systematic-Review.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
+<!--chapter:end:tmp.Rmd-->
+
 `r if(!knitr:::is_latex_output()) '# Bibliography {-}'`
@@
 
-This thesis was written in RMarkdown.
-Several R packages were used as part of this project.[@base; @cranlogs; @dplyr; @flextable; @ggplot2; @glue; @gt; @here; @kableExtra; @knitr; @medrxivr; @plyr; @robvis; @stringr; @tidyverse; @wordcountaddin; @xfun; @rbiorxiv]
-
+```{r, include = FALSE}
+knitr::write_bib(c(.packages(), "bookdown", "knitr"), here::here("bibliography/packages.bib"))
+```
+
+This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
 All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]

### 2021-09-28 R/03-Code-Systematic-Review.R

@@ -177,7 +177,7 @@ if(doc_type == "docx") {
 }
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- studyCharacteristics-table
+# ---- characteristicsSetup
 
 toc_df <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which = 1) %>%
   janitor::clean_names() %>%
@@ -185,20 +185,16 @@ toc_df <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which
   select(study_id, author, year, number_participants, subtype, age_at_baseline, female_percent, location, data_source, group_sizes_if_applicable) %>%
   mutate(type = subtype) %>%
   mutate(author = ifelse(grepl("Heart Protection",author),"HPS",author)) %>%
-  mutate(age_at_baseline = stringr::str_remove_all(age_at_baseline," "),
-         female_percent = stringr::str_remove_all(female_percent," "),
-         group_sizes_if_applicable = stringr::str_remove_all(group_sizes_if_applicable," ")) %>%
+  mutate(group_sizes_if_applicable = stringr::str_remove_all(group_sizes_if_applicable," ")) %>%
   rowwise() %>%
   mutate(age_combo = ifelse(grepl("\\|",age_at_baseline),combine_age(age_at_baseline,group_sizes_if_applicable), age_at_baseline)) %>%
   mutate(female_combo = ifelse(grepl("\\|",female_percent),combine_female(female_percent,group_sizes_if_applicable), female_percent)) %>%
   mutate(female_combo = case_when(female_combo=="64.400000000000006"~"64.4", T ~ female_combo),
          age_combo = case_when(age_combo=="74.900000000000006"~"74.9", T ~ age_combo))
 
-
-# toc_df %>%
-#   filter(is.na(exclude)) %>%
-#   distinct(study_id,.keep_all = T) %>%
-#   count()
+n_included <- toc_df %>%
+ distinct(study_id,.keep_all = T) %>%
+  n_distinct()
 
 toc_df2 <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which = 2) %>%
   janitor::clean_names() %>%
[…]

### 2021-09-28 R/05-Code-IPD-Analysis.R

@@ -1,3 +1,6 @@
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# primaryFigures ----
+
 tmp <-
   read.csv(
     "data/ipd/ipd_age_sex.csv",
@@ -30,3 +33,121 @@ forest_save <- function(data, lipid) {
 }
 
 purrr::map2(.x = tmp$data, .y = tmp$lipid, ~ forest_save(.x, .y))
+
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- dataExcluded-table
+
+dataExcluded_table <- read.csv(here::here("data/ipd/dataExcluded.csv"), stringsAsFactors = F) %>%
+  arrange(Cohort)
+
+if (doc_type == "docx") {
+  apply_flextable(dataExcluded_table, caption = "(ref:dataExcluded-caption)")
+} else{
+  knitr::kable(
+    dataExcluded_table,
+    format = "latex",
+    caption = "(ref:dataExcluded-caption)",
+    caption.short = "(ref:dataExcluded-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"))
+}
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- cohortFlowchartSetup
+
+library(DiagrammeR)
+
+graph <- grViz(diagram = "digraph cfa {
+      # define node aesthetics
+      node [fontname = Arial,fixedsize = true,width = 3.5, height = 1.5,color = 'black',shape = rectangle, fontcolor = black] 
+      
+      tab0 [label = <<font> <b>Systematic review</b>  </font>>, height = 1, color = 'grey90',shape = rectangle, style = filled, fontcolor = black]
+      tab1 [label = <<font> <b>Systematic review + DPUK </b>  </font>>, height = 1, color = 'grey90',shape = rectangle, style = filled, fontcolor = black]
[…]

### 2021-09-29 front-and-back-matter/_00-introduction.Rmd
Back to working version General clean-up Proper counting of words included in tables

@@
 
-get_words_short <- function(){
-
-files <- list.files(path = here::here(), pattern = "\\.Rmd$")
-
-files <- files[which(!(files %in% c("_main.Rmd","index.Rmd")))]
-
-words_v <- c()
-
-for (file in 1:length(files)) {
-  tmp <- wordcountaddin::word_count(here::here(files[file]))
-  words_v <- c(words_v, tmp)
-}
-
-words <- sum(words_v)
-
-return(words)
-
-}
-
-get_words <- function(){
-
-files <- list.files(path = here::here(), pattern = "\\.Rmd$")
-
-files <- files[which(!(files %in% c("_main.Rmd","index.Rmd", "tmp.Rmd")))]
-
-words_v <- c()
-
-for (file in 1:length(files)) {
-  tmp <- wordcountaddin::word_count(here::here(files[file]))
-  words_v <- c(words_v, tmp)
-}
-
-# TODO Work out what an appropriate number of words for tables is
-# Sum words and add number of words in tables
-words <- sum(words_v) + 250
-
-date <- as.character(format(Sys.time(),"%Y%m%d"))
-time <- as.character(format(Sys.time(),"%H%M"))
-
-tmpWords <- data.frame(words = words,
-                       date = date,
-                       time = time)
-
-masterWords <- read.csv(here::here("data","words","words.csv"),
-                        header = TRUE)
-
-masterWords <- rbind(masterWords,
-                     tmpWords) %>%
-  dplyr::group_by(date) %>%
-  slice(which.max(time)) %>%
-  dplyr::ungroup()
-
-return(masterWords)
-
-}
+source(here::here("R/helper.R"))
 
 words <- get_words()
+
+table_words <- table_words()
 
@@
 
+Table words: `r table_words`
+
 Days: `r date_diff`

### 2021-09-29 R/03-Code-Systematic-Review.R

@@ -77,7 +77,8 @@ gwet_table <- data.frame(
     "Strong",
     "Almost perfect"
   )
-)
+)  %T>%
+write.csv("data/table_words/gwet.csv")
 
 if(doc_type == "docx") {
   knitr::kable(gwet_table, caption = "(ref:gwet-caption)")
@@ -109,7 +110,8 @@ discrepancy_Inter <- agreeInter_table$Exclude[2]
 
 agreeInter_coeff_table <- agreeInter_table[1:2,2:4]
 rownames(agreeInter_coeff_table) <- agreeInter_coeff_table[,1]
-agreeInter_coeff_table <- agreeInter_coeff_table[-1]
+agreeInter_coeff_table <- agreeInter_coeff_table[-1] %T>%
+  write.csv("data/table_words/agreeInter.csv")
 
 agreeInter_coeff <- unlist(c(comma(irrCAC::gwet.ac1.table(agreeInter_coeff_table)[2]),
                              comma(irrCAC::kappa2.table(agreeInter_coeff_table)[2])))
@@ -125,7 +127,8 @@ discrepancy_Intra <- agreeIntra_table$Exclude[2]
 
 agreeIntra_coeff_table <- agreeIntra_table[1:2,2:4]
 rownames(agreeIntra_coeff_table) <- agreeIntra_coeff_table[,1]
-agreeIntra_coeff_table <- agreeIntra_coeff_table[-1]
+agreeIntra_coeff_table <- agreeIntra_coeff_table[-1] %T>%
+  write.csv("data/table_words/agreeIntra.csv")
 
 agreeIntra_coeff <- unlist(c(comma(irrCAC::gwet.ac1.table(agreeIntra_coeff_table)[2]),
                              comma(irrCAC::kappa2.table(agreeIntra_coeff_table)[2])))
@@ -193,7 +196,7 @@ toc_df <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which
          age_combo = case_when(age_combo=="74.900000000000006"~"74.9", T ~ age_combo))
 
 n_included <- toc_df %>%
- distinct(study_id,.keep_all = T) %>%
+  distinct(study_id,.keep_all = T) %>%
   n_distinct()
 
 toc_df2 <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),which = 2) %>%
@@ -253,7 +256,8 @@ studyCharacteristics_table <- study_details %>%
   tidy_nums() %>%
[…]

### 2021-09-29 R/04-Code-CPRD-Analysis.R

@@ -48,7 +48,8 @@ p1 <- p1[order(p1$outcome), ]
 readExample_table <-
   read.csv(here::here("data", "cprd", "read_code_example.csv")) %>%
   dplyr::mutate("Read code" = Read.code) %>%
-  dplyr::select("Level", "Read code", "Term")
+  dplyr::select("Level", "Read code", "Term") %T>%
+  write.csv("data/table_words/readExample.csv")
 
 if (doc_type == "docx") {
   apply_flextable(readExample_table, caption = "(ref:readExample-caption)")
@@ -119,7 +120,8 @@ if (t[1] - sum(t[2:9]) != 0) {
 table1_disp[1,2:9] <- stringr::str_trim(comma(as.numeric(table1_disp[1,2:9])))
 
 # Create display table using kable
-cprdCharacteristics_table <- comma(table1_disp)
+cprdCharacteristics_table <- comma(table1_disp) %T>%
+  write.csv("data/table_words/cprdCharacteristics.csv")
 
 if (doc_type == "docx") {
   apply_flextable(cprdCharacteristics_table, caption = "(ref:cprdCharacteristics-caption)") %>%
@@ -178,7 +180,8 @@ if (doc_type == "docx") {
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- cprdSSA-table
 
-cprdSSA_table <- table1[19:21, -3]
+cprdSSA_table <- table1[19:21, -3] %T>%
+  write.csv("data/table_words/cprdSSA.csv")
 
 if (doc_type == "docx") {
   apply_flextable(cprdSSA_table, caption = "(ref:cprdSSA-caption)")
@@ -1224,7 +1227,8 @@ statinTypeTable_table <-
   mutate(Hydrophilic = paste0(Hydrophilic, "%)")) %>%
   mutate(Lipophilic = paste0(Lipophilic, "%)")) %>%
   rename("Total" = V6) %>%
-  rename("Prescription Year Group" = V1)
+  rename("Prescription Year Group" = V1) %T>%
+  write.csv("data/table_words/statinType.csv")
 
 if (doc_type == "docx") {
   apply_flextable(statinTypeTable_table, caption = "(ref:statinTypeTable-caption)")
@@ -1410,7 +1414,8 @@ diagnosisType_table <-
[…]

### 2021-09-29 05-Chp-IPD-Analysis.Rmd
Back to working version General clean-up Proper counting of words included in tables
End of day:

@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
 output:
@@
 
+### Eligibility criteria
+
+Eligible data sources were defined as those that contained lipid measurements and  ipids reported/available as a continuous measure, Data sources which were cross-sectional, either by design or due to the available data (e.g.
+a study conducted multiple waves, but onyl data from a single wave could be accessed) were excluded.
+Similarly, due to the limited time-frame, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
+The one exception to this was data from the CPRD, which I already had access to as part of the analysis reported in Chapter \ref(cprd-heading).
+
+<!-- TODO Read this[@riley2020] -->
+
 ### Applying for data access
@@
 
-As part
+As part of the IPD analysis, eligible observational prospective cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were approached for data access.
 
-As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
-In the first instance, the corresponding author on the main man
+In the first instance, the first author on the main study report was emailed (see Appendix \@ref() for a copy of the text and documentation sent).
+If this did not elict a response, the last/corresponding author was contacted, on the basis that the first author may have been a more junior member.
+
+examining the effect of lipid levels
 
@@
 
+In addition, in an attempt to supplement the analysis with
+
 In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
+In short, this approach is intended to make it easier to access data from existing dementia cohorts through a centralised application process.
 
-Talk about how different covariates were managed across cohorts,
-
-### Eligibility criteria
-
-Lipids reported/available as a continuous measure, and were not cross-sectional.
-
-Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
-
-<!-- TODO Read this[@riley2020] -->
-
-### Missing data
-
-Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-There is some concerns about performing risk of bias assessments on your own analysis, and so
+Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
 
@@
 
+### Missing data
+
+<!-- TODO This was taken from Chapter 4, so may need to rephrase slightly -->
+<!-- IDEA See Sean's thesis for some additional detail on this -->
+
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the XXX command in R.
+
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
+
+<!-- TODO Need to talk about how missing variables were handled across studies -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
 ### Analysis
 
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
+_Individual patient data approached__
 
-&nbsp;<!----------------------------------------------------------------------->
+Two stage versus one-stage approach
+
+A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
+
+__Statistical methods__
+
+Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
+A common model, adjusted for identical covariates, were obtained using a common model.
+
+To aid interpretability of the outcome, all analyses were standardised by changes in 1-SD of the exposure variable.
+Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+
+Hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017]
+
+The estimates from each data source were then combined using a random-effects meta-analysis
 
@@
 
-All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
+&nbsp;<!----------------------------------------------------------------------->
 
-Similary,
-
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Stratified by age-at-entry and sex, and ethnicity where possible.
-
-Hazard ratios were utilised to
-
-In order to investigate the interaction of sex with
-
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
-
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
+__Investigating effect of patient-level covariates__
 
@@
 
-Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.
-
-The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
+Where an included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
+If discrepancies were identified, these were investigate.
+
+__Combining published aggregate data and individual participant data__
+
+Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the agregate date and individual data were combined.
+
+<!-- TODO Need more on this method here -->
+
+__Author statements on data availability__
+
+As a sensitivity analysis, I examined the data sharing statements for each using a predefined categories used in a similar previous analysis.[@mcguinness2020DAScomparison]
+
+<!-- TODO This should have a plot showing how many over time had good vs bad DAS -->
+
+<!-- TODO In addition, need plot similar to study design over time in Chapter 3, showing cohort responses over time -->
 
@@
 
-For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th
+For the streamlined DPUK process, where a dedicated project manager liaises with cohort owners on the applicants behalf, the overall response rate was higher, resulting in access to three cohorts.
+However, even using this dedicated access approach, a response was obtained for less than half of the approach cohorts
 
@@
 
-I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
+As highlighted in the
 
-As highlighted in the
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
+The four data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
 
@@
 
-<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->
+<!-- TODO Update table with SD for age, and types of outcomes, and follow-up, and check why number of events in EPIC is less than expected (5 vs 8)-->
 
@@
 
-Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
-As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.
+Cholesterol measures (total, LDL-c, HDL-c and triglyceride) were measured at baseline in 1979-1983. 
+As the study population has aged, additional outcomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
 
@@
 
-Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
+Additionally, other number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
 
@@
 
-Has only 8 events
+The added evidental value of the EPIC cohort is small, given the relatively small number of participants and the fact that the cohort has only 8 dementia events.
 
-```{r tests, }
-
+```{r tests}
 ```
@@
 
-This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]
-
-This gave
+This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
 
@@
 
-### Cohorts provided data but ultimately excluded
+### Excluded data sources
+
+#### Cohorts identified the systematic review but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+Electronic health record co
+
+Lothian Birth Cohort - 1936
+
+Taiwan, etc.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Cohorts identified in the DPUK but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+Several additional cohorts are present in the DPUK collection but were not approach with a request for data acccess.
+This was primarily due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
+
+Electronic health record co
+
+LBC - 1936
+
+Taiwan etc,
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Cohorts providing data but ultimately excluded
 
@@
 
-Likley had dementia at baseline
+Likley had dementia at baseline. However, on further investigation of the cohort, it was discovered that
 
@@
 
-### Cohorts identified the systematic review but excluded from the IPD analysis
-
-<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
-
-Electronic health record co
-
-LBC - 1936
-
-Taiwan etc,
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Cohorts approach but received no answer
+#### Cohorts approach but received no answer
 
@@
 Despite multiple attempts to contact the team, there was no response received.
+
+These included studies with  a dedicated access process or data access committee.
+A cohort of particular interest, having been used in multiple studies identified by the systematic review is the Three City Study in France.
+This study was approach at multiple points over the curse of this analysis, and no answer was received.
+
+This was also a problem for cohorts approach via the DPUK - half of the cohorts applied to did not respond to the application within a year.
 
@@
 
-The advantage of this approach is that it reduces the liklihood of errors in model mis-speciication if needing to change variables names from cohort to cohort.
+The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
 
@@
 <!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
+
+# Results
+
+<!----------------------------------------------------------------------------->
+(ref:tcDementiaMain-cap) __Random effects meta-analysis of estimates from included data sources:__
+
+(ref:tcDementiaMain-scap) IPD analysis of total cholesterol and dementia
+
+```{r tcDementiaMain, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:tcDementiaMain-cap)', out.width='100%', fig.scap='(ref:tcDementiaMain-scap)'}
+knitr::include_graphics(file.path("figures/ipd/TC.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
+#### Risk of bias assessment
+
+There is some concerns about performing risk of bias assessments on your own analysis, and so two secondary reviewers
+
+#### Opportunistic inclusion of CPRD data
+
 &nbsp;<!----------------------------------------------------------------------->
 
-### Resources
+### Strengths
 
-While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
+While this analysis did not manage to systematically obtain and analyse a large proporiton of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the - providing additional data points in
 
-Given the resource intensity of data cleaning and harmonisation,
+it also attempted to make use
 
@@
 * Problems with getting data from studies
-*
+* Problems with current methods of tracking people down via .
+Particularly when studies were older, several cases of the address/contact details for the corresponding author being out of date.
+Matches with decrease in availability as the studies get older.
 
-Sharing data has several legal, ethical and logistical challenges, and can often
+__Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases—that when data is requested, it is not actually made available.
+[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014]__ <!-- TODO taken from DAS paper, so will need to change language -->
 
-This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
+Qualitatively, investigation of a subset of cohorts on an _ad-hoc_ basis reveal that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+All of these are arguments towards better reporting of data availability, ownership and
 
-Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
+Even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
+Sharing data has several legal, ethical and logistical challenges, and can often taken several years to obtain.
+This is in theory what the DPUK was built to address.
+However, despite claims to a streamlined process, the response rate among cohorts a year after application was 50%.
+In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
 
-Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
-
-Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+#### Aims/Resources
+
 May have been overly ambitious
+
+While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
+
+Given the resource intensity of data cleaning and harmonisation,
+
+&nbsp;<!----------------------------------------------------------------------->
 

### 2021-09-29 _main.Rmd
End of day:

@@
 
-#### Non-randomised studies of interventions/exposures
+#### Non-randomised studies of interventions/exposures {#rob-tools-nrse}
 
@@
 
-As part
-
-As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
-In the first instance, the corresponding author on the main man
+As part of the IPD analysis, eligible observational prospective cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were approached for data access.
+
+In the first instance, the first author on the main study report was emailed (see Appendix \@ref() for a copy of the text and documentation sent).
+If this did not elict a response, the last/corresponding author was contacted, on the basis that the first author may have been a more junior member.
+
+examining the effect of lipid levels
 
@@
 
+In addition, in an attempt to supplement the analysis with
+
 In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
-
-Talk about how different covariates were managed across cohorts,
-
-### Eligibility criteria
-
-Lipids reported/available as a continuous measure, and were not cross-sectional.
-
-Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
-
-<!-- TODO Read this[@riley2020] -->
+In short, this approach is intended to make it easier to access data from existing dementia cohorts through a centralised application process.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Risk of bias assessment
+
+Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
+
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-There is some concerns about performing risk of bias assessments on your own analysis, and so
-
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
-
-&nbsp;<!----------------------------------------------------------------------->
+<!-- TODO This was taken from Chapter 4, so may need to rephrase slightly -->
+<!-- IDEA See Sean's thesis for some additional detail on this -->
+
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the XXX command in R.
+
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
+
+<!-- TODO Need to talk about how missing variables were handled across studies -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
-
-&nbsp;<!----------------------------------------------------------------------->
+_Individual patient data approached__
+
+Two stage versus one-stage approach
+
+A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
+
+__Statistical methods__
+
+Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
+A common model, adjusted for identical covariates, were obtained using a common model.
+
+To aid interpretability of the outcome, all analyses were standardised by changes in 1-SD of the exposure variable.
+Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
+
+Hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017]
+
+The estimates from each data source were then combined using a random-effects meta-analysis
 
@@
 
-All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
-
-Similary,
-
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Stratified by age-at-entry and sex, and ethnicity where possible.
-
-Hazard ratios were utilised to
-
-In order to investigate the interaction of sex with
-
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
-
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
+&nbsp;<!----------------------------------------------------------------------->
+
+__Investigating effect of patient-level covariates__
 
@@
 
-I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
-
 As highlighted in the
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Included data sources
 
-The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
+The four data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
 
@@
 
-Has only 8 events
-
-```{r tests, }
-
+The added evidental value of the EPIC cohort is small, given the relatively small number of participants and the fact that the cohort has only 8 dementia events.
+
+```{r tests}
 ```
@@
 
+These included studies with  a dedicated access process or data access committee.
+A cohort of particular interest, having been used in multiple studies identified by the systematic review is the Three City Study in France.
+This study was approach at multiple points over the curse of this analysis, and no answer was received.
+
+This was also a problem for cohorts approach via the DPUK - half of the cohorts applied to did not respond to the application within a year.
+
 <!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
@@
 
+#### Risk of bias assessment
+
+There is some concerns about performing risk of bias assessments on your own analysis, and so two secondary reviewers
+
+#### Opportunistic inclusion of CPRD data
+
 &nbsp;<!----------------------------------------------------------------------->
 
-### Resources
+### Strengths
+
+While this analysis did not manage to systematically obtain and analyse a large proporiton of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the - providing additional data points in
+
+it also attempted to make use
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Data access
+
+Couple of sections
+
+* Problems with getting data from studies
+* Problems with current methods of tracking people down via .
+Particularly when studies were older, several cases of the address/contact details for the corresponding author being out of date.
+Matches with decrease in availability as the studies get older.
+
+__Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases—that when data is requested, it is not actually made available.
+[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014]__ <!-- TODO taken from DAS paper, so will need to change language -->
+
+Qualitatively, investigation of a subset of cohorts on an _ad-hoc_ basis reveal that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+All of these are arguments towards better reporting of data availability, ownership and
+
+Even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
+Sharing data has several legal, ethical and logistical challenges, and can often taken several years to obtain.
+This is in theory what the DPUK was built to address.
+However, despite claims to a streamlined process, the response rate among cohorts a year after application was 50%.
+In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Study within a review
+
+In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
+
+Options could include
+
+Previous SWARs have been registered as protocols, but have not yet reported!
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reflections on the process
+
+#### Aims/Resources
+
+May have been overly ambitious
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-
-### Data access
-
-Couple of sections
-
-* Problems with getting data from studies
-*
-
-Sharing data has several legal, ethical and logistical challenges, and can often
-
-This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
-
-Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
-
-Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
-
-Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Study within a review
-
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
-
-Options could include
-
-Previous SWARs have been registered as protocols, but have not yet reported!
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Reflections on the process
-
-May have been overly ambitious
 
@@
 
-<!-- ### Triangulation across evidence sources -->
+<!-- ### Triangulation  -->
 
@@
 
-# Triangulation {#tri-heading}
+# Aetiological triangulation across evidence sources {#tri-heading}
 
@@
 ```
+
+<!-- TODO These citations are not rendering properly - I think because bookdown using this latex format only allows 1 .bib file. -->
 

### 2021-09-29 front-and-back-matter/_00-introduction.Rmd
End of day:

@@
 ```{r word-count, echo=FALSE, warning=FALSE, message=FALSE}
-library(dplyr)
-library(ggplot2)
-
 options(scipen=999)
@@
   scale_x_date(limits = c(as.Date("20201124", format="%Y%m%d"),as.Date("20211231", format="%Y%m%d"))) +
-  geom_step(data = words, colour = "red")
+  geom_step(data = words, colour = "red") +
+  geom_text(aes(x = as.Date("20210910", format="%Y%m%d"), y = 30000, label = "Tables"))
 

### 2021-09-29 R/helper.R

@@ -1,9 +1,11 @@
+# Load key libraries
 library(magrittr)
 library(dplyr)
 library(ggplot2)
 library(patchwork)
 library(metafor)
 
+# Sort out conflicts in function names
 conflicted::conflict_prefer("summarize", "dplyr")
 conflicted::conflict_prefer("filter", "dplyr")
 conflicted::conflict_prefer("last", "data.table")
@@ -14,48 +16,54 @@ library(grDevices)
 extrafont::loadfonts(device = "win")
 grDevices::windowsFonts("Fira Sans" = grDevices::windowsFont("Fira Sans"))
 
-# Load forester function
+# Load forest plotting functions
 source(here::here("R/forester.R"))
 source(here::here("R/forest flexi.R"))
 
+# Make sure plotting device is closed
 try(dev.off())
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# General ----
 
 # Clean output of metafor using sensible defaults
 broom_ma <- function(metafor_obj, exp = TRUE) {
-  return(broom::tidy(
-    metafor_obj,
-    conf.int = TRUE,
-    include_studies = TRUE,
-    exponentiate = exp
-  ) %>%
-    rename("Study" = term) %>%
-    mutate(Study = ifelse(Study == "overall", "Overall",Study),
-           Study = stringr::str_replace(Study,c(".1$",".2$",".3$"),c("a","b","c"))))
+  return(
+    broom::tidy(
+      metafor_obj,
+      conf.int = TRUE,
+      include_studies = TRUE,
+      exponentiate = exp
+    ) %>%
+      rename("Study" = term) %>%
+      mutate(
+        Study = ifelse(Study == "overall", "Overall", Study),
+        Study = stringr::str_replace(Study, c(".1$", ".2$", ".3$"), c("a", "b", "c"))
+      )
+  )
 }
 
 
 # Generates an line pandoc citation string for all packages used in the thesis
-
-gen_rmd_citation <- function(filename = "pkg-refs.bib") {
-  
+gen_rmd_citation <- function(filename = "packages.bib") {
   # Read in bib file
-  pkgs <- readLines(here::here("bibliography",filename))
+  pkgs <- readLines(here::here("bibliography", filename))
   
   # Extract bibtex keys to a string
-  pkg_names <- unique(pkgs[which(grepl("@",pkgs))])
[…]

### 2021-09-30 03-Chp-Systematic-Review.Rmd
End of day:
Back to working version

@@
 
-<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
-
-Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
-
-&nbsp;
+Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009]
 
@@
 Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
+
+Generalisability was aided by the large number of studies performed using the Taiwan health database, which represents a good sources of evidence on non-Caucasian populations -->
 

### 2021-09-30 R/forest flexi.R

@@ -257,13 +257,13 @@ for (i in 1:nrow(dat_rob_vec)) {
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 
-if (length(unique(dat_rob$overall))>1) {
+if (length(unique(dat_rob$overall))>1 && nrow(dat)>2) {
 
 # Fit meta-regression model to test for subgroup differences
 
   if (!hasArg(sei)) {
     
-res <- rma(yi, vi, mods = ~ overall, data = dat)
+    res <- rma(yi, vi, mods = ~ overall, data = dat)
   } else {
     res <- rma(yi, sei=sei, mods = ~ overall, data = dat)
     

### 2021-10-01 03-Chp-Systematic-Review.Rmd
End of day:

--- 2021-09-29 03-Chp-Systematic-Review.Rmd
@@
 
+```{r prisma-flow-setup, include = FALSE}
+```
+
 ## Lay summary
@@
 
-There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
+There were `n_included` primary studies that contained information on this relationship.
 I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
@@
 I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
+In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies (see Appendix \@ref(appendix-medrxivr-code) for the code used to search these preprint repositories).
 
@@
 Participants were screened for dementia at baseline and prevalent cases excluded.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
+Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
 Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
@@
 Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
-assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
+assessment of consistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
 assessment of accuracy).
@@
 
-Gwet's AC1 is defined as:
-
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
-
-In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
-
-\begin{equation}
-  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
-  (\#eq:AC1-main)
-\end{equation}
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-\begin{equation}
-  q = \frac{(A+C)+(A+B)}{2N}
-  (\#eq:AC1-supp)
-\end{equation}
-
-<!-- TODO Need to be sure of how to calculate. -->
-
 How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.
+If this assessment demonstrated issues with the screening process (defined as an AC1 of less than .9), a larger proportion of records would have been dual-screened.
 
@@
 
-#### Risk of bias due to missing evidence
+#### Risk of bias due to missing evidence {#methods-rob-me}
 
@@
 
-Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
+A random-effects meta-analysis model was employed to combine the different included studies.
 <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
@@
 
+Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
+Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate.
+Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
+
+[Do I need to include]
+
+Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$
+
 \begin{equation}
-  \theta_i = \mu + u_i
-  (\#eq:meta-analysis-random)
+  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
 \end{equation}
 
+Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
+There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article.
+The estimate of $\tau^2$ is incorporated into the weighting of each study
+
 \begin{equation}
-  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
-  (\#eq:meta-analysis-fixed)
+  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
 \end{equation}
 
+<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g.
+log-ORs) between studies, with a variance of 𝜏2.
+The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance.
+The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance.
+So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis.
+If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model.
+-->
+<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way.
+The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
+<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
+<!-- (2) -->
+<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
+<!-- (3) -->
+<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->
+
+<!-- \begin{equation} -->
+<!--   \theta_i = \mu + u_i -->
+<!--   (\#eq:meta-analysis-random) -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
+<!--   (\#eq:meta-analysis-fixed) -->
+<!-- \end{equation} -->
+
 <!-- where ... -->
@@
 
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
-
 <!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
@@
 This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
 
@@
 
-#### Sensitivity analyses
-
-I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
-<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
+#### Additional analyses
+
+Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
 _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
@@
 
-#### Visualisation of results
+#### Visualisation of results {#sys-rev-visualising-results}
 
@@
 One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-
 In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
@@
 The database search identified `r num_to_text(23447)` records, of which
-
-<!-- TODO Cross check this with the actual numbers included -->
 
@@
 `r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-<!-- TODO Check these figures & Finish PRISMA -->
 
@@
 <!----------------------------------------------------------------------------->
-
-<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
-
-```{r prisma-flow-setup, include = FALSE}
-```
 
@@
 
-Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
-Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
-
-Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
-For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
+Following full-text screening, `r n_reports_included` reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @su2017; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yamada2009b; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial,[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both examining statins use on all-cause dementia in older adults.
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published GWAS, leading to complications in the synthesis (see Section \@ref(res-AD)).
+
+Of the `r_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also examined other non-statins agents such as fibrates (`r n_fibrates`).
+In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia `r n_hyperchol` and `r n_TC` were the most frequently reported risk factors.
+
+In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`.
 Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
 
-Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
-
-Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
-
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
-All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
-
-Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
-As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
--->.
-As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
-
-<!--- TODO Figures and tables to include here:
-
--   Summary of risk of bias (not done)
-
---->
+<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->
+
+<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->
+
+<!--- TODO Talk a little bit more about age here --->
+
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and described a Mendelian randomisation analysis.
+
+<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->
+
+<!-- TODO Figures and tables to include here: -   Summary of risk of bias (not done) -->
 
@@
 
+```{r cohortLocationsSetup, include = FALSE}
+```
+
 As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
-
-<!----------------------------------------------------------------------------->
-```{r cohortLocationsSetup, include = FALSE}
-```
+Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
+Finally, several eligible studies reported as conference abstracts did not present numerical results.
+These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
+As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result.
+A more detailed discussion fo the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section
 
@@
 
-Both randomised controlled trials were considered to be at low risk of bias.
-
-For NRSI
-For NRSE
-
-For MR studies
-
-Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
-A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
+<!-- Both randomised controlled trials were considered to be at low risk of bias.  -->
+
+<!-- For NRSI, common biases include immortal time (where participants in the exposure group are followed up) -->
+<!-- For NRSE  -->
+
+<!-- For MR studies, concerns over potential genetic pleiotropy -->
+
+<!-- Additionally, several synthesis were also assessed to be at risk of bias due to missing evidence.  -->
+
+<!-- A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
 This is discussed further in Section \@ref(rev-discussion-MR).
-
-<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
-
-Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
-
-&nbsp;
+-->
+
+<!-- Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009] -->
 
@@
 ```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
 ```
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
@@
 
-In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
 
@@
 
-A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
+Finally, a single Mendelian randomisation analysis was identified examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of all-cause dementia, which provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
+
+&nbsp;
 
@@
 
-* NRSE
-
-* MR studies per 1-SD
-
-In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
-
-&nbsp;
-
-Several studies presented results per SD change in a lipid fraction.
-
-In Mendelian randomisation studies, a similar
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Alzheimer's disease
-
-There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
+Across all outcomes, lipid levels were categorised in a number of ways.
+The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
+
+`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperDementia-cap) __shortcap:__
+
+(ref:obsHyperDementia-scap) shortcap
+
+```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_HDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) or triglycerides (`r n_effect(obsLipids$Dementia_HDL)`).
+Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on all-cause dementia risk.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Alzheimer's disease {#res-AD}
+
+There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome and provid evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
+(ref:mrStatinAD-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
@@
 
+&nbsp;
+
 __Lipids__
 
-<!----------------------------------------------------------------------------->
+`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperAD-cap) __shortcap:__
+
+(ref:obsHyperAD-scap) shortcap
+
+```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_HDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_HDL)`).
+Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
+
+Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(mrDuplication)).
+However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
+Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of participants, no meta-analysis of these studies was performed.
+However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
+
+(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
+
+```{r mrDuplicationSetup, include=FALSE}
+```
+
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;
@@
 __Statins__
+
+As noted above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
+
+There were no randomised trials for this outcome.
+`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
 
@@
 
+A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).
+
+&nbsp;
+
 __Lipids__
 
+`r obsHyperchol$VaD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperVaD-cap) __shortcap:__
+
+(ref:obsHyperVaD-scap) shortcap
+
+```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$VaD_TC)`), LDL-c (`r n_effect(obsLipids$VaD_HDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_HDL)`).
+Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on vascular dementia risk.
+
+&nbsp;
+
 ### Dose response meta-analysis of lipid levels {#dose-response-results}
@@
 <!-- TODO Cite excluded studies and list exclusion reasons -->
+
+<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks -->
 
@@
 Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
+
+<!-- TODO Can only do meta-regression in analysis with 10 studies, so statins and hypercholesterolemia should -->
+
+Across all analysis with
 
@@
 
-### Sensitivity analysis
-
-Given that the majority of the studies included in the review were of
-
 ### Small study effects {#sys-rev-pub-bias}
 
-<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
-<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
-
-There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
+<!--    Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
+<!--    Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
+
+There was little evidence of small study effects across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
 
@@
 
-<!-- TODO Will have to get actual numbers for this section -->
-
 As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
-
-For the analysis of XX on YYY, preprints added ...
-
-Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
-
-<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
+From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019a; @so2017]
+
+All identified preprinted studies were.
+However, including preprints did provide useful additional evidence value in a number of meta-analysis.
+For example, re-analysing the results of available for the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref) in Mendelian randomisation studies, illustrates that the result only available from a preprint contributed `r mrStatinPreprintWeight` of the weight in a fixed-effect meta-analysis.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis
+
+(ref:preprintWeights-scaption) Added information due to inclusion of preprints
+
+```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+<!-- TODO Add extra column with details of Figure showing met-analysis -->
+
+&nbsp;
+
+Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date),[@andrews2019; @andrews2021].
+The final preprint has not yet been published.[@so2017]
 
@@
 Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
+
+<!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->
 
@@
 
+Generalisability was aided by the large number of studies performed using the Taiwan health database, which represents a good sources of evidence on non-Caucasian populations
+
 <!----------------------------------------------------------------------------->
@@
 Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
+
+<!----------------------------------------------------------------------------->
+(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
+there is no horizontal pleiotropy).
+
+(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses
+
+```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='100%', fig.scap='(ref:mrAssumptions-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
 <!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
@@
 published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
-There were several relevant preprints captured by the search.
-The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).
-
-Three relevant preprints were identified
-
-medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
 The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
+The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
+As such, at the point it was searched, the medRxiv database contained only a very small number of records (n=`r n_at_search["med"]`).
+
+<!----------------------------------------------------------------------------->
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
+
+(ref:preprintGrowth-scap) Growth of preprint repositories over time
+
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Three relevant preprints from the bioRxiv hits were identified.
+The added evidential value of including these preprints was described in Section \ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
+Of note, all three included preprints described Mendelian randomisation analysis, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
 
 Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
-
-While none of the preprints contributed uniquely to the review, this is again.
+This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
+Firstly, preprints provide an advance snapshot of the literature, capturing preprinted articles that are subsequently published but were not .
+Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise.
+
 Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
@@
 
-Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
-However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
-
-<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
-
-<!-- Regardless, some studies were identified -->
+More recently, inclusion of preprints in systematic reviews has become significantly more widespread.
+This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
+How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
 

### 2021-10-01 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 
+### Calculating Gwet's AC1
+
+Gwet's AC1 is defined as:
+
+$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
+
+In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
+
+\begin{equation}
+  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
+  (\#eq:AC1-main)
+\end{equation}
+
+where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
+
+\begin{equation}
+  q = \frac{(A+C)+(A+B)}{2N}
+  (\#eq:AC1-supp)
+\end{equation}
+
 <!----------------------------------------------------------------------------->
 ### MR risk of bias tool {#appendix-mr-rob}
+
+<!-- TODO Need to include -->
+
+<!----------------------------------------------------------------------------->
+
+### Forest plots for lipid fractions {#lipid-fraction-forest-plots}
+
+<!-- TODO Need to add labels/captions to these -->
+
+<!----------------------------------------------------------------------------->
+```{r obsLipidsDementiaTC, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TC_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+```{r obsLipidsDementiaLDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_LDL_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+```{r obsLipidsDementiaHDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_HDL_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+```{r obsLipidsDementiaTG, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TG_.png"))
+```
+<!----------------------------------------------------------------------------->
 

### 2021-10-01 03-Chp-Systematic-Review.Rmd
End of day:

@@
 
-Following full-text screening, `r n_reports_included` reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @su2017; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yamada2009b; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @su2017; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yamada2009b; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] <!-- TODO implement citation column in and check in rendered version that there are X references -->
+
+Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
 
@@
 
-__Statins__
+#### Statins
 
@@
 
-__Lipids__
+#### Lipids
 
@@
 
+#### Statins
+
 There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome and provid evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).

### 2021-10-01 05-Chp-IPD-Analysis.Rmd
End of day:

@@
 ---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
   bookdown::pdf_document2:
     template: templates/brief_template.tex
-  bookdown::word_document2: default
   bookdown::html_document2: default
@@
 
+```{r cohortNumbers, message=FALSE,echo = FALSE}
+```
+
 ## Lay Summary
 
-As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
+As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglycerides) on any dementia outcome.
+In addition, patients characteristics such as age and sex did not have any impact on the relationship of lipid fractions and dementia outcomes.
+
+Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.
 
@@
 
-Is there a good way to visualise input of cohorts into an IPD analysis?
+Individual patient data meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.
+They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results have been explicitly stratified by the characteristic of interest.
 
-Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
+While the systematic review presented in Chapter \@ref(sys-rev-heading) did not provide strong evidence for an effect of age at lipid measurement or patient sex on the relationship between lipids and dementia, the number of included studies in the lipid fraction meta-analyses were very small, due to both the relatively small number of studies reporting on this exposure and the poor reporting of smmary statistics of patient characteristics.
+
+As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by incorporating previously unanalysed cohorts contained in the Dementia Platform UK, a large consortia of dementia cohorts.
 
@@
 
-Eligible data sources were defined as those that contained lipid measurements and  ipids reported/available as a continuous measure, Data sources which were cross-sectional, either by design or due to the available data (e.g.
+Eligible data sources were defined as those that contained lipid measurements and lipids reported/available as a continuous measure, Data sources which were cross-sectional, either by design or due to the available data (e.g.
 a study conducted multiple waves, but onyl data from a single wave could be accessed) were excluded.
 Similarly, due to the limited time-frame, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which I already had access to as part of the analysis reported in Chapter \ref(cprd-heading).
+The one exception to this was data from the CPRD, which I already had access to as part of the analysis reported in Chapter \ref(cprd-analysis-heading).
 
@@
 
-__Systematic review__
+Potentially eligible data sources were identified via two mechanisms with a distinct focus.
+For each approach, the number of cohorts responding to the request, and where applciable, the reasons given for a lack of data sharing were recorded.
 
-As part of the IPD analysis, eligible observational prospective cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were approached for data access.
+#### Systematic review
 
-In the first instance, the first author on the main study report was emailed (see Appendix \@ref() for a copy of the text and documentation sent).
-If this did not elict a response, the last/corresponding author was contacted, on the basis that the first author may have been a more junior member.
+The first approach focused on previously analysed data sources.
+The systematic review detailed in Chapter \@ref(sys-rev-heading) identified several observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes.
+The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
+In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potentially collaborators) in Autumn 2020.
+If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who has moved to a different institution.
 
-examining the effect of lipid levels
+#### Dementia Platform UK
 
-__Dementia platform UK__
+The second approach focused on incorporating previously unanalysed data, thus providing additional evidence on the relationship between statins and dementia risk.
 
-In addition, in an attempt to supplement the analysis with
+This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application processs for all cohorts with the intent of making it easier to access data from existing data sources.
 
-In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from existing dementia cohorts through a centralised application process.
+Cohorts included in the DPUK were assessed against the eligibility criteria, and in Autumn 2020, an application for access to a subset of 16 cohorts was made via the common-access procedure.
 
@@
 Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
+
+Due to the inherent conflict of interest in assessing my own analysis, the result were also assessed by two independent reviewers.
 
@@
 
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
-
 <!-- TODO Need to talk about how missing variables were handled across studies -->
@@
 
-### Analysis
+### Variable definition
 
-_Individual patient data approached__
+#### Exposure
 
-Two stage versus one-stage approach
+To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
 
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
+#### Outcomes
 
-__Statistical methods__
+Similar to the analyses presented in othe chapters, th endpoints in this analysis was incidience of dementia and related sub-types (AD, vascular dementia).
+
+#### Covariates
+
+Relevant covariates were adjusted for in all models. these included age, sex,education and comorbities. For information on how these were defined across cohorts, see Appendix \@ref(hold).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Statistical analysis
+
+#### Descriptive statistics
+
+All IPD obtained was examined and recoded as necessary to ensure they comply with the coding guideline for the IPD database.
+As recommended , summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process.[@levis2021] Any discrepancies were investigated.
+
+#### Data cleaning and harmonisation
+
+Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
+The one exception to this is the CPRD data, which was held in a different system to the rest.
+However, an identical model was applied within this cohort.
+The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+
+#### Individual patient data analysis
+
+<!-- Need detailed paragraph here describing the different between two stage versus one-stage approach -->
+
+In this analysis, an two-stage individual patient data model was used out of necessity, with the one-stage model being precluded by the included datasets being in protected data silos.
+It also allows for each studys' data to be analysed according to a common analysis plan, which is particularly important in this topic, due to the differing definitions between studies of the serum concentrations above or below which lipids are deemed to be at abnormal levels.
 
 Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
-A common model, adjusted for identical covariates, were obtained using a common model.
-
-To aid interpretability of the outcome, all analyses were standardised by changes in 1-SD of the exposure variable.
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017]
-
-The estimates from each data source were then combined using a random-effects meta-analysis
+Effect estimates for the associations between lipid fractions and incident dementia, adjusted for identical covariates, were obtained by applying a common model to each data source.
+More specifically, hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017] An overall effect estimate was then produced by combining data-source-specific estimtes in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
+Following best practice, clustering within studies was accounted for.[@abo-zaid2013]
 
@@
 
-__Investigating effect of patient-level covariates__
+#### Investigating effect of patient-level covariates
 
@@
 
-__Replicating published findings__
+#### Combining published aggregate data and individual participant data
 
-Where an included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
-If discrepancies were identified, these were investigate.
+Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the aggregate data and individual data were combined.
 
-__Combining published aggregate data and individual participant data__
+<!-- TODO How does this work? -->
 
-Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the agregate date and individual data were combined.
+&nbsp;<!----------------------------------------------------------------------->
+
+### Comparison with published findings
+
+Where an included data source had previously been analysed and results for the association between lipid levels and dementia outcomes reported, these were compared to the results of this analysis.
+If discrepancies were identified, these were investigated.
 
@@
 
-__Author statements on data availability__
+### Secondary analyses
+
+#### Amount of information added
+
+The proportion of new information added to the evidence base via incorporation of the unanalysed datasets was quantified, by addding the additional results to the lipid-dementia meta-analyses presented in Section \@ref(hold), and extracting the combined weights assigned to the new data in a fixed-effect model.
+
+<!-- #### Contact information  -->
+
+#### Data availability statements
 
@@
 
-Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
+Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) provided data and were included in the analysis.
 Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
+In addition, the reasons for cohorts not being included in the analysis are presented, stratified by application approach.
 
-In addition, the reasons for cohorts not being included in the analysis are presented.
 In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked with the same group and did not know if the data were available or how to obtain it, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
 
-For the streamlined DPUK process, where a dedicated project manager liaises with cohort owners on the applicants behalf, the overall response rate was higher, resulting in access to three cohorts.
-However, even using this dedicated access approach, a response was obtained for less than half of the approach cohorts
+With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher resulting in eventual access to three cohorts (one of which was also identified by the systematic review).
+However, even using this streamlined approach, a response was obtained for only half of the approach cohorts.
 
@@
 
-Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.
-
-As highlighted in the
+As highlighted in Figure \@ref(fig:cohortFlowchart), there was little overlap between cohorts identified by the systematic review and those contained in the DPUK (`r fmt_applied(n_applied$DPUK_sysrev)`), indicating that the DPUK is a useful source of unanalysed data with respect to this question.
 
@@
 The four data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
-
-Of note, all data sources included in the analysis were based in the United Kingdom.
-This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.
+Of note, all included data sources were based in the United Kingdom.
+This is likely due to the majority of included datasets coming from the Dementia Platform UK route (Figure  \@ref(fig:cohortFlowchart)), which as implied by the name, has a geographical focus on cohorts performed in the United Kingdom.[@bauermeister2020]
 
@@
 
-Electronic health record co
-
-Lothian Birth Cohort - 1936
-
-Taiwan, etc.
+The main reason for exclusion within this records was use of an electronic health record database.
+Examples included the Taiwan National Health Insurance database and studies run in the US making use of Medicare data.
 
@@
 
-Several additional cohorts are present in the DPUK collection but were not approach with a request for data acccess.
-This was primarily due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
+Several additional cohorts are present in the DPUK collection but were not formally approached with a request for data access.
+This was primarily due to the information obtained via the online data dictionary system or via initial contact with the cohort owners indicating that the study was relatively new (and so was yet to collect more than 1 wave of data) or that the exposure variables of interest were not recorded.
 
-Electronic health record co
-
-LBC - 1936
-
-Taiwan etc,
+<!-- TODO LBC 1936 -->
 
@@
 
-As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
-
-Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
-
-The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
-
-__BRACE__
-
-Likley had dementia at baseline. However, on further investigation of the cohort, it was discovered that
-
-__Memento__
-
-Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
-
-__Generation Scotland__
-
-Cross-sectional data only
-
-__NICOLA__
-
-NICOLA study - only had cross-sectional data
-
-__ELSA__
-
-Data provided but only had ever high cholesterol as a binary variable. Not compatible with
+As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
+The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:dataExcluded-caption) dataExcluded
+(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
 
-(ref:dataExcluded-scaption) dataExcluded
+(ref:dataExcluded-scaption) Exclusion reasons for cohorts providing data
 
@@
 
+BRACE is a memory-complaint-based cohort, suggesting that it is unlikely they were dementia-free at baseline).
+<!-- TODO CITATION NEEDED --> Similarly, the Memento study was excluded as it's criteria for entry required participants to be outpatients from a memory clinic.
+<!-- TODO CITATION NEEDED --> The Generation Scotland provided only cross-sectional data only for the variables of interest, as did the the NICOLA study.
+<!-- TODO CITATION NEEDED x2 --> Finally, the ELSA study was excluded based on the definition of the exposure variable.
+This study provided a "high cholesterol" a binary variable rather than the raw continuous lipid measurement data.
+<!-- TODO CITATION NEEDED -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Cohorts approach but received no answer
 
-A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
+This was particularly common among the cohorts identified via the systematic review and included studies with  a dedicated access process or data access committee.
+A cohort of particular interest, having been used in multiple studies identified by the systematic review, is the Three City Study in France.
 Despite multiple attempts to contact the team, there was no response received.
-
-These included studies with  a dedicated access process or data access committee.
-A cohort of particular interest, having been used in multiple studies identified by the systematic review is the Three City Study in France.
-This study was approach at multiple points over the curse of this analysis, and no answer was received.
+<!-- TODO CITATION NEEDED --> This study was approach at multiple points over the curse of this analysis, and no answer was received.
 
 This was also a problem for cohorts approach via the DPUK - half of the cohorts applied to did not respond to the application within a year.
+
+### Analytical results
+
+There was no evidence for an effect of any lipid fraction on any dementia outcome (Figure \@ref(fig:tcDementiaMain)).
+Additionally, meta-analysis of the interaction coefficients for age-at-lipid-measurement and participant sex did not reveal an evidence for an varying effect across these variables.
 
@@
 
-### Data cleaning and harmonisation
-
-Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
-
-The one exception to this is the CPRD data, which was held in a different system to the rest.
-
-The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
-
-For all cohorts, the first lipid measurement was used for the exposure method,
-
-For heterogeneity across the cohorts, the total time-at-risk was investigated.
-
 <!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
-
-# Results
 
@@
 
+<!-- ### Effect by age -->
+
+<!-- ### Heterogeneity -->
+
 <!----------------------------------------------------------------------------->
@@
 
-Useful citation for discussion[@levis2021]
+### Summary of findings
+
+This analysis requested data from `r n_applied$total` data sources, but only obtained data from `r fmt_applied(n_accessed$total)`, all of which were based in the United Kingdom.
+No evidence for an effect of lipids on the risk of dementia or related outcomes was identified.
+Similalarly, there was no evidence for an effect of age-at-measurement or sex on the lipid-dementia relationship.
+
+Additionally analyses revealed that authors of cohorts indentified by the systematic review rarely stated that the data underpinning their analyses would be freely available, while a review of corresponding authors of these publications demonstrated that for many, the institutional email address provided was out of date.
+
+<!-- Useful citation for discussion[@levis2021] -->
 
@@
 <!-- TODO Plot showing when datasets requested were published and comparing this with the -->
+A key limitation of this analysis is the very low response rate to requests for data access.
+This finding is not unexpected however, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
+--> and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
 
-This review had a low response rate to requests for data access.
+There are likely several likely reasons for this low response rate.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.
+<!-- TODO CITATION NEEDED -->
 
-While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
-test
-There are likely several reasons for this.
+More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
+The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other work.
 
-* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
+_Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases - that when data is requested, it is not actually made available.
+[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014] Several of the included studies are greater than 10 years old, and so obtaining data from these cohorts is less likely compared with more recently published studies._ <!-- TODO taken from DAS paper, so will need to change language -->
 
-* While there is no
+One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
+Qualitatively, investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+<!-- All of these are arguments towards better reporting of data availability, ownership - also talk about the ORCID and advatnages of permanent identifier-->
 
-For many other reasons also - if
+ These challenges are in theory what the DPUK was built to address.
+However, even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
+The response rate among DPUK cohorts a year after application was just 50%.
+In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
 
-A potential further reason was highlighted during my attendance at the
+<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
 
-Letters sent to all cohorts identified through the systematic review 
-<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
-
-This is likely due to my junior position as a early career research combined with the impact
-
-Range of reasons why data is not readily available.
-Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
-primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
-
-Unfortunately,
-
-The low response rate and the
-
-Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
+Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
 
@@
 
-For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
+For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
+In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
 
-On a personal level, given the
-
-In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-#### Opportunistic inclusion of CPRD data
+<!-- #### Opportunistic inclusion of CPRD data -->
 
@@
 
-While this analysis did not manage to systematically obtain and analyse a large proporiton of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the - providing additional data points in
-
-it also attempted to make use
+While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the EPIC Norfolk study - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
 
@@
 
-### Data access
+<!-- ### Study within a review -->
 
-Couple of sections
+<!-- In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data. -->
 
-* Problems with getting data from studies
-* Problems with current methods of tracking people down via .
-Particularly when studies were older, several cases of the address/contact details for the corresponding author being out of date.
-Matches with decrease in availability as the studies get older.
+<!-- Options could include an investigation of the impact of applicant chacateristics  -->
 
-__Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases—that when data is requested, it is not actually made available.
-[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014]__ <!-- TODO taken from DAS paper, so will need to change language -->
-
-Qualitatively, investigation of a subset of cohorts on an _ad-hoc_ basis reveal that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
-All of these are arguments towards better reporting of data availability, ownership and
-
-Even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
-Sharing data has several legal, ethical and logistical challenges, and can often taken several years to obtain.
-This is in theory what the DPUK was built to address.
-However, despite claims to a streamlined process, the response rate among cohorts a year after application was 50%.
-In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
-In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
-Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Study within a review
-
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
-
-Options could include
-
-Previous SWARs have been registered as protocols, but have not yet reported!
+<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->
 
@@
 
-#### Aims/Resources
+In hindsight, attempting to undertake a large-scale IPD meta-analysis as part of a larger PhD project may have been overly ambitious.
+Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
 
-May have been overly ambitious
-
-While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
-
-Given the resource intensity of data cleaning and harmonisation,
+<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->
 
 &nbsp;<!----------------------------------------------------------------------->
+
+## Conclusion
+
+This analysis provided very weak evidence for an effect of lipid fractions on dementia outcomes.
+However, it does provide an analysis two previous unanalysed data sources that are subsequently used in Chapter \@ref(tri-heading).
 

### 2021-10-01 06-Chp-Triangulation.Rmd
Back to working version General clean-up Proper counting of words included in tables
End of day:

@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
@@
 These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
+
+While the triangulation framework provides for inclusion of multiple distinct types of evidence, based on the scoping search, it is likely that the three main sources will be RCTs of statins, multivariable regression of prospective cohorts, and the use of genetic instruments in observational data (Mendelian Randomisation studies).
+One important difference between these approaches that will need to be addressed in the triangulation
+is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
+The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course.
 

### 2021-10-01 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 <!----------------------------------------------------------------------------->
-### Section 1
+### Email and documents sent to potental collaborators {#ipd-email-collab}
 

### 2021-10-05 01-Chp-Background.Rmd
End of day:

@@
 
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
+Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMGCR).
 This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.

### 2021-10-05 03-Chp-Systematic-Review.Rmd
End of day:

--- 2021-10-01 03-Chp-Systematic-Review.Rmd
@@
 
-# Systematic review of all evidence available on the association between blood lipids (and treatment) and dementia outcomes {#sys-rev-heading}
+# Systematic review of all evidence available on the association between blood lipids and dementia outcomes {#sys-rev-heading}
 
@@
 <!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-<!-- * Statins and the risk of dementia Jick -->
 
@@
 
-Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
-They do this by finding and combining the results from many related primary research studies.
-Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
-
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
-
-There were `n_included` primary studies that contained information on this relationship.
-I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipids were not associated with any outcome.
+Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
+Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's methods.
+
+This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels such as statins, and dementia outcomes.
+
+My review included `r n_included` primary studies that contained information on this relationship.
+I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
+Lipid levels were not associated with any outcome.
 The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
@@
 
-<!-- TODO text -->
-
 &nbsp;
@@
 In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
+
 This analysis sought to address two specific aims.
-
 Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
@@
 Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
-As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.
-
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies.
-As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
-This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
-
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
+As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.
+
+Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but  report relevant unpublished analyses.
+As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
+
+The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).
 
@@
 
-A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
+A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
 
@@
 In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration).
+Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements and Author Declaration in the front matter).
 <!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
@@
 The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
+As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
 The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
 The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
 <!-- TODO Need to actually attach each search strategy.
@@
 When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
+To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
 
@@
 (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
-those matched based on the "Title" field alone).
-
-Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.
-
-Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer.
-In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
+those identified as duplicates based on the "Title" field alone).
+
+Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.
+
+Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
 Reasons for exclusion at this stage were recorded.
@@
 
-The criteria used to assess eligibility are presented in the subsequent sections.
+The criteria against which records were assessed for eligibility are presented in the subsequent sections.
 
@@
 
-I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
+I sought to include studies that examined blood lipid levels as a risk factor for demenita outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
+I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
 Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
 
-Participants were screened for dementia at baseline and prevalent cases excluded.
+Eligible studies screened participants for dementia at baseline and excluded any prevalent cases.
 Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
@@
 
-Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.
+Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.
+
+Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status.
+No limitations were imposed on publication status, date, venue or language.
 
@@
 
-No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
-
 <!----------------------------------------------------------------------------->
@@
 Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded.
-Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
-Studies that measure change in continuous cognitive measures (e.g.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
 MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia) were excluded.
-Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status.
+no dementia/dementia).
 Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
@@
 Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
 
@@
 
-#### Study-fication
-
-As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
-Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
+#### Grouping multiple reports into studies
+
+As part of the data extraction process, multiple records resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
+This was common in cases where multiple papers report results on the same cohort but at different time points.
+This process builds out the most comprehensive account of a given studies possible by incorporating information from all available records.
 
@@
 Following best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups.
-[@higgins2019]
+age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
 
@@
 
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.
+This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.
 
@@
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]
-
-Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
-Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
-<!-- TODO Need to really fix this -->
-
-In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.
+As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] If the outcome is rare, as is the case for dementia outcomes, the estimated prevalence of  odds and risk ratios will approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-time-at-risk in each treatment group.
+
+Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate.
+However, in this review, the small subset of studies reporting odds/risk ratios and synthesised separately to those reporting hazard ratios.
 
@@
 
-A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
+A key aim of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
 To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
 
-There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
+There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
 Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
 
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
+This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
+<!-- TODO CITATION NEEDED --> As part of this shift, the focus shifted from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+<!-- TODO CITATION NEEDED -->
+Finally, tools movide from assessing bias at the study level to considering each indivudal result reported seperately.
 For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.
+In this case, missing outcome data that is not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
 
@@
 
-Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
-Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
-Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
+Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assess the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
+Acceptable judgements for each domain include: "low risk", "some concerns", "high risk".
+Each of the five domains contains a series of signalling questions or prompts which guide the user through the tool.
 Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
@@
 
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
-Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial.
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result.
+Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “low risk”, “moderate risk”, “serious risk” and “critical risk”.
+In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial.
 Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
@@
 While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level.
-The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
+Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signalling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
+The motivation using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
 In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
-Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
+Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.
 
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors.).
+<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
+Acceptable judgements for each fo the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
 
@@
 
-A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
+This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
 <!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
@@
 
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design
-
+An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design.
 Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-<!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
-
-Of note, studies were not combined across different study designs (i.e.
+<!-- TODO CITATION NEEDED -->
+
+Results were not combined across different study designs (i.e.
 RCTs were not combined in a meta-analysis with results from observational studies).
-The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)
+The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading)
 
@@
 #### Standard meta-analysis
+
+For
 
@@
 
-[Do I need to include]
-
 Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$
@@
 
-Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
+<!-- Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
 There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article.
-The estimate of $\tau^2$ is incorporated into the weighting of each study
+The estimate of $\tau^2$ is incorporated into the weighting of each study -->
 
@@
 
-This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
 Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
@@
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
-
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
-
+This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.
+
+Studies were excluded from this analysis if the number of categories was less than three or if the necessary information for synthesis (cut-off points, number of participants and number of events per category) was not available.
 A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
+<!-- TODO CITATION NEEDED --> The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
+Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
 Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
 
-Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
+When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
+Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
 
@@
 _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
+Syntheses with greater than 10 studies were assessed for heterogeneity across these covariates.
 <!-- TODO Need more here -->
 
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
+Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.
 <!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
@@
 
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
+Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
 
 One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+<!-- TODO CITATION NEEDED --> In response to this criticism, I developed a new visualisation tool was designed to allow for the production of "paired" forest plots, as recommended by the ROB2 publication, where a risk-of-bias assessment is presented alongside it's corresponding numerical results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
-__[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]__
-
-Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
-
-As a sensitivity analysis, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
+_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]_
+
+Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)).
+As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+
+Additionally, I followed identified preprints up after a two-year lag to investigate whether they had been subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).
 
@@
 
-The database search identified `r num_to_text(23447)` records, of which
-
+The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records.
 Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
@@
 
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
+The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the right of the diagram).
+
+Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g.
 change in cognitive scores).
-
-### Validation of screening
 
@@
 <!----------------------------------------------------------------------------->
+
+### Validation of screening
 
@@
 Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline/MCI versus dementia, and the definition of eligible lipids fractions.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and the definition of eligible lipids fractions.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+### Characteristics of included studies {#sys-rev-characteristics}
 
@@
 
-Following full-text screening, `r n_reports_included` reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @su2017; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yamada2009b; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial,[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both examining statins use on all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published GWAS, leading to complications in the synthesis (see Section \@ref(res-AD)).
-
-Of the `r_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also examined other non-statins agents such as fibrates (`r n_fibrates`).
-In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia `r n_hyperchol` and `r n_TC` were the most frequently reported risk factors.
+Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
+
+Of the `r n_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also reported on other non-statins agents such as fibrates (`r n_fibrates`).
+In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia (`r n_hyperchol`) and total cholesterol levels (`r n_TC`) were the most frequently reported risk factors.
 
 In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`.
-Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
+Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated, but were myc rarer.
 
@@
 
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and described a Mendelian randomisation analysis.
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
 
@@
 (ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple study designs, and these have been duplicated across the relevant sub-sections.
+Note that three studies reported on multiple analytical designs within a single study, and these have been duplicated across the relevant sub-sections.
 
@@
 
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most high represented region being North America.
 Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
@@
 
-Finally, several eligible studies reported as conference abstracts did not present numerical results.
+Finally, there were several eligible studies reported as conference abstracts that did not present numerical results.
 These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).
@@
 
+```{r riskOfBias, include = FALSE, message=FALSE, warning=FALSE}
+```
+
 As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result.
-A more detailed discussion fo the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section
-
-However, as a brief summary of the biases at play:
+A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases at play.
+
+Following best practice, studies judged to be at critical risk of bias should be excluded from any quantitative analyses.
+<!-- TODO CITATION NEEDED --> `r num_to_words(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e.
+the study reported unadjusted estimates).`r critical_citations`
 
@@
 
-### All-cause dementia
-
-__Statins__
+### All-cause dementia {#sys-rev-res-Dementia}
+
+#### Statins
 
@@
 ```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
 ```
@@
 
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
 
@@
 
-Finally, a single Mendelian randomisation analysis was identified examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of all-cause dementia, which provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
-
-&nbsp;
-
-__Lipids__
+Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
+This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
+
+&nbsp; <!---------------------------------------------------------------------->
+
+#### Fibrates
+
+```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found very weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsFibrateDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
+
+(ref:obsFibrateDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+#### Lipids
 
@@
 
-`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) __shortcap:__
-
-(ref:obsHyperDementia-scap) shortcap
+`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
+
+(ref:obsHyperDementia-scap) sMeta-analysis of hypercholesterolemia on all-cause dementia
 
@@
 
-Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_HDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) or triglycerides (`r n_effect(obsLipids$Dementia_HDL)`).
-Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on all-cause dementia risk.
+Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsDementia-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsDementia-scap) Random effects meta-analysis of four lipid fractions on all-cause dementia
+```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
 
@@
 
-### Alzheimer's disease {#res-AD}
-
-There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome and provid evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
+### Alzheimer's disease {#sys-rev-res-AD}
+
+#### Statins
+
+There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
 
@@
 
-Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
-The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinAD-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
+Two Mendelian randomisation studies looked at specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinAD-cap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) __shortcap:__
-
-(ref:obsHyperAD-scap) shortcap
+(ref:obsHyperAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
+
+(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
 
@@
 
-Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_HDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_HDL)`).
-Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
-
-Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(mrDuplication)).
+Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsAD-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsAD-scap) Random effects meta-analysis of four lipid fractions on Alzheimer's disease
+
+```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(fig:mrDuplication)).
 However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
-Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of participants, no meta-analysis of these studies was performed.
+Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
 However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).
@@
 
-### Vascular dementia
-
-__Statins__
-
-As noted above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
-
-There were no randomised trials for this outcome.
+### Vascular dementia {#sys-rev-res-VaD}
+
+#### Statins
+
+As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
+There were no available randomised trials for this outcome.
 `r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
@@
 
-&nbsp;
-
-__Lipids__
-
-`r obsHyperchol$VaD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) __shortcap:__
-
-(ref:obsHyperVaD-scap) shortcap
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Lipids
+
+`r num_to_words(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperVaD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+
+(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
 
@@
 
-Similarly to all-cause dementia everal studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction.
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$VaD_TC)`), LDL-c (`r n_effect(obsLipids$VaD_HDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_HDL)`).
-Forest plots for these analyses are presented in Appendix \@ref(lipid-fraction-forest-plots).
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lipid levels on vascular dementia risk.
+Few studies investigated the effect of individual lipid fractions.
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found very weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsVaD-cap) Random effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsVaD-scap) Random effects meta-analysis of total cholesterol on vascular dementia
+
+```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of genetically determined lipid levels on vascular dementia risk.
 
@@
 &nbsp;
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+### Missing evidence
+
+The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
+For randomised controlled trials and non-randomised studies of interventions, the risk of missing.
+However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (as shown in Figures \@ref(fig:lipidFractionsDementia), \@(lipidFractionsAD) and lipidFractionsAD).
+A key example is
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Added evidental value of including preprints {#sys-rev-including-preprints-res}
@@
 As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019a; @so2017]
+From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
 
@@
 <!----------------------------------------------------------------------------->
+```{r mrAssumptionsSetup, include = FALSE}
+```
+
 (ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
@@
 
-<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
-
 MR are limited by the need for SNP to be present in both datasets (for TSMR).
@@
 
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here.
 -->
@@
 
-Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. <!-- TODO Cite the Zenodo repo here! -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
+Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. __[Zenodo repository will be cited here]__
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
+I believe there are four aspects where this review is distinct from those reviews already available in the published literature.
+While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
@@
 
--   *Structured risk-of-bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
+In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
+The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or do not use an appropriate domain-based assessment tool (e.g.
+ROBINS-I/E).[@poly2020]
+
+This is important strength of this review, and a necessary art of the thesis, as the detailed risk of bias assessments are used in
+
+, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
 

### 2021-10-05 _main.Rmd
End of day:

@@
 <!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-<!-- * Statins and the risk of dementia Jick -->
+
+```{r prisma-flow-setup, include = FALSE}
+```
 
@@
 
-Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
-They do this by finding and combining the results from many related primary research studies.
-Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
-
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
-
-There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
-I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipids were not associated with any outcome.
+Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
+Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's methods.
+
+This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels such as statins, and dementia outcomes.
+
+My review included `r n_included` primary studies that contained information on this relationship.
+I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
+Lipid levels were not associated with any outcome.
 The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
@@
 
-I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
+I sought to include studies that examined blood lipid levels as a risk factor for demenita outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
+I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
 Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
 
-Participants were screened for dementia at baseline and prevalent cases excluded.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
+Eligible studies screened participants for dementia at baseline and excluded any prevalent cases.
+Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
 Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
@@
 Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
-
-Gwet's AC1 is defined as:
-
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
-
-In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
-
-\begin{equation}
-  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
-  (\#eq:AC1-main)
-\end{equation}
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-\begin{equation}
-  q = \frac{(A+C)+(A+B)}{2N}
-  (\#eq:AC1-supp)
-\end{equation}
-
-<!-- TODO Need to be sure of how to calculate. -->
+[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
 
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Risk of bias due to missing evidence
-
-A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors.).
+<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
+Acceptable judgements for each fo the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Risk of bias due to missing evidence {#methods-rob-me}
+
+In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
+This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
 <!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
@@
 
-Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
+For
+
+A random-effects meta-analysis model was employed to combine the different included studies.
 <!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
@@
 
+Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
+Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate.
+Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
+
+Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$
+
 \begin{equation}
-  \theta_i = \mu + u_i
-  (\#eq:meta-analysis-random)
+  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
 \end{equation}
 
+<!-- Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
+There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article.
+The estimate of $\tau^2$ is incorporated into the weighting of each study -->
+
 \begin{equation}
-  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
-  (\#eq:meta-analysis-fixed)
+  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
 \end{equation}
 
+<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g.
+log-ORs) between studies, with a variance of 𝜏2.
+The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance.
+The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance.
+So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis.
+If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model.
+-->
+<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way.
+The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
+<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
+<!-- (2) -->
+<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
+<!-- (3) -->
+<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->
+
+<!-- \begin{equation} -->
+<!--   \theta_i = \mu + u_i -->
+<!--   (\#eq:meta-analysis-random) -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
+<!--   (\#eq:meta-analysis-fixed) -->
+<!-- \end{equation} -->
+
 <!-- where ... -->
@@
 
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
-
 <!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
-
-This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
 
@@
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
-
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
-
+This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.
+
+Studies were excluded from this analysis if the number of categories was less than three or if the necessary information for synthesis (cut-off points, number of participants and number of events per category) was not available.
 A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
+<!-- TODO CITATION NEEDED --> The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
+Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
 Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
 
-Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity analyses
-
-I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
-<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
+When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
+Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Additional analyses
+
+Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
 _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
+Syntheses with greater than 10 studies were assessed for heterogeneity across these covariates.
 <!-- TODO Need more here -->
 
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
+Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.
 <!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
@@
 
-#### Visualisation of results
-
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
+#### Visualisation of results {#sys-rev-visualising-results}
+
+Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
 
 One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-
-In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+<!-- TODO CITATION NEEDED --> In response to this criticism, I developed a new visualisation tool was designed to allow for the production of "paired" forest plots, as recommended by the ROB2 publication, where a risk-of-bias assessment is presented alongside it's corresponding numerical results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
-The database search identified `r num_to_text(23447)` records, of which
-
-<!-- TODO Cross check this with the actual numbers included -->
-
+The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records.
 Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
@@
 `r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-<!-- TODO Check these figures & Finish PRISMA -->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
+
+The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the right of the diagram).
+
+Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g.
 change in cognitive scores).
 
-### Validation of screening
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
-
-```{r prisma-flow-setup, include = FALSE}
-```
+<!----------------------------------------------------------------------------->
 
@@
 
-Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
-Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
-
-Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
-For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
-Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
-
-Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
-
-Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
-
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
-All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
-
-Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
-As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
--->.
-As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
-
-<!--- TODO Figures and tables to include here:
-
--   Summary of risk of bias (not done)
-
---->
+Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
+
+Of the `r n_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also reported on other non-statins agents such as fibrates (`r n_fibrates`).
+In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia (`r n_hyperchol`) and total cholesterol levels (`r n_TC`) were the most frequently reported risk factors.
+
+In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`.
+Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated, but were myc rarer.
+
+<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->
+
+<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->
+
+<!--- TODO Talk a little bit more about age here --->
+
+Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
+
+<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->
+
+<!-- TODO Figures and tables to include here: -   Summary of risk of bias (not done) -->
 
@@
 
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
-
-<!----------------------------------------------------------------------------->
 ```{r cohortLocationsSetup, include = FALSE}
 ```
+
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most high represented region being North America.
+Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
+
+<!----------------------------------------------------------------------------->
 
@@
 
-of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
+Finally, there were several eligible studies reported as conference abstracts that did not present numerical results.
+These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
-
-However, as a brief summary of the biases at play:
-
-Both randomised controlled trials were considered to be at low risk of bias.
-
-For NRSI
-For NRSE
-
-For MR studies
-
-Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
-A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
+```{r riskOfBias, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result.
+A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases at play.
+
+Following best practice, studies judged to be at critical risk of bias should be excluded from any quantitative analyses.
+<!-- TODO CITATION NEEDED --> `r num_to_words(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e.
+the study reported unadjusted estimates).`r critical_citations`
+
+<!-- Both randomised controlled trials were considered to be at low risk of bias.  -->
+
+<!-- For NRSI, common biases include immortal time (where participants in the exposure group are followed up) -->
+<!-- For NRSE  -->
+
+<!-- For MR studies, concerns over potential genetic pleiotropy -->
+
+<!-- Additionally, several synthesis were also assessed to be at risk of bias due to missing evidence.  -->
+
+<!-- A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
 This is discussed further in Section \@ref(rev-discussion-MR).
-
-<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
-
-Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### All-cause dementia
-
-__Statins__
+-->
+
+<!-- Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009] -->
+
+<!----------------------------------------------------------------------------->
+
+### All-cause dementia {#sys-rev-res-Dementia}
+
+#### Statins
 
 ```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
 ```
@@
 
-In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
 
@@
 
-A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
-
-__Lipids__
-
-* NRSE
-
-* MR studies per 1-SD
-
-In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
-
-&nbsp;
-
-Several studies presented results per SD change in a lipid fraction.
-
-In Mendelian randomisation studies, a similar
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Alzheimer's disease
-
-There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
+Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
+This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
+
+&nbsp; <!---------------------------------------------------------------------->
+
+#### Fibrates
+
+```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found very weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsFibrateDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
+
+(ref:obsFibrateDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+
+```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+#### Lipids
+
+Across all outcomes, lipid levels were categorised in a number of ways.
+The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
+
+`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
+
+(ref:obsHyperDementia-scap) sMeta-analysis of hypercholesterolemia on all-cause dementia
+
+```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsDementia-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsDementia-scap) Random effects meta-analysis of four lipid fractions on all-cause dementia
+```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Alzheimer's disease {#sys-rev-res-AD}
+
+#### Statins
+
+There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
 
@@
 
-Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
-The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
+Two Mendelian randomisation studies looked at specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinAD-cap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
@@
 
-__Lipids__
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Vascular dementia
-
-__Statins__
+&nbsp;
+
+#### Lipids
+
+`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
+
+(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
+
+```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
+Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsAD-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsAD-scap) Random effects meta-analysis of four lipid fractions on Alzheimer's disease
+
+```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(fig:mrDuplication)).
+However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
+Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
+However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
+
+(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
+
+```{r mrDuplicationSetup, include=FALSE}
+```
+
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+### Vascular dementia {#sys-rev-res-VaD}
+
+#### Statins
+
+As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
+There were no available randomised trials for this outcome.
+`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
 
@@
 
-__Lipids__
+A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Lipids
+
+`r num_to_words(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperVaD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+
+(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
+
+```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Few studies investigated the effect of individual lipid fractions.
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found very weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsVaD-cap) Random effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsVaD-scap) Random effects meta-analysis of total cholesterol on vascular dementia
+
+```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of genetically determined lipid levels on vascular dementia risk.
+
+&nbsp;
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Sources of heterogeneity
@@
 
+### Missing evidence
+
+The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
+For randomised controlled trials and non-randomised studies of interventions, the risk of missing.
+However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (as shown in Figures \@ref(fig:lipidFractionsDementia), \@(lipidFractionsAD) and lipidFractionsAD).
+A key example is
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Added evidental value of including preprints {#sys-rev-including-preprints-res}
 
-<!-- TODO Will have to get actual numbers for this section -->
-
 As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
-
-For the analysis of XX on YYY, preprints added ...
-
-Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
-
-<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
+From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
+
+All identified preprinted studies were.
+However, including preprints did provide useful additional evidence value in a number of meta-analysis.
+For example, re-analysing the results of available for the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref) in Mendelian randomisation studies, illustrates that the result only available from a preprint contributed `r mrStatinPreprintWeight` of the weight in a fixed-effect meta-analysis.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis
+
+(ref:preprintWeights-scaption) Added information due to inclusion of preprints
+
+```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+<!-- TODO Add extra column with details of Figure showing met-analysis -->
+
+&nbsp;
+
+Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date),[@andrews2019; @andrews2021].
+The final preprint has not yet been published.[@so2017]
 
@@
 Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
+
+<!----------------------------------------------------------------------------->
+```{r mrAssumptionsSetup, include = FALSE}
+```
+
+(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
+there is no horizontal pleiotropy).
+
+(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses
+
+```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='100%', fig.scap='(ref:mrAssumptions-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
-
 MR are limited by the need for SNP to be present in both datasets (for TSMR).
 
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
 <!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
 
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here.
 -->
@@
 
+```{r cohortNumbers, message=FALSE,echo = FALSE}
+```
+
 ## Lay Summary
 
-As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
+
+The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglycerides) on any dementia outcome.
+In addition, patients characteristics such as age and sex did not have any impact on the relationship of lipid fractions and dementia outcomes.
+
+Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.
 
@@
 
-Is there a good way to visualise input of cohorts into an IPD analysis?
-
-Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
+Individual patient data meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.
+They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results have been explicitly stratified by the characteristic of interest.
+
+While the systematic review presented in Chapter \@ref(sys-rev-heading) did not provide strong evidence for an effect of age at lipid measurement or patient sex on the relationship between lipids and dementia, the number of included studies in the lipid fraction meta-analyses were very small, due to both the relatively small number of studies reporting on this exposure and the poor reporting of smmary statistics of patient characteristics.
+
+As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by incorporating previously unanalysed cohorts contained in the Dementia Platform UK, a large consortia of dementia cohorts.
 
@@
 
-__Systematic review__
-
-As part of the IPD analysis, eligible observational prospective cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were approached for data access.
-
-In the first instance, the first author on the main study report was emailed (see Appendix \@ref() for a copy of the text and documentation sent).
-If this did not elict a response, the last/corresponding author was contacted, on the basis that the first author may have been a more junior member.
-
-examining the effect of lipid levels
-
-__Dementia platform UK__
-
-In addition, in an attempt to supplement the analysis with
-
-In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from existing dementia cohorts through a centralised application process.
+Potentially eligible data sources were identified via two mechanisms with a distinct focus.
+For each approach, the number of cohorts responding to the request, and where applciable, the reasons given for a lack of data sharing were recorded.
+
+#### Systematic review
+
+The first approach focused on previously analysed data sources.
+The systematic review detailed in Chapter \@ref(sys-rev-heading) identified several observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes.
+The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
+In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potentially collaborators) in Autumn 2020.
+If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who has moved to a different institution.
+
+#### Dementia Platform UK
+
+The second approach focused on incorporating previously unanalysed data, thus providing additional evidence on the relationship between statins and dementia risk.
+
+This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application processs for all cohorts with the intent of making it easier to access data from existing data sources.
+
+Cohorts included in the DPUK were assessed against the eligibility criteria, and in Autumn 2020, an application for access to a subset of 16 cohorts was made via the common-access procedure.
 
@@
 
-### Analysis
-
-_Individual patient data approached__
-
-Two stage versus one-stage approach
-
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
-
-__Statistical methods__
+### Variable definition
+
+#### Exposure
+
+To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
+
+#### Outcomes
+
+Similar to the analyses presented in othe chapters, th endpoints in this analysis was incidience of dementia and related sub-types (AD, vascular dementia).
+
+#### Covariates
+
+Relevant covariates were adjusted for in all models. these included age, sex,education and comorbities. For information on how these were defined across cohorts, see Appendix \@ref(hold).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Statistical analysis
+
+#### Descriptive statistics
+
+All IPD obtained was examined and recoded as necessary to ensure they comply with the coding guideline for the IPD database.
+As recommended , summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process.[@levis2021] Any discrepancies were investigated.
+
+#### Data cleaning and harmonisation
+
+Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
+The one exception to this is the CPRD data, which was held in a different system to the rest.
+However, an identical model was applied within this cohort.
+The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+
+#### Individual patient data analysis
+
+<!-- Need detailed paragraph here describing the different between two stage versus one-stage approach -->
+
+In this analysis, an two-stage individual patient data model was used out of necessity, with the one-stage model being precluded by the included datasets being in protected data silos.
+It also allows for each studys' data to be analysed according to a common analysis plan, which is particularly important in this topic, due to the differing definitions between studies of the serum concentrations above or below which lipids are deemed to be at abnormal levels.
 
 Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
-A common model, adjusted for identical covariates, were obtained using a common model.
-
-To aid interpretability of the outcome, all analyses were standardised by changes in 1-SD of the exposure variable.
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017]
-
-The estimates from each data source were then combined using a random-effects meta-analysis
+Effect estimates for the associations between lipid fractions and incident dementia, adjusted for identical covariates, were obtained by applying a common model to each data source.
+More specifically, hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017] An overall effect estimate was then produced by combining data-source-specific estimtes in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
+Following best practice, clustering within studies was accounted for.[@abo-zaid2013]
 
@@
 
-__Replicating published findings__
-
-Where an included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
-If discrepancies were identified, these were investigate.
-
-__Combining published aggregate data and individual participant data__
-
-Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the agregate date and individual data were combined.
+#### Combining published aggregate data and individual participant data
+
+Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the aggregate data and individual data were combined.
+
+<!-- TODO How does this work? -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Comparison with published findings
+
+Where an included data source had previously been analysed and results for the association between lipid levels and dementia outcomes reported, these were compared to the results of this analysis.
+If discrepancies were identified, these were investigated.
 
@@
 
-Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
+Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) provided data and were included in the analysis.
 Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
-
-In addition, the reasons for cohorts not being included in the analysis are presented.
+In addition, the reasons for cohorts not being included in the analysis are presented, stratified by application approach.
+
 In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
-
-For the streamlined DPUK process, where a dedicated project manager liaises with cohort owners on the applicants behalf, the overall response rate was higher, resulting in access to three cohorts.
-However, even using this dedicated access approach, a response was obtained for less than half of the approach cohorts
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked with the same group and did not know if the data were available or how to obtain it, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+
+With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher resulting in eventual access to three cohorts (one of which was also identified by the systematic review).
+However, even using this streamlined approach, a response was obtained for only half of the approach cohorts.
 
@@
 
-Several additional cohorts are present in the DPUK collection but were not approach with a request for data acccess.
-This was primarily due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
-
-Electronic health record co
-
-LBC - 1936
-
-Taiwan etc,
+Several additional cohorts are present in the DPUK collection but were not formally approached with a request for data access.
+This was primarily due to the information obtained via the online data dictionary system or via initial contact with the cohort owners indicating that the study was relatively new (and so was yet to collect more than 1 wave of data) or that the exposure variables of interest were not recorded.
+
+<!-- TODO LBC 1936 -->
 
@@
 
-As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
-
-Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
-
-The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
-
-__BRACE__
-
-Likley had dementia at baseline. However, on further investigation of the cohort, it was discovered that
-
-__Memento__
-
-Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
-
-__Generation Scotland__
-
-Cross-sectional data only
-
-__NICOLA__
-
-NICOLA study - only had cross-sectional data
-
-__ELSA__
-
-Data provided but only had ever high cholesterol as a binary variable. Not compatible with
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:dataExcluded-caption) dataExcluded
-
-(ref:dataExcluded-scaption) dataExcluded
+As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
+The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
+
+(ref:dataExcluded-scaption) Exclusion reasons for cohorts providing data
 
@@
 
+BRACE is a memory-complaint-based cohort, suggesting that it is unlikely they were dementia-free at baseline).
+<!-- TODO CITATION NEEDED --> Similarly, the Memento study was excluded as it's criteria for entry required participants to be outpatients from a memory clinic.
+<!-- TODO CITATION NEEDED --> The Generation Scotland provided only cross-sectional data only for the variables of interest, as did the the NICOLA study.
+<!-- TODO CITATION NEEDED x2 --> Finally, the ELSA study was excluded based on the definition of the exposure variable.
+This study provided a "high cholesterol" a binary variable rather than the raw continuous lipid measurement data.
+<!-- TODO CITATION NEEDED -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Cohorts approach but received no answer
 
-A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
+This was particularly common among the cohorts identified via the systematic review and included studies with  a dedicated access process or data access committee.
+A cohort of particular interest, having been used in multiple studies identified by the systematic review, is the Three City Study in France.
 Despite multiple attempts to contact the team, there was no response received.
-
-These included studies with  a dedicated access process or data access committee.
-A cohort of particular interest, having been used in multiple studies identified by the systematic review is the Three City Study in France.
-This study was approach at multiple points over the curse of this analysis, and no answer was received.
+<!-- TODO CITATION NEEDED --> This study was approach at multiple points over the curse of this analysis, and no answer was received.
 
@@
 
+### Analytical results
+
+There was no evidence for an effect of any lipid fraction on any dementia outcome (Figure \@ref(fig:tcDementiaMain)).
+Additionally, meta-analysis of the interaction coefficients for age-at-lipid-measurement and participant sex did not reveal an evidence for an varying effect across these variables.
+
 <!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
@@
 <!-- TODO Plot showing when datasets requested were published and comparing this with the -->
-
-This review had a low response rate to requests for data access.
-
-While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
-test
-There are likely several reasons for this.
-
-* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
-
-* While there is no
-
-For many other reasons also - if
-
-A potential further reason was highlighted during my attendance at the
-
-Letters sent to all cohorts identified through the systematic review 
-<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
-
-This is likely due to my junior position as a early career research combined with the impact
-
-Range of reasons why data is not readily available.
-Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
-primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
-
-Unfortunately,
-
-The low response rate and the
-
-Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
+A key limitation of this analysis is the very low response rate to requests for data access.
+This finding is not unexpected however, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
+--> and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
+
+There are likely several likely reasons for this low response rate.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.
+<!-- TODO CITATION NEEDED -->
+
+More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
+The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other work.
+
+_Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases - that when data is requested, it is not actually made available.
+[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014] Several of the included studies are greater than 10 years old, and so obtaining data from these cohorts is less likely compared with more recently published studies._ <!-- TODO taken from DAS paper, so will need to change language -->
+
+One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
+Qualitatively, investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+<!-- All of these are arguments towards better reporting of data availability, ownership - also talk about the ORCID and advatnages of permanent identifier-->
+
+ These challenges are in theory what the DPUK was built to address.
+However, even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
+The response rate among DPUK cohorts a year after application was just 50%.
+In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
+
+<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
+
+Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
 
@@
 
-For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
-
-On a personal level, given the
-
+For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
 In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
 
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Risk of bias assessment
@@
 
-### Data access
-
-Couple of sections
-
-* Problems with getting data from studies
-* Problems with current methods of tracking people down via .
-Particularly when studies were older, several cases of the address/contact details for the corresponding author being out of date.
-Matches with decrease in availability as the studies get older.
-
-__Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases—that when data is requested, it is not actually made available.
-[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014]__ <!-- TODO taken from DAS paper, so will need to change language -->
-
-Qualitatively, investigation of a subset of cohorts on an _ad-hoc_ basis reveal that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
-All of these are arguments towards better reporting of data availability, ownership and
-
-Even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
-Sharing data has several legal, ethical and logistical challenges, and can often taken several years to obtain.
-This is in theory what the DPUK was built to address.
-However, despite claims to a streamlined process, the response rate among cohorts a year after application was 50%.
-In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
-In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
-Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
+<!-- ### Study within a review -->
+
+<!-- In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data. -->
+
+<!-- Options could include an investigation of the impact of applicant chacateristics  -->
+
+<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->
 
@@
 
-### Study within a review
-
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
-
-Options could include
-
-Previous SWARs have been registered as protocols, but have not yet reported!
+### Reflections on the process
+
+In hindsight, attempting to undertake a large-scale IPD meta-analysis as part of a larger PhD project may have been overly ambitious.
+Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
+
+<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->
 
@@
 
-### Reflections on the process
-
-#### Aims/Resources
-
-May have been overly ambitious
-
-While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
-
-Given the resource intensity of data cleaning and harmonisation,
-
-&nbsp;<!----------------------------------------------------------------------->
+## Conclusion
+
+This analysis provided very weak evidence for an effect of lipid fractions on dementia outcomes.
+However, it does provide an analysis two previous unanalysed data sources that are subsequently used in Chapter \@ref(tri-heading).
 
@@
 <!--chapter:end:05-Chp-IPD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-<!-- TODO Add this to the Chapter summary in the introduction and  -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-<!-- ### Triangulation  -->
-
-<!-- TODO Have a look at this - potentially move to triangulation chapter -->
-
-<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
-
-<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
-For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011] -->
-
-<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
--->
-
-# Aetiological triangulation across evidence sources {#tri-heading}
-
-## Lay Summary
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Introduction
-
-This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)
-
-### Data sources
-
-This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Background to the causal question
-
-Following best practice guidance, three
-
-Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
-
-This was also guideded by the forthcoming ROBINS-E tool, which has
-
-<!----------------------------------------------------------------------------->
-
-### Definition of the causal question
-
-<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
-
-### Summary of triangulation
-
-Need to check how much I talk about this in the introduction
-
-Describe in detail
-
-### Risk of bias tool
-
-In addition, the tool also aim to capture the potential direction of bias for each result.
-Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
-Highlight that this is slightly different for the confounding domain in non-randomised studies.
-
-These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Graphical representation
-
-For the graphs, the direction of bias is important.
-
-Where the direction of bias was unclear/could not be determined from the report, this is indicated
-
-In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
-The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
-
-Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
-Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
-non-differential misclassification).
-In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
-For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
-In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
-If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
-
-These graphs were built using the risk of bias tool described in Appendix \ref()
-
-<!-- TODO Does immortal time bias not also have a consistent effect -->
-
-<!----------------------------------------------------------------------------->
-
-### Standardisation across study designs
-
-Standardising across different measures of ex
-
-Want best information across lipids, and so standardised across differnt measures
-
-Fixing directions of effect - get everything pointing the same way
-
-<!----------------------------------------------------------------------------->
-### Analyses
-
-Bias-adjusted meta-analysis [@higgins2008a]
-
-<!----------------------------------------------------------------------------->
-
-## Results
-
-Summary of risk-of-bias/triangulation results
-
-Percentage of domains for which a direction of bias could be assigned?
-
-Compare bias-adjusted and
-
-See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
-
-Applicability/indirectness as an issue 
-Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
-
-### Challenges of real-life data
-
-Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-ALso highlight the issue with assigning a direct of bias in many studies
-
-### Need for new methods
-
-Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
-
-<!--chapter:end:06-Chp-Triangulation.Rmd-->
-
----
-output:
-  bookdown::word_document2: 
-      reference_docx: templates/word-styles-reference-01.docx   
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Discussion {#discussion-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-<!----------------------------------------------------------------------------->
-## Triangulation across exisiting evidence and evidence produced in this thesis
-
-### Overview of triangulation {#triangulation-overview}
-
-Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
-
-Summary table of different studies and results
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Qualitative vs qunatitative triangulation
-
-### Researcher positionality statement
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion of E-values
-
-How strong unmeasured confounding would have to be in order to explain the observed effect.
-
-Heavily criticised in a range of papers.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Use of concensus panel to bring everything together
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Additional topics for the discussion
-
-There are several addition topics I would like to cover:
-
-* The difference between the peer review of the software vs.
-the peer review of papers.
-A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
-Essentially, a more transparent and open
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Summary of findings (and implications for policy makers)
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Strengths and Limitations
-
-There are several strengths and limitations to the work presented in this thesis.
-One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
-
-Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Reproducible research
-
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
-In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
-
-Containerisation was used to ensure that the code is reproducible, in line iwht best practices
-
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
-
-One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
-However, access is dependency on an ISAC application to the managing body of the CPRD.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Public involvement and engagement {#disc-PPI}
-
-Involving and engaging the public and patients has been a central theme to this thesis.
-
-Public engagement activities included
-
-Public involvement also steered the creation of the topic
-
-P
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Future work
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Overall conclusions
-
-<!--chapter:end:07-Discussion.Rmd-->
 
@@
 
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
+
+<!-- TODO Add this to the Chapter summary in the introduction and  -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- ### Triangulation  -->
+
+<!-- TODO Have a look at this - potentially move to triangulation chapter -->
+
+<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
+
+<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
+For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
+[@guyatt2011] -->
+
+<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+-->
+
+# Aetiological triangulation across evidence sources {#tri-heading}
+
+## Lay Summary
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Introduction
+
+This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)
+
+### Data sources
+
+This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
+
+<!----------------------------------------------------------------------------->
+
+### Background to the causal question
+
+Following best practice guidance, three
+
+Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
+
+This was also guideded by the forthcoming ROBINS-E tool, which has
+
+<!----------------------------------------------------------------------------->
+
+### Definition of the causal question
+
+<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
+
+### Summary of triangulation
+
+Need to check how much I talk about this in the introduction
+
+Describe in detail
+
+### Risk of bias tool
+
+In addition, the tool also aim to capture the potential direction of bias for each result.
+Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
+Highlight that this is slightly different for the confounding domain in non-randomised studies.
+
+These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
+
+While the triangulation framework provides for inclusion of multiple distinct types of evidence, based on the scoping search, it is likely that the three main sources will be RCTs of statins, multivariable regression of prospective cohorts, and the use of genetic instruments in observational data (Mendelian Randomisation studies).
+One important difference between these approaches that will need to be addressed in the triangulation
+is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
+The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Graphical representation
+
+For the graphs, the direction of bias is important.
+
+Where the direction of bias was unclear/could not be determined from the report, this is indicated
+
+In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
+The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
+
+Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
+Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
+non-differential misclassification).
+In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
+For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
+In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
+If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
+
+These graphs were built using the risk of bias tool described in Appendix \ref()
+
+<!-- TODO Does immortal time bias not also have a consistent effect -->
+
+<!----------------------------------------------------------------------------->
+
+### Standardisation across study designs
+
+Standardising across different measures of ex
+
+Want best information across lipids, and so standardised across differnt measures
+
+Fixing directions of effect - get everything pointing the same way
+
+<!----------------------------------------------------------------------------->
+### Analyses
+
+Bias-adjusted meta-analysis [@higgins2008a]
+
+<!----------------------------------------------------------------------------->
+
+## Results
+
+Summary of risk-of-bias/triangulation results
+
+Percentage of domains for which a direction of bias could be assigned?
+
+Compare bias-adjusted and
+
+See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
+
+Applicability/indirectness as an issue 
+Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
+
+<!----------------------------------------------------------------------------->
+
+## Discussion
+
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+
+### Challenges of real-life data
+
+Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
+ALso highlight the issue with assigning a direct of bias in many studies
+
+### Need for new methods
+
+Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
+
+<!--chapter:end:06-Chp-Triangulation.Rmd-->
+
+---
+output:
+  bookdown::word_document2: 
+      reference_docx: templates/word-styles-reference-01.docx   
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::html_document2: default
+documentclass: book
+---
+
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
+
+# Discussion {#discussion-heading}
+\minitoc <!-- this will include a mini table of contents-->
+
+<!----------------------------------------------------------------------------->
+## Triangulation across exisiting evidence and evidence produced in this thesis
+
+### Overview of triangulation {#triangulation-overview}
+
+Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
+
+Summary table of different studies and results
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Qualitative vs qunatitative triangulation
+
+### Researcher positionality statement
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Discussion of E-values
+
+How strong unmeasured confounding would have to be in order to explain the observed effect.
+
+Heavily criticised in a range of papers.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Use of concensus panel to bring everything together
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Additional topics for the discussion
+
+There are several addition topics I would like to cover:
+
+* The difference between the peer review of the software vs.
+the peer review of papers.
+A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
+Essentially, a more transparent and open
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Summary of findings (and implications for policy makers)
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Strengths and Limitations
+
+There are several strengths and limitations to the work presented in this thesis.
+One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
+
+Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Reproducible research
+
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
+In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+
+Containerisation was used to ensure that the code is reproducible, in line iwht best practices
+
+Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
+
+One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
+IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
+However, access is dependency on an ISAC application to the managing body of the CPRD.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Public involvement and engagement {#disc-PPI}
+
+Involving and engaging the public and patients has been a central theme to this thesis.
+
+Public engagement activities included
+
+Public involvement also steered the creation of the topic
+
+P
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Future work
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+## Overall conclusions
+
+<!--chapter:end:07-Discussion.Rmd-->
+
+---
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
+output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
+  bookdown::html_document2: default
+documentclass: book
+---
+
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}

### 2021-10-05 R/03-Code-Systematic-Review.R

@@ -1,33 +1,34 @@
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- searchOverview-table
 
-searchOverview_table <- read.csv(here::here("data","sys-rev","searchOverview.csv"))
+searchOverview_table <-
+  read.csv(here::here("data", "sys-rev", "searchOverview.csv"))
 
-  if(doc_type == "docx") {
-    knitr::kable(searchOverview_table, caption = "(ref:searchOverview-caption)")
-  } else{
-    knitr::kable(
-      searchOverview_table,
-      format = "latex", 
-      caption = "(ref:searchOverview-caption)",
-      caption.short = "(ref:searchOverview-scaption)",
-      booktabs = TRUE,
-      align = "cl"
-    ) %>%
-      row_spec(0, bold = TRUE) %>%
-      row_spec(2:nrow(searchOverview_table)-1, hline_after = TRUE) %>%
-      kableExtra::column_spec(1, bold= FALSE) %>%
-      kable_styling(latex_options = c("HOLD_position"), font_size = 10)  %>%
-      kableExtra::footnote(
-        threeparttable = TRUE,
-        general_title = "",
-        general = paste("For all topics, search queries were comprised",
-                        "of relevant free text & controlled vocabulary terms."
-        )
+if (doc_type == "docx") {
+  knitr::kable(searchOverview_table, caption = "(ref:searchOverview-caption)")
+} else{
+  knitr::kable(
+    searchOverview_table,
+    format = "latex",
+    caption = "(ref:searchOverview-caption)",
+    caption.short = "(ref:searchOverview-scaption)",
+    booktabs = TRUE,
+    align = "cl"
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    row_spec(2:nrow(searchOverview_table) - 1, hline_after = TRUE) %>%
+    kableExtra::column_spec(1, bold = FALSE) %>%
+    kable_styling(latex_options = c("HOLD_position"),
+                  font_size = 10)  %>%
+    kableExtra::footnote(
+      threeparttable = TRUE,
+      general_title = "",
+      general = paste(
[…]

### 2021-10-05 R/forest flexi.R

@@ -1,4 +1,4 @@
-forest_strata_rob <- function(dat, dat_rob, rob_tool = "ROB2",rob_me = "Low",sei = NULL,...){
+forest_strata_rob <- function(dat, dat_rob, rob_tool = "ROB2",rob_me = "Low",sei = NULL, title = NULL, ...){
 
 ### calculate log risk ratios and corresponding sampling variances (and use
 ### the 'slab' argument to store study labels as part of the data frame)
@@ -150,9 +150,9 @@ tsize <- rob_psize * 0.3
 
 ### fit random-effects model
 if (!hasArg(sei)) {
-  res <- rma(yi, vi, data=dat, slab = paste0(author, ", ", year))
+  res <- rma(yi, vi, data=dat, slab = paste0(author, ", ", year), method = "DL")
 } else {
-  res <- rma(yi, sei = sei, data=dat, slab = paste0(author, ", ", year))
+  res <- rma(yi, sei = sei, data=dat, slab = paste0(author, ", ", year), method = "DL")
 }
 
 ### indent study names
@@ -220,10 +220,10 @@ par(op)
 
 if (!hasArg(sei)) {
 rma_flexi <- function(x) {
-  rma(yi, vi, subset = (overall == x), data = dat)
+  rma(yi, vi, subset = (overall == x), data = dat, method = "DL")
 } } else{
   rma_flexi <- function(x) {
-    rma(yi, sei=sei, subset = (overall == x), data = dat)
+    rma(yi, sei=sei, subset = (overall == x), data = dat, method = "DL")
   }
 }
 
@@ -258,6 +258,13 @@ for (i in 1:nrow(dat_rob_vec)) {
 }
 }
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+
+if(!is.null(title)){
+  par(font = 2)
+  text(x_min, y_max, pos=4, bquote(bold(underline(.(title)))), cex = 1.2)
+  par(op)
+}
 
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
@@ -268,9 +275,9 @@ if (length(unique(dat_rob$overall))>1 && nrow(dat)>2) {
 
   if (!hasArg(sei)) {
     
[…]

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Working version

@@
 
-# Systematic review of all evidence available on the association between blood lipids and dementia outcomes {#sys-rev-heading}
+# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Grouping multiple reports into studies
@@
 
-For
-
-A random-effects meta-analysis model was employed to combine the different included studies.
-<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
---> The fixed-effect method was implemented as:
-
-<!-- TODO Check these against those in Ben's thesis paper -->
-
-Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
+A straight-forward random-effects meta-analysis model was employed to combine the identified results. A random-effects model was chosen due to the ...
+
+<!-- TODO Finish this description -->
+
+Results were stratified into subgroups on the basis of the overall risk of bias 
+assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate.
 Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
-
-Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$
-
-\begin{equation}
-  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
-\end{equation}
-
-<!-- Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
-There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article.
-The estimate of $\tau^2$ is incorporated into the weighting of each study -->
-
-\begin{equation}
-  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
-\end{equation}
-
-<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g.
-log-ORs) between studies, with a variance of 𝜏2.
-The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance.
-The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance.
-So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis.
-If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model.
--->
-<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way.
-The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
-<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
-<!-- (2) -->
-<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
-<!-- (3) -->
-<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->
-
-<!-- \begin{equation} -->
-<!--   \theta_i = \mu + u_i -->
-<!--   (\#eq:meta-analysis-random) -->
-<!-- \end{equation} -->
-
-<!-- \begin{equation} -->
-<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
-<!--   (\#eq:meta-analysis-fixed) -->
-<!-- \end{equation} -->
-
-<!-- where ... -->
-
-<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
+All models were implemented using the `metafor` R package.
+
+&nbsp;<!----------------------------------------------------------------------->
 
 #### Dose-response analyses
-
-<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
 
@@
 Following best practice, studies judged to be at critical risk of bias should be excluded from any quantitative analyses.
-<!-- TODO CITATION NEEDED --> `r num_to_words(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e.
+<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e.
 the study reported unadjusted estimates).`r critical_citations`
@@
 
-`r num_to_words(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
 
@@
 
-<!-- TODO Cite excluded studies and list exclusion reasons -->
-
 <!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks -->
 
-Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
-The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
-
-&nbsp;
+```{r doseResponse, include = FALSE}
+```
+
+There were `r n_dr_initial` studies that were eligible for dose-response meta-analysis as they provide several categories of lipid exposure.
+However, following data extract, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
+
+Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of studies (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
+This analysis provided very weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
+Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
+
+(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
+
+```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:lipidsDoseResponse-cap)', out.width='70%', fig.scap='(ref:lipidsDoseResponse-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/dr_AD_TC.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-Data on another potentially important source of heterogeneity
+Data on another potentially important source of heterogeneity.
+
 Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
@@
 <!----------------------------------------------------------------------------->
-(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia
-
-(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
-
-```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-<!----------------------------------------------------------------------------->
 &nbsp;
@@
 The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
-For randomised controlled trials and non-randomised studies of interventions, the risk of missing.
-However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (as shown in Figures \@ref(fig:lipidFractionsDementia), \@(lipidFractionsAD) and lipidFractionsAD).
-A key example is
+For randomised controlled trials and non-randomised studies of interventions, the risk of bias due to missing evidence was assessed to be minimal.
+However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (Figures \@ref(fig:lipidFractionsDementia), \@ref(fig:lipidFractionsAD) and \@ref(fig:lipidFractionsVaD).
 
@@
 
-As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
+As show in Figure \@ref(fig:prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
 From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
 
-All identified preprinted studies were.
-However, including preprints did provide useful additional evidence value in a number of meta-analysis.
-For example, re-analysing the results of available for the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref) in Mendelian randomisation studies, illustrates that the result only available from a preprint contributed `r mrStatinPreprintWeight` of the weight in a fixed-effect meta-analysis.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis
-
-(ref:preprintWeights-scaption) Added information due to inclusion of preprints
-
-```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
+Including preprints did provide useful additional evidential value in a number of meta-analysis.
+To demonstrate this, the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref(fig:mrStatinADFig)) in Mendelian randomisation studies was re-analysed using a fixed-effect model.
+Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
+
+&nbsp;
+
+<!-- <!-----------------------------------------------------------------------------> -->
+<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->
+
+<!-- (ref:preprintWeights-scaption) Added information due to inclusion of preprints -->
+
+<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
+<!-- ``` -->
+<!-- <!-----------------------------------------------------------------------------> -->
 
@@
 
-Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date),[@andrews2019; @andrews2021].
-The final preprint has not yet been published.[@so2017]
+Investigation of the publication status of the two preprints reporting studies not also identified by the main search after a two-year lag found that one had been subsequently published in late 2019.[@andrews2019; @andrews2021] The final preprint has not yet been published.[@so2017]
 
@@
 This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-
-The discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
-A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise (Chapter \@ref(tri-heading)).
+This discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
+A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
 
@@
 There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogenity in exposure (e.g.
+This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
 mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
 
-Some evidence that age has impact on observed lipid-dementia relationship - use to link
+<!-- Some evidence that age has impact on observed lipid-dementia relationship - use to link  -->
 
@@
 This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
+Randomised controlled trials of dementia are particularly challenging, as the long follow-up made necessary by the long latent period of the condition, makes trials logistically challenging and financial expensive.
+Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), which appears in the literature in recent years, driven by the availability of summary genome wide association studies (GWAS) that form the basis of the two-sample Mendelian randomisation approach.
 
 <!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-A common theme across the evidence base was a lack of data on the association of vascular dementia.
-This is particularly interesting given that lipids and statins are primarily related to vascular disease.
-__Can't look forward to other chapter__ There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of GWAS of this outcome.
-
-<!--- 
-QUESTION
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-- No these studies should not be included, as not recognised criteria.
--->
-
-<!-- __Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
--->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk,[@shepherd2002a] reporting on cognitive outcomes as one of several secondary outcomes.
-While widely cited in relation to the effect of statins on dementia and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial only reported on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
+&nbsp;<!----------------------------------------------------------------------->
+
+A common theme was an absence of studies examining vascular dementia as an outcome, most noticeable when comparing the evidence base for statins in dementia/Alzheimer's (Figures \@ref(fig:obsStatinDementiaFig) & \@ref(fig:obsStatinADFig)) with that available for vascular dementia (Figure \@ref(fig:obsStatinVaDFig)).
+This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
+A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was very weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
+
+Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002a] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
 As such, this trial did not met the inclusion criteria for this review.
@@
 
-Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
-
-Generalisability was aided by the large number of studies performed using the Taiwan health database, which represents a good sources of evidence on non-Caucasian populations
+Risk of bias across the individual results was generally quite high, and the causes and expected directions of these biases are discussed in more detail in Chapter \@ref(tri-heading).
+Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of statin levels.
+In many cases, estimates were know to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
+These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009; @yamada2009a] In addition, some authors stated outright that non-significant results were not reported (e.g.
+"The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
+were not reported in the Table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided very weak evidence for an effect), other than increasing the precision of the summary estimate.
+
+Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:)), the applicability of my results to other populations is aided by th inclusion of studies which made use of data from the Taiwan health insurance database.
 
@@
 
-__This section will be completed once Georgia has completed her analysis, and can also be cross-references with the meta-meta analysis published is Brain Sciences recently.__
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
-
-Similar the on previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease was conducted prior to the majority of MR studies included in this review being published, and extracted results including SNPs in APoE4 (see the following section for a discussion of the bias this introduces).
-
-However, despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
+The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
+the Newcastle-Ottowa Scale).[@poly2020]
+
+I identified one previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease.
+However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).
+
+Despite these differences in time-scales and methodology, the duplication of work across reviews (including this review) is substantial.
 In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
@@
 
-One of the strengths of this review is it's inclusion of Mendelian randomisation studies as a source of evidence.
-
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
+One of the particular strengths of this review is the inclusion and critical assessment of Mendelian randomisation studies as a source of evidence.
+
+Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
+However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
 
@@
 
-```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='100%', fig.scap='(ref:mrAssumptions-scap)'}
+```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
@@
 Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI.
-As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
+Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availabilt of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses.
+As such, the process and tools for systematically assessing this study design are not as well developed.
 A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application.
+This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.
 
@@
 A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref().
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool, which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not access the additional methodological considerations of the analysis of the Mendelian randomisation analysis itself.
+While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias).
+Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
 <!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced on a recent review of systematic reviews of Mendelian randomisation studies.
-
-<!-- TODO Need to add some text to the ROB section of this chapter on distinction between reporting and quality -->
-
-<!-- Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants -->
-<!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
-<!-- TODO Email George with query on dual counting, following review of email with Julian -->
+--> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.
 
@@
 
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`).
+Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation" followed by manual review of studies that look across multiple risk factors would be advisable.
+This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (n=`r comma(16109)`).
 Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Talk about problem with studies sharing underlying datasets in two sample Mendelian randomisation frameworks - c.f.
-EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, Mendelian randomisation analysis can be multiple studies using the exact same summary statistics from the same cohorts
+Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit to the field.
 
 One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref()), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria of .
-
-Introduce assumptions underlying Mendelian randomisation (with image).
-Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
-Note the region must be quite wide - talk about controversy surrounding Benn paper
-
-Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
-This point is important given one of the core assumptions of
-
-MR are limited by the need for SNP to be present in both datasets (for TSMR).
-
-<!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
-
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here.
--->
-
-A key example of the importance of .
-In almost all cases, Mendelian randomisation studies examine.
-A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
-
-<!----------------------------------------------------------------------------->
-&nbsp;
+As covered in the introduction (see Section \@ref(intro-basic-science)), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
+In all cases, excluding these variants attenuates the observed effect to the null.
+A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
-The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
+The small number of studies returned by the searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
 The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
@@
 
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='80%',fig.align='center',fig.scap='(ref:preprintGrowth-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
@@
 Three relevant preprints from the bioRxiv hits were identified.
-The added evidential value of including these preprints was described in Section \ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
-Of note, all three included preprints described Mendelian randomisation analysis, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
+The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
+Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
 
 Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
-Firstly, preprints provide an advance snapshot of the literature, capturing preprinted articles that are subsequently published but were not .
-Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise.
-
-Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
-The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
-This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
+This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
+
+Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
+Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019b] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
 
 More recently, inclusion of preprints in systematic reviews has become significantly more widespread.
-This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
-How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
+This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.[@fraser2020preprinting] How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
 
@@
 
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important elements, and so these could not be extracted.
-This limiation was compounded by the expected low response rate to requests for further information from primary authors (although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019]).
-
+As discussed in Section \@ref(dose-response-results), many primary studies did not report important information required for the dose-response meta-analysis, and so could not be included in the synthesis.
+This limitation was compounded by the expected low response rate to requests for further information from primary authors.
 While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
 
-Based on my experience of extracting data for this review, I co-wrote an guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021]
-
-Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. __[Zenodo repository will be cited here]__
+Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.
+A copy of this publication is available in Appendix \@ref(published-papers).[@hennessy2021] In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
+__[Zenodo repository will be cited here]__
 
@@
 
-I believe there are four aspects where this review is distinct from those reviews already available in the published literature.
+I believe there are several aspects where this review is distinct from those reviews already available in the published literature.
 While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition
-
-In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).[@poly2020]
-
-This is important strength of this review, and a necessary art of the thesis, as the detailed risk of bias assessments are used in
-
-, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related manuscripts as a source of grey literature.
-As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
-
-<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
-they would not have been captured by the search for published papers) -->
-
-- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
-This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
-In addition this review was used to pilot an upcoming risk of bias tool
+<!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
+This repres important strength of this review, as the detailed risk of bias assessments are used in
+
+Thirdly, as discussed at length in the section above, in contrast to other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related preprints.
+Finally, as a secondary element, I used this review to pilot new research synthesis methodologies, in particular a new visualisation approach for risk-of-bias assessments and a forthcoming tool for assessing the risk-of-bias due to missing evidence.
 

### 2021-10-06 published/03-Chp-Systematic-Review.Rmd
Working version

--- 2021-10-06 03-Chp-Systematic-Review.Rmd
@@
 
-# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}
+# Systematic review of all evidence available on the association between blood lipids and dementia outcomes {#sys-rev-heading}
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
-
 #### Grouping multiple reports into studies
@@
 
-A straight-forward random-effects meta-analysis model was employed to combine the identified results. A random-effects model was chosen due to the ...
-
-<!-- TODO Finish this description -->
-
-Results were stratified into subgroups on the basis of the overall risk of bias 
-assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
+For
+
+A random-effects meta-analysis model was employed to combine the different included studies.
+<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
+--> The fixed-effect method was implemented as:
+
+<!-- TODO Check these against those in Ben's thesis paper -->
+
+Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate.
 Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
-All models were implemented using the `metafor` R package.
-
-&nbsp;<!----------------------------------------------------------------------->
+
+Random-effects analyses assume that differences in study design and execution mean that the study effects are normally distributed around a common treatment effect ($\mu$) with a variance of $\tau^2$
+
+\begin{equation}
+  \theta_i \sim \mathcal{N}(\mu, \tau^2) (\#eq:eq9)
+\end{equation}
+
+<!-- Random-effects methods estimate $\tau^2$ to estimate the common effect ($\mu$).
+There are many estimators of $\tau^2$ with varying assumptions [@Veroniki2016; @Bakbergenuly2020], the details of which are beyond the scope of this article.
+The estimate of $\tau^2$ is incorporated into the weighting of each study -->
+
+\begin{equation}
+  w_i = \frac{1}{v_i + \hat{\tau^2}} (\#eq:eq10)
+\end{equation}
+
+<!-- A random-effects meta-analysis allows for study-specific effects, and assumes that the true effect estimated by each study varies and is assumed to be randomly and normally distributed on the transformed scale (e.g.
+log-ORs) between studies, with a variance of 𝜏2.
+The between-study variance is estimated (usually using the “method of moments” or DerSimonian and Laird estimate), and used to modify the weights of studies when calculating the summary effect estimate and variance.
+The weight of each study is 1𝑣𝑖+𝜏2 where 𝑣𝑖 is the variance of the 𝑖𝑡ℎ study and 𝜏2 is the estimate of the between-study variance.
+So long as the between-study variance is larger than 0, smaller studies will be given more weight in random-effects meta-analysis than in a fixed-effect meta-analysis.
+If the between-study variance is 0, then the random-effects model is equivalent to the fixed-effect model.
+-->
+<!-- In both fixed-effect and random-effects inverse-variance meta-analysis, the summary effect estimate and variance are estimated in the same way.
+The effect estimates (𝜃𝑖) from each study can be (transformed) ORs, relative risks (RRs), standardised mean differences (SMDs) or other types of estimates: -->
+<!-- 𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡Σ𝑤𝑖𝜃𝑖Σ𝑤𝑖 -->
+<!-- (2) -->
+<!-- 𝑉𝑎𝑟𝑖𝑎𝑛𝑐𝑒⁡𝑜𝑓⁡𝜃̂𝑆𝑢𝑚𝑚𝑎𝑟𝑦=⁡1Σ𝑤𝑖 -->
+<!-- (3) -->
+<!-- where 𝜃𝑖 is effect estimate and 𝑤𝑖 is the weight from the 𝑖𝑡ℎ study on an approximately normal scale. -->
+
+<!-- \begin{equation} -->
+<!--   \theta_i = \mu + u_i -->
+<!--   (\#eq:meta-analysis-random) -->
+<!-- \end{equation} -->
+
+<!-- \begin{equation} -->
+<!--   $weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}$ -->
+<!--   (\#eq:meta-analysis-fixed) -->
+<!-- \end{equation} -->
+
+<!-- where ... -->
+
+<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
 
 #### Dose-response analyses
+
+<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
 
@@
 
-```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
+```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
@@
 
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='80%',fig.align='center',fig.scap='(ref:preprintGrowth-scap)'}
+```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))

### 2021-10-06 R/03-Code-Systematic-Review.R

@@ -206,6 +206,7 @@ if (doc_type == "docx") {
     row_spec(0, bold = TRUE) %>%
     kable_styling(latex_options = c("HOLD_position")) %>%
     kableExtra::add_header_above(c(" " = 2, "Initial screening decision" = 3)) %>%
+    kableExtra::column_spec(1, width = "12em") %>%
     kableExtra::column_spec(0:2, bold = T) %>%
     kableExtra::column_spec(4, border_right = T) %>%
     kableExtra::collapse_rows(columns = 1, valign = "middle") %>%
@@ -230,6 +231,7 @@ if (doc_type == "docx") {
     kable_styling(latex_options = c("HOLD_position"))  %>%
     kableExtra::add_header_above(c(" " = 2, "Initial screening decision" = 3)) %>%
     kableExtra::column_spec(0:2, bold = T) %>%
+    kableExtra::column_spec(1, width = "12em") %>%
     kableExtra::column_spec(4, border_right = T) %>%
     kableExtra::collapse_rows(columns = 1, valign = "middle") %>%
     kableExtra::row_spec(2, extra_css = "border-bottom: 1px solid")
@@ -1037,7 +1039,7 @@ critical <-
     primary == 1
   )
 
-critical_citations <- get_citations_per_analysis(n_critical)
+critical_citations <- get_citations_per_analysis(critical)
 
 n_critical <- critical %>%
   group_by(study_id) %>%
@@ -1217,16 +1219,23 @@ obsLipids <- purrr::map(dat$data,  ~ meta_estimate(.x, type = "HR"))
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- doseResponse
 
-results_tc_dr <-
+dat <-
   rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),
               which = 2) %>%
   general_filters() %>%
+  filter(exposure_category == "Lipids - DR")
+
+n_dr_initial <- dat %>%
+  distinct(study_id) %>%
+  nrow()
+
+dat <- dat %>%
   filter(
-    exposure_category == "Lipids - DR",
-    author != "Beydoun",
     !is.na(number_exposed),
-    !grepl("Quartile", dose_range),
[…]

### 2021-10-06 R/helper.R

@@ -652,9 +652,6 @@ get_all_citations <- function() {
                 which = 1) %>%
     janitor::clean_names() %>%
     filter(!is.na(citation)) %>%
-    select(citation) %>%
-    arrange(citation) %>%
-    distinct() %>%
     pull(citation)
   
   
@@ -677,9 +674,7 @@ get_citations_per_analysis <- function(data){
                 which = 1) %>%
     janitor::clean_names() %>%
     filter(!is.na(citation)) %>%
-    select(study_id, citation) %>%
-    group_by(study_id) %>%
-    distinct()
+    select(study_id, citation)
   
   
   citation_vec <- data %>%
@@ -792,12 +787,9 @@ meta_estimate <- function(dat, ...) {
     distinct(result_id) %>%
     nrow()
   
-  citations <- get_citations_per_analysis(dat)
-  
   return(list(
     n = dat_n,
-    estimate =  estimate(t$beta, t$ci.lb, t$ci.ub, exp = T, ...),
-    citations = citations
+    estimate =  estimate(t$beta, t$ci.lb, t$ci.ub, exp = T, ...)
   ))
 }
 

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Back to working versions

@@
 
-Following best practice, where summary data was presented across two groups (e.g.
+In line with best practice, where summary data was presented across two groups (e.g.
 age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
@@
 \end{equation}
+
+&nbsp;
 
@@
 This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
-This is largely because the tool did not exist when the protocol was originally registered.
+This is largely because the tool did not exist when the protocol was registered.
 
@@
 
-_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]_
+_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_
 
@@
 Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected.
+Many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
 <!-- TODO include some example citations here -->
@@
 The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using the identical summary statistics from published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
 
@@
 
-In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia `r n_VaD`.
-Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated, but were myc rarer.
+In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia (`r n_VaD`).
+Some other outcome classifications such as vascular-component or mixed dementia were also investigated, but were much rarer.
 
@@
 
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
+Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
 
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \ref(fig:mrDuplication)).
+Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
 However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
 Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
-However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \ref(mrDuplication)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
 Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
@@
 
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
 knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Draft of chapter 3

@@
 
-The use of the results of this review in subsequent chapters is dicussed.
+The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.
 
@@
 Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate.
-However, in this review, the small subset of studies reporting odds/risk ratios and synthesised separately to those reporting hazard ratios.
+However, in this review, the small subset of studies reporting odds/risk ratios are synthesised separately to those reporting hazard ratios.
 
@@
 RCTs were not combined in a meta-analysis with results from observational studies).
-The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading)
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Standard meta-analysis
-
-A straight-forward random-effects meta-analysis model was employed to combine the identified results. A random-effects model was chosen due to the ...
-
-<!-- TODO Finish this description -->
-
-Results were stratified into subgroups on the basis of the overall risk of bias 
-assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed.
-Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line around the overall effect estimate.
-Finally, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
+The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+#### Random-effects meta-analysis
+
+For results examining the effect of binary or continuous exposure (as opposed to categorical/dose-response, as discussed in the next section) on any dementia outcome, a random-effects meta-analysis model was used.
+Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
+The weight ($w$) assigned to each result (denoted as $y_i$) is then give as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
+
+Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:
+
+\begin{equation}
+\hat{y} = \frac{\sum{y_iw_i}}{\sum{w_i}}
+  (\#eq:rmaEstimate)
+\end{equation}
+
+\begin{equation}
+Var(\hat{y}) = \frac{1}{\sum{w_i}}
+  (\#eq:rmaVariance)
+\end{equation}
+
+&nbsp;
+
+Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
+Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
+Finally, where at least 10 results are available, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
 All models were implemented using the `metafor` R package.
@@
 (ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple analytical designs within a single study, and these have been duplicated across the relevant sub-sections.
+Note that three studies reported on multiple analytical designs within a single study report, and these have been duplicated across the relevant sub-sections.
 
@@
 
-As discussed above, the results of the risk-of-bias assessments are presented alongside their corresponding result.
-A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases at play.
-
-Following best practice, studies judged to be at critical risk of bias should be excluded from any quantitative analyses.
-<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any confounders (i.e.
+As discussed above, the risk-of-bias assessments are presented alongside their corresponding numerical result.
+A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
+
+For the two randomised controlled trials, both were judged to be at low risk of bias.
+In contrast, many of the non-randomised studies of statin use were at serious risk of bias due poor controlling for confounding, immortal time bias, and missing outcome data (as noted above, a judgement of low risk of bias for a non-randomised study is rare).
+Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g.
+examination of lipids as a binary or continuous variable).
+Finally, bias was introduced into Mendelian randomisation studies via the potential for hoziontal pleiotropy and population stratification.[@davies2018]
+
+Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.
+<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
 the study reported unadjusted estimates).`r critical_citations`
 
-<!-- Both randomised controlled trials were considered to be at low risk of bias.  -->
-
-<!-- For NRSI, common biases include immortal time (where participants in the exposure group are followed up) -->
-<!-- For NRSE  -->
-
-<!-- For MR studies, concerns over potential genetic pleiotropy -->
-
-<!-- Additionally, several synthesis were also assessed to be at risk of bias due to missing evidence.  -->
-
-<!-- A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
-This is discussed further in Section \@ref(rev-discussion-MR).
--->
-
-<!-- Several eligible studies included in the analysis did not have available results, either due to selective reporting of significant results in conference abstracts,[@su2017; @yamada2009b] or due to the unavailability of supplementary materials containing the relevant results.[@haag2009] -->
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
+(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
+
+(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+
+(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
-
-(ref:obsFibrateDementia-scap) Random effects meta-analysis of statins on all-cause dementia
+(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
+
+(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
 
@@
 
+<!-- TODO Deal with awkward hypercholesterolemia definition -->
+
 Across all outcomes, lipid levels were categorised in a number of ways.
@@
 
-`r obsHyperchol$Dementia$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
-
-(ref:obsHyperDementia-scap) sMeta-analysis of hypercholesterolemia on all-cause dementia
+`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
+
+(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsDementia-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsDementia-scap) Random effects meta-analysis of four lipid fractions on all-cause dementia
+(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
 ```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease
+(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+
+(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinAD-scap) Random effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
+(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsAD-scap) Random effects meta-analysis of four lipid fractions on Alzheimer's disease
+(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
+(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
+
+(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia
+
+```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsVaD-scap) Random effects meta-analysis of total cholesterol on vascular dementia
+(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
 
@@
 
-### Sources of heterogeneity
-
-Data on another potentially important source of heterogeneity.
-
-Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
-
-<!-- TODO Can only do meta-regression in analysis with 10 studies, so statins and hypercholesterolemia should -->
-
-Across all analysis with
-
-<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->
-
-<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->
-
-<!-- Also important to examine the effect of: -->
-
-<!-- * age at baseline -->
-<!-- * sex (percentage) -->
-<!-- * education -->
-<!-- * baseline cognitive scores (how to group) -->
-
-<!-- ### Sensitivity analyses -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Small study effects {#sys-rev-pub-bias}
-
-<!--    Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
-<!--    Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
-
-There was little evidence of small study effects across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
+### Additional analyses
+
+Investigation of potential sources of heterogeneity was complicated by two factors.
+In the first instance, few meta-analysis included more than 10 results, the recommended minimum.
+Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
+
+Age and sex were assessed as potential causes of heterogeneity for meta-analysis of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
+
+Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
+However, all analyses assessed provided weak evidence of small-study effects.
+
+[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]
 
@@
 
-&nbsp;
-
-<!-- <!-----------------------------------------------------------------------------> -->
+<!-- &nbsp; -->
+
+<!----------------------------------------------------------------------------->
 <!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->
@@
 <!-- ``` -->
-<!-- <!-----------------------------------------------------------------------------> -->
+<!----------------------------------------------------------------------------->
 
@@
 
-&nbsp;
+<!-- &nbsp; -->
 
@@
 <!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) __Study designs by year of publication__ -
+(ref:typeByYear-cap) Included study designs by year of publication
 
@@
 
-Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:)), the applicability of my results to other populations is aided by th inclusion of studies which made use of data from the Taiwan health insurance database.
+Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of studies which made use of data from the Taiwan health insurance database.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
+(ref:preprintGrowth-cap) Growth of preprint repositories over time.
+Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
 

### 2021-10-06 03-Chp-Systematic-Review.Rmd
Draft of chapter 3

@@
 
-### Added evidental value of including preprints {#sys-rev-including-preprints-res}
+### Added evidential value of including preprints {#sys-rev-including-preprints-res}
 
@@
 While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias).
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
+Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
 <!-- TODO Read this tool.
@@
 One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref(intro-basic-science)), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
+As covered in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
 In all cases, excluding these variants attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
+A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
 

### 2021-10-07 03-Chp-Systematic-Review.Rmd
Submitted draft of Chapter 3

@@
 Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, few meta-analysis included more than 10 results, the recommended minimum.
+In the first instance, few meta-analysis included more than 10 results, the recommended minimum required for meta-regression.
 Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
 
-Age and sex were assessed as potential causes of heterogeneity for meta-analysis of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
+Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
 

### 2021-10-07 R/03-Code-Systematic-Review.R

@@ -1528,32 +1528,35 @@ img$TG <-
 
 # setup plot
 try(dev.off())
-pdf(
-  here::here("figures/sys-rev/fp_lipids_composite_Dementia.pdf"),
-  width = 8,
-  height = 12
-)
-par(mai = rep(0, 4)) # no margins
 
-# layout the plots into a matrix w/ 12 columns, by row
-layout(matrix(1:4, ncol = 1, byrow = TRUE))
-
-# do the plotting
-for (i in 1:4) {
-  plot(
-    NA,
-    xlim = 0:1,
-    ylim = 0:1,
-    bty = "n",
-    axes = 0,
-    xaxs = 'i',
-    yaxs = 'i'
+  pdf(
+    here::here("figures/sys-rev/fp_lipids_composite_Dementia.pdf"),
+    width = 8,
+    height = 12
   )
-  rasterImage(img[[i]], 0, 0, 1, 1)
-}
+  par(mai = rep(0, 4)) # no margins
+  
+  # layout the plots into a matrix w/ 12 columns, by row
+  layout(matrix(1:4, ncol = 1, byrow = TRUE))
+  
+  # do the plotting
+  for (i in 1:4) {
+    plot(
+      NA,
+      xlim = 0:1,
+      ylim = 0:1,
+      bty = "n",
+      axes = 0,
+      xaxs = 'i',
+      yaxs = 'i'
+    )
+    rasterImage(img[[i]], 0, 0, 1, 1)
+  }
+  
+  # write to PDF
+  dev.off()
 
-# write to PDF
-dev.off()
+
 
 
 ## Don't need to do for vascular dementia as only one lipid fraction (TC) has

### 2021-10-08 07-Chp-Triangulation.Rmd
Creat final thesis structure

--- 2021-09-28 _main.Rmd
@@
----
-#####################
-## thesis metadata ##
-#####################
-title: |
-   Lipids and dementia:\
-   An investigation of their relationship
-
-author: Luke A McGuinness
-college: 
-degree: Doctor of Philosophy
-degreedate: 2022
-word-count: |
-  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
-abstract: |
-  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
-acknowledgements: |
-  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
-declaration: |
-  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
-dedication: For Brendan McHugh
-covidStatment: |
-  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
-abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
-
-#######################
-## bibliography path ##
-#######################
-bibliography: [bibliography/references.bib, bibliography/packages.bib]
-csl: bibliography/nature.csl
-bibliography-heading-in-pdf: Bibliography
-
-#####################
-## PDF formatting  ##
-#####################
-abstractseparate: true  # include front page w/ abstract for examination schools?
-bib-humanities: false   #set to true if you want in-text references formatted as author-year
-doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
-draft: false # add as DRAFT mark in the footer?
-page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
-hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
-toc-depth: 2 # depth of heading to include in table of contents
-lof: true # list of figures in front matter?
-lot: true # list of tables in front matter?
-mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
-mini-toc-depth: 1
-mini-lot: false  # mini-list of tables by start of each chapter?
-mini-lof: false  # mini-list of figures by start of each chapter?
-
-params:
-  corrections: true # set false to stop applying blue background to blocks of corrections
-
-#####################
-## output options  ##
-#####################
-output:
-  bookdown::pdf_book:
-    template: templates/template.tex
-    keep_tex: true
-    citation_package: default 
-    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
-  bookdown::gitbook:
-    css: templates/style.css
-    download: ["pdf"]
-    output_dir: "docs"
-    split_bib: false
-    config:
-      toc:
-        before: |
-          <li><a href="./">Thesis - Draft</a></li>
-        after: |
-          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
-      sharing:
-        facebook: false
-        twitter: yes
-        all: false
-  bookdown::word_document2:
-    output_dir: "docs"
-    toc: true
-    toc_depth: 2
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false   
-link-citations: true
-documentclass: book
-
----
-
-```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
-source('scripts_and_filters/create_chunk_options.R')
-source("R/helper.R")
-options(scipen=999)
-```
-
-<!--
-Include the create_chunk_options chunk above at the top of your index.Rmd file
-This will include code to create additional chunk options (e.g. for adding author references to savequotes)
-If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
--->
-
-```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
-```
-
-<!--chapter:end:index.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Introduction {#intro-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-## Additional ideas
-
-### General
-
-* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published.
-Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished.
-
-* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.
-
-*
-
-### Background
-
-### medrxivr
-
-###
-
-&nbsp;
-
-<!--chapter:end:00-Chp-Introduction.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2:
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
-Science knows it doesn't know everything; otherwise, it'd stop.
-```
-
-(ref:dara-quote) --- Dara O'Briain
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/01-Code-Background.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-# Background, Theoretical framework, Aims & Objectives {#background-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-## Lay summary
-
-[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]
-
-Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
-Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition.
-The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change.
-Avoiding a risk factor does not guarantee that a person will not develop dementia but makes it less likely.
-A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
-The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
-
-This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them.
-It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
-Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction
-
-This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
-It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research.
-It then provides background on blood lipids and lipid-modifying treatments, and summarises the types of evidence used to examine the effect of these exposures on dementia outcomes.
-
-The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
-Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
-
-<!----------------------------------------------------------------------------->
-
-## Dementia
-
-<!----------------------------------------------------------------------------->
-
-### Definition and underlying pathologies {#underlying-pathologies}
-
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
-
-Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.
-Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
-Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
-
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
-
-The remaining 10-30% of cases are caused by other dementia subtypes (e.g.
-Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).[@burns2009]
-
-<!----------------------------------------------------------------------------->
-
-### Diagnostic criteria {#diagnostic-criteria}
-
-Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]
-
-(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.
-
-```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
-
-Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
-The distinction between these memory scales and diagnostic criteria presented above should be noted.
-For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
-Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
-
-Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
-Cause-specific criteria exist for the diagnosis of dementia sub-types.
-For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
-
-<!-- ### Differing risk by sex -->
-
-<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->
-
-<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
-
-<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->
-
-<!----------------------------------------------------------------------------->
-
-### Public health importance
-
-Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only one without a proven cure.
-
-Dementia also has a substantial economic impact.
-In 2015, the estimated total cost of dementia in England was £24.2 billion.
-Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]
-
-As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.
-
-<!----------------------------------------------------------------------------->
-
-### Treatments {#intro-treatments}
-
-Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020].
-At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.
-
-The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
-Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]
-
-### Risk factors
-
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
-
-The benefits of a prevention-based approach based on addressing these risk factors are well-studied.
-Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
-
-In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
-
-This thesis will focus on blood lipids as the primary risk factor of interest.
-The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the existing evidence for an association between lipids and dementia outcomes.
-
-<!----------------------------------------------------------------------------->
-
-## Serum lipids
-
-<!----------------------------------------------------------------------------->
-
-### Lipid fractions {#intro-lipid-fractions}
-
-The blood lipid profile contains a range of component parts, or fractions.
-However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
-
-Triglycerides are the simplest and most common type of lipids found across the body.
-They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
-Low-density-lipoprotein cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
-In contrast, High density-lipoprotein cholesterol (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
-
-In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood.
-The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
-
-\begin{equation}
-  TC \approx LDLc + HDLc + kTG
-  (\#eq:total-cholesterol-formula)
-\end{equation}
-
-where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
-
-Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
-
-(ref:lipidLevels-scaption) Classification of blood lipid levels
-
-```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
-These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.
-
-<!----------------------------------------------------------------------------->
-
-### Statins {#intro-statins}
-
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
-This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.
-
-(ref:statin-mechanisam-scap) Statin mechanism of action
-
-```{r statin-mechanisam, echo = FALSE, results="asis",fig.pos = "H", fig.align = 'center', fig.cap='(ref:statin-mechanisam-cap)', out.width='50%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/background/statinPath.png"))
-```
-
-&nbsp;
-
-Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)).
-Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g.
-ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-<!-- TODO Review the look and feel of this table -->
-
-(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.
-
-(ref:statinOverview-scaption) Overview of common statins
-
-```{r statinOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Other lipid regulating agents (LRA)
-
-There are several other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
-However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
-
-<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->
-
-The most commonly used non-statin therapeutic is ezetimibe,[@kosoglou2005] which prevents intestinal absorption of cholesterol.
-However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).[@genest2006]
-
-Fibrates provide a second example of non-statin therapy.
-They are used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
-They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
-
-Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.
-
-Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.
-
-```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Evidence for the association between blood lipids and dementia {#evidence-association}
-
-This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
-
-<!----------------------------------------------------------------------------->
-### Basic science
-
-A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]
-
-Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.
-
-<!----------------------------------------------------------------------------->
-### Observational studies
-
-By far the largest source of evidence on the relationship between comes from observational designs.
-Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a].
-With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]
-
-Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020c] on dementia outcomes have been performed.
-However, these reviews have several limitations.
-Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey2015;@poly2020c]
-
-<!----------------------------------------------------------------------------->
-
-### Randomised controlled trials
-
-In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.
-
-While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
-One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
-
-Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
-As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
-
-Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
-Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]
-
-<!----------------------------------------------------------------------------->
-
-### Mendelian randomisation
-
-Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
-
-1. the IV is associated with the exposure of interest (the relevance assumption);
-2. the IV and outcome do not share a common cause (the independence assumption); and
-3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).
-
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]
-
-Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In summary, multiple sources of evidence exist on the relationship between statins and dementia.
-In the next section, I introduce the synthesis of diverse sources of evidence as the theoretical framework used in this thesis.
-
-<!----------------------------------------------------------------------------->
-
-## Theoretical framework: Evidence synthesis
-
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
-
-The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
-
-This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
-Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:
-
-* Inclusion of preprints
-* Triangulation across evidence sources
-* Individual patient data meta-analysis
-
-These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.
-
-<!----------------------------------------------------------------------------->
-
-### Inclusion of preprints  {#diverse-sources-preprints}
-
-<!-- TODO Incorporate Julian's comments below -->
-
-<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
-Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
-It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
-Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
-We have no clear and widely used definition of grey literature.
--->
-
-The importance of including grey (or gray) literature in systematic reviews is widely acknowledged.
-Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]
-
-A important developing source of grey literature are preprints.
-Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
-
-One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
-Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
-
-In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic.
-However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
-
-<!----------------------------------------------------------------------------->
-### Triangulating across study designs {#intro-triangulation}
-
-As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
-
-This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.
-
-All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading).
-Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
-
-Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Individual patient data meta-analysis
-
-Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]
-
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
-
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
-
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
-Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
-
-In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop.
-The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.
-
-I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
-<!----------------------------------------------------------------------------->
-
-## Thesis overview
-
-### Aims and objectives
-
-The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes
-
-The specific research objectives that this thesis seeks to address are:
-
-* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
-* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
-* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
-* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
-
-### Structure {#thesis-structure}
-
-Chapters are self-contained, presenting the methods and results of that specific research project.
-They are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
-
--   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
--   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
--   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis.
-The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.
-
-An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)
-
-\blandscape
-<!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading).
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
-
-(ref:thesisOverview-scaption) Summary of studies included in this thesis
-
-```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape
-
-## Outputs from this thesis {#thesis-output}
-
-The outputs of this thesis are detailed below, and include peer-reviewed papers, presentations, and open-source evidence synthesis tools.
-
-### Contributions to the scientific literature
-
-During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.
-
-<!-- TODO Ideally the two preprints for the CPRD and systematic review papers will go here -->
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and L Schmidt.
-(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R.
-Journal of Open Source Software 5.54 2651.
-DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
-
-A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
-As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see Section \@ref(sys-rev-tools-intro) for more details).
-
-&nbsp;
-
-_Hennessy, E.
-A., Acabchuk, R., Arnold, P.
-A., Dunn, A.
-G., Foo, Y.
-Z., Johnson, B.
-T., Geange, S.
-R., Haddaway, N.
-R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
-Welch, V.,  **McGuinness L.
-A.** (2021).
-Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
-Prevention Science .
-DOI: [10.1007/s11121-021-01279-8](https://doi.org/10.1007/s11121-021-01279-8)_
-
-The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers.
-This piece was co-written with Dr.
-Emily Hennessy (see Author Declarations in the front materials).
-<!-- TODO Need to create author declarations section -->
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Higgins J.
-P.
-T.
-(2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method).
-DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
-
-The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
-See Appendix \@ref(appendix-robvis) for more details on this tool.
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Sheppard A.
-L.
-2020.
-“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887.
-DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_
-
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
-
-&nbsp;
-
-For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
-
-&nbsp;
-
-### Presentations/Talks
-
-<!--- Include links here for slides for each talk/poster --->
-
-_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Poster presentation, Alzheimer's Association International Conference 2021.
-&nbsp;
-
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
-
-&nbsp;
-
-_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.
-
-&nbsp;
-
-_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
-
-### Software {#outputs-software}
-**`medrxvir`**
-
-An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
-See Chapter \@ref(sys-rev-tools-heading) for more details.
-Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:
-
-```{r, eval = FALSE}
-# CRAN version
-install.packages("medrxivr")
-
-# Development version
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-**`robvis`**
-
-An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
-See Appendix \@ref(appendix-robvis) for more details.
-Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:
-
-``` {r, eval = FALSE}
-# CRAN version
-install.packages("robvis")
-
-# Development version
-devtools::install_github("mcguinlu/robvis")
-```
-
-&nbsp;
-
-## Summary
-
-This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.
-
-\newpage
-
-## References
-
-<!--chapter:end:01-Chp-Background.Rmd-->
-
 ---
@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
-Why are open source statistical programming  
-languages the best?
-
-Because they R.
-```
-
-(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
-
-# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r setup, include=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-library(medrxivr)
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO I might need to make it clearer thatthe tool was always intended to search both databases, as medRxiv grew out of bioRxiv categories, and no relevant records identified by the search in medRxiv -->
-
-## Lay summary
-
-Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal.
-They represent an important source of scientific literature.
-A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way.
-Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction {#sys-rev-tools-intro}
-
-Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)).
-As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
-The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which launched in 2019 and was designed to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv.[@rawlinson2019]
-
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
-As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
-
-This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool I created to facilitate the systematic searching of medRxiv and bioRxiv preprints.
-The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in my own projects and by other researchers is discussed.
-As the majority of work on this aspect of my thesis is represented by lines of code or online documentation (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr) and [https://docs.ropensci.org/medrxivr/](https://docs.ropensci.org/medrxivr/) respectively), this chapter is an intentionally short, high-level summary of my work on this project.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.[@zotero-15029]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-<!-- IDEA Could remake this using Diagrammr? -->
-
-(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow** - `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
-Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
-
-(ref:medrxivr-sr-scap) Role of `medrxivr` in a systematic review workflow
-
-```{r medrxivr-sr, echo = FALSE, fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-## Development
-
-<!-- IDEA Add timeline chart as seen here: https://bookdown.org/alecri/thesis/4-methods.html#sec:dosresmeta -->
-
-### Success criteria {#success-criteria}
-
-I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
-The criteria were as follows:
-
-1.  reliable, reproducible and transparent search functionality, allowing for Boolean (AND/OR/NOT) operator logic;
-
-2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
-
-3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Alternative medRxiv/bioRxiv interfaces
-
-Prior to development of this tool, I conducted an audit of existing tools for accessing medRxiv and bioRxiv metadata.
-While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
-
-The first, a platform called Rxivist[@abdill2019], allows users to search preprints using keywords.
-However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface[@zotero-15027] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
-
-The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
-As such, the platform only returns the most recent `r comma(1000)` records by publication date.
-
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Early versions
-
-Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and I released the initial version of the `medrxivr` R package in February 2020.
-
-Early versions of the tool had a reliance on scraping data directly from the repository website.
-Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required me to regularly update or fix the script.
-
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
-This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Package infrastructure
-
-I wrote the `medrxvir` package in R using RStudio,[@rcoreteam2019] and followed development best-practice, including development of detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Usage
-
-The `medrxivr` R package is split into two component parts:
-
--   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
--   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
-
-The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy.
-This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.
-
-While the package allows users to interact with and search both medRxiv and bioRxiv metadata, as the process is identical for both, searching the medRxiv database is used as an illustrative example throughout this chapter.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Installation
-
-`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code:
-
-&nbsp;
-
-```{r, eval = FALSE}
-install.packages("medrxivr")
-```
-
-&nbsp;
-
-Alternatively, the development version of the package can be installed from GitHub:
-
-&nbsp;
-
-```{r, eval = FALSE}
-# install.packages("devtools") 
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Importing preprint metadata
-
-<!-- TODO Clean up this section -->
-
-<!-- REVIEW Not clear why there are two, or what are advantages or disadvantages of each. There’s a hint below (“can become unavailable during peak usage times”), but perhaps add some more -->
-
-Prior to searching the metadata, it must first be imported in R.
-In `medrixvr`, I have provided two separate but related methods for users to import the data (Figure \@ref(fig:medrxivr-data-sources)).
-The first of these methods, accessed via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Get a copy of the database from the live medRxiv API endpoint
-mx_data <- mx_api_content()
-```
-
-&nbsp;
-
-This provides an up-to-the-minute reflection of the medRxiv preprint repository.
-However, this approach has two limitations.
-Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database  <!-- TODO Get numbers here, at a given date --> requires a time-intensive process of cycling through multiple pages.
-Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
-
-To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Import a copy of the medRxiv data from the snapshot
-mx_data <- mx_snapshot()
-```
-
-&nbsp;
-
-This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file to an online server (Figure \@ref(fig:medrxivr-data-sources)).
-Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
-
-The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
-However, given that the number of records added each day is relatively low, this should pose minor issues.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources** - Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
-Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
-
-(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources
-
-```{r medrxivr-data-sources, fig.pos="H", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Performing a search
-
-Once a local copy of the metadata is created, the first step in searching it is to create a search strategy.
-Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(...)`).
-
-&nbsp;
-
-```{r, eval = TRUE}
-# Create the search query
-topic1  <- c("dementia","alzheimer's")  # Combined with OR
-topic2  <- c("lipids","statins")        # Combined with OR
-
-myquery <- list(topic1, topic2)         # Combined with AND
-```
-
-&nbsp;
-
-For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
-There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
-Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
-"randomi*s*ation" vs "randomi*z*ation".
-
-Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Run the search
-results <- mx_search(mx_data,
-                     myquery)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Refining a search
-
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.[@rethlefsen2021prisma]
-
-&nbsp;
-
-```{r, eval = FALSE}
-results  <- mx_search(mx_data,
-                      myquery,
-                      report = TRUE)
-```
-
-```{r, eval = FALSE}
-## Found 1 record(s) matching your search.
-## 
-## Total topic 1 records: 224
-## dementia: 224
-## alzheimer's: 0
-## 
-## Total topic 2 records: 119
-## lipids: 90
-## statins: 33
-```
-
-&nbsp;
-
-This allows users to discover which terms in their search are contributing most to the total number of results returned.
-This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
-It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results.
-As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
-
-<!-- TODO Add some text to this section about the challenges of defaults, and the fact that the autocaps option exists -->
-
-<!-- REVIEW Can you not just make the search case insensitive?
-It means you often need to include capitalized and non-capitalized versions in case a word appears at the start of a sentence or is capitalized for some other reason?
-(I find a lot of people these days pseudo-randomly capitalize words for no good reason (like you did in “Application Programming Interface” on page 4 above!!)) -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Exporting to a bibliography file
-
-In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
-While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
-
-For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
-
-&nbsp;
-
-```{r, eval = FALSE}
-mx_export(results, 
-          file = "medrxiv_export.bib",
-          report = TRUE)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Downloading the PDFs of relevant records
-
-`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
-`mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
-This functionality is similar to the "Find Full Text" feature offered by EndNote.
-
-&nbsp;
-
-```{r, eval = FALSE}
-mx_download(results,  # Search results, less excluded records
-            "pdf/")   # Directory to save PDFs to 
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-### Reception and future plans
-
-```{r, echo = FALSE, warning=FALSE}
-
-medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = "2021-12-01")
-
-medrxivr_downloads <- plyr::round_any(sum(medstats$count), 100, f = floor)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-```
-
-The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]
-
-The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
-
-Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing.
-This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
-For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Use case
-
-In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
-For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
-
-By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two differnt publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
-We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
-This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
-Author contributions are discussed in the
-
-In short, this use case illustrates that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints as a part of evidence synthesis exercises.
-
-<!----------------------------------------------------------------------------->
-
-### Limitations of `medrxivr` {#medrxivr-limitations}
-
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
-However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
-A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
-
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
-
-<!-- TODO Clean-up this section -->
-
-<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
-
-```{r, include=FALSE}
-med_res <-
-  # Use snapshot from July 2021
-  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
-                      "*",
-                      from_date = "2019-07-01",
-                      to_date = "2019-08-01") %>%
-mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
-  group_by(pub_ind) %>%
-  count()
-
-published <- med_res$n[2]
-publication_n <- sum(med_res$n)
-publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
-```
-
-<!-- TODO Need to finish this bit and move it to the use-case section! -->
-
-Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
-`r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
-allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
-
-<!-- TODO replicate this analysis -->
-
-It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Role of open source tools in evidence synthesis
-
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
-
-<!----------------------------------------------------------------------------->
-
-## Summary
-
--   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
-
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
-
--   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
-
-\newpage
-
-## References
-
-<!--chapter:end:02-Chp-Systematic-Review-Tools.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-documentclass: book
----
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
-```
-
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
-
-# Systematic review of all evidence available on the association between blood lipids (and treatment) and dementia outcomes {#sys-rev-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!-- ## To Do -->
-
-<!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-<!-- * Statins and the risk of dementia Jick -->
-
-## Lay summary
-
-Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
-They do this by finding and combining the results from many related primary research studies.
-Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
-
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
-
-There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
-I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipids were not associated with any outcome.
-The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
-
-The use of the results of this review in subsequent chapters is dicussed.
-
-<!-- TODO Search for MCI -->
-
-<!-- TODO text -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-## Introduction {#sys-rev-intro}
-
-In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
-This analysis sought to address two specific aims.
-
-Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
-These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
-However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
-Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
-As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.
-
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies.
-As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
-This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
-
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Methods
-
-### Protocol
-
-A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Contributions
-
-In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration).
-<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
-In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
-
-<!-- TODO Double check this list at the end of the project. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Search strategy
-
-I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
-<!-- TODO Need to actually attach each search strategy.
-Should be able to loop through search strategy results.
--->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic.
-The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
-
-(ref:searchOverview-scaption) searchOverview
-
-```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
-
-<!-- TODO need to comment on this feed-back process, or remove -->
-
-I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
-
-Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-In addition, the abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
-<!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Study selection
-
-Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
-those matched based on the "Title" field alone).
-
-Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.
-
-Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer.
-In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
-Reasons for exclusion at this stage were recorded.
-Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
-
-The criteria used to assess eligibility are presented in the subsequent sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Inclusion criteria
-
-I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
-Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants were screened for dementia at baseline and prevalent cases excluded.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits were placed on the sample size of included studies.
-
-Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.
-
-<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
-
-<!-- TODO Any study using EHR - go back and extract codelists -->
-
-No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Exclusion criteria
-
-Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded.
-Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
-Studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia) were excluded.
-Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status.
-Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
-
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) were excluded.
-Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
-Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Validation of screening process
-
-Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
-assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
-assessment of accuracy).
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
-
-Gwet's AC1 is defined as:
-
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
-
-In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
-
-\begin{equation}
-  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
-  (\#eq:AC1-main)
-\end{equation}
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-\begin{equation}
-  q = \frac{(A+C)+(A+B)}{2N}
-  (\#eq:AC1-supp)
-\end{equation}
-
-<!-- TODO Need to be sure of how to calculate. -->
-
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
-Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Data extraction
-
-Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
-I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
-
-#### Study-fication
-
-As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
-Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Combining across groups
-
-Following best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups.
-[@higgins2019]
-
-\begin{equation}
-N = N_1 + N_2
-  (\#eq:combiningGroups1)
-\end{equation}
-
-\begin{equation}
-Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
-  (\#eq:combiningGroups2)
-\end{equation}
-
-\begin{equation}
-SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
-  (\#eq:combiningGroups3)
-\end{equation}
-
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Harmonisation of cholesterol measures
-
-<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
-not providing qratile cut-off values, not poviding numbers per group, etc.
---> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
-
-\begin{equation} 
-  mg/dL = mmol/L \times{} Z
-  (\#eq:lipidConversion)
-\end{equation}
-
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Following up with authors {#contacting-authors}
-
-Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Analysis of varying effect measures
-
-<!-- TODO Include formulae and informed assumptions  -->
-
-The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]
-
-Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
-Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
-<!-- TODO Need to really fix this -->
-
-In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk-of-bias assessment {#risk-of-bias}
-
-A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
-To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
-
-There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
-Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
-
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
-For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.
-
-In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
-The study design-specific tools are introduced and discussed in more detail in the following sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Randomised controlled trials
-
-Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
-Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
-Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
-Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Non-randomised studies of interventions/exposures
-
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
-Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial.
-Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
-
-While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level.
-The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
-In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
-Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Mendelian randomisation studies
-
-At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Risk of bias due to missing evidence
-
-A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
-<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
-
-This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
-This is largely because the tool did not exist when the protocol was originally registered.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Analysis methods
-
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design
-
-Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-<!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
-
-Of note, studies were not combined across different study designs (i.e.
-RCTs were not combined in a meta-analysis with results from observational studies).
-The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Standard meta-analysis
-
-Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
-<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
---> The fixed-effect method was implemented as:
-
-<!-- TODO Check these against those in Ben's thesis paper -->
-
-\begin{equation}
-  \theta_i = \mu + u_i
-  (\#eq:meta-analysis-random)
-\end{equation}
-
-\begin{equation}
-  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
-  (\#eq:meta-analysis-fixed)
-\end{equation}
-
-<!-- where ... -->
-
-<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
-
-#### Dose-response analyses
-
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
-
-<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
-
-This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
-
-Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
-for example, highest vs lowest quartile).
-<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
---> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
-
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
-
-A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
-Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
-
-Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity analyses
-
-I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
-<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
-_A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
-<!-- TODO Need more here -->
-
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
-<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Visualisation of results
-
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
-
-One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-
-In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Assessment of added value of including preprints
-
-__[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]__
-
-Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
-
-As a sensitivity analysis, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Results
-
-<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
-
-### Initial search and validation of search filters
-
-The database search identified `r num_to_text(23447)` records, of which
-
-<!-- TODO Cross check this with the actual numbers included -->
-
-Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected.
-<!-- TODO include some example citations here -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Screening results
-
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-<!-- TODO Check these figures & Finish PRISMA -->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
-change in cognitive scores).
-
-### Validation of screening
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
-
-```{r prisma-flow-setup, include = FALSE}
-```
-
-\blandscape{}
-
-&nbsp;
-
-(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-\elandscape{}
-
-<!----------------------------------------------------------------------------->
-
-```{r agree-setup, include = FALSE}
-```
-
-For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
-For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
-
-<!-- TODO Include AC1 result in caption above -->
-
-(ref:agreeInter-scaption) Inter-rater agreement
-
-```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
-
-(ref:agreeIntra-scaption) Inter-rater agreement
-
-```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline/MCI versus dementia, and the definition of eligible lipids fractions.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies
-
-```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
-```
-
-Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
-Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
-
-Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
-For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
-Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
-
-Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
-
-Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
-
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
-All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
-
-Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
-As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
--->.
-As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
-
-<!--- TODO Figures and tables to include here:
-
--   Summary of risk of bias (not done)
-
---->
-
-<!-- TODO Also need to extract the codes used in each study -->
-
-<!-- TODO Need to add abbreviations to table -->
-
-\blandscape{}
-<!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple study designs, and these have been duplicated across the relevant sub-sections.
-
-(ref:studyCharacteristics-scaption) Characteristics of included studies
-
-```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape{}
-
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
-
-<!----------------------------------------------------------------------------->
-```{r cohortLocationsSetup, include = FALSE}
-```
-
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
-
-(ref:cohortLocations-scap) Geographical distribution of study cohorts
-
-```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
-```
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
-
-### Risk of bias {#risk-of-bias-res}
-
-As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
-
-However, as a brief summary of the biases at play:
-
-Both randomised controlled trials were considered to be at low risk of bias.
-
-For NRSI
-For NRSE
-
-For MR studies
-
-Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
-A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
-This is discussed further in Section \@ref(rev-discussion-MR).
-
-<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
-
-Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### All-cause dementia
-
-__Statins__
-
-```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
-
-__Lipids__
-
-* NRSE
-
-* MR studies per 1-SD
-
-In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
-
-&nbsp;
-
-Several studies presented results per SD change in a lipid fraction.
-
-In Mendelian randomisation studies, a similar
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Alzheimer's disease
-
-There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease
-
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
-The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-__Lipids__
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Vascular dementia
-
-__Statins__
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-__Lipids__
-
-### Dose response meta-analysis of lipid levels {#dose-response-results}
-
-<!-- TODO Cite excluded studies and list exclusion reasons -->
-
-Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
-The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
-
-&nbsp;
-
-### Sources of heterogeneity
-
-Data on another potentially important source of heterogeneity
-Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
-
-<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->
-
-<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->
-
-<!-- Also important to examine the effect of: -->
-
-<!-- * age at baseline -->
-<!-- * sex (percentage) -->
-<!-- * education -->
-<!-- * baseline cognitive scores (how to group) -->
-
-<!-- ### Sensitivity analyses -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Sensitivity analysis
-
-Given that the majority of the studies included in the review were of
-
-### Small study effects {#sys-rev-pub-bias}
-
-<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
-<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
-
-There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
-
-<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
-
-<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
-Depsite attempts to obtain this additional information through contact with a -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia
-
-(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
-
-```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Added evidental value of including preprints {#sys-rev-including-preprints-res}
-
-<!-- TODO Will have to get actual numbers for this section -->
-
-As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
-
-For the analysis of XX on YYY, preprints added ...
-
-Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
-
-<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-<!-- TODO Check inclusion of Rockwood 2002:  -->
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-
-The discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
-A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise (Chapter \@ref(tri-heading)).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Summary of findings
-
-There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogenity in exposure (e.g.
-mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
-
-Some evidence that age has impact on observed lipid-dementia relationship - use to link
-
-The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
-This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
-
-<!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) __Study designs by year of publication__ -
-
-(ref:typeByYear-scap) Study designs by year of publication
-
-```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A common theme across the evidence base was a lack of data on the association of vascular dementia.
-This is particularly interesting given that lipids and statins are primarily related to vascular disease.
-__Can't look forward to other chapter__ There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of GWAS of this outcome.
-
-<!--- 
-QUESTION
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-- No these studies should not be included, as not recognised criteria.
--->
-
-<!-- __Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
--->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk,[@shepherd2002a] reporting on cognitive outcomes as one of several secondary outcomes.
-While widely cited in relation to the effect of statins on dementia and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial only reported on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
-As such, this trial did not met the inclusion criteria for this review.
-
-<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
-The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
-from Anstey 2017 -->
-
-Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Comparison with previous reviews {#rev-previous-reviews}
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-__This section will be completed once Georgia has completed her analysis, and can also be cross-references with the meta-meta analysis published is Brain Sciences recently.__
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
-
-Similar the on previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease was conducted prior to the majority of MR studies included in this review being published, and extracted results including SNPs in APoE4 (see the following section for a discussion of the bias this introduces).
-
-However, despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
-In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
-
-One of the strengths of this review is it's inclusion of Mendelian randomisation studies as a source of evidence.
-
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
-
-Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI.
-As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
-A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application.
-
-Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref().
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool, which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not access the additional methodological considerations of the analysis of the Mendelian randomisation analysis itself.
-<!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced on a recent review of systematic reviews of Mendelian randomisation studies.
-
-<!-- TODO Need to add some text to the ROB section of this chapter on distinction between reporting and quality -->
-
-<!-- Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants -->
-<!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
-<!-- TODO Email George with query on dual counting, following review of email with Julian -->
-
-As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
-This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
-Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
-This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
-
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`).
-Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Talk about problem with studies sharing underlying datasets in two sample Mendelian randomisation frameworks - c.f.
-EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, Mendelian randomisation analysis can be multiple studies using the exact same summary statistics from the same cohorts
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref()), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria of .
-
-Introduce assumptions underlying Mendelian randomisation (with image).
-Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
-Note the region must be quite wide - talk about controversy surrounding Benn paper
-
-Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
-This point is important given one of the core assumptions of
-
-<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
-
-MR are limited by the need for SNP to be present in both datasets (for TSMR).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
-
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
--->
-
-A key example of the importance of .
-In almost all cases, Mendelian randomisation studies examine.
-A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of preprints
-
-```{r preprintGrowthSetup, include=FALSE}
-```
-
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
-There were several relevant preprints captured by the search.
-The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).
-
-Three relevant preprints were identified
-
-medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
-The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
-
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
-
-While none of the preprints contributed uniquely to the review, this is again.
-Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
-The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
-This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
-However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
-
-<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
-
-<!-- Regardless, some studies were identified -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Comments on the process -->
-
-<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
-
-<!-- &nbsp; -->
-
-<!-- #### Protocol registration -->
-
-<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
-In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
--->
-
-<!-- &nbsp; -->
-
-<!-- #### Workload -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-<!-- &nbsp; -->
-
-<!-- #### People management -->
-
-<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
-However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
--->
-
-<!-- &nbsp; -->
-<!----------------------------------------------------------------------------->
-
-<!-- ### Validation against recent umbrella review -->
-
-<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
-
-<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
-
-<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
-In fields where there is a lot of existing reviews, they -->
-
-<!-- All studies identified by reviews included in te -->
-
-<!-- In hindsight, this approach ma -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important elements, and so these could not be extracted.
-This limiation was compounded by the expected low response rate to requests for further information from primary authors (although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019]).
-
-While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
-
-Based on my experience of extracting data for this review, I co-wrote an guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021]
-
-Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. <!-- TODO Cite the Zenodo repo here! -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Strengths and limitations
-
-<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
-
-#### Strengths
-
-I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition
-
--   *Structured risk-of-bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related manuscripts as a source of grey literature.
-As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
-
-<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
-they would not have been captured by the search for published papers) -->
-
-- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
-This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
-In addition this review was used to pilot an upcoming risk of bias tool
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Limitations
-
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
-
-In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
-
-One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
-
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Conclusions
-
-In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
-
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
-
-\newpage
-
-## References
-
-<!--chapter:end:03-Chp-Systematic-Review.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
-When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
-```
-(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]
-
-# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-<!-- Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-library(dplyr)
-options(scipen = 99)
-knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-```{r load-files, echo = FALSE}
-```
-
-<!-- ## Additional ideas -->
-
-<!-- TODO Need to add some information on the generation and use of propensity scores -->
-
-<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
--->
-
-<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
-
-<!-- __Things we tried__ -->
-
-<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
-Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
-Need total number of those starting and average time to start.
--->
-<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
-<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
-<!-- - Allowing for time-varying confounders for binary covariates. -->
-
-<!-- __Things we could try__ -->
-
-<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
-<!-- - Examine Cramer et al. thesis and see what they did -->
-<!-- - Marginal structural models approach (a la J. Sterne) -->
-
-<!--------------------------------------------------------------------------->
-
-<!-- TODO Check lipid-regulating vs lipid regulating -->
-
-<!-- TODO Check all fig/table cross-references evaluate -->
-
-## Lay summary
-
-Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
-Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
-These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
-This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
-
-This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
-Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
-
-Little evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
-In contrast, I found an increased risk of vascular and other (i.e.
-non-Alzheimer's) dementia with lipid regulating agent use.
-
-This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
-This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
-However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Introduction
-
-In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
-
-The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
-
-Firstly, it explicitly examines vascular dementia as an outcome.
-The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
-As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
-
-Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
-This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Methods
-
-### Study protocol
-
-An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
-
-<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
-
-<!-- TODO Add amendments to Appendix -->
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Data source {#cprd-data-source}
-
-Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
-The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
-Eu...
-- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
-Eu001 - Dementia in Alzheimer's disease with late onset).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
-Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
-
-(ref:readExample-scaption) Example of CPRD Read code hierarchy
-
-```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
-
-&nbsp;
-
-### Cohort definition
-
-This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
-However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
-
-Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
-These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-
-All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
-
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
-had less than one full day of follow-up).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Exposures
-
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
-
-A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class altered according to one of three criteria:
-
-- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
-- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
-- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Outcomes {#cprd-outcomes}
-
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
-The diagnosis date of the outcome was determined by the first record of a relevant code.
-
-<!----------------------------------------------------------------------------->
-(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
-Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
-
-(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes
-
-```{r decisionTree, include = FALSE}
-```
-
-```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
-
-&nbsp;
-
-### Covariates
-
-A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
-
-Demographic covariates adjusted for included age and gender.
-Age was calculated at date of entry into the cohort.
-Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
-To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
-Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
-
-Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
-A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
-To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
-
-Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
-The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
-
-Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
-
-<!-- IDEA Add more detail here on the missing data approach -->
-
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
-
-Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
-BMI), or where a code existed for the absence of the condition (e.g.
-categorical smoking status).
-This approach was necessary, as absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
-
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Estimation methods
-
-A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
-
-\begin{equation}
-  h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)
-  (\#eq:cox-model)
-\end{equation}
-
-where:
-
-* $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
-* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
-
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
-A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
-Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
-This is discussed in detail in the following section.
-
-<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
-
-<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}
-
-Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
-
-The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
-This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
-
-This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
-To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
-Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
-they enter the cohort and move into the exposed group on the same day).
-
-<!--------------------------------------------------------------------------->
-(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
-
-(ref:immortalTimeBias-scap) shortcap
-
-```{r, immortalTime, include = FALSE}
-```
-
-```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
-```
-<!--------------------------------------------------------------------------->
-
-### Time axis
-
-<!-- IDEA Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
-As such, the main analyses presented all used age as the time axis.
-
-<!-- TODO Will need to expand on choice of time axis here -->
-
-<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
--->
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Sensitivity analyses
-
-The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
-To assess the robustness of the results, a number of sensitivity analyses were performed.
-These are described in the following sections.
-
-#### Control outcomes
-
-In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
-The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
-Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
-
-Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
-Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-
-Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
-Muscular backpain was chosen as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
-As such, if statins are not associated with backpain in this analysis, then confidence in the results for the dementia outcomes is increased.
-
-Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
-
-<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
-
-<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->
-
-<!----------------------------------------------------------------------------->
-(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
-Note the absence of any arrow between $X$ and $N$.
-In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).
-
-(ref:negativeOutcome-scap) DAG of ideal negative outcome
-
-```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
-library(dagitty)
-library(ggdag)
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
-  dagitty::dagitty("dag {
-    U -> N
-    C -> N
-    X <- U -> Y
-    X <- C -> Y
-    X -> Y
-    bb =\"-2.368,-2.972,2.597,2.726\"
-    C [pos=\"-0.3,0\"]
-    N [pos=\"0.5,1\"]
-    U [pos=\"-0.15,1.5\"]
-    X [exposure,pos=\"0,-1\"]
-    Y [outcome,pos=\"0.5,-1\"]
-  }"
-) %>% ggdag_classic() +
-  theme_dag()
-
-,
-height = 3
-)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))
-
-```
-<!----------------------------------------------------------------------------->
-
-#### Impact of additional covariates
-
-To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
-
-&nbsp;
-
-#### Sensitivity cohorts
-
-Two sensitivity cohorts were also created.
-The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
-The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
-
-<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
-
-&nbsp;
-
-#### Statin properties
-
-<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
-
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
-
-To explore whether any observed associations in the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
-
-<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
-
-&nbsp;
-
-#### Impact of dementia code lists
-
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
-
-This previous study used a propensity matching approach to estimate the association of statins with a range of outcomes, and found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
-
-The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-## Results
-
-### Patient characteristics
-
-```{r characteristics, echo = FALSE}
-```
-
-```{r attritionFigure, include = FALSE}
-```
-
-Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
-
-(ref:cprdFlowchart-scap) Attrition of CPRD participants
-
-<!-- This figure needs to have comma seperated numbers in order to agree with text. -->
-
-```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia: Table \@ref(tab:followUp-table)).
-The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-
-\blandscape
-<!--------------------------------------------------------------------------->
-(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
-
-(ref:cprdCharacteristics-scaption) Patient characteristics by drug class
-
-```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-\elandscape
-
-A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
-Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
-
-<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
-
-<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
-
-(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
-
-```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-```{r missing-data, echo = FALSE}
-```
-
-```{r azd-text, echo = FALSE}
-```
-
-Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
-
-&nbsp;
-
-### Primary analysis
-
-Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
-
-\blandscape
-
-<!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary
-
-(ref:followUp-scaption) followUp
-
-```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-\elandscape
-
-The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
-
-For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
-
-(ref:cprdPrimary-scap) Results from primary analyses of CPRD data
-
-```{r p1Figure, include = FALSE}
-```
-
-```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_p1.png"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
-
-__Alzheimer's disease__
-
-My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
-
-&nbsp;
-
-__Non-Alzheimer's disease dementias__
-
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
-Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
-
-&nbsp;
-
-__All-cause dementia__
-
-For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
-There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
-
-&nbsp;
-
-### Sensitivity analyses
-
-The results of the series of sensitivity analyses performed are described in the following sections.
-
-#### Complete case versus imputed data
-
-In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
-It should be noted that due to the large amount of missing data (e.g.
-`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
-In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
-
-(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
-
-```{r completeCase, include= FALSE}
-```
-
-```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_complete_case.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Control outcomes
-
-```{r controlOutcomesText, echo = FALSE, message = FALSE}
-```
-
-```{r controlOutcomes, echo = FALSE, message = FALSE}
-```
-
-Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
-The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
-
-For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
-However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:controlOutcomeFig-cap) Results of control outcome analysis.
-
-(ref:controlOutcomeFig-scap) Results of control outcome analysis
-
-```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_control_outcomes.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Impact of additional covariates
-
-The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
-
-These models were used to estimate the impact of adjustment for additional covariates.
-Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
-
-Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
-In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
-
-(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
-
-```{r unadjustedComparison, include=FALSE}
-```
-
-```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_unadjusted.png"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity cohorts: Entry year
-
-When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).
-
-&nbsp;
-
-```{r cohortEntry, include=FALSE}
-```
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
-
-(ref:diagnosisTypeFig-scap) Sensitivty analus
-
-```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/forester_cohort_entry.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
-While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
-
-(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
-
-```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Sensitivity cohorts: Pregnancy
-
-In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
-
-(ref:pregnancyFig-scap) Comparison of pregnancy analysis
-
-```{r pregnancy, include = FALSE}
-```
-
-```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_pregnancy.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Statin properties
-
-In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
-Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
-
-(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
-
-```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
-Additionally, in the AD outcomes, hydrophilic statins were associated with a small reduction in risk, compared to the weak evidence for an effect for lipophilic statins.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
-
-(ref:statinTypeFig-scap) Analysis stratified by statin properties
-
-```{r statinType, include = FALSE}
-
-```
-
-```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_sta_type.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Comparing codelists {#comparing-codelists}
-
-```{r smeethText, include = FALSE}
-```
-
-When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
-
-However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
-Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
-The joining lines showing the overlap between the categories in the two analyses.
-
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-```{r sankeydiagram, include=FALSE}
-```
-
-```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
-```
-<!----------------------------------------------------------------------------->
-
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
-
-&nbsp;
-
-<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
-
-<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
-
-## Discussion
-
-<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
-
-### Summary of findings
-
-Lipid-regulating agents showed little evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
-
-The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
-When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
-
-<!-- QUESTION Why are fibrates different? -->
-
-<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->
-
-<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
-
-<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
-However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Interpretation of results
-
-<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
-
-This section will expand on a potential explanation for the observed results detailed above.
-However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
-
-A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
-While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
-
-<!----------------------------------------------------------------------------->
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
-
-(ref:indicationBias-scap) Confounding by indication causal diagram
-
-```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
-dagitty::dagitty("dag {
-  Statin [exposure,pos=\"0.000,0.000\"]
-  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
-  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
-  \"Uncontrolled variable\" -> Statin
-  \"Uncontrolled variable\" -> \"Vascular outcomes\"
-}") %>% ggdag_classic(size = 6) +
-  xlim(-0.5,3) +
-  geom_text(data = data.frame(x = 0.316392393234329,
-                              y = 0.537705383514239,
-                              label = "Prompts"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 1.65891420807966,
-                              y = 0.537705383514239,
-                              label = "Causes"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_curve(data = data.frame(x = 0.220612676359188,
-                               y = -0.000788829298738025,
-                               xend = 1.45,
-                               yend = -0.00157828084913909),
-             mapping = aes(x = x,
-                           y = y,
-                           xend = xend,
-                           yend = yend),
-             linetype = "dashed",
-             angle = 0L,
-             size = 0.6,
-             colour = "black",
-             curvature = 0,
-             arrow = structure(list(angle = 0,
-                                    length = structure(0,
-                                                       class = "unit",
-                                                       valid.unit = 2L,
-                                                       unit = "inches"),
-                                    ends = 2L,
-                                    type = 2L),
-                               class = "arrow"),
-             inherit.aes = FALSE,
-             show.legend = FALSE) +
-
-  theme_dag(),
-width = 8,
-height = 3)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
-```
-<!----------------------------------------------------------------------------->
-
-In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
-
-Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
-The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
-This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
-
-A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
-
-Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-I also adjusted for several additional potential baseline variables.
-However, important confounding variables for which I have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
-
-On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
-It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
-
-<!-- IDEA talk about time-varying confounding here -->
-
-In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Strengths and limitations
-
-The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
-Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
-Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
-This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
-
-However, the findings of this analysis are subject to several limitations.
-There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
-As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
-
-Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
-This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
-
-<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
-
-<!-- IDEA there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
--->
-
-<!--------------------------------------------------------------------------->
-
-<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
-
-<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
-
-<!-- However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
--->
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
--->
-
-<!-- This hasn't been done! Plus I do not think this is the case -->
-
-<!--------------------------------------------------------------------------->
-
-<!--------------------------------------------------------------------------->
-<!-- &nbsp; -->
-
-<!-- IDEA Issues with large-scale EHR databases -->
-
-<!-- __Missclassification__ -->
-
-<!-- __Coding quality in the CPRD__ -->
-
-<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
-
-<!-- There is the possibility of ascertainment bias -  -->
-
-<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Enabling easy synthesis of this analysis {#cprd-data-avail}
-
-In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
-
-All code, Read codelists and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
-<!-- TODO Archive on Zenodo.
--->
-
-The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
-
-Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
-
-This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Conclusions
-
-This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
-
-It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
-However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
-
-This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
-Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
-
-Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
-
-\newpage
-
-## References
-
-<!--chapter:end:04-Chp-CPRD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Individual participant data meta-analysis {#ipd-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/05-Code-IPD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-## Lay Summary
-
-As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Introduction
-
-Is there a good way to visualise input of cohorts into an IPD analysis?
-
-Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Methods
-
-### Applying for data access
-
-__Systematic review__
-
-As part
-
-As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
-In the first instance, the corresponding author on the main man
-
-__Dementia platform UK__
-
-In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
-
-Talk about how different covariates were managed across cohorts,
-
-### Eligibility criteria
-
-Lipids reported/available as a continuous measure, and were not cross-sectional.
-
-Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
-
-<!-- TODO Read this[@riley2020] -->
-
-### Missing data
-
-Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-There is some concerns about performing risk of bias assessments on your own analysis, and so
-
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Analysis
-
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
-<!-- TODO Figure showing the outline of interval censored studies. -->
-
-All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
-
-Similary,
-
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Stratified by age-at-entry and sex, and ethnicity where possible.
-
-Hazard ratios were utilised to
-
-In order to investigate the interaction of sex with
-
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
-
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
-
-In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
-These were extracted and synthesised using a random effects meta-analysis.
-
-Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.
-
-The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]
-
-__Replicating published findings__
-
-Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-## Results
-
-### Data access
-
-<!-- Need exact number from each approach, plus detailed exclusion reasons -->
-
-Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
-Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
-
-In addition, the reasons for cohorts not being included in the analysis are presented.
-In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
-
-For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th
-
-<!----------------------------------------------------------------------------->
-```{r cohortFlowchartSetup, include = FALSE}
-```
-
-(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
-
-(ref:cohortFlowchart-scap) Flowchart
-
-```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
-knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.
-
-I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
-
-As highlighted in the
-
-### Included data sources
-
-The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
-
-Of note, all data sources included in the analysis were based in the United Kingdom.
-This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:cohortOverview-caption) Summary of cohorts for which data were available
-
-(ref:cohortOverview-scaption) Summary of included cohorts
-
-```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->
-
-<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Caerphilly Prospective Study
-
-The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
-
-Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
-As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### CPRD
-
-The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
-
-Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
-
-Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
-
-the
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Epic Norfolk
-
-The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]
-
-Has only 8 events
-
-```{r tests, }
-
-```
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Whitehall II
-
-_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
-Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
-
-This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]
-
-This gave
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Cohorts provided data but ultimately excluded
-
-As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
-
-Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
-
-The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
-
-__BRACE__
-
-Likley had dementia at baseline
-
-__Memento__
-
-Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
-
-__Generation Scotland__
-
-Cross-sectional data only
-
-__NICOLA__
-
-NICOLA study - only had cross-sectional data
-
-__ELSA__
-
-Data provided but only had ever high cholesterol as a binary variable. Not compatible with
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:dataExcluded-caption) dataExcluded
-
-(ref:dataExcluded-scaption) dataExcluded
-
-```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Cohorts identified the systematic review but excluded from the IPD analysis
-
-<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
-
-Electronic health record co
-
-LBC - 1936
-
-Taiwan etc,
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Cohorts approach but received no answer
-
-A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
-Despite multiple attempts to contact the team, there was no response received.
-
-<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Data cleaning and harmonisation
-
-Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
-
-The one exception to this is the CPRD data, which was held in a different system to the rest.
-
-The advantage of this approach is that it reduces the liklihood of errors in model mis-speciication if needing to change variables names from cohort to cohort.
-
-For all cohorts, the first lipid measurement was used for the exposure method,
-
-For heterogeneity across the cohorts, the total time-at-risk was investigated.
-
-<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion
-
-Useful citation for discussion[@levis2021]
-
-### Limitations
-
-#### Low response rate to request for data
-
-<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
-
-This review had a low response rate to requests for data access.
-
-While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
-test
-There are likely several reasons for this.
-
-* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
-
-* While there is no
-
-For many other reasons also - if
-
-A potential further reason was highlighted during my attendance at the
-
-Letters sent to all cohorts identified through the systematic review 
-<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
-
-This is likely due to my junior position as a early career research combined with the impact
-
-Range of reasons why data is not readily available.
-Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
-primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
-
-Unfortunately,
-
-The low response rate and the
-
-Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
-
-<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
-The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
-Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
-However, analysis combining individual and study level data may mitigate these effects [3, 21].
-from [@ventresca2020a] -->
-
-For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
-
-On a personal level, given the
-
-In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Resources
-
-While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
-
-Given the resource intensity of data cleaning and harmonisation,
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Data access
-
-Couple of sections
-
-* Problems with getting data from studies
-*
-
-Sharing data has several legal, ethical and logistical challenges, and can often
-
-This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
-
-Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
-
-Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
-
-Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Study within a review
-
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
-
-Options could include
-
-Previous SWARs have been registered as protocols, but have not yet reported!
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Reflections on the process
-
-May have been overly ambitious
-
-\newpage
-
-## References
-
-<!--chapter:end:05-Chp-IPD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
-
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
@@
 
+While the triangulation framework provides for inclusion of multiple distinct types of evidence, based on the scoping search, it is likely that the three main sources will be RCTs of statins, multivariable regression of prospective cohorts, and the use of genetic instruments in observational data (Mendelian Randomisation studies).
+One important difference between these approaches that will need to be addressed in the triangulation
+is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
+The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course.
+
 <!----------------------------------------------------------------------------->
@@
 
-<!----------------------------------------------------------------------------->
-
-## Results
-
-Summary of risk-of-bias/triangulation results
-
-Percentage of domains for which a direction of bias could be assigned?
-
-Compare bias-adjusted and
-
-See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
-
-Applicability/indirectness as an issue 
-Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
-
-### Challenges of real-life data
-
-Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-ALso highlight the issue with assigning a direct of bias in many studies
-
-### Need for new methods
-
-Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
-
-<!--chapter:end:06-Chp-Triangulation.Rmd-->
-
----
-output:
-  bookdown::word_document2: 
-      reference_docx: templates/word-styles-reference-01.docx   
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Discussion {#discussion-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-<!----------------------------------------------------------------------------->
 ## Triangulation across exisiting evidence and evidence produced in this thesis
@@
 <!----------------------------------------------------------------------------->
-&nbsp;
 
-## Additional topics for the discussion
+## Results
 
-There are several addition topics I would like to cover:
+Summary of risk-of-bias/triangulation results
 
-* The difference between the peer review of the software vs.
-the peer review of papers.
-A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
-Essentially, a more transparent and open
+Percentage of domains for which a direction of bias could be assigned?
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+Compare bias-adjusted and
 
-## Summary of findings (and implications for policy makers)
+See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
 
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Strengths and Limitations
-
-There are several strengths and limitations to the work presented in this thesis.
-One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
-
-Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Reproducible research
-
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
-In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
-
-Containerisation was used to ensure that the code is reproducible, in line iwht best practices
-
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
-
-One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
-However, access is dependency on an ISAC application to the managing body of the CPRD.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Public involvement and engagement {#disc-PPI}
-
-Involving and engaging the public and patients has been a central theme to this thesis.
-
-Public engagement activities included
-
-Public involvement also steered the creation of the topic
-
-P
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Future work
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Overall conclusions
-
-<!--chapter:end:07-Discussion.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!--chapter:end:tmp.Rmd-->
-
-`r if(!knitr:::is_latex_output()) '# Bibliography {-}'`
-
-<!-- If you're outputting to LaTeX, the heading and references will be generated by the OxThesis LaTeX template.
-This .Rmd file serves only to add the References headline to gitbook output before the references are added by pandoc -->
-
-```{block type='savequote', include=knitr::is_latex_output(), echo = TRUE}
-Lasciate ogne speranza, voi ch'intrate. . .
-```
-
-# Bibliography
-
-<div id="refs"></div>
-
-<!--chapter:end:front-and-back-matter/98-references.Rmd-->
-
-`r if(knitr:::is_latex_output()) '\\startappendices'`
-
-`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
-
-<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-knitr::read_chunk(here::here("R/appendix.R"))
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!----------------------------------------------------------------------------->
-# By Chapter {#chapter-appendix-heading}
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(background-heading) {#appendix-into}
-
-<!----------------------------------------------------------------------------->
-### Publications beyond the scope of this thesis {#appendix-publications}
-
-__Peer reviewed__
-
-  * PRISMA main paper
-
-  * PRISMA E&E
-
-  * PRISMA 2020 software
-
-  * COVID Suicide Living Review
-
-  * Data extraction tools systematic review
-
-<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->
-
-__Under review/Preprints__
-
-  * MSc Paper on systematic reviews of this thesis topic
-
-  *
+Applicability/indirectness as an issue 
+Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
 
@@
 
-### Involvement of patients and the public {#appendix-ppi}
+## Discussion
 
-Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
 
-Additionally,
+### Challenges of real-life data
 
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
+Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
+ALso highlight the issue with assigning a direct of bias in many studies
 
-<!----------------------------------------------------------------------------->
+### Need for new methods
 
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
-<!----------------------------------------------------------------------------->
-
-### Code for publication rate analysis
-
-```{r, eval=FALSE}
-med_res <-
-  # Use snapshot of published status from July 2021
-  medrxivr::mx_search(
-    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
-    query = "*",
-    from_date = "2019-07-01",
-    to_date = "2019-08-01"
-  ) %>%
-  # Create indicator to show which records have been published
-  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
-  # Group by indicator variable and count
-  group_by(pub_ind) %>%
-  count()
-
-```
-
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
-<!----------------------------------------------------------------------------->
-
-### Search strategy {#appendix-search-strategy}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchHits-caption) Overview of the full Medline search strategy.
-
-(ref:searchHits-scaption) searchHits
-
-```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
-```
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Web of Science Databases Searched {#appendix-wos-databases}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:wosDatabases-caption) Summary of Web of Science databases searched.
-
-(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
-
-```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
-
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-### Code to search preprints {#appendix-medrxivr-code}
-
-<!-- TODO Double check this is the final code used -->
-
-```{r, eval = FALSE}
-
-library(medrxivr)
-
-mx_data <- mx_api_content(to_date = "2019-09-01")
-
-bx_data <- mx_api_content(server = "biorxiv",
-                                    to_date = "2019-09-01")
-
-topic1 <- c(mx_caps("statin"),
-            mx_caps("ldl"),
-            mx_caps("hdl"),
-            mx_caps("TG"),
-            mx_caps("triglycer"),
-            paste0("\\b",mx_caps("TC"),"\\b"),
-            mx_caps("ezetim"),
-            mx_caps("fibrate"),
-            mx_caps("bile acid"),
-            mx_caps("lipoprotein"),
-            mx_caps("lipid"),
-            mx_caps("cholesterol"))
-
-topic2 <- c(mx_caps("dementia"),
-            mx_caps("alzheim"),
-            mx_caps("MCI"),
-            mx_caps("mild cognitive"))
-
-query <- list(
-  topic1,
-  topic2
-)
-
-bx_results <- mx_search(bx_data, query)
-
-mx_results <- mx_search(mx_data, query)
-
-```
-
-Note
-
-<!----------------------------------------------------------------------------->
-### MR risk of bias tool {#appendix-mr-rob}
-
-<!----------------------------------------------------------------------------->
-(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
-
-(ref:mrTool-scaption) Mendelian randomisation risk-of-bias assessment tool
-
-```{r mrTool-table, message=FALSE, results="asis", echo = FALSE}
-
-mrTool_table <- read.csv(here::here("data/sys-rev/mrRobTool.csv")) %>%
-  select(1:5) %>%
-  rename("Bias domain" = Bias.domain)
-
-if(doc_type == "docx") {
-  knitr::kable(mrTool_table, caption = "(ref:mrTool-caption)")
-} else{
-  knitr::kable(
-    mrTool_table,
-    format = "latex",
-    caption = "(ref:mrTool-caption)",
-    caption.short = "(ref:mrTool-scaption)",
-    longtable = TRUE,
-    booktabs = TRUE
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    column_spec(column = 1:5, width = paste0(32/5,"em")) %>%
-    row_spec(2:nrow(mrTool_table)-1, hline_after = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position","repeat_header"))
-}
-
-```
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-<!----------------------------------------------------------------------------->
-### Amendments to protocol {#appendix-cprd-amendments}
-
-<!----------------------------------------------------------------------------->
-### Code lists
-
-## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
-<!----------------------------------------------------------------------------->
-### Section 1
-
-<!----------------------------------------------------------------------------->
-### Section 2
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(discussion-heading)
-
-<!----------------------------------------------------------------------------->
-### Catalogue of failures
-
-Short section detailing the things I tried to do but which did not work.
-
-<!----------------------------------------------------------------------------->
-# Other Appendix {#other-appendix-heading}
-
-## Software used to create this thesis
-
-```{r, include = FALSE}
-knitr::write_bib(c(.packages(), "bookdown", "knitr"), here::here("bibliography/packages.bib"))
-```
-
-This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
-All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
-
-<!----------------------------------------------------------------------------->
-## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
-
-### Introduction
-
-Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
-A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
-
-Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
-Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
-Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
-For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.
-
-Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
-Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
-
-The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).
-
-### Development
-
-Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
-Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback.
-This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
-The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]
-
-### Installation
-
-A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:
-
-```{r, eval = FALSE}
-install.packages("robvis")
-```
-
-As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version.
-The most recent development version can be install from GitHub using:
-
-```{r, eval = FALSE}
-devtools::install_github("mcguinlu/robvis")
-```
-
-### Usage
-
-`robvis` contains two main functions.
-The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
-The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.
-
-A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
-A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)
-
-Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
-
-<!-- TODO __NEED TO ADD DATA HERE!__ -->
-
-```{r, eval = FALSE}
-
-rob_traffic_light(data = data_rob2,
-                  tool = "ROB2",
-                  psize = 15)
-```
-
-```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
-
-plotdata <- robvis::data_rob2
-
-tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)
-
-robvis::rob_save(tfplot, 
-                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
-```
-
-Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
-
-```{r, eval = FALSE}
-
-rob_summary(data = data_rob2,
-            tool = "ROB2", 
-            overall = TRUE)
-
-```
-
-```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
-
-sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)
-
-robvis::rob_save(sumplot,
-                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-```
-
-A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)
-
-`r br`
-
-```{r robvisarguments, echo = FALSE, eval = TRUE}
-
-arguments <- data.frame(stringsAsFactors=FALSE,
-              argument = c("data", "tool", "colour", "overall", "weighted",
-                           "psize"),
-     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
-           rob_summary = c("X", "X", "X", "X", "X", ""),
-           Description = c(
-"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
-"Defines the risk of bias assessment tool used.
-The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
-Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
-"Defines the colour scheme for the plot.
-The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`).
-Alternatively, users can specify their own colour scheme e.g.
-`colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
-"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
-"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
-"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
-
-if(doc.type == "docx"){
-
-  knitr::kable(arguments,escape = T,
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))
-
-}else{
-
-  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-             align = c("l","c","c","l"),
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
-  column_spec(4,"5cm") %>%
-  kable_styling(font_size = 9, 
-                bootstrap_options = c("striped", "hover"),
-                latex_options = c("repeat_header", "striped"))
-}
-
-```
-
-`r br`
-
-### Reception and Future Plans
-
-```{r, echo = FALSE}
-robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
-
-robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-
-```
-
-As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times.
-It has been well received but the systematic review community, and has been cited frequently in the published literature.
-A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods.
-A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]
-
-While `robvis` is a stable package, a range of additional functionality could be added.
-At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
-However, following user-driven demand, this functionality is in development and will be available in the near future.
-Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
-The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
-
-## Creating
-
-## Copies of papers arising from this thesis {#published-papers}
-
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
-
-<!--chapter:end:front-and-back-matter/99-appendices.Rmd-->
+Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?

### 2021-10-08 08-Discussion.Rmd
Creat final thesis structure

--- 2021-09-28 _main.Rmd
@@
----
-#####################
-## thesis metadata ##
-#####################
-title: |
-   Lipids and dementia:\
-   An investigation of their relationship
-
-author: Luke A McGuinness
-college: 
-degree: Doctor of Philosophy
-degreedate: 2022
-word-count: |
-  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
-abstract: |
-  `r paste(readLines("front-and-back-matter/_abstract.Rmd"), collapse = '\n  ')`
-acknowledgements: |
-  `r paste(readLines("front-and-back-matter/_acknowledgements.md"), collapse = '\n  ')`
-declaration: |
-  `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
-dedication: For Brendan McHugh
-covidStatment: |
-  `r paste(readLines("front-and-back-matter/_covidStatment.Rmd"), collapse = '\n  ')`
-abbreviations: "front-and-back-matter/abbreviations" # path to .tex file with abbreviations
-
-#######################
-## bibliography path ##
-#######################
-bibliography: [bibliography/references.bib, bibliography/packages.bib]
-csl: bibliography/nature.csl
-bibliography-heading-in-pdf: Bibliography
-
-#####################
-## PDF formatting  ##
-#####################
-abstractseparate: true  # include front page w/ abstract for examination schools?
-bib-humanities: false   #set to true if you want in-text references formatted as author-year
-doi-in-bibliography: true #set to true if you want DOI's to be shown in the bibliography
-draft: false # add as DRAFT mark in the footer?
-page-layout: twoside #'nobind' for PDF output (equal margins), 'twoside' for two-sided binding (mirror margins and blank pages), leave blank for one-sided binding (left margin > right margin)
-hidelinks: true #if false, the PDF output highlights clickable links with a colored border - you will probably want to set this to true for PDF version you wish to physically print
-toc-depth: 2 # depth of heading to include in table of contents
-lof: true # list of figures in front matter?
-lot: true # list of tables in front matter?
-mini-toc: true  # mini-table of contents at start of each chapter? (this just prepares it; you must also add \minitoc after the chapter titles)
-mini-toc-depth: 1
-mini-lot: false  # mini-list of tables by start of each chapter?
-mini-lof: false  # mini-list of figures by start of each chapter?
-
-params:
-  corrections: true # set false to stop applying blue background to blocks of corrections
-
-#####################
-## output options  ##
-#####################
-output:
-  bookdown::pdf_book:
-    template: templates/template.tex
-    keep_tex: true
-    citation_package: default 
-    pandoc_args: ["--lua-filter=scripts_and_filters/correction_filter.lua", "--csl","bibliography/nature.csl"] #remove filter to stop applying blue background to inline corrections
-  bookdown::gitbook:
-    css: templates/style.css
-    download: ["pdf"]
-    output_dir: "docs"
-    split_bib: false
-    config:
-      toc:
-        before: |
-          <li><a href="./">Thesis - Draft</a></li>
-        after: |
-          <li><a href="https://github.com/mcguinlu/thesis" target="blank">Associated repository</a></li>
-      sharing:
-        facebook: false
-        twitter: yes
-        all: false
-  bookdown::word_document2:
-    output_dir: "docs"
-    toc: true
-    toc_depth: 2
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false   
-link-citations: true
-documentclass: book
-
----
-
-```{r create_chunk_options, include=FALSE, eval=knitr::is_latex_output()}
-source('scripts_and_filters/create_chunk_options.R')
-source("R/helper.R")
-options(scipen=999)
-```
-
-<!--
-Include the create_chunk_options chunk above at the top of your index.Rmd file
-This will include code to create additional chunk options (e.g. for adding author references to savequotes)
-If you need to create your own additional chunk options, edit the file R/create_chunk_options.R
--->
-
-```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
-```
-
-<!--chapter:end:index.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-  bookdown::word_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Introduction {#intro-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-## Additional ideas
-
-### General
-
-* Explore difference/similarities between the published and unpublished literature, potentially formally, using funnel plots and also by following up preprints to see if they are eventually published.
-Limit to the date we ran the original search and see if any study included in the study had not been published by the time the review was finished.
-
-* Compare and contrast the codes used to find the AzD cases in the previous study and in this study, potentially with a view to contrasting misclassification between the two.
-
-*
-
-### Background
-
-### medrxivr
-
-###
-
-&nbsp;
-
-<!--chapter:end:00-Chp-Introduction.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2:
-    reference_docx: templates/word-styles-reference-01.docx
-    number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
-Science knows it doesn't know everything; otherwise, it'd stop.
-```
-
-(ref:dara-quote) --- Dara O'Briain
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/01-Code-Background.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-# Background, Theoretical framework, Aims & Objectives {#background-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-## Lay summary
-
-[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]
-
-Around 850,000 people in the UK live with dementia, and by 2040, nearly twice as many will have the condition.
-Despite many promising candidates, no cure for dementia currently exists, meaning the focus is on finding ways to prevent the condition.
-The best way to do this is to find risk factors (characteristics that influence a person's chance of developing a disease) for dementia that we can easily change.
-Avoiding a risk factor does not guarantee that a person will not develop dementia but makes it less likely.
-A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
-The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
-
-This introductory chapter provides background information on both dementia and blood lipids, and on the potential link between them.
-It introduces the theory used to frame the research presented here, and then maps the formal aims and objectives of the research project to the relevant chapters of this thesis.
-Finally, it summarises the outputs (journal articles, presentations and software) that were created as part of this thesis.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction
-
-This chapter provides an overview of the broad context of this thesis, introducing the core concepts used throughout and providing some background on each.
-It briefly discusses the underlying pathologies and diagnosis of dementia, its public health importance, and the current state of treatment and prevention research.
-It then provides background on blood lipids and lipid-modifying treatments, and summarises the types of evidence used to examine the effect of these exposures on dementia outcomes.
-
-The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
-Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
-
-<!----------------------------------------------------------------------------->
-
-## Dementia
-
-<!----------------------------------------------------------------------------->
-
-### Definition and underlying pathologies {#underlying-pathologies}
-
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
-
-Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.
-Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
-Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
-
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
-
-The remaining 10-30% of cases are caused by other dementia subtypes (e.g.
-Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).[@burns2009]
-
-<!----------------------------------------------------------------------------->
-
-### Diagnostic criteria {#diagnostic-criteria}
-
-Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]
-
-(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.
-
-```{r diagnosticCriteria-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
-
-Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
-The distinction between these memory scales and diagnostic criteria presented above should be noted.
-For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
-Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
-
-Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
-Cause-specific criteria exist for the diagnosis of dementia sub-types.
-For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
-
-<!-- ### Differing risk by sex -->
-
-<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->
-
-<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
-
-<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->
-
-<!----------------------------------------------------------------------------->
-
-### Public health importance
-
-Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only one without a proven cure.
-
-Dementia also has a substantial economic impact.
-In 2015, the estimated total cost of dementia in England was £24.2 billion.
-Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]
-
-As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.
-
-<!----------------------------------------------------------------------------->
-
-### Treatments {#intro-treatments}
-
-Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020].
-At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.
-
-The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
-Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]
-
-### Risk factors
-
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
-
-The benefits of a prevention-based approach based on addressing these risk factors are well-studied.
-Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
-
-In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
-
-This thesis will focus on blood lipids as the primary risk factor of interest.
-The next section provides an overview of blood lipid fractions and therapeutic interventions that modify them, while Section \@ref(evidence-association) provides an overview of the existing evidence for an association between lipids and dementia outcomes.
-
-<!----------------------------------------------------------------------------->
-
-## Serum lipids
-
-<!----------------------------------------------------------------------------->
-
-### Lipid fractions {#intro-lipid-fractions}
-
-The blood lipid profile contains a range of component parts, or fractions.
-However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
-
-Triglycerides are the simplest and most common type of lipids found across the body.
-They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
-Low-density-lipoprotein cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
-In contrast, High density-lipoprotein cholesterol (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
-
-In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood.
-The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
-
-\begin{equation}
-  TC \approx LDLc + HDLc + kTG
-  (\#eq:total-cholesterol-formula)
-\end{equation}
-
-where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
-
-Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
-
-(ref:lipidLevels-scaption) Classification of blood lipid levels
-
-```{r lipidLevels-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
-These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.
-
-<!----------------------------------------------------------------------------->
-
-### Statins {#intro-statins}
-
-Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMG-CoA-R).
-This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.
-
-(ref:statin-mechanisam-scap) Statin mechanism of action
-
-```{r statin-mechanisam, echo = FALSE, results="asis",fig.pos = "H", fig.align = 'center', fig.cap='(ref:statin-mechanisam-cap)', out.width='50%', fig.scap='(ref:statin-mechanisam-scap)'}
-knitr::include_graphics(file.path("figures/background/statinPath.png"))
-```
-
-&nbsp;
-
-Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)).
-Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g.
-ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-<!-- TODO Review the look and feel of this table -->
-
-(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.
-
-(ref:statinOverview-scaption) Overview of common statins
-
-```{r statinOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Other lipid regulating agents (LRA)
-
-There are several other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
-However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
-
-<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->
-
-The most commonly used non-statin therapeutic is ezetimibe,[@kosoglou2005] which prevents intestinal absorption of cholesterol.
-However, when used alone, it has a limited LDL-c lowering effect, leading to the creation of combined statin/ezetimibe therapies (both compounds contained in a single pill, as opposed to complimentary treatments).[@genest2006]
-
-Fibrates provide a second example of non-statin therapy.
-They are used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
-They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
-
-Finally, PCSK9 inhibitors (or PCSK9i) are a relatively new treatment with strong lipid lowering effects, lauded as a potential alternative to statins.[@chaudhary2017] Their mechanism of action is to bind to and inhibit PCSK9, which breaks down LDL-c receptors on the surface of the liver, thus allowing more LDL-c to be internalised and broken down.
-
-Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.
-
-```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Evidence for the association between blood lipids and dementia {#evidence-association}
-
-This section provides an overview of the varying sources of evidence on the relationship between blood lipid levels and dementia risk.
-
-<!----------------------------------------------------------------------------->
-### Basic science
-
-A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
-Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]
-
-Despite these results, evidence from the diverse range of epidemiological studies on this topic has been inconclusive.
-
-<!----------------------------------------------------------------------------->
-### Observational studies
-
-By far the largest source of evidence on the relationship between comes from observational designs.
-Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a].
-With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]
-
-Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020c] on dementia outcomes have been performed.
-However, these reviews have several limitations.
-Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey2015;@poly2020c]
-
-<!----------------------------------------------------------------------------->
-
-### Randomised controlled trials
-
-In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.
-
-While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
-One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
-
-Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
-As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
-
-Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
-Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]
-
-<!----------------------------------------------------------------------------->
-
-### Mendelian randomisation
-
-Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
-
-1. the IV is associated with the exposure of interest (the relevance assumption);
-2. the IV and outcome do not share a common cause (the independence assumption); and
-3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).
-
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]
-
-Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-In summary, multiple sources of evidence exist on the relationship between statins and dementia.
-In the next section, I introduce the synthesis of diverse sources of evidence as the theoretical framework used in this thesis.
-
-<!----------------------------------------------------------------------------->
-
-## Theoretical framework: Evidence synthesis
-
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
-
-The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
-
-This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes. 
-Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:
-
-* Inclusion of preprints
-* Triangulation across evidence sources
-* Individual patient data meta-analysis
-
-These three elements are expanded on below and are used to frame the research presented in the subsequent Chapters.
-
-<!----------------------------------------------------------------------------->
-
-### Inclusion of preprints  {#diverse-sources-preprints}
-
-<!-- TODO Incorporate Julian's comments below -->
-
-<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
-Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
-It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
-Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
-We have no clear and widely used definition of grey literature.
--->
-
-The importance of including grey (or gray) literature in systematic reviews is widely acknowledged.
-Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]
-
-A important developing source of grey literature are preprints.
-Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
-
-One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
-Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
-
-In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic.
-However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
-
-<!----------------------------------------------------------------------------->
-### Triangulating across study designs {#intro-triangulation}
-
-As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
-
-This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.
-
-All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading).
-Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
-
-Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Individual patient data meta-analysis
-
-Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]
-
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
-
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
-
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
-Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
-
-In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop.
-The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.
-
-I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
-<!----------------------------------------------------------------------------->
-
-## Thesis overview
-
-### Aims and objectives
-
-The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes
-
-The specific research objectives that this thesis seeks to address are:
-
-* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
-* To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
-* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
-* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
-
-### Structure {#thesis-structure}
-
-Chapters are self-contained, presenting the methods and results of that specific research project.
-They are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
-
--   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
--   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
--   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis.
-The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.
-
-An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)
-
-\blandscape
-<!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading).
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
-
-(ref:thesisOverview-scaption) Summary of studies included in this thesis
-
-```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape
-
-## Outputs from this thesis {#thesis-output}
-
-The outputs of this thesis are detailed below, and include peer-reviewed papers, presentations, and open-source evidence synthesis tools.
-
-### Contributions to the scientific literature
-
-During the course of this thesis, I have made several contributions to the scientific literature. Those arising from or directly related to the contents of this submission are presented below.
-
-<!-- TODO Ideally the two preprints for the CPRD and systematic review papers will go here -->
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and L Schmidt.
-(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R.
-Journal of Open Source Software 5.54 2651.
-DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
-
-A paper introducing the open-source preprint search tool described in Chapter \@ref(sys-rev-tools-heading).
-As is common for journal articles describing software, the paper is intentionally short providing only a broad overview of the tool while extensive documentation is available from the project website (see Section \@ref(sys-rev-tools-intro) for more details).
-
-&nbsp;
-
-_Hennessy, E.
-A., Acabchuk, R., Arnold, P.
-A., Dunn, A.
-G., Foo, Y.
-Z., Johnson, B.
-T., Geange, S.
-R., Haddaway, N.
-R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
-Welch, V.,  **McGuinness L.
-A.** (2021).
-Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
-Prevention Science .
-DOI: [10.1007/s11121-021-01279-8](https://doi.org/10.1007/s11121-021-01279-8)_
-
-The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers.
-This piece was co-written with Dr.
-Emily Hennessy (see Author Declarations in the front materials).
-<!-- TODO Need to create author declarations section -->
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Higgins J.
-P.
-T.
-(2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method).
-DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
-
-The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
-See Appendix \@ref(appendix-robvis) for more details on this tool.
-
-&nbsp;
-
-_**McGuinness, L.
-A.**, and Sheppard A.
-L.
-2020.
-“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887.
-DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_
-
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
-
-&nbsp;
-
-For information on additional contributions to the scientific literature not directly related to this thesis, see Appendix \@ref(appendix-publications).
-
-&nbsp;
-
-### Presentations/Talks
-
-<!--- Include links here for slides for each talk/poster --->
-
-_"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Poster presentation, Alzheimer's Association International Conference 2021.
-&nbsp;
-
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
-
-&nbsp;
-
-_"On the shoulders of giants": advantages and challenges to building on established evidence synthesis packages, using the {robvis} package as a case study"_: Oral presentation, Evidence Synthesis and Meta-Analysis in R Conference (ESMARConf) 2021.
-
-&nbsp;
-
-_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
-
-### Software {#outputs-software}
-**`medrxvir`**
-
-An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
-See Chapter \@ref(sys-rev-tools-heading) for more details.
-Install a stable version of the package from the Comprehensive R Archive Network (CRAN), or alternatively install the development version from GitHub, using:
-
-```{r, eval = FALSE}
-# CRAN version
-install.packages("medrxivr")
-
-# Development version
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-**`robvis`**
-
-An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
-See Appendix \@ref(appendix-robvis) for more details.
-Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:
-
-``` {r, eval = FALSE}
-# CRAN version
-install.packages("robvis")
-
-# Development version
-devtools::install_github("mcguinlu/robvis")
-```
-
-&nbsp;
-
-## Summary
-
-This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.
-
-\newpage
-
-## References
-
-<!--chapter:end:01-Chp-Background.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
-Why are open source statistical programming  
-languages the best?
-
-Because they R.
-```
-
-(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
-
-# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r setup, include=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-library(medrxivr)
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO I might need to make it clearer thatthe tool was always intended to search both databases, as medRxiv grew out of bioRxiv categories, and no relevant records identified by the search in medRxiv -->
-
-## Lay summary
-
-Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal.
-They represent an important source of scientific literature.
-A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way.
-Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
-
-<!----------------------------------------------------------------------------->
-
-## Introduction {#sys-rev-tools-intro}
-
-Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)).
-As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
-The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which launched in 2019 and was designed to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv.[@rawlinson2019]
-
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
-As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
-
-This chapter outlines the development and key functionality of `medrxivr` (version 0.0.5), a tool I created to facilitate the systematic searching of medRxiv and bioRxiv preprints.
-The factors that necessitated the development of this tool in the context of this thesis are outlined, and the use of `medrxivr` in my own projects and by other researchers is discussed.
-As the majority of work on this aspect of my thesis is represented by lines of code or online documentation (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr) and [https://docs.ropensci.org/medrxivr/](https://docs.ropensci.org/medrxivr/) respectively), this chapter is an intentionally short, high-level summary of my work on this project.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.[@zotero-15029]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-<!-- IDEA Could remake this using Diagrammr? -->
-
-(ref:medrxivr-sr-cap) **Role of `medrxivr` in a systematic review workflow** - `medrxivr` allows for systematic searching of biomedical preprints as part of the initial literature searching.
-Following title and abstract screening, reviewers can then programmatically retrieve a copy of the PDF of included records to facilitate the full-text screening stage (similar to Endnote's "Find Full Text" feature).
-
-(ref:medrxivr-sr-scap) Role of `medrxivr` in a systematic review workflow
-
-```{r medrxivr-sr, echo = FALSE, fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
-```
-
-<!----------------------------------------------------------------------------->
-
-## Development
-
-<!-- IDEA Add timeline chart as seen here: https://bookdown.org/alecri/thesis/4-methods.html#sec:dosresmeta -->
-
-### Success criteria {#success-criteria}
-
-I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
-The criteria were as follows:
-
-1.  reliable, reproducible and transparent search functionality, allowing for Boolean (AND/OR/NOT) operator logic;
-
-2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
-
-3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Alternative medRxiv/bioRxiv interfaces
-
-Prior to development of this tool, I conducted an audit of existing tools for accessing medRxiv and bioRxiv metadata.
-While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
-
-The first, a platform called Rxivist[@abdill2019], allows users to search preprints using keywords.
-However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface[@zotero-15027] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
-
-The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
-As such, the platform only returns the most recent `r comma(1000)` records by publication date.
-
-Finally, neither tool provides an easy way to programmatically download a copy of the PDF of relevant preprints as part of the preparation for the full-text screening stage of a systematic review.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Early versions
-
-Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
-Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and I released the initial version of the `medrxivr` R package in February 2020.
-
-Early versions of the tool had a reliance on scraping data directly from the repository website.
-Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required me to regularly update or fix the script.
-
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
-This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Package infrastructure
-
-I wrote the `medrxvir` package in R using RStudio,[@rcoreteam2019] and followed development best-practice, including development of detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Usage
-
-The `medrxivr` R package is split into two component parts:
-
--   an interface to the Cold Springs Harbor Laboratory API, which imports medRxiv and bioRxiv metadata into R; and
--   a collection of functions for working with the imported metadata, with an explicit focus on searching this data as part of a systematic review or evidence synthesis project.
-
-The standard workflow is to download a copy of all metadata contained in the repository, and then to perform searches on this local copy.
-This is a workaround as the Cold Springs Harbor Laboratory API does not provide any functionality to search the database.
-
-While the package allows users to interact with and search both medRxiv and bioRxiv metadata, as the process is identical for both, searching the medRxiv database is used as an illustrative example throughout this chapter.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Installation
-
-`medrxivr` has been released to the Comprehensive R Archive Network (CRAN), and can be installed with the following code:
-
-&nbsp;
-
-```{r, eval = FALSE}
-install.packages("medrxivr")
-```
-
-&nbsp;
-
-Alternatively, the development version of the package can be installed from GitHub:
-
-&nbsp;
-
-```{r, eval = FALSE}
-# install.packages("devtools") 
-devtools::install_github("ropensci/medrxivr")
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Importing preprint metadata
-
-<!-- TODO Clean up this section -->
-
-<!-- REVIEW Not clear why there are two, or what are advantages or disadvantages of each. There’s a hint below (“can become unavailable during peak usage times”), but perhaps add some more -->
-
-Prior to searching the metadata, it must first be imported in R.
-In `medrixvr`, I have provided two separate but related methods for users to import the data (Figure \@ref(fig:medrxivr-data-sources)).
-The first of these methods, accessed via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Get a copy of the database from the live medRxiv API endpoint
-mx_data <- mx_api_content()
-```
-
-&nbsp;
-
-This provides an up-to-the-minute reflection of the medRxiv preprint repository.
-However, this approach has two limitations.
-Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database  <!-- TODO Get numbers here, at a given date --> requires a time-intensive process of cycling through multiple pages.
-Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
-
-To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Import a copy of the medRxiv data from the snapshot
-mx_data <- mx_snapshot()
-```
-
-&nbsp;
-
-This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file to an online server (Figure \@ref(fig:medrxivr-data-sources)).
-Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
-
-The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
-However, given that the number of records added each day is relatively low, this should pose minor issues.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-(ref:medrxivr-data-sources-cap) **Overview of `medrxivr` data sources** - Users can either access the API directly via `mx_api_content()`, or can import a maintained snapshot of the database, taken each morning at 6am, via the `mx_snapshot()` function.
-Note: due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
-
-(ref:medrxivr-data-sources-scap) Overview of `medrxivr` data sources
-
-```{r medrxivr-data-sources, fig.pos="H", echo = FALSE, results="asis", fig.cap='(ref:medrxivr-data-sources-cap)', out.width='100%', fig.scap='(ref:medrxivr-data-sources-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev-tools","data_sources.png"))
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Performing a search
-
-Once a local copy of the metadata is created, the first step in searching it is to create a search strategy.
-Search terms to be combined with the OR operator are contained in vectors (`c(...)`), while topics to be combined with the AND operator are contained in lists (`list(...)`).
-
-&nbsp;
-
-```{r, eval = TRUE}
-# Create the search query
-topic1  <- c("dementia","alzheimer's")  # Combined with OR
-topic2  <- c("lipids","statins")        # Combined with OR
-
-myquery <- list(topic1, topic2)         # Combined with AND
-```
-
-&nbsp;
-
-For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
-There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
-Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
-"randomi*s*ation" vs "randomi*z*ation".
-
-Once a strategy has been defined, it is passed along with the local copy of the database to the `mx_search()` function.
-
-&nbsp;
-
-```{r, eval = FALSE}
-# Run the search
-results <- mx_search(mx_data,
-                     myquery)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Refining a search
-
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.[@rethlefsen2021prisma]
-
-&nbsp;
-
-```{r, eval = FALSE}
-results  <- mx_search(mx_data,
-                      myquery,
-                      report = TRUE)
-```
-
-```{r, eval = FALSE}
-## Found 1 record(s) matching your search.
-## 
-## Total topic 1 records: 224
-## dementia: 224
-## alzheimer's: 0
-## 
-## Total topic 2 records: 119
-## lipids: 90
-## statins: 33
-```
-
-&nbsp;
-
-This allows users to discover which terms in their search are contributing most to the total number of results returned.
-This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
-It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results.
-As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
-
-<!-- TODO Add some text to this section about the challenges of defaults, and the fact that the autocaps option exists -->
-
-<!-- REVIEW Can you not just make the search case insensitive?
-It means you often need to include capitalized and non-capitalized versions in case a word appears at the start of a sentence or is capitalized for some other reason?
-(I find a lot of people these days pseudo-randomly capitalize words for no good reason (like you did in “Application Programming Interface” on page 4 above!!)) -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Exporting to a bibliography file
-
-In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
-While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
-
-For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
-
-&nbsp;
-
-```{r, eval = FALSE}
-mx_export(results, 
-          file = "medrxiv_export.bib",
-          report = TRUE)
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Downloading the PDFs of relevant records
-
-`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
-`mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
-This functionality is similar to the "Find Full Text" feature offered by EndNote.
-
-&nbsp;
-
-```{r, eval = FALSE}
-mx_download(results,  # Search results, less excluded records
-            "pdf/")   # Directory to save PDFs to 
-```
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-### Reception and future plans
-
-```{r, echo = FALSE, warning=FALSE}
-
-medstats <- cranlogs::cran_downloads("medrxivr", from = "2019-11-22", to = "2021-12-01")
-
-medrxivr_downloads <- plyr::round_any(sum(medstats$count), 100, f = floor)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-```
-
-The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]
-
-The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
-
-Lobbying of the Cold Springs Harbor Laboratory to develop the API to allow for direct searching of the database has been ongoing.
-This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
-For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Use case
-
-In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
-For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
-
-By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two differnt publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
-We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
-This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
-Author contributions are discussed in the
-
-In short, this use case illustrates that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints as a part of evidence synthesis exercises.
-
-<!----------------------------------------------------------------------------->
-
-### Limitations of `medrxivr` {#medrxivr-limitations}
-
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
-However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
-A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
-
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
-
-<!-- TODO Clean-up this section -->
-
-<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
-
-```{r, include=FALSE}
-med_res <-
-  # Use snapshot from July 2021
-  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
-                      "*",
-                      from_date = "2019-07-01",
-                      to_date = "2019-08-01") %>%
-mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
-  group_by(pub_ind) %>%
-  count()
-
-published <- med_res$n[2]
-publication_n <- sum(med_res$n)
-publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
-```
-
-<!-- TODO Need to finish this bit and move it to the use-case section! -->
-
-Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
-`r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
-allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
-
-<!-- TODO replicate this analysis -->
-
-It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Role of open source tools in evidence synthesis
-
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
-
-<!----------------------------------------------------------------------------->
-
-## Summary
-
--   In this Chapter, I have introduced a new tool, `medrxivr`, for performing complex systematic searches of the medRxiv and bioRxiv preprint repositories.
-
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
-
--   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
-
-\newpage
-
-## References
-
-<!--chapter:end:02-Chp-Systematic-Review-Tools.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::html_document2: default
-documentclass: book
----
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
-```
-
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
-
-# Systematic review of all evidence available on the association between blood lipids (and treatment) and dementia outcomes {#sys-rev-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!-- ## To Do -->
-
-<!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-<!-- * Statins and the risk of dementia Jick -->
-
-## Lay summary
-
-Systematic reviews are a type of research that aim to use all existing evidence to provide the best answer to an important research question.
-They do this by finding and combining the results from many related primary research studies.
-Reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; assessment of each study's methods.
-
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels, and dementia.
-
-There were XXX primary studies <!-- TODO check this -->that contained information on this relationship.
-I found that statins reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipids were not associated with any outcome.
-The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
-
-The use of the results of this review in subsequent chapters is dicussed.
-
-<!-- TODO Search for MCI -->
-
-<!-- TODO text -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-## Introduction {#sys-rev-intro}
-
-In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
-This analysis sought to address two specific aims.
-
-Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
-These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
-However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
-Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
-As such, the primary aim of this analysis was to systematically review all available literature, regardless of study design.
-
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but may contain important unpublished studies.
-As a sensitivity analysis to the systematic review presented in this chapter, I sought to quantify the additional evidential value of including preprints.
-This inclusion of preprint serves makes use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
-
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Methods
-
-### Protocol
-
-A pre-specified protocol for this analysis was registered using the Open Science Framework, and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Contributions
-
-In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this systematic review was performed in conjunction with a team of secondary reviewers and an information specialist (see Acknowledgments and Author declaration).
-<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
-In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
-
-<!-- TODO Double check this list at the end of the project. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Search strategy
-
-I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-An outline of the general strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
-<!-- TODO Need to actually attach each search strategy.
-Should be able to loop through search strategy results.
--->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic.
-The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
-
-(ref:searchOverview-scaption) searchOverview
-
-```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
-To ensure that the study design filters are not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
-
-<!-- TODO need to comment on this feed-back process, or remove -->
-
-I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies.
-
-Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-In addition, the abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
-<!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Study selection
-
-Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
-those matched based on the "Title" field alone).
-
-Following deduplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, records were rescreened by me with a 1 month lag to intra-rater consistency.
-
-Similarly, I completed all full-text screening, with a random ~10% being screened in duplicate by a second reviewer.
-In addition, any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
-Reasons for exclusion at this stage were recorded.
-Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
-
-The criteria used to assess eligibility are presented in the subsequent sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Inclusion criteria
-
-I sought to include studies that examine the relationship between blood lipid levels (or any specific lipid fraction, including total cholesterol, HDL, LDL, and triglycerides) and risk of incident dementia and its subtypes.
-Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Participants were screened for dementia at baseline and prevalent cases excluded.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than <50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits were placed on the sample size of included studies.
-
-Eligible studies defined dementia according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that these criteria were used when entering the outcome into the EHR.
-
-<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
-
-<!-- TODO Any study using EHR - go back and extract codelists -->
-
-No limitations were imposed on publication status, publication date, venue or language, although sufficiently detailed reports of the studies to be able to examine their methods were required for inclusion.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Exclusion criteria
-
-Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded.
-Studies which presented no evidence of attempting to exclude prevalent cases from their analyses were also excluded.
-Studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia) were excluded.
-Conference abstracts with no corresponding full-text publication were examined, and where required, I contacted authors to obtain information on the study's status.
-Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
-
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) were excluded.
-Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
-Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Validation of screening process
-
-Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
-assessment of conistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
-assessment of accuracy).
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is an important characteristic.
-
-Gwet's AC1 is defined as:
-
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
-
-In reference to a two-by-two table with cells A, B, C and D, it is calculated using the following:
-
-\begin{equation}
-  AC1 = \frac{\frac{A+D}{N}-e(\gamma)}{1-e(\gamma)}
-  (\#eq:AC1-main)
-\end{equation}
-
-where $e(\gamma)$ is the chance agreement between raters, given as $2q(1-q)$, where
-
-\begin{equation}
-  q = \frac{(A+C)+(A+B)}{2N}
-  (\#eq:AC1-supp)
-\end{equation}
-
-<!-- TODO Need to be sure of how to calculate. -->
-
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
-Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of <.9), a larger proportion of records would have been dual-screened.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Data extraction
-
-Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
-I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
-
-#### Study-fication
-
-As part of the data extraction process, multiple resords resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This is likely in the advent of multiple papers reporting results on the same cohort, but say, at different time points.
-Study-fication builds out the most comprehensive accounts of the studies and results from as many published articles were applicable.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Combining across groups
-
-Following best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups.
-[@higgins2019]
-
-\begin{equation}
-N = N_1 + N_2
-  (\#eq:combiningGroups1)
-\end{equation}
-
-\begin{equation}
-Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
-  (\#eq:combiningGroups2)
-\end{equation}
-
-\begin{equation}
-SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
-  (\#eq:combiningGroups3)
-\end{equation}
-
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script written to combine the groups for analysis.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Harmonisation of cholesterol measures
-
-<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
-not providing qratile cut-off values, not poviding numbers per group, etc.
---> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
-
-\begin{equation} 
-  mg/dL = mmol/L \times{} Z
-  (\#eq:lipidConversion)
-\end{equation}
-
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Following up with authors {#contacting-authors}
-
-Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Analysis of varying effect measures
-
-<!-- TODO Include formulae and informed assumptions  -->
-
-The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-If the outcome is rare, as is the case for dementia outcomes at and estimated prevalence of  odds and risk ratios approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-timea-at-risk in each treatment group.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019]
-
-Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect.
-In addition, there is some evidence of manipulation of effect estimates in previous reviews,(e.g.
-Chou, Sci Reports - at least one study disagrees with) but this is not accurately documented in the review text.
-<!-- TODO Need to really fix this -->
-
-In this review, studies reporting hazard ratios were synthesised separately to those reporting odds/risk ratios.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk-of-bias assessment {#risk-of-bias}
-
-A key use of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Section \@ref(intro-triangulation) for the results of this qualitative analysis).
-To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
-
-There has been a recent movement within the evidence synthesis community from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
-Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
-
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, and challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the community also moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-Additionally, bias should be assessed at the result (defined as a a specific outcome at a specific timepoint) rather than the study level.
-For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that is not an issue at six months may introduce bias at 2 year follow-up, and assigning a bias judgement to the study as a whole masks the different level of bias for each unique result.
-
-In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
-The study design-specific tools are introduced and discussed in more detail in the following sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Randomised controlled trials
-
-Randomized controlled trials were assessed using the RoB2 tool.[@sterne2019] The tool assess the risk of bias across five domains: Bias arising from the randomization process, Bias due to deviations from intended intervention, Bias due to missing outcome data, Bias in measurement of the outcome, Bias in selection of the reported result.
-Acceptable judgements include: low risk of bias, some concerns, high risk of bias.
-Each of the 5 domains contains a series of signalling questions or prompts, which guide the user through the tool.
-Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Non-randomised studies of interventions/exposures
-
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: Bias due to confounding, Bias due to selection of participants, Bias in classification of interventions, Bias due to deviations from intended interventions, Bias due to missing data, Bias in measurement of outcomes, and Bias in selection of the reported result.
-Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “Low risk”, “Moderate risk”, “Serious risk” and “Critical risk”.
-Ideally, observational studies should be assessed in reference to an idealised randomised controlled trial.
-Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
-
-While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (“Risk of Bias In Non-randomised Studies – of Exposure”), which I had applied in a published review.[@french2019] The version had no signalling questions and so judgements were made at the domain level.
-The motivation for this using this tool above other established tools such as the Newcastle-Ottowa scale (NOS).[@wells2000] was two-fold.
-In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
-Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Mendelian randomisation studies
-
-At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy, and selection of participants.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Risk of bias due to missing evidence
-
-A recent shift towards the assessment of missing evidence due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - is demonstrated via the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
-<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
-
-This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
-This is largely because the tool did not exist when the protocol was originally registered.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Analysis methods
-
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design
-
-Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-<!-- TODO CITATION NEEDED --> Meta-analysis provides a summary or pooled effect estimate across studies.
-
-Of note, studies were not combined across different study designs (i.e.
-RCTs were not combined in a meta-analysis with results from observational studies).
-The results from each individual analytical approach were summarised, but are compare and contrasted more fully in the triangulation exercise presented in Chapter \@ref(discussion-heading)
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Standard meta-analysis
-
-Both a fixed-effect and random-effects meta-analysis model was employed to combine the different included studies.
-<!-- TODO Need more information on the difference between the two approaches, and their formula here, and description of different methods and quarrels regarding distinction fixed effect vs random effects meta-analyses.
---> The fixed-effect method was implemented as:
-
-<!-- TODO Check these against those in Ben's thesis paper -->
-
-\begin{equation}
-  \theta_i = \mu + u_i
-  (\#eq:meta-analysis-random)
-\end{equation}
-
-\begin{equation}
-  weighted\ average = \frac{\sum Y_i (1/SE_i^2)}{\sum(1/SE_i^2)}
-  (\#eq:meta-analysis-fixed)
-\end{equation}
-
-<!-- where ... -->
-
-<!-- TODO Need equation for random effects too. See Sean's thesis here. -->
-
-#### Dose-response analyses
-
-<!-- TODO Explore how to map from simple diagnosis of hyperchol to dose response. Seems that does response needs >3 categories -->
-
-<!-- Will also need description of dose-response meta-analysis here, with reference to forthcoming book Julian sent on. -->
-
-This was particularly important for the dose response meta-analysis, where the number of participants and the cut-offs per category were often not reported.
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks  -->
-
-Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
-for example, highest vs lowest quartile).
-<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
---> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
-
-Studies were excluded from this analysis if the number of categories was less than three, if the exposure cut-off points for for each category were not reported (e.g.
-if the study reports splitting participants into quartiles and comparing the highest vs lowest without giving the quartile bands).
-
-A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fractions, as detailed in Table \@ref(tab:lipidLevels-table).
-Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
-
-Due to the requirements for the dose response analysis, studies were excluded from this secondary analysis if they did not provide the require information: cut-off points.
-
-Where this was not reported in the study, I contacted the corresponding author to attempt to obtain the required information (see Section \@ref(contacting-authors)).
-
-When the highest category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when, the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur natually, it was difficult to define).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity analyses
-
-I conducted a leave-one-out analysis in order to explore the impact of any results on the summary effect estimate.
-<!-- TODO CITATION NEEDED --> In addition, where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
-_A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
-<!-- TODO Need more here -->
-
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and statistically using Egger's regression test.
-<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Visualisation of results
-
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As such, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
-
-One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-
-In response to this criticism, I developed a new visualisation tool was designed to allow for "paired" forest plots, as recommended by the ROB2 publication, where the risk-of-bias assessment is presented alongside the results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Assessment of added value of including preprints
-
-__[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints)), as I am not convinced on the language I am using]__
-
-Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)) but their inclusion in a systematic review.
-
-As a sensitivity analysis, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
-
-Additionally, I followed preprints up over time to investigate whether all identified preprints included in the review were subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or alternatively, if some preprints were not published, then preprints provide a distinct evidence source.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Results
-
-<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
-
-### Initial search and validation of search filters
-
-The database search identified `r num_to_text(23447)` records, of which
-
-<!-- TODO Cross check this with the actual numbers included -->
-
-Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were basic science studies, commentaries or educational articles, as expected.
-<!-- TODO include some example citations here -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Screening results
-
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-<!-- TODO Check these figures & Finish PRISMA -->
-
-A PRISMA (Preferred Reporting Items for Systematic Reviews and Meta-analyses) flow diagram,[@page2021] <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the right of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the left of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = XXX; most commonly a inelgible lipid fraction), used the wrong study design (n= XXX), or reported on a wrong outcome (n=24; e.g.
-change in cognitive scores).
-
-### Validation of screening
-
-<!----------------------------------------------------------------------------->
-
-<!-- TODO PRISMA must include reasons for exclusion - extract from Rayyan -->
-
-```{r prisma-flow-setup, include = FALSE}
-```
-
-\blandscape{}
-
-&nbsp;
-
-(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-\elandscape{}
-
-<!----------------------------------------------------------------------------->
-
-```{r agree-setup, include = FALSE}
-```
-
-For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
-For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
-
-<!-- TODO Include AC1 result in caption above -->
-
-(ref:agreeInter-scaption) Inter-rater agreement
-
-```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
-
-(ref:agreeIntra-scaption) Inter-rater agreement
-
-```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, specifically around the definition of cognitive decline/MCI versus dementia, and the definition of eligible lipids fractions.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies
-
-```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
-```
-
-Following full-text screening, 87 reports describing `r n_included` unique studies met the criteria for inclusion in the review.[@ancelin2012a; @ancelin2013; @andrews2019a; @arvanitakis2008; @batty2014; @benn2017b; @bettermann2012a; @beydoun2011; @bruce2017; @burgess2017; @chao2015a; @chen2014; @chiang2007; @chitnis2015; @chou2014a; @chuang2015; @cramer2008; @dodge2011; @forti2010; @gnjidic2016; @gottesman2017; @gustafson2012; @haag2009; @hayden2006; @heartprotectionstudycollaborativegroup2002; @hendrie2015; @hippisley-cox2010a; @jick2000; @kimm2011; @kivipelto2001; @kivipelto2005a; @kuo2015; @li2004; @li2005a; @li2010; @liao2013; @liu2019a; @mainousa.g.2005; @mielke2005a; @mielke2010a; @mielke2011; @mukherjee2013; @muller2007; @noale2013; @notkola1998; @ostergaard2017; @pan2018; @parikh2011; @peters2009; @raffaitin2009; @rantanen2017; @rea2005a; @redelmeier2019; @reitz2004a; @reitz2010; @ridker2008; @ronnemaa2011; @schilling2017a; @smeeth2009a; @so2017; @solomon2007; @solomon2009a; @solomon2010; @sparks2008; @strand2013; @svensson2019; @szwast2007; @tan2003a; @tynkkynen2016; @tynkkynen2018; @wang2012; @whitmer2005a; @yang2015; @yoshitake1995; @zamrini2004; @zandi2005; @zhu2018a; @zimetbaum1992] Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of studies were non-randomised studies with the sole two included randomised controlled trials both examining all-cause dementia.
-Similarly, a relatively small number of Mendelian randomisation studies were identified, and several performed a two-sample MR analysis using the same summary statistics from published GWAS, leading to complications in synthesis (see Section\@ref()).
-
-Of the non-randomised studies examining treatments that modify lipid levels, the overwhelming majority examined statin use.
-For exposue studies, total cholesterol and LDL-cw were the most frequently reported lipid elements.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia or Alzheimer's disease, with only a small proportion examining vascular dementia (n=XXX, %).
-Some rarer outcome classifications such as vascular-component or mixed dementia were also investigated.
-
-Of note, several studies provided evidence on a lipid fraction as part of a wider study on Mets. Raffatin/Ng
-
-Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases.
-
-Midlife cholesterol levels were of particular interest, with several studies examining this age-range. <!-- TODO Talk a little bit more about age here -->
-
-Three included reports were preprints (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk), one of which had subsequently been published and was captured by the primary literature search.
-All three included preprints were obtained from the bioRxiv preprint server and described Mendelian randomisation analyses.
-
-Several Mendelian random studies made use of summary level data from the same published GWAS (the Global Lipids Genetics Consortium and the IGAP consortium <!-- TODO CITATION NEEDED -->).
-As this could incur double counting of participants, and so produce artifically precise estimates if meta-analysed, only results from one of these studies were included <!-- TODO How chosen??
--->.
-As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable.
-
-<!--- TODO Figures and tables to include here:
-
--   Summary of risk of bias (not done)
-
---->
-
-<!-- TODO Also need to extract the codes used in each study -->
-
-<!-- TODO Need to add abbreviations to table -->
-
-\blandscape{}
-<!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple study designs, and these have been duplicated across the relevant sub-sections.
-
-(ref:studyCharacteristics-scaption) Characteristics of included studies
-
-```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape{}
-
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries.
-
-<!----------------------------------------------------------------------------->
-```{r cohortLocationsSetup, include = FALSE}
-```
-
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
-
-(ref:cohortLocations-scap) Geographical distribution of study cohorts
-
-```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
-```
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-of interest, many of the included studies were peformed in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance.
-
-### Risk of bias {#risk-of-bias-res}
-
-As discussed, the results of the risk of bias assessments are presented alongside their corresponding result.
-
-However, as a brief summary of the biases at play:
-
-Both randomised controlled trials were considered to be at low risk of bias.
-
-For NRSI
-For NRSE
-
-For MR studies
-
-Additionally, Several synthesis were also assessed to be at risk of bias due to missing evidence.
-A key issue identified relating to bias due to missing data was the potential for the search to miss relevant Mendelian randomisation studies which had examined the association between Alzhiemer's disease and multiple risk factors.
-This is discussed further in Section \@ref(rev-discussion-MR).
-
-<!-- TODO Discuss Taiwan health database as good evidence on non-Caucasian idenitiies -->
-
-Haag is a good example of potentially missing results - number of cases of other outcoems reported, but no analysis performed.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### All-cause dementia
-
-__Statins__
-
-```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-In contrast, a meta-analysis of prospective observational studies provided evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-A single study examing the effect of HMGCR inhibition on any dementia, via a , and found weak evidence for an effect (`r mrStatin$Dementia`).
-
-__Lipids__
-
-* NRSE
-
-* MR studies per 1-SD
-
-In NRSI, statin use was associated with a reduce risk of all-cause dementia (`r obsStatins$Dementia`, Figure \@ref(fig:statinsNRSI)).
-
-&nbsp;
-
-Several studies presented results per SD change in a lipid fraction.
-
-In Mendelian randomisation studies, a similar
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Alzheimer's disease
-
-There were no randomised trials of statin, or any other lipid regulating agent, use on Alzheimer's disease, though several observational studies reported on this outcome, providing evidence for a protective effect (`r obsStatins$AD`; Figure \@ref(fig:obsStatinADFig))
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random effects meta-analysis of statins on Alzheimer's disease
-
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Two Mendelian randomisation studies looked at specifically as a result of by HMGCR inhibition (mediated by a single SNP; rs17238484).
-The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinDementia-cap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinDementia-scap) Random effects meta-analysis of LDL-c lowering via genetic HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinDementia-cap)', out.width='100%', fig.scap='(ref:mrStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-__Lipids__
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Vascular dementia
-
-__Statins__
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinDVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-__Lipids__
-
-### Dose response meta-analysis of lipid levels {#dose-response-results}
-
-<!-- TODO Cite excluded studies and list exclusion reasons -->
-
-Several studies were excluded from the dose-response meta-analysis, as the number of cases/controls per dose group could not be calculated and the corresponding author for the study did not respond to clarification requests.
-The results from the dose response analysis can be seen in Figure \@ref(fig:lipidsDoseResponse).
-
-&nbsp;
-
-### Sources of heterogeneity
-
-Data on another potentially important source of heterogeneity
-Plus other such as education level and baseline cognitive scores, but data were either not reported for most studies or when reported, were too diverse to synthesize.
-
-<!-- Detail that some of these are exploratory, in particular the effect of different scales on the association between the groups. **[CROSS]** -->
-
-<!-- Important here to examine effect of risk of bias (due to immortal time in observational studies). -->
-
-<!-- Also important to examine the effect of: -->
-
-<!-- * age at baseline -->
-<!-- * sex (percentage) -->
-<!-- * education -->
-<!-- * baseline cognitive scores (how to group) -->
-
-<!-- ### Sensitivity analyses -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Sensitivity analysis
-
-Given that the majority of the studies included in the review were of
-
-### Small study effects {#sys-rev-pub-bias}
-
-<!-- -   Check if there are protocols available for any of the published reports (unlikely for non-randomised controlled trials), and whether there were -->
-<!-- -   Vascular dementia has substantially less published reports. Many (reference Smeeth et al 2010 here) simply group into AD and non-AD making comparison between published studies difficult -->
-
-There was little evidence of publication bias across the evidence base (Figure \@ref(fig:funnelStatinsAny)).
-
-<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
-
-<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
-Depsite attempts to obtain this additional information through contact with a -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:funnelStatinsAny-cap) Funnel plot of results examining the relationship between statins and any dementia
-
-(ref:funnelStatinsAny-scap) Funnel plot of results examining the relationship between statins and any dementia
-
-```{r funnelStatinsAny, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnelStatinsAny-cap)', out.width='100%', fig.scap='(ref:funnelStatinsAny-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Added evidental value of including preprints {#sys-rev-including-preprints-res}
-
-<!-- TODO Will have to get actual numbers for this section -->
-
-As show in Figure \@ref(prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprints were included in the review as reports of eligible studies, of which two were unique reports not captured by the main search.
-
-For the analysis of XX on YYY, preprints added ...
-
-Investigation of the publication status of the two unique preprints indicated that one has since been published (in late 2019 date).<!-- TODO check publication date -->
-
-<!-- QUESTION Can I explore the amount of information added by the preprints quantitatively using the weights in the meta-analysis -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-<!-- TODO Check inclusion of Rockwood 2002:  -->
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-
-The discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
-A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise (Chapter \@ref(tri-heading)).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Summary of findings
-
-There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogenity in exposure (e.g.
-mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
-
-Some evidence that age has impact on observed lipid-dementia relationship - use to link
-
-The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
-This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up, necessary due to the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), and so only appears in the literature in recent years, driven by the availability of Alzheimer's disease summary genome wide association studies (GWAS) that form the basis of two-sample Mendelian randomisation approach.
-
-<!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) __Study designs by year of publication__ -
-
-(ref:typeByYear-scap) Study designs by year of publication
-
-```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A common theme across the evidence base was a lack of data on the association of vascular dementia.
-This is particularly interesting given that lipids and statins are primarily related to vascular disease.
-__Can't look forward to other chapter__ There is the potential that studies encountered similar difficulties in address the unexpected results observed in the CPRD analysis in Chapter \@ref(cprd-analysis-heading), likely due to confounding by indication, and so may suffer from the "file-drawer effect".[@rosenthal1979] For vascular dementia, few Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of GWAS of this outcome.
-
-<!--- 
-QUESTION
-This does introduce some conflicts with other studies where a change score has been dichotomised in order to have a binary dementia or not dementia outcome.
-- No these studies should not be included, as not recognised criteria.
--->
-
-<!-- __Exclusion of the PROSPER trial__ Will need to have a good bit here on the exclusion of this RCT, particularly as it is included in the Cochrane review on the topic.
-Cross-reference with the meta-bias section in the early section, on the impact of only included studies that sought to make a definitive diagnosis, rather than using change in cognitive assessment scales.
--->
-
-Of note, this review did not include the commonly cited PROSPER study, which examined the effect of pravastatin on CVD risk,[@shepherd2002a] reporting on cognitive outcomes as one of several secondary outcomes.
-While widely cited in relation to the effect of statins on dementia and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial only reported on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
-As such, this trial did not met the inclusion criteria for this review.
-
-<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
-The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
-from Anstey 2017 -->
-
-Questions over missing results - evidence from one of the conference abstract analysis pairs that a non-significant results are being suppressed.[@yamada2009; @yamada2009a] In addition, there were some concerns over the potential for estimates to be missing from the meta-analysis of observational studies not at random, given the preferential reporting of significant results observed in a number of analysis (see Section \@ref(risk-of-bias-res)).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Comparison with previous reviews {#rev-previous-reviews}
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-__This section will be completed once Georgia has completed her analysis, and can also be cross-references with the meta-meta analysis published is Brain Sciences recently.__
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies, and explore the heterogeneity of results across different levels of risk of bias levels.
-Some previous reviews did assess risk of bias, but used non-domain based assessment tools, such as the Newcastle-Ottowa scale.[@anstey2015; @poly2020]
-
-Similar the on previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease was conducted prior to the majority of MR studies included in this review being published, and extracted results including SNPs in APoE4 (see the following section for a discussion of the bias this introduces).
-
-However, despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
-In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
-
-One of the strengths of this review is it's inclusion of Mendelian randomisation studies as a source of evidence.
-
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to (assuming the assumptions of the method are valid), though it's inclusion as an acceptable study design in this review was complicated by a number of factors.
-
-Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI.
-As such, the process and tools for systematically assessing them are not as well developed, likely due to the limited availabilt of large scale GWAS datasets needed for two sample MR.
-A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application.
-
-Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref().
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool, which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool addresses the studies used, it does not access the additional methodological considerations of the analysis of the Mendelian randomisation analysis itself.
-<!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced on a recent review of systematic reviews of Mendelian randomisation studies.
-
-<!-- TODO Need to add some text to the ROB section of this chapter on distinction between reporting and quality -->
-
-<!-- Problems with overlapping samples in reviews of Mendelian randomisation studies in that may be double counting participants -->
-<!-- TODO Check discussion on this point from Matt Lee thesis, in email -->
-<!-- TODO Email George with query on dual counting, following review of email with Julian -->
-
-As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
-This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
-Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
-This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
-
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation", followed by manual review of studies that look across multiple risk factors, would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened, even when using study design filters (n=`r comma(16109)`).
-Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool by a panel of methodologists and analysts would be of substantial benefit.
-
-<!-- TODO Ask Matt Page whether he has done any work on this? Studies looking at many risk factors don't report null results in abstract and so do no -->
-
-Talk about problem with studies sharing underlying datasets in two sample Mendelian randomisation frameworks - c.f.
-EHR databases, which contain the same underlying sample but use different sub-samples on account of the distinct codes/conditions and timepoints used to defined the study cohorts, Mendelian randomisation analysis can be multiple studies using the exact same summary statistics from the same cohorts
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref()), increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria of .
-
-Introduce assumptions underlying Mendelian randomisation (with image).
-Higlight that most if not all included analysis initially describing a protective effect of LDL-c, which attenuates to the NULL once ApoE4 gene regions are removed.
-Note the region must be quite wide - talk about controversy surrounding Benn paper
-
-Additionally many of the studies suggested a link between, but then in the sensitivity analyses or in the Discussion disclaim that when adjusted for ApoE4, any association was attenuated to the null.
-This point is important given one of the core assumptions of
-
-<!-- TODO Diagram showing three assumptions of MR, comparing it to a graph showing the invalidation of no pleiotopy assumption -->
-
-MR are limited by the need for SNP to be present in both datasets (for TSMR).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication of Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is one of the component consortia of IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication of Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrDuplication-cap)', out.width='100%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!-- TODO Talk about discrepancies between results of different methods, but highlight that it is a problem as the information is being contributed by the same people. -->
-
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least on vascular dementia GWAS exists - find it and cite it here.
--->
-
-A key example of the importance of .
-In almost all cases, Mendelian randomisation studies examine.
-A clear exampe of this is Ben et al, 2017, where the ApoE variants were not sufficient identified and excluded, and the published paper detailed evidence for a protective effect of LDL-c was identified (`estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated this finding towards the null.[@benn2017a]
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of preprints
-
-```{r preprintGrowthSetup, include=FALSE}
-```
-
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review (see Appendix \@ref(appendix-medrxivr-code) for the code used to search the repositories).
-There were several relevant preprints captured by the search.
-The added evidential value of including these preprints was highlighted in Section \ref(sys-rev-including-preprints-res).
-
-Three relevant preprints were identified
-
-medRxiv grew out of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server.
-The small number of studies return by the searches (or the absence of any hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the first medRxiv preprint was registered on 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a small number of records (n=`r n_at_search["med"]`).
-
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Section \@ref(medrxivr-limitations) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
-
-While none of the preprints contributed uniquely to the review, this is again.
-Consider the example of one of the Mendelian randomisation analyses of the effect of LDl-c on Alzheimer's disease, which found no impact of LDL-c on AD following removal of APOE4.
-The manuscript was initially published in bioRxiv in July 2017[@zhu2017] which was subsequently published in Nature Communications in January 2018, following peer-review.[@zhu2018] While this study was captured by both the preprint and published searches in this review, had the searches been run within this window, the preprint would have contributed unique data to the review.
-This illustrates that while it may not have aided this review, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-Of note, since the start of my review, inclusion of preprints in systematic reviews has now become widespread due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.
-However, how well this adoption of preprints will transfer to other topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-<!-- TODO Discuss information here that I responded to Julian with re: % of preprints that published -->
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:preprintGrowth-cap)', out.width='100%', fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-<!-- TODO Cite studies detailing increasing acceptance as a valid form of evidence.  -->
-
-<!-- This does speak to the over-representation of certain study designs in the preprint literature  -->
-
-<!-- Regardless, some studies were identified -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Comments on the process -->
-
-<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
-
-<!-- &nbsp; -->
-
-<!-- #### Protocol registration -->
-
-<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
-In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
--->
-
-<!-- &nbsp; -->
-
-<!-- #### Workload -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-<!-- &nbsp; -->
-
-<!-- #### People management -->
-
-<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
-However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
--->
-
-<!-- &nbsp; -->
-<!----------------------------------------------------------------------------->
-
-<!-- ### Validation against recent umbrella review -->
-
-<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
-
-<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
-
-<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
-In fields where there is a lot of existing reviews, they -->
-
-<!-- All studies identified by reviews included in te -->
-
-<!-- In hindsight, this approach ma -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important elements, and so these could not be extracted.
-This limiation was compounded by the expected low response rate to requests for further information from primary authors (although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019]).
-
-While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
-
-Based on my experience of extracting data for this review, I co-wrote an guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021]
-
-Similarly, a substantial amount of time and effort has gone into making the data obtained by this review openly available to other researchers. <!-- TODO Cite the Zenodo repo here! -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Strengths and limitations
-
-<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
-
-#### Strengths
-
-I believe there are four aspects where this review is distinct from those reviews already available in the published literature (as identified by <!-- TODO CITATION NEEDED -->):
-
--   *Comprehensiveness:* While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition
-
--   *Structured risk-of-bias assessment:* The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
-This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any review on this topic.
-
--   *Inclusion of preprints:* Unlike other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related manuscripts as a source of grey literature.
-As part of this chapter, I plan to examine the extent of the additional information provided to the review by the inclusion of preprints.
-
-<!-- TODO Comment on the fact that several of the studies identified through the search of preprints, were subsequently published, but much later than the cut-off point for the search (e.g.
-they would not have been captured by the search for published papers) -->
-
-- *Contribution to methods work:* A large part of this review was the associated work on improving research synthesis methods.
-This work is detailed as relevant throughout the Chapter, often referring to additional work detailed in the .
-In addition this review was used to pilot an upcoming risk of bias tool
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Limitations
-
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
-
-In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
-
-One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
-
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Conclusions
-
-In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
-
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
-
-\newpage
-
-## References
-
-<!--chapter:end:03-Chp-Systematic-Review.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
-When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.
-```
-(ref:cprdquote) --- Harold F. Dorn, 1953 [@dorn1953]
-
-# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}
-
-\minitoc <!-- this will include a mini table of contents-->
-
-<!-- Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-library(dplyr)
-options(scipen = 99)
-knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-```{r load-files, echo = FALSE}
-```
-
-<!-- ## Additional ideas -->
-
-<!-- TODO Need to add some information on the generation and use of propensity scores -->
-
-<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
--->
-
-<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
-
-<!-- __Things we tried__ -->
-
-<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
-Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
-Need total number of those starting and average time to start.
--->
-<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
-<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
-<!-- - Allowing for time-varying confounders for binary covariates. -->
-
-<!-- __Things we could try__ -->
-
-<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
-<!-- - Examine Cramer et al. thesis and see what they did -->
-<!-- - Marginal structural models approach (a la J. Sterne) -->
-
-<!--------------------------------------------------------------------------->
-
-<!-- TODO Check lipid-regulating vs lipid regulating -->
-
-<!-- TODO Check all fig/table cross-references evaluate -->
-
-## Lay summary
-
-Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
-Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
-These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
-This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
-
-This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
-Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
-
-Little evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
-In contrast, I found an increased risk of vascular and other (i.e.
-non-Alzheimer's) dementia with lipid regulating agent use.
-
-This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
-This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
-However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Introduction
-
-In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
-
-The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
-
-Firstly, it explicitly examines vascular dementia as an outcome.
-The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
-As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
-
-Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
-This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-## Methods
-
-### Study protocol
-
-An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
-
-<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
-
-<!-- TODO Add amendments to Appendix -->
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Data source {#cprd-data-source}
-
-Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
-The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
-Eu...
-- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
-Eu001 - Dementia in Alzheimer's disease with late onset).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
-Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
-
-(ref:readExample-scaption) Example of CPRD Read code hierarchy
-
-```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
-
-&nbsp;
-
-### Cohort definition
-
-This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
-However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
-
-Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
-These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-
-All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
-
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
-had less than one full day of follow-up).
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Exposures
-
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
-
-A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class altered according to one of three criteria:
-
-- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
-- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
-- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.
-
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-### Outcomes {#cprd-outcomes}
-
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
-The diagnosis date of the outcome was determined by the first record of a relevant code.
-
-<!----------------------------------------------------------------------------->
-(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
-Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
-
-(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes
-
-```{r decisionTree, include = FALSE}
-```
-
-```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
-
-&nbsp;
-
-### Covariates
-
-A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
-
-Demographic covariates adjusted for included age and gender.
-Age was calculated at date of entry into the cohort.
-Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
-To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
-Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
-
-Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
-A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
-To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
-
-Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
-The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
-
-Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
-
-<!-- IDEA Add more detail here on the missing data approach -->
-
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
-
-Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
-BMI), or where a code existed for the absence of the condition (e.g.
-categorical smoking status).
-This approach was necessary, as absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
-
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Estimation methods
-
-A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
-
-\begin{equation}
-  h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)
-  (\#eq:cox-model)
-\end{equation}
-
-where:
-
-* $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
-* $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
-
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
-A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
-Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
-This is discussed in detail in the following section.
-
-<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
-
-<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}
-
-Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
-
-The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
-This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
-
-This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
-To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
-Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
-they enter the cohort and move into the exposed group on the same day).
-
-<!--------------------------------------------------------------------------->
-(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
-
-(ref:immortalTimeBias-scap) shortcap
-
-```{r, immortalTime, include = FALSE}
-```
-
-```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
-```
-<!--------------------------------------------------------------------------->
-
-### Time axis
-
-<!-- IDEA Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
-As such, the main analyses presented all used age as the time axis.
-
-<!-- TODO Will need to expand on choice of time axis here -->
-
-<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
--->
-
-&nbsp;
-<!--------------------------------------------------------------------------->
-
-### Sensitivity analyses
-
-The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
-To assess the robustness of the results, a number of sensitivity analyses were performed.
-These are described in the following sections.
-
-#### Control outcomes
-
-In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
-The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
-Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
-
-Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
-Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-
-Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
-Muscular backpain was chosen as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
-As such, if statins are not associated with backpain in this analysis, then confidence in the results for the dementia outcomes is increased.
-
-Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
-
-<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
-
-<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->
-
-<!----------------------------------------------------------------------------->
-(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
-Note the absence of any arrow between $X$ and $N$.
-In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).
-
-(ref:negativeOutcome-scap) DAG of ideal negative outcome
-
-```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
-library(dagitty)
-library(ggdag)
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
-  dagitty::dagitty("dag {
-    U -> N
-    C -> N
-    X <- U -> Y
-    X <- C -> Y
-    X -> Y
-    bb =\"-2.368,-2.972,2.597,2.726\"
-    C [pos=\"-0.3,0\"]
-    N [pos=\"0.5,1\"]
-    U [pos=\"-0.15,1.5\"]
-    X [exposure,pos=\"0,-1\"]
-    Y [outcome,pos=\"0.5,-1\"]
-  }"
-) %>% ggdag_classic() +
-  theme_dag()
-
-,
-height = 3
-)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))
-
-```
-<!----------------------------------------------------------------------------->
-
-#### Impact of additional covariates
-
-To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
-
-&nbsp;
-
-#### Sensitivity cohorts
-
-Two sensitivity cohorts were also created.
-The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
-The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
-
-<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
-
-&nbsp;
-
-#### Statin properties
-
-<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
-
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
-
-To explore whether any observed associations in the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
-
-<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
-
-&nbsp;
-
-#### Impact of dementia code lists
-
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
-
-This previous study used a propensity matching approach to estimate the association of statins with a range of outcomes, and found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
-
-The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
-
-## Results
-
-### Patient characteristics
-
-```{r characteristics, echo = FALSE}
-```
-
-```{r attritionFigure, include = FALSE}
-```
-
-Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
-
-(ref:cprdFlowchart-scap) Attrition of CPRD participants
-
-<!-- This figure needs to have comma seperated numbers in order to agree with text. -->
-
-```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia: Table \@ref(tab:followUp-table)).
-The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-
-\blandscape
-<!--------------------------------------------------------------------------->
-(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
-
-(ref:cprdCharacteristics-scaption) Patient characteristics by drug class
-
-```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-\elandscape
-
-A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
-Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
-
-<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
-
-<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
-
-(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
-
-```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Missing data
-
-```{r missing-data, echo = FALSE}
-```
-
-```{r azd-text, echo = FALSE}
-```
-
-Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
-
-&nbsp;
-
-### Primary analysis
-
-Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
-
-\blandscape
-
-<!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary
-
-(ref:followUp-scaption) followUp
-
-```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-\elandscape
-
-The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
-
-For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
-
-(ref:cprdPrimary-scap) Results from primary analyses of CPRD data
-
-```{r p1Figure, include = FALSE}
-```
-
-```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_p1.png"))
-```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
-
-__Alzheimer's disease__
-
-My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
-
-&nbsp;
-
-__Non-Alzheimer's disease dementias__
-
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
-Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
-
-&nbsp;
-
-__All-cause dementia__
-
-For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
-There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
-
-&nbsp;
-
-### Sensitivity analyses
-
-The results of the series of sensitivity analyses performed are described in the following sections.
-
-#### Complete case versus imputed data
-
-In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
-It should be noted that due to the large amount of missing data (e.g.
-`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
-In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
-
-(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
-
-```{r completeCase, include= FALSE}
-```
-
-```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_complete_case.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Control outcomes
-
-```{r controlOutcomesText, echo = FALSE, message = FALSE}
-```
-
-```{r controlOutcomes, echo = FALSE, message = FALSE}
-```
-
-Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
-The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
-
-For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
-However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:controlOutcomeFig-cap) Results of control outcome analysis.
-
-(ref:controlOutcomeFig-scap) Results of control outcome analysis
-
-```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_control_outcomes.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Impact of additional covariates
-
-The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
-
-These models were used to estimate the impact of adjustment for additional covariates.
-Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
-
-Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
-In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
-
-(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
-
-```{r unadjustedComparison, include=FALSE}
-```
-
-```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_unadjusted.png"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Sensitivity cohorts: Entry year
-
-When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).
-
-&nbsp;
-
-```{r cohortEntry, include=FALSE}
-```
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
-
-(ref:diagnosisTypeFig-scap) Sensitivty analus
-
-```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/forester_cohort_entry.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
-While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
-
-(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
-
-```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Sensitivity cohorts: Pregnancy
-
-In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
-
-(ref:pregnancyFig-scap) Comparison of pregnancy analysis
-
-```{r pregnancy, include = FALSE}
-```
-
-```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_pregnancy.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Statin properties
-
-In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
-Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
-
-(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
-
-```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
-Additionally, in the AD outcomes, hydrophilic statins were associated with a small reduction in risk, compared to the weak evidence for an effect for lipophilic statins.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
-
-(ref:statinTypeFig-scap) Analysis stratified by statin properties
-
-```{r statinType, include = FALSE}
-
-```
-
-```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
-knitr::include_graphics(file.path("figures","cprd-analysis","forester_sta_type.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Comparing codelists {#comparing-codelists}
-
-```{r smeethText, include = FALSE}
-```
-
-When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
-
-However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
-Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
-The joining lines showing the overlap between the categories in the two analyses.
-
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-```{r sankeydiagram, include=FALSE}
-```
-
-```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
-```
-<!----------------------------------------------------------------------------->
-
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
-
-&nbsp;
-
-<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
-
-<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
-
-## Discussion
-
-<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
-
-### Summary of findings
-
-Lipid-regulating agents showed little evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
-
-The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
-When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
-
-<!-- QUESTION Why are fibrates different? -->
-
-<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->
-
-<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
-
-<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
-However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
-
-### Interpretation of results
-
-<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
-
-This section will expand on a potential explanation for the observed results detailed above.
-However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
-
-A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
-While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
-
-<!----------------------------------------------------------------------------->
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
-
-(ref:indicationBias-scap) Confounding by indication causal diagram
-
-```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
-dagitty::dagitty("dag {
-  Statin [exposure,pos=\"0.000,0.000\"]
-  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
-  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
-  \"Uncontrolled variable\" -> Statin
-  \"Uncontrolled variable\" -> \"Vascular outcomes\"
-}") %>% ggdag_classic(size = 6) +
-  xlim(-0.5,3) +
-  geom_text(data = data.frame(x = 0.316392393234329,
-                              y = 0.537705383514239,
-                              label = "Prompts"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 1.65891420807966,
-                              y = 0.537705383514239,
-                              label = "Causes"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_curve(data = data.frame(x = 0.220612676359188,
-                               y = -0.000788829298738025,
-                               xend = 1.45,
-                               yend = -0.00157828084913909),
-             mapping = aes(x = x,
-                           y = y,
-                           xend = xend,
-                           yend = yend),
-             linetype = "dashed",
-             angle = 0L,
-             size = 0.6,
-             colour = "black",
-             curvature = 0,
-             arrow = structure(list(angle = 0,
-                                    length = structure(0,
-                                                       class = "unit",
-                                                       valid.unit = 2L,
-                                                       unit = "inches"),
-                                    ends = 2L,
-                                    type = 2L),
-                               class = "arrow"),
-             inherit.aes = FALSE,
-             show.legend = FALSE) +
-
-  theme_dag(),
-width = 8,
-height = 3)
-
-knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
-```
-<!----------------------------------------------------------------------------->
-
-In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
-
-Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
-The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
-This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
-
-A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
-
-Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-I also adjusted for several additional potential baseline variables.
-However, important confounding variables for which I have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
-
-On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
-It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
-
-<!-- IDEA talk about time-varying confounding here -->
-
-In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Strengths and limitations
-
-The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
-Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
-Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
-This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
-
-However, the findings of this analysis are subject to several limitations.
-There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
-As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
-
-Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
-This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
-
-<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
-
-<!-- IDEA there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
--->
-
-<!--------------------------------------------------------------------------->
-
-<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
-
-<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
-
-<!-- However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
--->
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
--->
-
-<!-- This hasn't been done! Plus I do not think this is the case -->
-
-<!--------------------------------------------------------------------------->
-
-<!--------------------------------------------------------------------------->
-<!-- &nbsp; -->
-
-<!-- IDEA Issues with large-scale EHR databases -->
-
-<!-- __Missclassification__ -->
-
-<!-- __Coding quality in the CPRD__ -->
-
-<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
-
-<!-- There is the possibility of ascertainment bias -  -->
-
-<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Enabling easy synthesis of this analysis {#cprd-data-avail}
-
-In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
-
-All code, Read codelists and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
-<!-- TODO Archive on Zenodo.
--->
-
-The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
-
-Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
-
-This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
-
-<!--------------------------------------------------------------------------->
-&nbsp;
-
-### Conclusions
-
-This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
-
-It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
-However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
-
-This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
-Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
-
-Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
-
-\newpage
-
-## References
-
-<!--chapter:end:04-Chp-CPRD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-# Individual participant data meta-analysis {#ipd-heading}
-\minitoc <!-- this will include a mini table of contents-->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/05-Code-IPD-Analysis.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-## Lay Summary
-
-As part of a broader investigation into the relationship between lipid levels and dementia risk, I sought to
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Introduction
-
-Is there a good way to visualise input of cohorts into an IPD analysis?
-
-Justify analysis based on findings of systematic review - suggestion of variation of effect by age, specifically
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Methods
-
-### Applying for data access
-
-__Systematic review__
-
-As part
-
-As part of the IPD analysis, relevant cohort studies identified through the systematic review detailed in Chapters \@ref(sys-rev-heading) were.
-In the first instance, the corresponding author on the main man
-
-__Dementia platform UK__
-
-In addition, to assess the results for  the Dementia Platform UK common-access procedure was utilised.
-In short, this approach is intended to make it easier to access data from exisiting dementia cohorts through a centralised application process.
-
-Talk about how different covariates were managed across cohorts,
-
-### Eligibility criteria
-
-Lipids reported/available as a continuous measure, and were not cross-sectional.
-
-Due to the limited time-frame, studies making use of population-level electronic health records, which often require an entire project proposal, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which we already had access to via the study reported in Chapter \'ref(cprd-heading).
-
-<!-- TODO Read this[@riley2020] -->
-
-### Missing data
-
-Talk about missing data were handled <!-- IDEA See Sean's thesis for some additional detail on this -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk of bias assessment
-
-Risk of bias assessment was performed for each of the included cohorts using the relevant tool described in Section \@ref(risk-of-bias).
-
-There is some concerns about performing risk of bias assessments on your own analysis, and so
-
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Analysis
-
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
-<!-- TODO Figure showing the outline of interval censored studies. -->
-
-All analysis were standardised by changes in 1-SD of the exposure variable. This was done to aid interpretability of the outcome.
-
-Similary,
-
-Clustering within studies was accounted for, given the evidence that ...[@abo-zaid2013]
-
-Stratified by age-at-entry and sex, and ethnicity where possible.
-
-Hazard ratios were utilised to
-
-In order to investigate the interaction of sex with
-
-A two-stage model was used out of necessity, with the one-stage model being precluded by the different datasets being in protected data silos.
-
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design o fthe longitudinal cohort studies.[@wang2017]
-
-In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
-These were extracted and synthesised using a random effects meta-analysis.
-
-Where results were comparably to previously published estimates, these were compared and reasons for any discrepancies discussed.
-
-The analysis were carried out in R (Version...) using the following packages: `survival`[@survival-book], `metafor`[@viechtbauer2010a]
-
-__Replicating published findings__
-
-Where any included data source had previously been analysed and results for the association between lipid levels and dementia reported, these were compared to the results of this analysis.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-## Results
-
-### Data access
-
-<!-- Need exact number from each approach, plus detailed exclusion reasons -->
-
-Of the XXX studies to which I applied for data access, only three were eventually included in the analysis.
-Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
-
-In addition, the reasons for cohorts not being included in the analysis are presented.
-In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked in the lab, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
-
-For the streamlined DPUK process, where a dedicated project manager liases with cohort owners, the overall response rate was higher, result in access to three cohorts. However, even using th
-
-<!----------------------------------------------------------------------------->
-```{r cohortFlowchartSetup, include = FALSE}
-```
-
-(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
-
-(ref:cohortFlowchart-scap) Flowchart
-
-```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
-knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few cohorts were included in both the DPUK and the systematic review sets of cohorts indicating that the DPUK.
-
-I did not request data from several DPUK cohorts due to the information on the online system indicating that the study was relatively new (and so was yet to collect >1 wave of data, as in the case of the XXXX cohort) or the online data dictionary indicating that the exposure variables of interest were not recorded.
-
-As highlighted in the
-
-### Included data sources
-
-The three datasets included are described in detail in the following section, and are summarised in Table \@ref(tab:cohortOverview-table).
-
-Of note, all data sources included in the analysis were based in the United Kingdom.
-This is likely due to the majority of included datasets coming from the Dementia Platform UK route \@ref(fig:cohortFlowchart), which as implied by the name, has a geographical focus on studies performed in Great Britain United Kingdom.
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:cohortOverview-caption) Summary of cohorts for which data were available
-
-(ref:cohortOverview-scaption) Summary of included cohorts
-
-```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!-- TODO Update table with SD for age, and check why number of events in EPIC is less than expected (5 vs 8)-->
-
-<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Caerphilly Prospective Study
-
-The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
-
-Cholesterol measures (total, LDL-c, HDL-c and triglycerides) were measured at baseline in 1979-1983. 
-As the study population has aged, additional outomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of congnitive tests were introduced.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### CPRD
-
-The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
-
-Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
-
-Additionally, ther number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
-
-the
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Epic Norfolk
-
-The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]
-
-Has only 8 events
-
-```{r tests, }
-
-```
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Whitehall II
-
-_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
-Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
-
-This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading).[@tynkkynen2018]
-
-This gave
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Cohorts provided data but ultimately excluded
-
-As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded.
-
-Several cohorts were excluded on the basis of a lack of exposure variables, including Cam-CAN (had cardiovascular category, but only contained blood pressure).
-
-The reasons for exclusion of these cohorts for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
-
-__BRACE__
-
-Likley had dementia at baseline
-
-__Memento__
-
-Excluded as criteria for entry was outpatients from memory clinic (unlikely to be dementia free at baseline)
-
-__Generation Scotland__
-
-Cross-sectional data only
-
-__NICOLA__
-
-NICOLA study - only had cross-sectional data
-
-__ELSA__
-
-Data provided but only had ever high cholesterol as a binary variable. Not compatible with
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:dataExcluded-caption) dataExcluded
-
-(ref:dataExcluded-scaption) dataExcluded
-
-```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Cohorts identified the systematic review but excluded from the IPD analysis
-
-<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
-
-Electronic health record co
-
-LBC - 1936
-
-Taiwan etc,
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Cohorts approach but received no answer
-
-A particularly frustrating in the case of cohorts which had a dedicated data access panel, for example, the Three City Study.
-Despite multiple attempts to contact the team, there was no response received.
-
-<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Data cleaning and harmonisation
-
-Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
-
-The one exception to this is the CPRD data, which was held in a different system to the rest.
-
-The advantage of this approach is that it reduces the liklihood of errors in model mis-speciication if needing to change variables names from cohort to cohort.
-
-For all cohorts, the first lipid measurement was used for the exposure method,
-
-For heterogeneity across the cohorts, the total time-at-risk was investigated.
-
-<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion
-
-Useful citation for discussion[@levis2021]
-
-### Limitations
-
-#### Low response rate to request for data
-
-<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
-
-This review had a low response rate to requests for data access.
-
-While this is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
-test
-There are likely several reasons for this.
-
-* Individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a]
-
-* While there is no
-
-For many other reasons also - if
-
-A potential further reason was highlighted during my attendance at the
-
-Letters sent to all cohorts identified through the systematic review 
-<!-- TODO will need quite a bit here on the numbers approached and how they responded if at all. Will also need to comment on the additional tactics used.  -->
-
-This is likely due to my junior position as a early career research combined with the impact
-
-Range of reasons why data is not readily available.
-Privacy concerns, concerns around scoping or "parasitic" behaviour, and a lack of trust (i.e.
-primary researchers do not trust secondary researchers).<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
-
-Unfortunately,
-
-The low response rate and the
-
-Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
-
-<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
-The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
-Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
-However, analysis combining individual and study level data may mitigate these effects [3, 21].
-from [@ventresca2020a] -->
-
-For the purposes of this thesis, conducting the IPD was useful as it afforded me the opportunity to experience the methodology.
-
-On a personal level, given the
-
-In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Resources
-
-While it was disappointing that such a small proportion of the available data were obtained for analysis, in terms of project completion, it is probably a good thing.
-
-Given the resource intensity of data cleaning and harmonisation,
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Data access
-
-Couple of sections
-
-* Problems with getting data from studies
-*
-
-Sharing data has several legal, ethical and logistical challenges, and can often
-
-This is in theory what the DPUK was built to address. However, despite claims to a streamlined process, the response rate amond cohorts participating
-
-Describe your experience of trying to access the DPUK - while a great resources, frustrating at times. The portal would benefit from a centralised management system and
-
-Even with the guaranteed data access afforded by the DPUK, accessing sufficient data were
-
-Of the XXX cohorts requested from the DPUK, allowing for a year lag since application, a response was received from only XXX (XXX%), while of those responding a minority
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Study within a review
-
-In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data.
-
-Options could include
-
-Previous SWARs have been registered as protocols, but have not yet reported!
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Reflections on the process
-
-May have been overly ambitious
-
-\newpage
-
-## References
-
-<!--chapter:end:05-Chp-IPD-Analysis.Rmd-->
-
----
-#########################################
-# options for knitting a single chapter #
-#########################################
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: default
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
-```
-(ref:intro-quote) --- Hold
-
-<!-- TODO Add this to the Chapter summary in the introduction and  -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-<!-- ### Triangulation across evidence sources -->
-
-<!-- TODO Have a look at this - potentially move to triangulation chapter -->
-
-<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
-
-<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
-Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
-For example, if the propensity to treatment is related to comorbidity burden, but those on treatment still have better outcomes then those on control, it is likely that the true effect of the intervention is being underestimated.
-[@guyatt2011] -->
-
-<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
--->
-
-# Triangulation {#tri-heading}
-
-## Lay Summary
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Introduction
-
-This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)
-
-### Data sources
-
-This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Background to the causal question
-
-Following best practice guidance, three
-
-Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
-
-This was also guideded by the forthcoming ROBINS-E tool, which has
-
-<!----------------------------------------------------------------------------->
-
-### Definition of the causal question
-
-<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
-
-### Summary of triangulation
-
-Need to check how much I talk about this in the introduction
-
-Describe in detail
-
-### Risk of bias tool
-
-In addition, the tool also aim to capture the potential direction of bias for each result.
-Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
-Highlight that this is slightly different for the confounding domain in non-randomised studies.
-
-These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Graphical representation
-
-For the graphs, the direction of bias is important.
-
-Where the direction of bias was unclear/could not be determined from the report, this is indicated
-
-In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
-The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
-
-Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
-Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
-non-differential misclassification).
-In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
-For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
-In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
-If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
-
-These graphs were built using the risk of bias tool described in Appendix \ref()
-
-<!-- TODO Does immortal time bias not also have a consistent effect -->
-
-<!----------------------------------------------------------------------------->
-
-### Standardisation across study designs
-
-Standardising across different measures of ex
-
-Want best information across lipids, and so standardised across differnt measures
-
-Fixing directions of effect - get everything pointing the same way
-
-<!----------------------------------------------------------------------------->
-### Analyses
-
-Bias-adjusted meta-analysis [@higgins2008a]
-
-<!----------------------------------------------------------------------------->
-
-## Results
-
-Summary of risk-of-bias/triangulation results
-
-Percentage of domains for which a direction of bias could be assigned?
-
-Compare bias-adjusted and
-
-See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
-
-Applicability/indirectness as an issue 
-Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
-
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
-
-### Challenges of real-life data
-
-Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-ALso highlight the issue with assigning a direct of bias in many studies
-
-### Need for new methods
-
-Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
-
-<!--chapter:end:06-Chp-Triangulation.Rmd-->
-
 ---
@@
 
-<!----------------------------------------------------------------------------->
-## Triangulation across exisiting evidence and evidence produced in this thesis
+<!-- ## Additional topics for the discussion -->
 
-### Overview of triangulation {#triangulation-overview}
+<!-- There are several addition topics I would like to cover: -->
 
-Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
-
-Summary table of different studies and results
+<!-- * The difference between the peer review of the software vs.
+the peer review of papers.
+A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
+Essentially, a more transparent and open -->
 
@@
 
-## Qualitative vs qunatitative triangulation
+## Summary of findings (by chapter)
 
-### Researcher positionality statement
+### Systematic review
+#### Principal findings
+#### Comparison with existing literature
+#### Strenghts and limitations
+#### Implications of this research
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+### CPRD
+#### Principal findings
+#### Comparison with existing literature
+#### Strenghts and limitations
+#### Implications of this research
 
-## Discussion of E-values
+### Individual participant data meta-analysis
+#### Principal findings
+#### Comparison with existing literature
+#### Strenghts and limitations
+#### Implications of this research
 
-How strong unmeasured confounding would have to be in order to explain the observed effect.
+### Triangulation
+#### Principal findings
+#### Comparison with existing literature
+#### Strenghts and limitations
+#### Implications of this research
 
-Heavily criticised in a range of papers.
+## Overall strengths and limitations
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+## Implications 
+### Clinical practice
+### Future research
 
-## Use of concensus panel to bring everything together
+## Conclusions
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
-## Additional topics for the discussion
-
-There are several addition topics I would like to cover:
-
-* The difference between the peer review of the software vs.
-the peer review of papers.
-A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
-Essentially, a more transparent and open
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Summary of findings (and implications for policy makers)
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Strengths and Limitations
+### Strengths and Limitations
 
@@
 
+Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here.
+-->
+
 &nbsp;
@@
 ## Overall conclusions
-
-<!--chapter:end:07-Discussion.Rmd-->
-
----
-bibliography: bibliography/references.bib
-csl: bibliography/nature.csl
-output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-  bookdown::word_document2: 
-      toc: false
-      toc_depth: 3
-      reference_docx: templates/word-styles-reference-01.docx
-      number_sections: false 
-  bookdown::html_document2: default
-documentclass: book
----
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
-source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!--chapter:end:tmp.Rmd-->
-
-`r if(!knitr:::is_latex_output()) '# Bibliography {-}'`
-
-<!-- If you're outputting to LaTeX, the heading and references will be generated by the OxThesis LaTeX template.
-This .Rmd file serves only to add the References headline to gitbook output before the references are added by pandoc -->
-
-```{block type='savequote', include=knitr::is_latex_output(), echo = TRUE}
-Lasciate ogne speranza, voi ch'intrate. . .
-```
-
-# Bibliography
-
-<div id="refs"></div>
-
-<!--chapter:end:front-and-back-matter/98-references.Rmd-->
-
-`r if(knitr:::is_latex_output()) '\\startappendices'`
-
-`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
-
-<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
-
-```{r, echo = FALSE, warning=FALSE, message=FALSE}
-knitr::read_chunk(here::here("R/appendix.R"))
-doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
-```
-
-<!----------------------------------------------------------------------------->
-# By Chapter {#chapter-appendix-heading}
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(background-heading) {#appendix-into}
-
-<!----------------------------------------------------------------------------->
-### Publications beyond the scope of this thesis {#appendix-publications}
-
-__Peer reviewed__
-
-  * PRISMA main paper
-
-  * PRISMA E&E
-
-  * PRISMA 2020 software
-
-  * COVID Suicide Living Review
-
-  * Data extraction tools systematic review
-
-<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->
-
-__Under review/Preprints__
-
-  * MSc Paper on systematic reviews of this thesis topic
-
-  *
-
-<!----------------------------------------------------------------------------->
-
-### Involvement of patients and the public {#appendix-ppi}
-
-Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.
-
-Additionally,
-
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
-
-<!----------------------------------------------------------------------------->
-
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
-<!----------------------------------------------------------------------------->
-
-### Code for publication rate analysis
-
-```{r, eval=FALSE}
-med_res <-
-  # Use snapshot of published status from July 2021
-  medrxivr::mx_search(
-    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
-    query = "*",
-    from_date = "2019-07-01",
-    to_date = "2019-08-01"
-  ) %>%
-  # Create indicator to show which records have been published
-  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
-  # Group by indicator variable and count
-  group_by(pub_ind) %>%
-  count()
-
-```
-
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
-<!----------------------------------------------------------------------------->
-
-### Search strategy {#appendix-search-strategy}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchHits-caption) Overview of the full Medline search strategy.
-
-(ref:searchHits-scaption) searchHits
-
-```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
-```
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Web of Science Databases Searched {#appendix-wos-databases}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:wosDatabases-caption) Summary of Web of Science databases searched.
-
-(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
-
-```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
-
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-### Code to search preprints {#appendix-medrxivr-code}
-
-<!-- TODO Double check this is the final code used -->
-
-```{r, eval = FALSE}
-
-library(medrxivr)
-
-mx_data <- mx_api_content(to_date = "2019-09-01")
-
-bx_data <- mx_api_content(server = "biorxiv",
-                                    to_date = "2019-09-01")
-
-topic1 <- c(mx_caps("statin"),
-            mx_caps("ldl"),
-            mx_caps("hdl"),
-            mx_caps("TG"),
-            mx_caps("triglycer"),
-            paste0("\\b",mx_caps("TC"),"\\b"),
-            mx_caps("ezetim"),
-            mx_caps("fibrate"),
-            mx_caps("bile acid"),
-            mx_caps("lipoprotein"),
-            mx_caps("lipid"),
-            mx_caps("cholesterol"))
-
-topic2 <- c(mx_caps("dementia"),
-            mx_caps("alzheim"),
-            mx_caps("MCI"),
-            mx_caps("mild cognitive"))
-
-query <- list(
-  topic1,
-  topic2
-)
-
-bx_results <- mx_search(bx_data, query)
-
-mx_results <- mx_search(mx_data, query)
-
-```
-
-Note
-
-<!----------------------------------------------------------------------------->
-### MR risk of bias tool {#appendix-mr-rob}
-
-<!----------------------------------------------------------------------------->
-(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
-
-(ref:mrTool-scaption) Mendelian randomisation risk-of-bias assessment tool
-
-```{r mrTool-table, message=FALSE, results="asis", echo = FALSE}
-
-mrTool_table <- read.csv(here::here("data/sys-rev/mrRobTool.csv")) %>%
-  select(1:5) %>%
-  rename("Bias domain" = Bias.domain)
-
-if(doc_type == "docx") {
-  knitr::kable(mrTool_table, caption = "(ref:mrTool-caption)")
-} else{
-  knitr::kable(
-    mrTool_table,
-    format = "latex",
-    caption = "(ref:mrTool-caption)",
-    caption.short = "(ref:mrTool-scaption)",
-    longtable = TRUE,
-    booktabs = TRUE
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    column_spec(column = 1:5, width = paste0(32/5,"em")) %>%
-    row_spec(2:nrow(mrTool_table)-1, hline_after = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position","repeat_header"))
-}
-
-```
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-<!----------------------------------------------------------------------------->
-### Amendments to protocol {#appendix-cprd-amendments}
-
-<!----------------------------------------------------------------------------->
-### Code lists
-
-## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
-<!----------------------------------------------------------------------------->
-### Section 1
-
-<!----------------------------------------------------------------------------->
-### Section 2
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(discussion-heading)
-
-<!----------------------------------------------------------------------------->
-### Catalogue of failures
-
-Short section detailing the things I tried to do but which did not work.
-
-<!----------------------------------------------------------------------------->
-# Other Appendix {#other-appendix-heading}
-
-## Software used to create this thesis
-
-```{r, include = FALSE}
-knitr::write_bib(c(.packages(), "bookdown", "knitr"), here::here("bibliography/packages.bib"))
-```
-
-This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
-All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
-
-<!----------------------------------------------------------------------------->
-## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
-
-### Introduction
-
-Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
-A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
-
-Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
-Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
-Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
-For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.
-
-Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
-Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
-
-The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).
-
-### Development
-
-Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
-Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback.
-This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
-The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]
-
-### Installation
-
-A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:
-
-```{r, eval = FALSE}
-install.packages("robvis")
-```
-
-As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version.
-The most recent development version can be install from GitHub using:
-
-```{r, eval = FALSE}
-devtools::install_github("mcguinlu/robvis")
-```
-
-### Usage
-
-`robvis` contains two main functions.
-The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
-The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.
-
-A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
-A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)
-
-Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
-
-<!-- TODO __NEED TO ADD DATA HERE!__ -->
-
-```{r, eval = FALSE}
-
-rob_traffic_light(data = data_rob2,
-                  tool = "ROB2",
-                  psize = 15)
-```
-
-```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
-
-plotdata <- robvis::data_rob2
-
-tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)
-
-robvis::rob_save(tfplot, 
-                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
-```
-
-Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
-
-```{r, eval = FALSE}
-
-rob_summary(data = data_rob2,
-            tool = "ROB2", 
-            overall = TRUE)
-
-```
-
-```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
-
-sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)
-
-robvis::rob_save(sumplot,
-                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-```
-
-A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)
-
-`r br`
-
-```{r robvisarguments, echo = FALSE, eval = TRUE}
-
-arguments <- data.frame(stringsAsFactors=FALSE,
-              argument = c("data", "tool", "colour", "overall", "weighted",
-                           "psize"),
-     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
-           rob_summary = c("X", "X", "X", "X", "X", ""),
-           Description = c(
-"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
-"Defines the risk of bias assessment tool used.
-The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
-Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
-"Defines the colour scheme for the plot.
-The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`).
-Alternatively, users can specify their own colour scheme e.g.
-`colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
-"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
-"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
-"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
-
-if(doc.type == "docx"){
-
-  knitr::kable(arguments,escape = T,
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))
-
-}else{
-
-  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-             align = c("l","c","c","l"),
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
-  column_spec(4,"5cm") %>%
-  kable_styling(font_size = 9, 
-                bootstrap_options = c("striped", "hover"),
-                latex_options = c("repeat_header", "striped"))
-}
-
-```
-
-`r br`
-
-### Reception and Future Plans
-
-```{r, echo = FALSE}
-robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
-
-robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-
-```
-
-As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times.
-It has been well received but the systematic review community, and has been cited frequently in the published literature.
-A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods.
-A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]
-
-While `robvis` is a stable package, a range of additional functionality could be added.
-At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
-However, following user-driven demand, this functionality is in development and will be available in the near future.
-Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
-The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
-
-## Creating
-
-## Copies of papers arising from this thesis {#published-papers}
-
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
-
-<!--chapter:end:front-and-back-matter/99-appendices.Rmd-->

### 2021-10-08 R/helper.R
General updates

@@ -836,7 +836,10 @@ get_words <- function() {
   files <- list.files(path = here::here(), pattern = "\\.Rmd$")
   
   files <-
-    files[which(!(files %in% c("_main.Rmd", "index.Rmd", "tmp.Rmd")))]
+    files[which(!(files %in% c("_main.Rmd",
+                               "index.Rmd",
+                               "tmp.Rmd",
+                               "04-Chp-Systematic-Review-Results.Rmd")))]
   
   words_v <- c()
   

### 2021-10-08 01-Chp-Background.Rmd
Working version
End of day:

@@
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
 source("R/helper.R")
@@
 ## Lay summary
-
-[Note: see Section \@ref(thesis-structure) for details on the layout of each chapter.]
 
@@
 <!----------------------------------------------------------------------------->
-### Basic science
+### Basic science {#intro-basic-science}
 
@@
 <!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(discussion-heading).
+(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(tri-heading).
 Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.

### 2021-10-08 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 ```{r setup, include=FALSE}
-source("R/doc_options.R")
 source("R/helper.R")
@@
 
+<!-- TODO Need to finish this bit and move it to the use-case section! -->
+
 Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).

### 2021-10-08 03-Chp-Systematic-Review-Methods.Rmd
Creat final thesis structure
End of day:

--- 2021-10-07 03-Chp-Systematic-Review.Rmd
@@
 
-# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}
+# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-methods-heading}
 

### 2021-10-08 05-Chp-CPRD-Analysis.Rmd
End of day:

--- 2021-04-26 05-Chp-CPRD-Analysis.Rmd
@@
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
 source("R/helper.R")
-knitr::read_chunk("R/Chp3-CPRD-Analysis.R")
+knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
@@
 
-## Additional ideas
+```{r load-files, echo = FALSE}
+```
 
-One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+<!-- ## Additional ideas -->
 
-Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?)
+<!-- TODO Need to add some information on the generation and use of propensity scores -->
 
-__Things we tried__
+<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
+-->
 
-- Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
+<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
+
+<!-- __Things we tried__ -->
+
+<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
 Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
 Need total number of those starting and average time to start.
-- Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper.
-- Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results
-- Allowing for time-varying confounders for binary covariates.
+-->
+<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
+<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
+<!-- - Allowing for time-varying confounders for binary covariates. -->
 
-__Things we could try__
+<!-- __Things we could try__ -->
 
-- Work through data using positive control to see if the way it is being added is what is causing the issues.
-- Examine Cramer et al. thesis and see what they did
-- Marginal structural models approach (a la J. Sterne)
+<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
+<!-- - Examine Cramer et al. thesis and see what they did -->
+<!-- - Marginal structural models approach (a la J. Sterne) -->
 
-<!----------------------------------------------------------------------------->
+<!--------------------------------------------------------------------------->
+
+<!-- TODO Check lipid-regulating vs lipid regulating -->
+
+<!-- TODO Check all fig/table cross-references evaluate -->
 
 ## Lay summary
-Large scale database such as this are often called population level, and studies that make use of them have a number of advantages.
 
-This analysis uses one of these databases, the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of XXXXXX people from YYYYYY general practices across England.
+Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
+Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
+These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
+This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
 
-Using this data, I have analysed the ...
+This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
+Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
 
-<!----------------------------------------------------------------------------->
+Little evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
+In contrast, I found an increased risk of vascular and other (i.e.
+non-Alzheimer's) dementia with lipid regulating agent use.
+
+This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
+This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
+However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
+
+<!--------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-Lack of evidence for the association of statins on vascular dementia risk
+In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
 
-Large scale databases advantages over other means
+The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
 
-Cross reference here aswell re: the lack of information on Vascular dementia and the need for analyses at different sources of bias.
+Firstly, it explicitly examines vascular dementia as an outcome.
+The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
+As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
 
-<!----------------------------------------------------------------------------->
+Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
+Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
+This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
+
+<!--------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-### Data source {#cprd-data-source}
+### Study protocol
 
-The Clinical Practice Research Datalink (CPRD) is a large, population-based, electronic health record database.[@herrett2015] It contains the primary care records for
+An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
 
-Originally termed the GPRD (General Practice Research Database),
+<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
 
-The
+<!-- TODO Add amendments to Appendix -->
 
-Data completeness and collection of certain disease are heavily influenced by exercises that reward doctors for capturing certain diagnoses, such as the Quality and Outcomes Framework.
-However, these drives can oftern have unintended consequences [@liu2019]
-
-The CPRD uses a coding system called Read code <!--- check capitalisation --->
-
-### Study design and protocol
-
-We performed a prospective cohort study using data from the CPRD.
-Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
-
-An *a priori* protocol for this study was published, [@walker2016a] and amendments to this are recorded in Supplementary Materials 1.
-This study was reported in line with the STROBE Cohort guidelines (Supplementary Table 3).[@vonelm2008]
-
-<!-- Note: If protocol was written by Venexia, how do I reference this? -->
+<!--------------------------------------------------------------------------->
 
@@
 
-### Study cohort
+### Data source {#cprd-data-source}
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
+Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
-These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
-This approach was employed in an attempt to reduce confounding by indication that we would expect to observe in the full cohort, because individuals not prescribed lipid-regulating agents likely be less healthy across a range of variables than those prescribed lipid-regulating agents, leading to a biased association been lipid-regulating agent use and dementia.
-Conditioning entry into the study into the study on being either “at-risk” or already diagnosed with hypercholesterolemia attempts to mitigate this bias.
+To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
+The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
+Eu...
+- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
+Eu001 - Dementia in Alzheimer's disease with late onset).
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
+Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
+
+(ref:readExample-scaption) Example of CPRD Read code hierarchy
+
+```{r readExample-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!--------------------------------------------------------------------------->
+
+&nbsp;
+
+Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
+
+&nbsp;
+
+### Cohort definition
+
+This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
+Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
+However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
+
+Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
+These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
+
+All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
 
 The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+had less than one full day of follow-up).
+
+<!--------------------------------------------------------------------------->
 
@@
 
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF)[@wishart2017], namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
+We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
 
 A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class was stopped (defined as last prescription of the primary class being followed by at least six months of observation), added to (defined as a second drug class being prescribed before the last prescription of the initial class), or switched (defined as a second drug class being prescribed after the last prescription of the initial class).
+We did however examine how often the initial drug class altered according to one of three criteria:
+
+- __stopped__: defined as the last prescription of the primary class being followed by at least six months of observation; 
+- __added__: defined as a second drug class being prescribed before the last prescription of the initial class; and 
+- __switched__: defined as a second drug class being prescribed after the last prescription of the initial class.
+
+<!--------------------------------------------------------------------------->
 
@@
 
-### Outcomes
+### Outcomes {#cprd-outcomes}
 
-<!--- Include short bit on follow-up here, describing how and why it was defined --->
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
+When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
+The diagnosis date of the outcome was determined by the first record of a relevant code.
 
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome (Supplementary Figure 1).
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1).
-The diagnosis date of the outcome was determined by the first record of a relevant code.
+<!----------------------------------------------------------------------------->
+(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
+Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
+
+(ref:decisionTreeFig-scap) Decision tree for assigning dementia subtypes
+
+```{r decisionTree, include = FALSE}
+```
+
+```{r decisionTreeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:decisionTreeFig-cap)', out.width='100%', fig.scap='(ref:decisionTreeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","decision_tree.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
 
@@
 
-A range of additional variables were included in the analysis, intended to address differential distributions of potnetial confounding variables between those who had a
+A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
 
-<!--- Need a lot more here - see other thesis for example of how covariates are described --->
+Demographic covariates adjusted for included age and gender.
+Age was calculated at date of entry into the cohort.
+Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
+To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
+Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
 
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010),
+Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
+A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
+To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
 
-Charlson co-morbidity index,
+Finally, presence of a range of related conditions at baseline were accounted for, including cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
+The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
 
-Index of Multiple Deprivation (IMD),
+Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
 
-consultation rate,
+&nbsp;
 
-alcohol (current, former,  never),
-
-smoking (current, former,  never),
-
-BMI,
-
-baseline total cholesterol,
-
-and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-
-All covariates were determined at index and definitions for each can be found in Supplementary Table 1.
+<!--------------------------------------------------------------------------->
 
@@
 
-Missing data was handled using a multiple imputation approach. Variables with missing observations were identified, and
+Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
 
-Binary variables were modelled using a
+<!-- IDEA Add more detail here on the missing data approach -->
 
-continuo
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
 
-As per best practice, all other variables, including the out
+Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
+BMI), or where a code existed for the absence of the condition (e.g.
+categorical smoking status).
+This approach was necessary, as absence of a code for other treatments or conditions (e.g.
+statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
 
-The MICE command in Stata was used
-
-### Time axis
-
-In Cox models, there is the option to
-
-Age vs time-since entry
-
-Expand on use of age as the time scale, but describe the problems this introduced
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
 
 &nbsp;
+<!--------------------------------------------------------------------------->
 
@@
 
-Potential biases included time varying confounding, selection bias due to censoring on death and 
-We use a Cox proportional hazards model with a time-varying treatment indicator.
+A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
 
-Expand on post estimation analyses, which showed that nothing except age had an effect.
-
-$$h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)$$
+\begin{equation}
+  h(t) = h_o(t) \times exp(b_1x_1 + b_2x_2 + ... +b_px_p)
+  (\#eq:cox-model)
+\end{equation}
 
@@
 
-__Bit on why Cox models are slightly different from others, due to proportional hazards assumptions__
+A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
+Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
+This is discussed in detail in the following section.
 
-Hazard rations are
+<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
 
-Test for non-proportionality are therefore very important, as models which fail
-
-Problems with testing for non-proportional hazards when
+<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
 
 <!----------------------------------------------------------------------------->
-(ref:cprd-dag-1-cap) __Directed acyclic graph showing assumed relationship between exposure and covariate:__
+&nbsp;
 
-(ref:cprd-dag-1-scap) Directed acyclic graph showing assumed relationship between exposure and covariate
+### Immortal time bias and time-varying treatment indicators {#cprd-immortal-time-bias}
 
-```{r cprd-dag-1, echo = FALSE, results="asis", fig.cap='(ref:cprd-dag-1-cap)', out.width='100%', fig.scap='(ref:cprd-dag-1-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prisma_flow.png"))
+Immortal time bias covers two distinct but related types of bias.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
+
+The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
+It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
+This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
+
+This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
+To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
+
+Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
+Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
+they enter the cohort and move into the exposed group on the same day).
+
+<!--------------------------------------------------------------------------->
+(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
+
+(ref:immortalTimeBias-scap) shortcap
+
+```{r, immortalTime, include = FALSE}
+```
+
+```{r immortalTimeBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:immortalTimeBias-cap)', out.width='100%', fig.scap='(ref:immortalTimeBias-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","immortal_time.png"))
+```
+<!--------------------------------------------------------------------------->
+
+### Time axis
+
+<!-- IDEA Finish paragraph from fragments below -->
+
+<!-- In Cox models, there is the option to -->
+
+<!-- Age vs time-since entry -->
+
+<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
+
+As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
+As such, the main analyses presented all used age as the time axis.
+
+<!-- TODO Will need to expand on choice of time axis here -->
+
+<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
+-->
+
+&nbsp;
+<!--------------------------------------------------------------------------->
+
+### Sensitivity analyses
+
+The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
+To assess the robustness of the results, a number of sensitivity analyses were performed.
+These are described in the following sections.
+
+#### Control outcomes
+
+In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
+The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
+Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
+
+Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
+Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
+
+Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
+Muscular backpain was chosen as a negative control outcome in this analysis.
+Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
+As such, if statins are not associated with backpain in this analysis, then confidence in the results for the dementia outcomes is increased.
+
+Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
+
+<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
+
+<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->
+
+<!----------------------------------------------------------------------------->
+(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
+Note the absence of any arrow between $X$ and $N$.
+In this scenario, any association observed between $X$ and $N$ is due to the presence of uncontrolled confounders $U$ (assuming $C$ has been adjusted for).
+
+(ref:negativeOutcome-scap) DAG of ideal negative outcome
+
+```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
+library(dagitty)
+library(ggdag)
+
+ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
+  dagitty::dagitty("dag {
+    U -> N
+    C -> N
+    X <- U -> Y
+    X <- C -> Y
+    X -> Y
+    bb =\"-2.368,-2.972,2.597,2.726\"
+    C [pos=\"-0.3,0\"]
+    N [pos=\"0.5,1\"]
+    U [pos=\"-0.15,1.5\"]
+    X [exposure,pos=\"0,-1\"]
+    Y [outcome,pos=\"0.5,-1\"]
+  }"
+) %>% ggdag_classic() +
+  theme_dag()
+
+,
+height = 3
+)
+
+knitr::include_graphics(file.path("figures","cprd-analysis","negativeOutcome.png"))
+
 ```
@@
 
-### Immortal time bias and time-varying treatment indicators
+#### Impact of additional covariates
 
-Immortal time bias is a type of misclassification bias. It occurs when
+To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
 
-One potential way to address this is the use of a time-varying treatment indicator, a factor which modi
+&nbsp;
 
-In the case of this analysis, this treatment indicator is statin use. Using codes for statins (see Appendix \@ref())
+#### Sensitivity cohorts
+
+Two sensitivity cohorts were also created.
+The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
+The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
+
+<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
+
+&nbsp;
+
+#### Statin properties
+
+<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
+
+As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
+
+To explore whether any observed associations in the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
+
+<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
+
+&nbsp;
+
+#### Impact of dementia code lists
+
+As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
+
+This previous study used a propensity matching approach to estimate the association of statins with a range of outcomes, and found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+
+The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
+
+&nbsp;
+
+## Results
+
+### Patient characteristics
+
+```{r characteristics, echo = FALSE}
+```
+
+```{r attritionFigure, include = FALSE}
+```
+
+Of the `r comma(attrition[1,1])` participants included in the extract, `r comma(attrition[14,1])` met the inclusion criteria (Figure \@ref(fig:cprdFlowchart)), with a total follow-up of `r comma(total_followup)` patient years at risk.
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
+
+(ref:cprdFlowchart-scap) Attrition of CPRD participants
+
+<!-- This figure needs to have comma seperated numbers in order to agree with text. -->
+
+```{r cprdFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdFlowchart-cap)', out.width='100%', fig.scap='(ref:cprdFlowchart-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","cohort_attrition.png"))
+```
+<!--------------------------------------------------------------------------->
+
+&nbsp;
+
+The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia: Table \@ref(tab:followUp-table)).
+The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+
+\blandscape
+<!--------------------------------------------------------------------------->
+(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
+
+(ref:cprdCharacteristics-scaption) Patient characteristics by drug class
+
+```{r cprdCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!--------------------------------------------------------------------------->
+\elandscape
+
+A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
+I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
+Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
+
+<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
+
+<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
+
+(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
+
+```{r cprdSSA-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!--------------------------------------------------------------------------->
+
+&nbsp;
+
+The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+
+### Missing data
+
+```{r missing-data, echo = FALSE}
+```
+
+```{r azd-text, echo = FALSE}
+```
+
+Full covariate information was available for `r missingtext`.
+Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
+
+&nbsp;
+
+### Primary analysis
+
+Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
+
+\blandscape
 
 <!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary
 
-### Estimating the value of the time-varying confounders
+(ref:followUp-scaption) followUp
 
-Mean time from index event to first prescription of statins was 2.4 years.
-This negates the promised benefit of ruling out confounding by indication (where the test result leads to the prescription of the treatment and also increases the risk of the outcome, distorting the relationship between the two), as there is no relationship between index TC/LDL-c and eventual LRA prescription.
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
 
-Additionally, the time between index event and prescription does lead to a problem in terms of time varying confounding, as an average time of 2.4 years between current measurement of the covariates and treatment switching means there is plenty of time for the value of the covariate to change.
-This is problematic when the decision to change treatments (in this case to move from no LRA use to LRA use) is influenced by a set of prognostic factors that in turn may have been influenced by the initial treatment decision, as is likely to be the case for a range of covariates included in the model.
-For example:
+\elandscape
 
-    _No CVD (t=0) -> No LRA (t=0) -> CVD (t=1) -> LRA (t=1) -> Dementia (t=2)_
+The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
 
-In this case, the decision to move to LRA use is influenced by CVD status at _Time 1_, which will not be captured by adjusting only for CVD status at _Time 0_.
+For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
 
-In practice, this means that the value of the prognostic factor should be regularly captured
+&nbsp;
 
-However, in electronic health records, a change in the value of the prongostic factors is only important if it is recorded in a patients record, as for it to have an impact on treatment decisions, it must be recorded.
+<!--------------------------------------------------------------------------->
+(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
 
-This means we can find the most recent value of the covariate before the switch and apply a marginal structural model approach, filling all values for that variable before the most recent measure with the baseline measurement, and all after the most recent meausure with the value of the most recent measure (on the basis that you won't go from having CVD back to not having CVD).
+(ref:cprdPrimary-scap) Results from primary analyses of CPRD data
 
-i.e.  
-Timepoint 12345678  
-CVD       00001111  
-Treatment 00000111
+```{r p1Figure, include = FALSE}
+```
 
-Split into 3 month blocks since index event and use the same approach as above to work out the values of each covariate at each time point.
+```{r cprdPrimary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdPrimary-cap)', out.width='100%', fig.scap='(ref:cprdPrimary-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_p1.png"))
+```
+<!--------------------------------------------------------------------------->
 
-Note: this will be harder for things that are not dichotomous and can go up as well as down. Examples include total cholesterol and BMI, which can go up as well as down.
+&nbsp;
+
+<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
+
+__Alzheimer's disease__
+
+My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+
+&nbsp;
+
+__Non-Alzheimer's disease dementias__
+
+In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
+Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+
+&nbsp;
+
+__All-cause dementia__
+
+For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
+
+&nbsp;
+
+### Sensitivity analyses
+
+The results of the series of sensitivity analyses performed are described in the following sections.
+
+#### Complete case versus imputed data
+
+In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
+It should be noted that due to the large amount of missing data (e.g.
+`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
+In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]
+
+&nbsp;
 
 <!----------------------------------------------------------------------------->
+(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
 
-### The effect of total cholesterol or LDL-cholesterol on LRA prescription
+(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
 
-It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.
+```{r completeCase, include= FALSE}
+```
 
-However, this is not the case.
+```{r completeCaseFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:completeCaseFig-cap)', out.width='100%', fig.scap='(ref:completeCaseFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_complete_case.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Control outcomes
+
+```{r controlOutcomesText, echo = FALSE, message = FALSE}
+```
+
+```{r controlOutcomes, echo = FALSE, message = FALSE}
+```
+
+Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
+The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
+
+For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
+However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:controlOutcomeFig-cap) Results of control outcome analysis.
+
+(ref:controlOutcomeFig-scap) Results of control outcome analysis
+
+```{r controlOutcomeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:controlOutcomeFig-cap)', out.width='100%', fig.scap='(ref:controlOutcomeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_control_outcomes.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Impact of additional covariates
+
+The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
+
+These models were used to estimate the impact of adjustment for additional covariates.
+Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
+
+Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
+In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
+
+(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
+
+```{r unadjustedComparison, include=FALSE}
+```
+
+```{r unadjustedComparisonFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:unadjustedComparisonFig-cap)', out.width='100%', fig.scap='(ref:unadjustedComparisonFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_unadjusted.png"))
+```
+<!----------------------------------------------------------------------------->
+
+#### Sensitivity cohorts: Entry year
+
+When stratifying based on year of entry to the cohort, I observed no variation in risk by time period in any subgroup except for probable Alzheimer’s disease (Figure \@ref(fig:diagnosisTypeFig)).
+
+&nbsp;
+
+```{r cohortEntry, include=FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
+
+(ref:diagnosisTypeFig-scap) Sensitivty analus
+
+```{r diagnosisTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:diagnosisTypeFig-cap)', out.width='100%', fig.scap='(ref:diagnosisTypeFig-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/forester_cohort_entry.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
+While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
+
+(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
+
+```{r diagnosisType-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Sensitivity cohorts: Pregnancy
+
+In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
+
+(ref:pregnancyFig-scap) Comparison of pregnancy analysis
+
+```{r pregnancy, include = FALSE}
+```
+
+```{r pregnancyFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:pregnancyFig-cap)', out.width='100%', fig.scap='(ref:pregnancyFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_pregnancy.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Statin properties
+
+In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
+Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
+
+(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
+
+```{r statinTypeTable-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
+Additionally, in the AD outcomes, hydrophilic statins were associated with a small reduction in risk, compared to the weak evidence for an effect for lipophilic statins.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
+
+(ref:statinTypeFig-scap) Analysis stratified by statin properties
+
+```{r statinType, include = FALSE}
+
+```
+
+```{r statinTypeFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinTypeFig-cap)', out.width='100%', fig.scap='(ref:statinTypeFig-scap)'}
+knitr::include_graphics(file.path("figures","cprd-analysis","forester_sta_type.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Comparing codelists {#comparing-codelists}
+
+```{r smeethText, include = FALSE}
+```
+
+When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
+
+However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
+While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
+Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
+The joining lines showing the overlap between the categories in the two analyses.
+
+(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
+
+```{r sankeydiagram, include=FALSE}
+```
+
+```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
+```
+<!----------------------------------------------------------------------------->
+
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
+
+&nbsp;
+
+<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
+
+<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
+
+## Discussion
+
+<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
+
+### Summary of findings
+
+Lipid-regulating agents showed little evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
+The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
+For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+
+The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
+When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
+
+<!-- QUESTION Why are fibrates different? -->
+
+<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->
+
+<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
+
+<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
+However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
+
+&nbsp;
+
+<!--------------------------------------------------------------------------->
+
+### Interpretation of results
+
+<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
+
+This section will expand on a potential explanation for the observed results detailed above.
+However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
+For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
+
+A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
+While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
+In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
+
+<!----------------------------------------------------------------------------->
+(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
+
+(ref:indicationBias-scap) Confounding by indication causal diagram
+
+```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
+
+ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
+dagitty::dagitty("dag {
+  Statin [exposure,pos=\"0.000,0.000\"]
+  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
+  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
+  \"Uncontrolled variable\" -> Statin
+  \"Uncontrolled variable\" -> \"Vascular outcomes\"
+}") %>% ggdag_classic(size = 6) +
+  xlim(-0.5,3) +
+  geom_text(data = data.frame(x = 0.316392393234329,
+                              y = 0.537705383514239,
+                              label = "Prompts"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "black",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_text(data = data.frame(x = 1.65891420807966,
+                              y = 0.537705383514239,
+                              label = "Causes"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "black",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_curve(data = data.frame(x = 0.220612676359188,
+                               y = -0.000788829298738025,
+                               xend = 1.45,
+                               yend = -0.00157828084913909),
+             mapping = aes(x = x,
+                           y = y,
+                           xend = xend,
+                           yend = yend),
+             linetype = "dashed",
+             angle = 0L,
+             size = 0.6,
+             colour = "black",
+             curvature = 0,
+             arrow = structure(list(angle = 0,
+                                    length = structure(0,
+                                                       class = "unit",
+                                                       valid.unit = 2L,
+                                                       unit = "inches"),
+                                    ends = 2L,
+                                    type = 2L),
+                               class = "arrow"),
+             inherit.aes = FALSE,
+             show.legend = FALSE) +
+
+  theme_dag(),
+width = 8,
+height = 3)
+
+knitr::include_graphics(file.path("figures","cprd-analysis","indicationBias.png"))
+```
+<!----------------------------------------------------------------------------->
+
+In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
+
+Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
+The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
+This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
+
+A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
+
+Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
+I also adjusted for several additional potential baseline variables.
+However, important confounding variables for which I have not adjusted could include genetic factors.
+A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
+
+On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
+It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
+
+<!-- IDEA talk about time-varying confounding here -->
+
+In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
+
+<!--------------------------------------------------------------------------->
+&nbsp;
+
+### Strengths and limitations
+
+The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
+Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
+Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
+This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
+
+However, the findings of this analysis are subject to several limitations.
+There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
+As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+
+Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
+This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
+
+<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
+
+<!-- IDEA there is also the potential for reverse causation in this analysis.
+Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
+-->
+
+<!--------------------------------------------------------------------------->
+
+<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
+
+<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
+
+<!-- However, this is not the case.
 Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
@@
 However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
+-->
 
@@
 
-As expected, in a confirmatory analysis using lipid levels, there was no association between *the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.*
-
-<!--- This hasn't been done! --->
-
-### Replicating other analytical strategies
-
-**Comparing and contrasting between different studies is particularly difficult** because of the impact that the use of different code list can have on the analysis [@wilkinson2018a; @mcguinness2019c] This highlights a particular challenge in comparing research across different time-periods and coding systems.
-Previous work has demonstrated that electronic health records have variable positive and negative predictive values, based substantially on the exact code-lists used to define each outcome.
-
-In order to
-
-As part of my exploration of the unexpected results, I attempted to replicate the analyses of another paper that used a different approach to
-
-Having contacted the authors to address these concerns, it was noted that
-
-Propensity scores are based on a range of baseline variables, and provide an estimates of the
-
-They used propensity scores to attempt to matcch patients equally likely to recieve the vaccine
-
-In addition, the need to contact the authors for their code-lists reinforces the points raised in Section \@ref(sys-rev-open-data) - that all relevant material should be readily shared.
-Fortunately, the authors kindly shared their
-
-However, there was a large difference in the case mix of dementia diagnoses between the two analyses.
-
-However, as shown in Table \@ref(tab:smeethComparison-table), there is substantial divergence between the two sets of code-lists.
-
-The reason for the discrepancy in terms of the number of Alzheimer cases as a percentage of total dementia cases between our study and the Smeeth 2010 paper is due to two things:
-•	While all of the codes used to define Alzheimer’s in the Smeeth paper are included in our “Probable Alzheimer’s” code-list, we also have several additional codes used to define this outcome (including, for example, “Eu00013: [X]Alzheimer's disease type 2”).
-•	Several of the codes in our “Possible Alzheimer’s” code list are included in the “Other dementia” code list used by Smeeth.
-
-Using the Smeeth code-list, we get a similar breakdown of cases to that paper, with Alzheimer’s disease being a lot less frequent than when using our code-lists (which is not surprising based on the points above).
-<!-- This, in addition to unexplained statistical issues such as adjusting for post-baseline covariates, means I am sceptical of the value of comparing our findings with Smeeth.
+<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
 -->
 
-Replicating a matched analysis a la Smeeth et al 2010 - though questions were raised as to how they had actually done the analysis (they did not match on propensity score, they simply adjusted for it - find paper that explores 4 ways of accounting for PS and shows this is the worst), they adjusted for things likely to be on the causal pathway, and they saw a huge change in direction for MI pre- vs post- adjustment.
+<!-- This hasn't been done! Plus I do not think this is the case -->
 
+<!--------------------------------------------------------------------------->
+
+<!--------------------------------------------------------------------------->
+<!-- &nbsp; -->
+
+<!-- IDEA Issues with large-scale EHR databases -->
+
+<!-- __Missclassification__ -->
+
+<!-- __Coding quality in the CPRD__ -->
+
+<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
+
+<!-- There is the possibility of ascertainment bias -  -->
+
+<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
+
+<!--------------------------------------------------------------------------->
 &nbsp;
 
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-caption) Comparison of code lists used in this analysis and in Smeeth et al.
+### Enabling easy synthesis of this analysis {#cprd-data-avail}
 
-(ref:smeethComparison-scaption) Comparison of code lists used in this analysis and in Smeeth et al.
+In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
 
-```{r smeethComparison-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
+All code, Read codelists and summary statistics (i.e.
+the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
+as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
+<!-- TODO Archive on Zenodo.
+-->
 
-&nbsp;
+The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
+In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
 
-## Discussion
+Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
+<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
 
-### Main findings
+This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
 
-Lipid-regulating agents had no effect on probable and possible Alzheimer's when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
-
-&nbsp;
-
-### Comparison to other literature
-
-Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] This echoes the distribution of participants among subgroups in our analysis, with the statin subgroup including almost all participants.
-
-&nbsp;
-
-__Statins and all-cause dementia__
-
-A recent Cochrane Review identified two randomized trials comparing treatment with statins versus non-treatment for the prevention of dementia, only one of which presented information on the incidence of dementia.[@mcguinness2016a] This study (Heart Protection Study) showed no effect of treatment with simvastatin on all-cause dementia risk (OR: 1.00,  95%CI:0.61-1.65),[@heartprotectionstudycollaborativegroup2002] but concerns were raised over the diagnostic criteria used.
-A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020]
-
-These sources of evidence conflict with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia.
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may lead to a artifical protective effect of statins on all-cause dementia
-
-&nbsp;
-
-__Statins and Alzheimer's disease__
-
-Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80), though the reduction was more extreme than observed in our analysis.[@poly2020] In addition, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease found a small reduction in risk of Alzheimer's disease, comparable in magnitude to our findings, but could not rule out no effect (OR: 0.91, 95%CI: 0.63-1.31).[@williams]
-
-An additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis.[@chu2018]
-
-&nbsp;
-
-__Statins and non-Alzheimer's disease dementia__
-
-Much less literature is available on the association between lipid-regulating agents and vascular dementia or other dementia.
-A recent review found four observational studies examining the association of statins and vascular dementia found no effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis.
-An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
-
-&nbsp;
-
-__Other drug classes__
-
-Apart from statins, few studies examining a lipid-regulating agent have been reported.
-One of the few classes for which data was available were fibrates, which were shown to have no effect on all-cause dementia, [@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
-
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on any dementia outcome, and so we cannot compare our unexpected finding that treatment with the drug associated with an increased risk of the vascular and other dementia outcomes.
-
-&nbsp;
-
-### Original contribution to research
-
-There are two primary ways in which this research adds to the topic:
-
-* _Size of the CPRD and length of follow-up:_ Having reviewed the other studies identified by the systematic review in Chapter 4, this analysis of 1.7 million participants is one of the largest studies of this research question.
-* _Addressing the limitations of other observational analyses:_ Analyzing this data has provided the opportunity to use a separate analytical technique to many of the studies identified in the systematic review, As an example, the Hippsley-Cox BMJ paper examining the effect of statins, which makes use of the THIN EHR database, likely suffers from immortal time bias as exposed and unexposed participants are not followed up from a common time point.[@hippisley-cox2010] As touched on in the section above, this provides an additional evidence point with a different source and direction of bias, which is useful for the triangulation aspect of the thesis.
-
-### Coding quality in the CPRD
-
-Lots of things influence prevalence: historic trends, availability of good codes
-
-There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013]
-
-### Strengths and Limitations
-
-A major strength of our analysis is the size of the included cohort and the length of follow-up that the use of electronic health records allowed.
-In addition, we followed users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
-
-However, the findings of our analysis are subject to several limitations.
-There is a strong possibility of differential misclassification of dementia-related condition based on the exposure, as those with memory complaints are more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019b]
-
-Our study may be subject to confounding by indication, which occurs when factors that affect whether a participant is exposed also affect their outcome.
-We attempted to address this by limiting inclusion to those either prescribed or “at risk” of being prescribed, which was determined using an elevated test result.
-We also adjusted for several additional potential confounding variables.
-However, the negative control analysis of back pain demonstrated a harmful association with lipid-regulating agent use, indicting that our findings may be biased by residual confounding.
-Important confounding variables for which we have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of unspecified Alzheimer’s and vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020] This finding, combined with the potential for differential misclassification between Alzheimer’s disease and vascular dementia, could explain part of the observed association between lipid-regulating agents and vascular dementia.
-
-A further limitation is the possibility of time-varying confounding <!--- Either deal with this issue here, or keep the section above dealing with time-varying confounding. --->
-
-Finally, there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
-
-### Enabling easy synthesis
-
-In light of my own experiences in attempting to extract information for papers assessing prevantive measures, I attempted to document
-
-This study was reported in line with the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines[@vandenbroucke2007] (see Appendix \@ref() for the STROBE checklist) <!--- Maybe don't include the whole thing, or apply it to this thesis rather than the paper --->
-
-Reporting guidelines do not always work, but help to guide
-
-All code and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats, without any formatting, from the Github repository for this project.
-
+<!--------------------------------------------------------------------------->
 &nbsp;
@@
 
-We have provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-We found use of lipid-regulating agents not associated with probable or possible Alzheimer’s disease, but were associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of participants in our cohort.
+This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
 
-We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature.
-However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which raises questions about our findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-Future research should aim to address these potential biases and, while it may be costly in terms of time and resources, a large scale, long-term randomized controlled trial would provide useful additional information on the effect of lipid-regulating agents on the risk of dementia and related outcomes.
+It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
+However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
+In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
+
+This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
+However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
+Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
+
+Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
+In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
 

### 2021-10-08 06-Chp-IPD-Analysis.Rmd
End of day:

--- 2021-03-10 06-Chp-IPD-Analysis.Rmd
@@
 ---
-#########################################
-# options for knitting a single chapter #
-#########################################
+bibliography: bibliography/references.bib
+csl: bibliography/nature.csl
 output:
-  bookdown::html_document2: default
-  bookdown::word_document2: default
+  bookdown::word_document2: 
+      toc: false
+      toc_depth: 3
+      reference_docx: templates/word-styles-reference-01.docx
+      number_sections: false 
   bookdown::pdf_document2:
     template: templates/brief_template.tex
+  bookdown::html_document2: default
 documentclass: book
 ---
+
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+Hold
+```
+(ref:intro-quote) --- Hold
 
@@
 
-## Data sources
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/helper.R")
+knitr::read_chunk("R/05-Code-IPD-Analysis.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
 
-As part of this Chapter, I will use individual patient data from a range of sources. These sources are described here in detail for reference.
+```{r cohortNumbers, message=FALSE,echo = FALSE}
+```
 
-Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get
+## Lay Summary
 
-Each should have:
+As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
 
-* Description (including observation period, numbers, numbers with outcome, etc)
-* Whether they are a known genetically at-risk cohort
-*
+The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglycerides) on any dementia outcome.
+In addition, patients characteristics such as age and sex did not have any impact on the relationship of lipid fractions and dementia outcomes.
 
-### Epic Norfolk
+Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Introduction
+
+Individual patient data meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.
+They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results have been explicitly stratified by the characteristic of interest.
+
+While the systematic review presented in Chapter \@ref(sys-rev-heading) did not provide strong evidence for an effect of age at lipid measurement or patient sex on the relationship between lipids and dementia, the number of included studies in the lipid fraction meta-analyses were very small, due to both the relatively small number of studies reporting on this exposure and the poor reporting of smmary statistics of patient characteristics.
+
+As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by incorporating previously unanalysed cohorts contained in the Dementia Platform UK, a large consortia of dementia cohorts.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+## Methods
+
+### Eligibility criteria
+
+Eligible data sources were defined as those that contained lipid measurements and lipids reported/available as a continuous measure, Data sources which were cross-sectional, either by design or due to the available data (e.g.
+a study conducted multiple waves, but onyl data from a single wave could be accessed) were excluded.
+Similarly, due to the limited time-frame, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
+The one exception to this was data from the CPRD, which I already had access to as part of the analysis reported in Chapter \ref(cprd-analysis-heading).
+
+<!-- TODO Read this[@riley2020] -->
+
+### Applying for data access
+
+Potentially eligible data sources were identified via two mechanisms with a distinct focus.
+For each approach, the number of cohorts responding to the request, and where applciable, the reasons given for a lack of data sharing were recorded.
+
+#### Systematic review
+
+The first approach focused on previously analysed data sources.
+The systematic review detailed in Chapter \@ref(sys-rev-heading) identified several observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes.
+The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
+In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potentially collaborators) in Autumn 2020.
+If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who has moved to a different institution.
+
+#### Dementia Platform UK
+
+The second approach focused on incorporating previously unanalysed data, thus providing additional evidence on the relationship between statins and dementia risk.
+
+This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application processs for all cohorts with the intent of making it easier to access data from existing data sources.
+
+Cohorts included in the DPUK were assessed against the eligibility criteria, and in Autumn 2020, an application for access to a subset of 16 cohorts was made via the common-access procedure.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Risk of bias assessment
+
+Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
+
+Due to the inherent conflict of interest in assessing my own analysis, the result were also assessed by two independent reviewers.
+
+<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Missing data
+
+<!-- TODO This was taken from Chapter 4, so may need to rephrase slightly -->
+<!-- IDEA See Sean's thesis for some additional detail on this -->
+
+In this analysis, missing data were handled using a multiple imputation approach.
+Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the XXX command in R.
+
+<!-- TODO Need to talk about how missing variables were handled across studies -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Variable definition
+
+#### Exposure
+
+To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
+
+#### Outcomes
+
+Similar to the analyses presented in othe chapters, th endpoints in this analysis was incidience of dementia and related sub-types (AD, vascular dementia).
+
+#### Covariates
+
+Relevant covariates were adjusted for in all models. these included age, sex,education and comorbities. For information on how these were defined across cohorts, see Appendix \@ref(hold).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Statistical analysis
+
+#### Descriptive statistics
+
+All IPD obtained was examined and recoded as necessary to ensure they comply with the coding guideline for the IPD database.
+As recommended , summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process.[@levis2021] Any discrepancies were investigated.
+
+#### Data cleaning and harmonisation
+
+Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
+The one exception to this is the CPRD data, which was held in a different system to the rest.
+However, an identical model was applied within this cohort.
+The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+
+#### Individual patient data analysis
+
+<!-- Need detailed paragraph here describing the different between two stage versus one-stage approach -->
+
+In this analysis, an two-stage individual patient data model was used out of necessity, with the one-stage model being precluded by the included datasets being in protected data silos.
+It also allows for each studys' data to be analysed according to a common analysis plan, which is particularly important in this topic, due to the differing definitions between studies of the serum concentrations above or below which lipids are deemed to be at abnormal levels.
+
+Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
+Effect estimates for the associations between lipid fractions and incident dementia, adjusted for identical covariates, were obtained by applying a common model to each data source.
+More specifically, hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017] An overall effect estimate was then produced by combining data-source-specific estimtes in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
+Following best practice, clustering within studies was accounted for.[@abo-zaid2013]
+
+<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
+<!-- TODO Figure showing the outline of interval censored studies. -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Investigating effect of patient-level covariates
+
+In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
+These were extracted and synthesised using a random effects meta-analysis.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Combining published aggregate data and individual participant data
+
+Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the aggregate data and individual data were combined.
+
+<!-- TODO How does this work? -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Comparison with published findings
+
+Where an included data source had previously been analysed and results for the association between lipid levels and dementia outcomes reported, these were compared to the results of this analysis.
+If discrepancies were identified, these were investigated.
+
+<!-- TODO Need more on this method here -->
+
+### Secondary analyses
+
+#### Amount of information added
+
+The proportion of new information added to the evidence base via incorporation of the unanalysed datasets was quantified, by addding the additional results to the lipid-dementia meta-analyses presented in Section \@ref(hold), and extracting the combined weights assigned to the new data in a fixed-effect model.
+
+<!-- #### Contact information  -->
+
+#### Data availability statements
+
+As a sensitivity analysis, I examined the data sharing statements for each using a predefined categories used in a similar previous analysis.[@mcguinness2020DAScomparison]
+
+<!-- TODO This should have a plot showing how many over time had good vs bad DAS -->
+
+<!-- TODO In addition, need plot similar to study design over time in Chapter 3, showing cohort responses over time -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Results
+
+### Data access
+
+<!-- Need exact number from each approach, plus detailed exclusion reasons -->
+
+Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) provided data and were included in the analysis.
+Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
+In addition, the reasons for cohorts not being included in the analysis are presented, stratified by application approach.
+
+In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked with the same group and did not know if the data were available or how to obtain it, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+
+With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher resulting in eventual access to three cohorts (one of which was also identified by the systematic review).
+However, even using this streamlined approach, a response was obtained for only half of the approach cohorts.
+
+<!----------------------------------------------------------------------------->
+```{r cohortFlowchartSetup, include = FALSE}
+```
+
+(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
+
+(ref:cohortFlowchart-scap) Flowchart
+
+```{r cohortFlowchart, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortFlowchart-cap)', out.width='100%', fig.scap='(ref:cohortFlowchart-scap)'}
+knitr::include_graphics(file.path("figures/ipd/cohortFlowchart.png"))
+```
+<!----------------------------------------------------------------------------->
+
+As highlighted in Figure \@ref(fig:cohortFlowchart), there was little overlap between cohorts identified by the systematic review and those contained in the DPUK (`r fmt_applied(n_applied$DPUK_sysrev)`), indicating that the DPUK is a useful source of unanalysed data with respect to this question.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Included data sources
+
+The four data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
+Of note, all included data sources were based in the United Kingdom.
+This is likely due to the majority of included datasets coming from the Dementia Platform UK route (Figure  \@ref(fig:cohortFlowchart)), which as implied by the name, has a geographical focus on cohorts performed in the United Kingdom.[@bauermeister2020]
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:cohortOverview-caption) Summary of cohorts for which data were available
+
+(ref:cohortOverview-scaption) Summary of included cohorts
+
+```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!-- TODO Update table with SD for age, and types of outcomes, and follow-up, and check why number of events in EPIC is less than expected (5 vs 8)-->
+
+<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Caerphilly Prospective Study
+
+The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
+
+Cholesterol measures (total, LDL-c, HDL-c and triglyceride) were measured at baseline in 1979-1983. 
+As the study population has aged, additional outcomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### CPRD
+
+The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+
+The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
+
+Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
+
+Additionally, other number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
+
+the
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Epic Norfolk
 
@@
 
-```{r tests, }
+The added evidental value of the EPIC cohort is small, given the relatively small number of participants and the fact that the cohort has only 8 dementia events.
 
+```{r tests}
 ```
 
-Different approaches to combining subgroups. [@fisher2017]
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Whitehall II
+
+_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
+Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
+
+This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Excluded data sources
+
+#### Cohorts identified the systematic review but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+The main reason for exclusion within this records was use of an electronic health record database.
+Examples included the Taiwan National Health Insurance database and studies run in the US making use of Medicare data.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Cohorts identified in the DPUK but excluded from the IPD analysis
+
+<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+
+Several additional cohorts are present in the DPUK collection but were not formally approached with a request for data access.
+This was primarily due to the information obtained via the online data dictionary system or via initial contact with the cohort owners indicating that the study was relatively new (and so was yet to collect more than 1 wave of data) or that the exposure variables of interest were not recorded.
+
+<!-- TODO LBC 1936 -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Cohorts providing data but ultimately excluded
+
+As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
+The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
+
+(ref:dataExcluded-scaption) Exclusion reasons for cohorts providing data
+
+```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+BRACE is a memory-complaint-based cohort, suggesting that it is unlikely they were dementia-free at baseline).
+<!-- TODO CITATION NEEDED --> Similarly, the Memento study was excluded as it's criteria for entry required participants to be outpatients from a memory clinic.
+<!-- TODO CITATION NEEDED --> The Generation Scotland provided only cross-sectional data only for the variables of interest, as did the the NICOLA study.
+<!-- TODO CITATION NEEDED x2 --> Finally, the ELSA study was excluded based on the definition of the exposure variable.
+This study provided a "high cholesterol" a binary variable rather than the raw continuous lipid measurement data.
+<!-- TODO CITATION NEEDED -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Cohorts approach but received no answer
+
+This was particularly common among the cohorts identified via the systematic review and included studies with  a dedicated access process or data access committee.
+A cohort of particular interest, having been used in multiple studies identified by the systematic review, is the Three City Study in France.
+Despite multiple attempts to contact the team, there was no response received.
+<!-- TODO CITATION NEEDED --> This study was approach at multiple points over the curse of this analysis, and no answer was received.
+
+This was also a problem for cohorts approach via the DPUK - half of the cohorts applied to did not respond to the application within a year.
+
+### Analytical results
+
+There was no evidence for an effect of any lipid fraction on any dementia outcome (Figure \@ref(fig:tcDementiaMain)).
+Additionally, meta-analysis of the interaction coefficients for age-at-lipid-measurement and participant sex did not reveal an evidence for an varying effect across these variables.
+
+<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
+
+<!----------------------------------------------------------------------------->
+(ref:tcDementiaMain-cap) __Random effects meta-analysis of estimates from included data sources:__
+
+(ref:tcDementiaMain-scap) IPD analysis of total cholesterol and dementia
+
+```{r tcDementiaMain, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:tcDementiaMain-cap)', out.width='100%', fig.scap='(ref:tcDementiaMain-scap)'}
+knitr::include_graphics(file.path("figures/ipd/TC.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!-- ### Effect by age -->
+
+<!-- ### Heterogeneity -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
 
@@
 
-Letters sent to
+### Summary of findings
 
-This is likely due to my junior position as a ECR
+This analysis requested data from `r n_applied$total` data sources, but only obtained data from `r fmt_applied(n_accessed$total)`, all of which were based in the United Kingdom.
+No evidence for an effect of lipids on the risk of dementia or related outcomes was identified.
+Similalarly, there was no evidence for an effect of age-at-measurement or sex on the lipid-dementia relationship.
 
-Range of reasons why
+Additionally analyses revealed that authors of cohorts indentified by the systematic review rarely stated that the data underpinning their analyses would be freely available, while a review of corresponding authors of these publications demonstrated that for many, the institutional email address provided was out of date.
+
+<!-- Useful citation for discussion[@levis2021] -->
+
+### Limitations
+
+#### Low response rate to request for data
+
+_(although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019])_
+
+<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
+A key limitation of this analysis is the very low response rate to requests for data access.
+This finding is not unexpected however, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
+--> and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
+
+There are likely several likely reasons for this low response rate.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.
+<!-- TODO CITATION NEEDED -->
+
+More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
+The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other work.
+
+_Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases - that when data is requested, it is not actually made available.
+[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014] Several of the included studies are greater than 10 years old, and so obtaining data from these cohorts is less likely compared with more recently published studies._ <!-- TODO taken from DAS paper, so will need to change language -->
+
+One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
+Qualitatively, investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+<!-- All of these are arguments towards better reporting of data availability, ownership - also talk about the ORCID and advatnages of permanent identifier-->
+
+ These challenges are in theory what the DPUK was built to address.
+However, even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
+The response rate among DPUK cohorts a year after application was just 50%.
+In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
+
+<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
+
+Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
+
+<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
+The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
+Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
+However, analysis combining individual and study level data may mitigate these effects [3, 21].
+from [@ventresca2020a] -->
+
+For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
+In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Risk of bias assessment
+
+There is some concerns about performing risk of bias assessments on your own analysis, and so two secondary reviewers
+
+<!-- #### Opportunistic inclusion of CPRD data -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Strengths
+
+While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the EPIC Norfolk study - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+<!-- ### Study within a review -->
+
+<!-- In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data. -->
+
+<!-- Options could include an investigation of the impact of applicant chacateristics  -->
+
+<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reflections on the process
+
+In hindsight, attempting to undertake a large-scale IPD meta-analysis as part of a larger PhD project may have been overly ambitious.
+Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
+
+<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Conclusion
+
+This analysis provided very weak evidence for an effect of lipid fractions on dementia outcomes.
+However, it does provide an analysis two previous unanalysed data sources that are subsequently used in Chapter \@ref(tri-heading).
+
+\newpage
+
+## References

### 2021-10-08 07-Chp-Triangulation.Rmd
End of day:

@@
 
+\minitoc <!-- this will include a mini table of contents-->
+
 ## Lay Summary
@@
 
+This chapter will consider two questions
+
+Firstly, an ter
+
+Secondly an
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Terminology
+
+The terminology used in describing different mechanisms by which an observed result may  complicate interpretation. This section clearly defines how each are used in h
+
+Here, internal bias is used in terms of
+
+In contrast, external bias (also called indirectness, or )
+
+Additionally, potential biases can be additive or proportional. Pro
+
 ### Summary of triangulation
@@
 Describe in detail
+
+### Evidence sources
+
+As outlined in the thesis overview presented in Section \@ref(hold), the triangulation draws on the research produced in the preceding chapters.
+
+a)	Proposed method for this chapter
+i)	Example: LDL-c at midlife on Alzheimer’s disease risk
+ii)	Specific causal effect of interest using ROBINS-E framework:
+•	Population of interest: General population
+•	Exposure of interest: Low density lipoprotein cholesterol
+•	Exposure window of interest: Midlife (45-60)
+•	How exposure over time should be summarized: Cumulative exposure
+iii)	Identify relevant studies from evidence base
+•	LDL-c assessed at midlife
+•	MR of LDL-c
+•	Statin use at midlife
+iv)	Assess risk of bias in each result, define expected directions of each bias and plot
+
+v)	Assign additive value to each level of bias (High = 0.2, Some concerns =0.1, Low = 0), assign sign to these values based on predicted direction and sum across result
+vi)	E.g. for effect estimate 0.71 (0.57-0.89):
+
+Element	D1	D2	D3	D4	D5	D6	D7	Overall
+Bias	High	Some concerns	Low	Low	Low	Some concerns	Some concerns	Serious
+Direction	Left	Away from null	-	-	-	Towards null	Away from null	
+Modifier	-0.2	-0.1	0	0	0	0.1	-0.1	-0.3
+
+vii)	Assign a proportional value representing the indirectness for each result
+•	Statin studies would give smaller proportion (e.g. 0.7) of effect observed for generally lower lipids, as they would reduce cumulative exposure 
+•	SNPs predict quite strongly LDL-c and so would have minimal indirectness
+viii)	Combine in a bias-adjusted meta-analysis
+
+###	Limitations
+
+In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elictation process using a number of experts.
+
+Ideally, the modifying values )
+
+i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)?
+Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate
 

### 2021-10-08 front-and-back-matter/99-appendices.Rmd
Working version
End of day:

@@
+---
+output:
+  pdf_document: default
+  html_document: default
+---
 `r if(knitr:::is_latex_output()) '\\startappendices'`
@@
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
+
 knitr::read_chunk(here::here("R/appendix.R"))
@@
 
-`r br`
+&nbsp;
 
@@
 
-if(doc.type == "docx"){
+if(doc_type == "docx"){
 
-  knitr::kable(arguments,escape = T,
+  knitr::kable(arguments,
+               escape = T,
              caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
@@
 
-}else{
+} else {
 
-  knitr::kable(arguments, booktabs = TRUE, longtable = TRUE, 
+  knitr::kable(
+    arguments,
+    format = "latex",
+    booktabs = TRUE,
+    longtable = TRUE,
     caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-             align = c("l","c","c","l"),
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description")) %>%
-  column_spec(4,"5cm") %>%
-  kable_styling(font_size = 9, 
+    align = c("l", "c", "c", "l"),
+    col.names = c(
+      "Argument",
+      "rob_traffic_light()",
+      "rob_summary()",
+      "Description"
+    )
+  ) %>%
+    column_spec(4, "5cm") %>%
+    kable_styling(
+      font_size = 9,
       bootstrap_options = c("striped", "hover"),
-                latex_options = c("repeat_header", "striped"))
+      latex_options = c("repeat_header", "striped")
+    )
 }
@@
 
+\newpage
+
 ## Copies of papers arising from this thesis {#published-papers}
+
+The following pages contain copies of papers arising from work performed as part of this thesis.
+
+<!-- TODO May need to reiterate contributions here -->
 
@@
 \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

### 2021-10-08 index.Rmd
End of day:

@@
 #######################
-bibliography: [bibliography/references.bib, bibliography/packages.bib]
+bibliography: bibliography/references.bib
 csl: bibliography/nature.csl
@@
 ---
+<!-- TODO Confirm thesis title! -->
 
@@
 source("R/helper.R")
-options(scipen=999)
 ```

### 2021-10-08 R/abbreviations.R

@@ -1,4 +1,4 @@
-# IMport, sort and arragn
+# Import, sort and arrange abbreviations by alpha order
 
 abbr <-
   dplyr::arrange(read.csv(
@@ -22,6 +22,7 @@ abbr_text <- c(
 
 writeLines(abbr_text, here::here("front-and-back-matter","abbreviations.tex"))
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # Render the acknowledgements section from Rmd to Md and paste in the output of
 # github_thanks()
 
@@ -35,3 +36,4 @@ writeLines(glue::glue(
   .close = ">>"
 ),
 here::here("front-and-back-matter","_acknowledgements.md"))
+

### 2021-10-08 R/doc_options.R

@@ -1,31 +1,0 @@
-options(kableExtra.auto_format = FALSE, scipen = 999,
-        knitr.kable.NA = '')
-
-library(robvis)
-library(medrxivr)
-library(kableExtra)
-library(dplyr)
-library(data.table)
-library(flextable)
-library(ggplot2)
-library(patchwork)
-library(sf)
-
-doc.type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
-
-if(doc.type=="docx"){
-  br <-"&nbsp;"
-  pb <- "#####"
-} 
-
-if(doc.type=="html"){
-  br <- "<br>"
-  pb <- ""
-}
-
-if(doc.type=="latex"){
-  br <- ""
-  pb <- ""
-}
-
-knitr::opts_chunk$set(echo = TRUE)

### 2021-10-08 R/triangulation.R

@@ -1,322 +1,0 @@
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# Statins RCT
-
-results_statins_rct <- rio::import("data/sys-rev/data_extraction_main.xlsx", which = 2) %>%
-  janitor::clean_names() %>%
-  # Extract two trials
-  filter(study_id %in% c("10562","90003")) %>%
-  rename("lower_CI" = upper_95_percent, 
-         "upper_CI" = lower_95_percent) %>%
-  mutate(across(c(point_estimate,starts_with(c("number_","cases_")), ends_with("_CI")),as.numeric)) %>%
-  mutate(point = log(point_estimate),
-         SE = (log(upper_CI) - log(lower_CI))/3.92) %>%
-  mutate(author = ifelse(grepl("Heart",author),"HPS",author),
-         author = ifelse(grepl("FDA",author),"JUPITER",author)) %>%
-  mutate(number_exposed = as.numeric(number_exposed)) %>%
-  mutate(tpos = cases_exposed,
-         tneg = number_exposed - cases_exposed,
-         cpos = cases_unexposed,
-         cneg = number_unexposed - cases_unexposed)
-
-dat <- escalc(measure="OR", ai=tpos, bi=tneg, ci=cpos, di=cneg, data=results_statins_rct)
-
-rob_dat <- robvis::data_rob2[1:2,]
-rob_dat$studyid <- c(10562,90003)
-
-png("test.png", width = 800, height = 500)
-forest_strata_rob(dat, rob_dat)
-dev.off()
-
-
-
-
-res <- metafor::rma.uni(data = dat,
-                        yi, vi, 
-                        slab = paste(author, year))
-
-rct_tri_res <- data.frame(
-  stringsAsFactors = FALSE,
-  Type = "RCT",
-  exposure = "Statin",
-  outcome = "Dementia",
-  studies = 2,
-  bias = "Low",
-  I2 = res$I2,
-  predict.rma(res, transf = exp)
-)
-
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# Obs lipids per SD
-
-res <- rio::import("data/sys-rev/data_extraction_main.xlsx", which = 2) %>%
[…]

### 2021-10-13 manuscripts/cprd/manuscript.Rmd
Pre-final changes to manuscript

@@
 knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
-options(scipen = 999)
-source(here::here("R/doc_options.R"))
 source(here::here("R/helper.R"))
@@
 
-knitr::read_chunk(here::here("R/04-Code-CPRD-Analysis.R"))
+knitr::read_chunk(here::here("R/05-Code-CPRD-Analysis.R"))
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
@@
 
-__Conflict of interest statement__
-None declared.
-
-&nbsp;
-
-__Sources of funding__
-
-LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
-JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
-The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care.
-YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
-LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1, MC_UU_00011/4).
-JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
-The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.
-NMD is supported by a Norwegian Research Council Grant number 295989.
-
-&nbsp;
-
 __Word counts__
@@
 * Abstract word count (max 250): 250
-
-&nbsp;
-
-__Data/code availability__
-This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
-The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of submission on Zenodo (DOI: __TBC__).
 
@@
 
-<!-- TODO Check scale in figures -->
 <!-- TODO Check cross link between supplementary tables and text -->
@@
 
-__Check TODOs!__
+__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia.
+These modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
+Here, we test the association between lipid-regulating agents and risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a United Kingdom electronic health record database.
 
-<!-- TODO Fix total length of follow-up between text and table 2 -->
+__Methods:__ A retrospective cohort study was performed using routinely collected data from the CPRD (January 1995 and March 2016).
+Multivariable Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
+no drug) and five dementia outcomes (all-cause, vascular and other dementias, and probable and possible Alzheimer's disease).
 
-__Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia.
-As a result, these modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
-Here, we test the association between lipid-regulating agents and risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), an electronic health record database.
+__Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` patient-years (median: `r fu_text`).
+We found little evidence that lipid-regulating agents were associated with incidence of Alzheimer's disease (probable `r probad_text`; possible `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementias (`r othdem_text`).
+Evidence from a number of control outcomes indicated the presence of substantial residual confounding by indication (ischaemic heart disease `r ihd_text`; backpain `r backpain_text`; and Type 2 diabetes `r dm_type2_text`).
 
-__Methods:__ A cohort study using data from the CPRD, routinely collected between January 1995 and March 2016, was performed.
-Multivariable Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
-no drug) and five dementia outcomes (all-cause, vascular and other dementia, and probable and possible Alzheimer's disease).
-
-__Results:__ We analyzed `r totaltext` with a total follow-up of `r comma(total_followup)` participant-years (median: `r fu_text`).
-We found little evidence that lipid-regulating agents were associated with Alzheimer's disease (probable `r probad_text`; possible `r possad_text`), but there was evidence of an increased risk of all-cause (`r anydem_text`), vascular (`r vasdem_text`) and other dementia (`r othdem_text`).
-Evidence from a number of control outcomes (ischaemic heart disease `r ihd_text`; backpain `r backpain_text`; and Type 2 diabetes `r dm_type2_text`) indicated the presence of substantial residual confounding by indication.
-
-__Conclusion:__ We found little evidence that lipid-regulating agents were associated with reduced Alzheimer’s disease risk.
-There was some evidence of an increased the risk of all-cause, vascular and other dementia, likely due to residual confounding by indication.
+__Conclusion:__ Lipid-regulating agents were not associated with reduced Alzheimer’s disease risk.
+There was some evidence of an increased the risk of all-cause, vascular and other dementias, likely due to residual confounding by indication.
 
@@
 
-* A large cohort of patients from the Clinical Practice Research Datalink electronic health record database was assembled to examine the effect of lipid-regulating agents, such as statins, on dementia outcomes.
+* A large cohort of patients from the Clinical Practice Research Datalink electronic health record database was assembled to examine the association of lipid-regulating agents, such as statins, with dementia outcomes.
 
-* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful effect on all-cause, vascular and other dementia.
+* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful association with all-cause, vascular and other dementias.
 In all cases, the estimated associations were driven by the any statin subgroup, which comprised most participants in our cohort.
@@
 In this context, determining whether lipid-regulating agents (LRA) could be repurposed for the prevention of dementia and related diseases would be helpful in the development of evidence-based prevention policy.
-Several existing prospective studies have examined the association of LRA use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and have limited follow-up.
+Several existing prospective studies have examined the association of LRA use with dementia.[@chu2018; @larsson2018; @ancelin2012; @bettermann2012;@rea2005] However, many of these studies are small, record few outcomes, and had limited follow-up.
 
@@
 
-We therefore aimed to test the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementia, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database.[@herrett2015]
+We therefore aimed to test the association between several major classes of LRA and all-cause dementia, Alzheimer's disease, vascular dementia and other dementias, in the Clinical Practice Research Datalink (CPRD), a large, population-based electronic health record (EHR) database from the United Kingdom.[@herrett2015]
 
@@
 
-We performed a cohort study using data from the CPRD.
+We defined a longitudinal cohort using data from the CPRD.
 Our initial sample included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cut-off were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
+Records pre-dating the 1995 cut-off were excluded from the analysis as data quality and reliability are thought to be higher after this date.[@wolf2019] All events of interest were identified using predetermined code lists, which are available for inspection (see [Data/code availability](#data-code-avail)).
 
@@
 
-Participants were included in our study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a LRA (such as statins); a total cholesterol test result of >4mmol/L; or a low density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: (a) a Read code for a diagnosis of hypercholesterolemia or related condition; (b) a Read code for prescription of a LRA (such as statins); (c) a total cholesterol test result of >4mmol/L; (d) or a low-density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
 
 These index events allowed us to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL-c test results, or had already been diagnosed with it, as indicated by a diagnostic code or related prescription.
-This approach, conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia, was employed to reduce confounding by indication that we would expect to observe in a general population cohort.
+This approach, conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia, was employed to reduce the "confounding by indication" that we would expect to observe if we had used a general population cohort.
 
-The index date for a participant was defined as the date where the first relevant code or test result (as detailed above) was recorded on their clinical record.
-Participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); last registration date with their GP practice; or the last CPRD collection date for their practice.
-Participants were removed from our sample if they were less than 40 years of age, had less than 12 months of "research quality" data prior to their index date, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
+An index date for each participant was defined as the date when the first relevant code or test result (as detailed above) was recorded on their clinical record.
+Participants were followed up until the earliest of (a) an outcome of interest; (b) death; (c) end of follow-up (29 February 2016); (d) last registration date with their GP practice; or (e) the last CPRD collection date for their practice.
+Participants were removed from our sample if they were less than 40 years of age at entry (as these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data prior to their index date, were simultaneously prescribed more than one LRA (due to the difficulty of assigning these patients to a single exposure group), or were diagnosed with dementia before or on the date of the index event.
 
@@
 
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome.
 When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Supplementary Figure 1).
@@
 
-The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
-All covariates were determined at index and definitions for each can be found in Supplementary Table 2.
+The analysis was adjusted for a range of baseline covariates including sex, grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010), Charlson co-morbidity index, Index of Multiple Deprivation (IMD), consultation rate, alcohol use (current, former,  never), smoking (current, former,  never), BMI, baseline total cholesterol, and history of cardiovascular disease, coronary bypass surgery, coronary artery disease, peripheral arterial disease, hypertension, chronic kidney disease, and Type 1 and Type 2 diabetes.
+These variables were selected as potential confounders between dementia outcomes and use of a LRA.
+All covariates were determined at the index date and definitions for each can be found in Supplementary Table 2.
 
@@
 
-All analyses were performed in STATA 15.
+All analyses were performed in STATA (V16, StataCorp LLC, College Station, TX).
 Cox proportional hazard models with a time-varying treatment indicator were used to estimate the hazard ratio and corresponding 95% confidence intervals, allowing for potential clustering of outcomes by practice.
-Participant's age was used as the time axis for all models.[@lamarca1998; @gail2009; @pencina2007] To observe the effect of adjusting for additional covariates, we compared models adjusted for age only and age and sex to the fully adjusted model.
+Participant's age was used as the time axis for all models.[@lamarca1998; @gail2009; @pencina2007] To observe the effect of adjusting for additional covariates, we compared models adjusted for age only and age and sex with the fully adjusted model.
 Additional analyses stratified by outcome and drug class were also performed.
@@
 Given the different ability of lipophilic statins to cross the blood-brain barrier,[@sierra2011] we further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
-Finally, we included three control outcomes with known associations with statin use.[@collins2016a; @herrett2021] Using the fully adjusted model, we investigated the association between LRA and back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
+Finally, we included three alternative outcomes with known associations with statin use as positive or negative controls using the fully adjusted model: back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).[@collins2016a; @herrett2021]
 
@@
 Most participants were included in the cohort due to an elevated test result (`r index_event_text`).
-The median age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
+The median age at the index date was `r age_text` and participants were followed up for a median of `r fu_text`.
 During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable Alzheimer's disease, `r format(p1[3,2], big.mark = ",")` possible Alzheimer's disease, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia).
-The distribution of baseline characteristics across the drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-
+The number of events, time-at-risk and crude rates for each drug class, tabulated by dementia outcome, are shown in Table \@ref(tab:followUp-table).
 Most participants (`r percentage.statins`) prescribed a lipid-regulating agent were prescribed a statin.
-We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (Table \@ref(tab:cprdCharacteristics-table)).
+We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent subgroup analyses based on the extremely small number of participants in these groups (Table \@ref(tab:followUp-table)).
+The distribution of baseline characteristics across the remaining seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
 The stopping, addition and switching of drug classes was common across all exposure groups (Supplementary Table 3).
@@
 Full covariate information was available for `r missingtext`.
-Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
+Five key variables had some missing data: IMD 2010 score, a proxy for socioeconomic position that is measured as twentiles with 1 indicating the least deprived and 20 indicating the most deprived, was missing for `r imdtext`, because it is only recorded for selected English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
 
@@
 
-As shown in Figure \@ref(fig:cprdPrimary), our results show little evidence of an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, except for fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+As shown in Figure \@ref(fig:cprdPrimary), our results show little evidence of an association between lipid-regulating agents and probable (`r probad_text`) or possible (`r possad_text`) Alzheimer's disease when compared with no treatment, except for an adverse association between fibrates and probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
-Again, this effect was driven mainly by the any statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementias (`r othdem_text`).
+Again, the observed estimate was driven mainly by the any statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
 
@@
 
-For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), which lies between the associations for the Alzheimer and non-Alzheimer dementia outcomes as would be expected.
 There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
@@
 
-Adjustment for additional covariates beyond age and sex had a limited impact (Supplementary Figure 3), except for the Probable Alzheimer's disease outcome, where the full adjustment attenuated to the null the protective effect observed when adjusting only for age and sex.
+Adjustment for additional covariates beyond age and sex had a limited impact (Supplementary Figure 3), except for the probable Alzheimer's disease outcome, where the full adjustment attenuated to the null the protective association observed when adjusting only for age and sex.
 
-Removing participants aged 55 and under at index from our analysis had minimal effect on our estimates (Supplementary Figure 4).
-When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Supplementary Figure 5).
-Additionally, in the Alzheimer's disease outcomes, hydrophilic statins had a small protective effect, compared to the absence of evidence for an effect for lipophilic statins.
+Removing participants aged 55 and under at the index date from our analysis had minimal effect on our estimates (Supplementary Figure 4).
+When stratifying by statin properties, hydrophilic statins were less harmful in relation to the any, vascular and other dementias outcomes compared with lipophilic statins (Supplementary Figure 5).
+Similarly, hydrophilic statins were associated with a reduced incidence of Alzheimer's disease, compared with the absence of evidence for an association with lipophilic statins.
 
@@
 
-There was little evidence that lipid-regulating agents had any observed effect on probable and possible Alzheimer's when compared with no treatment, but some evidence they were associated with an increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the any statin subgroup, which included a substantial majority of participants.
+There was little evidence for an association between lipid-regulating agents and probable and possible Alzheimer's when compared with no treatment, but some evidence they were associated with an increased risk of an all-cause dementia, secondary to their association with vascular and other dementias diagnoses.
+The association observed in each case was driven by the any statin subgroup, which included a substantial majority of participants.
 For the other drug classes, there was limited evidence of an association with any outcome, with two exceptions.
-Ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increased risk of all-cause dementia and probable Alzheimer's disease.
+Ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increased risk of all-cause dementia and probable Alzheimer's disease.
 
@@
 
-## Comparison to other literature
-
-<!-- TODO Need a little bit here on comparison with Smeeth -->
+## Comparison with other literature
 
@@
 A meta-analysis of 30 observational studies found a reduced risk of all-cause dementia was associated with statin treatment (RR 0.83, 95%CI: 0.79–0.87).[@poly2020] This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-However, some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with the results of this analysis.
+Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
 
-Additionally, a previous analysis of the THIN EHR database using a propensity score matching analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96),[@smeeth2009].
-Differences in dementia coding over time, in addition to a different set of covariates adjusted for in the analysis, may go someway to explaining the discrepancy.
+Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
+Differences in the code-lists used to define dementia outcomes, in addition an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining the discrepancy.
 
@@
 Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was not inconsistent with our results.[@williams2020]
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
+Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
 
-Our additional analysis found no difference in effect between lipophilic and hydrophilic statins for the prevention of Alzheimer's disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
-
-<!-- TODO Need to cite Smeeth paper and discuss -->
+Our additional analyses of statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
 
@@
 
-Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementia.
-A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the increased effect found in our analysis (`r vasdem_text`).
-An additional analysis found that lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
+Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
+A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
+When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
 
@@
 Apart from statins, few studies examining a lipid-regulating agent have been reported.
-One of the few classes for which data was available were fibrates, minimal evidence of an effect on all-cause dementia was identified,[@ancelin2012] inconsistent with our finding of a small increase in all-cause dementia risk in those prescribed a fibrate.
+One of the few classes for which a previous analysis was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
 
-A previous Mendelian randomization study provided an estimate of the effect of ezetimibe on Alzheimer's disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with the finding from our analyses.
-To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on risk of vascular dementia, and so we cannot compare our unexpected finding for that comparison.
+A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
+To our knowledge, there is no previous study of the effect of preventative treatment with ezetimibe on risk of vascular dementia.
 
@@
 
-## Strengths and Limitations
+## Strengths and limitations
 
@@
 However, the findings of our analysis are subject to several limitations.
-There was a  possibility of differential outcome misclassification based on the exposure, as we cannot exclude the possibility that for people with memory complaints, a diagnosis of vascular dementia might be made more frequently than Alzheimer’s disease if their medical records contain prescriptions for lipid-regulating agents.
+Confounding by indication is a major bias in pharmacoepidemiological studies and could provide a potential explanation for the observed increased risk of vascular and other dementias with lipid regulating agent use.
+Patients with vascular risk factors are more likely to receive a statin prescription and also to be diagnosed with vascular dementia.
+Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
+This would explain the increased risk for the ischaemic heart disease outcome, for which statins are known to be protective, whilst almost no association was observed with the backpain outcome, indicating that most of the uncontrolled confounding is likely to be related to vascular factors.
+Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is unlikely to be vascular,[@collins2016a; @macedo2014; @smit2020] Further supporting evidence comes from the increasingly harmful association observed when moving from the probable and possible Alzheimer's disease outcome to the other dementias outcome, and finally to the vascular dementia outcomes.
+This pattern suggests that the strength of the residual confounding by indication increases as the proportion of cases with a vascular component in an outcome definition increases.
+A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Control for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
 
-Further, there is a potential for non-differential misclassification of the outcome based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+A secondary limitation is the potential for differential outcome misclassification based on the exposure, as we cannot exclude the possibility that for people with memory complaints, a diagnosis of vascular dementia might be made more frequently than Alzheimer’s disease if their medical records contain prescriptions for lipid-regulating agents.
+Further, there is also the potential for non-differential misclassification of the outcome ,based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 
-Our study is likely to be subject to confounding by indication, which could provide a potential explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use.
-Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
-The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischaemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is unlikely to be vascular.[@collins2016a; @macedo2014] Further supporting evidence comes from the increasingly harmful effect when moving from the Probable/Possible Alzheimer's disease to other dementia to vascular dementia outcomes, indicating that confounding by indication likely increases as the proportion of cases with a vascular component increases.
-A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication in that study through use of a trial emulation analysis, the expected protective effect of statins was observed.
+A further limitation stems from uncontrolled confounding due to genetic factors.
+Number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+We were unable to control for ApoE genotype in this analysis as we did not have access to genetic data on participants.
+As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.
 
-Finally, there is also the potential for reverse causation in this analysis.
+Finally, as with many studies of dementia, there is a risk of reverse causation in our analysis.
 Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.
@@
 
-We have provided new evidence on the association of lipid-regulating agent prescription with all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-We found limited evidence to support the use of lipid-regulating agents for the prevention of  probable or possible Alzheimer’s disease, but they were associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the any statin subgroup, which comprised the majority of participants in our cohort.
+We have provided new evidence on the association of lipid-regulating agent prescription, predominantly statins, with all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementias.
+We found limited evidence that use of lipid-regulating agents was associated with incidence of probable or possible Alzheimer’s disease, but they were associated with an increased risk of all-cause, vascular and other dementias.
+Despite our attempts to account for bias in our analysis, there is a strong potential for residual confounding, misclassification and reverse causation.
 
-We have attempted to account for important sources of bias in our analysis and provide a comparison with other available literature.
-However, there is a strong potential for unmeasured confounding, misclassification and reverse causation, which may relate to the unexpected increase in risk of vascular dementia associated with statin use.
-Other analytical methods.
-Future research should aim to address these biases, potentially via a trial emulation analysis.
+This is most likely to explain the unexpected increase in risk of vascular dementia associated with statin use.
+Future research should aim to address these biases using newer methods such as a trial emulation analysis.
 
@@
 
-# Main table
+# Declarations
+
+__Ethics approval__
+
+The protocol for this study was approved by the CPRD’s Independent Scientific Advisory Committee (ISAC 15_246R).
+This study did not directly involve patients, and so further ethical approval was not required.
+
+&nbsp;
+
+__Data/code availability__
+This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
+The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of publication on Zenodo (DOI: __TBC__).
+
+&nbsp;
+
+__Supplementary data__
+
+Supplementary data are available at IJE online.
+
+&nbsp;
+
+__Sources of funding__
+
+LAM is supported by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+JPTH, RMM and GDS are supported by the NIHR Biomedical Research Centre at University Hospitals Bristol and Weston NHS Foundation Trust and the University of Bristol.
+The views expressed are those of the author(s) and not necessarily those of the NIHR or the Department of Health and Social Care.
+YBS and JPTH are supported by the NIHR Applied Research Collaboration West (ARC West) at University Hospitals Bristol NHS Foundation Trust.
+LAM, VMW, NMD, RMM, JPTH and GDS are members of the MRC Integrative Epidemiology Unit at the University of Bristol (MC_UU_00011/1, MC_UU_00011/4).
+JPTH is a National Institute for Health Research (NIHR) Senior Investigator (NF-SI-0617-10145).
+The views expressed in this article are those of the authors and do not necessarily represent those of the NHS, the NIHR, MRC, or the Department of Health and Social Care.
+NMD is supported by a Norwegian Research Council Grant number 295989.
+
+&nbsp;
+
+__Conflict of interest statement__
+None declared.
+
+\newpage
+
+# Tables
+<!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary of person-time at risk and number of events by exposure group.
+
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+\newpage
+
+&nbsp;
 
@@
 
-\newpage
-
 &nbsp;
 
-<!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary of person-time at risk and number of events by exposure group.
-
-```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-# Main figure
-
-<!-- TODO 11,119 participants removed because their endate was . This explains the discrepancy between the total number in this figure and the table above. -->
+# Figures
 

### 2021-10-13 manuscripts/cprd/supp-materials.Rmd
Pre-final changes to manuscript

@@
 knitr::opts_chunk$set(echo = FALSE, eval = TRUE) # Remove to knit with plots/data
-options(scipen = 999)
-source(here::here("R/doc_options.R"))
 source(here::here("R/helper.R"))
-
 #Load relevant libraries and datasets from the 'outputs' folder
-
-knitr::read_chunk(here::here("R/04-Code-CPRD-Analysis.R"))
+knitr::read_chunk(here::here("R/05-Code-CPRD-Analysis.R"))
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to')
@@
 
-Any changes made to the approved procotol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".
+Any changes made to the approved protocol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".
 

### 2021-10-13 R/05-Code-CPRD-Analysis.R

@@ -49,7 +49,7 @@ readExample_table <-
   read.csv(here::here("data", "cprd", "read_code_example.csv")) %>%
   dplyr::mutate("Read code" = Read.code) %>%
   dplyr::select("Level", "Read code", "Term") %T>%
-  write.csv("data/table_words/readExample.csv")
+  write.csv(here::here("data/table_words/readExample.csv"))
 
 if (doc_type == "docx") {
   apply_flextable(readExample_table, caption = "(ref:readExample-caption)")
@@ -121,7 +121,7 @@ table1_disp[1,2:9] <- stringr::str_trim(comma(as.numeric(table1_disp[1,2:9])))
 
 # Create display table using kable
 cprdCharacteristics_table <- comma(table1_disp) %T>%
-  write.csv("data/table_words/cprdCharacteristics.csv")
+  write.csv(here::here("data/table_words/cprdCharacteristics.csv"))
 
 if (doc_type == "docx") {
   apply_flextable(cprdCharacteristics_table, caption = "(ref:cprdCharacteristics-caption)") %>%
@@ -181,7 +181,7 @@ if (doc_type == "docx") {
 # ---- cprdSSA-table
 
 cprdSSA_table <- table1[19:21, -3] %T>%
-  write.csv("data/table_words/cprdSSA.csv")
+  write.csv(here::here("data/table_words/cprdSSA.csv"))
 
 if (doc_type == "docx") {
   apply_flextable(cprdSSA_table, caption = "(ref:cprdSSA-caption)")
@@ -290,7 +290,7 @@ fu_ab_text <- paste0(round(characteristics$c1[1], 1),
 # Median and IQR for age at index
 age_text <- paste0(
   characteristics$c1[4],
-  " years (Inter quartile range (IQR):",
+  " years (inter-quartile range (IQR):",
   characteristics$c1[5],
   "-",
   characteristics$c1[6],
@@ -1228,7 +1228,7 @@ statinTypeTable_table <-
   mutate(Lipophilic = paste0(Lipophilic, "%)")) %>%
   rename("Total" = V6) %>%
   rename("Prescription Year Group" = V1) %T>%
-  write.csv("data/table_words/statinType.csv")
+  write.csv(here::here("data/table_words/statinType.csv"))
 
 if (doc_type == "docx") {
   apply_flextable(statinTypeTable_table, caption = "(ref:statinTypeTable-caption)")
[…]

### 2021-10-13 04-Chp-Systematic-Review-Results.Rmd
End of day

--- 2021-10-07 03-Chp-Systematic-Review.Rmd
@@
 
-## Lay summary
-
-Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
-Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's methods.
-
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels such as statins, and dementia outcomes.
-
-My review included `r n_included` primary studies that contained information on this relationship.
-I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipid levels were not associated with any outcome.
-The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
-
-The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.
-
-<!-- TODO Search for MCI -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-## Introduction {#sys-rev-intro}
-
-In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
-
-This analysis sought to address two specific aims.
-Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
-These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
-However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
-Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
-As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.
-
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but  report relevant unpublished analyses.
-As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
-
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Methods
-
-### Protocol
-
-A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Contributions
-
-In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements and Author Declaration in the front matter).
-<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
-In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
-
-<!-- TODO Double check this list at the end of the project. -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Search strategy
-
-I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
-<!-- TODO Need to actually attach each search strategy.
-Should be able to loop through search strategy results.
--->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic.
-The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
-
-(ref:searchOverview-scaption) searchOverview
-
-```{r searchOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
-To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
-
-<!-- TODO need to comment on this feed-back process, or remove -->
-
-I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
-In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies (see Appendix \@ref(appendix-medrxivr-code) for the code used to search these preprint repositories).
-
-Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-In addition, the abstracts list of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
-<!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Study selection
-
-Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
-those identified as duplicates based on the "Title" field alone).
-
-Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.
-
-Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
-Reasons for exclusion at this stage were recorded.
-Disagreements occurring during either stage of the screening process were resolved through discussion with a senior colleague.
-A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
-
-The criteria against which records were assessed for eligibility are presented in the subsequent sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Inclusion criteria
-
-I sought to include studies that examined blood lipid levels as a risk factor for demenita outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
-I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
-Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Eligible studies screened participants for dementia at baseline and excluded any prevalent cases.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits were placed on the sample size of included studies.
-
-Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.
-
-Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status.
-No limitations were imposed on publication status, date, venue or language.
-
-<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
-
-<!-- TODO Any study using EHR - go back and extract codelists -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Exclusion criteria
-
-Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia).
-Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
-
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) were excluded.
-Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
-Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Validation of screening process
-
-Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
-assessment of consistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
-assessment of accuracy).
-
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
-[@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
-
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
-Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
-
-(ref:gwet-scaption) Ranges for Gwet's AC1
-
-```{r gwet-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of less than .9), a larger proportion of records would have been dual-screened.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Data extraction
-
-Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
-I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Grouping multiple reports into studies
-
-As part of the data extraction process, multiple records resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This was common in cases where multiple papers report results on the same cohort but at different time points.
-This process builds out the most comprehensive account of a given studies possible by incorporating information from all available records.
-
-This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Combining across groups
-
-In line with best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
-
-\begin{equation}
-N = N_1 + N_2
-  (\#eq:combiningGroups1)
-\end{equation}
-
-\begin{equation}
-Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
-  (\#eq:combiningGroups2)
-\end{equation}
-
-\begin{equation}
-SD = \sqrt{\frac{(N_1-1)SD_1^2 + (N_2-1)SD_2^2 + \frac{N_1N_2}{N_1 + N_2}(M_1^2 + M_2^2 - 2M_1M_2)}{N1 + N2 -1}}
-  (\#eq:combiningGroups3)
-\end{equation}
-
-&nbsp;
-
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Harmonisation of cholesterol measures
-
-<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
-not providing qratile cut-off values, not poviding numbers per group, etc.
---> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
-
-\begin{equation} 
-  mg/dL = mmol/L \times{} Z
-  (\#eq:lipidConversion)
-\end{equation}
-
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Following up with authors {#contacting-authors}
-
-Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Analysis of varying effect measures
-
-<!-- TODO Include formulae and informed assumptions  -->
-
-The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] If the outcome is rare, as is the case for dementia outcomes, the estimated prevalence of  odds and risk ratios will approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-time-at-risk in each treatment group.
-
-Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate.
-However, in this review, the small subset of studies reporting odds/risk ratios are synthesised separately to those reporting hazard ratios.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Risk-of-bias assessment {#risk-of-bias}
-
-A key aim of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
-To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
-
-There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
-Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
-
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the focus shifted from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-<!-- TODO CITATION NEEDED -->
-Finally, tools movide from assessing bias at the study level to considering each indivudal result reported seperately.
-For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that is not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
-
-In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
-The study design-specific tools are introduced and discussed in more detail in the following sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Randomised controlled trials
-
-Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assess the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
-Acceptable judgements for each domain include: "low risk", "some concerns", "high risk".
-Each of the five domains contains a series of signalling questions or prompts which guide the user through the tool.
-Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Non-randomised studies of interventions/exposures {#rob-tools-nrse}
-
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result.
-Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “low risk”, “moderate risk”, “serious risk” and “critical risk”.
-In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial.
-Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
-
-While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signalling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
-The motivation using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
-In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
-Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Mendelian randomisation studies
-
-At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
-Acceptable judgements for each fo the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Risk of bias due to missing evidence {#methods-rob-me}
-
-In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
-This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
-<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
-
-This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
-This is largely because the tool did not exist when the protocol was registered.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Analysis methods
-
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design.
-Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-<!-- TODO CITATION NEEDED -->
-
-Results were not combined across different study designs (i.e.
-RCTs were not combined in a meta-analysis with results from observational studies).
-The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Random-effects meta-analysis
-
-For results examining the effect of binary or continuous exposure (as opposed to categorical/dose-response, as discussed in the next section) on any dementia outcome, a random-effects meta-analysis model was used.
-Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
-The weight ($w$) assigned to each result (denoted as $y_i$) is then give as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
-
-Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:
-
-\begin{equation}
-\hat{y} = \frac{\sum{y_iw_i}}{\sum{w_i}}
-  (\#eq:rmaEstimate)
-\end{equation}
-
-\begin{equation}
-Var(\hat{y}) = \frac{1}{\sum{w_i}}
-  (\#eq:rmaVariance)
-\end{equation}
-
-&nbsp;
-
-Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
-Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
-Finally, where at least 10 results are available, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
-All models were implemented using the `metafor` R package.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Dose-response analyses
-
-Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
-for example, highest vs lowest quartile).
-<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
---> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
-In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
-This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.
-
-Studies were excluded from this analysis if the number of categories was less than three or if the necessary information for synthesis (cut-off points, number of participants and number of events per category) was not available.
-A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-<!-- TODO CITATION NEEDED --> The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
-Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
-
-When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Additional analyses
-
-Where there was evidence of heterogeneity between results included in a meta-analysis, I investigated this further using meta-regression against reported characteristics.
-_A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
-Syntheses with greater than 10 studies were assessed for heterogeneity across these covariates.
-<!-- TODO Need more here -->
-
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.
-<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Visualisation of results {#sys-rev-visualising-results}
-
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
-
-One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-<!-- TODO CITATION NEEDED --> In response to this criticism, I developed a new visualisation tool was designed to allow for the production of "paired" forest plots, as recommended by the ROB2 publication, where a risk-of-bias assessment is presented alongside it's corresponding numerical results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Assessment of added value of including preprints
-
-_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_
-
-Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)).
-As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
-
-Additionally, I followed identified preprints up after a two-year lag to investigate whether they had been subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
 ## Results

### 2021-10-13 05-Chp-CPRD-Analysis.Rmd
End of day

@@
 
-# Primary analysis of lipid regulating agents and dementia outcomes {#cprd-analysis-heading}
+# Primary analysis of lipid-regulating agents and dementia outcomes {#cprd-analysis-heading}
 
@@
 source("R/helper.R")
-knitr::read_chunk("R/04-Code-CPRD-Analysis.R")
+knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
@@
 <!-- ## Additional ideas -->
-
-<!-- TODO Need to add some information on the generation and use of propensity scores -->
 
@@
 
-<!-- TODO Check lipid-regulating vs lipid regulating -->
-
 <!-- TODO Check all fig/table cross-references evaluate -->
@@
 
-Electronic health record (EHR) databases are large collections of patients data, used to manage patient administration and care.
-Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standard set of codes.
+Electronic health record (EHR) databases are large collections of medical data, used to manage patient administration and care.
+Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standardised coding system.
 These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
@@
 
-This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across the UK.
-Using this data, the analysis presented in this chapter examined the effect of treatment which lower cholesterol levels, such as statins, on the risk of dementia and related outcomes.
-
-Little evidence for an effect of lipid regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of drugs called fibrates.
+This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across England.
+Using this data, the analysis presented in this chapter examined whether treatments which lower cholesterol levels (also known as lipid-regulating agents or LRA) of which statins are a prime example, affect the risk of all-cause dementia and related outcomes (Alzheimer's disease, vascular dementia and other dementias).
+
+Little evidence for an effect of lipid-regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipi-regulatin agent called fibrates.
 In contrast, I found an increased risk of vascular and other (i.e.
-non-Alzheimer's) dementia with lipid regulating agent use.
-
-This increased risk is unexpected, and is very likely to be due to the presence of bias in the analysis.
-This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, and so it appears as if statins are harmful.
-However, despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
+non-Alzheimer's) dementia was associated with lipid-regulating agent use.
+
+This increased risk in outcomes with a vascular element (e.g.
+vascular dementia) is unexpected, and is very likely to be due to the presence of bias in the analysis.
+This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, which makes it appear as if statins are harmful.
+Despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
 
@@
 
-In this Chapter, I present the results of an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid regulating agent (LRA) use and dementia outcomes.
-
+In this Chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
 The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
@@
 Firstly, it explicitly examines vascular dementia as an outcome.
-The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid regulating agents on the risk of vascular dementia.
+The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid-regulating agents on the risk of vascular dementia.
 As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
 
-Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia (as identified by the systematic review).
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox Proportional time-varying treatment indicator.
-This approach provides a evidence source at risk of a distinct set of biases due to the alternative analytical strategy that will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
+Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia as identified by the systematic review.
+Specifically, this involved a concerted effort to address immortal time bias though use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] This approach provides a evidence source at risk of a distinct bias due to the alternative analytical strategy.
+The results from this analysis will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
 
@@
 
-Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
@@
 
-Lists of relevant codes for each of the index events, exposures and outcomes used in the analysis were created. Each of these are described in more detail in the following sections.
+The index events, exposures and outcomes used in this analysis were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
+
+<!-- TODO, ensure code list position is accurately documented in  -->
 
@@
 This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
-Records pre-dating the 1995 cutoff were included in the original CPRD extract obtained for this analysis.
-However, these were excluded from the analysis as data quality and reliability is thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
+Records pre-dating the 1995 cut-off were included in the original CPRD extract obtained for this analysis.
+However, these were excluded from the analysis as data quality and reliability are thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
 
@@
 
-All events of interest were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
-
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: an outcome of interest; death; end of follow-up (29 February 2016); or last registration date with their GP practice.
-Participants were removed from the sample if they were less than 40 years of age, had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: (a) an outcome of interest; (b) death; (c) end of follow-up (29 February 2016); (d) last registration date with their GP practice; or (e) the last CPRD collection date for their practice.
+Participants were ineligble for our cohort if they were less than 40 years of age (as these patients are are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
 had less than one full day of follow-up).
@@
 
-A participant’s drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
+A participants drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
 We did however examine how often the initial drug class altered according to one of three criteria:
@@
 
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementia, and a composite all-cause dementia outcome.
-When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (see Figure \@ref(fig:decisionTreeFig)).
+We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome.
+When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Figure \@ref(fig:decisionTreeFig)).
 The diagnosis date of the outcome was determined by the first record of a relevant code.
@@
 (ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
-Note that an outcome of "Probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
+Note that an outcome of "probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
 
@@
 
-Participants were censored at the earliest of date of: diagnosis; death; transfer out of the study cohort; or end of follow-up (29th February 2016).
-
 &nbsp;
@@
 A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
+These are discussed in detail below and summarised in Table \@ref(tab:covariateDef-table).
+
+(ref:covariateDef-caption) Definition of covariates adjusted for in the Cox PR model.
+The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
+
+```{r covariateDef-table, echo = FALSE}
+```
 
 Demographic covariates adjusted for included age and gender.
-Age was calculated at date of entry into the cohort.
+Age was calculated at date of entry into the cohort, and adjusted for via its use as the time axis for the Cox model (see Section \@ref(cprd-time-axis)).
 Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
@@
 
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) command in STATA16.
+In this analysis, missing data were handled using a multiple imputation approach.[@sterne2009] Variables with missing observations were identified for inclusion in the imputation model.
+Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Using the MICE (Multiple Imputation by Chained Equations) command in STATA16, 20 imputed datasets were created.
 
@@
 This approach was necessary, as absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition, rather than being considered missing.[@wells2013strategies]
-
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
-As a sensitivity analysis, I preformed and compared the results of both methods,[@hughes2019] to investigate the impact of multiple imputation on the results.
+statin use or dementia) was assumed to indicate absence of the treatment/condition rather than being considered missing.[@wells2013strategies]
 
@@
 
-A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined, in general terms, as:
+A Cox proportional hazards (PR) model was used to estimate the effect of statins on dementia outcomes. Cox PR models are defined in general terms as:
 
@@
 
-As the values of $b_i$ increases, value of $exp(b_i)$ (i.e. the hazard ratio) increases in tandem, thus reducing the survival time, $t$.
-
 A Cox PR model was chosen for this analysis as it inherently accounts for the length of time participants spend in each exposure group.
-Using this approach, time-at-risk can be properly attributed, thus mitigating the impact of immortal time bias.
+Using this approach, time-at-risk can be properly attributed to the appropriate exposure group, thus mitigating the impact of immortal time bias.
 This is discussed in detail in the following section.
@@
 
-<!-- IDEA Need to describe accounting for clustering here: id it somethings I did? See other thesis for clustering by practice -->
+<!-- IDEA Need to describe accounting for clustering here: id it something I did? See other thesis for clustering by practice -->
 
@@
 
-Immortal time bias covers two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] For example, if the unexposed group are followed from a cholesterol test result, while the exposed group is followed from date of LRA prescription, any events that occur in the exposed group prior to the exposure event will be inappropriately excluded from the analysis.
+Immortal time bias describes two distinct but related types of bias.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] Following the example displayed in the figure, the unexposed group are followed from the date of a diagnosis, while the exposed group is followed from date of a prescription.
+In this scenario, the time between diangosis and prescription for the exposure group is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
 
 The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the exposure date, and any events occurring within it, is inappropriately assigned to the exposed group.
-This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
-
-This analysis is primarily concerned with the second presentation of immortal time bias, as all participants were followed from a common index date (earliest of: date of raised cholesterol test results; hypercholesterolemeia diagnosis; or LRA prescription).
-To address the potential for this second form of immortal time bias in the analysis, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-Under this approach, all patients start in the unexposed group, & contribute time-at-risk until they are prescribed a lipid regulating agent and move into the exposed group.
-Note, patients for whom prescription of a lipid regulating agent was the index event only contribute time to the exposed group (i.e.
-they enter the cohort and move into the exposed group on the same day).
-
-<!--------------------------------------------------------------------------->
+It occurs when the exposure time prior to the prescription, and any events occurring within it, is inappropriately assigned to the exposed group.
+
+&nbsp;<!----------------------------------------------------------------------->
+
 (ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
@@
 ```
-<!--------------------------------------------------------------------------->
-
-### Time axis
+
+&nbsp;<!----------------------------------------------------------------------->
+
+This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
+Both presentations of immortal time bias appear in the literature on the relationship of statins and dementia, as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)
+
+<!-- TODO May need to crosslink a bit better -->
+
+This analysis attempted to address this issue by following all participants from a common index date (defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemeia diagnosis; or (c) LRA prescription).
+Following a recommended approach to addressing the second form of immortal time bias, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
+
+Under this approach, all patients start in the unexposed group and contribute time-at-risk until they are prescribed a lipid-regulating agent and move into the exposed group.
+Note, patients for whom prescription of a lipid-regulating agent was the index event only contribute time to the exposed group (i.e.
+they enter the cohort and move into the exposed group on the same day).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Time axis {#cprd-time-axis}
 
@@
 
-The primary analysis examined the effect of a lipid regulating agent on dementia risk, stratified by outcome and drug class.
+The primary analysis examined the effect of a lipid-regulating agent on dementia risk, stratified by outcome and drug class.
 To assess the robustness of the results, a number of sensitivity analyses were performed.
@@
 
+#### Complete case vs imputed data
+
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+As a recommended sensitivity analysis,[@hughes2019] I preformed and compared the results of both methods, to investigate the impact of multiple imputation on the results.
+
 #### Control outcomes
 
-In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on two additional control outcomes.
+In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on three additional control outcomes.
 The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
-Negative outcomes are those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph describing an ideal negative outcome).
-
+
+Negative outcomes are defined as those without a likely causal path between the exposure and outcome (see Figure \@ref(fig:negativeOutcome) for a directed acyclic graph, or DAG, describing an ideal negative outcome).
 Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
 Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-
-Due to the wealth of data available on statins as a lipid regulating agent, control outcomes were chosen in reference to this drug class.
-Muscular backpain was chosen as a negative control outcome in this analysis.
-Despite observational analyses suggesting a link between statins and muscle pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
-As such, if statins are not associated with backpain in this analysis, then confidence in the results for the dementia outcomes is increased.
-
-Additionally, incident ischemic heart disease was included as a positive control outcome, given the well-established protective effect of lipid-lowering treatment, via statins, on the risk of this condition.[@collins2016a] Similar to the backpain outcome, if the analysis strategy can reproduce this known protective association, this will provide evidence that potential confounders have been sufficiently adjusted for.
-
-<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
-
-<!-- TODO Need to add bit to this section and to results on outcome for Type 2 Diabetes outcome -->
-
-<!----------------------------------------------------------------------------->
-(ref:negativeOutcome-cap) Causal diagram showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
+Due to the wealth of data available on statins as a lipid-regulating agent, I chose three control outcomes were chosen in reference to this drug class: back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:negativeOutcome-cap) Causal diagram (directed acyclic graph) showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
 Note the absence of any arrow between $X$ and $N$.
@@
 
-(ref:negativeOutcome-scap) DAG of ideal negative outcome
-
-```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:negativeOutcome-cap)', out.width='100%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
+(ref:negativeOutcome-scap) Causal diagram for ideal negative outcome
+
+```{r negativeOutcome, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:negativeOutcome-cap)', out.width='80%', fig.scap='(ref:negativeOutcome-scap)', message=FALSE, warning = FALSE}
 library(dagitty)
@@
 
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","negativeOutcome.png"),
+ggplot2::ggsave(filename = file.path("figures",
+                                     "cprd-analysis",
+                                     "negativeOutcome.png"),
   dagitty::dagitty("dag {
@@
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
+Despite observational analyses suggesting a link between statins and muscular pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
+This suggests that muscular backpain would be suitable for use as a negative control outcome in this analysis.
+Under this approach, if statin use is found to be associated with muscular backpain in this analysis, this suggests the presence of residual confounding and reduces my confidence in the results for the dementia outcomes.
+
+Similarly, incident ischemic heart disease and Type 2 diabetes were included as a protective and harmful positive control outcome, respectively.
+The protective effect of lipid-lowering treatment, via statins, on the risk of ischemic heart disease is well-established, [@collins2016a] while there is growing evidence for an increased risk of Type 2 diabetes with statin use.[@collins2016a; @macedo2014; @smit2020] Similar to the negative outcome, if the analysis strategy can reproduce these known associations, this will provide evidence that potential confounders have been sufficiently adjusted for.
+
+<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-To observe the effect of adjusting for additional covariates, I ran a model unadjusted except for age (captured via the time axis in the Cox model) and gender, and compared the results with the full adjusted model.
-
-&nbsp;
+To observe the effect of adjusting for additional covariates, I ran two additional models unadjusted except for: (a) age; and (b) age and gender.
+The results of these models was then compared the results with the fully adjusted model.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 The first stratified by year of entry into the cohort in an attempt to assess for time period effects.
-The second removed participants who may have been pregnant  (coded as under 55 and female) to assess the robustness of the estimates, as statins are contraindicated in pregnancy, .[@karalis2016]
+The second removed participants who may have been pregnant (coded as under 55) to assess the robustness of the estimates, as statins are contraindicated in pregnancy.[@karalis2016]
 
@@
 
-#### Impact of dementia code lists
-
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a previous study published in 2009 by Smeeth _et al_.[@smeeth2009]
-
-This previous study used a propensity matching approach to estimate the association of statins with a range of outcomes, and found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
-
-The code lists used were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
-
-&nbsp;
+#### Comparing dementia codelists
+
+As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a published study by Smeeth _et al_.[@smeeth2009]
+
+This previous analysis used a propensity matching approach to estimate the association of statins with a range of outcomes in The Health Improvement Network (THIN) database, a alternative source of English electronic health records which has substantial overlap with the CPRD.[@carbonari2015] The code lists used in this analysis were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+```{r cprdCharacteristics-setUp, echo = FALSE}
+```
+
 ```{r attritionFigure, include = FALSE}
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. Most attrition was due to the absence of an index event of interest.
+(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. The largest cause of attrition was the absence of an index event of interest.
 
@@
 The median participant age at index was `r age_text` and participants were followed up for a median of `r fu_text`.
-During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementia: Table \@ref(tab:followUp-table)).
-The distribution of baseline characteristics across the seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+During follow-up, an all-cause dementia diagnosis was recorded for `r comma(p1[1,2])` patients  (`r comma(p1[2,2])` probable AD, `r comma(p1[3,2])` possible AD, `r comma(p1[4,2])` vascular dementia, `r comma(p1[5,2])` other dementias).
+
+The number of events, time-at-risk and crude rates for each drug class, tabulated by dementia outcome, are shown in Table \@ref(tab:followUp-table).
+A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
+I excluded the "Ezetimibe and statins" (n=`r eze_sta_n`) and "Nicotinic acid groups" (n= `r nag_n``) classes from subsequent class-based subgroup analyses based on the extremely small number of participants in these groups.
+Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
 
 \blandscape
-<!--------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:followUp-caption) Summary of number of events, years at risk and crude rates per 100,000 participant-years-at-risk stratified by dementia outcome and drug class of interest.
+
+(ref:followUp-scaption) Crude rates, stratified by outcome and drug class of interest.
+
+```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
+```
 (ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
@@
 
-A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent analysis based on the extremely small number of participants in these groups (N=127 & N=168 respectively; see Table \@ref(tab:cprdCharacteristics-table)).
-Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
-
 <!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
 
-<!-- IDEA Described the average length of time between patients being prescribed a statin and being diagnosed with dementia -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
+The distribution of baseline characteristics across the remaining seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
+Note due to the experimental design, the median year of entry is expected to be later for those not prescribed an LRA, as this exposure group is more likely to include those who entered into the cohort towards the end of study window (as these people had less follow-up time in which to be prescribed an LRA).
+
+The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
+
+&nbsp;<!----------------------------------------------------------------------->  
 (ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
@@
 ```
-<!--------------------------------------------------------------------------->
-
-&nbsp;
-
-The stopping, addition and switching of drug classes was common across all drug classes (Table \@ref(tab:cprdSSA-table)).
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Crude rate ratios per 100,000 participant-years-at-risk were calculated for each outcome and class of interest and are presented in Table \@ref(tab:followUp-table).
-
-\blandscape
-
-<!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary
-
-(ref:followUp-scaption) followUp
-
-```{r followUp-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-\elandscape
-
 The results of the primary analysis using the fully adjusted Cox proportional hazards model with participant age as the time scale are presented for each drug/outcome combination in Figure \@ref(fig:cprdPrimary).
 
-For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on it's large size relative to the other drug classes.
+For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on its large size relative to the other drug classes.
 
@@
 
-My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared with no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared to no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementia (`r othdem_text`).
+In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementias (`r othdem_text`).
 Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
@@
 
-For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), but the magnitude of the association was not as extreme as that observed for the vascular dementia subgroup.
+For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), which lies between the associations for the Alzheimer and non-Alzheimer dementia outcomes as would be expected.
 There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
@@
 <!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) Comparison of complete case versus imputed data analyses.
+(ref:completeCaseFig-cap) Comparison of analyses using the complete case versus imputed cohorts.
 
@@
 For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
-However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`).
+However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
 
@@
 The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
-
 These models were used to estimate the impact of adjustment for additional covariates.
@@
 
-Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the Probable AD outcome.
+Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the probable AD outcome.
 In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
@@
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosisTypeFig-cap) Analysis of any lipid regulating agent on Probable AD outcome, stratified by grouped year of cohort entry.
+(ref:diagnosisTypeFig-cap) Analysis of any lipid-regulating agent on probable AD outcome, stratified by grouped year of cohort entry.
 
@@
 
-On the assumption that this variation could be caused by changes in the frequency of codes used to define Probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
-While the total frequency of any dementia outcome declines in more recent strata, likely due to the limited follow-up inherent to these groups, the decline in frequency is relatively constant across all dementia subtypes.
+On the assumption that this variation could be caused by changes in the frequency of codes used to define probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
+While the frequency of outcomes declines in more recent strata, likely due to the limited follow-up inherent to these groups, this decline in frequency is relatively constant across the dementia subtypes.
 
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
 (ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
@@
 ```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
 (ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
@@
 ```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+When stratifying by statin properties, hydrophilic statins were less harmful in the any, vascular and other dementias outcomes compared to lipophilic statins (Figure \@ref(fig:statinTypeFig)).
 Additionally, in the AD outcomes, hydrophilic statins were associated with a small reduction in risk, compared to the weak evidence for an effect for lipophilic statins.
@@
 
-#### Comparing codelists {#comparing-codelists}
+#### Impact of dementia code lists {#comparing-codelists}
 
@@
 
-When using the Smeeth et al code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's dementia outcomes respectively.
+When using the Smeeth _et al._ code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's ("other") dementia outcomes, respectively.
+
+The authors found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
 
 However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the Probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
+While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
 Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
+
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are used to define competing outcomes (e.g.
+AD vs non-AD dementia).
 
@@
 
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are competing (e.g. AD vs non-AD dementia).
-
 &nbsp;
@@
 
-Lipid-regulating agents showed little evidence of an effect on probable and possible Alzheimer's disease when compared with no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementia diagnosis.
-The effect observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementia, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
-
-The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except Probable AD, no variation across grouped year of entry was observed.
-When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins.
-
-<!-- QUESTION Why are fibrates different? -->
-
-<!-- TODO Check comments from co-authors have been addressed for this chapter?  -->
-
-<!-- QUESTION How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained -->
-
-<!-- IDEA Discuss impact of consulation rate and effect on ascertainment bias - only adjusting for prior ascertainment rate, which could change once prescribed statins.
-However, would see increase effect across all sub-types, and ascertainment bias less likely for important high-impact events such as IHD -->
-
-&nbsp;
-
-<!--------------------------------------------------------------------------->
+Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnosis.
+The estimate observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
+For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+
+The effect estimates were robust to the exclusion of potentially pregnant participants, and for all outcomes except probable AD, no variation across grouped year of entry was observed.
+When looking at the statin subgroup alone, statin properties appeared to have a modifying effect, with hydrophilic statins being less harmful in the any, vascular and other dementias outcomes compared to lipophilic statins.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Comparison with existing literature
+
+__[Feedback requested: How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained and only refer to ?]__
+
+__Statins and all-cause dementia__
+
+This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
+Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
+
+Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
+
+&nbsp;
+
+__Statins and Alzheimer's disease__
+
+Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
+Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
+
+Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
+
+&nbsp;
+
+__Statins and vascular/other dementia__
+
+Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
+A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
+When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
+
+&nbsp;
+
+__Other drug classes__
+
+Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
+
+One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
+
+A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
+Note that this study was published in 2020 and so was not included in the review.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Section \@ref(discussion-heading).
-
-A likely explanation for the observed increased risk of vascular and other dementia with lipid regulating agent use is residual confounding by indication.
+For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Chapter \@ref(tri-heading).
+
+#### Confounding by indication
+
+A likely explanation for the observed increased risk of vascular and other dementias with lipid-regulating agent use, and an important limitation of this analysis, is residual confounding by indication.
 While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference language, statins and dementia are said to be d-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
-
-<!----------------------------------------------------------------------------->
+In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
+
+&nbsp;<!----------------------------------------------------------------------->  
 (ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
@@
 
-```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:indicationBias-cap)', out.width='100%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
+```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:indicationBias-cap)', out.width='80%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
 
@@
 ```
-<!----------------------------------------------------------------------------->
-
-In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins (or another lipid regulating agent) but also represent a vascular risk factor that contributes to the development of the vascular dementia.
+&nbsp;<!----------------------------------------------------------------------->
+
+In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins but also represent a vascular risk factor that contributes to the development of the vascular dementia.
 
@@
 The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-This is supported by the increasingly harmful effect moving from Probable/Possible AD to other dementia to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
-This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementia codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
-
-A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Following control for confounding by indication through use of a trial emulation analysis, the expected protective effect of statins was observed.
+This is supported by the increasingly harmful effect moving from probable/Possible AD to other dementias to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
+This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementias codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
+
+A review of other available literature suggests that this observation (a harmful effect of lipid-regulating agents on vascular-related outcome) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
 
 Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-I also adjusted for several additional potential baseline variables.
-However, important confounding variables for which I have not adjusted could include genetic factors.
-A recent preprint of a study in the UK Biobank demonstrated that an Alzheimer’s disease polygenic risk score was associated with an increased risk of vascular dementia, and also with an increased frequency of self-reported raised cholesterol levels, a diagnosis of hypercholesterolaemia, and a history of taking lipid-regulating agents such as statins or ezetimibe.[@korologou-linden2020]
 
 On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
-It is possible that previous research identified a similar effect to this analysis, and via a publication bias mechanism, these results did not make it into the evidence base.
+It is possible that previous research encountered similar methodological issues to this analysis, and via a publication bias mechanism, the results from these analyses did not make it into the evidence base.
 
@@
 
-In summary, despite best efforts to account for strong confounding, participants prescribed a lipid regulating agent likely have a different vascular risk profile that those who are not, which may induce a spurious harmful association between lipid regulating agent use and vascular dementia outcomes.
+#### Time period effect in probable Alzheimer's disease
+
+The time period effect observed for the Alzheimer's disease outcome, where statins appear more protective in participants who entered the cohort at a later date, is an interesting result.
+An expected cause was an change in how different dementia sub-types were diagnosed over time, but no corresponding inverse trend in any of the other dementia outcomes.
+For example, if the observed trend was due to increasing differential misclassification with vascular dementia, then we would expect vascular dementia to appear increasingly harmful in more recent time periods which is not the case.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Statin properties
+
+The observation that hydrophilic statins appear more protective than their lipophilic counterparts, runs counter to the theory that lipophilic drugs are able to cross the blood brain barrier.
+However, it does agree with previous findings for this comparison.
+
+Additionaly, the relative precision of the two groups is expected, as the two most commonly prescribed statins in the UK are lipophilic (simvastatin and atorvastatin). <!-- TODO CITATION NEEDED -->
+
+An initial interpretation for the discrepancy was that lipophilic statins may as a class be stronger, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
+However, the statin with the strongest lipid lowering effect available via the NHS, rosuvastatin, is hydrophobic.
+
+however, two of the most widely used
+
+__[Yoav: are there are particular indications/contraindications for statins with different properties?]__
+
+* Blood brain barrier
+*
+*
 
@@
 
-However, the findings of this analysis are subject to several limitations.
+However, the findings of this analysis are subject to several limitations in addition to the confounding by indication discussed above.
 There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
@@
 Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+<!-- though there is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database and does not add a substantial administrative burden.[@russell2013] -->
 
 Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis.
-This is a particular challenge in comparing research across different time-periods and coding systems, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
-
-<!-- IDEA A further limitation is the possibility of time-varying confounding  Either deal with this issue here, or keep the section above dealing with time-varying confounding. -->
-
-<!-- IDEA there is also the potential for reverse causation in this analysis.
-Dementia and associated conditions have a long prodromal period, during which preclinial disease could cause indications for the prescription of a lipid-regulating agent.
--->
-
-<!--------------------------------------------------------------------------->
-
-<!-- ### The effect of total cholesterol or LDL-cholesterol on LRA prescription -->
-
-<!-- It would be fair to assume that the baseline total cholesterol/LDL-cholesterol would at least in part predict the likelihood of someone being prescribed a statin.  -->
-
-<!-- However, this is not the case.
-Baseline cholesterol level are predicted to be a poorer instrument for than QRISK2 score,[@hippisley-cox2008] which estimates a patients' 10-year risk of a cardiovascular event.
-Current NICE guidelines state that those with a QRISK score of 10% or higher, and in whom lifestyle modification is ineffective/inappropriate, should received a lipid regulation agent.
-However, this analysis could not find any effect of QRISK2 scores on statins prescription levels at 6 months.
--->
-
-<!-- Need to cite Lauren's eventual paper here focusing on QRISK2, but also display a RD analysis of TC/LDL-c levels here on statins at 6 months.
-Need also to check, as Lauren mentioned she found some evidence that there is a relationship in practices that actually did what they should.
--->
-
-<!-- As expected, in a confirmatory analysis using lipid levels, there was no association between the most recent total cholesterol or LDL-cholesterol reading in the CPRD and the treatment, indicating that adjusting for this variable was not required.
--->
-
-<!-- This hasn't been done! Plus I do not think this is the case -->
-
-<!--------------------------------------------------------------------------->
-
-<!--------------------------------------------------------------------------->
-<!-- &nbsp; -->
-
-<!-- IDEA Issues with large-scale EHR databases -->
-
-<!-- __Missclassification__ -->
-
-<!-- __Coding quality in the CPRD__ -->
-
-<!-- Lots of things influence prevalence: historic trends, availability of good codes -->
-
-<!-- There is the possibility of ascertainment bias -  -->
-
-<!-- There is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database, and does not add a substantial administrative burden.[@russell2013] -->
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
+This is a particular challenge in comparing research across different time-periods and coding systems,
+
+A further limitation stems from uncontrolled confounding due to genetic factors.
+Number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+We were unable to control for ApoE genotype in this analysis as we did not have access to genetic data on participants.
+As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.
+
+Finally, as with many studies of dementia, there is a risk of reverse causation in our analysis.
+Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.
 
@@
 
-All code, Read codelists and summary statistics (i.e.
+The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
+In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c] As such, all code, Read code lists and summary statistics (i.e.
 the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: XXXX-XXXX).
+as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: __TBC__).
 <!-- TODO Archive on Zenodo.
@@
 
-The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c]
-
-Additionally, to help ensure accurate reporting of this analysis, the Strengthening the Reporting of Observational Studies in Epidemiology (STROBE) reporting guidelines were used[@vandenbroucke2007] (see Appendix \@ref(hold) for the STROBE checklist).
-<!-- QUESTION Maybe don't include the whole thing, or apply it to this thesis rather than the paper -->
-
-This open approach will enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to readily build on that presented here.
+This open approach should enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to build on that presented here.
 
@@
 
-This chapter has provided new evidence on the potential repurposing of lipid-regulating agents for the prevention of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+This chapter has provided new evidence on the association of lipid-regulating agents with incidence of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
 It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
@@
 It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
-However, lipid regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
+However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
 In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
@@
 Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of treatment.
+In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of lipid-regulating treatment.
 

### 2021-10-13 06-Chp-IPD-Analysis.Rmd
End of day

@@
 source("R/helper.R")
-knitr::read_chunk("R/05-Code-IPD-Analysis.R")
+knitr::read_chunk("R/06-Code-IPD-Analysis.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format

### 2021-10-13 manuscripts/cprd/manuscript.Rmd
End of day

@@
 __Background:__ There is some evidence that circulating blood lipids play a role in the development of Alzheimer's disease (AD) and dementia.
-These modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for the prevention of dementia.
-Here, we test the association between lipid-regulating agents and risk of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), a United Kingdom electronic health record database.
+These modifiable risk factors could be targeted by existing lipid-regulating agents, including statins, for dementia prevention.
+Here, we test the association between lipid-regulating agents and incidence of dementia and related conditions in the Clinical Practice Research Datalink (CPRD), an United Kingdom-based electronic health record database.
 
-__Methods:__ A retrospective cohort study was performed using routinely collected data from the CPRD (January 1995 and March 2016).
+__Methods:__ A retrospective cohort study was performed using routinely collected CPRD data (January 1995 and March 2016).
 Multivariable Cox proportional hazard models, allowing for a time-varying treatment indicator, were used to estimate the association between seven lipid-regulating drug classes (vs.
@@
 
-* A large cohort of patients from the Clinical Practice Research Datalink electronic health record database was assembled to examine the association of lipid-regulating agents, such as statins, with dementia outcomes.
+* A large cohort of patients from the Clinical Practice Research Datalink (CPRD) electronic health record database was assembled to examine the association of lipid-regulating agents, such as statins, with dementia outcomes.
 
-* Little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful association with all-cause, vascular and other dementias.
+* There was little evidence that lipid-regulating agents were associated with Alzheimer’s disease, but there was some evidence for a harmful association with all-cause, vascular and other dementias.
 In all cases, the estimated associations were driven by the any statin subgroup, which comprised most participants in our cohort.
@@
 An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Supplementary Materials 1.
-This study was reported in line with the RECORD guidelines (Supplementary Table 1).[@nicholls2016record]
+This study was reported in line with the RECORD guidelines (Supplementary Materials 2).[@nicholls2016record]
 
@@
 
-Participants were included in our study cohort if their record contained any of the following index events: (a) a Read code for a diagnosis of hypercholesterolemia or related condition; (b) a Read code for prescription of a LRA (such as statins); (c) a total cholesterol test result of >4mmol/L; (d) or a low-density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
+Participants were included in our study cohort if their record contained any of the following index events: (a) a code for a diagnosis of hypercholesterolemia or related condition; (b) a code for prescription of a LRA (such as statins); (c) a total cholesterol test result of >4mmol/L; (d) or a low-density lipoprotein cholesterol (LDL-c) test result of >2mmol/L.
 
@@
 These variables were selected as potential confounders between dementia outcomes and use of a LRA.
-All covariates were determined at the index date and definitions for each can be found in Supplementary Table 2.
+All covariates were determined at the index date and definitions for each can be found in Supplementary Table 1.
 
@@
 During follow-up, an all-cause dementia diagnosis was recorded for `r format(p1[1,2], big.mark = ",")` patients  (`r format(p1[2,2], big.mark = ",")` probable Alzheimer's disease, `r format(p1[3,2], big.mark = ",")` possible Alzheimer's disease, `r format(p1[4,2], big.mark = ",")` vascular dementia, `r format(p1[5,2], big.mark = ",")` other dementia).
+
 The number of events, time-at-risk and crude rates for each drug class, tabulated by dementia outcome, are shown in Table \@ref(tab:followUp-table).
 Most participants (`r percentage.statins`) prescribed a lipid-regulating agent were prescribed a statin.
-We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" classes from subsequent subgroup analyses based on the extremely small number of participants in these groups (Table \@ref(tab:followUp-table)).
+We excluded the "Ezetimibe and statins" and "Nicotinic acid groups" drug classes from subsequent subgroup analyses based on the extremely small number of participants in these groups (Table \@ref(tab:followUp-table)).
 The distribution of baseline characteristics across the remaining seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-The stopping, addition and switching of drug classes was common across all exposure groups (Supplementary Table 3).
+The stopping, addition and switching of drug classes was common across all exposure groups (Supplementary Table 2).
 
@@
 In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementias (`r othdem_text`).
-Again, the observed estimate was driven mainly by the any statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
+Again, the observed estimate was driven mainly by the any statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementias.
 
@@
 
-Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs".[@ancelin2012] echoing the distribution of participants in our analysis.
+Much of the existing literature focuses on the association of statins alone with neurodegenerative outcomes, with other lipid-regulating agents being grouped as "non-statin cholesterol-lowering drugs",[@ancelin2012] echoing the distribution of participants in our analysis.
 
@@
 
-Our additional analyses of statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
+Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
 
@@
 This would explain the increased risk for the ischaemic heart disease outcome, for which statins are known to be protective, whilst almost no association was observed with the backpain outcome, indicating that most of the uncontrolled confounding is likely to be related to vascular factors.
-Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is unlikely to be vascular,[@collins2016a; @macedo2014; @smit2020] Further supporting evidence comes from the increasingly harmful association observed when moving from the probable and possible Alzheimer's disease outcome to the other dementias outcome, and finally to the vascular dementia outcomes.
+Additionally, we obtained the expected harmful result for Type 2 diabetes, where statins' mechanism of action on this outcome is unlikely to be vascular.[@collins2016a; @macedo2014; @smit2020] Further supporting evidence comes from the increasingly harmful association observed when moving from the probable and possible Alzheimer's disease outcome to the other dementias outcome, and finally to the vascular dementia outcomes.
 This pattern suggests that the strength of the residual confounding by indication increases as the proportion of cases with a vascular component in an outcome definition increases.
 A review of other available literature suggests that this observation (a harmful effect of lipid regulating agents on vascular-related outcome due to confounding by indication) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Control for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischaemic heart disease outcome used in our analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
 
 A secondary limitation is the potential for differential outcome misclassification based on the exposure, as we cannot exclude the possibility that for people with memory complaints, a diagnosis of vascular dementia might be made more frequently than Alzheimer’s disease if their medical records contain prescriptions for lipid-regulating agents.
-Further, there is also the potential for non-differential misclassification of the outcome ,based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+Further, there is also the potential for non-differential misclassification of the outcome, based on the use of electronic health records to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 
@@
 
-This is most likely to explain the unexpected increase in risk of vascular dementia associated with statin use.
+This is likely to explain the unexpected increase in risk of vascular dementia associated with statin use.
 Future research should aim to address these biases using newer methods such as a trial emulation analysis.
@@
 __Data/code availability__
+
 This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
@@
 __Conflict of interest statement__
+
 None declared.
@@
 <!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary of person-time at risk and number of events by exposure group.
+(ref:followUp-caption) Summary of number of events, participant-time-at-risk and crude rates by drug class and dementia outcome.
 
@@
 (ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
+
+```{r cprdCharacteristics-setUp, echo = FALSE}
+```
 

### 2021-10-13 manuscripts/cprd/supp-materials.Rmd
End of day

@@
 
-# Supplementary tables {#supp-tab}
-
-## Supplementary Table 1: RECORD Reporting Guidelines {#supp-tab-strobe}
+## Supplementary Material 2: RECORD Reporting Guidelines {#supp-tab-strobe}
 
@@
 
-## Supplementary Table 2: Definition of exposures and covariates
+# Supplementary tables {#supp-tab}
+
+## Supplementary Table 1: Definition of exposures and covariates
 
@@
 
-## Supplementary Table 3: Adherence and switching by drug class
+## Supplementary Table 2: Adherence and switching by drug class
 

### 2021-10-13 R/05-Code-CPRD-Analysis.R

@@ -67,7 +67,7 @@ if (doc_type == "docx") {
 }
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- cprdCharacteristics-table
+# ---- cprdCharacteristics-setUp
 
 table1 <-
   read.csv(here::here("data", "cprd", "table1.csv"), header = FALSE)
@@ -78,9 +78,9 @@ table1 = table1[-1,]
 colnames(table1)[1] <- " "
 
 table1[1, 1] <- "Sample size (N)"
-table1[2, 1] <- "Year of \\newline cohort entry \\newline (median)"
+table1[2, 1] <- "Year of cohort entry \\newline (median)"
 table1[3, 1] <- "Female"
-table1[4, 1] <- "Age at \\newline cohort entry \\newline (median)"
+table1[4, 1] <- "Age at cohort entry \\newline (median)"
 table1[5, 1] <- "CAD"
 table1[6, 1] <- "CBS"
 table1[7, 1] <- "CVD"
@@ -106,18 +106,24 @@ table1[24, 1] <- "Follow up \\newline(years; median)"
 table1.copy <- table1
 
 table1 <- table1[, c(1, 10, 7, 9, 2:6, 8)]
-table1_disp <- table1[c(1:16, 22, 17:18, 23), ]
 
-# Quick check to ensure data quality
-t <- table1_disp[1, 2:10]
-t <- as.numeric(table1_disp[1, 2:10])
+eze_sta_n <- table1[1,7]
+nag_n <- table1[1,9]
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- cprdCharacteristics-table
 
-if (t[1] - sum(t[2:9]) != 0) {
+table1_disp <- table1[c(1:16, 22, 17:18, 23), c(1:6,8,10)]
+
+#Quick check to ensure data quality
+t <- table1_disp[1, 2:8]
+t <- as.numeric(table1_disp[1, 2:8])
+
+if (t[1] - sum(t[2:7], as.numeric(eze_sta_n), as.numeric(nag_n)) != 0) {
   stop("cprdCharacteristics-table: Sum of subgroups != Total sample size")
 }
 
[…]

### 2021-10-13 R/helper.R

@@ -238,11 +238,18 @@ todo <- function(fp,...) {
   
 }
 
-todo_report <- function(){
+todo_report <- function(fp){
+  
+  if (!hasArg(fp)) {
+    text <- todor::todor(output = "markdown")
+    
+  } else {
+    text <- todor::todor_file(fp,output = "markdown")
+  }
+  
+  
   
   tmp <- tempfile()
-  
-  text <- todor::todor(output = "markdown")
   
   writeLines(text,paste0(tmp,".Rmd"))
   

### 2021-10-20 01-Chp-Background.Rmd
End of day:

@@
 ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circualting more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
 

### 2021-10-20 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 output:
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
   bookdown::word_document2: 
@@
       number_sections: false 
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
   bookdown::html_document2: default
@@
 
+This chapter represents an extended version of a preprint manuscript, a copy of which is available in Appendix \@ref(published-papers).
+
 <!--------------------------------------------------------------------------->
@@
 
-An *a priori* protocol for this study was published, [@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
+An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
 
@@
 
-Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.
+Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.[@walker2016] The blood lipid cut-offs were based on NIHR-recommended levels at the time the protocol was written.
 These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
@@
 
-(ref:covariateDef-caption) Definition of covariates adjusted for in the Cox PR model.
-The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
-
-```{r covariateDef-table, echo = FALSE}
-```
+&nbsp;
+
+<!-- TODO May need to reword this table slightly as taken from Venexia walkers -->
+
+<!----------------------------------------------------------------------------->
+(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model.
+The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
+
+(ref:covariateDef-scaption) Covariates adjusted for.
+
+(ref:covariateDef-cell1) Charlson index implemented using Read code lists.[@khan2010] Code lists based on those by Taylor et al.[@taylor2016]
+
+(ref:covariateDef-cell2) Most recent of recorded value (current, former or never) or Read code indicating a recorded value. Code lists based on those by Wright et al.[@wright2017]
+
+```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
-A variable indicating grouped year of entry into the cohort (<2000, 2000-2004, 2005-2009, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
+A variable indicating grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
 To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
@@
 
+&nbsp;
+
 #### Complete case vs imputed data
@@
 As a recommended sensitivity analysis,[@hughes2019] I preformed and compared the results of both methods, to investigate the impact of multiple imputation on the results.
+
+&nbsp;
 
@@
 
-As detailed in the introduction, the properties of statins may be important in their effect, based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins) in the Introductory Chapter).
-
-To explore whether any observed associations in the statin analysis varied by statin property, a sensitivity analysis was performed, stratifying by statin lipophilicity.
-
-<!-- TODO Previous review of the evidence have recommended that future studies take account of statins varying ability to cross the BBB [@shepardson2011] -->
-
-&nbsp;
+As detailed in the introduction, the properties of statins may be important in their effect based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] To investigate this, I further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" (n=`r eze_sta_n`) and "Nicotinic acid groups" (n= `r nag_n``) classes from subsequent class-based subgroup analyses based on the extremely small number of participants in these groups.
+I excluded the "Ezetimibe and statins" (n=`r eze_sta_n`) and "Nicotinic acid groups" (n= `r nag_n`) classes from subsequent class-based subgroup analyses based on the extremely small number of participants in these groups.
 Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
@@
 
-(ref:diagnosisTypeFig-scap) Sensitivty analus
+(ref:diagnosisTypeFig-scap) Sensitivity analysis: grouped year of entry
+
+<!-- TODO Need to fix grouping labels here -->
 
@@
 
-The authors found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
-
-However, comparison of the results using the two sets of code lists was deemed less useful following a comparison of the codes used.
-While all of the codes used to define Alzheimer’s in the Smeeth paper are included in the probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
-Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
-
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are used to define competing outcomes (e.g.
-AD vs non-AD dementia).
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
-The joining lines showing the overlap between the categories in the two analyses.
-
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
-
-```{r sankeydiagram, include=FALSE}
-```
-
-```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
-knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
-
-### Comparison with existing literature
-
-__[Feedback requested: How much should I be cross-referencing with the systematic review at this stage? Or should I keep it self-contained and only refer to ?]__
-
-__Statins and all-cause dementia__
-
-This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
-
-Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
-
-&nbsp;
-
-__Statins and Alzheimer's disease__
-
-Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
-Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
-
-Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
-
-&nbsp;
-
-__Statins and vascular/other dementia__
-
-Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
-A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
-When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
-
-&nbsp;
-
-__Other drug classes__
-
-Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
-
-One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
-
-A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
-Note that this study was published in 2020 and so was not included in the review.
+<!-- TODO Need to discuss fibrate results as part of qualitative triangulation -->
 
@@
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
-For a comparison of the result presented above with those from the systematic review (Chapter \@ref(sys-rev-heading)) and the individual patient data analysis (Chapter \@ref(ipd-heading)), see Chapter \@ref(tri-heading).
+For a detailed comparison of the result presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
+
+__[Feedback requested: How much should I be cross-referencing with the systematic review at this stage?
+Or should I keep it self-contained, and then provide a comparison across the review/CPRD/IPD analyses as the first part of the triangulation chapter?]__
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-A likely explanation for the observed increased risk of vascular and other dementias with lipid-regulating agent use, and an important limitation of this analysis, is residual confounding by indication.
-While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] "confounding by indication" is used here to described the role of risk factors that both prompt treatment (in this case statins) and increase the risk of the outcome (in this case vascular dementia), thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015]
-
-&nbsp;<!----------------------------------------------------------------------->  
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating confounding by indication.
+<!-- IDEA Cite study/paper mentioned by GDS about getting better estimate for effect when dealing with off-target outcomes -->
+
+A likely explanation for the observed increased risk of dementia outcomes with a vascular component (e.g.
+vascular and other dementias) with lipid-regulating agent use, and an important limitation of this analysis, is residual "confounding by indication".
+While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] it is used here to described the role of risk factors that both prompt treatment and increase the risk of the outcome, thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
+In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015] In the context of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins but also represent a vascular risk factor that contributes to the development of the vascular dementia.
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating how confounding by indication could induce a positive association between statins and vascular dementia.
 
@@
                               label = "Prompts"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "black",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_text(data = data.frame(x = 0.88,
+                              y = 0.05,
+                              label = "Induced positive"),
+            mapping = aes(x = x,
+                          y = y,
+                          label = label),
+            angle = 0L,
+            lineheight = 1L,
+            hjust = 0.5,
+            vjust = 0.5,
+            colour = "black",
+            family = "sans",
+            fontface = "bold",
+            inherit.aes = FALSE,
+            show.legend = FALSE) +
+  geom_text(data = data.frame(x = 0.88,
+                              y = -0.04,
+                              label = "association"),
             mapping = aes(x = x,
@@
 
-In the case of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins but also represent a vascular risk factor that contributes to the development of the vascular dementia.
-
-Supporting evidence for this interpretation comes from a variety of sources, including the results of the control outcome analyses.
+Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
 The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
-This is supported by the increasingly harmful effect moving from probable/Possible AD to other dementias to vascular dementia, indicating that the confounding by indication likely increases as the proportion of vascular outcomes increase.
-This is supported by the decision tree for assigning outcomes in the presence of greater than one dementia code, where the Alzheimer's disease outcomes require a "pure" condition, and the presence of any vascular or other dementias codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
-
-A review of other available literature suggests that this observation (a harmful effect of lipid-regulating agents on vascular-related outcome) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to ischemic heart disease) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
-
-Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-
-On a more general note, the unexpected increase in vascular dementia risk with statin use is particularly interesting given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)).
-It is possible that previous research encountered similar methodological issues to this analysis, and via a publication bias mechanism, the results from these analyses did not make it into the evidence base.
-
-<!-- IDEA talk about time-varying confounding here -->
-
-#### Time period effect in probable Alzheimer's disease
-
-The time period effect observed for the Alzheimer's disease outcome, where statins appear more protective in participants who entered the cohort at a later date, is an interesting result.
-An expected cause was an change in how different dementia sub-types were diagnosed over time, but no corresponding inverse trend in any of the other dementia outcomes.
+
+In line with this, an increasingly harmful effect is observed when moving from the probable and possible Alzheimer's disease outcome to the other dementias outcome, and finally to the vascular dementia outcomes.
+This pattern suggests that the strength of the residual confounding by indication increases as the proportion of cases with a vascular component in an outcome definition increases.
+Given confounding related to vascular factors, this pattern is also expected given the decision tree for assigning outcomes in the presence of greater than one dementia code.
+Under this system, the Alzheimer's disease outcomes require a "pure" condition and the presence of any vascular or other dementias codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
+
+A review of other available literature suggests that this observation (a harmful effect of lipid-regulating agents on vascular-related outcomes) is not unusual.
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in this analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
+
+Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)), the unexpected increase in vascular dementia risk with statin use is particularly interesting  It is possible that previous research encountered similar methodological issues to this analysis, and via a publication bias mechanism where unexpected or assumedly incorrect results are less likely to be published, the results from these analyses did not make it into the evidence base.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+<!-- #### Time period effect in probable Alzheimer's disease -->
+
+<!-- An expected explanation for the time period effect observed for the Alzheimer's disease outcome, where statins appear more protective in participants who entered the cohort at a later date, was an change in how different dementia sub-types were diagnosed over time.
 For example, if the observed trend was due to increasing differential misclassification with vascular dementia, then we would expect vascular dementia to appear increasingly harmful in more recent time periods which is not the case.
+However, when investigated via tabulation of dementia outcomes by grouped year of entry (Table \@ref(tab:diagnosisType-table)), no corresponding inverse trend is observed for any of the other dementia outcomes.
+-->
+
+<!-- Similarly, the absence of  -->
 
@@
 
-The observation that hydrophilic statins appear more protective than their lipophilic counterparts, runs counter to the theory that lipophilic drugs are able to cross the blood brain barrier.
-However, it does agree with previous findings for this comparison.
-
-Additionaly, the relative precision of the two groups is expected, as the two most commonly prescribed statins in the UK are lipophilic (simvastatin and atorvastatin). <!-- TODO CITATION NEEDED -->
-
-An initial interpretation for the discrepancy was that lipophilic statins may as a class be stronger, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
-However, the statin with the strongest lipid lowering effect available via the NHS, rosuvastatin, is hydrophobic.
-
-however, two of the most widely used
-
-__[Yoav: are there are particular indications/contraindications for statins with different properties?]__
-
-* Blood brain barrier
-*
-*
+This analysis found that hydrophilic statins were less harmful in the any, vascular and other dementias outcomes compared to lipophilic statins, and were associated with a small reduction in the risk of the probable and possible AD outcomes.
+The relative precision of the estimates in each group is expected, as the two most commonly prescribed statins are lipophilic (simvastatin and atorvastatin).[@newman2019]
+
+A widely discussed concept in the literature surrounding statin use and cognitive outcomes is the fact that lipophilic statins are more likely to be able to cross the blood brain barrier, and so have a more potent protective effect by directly lowering brain cholesterol.[@shepardson2011] My findings that hydrophilic statins appear to be more protective/less harmful than their lipophilic counterparts runs counter to this assertion.
+
+An initial interpretation of the the different association observed in the two groups was that the lipophilic statins may be more potent, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
+However, the statin with the strongest lipid lowering effect that is available via the NHS, rosuvastatin, is hydrophobic.
+
+__[Yoav, are there are particular indications/contraindications for statins with different properties? And any general comments on the interpretation of these findings would be welcome!]__
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Impact of code lists
+
+As part of a sensitivity analysis exploring the impact of outcome code-lists, I used definitions for Alzheimer's disease and other dementias obtained from a previously published paper (Smeeth _et al._).[@smeeth2009] Using these lists in my analytical set-up, I found a harmful association of statin use with both outcomes.
+
+TThis finding disagrees with the results of the original analysis, which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+
+However, comparison of the results obtained using the two sets of code lists was deemed less useful following a detailed comparison of the codes used.
+While all of the codes used to define Alzheimer’s in the Smeeth _et al._ paper are included in the probable Alzheimer’s code-list (see Figure \@ref(fig:smeethComparison)), I included several additional codes used to define this outcome (including, for example, “Eu00013: [X]AD disease type 2”).
+Additionally, several of the codes used to define “Possible Alzheimer’s” in this analysis are included in the “Other dementia” code list used by Smeeth.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
+The joining lines showing the overlap between the categories in the two analyses.
+
+(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
+
+```{r sankeydiagram, include=FALSE}
+```
+
+```{r smeethComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:smeethComparison-cap)', out.width='100%', fig.scap='(ref:smeethComparison-scap)'}
+knitr::include_graphics(file.path("figures/cprd-analysis/sankey_diagram.png"))
+```
+<!----------------------------------------------------------------------------->
+
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are used to define competing outcomes (e.g.
+AD vs non-AD dementia).
+This different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why our analysis obtained different results despite the substantial overlap in the data sources used.
 
@@
 
-The primary strength of this analysis compared to others available in the literature is the relative size of the CPRD and length of follow-up.
-Having reviewed the other studies identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
+The primary strength of this analysis is the relative size of the CPRD and length of follow-up.
+Having reviewed the existing literature, as identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
 Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.
 This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
+Finally, it is one of the few that provide evidence on the association of lipid-regulating agent use and vascular and other dementias.
 
 However, the findings of this analysis are subject to several limitations in addition to the confounding by indication discussed above.
-There is a strong possibility of differential misclassification[@porta2014dictionary] of dementia-related conditions based on the exposure.
-As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome based on varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014dictionary] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+Further, there is a potential for general non-differential misclassification of the outcome due to the varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 <!-- though there is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database and does not add a substantial administrative burden.[@russell2013] -->
@@
 Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
-This is a particular challenge in comparing research across different time-periods and coding systems,
-
-A further limitation stems from uncontrolled confounding due to genetic factors.
+This presents a particular challenge in comparing research across different time-periods and coding systems, particularly the unexpected results I obtained for the vascular and other dementias outcomes.
+
+A further limitation stems from the possibility of uncontrolled confounding due to genetic factors.
 Number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
-We were unable to control for ApoE genotype in this analysis as we did not have access to genetic data on participants.
+I was unable to control for ApoE genotype in this analysis as I did not have access to genetic data on participants.
 As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.
 
-Finally, as with many studies of dementia, there is a risk of reverse causation in our analysis.
+Finally, as with many studies of dementia, there is a risk of reverse causation in my analysis.
 Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.
@@
 
-In light of my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis are readily available.
-
-The raw data supporting this analysis is not available, as access to the CPRD data is controlled by a data monitoring committee.
-In the context of access-controlled data, sharing the analysis code represents a way for readers to validate the findings.[@goldacre2019c] As such, all code, Read code lists and summary statistics (i.e.
-the tables presented in this chapter, plus summary tables of effect estimates) are readily available in machine readable formats (i.e.
-as comma separated values, or CSV, files) from the archived repository for this project (Zotero DOI: __TBC__).
+The raw data supporting this analysis is not publicly available, as access to the CPRD data is controlled by a data monitoring committee.
+However, when data are not readily available, sharing the analysis code and summary statistics represents a way for readers to validate the findings.[@goldacre2019c]
+
+In light of this and my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis have been made readily available.
+All code, Read code lists and summary statistics (namely the tables presented in this chapter plus summary tables of effect estimates) can be downloaded in a machine readable format from the archived repository for this project (Zotero DOI: __TBC__).
 <!-- TODO Archive on Zenodo.
--->
-
-This open approach should enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to build on that presented here.
+--> This open approach should enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to build on that presented here.
 
@@
 This chapter has provided new evidence on the association of lipid-regulating agents with incidence of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for the potential immortal time bias.
+It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for potential immortal time bias.
 
@@
 However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-This is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of vascular dementia.
+The presence of bias is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of dementia outcomes with a vscular component.
 Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
@@
 Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an IPD analysis to investigate the effect of blood lipid levels on dementia outcomes directly, rather than via the proxy of lipid-regulating treatment.
+In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an individual patient data analysis to investigate the association of blood lipid levels with incidence of dementia outcomes directly, rather than via the proxy of lipid-regulating treatment.
 

### 2021-10-20 07-Chp-Triangulation.Rmd
End of day
End of day:

@@
 
+### Qualitative triangulation
+
+<!-- TODO Need to talk about fibrates here too -->
+
+__Statins and all-cause dementia__
+
+This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
+Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
+
+Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
+
+&nbsp;
+
+__Statins and Alzheimer's disease__
+
+Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
+Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
+
+Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
+
+&nbsp;
+
+__Statins and vascular/other dementia__
+
+Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
+A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
+When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
+
+&nbsp;
+
+__Other drug classes__
+
+Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
+
+One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
+
+A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
+Note that this study was published in 2020 and so was not included in the review.
+
 ### Background to the causal question
@@
 
-Table with columns describing exposure, outcome, timepoint, other aspects (cumulative), and
+Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and
 

### 2021-10-20 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 
-* Main text word count (max 4000): 3104
+* Main text word count (max 4000): 3442
 * Abstract word count (max 250): 250
@@
 This analysis used the CPRD-GOLD primary care dataset March 2016 snapshot (ISAC 15_246R), which is available upon application to the CPRD Independent Scientific Advisory Committee.
-The code lists used to define the outcomes and covariates for this study, in addition to the cleaning and analysis scripts used to create the study cohort and perform the analyses, are available on GitHub (https://github.com/mcguinlu/CPRD-LRA), and were archived at the time of publication on Zenodo (DOI: __TBC__).
+The code lists used to define the outcomes and covariates for this study are available as a supplementary file.
+The code lists, as well as the scripts used to create the study cohort and perform the analyses, are also available from the GitHub repository for this project (https://github.com/mcguinlu/CPRD-LRA), which was archived at the time of publication on Zenodo (DOI: __TBC__).
 
@@
 
-_Figure 1: Results from the primary analyses of CPRD data comparing prescription of an lipid-regulating drug with no prescription, stratified by dementia outcome and drug class.
+_Figure 1: Results from the primary analyses of CPRD data comparing prescription of a lipid-regulating drug with no prescription, stratified by dementia outcome and drug class.
 All results were obtained using the fully adjusted model and participant age as the time scale._

### 2021-10-20 tmp.Rmd
End of day:

@@
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
-source("R/doc_options.R")
 source("R/helper.R")
-knitr::read_chunk("R/03-Code-Systematic-Review.R")
+knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
 doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
 ```
+
+<!----------------------------------------------------------------------------->
+(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model.
+The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]
+
+(ref:covariateDef-scaption) Covariates adjusted for.
+
+(ref:covariateDef-cell1) Charlson index implemented using Read code lists.[@khan2010] Code lists based on those by Taylor et al.[@taylor2016]
+
+(ref:covariateDef-cell2) Most recent of recorded value (current, former or never) or Read code indicating a recorded value. Code lists based on those by Wright et al.[@wright2017]
+
+```{r covariateDef-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->

### 2021-10-20 R/03-Code-Systematic-Review.R

@@ -449,11 +449,17 @@ n_VaD <- study_details %>%
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- studyCharacteristics-table
 
+# TODO Ensure the citations here match up
+# Do it in relation to the full render as some citations are included in early questions
+# Also, need to deal with the fact that some studies are included >1 in the table
+
 studyCharacteristics_table <- study_details %>%
-  # Add asterisk to preprinted studies
+  ungroup() %>%
+  # Add asterisk to preprinted 
   mutate(Study = ifelse(study_id %in% c(90004, 90005, 3232), paste0(Study, "*"), Study)) %>%
   select(
     Study,
+    #Citation,
     type,
     location,
     number_participants,
@@ -474,12 +480,14 @@ studyCharacteristics_table <- study_details %>%
   tidy_nums() %>%
   arrange(desc(Type), Study) %>%
   select(-Type) %>%
+  # Add citation
   mutate(across(everything(),  ~ stringr::str_replace(., "NA", "NR"))) %T>%
   write.csv("data/table_words/studyCharacteristics.csv")
 
 if (doc_type == "docx") {
   apply_flextable(studyCharacteristics_table, caption = "(ref:studyCharacteristics-caption)")
 } else{
+  
   knitr::kable(
     studyCharacteristics_table,
     format = "latex",

### 2021-10-20 R/helper.R

@@ -687,8 +687,9 @@ get_all_citations <- function() {
                 which = 1) %>%
     janitor::clean_names() %>%
     filter(!is.na(citation)) %>%
+    mutate(type = factor(subtype, levels = c("RCT", "NRSI", "NRSE", "MR"))) %>%
+    arrange(type, author) %>%
     select(citation) %>%
-    arrange(citation) %>%
     distinct() %>%
     pull(citation)
   

### 2021-10-26 02-Chp-Systematic-Review-Tools.Rmd
Updates

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = FALSE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:sys-rev-tools-quote)', echo = TRUE}
 Why are open source statistical programming  

### 2021-10-26 04-Chp-Systematic-Review-Results.Rmd
Updates

@@
 ```
-
-<!-- ## To Do -->
-
-<!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-
-```{r prisma-flow-setup, include = FALSE}
-```
-
-## Results
-
-<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
-
-### Initial search and validation of search filters
-
-The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records.
-Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
-<!-- TODO include some example citations here -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Screening results
-
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-
-The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the right of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g.
-change in cognitive scores).
-
-<!----------------------------------------------------------------------------->
-
-\blandscape{}
-
-&nbsp;
-
-(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-\elandscape{}
-
-<!----------------------------------------------------------------------------->
-
-### Validation of screening
-
-```{r agree-setup, include = FALSE}
-```
-
-For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
-For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
-
-<!-- TODO Include AC1 result in caption above -->
-
-(ref:agreeInter-scaption) Inter-rater agreement
-
-```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
-
-(ref:agreeIntra-scaption) Inter-rater agreement
-
-```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and the definition of eligible lipids fractions.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies {#sys-rev-characteristics}
-
-```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
-```
-
-Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
-
-Of the `r n_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also reported on other non-statins agents such as fibrates (`r n_fibrates`).
-In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia (`r n_hyperchol`) and total cholesterol levels (`r n_TC`) were the most frequently reported risk factors.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia (`r n_VaD`).
-Some other outcome classifications such as vascular-component or mixed dementia were also investigated, but were much rarer.
-
-<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->
-
-<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->
-
-<!--- TODO Talk a little bit more about age here --->
-
-Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
-
-<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->
-
-<!-- TODO Figures and tables to include here: -   Summary of risk of bias (not done) -->
-
-<!-- TODO Also need to extract the codes used in each study -->
-
-<!-- TODO Need to add abbreviations to table -->
-
-\blandscape{}
-<!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple analytical designs within a single study report, and these have been duplicated across the relevant sub-sections.
-
-(ref:studyCharacteristics-scaption) Characteristics of included studies
-
-```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape{}
-
-```{r cohortLocationsSetup, include = FALSE}
-```
-
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most high represented region being North America.
-Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
-
-<!----------------------------------------------------------------------------->
-
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
-
-(ref:cohortLocations-scap) Geographical distribution of study cohorts
-
-```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
-```
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-Finally, there were several eligible studies reported as conference abstracts that did not present numerical results.
-These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Risk of bias {#risk-of-bias-res}
-
-```{r riskOfBias, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-As discussed above, the risk-of-bias assessments are presented alongside their corresponding numerical result.
-A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
-
-For the two randomised controlled trials, both were judged to be at low risk of bias.
-In contrast, many of the non-randomised studies of statin use were at serious risk of bias due poor controlling for confounding, immortal time bias, and missing outcome data (as noted above, a judgement of low risk of bias for a non-randomised study is rare).
-Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g.
-examination of lipids as a binary or continuous variable).
-Finally, bias was introduced into Mendelian randomisation studies via the potential for hoziontal pleiotropy and population stratification.[@davies2018]
-
-Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.
-<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
-the study reported unadjusted estimates).`r critical_citations`
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### All-cause dementia {#sys-rev-res-Dementia}
-
-#### Statins
-
-```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-&nbsp;<!----------------------------------------------------------------------->
-
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
-This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
-
-&nbsp; <!---------------------------------------------------------------------->
-
-#### Fibrates
-
-```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found very weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
-
-(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Lipids
-
-<!-- TODO Deal with awkward hypercholesterolemia definition -->
-
-Across all outcomes, lipid levels were categorised in a number of ways.
-The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
-
-`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
-
-(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
-
-```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
-```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Alzheimer's disease {#sys-rev-res-AD}
-
-#### Statins
-
-There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
-
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Two Mendelian randomisation studies looked at specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Lipids
-
-`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
-
-(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
-
-```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
-
-```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
-However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
-Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
-However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Vascular dementia {#sys-rev-res-VaD}
-
-#### Statins
-
-As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
-There were no available randomised trials for this outcome.
-`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Lipids
-
-`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
-
-(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
-
-```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found very weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
-A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
-
-```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of genetically determined lipid levels on vascular dementia risk.
-
-&nbsp;
-
-### Dose response meta-analysis of lipid levels {#dose-response-results}
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks -->
-
-```{r doseResponse, include = FALSE}
-```
-
-There were `r n_dr_initial` studies that were eligible for dose-response meta-analysis as they provide several categories of lipid exposure.
-However, following data extract, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
-
-Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of studies (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
-This analysis provided very weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
-Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
-
-(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
-
-```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:lipidsDoseResponse-cap)', out.width='70%', fig.scap='(ref:lipidsDoseResponse-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/dr_AD_TC.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Additional analyses
-
-Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, few meta-analysis included more than 10 results, the recommended minimum required for meta-regression.
-Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
-
-Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
-
-Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
-However, all analyses assessed provided weak evidence of small-study effects.
-
-[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]
-
-<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
-
-<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
-Depsite attempts to obtain this additional information through contact with a -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Missing evidence
-
-The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
-For randomised controlled trials and non-randomised studies of interventions, the risk of bias due to missing evidence was assessed to be minimal.
-However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (Figures \@ref(fig:lipidFractionsDementia), \@ref(fig:lipidFractionsAD) and \@ref(fig:lipidFractionsVaD).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Added evidential value of including preprints {#sys-rev-including-preprints-res}
-
-As show in Figure \@ref(fig:prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
-
-Including preprints did provide useful additional evidential value in a number of meta-analysis.
-To demonstrate this, the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref(fig:mrStatinADFig)) in Mendelian randomisation studies was re-analysed using a fixed-effect model.
-Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
-
-<!-- &nbsp; -->
-
-<!----------------------------------------------------------------------------->
-<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->
-
-<!-- (ref:preprintWeights-scaption) Added information due to inclusion of preprints -->
-
-<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
-<!-- ``` -->
-<!----------------------------------------------------------------------------->
-
-<!-- TODO Add extra column with details of Figure showing met-analysis -->
-
-<!-- &nbsp; -->
-
-Investigation of the publication status of the two preprints reporting studies not also identified by the main search after a two-year lag found that one had been subsequently published in late 2019.[@andrews2019; @andrews2021] The final preprint has not yet been published.[@so2017]
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-<!-- TODO Check inclusion of Rockwood 2002:  -->
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-This discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
-A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Summary of findings
-
-There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
-mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
-
-<!-- Some evidence that age has impact on observed lipid-dementia relationship - use to link  -->
-
-The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
-This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up made necessary by the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), which appears in the literature in recent years, driven by the availability of summary genome wide association studies (GWAS) that form the basis of the two-sample Mendelian randomisation approach.
-
-<!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) Included study designs by year of publication
-
-(ref:typeByYear-scap) Study designs by year of publication
-
-```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-A common theme was an absence of studies examining vascular dementia as an outcome, most noticeable when comparing the evidence base for statins in dementia/Alzheimer's (Figures \@ref(fig:obsStatinDementiaFig) & \@ref(fig:obsStatinADFig)) with that available for vascular dementia (Figure \@ref(fig:obsStatinVaDFig)).
-This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
-A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was very weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
-
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002a] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
-As such, this trial did not met the inclusion criteria for this review.
-
-<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
-The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
-from Anstey 2017 -->
-
-Risk of bias across the individual results was generally quite high, and the causes and expected directions of these biases are discussed in more detail in Chapter \@ref(tri-heading).
-Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of statin levels.
-In many cases, estimates were know to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
-These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009; @yamada2009a] In addition, some authors stated outright that non-significant results were not reported (e.g.
-"The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
-were not reported in the Table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided very weak evidence for an effect), other than increasing the precision of the summary estimate.
-
-Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of studies which made use of data from the Taiwan health insurance database.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Comparison with previous reviews {#rev-previous-reviews}
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
-the Newcastle-Ottowa Scale).[@poly2020]
-
-I identified one previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease.
-However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).
-
-Despite these differences in time-scales and methodology, the duplication of work across reviews (including this review) is substantial.
-In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
-
-One of the particular strengths of this review is the inclusion and critical assessment of Mendelian randomisation studies as a source of evidence.
-
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
-However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
-
-<!----------------------------------------------------------------------------->
-```{r mrAssumptionsSetup, include = FALSE}
-```
-
-(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
-there is no horizontal pleiotropy).
-
-(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses
-
-```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availabilt of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses.
-As such, the process and tools for systematically assessing this study design are not as well developed.
-A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.
-
-Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias).
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
-<!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.
-
-As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
-This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
-Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
-This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
-
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation" followed by manual review of studies that look across multiple risk factors would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (n=`r comma(16109)`).
-Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit to the field.
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
-In all cases, excluding these variants attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Inclusion of preprints
-
-```{r preprintGrowthSetup, include=FALSE}
-```
-
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
-The small number of studies returned by the searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a very small number of records (n=`r n_at_search["med"]`).
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) Growth of preprint repositories over time.
-Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='80%',fig.align='center',fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Three relevant preprints from the bioRxiv hits were identified.
-The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
-Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
-
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
-
-Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
-Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019b] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-More recently, inclusion of preprints in systematic reviews has become significantly more widespread.
-This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.[@fraser2020preprinting] How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Comments on the process -->
-
-<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
-
-<!-- &nbsp; -->
-
-<!-- #### Protocol registration -->
-
-<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
-In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
--->
-
-<!-- &nbsp; -->
-
-<!-- #### Workload -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-<!-- &nbsp; -->
-
-<!-- #### People management -->
-
-<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
-However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
--->
-
-<!-- &nbsp; -->
-<!----------------------------------------------------------------------------->
-
-<!-- ### Validation against recent umbrella review -->
-
-<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
-
-<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
-
-<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
-In fields where there is a lot of existing reviews, they -->
-
-<!-- All studies identified by reviews included in te -->
-
-<!-- In hindsight, this approach ma -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important information required for the dose-response meta-analysis, and so could not be included in the synthesis.
-This limitation was compounded by the expected low response rate to requests for further information from primary authors.
-While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
-
-Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.
-A copy of this publication is available in Appendix \@ref(published-papers).[@hennessy2021] In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
-__[Zenodo repository will be cited here]__
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Strengths and limitations
-
-<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
-
-#### Strengths
-
-I believe there are several aspects where this review is distinct from those reviews already available in the published literature.
-While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This repres important strength of this review, as the detailed risk of bias assessments are used in
-
-Thirdly, as discussed at length in the section above, in contrast to other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related preprints.
-Finally, as a secondary element, I used this review to pilot new research synthesis methodologies, in particular a new visualisation approach for risk-of-bias assessments and a forthcoming tool for assessing the risk-of-bias due to missing evidence.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Limitations
-
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
-
-In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
-
-One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
-
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Conclusions
-
-In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
-
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
-
-\newpage
-
-## References

### 2021-10-26 06-Chp-IPD-Analysis.Rmd
Updates

@@
 (ref:intro-quote) --- Hold
+
+<!-- TODO Need quote for here -->
 
@@
 
-<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->
+<!-- Previous SWARs have been registered as protocols, but have not yet reported! - Not sure this is actually true! Double check. -->
 
@@
 
-<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->
+<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts, all full-scale IPD would have been logisitically challenging.
+It is positive that off the cohorts analysed, the majority represented new data not previously considered -->
 

### 2021-10-26 07-Chp-Triangulation.Rmd
Updates

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:tri-quote)', echo = TRUE}
+Next on my list of features to be specially considered I would place the consistency
+of the observed association. Has it been repeatedly observed by different persons, in different places, circumstances and times?
 ```
-(ref:intro-quote) --- Hold
+(ref:tri-quote) --- Sir Austin Bradford Hill, 1965 [@hill1965]
 
 <!-- TODO Add this to the Chapter summary in the introduction and  -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
 
@@
 
-<!-- Without our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
--->
-
 # Aetiological triangulation across evidence sources {#tri-heading}
@@
 
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+source("R/helper.R")
+knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
+knitr::read_chunk("R/07-Code-Triangulation-Analysis.R")
+doc_type <- knitr::opts_knit$get('rmarkdown.pandoc.to') # Info on knitting format
+```
+
 ## Lay Summary
+
+Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
+Different sources of evidence will have different limitations.
+If the result from each source points towards the same answer, this improves our confidence in the conclusion.
 
@@
 
-This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading)
-
-### Data sources
-
-This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) & \@ref(ipd-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Qualitative triangulation
-
-<!-- TODO Need to talk about fibrates here too -->
-
-__Statins and all-cause dementia__
-
-This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
-
-Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
-
-&nbsp;
-
-__Statins and Alzheimer's disease__
-
-Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
-Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
-
-Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
-
-&nbsp;
-
-__Statins and vascular/other dementia__
-
-Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
-A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
-When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
-
-&nbsp;
-
-__Other drug classes__
-
-Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
-
-One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
-
-A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
-Note that this study was published in 2020 and so was not included in the review.
-
-### Background to the causal question
-
-Following best practice guidance, three
-
-Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and
-
-This was also guideded by the forthcoming ROBINS-E tool, which has
-
-<!----------------------------------------------------------------------------->
-
-### Definition of the causal question
-
-<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
-
-This chapter will consider two questions
-
-Firstly, an ter
-
-Secondly an
+This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \ref(cprd-heading) and IPD \ref(ipd-heading).
 
@@
 
-## Terminology
+### Overview of triangulation {#triangulation-overview}
+
+### Terminology
+
+__Different types of triangulation__
+
+Qualitative triangulation is describing the different results.It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different "contexts".
+In this framework.
+
+However, previous attempts at triangulation ignore the potential for varying and opposing sources of bias within a evidence source. For example,
 
@@
 
-### Summary of triangulation
+<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity.
+The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation.
+-->
 
-Need to check how much I talk about this in the introduction
+&nbsp;<!----------------------------------------------------------------------->
 
-Describe in detail
+## Methods
+### Data sources
 
-### Evidence sources
+This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (statins on dementia outcomes in the CPRD) & \@ref(ipd-heading) (lipids on dementia outcomes in IPD).
+
+Table \@ref(triSummary) illustrates the causal question each approach attempted to answer, along with the exposures and outcomes for each.
+
+<!----------------------------------------------------------------------------->
+(ref:triSummary-caption) triSummary
+
+(ref:triSummary-scaption) triSummary
+
+```{r triSummary-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Qualitative triangulation
+
+As a first step to assessing the evidence, all evidence sources were grouped by outcome and compared and contrasted.
+Potential reasons for heterogeneity were examined with specific reference to the risk of bias assessments performed.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Quantitative triangulation
+
+In addition to the qualitative discussion of evidence, I attempted to integrate the .
+This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Definition of the causal questions of interest (case-studies)
+<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
+
+This chapter will consider two questions
+
+Firstly, an ter
+
+Secondly an
+
+Background to the causal question
+
+Following best practice guidance, three
+
+Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and
+
+This was also guided by the forthcoming ROBINS-E tool, which has
+
+•	One interventional: Effect of average exposure to LDL-c during midlife on AD 
+•	One aetiological: Effect of cumulative LDL-c from birth
 
@@
 
-###	Limitations
+&nbsp;<!----------------------------------------------------------------------->
 
-In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elictation process using a number of experts.
+####	Identify relevant studies
 
-Ideally, the modifying values )
+Once the causal question of interest had been defined, studies related to it were
 
-i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)?
-Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate
+&nbsp;<!----------------------------------------------------------------------->
 
-### Risk of bias tool
+####	Assess risk of bias in each result, define expected directions of each bias
 
@@
 
-While the triangulation framework provides for inclusion of multiple distinct types of evidence, based on the scoping search, it is likely that the three main sources will be RCTs of statins, multivariable regression of prospective cohorts, and the use of genetic instruments in observational data (Mendelian Randomisation studies).
-One important difference between these approaches that will need to be addressed in the triangulation
-is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
-The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course.
+&nbsp;<!----------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+#### Visually inspect results and bias
 
-### Graphical representation
+Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+
+Talk about new visualisation method here, and the different
 
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
-### Standardisation across study designs
+####	Assign modifying values to risk/direction of bias
 
-Standardising across different measures of ex
+One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e.
+a high risk of bias in one domain is equivalent to a high risk fo bias in any other.
+This runs contrary to the idea put forward in some previous tools where certain domains
 
-Want best information across lipids, and so standardised across differnt measures
+However, this also allows us to a priori define common modifying values across all domains of bias.
+In a bias-adjusted meta-analysis using this approach, a high risk of bias in the will have the same modifying effect on the results.
 
-Fixing directions of effect - get everything pointing the same way
+As such, a simulation approach was taken to explore the impacts of several different strategies
 
-<!----------------------------------------------------------------------------->
-### Analyses
+<!-- TODO Discuss proportional versus additive, and the fact that all biases considered previously for internal were deemed to be additive. -->
 
-Bias-adjusted meta-analysis [@higgins2008a]
+&nbsp;<!----------------------------------------------------------------------->
 
-## Triangulation across exisiting evidence and evidence produced in this thesis
+####	Assign modifying values to risk/direction of bias
 
-### Overview of triangulation {#triangulation-overview}
+"One important difference between these approaches that will need to be addressed in the triangulation is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
+The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course."
 
-Using the review of the literature as a guide to identify useful further studies that could be performed, I then performed .
+####	Combine in a bias-adjusted meta-analysis
 
-Summary table of different studies and results
+<!-- TODO Deal with the fact that the Panel wasn't super useful -->
 
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Qualitative vs qunatitative triangulation
-
-### Researcher positionality statement
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Discussion of E-values
-
-How strong unmeasured confounding would have to be in order to explain the observed effect.
-
-Heavily criticised in a range of papers.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Use of concensus panel to bring everything together
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
 ## Results
+### Intro
 
@@
 
+### Qualitative triangulation
+
+```{r azd-text, echo = FALSE}
+```
+
+#### All-cause dementia
+
+<!-- TODO Need to talk about fibrates here too -->
+
+__Statins and all-cause dementia__
+
+This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
+Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
+
+Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Alzheimer's disease
+
+__Statins and Alzheimer's disease__
+
+Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
+No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
+Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
+
+Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Vascular dementia
+
+__Statins and vascular/other dementia__
+
+Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
+A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
+When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+__Other drug classes__
+
+Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
+
+One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
+
+A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
+Note that this study was published in 2020 and so was not included in the review.
+
+__Impact of patient characteristics__
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Quantitative triangulation
+
+### Standardisation across study designs
+
+Standardising across different measures of ex
+
+Want best information across lipids, and so standardised across differnt measures
+
+Fixing directions of effect - get everything pointing the same way
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ## Discussion
 
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+Future quantitative triangulation should move beyond the concept of comparing results at the approach leve, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.
+
+While this makes the process both more labour intensive and complex, to assume that, for example, all retro-spective studies are equally at risk is to overlook.
+While ti could be true thtat all retrospective studies share some _minimal level_ of bias, there are several opportunities.
+Failing to seperate these out results in a lack of information.
+
+In this chapter, I have presented a new visualistion fo the bias inherent to each result, and suggested hwo.
+While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiologic studies, these do not yet exist.
+
+### Problems with quantitative triangulation approach
+
+Missing natural variation obtained from elicitation approach. Trade-off between systematic approach presented here and personal variation obtained from several reviewers.
+
+A potential combination between the two would be to use the variation in risk-of-bias assessments
+
+Eliciation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.
+
+No good information on what the potential biases should be.
+
+Meta-epidemiological studies on the effect of different methodological issues on results exist for randomised controlled trials,[@amer2021; @page2016] suggesting that X, Y and Z.
+
+However, there is substantially less , arguably because of the absence of clear
+Many meta-epi studies of non-randomised studies assume bias at the study-design level, similar to the early triangulation frame-work, rather than considering the actual biases deemed to be present in a given result.
+In this scenario, study
+
+Potential future meta-epidemiology studies should begin to create these datasets.
+
+A key example of a useful future study in this domain would be the mining of maximally adjusted vs.
+unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic.
+However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information
+
+For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and review of Research group has this as a secondary methodological aim.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+###	Limitations
+
+In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elicitation process using a number of experts.
+
+Ideally, the modifying values )
+
+<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
+
+i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)?
+Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Discussion of E-values
+
+Present as an alternative to putting priors on the level of bias due to confounding.
+E-values work the other way around - get result then work out how strong a biasing factor would have to be to negate the result.
+One major problem is that they can only be used to evaluate negating biases, not other biases.
+
+How strong unmeasured confounding would have to be in order to explain the observed effect.
+
+Heavily criticised in a range of papers.
+
+Also, no useful to focus on a specific bias in the context of risk of bias domains
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Need for new methods
@@
 Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Conclusion
+
+Triangulation is a promising developing field, somewhat hamstrung by the limited understanding of the impact of biases at the meta-epidemiological level.
+
+\newpage
+
+## References

### 2021-10-26 08-Discussion.Rmd
Updates

@@
 
-## Summary of findings (by chapter)
+## Lay summary
 
-### Systematic review
-#### Principal findings
-#### Comparison with existing literature
-#### Strenghts and limitations
-#### Implications of this research
+This chapter
 
-### CPRD
-#### Principal findings
-#### Comparison with existing literature
-#### Strenghts and limitations
-#### Implications of this research
+## Chapter overview
 
-### Individual participant data meta-analysis
-#### Principal findings
-#### Comparison with existing literature
-#### Strenghts and limitations
-#### Implications of this research
+<!-- In this final chapter I will: -->
+<!--  Summarise the main findings from each chapter in relation to my two thesis hypotheses. -->
+<!-- Chapter 6: Discussion -->
+<!-- 162 -->
+<!--  Discuss the similarities and differences between my findings and the published literature. -->
+<!--  Critically evaluate the novel contributions and implications of my research. -->
+<!--  Describe the limitations of my studies and consider what I would do differently given what I have learnt. -->
+<!--  Recommend avenues for future research. -->
 
-### Triangulation
-#### Principal findings
-#### Comparison with existing literature
-#### Strenghts and limitations
-#### Implications of this research
+&nbsp;<!----------------------------------------------------------------------->
+
+## Summary of principal findings
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+<!-- TODO May need to tone this down a little bit -->
+
 Involving and engaging the public and patients has been a central theme to this thesis. 
-
 Public engagement activities included
@@
 
-Recommend future large scale GWAS of other dementia outcomes, notably vascular dementia, or the use of existing GWAS to  <!-- TODO At least one vascular dementia GWAS exists - find it and cite it here.
--->
+Normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()
+
+Secondly, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of.
+While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.
+
+ <!-- TODO See notes from Pat/Emma on this -->
+
+As a field, and as noted in Chapter \@ref(sys-rev-heading-results), the evidence synthesis theory and methods have not been sufficient developed for Mendelian randomisation studies.
+Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
+genetic instrumental variable analysis.)
+
+Finally, substantial future work should be directed towards the conduct of meta-epidemiologocial studies to assess the impact of different bias in non-pbservational studies.
+While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.
 

### 2021-10-26 R/06-Code-IPD-Analysis.R

@@ -21,6 +21,75 @@ fmt_accessed <- function(dat){
   paste0("n = ",dat,", ",comma((dat/n_accessed$total)*100),"%")
 }
 
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- cohortFlowchartSetup
+
+library(DiagrammeR)
+
+graph <- grViz(diagram = "digraph cfa {
+      # define node aesthetics
+      node [fontname = Arial,fixedsize = true,width = 3.5, height = 1.5,color = 'black',shape = rectangle, fontcolor = black] 
+      
+      tab0 [label = <<font> <b>Systematic review</b>  </font>>, height = 1, color = 'grey90',shape = rectangle, style = filled, fontcolor = black]
+      tab1 [label = <<font> <b>Systematic review + DPUK </b>  </font>>, height = 1, color = 'grey90',shape = rectangle, style = filled, fontcolor = black]
+      tab2 [label = <<font> <b>DPUK</b> </font>>, height = 1, color = 'grey90',shape = rectangle, style = filled, fontcolor = black]
+      
+      tab01 [label = 'N identified: @@1-2',height = 1]
+      tab11 [label = 'N identified: @@1-3',height = 1]
+      tab21 [label = 'N identified: @@1-1',height = 1]
+      
+      tab02 [label = 'N data obtained: 0 \n\n Exclusion reasons:\n-No response (n= 14)\n-No access to data (n= 2)\n-Planned analysis (n= 3)',height = 2]
+      tab12 [label = 'N data obtained: 1, height = 2]
+      tab22 [label = 'N data obtained: \n\n Exclusion reasons:\n-Dementia cohort (n= )\n-No exposure variables (n= )\n-Planned analysis (n= )',height = 2]
+      
+      tab3 [label = 'N assessed for inclusion: 8',height = 1]
+      tab4 [label = 'N excluded following investigation: 5 \n\n Exclusion reasons:\n-Single wave (n= 2) \n-Cognitively impaired cohort (n= 2) \n-No lipid measurements at baseline (n=1)',height = 1]
+      tab5 [label = 'Final number of \ncohorts included: @@2-4',height = 1]
+
+      subgraph {
+          rank = same; tab02;tab12;tab22
+      }
+      subgraph {
[…]

### 2021-10-26 R/07-Code-Triangulation-Analysis.R

@@ -1,0 +1,19 @@
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- triSummary-table
+
+triSummary_table <- rio::import("data/background/thesisOverview.csv") %T>%
+  write.csv("data/table_words/triSummary.csv")
+
+if (doc_type == "docx") {
+  apply_flextable(triSummary_table, caption = "(ref:triSummary-caption)")
+} else{
+  knitr::kable(
+    triSummary_table,
+    format = "latex",
+    caption = "(ref:triSummary-caption)",
+    caption.short = "(ref:triSummary-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"))
+}

### 2021-11-04 07-Chp-Triangulation.Rmd
Back to working version

@@
 
-<!-- TODO Add this to the Chapter summary in the introduction and  -->
+<!-- TODO Add this to the Chapter summary in the introduction -->
 
@@
 
-This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \ref(cprd-heading) and IPD \ref(ipd-heading).
+This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \@ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \@ref(cprd-heading) and IPD \@ref(ipd-heading).
 
@@
 
+Aetiological triangulation, or simply triangulation, is the process of comparing and contrasting across result in order to .
+
+It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] In this framework,
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Terminology
@@
 
-Qualitative triangulation is describing the different results.It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different "contexts".
-In this framework.
+_Qualitative_ triangulation is describing the different results.
+It regularly appears though not under that name, in the discussion of results section under the name "comparison with other literature".
+
+Previous examples of this approach have used criteria such as
+
+In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.
 
@@
 
-<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity.
-The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation.
--->
+Talk about problems of sclae - assuming bias direction at the study level works well if you only have one study per design category as in the example by Ference et al (e.g. IPD analysis of )
 
@@
 ### Data sources
+
+As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), the triangulation draws on the research produced in the preceding chapters.
 
@@
 
+This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()), and the results of the
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-In addition to the qualitative discussion of evidence, I attempted to integrate the .
+In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.
+
+A framework for bias-adjusted meta-analysis
+
+The code supporting the original implementation (written as a STATA do file) was converted into R code, and
+
 This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and
+
+This was implemented via a bias-adjusted meta-analytical framework.
+
+Several steps were used to accomplish this approach, as described in the following sections.
 
@@
 #### Definition of the causal questions of interest (case-studies)
-<!-- TODO See ROBINS-E for this, as to how to think about exposures -->
+<!-- TODO See ROBINS-E for this, as to how to think about exposures, adn the "Duration and timing of exposure being assessed with different approachesDuration and timing of exposure being assessed with different approaches" section of the aetiological triangulation -->
+
+In the first instance, following standard triangulation
 
@@
 
-•	One interventional: Effect of average exposure to LDL-c during midlife on AD 
-•	One aetiological: Effect of cumulative LDL-c from birth
+*	Effect of average exposure to LDL-c during midlife on AD 
+*	Effect of cumulative LDL-c from birth to mid-life on AD
+* Effect of late-life LDL-c on all-cause dementia
 
-As outlined in the thesis overview presented in Section \@ref(hold), the triangulation draws on the research produced in the preceding chapters.
+&nbsp;
+
+<!-- TODO This table will describe the causal questions of interest, following the ROBINS-E framework as columns, and list the included studies adn the relative weights of each. -->
+
+<!----------------------------------------------------------------------------->
+(ref:questionsOfInterest-caption) questionsOfInterest
+
+(ref:questionsOfInterest-scaption) questionsOfInterest
+
+```{r questionsOfInterest-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 
-####	Assign modifying values to risk/direction of bias
+####	Assign modifying values to indirectness
 
@@
 The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course."
+
+<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity.
+The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation.
+-->
 
@@
 ## Results
-### Intro
-
-Summary of risk-of-bias/triangulation results
-
-Percentage of domains for which a direction of bias could be assigned?
-
-Compare bias-adjusted and
-
-See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
-
-Applicability/indirectness as an issue 
-Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
-
-<!----------------------------------------------------------------------------->
 
@@
 
-### Standardisation across study designs
+#### Intro
+
+Summary of risk-of-bias/triangulation results
+
+Percentage of domains for which a direction of bias could be assigned?
+
+Compare bias-adjusted and
+
+See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
+
+Applicability/indirectness as an issue 
+Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Standardisation across study designs
 
@@
 
-In this chapter, I have presented a new visualistion fo the bias inherent to each result, and suggested hwo.
-While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiologic studies, these do not yet exist.
+In this chapter, I have presented a new visualisation fo the bias inherent to each result, and suggested hwo.
+While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies, these do not yet exist.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Eliciation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.
+Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.
 
@@
 
-### Discussion of E-values
+### Challenges of real-life data
+
+Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
+ALso highlight the issue with assigning a direct of bias in many studies
+
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Alternative approaches
+
+#### E-values
 
@@
 
+As an example, I calculated the E-value required to attenuate the hamrful association observed between statin use and vascular dementia in the CPRD analysis ( `r hold()`` ) presented in Chapter \@ref(cprd-heading).
+Assuming an outcome prevalence of <15%, an E-value of 3.31 was identified
+
+This calculation was performed using the XXX R package.
+
+<!-- TODO Ensure that the example is provided first, as you then go on to disparage it - in the example given, the main driver of bias is likely to be confounding (though some may be due to misclassification) -->
+
+However, this approach is only useful if the only source of bias in a result is due to uncontrolled confounding (as assessed by a domain-based risk of bias tool).
+
+Otherwise, it's interpretation is more challenging, as the biasing effect is incorrectly assinged complete to confoudning, thus overestimating the expected effect of confounding.
+
+the contribution of confounding to the bias in a result, and while it may be applicable if the only bias assessed to
+
 &nbsp;<!----------------------------------------------------------------------->
 
-### Challenges of real-life data
+### Methods for combining different exposures
 
-Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-ALso highlight the issue with assigning a direct of bias in many studies
+Present as an alternative
 
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+Well-used body of literature to combine different outcome measurements, but unclear as to how to combine
+
+It may be possible to combine the different exposure measures
+
+However, in my approach, I treated te
 
@@
 
+This chapter has demonstrated a repurposed framework for quantitative triangulation, exploiting existing methods in evidence synthesis and developments in the assessment of different risks of bias.
+
+It also introduce a new way to visualise the biases at work in a particular result, rather than making assumptions about the type and directions of bias at the study design level as suggested by previous work on this topic.
+
+Finally, it highlighted the limitations of current methods for triangulation in the absence of informative priors for the impact of biases across the
+
 \newpage

### 2021-11-04 08-Discussion.Rmd
Back to working version

@@
 
+In this chapter I will summarise the principal findings from my thesis,
+
+assess the unique contributions of this thesis to the field of research,
+
+discuss the implications for both clinical and public health policy,
+
+describe the overall strengths and limitations of this thesis as a whole,
+
+suggest avenues for impactful future research based on my findings and experiences.
+
 <!-- In this final chapter I will: -->
@@
 
-## Implications 
-### Clinical practice
-### Future research
+This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk.
 
-## Conclusions
+It has highlighted the importance of including preprints in systematic review, and provided a tool to enable researchers to easily do so.
 
-&nbsp;<!----------------------------------------------------------------------->
+It has analysed two previously unalysed datasets, adding useful information to the evidence base
 
-### Strengths and Limitations
+However, the thesis as a whole is subject to some strong limitations.
 
@@
 
-&nbsp;
-<!----------------------------------------------------------------------------->
+This thesis is limited by the low response rate to data access requests, and the
+
+The lack of large, precise studies made comparison across different types of evidence difficult, while the low number of eligible studies for a
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Implications of this research
+
+### Clinical practice
+
+The clinical recommendations that can be drawn from the work in this thesis are limited, due to the
+
+however, a key limiting factor is the absence of a detailed pathological mechanism for Alzheimer's disease. Additionally, vascular dementia
+
+However, based on the available evidence
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Public health
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+
+<!-- TODO Could he get it work, could he feck. -->
 
@@
 
-&nbsp;
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-P
-
 &nbsp;
@@
 
+### Inclusion of preprints
+
 Normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()
 
-Secondly, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of.
+Studying of factors which influence eventual publication would also help to identify the extent and strength of publication bias by providing a
+
+Preprints also represent a key oppportunity to assess the impact of peer review on qualitivative changes within
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Evidence on vascular dementia
+
+As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven y
+
+large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of.
 While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.
@@
  <!-- TODO See notes from Pat/Emma on this -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reviewing of Mendelian randomisation studies
 
@@
 
-Finally, substantial future work should be directed towards the conduct of meta-epidemiologocial studies to assess the impact of different bias in non-pbservational studies.
+Work is ongoing in this field, and new methodological work such as the release of teh MR-STROBE guidelines will aid in the future assessing by helping to improve the reporting of Mendelian randomisation studies.
+
+Problems with reporting of MR studies will hopefully
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Empirical estimates of bias
+
+Finally, substantial future work should be directed towards the conduct of meta-epidemiological studies to assess the impact of different bias in non-observational studies.
 While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Imporved analytical designs
+
+Use of the real-world evidence approach needs to be traded off against the important limitations that t
+
+Talk about the problems with real world evidence, and highlight that even when using these techniques, you still don't get the correct answers.
+
+Tie in with GDS comments on off-targets effect.
 
@@
 ## Overall conclusions
+
+This thesis has made unique and novel contributions to the
+
+Illustrating that commonly employed approaches to address

### 2021-11-04 tmp.Rmd
Updates
Back to working version

@@
 (ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model.
-The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while otherss were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]
+The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]
 

### 2021-11-04 R/07-Code-Triangulation-Analysis.R

@@ -17,3 +17,19 @@ if (doc_type == "docx") {
     row_spec(0, bold = TRUE) %>%
     kable_styling(latex_options = c("HOLD_position"))
 }
+
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- questionsOfInterest-table
+
+questionsOfInterest_table <- rio::import("data/background/thesisOverview.csv") %T>%
+  write.csv("data/table_words/questionsOfInterest.csv")
+
+
+if(doc_type == "docx"){
+apply_flextable(questionsOfInterest_table,caption = "(ref:questionsOfInterest-caption)")
+}else{
+knitr::kable(questionsOfInterest_table, format = "latex", caption = "(ref:questionsOfInterest-caption)", caption.short = "(ref:questionsOfInterest-scaption)", booktabs = TRUE) %>% 
+row_spec(0, bold = TRUE) %>%
+kable_styling(latex_options = c("HOLD_position"))
+}

### 2021-11-11 01-Chp-Background.Rmd
Updates
Back to working version
End of day

@@
 ```
-
 (ref:dara-quote) --- Dara O'Briain
@@
 
-## Thesis overview
+## Thesis overview {#background-thesis-overview}
 

### 2021-11-11 02-Chp-Systematic-Review-Tools.Rmd
Back to working version
End of day

@@
 
-### Use case
+### Use cases
 
 In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
+
 For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
-
-By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two differnt publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
+By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two different publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
 We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
 This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
-Author contributions are discussed in the
-
-In short, this use case illustrates that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints as a part of evidence synthesis exercises.
-
-<!----------------------------------------------------------------------------->
-
-### Limitations of `medrxivr` {#medrxivr-limitations}
-
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
-However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
-A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
-
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
-
-<!-- TODO Clean-up this section -->
-
-<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
 
@@
 
-Using `medrxivr` an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
+Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
 `r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
@@
 This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
+
+In short, these use cases illustrate that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints by enabling meta-research/methodological analyses.
+
+<!----------------------------------------------------------------------------->
+
+### Limitations of `medrxivr` {#medrxivr-limitations}
+
+While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
+However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
+A key example of the reduced specificity when searching the full text, identified during development of `medrxivr`, is that a search for "dementia" would return a record where the only occurrence of this term is in the title of one of the references.[@bong2019]
+
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
+
+<!-- TODO Clean-up this section -->
+
+<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
 

### 2021-11-11 03-Chp-Systematic-Review-Methods.Rmd
End of day:
End of day

@@
 
+<!-- IDEA Stratify by ApoE4 genotype -->
+
+<!-- TODO Gib Hermani question on bias in selection of AD patients in Ostergaard -->
+
 ## Lay summary
@@
 <!-- TODO CITATION NEEDED -->
-Finally, tools movide from assessing bias at the study level to considering each indivudal result reported seperately.
+Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.
 For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
@@
 
+<!-- TODO Ensure citations make sense, and are correct! Get first reference and then add -->
+
 \blandscape{}
@@
 (ref:studyCharacteristics-scaption) Characteristics of included studies
+
+(ref:studyCharacteristics-first-cite) [@heartprotectionstudycollaborativegroup2002]
 
@@
 Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
+
+<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
 

### 2021-11-11 07-Chp-Triangulation.Rmd
End of day

@@
 Several steps were used to accomplish this approach, as described in the following sections.
+As an illustrative example, the approach was implemented first for a single result and then for all results related to two causal questions of interest, as defined in the following section.
 
@@
 
+Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+
+All of the risk-of-bias tools
+
 In addition, the tool also aim to capture the potential direction of bias for each result.
 Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
-Highlight that this is slightly different for the confounding domain in non-randomised studies.
+Highlight that this is slightly different for the confounding domain in non-randomised studies, which only allows for the "Favours experimental", "Favours comparator", and "Unpredictable" options..
 
@@
 
+Of note, the guidance for the tools suggests that if assessors are not able to articulate why the bias in a given domain will "pull" the observed estimate in a specific direction, they should not try to guess.
+
+To assess the usefulness of this system, the number of domains for which bias was expected (i.e.
+judged to be a more than Low risk of bias) but for which no expected direction could be identified were expressed as a percentage.
+If this percentage is high, the helpfulness of the approach is
+
+In line with best practice for meta-analyses, observational studies deemed to be at critical risk of bias were excluded from all quantiative syntheses.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Mapping between different risk of bias tools
+
+For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set: "Low", "Moderate","High".
+The mapping can be seen in Table \@ref(tab:robLevelsMapping-caption).
+
+Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies of interventions.
+This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:robLevelsMapping-caption) robLevelsMapping
+
+(ref:robLevelsMapping-scaption) robLevelsMapping
+
+```{r robLevelsMapping-table, message=FALSE, results="asis", echo = FALSE}
+```
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
+In order to aid with the triangulation exercise, I created a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
 
-Talk about new visualisation method here, and the different
+Similar to the standard paired forest plots introduced in Chapter \@ref(), the level of bias across the domains in each study is reported using coloured blocks.
+However, in contrast to the previous plots, arrows are used in place to illustrate the predicted direction of bias in that domain, categorised as pulling towards the left or the right.
 
-For the graphs, the direction of bias is important.
+This second aspect required some additional consideration, given the distinct and competing options available to assessors.
+For example, the direction of the arrow when the direction of bias is thought to favour the intervention/exposure will be be same regardless of the position of the point estimate.
+The same is not true for the "Towards the null"/"Away from the null" options.
+For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be represented by a right pointing arrow (Figure \@ref(fig:)).
+In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null will be represented by a right-pointing arrow.
+The program to create these figures thus requires knowledge of both the predicted direction of bias and the effect estimate.
 
-Where the direction of bias was unclear/could not be determined from the report, this is indicated
+Tha
 
-In order to aid with the triangulation exercise, a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
-The level of bias in each study is reported using coloured blocks, while the predicted direction of bias in that domain, categorised as towards or away from the null, is indicated using an arrow
+Helper functions in the forthcoming `triangulate` package - see Appendix BLAH.
 
-Of note, a different approach was required for the confounding domains in the assesment tools used for non-randomised studies.
-Confounding in a study will either pull to the left or right, regardless of where the effect estimate is, while other domains will pull towards/away from the null (e.g.
-non-differential misclassification).
-In this case, the program accounted for the position of the effect estimate when assigning a directional arrow in relation to the positon of the effect estimate.
-For example, see Figure \@ref(), which shows an example study under the same confounding structure (protective), but with protective and harmful effect estimates.
-In this case, when the estimated effect is protective (Study 1), the arrow for the confounding domain indicates that the bias is pulling it away from the null.
-If the estimated effect is harmful, the arrow indicates that the results is being biased towards the null.
+<!-- TODO include illustrative example here -->
+
+Where the direction of bias was unclear/could not be determined from the report, this is indicated by a dash.
 
@@
 
+#### Types of bias
+
+Additive biases are those independent of the effect estimate - they shift it left or right. These biases are indicated by the "Favours comparator"/"Favours experiment/exposure" options in the
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ####	Assign modifying values to risk/direction of bias
 
+<!-- TODO Note that they are on the log scale - Lines 45-50 of addbias -->
+
+For example, for a "High" additive bias in $j$th domain of the $i$th study:
+
+$\delta_{ij}^{\mathrm{High}}$
+
+Uncertainty around this estimate, $\delta_{ij}^{\mathrm{High}}$, is given by a distribution:
+
+$$
+\delta_{ij}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
+$$
+
+The sign of $\mu_{i,j}^{\mathrm{High}}$ is defined by the relative direction of the bias in relation to the point estimate.
+If the bias is expected to pull the effect to the left, the position is given a negative sign, and if it is expected to pull the effect to the right, it is given a positive sign.
+
 One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e.
-a high risk of bias in one domain is equivalent to a high risk fo bias in any other.
-This runs contrary to the idea put forward in some previous tools where certain domains
+a "high" bias in one domain is equivalent to a "high" bias in any other.
+As such, for this analysis, I assumed that the distributions assigned to each level of bias is contrast across all values of j, or alternatively, is constant across all domains in the risk of bias assessment tool.
+
+$$
+\delta_{i,1}^{\mathrm{High}} = \delta_{i,2}^{\mathrm{High}} = ... = \delta_{i,j}^{\mathrm{High}}
+$$
+
+and similarly
+
+$$
+\delta_{i,1}^{\mathrm{Moderate}} = \delta_{i,2}^{\mathrm{Moderate}} = ... = \delta_{i,j}^{\mathrm{Moderate}}
+$$
+
+For the purposes of this example analysis,
+
+High
+Some concerns
+
+These figures were sense-checked against
 
@@
 
+As I am attempting to identify the causal effect across different study designs, I needed to . This is not necessary if just summarising the literature.
+
+A similar approach was used to define prior distributions for external bias or indirectness.
+I used a similar enforced scale of "Low/"Moderate"/"High" indirectness versus each of the 4 aspects of the target causal question.
+(recap).
+
+In the original method, this was assessed against 4 categories of internal bias.
+
+In this
+
 "One important difference between these approaches that will need to be addressed in the triangulation is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
 The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course."
+
+<!-- From NIHR applications -->
 
@@
 ####	Combine in a bias-adjusted meta-analysis
+
+Once the total internal and external additive and proportional biases for each result were computed, they were used to define an adjusted estimate and
+
+Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate is defined as:
+
+$$
+\hat{\theta} = \frac{y_i - \mu_{i\delta}^{\mathrm{I}} - \mu_{i\beta}^{\mathrm{E}}\mu_{i\delta}^{\mathrm{E}}}{\mu_{i\beta}^{\mathrm{I}}\mu_{i\delta}^{\mathrm{E}}}
+$$
+
+The standard error of this estimate is then calculated as:
+
+$$
+\mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{I}} \mu_{i \beta}^{\mathrm{E}}}\right)^{2}\left\{s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{I}} 2+\sigma_{i \beta}^{\mathrm{I}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{E} 2}+\sigma_{i \delta}^{\mathrm{E} 2}\right)+\sigma_{i \beta}^{\mathrm{I}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{E}}+\mu_{i \delta}^{\mathrm{E}}\right)^{2}+\sigma_{i \delta}^{\mathrm{I} 2}\right\}
+$$
+
+Once each individual result has been adjusted, they are combined n a standard random-effects meta-analysis, conducted using the `metafor` R package.
+
+The code to implement this model was obtained via contact with the primary author of the original paper proposing the elicitation.
+For compatibility, the STATA code was converted to R, and to verify the accuracy of the translation, the results of the original analyses were reproduced (see Appendix \@ref() for details).
 
@@
 
-__Impact of patient characteristics__
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-#### Intro
+#### Single study
+
+Explain how example study was chosen
+
+#### Causal question #1
+
+Including sensitivity analyses
+
+and citations of studies - going to be a bit of pain
+
+#### Causal question #2
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Discussion
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
+### Summary of findings
 
-#### Standardisation across study designs
+This chapter has demonstrated how new developments in systematic risk of bias assessment.
 
-Standardising across different measures of ex
+Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.
 
-Want best information across lipids, and so standardised across differnt measures
+While this makes the process both more labour intensive and complex, to assume that, for example, all retrospective studies are equally at risk is to overlook.
+While ti could be true that all retrospective studies share some _minimal level_ of bias, there are several opportunities.
+Failing to separate these the individual results loses information, particularly given the now widespread availability of tools to systematically assess the biases present in each result.
 
-Fixing directions of effect - get everything pointing the same way
+In this chapter, I have presented a new method of visualising both the level and expected direction of bias inherent to each result, and suggested how this could be incorporated with a bias-adjusted meta-analysis approach to work towards a generalised qunatitative triangulation framework.
+
+I've highlighted the limitations of this method, as the correct distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies which do not yet exist, framing them as opportunities for future research.
 
@@
 
-## Discussion
+###	Limitations and strengths
 
-Future quantitative triangulation should move beyond the concept of comparing results at the approach leve, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.
+<!-- TODO See discussion of original Turner paper -->
 
-While this makes the process both more labour intensive and complex, to assume that, for example, all retro-spective studies are equally at risk is to overlook.
-While ti could be true thtat all retrospective studies share some _minimal level_ of bias, there are several opportunities.
-Failing to seperate these out results in a lack of information.
-
-In this chapter, I have presented a new visualisation fo the bias inherent to each result, and suggested hwo.
-While this work is largely illustrative, as the correst distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies, these do not yet exist.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Problems with quantitative triangulation approach
+#### Problems with quantitative triangulation approach
 
@@
 
-Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk of bias level loses some of the information contained in domain-level based assessments.
+Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk-of-bias level loses some of the information contained in domain-level based assessments.
 
-No good information on what the potential biases should be.
+No good information on what the potential distributions for different levels of bias (High vs Moderate vs Low) should be.
 
@@
 
-###	Limitations
+This approach has a number of advantages. One of the key ones is modifying distributions of each level of bias could be defined _a priori_ in contrast to the .
+
+In addition, the generalised framework will allow for
+
+#### Subjectivity of risk of bias assessments
+
+By definition, . In this case of this proof-of-concept analysis, the direction of bias was assessed by a single assessor. If attempting to impact policy, the
+
+#### Defining appropriate levels of bias
 
@@
 
-Ideally, the modifying values )
+Ideally, the modifying values
 
@@
 i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)?
+
 Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate
+
+Similar there are several examples of usmeta to define priors for other statistical terms in meta-analysis. For example, previous work has looked at het
+
+Like other studies examining the prior distributions of heterogeneity across different topic areas <!-- TODO Cite turner etc -->
+
+Talk about different ways to define bias terms, using expert-elicitation vs .[@rhodes2020]
+
+Also, talk about the fact that much of the bias-adjusted analysis work to date has been done on trials.
+Describe reasons for this but highlight that for triangulation, there needs to be better coverage of
 
@@
 
-### Challenges of real-life data
+#### Exclusion of studies at critical risk of bias
+
+One potential - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
+
+In any case, it represented a small number of studies.s
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Type of bias (proportional vs additive) not shown on figure
+
+In contrast
+
+The graphics shown in Section \@ref() do not show the type of bias (additive or proportional), only the direction.
+While this is acceptable, future work could assess, potentially by using different arrow types to denote the different types of bias.
+
+A key strength of this project is the development of a standardised way of capturing bias domains and converting the.
+
+Helper functions in the triangulate package convert risk-of-bias assessment
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Challenges of real-life data
 
 Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-ALso highlight the issue with assigning a direct of bias in many studies
+Also highlight the issue with assigning a direct of bias in many studies
 
 I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Standardisation across study designs
+
+Standardising across different measures of ex
+
+Want best information across lipids, and so standardised across different measures
+
+Fixing directions of effect - get everything pointing the same way
 
@@
 Present as an alternative to putting priors on the level of bias due to confounding.
+
 E-values work the other way around - get result then work out how strong a biasing factor would have to be to negate the result.
+IN other words, they represent an estimate ho how strong the total residual confounding would have to be in order to full explain away the observed result.[@vanderweele2017]
+
 One major problem is that they can only be used to evaluate negating biases, not other biases.
@@
 
-### Methods for combining different exposures
-
-Present as an alternative
-
-Well-used body of literature to combine different outcome measurements, but unclear as to how to combine
-
-It may be possible to combine the different exposure measures
-
-However, in my approach, I treated te
-
 &nbsp;<!----------------------------------------------------------------------->
 
-### Need for new methods
+### Need for new method
+
+As the need and appetite for snthesis of different, future iterations of the risk of bias tools should take this into account.
+Simple things like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
+Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.
 
 Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
+
+While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e.
+not applying expected directions of effects to a ).
+
+This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result seperately.
+This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.
 

### 2021-11-11 index.Rmd
End of day

@@
 title: |
-   Lipids and dementia:\
-   An investigation of their relationship
+   Determining the causal effects of lipid levels on risk of dementia:\
+   a triangulation of new and existing evidence
 

### 2021-11-11 R/bias_adjusted.R

@@ -263,6 +263,9 @@ dat <- read.csv("turner_bias/real_example_rob.csv",stringsAsFactors = F) %>%
       select(result_id, author, year)
   )
 
+dat <- dat %>%
+  select(result_id, author, type, yi, sei, everything())
+
 png(
   here::here("triangulation_example_LDL_AD.png"),
   width = 1750,
@@ -298,9 +301,18 @@ turner <- rio::import("turner_bias/propbias.dta") %>%
   
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 
-    
+get_max_domain <- function(data) {
   
+    data %>%
+    janitor::clean_names() %>%
+    select(starts_with("d")) %>%
+    colnames() %>%
+    stringr::str_extract("[0-9].*") %>%
+    as.numeric() %>%
+    max() %>%
+    return()
   
+}  
 
 
   

### 2021-11-12 01-Chp-Background.Rmd
End of day: 39966

@@
 However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapter \@ref(sys-rev-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
+As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
 
@@
 
-All existing evidence, regardless of study design, is first identified by the by the systematic review presented in Chapter \@ref(sys-rev-heading).
+All existing evidence, regardless of study design, is first identified by the by the systematic review presented inChapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
 Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
@@
 
-I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapter \@ref(sys-rev-heading).
+I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
 Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
@@
 -   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapter \@ref(sys-rev-heading):** This Chapter describes a comprehensive systematic review and meta-analysis of all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
+-   **Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading):** These Chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
+This review examined all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
 -   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
@@
 The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.
-
-An overview of how all research studies in this thesis can be found in Table \@ref(tab:thesisOverview-table)
-
-\blandscape
-<!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise performed in Chapter \@ref(tri-heading).
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
-
-(ref:thesisOverview-scaption) Summary of studies included in this thesis
-
-```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape
 
@@
 
-The experience of extracting data for the systematic review in Chapter \@ref(sys-rev-heading) inspired a practical guide for researchers.
+The experience of extracting data for the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) inspired a practical guide for researchers.
 This piece was co-written with Dr.
@@
 
-The tool used to visualise the risk-of-bias assessments in Chapter \@ref(sys-rev-heading) has been published in Research Synthesis Methods.
+The tool used to visualise the risk-of-bias assessments in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) has been published in Research Synthesis Methods.
 See Appendix \@ref(appendix-robvis) for more details on this tool.
+Note that this publication does not describe the recently-developed functionality for producing bias direction plots, as described in Chapter \@ref(tri-heading).
 

### 2021-11-12 03-Chp-Systematic-Review-Methods.Rmd
End of day: 39966

@@
 
-<!-- ## To Do -->
+<!-- TODO Consider reordering the forest plots so that they are the other way around -->
 
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors.).
-<!-- TODO CITATION NEEDED - add once published as a preprint --> A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
 Acceptable judgements for each fo the 5 domains in the tool included "low", "moderate" and "high" risk of bias.

### 2021-11-12 07-Chp-Triangulation.Rmd
End of day: 39966

@@
 
-# Aetiological triangulation across evidence sources {#tri-heading}
+# Aetiological triangulation across new and existing evidence sources {#tri-heading}
 
@@
 
-## Lay Summary
+## Lay summary
 
@@
 ## Methods
-### Data sources
+### Data sources {#tri-data-sources}
 
-As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), the triangulation draws on the research produced in the preceding chapters.
+As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), this triangulation exercise draws on the research produced in each of the preceding chapters.
+More specifically, this chapter builds on the comprehensive systematic review presented in chapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (assocation of statins with dementia outcomes in the CPRD) & \@ref(ipd-heading) (association of lipids with dementia outcomes in IPD).
 
-This chapter builds on the comprehensive systematic review presented in CHapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (statins on dementia outcomes in the CPRD) & \@ref(ipd-heading) (lipids on dementia outcomes in IPD).
+Table \@ref(tab:thesisOverview-table) illustrates the causal question each approach has attempted to address, along with the exposures and outcomes for each.
 
-Table \@ref(triSummary) illustrates the causal question each approach attempted to answer, along with the exposures and outcomes for each.
+\blandscape
+<!----------------------------------------------------------------------------->
+(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise.
+Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
 
-<!----------------------------------------------------------------------------->
-(ref:triSummary-caption) triSummary
+(ref:thesisOverview-scaption) Summary of research designs included in this thesis
 
-(ref:triSummary-scaption) triSummary
-
-```{r triSummary-table, message=FALSE, results="asis", echo = FALSE}
+```{r thesisOverview-table, message=FALSE, results="asis", echo = FALSE}
 ```
 <!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
+\elandscape
 
@@
 
-As a first step to assessing the evidence, all evidence sources were grouped by outcome and compared and contrasted.
-Potential reasons for heterogeneity were examined with specific reference to the risk of bias assessments performed.
+As a first step to triangulating the available evidence, all information sources were grouped by outcome, and systematically compared and contrasted.
+Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.
 
-This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()), and the results of the
+<!-- TODO Use the fact that it doesn't make sense to qualitatively compare at the single result level to highlight the need for a more quantitative approach - usually default to summary at the -->
+
+<!-- IDEA Note the text by Turner on the fact that you can just adjust for a single type of bias - a good example of this would be to try and adjust for internal biases so you get the best possible estimate and then apply it to something like a assumed life-course model - steal from NIHR text, and refer to the appendix  -->
+
+This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()).
+Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis, details of which are available in Appendix \@ref(?).
+
+<!-- TODO Need to actually do these, and include results in the analysis. -->
 
@@
 In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.
+This proof-of-concept approach incorporated advancements in the way that bias in results is assessed (domain-based assessment tools) and existing methods for bias-adjusted meta-analysis[@turner2009] to to illustrate how causal questions could be addressed under this quantitative triangulation framework.
 
-A framework for bias-adjusted meta-analysis
+Several steps were used to accomplish this approach, as described in the following sections. In summary these steps are:
 
-The code supporting the original implementation (written as a STATA do file) was converted into R code, and
+1. Define the causal question of interest
+1. Identify of relevant evidence sources
+1. Assess(and visualise) the extent and direction of bias in each result
+1. Define modifying terms for bias and indirectness in each result
+1. Perform bias-adjusted meta-analysis using bias-/indirectness-adjusted results
 
-This approach incorporated advancements in the way that bias in results is assessed to illustrate both how causal questions could be addressed under this quantitative triangulation framework, and
-
-This was implemented via a bias-adjusted meta-analytical framework.
-
-Several steps were used to accomplish this approach, as described in the following sections.
-As an illustrative example, the approach was implemented first for a single result and then for all results related to two causal questions of interest, as defined in the following section.
+The approach was implemented for two causal questions of interest, as defined below.
 
@@
 #### Definition of the causal questions of interest (case-studies)
+
 <!-- TODO See ROBINS-E for this, as to how to think about exposures, adn the "Duration and timing of exposure being assessed with different approachesDuration and timing of exposure being assessed with different approaches" section of the aetiological triangulation -->
-
-In the first instance, following standard triangulation
-
-This chapter will consider two questions
-
-Firstly, an ter
-
-Secondly an
-
-Background to the causal question
-
-Following best practice guidance, three
-
-Table with columns describing exposure, outcome, time-point, other aspects (cumulative), and
 
@@
 *	Effect of average exposure to LDL-c during midlife on AD 
-*	Effect of cumulative LDL-c from birth to mid-life on AD
 * Effect of late-life LDL-c on all-cause dementia
@@
 <!-- TODO This table will describe the causal questions of interest, following the ROBINS-E framework as columns, and list the included studies adn the relative weights of each. -->
-
-<!----------------------------------------------------------------------------->
-(ref:questionsOfInterest-caption) questionsOfInterest
-
-(ref:questionsOfInterest-scaption) questionsOfInterest
-
-```{r questionsOfInterest-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-a)	Proposed method for this chapter
-i)	Example: LDL-c at midlife on Alzheimer’s disease risk
-ii)	Specific causal effect of interest using ROBINS-E framework:
-•	Population of interest: General population
-•	Exposure of interest: Low density lipoprotein cholesterol
-•	Exposure window of interest: Midlife (45-60)
-•	How exposure over time should be summarized: Cumulative exposure
-iii)	Identify relevant studies from evidence base
-•	LDL-c assessed at midlife
-•	MR of LDL-c
-•	Statin use at midlife
-iv)	Assess risk of bias in each result, define expected directions of each bias and plot
-
-v)	Assign additive value to each level of bias (High = 0.2, Some concerns =0.1, Low = 0), assign sign to these values based on predicted direction and sum across result
-vi)	E.g. for effect estimate 0.71 (0.57-0.89):
-
-Element	D1	D2	D3	D4	D5	D6	D7	Overall
-Bias	High	Some concerns	Low	Low	Low	Some concerns	Some concerns	Serious
-Direction	Left	Away from null	-	-	-	Towards null	Away from null	
-Modifier	-0.2	-0.1	0	0	0	0.1	-0.1	-0.3
-
-vii)	Assign a proportional value representing the indirectness for each result
-•	Statin studies would give smaller proportion (e.g. 0.7) of effect observed for generally lower lipids, as they would reduce cumulative exposure 
-•	SNPs predict quite strongly LDL-c and so would have minimal indirectness
-viii)	Combine in a bias-adjusted meta-analysis
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
+individual results were obtained from the general evidence sources described in Section \@ref(tri-data-sources)
 
-####	Assess risk of bias in each result, define expected directions of each bias
-
-Within our framework and as part of the risk-of-bias assessments reported in \@ref(risk-of-bias-subheading), I attempted to records the direction of the bias, so that it could feed into the triangulation.
-
-All of the risk-of-bias tools
-
-In addition, the tool also aim to capture the potential direction of bias for each result.
-Possible responses included: "Favours experimental", "Favours comparator", "Towards null", "Away from null", and "Unpredictable".
-Highlight that this is slightly different for the confounding domain in non-randomised studies, which only allows for the "Favours experimental", "Favours comparator", and "Unpredictable" options..
-
-These levels only apply to existing tools, not the MR tool. However, a similar approach was employed.
-
-Of note, the guidance for the tools suggests that if assessors are not able to articulate why the bias in a given domain will "pull" the observed estimate in a specific direction, they should not try to guess.
-
-To assess the usefulness of this system, the number of domains for which bias was expected (i.e.
-judged to be a more than Low risk of bias) but for which no expected direction could be identified were expressed as a percentage.
-If this percentage is high, the helpfulness of the approach is
-
-In line with best practice for meta-analyses, observational studies deemed to be at critical risk of bias were excluded from all quantiative syntheses.
+In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate for a single study is described in detail for a single study.
+Following this, the process was applied to the two subsets of studies related to the causal questions of interest.
 
@@
 
-#### Mapping between different risk of bias tools
+####	Assess risk and direction of bias in each result
 
-For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set: "Low", "Moderate","High".
-The mapping can be seen in Table \@ref(tab:robLevelsMapping-caption).
+The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias).
+In summary, randomized controlled trials were assessed using the RoB 2 tool;[@sterne2019] non-randomised studies of interventions (NRSI), were assessed using the ROBINS-I tool;[@sterne2016]
 
-Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies of interventions.
+For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set of judgements: "Low", "Moderate","High".
+The exact mapping can be seen in Table \@ref(tab:robLevelsMapping-table).
+Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies.
 This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.
+<!-- TODO CITATION NEEDED -->
 
@@
 
-#### Visually inspect results and bias
+In addition to assessing the extent of bias in each domain, as defined by the three levels detailed above, I attempted to records the direction of the bias, so that it could feed into the triangulation.
 
-In order to aid with the triangulation exercise, I created a new method of presentation of these results was developed to enable detailed comparison across different studies contributing to the causal question.
+This was achieved via an additional question at the end of each bias domain, which asked assessors to predict the expected direction of bias in that domain.
+Note that this question is only apply to existing tools (ROB2/ROBINS-I/ROBINS-E), but I employed an identical approach during assessment of Mendelian randomisation studies.
+This optional question response were:
 
-Similar to the standard paired forest plots introduced in Chapter \@ref(), the level of bias across the domains in each study is reported using coloured blocks.
-However, in contrast to the previous plots, arrows are used in place to illustrate the predicted direction of bias in that domain, categorised as pulling towards the left or the right.
+* "Favours experimental"/"Favours comparator" (additive bias)
+* "Towards null"/"Away from null" (proportional bias)
+* "Unpredictable"
 
-This second aspect required some additional consideration, given the distinct and competing options available to assessors.
-For example, the direction of the arrow when the direction of bias is thought to favour the intervention/exposure will be be same regardless of the position of the point estimate.
+As indicated in the options above, the response t this prompt is used both to define the direction and type (additive or proportional) of bias.
+
+Additive biases (identified by a "Favours experimental"/"Favours comparator" response) are XXXX. A key example of additive bias is immortal time bias, which will always favour the intervention.
+
+Proportional biases (identified by a "Towards null"/"Away from null" response) are those related to the magnitude of the effect.
+A key example of this type of bias is non-differential misclassification bias, which will bias the effect estimate towards the null.
+
+When predicting the direction of effect
+
+From these response the direction of effect was calculated. For additive biases, this was simply a case of shifting the effect estimate to the left or right. For proportional biases, decide
+
+For example, the direction of the bias when the direction of bias is thought to favour the intervention/exposure will be be same regardless of the position of the point estimate.
 The same is not true for the "Towards the null"/"Away from the null" options.
+
 For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be represented by a right pointing arrow (Figure \@ref(fig:)).
@@
 
+However,
+
+S
+
+Highlight that this is slightly different for the confounding domain in non-randomised studies, which only allows for the "Favours experimental", "Favours comparator", and "Unpredictable" options.
+
+Of note, the guidance for the tools suggests that if assessors are not able to articulate why the bias in a given domain will "pull" the observed estimate in a specific direction, they should not try to guess.
+
+To assess the usefulness of this system, the number of domains for which bias was expected (i.e.
+judged to be a more than Low risk of bias) but for which no expected direction could be identified were expressed as a percentage.
+If this percentage is high, the helpfulness of the approach is
+
+<!-- TODO text -->
+
+#### Visualisation of extent and direction of bias
+
+To aid with the triangulation exercise and to act as, I created a new method of presentation of the extent/direction bias asessment results to enable detailed comparison across different studies contributing to the synthesis.
+While these figures do not
+
+Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), the level of bias across the domains in each study is reported using coloured blocks.
+However, in contrast to the previous plots, arrows are used in place to illustrate the predicted direction of bias in that domain, categorised as pulling towards the left or the right.
+
+This second aspect required some additional consideration, given the distinct and competing options available to assessors.
+
 Tha
 
-Helper functions in the forthcoming `triangulate` package - see Appendix BLAH.
+Helper functions in the forthcoming `triangulate` package - see Appendix \@ref() - help to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses.
+These bias direction plots themselves were created using the risk of bias isualisation tool described in Appendix \ref().
 
@@
 
-These graphs were built using the risk of bias tool described in Appendix \ref()
-
-<!-- TODO Does immortal time bias not also have a consistent effect -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Types of bias
-
-Additive biases are those independent of the effect estimate - they shift it left or right. These biases are indicated by the "Favours comparator"/"Favours experiment/exposure" options in the
+<!-- TODO Does immortal time bias not also have a consistent effect? yes, but inception bias does not necessarily -->
 
@@
 
-For example, for a "High" additive bias in $j$th domain of the $i$th study:
-
-$\delta_{ij}^{\mathrm{High}}$
-
-Uncertainty around this estimate, $\delta_{ij}^{\mathrm{High}}$, is given by a distribution:
+For example, for a "High" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
 
 $$
-\delta_{ij}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
+\delta_{i,j}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
 $$
@@
 a "high" bias in one domain is equivalent to a "high" bias in any other.
-As such, for this analysis, I assumed that the distributions assigned to each level of bias is contrast across all values of j, or alternatively, is constant across all domains in the risk of bias assessment tool.
+As such, for this analysis, I assumed that the distributions assigned to each level of bias are identical across all values of $j$, that is, are identical for all domains in the risk of bias assessment tool.
 
@@
 
-<!-- TODO Discuss proportional versus additive, and the fact that all biases considered previously for internal were deemed to be additive. -->
+&nbsp;<!----------------------------------------------------------------------->
+
+(ref:priorsAdd-caption) Distributions for additive bias assigned to each bias judgement under two sensitivity scenarios, on the log scale.
+
+(ref:priorsAdd-scaption) Additive bias distributions
+
+```{r priorsAdd-table, message=FALSE, results="asis", echo = FALSE}
+```
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ####	Combine in a bias-adjusted meta-analysis
 
-Once the total internal and external additive and proportional biases for each result were computed, they were used to define an adjusted estimate and
+Once the total internal and external additive and proportional biases for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis
 
-Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate is defined as:
+Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate for each result is defined as:
 
@@
 
-The standard error of this estimate is then calculated as:
+where $\mu_{i\delta}$ denotes total additive and $\mu_{i\beta}$ the total proportional bias, and the $^{\mathrm{I}}$ and $^{\mathrm{E}}$ superscripts denote internal and external (indirectness) biases respectively.
+
+using the same terms, the standard error of this estimate, $\hat{\theta}$, is then calculated as:
 
 $$
-\mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{I}} \mu_{i \beta}^{\mathrm{E}}}\right)^{2}\left\{s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{I}} 2+\sigma_{i \beta}^{\mathrm{I}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{E} 2}+\sigma_{i \delta}^{\mathrm{E} 2}\right)+\sigma_{i \beta}^{\mathrm{I}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{E}}+\mu_{i \delta}^{\mathrm{E}}\right)^{2}+\sigma_{i \delta}^{\mathrm{I} 2}\right\}
+\mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{I}} \mu_{i \beta}^{\mathrm{E}}}\right)^{2}\left(s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{I}} 2+\sigma_{i \beta}^{\mathrm{I}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{E} 2}+\sigma_{i \delta}^{\mathrm{E} 2}\right)+\sigma_{i \beta}^{\mathrm{I}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{E}}+\mu_{i \delta}^{\mathrm{E}}\right)^{2}+\sigma_{i \delta}^{\mathrm{I} 2}\right)
 $$
 
-Once each individual result has been adjusted, they are combined n a standard random-effects meta-analysis, conducted using the `metafor` R package.
+Once each individual result has been adjusted, they are combined n a standard random-effects meta-analysis <!-- TODO CITATION NEEDED -->
 
-The code to implement this model was obtained via contact with the primary author of the original paper proposing the elicitation.
-For compatibility, the STATA code was converted to R, and to verify the accuracy of the translation, the results of the original analyses were reproduced (see Appendix \@ref() for details).
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Software
+
+Personal communication with the authors of the original method resulted in the STATA code to implement the
+
+As detailed in the introduction to this section, the model for defining bias-indirectness-adjusted results was available as STATA code.
+The  has since been generalised as part of the `triangulate` R package to allow for users to apply the approach detailed here.
+
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, calculate bias/indirectness-adjusted estimates for each result, and synthesise these adjusted results in a standard random-effects meta-analysis.
+
+All meta-analyses conducted within the package are implemented using the `metafor` R package.
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
+```{r biasDirectionPlots, include = F}
+```
+
+(ref:ldlAdBiasDirection-cap) __Bias direction plot, summarising internal biases related to effect of LDL-c on Alzheimer's disease :__
+
+(ref:ldlAdBiasDirection-scap) Bias direction plot, summarising internal biases related to the
+
+```{r ldlAdBiasDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:ldlAdBiasDirection-cap)', out.width='100%', fig.scap='(ref:ldlAdBiasDirection-scap)'}
+knitr::include_graphics(file.path("figures/tri/midlife_AD.png"))
+```
+&nbsp;<!----------------------------------------------------------------------->
+
 Including sensitivity analyses
@@
 and citations of studies - going to be a bit of pain
+
+As expected
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Percentage of domains for which a direction of bias could be assigned?
+
+Main takeway is that heteorgeneity between study designs is substantially reduced
 
@@
 
+Previous work on assessing the impact of different sources of bias on effect estimates . For example, a study examining the effect of found that studies with
+
+Previous work examining
+
+A further issue is the "Low" risk of bias domain.
+In this proof-of-concept analysis, I assumed that domains at "Low" risk of bias did not require any adjustment.
+However, "Low" risk of bias is not equivalent to the absence of bias, and potentially should still be adjusted for.
+In this case, defining the predicted direction of bias would be challenging in the absence of obvious sources of bias (particularly given how challenging it can be when sources of bias are evident within a domain).
+
 In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elicitation process using a number of experts.
+This approach is potentially subject to misclassification of the impact of bias on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount.
+For example, if experts are influenced by the absolute effect estimate, then a result demonstrating a stronger protective effect may receive greater modification than a study at the same "risk" of confounding but with a more modest effect.
+This is particular true where experts have preconceived ideas about the true effectiveness of the intervention.
+
+In this case, separating the assessment of bias from the assignment of modifying values to each level of bias will limit the potential for.
+Alternatively, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team, similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.
+
+In the mean time, the extent of the impact of knowledge of the results could be analysed using existing data.
+For example, a re-analysis of the data presented in a recent paper where both expert eliciation and structured
 
@@
 <!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
-
-i)	Ideally modifying values (both internal and external) would be based on empirical research, but in absence of this, sufficient to model multiple values (High = 0.1, Some concerns =0.05, Low = 0) and relationships (High = 0.3, Some concerns =0.1, Low = 0)?
-
-Need range around modifying values, as total variance of the biases is added to the total variance of the studies (elicitation on scale presented above asks for range rather than single estimate
 
@@
 
+This method is also different from previous implementations of the bias-adjusted meta-analysis approach, in that for each domain for each study, the bias can be either proportional or.
+IN previous implementations, distributions for each source of bias (pre-domain-based tools) were elicted on both the additive and proportional scales.[@turner2009] Puts more pressure on the assessor to correct sum additive and proportional biases highlighted, and answer with only a single option.
+
 #### E-values
@@
 
+### Filling in the gaps
+
+Triangulation as a extension of evidence synthesis.
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ## Conclusion

### 2021-11-12 front-and-back-matter/_00-introduction.Rmd
End of day: 39966

--- 2021-09-29 front-and-back-matter/_00-introduction.Rmd
@@
 
-```{r word-count, echo=FALSE, warning=FALSE, message=FALSE}
-library(dplyr)
-library(ggplot2)
-
+```{r wordcount, echo=FALSE, warning=FALSE, message=FALSE}
 options(scipen=999)
@@
 
-```{r word-count-fig, echo=FALSE, warning=FALSE, message=FALSE}
+```{r wordcount-fig, echo=FALSE, warning=FALSE, message=FALSE}
 ggplot(mapping = aes(x=date,y=words)) +

### 2021-11-13 07-Chp-Triangulation.Rmd
End of day: 40371

@@
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
+
+\newpage
 
@@
 
+\newpage
+
 ### Overview of triangulation {#triangulation-overview}
@@
 
-It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] In this framework,
+It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] A good working definition of the triangulation is:
+
+> The practice of strengthening causal inferences by integrating results from several different approaches, where each approach has different (and assumed to be largely unrelated) key sources of potential bias.[@lawlor2016]
+
+This represents a significant step forward from the current evidence synthesis practice of synthesising evidence from only one approach (e.g. RCT, observational study, etc.).
+
+However, previous attempts at triangulation have ignored the potential for varying and opposing sources of bias within an approach, assigning a level and direction of bias to entire categories of studies.
+
+Recent development in bias assessment have a allowed fro a much more granular consideration of the threats to the internal validity of a result.
+
+For example, while it may be true that all non-randomised studies share some _minimal level_ of bias, investigation of the biases applicable to each individual result gives useful additional information, and is essential for any attempt at quantitative triangulation.
+
+This chapter, in addition to providing a narrative comparison of the existing and new evidence identified in this thesis, attempts to combine the results numerically by building on existing work on this topic.
+
+In the following section, I define important terms used throughout this chapter.
 
@@
 
-### Terminology
+\newpage
+
+### Terminology {#tri-terminology}
+
+<!-- Discuss and defined three things: -->
+
+<!-- * Qualitative vs quantitative triangulation -->
+<!-- * Bias vs. indirectness -->
+<!-- * Additive vs proportion effect of bias/indirectness -->
 
 __Different types of triangulation__
+
+Triangulation exercises can be characterised as either qualitative or quantitative.
 
@@
 
-Previous examples of this approach have used criteria such as
+In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.
+This method is in its infancy, given important methodological challenges that are illustrated in this Chapter.
 
-In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.
+Both
 
-However, previous attempts at triangulation ignore the potential for varying and opposing sources of bias within a evidence source. For example,
+Bias (or internal bias) in the result is defined as systematic deviation from result the "idealised" version of the study (that is, )
 
-The terminology used in describing different mechanisms by which an observed result may  complicate interpretation. This section clearly defines how each are used in h
+In contrast, the indirectness of the result (also called generalisability or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.
+Problems with indirectness can be arise from differences in population, intervention/exposure, outcomes and
 
-Here, internal bias is used in terms of
+Of note, the original method employed in this chapter refers indirectness as "external bias" - however.
+This distinction is important, as bias and indirectness describe two different issues, and referring to both as bias
 
-In contrast, external bias (also called indirectness, or )
+In addition, indirectness is the widely used term, including by widely-adopted methods such as the GRADE framework.[@guyatt2011]
 
-Additionally, potential biases can be additive or proportional. Pro
+__Additive vs proportional effects__
 
-Talk about problems of sclae - assuming bias direction at the study level works well if you only have one study per design category as in the example by Ference et al (e.g. IPD analysis of )
+The effects of both bias and indirectness can be either additive or propotional.
+
+Additive bias/indirectness is
+
+Both bias and indirectness can be defined as additive or propotional. Additive bias/indirectness is that which can shift the p
 
 &nbsp;<!----------------------------------------------------------------------->
+
+\newpage
 
@@
 1. Define modifying terms for bias and indirectness in each result
-1. Perform bias-adjusted meta-analysis using bias-/indirectness-adjusted results
+1. Perform bias-adjusted meta-analysis using bias-adjusted results
 
@@
 
-As indicated in the options above, the response t this prompt is used both to define the direction and type (additive or proportional) of bias.
+As indicated in the options above, the response t this prompt is used both to define the direction and type (additive or proportional) of bias (see ).
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Visualisation of extent and direction of bias
@@
 
-For example, for a "High" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
+For example, for a "High" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution
 
-$$
+\begin{equation}
   \delta_{i,j}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
-$$
+  (\#eq:name)
+\end{equation}
 
@@
 
-For the purposes of this example analysis,
-
-High
-Some concerns
-
-These figures were sense-checked against
-
-However, this also allows us to a priori define common modifying values across all domains of bias.
-In a bias-adjusted meta-analysis using this approach, a high risk of bias in the will have the same modifying effect on the results.
-
-As such, a simulation approach was taken to explore the impacts of several different strategies
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-####	Assign modifying values to indirectness
+<!-- TODO In the absence of any empirical data regarding the priors, I used the data from the expert elicication approach to calculate both the mean and max.
+These estimates, in addition to conversations with topic experts -->
 
-As I am attempting to identify the causal effect across different study designs, I needed to . This is not necessary if just summarising the literature.
+For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I defined two sets of modifying distributions (Table 1).
+In the first scenario, the relationship between the position assigned to each judgement is linear.
+In the second scenario, .
+In both cases, the variance of the "High" risk of bias judgement was defined to be great than the "Moderate" risk of bias judgement.
+The two scenarios are illustrated in Figure \@ref(fig).
+
+Reasonable values for the position and spread of the distributions were informed by calculating the mean and maximum adjustment values as defined by the original elicitation exercise (see Appendix \@ref(?) for more details on how these were calculated).
+[@turner2009] <!-- TODO Link this to open data!
+-->
+
+Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain, but the appropriate variance for (i.e.
+no predicted direction, but increased uncretainty in line with judgement).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+####	Assessing and assigning modifying values to indirectness
 
@@
 
-In the original method, this was assessed against 4 categories of internal bias.
+In the original method, this was assessed against 4 categories of external bias (population/intervention/control/outcome)
 
@@
 
-"One important difference between these approaches that will need to be addressed in the triangulation is that RCTs relate to short-term modification of lipid levels, whereas Mendelian randomisation studies typically refer to lifelong exposures; and traditional observational epidemiology approaches may refer to short or longterm exposure (although are often not explicit about this).
-The triangulation will take these into account, for example by superimposing the studies on a hypothetical model for exposure-outcome relationship across the life course."
+A key example here is that
 
-<!-- From NIHR applications -->
+All indirectness bias were defined as being proportional. As described i
 
-<!-- "If the aim of a meta-analysis is to summarize the literature rather than to address a target question, there is no need to adjust for external biases since differences between the (idealized) studies are accepted as diversity.
-The need to adjust for internal biases remains and our method can be applied directly to these." Taken from https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2667303/ - good explanation on difference between qualitative and quantitative triangulation.
--->
+This is also in line with previous efforts to assess the adjustment needed due to indirectness
+
+As crude example focusing on the intervention , versus the causal question of the effect of LDL-c in mid-life on Alzheimer's disease, studies of lipids levels in this time period would require minial adjustment, whereas studies
+...
 
@@
 
-Once the total internal and external additive and proportional biases for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis
+Once the total additive and proportional biases for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis.
 
-Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate for each result is defined as:
+Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate for each result, $\hat\theta$, is defined as:
 
-$$
-\hat{\theta} = \frac{y_i - \mu_{i\delta}^{\mathrm{I}} - \mu_{i\beta}^{\mathrm{E}}\mu_{i\delta}^{\mathrm{E}}}{\mu_{i\beta}^{\mathrm{I}}\mu_{i\delta}^{\mathrm{E}}}
-$$
+\begin{equation}
+  \hat{\theta} = \frac{y_i - \mu_{i\beta}^{\mathrm{In}}\mu_{i\delta}^{\mathrm{In}} - \mu_{i\delta}^{\mathrm{B}}}{\mu_{i\beta}^{\mathrm{B}}\mu_{i\beta}^{\mathrm{In}}}
+  (\#eq:adjusted-mean)
+\end{equation}
 
-where $\mu_{i\delta}$ denotes total additive and $\mu_{i\beta}$ the total proportional bias, and the $^{\mathrm{I}}$ and $^{\mathrm{E}}$ superscripts denote internal and external (indirectness) biases respectively.
+where $\mu_{i\delta}$ denotes total additive and $\mu_{i\beta}$ the total proportional adjustment, and the $^{\mathrm{B}}$ and $^{\mathrm{In}}$ superscripts denote wether the adjustment relates to internal bias or indirectness respectively.
 
-using the same terms, the standard error of this estimate, $\hat{\theta}$, is then calculated as:
+Using the same terms, the standard error of this estimate, $\hat{\theta}$, is then calculated as:
 
-$$
-\mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{I}} \mu_{i \beta}^{\mathrm{E}}}\right)^{2}\left(s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{I}} 2+\sigma_{i \beta}^{\mathrm{I}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{E} 2}+\sigma_{i \delta}^{\mathrm{E} 2}\right)+\sigma_{i \beta}^{\mathrm{I}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{E}}+\mu_{i \delta}^{\mathrm{E}}\right)^{2}+\sigma_{i \delta}^{\mathrm{I} 2}\right)
-$$
+\begin{equation}
+  \mathrm{SE}(\hat{\theta})=\left(\frac{1}{\mu_{i \beta}^{\mathrm{B}} \mu_{i \beta}^{\mathrm{In}}}\right)^{2}\left(s_{i}^{2}+\left(\mu_{i \beta}^{\mathrm{B}} 2+\sigma_{i \beta}^{\mathrm{B}}\right)\left(\hat{\theta}^{2} \sigma_{i \beta}^{\mathrm{In} 2}+\sigma_{i \delta}^{\mathrm{In} 2}\right)+\sigma_{i \beta}^{\mathrm{B}}\left(\hat{\theta} \mu_{i \beta}^{\mathrm{In}}+\mu_{i \delta}^{\mathrm{In}}\right)^{2}+\sigma_{i \delta}^{\mathrm{B} 2}\right)
+  (\#eq:adjusted-se)
+\end{equation}
 
@@
 
-#### Software
+#### Software {#tri-software}
 
@@
 
+Show result and bias
+
+Reproduce version of Table 2 rom the "proposed method" paper for indirectness
+
+Calculate internal-bias adjusted
+
+Calculate both-adjusted
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Causal question #1
+
+Midlife LDL-c on Alzheimer's disease
 
@@
 
+<!----------------------------------------------------------------------------->
+(ref:ldlDemBiasDirection-cap) __Effect of LDL-c on All-cause dementia in late life:__
+
+(ref:ldlDemBiasDirection-scap) Effect of LDL-c on All-cause dementia in late life
+
+```{r ldlDemBiasDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:ldlDemBiasDirection-cap)', out.width='100%', fig.scap='(ref:ldlDemBiasDirection-scap)'}
+knitr::include_graphics(file.path("figures/misc/UoBcrest.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-Main takeway is that heteorgeneity between study designs is substantially reduced
+Main takeaway is that heterogeneity between study designs is substantially reduced
 
@@
 
-This chapter has demonstrated how new developments in systematic risk of bias assessment.
+Thsi chapter has narratiely synthesised the exsiting and new evidence from the previous chapters, highlighting the lim
+
+In addition, it has sought to provide a generalised framework for quantitative triangulation, building on existing methods for systematic domain-based risk of bias assessment and bias-/indirectness-adjusted meta-analysis.
 
 Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.
-
 While this makes the process both more labour intensive and complex, to assume that, for example, all retrospective studies are equally at risk is to overlook.
-While ti could be true that all retrospective studies share some _minimal level_ of bias, there are several opportunities.
-Failing to separate these the individual results loses information, particularly given the now widespread availability of tools to systematically assess the biases present in each result.
-
-In this chapter, I have presented a new method of visualising both the level and expected direction of bias inherent to each result, and suggested how this could be incorporated with a bias-adjusted meta-analysis approach to work towards a generalised qunatitative triangulation framework.
-
-I've highlighted the limitations of this method, as the correct distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies which do not yet exist, framing them as opportunities for future research.
 
@@
 
-For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and review of Research group has this as a secondary methodological aim.
-
-&nbsp;<!----------------------------------------------------------------------->
+For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and Review of Research group has this as a secondary methodological aim.
 
@@
 
+Appreciation that both the risk of bias and indirectness of a result should be assessed is growing.
+Indeed, some existing risk of bias for the assessment of diagnostic test accurary[@whiting2011a] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
+<!-- TODO Cite PROBAS and QUADAS -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Subjectivity of risk of bias assessments
@@
 
-#### Defining appropriate levels of bias
+&nbsp;<!----------------------------------------------------------------------->
 
-Previous work on assessing the impact of different sources of bias on effect estimates . For example, a study examining the effect of found that studies with
+#### Defining appropriate values for bias/indirectness adjustment
 
-Previous work examining
+Much of the attention to date has been on assessing the impact of different sources of bias on effect estimates has focused predominantly on randomised controlled trials.
+
+For example, a study examining the effect of found that only a subset of domains appear to impact the result, and that this effect is modest (10% change).[@savovic2018] However, this work examined RCTs, and these findings may not hold for other non-randomised study designs.
+<!-- TODO Double check this citation actually says what you think it does!
+-->
 
@@
 
-Ideally, the modifying values
-
 <!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
@@
 
-One potential - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
+As illustrated in Table \@ref(tab:robLevelsMapping-table), studies at critical risk of bias were not included in the analysis.
+
+one potential limitation of the  - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
 
@@
 
-#### Type of bias (proportional vs additive) not shown on figure
+#### Type of bias (proportional vs additive) not shown on bias direction plot
 
@@
 
-### Alternative approaches
+### Related approaches
 
-This method is also different from previous implementations of the bias-adjusted meta-analysis approach, in that for each domain for each study, the bias can be either proportional or.
-IN previous implementations, distributions for each source of bias (pre-domain-based tools) were elicted on both the additive and proportional scales.[@turner2009] Puts more pressure on the assessor to correct sum additive and proportional biases highlighted, and answer with only a single option.
-
-#### E-values
-
-Present as an alternative to putting priors on the level of bias due to confounding.
-
-E-values work the other way around - get result then work out how strong a biasing factor would have to be to negate the result.
-IN other words, they represent an estimate ho how strong the total residual confounding would have to be in order to full explain away the observed result.[@vanderweele2017]
-
-One major problem is that they can only be used to evaluate negating biases, not other biases.
-
-How strong unmeasured confounding would have to be in order to explain the observed effect.
-
-Heavily criticised in a range of papers.
-
-Also, no useful to focus on a specific bias in the context of risk of bias domains
-
-As an example, I calculated the E-value required to attenuate the hamrful association observed between statin use and vascular dementia in the CPRD analysis ( `r hold()`` ) presented in Chapter \@ref(cprd-heading).
-Assuming an outcome prevalence of <15%, an E-value of 3.31 was identified
-
-This calculation was performed using the XXX R package.
-
-<!-- TODO Ensure that the example is provided first, as you then go on to disparage it - in the example given, the main driver of bias is likely to be confounding (though some may be due to misclassification) -->
-
-However, this approach is only useful if the only source of bias in a result is due to uncontrolled confounding (as assessed by a domain-based risk of bias tool).
-
-Otherwise, it's interpretation is more challenging, as the biasing effect is incorrectly assinged complete to confoudning, thus overestimating the expected effect of confounding.
-
-the contribution of confounding to the bias in a result, and while it may be applicable if the only bias assessed to
+<!-- TODO Need more here on the other approaches discussed in the recent comparison paper -->
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
+\newpage
 
@@
 
-As the need and appetite for snthesis of different, future iterations of the risk of bias tools should take this into account.
-Simple things like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
+As the need and appetite for synthesis of different, future iterations of the risk of bias tools should take this into account.
+Simple steps like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
 Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.
@@
 While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e.
-not applying expected directions of effects to a ).
+not applying expected directions of effects to an entire category of studies ).
 
-This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result seperately.
+This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result separately.
 This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.
@@
 
-Triangulation as a extension of evidence synthesis.
+Triangulation, both qualitative and quantitative, should be considered an extension of evidence synthesis, and so.
+Triangulation exercises should be based on comprehensive systematic reviews to create.
+If needed, evidence gaps can be addressed through additional studies, as in the case of this analysis,
+
+### Outputs
+
+Software
+
+Annotated example dataset
+
+this ties in with the open data sharing of the by-assessor elictation data from, which i sued in this analysis to frame the modifying values assigned to
+
+Generalised version of code, allowing for different distributions in each domain of bias (which will be handy once we get a better idea of what they should be).
 
@@
 
+In this chapter, I have presented a new method of visualising both the level and expected direction of bias inherent to each result, and suggested how this could be incorporated with a bias-adjusted meta-analysis approach to work towards a generalised quantitative triangulation framework.
+
+Finally, I've highlighted the limitations of this method, as the correct distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies which do not yet exist, framing them as opportunities for future research.
+
 This chapter has demonstrated a repurposed framework for quantitative triangulation, exploiting existing methods in evidence synthesis and developments in the assessment of different risks of bias.
@@
 
+The implications of this work to clinical practice, public health and future research is considered in the following chapter.
+
 \newpage

### 2021-11-13 08-Discussion.Rmd
End of day: 40371

@@
 
+Given the detailed discussion
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## New evidence
+
+Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at midlife, driven by the finding for Alzheimer's disease [@iwagami2021].
+Not inconsistent with the findings presented in this thesis
+
+## Lessons learned
+
+There are
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-It has analysed two previously unalysed datasets, adding useful information to the evidence base
+It has analysed two previously unanalysed datasets, adding useful information to the evidence base.
 
@@
 
-The clinical recommendations that can be drawn from the work in this thesis are limited, due to the
+Across multiple sources of evidence, there was no consistent effect of blood lipids, or . Some
 
-however, a key limiting factor is the absence of a detailed pathological mechanism for Alzheimer's disease. Additionally, vascular dementia
+The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence related to the
+
+There was very we. Conversely however, there was an absence of evidence for a harmful effect of statins on. Given the reality that given the choice, given the conflicting evidence
+
+Patients must live to a sufficient age to be at risk of dementia outcomes, which is substantially less like if high lipid levels in mid-life.
+
+The role of lipid-lowering
+
+As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for Alzheimer's disease.
+It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.
 
 However, based on the available evidence
+
+For other dementia outcomes,
 
@@
 ## Future work
+
+Several avenues for future research, buiding on the work presented here,
+
+###
 

### 2021-11-13 R/bias_adjusted.R

@@ -253,18 +253,40 @@ dat_rob <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"), whi
 final <- left_join(ids, dat_rob, by = c("result_id" = "result_id")) %>%
   rename_at(vars(starts_with('d')), funs(paste0(.,"j"))) 
 
-
-dat <- read.csv("turner_bias/real_example_rob.csv",stringsAsFactors = F) %>%
+dat2 <- read.csv("turner_bias/real_example_rob.csv",stringsAsFactors = F) %>%
   left_join(
     rio::import(
       here::here("data/sys-rev/data_extraction_main.xlsx"),
       which = 2
     ) %>% janitor::clean_names() %>%
       select(result_id, author, year)
-  )
-
-dat <- dat %>%
-  select(result_id, author, type, yi, sei, everything())
+  ) %>%
+  mutate(vi = sei^2) %>%
+  select(-sei) %>%
+  select(result_id, author, type, yi, vi, everything()) %>%
+  tidyr::pivot_longer(matches("d[0-9]+(d|j|t)"), 
+                      names_to = c("domain",".value"),
+                      names_pattern = "(d[0-9]+)(d|j|t)") %>%
+  mutate(across(c(j,d,t), stringr::str_to_lower)) %>%
+  # Additive biases
+  mutate(m_add = case_when(t == "add" & j == "serious" ~ 0.16,
+                           t == "add" & j == "moderate" ~ 0.08,
+                       T ~ 0),
+         v_add = case_when(t == "add" & j == "serious" ~ 0.1,
+                           t == "add" & j == "moderate" ~ 0.05,
+                       T ~ 0)) %>%
+  # Proportional biases
+  mutate(m_prop = case_when(t == "prop" & j == "serious" ~ 0.1,
+                            t == "prop" & j == "moderate" ~ 0.03,
+                            T ~ 0),
+         v_prop = case_when(t == "prop" & j == "serious" ~ 0.05,
+                            t == "prop" & j == "moderate" ~ 0.016,
+                           T ~ 0)) %>%
+  # Signs
+  mutate(m_add = case_when(d == "left" ~ m_add*-1,
+                           T ~ m_add), 
+         m_prop = case_when(d == "left" ~ m_prop*-1,
[…]

### 2021-11-13 R/bias_adjusted_clean.R

@@ -1,0 +1,107 @@
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# INTERNAL BIAS
+# Generate internal summaries
+
+# write code to create this from spreadsheet
+
+values <- list(
+  d1 = c(
+    "add_serious_mn" = 0.16,
+    "add_serious_var" = 0.1,
+    "add_moderate_mn" = 0.08,
+    "add_moderate_var" = 0.05, 
+    "prop_serious_mn" = 0.1,
+    "prop_serious_var" = 0.05,
+    "prop_moderate_mn" = 0.03,
+    "prop_moderate_var" = 0.016
+  )
+)
+
+dat <- read.csv("turner_bias/real_example_rob.csv",
+                stringsAsFactors = F) %>%
+  left_join(
+    rio::import(
+      here::here("data/sys-rev/data_extraction_main.xlsx"),
+      which = 2
+    ) %>% janitor::clean_names() %>%
+      select(result_id, author, year)
+  ) %>%
+  mutate(vi = sei^2) %>%
+  select(result_id, author, type, yi, vi, everything())
+
+
+append_values <- function(data, values) {
+
+  data %>%
+    # Clean and covert to long format
+    tidyr::pivot_longer(
+      matches("d[0-9]+(d|j|t)"),
+      names_to = c("domain", ".value"),
+      names_pattern = "(d[0-9]+)(d|j|t)"
+    ) %>%
+    mutate(across(c(j, d, t), stringr::str_to_lower)) %>%
+  # Additive biases
+  mutate(m_add = case_when(t == "add" & j == "serious" ~ values[["d1"]][["add_serious_mn"]],
+                           t == "add" & j == "moderate" ~ values[["d1"]][["add_moderate_mn"]],
+                           T ~ 0),
+         v_add = case_when(t == "add" & j == "serious" ~ values[["d1"]][["add_serious_var"]],
+                           t == "add" & j == "moderate" ~ values[["d1"]][["add_moderate_var"]],
+                           T ~ 0)) %>%
+  # Proportional biases
+  mutate(m_prop = case_when(t == "prop" & j == "serious" ~ values[["d1"]][["prop_serious_mn"]],
+                            t == "prop" & j == "moderate" ~ values[["d1"]][["prop_moderate_mn"]],
+                            T ~ 0),
[…]

### 2021-11-13 R/07-Code-Triangulation-Analysis.R
End of day: 40371

@@ -94,7 +94,7 @@ dat <- read.csv("turner_bias/real_example_rob.csv",stringsAsFactors = F) %>%
   mutate(vi = sei^2)
 
 dat <- dat %>%
-  select(result_id, author, type, yi, vi, everything(), -sei)
+  select(result_id, author, type, yi, vi, everything())
 
 png(
   here::here("figures/tri/midlife_AD.png"),

### 2021-11-14 07-Chp-Triangulation.Rmd
working triangulation framework

@@
 
+<!----------------------------------------------------------------------------->
+(ref:biasDirectionSingle-cap) Bias direction plot for a single study showing the predicted direction of bias in each domain.
+Additive biases are characterised using arrows, while the proportional biases are denoted using $<$ and $>$.
+A question mark indicates that the direction of bias was unpredictable.
+
+(ref:biasDirectionSingle-scap) Bias direction plot for a single study
+```{r biasDirectionSingle, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:biasDirectionSingle-cap)', out.width='100%', fig.scap='(ref:biasDirectionSingle-scap)'}
+knitr::include_graphics(file.path("figures/misc/UoBcrest.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-```{r biasDirectionPlots, include = F}
+```{r ldlAdBIAMA, include = F}
 ```
@@
 As expected
+
+<!----------------------------------------------------------------------------->
+(ref:fpLdlAd-cap) __shortcap:__
+
+(ref:fpLdlAd-scap) shortcap
+
+```{r fpLdlAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAd-cap)', out.width='100%', fig.scap='(ref:fpLdlAd-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad.png"))
+```
+<!----------------------------------------------------------------------------->
 

### 2021-11-14 R/07-Code-Triangulation-Analysis.R

@@ -76,39 +76,6 @@ if (doc_type == "docx") {
     kable_styling(latex_options = c("HOLD_position"))
 }
 
-
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- biasDirectionPlots
-
-source("R/forest tri.R")
-
-dat <- read.csv("turner_bias/real_example_rob.csv",stringsAsFactors = F) %>%
-  left_join(
-    rio::import(
-      here::here("data/sys-rev/data_extraction_main.xlsx"),
-      which = 2
-    ) %>% janitor::clean_names() %>%
-      select(result_id, author, year)
-  ) %>%
-  # Get sampling variance (square of standard error)
-  mutate(vi = sei^2)
-
-dat <- dat %>%
-  select(result_id, author, type, yi, vi, everything())
-
-png(
-  here::here("figures/tri/midlife_AD.png"),
-  width = 1750,
-  height = 1200,
-  pointsize = 15,
-  res = 100
-)
-
-forest_triangulation(dat, sei = dat$sei, title = "LDL-c and AD")
-
-dev.off()
-
-
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- turnerEstimates
 
@@ -161,6 +128,122 @@ prop <- rio::import("turner_bias/propbias_full.dta") %>%
   summarise(mean = mean(value),
             max = max(value))
 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- ldlAdBIAMA 
 
+# read in values from spreadsheet
+
+bias_values <- rio::import("turner_bias/bias_values.csv") %>%
+  rename_with(~paste0("bias_",.), matches("_"))
+
+indirect_values <- rio::import("turner_bias/indirectness_values.csv")  %>%
+  rename_with(~paste0("ind_",.), matches("_"))
+
+# Load general data
+dat_gen <- rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),
+                       which = 2) %>% janitor::clean_names() %>%
+  select(result_id, author, year)
+
+# Read in result and risk of bias data
[…]

### 2021-11-14 07-Chp-Triangulation.Rmd
End of day:

@@
 
-Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
+__TBC__
+
+<!-- Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
 Different sources of evidence will have different limitations.
 If the result from each source points towards the same answer, this improves our confidence in the conclusion.
+-->
 
@@
 
-## Introduction
-
-This chapter will attempt to triangulate the evidence identified by the systematic review in Chapter \@ref(sys-rev-heading-results), with the the results from the analysis of CPRD data (Chapter \@ref(cprd-heading) and IPD \@ref(ipd-heading).
-
-&nbsp;<!----------------------------------------------------------------------->
-
 \newpage
 
-### Overview of triangulation {#triangulation-overview}
+## Introduction {#triangulation-overview}
 
-Aetiological triangulation, or simply triangulation, is the process of comparing and contrasting across result in order to .
-
-It has been widely used in the literature, and is comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts.[@hill1965] A good working definition of the triangulation is:
+Aetiological triangulation, or simply triangulation, is the process of comparing and contrasting across different sources of evidence.
+Triangulation is broadly comparable to Bradford-Hill's criteria of "consistency", that is the replication of an observed relationship across several different contexts,[@hill1965] where contexts are assumed to have different underlying bias structures.
+More formally it can be defined as:
 
@@
 
-This represents a significant step forward from the current evidence synthesis practice of synthesising evidence from only one approach (e.g. RCT, observational study, etc.).
+This approach represents a significant step forward from the current evidence synthesis practice of synthesising evidence from only one approach (e.g.
+randomised controlled trials (RCTs), non-randomised studies of exposures (NRSE) or interventions (NRSI), etc.).
+The most common implementation of this method to date has been in the form of _qualitative triangulation_ - that is the identification and a narrative comparison, where the internal biases and differences between the study question and the causal question of interest (indirectness) of each result are discussed.
 
-However, previous attempts at triangulation have ignored the potential for varying and opposing sources of bias within an approach, assigning a level and direction of bias to entire categories of studies.
+However, qualitative triangulation faces issues at scale.
+There is a need to include all evidence, as otherwise the potential for cherry-picking, yet as the number  as it is not possible to compare and contrast across multiple results in any meaningful way.
+This fact is also illustrated by previous exemplars of triangulation only considering three individual results.
+<!-- TODO CITATION NEEDED - original triangulation paper and Ference --> An alternative option previously employed is to assign bias to the output of a meta-analysis of similarly designed studies, but this loses information on the specific biases inherent to each results contributing to the summary estimate.
+For example, while it may be true that all non-randomised studies share some minimal level of bias, investigation of the biases applicable to each individual result gives useful additional information.
+Recent development in bias assessment have allowed for a much more granular consideration of the threats to the internal validity of a result.
+In combination, these limitations to qualitative triangulation detail a need for a more systematic way to integrate across multiple evidence sources as the number of individual results contributing to the exercise increases.
 
-Recent development in bias assessment have a allowed fro a much more granular consideration of the threats to the internal validity of a result.
-
-For example, while it may be true that all non-randomised studies share some _minimal level_ of bias, investigation of the biases applicable to each individual result gives useful additional information, and is essential for any attempt at quantitative triangulation.
-
-This chapter, in addition to providing a narrative comparison of the existing and new evidence identified in this thesis, attempts to combine the results numerically by building on existing work on this topic.
-
+This chapter, in addition to providing a narrative comparison of the existing and new evidence identified in this thesis, builds on recent developments in risk-of-bias assessment and existing methods for bias-/indirectness-adjusted meta-analysis to propose a generalised framework for quantitative triangulation.
+The method, along with the methodological challenges to its implementation, is illustrated via a proof-of-concept case study examining the causal effect of average exposure to LDL-c at mid-life on Alzheimer's disease risk.
 In the following section, I define important terms used throughout this chapter.
@@
 
-__Different types of triangulation__
+For the sake of clarity, and given the multiple competiting defitions used to define key concepts on this topic, I begin by defining the terms as used in this chapter.
 
-Triangulation exercises can be characterised as either qualitative or quantitative.
+<!-- TODO Does Julian have a good reference for the conflict between different terms used for biases? -->
 
-_Qualitative_ triangulation is describing the different results.
-It regularly appears though not under that name, in the discussion of results section under the name "comparison with other literature".
-
-In contrast, _quantitative triangulation_ attempts to obtain a overall numerical result by synthesising the different types of evidence.
-This method is in its infancy, given important methodological challenges that are illustrated in this Chapter.
+__Bias vs indirectness__
 
@@
 
+Additive biases (identified by a "Favours experimental"/"Favours comparator" response) are XXXX. A key example of additive bias is immortal time bias, which will always favour the intervention.
+
+Proportional biases (identified by a "Towards null"/"Away from null" response) are those related to the magnitude of the effect.
+A key example of this type of bias is non-differential misclassification bias, which will bias the effect estimate towards the null.
+
 The effects of both bias and indirectness can be either additive or propotional.
@@
 
-As outlined in the thesis overview presented in Section \@ref(background-thesis-overview), this triangulation exercise draws on the research produced in each of the preceding chapters.
-More specifically, this chapter builds on the comprehensive systematic review presented in chapter \@re(sys-rev-heading), and incorporates the results of the analyses presented in Chapters \@ref(cprd-heading) (assocation of statins with dementia outcomes in the CPRD) & \@ref(ipd-heading) (association of lipids with dementia outcomes in IPD).
+This triangulation exercise draws on the research produced in each of the preceding chapters.
+More specifically, this chapter builds on the comprehensive systematic review presented in chapter \@ref(sys-rev-heading).
+It also incorporates the new evidence produced by the analysis of the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-heading)) and of the association of lipids with dementia outcomes in previously unanalysed datasets accesssed via the DPUK (Chapter \@ref(ipd-heading)).
 
-Table \@ref(tab:thesisOverview-table) illustrates the causal question each approach has attempted to address, along with the exposures and outcomes for each.
+Table \@ref(tab:thesisOverview-table) summarises the research each approach has attempted to address, the exposures and outcomes considered in each study, and the contribution of each chapter to the triangulation exercise presented here.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in the triangulation exercise.
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a tool rather than a research study.
+(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in this triangulation exercise.
+Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.
 
@@
 
-As a first step to triangulating the available evidence, all information sources were grouped by outcome, and systematically compared and contrasted.
+As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were grouped by outcome, and systematically compared and contrasted.
 Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.
@@
 In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.
-This proof-of-concept approach incorporated advancements in the way that bias in results is assessed (domain-based assessment tools) and existing methods for bias-adjusted meta-analysis[@turner2009] to to illustrate how causal questions could be addressed under this quantitative triangulation framework.
+This proof-of-concept approach incorporates recent advancements in the way that bias in results is assessed (move from checklists to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to to illustrate how causal questions could be addressed under this quantitative triangulation framework.
 
-Several steps were used to accomplish this approach, as described in the following sections. In summary these steps are:
+This proposed framework involves several steps, as described in detail in the following sections. In summary these steps are:
 
 1. Define the causal question of interest
-1. Identify of relevant evidence sources
-1. Assess(and visualise) the extent and direction of bias in each result
+1. Identify of relevant evidence sources and standardisation of effect directions
+1. Assess and visualise the extent and direction of bias in each result
 1. Define modifying terms for bias and indirectness in each result
-1. Perform bias-adjusted meta-analysis using bias-adjusted results
+1. Caclulate bias-/indirectness-adjusted results and perform meta-analysis
 
-The approach was implemented for two causal questions of interest, as defined below.
+In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate for a single study is described in detail for a single study.
+<!-- TODO CITATION NEEDED need to cite single paper here --> Following this, the process for an example causal question as a case study, as defined below.
 
@@
 
-<!-- TODO See ROBINS-E for this, as to how to think about exposures, adn the "Duration and timing of exposure being assessed with different approachesDuration and timing of exposure being assessed with different approaches" section of the aetiological triangulation -->
+Given that this quantitative analysis is intended as a proof-of-concept for the framework, rather than aiming to produce findings that should guide clinical practice, I consider only one of the multiple possible causal questions related to the broad topic of the effect of lipids on dementia outcomes.
 
-This was also guided by the forthcoming ROBINS-E tool, which has
+Using the ROBINS-E framework I defined the parameters of my causal question of interest:
 
-*	Effect of average exposure to LDL-c during midlife on AD 
-* Effect of late-life LDL-c on all-cause dementia
+*	_Population of interest_: General population
+*	_Exposure of interest_: Low density lipoprotein cholesterol
+*	_Exposure window of interest_: Mid-life (45-60)
+* _Summary measure of exposure over time_: Average exposure
 
-&nbsp;
+This question was chosen for a number of reason.
+Firstly, given the long prodomal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period is particularly important.
+Secondly, examining the causal impact of lipids on a specific outcome (in this case, Alzheimer's disease), rather than a composite outcome (all-cause dementia), focuses on an single causal pathway rather than including conditions that likely have very different mechanisms of disease.
+Finally, and relevant to its use as a case study for the quantitative triangulation approach, this question had several relevant sources of evidence available (versus, for example, any question looking at vascular dementia).
 
@@
 
-Once the causal question of interest had been defined, studies related to it were
+Once the causal question of interest had been defined, relevant individual results were obtained from the data sources described in Section \@ref(tri-data-sources).
+In a broad sense, this meant pulling out studies that examined the relationship between LDL-c and Alzheimer's disease risk, either directly (non-randomised studies of LDL-c levels) or indirectly (non-randomised studies of statins, Mendelian randomisation studies using genetic instruments for LDL-c levels).
 
-individual results were obtained from the general evidence sources described in Section \@ref(tri-data-sources)
-
-In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate for a single study is described in detail for a single study.
-Following this, the process was applied to the two subsets of studies related to the causal questions of interest.
+Once the set of relevant results were identified, effects were standardised to refer to the risk of Alzheimer's disease resulting from a "reduction" in LDL-c.
+For studies of statins, th.
+However, for both non-randomised studies and Mendelian randomisation analysis of lipid levels, the effect is usually reported per 1-SD increase in LDL-c.
+In this case, the effect estimates were inverted to ensure consistency across study designs.
 
@@
 The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias).
-In summary, randomized controlled trials were assessed using the RoB 2 tool;[@sterne2019] non-randomised studies of interventions (NRSI), were assessed using the ROBINS-I tool;[@sterne2016]
+In summary, RTCS were assessed using the RoB 2 tool;[@sterne2019] NRSI  using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(#rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
+tool.[@mamluk2020]
 
@@
 Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies.
-This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.
-<!-- TODO CITATION NEEDED -->
+This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.[@sterne2016]
 
@@
 
-In addition to assessing the extent of bias in each domain, as defined by the three levels detailed above, I attempted to records the direction of the bias, so that it could feed into the triangulation.
+In addition to assessing the extent of bias in each domain, as defined by the three levels detailed above, I attempted to record the predicted direction and type of bias.
+This was achieved via an additional question at the end of each bias domain, which asked assessors to predict the expected direction of bias in that domain.
+Note that this question is currently only formally included in two existing tools (ROB2/ROBINS-I), but I employed an identical approach during assessment of non-randomised studies of exposure and Mendelian randomisation studies.
+Acceptable responses to this question included:
 
-This was achieved via an additional question at the end of each bias domain, which asked assessors to predict the expected direction of bias in that domain.
-Note that this question is only apply to existing tools (ROB2/ROBINS-I/ROBINS-E), but I employed an identical approach during assessment of Mendelian randomisation studies.
-This optional question response were:
-
-* "Favours experimental"/"Favours comparator" (additive bias)
-* "Towards null"/"Away from null" (proportional bias)
+* "Favours experimental"/"Favours comparator" (defines an additive bias)
+* "Towards null"/"Away from null" (defines a proportional bias)
 * "Unpredictable"
 
-As indicated in the options above, the response t this prompt is used both to define the direction and type (additive or proportional) of bias (see ).
+As indicated in the options above, the response to this question is also used to determine the predicted type of bias (additive or proportional - see Section \@ref(tri-terminology)) in addition to the direction.
+For additive biases, determining the absolute direction of bias was simply a case of whether the bias shift the effect estimate to the left or right on an imaginary forest plot.
+For example, if a bias was predicted to favour the intervention, then the estimate would be shifted to the right.
 
-Additive biases (identified by a "Favours experimental"/"Favours comparator" response) are XXXX. A key example of additive bias is immortal time bias, which will always favour the intervention.
+In contrast, for proportional biases, whether the estimate should be increased or decreased proportionally depends on the current position of the point estimate relative to the null.
+For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be adjusted for by moving the effect estimate propotionally to the right.
+In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null would be adjusted for by moving the effect estimate propotionally to the left.
 
-Proportional biases (identified by a "Towards null"/"Away from null" response) are those related to the magnitude of the effect.
-A key example of this type of bias is non-differential misclassification bias, which will bias the effect estimate towards the null.
+<!----------------------------------------------------------------------------->
+(ref:exampleDirection-cap) Illustration of calculating the absolute direction of biases (indicated by arrows), based on bias type.
+For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null.
+In contrast, the position of the effect estimate is accounted for when determining the absolute direction of proportional biases.
 
-When predicting the direction of effect
+(ref:exampleDirection-scap) Illustration of calculating the absolute direction of biases, based on bias type.
 
-From these response the direction of effect was calculated. For additive biases, this was simply a case of shifting the effect estimate to the left or right. For proportional biases, decide
+```{r exampleDirection, include=F}
+```
 
-For example, the direction of the bias when the direction of bias is thought to favour the intervention/exposure will be be same regardless of the position of the point estimate.
-The same is not true for the "Towards the null"/"Away from the null" options.
+```{r exampleDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:exampleDirection-cap)', out.width='100%', fig.scap='(ref:exampleDirection-scap)'}
+knitr::include_graphics(file.path("figures/tri/exampleDirection.png"))
+```
+<!----------------------------------------------------------------------------->
 
-For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be represented by a right pointing arrow (Figure \@ref(fig:)).
-In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null will be represented by a right-pointing arrow.
-The program to create these figures thus requires knowledge of both the predicted direction of bias and the effect estimate.
-
-However,
-
-S
-
-Highlight that this is slightly different for the confounding domain in non-randomised studies, which only allows for the "Favours experimental", "Favours comparator", and "Unpredictable" options.
-
-Of note, the guidance for the tools suggests that if assessors are not able to articulate why the bias in a given domain will "pull" the observed estimate in a specific direction, they should not try to guess.
-
-To assess the usefulness of this system, the number of domains for which bias was expected (i.e.
-judged to be a more than Low risk of bias) but for which no expected direction could be identified were expressed as a percentage.
-If this percentage is high, the helpfulness of the approach is
-
-<!-- TODO text -->
+Note that for some domains, only one type of bias is allowed.
+For example, in the confounding domains in the ROBINS-I/ROBINS-E tools, only the "Favours experimental"/"Favours comparator", and "Unpredictable" options are available, meaning that bias in this domain will always be considered additive.
+Additionally, the predicted direction and type of bias were not recorded for domains at "Low" risk of bias.
 
@@
 
-To aid with the triangulation exercise and to act as, I created a new method of presentation of the extent/direction bias asessment results to enable detailed comparison across different studies contributing to the synthesis.
-While these figures do not
+To aid with the triangulation exercise and to act as a sense-check, I created a new method to visualise the extent, direction and type of bias in each result to enable detailed comparison across different studies contributing to a synthesis.
+Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), these "bias direction" plots show the  level of bias across the domains in each study is reported using coloured blocks.
+However, in contrast to the previous plots, symbols are used to illustrate the predicted absolute direction of bias in that domain, as discussed in the previous section.
+Distinct symbol pairs are used to denote additive and proportional biases.
 
-Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), the level of bias across the domains in each study is reported using coloured blocks.
-However, in contrast to the previous plots, arrows are used in place to illustrate the predicted direction of bias in that domain, categorised as pulling towards the left or the right.
-
-This second aspect required some additional consideration, given the distinct and competing options available to assessors.
-
-Tha
-
-Helper functions in the forthcoming `triangulate` package - see Appendix \@ref() - help to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses.
-These bias direction plots themselves were created using the risk of bias isualisation tool described in Appendix \ref().
-
-<!-- TODO include illustrative example here -->
-
-Where the direction of bias was unclear/could not be determined from the report, this is indicated by a dash.
-
-<!-- TODO Does immortal time bias not also have a consistent effect? yes, but inception bias does not necessarily -->
+Convience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections.
+These bias direction plots themselves were created using the risk-of-bias visualisation tool described in Appendix \ref(?).
 
@@
 ####	Assign modifying values to risk/direction of bias
-
 <!-- TODO Note that they are on the log scale - Lines 45-50 of addbias -->
 
-For example, for a "High" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution
+Following definition of the extent, type and direction of bias in each domain, I assigned a prior distribution on the log scale to each combination.
+For example, a "high" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
 
@@
 
-The sign of $\mu_{i,j}^{\mathrm{High}}$ is defined by the relative direction of the bias in relation to the point estimate.
+The sign of $\mu_{i,j}^{\mathrm{High}}$ is defined by the absolute direction of the bias.
 If the bias is expected to pull the effect to the left, the position is given a negative sign, and if it is expected to pull the effect to the right, it is given a positive sign.
@@
 One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e.
-a "high" bias in one domain is equivalent to a "high" bias in any other.
+a "high" judgement in one domain is equivalent to a "high" judgement in any other.
 As such, for this analysis, I assumed that the distributions assigned to each level of bias are identical across all values of $j$, that is, are identical for all domains in the risk of bias assessment tool.
+To illustrate, for additive biases these means:
 
@@
 
+Reasonable values for the position and spread of the prior distributions were informed by a previous reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean and maximum values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(?) for more details on how these were calculated).
+For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two sets of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
+In the first scenario, the relationship between the position assigned to each additive judgement is linear.
+In the second scenario, the step from "moderate" to high" is twice that from "low" to "moderate".
+Across both additive and proportional biases, the variance of the "high" risk--of-bias judgement distribution was defined to be greater than that for the "moderate" risk-of-bias judgement.
+
 &nbsp;<!----------------------------------------------------------------------->
 
-(ref:priorsAdd-caption) Distributions for additive bias assigned to each bias judgement under two sensitivity scenarios, on the log scale.
+(ref:priorsAdd-caption) Prior distributions for extent and type of bias under two scenarios, on the log scale.
+Note that the distributions for proportional biases were kept consistent across the two scenarios.
 
@@
 
-For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I defined two sets of modifying distributions (Table 1).
-In the first scenario, the relationship between the position assigned to each judgement is linear.
-In the second scenario, .
-In both cases, the variance of the "High" risk of bias judgement was defined to be great than the "Moderate" risk of bias judgement.
-The two scenarios are illustrated in Figure \@ref(fig).
+ <!-- TODO Link this to open data! -->
 
-Reasonable values for the position and spread of the distributions were informed by calculating the mean and maximum adjustment values as defined by the original elicitation exercise (see Appendix \@ref(?) for more details on how these were calculated).
-[@turner2009] <!-- TODO Link this to open data!
--->
-
-Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain, but the appropriate variance for (i.e.
-no predicted direction, but increased uncretainty in line with judgement).
+Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained.
+In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate, but does increase uncertainty around it.
 
@@
 
+An identical approach was employed to assess and assign prior distributions to the risk of indirectness in each result.
+The target question for each result was compared against the causal question of interest with respect to three domains (population, intervention/exposure, outcome), <!-- TODO CITATION NEEDED --> again using the scale of "Low/"Moderate"/"High" to quantify the extent of indirectness.
+
 A similar approach was used to define prior distributions for external bias or indirectness.
@@
 (recap).
+All indirectness were defined _a priori_ as being proportional in nature, in line with previous work on this topic.[@turner2009]
 
-In the original method, this was assessed against 4 categories of external bias (population/intervention/control/outcome)
-
-In this
-
-A key example here is that
-
-All indirectness bias were defined as being proportional. As described i
-
-This is also in line with previous efforts to assess the adjustment needed due to indirectness
-
-As crude example focusing on the intervention , versus the causal question of the effect of LDL-c in mid-life on Alzheimer's disease, studies of lipids levels in this time period would require minial adjustment, whereas studies
-...
+As crude illustrative example, consider the causal question of the interest in this exercise, the effect of LDL-c in mid-life on Alzheimer's disease.
+Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be downweighted due to reduced relevance to the causal question.
 
@@
 
-Once the total additive and proportional biases for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis.
+As per the method reported in, total additive and proportional bias and indirectness were calculated for each result. Briefly,
+
+<!-- TODO Talk about how total add/prop biases calculated -->
+
+Once the total additive and proportional bias and indirectness for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis.
 
@@
 
-where $\mu_{i\delta}$ denotes total additive and $\mu_{i\beta}$ the total proportional adjustment, and the $^{\mathrm{B}}$ and $^{\mathrm{In}}$ superscripts denote wether the adjustment relates to internal bias or indirectness respectively.
-
-Using the same terms, the standard error of this estimate, $\hat{\theta}$, is then calculated as:
+The standard error of this estimate is then calculated as:
 
@@
 
-Once each individual result has been adjusted, they are combined n a standard random-effects meta-analysis <!-- TODO CITATION NEEDED -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Software {#tri-software}
-
-Personal communication with the authors of the original method resulted in the STATA code to implement the
-
-As detailed in the introduction to this section, the model for defining bias-indirectness-adjusted results was available as STATA code.
-The  has since been generalised as part of the `triangulate` R package to allow for users to apply the approach detailed here.
-
-The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, calculate bias/indirectness-adjusted estimates for each result, and synthesise these adjusted results in a standard random-effects meta-analysis.
-
-All meta-analyses conducted within the package are implemented using the `metafor` R package.
+Once each individual result has been adjusted, I performed a random effects meta-analysis using the unadjusted and adjusted (under the two scenarios defined above) results.
+<!-- TODO CITATION NEEDED -->
 
@@
 
+Total additive bias (on the log scale) was `r hold()`. Similarly, total additive indirectness was (),
+
 Calculate internal-bias adjusted
 
-Calculate both-adjusted
+`r hold()`
+
+The unadjusted effect for this study was `r hold()` and the adjusted effect estimate for this study was `r hold()`
 
@@
 
-#### Causal question #1
+#### Case study: effect of LDL-c at midlife on Alzheimer's disease
 
-Midlife LDL-c on Alzheimer's disease
+From the data sources identified in Section \@(), I identified X results relevant to my causal question of interest.
+<!-- TODO CITATION NEEDED will need to cite these!
+--> The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
 
@@
 
-(ref:ldlAdBiasDirection-cap) __Bias direction plot, summarising internal biases related to effect of LDL-c on Alzheimer's disease :__
+(ref:ldlAdBiasDirection-cap) Bias direction plot, summarising the internal biases related to effect of LDL-c on Alzheimer's disease, stratified by study design.
 
@@
 ```
+<!-- TODO Bias direction plot is not producing subgroup test for some reason -->
 &nbsp;<!----------------------------------------------------------------------->
 
-Including sensitivity analyses
+The results of the unadjusted and the bias-/indirectness-adjusted (under the Scenario 1 of additive biases) are shown in Figure \@ref(fig:fpLdlAd).
+I observed no substantial change to the overall effect (unadjusted `r unadj_effect`; adjusted `r adj_effect`), though adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
+However, as can been seen from the right panel in the figure, this reduction in heterogeneity between studies is largely achieved via a reduction in precision.
 
-and citations of studies - going to be a bit of pain
+To explore the different impacts of the two defined scenarios for additive bias, I plotted these:
 
-As expected
+<!-- TODO Finish -->
 
-<!----------------------------------------------------------------------------->
-(ref:fpLdlAd-cap) __shortcap:__
+&nbsp;<!----------------------------------------------------------------------->
 
-(ref:fpLdlAd-scap) shortcap
+<!-- TODO This should really be stratified by type -->
+<!-- TODO Standardise effect estimates to same direction -->
+<!-- TODO Need to add my own evidence -->
+
+(ref:fpLdlAd-cap) Random effects meta-analysis using unadjusted and bias-/indirectness-adjusted results.
+
+(ref:fpLdlAd-scap) Random effects meta-analysis using unadjusted and bias-/indirectness-adjusted results.
 
@@
 ```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Causal question #2
-
-<!----------------------------------------------------------------------------->
-(ref:ldlDemBiasDirection-cap) __Effect of LDL-c on All-cause dementia in late life:__
-
-(ref:ldlDemBiasDirection-scap) Effect of LDL-c on All-cause dementia in late life
-
-```{r ldlDemBiasDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:ldlDemBiasDirection-cap)', out.width='100%', fig.scap='(ref:ldlDemBiasDirection-scap)'}
-knitr::include_graphics(file.path("figures/misc/UoBcrest.pdf"))
-```
-<!----------------------------------------------------------------------------->
 
@@
 
-Summary of risk-of-bias/triangulation results
-
-Percentage of domains for which a direction of bias could be assigned?
-
-Main takeaway is that heterogeneity between study designs is substantially reduced
-
-Compare bias-adjusted and
-
-See what happens if using additive (l=1,m=2,s=3,c=4) vs multiplicative/log scale (l=1,m=2,s=4,c=8). Present adjusted results and meta-analysis of adjusted results.
-
-Applicability/indirectness as an issue 
-Compare with GRADE and cite George's example of 40% of effect predicted by MR seen when using statins for 5 years
+<!-- IDEA Do turner et al standardise effect direction? -->
 
@@
 
-Thsi chapter has narratiely synthesised the exsiting and new evidence from the previous chapters, highlighting the lim
+This chapter has narratively synthesised the existing and new evidence identified and produced by the previous chapters, highlighting the absence of any consistent association between any blood lipid and any dementia outcome in the context of the bias in each approach.
 
 In addition, it has sought to provide a generalised framework for quantitative triangulation, building on existing methods for systematic domain-based risk of bias assessment and bias-/indirectness-adjusted meta-analysis.
-
-Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to internal validity present in each specific result relevant to the causal question.
-While this makes the process both more labour intensive and complex, to assume that, for example, all retrospective studies are equally at risk is to overlook.
+While a lack of information on the prior distributions of bias and indirectness in non-randomised studies precluded, to illustrate the method, I considered the example causal question of the effect of mid-life LDL-c on Alzheimer's disease risk derived from a previous expert elicitation exercise.
 
@@
 
-###	Limitations and strengths
+###	Limitations
 
@@
 
-#### Problems with quantitative triangulation approach
+#### Defining reasonable prior distributions for bias and indirectness
 
-Missing natural variation obtained from elicitation approach. Trade-off between systematic approach presented here and personal variation obtained from several reviewers.
+The key limitation of this quantitative synthesis presented in this chapter is the ambiguity
 
-A potential combination between the two would be to use the variation in risk-of-bias assessments
-
-Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk-of-bias level loses some of the information contained in domain-level based assessments.
-
-No good information on what the potential distributions for different levels of bias (High vs Moderate vs Low) should be.
+It is the reason that only one causal question is addressed as a case study, as to base clinical recommendations on a method dependent on non-empirical values would be inappropriate.
 
@@
 
-A key example of a useful future study in this domain would be the mining of maximally adjusted vs.
-unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic.
-However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information
-
-For example, if it was . New software for performing risk of bias assessments, being developed by the Bristol Appraisal and Review of Research group has this as a secondary methodological aim.
-
-This approach has a number of advantages. One of the key ones is modifying distributions of each level of bias could be defined _a priori_ in contrast to the .
-
-In addition, the generalised framework will allow for
-
-Appreciation that both the risk of bias and indirectness of a result should be assessed is growing.
-Indeed, some existing risk of bias for the assessment of diagnostic test accurary[@whiting2011a] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
-<!-- TODO Cite PROBAS and QUADAS -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Subjectivity of risk of bias assessments
-
-By definition, . In this case of this proof-of-concept analysis, the direction of bias was assessed by a single assessor. If attempting to impact policy, the
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Defining appropriate values for bias/indirectness adjustment
+New software for performing risk of bias assessments, being developed by the Bristol Appraisal and Review of Research group has this as a secondary methodological aim.
 
@@
 
+<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
+
+Similar there are several examples of usmeta to define priors for other statistical terms in meta-analysis.
+For example, previous work has looked at defining prior distributions of heterogeneity across different topic areas using a large collection of meta-analyses from the Cochrane Collaboration.<!-- TODO Cite turner etc -->
+
+<!-- TODO Talk about the fact recent paper does not favour bias-adjustment -->
+
+Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk-of-bias level loses some of the information contained in domain-level based assessments.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Low and critical risk of bias
+
+As illustrated in Table \@ref(tab:robLevelsMapping-table), studies at critical risk of bias were not included in the analysis.
+
+one potential limitation of the  - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
+
+In any case, it represented a small number of studies.s
+
 A further issue is the "Low" risk of bias domain.
@@
 In this case, defining the predicted direction of bias would be challenging in the absence of obvious sources of bias (particularly given how challenging it can be when sources of bias are evident within a domain).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Strenghts
+
+This approach has a number of advantages. One of the key ones is modifying distributions of each level of bias could be defined _a priori_ in contrast to the .
+
+In addition, the generalised framework will allow for future researchers to apply (see Section \@ref())
+
+Appreciation that both the risk of bias and indirectness of a result should be assessed is growing.
+Indeed, some existing risk of bias for the assessment of diagnostic test accurary[@whiting2011a] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
+<!-- TODO Cite PROBAS and QUADAS --> <!-- TODO CITATION NEEDED cite paper that shows that ROB is not being intergrated into synthesis --> The approach proposed here will capitalise on this, providing users of domain based tools with a further avenue by whih to incorporate the results of their risk-of-bias assessments quantitatively.
+
+Additional if users are interested in only a summary of the evidence rather than assessing results in relation to a target qusetion, then internal biases can be adjusted for on their own.
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
+\newpage
+
+### Future research
+
+As the need and appetite for synthesis of different sources of evidence (trials, non-randomised studies, etc.), future iterations of the risk of bias tools should take this into account.
+Simple steps like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
+Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.
+
+While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e.
+not applying expected directions of effects to an entire category of studies ).
+
+This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result separately.
+This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.
+
+A key example of a useful future study in this domain would be the mining of maximally adjusted vs.
+unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic.
+However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information
+
 In the mean time, the extent of the impact of knowledge of the results could be analysed using existing data.
-For example, a re-analysis of the data presented in a recent paper where both expert eliciation and structured
-
-<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
-
-Similar there are several examples of usmeta to define priors for other statistical terms in meta-analysis. For example, previous work has looked at het
-
-Like other studies examining the prior distributions of heterogeneity across different topic areas <!-- TODO Cite turner etc -->
-
-Talk about different ways to define bias terms, using expert-elicitation vs .[@rhodes2020]
-
-Also, talk about the fact that much of the bias-adjusted analysis work to date has been done on trials.
-Describe reasons for this but highlight that for triangulation, there needs to be better coverage of
+For example, a re-analysis of the data presented in a recent paper where both expert elicitation and structured
 
@@
 
-#### Exclusion of studies at critical risk of bias
+### Triangulation as an extension of evidence synthesis
 
-As illustrated in Table \@ref(tab:robLevelsMapping-table), studies at critical risk of bias were not included in the analysis.
-
-one potential limitation of the  - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
-
-In any case, it represented a small number of studies.s
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Type of bias (proportional vs additive) not shown on bias direction plot
-
-In contrast
-
-The graphics shown in Section \@ref() do not show the type of bias (additive or proportional), only the direction.
-While this is acceptable, future work could assess, potentially by using different arrow types to denote the different types of bias.
-
-A key strength of this project is the development of a standardised way of capturing bias domains and converting the.
-
-Helper functions in the triangulate package convert risk-of-bias assessment
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Challenges of real-life data
+Triangulation, both qualitative and quantitative, should be considered an extension of evidence synthesis, and so.
+Triangulation exercises should be based on comprehensive systematic reviews to create.
+If needed, evidence gaps can be addressed through additional studies, as in the case of this analysis,
 
@@
 
-#### Standardisation across study designs
+### Outputs {#tri-software}
 
-Standardising across different measures of ex
-
-Want best information across lipids, and so standardised across different measures
-
-Fixing directions of effect - get everything pointing the same way
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Related approaches
-
-<!-- TODO Need more here on the other approaches discussed in the recent comparison paper -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-\newpage
-
-### Need for new method
-
-As the need and appetite for synthesis of different, future iterations of the risk of bias tools should take this into account.
-Simple steps like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
-Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.
-
-Can I suggest any empirical studies that need to be performed? Average strength of immortal time bias/etc?
-
-While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e.
-not applying expected directions of effects to an entire category of studies ).
-
-This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result separately.
-This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Filling in the gaps
-
-Triangulation, both qualitative and quantitative, should be considered an extension of evidence synthesis, and so.
-Triangulation exercises should be based on comprehensive systematic reviews to create.
-If needed, evidence gaps can be addressed through additional studies, as in the case of this analysis,
-
-### Outputs
-
-Software
-
-Annotated example dataset
-
-this ties in with the open data sharing of the by-assessor elictation data from, which i sued in this analysis to frame the modifying values assigned to
+There are two key outputs from this project.
+The first is the `trinagulate` R package.
+Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.
+This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, calculation of bias/indirectness-adjusted estimates for each result, and synthesis these adjusted results in a standard random-effects meta-analysis.
+All meta-analyses conducted within the package are implemented using the `metafor` R package.
+<!-- TODO CITATION NEEDED and cite in Sys rev chapter too!
+-->
 
 Generalised version of code, allowing for different distributions in each domain of bias (which will be handy once we get a better idea of what they should be).
+
+Annotated example dataset for the LDL-c/Alzheimer's disease causal question is the second key output.
+Available via the `triangulate` package, this data will give developers of new triangulation methods an example dataset on which to test developments, something which seriously hindered development of this project.
+This also ties with the idea of open data that has been a consistent theme throughout this thesis.
+
+An additional note is that without the open data sharing of the by-assessor elictation data from, which i sued in this analysis to frame the modifying values assigned to
 
@@
 
+Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to the internal validity and directness of each specific result relevant to the causal question.
+While this makes the process both more labour intensive and complex,
+
 It also introduce a new way to visualise the biases at work in a particular result, rather than making assumptions about the type and directions of bias at the study design level as suggested by previous work on this topic.
@@
 
-The implications of this work to clinical practice, public health and future research is considered in the following chapter.
+The implications of th synthesised work of this thesis presened in this chapter to clinical practice, public health and future research is considered in the following chapter.
 

### 2021-11-14 R/07-Code-Triangulation-Analysis.R

@@ -68,10 +68,11 @@ if (doc_type == "docx") {
     caption = "(ref:priorsAdd-caption)",
     caption.short = "(ref:priorsAdd-scaption)",
     booktabs = TRUE, 
-    align = "lcc"
+    align = "lccc"
   ) %>%
     row_spec(0, bold = TRUE) %>%
     column_spec(1, bold = TRUE) %>%
+    kableExtra::add_header_above(c(" " = 1, "Additive bias" = 2," " = 1),bold = T) %>%
     row_spec(2:nrow(priors_add_table) - 1, hline_after = TRUE) %>%
     kable_styling(latex_options = c("HOLD_position"))
 }
@@ -180,6 +181,9 @@ model_unadj <- metafor::rma.uni(yi = yi,
                                 data = dat_final, 
                                 slab = paste(dat_final$author,dat_final$year))
 
+unadj_effect <- estimate(exp(model_unadj$b),exp(model_unadj$ci.lb),exp(model_unadj$ci.ub),type = "")
+
+unadj_tau2 <- model_unadj$tau2
 unadj_I2 <- model_unadj$I2
 
 metafor::forest(model_unadj, annotate = T, showweights = TRUE)
@@ -188,6 +192,9 @@ model_adj <- metafor::rma.uni(yi = yi_adj,
                               vi = vi_adj,
                               data = dat_final,
                               slab = paste(dat_final$author,dat_final$year))
+adj_effect <- estimate(exp(model_adj$b),exp(model_adj$ci.lb),exp(model_adj$ci.ub),type = "")
+adj_tau2 <- model_adj$tau2
+adj_I2 <- model_adj$I2
 
 metafor::forest(model_adj,annotate = T,  showweights = TRUE)
 
@@ -233,8 +240,8 @@ dev.off()
 
 # Validate formula using Turner data
 turner <- rio::import("turner_bias/propbias.dta") %>%
-  # arrange(study, assessor) %>%
-  # left_join(rio::import("turner_bias/addbias.dta")) %>%
+  arrange(study, assessor) %>%
+  left_join(rio::import("turner_bias/addbias.dta")) %>%
   filter(assessor == 1) %>%
   select(-assessor) %>%
   rename("yi" = estlogor,
@@ -247,3 +254,32 @@ model <- metafor::rma.uni(yi = yi_adj,
[…]

### 2021-11-14 R/forest tri.R

@@ -231,6 +231,43 @@ for (i in 1:nrow(dat_rob_vec)) {
 }
 }
 
+# 
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+  
+  # if (nrow(dat)>9) {
+  #   
+  #   # Fit meta-regression model to test for subgroup differences
+  #   
+  #   if (!is.null(sei)) {
+  #     
+  #     res <- rma(yi, vi, mods = ~ type, data = dat, method = "DL")
+  #     
+  #   } else {
+  #     
+  #     res <- rma(yi, sei=sei, mods = ~ type, data = dat, method = "DL")
+  #     
+  #   }
+  #   
+  #   ### add text for the test of subgroup differences
+  #   text(x_min,-1.8, pos = 4, cex = 1.2, bquote(
+  #     paste(
+  #       "Test for Subgroup Differences: ",
+  #       Q[M],
+  #       " = ",
+  #       .(formatC(
+  #         res$QM, digits = 2, format = "f"
+  #       )),
+  #       ", df = ",
+  #       .(res$p - 1),
+  #       ", p = ",
+  #       .(formatC(
+  #         res$QMp, digits = 2, format = "f"
+  #       ))
+  #     )
+  #   ))
+  # }
+
+
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 
 if(!is.null(title)){

### 2021-11-18 01-Chp-Background.Rmd
End of day:

@@
 
+<!-- TODO Consider inverting the order so that triangulation comes last - as it does in the thesis as a whole! -->
+
 Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
@@
 Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
+
 <!----------------------------------------------------------------------------->
@@
 * To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
+* To propose a generalised framework for the quantitative triangulation across diverse evidence sources
 

### 2021-11-18 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-We considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
+I considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
 
@@
 
-We considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome.
+I considered five outcomes as part of this analysis: probable  Alzheimer’s disease, possible Alzheimer’s disease, vascular dementia, other dementias, and a composite all-cause dementia outcome.
 When two or more outcomes were coded in a participant’s clinical record, a decision tree was used to differentiate between them (Figure \@ref(fig:decisionTreeFig)).

### 2021-11-18 06-Chp-IPD-Analysis.Rmd
End of day:

--- 2021-10-13 06-Chp-IPD-Analysis.Rmd
@@
 
-As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+TBC
+
+<!-- As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
 However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
+-->
 
-The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglycerides) on any dementia outcome.
+<!-- The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglyceride) on any dementia outcome.
 In addition, patients characteristics such as age and sex did not have any impact on the relationship of lipid fractions and dementia outcomes.
+-->
 
-Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.
+<!-- Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.  -->
 
@@
 
-Individual patient data meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.
-They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results have been explicitly stratified by the characteristic of interest.
+Individual patient data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005]
 
-While the systematic review presented in Chapter \@ref(sys-rev-heading) did not provide strong evidence for an effect of age at lipid measurement or patient sex on the relationship between lipids and dementia, the number of included studies in the lipid fraction meta-analyses were very small, due to both the relatively small number of studies reporting on this exposure and the poor reporting of smmary statistics of patient characteristics.
+While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of patient characteristics in those that did.
+Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on the between-study heterogeneity in a summary data meta-analysis, as similar distributions of patient covariates across studies may mask a true effect.[@riley2020]
 
-As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by incorporating previously unanalysed cohorts contained in the Dementia Platform UK, a large consortia of dementia cohorts.
+As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
 
+<!-- TODO Read this[@riley2020] -->
 <!----------------------------------------------------------------------------->
@@
 
-Eligible data sources were defined as those that contained lipid measurements and lipids reported/available as a continuous measure, Data sources which were cross-sectional, either by design or due to the available data (e.g.
-a study conducted multiple waves, but onyl data from a single wave could be accessed) were excluded.
-Similarly, due to the limited time-frame, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
-The one exception to this was data from the CPRD, which I already had access to as part of the analysis reported in Chapter \ref(cprd-analysis-heading).
+#### Study design
 
-<!-- TODO Read this[@riley2020] -->
+Eligible data sources were defined as those that contained measurements of blood lipids (total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-lipoprotein cholesterol (HDL-c), and triglyceride (TG)), available as a continuous measure.
+Additionally, they were required to contain data on at least one dementia outcome (all-cause dementia, Alzheimer's disease, vascular dementia).
+Participants must be free of dementia at baseline.
+
+Data sources which were cross-sectional, either by design or due to the available data (e.g.
+a study conducted across multiple waves, but only data from a single wave could be accessed) were excluded.
+Similarly, due to the limited time afforded by this thesis, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
+No restrictions were put on the number of participants or the length of follow-up.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Exposures/outcome
+
+I considered four blood lipid fractions as part of this analysis, namely: total cholesterol, low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides.
+Cohorts were eligible for inclusion if they contained data on at least one of these in a continuous format (i.e.
+studies with binary "hypercholesteromemia" would be excluded).
+
+In line with the analyses presented in other chapters, eligible cohorts were those containing data on at least one outcome of interest, namely: all-cause dementia, Alzheimer's disease, or vascular dementia.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Potentially eligible data sources were identified via two mechanisms with a distinct focus.
-For each approach, the number of cohorts responding to the request, and where applciable, the reasons given for a lack of data sharing were recorded.
+Potentially eligible data sources as defined above were identified via two mechanisms, each with a distinct focus.
+For both approaches, the number of cohorts responding to the request for data access, and where applicable, the reasons given for a lack of data sharing were recorded.
 
-#### Systematic review
+&nbsp;<!----------------------------------------------------------------------->
 
-The first approach focused on previously analysed data sources.
-The systematic review detailed in Chapter \@ref(sys-rev-heading) identified several observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes.
-The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
+#### Cohorts identified by the systematic review
+
+The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapter \@ref(sys-rev-heading)  The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
 In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potentially collaborators) in Autumn 2020.
@@
 
-#### Dementia Platform UK
+&nbsp;<!----------------------------------------------------------------------->
 
-The second approach focused on incorporating previously unanalysed data, thus providing additional evidence on the relationship between statins and dementia risk.
+#### Cohorts contained in Dementia Platform UK
 
+The second approach focused on incorporating relevant, previously-unanalysed data into the analysis, thus providing additional evidence on the relationship between blood lipids and dementia risk.
 This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application processs for all cohorts with the intent of making it easier to access data from existing data sources.
@@
 
-### Risk of bias assessment
+### Primary analysis
 
-Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
+#### Data cleaning and harmonisation
 
-Due to the inherent conflict of interest in assessing my own analysis, the result were also assessed by two independent reviewers.
+Where data on one of these exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
+Lipids levels were retained as continuous variables rather than dichotomising into, for example, a hypercholesterolemia exposure given the additional power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
+To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
 
-<!-- Be clear on the different types of databases, e.g. those where users are followed up regularly vs those where participants are captured via EHR-->
+Across all cohorts, data cleaning was performed in a similar manner, standardising to commonly named variables so that a single model could be applied using functional programming.[@wickham2016a] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+Following data cleaning, summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process, in line with best practice.[@levis2021]
 
@@
 
-### Missing data
+#### Covariate definition
 
-<!-- TODO This was taken from Chapter 4, so may need to rephrase slightly -->
-<!-- IDEA See Sean's thesis for some additional detail on this -->
-
-In this analysis, missing data were handled using a multiple imputation approach.
-Variables with missing observations were identified, and 20 imputed datasets were created.[@sterne2009] Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the XXX command in R.
-
-<!-- TODO Need to talk about how missing variables were handled across studies -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Variable definition
-
-#### Exposure
-
-To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
-
-#### Outcomes
-
-Similar to the analyses presented in othe chapters, th endpoints in this analysis was incidience of dementia and related sub-types (AD, vascular dementia).
-
-#### Covariates
-
-Relevant covariates were adjusted for in all models. these included age, sex,education and comorbities. For information on how these were defined across cohorts, see Appendix \@ref(hold).
+With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, ApoE4 status, smoking/alcohol status and prevalent cardiovascular disease.
+This set covers key risk factors for dementia/Alzheimer's disease in addition to general cardiovascular risk factors.
+Ethnicity was considered as a potential addition covariate of interest, but several of the DPUK cohorts (whose data dictionaries could be inspected in advance) made it clear that ethnicity data was either not available or would not be shared.
+Details on how these variables were coded, given the available data, are presented in Section \@ref(ipd-covar-definition).
 
@@
 
-### Statistical analysis
+#### Missing data
 
-#### Descriptive statistics
+Missing data in this analysis was classified as either relating to missing values (a cohort collected data on a variable of interest, but some values are missing) or missing variables (a cohort did not collect data on a variable of interest).
 
-All IPD obtained was examined and recoded as necessary to ensure they comply with the coding guideline for the IPD database.
-As recommended , summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process.[@levis2021] Any discrepancies were investigated.
+Variables with missing values were identified, and 20 imputed datasets were created.[@sterne2009] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the `mice` package in R.
 
-#### Data cleaning and harmonisation
+Systematically missing variables were originally intended to be addressed using a previously described method.[@fibrinogenstudiescollaboration2009] Here, the correlation between the fully-adjusted and partially-adjusted estimate in cohorts with the full set of covariates is used to estimate the fully-adjusted effect in those cohorts missing covariates.
+However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
+As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] Firstly, all cohorts were analysed adjusted for the set of common covariates across cohorts (age,sex,smoking, alcohol, presence of morbidities).
+Secondly, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model.
+Results between the common-set-adjusted and maximally-adjusted models were compared.
 
-Across all cohorts, data cleaning was performed in a similar manner, using commonly named variables, so that a single model could be applied using functional programming.
-The one exception to this is the CPRD data, which was held in a different system to the rest.
-However, an identical model was applied within this cohort.
-The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-<!-- Need detailed paragraph here describing the different between two stage versus one-stage approach -->
-
-In this analysis, an two-stage individual patient data model was used out of necessity, with the one-stage model being precluded by the included datasets being in protected data silos.
-It also allows for each studys' data to be analysed according to a common analysis plan, which is particularly important in this topic, due to the differing definitions between studies of the serum concentrations above or below which lipids are deemed to be at abnormal levels.
-
+In this analysis, an two-stage individual patient data analysis was planned.
 Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
 Effect estimates for the associations between lipid fractions and incident dementia, adjusted for identical covariates, were obtained by applying a common model to each data source.
-More specifically, hazard ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
-A discrete proportional hazards model was employed to account for the interval censoring introduced by design of the longitudinal cohort studies.[@wang2017] An overall effect estimate was then produced by combining data-source-specific estimtes in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
-Following best practice, clustering within studies was accounted for.[@abo-zaid2013]
+More specifically, odds ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+Examination of the data available via the DPUK indicated that the common time-to-event approach used in studies of dementia outcome would be precluded by the absence of detailed time-to-event data.
+An overall effect estimate was then produced by combining data-source-specific estimates in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
 
-<!-- TODO talk about different methods - see here: https://onlinelibrary.wiley.com/doi/10.1002/sim.8516 -->
-<!-- TODO Figure showing the outline of interval censored studies. -->
+A two-stage approach was employed for a number of reasons.
+Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to analyse themselves following a specified analysis plan.
+Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
+Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Comparison with published findings
+
+Following estimation of the main effect, where an included data source had previously been analysed, the results of this analysis were compared against those published previously.
+Where discrepancies were identified, these were investigated.
 
@@
 
-In order to investigate the interaction of patient-level characteristics with lipid levels, interaction terms for lipid-covariate terms were included in the model above.
-These were extracted and synthesised using a random effects meta-analysis.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Combining published aggregate data and individual participant data
-
-Where a data source did not provided their individual participant data, but stratified by a patient characteristic of interest in the published data, the aggregate data and individual data were combined.
-
-<!-- TODO How does this work? -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Comparison with published findings
-
-Where an included data source had previously been analysed and results for the association between lipid levels and dementia outcomes reported, these were compared to the results of this analysis.
-If discrepancies were identified, these were investigated.
-
-<!-- TODO Need more on this method here -->
-
-### Secondary analyses
-
-#### Amount of information added
-
-The proportion of new information added to the evidence base via incorporation of the unanalysed datasets was quantified, by addding the additional results to the lipid-dementia meta-analyses presented in Section \@ref(hold), and extracting the combined weights assigned to the new data in a fixed-effect model.
-
-<!-- #### Contact information  -->
-
-#### Data availability statements
-
-As a sensitivity analysis, I examined the data sharing statements for each using a predefined categories used in a similar previous analysis.[@mcguinness2020DAScomparison]
-
-<!-- TODO This should have a plot showing how many over time had good vs bad DAS -->
-
-<!-- TODO In addition, need plot similar to study design over time in Chapter 3, showing cohort responses over time -->
+In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.
+To avoid ecological bias, where between-study do not reflect the within-study association, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate, for example, the impact of sex on the lipid~dementia relationship in a study which contains female participants.
 
@@
 
+```{r ipdSummStat, include=F}
+```
+
+```{r prepIPDFigures,include=F}
+```
+
 ### Data access
@@
 
-Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) provided data and were included in the analysis.
+Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) were included in the final analysis.
 Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
-In addition, the reasons for cohorts not being included in the analysis are presented, stratified by application approach.
+In addition, the reasons for cohorts not being included in the analysis are presented, where available, stratified by application approach.
 
-In summary, the requests for data from cohorts identified by the systematic review was characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they no longer worked with the same group and did not know if the data were available or how to obtain it, had access to the data, or that they were currently or intended to perform a similar analysis as the one proposed.
+In summary, the requests for data from cohorts identified by the systematic review were characterised by a very low response rate.
+For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they: no longer worked with the same group and did not know if the data were available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
 
-With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher resulting in eventual access to three cohorts (one of which was also identified by the systematic review).
-However, even using this streamlined approach, a response was obtained for only half of the approach cohorts.
+<!-- TODO Need numbers in the above section. -->
+
+With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher.
+However, even using this streamlined approach, a response was obtained for only half of the approached cohorts, resulting in eventual access to eight (one of which was also identified by the systematic review).
+However, on inspection of the obtained data, five of these were deemed ineligible, the reasons for which are documented in the following section.
+
+<!-- TODO Fix width of this image, and one box is not rendering right, and update numbers! -->
 
@@
 
-### Included data sources
+### Data sources
 
-The four data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
+<!-- TODO Be clear on the different types of databases, e.g. those where users are followed up regularly vs. those where participants are captured via EHR-->
+
+<!-- TODO Need to talk about how dementia was assessed in each! -->
+
+<!-- TODO Link to appendix about data sources not approached -->
+
+The three data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
 Of note, all included data sources were based in the United Kingdom.
-This is likely due to the majority of included datasets coming from the Dementia Platform UK route (Figure  \@ref(fig:cohortFlowchart)), which as implied by the name, has a geographical focus on cohorts performed in the United Kingdom.[@bauermeister2020]
+This is due to the majority of included datasets coming from the Dementia Platform UK route (Figure \@ref(fig:cohortFlowchart)), which as implied by the name, has a narrow geographical focus.[@bauermeister2020]
 
-&nbsp;
+As highlighted in Figure \@ref(fig:cohortFlowchart), eight cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
+The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+In summary, two cohorts contained were memory-complaint cohorts, containing patients unlikely to be free of dementia at baseline (BRACE, MEMENTO).
+Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave, and so represented cross-sectional data (Generation Scotland, NICOLA).
+Finally TRACK HD is a genetic cohort where cohort owners advised me that dementia will inevitably develop in mid-life driven by the Huntington's (HTT gene) mutation and that this effect would likely far outweigh the effect of lipids.
+Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable <!-- TODO CITATION NEEDED for each study here!
+-->
 
-<!----------------------------------------------------------------------------->
-(ref:cohortOverview-caption) Summary of cohorts for which data were available
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
 
-(ref:cohortOverview-scaption) Summary of included cohorts
+(ref:dataExcluded-scaption) Exclusion reasons for cohorts providing data
 
-```{r cohortOverview-table, message=FALSE, results="asis", echo = FALSE}
+```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
-&nbsp;
-
-<!-- TODO Update table with SD for age, and types of outcomes, and follow-up, and check why number of events in EPIC is less than expected (5 vs 8)-->
-
-<!-- TODO * Description (including observation period, numbers, numbers with outcome, etc) -->
+The included data sources are described in detail below.
 
@@
 
-#### CPRD
-
-The Clinical Practice Research Datalink (CPRD) is a large population-based, electronic health record (EHR) database.[@herrett2015] containing the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
-
-The CPRD is introduced more fully in Chapter \@ref(). Briefly, a similar approach to the cohort definition as used in Chapter
-
-Participants were included from the first date of lipid measurement, so no issues with immortal time bias as discussed in Chapter ...
-
-Additionally, other number of participants is larger in this analysis as there is no restriction on the level which lipids should be in order to be included in the analysis.
-
-the
-
-&nbsp;<!----------------------------------------------------------------------->
-
 #### Epic Norfolk
@@
 The added evidental value of the EPIC cohort is small, given the relatively small number of participants and the fact that the cohort has only 8 dementia events.
-
-```{r tests}
-```
 
@@
 This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
+However, this previous analysis focused on all-cause dementia and Alzheimer's disease as outcomes, so the assessment of vascular dementia represents a new source of evidence.
 
@@
 
-### Excluded data sources
+### Covariate definition & missing data {#ipd-covar-definition}
 
-#### Cohorts identified the systematic review but excluded from the IPD analysis
+Based on available data across cohorts, smoking was classified as never/ever/current, while alcohol consumption was classified as never/ever.
+Education was categorised into 4 levels (None,O-levels,A-levels,Degree).
+BMI was treated as a continuous variable while presence of co-morbidities was treated as dichotomous.
 
-<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+A key consideration in the definition of covariates was the classification of age.
+The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age band (e.g.
+40-44, 45-49, etc.).
+To ensure comparability across the cohorts, I created identical categories in the CaPS and EPIC data.
+This grouped age variable was then used in all subsequent analyses.
 
-The main reason for exclusion within this records was use of an electronic health record database.
-Examples included the Taiwan National Health Insurance database and studies run in the US making use of Medicare data.
+Missing values in collected variables was common across the cohorts.
+A matrix of covariate, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(?).
+The Whitehall II and EPIC cohorts had data on all covariates of interest, while two systematically missing covariates were identified in the CaPS cohort, namely education and BMI.
+No included cohort provided information on the ApoE4 status of participants, and so this variable could not be adjusted for in the analysis.
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
-#### Cohorts identified in the DPUK but excluded from the IPD analysis
+### Analytical results
 
-<!-- Should also include a list of reasons why specific additional cohorts were not included - some like the EHR might be too big to get -->
+#### Descriptive statistics
 
-Several additional cohorts are present in the DPUK collection but were not formally approached with a request for data access.
-This was primarily due to the information obtained via the online data dictionary system or via initial contact with the cohort owners indicating that the study was relatively new (and so was yet to collect more than 1 wave of data) or that the exposure variables of interest were not recorded.
-
-<!-- TODO LBC 1936 -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Cohorts providing data but ultimately excluded
-
-As highlighted in Figure \@ref(fig:cohortFlowchart), several cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
-The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
+Altogether `r n_total_ipd` patients across the three cohorts were included in this analysis.
+Cumulatively, there were 1329 cases of all-cause dementia, with `r n_ipd_dementia` and `r n_ipd_vasdem` cases further classified as Alzheimer's disease and vascular dementia, respectively.
+Summary statistics for each cohort are provided in Table \@ref(tab:cohortOverview-table).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
+(ref:covariateSummary-caption) Summary of characteristics for cohorts included in the IPD  analysis
 
-(ref:dataExcluded-scaption) Exclusion reasons for cohorts providing data
+(ref:covariateSummary-scaption) Summary of characteristics of IPD cohorts
 
-```{r dataExcluded-table, message=FALSE, results="asis", echo = FALSE}
+```{r covariateSummary-table, message=FALSE, results="asis", echo = FALSE}
 ```
@@
 
-BRACE is a memory-complaint-based cohort, suggesting that it is unlikely they were dementia-free at baseline).
-<!-- TODO CITATION NEEDED --> Similarly, the Memento study was excluded as it's criteria for entry required participants to be outpatients from a memory clinic.
-<!-- TODO CITATION NEEDED --> The Generation Scotland provided only cross-sectional data only for the variables of interest, as did the the NICOLA study.
-<!-- TODO CITATION NEEDED x2 --> Finally, the ELSA study was excluded based on the definition of the exposure variable.
-This study provided a "high cholesterol" a binary variable rather than the raw continuous lipid measurement data.
-<!-- TODO CITATION NEEDED -->
+#### Main effects
+
+The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
+There was very weak evidence for the evidence for an association of an lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r tri_vasdem`).
+
+<!----------------------------------------------------------------------------->
+(ref:mainEffectDem-cap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+
+(ref:mainEffectDem-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+
+```{r mainEffectDem, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mainEffectDem-cap)', out.width='100%', fig.scap='(ref:mainEffectDem-scap)'}
+knitr::include_graphics(file.path("figures/ipd/main_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:mainEffectVad-cap) IPD meta-analysis of vascular dementia, stratified by lipid fraction. Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.
+
+(ref:mainEffectVad-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+
+```{r mainEffectVad, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mainEffectVad-cap)', out.width='100%', fig.scap='(ref:mainEffectVad-scap)'}
+knitr::include_graphics(file.path("figures/ipd/main_vasdem.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Estimates from the common-set-adjusted model were comparable to the fully-adjusted model (further adjusted for education and BMI) in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
+
+<!----------------------------------------------------------------------------->
+(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 1) analyses.
+
+(ref:ipdModelComparison-scap) Comparison of partially and maximally adjusted results
+
+```{r ipdModelComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:ipdModelComparison-cap)', out.width='100%', fig.scap='(ref:ipdModelComparison-scap)'}
+knitr::include_graphics(file.path("figures/ipd/main_model_comparison.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 
-#### Cohorts approach but received no answer
+#### Interaction effects
 
-This was particularly common among the cohorts identified via the systematic review and included studies with  a dedicated access process or data access committee.
-A cohort of particular interest, having been used in multiple studies identified by the systematic review, is the Three City Study in France.
-Despite multiple attempts to contact the team, there was no response received.
-<!-- TODO CITATION NEEDED --> This study was approach at multiple points over the curse of this analysis, and no answer was received.
+Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
+Further, while the maximally-adjusted could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
 
-This was also a problem for cohorts approach via the DPUK - half of the cohorts applied to did not respond to the application within a year.
-
-### Analytical results
-
-There was no evidence for an effect of any lipid fraction on any dementia outcome (Figure \@ref(fig:tcDementiaMain)).
-Additionally, meta-analysis of the interaction coefficients for age-at-lipid-measurement and participant sex did not reveal an evidence for an varying effect across these variables.
-
-<!-- TODO Will need some method to define how/from where the different cohorts were obtained. -->
+For all-cause dementia, there was no evidence of an nteraction of lipid levels with either age group or sex (Figures \@ref(fig:interactionDementiaAge) & \@ref(fig:interactionDementiaSex)).
 
 <!----------------------------------------------------------------------------->
-&nbsp;
+(ref:interactionDementiaAge-cap)  Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/dementia association
 
-<!-- TODO Create similar crude rate table as for CPRD analysis chapter -->
+(ref:interactionDementiaAge-scap) shortcap
 
-<!----------------------------------------------------------------------------->
-(ref:tcDementiaMain-cap) __Random effects meta-analysis of estimates from included data sources:__
-
-(ref:tcDementiaMain-scap) IPD analysis of total cholesterol and dementia
-
-```{r tcDementiaMain, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:tcDementiaMain-cap)', out.width='100%', fig.scap='(ref:tcDementiaMain-scap)'}
-knitr::include_graphics(file.path("figures/ipd/TC.png"))
+```{r interactionDementiaAge, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:interactionDementiaAge-cap)', out.width='100%', fig.scap='(ref:interactionDementiaAge-scap)'}
+knitr::include_graphics(file.path("figures/ipd/interaction_age_dementia.png"))
 ```
@@
 
-<!-- ### Effect by age -->
-
-<!-- ### Heterogeneity -->
+Similarly, there was no . Note that the CaPS cohort was excluded from this analysis, as it contains only a single sex and therefore provides no information on exposure-sex interaction.
 
 <!----------------------------------------------------------------------------->
-&nbsp;
+(ref:interactionDementiaSex-cap) Meta-analysis of interaction terms representing the effect of being male on the lipid/dementia association
+
+(ref:interactionDementiaSex-scap) shortcap
+
+```{r interactionDementiaSex, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:interactionDementiaSex-cap)', out.width='100%', fig.scap='(ref:interactionDementiaSex-scap)'}
+knitr::include_graphics(file.path("figures/ipd/interaction_sex_dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+For the consideration of vascular dementia, I was only able to explore the effect of age, as only the CaPS and Whitehall cohorts contained details on vascular dementia as an outcome.
+As discussed above, the CaPS data contained a single sex, excluding it from a exposure-sex analysis.
+Similar to all-cause dementia, there was very weak evidence for an effect of age on the assocation between lipid fractions and vascular dementia.
+
+<!----------------------------------------------------------------------------->
+(ref:interactionVascularAge-cap) Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/vascular dementia association
+
+(ref:interactionVascularAge-scap) shortcap
+
+```{r interactionVascularAge, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:interactionVascularAge-cap)', out.width='100%', fig.scap='(ref:interactionVascularAge-scap)'}
+knitr::include_graphics(file.path("figures/ipd/interaction_age_vasdem.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Comparison with previous analyses
+
+For the single cohort where a previously published analysis was available (Whitehall II),[@tynkkynen2018] results from the maximally-adjusted model for both all-cause dementia and Alzheimer's disease were comparable, with the exception of the trigluceride fraction (Figure \@ref(fig:whitehallComparison)).
+Tynkkynen _et al._ found a protective effect of triglycerides on all-cause dementia (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
+
+<!-- TODO These are generated - check they are correct! -->
+
+<!----------------------------------------------------------------------------->
+(ref:whitehallComparison-cap) Comparison of results across the two analysis of the Whitehall II cohort
+
+(ref:whitehallComparison-scap) Comparison of results across the two analysis of the Whitehall II cohort
+
+```{r whitehallComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparison-cap)', out.width='100%', fig.scap='(ref:whitehallComparison-scap)'}
+knitr::include_graphics(file.path("figures/ipd/whitehall_comparison.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-This analysis requested data from `r n_applied$total` data sources, but only obtained data from `r fmt_applied(n_accessed$total)`, all of which were based in the United Kingdom.
-No evidence for an effect of lipids on the risk of dementia or related outcomes was identified.
-Similalarly, there was no evidence for an effect of age-at-measurement or sex on the lipid-dementia relationship.
+This analysis requested data from `r n_applied$total` data sources, but only obtained data from three, all of which were based in the United Kingdom.
+No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with vascular dementia risk.
+Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with two participants age or sex.
 
-Additionally analyses revealed that authors of cohorts indentified by the systematic review rarely stated that the data underpinning their analyses would be freely available, while a review of corresponding authors of these publications demonstrated that for many, the institutional email address provided was out of date.
+I found a qualitative different between the association of triglycerides and all-cause dementia identified in this analysis and that previously reported by Tynkkynen _et al._[@tynkkynen2018]
+Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (n=287 vs n=114).
 
-<!-- Useful citation for discussion[@levis2021] -->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-_(although, in hindsight, the form of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning[@danko2019])_
+The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
 
-<!-- TODO Plot showing when datasets requested were published and comparing this with the -->
-A key limitation of this analysis is the very low response rate to requests for data access.
-This finding is not unexpected however, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
+A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
 --> and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
+However, it is assumed that a ~10% response rate is at the lower end of the scale.
 
 There are likely several likely reasons for this low response rate.
-In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.
-<!-- TODO CITATION NEEDED -->
-
-More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
 The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other work.
 
-_Many authors claim that their data can be made “available on request”, despite previous work establishing that these statements are demonstrably untrue in the majority of cases - that when data is requested, it is not actually made available.
-[@krawczyk2012; @miyakawa2020; @naudet2018] Additionally, previous work found that the availability of data “available on request” declines with article age, indicating that this approach is not a valid long term option for data sharing.[@vines2014] Several of the included studies are greater than 10 years old, and so obtaining data from these cohorts is less likely compared with more recently published studies._ <!-- TODO taken from DAS paper, so will need to change language -->
-
-One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
-Qualitatively, investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
-<!-- All of these are arguments towards better reporting of data availability, ownership - also talk about the ORCID and advatnages of permanent identifier-->
+Finally, the method of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning.[@danko2019] One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
+Anecdotally, post-hoc investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
 
@@
 In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
-Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
-
-<!-- TODO CITATION NEEDED: paper on trust as a big issue + paper on systematic review of barriers to data sharing -->
-
-Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014]
-
-<!-- However, fewer than half of systematic reviews with IPDMA, published between 1987 and 2015, retrieved data from at least 80% of relevant studies and from at least 80% of relevant participants [16].
-The number of IPDMAs increased over this period [17], but data retrieval rates remained unchanged [16, 18].
-Inability to include eligible studies compromises the systematic review’s purpose, decreases study power, and leads to healthcare decisions based on an incomplete, potentially biased data sample (studies with available data may differ from those whose data are not available) [10, 19, 20].
-However, analysis combining individual and study level data may mitigate these effects [3, 21].
-from [@ventresca2020a] -->
-
-For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
-In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" (i.e.
+where a copy of the data is already held on DPUK servers) versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
 
@@
 
-#### Risk of bias assessment
+#### Uncontrolled confounding
 
-There is some concerns about performing risk of bias assessments on your own analysis, and so two secondary reviewers
+Given the extremely low .
 
-<!-- #### Opportunistic inclusion of CPRD data -->
+[Note: this made sense to me, and I hope you agree with the approach]
+
+While IPD analysis, it is well recognised
+
+However, given the inherent limitations to this IPD analysis afford by the , I considered the maximally adjusted values more useful in broader terms of the thesis, as they could be considered individual sources of evidence in the triangulation exercise presented in Chapter 7.
+
+In addition, discrepancies between the age/sex adjusted models and the maximally adjusted
+
+Given the limited power of this analysis, I did not pursue further options to impute systematically missing variables, instead consid
 
@@
 
-While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS study and the EPIC Norfolk study - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
+While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
 
-&nbsp;<!----------------------------------------------------------------------->
-
-<!-- ### Study within a review -->
-
-<!-- In future, it could have been worth running a "study within a review", such as that used to examine the best method [@godolphin2019a] to identify and access study data. -->
-
-<!-- Options could include an investigation of the impact of applicant chacateristics  -->
-
-<!-- Previous SWARs have been registered as protocols, but have not yet reported! -->
+__[Note: I feel quite negatively about this analysis, so suggestions for other strengths to flesh out this section would be welcome!]__
 
@@
 Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
+While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situationin whcih all 37 cohorts responded positively would have been logistically challenging within the scope of my PhD.
 
-<!-- While the cohort response rate was substantially lower that expected, given the time and resource intensity of data cleaning and harmonisation for just 4 cohorts,  -->
+For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
+In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Future work
+
+While it is tempting to suggest that an IPD analysis of lipid levels be reattempted, without empirical guided approaches to increase the response rate, this may just result with a similar set of studies as described here.
+In line with this and the limitations considered earlier in this chapter, future methodological work could formally consider the effect of requester characteristics (sex, location, career stage) on response rates in IPD analyses.
+
+Additionally, the production of detailed guidance on handling cases where covariates are systematically missing.
+Much of the literature around IPD analysis is focused on the synthesis of trials, where additional covariate information is needed for the assessment of treatment-covariate interactions, rather than the adjustment of the estimate for confounding.
+Given the wide availability of non-randomised cohorts, improved guidance would support future work using this method.
+
+Finally, a movement towards both unique persistent identification of researchers, through schemes such as the ORCID programme,[@nature2009] would help with contact issues.
+Researchers move institutions frequently, and so the contact details provided on publications are frequently out of date.
 
@@
 
-This analysis provided very weak evidence for an effect of lipid fractions on dementia outcomes.
-However, it does provide an analysis two previous unanalysed data sources that are subsequently used in Chapter \@ref(tri-heading).
+This chapter described an attempted IPD analysis, provided very weak evidence for an interaction between patient characteristics and lipids levels on the risk of allc-cause and dementia outcomes.
+It  discussed potential reasons for the low response rate observed in this analysis and made recommendations for future work on this topic.
+
+In the subsequent chapter, the results of this analysis will be incorporated, along with those produced in previous chapter, into a proposed triangulation framework.
 

### 2021-11-18 07-Chp-Triangulation.Rmd
End of day:

@@
 
+The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias).
+In summary, RTCS were assessed using the RoB 2 tool;[@sterne2019] NRSI  using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(#rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
+tool.[@mamluk2020]
+
+<!-- TODO Talk about how the CPRD and IPD analysis results were assessed here! -->
+
+<!-- Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
+-->
+
+<!-- Due to the inherent conflict of interest in assessing my own analysis, the result were also assessed by two independent reviewers. -->
+
 ### Qualitative triangulation
@@
 
-The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias).
-In summary, RTCS were assessed using the RoB 2 tool;[@sterne2019] NRSI  using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(#rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
-tool.[@mamluk2020]
-
 For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set of judgements: "Low", "Moderate","High".
@@
 <!----------------------------------------------------------------------------->
+ ```{r exampleDirectionSetup, include = F}
+ ```
+
 (ref:exampleDirection-cap) Illustration of calculating the absolute direction of biases (indicated by arrows), based on bias type.
@@
 
-```{r exampleDirection, include=F}
-```
+```{r exampleDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:exampleDirection-cap)', out.width='100%', fig.scap='(ref:exampleDirection-scap)'}
 
-```{r exampleDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:exampleDirection-cap)', out.width='100%', fig.scap='(ref:exampleDirection-scap)'}
 knitr::include_graphics(file.path("figures/tri/exampleDirection.png"))
+
 ```
@@
 Following definition of the extent, type and direction of bias in each domain, I assigned a prior distribution on the log scale to each combination.
-For example, a "high" additive bias in $j$th domain of the $i$th study is deifined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
+For example, a "high" additive bias in $j$th domain of the $i$th study is defined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
 
@@
 The sign of $\mu_{i,j}^{\mathrm{High}}$ is defined by the absolute direction of the bias.
-If the bias is expected to pull the effect to the left, the position is given a negative sign, and if it is expected to pull the effect to the right, it is given a positive sign.
+If the bias is expected to pull the effect to the left, $\mu_{i,j}^{\mathrm{High}}$ is given a negative sign, and if it is expected to pull the effect to the right, it is given a positive sign.
 
-One key feature of the domain-based risk-of-bias domains is that the domains are considered interchangeable - i.e.
+One key feature of the domain-based risk-of-bias tools is that the domains are considered interchangeable - i.e.
 a "high" judgement in one domain is equivalent to a "high" judgement in any other.
-As such, for this analysis, I assumed that the distributions assigned to each level of bias are identical across all values of $j$, that is, are identical for all domains in the risk of bias assessment tool.
-To illustrate, for additive biases these means:
+As such, for this analysis, I assumed that the distributions assigned to each extent of bias were identical across all values of $j$, that is, were identical for all domains in the risk-of-bias assessment tool.
+To illustrate for additive biases:
 
@@
 
-<!-- TODO In the absence of any empirical data regarding the priors, I used the data from the expert elicication approach to calculate both the mean and max.
+<!-- TODO In the absence of any empirical data regarding the priors, I used the data from the expert elicitation approach to calculate both the mean and max.
 These estimates, in addition to conversations with topic experts -->
@@
 
-Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained.
-In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate, but does increase uncertainty around it.
+Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained (e.g.
+for an unpredictable "high" assessment, the distribution would be $N(0,0.12)$).
+In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate, but does increase the uncertainty around it.
 
@@
 The target question for each result was compared against the causal question of interest with respect to three domains (population, intervention/exposure, outcome), <!-- TODO CITATION NEEDED --> again using the scale of "Low/"Moderate"/"High" to quantify the extent of indirectness.
-
-A similar approach was used to define prior distributions for external bias or indirectness.
-I used a similar enforced scale of "Low/"Moderate"/"High" indirectness versus each of the 4 aspects of the target causal question.
-(recap).
 All indirectness were defined _a priori_ as being proportional in nature, in line with previous work on this topic.[@turner2009]
@@
 
-As per the method reported in, total additive and proportional bias and indirectness were calculated for each result. Briefly,
+Using the the method reported in Turner _et al._,[@turner2009] total additive and proportional bias and indirectness were calculated for each result. Briefly,
 
@@
 ```{r biasDirectionSingle, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:biasDirectionSingle-cap)', out.width='100%', fig.scap='(ref:biasDirectionSingle-scap)'}
-knitr::include_graphics(file.path("figures/misc/UoBcrest.pdf"))
+knitr::include_graphics(file.path("figures/tri/midlife_AD_single.png"))
 ```
@@
 <!-- TODO Bias direction plot is not producing subgroup test for some reason -->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 The results of the unadjusted and the bias-/indirectness-adjusted (under the Scenario 1 of additive biases) are shown in Figure \@ref(fig:fpLdlAd).
-I observed no substantial change to the overall effect (unadjusted `r unadj_effect`; adjusted `r adj_effect`), though adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
+I observed no substantial change to the overall effect (unadjusted `r unadj_effect`; adjusted `r adj_effect_scenario1`), though adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
 However, as can been seen from the right panel in the figure, this reduction in heterogeneity between studies is largely achieved via a reduction in precision.
@@
 
+While this analysis may be biased from the non-empirical bias adjustment factors, at the very least, it acknowledges the the uncertainty of evidence via the widening of confidence intervals. 
+No less problematic than the analysis fo biased estimates in a meta-analysis which does not account for bias.
+
 ### Summary of findings
@@
 #### Defining reasonable prior distributions for bias and indirectness
+
+Allowing for the strong assumption that
 
@@
 
+#### Subjectivity of bias-/indirectness-assessment
+
+<!-- TODO Add text here on the subjectivity of qualitative risk of bias assessment and cite ROBINS-I to say that risk of bias is hard. Note that this will apply  -->
+
+A key issue in this analysis is t
+
+As observed from Figure \@ref(@) in the bias-adjusted analysis, the Ostergaard _et al._ 2017
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-Additional if users are interested in only a summary of the evidence rather than assessing results in relation to a target qusetion, then internal biases can be adjusted for on their own.
+Additional if users are interested in only a summary of the evidence rather than assessing results in relation to a target question, then internal biases can be adjusted for on their own by setting the indirectness distributions to $N(0,0)$.
 
-In previous attempts at bias/indirectness-adjusted meta-analysis, the extent to each was assessed via a elicitation process using a number of experts.
-This approach is potentially subject to misclassification of the impact of bias on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount.
-For example, if experts are influenced by the absolute effect estimate, then a result demonstrating a stronger protective effect may receive greater modification than a study at the same "risk" of confounding but with a more modest effect.
-This is particular true where experts have preconceived ideas about the true effectiveness of the intervention.
+The extent of a bias in a domain is unlikely to map accurately across the same domains in different studies, which
+
+It for this reason that in previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process using a panel of methodologists and topic experts.[@thompson2011; @turner2009; @wilks2011] However, this approach is potentially subject to misclassification of the impact of bias on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
+As an illustrative example, if experts are influenced by the knowledge of the effect estimate in a study, then a result demonstrating a stronger protective effect may receive greater modification than a study at the same "risk" of confounding but with a more modest effect.
+This is likely to be part where experts have preconceived ideas about the true effectiveness of the intervention.
 
 In this case, separating the assessment of bias from the assignment of modifying values to each level of bias will limit the potential for.
-Alternatively, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team, similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.
+Alternatively, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016]
 
@@
 
+Future research could and should also take into account bias at the analysis level in terms of missing evidence.
+For example, the set of previously published NRSE included in the case study were found to be at high risk of bias from missing evidence (see Figure \@ref(fig:lipidFractionsAD) in Chapter \@ref(sys-rev-results-heading)).
+Ideally, a quantitative triangulation framework would further account for this proportional evidence-level bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
+
+<!-- QUESTION - Can you meta-analyse meta-analysis results?
+As in, have a two-stage approach where you pool by evidence source, investigate bias at analysis level within evidence source, adjust these within-evidence-source results for ROB_ME bias, then pool them for final estimate?
+-->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain
+I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain evidence sources a
 
@@
 
-The implications of th synthesised work of this thesis presened in this chapter to clinical practice, public health and future research is considered in the following chapter.
+The implications of the synthesised work of this thesis presented in this chapter to clinical practice, public health and future research is considered in the following chapter.
 

### 2021-11-18 R/06-Code-IPD-Analysis.R

@@ -39,12 +39,12 @@ graph <- grViz(diagram = "digraph cfa {
       tab11 [label = 'N identified: @@1-3',height = 1]
       tab21 [label = 'N identified: @@1-1',height = 1]
       
-      tab02 [label = 'N data obtained: 0 \n\n Exclusion reasons:\n-No response (n= 14)\n-No access to data (n= 2)\n-Planned analysis (n= 3)',height = 2]
-      tab12 [label = 'N data obtained: 1, height = 2]
-      tab22 [label = 'N data obtained: \n\n Exclusion reasons:\n-Dementia cohort (n= )\n-No exposure variables (n= )\n-Planned analysis (n= )',height = 2]
+      tab02 [label = 'N data obtained: 0 \n\n Exclusion reasons:\n- No response (n= 15)\n- No access to data (n= 3)\n- Planned analysis (n= 2)',height = 2]
+      tab12 [label = 'N data obtained: 1', height = 2]
+      tab22 [label = 'N data obtained: 8\n\n Exclusion reasons:\n- No response (n= 8)',height = 2]
       
-      tab3 [label = 'N assessed for inclusion: 8',height = 1]
-      tab4 [label = 'N excluded following investigation: 5 \n\n Exclusion reasons:\n-Single wave (n= 2) \n-Cognitively impaired cohort (n= 2) \n-No lipid measurements at baseline (n=1)',height = 1]
+      tab3 [label = 'N data inspected: 9',height = 1]
+      tab4 [label = 'N excluded following investigation: 6 \n\n Exclusion reasons:\n- Cross-sectional data (n= 2) \n- Cognitively impaired cohort (n= 2) \n- Dichotomised exposure (n=1)\n- Genetic risk cohort (n=1)',height = 2]
       tab5 [label = 'Final number of \ncohorts included: @@2-4',height = 1]
 
       subgraph {
@@ -81,57 +81,20 @@ graph <- grViz(diagram = "digraph cfa {
 
 ")
 
-
 htmltools::html_print(DiagrammeR::add_mathjax(graph), viewer = NULL) %>%
[…]

### 2021-11-18 R/07-Code-Triangulation-Analysis.R

@@ -68,11 +68,12 @@ if (doc_type == "docx") {
     caption = "(ref:priorsAdd-caption)",
     caption.short = "(ref:priorsAdd-scaption)",
     booktabs = TRUE, 
-    align = "lccc"
+    align = "lccc",
+    col.names = c('', 'Scenario 1', 'Scenario 2', '')
   ) %>%
     row_spec(0, bold = TRUE) %>%
     column_spec(1, bold = TRUE) %>%
-    kableExtra::add_header_above(c(" " = 1, "Additive bias" = 2," " = 1),bold = T) %>%
+    kableExtra::add_header_above(c("Bias Level" = 1, "Additive bias" = 2,"Proportional bias" = 1),bold = T, line = F) %>%
     row_spec(2:nrow(priors_add_table) - 1, hline_after = TRUE) %>%
     kable_styling(latex_options = c("HOLD_position"))
 }
@@ -103,9 +104,36 @@ select(study,
   summarise(mean = mean(value),
             max = max(value))
 
-prop <- rio::import("turner_bias/propbias_full.dta") %>%
+prop_i <- rio::import("turner_bias/propbias_full.dta") %>%
   janitor::clean_names() %>%
   filter(external == 0) %>%
+  select(study, assessor, result, logbiasmean, logbiasvar) %>%
+  rename("domain" = result, 
+         "est" = logbiasmean, 
+         "var" = logbiasvar) %>%
+  tidyr::pivot_longer(!c(study, assessor, domain),
+                      names_to = "estimate", 
+                      values_to = "value") %>%
+  # On the log scale, so n adjusted = 0
+  mutate(value = ifelse(is.na(value),0,value)) %>%
+  # Get mean of assessors for each estimate in each domain in each study
+  # Take absolute, as direction is encoded in these values, whereas for us it
+  # will be defined separately, so just after the total amount it was adjusted
+  # by in any direction
+  group_by(study, estimate, domain) %>%
+  summarise(value = abs(mean(value))) %>%
+  ungroup() %>%
+  # Get mean across domains and studies, to give av impact of any single domain
+  # in any study + maximum across domains and studies to give max imapct of
[…]

### 2021-11-19 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 
-# Individual participant data meta-analysis {#ipd-heading}
+# Individual participant data meta-analysis of blood lipid levels and dementia outcomes {#ipd-heading}
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-Individual patient data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005]
+Individual patient data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
+IPD analysis also offer a mechanism by which previously unanalysed datasets can be incorporated into an analysis, thus expanding the evidence base for a particular research question.
 
-While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+Previous work has suggested a difference in the effect of lipids on dementia risk based on patient age and sex.[@ancelin2013; @mielke2010a] While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
 However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of patient characteristics in those that did.
@@
 
-As such, the aims of this analysis were two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
+As such, the aims of this analysis are two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
 
@@
 
+<!-- TODO Should this be reported in relation to the PRISMA-IPD statement -->
+
 ### Eligibility criteria
@@
 
-Eligible data sources were defined as those that contained measurements of blood lipids (total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-lipoprotein cholesterol (HDL-c), and triglyceride (TG)), available as a continuous measure.
-Additionally, they were required to contain data on at least one dementia outcome (all-cause dementia, Alzheimer's disease, vascular dementia).
-Participants must be free of dementia at baseline.
-
 Data sources which were cross-sectional, either by design or due to the available data (e.g.
@@
 Similarly, due to the limited time afforded by this thesis, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
-No restrictions were put on the number of participants or the length of follow-up.
+No restrictions were put on the number of participants or the length of follow-up, though participants must be free of dementia (or assumed to be free, based on age at entry)  at baseline.
 
@@
 
-#### Exposures/outcome
+#### Exposures/outcome definition
 
-I considered four blood lipid fractions as part of this analysis, namely: total cholesterol, low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides.
+I considered four blood lipid fractions as part of this analysis, namely: total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides (TG).
 Cohorts were eligible for inclusion if they contained data on at least one of these in a continuous format (i.e.
@@
 
-Cohorts included in the DPUK were assessed against the eligibility criteria, and in Autumn 2020, an application for access to a subset of 16 cohorts was made via the common-access procedure.
+Cohorts included in the DPUK were assessed against the eligibility criteria, and in Autumn 2020, an application for access to a subset of 17 cohorts was made via the common-access procedure.
 
@@
 Where data on one of these exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
-Lipids levels were retained as continuous variables rather than dichotomising into, for example, a hypercholesterolemia exposure given the additional power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
+Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
 To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
@@
 However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
-As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] Firstly, all cohorts were analysed adjusted for the set of common covariates across cohorts (age,sex,smoking, alcohol, presence of morbidities).
-Secondly, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model.
-Results between the common-set-adjusted and maximally-adjusted models were compared.
+As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were analysed adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, presence of morbidities).
+As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education and BMI).
+Results between the common-set-adjusted (Model 1) and maximally-adjusted (Model 2) models were then compared.
 
@@
 In this analysis, an two-stage individual patient data analysis was planned.
-Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes in each study were first calculated for each data source.
-Effect estimates for the associations between lipid fractions and incident dementia, adjusted for identical covariates, were obtained by applying a common model to each data source.
+Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes were first calculated for each data source.
 More specifically, odds ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
-Examination of the data available via the DPUK indicated that the common time-to-event approach used in studies of dementia outcome would be precluded by the absence of detailed time-to-event data.
+Examination of the data available via the DPUK indicated that the common time-to-event approach used in studies of dementia outcomes would be precluded by the absence of detailed time-to-event data.
 An overall effect estimate was then produced by combining data-source-specific estimates in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
 
-A two-stage approach was employed for a number of reasons.
-Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to analyse themselves following a specified analysis plan.
-Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
+A two-stage IPD approach was employed for a number of reasons.
+Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to analyse themselves following a specified analysis plan.[@riley2010] Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
 Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
@@
 
-#### Investigating effect of patient-level covariates
+#### Investigating the effect of patient-level covariates
 
 In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.
-To avoid ecological bias, where between-study do not reflect the within-study association, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate, for example, the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+All interaction analysis were performed using the common-set-adjusted model (Model 1).
 
@@
 In summary, the requests for data from cohorts identified by the systematic review were characterised by a very low response rate.
-For the minority who did respond, common reasons given by corresponding authors for not sharing the data included that they: no longer worked with the same group and did not know if the data were available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
+For the minority who did respond, common reasons given by authors for not sharing the data included that they: no longer worked with the same group and did not know if the data were available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
 
@@
 With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher.
-However, even using this streamlined approach, a response was obtained for only half of the approached cohorts, resulting in eventual access to eight (one of which was also identified by the systematic review).
-However, on inspection of the obtained data, five of these were deemed ineligible, the reasons for which are documented in the following section.
+However, even using this streamlined approach, a response was obtained for approximately half (N=9, 53%) of the approached cohorts, one of which (Whitehall II) was also identified by the systematic review.
 
@@
 
-As highlighted in Figure \@ref(fig:cohortFlowchart), there was little overlap between cohorts identified by the systematic review and those contained in the DPUK (`r fmt_applied(n_applied$DPUK_sysrev)`), indicating that the DPUK is a useful source of unanalysed data with respect to this question.
+As highlighted in Figure \@ref(fig:cohortFlowchart), there was little overlap between cohorts identified by the systematic review and those contained in the DPUK (`r n_applied$DPUK_sysrev`), indicating that the DPUK is a useful source of unanalysed data with respect to this question.
 
-&nbsp;<!----------------------------------------------------------------------->
-
-### Data sources
-
-<!-- TODO Be clear on the different types of databases, e.g. those where users are followed up regularly vs. those where participants are captured via EHR-->
-
-<!-- TODO Need to talk about how dementia was assessed in each! -->
-
-<!-- TODO Link to appendix about data sources not approached -->
-
-The three data sources used in this analysis are summarised in Table \@ref(tab:cohortOverview-table) and are described in detail in the following sections.
-Of note, all included data sources were based in the United Kingdom.
-This is due to the majority of included datasets coming from the Dementia Platform UK route (Figure \@ref(fig:cohortFlowchart)), which as implied by the name, has a narrow geographical focus.[@bauermeister2020]
-
-As highlighted in Figure \@ref(fig:cohortFlowchart), eight cohorts from the DPUK responding positively but on inspection of data provided these cohorts were excluded for a range of reason.
+As highlighted in Figure \@ref(fig:cohortFlowchart), nice cohorts (8 DPUK only, 1 Systematic review + DPUK) responding positively to requests for data access.
+However, on inspection of data provided, six of these cohorts were excluded for a range of reasons.
 The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
 In summary, two cohorts contained were memory-complaint cohorts, containing patients unlikely to be free of dementia at baseline (BRACE, MEMENTO).
-Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave, and so represented cross-sectional data (Generation Scotland, NICOLA).
+Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave and so represented cross-sectional data (Generation Scotland, NICOLA).
 Finally TRACK HD is a genetic cohort where cohort owners advised me that dementia will inevitably develop in mid-life driven by the Huntington's (HTT gene) mutation and that this effect would likely far outweigh the effect of lipids.
@@
 
-The included data sources are described in detail below.
+### Included data sources
+
+<!-- TODO Be clear on the different types of databases, e.g. those where users are followed up regularly vs. those where participants are captured via EHR-->
+
+<!-- TODO Need to talk about how dementia was assessed in each! -->
+
+<!-- TODO Link to appendix about data sources not approached -->
+
+The three data sources used in this analysis are described in detail in the following sections.
+Of note, all included data sources were based in the United Kingdom.
+This is due to the majority of included datasets being identified via the Dementia Platform UK route (Figure \@ref(fig:cohortFlowchart)), which as implied by the name, has a narrow geographical focus.[@bauermeister2020]
 
@@
 
-The Caerphilly <!-- TODO Check spelling --> Prospective Study is a longitudinal study of men in the
-
-Cholesterol measures (total, LDL-c, HDL-c and triglyceride) were measured at baseline in 1979-1983. 
-As the study population has aged, additional outcomes. Of particular relevance to this analysis, from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
+The Caerphilly Prospective Study (CaPS) is a longitudinal study of men in South Wales, UK.[@zotero-15398;@elwood2013] Blood lipids (TC, LDL-c, HDL-c and TG) were measured at baseline in 1979-1983, and from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
+The cohort contains data on dementia outcomes sub-classified as vascular and non-vascular dementia.
+Data were available for all covariates of interest except for education, BMI and ApoE4 status.
 
@@
 
-The European Prospective Investigation of Cancer - Norfolk is a  [@riboli1997; @riboli2002]
-
-The added evidental value of the EPIC cohort is small, given the relatively small number of participants and the fact that the cohort has only 8 dementia events.
+The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] The added evidential value of the EPIC cohort is small, given the the fact that the data obtained contains only 8 dementia events.
+The cohort contains no information on dementia subtype, while all covariates of interest bar ApoE4 were available.
 
@@
 
-_The Whitehall II study is a prospective cohort study of 10 308 participants (70% men), aged 35–55 years and recruited between 1985 and 1989 from 20 London-based Civil service departments (https://www.ucl.ac.uk/whitehallII).
-Clinical examinations have been performed in 1991-1994, 1997-1999, 2002-2004, 2007-2009, 2012-2013, 2015-2016 with the data from circulating metabolomic traits and cognitive testing for the present study obtained from the 1997-1999 clinic phase._ - taken from EN ID: 2140
+The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of patient events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
+This data source contained details on all covariates of interest except for ApoE4 status.
 
-This data source was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
-However, this previous analysis focused on all-cause dementia and Alzheimer's disease as outcomes, so the assessment of vascular dementia represents a new source of evidence.
+Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
 
@@
 Education was categorised into 4 levels (None,O-levels,A-levels,Degree).
-BMI was treated as a continuous variable while presence of co-morbidities was treated as dichotomous.
+BMI was treated as a continuous variable while presence of vascular co-morbidities was treated as dichotomous.
 
-A key consideration in the definition of covariates was the classification of age.
+A key consideration in the definition of covariates across cohorts was the classification of age.
 The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age band (e.g.
@@
 Missing values in collected variables was common across the cohorts.
-A matrix of covariate, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(?).
-The Whitehall II and EPIC cohorts had data on all covariates of interest, while two systematically missing covariates were identified in the CaPS cohort, namely education and BMI.
+A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(hold).
+The Whitehall II and EPIC cohorts containted data on all but one covariates of interest, while two systematically missing covariates were identified in the CaPS cohort, namely education and BMI.
 No included cohort provided information on the ApoE4 status of participants, and so this variable could not be adjusted for in the analysis.
@@
 
-Altogether `r n_total_ipd` patients across the three cohorts were included in this analysis.
-Cumulatively, there were 1329 cases of all-cause dementia, with `r n_ipd_dementia` and `r n_ipd_vasdem` cases further classified as Alzheimer's disease and vascular dementia, respectively.
-Summary statistics for each cohort are provided in Table \@ref(tab:cohortOverview-table).
+Across the three cohorts, `r n_total_ipd` patients were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512).
+All cohorts contained data on the four exposure variables of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes.
+The only other dementia outcome examined across cohorts was vascular dementia, which was reported in the CaPS and Whitehall II studies.
+The definitions of dementia outcomes used across cohorts can be seen in Appendix \@ref(hold).
+Cumulatively, there were `r n_ipd_dementia` cases of all-cause dementia, with `r n_ipd_vasdem` further classified as vascular dementia.
+Summary statistics for each cohort are provided in Table \@ref(tab:cohortSummary-table).
 
@@
 The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
-There was very weak evidence for the evidence for an association of an lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r tri_vasdem`).
+There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r tri_vasdem`).
 
 <!----------------------------------------------------------------------------->
-(ref:mainEffectDem-cap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+(ref:mainEffectDem-cap) IPD meta-analysis (model 1) of all-cause dementia outcomes, stratified by lipid fraction
 
@@
 <!----------------------------------------------------------------------------->
-(ref:mainEffectVad-cap) IPD meta-analysis of vascular dementia, stratified by lipid fraction. Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.
+(ref:mainEffectVad-cap) IPD meta-analysis (model 1) of vascular dementia outcomes, stratified by lipid fraction.
+Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.
 
@@
 
-Estimates from the common-set-adjusted model were comparable to the fully-adjusted model (further adjusted for education and BMI) in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
+Estimates from the common-set-adjusted model (Model 1: adjusted for age, sex, smoking, alcohol, presence of vascular comorbidites) were comparable to the fully-adjusted model (Model 2: Model 1 further adjusted for education and BMI) for the effect of lipids on all-cause dementia in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
 
 <!----------------------------------------------------------------------------->
-(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 1) analyses.
+(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses.
 
@@
 
-Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
+<!-- Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
 Further, while the maximally-adjusted could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
+-->
 
-For all-cause dementia, there was no evidence of an nteraction of lipid levels with either age group or sex (Figures \@ref(fig:interactionDementiaAge) & \@ref(fig:interactionDementiaSex)).
+For all-cause dementia, there was no evidence of an interaction of lipid levels with either age group or sex (Figures \@ref(fig:interactionDementiaAge) & \@ref(fig:interactionDementiaSex)).
+Note that for the sex interaction analysis, the CaPS cohort was excluded as it contains only a single sex and therefore provides no information on exposure-sex interaction.
 
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaAge-cap)  Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/dementia association
+(ref:interactionDementiaAge-cap)  Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/all-cause dementia association
 
@@
 
-Similarly, there was no . Note that the CaPS cohort was excluded from this analysis, as it contains only a single sex and therefore provides no information on exposure-sex interaction.
-
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaSex-cap) Meta-analysis of interaction terms representing the effect of being male on the lipid/dementia association
+(ref:interactionDementiaSex-cap) Meta-analysis of interaction terms representing the effect of male gender on the lipid/all-cause dementia association
 
@@
 For the consideration of vascular dementia, I was only able to explore the effect of age, as only the CaPS and Whitehall cohorts contained details on vascular dementia as an outcome.
-As discussed above, the CaPS data contained a single sex, excluding it from a exposure-sex analysis.
-Similar to all-cause dementia, there was very weak evidence for an effect of age on the assocation between lipid fractions and vascular dementia.
+As discussed above, the CaPS data contained a single sex excluding it from a exposure-sex analysis, leaving Whitehall II as the sole eligible study.
 
@@
 
-For the single cohort where a previously published analysis was available (Whitehall II),[@tynkkynen2018] results from the maximally-adjusted model for both all-cause dementia and Alzheimer's disease were comparable, with the exception of the trigluceride fraction (Figure \@ref(fig:whitehallComparison)).
-Tynkkynen _et al._ found a protective effect of triglycerides on all-cause dementia (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
+For the single cohort where a previously published analysis was available (Whitehall II), results from the maximally-adjusted model for both all-cause dementia and Alzheimer's disease were comparable, with the exception of the trigluceride fraction (Figure \@ref(fig:whitehallComparison)).
+Tynkkynen _et al._[@tynkkynen2018] found a protective effect of triglycerides on all-cause dementia (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
 
 <!-- TODO These are generated - check they are correct! -->
+
+<!-- TODO Confirm the results of Tyn for HDL are different between the below figure and the results presented in the systematic review -->
 
@@
 This analysis requested data from `r n_applied$total` data sources, but only obtained data from three, all of which were based in the United Kingdom.
-No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with vascular dementia risk.
-Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with two participants age or sex.
+No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia  Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants age, grouped into 5 year bands, or sex.
 
-I found a qualitative different between the association of triglycerides and all-cause dementia identified in this analysis and that previously reported by Tynkkynen _et al._[@tynkkynen2018]
-Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (n=287 vs n=114).
+Similar to the analysis of CPRD data presented in the previous chapter, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except where needed to illustrate a methodological point.
+For a detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
 
@@
 
-The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
+The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in pplication of the methods in addition to providing additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
 
-A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, <!-- TODO CITE and are these RCTs or all studies?
---> and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.
-However, it is assumed that a ~10% response rate is at the lower end of the scale.
+A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.[@nevitt2017a] However, it is assumed that a ~10% response rate is at the lower end of the scale.
 
-There are likely several likely reasons for this low response rate.
-In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy, concerns around scoping or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known professor might.
-The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other work.
+There are likely several likely reasons for this low response rate to requests for data access.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy and "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
+The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other COVID-related work.
 
@@
 
-These challenges are in theory what the DPUK was built to address.
+The barriers to data access described above are in theory what the DPUK was built to address.
 However, even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
@@
 In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
-Finally, the DPUK should more clearly distinguish between those cohorts that are "DPUK native" (i.e.
+Finally, the DPUK process would be aided by a clearer distinction between those cohorts that are "DPUK native" (i.e.
 where a copy of the data is already held on DPUK servers) versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
@@
 
-Given the extremely low .
+A key limitation of this analysis is the potential for uncontrolled confounding.
+Across all cohorts, adjustment for ApoE4 was not possible as I did not have access to genetic data on participants.
+As discussed above in relation to the Tynkkynen _et al._ analysis, ApoE4 is a strong risk factor for both increased LDL-c levels and Alzheimer's disease.[@bennet2007;@safieh2019] Failing to adjust for this factor means confounding in the LDL-c fraction results is likely.
 
-[Note: this made sense to me, and I hope you agree with the approach]
+More generally, systematically missing variables meant that a trade-off between inclusion of cohort data and appropriate control for confounding was required, resulting in the potential for uncontrolled confounding due to education and BMI.
+However, sensitivity analysis comparing the commom-set-adjusted (Model 1) and fully-adjusted (Model 2) models in cohorts with a full complement of covariates indicated that further adjustment for BMI and education had minimal impact on the effect estimates.
 
-While IPD analysis, it is well recognised
+#### Discrepancy with previous analysis
 
-However, given the inherent limitations to this IPD analysis afford by the , I considered the maximally adjusted values more useful in broader terms of the thesis, as they could be considered individual sources of evidence in the triangulation exercise presented in Chapter 7.
-
-In addition, discrepancies between the age/sex adjusted models and the maximally adjusted
-
-Given the limited power of this analysis, I did not pursue further options to impute systematically missing variables, instead consid
+I found a qualitative difference between the association of triglycerides and all-cause dementia identified in this analysis and that previously reported by Tynkkynen _et al._[@tynkkynen2018]
+Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (n=287 in this analysis vs.
+n=114 in Tynkkynen _et al._).
+The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for ApoE4 status.
+However, given that ApoE4 is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
 
@@
 
+__[Note: I feel quite negatively about this analysis, so suggestions for other strengths to flesh out this section would be welcome!]__
+
 While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
 
-__[Note: I feel quite negatively about this analysis, so suggestions for other strengths to flesh out this section would be welcome!]__
+Additionally, it provides new evidence on a previously unexplored outcome, vascular dementia, in the Whitehall II dataset, adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-method-heading) & \@ref(sys-rev-results-heading).
 
@@
 Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
-While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situationin whcih all 37 cohorts responded positively would have been logistically challenging within the scope of my PhD.
-
-For the purposes of this thesis, conducting the IPD analysis was useful as it afforded me the opportunity to gain experience in applying the methodology.
-In addition, it allowed me to analysed two addition previously unanalysed cohort studies which were then utilised in the triangulation study detailed in Chapter \@ref(tri-heading).
+While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of my PhD.
 
@@
 
-While it is tempting to suggest that an IPD analysis of lipid levels be reattempted, without empirical guided approaches to increase the response rate, this may just result with a similar set of studies as described here.
-In line with this and the limitations considered earlier in this chapter, future methodological work could formally consider the effect of requester characteristics (sex, location, career stage) on response rates in IPD analyses.
+While it is tempting to suggest that an IPD analysis of lipid levels be reattempted, without empirically guided approaches to increase the response rate, this may just result in a similarly small set of studies as described here.
+In line with the limitations considered earlier in this chapter, future methodological work could formally consider the effect of requester characteristics (sex, location, career stage) on response rates in IPD analyses.
 
-Additionally, the production of detailed guidance on handling cases where covariates are systematically missing.
-Much of the literature around IPD analysis is focused on the synthesis of trials, where additional covariate information is needed for the assessment of treatment-covariate interactions, rather than the adjustment of the estimate for confounding.
-Given the wide availability of non-randomised cohorts, improved guidance would support future work using this method.
+Additionally, the production of detailed guidance for handling cases where covariates are systematically missing.
+Much of the literature around IPD analysis is focused on the synthesis of trials, where additional covariate information is needed primarily for the assessment of treatment-covariate interactions rather than the adjustment of the effect estimate for confounding.
+Given the wide availability of non-randomised cohorts, improved guidance on this challenge would support future work.
 
-Finally, a movement towards both unique persistent identification of researchers, through schemes such as the ORCID programme,[@nature2009] would help with contact issues.
-Researchers move institutions frequently, and so the contact details provided on publications are frequently out of date.
+Finally, a movement towards increased use of unique persistent identification of researchers, through schemes such as the ORCID programme,[@nature2009] would help with contact issues.
+Researchers move institutions regularly as their contracts come to an end, and so the institutional contact details provided on publications are frequently out of date.
 
@@
 
-## Conclusion
+## Summary
 
-This chapter described an attempted IPD analysis, provided very weak evidence for an interaction between patient characteristics and lipids levels on the risk of allc-cause and dementia outcomes.
-It  discussed potential reasons for the low response rate observed in this analysis and made recommendations for future work on this topic.
+- In this chapter, I performed an IPD meta-analysis to investigate the effect of blood lipid levels on risk of incident dementia.
+There was a very low response rate to requests for data access, resulting in the inclusion of only three cohorts.
 
-In the subsequent chapter, the results of this analysis will be incorporated, along with those produced in previous chapter, into a proposed triangulation framework.
+- I found very weak evidence for an association of any lipid with either all-cause or vascular dementia, except for an increased risk of vascular dementia associated with raised triglycerides.
+Similarly, there was very weak evidence that the association of blood lipids and dementia outcomes varied by patient age or sex.
+
+- I discussed potential reasons for the low response rate, and explored other limitations of this analysis.
+I highlighted the contribution of this work to the wider topic via the analysis of previously unexplored cohorts (CaPS & EPIC) and outcomes (vascular dementia).
+Finally, I recommended that future research formally investigate the impact of request characteristics on requests for data.
+
+- The new evidence produced by this analysis will be incorporated, along with evidence identified or produced in the previous chapters, into the triangulation analysis presented in the following chapter.
 

### 2021-11-19 07-Chp-Triangulation.Rmd
End of day:

@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Qualitative triangulation
@@
 
+<!-- TODO The additive biases in this example figure should refer to favouring the comparator, meaning that the bias is pulling towards the intervention side (i.e.
+is making the comparator look better).
+-->
+
 <!----------------------------------------------------------------------------->
@@
 
-Convience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections.
+Convenience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections.
 These bias direction plots themselves were created using the risk-of-bias visualisation tool described in Appendix \ref(?).
@@
 
-<!-- TODO Deal with the fact that the Panel wasn't super useful -->
+<!-- TODO Sensitivity analysis - set means to zero and only adjust for variance. Essentially adding uncertainty based on the amount of bias but not moving the effect estimate -->
 
@@
 
+In this study, there were 3 domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result.
+
+In Domain 1, the study did not adjust for ApoE4, which is predicted to mask any true assocation between statins and . As such, the bias is predicted to _favour the comparator_ and so the absolu
+
+In Domain 5, there was a moderate risk of differential miclassification on the basis of the exposure, and so the predicted direction of bias in this domain is to _favours the intervention_.
+As such, the absolute direction of bias is to the left.
+
+For consistency with the other NRSI, in the absence of a protocol, bias in the selection of the reported result is assumed to be _away from the null_.
+Given the position of the effect estimate below the null (`r hold()`), the absolute direction of bias in this domain is to the left.
+
 <!----------------------------------------------------------------------------->
@@
 --> The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
+
+<!-- Question - Hypercholesterolemia should not be included here, as it is focused on total cholesterol rather than specifically LDL-c, right? -->
 
@@
 
+<!-- TODO How effect are fibrates at lowering triglycerides? is it a direct effect, or are there alternative -->
+
 <!-- TODO Finish -->
@@
 &nbsp;<!----------------------------------------------------------------------->
+
+#### Case study: effect of triglycerides at midlife on vascular dementia
 
@@
 
+In future, domain specific.
+In fact, it may also be more reasonable for domains such as confounding to adjust on a per-confounder basis.
+In the approach, prior distributions are assigned to each of the confounding domains prespecified as part of the ROBINS-I tool.
+Then, rather than assigning a domain level distrbution based on an arbraty judgement of how many important confounders are missing, the result is adjusted for each confounder not accounted for in the original analysis.
+As an example, ApoE4 is a much stronger confounder of the LDL-c than a single lifestyle indicator.
+
+<!-- TODO Talk about sensitivity analysis that only added variance rather than moving the point estimate, and highlight that this is a way to account for bias without having to make strong predictions about the direction of bias in a given domain.
+-->
+
+Estimates of modifying means might be conservative in relation to some potentially strong confounders.
+A previous simulation study estimated that ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021a]
+
 #### Subjectivity of bias-/indirectness-assessment
@@
 
-A key issue in this analysis is t
+A key issue in this analysis is the subjectivity of both the
 
-As observed from Figure \@ref(@) in the bias-adjusted analysis, the Ostergaard _et al._ 2017
+Key problem here is if the rigourness of the tools is not equivalent.
+This is less of an issue for the ROB suite of tools (RoB 2.0, ROBINS-I, ROBINS-E).
+This can be illustrated by the Ostergaard _et al._ study having low risk of bias.
+
+This is particularly problematic given the default of the ROBINS-I and ROBINS-E tool to require a "Moderate" judgement in the confounding domain.
+It means that, if the MR tool is insufficiently assessing bias in MR studies, the best performed cohort study (low risk of bias across everything other that confounding) will  always downweighted versus potentialyl a poor MR study.
+
+Similarly,
 

### 2021-11-19 08-Discussion.Rmd
End of day:

@@
 
-This chapter
+This chapter details the
 
-## Chapter overview
+## Introduction
 
-In this chapter I will summarise the principal findings from my thesis,
+The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.
 
-assess the unique contributions of this thesis to the field of research,
+In this chapter I will summarise the principal findings from my thesis, assess the unique contributions of this thesis to the field of research, discuss the implications for both clinical and public health policy, describe the overall strengths and limitations of this thesis as a whole, suggest avenues for impactful future research based on my findings and experiences.
 
-discuss the implications for both clinical and public health policy,
+In __Chapter \@ref(sys-rev-tools-heading)__ presents a new tool for the systematic searching of health-related preprints, and detail
 
-describe the overall strengths and limitations of this thesis as a whole,
+In __Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)__ describe the methods and results of a comprehensive systematic review of the relationship between blood lipids (and treatments that modify them) and dementia outcomes.
 
-suggest avenues for impactful future research based on my findings and experiences.
+In __Chapter \@ref(cprd-heading)__ presents an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale
 
-<!-- In this final chapter I will: -->
-<!--  Summarise the main findings from each chapter in relation to my two thesis hypotheses. -->
-<!-- Chapter 6: Discussion -->
-<!-- 162 -->
-<!--  Discuss the similarities and differences between my findings and the published literature. -->
-<!--  Critically evaluate the novel contributions and implications of my research. -->
-<!--  Describe the limitations of my studies and consider what I would do differently given what I have learnt. -->
-<!--  Recommend avenues for future research. -->
+In __Chapter \@ref(ipd-heading)__ presents an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK.
+
+In __Chapter \@ref(tri-heading)__ presents a narrative summary of the evidence identified and produced by the preceding chapters, and proposes a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.
 
@@
 
-## Summary of principal findings
+## New evidence produced
 
-Given the detailed discussion
+Since the systematic review was performed, there have been some notable further analysis related to the central thesis question here.
+Two of these are discussed here notable studies are discussed here.
+
+Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease [@iwagami2021].
+Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
+
+<!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect.
+Main results are between 1.03 and 1.17.
+CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by ApoE4 which is just a single confounder out of many -->
+
+In relation to the suggestion in this analysis that raised triglycerides were associated with an increasede risk of vascular dementia, a 2021 study in a  125,727 Danish participants found the moderate hypertriglyceridemia was associated with increased risk of non-Alzheimer's dementia (`r estimate(1.79, 1.16,2.87,"HR")`).[@nordestgaard2021]
 
@@
 
-## New evidence
-
-Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at midlife, driven by the finding for Alzheimer's disease [@iwagami2021].
-Not inconsistent with the findings presented in this thesis
-
 ## Lessons learned
 
-There are
+As part
+
+In hindsight, the decision to take a broad approach to inclusion of dementia outcomes potentially resulted in larger workload than anticipated, particularly when considered evidence from across different study designs.
+In a do-over, I would have considered a single dementia outcome.
+
+Additionally, in hindsight, I may have considered a mor. However, under the conditions of my grant, the scope for chang
+
+As a reflective process throughout the PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)).
 
@@
 ## Overall strengths and limitations
+
+The strengths a limitations of each component of this thesis are discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.
 
@@
 However, the thesis as a whole is subject to some strong limitations.
+
+__Strengths__
+- New evidence sources for an under-studied condition
+- Development of new methods and tool
+
+__Weaknesses__
+A general limitation of this thesis is the absence of known results/data.
+This occured in both the systematic review, via the selection of reporting results and potential for publication bias.
+It was also observeed.
+
+These facts both potentially bias the summary associations observed here, in addition to weakening the precision of the estimates produced.
+
+- Confounding by indication
+
+- A lot of UK based data
 
@@
 
-Containerisation was used to ensure that the code is reproducible, in line iwht best practices
+Unfortunately, given the.
+However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
 
@@
 
-Several avenues for future research, buiding on the work presented here,
-
-###
+Several avenues for future research, building on the work presented here, are possible.
 
@@
 
-Preprints also represent a key oppportunity to assess the impact of peer review on qualitivative changes within
+Preprints also represent a key opportunity to assess the impact of peer review on qualitative changes within
 
@@
 
-As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven y
+As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven (for NRSI) at the leasby a publication
 
@@
 While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.
+
+This is particularly relevant given that there was some evidence for an association of hypertriglyceraecia with vascular dementia.
+Future research should explicitly examine this relationship as part o f wider exploration of vascular disease.
 
@@
 
-### Reviewing of Mendelian randomisation studies
+### Viewing of Mendelian randomisation studies
 
-As a field, and as noted in Chapter \@ref(sys-rev-heading-results), the evidence synthesis theory and methods have not been sufficient developed for Mendelian randomisation studies.
-Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
-genetic instrumental variable analysis.)
+As noted in Chapter \@ref(sys-rev-heading-results), evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.
 
-Work is ongoing in this field, and new methodological work such as the release of teh MR-STROBE guidelines will aid in the future assessing by helping to improve the reporting of Mendelian randomisation studies.
+A key issue arises from the lack of an established risk of bias tool, which adds uncertainty to the accuracy of risk-of-bias assessments which can influence future work based on them, as discussed in Chapter \@ref(7).
+In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics.
+This was illustrated in detail in Chapter \@ref(4), where XXX studies using the same , and meta-analysing these as independent effect estimates would provide an overly precise result.
+Finally, future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
+genetic instrumental variable analysis).
 
-Problems with reporting of MR studies will hopefully
+Synthesis of Mendelian randomisation studies is not helped by the varied (and often poor) reporting, though the recent release of the STROBE-MR reporting guidelines should go someway to addressing this.
 
@@
 
-### Imporved analytical designs
+### Triangulation
+
+The field of quantitative triangulation is one ripe for future work. In the first instance, guidance
+
+Finally, methods for the standardisation of meth
 

### 2021-11-19 Disc2.Rmd
End of day:

## Summary of principal findings

No impact of lipid factions on dementia outcomes, except for triglycerides on vascular dementia outcomes

Non-randomised studies of interventions demonstrated a slight protective effect of statins. MR studies and RCT did not replicate the findings. However, the risk of bias in many of these studies was high, and when included in a bias adjusted framework.

Statins are by far the most studied LRA in relation to dementia outcomes, while there was an absence of information on the

Including preprints adds valuable additional evidence to a synthesis.

Reporting bias is particularly prevalent in NRSE - many studies explicitly state that they choose not to report

Across the studies, seems to be some evidence of triglycerides of VaD

### 2021-11-19 front-and-back-matter/99-appendices.Rmd
End of day
End of day:

@@
 <!----------------------------------------------------------------------------->
-### Section 2
-
-<!----------------------------------------------------------------------------->
 ## Chapter \@ref(discussion-heading)
@@
 <!----------------------------------------------------------------------------->
-### Catalogue of failures
+### Catalogue of failures {#appendix-catalogue-failures}
 
-Short section detailing the things I tried to do but which did not work.
+Short section detailing the things I tried to do but which did not work:
+
+failing to realise that the initial codelist used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
 
@@
 \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}

### 2021-11-19 published/03-Code-Systematic-Review.R

@@ -1,1555 +1,0 @@
-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# ---- searchOverview-table
-
-searchOverview_table <-
-  read.csv(here::here("data", "sys-rev", "searchOverview.csv"))
-
-if (doc_type == "docx") {
-  knitr::kable(searchOverview_table, caption = "(ref:searchOverview-caption)")
-} else{
-  knitr::kable(
-    searchOverview_table,
-    format = "latex",
-    caption = "(ref:searchOverview-caption)",
-    caption.short = "(ref:searchOverview-scaption)",
-    booktabs = TRUE,
-    align = "cl"
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    row_spec(2:nrow(searchOverview_table) - 1, hline_after = TRUE) %>%
-    kableExtra::column_spec(1, bold = FALSE) %>%
-    kable_styling(latex_options = c("HOLD_position"),
-                  font_size = 10)  %>%
-    kableExtra::footnote(
-      threeparttable = TRUE,
-      general_title = "",
-      general = paste(
-        "For all topics, search queries were comprised",
-        "of relevant free text & controlled vocabulary terms."
-      )
-    )
-}
-
-# ---- prisma-flow-setup
-
-prisma_df <-
-  read.csv(here::here("data/sys-rev/PRISMAflow.csv"),
-           stringsAsFactors = F)
-
-n_included <-
-  rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),
-              which = 1) %>%
-  janitor::clean_names() %>%
-  filter(is.na(exclude)) %>%
-  distinct(study_id, author) %>%
-  n_distinct()
-
-prisma_df$n[24] <- n_included
-
-n_extra_reports <-
-  rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),
-              which = 1) %>%
-  janitor::clean_names() %>%
-  filter(!is.na(exclude)) %>%
-  filter(additional_record_for_included_study == "Y") %>%
-  n_distinct()
-
-n_reports_included <- n_included + n_extra_reports
-
[…]

### 2021-11-23 03-Chp-Systematic-Review-Methods.Rmd
Working version after Chapter 7

@@
 
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+<!-- TODO This should also show Raffatin! -->
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsAD-cap) Random-effects meta-analysis of LDL on vascular dementia risk, standardised per 1-SD increase in the lipid fraction.
 
@@
 A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
+
+<!-- TODO This is not technically - more studies available on vascular dementia -->
 

### 2021-11-23 06-Chp-IPD-Analysis.Rmd
Working version after Chapter 7

@@
 
-In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.
-To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.[@fisher2017a] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
 All interaction analysis were performed using the common-set-adjusted model (Model 1).
+
+<!-- QUESTION Why was Ancelin, which provides summary level data stratified by sex, not included in the analysis?
+Several reasons: i) cause it was not adjusted for the same covariates; ii) because the -->
 

### 2021-11-23 07-Chp-Triangulation.Rmd
Working version after Chapter 7

--- 2021-11-18 07-Chp-Triangulation.Rmd
@@
 
-This approach represents a significant step forward from the current evidence synthesis practice of synthesising evidence from only one approach (e.g.
-randomised controlled trials (RCTs), non-randomised studies of exposures (NRSE) or interventions (NRSI), etc.).
-The most common implementation of this method to date has been in the form of _qualitative triangulation_ - that is the identification and a narrative comparison, where the internal biases and differences between the study question and the causal question of interest (indirectness) of each result are discussed.
+This approach represents a significant step forward from the current practice of synthesising evidence from only one type of study (e.g.
+randomised controlled trials (RCTs), non-randomised studies of exposures (NRSE) or interventions (NRSI)).
+The most common implementation of this method to date has been in the form of _qualitative triangulation_ - that is the identification and narrative comparison of diverse evidence sources with respect to their underlying bias structures.[@lawlor2016]
 
 However, qualitative triangulation faces issues at scale.
-There is a need to include all evidence, as otherwise the potential for cherry-picking, yet as the number  as it is not possible to compare and contrast across multiple results in any meaningful way.
-This fact is also illustrated by previous exemplars of triangulation only considering three individual results.
-<!-- TODO CITATION NEEDED - original triangulation paper and Ference --> An alternative option previously employed is to assign bias to the output of a meta-analysis of similarly designed studies, but this loses information on the specific biases inherent to each results contributing to the summary estimate.
-For example, while it may be true that all non-randomised studies share some minimal level of bias, investigation of the biases applicable to each individual result gives useful additional information.
-Recent development in bias assessment have allowed for a much more granular consideration of the threats to the internal validity of a result.
-In combination, these limitations to qualitative triangulation detail a need for a more systematic way to integrate across multiple evidence sources as the number of individual results contributing to the exercise increases.
+There is a need to include all evidence to avoid potential confirmation bias,[@dubroff2018] yet as the number of evidence sources increases, it is not possible to narratively compare and contrast across multiple results in any meaningful way.
+This fact is illustrated by previous exemplars of triangulation only considering a small number of individual results.[@ference2014; @lawlor2016] To overcome this limitation, some attempts have considered the output of a meta-analysis of similarly-designed studies to be a single source of evidence, and have assessed bias in relation to this summary result.
+While this approach keeps the number of individual sources of evidence manageable, it loses useful information on the specific biases inherent to each result contributing to the summary estimate.
+For example, while it may be true that all non-randomised studies share some minimal level of bias, competing extents and directions of bias in individual results may be masked by the use of summary estimates.
+In addition, previous attempts at qualitative triangulation have not systematically assessed the indirectness of the results, that is the differences between the question of interest and the question addressed by a study.
 
-This chapter, in addition to providing a narrative comparison of the existing and new evidence identified in this thesis, builds on recent developments in risk-of-bias assessment and existing methods for bias-/indirectness-adjusted meta-analysis to propose a generalised framework for quantitative triangulation.
-The method, along with the methodological challenges to its implementation, is illustrated via a proof-of-concept case study examining the causal effect of average exposure to LDL-c at mid-life on Alzheimer's disease risk.
-In the following section, I define important terms used throughout this chapter.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-\newpage
-
-### Terminology {#tri-terminology}
-
-<!-- Discuss and defined three things: -->
-
-<!-- * Qualitative vs quantitative triangulation -->
-<!-- * Bias vs. indirectness -->
-<!-- * Additive vs proportion effect of bias/indirectness -->
-
-For the sake of clarity, and given the multiple competiting defitions used to define key concepts on this topic, I begin by defining the terms as used in this chapter.
-
-<!-- TODO Does Julian have a good reference for the conflict between different terms used for biases? -->
-
-__Bias vs indirectness__
-
-Both
-
-Bias (or internal bias) in the result is defined as systematic deviation from result the "idealised" version of the study (that is, )
-
-In contrast, the indirectness of the result (also called generalisability or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.
-Problems with indirectness can be arise from differences in population, intervention/exposure, outcomes and
-
-Of note, the original method employed in this chapter refers indirectness as "external bias" - however.
-This distinction is important, as bias and indirectness describe two different issues, and referring to both as bias
-
-In addition, indirectness is the widely used term, including by widely-adopted methods such as the GRADE framework.[@guyatt2011]
-
-__Additive vs proportional effects__
-
-Additive biases (identified by a "Favours experimental"/"Favours comparator" response) are XXXX. A key example of additive bias is immortal time bias, which will always favour the intervention.
-
-Proportional biases (identified by a "Towards null"/"Away from null" response) are those related to the magnitude of the effect.
-A key example of this type of bias is non-differential misclassification bias, which will bias the effect estimate towards the null.
-
-The effects of both bias and indirectness can be either additive or propotional.
-
-Additive bias/indirectness is
-
-Both bias and indirectness can be defined as additive or propotional. Additive bias/indirectness is that which can shift the p
+Taken together, these limitations to qualitative triangulation detail a need for a more systematic way to integrate across multiple evidence sources as the number of individual results contributing to the exercise increases.
+One such approach is _quantitative triangulation_, where results from different evidence sources are combined numerically while accounting for the key sources of bias and indirectness in each.
+This chapter, in addition to providing a narrative comparison of the existing and new evidence identified by this thesis, builds on recent developments in risk-of-bias assessment and methods for bias-/indirectness-adjusted meta-analysis to propose a generalised framework for quantitative triangulation.
+The framework, along with the methodological challenges to its implementation, is illustrated via two case studies examining the causal effect of lipids on dementia outcomes.
 
@@
 This triangulation exercise draws on the research produced in each of the preceding chapters.
-More specifically, this chapter builds on the comprehensive systematic review presented in chapter \@ref(sys-rev-heading).
-It also incorporates the new evidence produced by the analysis of the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-heading)) and of the association of lipids with dementia outcomes in previously unanalysed datasets accesssed via the DPUK (Chapter \@ref(ipd-heading)).
+More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).
 
-Table \@ref(tab:thesisOverview-table) summarises the research each approach has attempted to address, the exposures and outcomes considered in each study, and the contribution of each chapter to the triangulation exercise presented here.
+Table \@ref(tab:thesisOverview-table) summarises the research each data source has attempted to address, the exposures and outcomes considered in each case, and the contribution of each chapter to the triangulation exercise presented here.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis, and used as evidence sources in this triangulation exercise.
+(ref:thesisOverview-caption) Summary of studies included in this thesis and used as evidence sources in this triangulation exercise.
 Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.
@@
 
-The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias).
-In summary, RTCS were assessed using the RoB 2 tool;[@sterne2019] NRSI  using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(#rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
-tool.[@mamluk2020]
+&nbsp;<!----------------------------------------------------------------------->
 
-<!-- TODO Talk about how the CPRD and IPD analysis results were assessed here! -->
+### Qualitative triangulation {#qual-tri}
 
-<!-- Risk of bias assessment was performed for each of the included cohorts using the risk-of-bias assessment tool for non-randomised studies of exposures introduced previously (for a more detailed discussion of this tool, see Section \@ref(rob-tools-nrse)).
--->
-
-<!-- Due to the inherent conflict of interest in assessing my own analysis, the result were also assessed by two independent reviewers. -->
-
-### Qualitative triangulation
-
-As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were grouped by outcome, and systematically compared and contrasted.
+As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initally grouped by outcome, and the findings from each source were narratively compared and contrasted.
 Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.
 
-<!-- TODO Use the fact that it doesn't make sense to qualitatively compare at the single result level to highlight the need for a more quantitative approach - usually default to summary at the -->
-
-<!-- IDEA Note the text by Turner on the fact that you can just adjust for a single type of bias - a good example of this would be to try and adjust for internal biases so you get the best possible estimate and then apply it to something like a assumed life-course model - steal from NIHR text, and refer to the appendix  -->
-
-This analysis built on the detailed risk of bias assessments performed and presented as part of the systematic review (Chapter \@ref()/\@ref()).
-Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis, details of which are available in Appendix \@ref(?).
-
-<!-- TODO Need to actually do these, and include results in the analysis. -->
+This analysis built on the detailed risk-of-bias assessments performed and presented as part of the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)).
+Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis.
+The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias), but in summary, RCTS were assessed using the RoB 2 tool;[@sterne2019] NRSI using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
+tool.[@mamluk2020]
 
@@
 
-In addition to the qualitative discussion of evidence, I attempted to integrate the numerical results of the multiple approaches.
-This proof-of-concept approach incorporates recent advancements in the way that bias in results is assessed (move from checklists to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to to illustrate how causal questions could be addressed under this quantitative triangulation framework.
+In addition to a qualitative discussion of the evidence, I attempted to integrate the numerical results of the multiple approaches under a proposed quantitative triangulation framework.
+This approach incorporates recent advancements in the way that bias in results is assessed (namely the move to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to illustrate how causal questions could be addressed under this framework.
 
-This proposed framework involves several steps, as described in detail in the following sections. In summary these steps are:
+This proposed framework involves several steps, described in detail in the following sections. In summary, these steps are:
 
 1. Define the causal question of interest
-1. Identify of relevant evidence sources and standardisation of effect directions
+1. Identify of relevant evidence sources and standardise effect directions
 1. Assess and visualise the extent and direction of bias in each result
 1. Define modifying terms for bias and indirectness in each result
-1. Caclulate bias-/indirectness-adjusted results and perform meta-analysis
+1. Calculate bias-/indirectness-adjusted results and perform meta-analysis
 
-In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate for a single study is described in detail for a single study.
-<!-- TODO CITATION NEEDED need to cite single paper here --> Following this, the process for an example causal question as a case study, as defined below.
+In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate is described in detail for a single result.
+Following this, the framework is applied to two case studies, as defined below.
 
@@
 
-Given that this quantitative analysis is intended as a proof-of-concept for the framework, rather than aiming to produce findings that should guide clinical practice, I consider only one of the multiple possible causal questions related to the broad topic of the effect of lipids on dementia outcomes.
+Using the ROBINS-E framework,[@morganr2020] I defined the parameters of my causal questions of interest:
 
-Using the ROBINS-E framework I defined the parameters of my causal question of interest:
+__Case study #1: Effect of mid-life LDL-c on Alzheimer's disease__
 
@@
 * _Summary measure of exposure over time_: Average exposure 
+* _Outcome of interest:_ Alzheimer's disease
 
-This question was chosen for a number of reason.
-Firstly, given the long prodomal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period is particularly important.
-Secondly, examining the causal impact of lipids on a specific outcome (in this case, Alzheimer's disease), rather than a composite outcome (all-cause dementia), focuses on an single causal pathway rather than including conditions that likely have very different mechanisms of disease.
-Finally, and relevant to its use as a case study for the quantitative triangulation approach, this question had several relevant sources of evidence available (versus, for example, any question looking at vascular dementia).
+__Case study #2: Effect of mid-life triglycerides on vascular dementia__
 
-<!-- TODO This table will describe the causal questions of interest, following the ROBINS-E framework as columns, and list the included studies adn the relative weights of each. -->
+*	_Population of interest_: General population
+*	_Exposure of interest_: Triglycerides
+*	_Exposure window of interest_: Mid-life (45-60)
+* _Summary measure of exposure over time_: Average exposure
+* _Outcome of interest:_ Vascular dementia
+
+&nbsp;
+
+These questions were chosen for several reasons.
+Firstly, work presented in previous chapters had identified some evidence for an association in these exposure/outcome pairs.
+Secondly, given the long prodomal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period are particularly important.
+Finally, examining the causal impact of a lipid faction on a specific outcome (e.g.
+Alzheimer's disease), rather than a composite outcome (e.g.
+all-cause dementia), focuses on an single causal pathway rather than including several conditions in the outcome definition that likely have very different mechanisms of disease.
+In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(hold)), and use of an composite all-cause outcome in the triangulation framework may mask this.
 
@@
 
-####	Identify relevant studies
+####	Identify relevant results
 
 Once the causal question of interest had been defined, relevant individual results were obtained from the data sources described in Section \@ref(tri-data-sources).
-In a broad sense, this meant pulling out studies that examined the relationship between LDL-c and Alzheimer's disease risk, either directly (non-randomised studies of LDL-c levels) or indirectly (non-randomised studies of statins, Mendelian randomisation studies using genetic instruments for LDL-c levels).
+In a broad sense, this meant extracting results that examined the relationship between the exposure/outcome pair, either directly (e.g.
+non-randomised studies of LDL-c levels) or indirectly (e.g.
+non-randomised studies of statins, or Mendelian randomisation studies using genetic instruments for LDL-c levels).
 
-Once the set of relevant results were identified, effects were standardised to refer to the risk of Alzheimer's disease resulting from a "reduction" in LDL-c.
-For studies of statins, th.
-However, for both non-randomised studies and Mendelian randomisation analysis of lipid levels, the effect is usually reported per 1-SD increase in LDL-c.
+Once the set of relevant results were identified, effects were standardised to refer to the risk resulting from a "reduction" in the lipid fraction.
+For both non-randomised studies and Mendelian randomisation analysis of lipid levels, the association is usually reported per 1-SD increase in the lipid fraction.
 In this case, the effect estimates were inverted to ensure consistency across study designs.
@@
 
-For the sake of consistency, I mapped the different acceptable judgements in each risk-of-bias tool to a harmonised set of judgements: "Low", "Moderate","High".
+Risk of bias was assessed for each result as discussed in Section \@ref(qual-tri).
+For the sake of consistency and ease of computing, I mapped the different acceptable risk-of-bias judgements in each tool to a harmonised set: "Low", "Moderate", and "High".
 The exact mapping can be seen in Table \@ref(tab:robLevelsMapping-table).
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:robLevelsMapping-caption) robLevelsMapping
+(ref:robLevelsMapping-caption) Mapping of the different acceptable levels of bias across the assessment tools to a harmonised set.
+Note that no mapping for "Critical" risk of bias was performed, as best practice reccommends that studies at critical risk of bias are excluded from quantitative syntheses.
 
-(ref:robLevelsMapping-scaption) robLevelsMapping
+(ref:robLevelsMapping-scaption) Mapping of risk-of-bias judgements across assessment tools
 
@@
 
-In addition to assessing the extent of bias in each domain, as defined by the three levels detailed above, I attempted to record the predicted direction and type of bias.
+In addition to assessing the extent of bias, as defined by the three levels detailed above, I attempted to record the predicted direction and type of bias in each domain.
 This was achieved via an additional question at the end of each bias domain, which asked assessors to predict the expected direction of bias in that domain.
@@
 
-As indicated in the options above, the response to this question is also used to determine the predicted type of bias (additive or proportional - see Section \@ref(tri-terminology)) in addition to the direction.
-For additive biases, determining the absolute direction of bias was simply a case of whether the bias shift the effect estimate to the left or right on an imaginary forest plot.
-For example, if a bias was predicted to favour the intervention, then the estimate would be shifted to the right.
+As indicated in the options above, the response to this question is also used to determine the predicted type of bias as either additive or proportional.
+Proportional biases are dependent on the magnitude of the effect, while additive biases are not.[@turner2009]
+
+For additive biases, determining the absolute direction of bias was simply a case of whether the bias is expected to shift the effect estimate to the left or right on an imaginary forest plot.
+For example, the estimate would be shifted to the right if a bias was predicted to favour the comparator (Figure \@ref(fig:exampleDirection)).
 
 In contrast, for proportional biases, whether the estimate should be increased or decreased proportionally depends on the current position of the point estimate relative to the null.
-For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be adjusted for by moving the effect estimate propotionally to the right.
-In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null would be adjusted for by moving the effect estimate propotionally to the left.
+For example, if the effect estimate represents a protective effect (below the null), then bias towards the null would be adjusted for by moving the effect estimate proportionally to the right.
+In contrast, if the effect of the intervention is harmful (effect estimate above the null), bias towards the null would be adjusted for by moving the effect estimate proportionally to the left.
+Both scenarios are illustrated using example data in Figure \@ref(fig:exampleDirection).
 
@@
 (ref:exampleDirection-cap) Illustration of calculating the absolute direction of biases (indicated by arrows), based on bias type.
-For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null.
-In contrast, the position of the effect estimate is accounted for when determining the absolute direction of proportional biases.
+For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null - bias "favouring the comparator" will always pull the effect estimate to the right.
+In contrast, the position of the effect estimate is accounted for when determining the absolute direction of proportional biases, defined as towards or away from the null.
 
@@
 
-Note that for some domains, only one type of bias is allowed.
-For example, in the confounding domains in the ROBINS-I/ROBINS-E tools, only the "Favours experimental"/"Favours comparator", and "Unpredictable" options are available, meaning that bias in this domain will always be considered additive.
-Additionally, the predicted direction and type of bias were not recorded for domains at "Low" risk of bias.
+The predicted direction and type of bias were not recorded for domains at "Low" risk of bias.
+Finally, for some domains, only one type of bias is allowed.
+For example, in the confounding domains in the ROBINS-I/ROBINS-E tools, only the "Favours experimental"/"Favours comparator" and "Unpredictable" options are available, meaning that bias in this domain will always be considered additive.
 
@@
 
-To aid with the triangulation exercise and to act as a sense-check, I created a new method to visualise the extent, direction and type of bias in each result to enable detailed comparison across different studies contributing to a synthesis.
-Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), these "bias direction" plots show the  level of bias across the domains in each study is reported using coloured blocks.
-However, in contrast to the previous plots, symbols are used to illustrate the predicted absolute direction of bias in that domain, as discussed in the previous section.
+To aid with the quantitative triangulation exercise, I created a new method to visualise the extent, direction and type of bias in each result, enabling detailed comparison across different studies contributing to a synthesis.
+Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), these "bias direction" plots show the level (or extent) of bias across the domains for each result reported using coloured blocks.
+However, in contrast to the previous forest plots, symbols are used to illustrate the predicted absolute direction of bias in that domain.
 Distinct symbol pairs are used to denote additive and proportional biases.
-
-Convience functions in the `triangulate` package (see Section \@ref(tri-software)) were used to preprocess risk of bias data for use with both bias-direction plots and adjusted meta-analyses, as discussed in subsequent sections.
-These bias direction plots themselves were created using the risk-of-bias visualisation tool described in Appendix \ref(?).
 
@@
 
+<!-- QUESTION sign is negaitve if to the left, because you are taking it away in the final formula and it therefore needs a negative sign to be positive overall! -->
+
 One key feature of the domain-based risk-of-bias tools is that the domains are considered interchangeable - i.e.
@@
 
-Reasonable values for the position and spread of the prior distributions were informed by a previous reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean and maximum values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(?) for more details on how these were calculated).
-For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two sets of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
+Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(?) for more details on how these were calculated).
+For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
 In the first scenario, the relationship between the position assigned to each additive judgement is linear.
-In the second scenario, the step from "moderate" to high" is twice that from "low" to "moderate".
-Across both additive and proportional biases, the variance of the "high" risk--of-bias judgement distribution was defined to be greater than that for the "moderate" risk-of-bias judgement.
+In the second scenario, the step from "Moderate" to "High" is twice that from "Low" to "Moderate".
+Across both additive and proportional biases, the variance of the "High" judgement distribution was defined to be greater than that of the "Moderate" judgement.
 
@@
 
-(ref:priorsAdd-scaption) Additive bias distributions
+(ref:priorsAdd-scaption) Prior distributions mapped to different extents of bias.
 
@@
 
-Where the direction of bias in a domain was unpredictable for a given result, the mean of the adjustment distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained (e.g.
-for an unpredictable "high" assessment, the distribution would be $N(0,0.12)$).
-In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate, but does increase the uncertainty around it.
+Where the direction of bias in a domain was unpredictable for a given result, the mean of the prior distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained (e.g.
+for an unpredictable "High" additive bias, the distribution would be $N(0,0.1)$ under Scenario 1).
+In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate but does increase the uncertainty around it.
 
@@
 
-####	Assessing and assigning modifying values to indirectness
+####	Assessing and assigning prior values to indirectness
 
-An identical approach was employed to assess and assign prior distributions to the risk of indirectness in each result.
-The target question for each result was compared against the causal question of interest with respect to three domains (population, intervention/exposure, outcome), <!-- TODO CITATION NEEDED --> again using the scale of "Low/"Moderate"/"High" to quantify the extent of indirectness.
-All indirectness were defined _a priori_ as being proportional in nature, in line with previous work on this topic.[@turner2009]
+The indirectness of a result (also termed external bias, relevance, generalisability, or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.
 
-As crude illustrative example, consider the causal question of the interest in this exercise, the effect of LDL-c in mid-life on Alzheimer's disease.
-Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be downweighted due to reduced relevance to the causal question.
+An identical approach was employed to assess, and assign prior distributions to, the indirectness in each result.
+The target question for each result was compared against the causal question of interest with respect to three domains, defined as important by the GRADE framework for assessing the certainty of evidence:[@guyatt2011] population, intervention/exposure, and outcome.
+I again used the scale of "Low/"Moderate"/"High" to quantify the extent of indirectness in each domain.
+All indirectness was defined _a priori_ as being proportional in nature (i.e.
+depending on the magnitude of the effect), in line with previous work on this topic.[@turner2009;@thompson2011] As above, data from the previous elicitation exercise were used to inform reasonable prior distributions for each level of indirectness (Table \@ref(tab:priorsIndirect-table)).
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:priorsIndirect-caption) Prior distributions for extent of indirectness, on the log scale.
+
+(ref:priorsIndirect-scaption) Prior distributions mapped to different extents of indirectness.
+
+```{r priorsIndirect-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+As an illustrative example, consider the first causal question of the interest in this exercise, the effect of LDL-c in mid-life on Alzheimer's disease.
+Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be down-weighted due to reduced relevance to the causal question.
 
@@
 
-Using the the method reported in Turner _et al._,[@turner2009] total additive and proportional bias and indirectness were calculated for each result. Briefly,
+Using the the method reported in Turner _et al._,[@turner2009] total additive and proportional bias and indirectness were calculated and used to define an adjusted estimate for each result included in the synthesis.
 
-<!-- TODO Talk about how total add/prop biases calculated -->
-
-Once the total additive and proportional bias and indirectness for each result were computed, they were used to define an adjusted estimate for each result included in the synthesis.
-
-Using the method defined in Turner _et al_,[@turner2009] the adjusted estimate for each result, $\hat\theta$, is defined as:
+The adjusted estimate for each result, $\hat\theta$, is defined as:
 
@@
 \end{equation}
+
+where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness.
+Note that in this exercise, the total additive indirectness $\mu_{i\beta}^{\mathrm{In}} = 1$, as all indirectness was defined _a priori_ as being proportional.
 
@@
 
-Once each individual result has been adjusted, I performed a random effects meta-analysis using the unadjusted and adjusted (under the two scenarios defined above) results.
-<!-- TODO CITATION NEEDED -->
+Once each individual result had been adjusted using this approach, I performed a random effects meta-analysis using the unadjusted and adjusted results.
+I also compared the adjusted results under the two scenarios of additive bias defined.
+results.
+I extracted the overall effect estimates, along with measures of heterogeneity in each case ($\tau^2$, $I^2$).[@higgins2003; @higgins2008b]
 
-<!-- TODO Deal with the fact that the Panel wasn't super useful -->
+<!-- IDEA Sensitivity analysis - set means to zero and only adjust for variance. Essentially adding uncertainty based on the amount of bias but not moving the effect estimate -->
 
@@
 
-### Qualitative triangulation
+### Qualitative triangulation / narrative comparison
+
+__[Question: the "strength of evidence" language here makes for fairly ambiguous reading - e.g.
+"very weak evidence".
+Should I also include the effect estimates from each approach, which will help to clarify, if it is a narrative synthesis?]__
 
@@
 
+I identified no consistent effect of any lipid fraction on any dementia outcome  across the evidence sources presented in this thesis, through there was some suggestion of a protective effect of LDL-c lowering (via statin use) on all-cause dementia and Alzheimer's disease, and a harmful effect of raised triglyceride levels on vascular dementia.
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### All-cause dementia
 
-<!-- TODO Need to talk about fibrates here too -->
+Analysis of lipid levels across both the systematic review (Chapter \@ref(hold)) and the IPD analysis (Chapter \@ref(hold)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia.
+Similarly, both a meta-analysis of RCTs of statin use and of MR analyses of genetic instruments that mimic statin use found very weak evidence of an association, providing indirect evidence on the effect of LDL-c lowering on this outcome.
 
-__Statins and all-cause dementia__
+In contrast, the meta-analysis of NRSI of statin use found a slight protective effect, though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the intervention.
+Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(hold)) found evidence of a harmful effect, though this is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
 
-This conflicts with the findings of our analysis, where statin use was associated with an increased risk of all-cause dementia (`r anydem_text`).
-Some of the included studies in the meta-analysis specifically exclude vascular dementia from the definition of all-cause dementia,[@chao2015] which may limit the ability for comparison with our findings for the all-cause dementia outcome.
-
-Additionally, a previous analysis of the THIN EHR database using a propensity-score matched analysis found a protective effect of statins on all-cause dementia (HR:0.81, 95%CI:0.69-0.96)[@smeeth2009].
+For fibrates, an alternative lipid-regulating agent, there was some evidence of an increased risk of all-cause dementia in the CPRD, though this did not replicate in the meta-analysis of previous studies examining the association of fibrates and all-cause dementia.
 
@@
 
-__Statins and Alzheimer's disease__
+Meta-analysis of lipid levels in the systematic review (Chapter \@ref(hold)) found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease.
+Similarly, a meta-analysis of MR analyses of genetic instruments that mimic statin use found very weak evidence of an association.
 
-Our results are broadly in line with the findings of two distinct approaches examining the effect of statin treatment on subsequent Alzheimer's disease.
-No randomized trials of statins for the prevention of Alzheimer's disease have been reported, but a recent meta-analysis of 20 observational studies found statins were associated with a reduced risk of Alzheimer's disease (RR 0.69, 95% CI 0.60–0.80) with stronger evidence than observed in our analysis.[@poly2020] This review included case-control studies and analyses likely to be at risk of immortal time bias, which may account for the discrepancy with our findings.
-Additionally, a recent Mendelian randomization study examining the effect of genetic inhibition of HMGCR on Alzheimer’s disease (a genetic proxy for statin treatment) provided equivocal evidence (OR: 0.91, 95%CI: 0.63-1.31) but was consistent with our results.[@williams2020]
+In contrast, the meta-analysis of NRSI of statin use found a slight protective effect, though similar to the all-cause dementia outcome, many of the studies in this analysis were found to be at risk of immortal time bias.
+However, the CPRD analysis (Chapter \@ref(hold)) attempted to account for this potential bias through the use of time-varying treatment indicator.
+It found very weak evidence for an effect, though the potential for differential misclassification on the basis of the exposure limit the validity of this finding.
 
-Our additional analyses stratified by statin properties found little evidence of differences in associations of lipophilic and hydrophilic statins and incidence of Alzheimer’s disease, consistent with a recent meta-analysis of observational studies.[@chu2018]
+The IPD analysis (Chapter\@ref(hold)) provided no information on this outcome, as the sole cohort containing data on Alzheimer's disease (Whitehall II) had previously been analysed in respect to this outcome and so was included in the meta-analysis of NRSE.
 
@@
 
-__Statins and vascular/other dementia__
+There was a general absence of existing evidence on vascular dementia outcomes.
+Meta-analysis of the small number of studies examing  lipid levels in the systematic review (Chapter \@ref(hold)) found extremely weak evidence for an association of any lipid fraction with vascular dementia.
+Similarly, a meta-analysis of statin use found very weak evidence for an effect on this outcome.
+The CPRD analysis (Chapter \@ref(hold)) found evidence for a harmful association of statin use with vascular dementia, though this finding is likely to be the result of severe confounding by indication, as identified through the use of control outcomes.
 
-Far fewer studies have tested the association between lipid-regulating agents and vascular dementia or other dementias.
-A recent review found four observational studies examining the association of statins and vascular dementia found limited evidence for an effect (RR:0.93, 95% CI 0.74–1.16).[@poly2020] This contrasts with the harmful association found in our analysis (`r vasdem_text`).
-When stratifying by lipid properties, lipophilic statins were more harmful than hydrophilic statins in vascular dementia, potentially due to their ability to cross the blood brain barrier.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-__Other drug classes__
-
-Apart from statins, few studies examining a lipid-regulating agent have been reported (Chapter \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)).
-
-One of the few classes for which a evidence was available were fibrates, which found little evidence of an association with all-cause dementia was identified,[@ancelin2012] inconsistent with our finding that patients prescribed fibrates had higher all-cause dementia risk than those prescribed other lipid lowering agents.
-
-A previous Mendelian randomization study found little evidence that genetic variants that proxy for ezetimibe affect risk of Alzheimer’s disease (OR: 1.17, 95%CI: 0.73-1.87),[@williams2020] consistent with our findings.
-Note that this study was published in 2020 and so was not included in the review.
+Finally, the IPD analysis (Chapter \@Ref(hold)) provided supporting evidence for the absence of an effect of any fraction on vascular dementia, with the sole exception of triglycerides.
+Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts though there is the potential for uncontrolled confounding due to the limited information on covariates available.
+With respect to evidence on treatments for hypertriglyceridemia, examination of fibrates in the CPRD provided very weak evidence of an association with vascular dementia.
 
@@
 
+```{r ldlAdBIAMA, include = F}
+```
+
+```{r tgVadBIAMA, include = F}
+```
+
 #### Single study
 
-Explain how example study was chosen
+As an illustrative example, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD are considered here.
+For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
+In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(hold) for a fuller discussion).
+As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right.
+In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure.
+Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experiment_ (in this case, an intervention).
+As such, the absolute direction of bias is to the left.
+In Domain 7 (bias in selection of the reported result), for consistency with the other NRSI, in the absence of a protocol the bias is assumed to be _away from the null_.
+Given the position of the effect estimate below the null, the absolute direction of bias in this domain is to the left.
 
-Show result and bias
-
-Reproduce version of Table 2 rom the "proposed method" paper for indirectness
-
-Total additive bias (on the log scale) was `r hold()`. Similarly, total additive indirectness was (),
-
-Calculate internal-bias adjusted
-
-`r hold()`
-
-The unadjusted effect for this study was `r hold()` and the adjusted effect estimate for this study was `r hold()`
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->  
 (ref:biasDirectionSingle-cap) Bias direction plot for a single study showing the predicted direction of bias in each domain.
@@
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
+With respect to indirectness, the result was judged to be a low risk in the population and outcome domains.
+However, the fact the result refers to the effect of statins, which may have an effect on dementia outcomes through a mechanism other than LDL-c lowering, put it at high risk of indirectness in the intervention/exposure domain.
+
+The unadjusted estimate was `r single_unadjusted `. After accounting for the biases and indirectness described, the adjusted result was `r single_adjusted `.
 
@@
 
-#### Case study: effect of LDL-c at midlife on Alzheimer's disease
+#### Case study #1: effect of LDL-c at midlife on Alzheimer's disease
 
-From the data sources identified in Section \@(), I identified X results relevant to my causal question of interest.
-<!-- TODO CITATION NEEDED will need to cite these!
---> The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
+From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest.
+Most (n=17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-heading) provided an additional estimate from the CPRD analysis.
+The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
+
+<!-- QUESTION Hypercholesterolemia should not be included here, as it is focused on total cholesterol rather than specifically LDL-c, right? -->
 
@@
 
-```{r ldlAdBIAMA, include = F}
-```
-
 (ref:ldlAdBiasDirection-cap) Bias direction plot, summarising the internal biases related to effect of LDL-c on Alzheimer's disease, stratified by study design.
 
-(ref:ldlAdBiasDirection-scap) Bias direction plot, summarising internal biases related to the
+(ref:ldlAdBiasDirection-scap) Bias direction plot, summarising internal biases
 
@@
 
-The results of the unadjusted and the bias-/indirectness-adjusted (under the Scenario 1 of additive biases) are shown in Figure \@ref(fig:fpLdlAd).
-I observed no substantial change to the overall effect (unadjusted `r unadj_effect`; adjusted `r adj_effect_scenario1`), though adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
-However, as can been seen from the right panel in the figure, this reduction in heterogeneity between studies is largely achieved via a reduction in precision.
+The results of the unadjusted and the bias-/indirectness-adjusted (under Scenario 1) are shown in Figure \@ref(fig:fpLdlAd).
+Following adjustment for bias and indirectness, the observed effect attenuates to the null (unadjusted `r unadj_effect`; adjusted `r adj_effect_scenario1`).
+Additionally, adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
+However, as can been seen from the right panel in Figure \@ref(fig:fpLdlAd), this reduction in heterogeneity between studies is largely achieved via a reduction in the precision of each individual result.
 
-To explore the different impacts of the two defined scenarios for additive bias, I plotted these:
-
-<!-- TODO Finish -->
+<!-- TODO How effect are fibrates at lowering triglycerides? is it a direct effect, or are there alternative -->
 
@@
 <!-- TODO This should really be stratified by type -->
-<!-- TODO Standardise effect estimates to same direction -->
-<!-- TODO Need to add my own evidence -->
 
-(ref:fpLdlAd-cap) Random effects meta-analysis using unadjusted and bias-/indirectness-adjusted results.
+(ref:fpLdlAd-cap) Random effects meta-analysis of the association of midlife LDL-c with Alzheimer's disease, using unadjusted and bias-/indirectness-adjusted results.
 
@@
 
+The estimates obtained under the two scenarios of additive bias are plotted in Figure \@ref(fig:fpLdlAdComparison), and no substantial differences were observed between the them.
+
+<!----------------------------------------------------------------------------->
+(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
+The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
+
+(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+
+```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Case study #2: effect of triglycerides at midlife on vascular dementia
+
+From the data sources identified in Section \@ref(tri-data-sources), I identified 7 results relevant to my causal question of interest: 4 were identified via the systematic review,`r tg_vad_citations` while Chapter \@ref(cprd-heading) provided two additional estimates from unanalysed datasets (CaPS and Whitehall II), and Chapter \@ref(ipd-heading) provides an estimate for the effect of fibrates, a treatment for hypertriglyceridaemia.
+The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:tgVadBiasDirection), stratified by study design.
+
+<!----------------------------------------------------------------------------->
+(ref:tgVadBiasDirection-cap) Bias direction plot, summarising the internal biases related to effect of triglycerides on vascular dementia, stratified by study design.
+
+(ref:tgVadBiasDirection-scap) shortcap
+
+```{r tgVadBiasDirection, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:tgVadBiasDirection-cap)', out.width='100%', fig.scap='(ref:tgVadBiasDirection-scap)'}
+knitr::include_graphics(file.path("figures/tri/midlife_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Comparison of the unadjusted and bias-/indirectness-adjusted results for the effect of triglycerides on vascular dementia did not demonstrate a substantial difference (unadjusted `r unadj_effect_vad`; adjusted `r adj_effect_scenario1_vad`; Figure \@ref(fig:fpTgVad)), though again, heterogeneity between the adjusted results was greatly reduced (unadjusted $\tau^2$ = `r unadj_vad_tau2`, $I^2$ = `r unadj_vad_I2`; adjusted  $\tau^2$ = `r adj_vad_tau2`, $I^2$ = `r adj_vad_I2`).
+Similarly there was minimal difference between the results under the two scenarios of bias (Figure \@ref(fig:fpTgVaDComparison))
+
+<!----------------------------------------------------------------------------->
+(ref:fpTgVad-cap) Random effects meta-analysis of the association of midlife triglycerides and vascular dementia, using unadjusted and bias-/indirectness-adjusted (Scenario 1) results.
+
+(ref:fpTgVad-scap) shortcap
+
+```{r fpTgVad, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVad-cap)', out.width='100%', fig.scap='(ref:fpTgVad-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad.png"))
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
+The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
+
+(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+
+```{r fpTgVaDComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVaDComparison-cap)', out.width='100%', fig.scap='(ref:fpTgVaDComparison-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad_scenarios.png"))
+```
+<!----------------------------------------------------------------------------->
+
 ## Discussion
-
-<!-- IDEA Do turner et al standardise effect direction? -->
-
-While this analysis may be biased from the non-empirical bias adjustment factors, at the very least, it acknowledges the the uncertainty of evidence via the widening of confidence intervals. 
-No less problematic than the analysis fo biased estimates in a meta-analysis which does not account for bias.
 
@@
 
-This chapter has narratively synthesised the existing and new evidence identified and produced by the previous chapters, highlighting the absence of any consistent association between any blood lipid and any dementia outcome in the context of the bias in each approach.
+This chapter has narratively synthesised the evidence identified and produced by the previous chapters, highlighting the absence of any consistent association between any blood lipid and any dementia outcome.
 
 In addition, it has sought to provide a generalised framework for quantitative triangulation, building on existing methods for systematic domain-based risk of bias assessment and bias-/indirectness-adjusted meta-analysis.
-While a lack of information on the prior distributions of bias and indirectness in non-randomised studies precluded, to illustrate the method, I considered the example causal question of the effect of mid-life LDL-c on Alzheimer's disease risk derived from a previous expert elicitation exercise.
+To illustrate the method, I considered two causal questions: the effect of LDL-c at mid-life with Alzheimer's disease and the effect of triglycerides on vascular dementia.
+In the quantitative triangulation framework, there was very weak evidence for an effect in relation to either of the causal questions considered.
+The heterogeneity between results produced by different study designs contributing to the analysis was substantially reduced using this method, though this was largely due to a reduction in the precision of each individual result.
 
@@
 
-<!-- TODO See discussion of original Turner paper -->
+The quantitative analysis presented in this chapter is subject to some strong methodological limitation, which are discussed in detail below.
 
@@
 
-Allowing for the strong assumption that
+The key limitation of the quantitative synthesis presented in this chapter is the lack of empirical evidence available for the prior distributions for bias and indirectness.
+While I attempted to address this by informing the prior distributions using data from a previous expert elicitation exercise, the extent of bias/indirectness in that analysis may not generalise to the one presented here.
 
-The key limitation of this quantitative synthesis presented in this chapter is the ambiguity
+Ideally, these prior distributions would be based on empirical data on the effect of different domains of bias/indirectness on a result.
+Most meta-epidemiological studies examining the effect of different methodological issues studied only randomised controlled trials,[@amer2021; @page2016] and the estimates of bias they produce may not hold for non-randomised study designs.
+However, the prior distributions defined here are broadly comparable to previously reported estimates of the impact of bias in non-randomised trials.
+For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021a] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
 
-It is the reason that only one causal question is addressed as a case study, as to base clinical recommendations on a method dependent on non-empirical values would be inappropriate.
+A further limitation is the assumption that the distributions of bias are identical across domains of bias.
+Previous evidence from meta-epidemiological studies of randomised controlled trials that investigated the effects of different biases indicates that this is unlikely to be the case.[@savovic2018] The generalised framework for quantitative triangulation, presented here and available via the `triangulate` package (see Section \@ref(tri-software)), allows for domain-specific distributions of bias/indirectness.
+As more information on the effect of specific sources of bias becomes available, such domain-specific distributions should be used.
 
-Meta-epidemiological studies on the effect of different methodological issues on results exist for randomised controlled trials,[@amer2021; @page2016] suggesting that X, Y and Z.
+Finally, it may in fact be more reasonable for domains such as bias due to confounding to adjust on a per-confounder basis rather than mapping to a "Moderate" or "High" extent of bias.
+In this approach, prior distributions are assigned to each of the confounders pre-specified as part of the ROBINS-I/ROBINS-E tools.[@sterne2016] Then, rather than assigning a domain level distribution based on an arbitrary judgement of how many important confounders are missing, the result is adjusted for each confounder not accounted for in the original analysis.
 
-However, there is substantially less , arguably because of the absence of clear
-Many meta-epi studies of non-randomised studies assume bias at the study-design level, similar to the early triangulation frame-work, rather than considering the actual biases deemed to be present in a given result.
-In this scenario, study
+&nbsp;<!----------------------------------------------------------------------->
 
-Potential future meta-epidemiology studies should begin to create these datasets.
+#### Accuracy of bias-/indirectness-assessment
 
-New software for performing risk of bias assessments, being developed by the Bristol Appraisal and Review of Research group has this as a secondary methodological aim.
+A key issue in this analysis is the accuracy of the assessment of bias and indirectness in each result.
+It has been widely demonstrated that the inter-rater agreement when using risk-of-bias tools is low with regards to the extnet of bias assinged to each domain[@hartling2011; @minozzi2019; @minozzi2020] Though not previously studied, given the difficulty in assessing the predicted direction of bias, agreement on this aspect of the tools is likely to be lower still.
 
-Much of the attention to date has been on assessing the impact of different sources of bias on effect estimates has focused predominantly on randomised controlled trials.
-
-For example, a study examining the effect of found that only a subset of domains appear to impact the result, and that this effect is modest (10% change).[@savovic2018] However, this work examined RCTs, and these findings may not hold for other non-randomised study designs.
-<!-- TODO Double check this citation actually says what you think it does!
--->
-
-<!-- TODO Pretty sure Julian sent me some papers on have suggested values for randomised controlled trials (e.g. effect of poor blinding etc) -->
-
-Similar there are several examples of usmeta to define priors for other statistical terms in meta-analysis.
-For example, previous work has looked at defining prior distributions of heterogeneity across different topic areas using a large collection of meta-analyses from the Cochrane Collaboration.<!-- TODO Cite turner etc -->
-
-<!-- TODO Talk about the fact recent paper does not favour bias-adjustment -->
-
-Elicitation and bias-adjusted not as favoured versus weighting [@stone2020] <!-- TODO Check this is actually what this reference says --> though weighting at the overall risk-of-bias level loses some of the information contained in domain-level based assessments.
-
-#### Subjectivity of bias-/indirectness-assessment
-
-<!-- TODO Add text here on the subjectivity of qualitative risk of bias assessment and cite ROBINS-I to say that risk of bias is hard. Note that this will apply  -->
-
-A key issue in this analysis is t
-
-As observed from Figure \@ref(@) in the bias-adjusted analysis, the Ostergaard _et al._ 2017
+A further issue in this regard is that rigourness of the tools may not be equivalent.
+This issue can be illustrated by the Ostergaard _et al._ study[@ostergaard2017] having low risk of bias across all domains and thus receiving a substantial proportion of the weight in the first case study (Figure \@ref(fig:fpLdlAd)).
+While the RoB suite of tools (RoB 2.0, ROBINS-I, ROBINS-E) were developed by an expert working group and have been widely used, the Mamluk _et al._ tool[@mamluk2020] used to assess risk of bias in Mendelian randomisation studies was designed by the authors for use in their own review.
+If the Mamluk tool is failing to adequately assess bias in Mendelian randomisation studies, then any analysis based on its assessments is likely to be subject to bias.
+This observation is particularly problematic given the default position of the ROBINS-I and ROBINS-E tool to require a "Moderate" judgement in the confounding domain.
+Under these conditions, it is possible that a well performed cohort study (low risk of bias across everything other that bias due to confounding) will be down-weighted versus a potentially poor MR study.
 
@@
 As illustrated in Table \@ref(tab:robLevelsMapping-table), studies at critical risk of bias were not included in the analysis.
+While this is in line with best practice, there is theoretically no reason why studies with this extent of bias could not be included in the propsed framework.
+However, the estimation of an appropriate prior distribution for the effect of "Critical" bias would be substantially more challenging, and so was avoided here.
 
-one potential limitation of the  - however, the estimation of an appropriate adjustment value for these studies would be substantially more challenging.
-
-In any case, it represented a small number of studies.s
-
-A further issue is the "Low" risk of bias domain.
-In this proof-of-concept analysis, I assumed that domains at "Low" risk of bias did not require any adjustment.
-However, "Low" risk of bias is not equivalent to the absence of bias, and potentially should still be adjusted for.
-In this case, defining the predicted direction of bias would be challenging in the absence of obvious sources of bias (particularly given how challenging it can be when sources of bias are evident within a domain).
+A related issue is the "Low" risk of bias judgement.
+In this analysis, I assumed that domains at "Low" risk of bias did not require any adjustment.
+However, "Low" risk of bias is not equivalent to the absence of bias, and potentially should still be adjusted for, if only minimally.
+In this case, defining the predicted direction of bias would be particularly challenging in the absence of obvious sources of bias.
 
@@
 
-### Strenghts
+#### Combination of different effect measures
 
-This approach has a number of advantages. One of the key ones is modifying distributions of each level of bias could be defined _a priori_ in contrast to the .
+A final limitation to this analysis is the synthesis of different effect estimates.
+As discussed in Section \@ref(hold), hazard ratios are not directly comparable to odds ratios, as they inherently account for person time-at-risk.[@mckenzie2019] As non-randomised studies (NRSI/NRSI) of dementia outcomes report hazard ratios and Mendelian randomisation studies report odds ratios, the resulting synthesis may be biased by the integration of these two different effect measures.
 
-In addition, the generalised framework will allow for future researchers to apply (see Section \@ref())
+__[Note: I would be particularly interested in your feedback here.
+It seems quantitative triangulation will frequently require integration of different effect measures if comparing e.g.
+NRSI reporting hazard ratios with MR reporting odds ratios.
+How should this be handled?]__
 
-Appreciation that both the risk of bias and indirectness of a result should be assessed is growing.
-Indeed, some existing risk of bias for the assessment of diagnostic test accurary[@whiting2011a] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
-<!-- TODO Cite PROBAS and QUADAS --> <!-- TODO CITATION NEEDED cite paper that shows that ROB is not being intergrated into synthesis --> The approach proposed here will capitalise on this, providing users of domain based tools with a further avenue by whih to incorporate the results of their risk-of-bias assessments quantitatively.
+&nbsp;<!----------------------------------------------------------------------->
 
-Additional if users are interested in only a summary of the evidence rather than assessing results in relation to a target question, then internal biases can be adjusted for on their own by setting the indirectness distributions to $N(0,0)$.
+### Strengths
 
-The extent of a bias in a domain is unlikely to map accurately across the same domains in different studies, which
+The core strength of this analysis is that it is based on a comprehensive systematic review, supplemented by two additional primary studies to fill in the identified evidence gaps.
+In general, triangulation of any sort should be considered a natural extension of evidence synthesis, and therefore should follow best practice in relation to finding and critically assessing all relevant information.
+Additionally, the approach presented here also builds on recent developments in bias assessment to "explode out" the component results of a meta-analysis, and consider the effects of bias/indirectness in each separately.
 
-It for this reason that in previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process using a panel of methodologists and topic experts.[@thompson2011; @turner2009; @wilks2011] However, this approach is potentially subject to misclassification of the impact of bias on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
+A further advantage of this method comes from the ability to specify the prior distributions for each level of bias/indirectness in advance of performing the assessments.
+In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process using a panel of methodologists and topic experts.[@thompson2011; @turner2009; @wilks2011] However, this approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
 As an illustrative example, if experts are influenced by the knowledge of the effect estimate in a study, then a result demonstrating a stronger protective effect may receive greater modification than a study at the same "risk" of confounding but with a more modest effect.
 This is likely to be part where experts have preconceived ideas about the true effectiveness of the intervention.
+In this case, separating the assessment of bias/indirectness from the assignment of modifying values to each judgement will limit the potential for this misclassification.
+Using the framework proposed, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016]
 
-In this case, separating the assessment of bias from the assignment of modifying values to each level of bias will limit the potential for.
-Alternatively, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016]
+Finally, accounting for bias using an incorrect prior distribution is no less problematic that synthesising and drawing conclusions from effect estimates as if they were unbiased, a common occurrence in systematic reviews.[@katikireddi2015] While this analysis may be limited by the absence of empirically-derived adjustment distributions, it at the very least acknowledges the uncertainty of evidence due to bias/indirectness via a reduction in precision.
 
@@
 
-As the need and appetite for synthesis of different sources of evidence (trials, non-randomised studies, etc.), future iterations of the risk of bias tools should take this into account.
-Simple steps like harmonising the risk of bias levels across tools would be a good first move towards a more integrate suite of tools.
-Similarly, software that implements the risk-of-bias tools should both allow for direction of bias question and carefully consider how this data will be exported.
+An obvious avenue for future work in relation to quantitative triangulation is the identification of empirical prior distributions for the effect of bias/indirectness in non-randomised studies using meta-epidemiological approaches.
+This will be substantially more challenging than examining the effect of bias in RCTs,[@savovic2018] given the absence of an underlying database of meta-analysis of non-randomised studies.
 
-While the limitations inherent to this method are important, and limit the , they reflect a more detailed appreciation of the complexities of risk of bias assessment and triangulation as whole (i.e.
-not applying expected directions of effects to an entire category of studies ).
+Future development of this framework should also account for bias at the analysis level in terms of missing evidence.[@zotero-15123] For example, there is at least one known study relevant to the vascular dementia case study that reported a non-significant result but provided insufficient details to be included in the analysis.[@chiang2007] Ideally, a quantitative triangulation framework would further account for this proportional meta-bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
 
-This approach also builds on existing approaches employed previously by "exploding out" the results of a systematic review/meta-analysis and considering the effects of bias in each individual result separately.
-This more granular approach is to be preferred over assigning a bias judgement and direction to the summary effect produced by a meta-analysis,  which may mask the different biases applicable to each unique result.
-
-A key example of a useful future study in this domain would be the mining of maximally adjusted vs.
-unadjusted estimates from abstracts from primary studies to assess the impact of insufficient confounding by topic.
-However, these datasets could also be built from systematic reviews of a topic, as they would already be gruped by reserach domain and provided the risk of bias data is shared, provide a ready source of information
-
-In the mean time, the extent of the impact of knowledge of the results could be analysed using existing data.
-For example, a re-analysis of the data presented in a recent paper where both expert elicitation and structured
-
-Future research could and should also take into account bias at the analysis level in terms of missing evidence.
-For example, the set of previously published NRSE included in the case study were found to be at high risk of bias from missing evidence (see Figure \@ref(fig:lipidFractionsAD) in Chapter \@ref(sys-rev-results-heading)).
-Ideally, a quantitative triangulation framework would further account for this proportional evidence-level bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
-
-<!-- QUESTION - Can you meta-analyse meta-analysis results?
-As in, have a two-stage approach where you pool by evidence source, investigate bias at analysis level within evidence source, adjust these within-evidence-source results for ROB_ME bias, then pool them for final estimate?
--->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Triangulation as an extension of evidence synthesis
-
-Triangulation, both qualitative and quantitative, should be considered an extension of evidence synthesis, and so.
-Triangulation exercises should be based on comprehensive systematic reviews to create.
-If needed, evidence gaps can be addressed through additional studies, as in the case of this analysis,
-
-Compare and contrast with the nice example presented in the triangulation paper - realities of non-exemplars is that it is very hard to get this right.
-Also highlight the issue with assigning a direct of bias in many studies
-
-I hope this presents step forward in how researchers think about and visualise triangulation at the result level, rather than simply saying that certain evidence sources a
+Appreciation that both the risk-of-bias and indirectness of a result should be assessed is growing.
+Indeed, some existing for the assessment of diagnostic test accuracy[@whiting2011] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
+Future iterations of the core risk-of-bias tools (RoB 2, ROBINS-I, ROBINS-E) could take this into account, though there is an competing argument that indirectness is already handled via tools such as the GRADE framework.[@guyatt2011] In addition, simple steps like harmonising the risk-of-bias judgements across tools and making the direction of bias question mandatory (even if users default to "Unpredictable") would represent an improvement in the tools and encourage users to think about how the biases assessed affect the corresponding result.
+Similarly, software that implements a risk-of-bias tool should allow for direction/extent of bias question and carefully consider how this data will be exported.
 
@@
 There are two key outputs from this project.
-The first is the `trinagulate` R package.
-Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.
-This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
-The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, calculation of bias/indirectness-adjusted estimates for each result, and synthesis these adjusted results in a standard random-effects meta-analysis.
-All meta-analyses conducted within the package are implemented using the `metafor` R package.
-<!-- TODO CITATION NEEDED and cite in Sys rev chapter too!
--->
+The first is the `triangulate` R package.
+Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(?), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
 
-Generalised version of code, allowing for different distributions in each domain of bias (which will be handy once we get a better idea of what they should be).
-
-Annotated example dataset for the LDL-c/Alzheimer's disease causal question is the second key output.
-Available via the `triangulate` package, this data will give developers of new triangulation methods an example dataset on which to test developments, something which seriously hindered development of this project.
-This also ties with the idea of open data that has been a consistent theme throughout this thesis.
-
-An additional note is that without the open data sharing of the by-assessor elictation data from, which i sued in this analysis to frame the modifying values assigned to
+The second key output is an annotated example dataset for the LDL-c/Alzheimer's disease causal question addressed in this chapter.
+Available via the `triangulate` package, this data will provide developers of new triangulation methods with an example dataset on which to test new tools, something which seriously hindered development of this work.
 
@@
 
-## Conclusion
+## Summary
 
-Triangulation is a promising developing field, somewhat hamstrung by the limited understanding of the impact of biases at the meta-epidemiological level.
+* In this chapter, I narratively described the evidence identified or produced in previous chapters, and highlighted the issues with a qualitative approach to triangulation when there are several sources of evidence.
 
-In this chapter, I have presented a new method of visualising both the level and expected direction of bias inherent to each result, and suggested how this could be incorporated with a bias-adjusted meta-analysis approach to work towards a generalised quantitative triangulation framework.
+* I then illustrated a proposed generalised framework for quantitative triangulation, exploiting existing methods in evidence synthesis and recent developments in the assessment of different risks of bias.
+I illustrated this method using two case studies: the effect of mid-life LDL-c on Alzheimer's disease, and the effect of mid-life triglycerides on vascular dementia.
 
-Finally, I've highlighted the limitations of this method, as the correct distributions of modifying values in each risk-of-bias domain should be driven by meta-epidemiological studies which do not yet exist, framing them as opportunities for future research.
+* I discussed the limitations of this proposed method, given the absence of informative priors for the impact of bias/indirectness, and proposed future research (i.e.
+meta-epidemiological studies) that would address them.
 
-This chapter has demonstrated a repurposed framework for quantitative triangulation, exploiting existing methods in evidence synthesis and developments in the assessment of different risks of bias.
-
-Future quantitative triangulation should move beyond the concept of comparing results at the approach level, and instead focus on the inherent threats to the internal validity and directness of each specific result relevant to the causal question.
-While this makes the process both more labour intensive and complex,
-
-It also introduce a new way to visualise the biases at work in a particular result, rather than making assumptions about the type and directions of bias at the study design level as suggested by previous work on this topic.
-
-Finally, it highlighted the limitations of current methods for triangulation in the absence of informative priors for the impact of biases across the
-
-The implications of the synthesised work of this thesis presented in this chapter to clinical practice, public health and future research is considered in the following chapter.
+* In summary, quantitative triangulation is a promising field that should be considered a natural extension of evidence synthesis.
+The implications of the synthesised evidence presented here to clinical practice, public health and future research is considered in the following chapter.
 

### 2021-11-23 R/forest tri.R

@@ -50,7 +50,7 @@ if (is.null(arg$at)) {
   x_adj <- arg$at[3]
 }
 
-if (is.null(arg$at)) {
+if (is.null(arg$x_min)) {
   x_min = -10
 } else {
   x_min <- arg$x_min
@@ -136,7 +136,7 @@ forest(x = dat$yi,
        rows=rows,
        textpos = textpos,
        mlab = "",
-       header="Author(s) and Year", 
+       header="Author(s) and Year",
        ...)
 
 ### set font expansion factor (as in forest() above) and use a bold font

### 2021-11-23 R/helper.R

@@ -725,6 +725,7 @@ get_citations_per_analysis <- function(data){
     mutate(citation = paste0("@",citation)) %>%
     pull(citation)
   
+  citation_vec<- citation_vec[which(citation_vec != "@NA")]
   
   paste0("[",paste0(citation_vec,collapse = "; "),"]") %>%
     return()

### 2021-11-23 01-Chp-Background.Rmd
End of day:
Citations fixed!

@@
 \minitoc <!-- this will include a mini table of contents-->
+
+<!-- TODO Contributor statements -->
 
@@
 
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013diagnostic] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
+Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
 
@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013diagnostic]
+(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013]
 
@@
 
-One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013diagnostic] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
+One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
 
@@
 Cause-specific criteria exist for the diagnosis of dementia sub-types.
-For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993vascular]
+For example, the NINCDS-ADRDA criteria are commonly used to assess patients for Alzheimer's disease,[@dubois2007] while vascular dementia is diagnosed using the NINCDS-AIREN criteria.[@roman1993]
 
@@
 In 2015, the estimated total cost of dementia in England was £24.2 billion.
-Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014dementia]
+Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014]
 
@@
 
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016a] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
+Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
 
 The benefits of a prevention-based approach based on addressing these risk factors are well-studied.
-Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020association] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
+Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
 
-In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019a] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
+In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
 
@@
 ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016a; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+rosuvastatin 80 mg/day).[@collins2016; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
 
@@
 
-Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004new] and omega-3-fatty acids,[@skulas-rayannc.2019] but they far less effective in LDL-c lowering than the therapies described above.
+Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004] and omega-3-fatty acids,[@skulas2019] but they far less effective in LDL-c lowering than the therapies described above.
 
@@
 Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005a; @mainous2005; @mielke2010; @tan2003a] or a reduced susceptibility [@mielke2005; @reitz2004a].
-With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004a], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004a; @moroney1999]
+In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005; @mainous2005; @mielke2010; @tan2003] or a reduced susceptibility [@mielke2005; @reitz2004].
+With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004; @moroney1999]
 
-Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020c] on dementia outcomes have been performed.
+<!-- Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020] on dementia outcomes have been performed.
 However, these reviews have several limitations.
 Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018b] or used an outdated assessment tool.[@anstey2015;@poly2020c]
+Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018] or used an outdated assessment tool.[@anstey2015;@poly2020c] -->
 
@@
 
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016a] are in fact trials of statins for the prevention of coronary related outcomes.
+However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary related outcomes.
 
@@
 As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
-The second trial, the Medical Research Council/British Health Foundation Protection Study,[@2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
+The second trial, the Medical Research Council/British Health Foundation Protection Study,[@heartprotectionstudycollaborativegroup2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
 
@@
 
-Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
 Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016b]
+Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016]
 
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017c; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
 This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]
@@
 
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018a] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
+Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
 
@@
 Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020a] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020preprinting] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
 One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
-Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021a; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
+Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
 
@@
 However, each method is limited by its own biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016a] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016a] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
+Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
 A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
@@
 Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@Pagen71; @sterne2019a; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
+[@Pagen71; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
 
@@
 
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017a; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018a] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
+Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
 Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]

### 2021-11-23 02-Chp-Systematic-Review-Tools.Rmd
End of day:
Citations fixed!

@@
 Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018a;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
+At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
 As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
@@
 The tool has been well received by the community (as of `r date`, `medrxivr` has been downloaded more than `r medrxivr_downloads` times), and several use cases have been reported.
-It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020c]
+It has been used to investigate the role of preprints in the response to the 2019 coronavirus outbreak,[@kodvanj2020] perform searches of preprints as part of a systematic review,[@noone2020; @grassly2020] and examine how data-sharing behaviour is affected by journal policies (see \@ref(thesis-output)).[@mcguinness2020DAScomparison]
 
-The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020a] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
+The package has been accepted into the rOpenSci suite of packages, a collection of "carefully vetted, staff- and community-contributed R software tools that lower barriers to working with scientific data sources on the web".[@boettiger2015] As part of this process, following rigorous peer-review, an associated article introducing the tool was published by the Journal of Open Source Software.[@mcguinness2020medrxivr] The entire review discussion is publicly available and can be viewed online.[@zotero-15016] The tool has also been well received by the open-source community, demonstrated by the engagement of other developers in contributing to important new functionality and suggesting bug-fixes.
 
@@
 allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019b] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019popularity] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
 
@@
 
+<!-- TODO EMBASE will index medRxiv/bioRxiv from Christmas - need to make a note of this somewhere -->
+
 &nbsp;
@@
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019b; @mckiernan2016c] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@rbiorxiv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016c] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019; @mckiernan2016] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@fraser2020rbiorixv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 

### 2021-11-23 03-Chp-Systematic-Review-Methods.Rmd
Citations fixed!

@@
 <!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
+<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017] -->
 
@@
 The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020a] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
+As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
 The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
@@
 
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002a] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
 Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
@@
 In many cases, estimates were know to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
-These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009; @yamada2009a] In addition, some authors stated outright that non-significant results were not reported (e.g.
+These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
 "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
@@
 
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018a; @kuzma2018a] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
 The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
@@
 This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017b] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
+As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
 The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
@@
 In all cases, excluding these variants attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017a]
+A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017comment]
 
@@
 Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
-Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019b] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
+Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
 

### 2021-11-23 05-Chp-CPRD-Analysis.Rmd
End of day:
Citations fixed!

@@
 
+<!-- TODO text -->
+
 <!-- Include the early analysis we did here, that did not work as a result of limited scope.
@@
 Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006using] Using the MICE (Multiple Imputation by Chained Equations) command in STATA16, 20 imputed datasets were created.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006] Using the MICE (Multiple Imputation by Chained Equations) command in STATA16, 20 imputed datasets were created.
 
@@
 
-Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001review] where participants missing any covariate are dropped from the dataset.
+Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001] where participants missing any covariate are dropped from the dataset.
 As a recommended sensitivity analysis,[@hughes2019] I preformed and compared the results of both methods, to investigate the impact of multiple imputation on the results.
@@
 
-Despite observational analyses suggesting a link between statins and muscular pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016a] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
+Despite observational analyses suggesting a link between statins and muscular pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
 This suggests that muscular backpain would be suitable for use as a negative control outcome in this analysis.
@@
 Similarly, incident ischemic heart disease and Type 2 diabetes were included as a protective and harmful positive control outcome, respectively.
-The protective effect of lipid-lowering treatment, via statins, on the risk of ischemic heart disease is well-established, [@collins2016a] while there is growing evidence for an increased risk of Type 2 diabetes with statin use.[@collins2016a; @macedo2014; @smit2020] Similar to the negative outcome, if the analysis strategy can reproduce these known associations, this will provide evidence that potential confounders have been sufficiently adjusted for.
+The protective effect of lipid-lowering treatment, via statins, on the risk of ischemic heart disease is well-established, [@collins2016] while there is growing evidence for an increased risk of Type 2 diabetes with statin use.[@collins2016; @macedo2014; @smit2020] Similar to the negative outcome, if the analysis strategy can reproduce these known associations, this will provide evidence that potential confounders have been sufficiently adjusted for.
 
@@
 A review of other available literature suggests that this observation (a harmful effect of lipid-regulating agents on vascular-related outcomes) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in this analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013b] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in this analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
 
@@
 However, the findings of this analysis are subject to several limitations in addition to the confounding by indication discussed above.
-There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014dictionary] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
 Further, there is a potential for general non-differential misclassification of the outcome due to the varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
@@
 The raw data supporting this analysis is not publicly available, as access to the CPRD data is controlled by a data monitoring committee.
-However, when data are not readily available, sharing the analysis code and summary statistics represents a way for readers to validate the findings.[@goldacre2019c]
+However, when data are not readily available, sharing the analysis code and summary statistics represents a way for readers to validate the findings.[@goldacre2019]
 
@@
 The presence of bias is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of dementia outcomes with a vscular component.
-Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013b]
+Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013]
 

### 2021-11-23 06-Chp-IPD-Analysis.Rmd
Citations fixed!

@@
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on patient age and sex.[@ancelin2013; @mielke2010a] While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+Previous work has suggested a difference in the effect of lipids on dementia risk based on patient age and sex.[@ancelin2013; @mielke2010] While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
 However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of patient characteristics in those that did.
@@
 
-Across all cohorts, data cleaning was performed in a similar manner, standardising to commonly named variables so that a single model could be applied using functional programming.[@wickham2016a] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+Across all cohorts, data cleaning was performed in a similar manner, standardising to commonly named variables so that a single model could be applied using functional programming.[@wickham2016func] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
 Following data cleaning, summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process, in line with best practice.[@levis2021]
@@
 
-In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.[@fisher2017a] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
 All interaction analysis were performed using the common-set-adjusted model (Model 1).
@@
 
-A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.[@nevitt2017a] However, it is assumed that a ~10% response rate is at the lower end of the scale.
+A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.[@nevitt2017] However, it is assumed that a ~10% response rate is at the lower end of the scale.
 
 There are likely several likely reasons for this low response rate to requests for data access.
-In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy and "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017a] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
+In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy and "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
 The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other COVID-related work.

### 2021-11-23 07-Chp-Triangulation.Rmd
Citations fixed!

@@
 results.
-I extracted the overall effect estimates, along with measures of heterogeneity in each case ($\tau^2$, $I^2$).[@higgins2003; @higgins2008b]
+I extracted the overall effect estimates, along with measures of heterogeneity in each case ($\tau^2$, $I^2$).[@higgins2003; @higgins2008]
 
@@
 However, the prior distributions defined here are broadly comparable to previously reported estimates of the impact of bias in non-randomised trials.
-For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021a] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
+For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
 
@@
 A further issue in this regard is that rigourness of the tools may not be equivalent.
-This issue can be illustrated by the Ostergaard _et al._ study[@ostergaard2017] having low risk of bias across all domains and thus receiving a substantial proportion of the weight in the first case study (Figure \@ref(fig:fpLdlAd)).
+This issue can be illustrated by the Ostergaard _et al._ study[@ostergaard2015] having low risk of bias across all domains and thus receiving a substantial proportion of the weight in the first case study (Figure \@ref(fig:fpLdlAd)).
 While the RoB suite of tools (RoB 2.0, ROBINS-I, ROBINS-E) were developed by an expert working group and have been widely used, the Mamluk _et al._ tool[@mamluk2020] used to assess risk of bias in Mendelian randomisation studies was designed by the authors for use in their own review.

### 2021-11-23 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-<!-- Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
-
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
@@
 
-<!-- ## Additional ideas -->
-
-<!-- One of the problems I'll point out with the trials in the systematic review chapter (Chapter \@ref(sys-rev-heading)) is that they only included people with a high cardiovascular risk - we are kind of doing the same by using elevated test cholesterol results as the index event.
--->
-
-<!-- Might be able to get around this by pointing out that you need some index event to be able to do this analysis (?) -->
-
-<!-- __Things we tried__ -->
-
-<!-- - Conditioning entry to the cohort on QRISK score (as defined by codes) rather than by .
-Need to be able to demonstrate here that not many meeting our original entry criteria actually go on to have a statin quickly.
-Need total number of those starting and average time to start.
--->
-<!-- - Positive controls. Need to be able to explain why these controls have such wildly increased results. Cross-reference these results with the Hernan paper. -->
-<!-- - Competing risk analysis, with death as a competing risk. Need numbers of deaths in each group, and preliminary results -->
-<!-- - Allowing for time-varying confounders for binary covariates. -->
-
-<!-- __Things we could try__ -->
-
-<!-- - Work through data using positive control to see if the way it is being added is what is causing the issues. -->
-<!-- - Examine Cramer et al. thesis and see what they did -->
-<!-- - Marginal structural models approach (a la J. Sterne) -->
-
-<!--------------------------------------------------------------------------->
-
-<!-- TODO Check all fig/table cross-references evaluate -->
+<!--------------------------------------------------------------------------->
 
@@
 Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standardised coding system.
-These databases have several advantages over traditional methods of data collection, including the number of people they contain and the length of time for which participants are followed.
+These databases have several advantages over traditional methods of data collection, including the number of people they contain and the relatively low cost of data collection via routine care.
 This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
@@
 
-Little evidence for an effect of lipid-regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipi-regulatin agent called fibrates.
+Little evidence for an effect of lipid-regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
 In contrast, I found an increased risk of vascular and other (i.e.
@@
 Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia as identified by the systematic review.
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] This approach provides a evidence source at risk of a distinct bias due to the alternative analytical strategy.
+Specifically, this involved a concerted effort to address immortal time bias though use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] By employing this approach, the analysis provides an evidence source at risk of a distinct bias.
 The results from this analysis will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
@@
 
-<!-- TODO, ensure code list position is accurately documented in  -->
+<!-- TODO ensure code list position is accurately documented in Appendix -->
 
@@
 
-This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data.
+This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data (as defined by the CPRD).
 Records pre-dating the 1995 cut-off were included in the original CPRD extract obtained for this analysis.
@@
 The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: (a) an outcome of interest; (b) death; (c) end of follow-up (29 February 2016); (d) last registration date with their GP practice; or (e) the last CPRD collection date for their practice.
-Participants were ineligble for our cohort if they were less than 40 years of age (as these patients are are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+Participants were ineligible for our cohort if they were less than 40 years of age (as these patients are  less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
 had less than one full day of follow-up).
@@
 
+<!-- TODO Need to deal with the fact that the ordering is not accounted for, which could be critised -->
+
 <!----------------------------------------------------------------------------->
@@
 (ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model.
-The codelists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
+The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
 
@@
 Demographic covariates adjusted for included age and gender.
-Age was calculated at date of entry into the cohort, and adjusted for via its use as the time axis for the Cox model (see Section \@ref(cprd-time-axis)).
+Age in years was calculated at date of entry into the cohort, using the 1st of January of a patients' birth year (the exact date of birth was not provided by CPRD), and was adjusted for via its use as the time axis for the Cox model (see Section \@ref(cprd-time-axis)).
 Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
@@
 In addition to adjusting for these covariates individually, a Charlson co-morbidity index (CCI) score was calculated for each participant.
-The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
-
-Codelists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
+The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] The conditions considered under the index are: AIDS; cancer; cerebrovascular disease; chronic pulmonary disease; congestive heart disease; dementia; diabetes; diabetes with complications; hemiplegia; metastatic tumour; mild liver disease; moderate liver disease; myocardial infarction; peptic ulcer disease; peripheral vascular disease; renal disease; and rheumatological disease.
+Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
+
+code lists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
 
@@
 The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] Following the example displayed in the figure, the unexposed group are followed from the date of a diagnosis, while the exposed group is followed from date of a prescription.
-In this scenario, the time between diangosis and prescription for the exposure group is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
+In this scenario, the time between diagnosis and prescription for the exposure group is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
 
@@
 
-(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panal B).
+(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panel B).
 
@@
 
-This analysis attempted to address this issue by following all participants from a common index date (defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemeia diagnosis; or (c) LRA prescription).
+This analysis attempted to address this issue by following all participants from a common index date (defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemia diagnosis; or (c) LRA prescription).
 Following a recommended approach to addressing the second form of immortal time bias, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
@@
 
-As detailed in the introduction, the properties of statins may be important in their effect based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] To investigate this, I further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Comparing dementia codelists
-
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a published study by Smeeth _et al_.[@smeeth2009]
+As detailed in the introduction, the properties of statins may be important in their effect based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] As such, I expected that any effects of statins on dementia outcomes would be stronger in the lipophilic as compared to the hydrophilic statin subgroup.
+To investigate this, I further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Impact of using different code lists for defining dementia outcomes
+
+As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a published study by Smeeth _et al_.[@smeeth2009] The intended purpose of this analysis was to assess the robustness of my results to the choice of code list.
 
@@
 These models were used to estimate the impact of adjustment for additional covariates.
-Note that obtaining an completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
+Note that obtaining a completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
 
@@
 (ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
+Note that the x-axis cutoffs (.5,2) are different compared to other plots (0.3,3) to enable greater comparison between the different models.
 
@@
 
-On the assumption that this variation could be caused by changes in the frequency of codes used to define probable AD in the cohort, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
+On the assumption that this variation could be caused by changes in the frequency probable AD diagnoses in the cohort over time, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
 While the frequency of outcomes declines in more recent strata, likely due to the limited follow-up inherent to these groups, this decline in frequency is relatively constant across the dementia subtypes.
@@
 In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
-Additionally, there is evidence for a increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
+Additionally, there is evidence for an increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
 
@@
 
-#### Impact of dementia code lists {#comparing-codelists}
+#### Impact of dementia code lists {#comparing-code lists}
 
@@
 When using the Smeeth _et al._ code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's ("other") dementia outcomes, respectively.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!-- TODO Could include part here on the propensity score analysis trimming, and the fact that trimmming using the co-variates that we had access to  -->
-
-<!-- TODO Can also discuss the fact that off-target effects are much easier to get an accurate answer from as they are not as suceptible to confounding by indication -->
+While direct mapping to the outcomes used in this analysis was not possible, the most comparable are probable Alzheimer's disease (`r probad_text`) and other dementia (`r othdem_text`).
+
+&nbsp;<!----------------------------------------------------------------------->
 
 ## Discussion
-
-<!-- QUESTION To what extent should I cross-reference with the other literature here? -->
 
@@
 
-<!-- TODO Need to discuss fibrate results as part of qualitative triangulation -->
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 ### Interpretation of results
-
-<!-- IDEA Could include some text here about how you are more likely to get an accurate result when looking at off-target effects -->
 
@@
 
-__[Feedback requested: How much should I be cross-referencing with the systematic review at this stage?
-Or should I keep it self-contained, and then provide a comparison across the review/CPRD/IPD analyses as the first part of the triangulation chapter?]__
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 #### Confounding by indication
-
-<!-- IDEA Cite study/paper mentioned by GDS about getting better estimate for effect when dealing with off-target outcomes -->
 
@@
 While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] it is used here to described the role of risk factors that both prompt treatment and increase the risk of the outcome, thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015] In the context of this analysis, the confounding variable (or, more likely, variables) would prompt prescription of statins but also represent a vascular risk factor that contributes to the development of the vascular dementia.
+In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015] In the context of this analysis, the confounding variable (or, more likely, variables) would prompt both prescription of statins and also represent a vascular risk factor that contributes to the development of the vascular dementia.
+A similar confounding structure likely exists for ezetimibe, another hypercholesterolemia treatment, providing an explanation for the association of vascular/other dementia but not Alzheimer's disease with this exposure.
 
@@
 Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-The slight harmful effect for the backpain outcome is substantially smaller that that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+The slight effect observed for the negative control of backpain could be due to incomplete control for socioeconomic status, as deprivation data was provided in twentiles to preserve patient privacy.[@boruzs2016; @ikeda2019]
 
@@
 
-Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)), the unexpected increase in vascular dementia risk with statin use is particularly interesting  It is possible that previous research encountered similar methodological issues to this analysis, and via a publication bias mechanism where unexpected or assumedly incorrect results are less likely to be published, the results from these analyses did not make it into the evidence base.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!-- #### Time period effect in probable Alzheimer's disease -->
-
-<!-- An expected explanation for the time period effect observed for the Alzheimer's disease outcome, where statins appear more protective in participants who entered the cohort at a later date, was an change in how different dementia sub-types were diagnosed over time.
-For example, if the observed trend was due to increasing differential misclassification with vascular dementia, then we would expect vascular dementia to appear increasingly harmful in more recent time periods which is not the case.
-However, when investigated via tabulation of dementia outcomes by grouped year of entry (Table \@ref(tab:diagnosisType-table)), no corresponding inverse trend is observed for any of the other dementia outcomes.
--->
-
-<!-- Similarly, the absence of  -->
+Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)), the unexpected increase in vascular dementia risk with statin use is particularly interesting.
+It is possible that this finding reflects publication bias if previous research encountered similar methodological issues to this analysis, and these results did not make it into the evidence base as unexpected or assumedly incorrect results are less likely to be submitted or accepted for publication.
 
@@
 
-An initial interpretation of the the different association observed in the two groups was that the lipophilic statins may be more potent, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
+An initial interpretation of the different associations observed in the two groups was that the lipophilic statins may be more potent, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
 However, the statin with the strongest lipid lowering effect that is available via the NHS, rosuvastatin, is hydrophobic.
 
-__[Yoav, are there are particular indications/contraindications for statins with different properties? And any general comments on the interpretation of these findings would be welcome!]__
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-TThis finding disagrees with the results of the original analysis, which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+This finding disagrees with the results of the original analysis, which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
 
@@
 This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
-Finally, it is one of the few that provide evidence on the association of lipid-regulating agent use and vascular and other dementias.
+Finally, it is one of the few that provide evidence on the association of lipid-regulating agent use and vascular and other dementias, and used negative and positive controls to assess the potential for residual confounding.
 
 However, the findings of this analysis are subject to several limitations in addition to the confounding by indication discussed above.
-There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contains prescriptions for lipid-regulating agents.
+There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contain prescriptions for lipid-regulating agents.
 Further, there is a potential for general non-differential misclassification of the outcome due to the varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
-<!-- though there is some encouraging evidence that a dedicated coding exercise increases the identification of dementia case in primary care database and does not add a substantial administrative burden.[@russell2013] -->
 
 Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code list can have on the analysis, as illustrated by the discrepancy between the results when using the codes lists defined for this study and those used by Smeeth _et al_.
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code lists can have on the analysis, as illustrated by the discrepancy between the results when using the code lists defined for this study and those used by Smeeth _et al_.
 This presents a particular challenge in comparing research across different time-periods and coding systems, particularly the unexpected results I obtained for the vascular and other dementias outcomes.
@@
 A further limitation stems from the possibility of uncontrolled confounding due to genetic factors.
-Number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+The number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
 I was unable to control for ApoE genotype in this analysis as I did not have access to genetic data on participants.
@@
 
-### Conclusions
-
-This chapter has provided new evidence on the association of lipid-regulating agents with incidence of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
-It made use of a large scale electronic health record database, the CPRD, and employed a time-varying Cox proportional hazards model to account for potential immortal time bias.
-
-It found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
+### Summary
+
+* In this chapter, I produced new evidence on the association of lipid-regulating agents with incidence of all-cause dementia, Alzheimer’s disease, vascular dementia, and other dementia.
+
+* I found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
 However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the statin subgroup, which comprised the majority of exposed participants in this cohort.
-
-This chapter attempted to account for important sources of bias and provide a comparison with other available literature, as identified in the systematic review presented in Chapter \@ref(sys-rev-heading).
-However, there is a strong potential for uncontrolled confounding by indication and differential misclassification of the outcome on the basis of exposure, which raises questions about the findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
-The presence of bias is supported by our findings for the negative and positive control outcomes used, which provide some evidence of uncontrolled vascular confounders that may both prompt LRA prescription and increase risk of dementia outcomes with a vscular component.
-Future research using large scale electronic health records should aim to address these limitations, potentially by using a analytical design that more closely emulates a trial.[@danaei2013]
-
-Regardless, this analysis has provided an additional source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
-In the following Chapter, the dataset described here is incorporated along with several other datasets as part of an individual patient data analysis to investigate the association of blood lipid levels with incidence of dementia outcomes directly, rather than via the proxy of lipid-regulating treatment.
+In all cases, the estimated associations were driven by those observed in the large statin subgroup.
+
+* I attempted to account for important sources of bias through use of time-varying treatment indicator, though the control outcomes included in the analysis provided evidence for only partially controlled confounding by indication related to vascular factors.
+Additionally, there was the potential for differential misclassification of dementia subtype on the basis of the exposure.
+Combined, these biases reduce the confidence in my findings, in particular the unexpected increase in risk of vascular dementia associated with statin use.
+
+* Findings from this analysis are used as an additional source of evidence in the triangulation exercise presented in Chapter \@ref(discussion-heading).
 

### 2021-11-23 08-Discussion.Rmd
Citations fixed!
End of day:

@@
 
-This chapter details the
+TBC
 
@@
 The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.
+In this discussion, I will review the role of each chapter in the broader thesis, summarise the principal findings and contributions of this thesis, and discuss the implications of my findings for both clinical and public health policy.
+I consider the overall strengths and limitations of this thesis as a coherent body of work, and suggest avenues for impactful future research based on my findings and experiences.
 
-In this chapter I will summarise the principal findings from my thesis, assess the unique contributions of this thesis to the field of research, discuss the implications for both clinical and public health policy, describe the overall strengths and limitations of this thesis as a whole, suggest avenues for impactful future research based on my findings and experiences.
+## Chapter summary
 
-In __Chapter \@ref(sys-rev-tools-heading)__ presents a new tool for the systematic searching of health-related preprints, and detail
+This thesis is comprised of a mix of informative, methodological and applied chapters.
 
-In __Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)__ describe the methods and results of a comprehensive systematic review of the relationship between blood lipids (and treatments that modify them) and dementia outcomes.
+In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in thie
 
-In __Chapter \@ref(cprd-heading)__ presents an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale
+In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints, and detail
 
-In __Chapter \@ref(ipd-heading)__ presents an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK.
+In __Chapters \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of the relationship between dementia outcomes and blood lipids (and treatments that modify them).
+The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
 
-In __Chapter \@ref(tri-heading)__ presents a narrative summary of the evidence identified and produced by the preceding chapters, and proposes a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.
+In __Chapter \@ref(cprd-heading)__, I describe an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale electronic health database.
+I make use of control outcomes to illustrate insufficiently controlled biases
+
+In __Chapter \@ref(ipd-heading)__, I present an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK to add to the evidence base on the association of blood lipids and dementia outcomes.
+
+Finally, in __Chapter \@ref(tri-heading)__ I propose a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.
+I illustrate the method by considering two causal questions (LDL-c and Alzheimer's disease; triglycerides and vascular dementia), drawing on the evidence identified or produced by previous chapters.
 
@@
 
-## New evidence produced
+## Summary of principle findings
 
-Since the systematic review was performed, there have been some notable further analysis related to the central thesis question here.
+Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).
+
+While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
+However, this equally may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering.
+However, this observed effect could also be due to reporting biases, a
+
+The inclusion of preprints
+
+Statins were by far the most studied lipid-regulating agent in relation to dementia outcomes, a unsurprising finding given the large proportion of patients taking statins as indicated by my analysis of the CPRD data.
+
+The inclusion
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## New evidence
+
+Since the systematic review described in this thesis was performed, there have been two notable analysis of large cohorts performed related to the central thesis question here.
 Two of these are discussed here notable studies are discussed here.
 
-Found slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease [@iwagami2021].
-Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
+The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are n Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
 
@@
 
-In relation to the suggestion in this analysis that raised triglycerides were associated with an increasede risk of vascular dementia, a 2021 study in a  125,727 Danish participants found the moderate hypertriglyceridemia was associated with increased risk of non-Alzheimer's dementia (`r estimate(1.79, 1.16,2.87,"HR")`).[@nordestgaard2021]
+An analysis of 502,226 participants of the UK BioBank found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.6,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes.
+This is comparable to my findings.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Summary of contributions
+
+The research described in this thesis represents a number of novel contributions to the the fields of evidence synthesis
+
+With respect to dementia epidemiology, the systematic review reported in Chapters
 
@@
 
-As part
+As a reflective process throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing . here I present a more general rel
 
@@
 
-Additionally, in hindsight, I may have considered a mor. However, under the conditions of my grant, the scope for chang
+Additionally, in hindsight, I may have considered a more methodological thesis. The Chapter's I enjoyed working on the most (Chapters \@ref())
 
-As a reflective process throughout the PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)).
+Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors
+
+However, normal opportunities to tie people down in person were suspended during COVID.
 
@@
 
-The strengths a limitations of each component of this thesis are discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.
+The strengths a limitations of each component of this thesis have been discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.
 
-This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk.
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Strengths
+
+This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systemtatic manner, including diverse sources of evidence, inclu
 
@@
 
-It has analysed two previously unanalysed datasets, adding useful information to the evidence base.
+It has provided new evidence on an understudied condition (vascular demenita), analysing three previously unexplored datasets to provide evinde
+
+- New evidence sources for an under-studied condition
+- Development of new methods and tool
+
+One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Weaknessess
 
@@
 
-__Strengths__
-- New evidence sources for an under-studied condition
-- Development of new methods and tool
+A general limitation of this thesis is the absence of known results/data.
+This occurred in both the systematic review, via the selection of reporting results and potential for publication bias.
+It was also observed.
 
-__Weaknesses__
-A general limitation of this thesis is the absence of known results/data.
-This occured in both the systematic review, via the selection of reporting results and potential for publication bias.
-It was also observeed.
+Similarly, missing evidence was a common theme across this thesis.
+In Chapters \@ref(hold)/\@ref(hold), several studies stated that they did not report the results of an analysis because the results were not significant.
+This was particularly common among non-randomised studies of exposure examining blood lipids directly.
+Fortunately, new tools such as the forthcoming ROB-ME.
 
-These facts both potentially bias the summary associations observed here, in addition to weakening the precision of the estimates produced.
+Similarly, an absence of evidence on vascular dementia limits the certainty.
+In both these cases, accounting for missing evidence will be an important part of future evidence snythesis work on this topic.
 
-- Confounding by indication
+Missing evidence in the form of a poor response to data access requests was also observed in the IPD analysis reported in Chapter \@ref(hold).
 
-- A lot of UK based data
-
-There are several strengths and limitations to the work presented in this thesis.
-One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
-
-Need for large simple trials for common disease where small treatment effect can have large effect - [@yusuf1984]
-
-This thesis is limited by the low response rate to data access requests, and the
-
-The lack of large, precise studies made comparison across different types of evidence difficult, while the low number of eligible studies for a
+A final weakness of this thesis is the geographical focus. All primary analysis presented drew on data from the UK population (CPRD, CaPS, EPIC Norfolk, Whitehall II).
 
@@
 
-Across multiple sources of evidence, there was no consistent effect of blood lipids, or . Some
+The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
+Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
 
-The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence related to the
+However, even under the scenario that a strong protective effect was identified, whether or not to prescribed a statin at mid-life will always be guided by factors other than dementia prevention.
+Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early onset dementias), which is substantially less likely if hypercholesterolemia is left unchecked.
+
+However, while this thesis did not provide any evidence for a protective effect of lipid-lowering, it similarly did not provide any evidence for a harmful effect of statin exposure on dementia outcomes.
 
@@
 
-Patients must live to a sufficient age to be at risk of dementia outcomes, which is substantially less like if high lipid levels in mid-life.
-
-The role of lipid-lowering
-
-As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for Alzheimer's disease.
+As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for the condition.
 It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.
-
-However, based on the available evidence
-
-For other dementia outcomes,
 
@@
 ### Public health
+
+The absence of an effect of blood lipids on dementia outcomes is an unh
+
+However, future work
 
@@
 In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
-
-<!-- TODO Could he get it work, could he feck. -->
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
-
-## Public involvement and engagement {#disc-PPI}
-
-<!-- TODO May need to tone this down a little bit -->
-
-Involving and engaging the public and patients has been a central theme to this thesis. 
-Public engagement activities included
-
-Public involvement also steered the creation of the topic
-
 &nbsp;
@@
 
-Normalisation of inclusion of preprints in systematic reviews. Wider assessment of the evidence base that exists solely as preprinted literature ()
+Given the evidence that this thesis produced on the usefulness of including preprints, normalisation of inclusion of preprints in systematic reviews.
+Wider assessment of the evidence base that exists solely as preprinted literature ()
 
-Studying of factors which influence eventual publication would also help to identify the extent and strength of publication bias by providing a
+Meta-epidemiological studies examining the factors which influence eventual publication would also help to quantify the extent and strength of publication bias
 
 Preprints also represent a key opportunity to assess the impact of peer review on qualitative changes within
+
+Future work should also address how to handle discrepancies between the preprinted and published versions of a paper, particularly if the results are subtantially different between the two versions.
 
@@
 
-As discussed, there is an absence of evidence on vascular dementia across the evidence base, potentially driven (for NRSI) at the leasby a publication
+As discussed in an earlier section, there is an absence of evidence on vascular dementia across the evidence base
+
+Future work should aim to address this evidence gap.
 
@@
 
-This is particularly relevant given that there was some evidence for an association of hypertriglyceraecia with vascular dementia.
-Future research should explicitly examine this relationship as part o f wider exploration of vascular disease.
-
- <!-- TODO See notes from Pat/Emma on this -->
+This is particularly relevant given that there was some evidence for an association of hypertriglyceraemia with vascular dementia.
+Future research should explicitly examine this relationship as part of wider exploration of vascular disease.
 
@@
 
-### Viewing of Mendelian randomisation studies
+### Reviewing Mendelian randomisation studies
 
-As noted in Chapter \@ref(sys-rev-heading-results), evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.
+As noted in previous chapters, evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.
 
-A key issue arises from the lack of an established risk of bias tool, which adds uncertainty to the accuracy of risk-of-bias assessments which can influence future work based on them, as discussed in Chapter \@ref(7).
+A key issue arises from the lack of an established risk of bias tool, limiting future work that requires systematic risk-of-bias assessment, such as the triangulation framework presented in Chapter \@ref(hold).
 In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics.
@@
 
-The field of quantitative triangulation is one ripe for future work. In the first instance, guidance
+It is customary at this point to recommend that a large scale. However, based on the evidence described. In addition, logistical challenges in relation
 
-Finally, methods for the standardisation of meth
+In summary, there is a need to make better use of the existing evidence accounting for the
 
-Use of the real-world evidence approach needs to be traded off against the important limitations that t
+The field of quantitative triangulation is one ripe for future work.
 
-Talk about the problems with real world evidence, and highlight that even when using these techniques, you still don't get the correct answers.
+In the first instance, guidance
 
-Tie in with GDS comments on off-targets effect.
+Finally, accounting for bias (and indirectness, if considering causal effects rather than a summary of the literature) is essentially in the interpretation of published literature.
+While this can take many forms, from the stratification of forest plots by overall risk of bias level, to the or to the more advance bias adjustment approach detailed here, it is insufficient to draw clinical recommendations from meta-analysis that treat effect estimates as if they were unbiased.
 
@@
 
+The
+
+In addition, I have created
+
+and proposed a novel combination of existing methods in pursuit of a generalised quantitative framework.
+
 This thesis has made unique and novel contributions to the
@@
 Illustrating that commonly employed approaches to address
+
+Blood lipids

### 2021-11-23 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 ```{r, echo = FALSE, warning=FALSE, message=FALSE}
-
+source(here::here("R/helper.R"))
 knitr::read_chunk(here::here("R/appendix.R"))
@@
 
-<!-- TODO Need to include -->
-
-<!----------------------------------------------------------------------------->
-
-### Forest plots for lipid fractions {#lipid-fraction-forest-plots}
-
-<!-- TODO Need to add labels/captions to these -->
-
-<!----------------------------------------------------------------------------->
-```{r obsLipidsDementiaTC, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TC_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-```{r obsLipidsDementiaLDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_LDL_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-```{r obsLipidsDementiaHDL, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_HDL_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-```{r obsLipidsDementiaTG, echo = FALSE, results="asis", fig.pos = "H", out.width='100%'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Dementia_TG_.png"))
-```
-<!----------------------------------------------------------------------------->
-
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
+
 ### Amendments to protocol {#appendix-cprd-amendments}
+
+<!----------------------------------------------------------------------------->
+## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
+<!----------------------------------------------------------------------------->
+### Calculation of average adjustment from expert elicitation
 
@@
 
-failing to realise that the initial codelist used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
+Failing to properly scope the literature and correctly estimate the number of studies returned by the search
+
+failing to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
+
+<!-- TODO Include the early analysis we did here, that did not work as a result of limited scope.
+Could include some of the genetic work also.
+Will additionally need to put the relevant materials from the paper in the  -->
 
@@
 
-### Introduction
-
-Risk of bias assessment - evaluation of the internal validity of studies included in a systematic review - often forms a key part of the evidence synthesis process, particularly in the health sciences.[@cochranechpt7] A well-developed family of tools is widely used, which have in common the characteristic that they evaluate specific domains of bias rather being constructed as a checklist or a quantitative score.[@cochranechpt7] These tools include the RoB 2 tool for randomized trials,[@sterne2019rob] the ROBINS-I tool for non-randomized studies of interventions,[@sterne2016robins] the QUADAS 2 tool for test accuracy and the ROBIS tool for systematic reviews.[@whiting2011quadas] Within each bias domains a judgement is reached about the strength of the study in that regard: for example, the first domain in the Cochrane RoB 2 tool deals with bias arising from the randomization process.[@sterne2019rob] Accessible graphics summarizing the results of these domain-based risk-of-bias assessments are included in reports of systematic reviews.
-A convenient plot in many reviews is a "traffic light" plot, which tabulates the judgement for each study in each domain.
-For larger numbers of studies, when such a table become unmanageable, a popular alternative is a weighted bar plot, which show the proportion of information with each judgement for each domain.[@higgins2008assessing]
-
-Researchers can face a number of barriers in creating these plots.
-While some evidence synthesis platforms, such as Cochrane's Review Manager,[@cochrane2014review] are able to produce these visualizations, not all researchers use these systems to conduct their systematic reviews, and copying the risk-of-bias data into these systems simply to produce the plots is inefficient and error prone.
-Likewise, creating the figures by hand, through software such as MS PowerPoint or Adobe Illustrator, may lead to unintentional errors and require the plots to be redrawn during an update to the review.
-Additionally, while the field of evidence synthesis software has grown rapidly in recent years,[@marshall2015systematic] this growth has not been equally distributed across the different aspects of the systematic review process.
-For example, a recent review found several software offerings aimed specifically at the abstract screening stage of the review process,[@harrison2020software] but no similar time- and error-reducing tool has been proposed for visualizing the results of risk-of-bias assessments.
-
-Fortunately, tools such as R, RStudio and `Shiny` (an R package for building interactive web apps) have made it easier than ever to produce such a tool.[@rref; @rstudioref; @shinyref] Here, we present `robvis` (Risk Of Bias VISualiation),[@mcguinness2019a] an R package and `Shiny` web-app that allows users to create publication-ready risk-of-bias plots quickly and easily.
-Originally created for use with the major risk-of-bias assessment tools used in health research, the tool allows users to visualize the results from any domain-based risk-of-bias assessment or quality appraisal tool.
-
-The tool is open-source and available to use free of charge.
-Users can download a stable version of the R package from CRAN (<https://cran.r-project.org/package=robvis>); or access and contribute to the development version via GitHub (<https://github.com/mcguinlu/robvis>).
-
-### Development
-
-Development of `robvis` began in April 2019 at the Evidence Synthesis Hackathon (ESH), an event which brings together interested researchers, practitioners and coders to discuss and develop new open-source evidence synthesis technologies.
-Test versions of both the R package and the web app were made available in early June 2019, with attendees of the ESH and members of the Bristol Appraisal and Review of Research (BARR) group at the University of Bristol being invited to test the tool and provide feedback.
-This feedback, along with other feature suggestions from the wider evidence synthesis community captured via GitHub issues, was incorporated and the first release version of the package was uploaded to CRAN in November 2019.
-The tool has been well received and is beginning to be cited in the evidence synthesis literature.[@gibb2019consistent; @habadi2019prevalence; @veloso2020effectiveness; @simillis2020; @tanneru2020]
-
-### Installation
-
-A stable version of `robvis` is hosted on the Comprehensive R Archive Network (CRAN) and can be installed using:
-
-```{r, eval = FALSE}
-install.packages("robvis")
-```
-
-As development of `robvis` is ongoing, new features are often available in the development version some time before they appear in the stable CRAN version.
-The most recent development version can be install from GitHub using:
-
-```{r, eval = FALSE}
-devtools::install_github("mcguinlu/robvis")
-```
-
-### Usage
-
-`robvis` contains two main functions.
-The first, `rob_traffic_light()`, creates a traffic light plot by tabulating each study by each domain, providing a more detailed view of the results of the risk-of-bias assessment.
-The second, `rob_summary()`, creates a weighted bar plot showing the proportion of information with each judgement for each domain in the assessment tool specified.
-
-A worked example using these functions is outlined below, showing the ease with which risk-of-bias plots can be created using `robvis`.
-A detailed description of the additional options that can be used with each function is presented in Table \@ref(tab:robvisarguments)
-
-Using the example data set (`data_rob2`) which is built into the package and is presented in Table \@ref(tab:robdata) for reference, the traffic light plot shown in Figure \@ref(fig:trafficplot) is created using:
-
-<!-- TODO __NEED TO ADD DATA HERE!__ -->
-
-```{r, eval = FALSE}
-
-rob_traffic_light(data = data_rob2,
-                  tool = "ROB2",
-                  psize = 15)
-```
-
-```{r trafficplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias traffic light plot created using `robvis`", out.width = "100%", fig.align = "centre"}
-
-plotdata <- robvis::data_rob2
-
-tfplot <- robvis::rob_traffic_light(data = plotdata, "ROB2", psize = 5)
-
-robvis::rob_save(tfplot, 
-                 file = "figures/sys-rev-tools/example-rob-traffic-light-plot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-traffic-light-plot.png", auto_pdf = TRUE)
-```
-
-Similary, using the same data set, the summary barplot shown in Figure \@ref(fig:summaryplot) is created using:
-
-```{r, eval = FALSE}
-
-rob_summary(data = data_rob2,
-            tool = "ROB2", 
-            overall = TRUE)
-
-```
-
-```{r summaryplot, echo = FALSE, eval = TRUE, fig.cap = "Example risk of bias summary plot created using `robvis` and the example ROB2 dataset", out.width = "100%"}
-
-sumplot <- robvis::rob_summary(plotdata, "ROB2", overall = TRUE)
-
-robvis::rob_save(sumplot,
-                 file = "figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-knitr::include_graphics("figures/sys-rev-tools/example-rob-summary-barplot.png")
-
-```
-
-A list of arguments available to the two functions in robvis are shown in Table \@ref(tab:robvisarguments)
-
-&nbsp;
-
-```{r robvisarguments, echo = FALSE, eval = TRUE}
-
-arguments <- data.frame(stringsAsFactors=FALSE,
-              argument = c("data", "tool", "colour", "overall", "weighted",
-                           "psize"),
-     rob_traffic_light = c("\nX", "X", "X", "", "", "X"),
-           rob_summary = c("X", "X", "X", "X", "X", ""),
-           Description = c(
-"Defines the dataframe containing the summary (domain) level risk-of-bias assessments. See the text and Table 1 for the format expected by `robvis`",
-"Defines the risk of bias assessment tool used.
-The RoB2 (`tool=\"ROB2\"`), ROBINS-I (`tool=\"ROBINS-I\"`), and QUADAS-2 (`tool=\"QUADAS-2\"`) assessments tools are currently supported.
-Other tools can be visualised using the generic template (`tool = \"Generic\"`)",
-"Defines the colour scheme for the plot.
-The default is `colour = \"cochrane\"` which uses the \"Cochrane\" (red, yellow, green) colours, while a preset option for a colour-blind friendly palette is also available (`colour = \"colourblind\"`).
-Alternatively, users can specify their own colour scheme e.g.
-`colour = c(\"#f442c8\", \"#bef441\", \"#000000\")`",
-"Defines whether to include an additional bar showing the distibution of overall risk of bias judgements in the summary barplot figure. Default is `overall = FALSE`.",
-"Defines whether weights should be used to produce the summary barplot figure. Default is `weighted = TRUE`, in line with current Cochrane Collaboration guidance.",
-"Defines the size of the points in the traffic light plot. Default is `psize = 20`."))
-
-if(doc_type == "docx"){
-
-  knitr::kable(arguments,
-               escape = T,
-             caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-
-             col.names = c("Argument","rob_traffic_light()","rob_summary()", "Description"))
-
-} else {
-
-  knitr::kable(
-    arguments,
-    format = "latex",
-    booktabs = TRUE,
-    longtable = TRUE,
-    caption = "Description of the arguments available in the two main `robvis` functions. ‘X’ indicates that the option is available for the respective function.",
-    align = c("l", "c", "c", "l"),
-    col.names = c(
-      "Argument",
-      "rob_traffic_light()",
-      "rob_summary()",
-      "Description"
-    )
-  ) %>%
-    column_spec(4, "5cm") %>%
-    kable_styling(
-      font_size = 9,
-      bootstrap_options = c("striped", "hover"),
-      latex_options = c("repeat_header", "striped")
-    )
-}
-
-```
-
-&nbsp;
-
-### Reception and Future Plans
-
-```{r, echo = FALSE}
-robvisstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
-
-robvis_downloads <- format(plyr::round_any(sum(robvisstats$count),100, f = floor), scientific = FALSE)
-
-date <- format(as.Date("2021-12-01"),"%B %Y")
-
-```
-
-As of `r date`, `robvis` has been downloaded more than `r robvis_downloads` times.
-It has been well received but the systematic review community, and has been cited frequently in the published literature.
-A paper describing the tool was published in a special issue of Research Synthesis Methods focusing on data visualisation methods.
-A chapter on the tool has been incorporated in to the "Doing Meta-Analysis in R" online textbook.[@mathias_harrer_2019_2551803]
-
-While `robvis` is a stable package, a range of additional functionality could be added.
-At present, the number of tools with a specific template included in `robvis` is limited - adding additional templates is a priority.
-For example, a template for ROBIS, a tool for assessing risk of bias in systematic reviews, is in developement.[@whiting2016robis] Additionally, the tool does not yet allow for the production of paired forest plots, where the risk-of-bias judgement is presented alongside each specific result included in the meta-analysis.[@cochranechpt7] This was initially considered to be beyond the scope of the tool, as it involves the visualization of something other than risk-of-bias assessments.
-However, following user-driven demand, this functionality is in development and will be available in the near future.
-Finally, we would like to add similar functionality to that provided by the `metafor::reporter()` function, which generates a brief paragraph of text describing the results of a meta-analysis.
-The future `robvis::reporter()` function would provide a boilerplate description of the assessment tool used and the key domains at risk of bias.
-
-## Creating
-
 \newpage
@@
 
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
 \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
@@
 \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}

### 2021-11-23 front-and-back-matter/_acknowledgements.Rmd
End of day:

@@
 
-There are so many people without whom this would not have been possible:
+There are so many people without those input this work would have been severly diminised:
 
-[**Check all name spellings**]
+__Supervisors__
 
-Sharen O'Keffe
-Neal Haddaway
-Martin Westgate
+Sharen O'Keffe, Neal Haddaway, Martin Westgate, Emily Hennessy, Randall Boyes, Alex J Fowler,
 
-robvis contributors: (there are at least 3)
+`robvis` contributors: (there are at least 3)
 
@@
 
-Those who contributed their time to dual marking papers and code with me,
+Those who contributed their time to dual marking papers and data extracting with me,
 
-Thanks to Francesca for sharing advance copy of review of Mendelian randomisation studies, to inform choice of tool.
+Thanks to those researchers, namely Francesca for sharing advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner for pointing me towards the code underpinning the quantitative triangulation framework.
 
-I am a NIHR Doctoral Research Fellow with grant code **TBC**.
+I am a NIHR Doctoral Research Fellow, supported by grant **TBC**.
 The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.
@@
 
+My student, Georgia Gourlay
+
 __Personal__
 
-Finally, thanks to parents and Ciara Gardiner.
+Thanks to the Canygne hall crew, for keeping me sane during write-up.
+
+Finally, thanks to parents and
+
+Finally, thanks to my fianceé and project-manager-extordinaire, Ciara Gardiner.
 

### 2021-11-23 R/03-Code-Systematic-Review.R

@@ -857,10 +857,10 @@ forest_strata_rob(dat,
                   rob_me = "Low",
                   xlab = "Odds ratio")
 
-text(-5, c(1, 2), cex = 1.2, dat$tpos)
-text(-4, c(1, 2), cex = 1.2, dat$tneg)
-text(-2.5, c(1, 2), cex = 1.2, dat$cpos)
-text(-1.5, c(1, 2), cex = 1.2, dat$cneg)
+text(-5, c(2, 1), cex = 1.2, dat$tpos)
+text(-4, c(2, 1), cex = 1.2, dat$tneg)
+text(-2.5, c(2, 1), cex = 1.2, dat$cpos)
+text(-1.5, c(2, 1), cex = 1.2, dat$cneg)
 text(c(-5,-4,-2.5,-1.5),
      4.5,
      c("D+", "D-", "D+", "D-"),
@@ -868,7 +868,7 @@ text(c(-5,-4,-2.5,-1.5),
      font = 2)
 
 text(-7, 5, "Type", cex = 1.2, font = 2)
-text(-7, c(1, 2), cex = 1.2, dat$exposure)
+text(-7, c(2, 1), cex = 1.2, dat$exposure)
 
 text(c(-4.5,-2),
      5,

### 2021-11-25 03-Chp-Systematic-Review-Methods.Rmd
End of day:

@@
 
-# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-methods-heading}
+# Systematic review of existing evidence on the association between blood lipids and dementia outcomes: Methods {#sys-rev-methods-heading}
 
@@
 ```
-
-<!-- TODO Consider reordering the forest plots so that they are the other way around -->
-
-<!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017] -->
 
@@
 
-This chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides), and treatments that change these levels such as statins, and dementia outcomes.
-
-My review included `r n_included` primary studies that contained information on this relationship.
-I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipid levels were not associated with any outcome.
-The methods used in some of the primary studies meant that I was less confident in the accuracy of their results.
-
-The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.
-
-<!-- TODO Search for MCI -->
+This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
+In addition, the review examined the relationship betweeen treatments that change blood lipid levels, such as statins, and dementia outcomes.
+The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading.)
 
@@
 
-In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels, and treatments that modify them, and the subsequent risk of dementia and related outcomes.
+In this chapter, I describe a comprehensive systematic review of the relationship between blood lipid levels (and treatments that modify them) and the subsequent risk of dementia and related outcomes.
 
@@
 Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
-These include randomised controlled trials, observational studies of different analytical design, and Mendelian randomisation studies.
+These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies.
 However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
@@
 
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), in addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).
+Given the size of the review, I have seperated the methods and results into two chapters for ease of reading.
+This chapter details the methodology used, while CHapter \@ref(sys-rev-results-heading) presents the results of the review.
 
@@
 
-A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020] Deviations from this protocol are detailed in the relevant sections.
+A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020]
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements and Author Declaration in the front matter).
-<!-- TODO add the following to acknowledgements These included Alexandra MacAleenan, Athena Sheppard, and Matthew Lee.
-In addition, Sarah Dawson, an information specialist, provided input to the design of the search strategy.-->
-
-<!-- TODO Double check this list at the end of the project. -->
 
@@
 
-### Search strategy
+### Eligibility criteria
+
+#### Inclusion criteria
+
+I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
+I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
+Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+
+Eligible studies screened participants for dementia at baseline and excluded any prevalent cases.
+Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
+Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+No limits were placed on the sample size of included studies.
+
+Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.
+
+<!-- COMMENT Isn’t more true to say it was assumed that a health care professional had made the diagnosis (unlikely to use specific criteria) -->
+
+Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status.
+No limitations were imposed on publication status, date, venue or language.
+
+<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
+
+<!-- TODO Any study using EHR - go back and extract codelists -->
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+#### Exclusion criteria
+
+Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status, were eligible for inclusion.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
+MoCA score) without an attempt to map these scores to ordinal groups (e.g.
+no dementia/dementia).
+Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
+
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
+for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+below the age of 50) were excluded.
+Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
+Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
+
+<!----------------------------------------------------------------------------->
+&nbsp;
+
+### Information sources and search strategy
 
@@
 <!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"<!-- TODO CITATION NEEDED -->).
+Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"[@greenhalgh2005; @wohlin2014]).
 
@@
 
-The criteria against which records were assessed for eligibility are presented in the subsequent sections.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Inclusion criteria
-
-I sought to include studies that examined blood lipid levels as a risk factor for demenita outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
-I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
-Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
-
-Eligible studies screened participants for dementia at baseline and excluded any prevalent cases.
-Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
-No limits were placed on the sample size of included studies.
-
-Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.
-
-Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status.
-No limitations were imposed on publication status, date, venue or language.
-
-<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
-
-<!-- TODO Any study using EHR - go back and extract codelists -->
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Exclusion criteria
-
-Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though nested case-control studies, where historical records are used to determine the exposure status, were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia).
-Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
-
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
-below the age of 50) were excluded.
-Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
-Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
+The criteria against which records were assessed for eligibility are presented above.
 
@@
 
-How to interpret agreement co-efficients is widely debated, and while arbitary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+How to interpret agreement coefficients is widely debated, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
 Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
@@
 
+<!-- COMMENT [Yoav] How did you choose what data to include? re: studyification -->
+
 As part of the data extraction process, multiple records resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
@@
 \begin{equation}
-Mean = \frac{(N_1M_1 + N_2N_2)}{(N_1 + N_2)}
+Mean = \frac{(N_1M_1 + N_2M_2)}{(N_1 + N_2)}
   (\#eq:combiningGroups2)
@@
 
-<!-- TODO This might not be as accurate now given the focus on dose response --> <!-- TODO Cross reference with the data extraction issues here - i.e.
-not providing qratile cut-off values, not poviding numbers per group, etc.
---> Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
+Where necessary, lipid levels reported in _mmol/L_ were converted in _mg/dL_ using the following formula:
 
@@
 where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-For widely-used categorises of lipids levels on the _mg/dL_ scale, see Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+The choice of _mg/dL_ was influenced by the widely-used categorises of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
 
@@
 The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] If the outcome is rare, as is the case for dementia outcomes, the estimated prevalence of  odds and risk ratios will approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-time-at-risk in each treatment group.
+As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] If the outcome is rare, as is the case for dementia outcomes, the estimated odds and risk ratios will approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-time-at-risk in each treatment group.
 
@@
 
-This move was prompted by a unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
+This move was prompted by an unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
 <!-- TODO CITATION NEEDED --> As part of this shift, the focus shifted from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
@@
 
-Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assess the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
+Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
 Acceptable judgements for each domain include: "low risk", "some concerns", "high risk".
-Each of the five domains contains a series of signalling questions or prompts which guide the user through the tool.
+Each of the five domains contains a series of signaling questions or prompts which guide the user through the tool.
 Once a domain-level judgement for each domain has been assigned, an overall judgement, using the same three levels of risk of bias, is assigned to the result.
@@
 In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial.
-Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to produced by a randomised controlled trial.
+Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.
 
 While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signalling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
+Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
 The motivation using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
@@
 Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
-Acceptable judgements for each fo the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
+Acceptable judgements for each of the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
 
@@
 In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
-This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
-<!-- TODO Cite Ben's work on effect of missing study versus choice of analysis method -->
+This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
 
@@
 
-An inital qualiatative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design.
+An initial qualitative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design.
 Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
@@
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
-Finally, where at least 10 results are available, a test subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).
-All models were implemented using the `metafor` R package.
+Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.
 
@@
 <!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
---> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contain in the interim groups.
+--> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
@@
 A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-<!-- TODO CITATION NEEDED --> The locations of the knots in the model wer identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
+<!-- TODO CITATION NEEDED --> The locations of the knots in the model were identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
 Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
@@
 _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
-Syntheses with greater than 10 studies were assessed for heterogeneity across these covariates.
-<!-- TODO Need more here -->
+Syntheses with greater than 10 results were assessed for heterogeneity across these covariates.[@deeks2019]
 
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.
-<!-- TODO CITATION NEEDED - cite Jonathon on interpreting small study effects, and whatever citation is needed for  -->
+Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.[@sterne2011]
 
@@
 
-One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.
-<!-- TODO CITATION NEEDED --> In response to this criticism, I developed a new visualisation tool was designed to allow for the production of "paired" forest plots, as recommended by the ROB2 publication, where a risk-of-bias assessment is presented alongside it's corresponding numerical results.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] <!-- Apparently collaboration is a big thing they want to see --> A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
-_[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_
+<!-- TODO _[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_ -->
 
@@
 As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+
+<!-- COMMENT You need to state a priori in what objective way you can judge if pre-prints do or do not have added value -->
 
@@
 
-## Results
+## Summary
 
-<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
+* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and treatments for lowering blood lipids.
 
-### Initial search and validation of search filters
+* I have highlighted how this review will make use of preprinted literature, using the research tool introduced in the preceding chapter (Chapter \ref(sys-rev-tools-heading)).
 
-The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records.
-Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
-<!-- TODO include some example citations here -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Screening results
-
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
-
-The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the right of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g.
-change in cognitive scores).
-
-<!----------------------------------------------------------------------------->
-
-\blandscape{}
-
-&nbsp;
-
-(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
-
-(ref:prisma-flow-scap) PRISMA flow diagram
-
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
-```
-
-\elandscape{}
-
-<!----------------------------------------------------------------------------->
-
-### Validation of screening
-
-```{r agree-setup, include = FALSE}
-```
-
-For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
-For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
-
-<!-- TODO Include AC1 result in caption above -->
-
-(ref:agreeInter-scaption) Inter-rater agreement
-
-```{r agreeInter-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
-
-(ref:agreeIntra-scaption) Inter-rater agreement
-
-```{r agreeIntra-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and the definition of eligible lipids fractions.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-### Characteristics of included studies {#sys-rev-characteristics}
-
-```{r characteristicsSetup, message=FALSE, results="asis", echo = FALSE}
-```
-
-Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
-
-Of the `r n_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also reported on other non-statins agents such as fibrates (`r n_fibrates`).
-In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia (`r n_hyperchol`) and total cholesterol levels (`r n_TC`) were the most frequently reported risk factors.
-
-In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia (`r n_VaD`).
-Some other outcome classifications such as vascular-component or mixed dementia were also investigated, but were much rarer.
-
-<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->
-
-<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->
-
-<!--- TODO Talk a little bit more about age here --->
-
-Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
-
-<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->
-
-<!-- TODO Figures and tables to include here: -  Summary of risk of bias (not done) -->
-
-<!-- TODO Also need to extract the codes used in each study -->
-
-<!-- TODO Need to add abbreviations to table -->
-
-<!-- TODO Ensure citations make sense, and are correct! Get first reference and then add -->
-
-\blandscape{}
-<!----------------------------------------------------------------------------->
-(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple analytical designs within a single study report, and these have been duplicated across the relevant sub-sections.
-
-(ref:studyCharacteristics-scaption) Characteristics of included studies
-
-(ref:studyCharacteristics-first-cite) [@heartprotectionstudycollaborativegroup2002]
-
-```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
-```
-<!----------------------------------------------------------------------------->
-\elandscape{}
-
-```{r cohortLocationsSetup, include = FALSE}
-```
-
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most high represented region being North America.
-Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
-
-<!----------------------------------------------------------------------------->
-
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
-
-(ref:cohortLocations-scap) Geographical distribution of study cohorts
-
-```{r cohortLocations, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cohortLocations-cap)', out.width='100%', fig.scap='(ref:cohortLocations-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/cohortLocations.png"))
-```
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-Finally, there were several eligible studies reported as conference abstracts that did not present numerical results.
-These reports were included in the analysis to enable assessment of risk of bias due to missing evidence (see Section \@ref(methods-rob-me)).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Risk of bias {#risk-of-bias-res}
-
-```{r riskOfBias, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-As discussed above, the risk-of-bias assessments are presented alongside their corresponding numerical result.
-A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
-
-For the two randomised controlled trials, both were judged to be at low risk of bias.
-In contrast, many of the non-randomised studies of statin use were at serious risk of bias due poor controlling for confounding, immortal time bias, and missing outcome data (as noted above, a judgement of low risk of bias for a non-randomised study is rare).
-Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g.
-examination of lipids as a binary or continuous variable).
-Finally, bias was introduced into Mendelian randomisation studies via the potential for hoziontal pleiotropy and population stratification.[@davies2018]
-
-Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.
-<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
-the study reported unadjusted estimates).`r critical_citations`
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### All-cause dementia {#sys-rev-res-Dementia}
-
-#### Statins
-
-```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-&nbsp;<!----------------------------------------------------------------------->
-
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
-This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
-
-&nbsp; <!---------------------------------------------------------------------->
-
-#### Fibrates
-
-```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found very weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
-
-(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Lipids
-
-<!-- TODO Deal with awkward hypercholesterolemia definition -->
-
-Across all outcomes, lipid levels were categorised in a number of ways.
-The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
-
-`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
-
-(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
-
-```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
-```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Alzheimer's disease {#sys-rev-res-AD}
-
-#### Statins
-
-There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
-
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Two Mendelian randomisation studies looked at specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Lipids
-
-`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
-
-(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
-
-```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
-
-<!-- TODO This should also show Raffatin! -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random-effects meta-analysis of LDL on vascular dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
-
-```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
-However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
-Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
-However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Vascular dementia {#sys-rev-res-VaD}
-
-#### Statins
-
-As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
-There were no available randomised trials for this outcome.
-`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Lipids
-
-`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
-
-(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
-
-```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found very weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
-A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
-
-<!-- TODO This is not technically - more studies available on vascular dementia -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
-
-```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of genetically determined lipid levels on vascular dementia risk.
-
-&nbsp;
-
-### Dose response meta-analysis of lipid levels {#dose-response-results}
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks -->
-
-```{r doseResponse, include = FALSE}
-```
-
-There were `r n_dr_initial` studies that were eligible for dose-response meta-analysis as they provide several categories of lipid exposure.
-However, following data extract, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
-
-Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of studies (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
-This analysis provided very weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
-Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
-
-<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
-
-(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
-
-```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:lipidsDoseResponse-cap)', out.width='70%', fig.scap='(ref:lipidsDoseResponse-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/dr_AD_TC.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Additional analyses
-
-Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, few meta-analysis included more than 10 results, the recommended minimum required for meta-regression.
-Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
-
-Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
-
-Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
-However, all analyses assessed provided weak evidence of small-study effects.
-
-[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]
-
-<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
-
-<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
-Depsite attempts to obtain this additional information through contact with a -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Missing evidence
-
-The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
-For randomised controlled trials and non-randomised studies of interventions, the risk of bias due to missing evidence was assessed to be minimal.
-However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (Figures \@ref(fig:lipidFractionsDementia), \@ref(fig:lipidFractionsAD) and \@ref(fig:lipidFractionsVaD).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Added evidential value of including preprints {#sys-rev-including-preprints-res}
-
-As show in Figure \@ref(fig:prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
-From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
-
-Including preprints did provide useful additional evidential value in a number of meta-analysis.
-To demonstrate this, the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref(fig:mrStatinADFig)) in Mendelian randomisation studies was re-analysed using a fixed-effect model.
-Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
-
-<!-- &nbsp; -->
-
-<!----------------------------------------------------------------------------->
-<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->
-
-<!-- (ref:preprintWeights-scaption) Added information due to inclusion of preprints -->
-
-<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
-<!-- ``` -->
-<!----------------------------------------------------------------------------->
-
-<!-- TODO Add extra column with details of Figure showing met-analysis -->
-
-<!-- &nbsp; -->
-
-Investigation of the publication status of the two preprints reporting studies not also identified by the main search after a two-year lag found that one had been subsequently published in late 2019.[@andrews2019; @andrews2021] The final preprint has not yet been published.[@so2017]
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-## Discussion
-
-<!-- TODO Check inclusion of Rockwood 2002:  -->
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-This discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
-A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Summary of findings
-
-There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
-mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
-
-<!-- Some evidence that age has impact on observed lipid-dementia relationship - use to link  -->
-
-The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
-This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up made necessary by the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), which appears in the literature in recent years, driven by the availability of summary genome wide association studies (GWAS) that form the basis of the two-sample Mendelian randomisation approach.
-
-<!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-<!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) Included study designs by year of publication
-
-(ref:typeByYear-scap) Study designs by year of publication
-
-```{r typeByYear, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:typeByYear-cap)', out.width='100%', fig.scap='(ref:typeByYear-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/type_by_year.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-A common theme was an absence of studies examining vascular dementia as an outcome, most noticeable when comparing the evidence base for statins in dementia/Alzheimer's (Figures \@ref(fig:obsStatinDementiaFig) & \@ref(fig:obsStatinADFig)) with that available for vascular dementia (Figure \@ref(fig:obsStatinVaDFig)).
-This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
-A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was very weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
-
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
-As such, this trial did not met the inclusion criteria for this review.
-
-<!-- The findings on high TC in midlife being associated with increased risk of late-life AD are still limited to the few studies that report relevant data from Scandinavia and the United States.
-The wider literature shows that level of TC in populations varies according to diet, urbanization, ethnicity, and income [56, 57].
-from Anstey 2017 -->
-
-Risk of bias across the individual results was generally quite high, and the causes and expected directions of these biases are discussed in more detail in Chapter \@ref(tri-heading).
-Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of statin levels.
-In many cases, estimates were know to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
-These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
-"The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
-were not reported in the Table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided very weak evidence for an effect), other than increasing the precision of the summary estimate.
-
-Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of studies which made use of data from the Taiwan health insurance database.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Comparison with previous reviews {#rev-previous-reviews}
-
-<!-- TODO This section will be informed by the review published as a preprint -->
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
-the Newcastle-Ottowa Scale).[@poly2020]
-
-I identified one previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease.
-However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).
-
-Despite these differences in time-scales and methodology, the duplication of work across reviews (including this review) is substantial.
-In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
-
-One of the particular strengths of this review is the inclusion and critical assessment of Mendelian randomisation studies as a source of evidence.
-
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
-However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
-
-<!----------------------------------------------------------------------------->
-```{r mrAssumptionsSetup, include = FALSE}
-```
-
-(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
-there is no horizontal pleiotropy).
-
-(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses
-
-```{r mrAssumptions, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:mrAssumptions-cap)', out.width='70%', fig.scap='(ref:mrAssumptions-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/mrAssumptions.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availabilt of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses.
-As such, the process and tools for systematically assessing this study design are not as well developed.
-A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.
-
-Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias).
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
-<!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.
-
-As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
-This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
-Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
-This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
-
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation" followed by manual review of studies that look across multiple risk factors would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (n=`r comma(16109)`).
-Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit to the field.
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
-In all cases, excluding these variants attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017comment]
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Inclusion of preprints
-
-```{r preprintGrowthSetup, include=FALSE}
-```
-
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
-published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
-The small number of studies returned by the searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
-The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a very small number of records (n=`r n_at_search["med"]`).
-
-<!----------------------------------------------------------------------------->
-(ref:preprintGrowth-cap) Growth of preprint repositories over time.
-Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
-
-(ref:preprintGrowth-scap) Growth of preprint repositories over time
-
-```{r preprintGrowth, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:preprintGrowth-cap)', out.width='80%',fig.align='center',fig.scap='(ref:preprintGrowth-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/preprint_growth.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Three relevant preprints from the bioRxiv hits were identified.
-The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
-Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
-
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
-
-Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
-Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-More recently, inclusion of preprints in systematic reviews has become significantly more widespread.
-This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.[@fraser2020preprinting] How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Comments on the process -->
-
-<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
-
-<!-- &nbsp; -->
-
-<!-- #### Protocol registration -->
-
-<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
-In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
--->
-
-<!-- &nbsp; -->
-
-<!-- #### Workload -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-<!-- &nbsp; -->
-
-<!-- #### People management -->
-
-<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
-However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
--->
-
-<!-- &nbsp; -->
-<!----------------------------------------------------------------------------->
-
-<!-- ### Validation against recent umbrella review -->
-
-<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
-
-<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
-
-<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
-In fields where there is a lot of existing reviews, they -->
-
-<!-- All studies identified by reviews included in te -->
-
-<!-- In hindsight, this approach ma -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-
-### Open data sharing {#sys-rev-open-data}
-
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important information required for the dose-response meta-analysis, and so could not be included in the synthesis.
-This limitation was compounded by the expected low response rate to requests for further information from primary authors.
-While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
-
-Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.
-A copy of this publication is available in Appendix \@ref(published-papers).[@hennessy2021] In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
-__[Zenodo repository will be cited here]__
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Strengths and limitations
-
-<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
-
-#### Strengths
-
-I believe there are several aspects where this review is distinct from those reviews already available in the published literature.
-While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This repres important strength of this review, as the detailed risk of bias assessments are used in
-
-Thirdly, as discussed at length in the section above, in contrast to other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related preprints.
-Finally, as a secondary element, I used this review to pilot new research synthesis methodologies, in particular a new visualisation approach for risk-of-bias assessments and a forthcoming tool for assessing the risk-of-bias due to missing evidence.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-#### Limitations
-
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
-
-In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
-
-One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
-
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-## Conclusions
-
-In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
-
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
+* In the following chapter, I presented the results of this comprehensive systematic review and detail how the identified evidence is used throughout the remainder of the thesis.
 

### 2021-11-25 04-Chp-Systematic-Review-Results.Rmd
End of day: 39966
End of day:

--- 2021-10-13 04-Chp-Systematic-Review-Results.Rmd
@@
 ```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
+It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS.  
 ```
@@
 
-# Systematic review of all available evidence on the association between blood lipids and dementia outcomes {#sys-rev-heading}
+# Systematic review of existing evidence on the association between blood lipids and dementia outcomes: Results {#sys-rev-results-heading}
 
@@
 
-<!-- ## To Do -->
-
-<!-- TODO Extra studies to include: -->
-<!-- * Larsson - 10.1136/bmj.j5375 [@larsson2017b] -->
-
 ```{r prisma-flow-setup, include = FALSE}
 ```
+
+## Lay summary
+
+Using the methods outlined in the previous chapter, this chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
+In addition, it examined the relationship betweeen treatments that change blood lipid levels, such as statins, and dementia outcomes
+
+My review included `r n_included` primary studies that contained information on this relationship.
+I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
+Lipid levels were not associated with any outcome.
+The methods used in some of the primary studies meant that I was less confident in their results.
+
+The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.
+
+## Introduction
 
@@
 
-Common reasons for exclusion at the full text-stage included studies that reported on the wrong exposures (n = `r n_wrong_exposure` ; most commonly a ineligible lipid fraction), used the wrong study design (n= `r n_study_design`), or reported on a wrong outcome (n=24; e.g.
-change in cognitive scores).
+Common reasons for exclusion at the full text-stage included studies that reported on ineligible exposures (n = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (n=24; e.g.
+change in cognitive scores) or used an ineligible study design (n= `r n_study_design`).
 
@@
 
-The two randomised controlled trials provided very weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
+The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
 
@@
 
+<!-- TODO This should also show Raffatin! -->
+
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+(ref:lipidFractionsAD-cap) Random-effects meta-analysis of LDL on vascular dementia risk, standardised per 1-SD increase in the lipid fraction.
 
@@
 
+<!-- TODO This is not technically - more studies available on vascular dementia -->
+
 <!----------------------------------------------------------------------------->
@@
 
+<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
+
 <!----------------------------------------------------------------------------->
@@
 
-[_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_]
+<!-- TODO [_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_] -->
 
@@
 This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
-This discussion seeks to  to summarise the key findings in terms of literature sources and results as reported.
+This discussion seeks to summarise the key findings in terms of literature sources and results as reported.
 A detailed comparison across the evidence sources, exposure measures and sources of bias reported here is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
@@
 This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
-mid-life in studies of lipids with late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
+mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
 
@@
 
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002a] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though an useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
-As such, this trial did not met the inclusion criteria for this review.
+Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Though a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
+As such, this trial did not meet the inclusion criteria for this review.
 
@@
 
-I identified one previous review of Mendelian randomisation studies examining risk factors for Alzhiemer's disease.
+I identified one previous review of Mendelian randomisation studies examining risk factors for Alzheimer's disease.
 However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).
 
-Despite these differences in time-scales and methodology, the duplication of work across reviews (including this review) is substantial.
+Despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
 In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
@@
 
-### Inclusion of Mendelian randomisations studies {#rev-discussion-MR}
+### Inclusion of Mendelian randomisation studies {#rev-discussion-MR}
 
@@
 
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
+Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the three core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
+These assumptions are namely that: i) the genetic variant associates with the risk factor of interest (relevance assumption); ii) the variant-exposure association has no unmeasured confounders (independence assumption); and the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption).
 However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
+
+todo
 
@@
 Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
-Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availabilt of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses.
+Figure \@ref(fig:typeByYear) demonstrates that Mendelian randomisation studies only begin to appear in the evidence base much later than NRSE/NRSI, likely due to the limited availability of large scale GWAS datasets needed for two-sample Mendelian randomisation analyses.
 As such, the process and tools for systematically assessing this study design are not as well developed.
-A key example of this is in the absence of validated search filters for Mendelian randomisations studies.
+A key example of this is in the absence of validated search filters for Mendelian randomisation studies.
 This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.
@@
 Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
-<!-- TODO Read this tool.
---> For this review, I utilised the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.
+For this review, I used the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.[@spiga2021]
 
@@
 Three relevant preprints from the bioRxiv hits were identified.
-The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res), and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
-Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
+The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res) and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
+Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically focused study designs are over-represented in the bioRxiv repository.
 
@@
 <!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This repres important strength of this review, as the detailed risk of bias assessments are used in
+This represents an important strength of this review, as the detailed risk of bias assessments are used in
 
@@
 In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is is not a major concern.
+However,  evidence from assessments of inter- and intra-rater reliability indicate that is not a major concern.
 
-One particular limitiation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signalling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signalling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
+One particular limitation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
+This meant that there were no signaling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
+However, there is no published empirical evidence supporting the need for signaling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
 In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
 
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisations studies).
+One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
 Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
@@
 
-## Conclusions
+## Summary
+
+<!-- TODO Clean-up! -->
+
+The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), by identifying outcomes and analytical techniques that are under-represented in the literature.
+In addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).
+
+<!-- COMMENT What do you mean guide. Design the SAP or the interpretation or both? -->
 
@@
 
-This work built on the tool introduced in the preceeding chapter (Chapter \ref(sys-rev-tools-heading)), and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading),  summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
+ and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
 

### 2021-11-25 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-#### Confounding by indication
+#### Confounding by indication {#cprd-confounding-by-ind}
 
@@
 
+```{r dags, include=F}
+```
+
 ```{r indicationBias, echo = FALSE, results="asis", fig.pos = "H",fig.align='center',fig.cap='(ref:indicationBias-cap)', out.width='80%', fig.scap='(ref:indicationBias-scap)', message = FALSE}
-
-ggplot2::ggsave(filename = file.path("figures","cprd-analysis","indicationBias.png"),
-dagitty::dagitty("dag {
-  Statin [exposure,pos=\"0.000,0.000\"]
-  \"Vascular outcomes\" [outcome,pos=\"2.000,0.000\"]
-  \"Uncontrolled variable\" [pos=\"1.000,1.000\"]
-  \"Uncontrolled variable\" -> Statin
-  \"Uncontrolled variable\" -> \"Vascular outcomes\"
-}") %>% ggdag_classic(size = 6) +
-  xlim(-0.5,3) +
-  geom_text(data = data.frame(x = 0.316392393234329,
-                              y = 0.537705383514239,
-                              label = "Prompts"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 0.88,
-                              y = 0.05,
-                              label = "Induced positive"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 0.88,
-                              y = -0.04,
-                              label = "association"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_text(data = data.frame(x = 1.65891420807966,
-                              y = 0.537705383514239,
-                              label = "Causes"),
-            mapping = aes(x = x,
-                          y = y,
-                          label = label),
-            angle = 0L,
-            lineheight = 1L,
-            hjust = 0.5,
-            vjust = 0.5,
-            colour = "black",
-            family = "sans",
-            fontface = "bold",
-            inherit.aes = FALSE,
-            show.legend = FALSE) +
-  geom_curve(data = data.frame(x = 0.220612676359188,
-                               y = -0.000788829298738025,
-                               xend = 1.45,
-                               yend = -0.00157828084913909),
-             mapping = aes(x = x,
-                           y = y,
-                           xend = xend,
-                           yend = yend),
-             linetype = "dashed",
-             angle = 0L,
-             size = 0.6,
-             colour = "black",
-             curvature = 0,
-             arrow = structure(list(angle = 0,
-                                    length = structure(0,
-                                                       class = "unit",
-                                                       valid.unit = 2L,
-                                                       unit = "inches"),
-                                    ends = 2L,
-                                    type = 2L),
-                               class = "arrow"),
-             inherit.aes = FALSE,
-             show.legend = FALSE) +
-
-  theme_dag(),
-width = 8,
-height = 3)
 
@@
 
-### Strengths and limitations
+### Strengths and limitations {#cprd-limitations}
 

### 2021-11-25 07-Chp-Triangulation.Rmd
End of day:

@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:tri-quote)', echo = TRUE}
-Next on my list of features to be specially considered I would place the consistency
-of the observed association. Has it been repeatedly observed by different persons, in different places, circumstances and times?
+Next on my list of features to be specially considered I would place the consistency of the observed association.
+Has it been repeatedly observed by different persons, in different places, circumstances and times?
 ```
@@
 More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).
+This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).
 
@@
 
-As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initally grouped by outcome, and the findings from each source were narratively compared and contrasted.
+As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initially grouped by outcome, and the findings from each source were narratively compared and contrasted.
 Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.
@@
 Proportional biases are dependent on the magnitude of the effect, while additive biases are not.[@turner2009]
+
+<!-- TODO Need to include some text here on examples of each: e.g. immortal time bias, or  -->
 
@@
 
-The indirectness of a result (also termed external bias, relevance, generalisability, or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.
+The indirectness of a result (also termed external bias, external validity, relevance, generalisability, or applicability) is defined here as the discrepancy between the research question addressed by the "idealised" study and the causal question of interest.
 
@@
 For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
-In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(hold) for a fuller discussion).
+In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
 As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right.
@@
 
+<!-- TODO Need to add some text here that says that assessment of the different domains  -->
+
 __[Note: I would be particularly interested in your feedback here.

### 2021-11-25 08-Discussion.Rmd
End of day:

@@
 output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
   bookdown::word_document2: 
       reference_docx: templates/word-styles-reference-01.docx   
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
   bookdown::html_document2: default
@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
+Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
 ```
-(ref:intro-quote) --- Hold
+
+(ref:intro-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]
 
@@
 
-The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are n Not inconsistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
-
+The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are  consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
 <!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect.
@@
 
-An analysis of 502,226 participants of the UK BioBank found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.6,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes.
+The UKBioBank is a [@sudlow2015]
+
+A recent analysis of 502,226 participants of this found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.06,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97,.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes.
 This is comparable to my findings.
@@
 
-This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systemtatic manner, including diverse sources of evidence, inclu
+This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systematic manner, including diverse sources of evidence, inclu
 
@@
 
+This should focus on doctors being honesty with patients from the outset and describing what they know regarding the uncertainty of the evidence.
+
+While also recognising that the impact of statin or other LRA use on dementia is going to be secondary to their established effect on lipid-lowering.
+To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.
+
 The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
@@
 ### Public health
+
+This section should
 

### 2021-11-25 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 
-## Chapter \@ref(sys-rev-heading) {#appendix-sys-rev}
+## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}
 <!----------------------------------------------------------------------------->
+
+<!-- TODO This needs to be split in two!  -->
 
@@
 
+## Chapter \@ref(sys-rev-results-heading)
+
+### Dose response plots by fraction
+
+<!----------------------------------------------------------------------------->
+(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia
+
+(ref:drDemeniaTC-scap) shortcap
+
+```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease
+
+(ref:drAdLDL-scap) shortcap
+
+```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
+```
+<!----------------------------------------------------------------------------->
+
 <!----------------------------------------------------------------------------->

### 2021-11-25 R/helper.R

@@ -271,7 +271,7 @@ todo_report <- function(fp){
 #'
 #' @param N Chapter number
 
-chapter_edit <- function(N) {
+chapter_edit <- function(N, all = TRUE) {
   # Open Chapter RMarkdown file
   chapters <- list.files(pattern = ".Rmd")
   
@@ -279,13 +279,15 @@ chapter_edit <- function(N) {
   
   file.edit(chapter)
   
-  # Open associated R file
+  if (all) {
+    # Open associated R file
   rfiles <-
     list.files(path = "R",
                pattern = ".R",
                full.names = TRUE)
   
   file.edit(rfiles[which(data.table::like(rfiles, N))])
+  }
   
   # Put focus back on RMarkdown
   rstudioapi::navigateToFile(chapter)
@@ -959,7 +961,12 @@ save_dr <- function(dat, title, xref, preface){
     lines(get("rms::rcs(dose, knots)dose"), ci.lb, lty = "dashed")
     lines(get("rms::rcs(dose, knots)dose"), ci.ub, lty = "dashed")
   })
-    text(xref+130, 1, paste0("N studies = ",length(unique(dat$study_id))))
+    legend(x = "topright",          # Position
+           legend = c("Estimate", "95% CI",""),  # Legend texts
+           lty = c(1, 2,2),           # Line types
+           col = c("black", "black","transparent"),           # Line colors
+           lwd = 2)
+    text(xref+115, .81, paste0("N studies = ",length(unique(dat$study_id))))
     dev.off()
 }
 

### 2021-11-29 01-Chp-Background.Rmd
Working version!

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = FALSE}
-Science knows it doesn't know everything; otherwise, it'd stop.
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
+Considering everything, it seems we are dealing
+here with a special illness.
 ```
-(ref:dara-quote) --- Dara O'Briain
+(ref:dara-quote) --- Alois Alzheimer, 1907 [@alzheimer1907; @stelzmann1995]
 

### 2021-11-29 03-Chp-Systematic-Review-Methods.Rmd
Working version!

@@
 ---
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-methods-quote)', echo = TRUE}
 "It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
@@
 
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
+(ref:sys-rev-methods-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
 
@@
 Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
-Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's methods.
+Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
 
 This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
-In addition, the review examined the relationship betweeen treatments that change blood lipid levels, such as statins, and dementia outcomes.
+In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
 The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading.)
@@
 This analysis sought to address two specific aims.
-Firstly, as discussed in the Introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
+Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
 These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies.
@@
 I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
-I also aimed to include studies examining the effect of treatments that modify lipids levels as a source of indirect evidence.
-Eligible study designs included randomized controlled trials and non-randomized observational studies of lipid modifying treatments, longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+I also aimed to include studies examining the effect of treatments that modify blood lipid levels, such as statins or fibrates, as a source of indirect evidence.
+
+Eligible study designs were randomized controlled trials, non-randomized studies of exposures, non-randomised studies of  , longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
 
@@
 
-As part of the data extraction process, multiple records resulting from the analysis of the same data were included and grouped into single units, hereafter called studies.
-This was common in cases where multiple papers report results on the same cohort but at different time points.
-This process builds out the most comprehensive account of a given studies possible by incorporating information from all available records.
+<!-- COMMENT [Julian] Same analysis or same data? Don't want 2+ analyses of the same data to appear in a meta-analysis (unless orthogonal; e.g. MR + RCT) -->
+<!-- QUESTION Why does being orthogonal make it okay? And the Three City Study is likely to be included several times -->
+
+As part of the data extraction process, multiple records resulting from a single analysis were included and grouped into single units, hereafter called studies.
+This was most common in cases where multiple records reported on the same analysis but at different time points.
+In this case, the result corresponding to the longest follow-up was used.
+Grouping records into studies builds out the most comprehensive account of a given analysis by incorporating information from all available records.
 
@@
 
-In line with best practice, where summary data was presented across two groups (e.g.
+In line with best practice, where summary data were presented across two groups (e.g.
 age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
@@
 
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.
-The choice of _mg/dL_ was influenced by the widely-used categorises of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categorises of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-
-#### Analysis of varying effect measures
-
-<!-- TODO Include formulae and informed assumptions  -->
-
-The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
-As such, different effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] If the outcome is rare, as is the case for dementia outcomes, the estimated odds and risk ratios will approximate each other.<!-- TODO CITATION NEEDED --> However, hazard ratios provide a very different interpretation, taking into account person-time-at-risk in each treatment group.
-
-Several existing reviews do not distinguish between the types of effect measures and include all existing studies in a single meta-analysis to produce an overall effect estimate.
-However, in this review, the small subset of studies reporting odds/risk ratios are synthesised separately to those reporting hazard ratios.
-
-<!----------------------------------------------------------------------------->
-&nbsp;
 
@@
 For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that is not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
+In this case, missing outcome data that are not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
 
@@
 
-Results were not combined across different study designs (i.e.
-RCTs were not combined in a meta-analysis with results from observational studies).
-The summary effect estimates produced by meta-analysis of individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
 &nbsp;
@@
 
+#### Analysis overview
+
+Results were not combined across different study designs (i.e.
+RCTs were not combined in a meta-analysis with results from observational studies).
+The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
+Analysis are presented seperately for each dementia type of interest.
+
+The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
+As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.
+
 #### Random-effects meta-analysis
 
-For results examining the effect of binary or continuous exposure (as opposed to categorical/dose-response, as discussed in the next section) on any dementia outcome, a random-effects meta-analysis model was used.
-Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
-The weight ($w$) assigned to each result (denoted as $y_i$) is then give as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
+I used a random-effects model in all meta-analysis presented in this chapter.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
+The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
 
@@
 Studies were excluded from this analysis if the number of categories was less than three or if the necessary information for synthesis (cut-off points, number of participants and number of events per category) was not available.
-A restricted cubic spline model was fitted to allow for a non-linear relationship, for example a U or J-shaped relationship, where low and high levels of the exposure can have different effects versus a "normal" reference dose.
-<!-- TODO CITATION NEEDED --> The locations of the knots in the model were identified using fixed percentiles (25th, 50th, 75th) of the exposure data.
+When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
+Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
+
+I took a two-stage dose-response meta-analysis approach, where study-specific trends are estimated before being pooled acrosss studies.[@greenland1992] To estimate within-study trends, a restricted cubic spline model was fitted within each to allow for a non-linear relationship between lipid levels and dementia, for example a U or J-shaped relationship, where low and high levels of a lipid fraction can have different effects versus the "normal" reference dose.[@durrleman1989;@liu2009] <!-- TODO CITATION NEEDED -->
 Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
@@
 
-When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
-Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
+Restricted cubic spline models use "knots" to create separate the data into subsets or "windows", in which the trend is modelled.
+Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]
 
@@
 
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was quantified and visualised on a world map.
+Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was visualised on a world map.
 
-One of the limitations of current risk-of-bias assessments in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 
@@
 
-<!-- TODO _[Note: Julian, I am particularly interested in your feedback on this section, and the corresponding results section (Section \@ref(sys-rev-including-preprints-res)), as I am not convinced on the language I am using]_ -->
-
 Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)).
 As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.
 

### 2021-11-29 04-Chp-Systematic-Review-Results.Rmd
Working version!

@@
 ---
-```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-quote)', echo = FALSE}
-It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS.  
+```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-results-quote)', echo = TRUE}
+Hold  
 ```
 
-(ref:sys-rev-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
+(ref:sys-rev-results-quote) --- Hold
 
@@
 
-The added value of including preprinted study reports, made possible using the tool described in the previous chapter, along with the use of the results of this review in subsequent chapters, is discussed.
+The added value of including preprinted study reports, made possible using the tool described in the Chapter \@ref(sys-rev-tools-heading), along with the use of the results of this review in subsequent chapters, is discussed.
 
@@
 
-Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@ridker2008; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
-
-<!-- As discussed in Section \@ref(rev-discussion-MR), the choice was not material, as the results from all studies using these data sources were comparable. -->
-
-<!-- TODO Figures and tables to include here: -  Summary of risk of bias (not done) -->
+Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@andrews2019; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
 
 <!-- TODO Also need to extract the codes used in each study -->
+<!-- TODO Need to make sure that the MR studies actually don't report the  -->
 
-<!-- TODO Need to add abbreviations to table -->
-
-<!-- TODO Ensure citations make sense, and are correct! Get first reference and then add -->
+```{r studyCharacteristics-setup, include = F}
+```
 
@@
 <!----------------------------------------------------------------------------->
+<!-- To create the references below, go to the helper script and copy the output of  -->
+
+(ref:heartprotectionstudycollaborativegroup2002RCTcite) HPS 2002[@heartprotectionstudycollaborativegroup2002]
+
+(ref:ridker2008RCTcite) JUPITER 2009[@ridker2008]
+
+(ref:ancelin2012NRSIcite) Ancelin 2012[@ancelin2012]
+
+(ref:arvanitakis2008NRSIcite) Arvanitakis 2008[@arvanitakis2008]
+
+(ref:bettermann2012NRSIcite) Bettermann 2012[@bettermann2012]
+
+(ref:beydoun2011NRSIcite) Beydoun 2011[@beydoun2011]
+
+(ref:chao2015NRSIcite) Chao 2015[@chao2015]
+
+(ref:chen2014NRSIcite) Chen 2014[@chen2014]
+
+(ref:chitnis2015NRSIcite) Chitnis 2015[@chitnis2015]
+
+(ref:chou2014NRSIcite) Chou 2014[@chou2014]
+
+(ref:chuang2015NRSIcite) Chuang 2015[@chuang2015]
+
+(ref:cramer2008NRSIcite) Cramer 2008[@cramer2008]
+
+(ref:gnjidic2016NRSIcite) Gnjidic 2016[@gnjidic2016]
+
+(ref:haag2009NRSIcite) Haag 2009[@haag2009]
+
+(ref:hendrie2015NRSIcite) Hendrie 2015[@hendrie2015]
+
+(ref:hippisley-cox2010NRSIcite) Hippisley-Cox 2010[@hippisley-cox2010]
+
+(ref:jick2000NRSIcite) Jick 2000[@jick2000]
+
+(ref:li2010NRSIcite) Li 2004[@li2010]
+
+(ref:li2004NRSIcite) Li 2010[@li2004]
+
+(ref:liao2013NRSIcite) Liao 2013[@liao2013]
+
+(ref:liu2019NRSIcite) Liu 2019[@liu2019]
+
+(ref:pan2018NRSIcite) Pan 2018[@pan2018]
+
+(ref:parikh2011NRSIcite) Parikh 2011[@parikh2011]
+
+(ref:rea2005NRSIcite) Rea 2005[@rea2005]
+
+(ref:redelmeier2019NRSIcite) Redelmeier 2019[@redelmeier2019]
+
+(ref:reitz2010NRSIcite) Reitz 2004[@reitz2010]
+
+(ref:smeeth2009NRSIcite) Smeeth 2009[@smeeth2009]
+
+(ref:solomon2007NRSIcite) Solomon 2010[@solomon2007]
+
+(ref:sparks2008NRSIcite) Sparks 2008[@sparks2008]
+
+(ref:szwast2007NRSIcite) Szwast 2007[@szwast2007]
+
+(ref:yang2015NRSIcite) Yang 2015[@yang2015]
+
+(ref:zamrini2004NRSIcite) Zamrini 2004[@zamrini2004]
+
+(ref:zandi2005NRSIcite) Zandi 2005[@zandi2005]
+
+(ref:ancelin2013NRSEcite) Ancelin 2013[@ancelin2013]
+
+(ref:batty2014NRSEcite) Batty 2014[@batty2014]
+
+(ref:benn2017NRSEcite) Benn 2017[@benn2017]
+
+(ref:beydoun2011NRSEcite) Beydoun 2011[@beydoun2011]
+
+(ref:bruce2017NRSEcite) Bruce 2017[@bruce2017]
+
+(ref:chiang2007NRSEcite) Chiang 2007[@chiang2007]
+
+(ref:dodge2011NRSEcite) Dodge 2011[@dodge2011]
+
+(ref:forti2010NRSEcite) Forti 2010[@forti2010]
+
+(ref:gottesman2017NRSEcite) Gottesman 2017[@gottesman2017]
+
+(ref:gustafson2012NRSEcite) Gustafson 2012[@gustafson2012]
+
+(ref:hayden2006NRSEcite) Hayden 2006[@hayden2006]
+
+(ref:kimm2011NRSEcite) Kimm 2011[@kimm2011]
+
+(ref:kivipelto2001NRSEcite) Kivipelto 2001[@kivipelto2001]
+
+(ref:kivipelto2005NRSEcite) Kivipelto 2005[@kivipelto2005]
+
+(ref:kuo2015NRSEcite) Kuo 2015[@kuo2015]
+
+(ref:li2005NRSEcite) Li 2005[@li2005]
+
+(ref:mainous2005NRSEcite) Mainous 2005[@mainous2005]
+
+(ref:mielke2010NRSEcite) Mielke 2005[@mielke2010]
+
+(ref:mielke2005NRSEcite) Mielke 2010[@mielke2005]
+
+(ref:mielke2011NRSEcite) Mielke 2012[@mielke2011]
+
+(ref:muller2007NRSEcite) Muller 2007[@muller2007]
+
+(ref:noale2013NRSEcite) Noale 2013[@noale2013]
+
+(ref:notkola1998NRSEcite) Notkola 1998[@notkola1998]
+
+(ref:peters2009NRSEcite) Peters 2009[@peters2009]
+
+(ref:raffaitin2009NRSEcite) Raffaitin 2009[@raffaitin2009]
+
+(ref:rantanen2017NRSEcite) Rantanen 2017[@rantanen2017]
+
+(ref:reitz2010NRSEcite) Reitz 2004[@reitz2010]
+
+(ref:reitz2004NRSEcite) Reitz 2010[@reitz2004]
+
+(ref:ronnemaa2011NRSEcite) Ronnemaa 2011[@ronnemaa2011]
+
+(ref:schilling2017NRSEcite) Schilling 2017[@schilling2017]
+
+(ref:solomon2010NRSEcite) Solomon 2007[@solomon2010]
+
+(ref:solomon2009NRSEcite) Solomon 2009[@solomon2009]
+
+(ref:strand2013NRSEcite) Strand 2013[@strand2013]
+
+(ref:su2017NRSEcite) Su 2017[@su2017]
+
+(ref:svensson2019NRSEcite) Svensson 2019[@svensson2019]
+
+(ref:tan2003NRSEcite) Tan 2003[@tan2003]
+
+(ref:tynkkynen2016NRSEcite) Tynkkynen 2016[@tynkkynen2016]
+
+(ref:tynkkynen2018NRSEcite) Tynkkynen 2018[@tynkkynen2018]
+
+(ref:wang2012NRSEcite) Wang 2012[@wang2012]
+
+(ref:whitmer2005NRSEcite) Whitmer 2005[@whitmer2005]
+
+(ref:yamada2009NRSEcite) Yamada 2009[@yamada2009]
+
+(ref:yoshitake1995NRSEcite) Yoshitake 1995[@yoshitake1995]
+
+(ref:zimetbaum1992NRSEcite) Zimetbaum 1992[@zimetbaum1992]
+
+(ref:andrews2021MRcite) Andrews 2019[@andrews2019; @andrews2021] *
+
+(ref:benn2017MRcite) Benn 2017[@benn2017]
+
+(ref:burgess2017MRcite) Burgess 2017[@burgess2017]
+
+(ref:larsson2017MRcite) Larsson 2017[@larsson2017]
+
+(ref:mukherjee2013MRcite) Mukherjee 2013[@mukherjee2013]
+
+(ref:ostergaard2015MRcite) Ostergaard 2015[@ostergaard2015]
+
+(ref:so2017MRcite) So 2017[@so2017] *
+
+(ref:zhu2018MRcite) Zhu 2018[@zhu2018; @zhu2020] *
+
 (ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
-Note that three studies reported on multiple analytical designs within a single study report, and these have been duplicated across the relevant sub-sections.
+Note that three studies reported on multiple analytical designs within a single study report (Beydoun 2011,[@beydoun2011] Reitz 2010,[@reitz2010] and Benn 2017[@benn2017]), and these have been duplicated across the relevant sub-sections.
+Preprinted studies are denoted using an asterik.
 
@@
 
-(ref:studyCharacteristics-first-cite) [@heartprotectionstudycollaborativegroup2002]
+<!-- TODO Sort out the fact that statins are included as an exposure in NRSE -->
+
+<!-- TODO Enrure all abbreviations at the end of this table are in the abbreviation section at the start. -->
 
@@
 
-`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found very weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
+`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
 
@@
 
+<!-- TODO The number of studies in the inline text refer to the number of studies rather than the number of results.
+Note here that Tynkkyen examine multiple cohorts, which were extracted individually rather than as part of the reported meta-analysis.
+-->
+
 Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
+Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
 
@@
 
-Two Mendelian randomisation studies looked at specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+Two Mendelian randomisation studies looked at lipid-lowering specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
 Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
@@
 Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
-Very weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
+Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
 
@@
 There were no available randomised trials for this outcome.
-`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided very weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
+`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
 
@@
 Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found very weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
 A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
@@
 
-Finally, there were no identified Mendelian randomisation analysis examining the effect of genetically determined lipid levels on vascular dementia risk.
+Finally, no Mendelian randomisation analyses examining the effect of genetically determined lipid levels on vascular dementia risk were identified.
 
@@
 There were `r n_dr_initial` studies that were eligible for dose-response meta-analysis as they provide several categories of lipid exposure.
-However, following data extract, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
+However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
 
 Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of studies (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
-This analysis provided very weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
+This analysis provided weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
 Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
@@
 
-Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found very weak evidence for variation in the observed effect estimates due to these factors.
+Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
 
@@
 For randomised controlled trials and non-randomised studies of interventions, the risk of bias due to missing evidence was assessed to be minimal.
-However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (Figures \@ref(fig:lipidFractionsDementia), \@ref(fig:lipidFractionsAD) and \@ref(fig:lipidFractionsVaD).
+However, there was substantial evidence that results were selectively reported in studies examining the effect of lipid fractions on dementia outcomes (Figures \@ref(fig:lipidFractionsDementia), \@ref(fig:lipidFractionsAD) and \@ref(fig:lipidFractionsVaD)).
 
@@
 
-Including preprints did provide useful additional evidential value in a number of meta-analysis.
-To demonstrate this, the effect of HMGCR SNPS on Alzheimer's disease (Figure \@ref(fig:mrStatinADFig)) in Mendelian randomisation studies was re-analysed using a fixed-effect model.
+One preprint (So _et al_[@so2017]) provided additional evidential value in a single meta-analysis (`r comma(1/18*100)`% of all meta-analyses performed in this chapter).
+This meta-analysis of Mendelian randomisation studies examined the effects of lipid-lowering via HMGCR mutations on incidence of Alzheimer's disease (Figure \@ref(fig:mrStatinADFig).
+To assess the evidence added to the meta-analysis through inclusion of the preprint, the data were re-analysed using a fixed-effect model.
 Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
+However, the inclusion of the preprinted study did not have a substantial impact on the results (`r mrStatin$AD$estimate`) versus the single published study (`r estimate(0.59,0.25,1.39,"RR")`).
+
+The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLCC and IGAP consortia.
+As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add to the evidence base.
 
@@
 
-There was some evidence of protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
+There was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
 This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
@@
 
-The majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
+Across dementia outcomes, the majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
 This distribution of evidence between analytical designs is to be expected.
@@
 
-<!-- TODO Talk about problems with including Hippsley-Cox re double-counting -->
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) Included study designs by year of publication
+(ref:typeByYear-cap) Included study designs for any dementia outcome by year of publication
 
@@
 This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
-A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was very weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
+A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
 
@@
 
-Risk of bias across the individual results was generally quite high, and the causes and expected directions of these biases are discussed in more detail in Chapter \@ref(tri-heading).
-Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of statin levels.
-In many cases, estimates were know to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
+Risk of bias across the individual results was generally quite high.
+The causes and expected impact of these biases on the results are discussed in more detail in Chapter \@ref(tri-heading).
+Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of lipid levels.
+In many cases, estimates were known to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
 These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
 "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
-were not reported in the Table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided very weak evidence for an effect), other than increasing the precision of the summary estimate.
+were not reported in the table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence for an effect), other than increasing the precision of the summary estimate.
 
@@
 
-<!-- TODO This section will be informed by the review published as a preprint -->
-
 While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
+The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
 the Newcastle-Ottowa Scale).[@poly2020]
@@
 A key example of this is in the absence of validated search filters for Mendelian randomisation studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which lead o me including general terms for instrumental variable analyses in my search.
+This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which led to me including general terms for instrumental variable analyses in my search.
 
 Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-A recent commentary provided a checklist  interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.
-While reporting quality is important, it is a separate consideration to internal validity, as discussed in Section \@ref(risk-of-bias).
+While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] While reporting quality is an important consideration, as reflected by the recent release of a STROBE_MR reporting guidelines,[@skrivankova2021] it is a separate consideration to internal validity  as discussed in Section \@ref(risk-of-bias).
 Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
@@
 published).
-Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint serves related to health and biomedical sciences were search as part of this review.
+Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint servers related to health and biomedical sciences were searched as part of this review.
 The small number of studies returned by the searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
@@
 Three relevant preprints from the bioRxiv hits were identified.
-The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res) and indicated that results available only via preprinted reports can contribute substantially to a meta-analysis.
-Of note, all three included preprints described Mendelian randomisation studies, potentially indicating that more biologically focused study designs are over-represented in the bioRxiv repository.
+Of note, all three described Mendelian randomisation studies, potentially indicating that more biologically focused study designs are over-represented in the bioRxiv repository.
+The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res) and indicated that results available only via preprinted reports can contribute additional evidence to a meta-analysis.
+However, the scale of this contribution is questionable.
+Preprinted evidence was incorporated into only single meta-analysis, and in this case, inclusion of the preprint did not substantially impact the result.
 
-Of the three identified preprints, two were subsequently published as of September 2020.
-This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also nicely illustrates the dual advantages of preprinted reports to evidence syntheses.
+Of the three identified preprints, two were subsequently published as of September 2021.
+This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also illustrates the dual advantages of preprinted reports to evidence syntheses.
 
@@
 
-Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.
-A copy of this publication is available in Appendix \@ref(published-papers).[@hennessy2021] In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
-__[Zenodo repository will be cited here]__
+Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
+In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
+<!--- TODO GitHub repository will be cited here__ -->
 
@@
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-<!-- TODO Though this could --> In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This represents an important strength of this review, as the detailed risk of bias assessments are used in
+In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
+This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantiative triangulation analysis presented in Chapter \@ref(tri-analysis-heading).
 
@@
 The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter 4 (see Section \@ref(comparing-codelists)).
+An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter \@ref(cprd-analysis-heading) (see Section \@ref(comparing-codelists)).
 
@@
 One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased sensitivity must be balanced with a reasonable workload.
+Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased search sensitivity must be balanced with a reasonable workload.
 
@@
 
-<!-- TODO Clean-up! -->
+* In this chapter, I presented the results of a comprehensive systematic review of existing evidence on the association between lipid levels and dementia use.
+The review included both direct (studies that examined lipid levels directly) and indirect (studies examining lipid-lowering via treatments such as statins) forms of evidence.
+In contrast to previous reviews, I also included preprinted evidence, facilitated by the research tool introduced in Chapter \@ref(sys-rev-tools-heading).
 
-The results of this review are used to guide the primary analysis presented in Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-heading), by identifying outcomes and analytical techniques that are under-represented in the literature.
-In addition to forming a key evidence source used in the triangulation exercise presented in Chapter \@ref(tri-heading).
+* I found no consistent relationship across different evidence sources, though there was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia in non-randomised studies of interventions.
 
-<!-- COMMENT What do you mean guide. Design the SAP or the interpretation or both? -->
-
-In this chapter I have presented a comprehensive systematic review of the different sources of evidence available which examined the relationship between lipid levels and dementia use.
-
- and findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias; while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the cumulative effect measures calculated here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
-
-<!-- IDEA Link here to IPD, talking about how the meta-regression on key variables suggested the use of sex and age as key variables-->
+* The findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias and provided evidence on an under-studied outcome (vascular dementia); while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data ; finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
 

### 2021-11-29 05-Chp-CPRD-Analysis.Rmd
Working version!

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = FALSE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:cprdquote)', echo = TRUE}
 When dealing with human beings controlled experiments frequently prove to be impracticable, so for a scientific basis for our assumptions we turn to past history to reconstruct the suspected causal chain of events - and then our statistical troubles may begin.

### 2021-11-29 08-Discussion.Rmd
Working version!

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = FALSE}
 Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
@@
 
-(ref:intro-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]
+(ref:discussion-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]
 

### 2021-11-29 R/helper.R

@@ -708,7 +708,6 @@ get_all_citations <- function() {
   
 }
 
-
 get_citations_per_analysis <- function(data){
   
   if (is.grouped_df(data)) {

### 2021-11-30 01-Chp-Background.Rmd
Back to clean, working version

@@
 Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@Pagen71; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
+[@page2021; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
 

### 2021-12-02 03-Chp-Systematic-Review-Methods.Rmd
End of day:

@@
 Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
-Well-performed reviews involve multiple steps including: searching of existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
+Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
 
@@
 In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
-The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading.)
+The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).
 
@@
 
-Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but  report relevant unpublished analyses.
+Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses.
 As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
 
-Given the size of the review, I have seperated the methods and results into two chapters for ease of reading.
-This chapter details the methodology used, while CHapter \@ref(sys-rev-results-heading) presents the results of the review.
+Given the size of the review, I have separated the methods and results into two chapters for ease of reading.
+This chapter details the methodology used, while Chapter \@ref(sys-rev-results-heading) presents the results.
 
@@
 
-I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase of a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
-I also aimed to include studies examining the effect of treatments that modify blood lipid levels, such as statins or fibrates, as a source of indirect evidence.
+I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
+I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence.
+LRA are treatments used to modify blood lipids levels, and common examples include statins, fibrates, and ezetimibe.
 
-Eligible study designs were randomized controlled trials, non-randomized studies of exposures, non-randomised studies of  , longitudinal studies examining the effect of increased/decreased blood lipid levels, and genetic instrumental variable (Mendelian randomization) studies examining the effect of genetically increased/decreased blood lipid levels.
+Eligible study designs were randomized controlled trials of LRA, cohort studies examining blood lipids or LRA, and genetic instrumental variable studies (more commonly known as Mendelian randomization studies) examining the effect of genetically increased/decreased blood lipid levels.
 
@@
 Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate using meta-regression.
+Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate.
 No limits were placed on the sample size of included studies.
-
-Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the exception to this, as it was assumed that a valid criteria was employed when entering used when entering the outcome into the EHR.
-
-<!-- COMMENT Isn’t more true to say it was assumed that a health care professional had made the diagnosis (unlikely to use specific criteria) -->
+Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering used when entering the outcome into the EHR.
 
@@
 No limitations were imposed on publication status, date, venue or language.
-
-<!-- TODO Cite Peter Tennant's piece here on the problems with causal inference from analysis of change scores -->
 
@@
 
-Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status, were eligible for inclusion.
+Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion.
 Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
 MoCA score) without an attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia).
-Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
+no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
 
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging), studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arms (e.g.
-for example, a study examining exercise + statins vs statins alone, but a study examining exercise + statins vs exercise alone would be included), and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
 below the age of 50) were excluded.
-Finally, studies using a dietary intervention, for example omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
-Note, this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
+Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded.
+For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated.
+Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
+Note that this is distinct from studies which delivered a simple tablet-based omega-3 intervention, which would have been eligible for inclusion.
 
@@
 I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+The following databases were searched in June 2019 from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
 As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
@@
 
-When searching the bibliographic databases, study design filters were employed to try and reduce the screening load.
+When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try and reduce the screening load.
 To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
@@
 <!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing"[@greenhalgh2005; @wohlin2014]).
+Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing").[@greenhalgh2005; @wohlin2014]
 
@@
 
-Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records identified I identified as being difficult to assess against the inclusion criteria were screened in duplicate.
+Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records I identified as being difficult to assess against the inclusion criteria.
 Reasons for exclusion at this stage were recorded.
@@
 A PRIMSA flow diagram was produced to document how records moved through the review.[@page2021]
-
-The criteria against which records were assessed for eligibility are presented above.
 
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of less than .9), a larger proportion of records would have been dual-screened.
+If this assessment demonstrated issues with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.
 
@@
 Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author list, journal), study characteristics (study location, data source, exposure, outcomes, outcome criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
+Extracted items included: article metadata (year of publication, author, journal), study characteristics (study location, data source, exposure, outcomes, diagnostic criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
 I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
@@
 
-Where additional data points not included in the report of an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
+Where additional data not reported by an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
 This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
@@
 
-A key aim of the review presented in this chapter is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
-To enable this triangulation exercise, a detailed and structured risk-of-bias assessment formed an important part of this review.
+A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
+To enable this triangulation exercise, detailed and structured risk-of-bias assessment formed an important part of this review.
 
@@
 
-This move was prompted by an unclear definition of "methodological quality" which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the focus shifted from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-<!-- TODO CITATION NEEDED -->
-Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.
+This move was prompted by an unclear definition of methodological quality which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
+<!-- TODO CITATION NEEDED --> As part of this shift, the focus moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+<!-- TODO CITATION NEEDED --> Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.
 For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
-In this case, missing outcome data that are not an issue at six months may introduce bias after two years of follow-up, and assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
+In this case, the proportion of missing outcome data may not be an issue at six months but may introduce bias after two years of follow-up.
+In this case, assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
 
@@
 
-Randomized controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
+Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
 Acceptable judgements for each domain include: "low risk", "some concerns", "high risk".
@@
 For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result.
-Similar to RoB 2, it has a number of prompting questions per domain, with acceptable judgements including “low risk”, “moderate risk”, “serious risk” and “critical risk”.
+Similar to RoB 2, it has a number of signaling questions which inform the domain-level judgement, with acceptable judgements including “low”, “moderate”, “serious” and “critical”.
 In the context of the tool, observational studies are assessed in reference to an idealised randomised controlled trial.
-Under this approach, the (rare) overall judgement of "Low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.
+Under this approach, the (rare) overall judgement of "low" indicates that the results should be considered equivalent to that produced by a randomised controlled trial.
 
-While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] but was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
+While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
 Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
-The motivation using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
+The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
 In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
@@
 Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
-Acceptable judgements for each of the 5 domains in the tool included "low", "moderate" and "high" risk of bias.
+Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.
 
@@
 In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
-This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool, and provided feedback to the developers.
+This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.
 
@@
 The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
-Analysis are presented seperately for each dementia type of interest.
+Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Random-effects meta-analysis
 
-I used a random-effects model in all meta-analysis presented in this chapter.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
-The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
-
+I used a random-effects model in all meta-analyses.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
+The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of the variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
 Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:
@@
 
-Results were stratified into subgroups on the basis of the overall risk of bias assessment, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
+Results included in a meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
-Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.
+Finally, where at least 10 results are available, a test of subgroup differences between studies at different levels of risk of bias was performed (see subsequent Section \@ref(sys-rev-visualising-results)).[@deeks2019] All models were implemented using the `metafor` R package.[@R-metafor]
 
@@
 --> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
-In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories for lipid levels.
+In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.
 This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.
@@
 
-I took a two-stage dose-response meta-analysis approach, where study-specific trends are estimated before being pooled acrosss studies.[@greenland1992] To estimate within-study trends, a restricted cubic spline model was fitted within each to allow for a non-linear relationship between lipid levels and dementia, for example a U or J-shaped relationship, where low and high levels of a lipid fraction can have different effects versus the "normal" reference dose.[@durrleman1989;@liu2009] <!-- TODO CITATION NEEDED -->
-Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
+I took a two-stage dose-response meta-analysis approach, where study-specific trends are estimated before being pooled across studies.[@greenland1992] To estimate within-study trends, a restricted cubic spline model was fitted within each study.
+This approach allows for a non-linear relationship between lipid levels and dementia, for example a U or J-shaped relationship, where low and high levels of a lipid fraction can have different effects versus the "normal" reference dose.[@durrleman1989;@liu2009] Reference doses were defined _a priori_ as the cut-off of the "Normal"/"Optimal" categories for each fraction, as detailed in Table \@ref(tab:lipidLevels-table).
 Under this approach, the reference dose was defined as 200 mg/dL for total cholesterol, 100 mg/dL for LDL-c, 40 mg/dL for HDL-c, and 150 mg/dL for triglycerides.
 
-Restricted cubic spline models use "knots" to create separate the data into subsets or "windows", in which the trend is modelled.
-Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]
+Restricted cubic spline models use "knots" to separate the data into subsets or "windows", in which the trend is modelled.
+Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]
 
@@
 
-One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond.
+This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.
 
@@
 
-* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and treatments for lowering blood lipids.
+* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and lipid-regulating agents.
 
-* I have highlighted how this review will make use of preprinted literature, using the research tool introduced in the preceding chapter (Chapter \ref(sys-rev-tools-heading)).
+* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies.
+Additionally, I have highlighted how this review will examine the impact the of including preprinted results, as enabled by the research tool presented in the previous chapter.
 
-* In the following chapter, I presented the results of this comprehensive systematic review and detail how the identified evidence is used throughout the remainder of the thesis.
+* In the following chapter, I present the results of this review, and detail how the identified evidence is used throughout the remainder of the thesis.
 

### 2021-12-02 04-Chp-Systematic-Review-Results.Rmd
End of day:

@@
 
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-## Lay summary
-
-Using the methods outlined in the previous chapter, this chapter presents a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
-In addition, it examined the relationship betweeen treatments that change blood lipid levels, such as statins, and dementia outcomes
-
-My review included `r n_included` primary studies that contained information on this relationship.
-I found that statins appear to reduce the risk of Alzheimer's disease, but had no effect of vascular dementia.
-Lipid levels were not associated with any outcome.
-The methods used in some of the primary studies meant that I was less confident in their results.
-
-The added value of including preprinted study reports, made possible using the tool described in the Chapter \@ref(sys-rev-tools-heading), along with the use of the results of this review in subsequent chapters, is discussed.
+::: {.laybox data-latex=""}
+## Lay summary {-}
+
+Using the methods outlined in the previous chapter, here I present  the results of a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
+In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes
+
+My review included `r n_included` primary studies.
+I found that statins appear to reduce the risk of all-cause dementia and Alzheimer's disease, but were not associated with risk of vascular dementia.
+Lipid levels were not associated with any dementia outcome.
+However, problems with the methods used in some studies included in the review meant that I was less confident in their results.
+In addition, I found that several results were missing from my analysis as authors decided not to report them.
+
+:::
+
+<!-- TODO Complete! -->
 
@@
 
-## Results
+Following the methods outlined in the previous chapter, here I present the results of the comprehensive systematic review.
+The use of the evidence identified by the review in future chapters is discussed.
+Finally, I make recommendations for future methodological work around the inclusion of preprints and Mendelian randomisation studies in evidence synthesis exercises.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Search results
 
@@
 Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
-Many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
+As expected, many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
 <!-- TODO include some example citations here -->
@@
 
-The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described in the previous chapter (presented in grey on the right of the diagram).
-
-Common reasons for exclusion at the full text-stage included studies that reported on ineligible exposures (n = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (n=24; e.g.
-change in cognitive scores) or used an ineligible study design (n= `r n_study_design`).
+The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig) illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described previously (presented in grey on the right of the diagram).
+
+Common reasons for exclusion at the full text-stage included studies reporting on ineligible exposures (N = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
+change in cognitive scores), or usin an ineligible study design (N = `r n_study_design`).
 
@@
 
-```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="H", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
+```{r prisma-flow-fig, echo = FALSE, results="asis", fig.pos="h", fig.cap='(ref:prisma-flow-cap)', out.width='100%', fig.scap='(ref:prisma-flow-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/prismaflow.png"))
@@
 
-For the assessment of the intra-/inter-rater reliability, the estimated values of $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the assessment of the intra-/inter-rater reliability, the estimated values of Gwet's $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
 For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
@@
 
-Those records which were excluded in the initial screening, but were included by the second reviewer (n=`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and the definition of eligible lipids fractions.
+Those records which were excluded in the initial screening, but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and of eligible lipids fractions.
 
@@
 
-Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in the review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
-
-The majority of included studies described non-randomised analyses, with the sole two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS) leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
+Following full-text screening, `r n_included` unique studies (described across `r n_reports_included` reports) met the criteria for inclusion in this review.`r get_all_citations()` Table \@ref(tab:studyCharacteristics-table) presents a summary of the characteristics of each study.
+
+The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS), leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
 
@@
 
-<!-- TODO Enrure all abbreviations at the end of this table are in the abbreviation section at the start. -->
+<!-- TODO Ensure all abbreviations at the end of this table are in the abbreviation section at the start. -->
 
@@
 
+## Primary analyses
+
+In the following sections, analyses are grouped first by outcome (all-cause dementia, Alzheimer's disease and vascular dementia) and then are further stratified by exposure category.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### All-cause dementia {#sys-rev-res-Dementia}
+
+#### Statins
+
+```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+
+(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia.
+D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond in each forest plot presented above.
+
+(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
+
+```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
+```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+
+(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
+
+```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
+This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
+
+&nbsp; <!---------------------------------------------------------------------->
+
+#### Fibrates
+
+```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
+
+(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
+
+```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+#### Lipids
+
+<!-- TODO Deal with awkward hypercholesterolemia definition -->
+
+Across all outcomes, lipid levels were categorised in a number of ways.
+The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
+
+`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
+
+(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
+
+```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
+Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
+Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.
+
+(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
+```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Alzheimer's disease {#sys-rev-res-AD}
+
+#### Statins
+
+There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+
+(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
+
+```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Two Mendelian randomisation studies looked at lipid-lowering specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
+Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+#### Lipids
+
+`r num_to_text(obsHyperchol$AD$n,T)` studies reported on the association of hypercholesterolemia with Alzheimer's disease and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
+
+(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
+
+```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
+Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
+
+<!-- TODO This should also show Raffatin! -->
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsAD-cap)  Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
+Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.
+
+(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
+
+```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
+However, all of these studies took a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
+Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
+However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
+
+(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
+
+```{r mrDuplicationSetup, include=FALSE}
+```
+
+```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
+knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+### Vascular dementia {#sys-rev-res-VaD}
+
+#### Statins
+
+As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
+There were no available randomised trials for this outcome.
+`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
+
+(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia
+
+```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided some evidence for an effect (`r mrStatin$VaD$estimate`).
+
+<!-- TODO Might need to discuss this a bit further -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Lipids
+
+`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+
+(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
+
+```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Few studies investigated the effect of individual lipid fractions.
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL,F)`), HDL-c (`r n_effect(obsLipids$VaD_HDL,F)`) or triglycerides (`r n_effect(obsLipids$VaD_TG,F)`).
+
+<!-- TODO This is not technically - more studies available on vascular dementia -->
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
+
+```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, no Mendelian randomisation analyses examining the effect of genetically determined lipid levels on vascular dementia risk were identified.
+
+&nbsp;
+
 ### Risk of bias {#risk-of-bias-res}
@@
 
-As discussed above, the risk-of-bias assessments are presented alongside their corresponding numerical result.
-A more detailed discussion of the sources and directions of bias is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
+As shown in the forest plots in the above sections, the risk-of-bias assessments are presented alongside their corresponding numerical result.
+A more detailed discussion of the sources and directions of bias in each result is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
 
 For the two randomised controlled trials, both were judged to be at low risk of bias.
-In contrast, many of the non-randomised studies of statin use were at serious risk of bias due poor controlling for confounding, immortal time bias, and missing outcome data (as noted above, a judgement of low risk of bias for a non-randomised study is rare).
+In contrast, many of the non-randomised studies of statin use were at serious risk of bias primarily due to poor controlling for confounding, immortal time bias, and missing outcome data.
 Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g.
@@
 
-Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.
-<!-- TODO CITATION NEEDED --> `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
+Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.[@sterne2016] `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
 the study reported unadjusted estimates).`r critical_citations`
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### All-cause dementia {#sys-rev-res-Dementia}
-
-#### Statins
-
-```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia
-
-(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
-&nbsp;<!----------------------------------------------------------------------->
-
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
-This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
-
-&nbsp; <!---------------------------------------------------------------------->
-
-#### Fibrates
-
-```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
-```
-
-`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
-
-(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-#### Lipids
-
-<!-- TODO Deal with awkward hypercholesterolemia definition -->
-
-Across all outcomes, lipid levels were categorised in a number of ways.
-The most common categorisation was hypercholesterolemia at baseline, defined most frequently as a total cholesterol measurement of greater than 6.5 mmol/L.
-
-`r num_to_text(obsHyperchol$Dementia$n,T)` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$Dementia$estimate`, Figure \@ref(fig:obsHyperDementia)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
-
-(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
-
-```{r obsHyperDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperDementia-cap)', out.width='100%', fig.scap='(ref:obsHyperDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-<!-- TODO The number of studies in the inline text refer to the number of studies rather than the number of results.
-Note here that Tynkkyen examine multiple cohorts, which were extracted individually rather than as part of the reported meta-analysis.
--->
-
-Several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsDementia)).
-Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$Dementia_TC)`), LDL-c (`r n_effect(obsLipids$Dementia_LDL)`), HDL-c (`r n_effect(obsLipids$Dementia_HDL)`) and triglycerides (`r n_effect(obsLipids$Dementia_TG)`).
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesteol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
-```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_Dementia.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Alzheimer's disease {#sys-rev-res-AD}
-
-#### Statins
-
-There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
-
-(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
-
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Two Mendelian randomisation studies looked at lipid-lowering specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
-
-```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-#### Lipids
-
-`r obsHyperchol$AD$n` studies reported on the association of hypercholesterolemia with all-cause dementia and provided weak evidence for an effect (`r obsHyperchol$AD$estimate`, Figure \@ref(fig:obsHyperAD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
-
-(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
-
-```{r obsHyperAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperAD-cap)', out.width='100%', fig.scap='(ref:obsHyperAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_AD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Similarly to all-cause dementia, several studies analysed individual lipid fractions by estimating the risk of dementia per 1 standard deviation increase in that fraction (Figure \@ref(fig:lipidFractionsAD)).
-Weak evidence for an effect on all-cause dementia was found for total cholesterol (`r n_effect(obsLipids$AD_TC)`), LDL-c (`r n_effect(obsLipids$AD_LDL)`), HDL-c (`r n_effect(obsLipids$AD_HDL)`) or triglycerides (`r n_effect(obsLipids$AD_TG)`).
-
-<!-- TODO This should also show Raffatin! -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap) Random-effects meta-analysis of LDL on vascular dementia risk, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
-
-```{r lipidFractionsAD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_lipids_composite_AD.pdf"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
-However, all of these studies used a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
-Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
-However, across all analysis, using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
-
-<!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
-Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
-
-(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
-
-```{r mrDuplicationSetup, include=FALSE}
-```
-
-```{r mrDuplication, echo = FALSE, results="asis", fig.pos = "H", fig.align='center', fig.cap='(ref:mrDuplication-cap)', out.width='80%', fig.scap='(ref:mrDuplication-scap)'}
-knitr::include_graphics(file.path("figures","sys-rev","mrDuplication.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-### Vascular dementia {#sys-rev-res-VaD}
-
-#### Statins
-
-As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
-There were no available randomised trials for this outcome.
-`r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
-
-(ref:obsStatinVaD-scap) Random-effects meta-analysis of statins on vascular dementia
-
-```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided weak evidence for an effect (`r mrStatin$VaD$estimate`).
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Lipids
-
-`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
-
-(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
-
-```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
-A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL)`), HDL-c (`r n_effect(obsLipids$VaD_HDL)`) or triglycerides (`r n_effect(obsLipids$VaD_TG)`).
-
-<!-- TODO This is not technically - more studies available on vascular dementia -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
-
-```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, no Mendelian randomisation analyses examining the effect of genetically determined lipid levels on vascular dementia risk were identified.
-
-&nbsp;
-
-### Dose response meta-analysis of lipid levels {#dose-response-results}
-
-<!-- TODO Use the example of getting the cut-off points from the authors as an illustration of how reporting sucks -->
-
-```{r doseResponse, include = FALSE}
-```
-
-There were `r n_dr_initial` studies that were eligible for dose-response meta-analysis as they provide several categories of lipid exposure.
-However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
-
-Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of studies (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
-This analysis provided weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
-Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
-
-<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
-
-(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
-
-```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:lipidsDoseResponse-cap)', out.width='70%', fig.scap='(ref:lipidsDoseResponse-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/dr_AD_TC.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Additional analyses
-
-Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, few meta-analysis included more than 10 results, the recommended minimum required for meta-regression.
-Secondly, poor reporting of summary statistics including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
-
-Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
-
-Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
-However, all analyses assessed provided weak evidence of small-study effects.
-
-<!-- TODO [_Note: Julian, is this sufficient or should I report statistics for each? Additionally, are there any other sensitivity analyses I should be presenting here?_] -->
-
-<!-- One particularly interesting meta-bias potentially applicable in this review is the definition of code lists across -->
-
-<!-- Many studies using large observational electronic health records (n=?) did not report the code-lists used define the outcome events in their analysis.
-Depsite attempts to obtain this additional information through contact with a -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-&nbsp;
-
-### Missing evidence
 
@@
 
+## Additional analyses
+
+### Dose response meta-analysis of lipid levels {#dose-response-results}
+
+```{r doseResponse, include = FALSE}
+```
+
+There were `r n_dr_initial` studies initially considered eligible for the dose-response meta-analysis, as they appear to provide data on risk of dementia outcomes across several categories of lipid exposure.
+However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
+
+Across the remaining `r num_to_text(n_dr_final)` studies, a sufficient number of results (n $\geqslant$ 3) were identified only for the total cholesterol-Alzheimer's, LDL-Alzheimer's, and total cholesterol-dementia strata.
+This analysis provided weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
+Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
+
+<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
+
+<!----------------------------------------------------------------------------->
+(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
+
+(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
+
+```{r lipidsDoseResponse, echo = FALSE, results="asis", fig.pos = "H",fig.align='center', fig.cap='(ref:lipidsDoseResponse-cap)', out.width='70%', fig.scap='(ref:lipidsDoseResponse-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/dr_AD_TC.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Heterogeneity and publication bias
+
+Investigation of potential sources of heterogeneity was complicated by two factors.
+In the first instance, a minority of meta-analysis (4 out of 18, `r paste0(comma(4/18*100),"%")`) included more than 10 results, the recommended minimum required for meta-regression.
+Secondly, poor reporting of study characteristics of interest including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
+
+<!-- TODO Finish this analysis -->
+
+Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
+
+Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
+However, all analyses assessed provided weak evidence of small-study effects.
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Added evidential value of including preprints {#sys-rev-including-preprints-res}
 
-As show in Figure \@ref(fig:prisma-flow-fig), the number of hits returned by the preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
+As show in the PRISMA flow diagram (Figure \@ref(fig:prisma-flow-fig)), the number of hits returned by preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
 From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
 
-One preprint (So _et al_[@so2017]) provided additional evidential value in a single meta-analysis (`r comma(1/18*100)`% of all meta-analyses performed in this chapter).
-This meta-analysis of Mendelian randomisation studies examined the effects of lipid-lowering via HMGCR mutations on incidence of Alzheimer's disease (Figure \@ref(fig:mrStatinADFig).
-To assess the evidence added to the meta-analysis through inclusion of the preprint, the data were re-analysed using a fixed-effect model.
+One preprint (So _et al_[@so2017]) provided additional evidential value in a single meta-analysis (`r comma(1/18*100)`% of the 18 meta-analyses performed in this chapter).
+This meta-analysis of Mendelian randomisation studies examined the effects of lipid-lowering via HMGCR mutations on incidence of Alzheimer's disease (Figure \@ref(fig:mrStatinADFig)).
+To assess the evidence added to the meta-analysis through inclusion of the preprint, the data was re-analysed using a fixed-effect model.
 Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
-However, the inclusion of the preprinted study did not have a substantial impact on the results (`r mrStatin$AD$estimate`) versus the single published study (`r estimate(0.59,0.25,1.39,"RR")`).
+However, the inclusion of the preprinted study did not have a substantial impact on the result of the meta-analysis (`r mrStatin$AD$estimate`) as compared to that reported by the single published study (`r estimate(0.59,0.25,1.39,"RR")`).
 
 The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLCC and IGAP consortia.
-As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add to the evidence base.
+As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add to new information to the evidence base.
 
@@
 
-Investigation of the publication status of the two preprints reporting studies not also identified by the main search after a two-year lag found that one had been subsequently published in late 2019.[@andrews2019; @andrews2021] The final preprint has not yet been published.[@so2017]
+Investigation of the publication status of the two preprints reporting studies not also identified by the main search found that, allowing for a two-year lag, only one had been subsequently published.[@andrews2019; @andrews2021]
 
@@
 <!-- TODO Check inclusion of Rockwood 2002:  -->
-This review has presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+This review presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
 This discussion seeks to summarise the key findings in terms of literature sources and results as reported.
@@
 There was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of heterogeneity in exposure (e.g.
+This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of differing exposure windows (e.g.
 mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
@@
 
-Across dementia outcomes, the majority of studies were non-randomised studies of lipids, or treatments that affect lipid levels such as statins.
+Across dementia outcomes, the majority of studies were non-randomised studies of lipids or lipid regulating agents.
 This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the long follow-up made necessary by the long latent period of the condition, makes trials logistically challenging and financial expensive.
-Similarly, Mendelian randomisation is a comparatively new study design (as illustrated in Figure \@ref(fig:typeByYear)), which appears in the literature in recent years, driven by the availability of summary genome wide association studies (GWAS) that form the basis of the two-sample Mendelian randomisation approach.
+Randomised controlled trials of dementia are particularly challenging, as the follow-up made necessary by the long latent period of the condition makes trials logistically difficult and financial expensive.
+Similarly, Mendelian randomisation is a comparatively new study design, and studies employing it in relation to dementia outcomes only appear in the evidence base in recent years, as illustrated in Figure \@ref(fig:typeByYear).
+This recent increase is likely driven by the availability of summary genome wide association studies (GWAS) that form the basis of the two-sample Mendelian randomisation approach.
 
@@
 
-A common theme was an absence of studies examining vascular dementia as an outcome, most noticeable when comparing the evidence base for statins in dementia/Alzheimer's (Figures \@ref(fig:obsStatinDementiaFig) & \@ref(fig:obsStatinADFig)) with that available for vascular dementia (Figure \@ref(fig:obsStatinVaDFig)).
+A central finding of this review is the absence of studies examining vascular dementia as an outcome, most noticeable when comparing the evidence base for statins in dementia/Alzheimer's (Figures \@ref(fig:obsStatinDementiaFig) & \@ref(fig:obsStatinADFig)) with that available for vascular dementia (Figure \@ref(fig:obsStatinVaDFig)).
 This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
-A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was weak evidence of a small-study effects for this outcome (of which publication bias is a potential cause).[@sterne2011] Similarly, only one Mendelian randomisation studies examined this outcome, primarily because of the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
-
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on CVD risk, reporting on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
+A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was weak evidence of a small-study effects for this outcome (of which publication bias is one potential cause).[@sterne2011] Similarly, only one Mendelian randomisation study examined this outcome, likely due to the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
+
+Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on cardiovascular disease risk and reported on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
+Though a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
 As such, this trial did not meet the inclusion criteria for this review.
@@
 
-Risk of bias across the individual results was generally quite high.
+Risk of bias across the individual results was generally high.
 The causes and expected impact of these biases on the results are discussed in more detail in Chapter \@ref(tri-heading).
 Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of lipid levels.
-In many cases, estimates were known to be missing from meta-analyses not at random due to preferential reporting of significant results observed in a number of analysis, leading to the high-risk judgement.
+In many cases, estimates are known to be missing not at random from meta-analyses due to preferential reporting of significant results, leading to high risk of bias due to missing evidence.
 These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
 "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
-were not reported in the table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence for an effect), other than increasing the precision of the summary estimate.
-
-Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of studies which made use of data from the Taiwan health insurance database.
+were not reported in the table."[@ancelin2013]).
+However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence for an effect), other than increasing the precision of the summary estimate.
+
+Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of several studies which made use of data from the Taiwan health insurance database.
 
@@
 
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
+<!-- TODO Check none of these use a ROB tool -->
+
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
 The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
@@
 
-Despite these differences in timescales and methodology, the duplication of work across reviews (including this review) is substantial.
-In retrospect, an alternative approach to conducting a further systematic review from scratch could have been employed.
-Known as an umbrella review, or review-of-reviews, these studies use other systematic reviews rather than primary studies as the unit of analysis.[@aromataris2015; @smith2011] This approach would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart from other published reviews could have been applied.
+Despite these differences in time scales and methodology, the duplication of work across systematic reviews (including this one) is substantial.
+In retrospect, an alternative approach to conducting a further systematic review from scratch, known as an umbrella review or review-of-reviews,[@aromataris2015; @smith2011] could have been employed.
+This study design uses other systematic reviews rather than primary studies as the unit of analysis, and would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart could have been applied.
 
@@
 
-todo
-
 <!----------------------------------------------------------------------------->
@@
 As such, the process and tools for systematically assessing this study design are not as well developed.
-A key example of this is in the absence of validated search filters for Mendelian randomisation studies.
-This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of it's application, which led to me including general terms for instrumental variable analyses in my search.
+A key example of this is the absence of validated search filters for Mendelian randomisation studies.
+This limitation is further complicated by the varying terminology used to describe the method, particularly in the early years of its application, which led to me including general terms for instrumental variable analyses in my search.
 
 Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] While reporting quality is an important consideration, as reflected by the recent release of a STROBE_MR reporting guidelines,[@skrivankova2021] it is a separate consideration to internal validity  as discussed in Section \@ref(risk-of-bias).
-Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was validated to assess the quality of genetic association studies in meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not assess the additional methodological considerations of the Mendelian randomisation analysis itself.
+While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] Reporting quality is an important consideration for Mendelian randomisation studies, as reflected by the recent release of a STROBE MR reporting guidelines,[@skrivankova2021] but is a separate consideration to bias, as discussed in Section \@ref(risk-of-bias).
+Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was designed to assess the quality of GWAS included in a meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not address the additional methodological considerations of the Mendelian randomisation analysis itself.
 For this review, I used the best available author-devised tool, sourced from a recent review of systematic reviews of Mendelian randomisation studies.[@spiga2021]
 
-As a further stumbling block, Mendelian randomisation, particularly when using a two-sample summary data design, is a form of analysis that lends itself to multiple exposure-outcome comparisons.
+As a further stumbling block, Mendelian randomisation lends itself to the analysis of multiple exposure-outcome comparisons as part of a single study, particularly when using a two-sample summary data design.
 This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been identified by the search strategy.[@larsson2017] On review of this paper, the search would not have been expected to find it given the absence of any lipid-related keywords in the title and abstract.
-The study examined the association between lipid fractions with Alzheimer's disease as one of many risk factors for the condition.
-Studies such as this can introduce bias into a systematic review, as it is commonly only those risk factors that show a statistically significant result that are reported in the abstract and so are captured by the search.
-This may bias systematic reviews, including this one, as the analysis of multiple risk factors against a single outcome within a single publication becomes more common.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
-
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a dedicated search for "risk factors" and "dementia" and "Mendelian randomisation" followed by manual review of studies that look across multiple risk factors would be advisable.
-This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (n=`r comma(16109)`).
-Additionally, the value of methods that supporting the traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts should not be underestimated.
-Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit to the field.
-
-One item of particular interest is the attenuation of any effects observed by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As covered in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease, and so violates the exclusion restriction criteria (Figure \@ref(fig:mrAssumptions)).
-In all cases, excluding these variants attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where the ApoE variants were not sufficient identified and excluded and the published paper detailed evidence for a protective effect of LDL-c was identified (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed excluding a larger area around ApoE4 which attenuated the finding to the null.[@benn2017comment]
+As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been captured by the search strategy.[@larsson2017] This study examined lipid fractions as one of many risk factors for Alzheimer's disease, though the search would not have been expected to find it given the absence of any lipid-related keywords in the title or abstract.
+Studies examining multiple risk factors such as this can introduce bias into a systematic review, as it is commonly only those risk factors with statistically significant result that are reported in the abstract and so are captured by a systematic search.
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are considered to be particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
+
+Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a broader search (e.g.
+"risk factor" AND "dementia" AND "Mendelian randomisation") followed by manual review of studies that examined multiple risk factors would be advisable.
+This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (N = `r comma(16109)`).
+Additionally, the value of methods that support traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts, should not be underestimated.
+Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit.
+
+One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
+As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
+In all cases, excluding variants in the ApoE region attenuates the observed effect to the null.
+A clear example of this is Benn _et al_ (2017), where ApoE variants were not sufficient identified and excluded, leading the published paper to report a protective effect of LDL-c on Alzheimer's (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed to exclude a larger area around ApoE which attenuated the finding to the null.[@benn2017comment]
 
@@
 Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint servers related to health and biomedical sciences were searched as part of this review.
-The small number of studies returned by the searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is due to the timing of the preprint searches.
+The small number of studies returned by the preprint searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is largely due to the timing of the preprint searches.
 The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
-As such, at the point it was searched, the medRxiv database contained only a very small number of records (n=`r n_at_search["med"]`).
-
-<!----------------------------------------------------------------------------->
+As such, at the point it was searched, the medRxiv database contained only a very small number of records (N = `r n_at_search["med"]`; Figure \@ref(fig:preprintGrowth)).
+
+&nbsp;<!----------------------------------------------------------------------->
+
 (ref:preprintGrowth-cap) Growth of preprint repositories over time.
-Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv n= `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
+Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
 
@@
 
-Three relevant preprints from the bioRxiv hits were identified.
-Of note, all three described Mendelian randomisation studies, potentially indicating that more biologically focused study designs are over-represented in the bioRxiv repository.
+Three relevant preprints from bioRxiv were identified.
+Of note, all three described a Mendelian randomisation study, potentially indicating that more biologically-focused study designs are over-represented in the bioRxiv repository.
 The added evidential value of including these preprints was described in Section \@ref(sys-rev-including-preprints-res) and indicated that results available only via preprinted reports can contribute additional evidence to a meta-analysis.
 However, the scale of this contribution is questionable.
-Preprinted evidence was incorporated into only single meta-analysis, and in this case, inclusion of the preprint did not substantially impact the result.
+Preprinted evidence was incorporated into only single meta-analysis in this review, and inclusion of the preprinted result did not substantially impact the summary effect estimate.
 
 Of the three identified preprints, two were subsequently published as of September 2021.
-This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published, and also illustrates the dual advantages of preprinted reports to evidence syntheses.
-
+This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
+It also illustrates the dual advantages of preprinted reports to evidence syntheses.
 Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
-Consider the example of one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise as is the case with the second preprint included in this review.[@so2017] Both of these aspects illustrate that, if the aim is to find the current state of the art in the topic area at the time of searching, inclusion of preprints is a necessity.
-
-More recently, inclusion of preprints in systematic reviews has become significantly more widespread.
+For example one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise, as is the case with a second preprint included in this review.[@so2017] Both of these aspects illustrate that inclusion of preprints is a necessity if the aim is to find all relevant literature on a topic at the time of searching.
+
+Recently, inclusion of preprints in systematic reviews has become significantly more widespread.
 This is largely due to the role of preprint servers, in particular medRxiv, as a key evidence dissemination venue during the early stages of the COVID-19 pandemic.[@fraser2020preprinting] How well this adoption of preprints will transfer to other less-urgent topics, where the speed of research does not put the same focus on preprinted articles, is currently unknown.
 
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-<!-- ### Comments on the process -->
-
-<!-- As part of the reflective element of this thesis, I collated my experiences on performing a systematic review. -->
-
-<!-- &nbsp; -->
-
-<!-- #### Protocol registration -->
-
-<!-- While the protocol was registered on the Open Science Framework largely to allow for the sharing of associated documents such as the proposed search strategy, anecdotal evidence from colleagues and collaborators suggested that the findability of the protocol was limited.
-In hindsight, I should also have cross-posted the protocol on PROSPERO, the international prospective register of systematic reviews,[@booth2011] (which does not allow for the uploading of related files).
--->
-
-<!-- &nbsp; -->
-
-<!-- #### Workload -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-<!-- &nbsp; -->
-
-<!-- #### People management -->
-
-<!-- This review provide an excellent opportunity to gain experience in managing a team of researchers.
-However, due to the need for dual screening and data extraction over a long period of time, a number of external researchers became involved in this review.
-I found the people-management aspect particularly challenging, and in retrospect could definitely have improved the process through better communication of expectations and deadlines.
--->
-
-<!-- &nbsp; -->
-<!----------------------------------------------------------------------------->
-
-<!-- ### Validation against recent umbrella review -->
-
-<!-- In summer 2020, an umbrella review (also known as a review-of-reviews) of the impact of lipids levels of Alzheimer's disease risk -->
-
-<!-- The study included XXX reviews and YYY primary studies, and I used this list of primary studies as an extra validation step to assess the accuracy of my work. -->
-
-<!-- Umbrella reviews follow a systematic review approach, but their unit of interest is other systematic reviews rather than primary studies.
-In fields where there is a lot of existing reviews, they -->
-
-<!-- All studies identified by reviews included in te -->
-
-<!-- In hindsight, this approach ma -->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
-In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers.
-<!--- TODO GitHub repository will be cited here__ -->
+In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers, via a GitHub repository.
+
+<!-- TODO Upload as part of thesis repo. -->
 
@@
 
-I believe there are several aspects where this review is distinct from those reviews already available in the published literature.
-While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not 100%.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-In addition, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantiative triangulation analysis presented in Chapter \@ref(tri-analysis-heading).
+I believe there are several aspects where this review is distinct from those already available in the published literature.
+While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not complete.
+As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no relevant study has been omitted.
+
+Secondly, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
+This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantitative triangulation analysis presented in Chapter \@ref(tri-analysis-heading).
 
@@
 
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity [@hsieh2019] [@mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity between effect estimates.
+The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity.[@hsieh2019; @mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity into the analysis.
 An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter \@ref(cprd-analysis-heading) (see Section \@ref(comparing-codelists)).
@@
 
-One particular limitation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed without the tool being finalised.
-This meant that there were no signaling questions to guide the domain-level risk-of-bias assessment, which may have influenced the accuracy with which domain-level judgements were assigned.
-However, there is no published empirical evidence supporting the need for signaling questions, and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
+One particular limitation with regards to the risk-of-bias assessment is the fact that the ROBINS-E assessments were performed using an adapted version of the ROBINS-I tool.
+This meant that there were no signaling questions to guide the domain-level risk-of-bias assessments, which may have influenced the accuracy with which the judgements were assigned.
+However, there is no published empirical evidence supporting the need for signaling questions and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
 In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
 
-One further limitation is the fact that the risk of bias due to missing evidence assessment, combined with some empirical evidence that some studies were missed by the search but contained relevant studies is a definite limitation of this review (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
-Unfortunately, this is probably a common limitation across all reviews, based on the way in which increased search sensitivity must be balanced with a reasonable workload.
+A final limitation is the potential for missing evidence on the basis of the results.
+Evidence for this limitation came from the ROB-ME assessments and was supported by empirical evidence that some studies containing relevant results were missed by the search (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
+Unfortunately, this is probably a common limitation across all systematic reviews, based on the way in which increased search sensitivity must be balanced with a manageable workload.
 
@@
 * In this chapter, I presented the results of a comprehensive systematic review of existing evidence on the association between lipid levels and dementia use.
-The review included both direct (studies that examined lipid levels directly) and indirect (studies examining lipid-lowering via treatments such as statins) forms of evidence.
+The review included both direct (studies that examined lipid levels directly) and indirect (studies examining lipid regulating agents such as statins) forms of evidence.
 In contrast to previous reviews, I also included preprinted evidence, facilitated by the research tool introduced in Chapter \@ref(sys-rev-tools-heading).
 
-* I found no consistent relationship across different evidence sources, though there was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia in non-randomised studies of interventions.
-
-* The findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias and provided evidence on an under-studied outcome (vascular dementia); while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data ; finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \ref(discussion-heading).
+* I found no consistent relationship between lipids or lipid-regulating agents and dementia across different evidence sources.
+However, there was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia in non-randomised studies of interventions.
+
+* The findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias and provided evidence on an under-studied outcome (vascular dementia); while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
 
 \newpage
-
-## References

### 2021-12-02 08-Discussion.Rmd
End of day:

@@
 
+\newpage
+
 ## Introduction
@@
 
-## Chapter summary
+\newpage
+
+### Chapter summary
 
@@
 
-## Summary of principle findings
+\newpage
+
+### Lessons learned
+
+As a reflective process throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing . here I present a more general rel
+
+In hindsight, the decision to take a broad approach to inclusion of dementia outcomes potentially resulted in larger workload than anticipated, particularly when considered evidence from across different study designs.
+In a do-over, I would have considered a single dementia outcome.
+
+Additionally, in hindsight, I may have considered a more methodological thesis. The Chapter's I enjoyed working on the most (Chapters \@ref())
+
+Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors
+
+However, normal opportunities to tie people down in person were suspended during COVID.
+
+<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
+Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
+-->
+
+<!-- Average time to complete a s -->
+
+<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
+
+&nbsp;<!----------------------------------------------------------------------->
+
+\newpage
+
+### Reproducible research
+
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
+In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+
+Unfortunately, given the.
+However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
+
+Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
+
+One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
+IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
+However, access is dependency on an ISAC application to the managing body of the CPRD.
+
+&nbsp;
+<!----------------------------------------------------------------------------->
+
+\newpage
+
+## Summary of clinical findings
+
+### Effect of blood lipids on dementia outcomes
 
 Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).
-
 While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
@@
 
-## New evidence
+\newpage
+
+### Comparison with new evidence
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
+\newpage
 
-## Summary of contributions
+### Implications for clinical practice
+
+This should focus on doctors being honesty with patients from the outset and describing what they know regarding the uncertainty of the evidence.
+
+While also recognising that the impact of statin or other LRA use on dementia is going to be secondary to their established effect on lipid-lowering.
+To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.
+
+The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
+Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
+
+However, even under the scenario that a strong protective effect was identified, whether or not to prescribed a statin at mid-life will always be guided by factors other than dementia prevention.
+Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early onset dementias), which is substantially less likely if hypercholesterolemia is left unchecked.
+
+However, while this thesis did not provide any evidence for a protective effect of lipid-lowering, it similarly did not provide any evidence for a harmful effect of statin exposure on dementia outcomes.
+
+There was very we. Conversely however, there was an absence of evidence for a harmful effect of statins on. Given the reality that given the choice, given the conflicting evidence
+
+As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for the condition.
+It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+\newpage
+
+### Implications for public health
+
+This section should
+
+The absence of an effect of blood lipids on dementia outcomes is an unh
+
+However, future work
+
+&nbsp;<!----------------------------------------------------------------------->
+
+\newpage
+
+## Summary of methodological findings
 
@@
 
-With respect to dementia epidemiology, the systematic review reported in Chapters
+### Preprint search tool
+\newpage
+
+### Inclusion of preprints
+\newpage
+
+### Risk of bias visualisation
+\newpage
+
+### Triangulation framework
 
@@
 
-## Lessons learned
-
-As a reflective process throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing . here I present a more general rel
-
-In hindsight, the decision to take a broad approach to inclusion of dementia outcomes potentially resulted in larger workload than anticipated, particularly when considered evidence from across different study designs.
-In a do-over, I would have considered a single dementia outcome.
-
-Additionally, in hindsight, I may have considered a more methodological thesis. The Chapter's I enjoyed working on the most (Chapters \@ref())
-
-Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors
-
-However, normal opportunities to tie people down in person were suspended during COVID.
-
-&nbsp;<!----------------------------------------------------------------------->
+\newpage
 
@@
 
-#### Strengths
+### Strengths
 
@@
 
-#### Weaknessess
+\newpage
+
+### Weaknessess
 
@@
 
-## Implications of this research
-
-### Clinical practice
-
-This should focus on doctors being honesty with patients from the outset and describing what they know regarding the uncertainty of the evidence.
-
-While also recognising that the impact of statin or other LRA use on dementia is going to be secondary to their established effect on lipid-lowering.
-To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.
-
-The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
-Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
-
-However, even under the scenario that a strong protective effect was identified, whether or not to prescribed a statin at mid-life will always be guided by factors other than dementia prevention.
-Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early onset dementias), which is substantially less likely if hypercholesterolemia is left unchecked.
-
-However, while this thesis did not provide any evidence for a protective effect of lipid-lowering, it similarly did not provide any evidence for a harmful effect of statin exposure on dementia outcomes.
-
-There was very we. Conversely however, there was an absence of evidence for a harmful effect of statins on. Given the reality that given the choice, given the conflicting evidence
-
-As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for the condition.
-It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Public health
-
-This section should
-
-The absence of an effect of blood lipids on dementia outcomes is an unh
-
-However, future work
-
-&nbsp;<!----------------------------------------------------------------------->
-
-## Reproducible research
-
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
-In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
-
-Unfortunately, given the.
-However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
-
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
-
-One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
-However, access is dependency on an ISAC application to the managing body of the CPRD.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
+\newpage
 
@@
 Several avenues for future research, building on the work presented here, are possible.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
+\newpage
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
+\newpage
+
+It is customary at this point to recommend that a large scale. However, based on the evidence described. In addition, logistical challenges in relation
+
+Opportunistic follow-up of established trials.
+
+&nbsp;<!----------------------------------------------------------------------->  
+\newpage
 
 ### Triangulation
-
-It is customary at this point to recommend that a large scale. However, based on the evidence described. In addition, logistical challenges in relation
 
@@
 <!----------------------------------------------------------------------------->
+\newpage
 

### 2021-12-02 front-and-back-matter/99-appendices.Rmd
Working version!
End of day:

@@
 
-<!-- TODO This needs to be split in two!  -->
+### Deviations from protocol
+
+<!-- TODO Complete -->
+
+* MR tool, actually used Mamluk
+
+* ROB-ME
+
+* No MCI, given size of dementia findings
+
+* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered seperate things here.[@sterne2013]
+
+ * Dose response
 
@@
 
-mx_data <- mx_api_content(to_date = "2019-09-01")
+mx_data <- mx_api_content(to_date = "2019-07-01")
 
 bx_data <- mx_api_content(server = "biorxiv",
-                                    to_date = "2019-09-01")
+                                    to_date = "2019-07-01")
 

### 2021-12-02 front-and-back-matter/_abstract.Rmd
End of day:

@@
-__Background__  
-In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
-by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
-the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
-reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
-between modifiable targets and dementia risk is central to the development of evidence-based prevention
-strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
-levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
-but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
+Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies.
+Blood lipid levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies, but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
+This thesis sought to triangulate the causal effects of lipid levels on dementia (all-cause dementia, Alzheimer's disease and vascular dementia) risk using existing and new evidence.
+
+I conducted four distinct analyses as part of this thesis.
+Firstly, a systematic review of 81 published and preprinted studies was used to summarise the existing evidence base.
+Preprinted studies were identified using a research tool developed as part of this thesis.
+I then supplemented the existing evidence via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD), and ii) an individual patient data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK.
+Finally, I used a novel quantitative triangulation framework to incorporate the results produced by the diverse methodological approaches while attempting to account for their respective biases and indirectness.
+
+Overall I identified no consistent effect of any lipid fraction on any dementia outcome across the evidence sources presented in this thesis, through there was some suggestion of a protective effect of LDL-c lowering (via statin use) on all-cause dementia and Alzheimer's disease, and a harmful effect of raised triglyceride levels on vascular dementia.
+However, when assessed through the triangulation framework, both of these effects attenuated to the null.
+There was a noticeable absence of existing studies considering vascular dementia as an outcome, and
+
+Future work should focus on defining

### 2021-12-02 01-Chp-Background.Rmd
End of day:

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:dara-quote)', echo = TRUE}
-Considering everything, it seems we are dealing
-here with a special illness.
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:alzheimer-quote)', echo = TRUE}
+Alles in allem genommen haben wir hier offenbar einen eigenartigen Krankheitsprozeß vor uns.
+
+~
+
+Considering everything, it seems we are dealing here with a special illness.
 ```
-(ref:dara-quote) --- Alois Alzheimer, 1907 [@alzheimer1907; @stelzmann1995]
+(ref:alzheimer-quote) --- Alois Alzheimer, 1907 [@alzheimer1907; @stelzmann1995]
 
@@
 
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
 
-<!-- TODO Contributor statements -->
+\newpage
 
-## Lay summary
+::: {.laybox data-latex=""}
+
+## Lay summary {-}
 
@@
 A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
-The aim of this thesis is to use all available evidence to assess whether blood lipids levels are in fact a risk factor for dementia.
+The aim of this thesis is to use all available evidence to assess whether blood lipid levels are in fact a risk factor for dementia.
+
+&nbsp;
 
@@
 
-<!----------------------------------------------------------------------------->
+:::
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
+<!--- No nb here ---------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
-
 ### Definition and underlying pathologies {#underlying-pathologies}
 
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] cumulating in reduced motor control that affects patients ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
+Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] culminating in reduced motor control that affects patients' ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
 
 Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.
-Characterised by substantial cognitive impairment and difficulty with high level executive function to the extent that it interferes with, it is an insidious disease, within initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
+Characterised by substantial cognitive impairment and difficulty with high level executive function, it is an insidious disease, with initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
 Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
@@
 Dementia is difficult to diagnose, primarily due to its slow onset, in addition to the confusion of initial symptoms with normal ageing.[@robinson2015] Dementia is diagnosed on the basis of behavioral and cognitive changes as assessed by an experienced clinician, using one of several diagnostic criteria.
+
+One of the most commonly used sets of criteria for diagnosing dementia cases are the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013] Outlined in Table \@ref(tab:diagnosticCriteria-table), these form the broad definition of a dementia diagnoses, and are supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
+
+Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
+The distinction between these memory scales and diagnostic criteria presented above should be noted.
+For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
+Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
 
@@
 
-One of the most commonly used criteria are those found in the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013] These criteria are outlined in Table \@ref(tab:diagnosticCriteria-table), and form the broad definition of a dementia diagnoses, supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
-
-Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
-The distinction between these memory scales and diagnostic criteria presented above should be noted.
-For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
-Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
-
 Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
@@
 
-<!-- ### Differing risk by sex -->
-
-<!-- Transparency guidelines that suggest sex should eb treated as biological variable and so results should be presented stratified t -->
-
-<!-- Rate of dementia/AD differs in men and women <!--- Though is this just due to the different lifestyles and life expectancies --->
-
-<!-- Previous studies have hinted that the relationship is dependent on individual-level characteristics such as age and sex [16,28]. -->
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is the leading cause of death in the UK, and the only one without a proven cure.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is a leading cause of death in the UK,[@zotero-15757] and one of the few without a proven treatment.
 
@@
 In 2015, the estimated total cost of dementia in England was £24.2 billion.
-Health care costs alone were £3.8 billion,[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014]
+Health care costs alone were £3.8 billion, with the remainder being divided between unpaid care and social care costs.[@wittenberg2019] Globally, the cost of dementia care is expected to rise to $1tr by 2030.[@prince2014] As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.
 
-As such, the urgent need to reduce the burden of dementia, both at the personal and system level, is clear.
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Developing treatments for dementia is regularly deemed to be one of the hardest markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020].
+Developing treatments for dementia is regularly deemed to be one of the most challenging markets in the pharmaceutical world, with trials of seemingly promising therapeutics being regularly abandoned due to futility.[@cummings2020].
 At present, there are no known curative treatments for dementia, regardless of the underlying cause, though several available therapeutics can help alleviate the symptoms of Alzheimer's disease.
+The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
+Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and have shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]
 
-The most common of these are acetylcholinesterase (ACE) inhibitors, which inhibit the degradation of the neurotransmitter acetylcholine by competitively binding the ACE enzyme.
-Acetylcholine plays a key role in controlling the cholingeric synapses, which are highly concentrated in regions of the brain (such as the neocortex) that control higher level brain functions such as memory and attention.[@hampel2018] Commonly prescribed ACE inhibitors include donepezil and galantamine.[@pariente2008] ACE inhibitors increase the availability of the neurotransmitter, and has shown clinical effect is easing the behavioural and memory-related symptoms of Alzheimer's disease.[@marucci2020] ACE inhibitors represent only a stop-gap treatment, treating the symptoms rather than the underlying pathology which may continue to progress.[@francis2010]
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
 ## Serum lipids
-
-<!----------------------------------------------------------------------------->
 
@@
 In addition to the individual fractions, total serum cholesterol (TC) is a commonly-used summary measure to estimate the total amount of lipid present in the blood.
-The measure is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
+The level of TC is derived from measurements of the individual HDL-c, LDL-c and TG levels using the Friedwald formula:[@friedewald1972]
 
@@
 where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
-
 Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
 
-&nbsp;
+Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
+These deposits constrict blood flow and can lead to vascular complications.
+Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attack or stroke.[@libby2019]
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 ```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
-These deposits constrict blood flow and can lead to vascular complications.
-Alternatively, part of the deposit can detach from the artery walls, forming a clot that can lead to a heart attach or stroke.[@libby2019] Globally, the prevalence of elevated cholesterol was estimated by the World Health Organization to be approximately 40%.
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 <!----------------------------------------------------------------------------->
-<!-- TODO Review the look and feel of this table -->
 
@@
 
-<!----------------------------------------------------------------------------->
-
 ### Other lipid regulating agents (LRA)
 
-There are several other interventions that can be used to modify a persons lipid profile, which each acting in slightly different ways (Table \@ref(tab)).
+There are several other interventions that can be used to modify a persons lipid profile, each of which act via different mechanisms (Table \@ref(tab)).
 However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Basic science {#intro-basic-science}
 
-A role for lipids in the aetiology of the dementia is supported by both genetic linkage studies and functional cell biology studies.
+A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
 The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Observational studies
 
-By far the largest source of evidence on the relationship between comes from observational designs.
+By far the largest source of evidence on the relationship between blood lipids and dementia outcomes comes from observational designs.
 Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
 In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005; @mainous2005; @mielke2010; @tan2003] or a reduced susceptibility [@mielke2005; @reitz2004].
-With regards vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004; @moroney1999]
+With regard to vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004; @moroney1999]
 
-<!-- Several previous systematic review of observational studies examining the effect of lipids[@anstey2015] and lipid-regulating agents[@chu2018;@poly2020] on dementia outcomes have been performed.
-However, these reviews have several limitations.
-Many did not consider grey literature sources (see Section \@ref(diverse-sources-preprints)).
-Additionally, many of the reviews of observational studies did not perform any risk-of-bias assessment[@chu2018] or used an outdated assessment tool.[@anstey2015;@poly2020c] -->
+<!-- IDEA May need summary of NRSI here -->
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-
 However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary related outcomes.
 
-While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment on in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, there was no clinical cognitive evaluation of patients to determine a dementia outcome.
+While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment in assessing the impact of lipid-lowering treatment on dementia risk.
+Firstly, the criteria used to determine a dementia outcome are unclear.
 One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
@@
 Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
-As discussed in Section \@ref(underlying-pathologies), the different underlying pathology of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
+As discussed in Section \@ref(underlying-pathologies), the different underlying pathologies of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
 
-Both trials were also limited by the relatively short follow-up period examined, expected when the primary outcome of the trials were coronary related conditions rather than dementia.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+Both trials were also limited by the relatively short follow-up period examined.
+This limited follow-up was expected, as the primary aim of both trials was to assess the effect of statins on short-term coronary-related outcomes.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
 Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
@@
 
-Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk in an effort to combat the risk of reverse causation and residual confounding inherent to observational studies.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
+Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
+Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
 
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of ApoE4 variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017]
-
-Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
-
-<!----------------------------------------------------------------------------->
-
-&nbsp;
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _ApoE4_ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
 
@@
 
-<!-- TODO Consider inverting the order so that triangulation comes last - as it does in the thesis as a whole! -->
-
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018] A common tyoe of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
+Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018] A common type of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
 
@@
 * Inclusion of preprints
+* Individual patient data meta-analysis
 * Triangulation across evidence sources
-* Individual patient data meta-analysis
 
@@
 
-<!-- TODO Incorporate Julian's comments below -->
+The importance of including grey literature, defined as literature not published in peer-reviewed journals,[@paez2017] in systematic reviews is widely acknowledged.
+Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts, government reports and theses.[@paez2017;@lefebvre2019searching]
 
-<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
-Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
-It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
-Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
-We have no clear and widely used definition of grey literature.
--->
-
-The importance of including grey (or gray) literature in systematic reviews is widely acknowledged.
-Meta-research studies have demonstrated that systematic reviews excluding grey literature sources overestimate the effect of interventions.[@conn2003; @mcauley2000; @hopewell2007] Common, well-accepted forms of grey literature include conference abstracts and theses.[@lefebvre2019searching]
-
-A important developing source of grey literature are preprints.
+However, the role of preprints in evidence syntheses is less well defined.
 Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months,[@vale2016] to rapidly disseminate research findings, as occurred during the COVID-19 pandemic,[@fraser2020preprinting] and to make available publications that may not have been accepted elsewhere in an attempt to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, the allow for the rapid disseminate research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
@@
 In this thesis, preprints are considered an important source of evidence, in contrast to previous reviews on this topic.
-However, as with many sources of grey literature,[@mahood2014] there are several logistical issues with carrying out systematic searches in preprint repositories.
+However, as with grey literature,[@mahood2014] there are several logistical problems with carrying out systematic searches in preprint repositories.
 As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Individual patient data meta-analysis
+
+Individual participant data (IPD) meta-analyses are commonly considered to be the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]
+
+In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, participant age and sex are considered to be of particular interest.[@arain2009; @letenneur1999]
+
+An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and a common statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
+
+Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014].
+Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
+
+In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop.
+The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.
+
+I will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-analysis-heading).
+This will enable the assessment of the effect of lipids on dementia stratified by key variables such as sex.
 
@@
 Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provides us a middle-ground between the competing directions of bias.
-A triangulation approach can also prove useful in a prospective manner, helping to design new studies that are at risk of different sources of bias to that already available from the published literature.[@munafo2018]
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, one to strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provide a middle-ground between the competing directions of bias.
+A triangulation approach can also prove useful in helping to prospectively design new studies that are at risk of different sources of bias to those already observed in the published literature.[@munafo2018] However, existing methods for triangulation are limited to a qualitative discussion of the different identified results with respect to their biases,[@lawlor2016] an approach which faces issues in interpretability when assessing many results.
 
-This thesis seeks to apply a triangulation approach to provide the best available evidence on the effect of lipids, and lipid regulating agents, on dementia outcomes.
+To address this limitation, this thesis seeks to develop and apply a novel quantitative triangulation approach to answer causal questions on the effect of blood lipids on dementia outcomes.
+All existing evidence, regardless of study design, is first identified and assessed using domain-based tools by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+The existing evidence base is then supplemented by two primary analyses, presented in Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading).
+Finally all existing and new evidence is incorporated into the quantiatative triangulation framework in Chapter \@ref(tri-heading).
 
-All existing evidence, regardless of study design, is first identified by the by the systematic review presented inChapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
-Risk-of-bias assessment using a domain-based tool is already a recommended part of the systematic review process, but is particularly important to a triangulation exercise.
-[@page2021; @sterne2019; @mcguinness2018] As such, a core component of the review is a comprehensive domain-based risk-of-bias assessment for all included studies.
-
-Finally all evidence, both pre-existing and produced as part of this thesis (Chapter \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading)), are triangulated in Chapter \@ref(dicussion-heading).
-
-<!----------------------------------------------------------------------------->
-
-### Individual patient data meta-analysis
-
-Individual patient data meta-analyses are commonly held to represent the gold standard in evidence synthesis methodology.[@riley2010; @stewart1993] IPD methods seek to obtain the raw data from each study identified in a systematic review, rather than basing the meta-analysis on summary results extracted from the literature.[@riley2010]
-
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, patient sex is considered to be of particular interest.[@arain2009; @letenneur1999]
-
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
-
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014a].
-Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
-
-In response to these limitations, new collaborative initiatives have developed to enable rapid access to relevant data in a secure supported workshop.
-The most import in relation to this thesis is the Dementia Platform UK (DPUK),[@bauermeister2020] which aims to provide access to several dementia-related datasets via a single simplified application process.
-
-I will will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an individual participant data meta-analysis in Chapter \@ref(ipd-analysis-heading), enabling the assessment of the effect of lipids on dementia stratified by key variables such as sex.
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 * To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
-* To meta-analyse raw dementia-related datasets as part of a individual participant data (IPD meta-analysis) to produce evidence on exposure-covariate interactions
+* To produce evidence on lipid-covariate interactions as part of an IPD meta-analysis 
 * To propose a generalised framework for the quantitative triangulation across diverse evidence sources
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 They are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "Lay" or plain English summary, developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
+Each chapter is prefaced by a "lay" or plain English summary.
+<!-- TODO developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
+-->
 
@@
 This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This Chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading):** These Chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
-This review examined all available evidence on the effect of blood lipids, and interventions that modified blood lipids, on dementia outcomes.
--   **Chapter \@ref(cprd-analysis-heading):** This Chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This Chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
--   **Chapter \@ref(discussion-heading)**: This Chapter integrates the diverse evidence identified by, and produced as part of, this thesis.
+-   **Chapter \@ref(sys-rev-tools-heading):** This chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+-   **Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading):** These chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
+This review examined all available evidence on the effect of blood lipids and interventions that modified blood lipids on dementia outcomes.
+-   **Chapter \@ref(cprd-analysis-heading):** This chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
+-   **Chapter \@ref(ipd-heading):** This chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
+-   **Chapter \@ref(tri-heading)**: This chapter integrates the evidence identified and produced by the preceeding chapters as part of a quantitative triangulation framework.
+-   **Chapter \@ref(discussion-heading)**: This chapter summarise the key clinical and methodological findings of the thesis and discusses their implications for practice.
 The overall strengths and weaknesses of this project are discussed in detail, and further avenues of research are suggested.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Contributions to the scientific literature
@@
 
-<!-- TODO Ideally the two preprints for the CPRD and systematic review papers will go here -->
+_**McGuinness L.
+A.**, Higgins J.
+P.
+T., Walker, V.
+M., Davies, N.
+M., Martin, R.
+M., Coulthard, E., Davey-Smith, G., Kehoe, P.
+G., and Ben-Shlomo, Y.
+(2021) Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the Clinical Practice Research Datalink.
+medRxiv  [10.1101/2021.10.21.21265131](https://doi.org/10.1101/2021.10.21.21265131)_
+
+Preprinted manuscript of the analysis of lipid-regulating agents and dementia outcomes in the CPRD, which is presented in Chapter \@ref(cprd-analysis-heading).
 
@@
 R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
-Welch, V.,  **McGuinness L.
+Welch, V.,  **and McGuinness L.
 A.** (2021).
@@
 Emily Hennessy (see Author Declarations in the front materials).
-<!-- TODO Need to create author declarations section -->
 
@@
 _"Identifying and triangulating all available evidence on the effect of blood lipids and statins on dementia outcomes"_: Poster presentation, Alzheimer's Association International Conference 2021.
+
 &nbsp;
 
-_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic)
+_"medrxivr: A new tool for searching for and retrieving records and PDFs from the medRxiv preprint repository"_: Accepted oral presentation abstract, Cochrane Colloquium 2020 (note: event was cancelled due to the COVID-19 pandemic).
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Software {#outputs-software}
@@
 
-An R package that allows users to easily search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
+An R package that allows users to search and retrieve bibliographic data from the medRxiv[@rawlinson2019] and bioRxiv[@sever2019] preprint repositories.
 See Chapter \@ref(sys-rev-tools-heading) for more details.
@@
 
+**`triangulate`**
+
+An R package containing function to implement the quantitative triangulation approach detailed in Chapter \@ref(tri-heading).
+At present, only the development version of the package is available, which can be installed from GitHub using:
+
+``` {r, eval = FALSE}
+# Development version
+devtools::install_github("mcguinlu/triangulate")
+```
+
+&nbsp;
+
 **`robvis`**
 
-An R package and associated `shiny` web application that allows users to easily visualize the results of the risk-of-bias assessments performed as part of a systematic review.
+An R package and associated `shiny` web application that allows users to visualize the results of the risk-of-bias assessments performed as part of a systematic review.
 See Appendix \@ref(appendix-robvis) for more details.
@@
 
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-This Chapter has provided background information on the core elements of the central research question, framed the research presented in this thesis in the context of an evidence synthesis framework, and described the contributions of this thesis to the scientific literature.
+* In this introductory chapter, I provided background information on the core elements of the central research question and framed the research presented in the context of a theoretical framework of evidence synthesis.
+I outlined the central aim of the thesis and provided an overview of the individual analyses performed.
+
+* I also described the contributions of this thesis to the scientific literature.
+Finally, I discussed the research tools and software developed to support the analyses in this thesis, one of which (the preprint search tool) is introduced more fully in the following chapter.
 
 \newpage
-
-## References

### 2021-12-02 02-Chp-Systematic-Review-Tools.Rmd
End of day:

@@
 
-(ref:sys-rev-tools-quote) --- Bealy, 2013 [@bealy2013]
+(ref:sys-rev-tools-quote) --- Chris Beely, 2013 [@beely2013]
 
 # medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
+
+&nbsp;
 
@@
 
-<!-- TODO I might need to make it clearer thatthe tool was always intended to search both databases, as medRxiv grew out of bioRxiv categories, and no relevant records identified by the search in medRxiv -->
+\newpage
 
-## Lay summary
+::: {.laybox data-latex=""}
+
+## Lay summary {-}
 
@@
 They represent an important source of scientific literature.
-A new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way.
+A new software program called `medrxivr` was created as part of this thesis to allow researchers to find preprints related to their research in a transparent and reproducible way.
 Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
+
+:::
 
@@
 Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
-At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the often complex Boolean logic (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search were to go through each record, one-by-one, downloading individual citations.
+At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the complex searches containing Boolean logic operators (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search involved going through each record and downloading individual citations one-by-one.
 As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
@@
 <!----------------------------------------------------------------------------->
-
-<!-- IDEA Could remake this using Diagrammr? -->
 
@@
 Prior to development of this tool, I conducted an audit of existing tools for accessing medRxiv and bioRxiv metadata.
-While none address the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
+While none addresses the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
 
@@
 Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required me to regularly update or fix the script.
+In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required that I regularly update or fix the script.
 
@@
 
-I wrote the `medrxvir` package in R using RStudio,[@rcoreteam2019] and followed development best-practice, including development of detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
+I wrote the `medrxvir` package in R using RStudio,[@rcoreteam2019] and followed development best-practice, including detailed documentation, a robust unit testing framework (99% of all code lines within the package are formally tested across multiple platforms including Windows, MacOS, and Linux), and in-depth code review by two experienced, independent reviewers.
 
@@
 
-<!-- TODO Clean up this section -->
-
-<!-- REVIEW Not clear why there are two, or what are advantages or disadvantages of each. There’s a hint below (“can become unavailable during peak usage times”), but perhaps add some more -->
-
 Prior to searching the metadata, it must first be imported in R.
@@
 However, this approach has two limitations.
-Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database  <!-- TODO Get numbers here, at a given date --> requires a time-intensive process of cycling through multiple pages.
+Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database requires a time-intensive process of cycling through each page.
 Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
-
 To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
@@
 
-This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file to an online server (Figure \@ref(fig:medrxivr-data-sources)).
+This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file in an online repository (Figure \@ref(fig:medrxivr-data-sources)).
 Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
-
 The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
@@
 For example, when written in standard syntax, the search contained in the `myquery` object above would be: "((dementia **OR** alzheimer's) **AND** (lipids **OR** statins))".
-There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be search for.
-Search terms can also contain common syntax used by systematic reviewers and health librarians, including the use of NEAR statements which allows for identification of co-localised terms, and wild-cards, which allow for alternate spellings, e.g.
-"randomi*s*ation" vs "randomi*z*ation".
+There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be searched for.
+Search terms can also contain common syntax used by systematic reviewers and health librarians, including the NEAR operator for the identification of co-localised terms and wild-cards which allow for alternate spellings (e.g.
+"randomi*s*ation" vs "randomi*z*ation").
 
@@
 As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, as "Alzheimer" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
+This is expected, as "Alzheimer's" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
 
-<!-- TODO Add some text to this section about the challenges of defaults, and the fact that the autocaps option exists -->
-
-<!-- REVIEW Can you not just make the search case insensitive?
-It means you often need to include capitalized and non-capitalized versions in case a word appears at the start of a sentence or is capitalized for some other reason?
-(I find a lot of people these days pseudo-randomly capitalize words for no good reason (like you did in “Application Programming Interface” on page 4 above!!)) -->
+In hindsight, the decision to make the search case-sensitive was a poor one as users reported being unaware of this setting when searchin.
+However, changing the default behaviour of `mx_search()` to be case-insensitive is problematic, as it could result in different numbers of hits based solely on which version of the package the user has installed.
+To address this, `mx_search()` now contains an `autocaps` argument, which when set to `TRUE` will automatically search for both capitalised and uncapitalised versions of the search term.
 
@@
 
-In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
+In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to export easily the results of their systematic search to a reference manager.
 While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
@@
 
-`medrxivr` alos allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
+`medrxivr` also allows users to download the full text papers for records that are deemed eligible for full-text screening (see Figure \@ref(fig:medrxivr-sr)).
 `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
@@
 
-In addition to being used to search systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
+In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
 
 For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
-By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript (same content, authors and funders) under two different publication policies, and examine whether stricter policies which require data sharing as a condition of publication actually result in increased data availability.
-We found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing compared to when the journal did not mandate data sharing.
-This study has since been published in PLOS One, and a copy is included in Appendix \@ref(published-papers).
+By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript - same content, authors and funders - under two different publication policies (preprint server vs peer-review journal).
+This comparison provides evidence on whether stricter policies which require data sharing as a condition of publication result in increased data availability.
+The analysis found some evidence that data availability statements more frequently described open data on publication when the journal mandated data sharing, compared to when the journal did not mandate data sharing.
+This study has since been published,[@mcguinness2020DAScomparison] and a copy is included in Appendix \@ref(published-papers).
 
@@
 publication_n <- sum(med_res$n)
-publish <- paste0(num_to_text(published,T)," (", round(published/publication_n*100,1),"%)")
+publish_percent <- paste0("(", round(published/publication_n*100,1),"%)")
 ```
 
-<!-- TODO Need to finish this bit and move it to the use-case section! -->
+Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
+`r published` of the `r publication_n` records `r publish_percent` posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
+allowing for a two-year lag between preprint posting and publication).
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
 
-Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
-`r publish` of the `r publication_n` records posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
-allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting,[@abdill2019popularity] indicating that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
-
-In short, these use cases illustrate that easy access to medRxiv/bioRxiv metadata has applications beyond systematic searching of preprints by enabling meta-research/methodological analyses.
+In summary, the meta-research/methodological analyses described above illustrate that easy access to medRxiv/bioRxiv metadata has applications beyond the inclusion of preprints in systeamtic review.
 
@@
 While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
-A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, meaning some relevant records might be missed.
+A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, and so some relevant records might be missed.
 However, this approach echoes that used by other search platforms such as OvidSP, and while some relevant records may be missed (reduced sensitivity), limiting the search to the metadata fields prevents non-relevant records from being returned (high specificity).
@@
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
+There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different to those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
 
-<!-- TODO Clean-up this section -->
-
-<!-- REVIEW I don’t think anyone would assume that preprints would help much here… I’d have thought the main argument is getting hold of evidence in a more timely manner.-->
-
-<!-- TODO replicate this analysis -->
-
-It is likely too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
-
-<!-- TODO EMBASE will index medRxiv/bioRxiv from Christmas - need to make a note of this somewhere -->
+It is probably too early (and likely too methodologically difficult) to tell whether the increased popularity and acceptance of preprint repositories will have any effect of the availability of research that was not considered "publishable" at other venues.
 
@@
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019; @mckiernan2016] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@fraser2020rbiorixv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019; @mckiernan2016] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@fraser2020rbiorixv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 
@@
 
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of a key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
+-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
 

### 2021-12-02 04-Chp-Systematic-Review-Results.Rmd
End of day:

@@
 I identified one previous review of Mendelian randomisation studies examining risk factors for Alzheimer's disease.
-However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the APoE4 genetic region (see the following section for a discussion of the bias this introduces).
+However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the _ApoE4_ genetic region (see the following section for a discussion of the bias this introduces).
 
@@
 
-One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the Apoe4 gene region.
-As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of ApoE4 alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
-In all cases, excluding variants in the ApoE region attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where ApoE variants were not sufficient identified and excluded, leading the published paper to report a protective effect of LDL-c on Alzheimer's (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed to exclude a larger area around ApoE which attenuated the finding to the null.[@benn2017comment]
+One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the _ApoE4_ gene region.
+As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of _ApoE4_ alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
+In all cases, excluding variants in the _ApoE_ region attenuates the observed effect to the null.
+A clear example of this is Benn _et al_ (2017), where _ApoE_ variants were not sufficient identified and excluded, leading the published paper to report a protective effect of LDL-c on Alzheimer's (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed to exclude a larger area around _ApoE_ which attenuated the finding to the null.[@benn2017comment]
 

### 2021-12-02 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
-This chapter represents an extended version of a preprint manuscript, a copy of which is available in Appendix \@ref(published-papers).
+This chapter represents an extended version of a preprinted manuscript, a copy of which is available in Appendix \@ref(published-papers).
 
@@
 A further limitation stems from the possibility of uncontrolled confounding due to genetic factors.
-The number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
-I was unable to control for ApoE genotype in this analysis as I did not have access to genetic data on participants.
+The number of _ApoE_ $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+I was unable to control for _ApoE_ genotype in this analysis as I did not have access to genetic data on participants.
 As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.

### 2021-12-02 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = FALSE}
-Hold
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:intro-quote)', echo = TRUE}
+These particular systematic reviews [individual participant data reviews] remain yardsticks against which the quality of other reviews continues to be judged.
 ```
-(ref:intro-quote) --- Hold
+(ref:intro-quote) --- Ian Chalmers, 1993[@chalmers1993]
 
@@
 
+::: {.laybox data-latex=""}
+
 ## Lay Summary
 
-TBC
+<!-- TODO Finish lay summary -->
 
-<!-- As part of a broader investigation into the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+Individual participant data (IPD) meta-analyses are a special type of meta-analysis that contact the authors of relevant studies to request access to the raw data on each participant.
+This is different to the meta-analyses presented in the previous chapter, which used published summary results.
+
+&nbsp;
+
+To examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
 However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
--->
 
-<!-- The resulting analysis did not suggest an effect of any lipid fraction (total cholesterol, LDL-c, HDL-c, or triglyceride) on any dementia outcome.
-In addition, patients characteristics such as age and sex did not have any impact on the relationship of lipid fractions and dementia outcomes.
--->
+&nbsp;
 
-<!-- Finally, the reasons for the low response rate are explored and future studies to investigate how data access rates could be improved are suggested.  -->
+The resulting analysis of these data sources did not suggest a relationship between any blood lipid and any dementia outcome.
+The sole exception was an increased risk of vascular dementia in those with higher triglyceride levels.
+In addition, participants age and sex did not appear to influence the relationship of lipid fractions and dementia outcomes.
+
+&nbsp;
+
+The reasons for the low response rate to request for data are explored. Finally, I suggest future studies to investigate how data access rates could be improved.
+
+:::
 
@@
 
-Individual patient data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of patient-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
+Individual participant data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of participant-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
 IPD analysis also offer a mechanism by which previously unanalysed datasets can be incorporated into an analysis, thus expanding the evidence base for a particular research question.
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on patient age and sex.[@ancelin2013; @mielke2010] While the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
-However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of patient characteristics in those that did.
-Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on the between-study heterogeneity in a summary data meta-analysis, as similar distributions of patient covariates across studies may mask a true effect.[@riley2020]
+Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
+Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on the between-study heterogeneity in a summary data meta-analysis, as similar distributions of participant covariates across studies may mask a true effect.[@riley2020]
 
-As such, the aims of this analysis are two fold: firstly, to perform a individual patient data meta-analysis across identified cohorts to examine the impact of patient age-at-measurement and sex on the effect of lipids on dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
+As such, the aims of this analysis are two fold: firstly, to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the effect of lipids on dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
 
 <!-- TODO Read this[@riley2020] -->
+
 <!----------------------------------------------------------------------------->
@@
 
+<!-- TODO Should start with inclusion criteria -->
+
+Eligible data sources for this analysis were prospective cohort studies.
 Data sources which were cross-sectional, either by design or due to the available data (e.g.
 a study conducted across multiple waves, but only data from a single wave could be accessed) were excluded.
-Similarly, due to the limited time afforded by this thesis, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
+Similarly, due to time restrictions within the scope of my thesis project, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
 No restrictions were put on the number of participants or the length of follow-up, though participants must be free of dementia (or assumed to be free, based on age at entry)  at baseline.
@@
 Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
-To aid interpretability of the outcome, all analyses were standardised to refer to a 1-standard deviation increase in the lipid fraction under investigation.
+
+<!-- TODO Ensure that the results are actually on the mmol/L scale -->
 
 Across all cohorts, data cleaning was performed in a similar manner, standardising to commonly named variables so that a single model could be applied using functional programming.[@wickham2016func] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
-Following data cleaning, summary statistics for each data source were calculated and compared to publicly available statistics to ensure no errors were introduced in the data cleaning process, in line with best practice.[@levis2021]
+Following data cleaning, summary statistics for each data source were calculated and compared with publicly available statistics to ensure no errors were introduced in the data cleaning process, in line with best practice.[@levis2021]
 
@@
 
-With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, ApoE4 status, smoking/alcohol status and prevalent cardiovascular disease.
+A range of additional variables were included in the analysis, intended to address the potential for confounding.
+With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _ApoE4_ status, smoking/alcohol status, ethnicity, and prevalent cardiovascular disease.
 This set covers key risk factors for dementia/Alzheimer's disease in addition to general cardiovascular risk factors.
-Ethnicity was considered as a potential addition covariate of interest, but several of the DPUK cohorts (whose data dictionaries could be inspected in advance) made it clear that ethnicity data was either not available or would not be shared.
 Details on how these variables were coded, given the available data, are presented in Section \@ref(ipd-covar-definition).
@@
 Missing data in this analysis was classified as either relating to missing values (a cohort collected data on a variable of interest, but some values are missing) or missing variables (a cohort did not collect data on a variable of interest).
-
 Variables with missing values were identified, and 20 imputed datasets were created.[@sterne2009] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the `mice` package in R.
 
-Systematically missing variables were originally intended to be addressed using a previously described method.[@fibrinogenstudiescollaboration2009] Here, the correlation between the fully-adjusted and partially-adjusted estimate in cohorts with the full set of covariates is used to estimate the fully-adjusted effect in those cohorts missing covariates.
+Missing variables were originally intended to be addressed using a previously described method.[@fibrinogenstudiescollaboration2009] Here, the correlation between the fully-adjusted and partially-adjusted estimate in cohorts with the full set of covariates is used to estimate the fully-adjusted effect in those cohorts missing covariates.
 However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
@@
 
-#### Individual patient data analysis
+#### IPD analysis
 
-In this analysis, an two-stage individual patient data analysis was planned.
-Under a two-stage approach, estimates for the effect of each lipid fraction on available dementia outcomes were first calculated for each data source.
-More specifically, odds ratios were used to quantify the effect of a 1-SD lower exposure to a lipid fraction on dementia outcomes.
+In this analysis, a two-stage IPD analysis was planned.
+Under a two-stage approach, estimates for the effect of each lipid fraction on incident dementia were first calculated for each data source.
+More specifically, a logistic regression model adjusted for relevant covariates as detailed in the above section was used to quantify the effect of a 1 _mmol/L_ increase in each lipid fraction on each dementia outcome.
+Results were expressed as odds ratios (OR).
 Examination of the data available via the DPUK indicated that the common time-to-event approach used in studies of dementia outcomes would be precluded by the absence of detailed time-to-event data.
 An overall effect estimate was then produced by combining data-source-specific estimates in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
+
+<!-- REVIEW ORs - the one issue here may be the length of follow-up. Was it roughly equal across cohorts such that the ORs are comparable? -->
 
@@
 
-#### Comparison with published findings
+#### Investigating the effect of participant-level covariates
 
-Following estimation of the main effect, where an included data source had previously been analysed, the results of this analysis were compared against those published previously.
-Where discrepancies were identified, these were investigated.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Investigating the effect of patient-level covariates
-
-In order to investigate the interaction of patient-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a random effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
 All interaction analysis were performed using the common-set-adjusted model (Model 1).
 
-<!-- QUESTION Why was Ancelin, which provides summary level data stratified by sex, not included in the analysis?
-Several reasons: i) cause it was not adjusted for the same covariates; ii) because the -->
+<!-- QUESTION   -->
 
@@
 
-In summary, the requests for data from cohorts identified by the systematic review were characterised by a very low response rate.
-For the minority who did respond, common reasons given by authors for not sharing the data included that they: no longer worked with the same group and did not know if the data were available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
-
-<!-- TODO Need numbers in the above section. -->
+In summary, the requests for data from cohorts identified by the systematic review were characterised by a very low response rate (N = 5, 25%).
+For the minority who did respond, common reasons given by authors for not sharing the data included that they: no longer worked with the same group and did not know if the data was available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
 
 With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher.
-However, even using this streamlined approach, a response was obtained for approximately half (N=9, 53%) of the approached cohorts, one of which (Whitehall II) was also identified by the systematic review.
+However, even using this streamlined approach, a positive response was obtained for approximately half (N=9, 53%) of the approached cohorts.
 
-<!-- TODO Fix width of this image, and one box is not rendering right, and update numbers! -->
-
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->  
 ```{r cohortFlowchartSetup, include = FALSE}
@@
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
 As highlighted in Figure \@ref(fig:cohortFlowchart), there was little overlap between cohorts identified by the systematic review and those contained in the DPUK (`r n_applied$DPUK_sysrev`), indicating that the DPUK is a useful source of unanalysed data with respect to this question.
+A single cohort (Whitehall II) was identified by the systematic review and was also present in the DPUK.
 
-As highlighted in Figure \@ref(fig:cohortFlowchart), nice cohorts (8 DPUK only, 1 Systematic review + DPUK) responding positively to requests for data access.
-However, on inspection of data provided, six of these cohorts were excluded for a range of reasons.
-The exclusion reason for each cohort for which data were provided is illustrated in Table \@ref(tab:dataExcluded-table).
-In summary, two cohorts contained were memory-complaint cohorts, containing patients unlikely to be free of dementia at baseline (BRACE, MEMENTO).
+Nine cohorts (8 DPUK only, 1 Systematic review + DPUK) responded positively to requests for data access.
+However, on inspection of data provided, six of these cohorts were excluded and the reason for exlcusion in each case is summarised in Table \@ref(tab:dataExcluded-table).
+In summary, two cohorts contained were memory-complaint cohorts, containing participants unlikely to be free of dementia at baseline (BRACE, MEMENTO).
 Two cohorts, despite being designed as multi-wave studies, only shared data related to a single wave and so represented cross-sectional data (Generation Scotland, NICOLA).
 Finally TRACK HD is a genetic cohort where cohort owners advised me that dementia will inevitably develop in mid-life driven by the Huntington's (HTT gene) mutation and that this effect would likely far outweigh the effect of lipids.
-Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable <!-- TODO CITATION NEEDED for each study here!
+Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable.
+<!-- TODO CITATION NEEDED for each study here!
 -->
@@
 The cohort contains data on dementia outcomes sub-classified as vascular and non-vascular dementia.
-Data were available for all covariates of interest except for education, BMI and ApoE4 status.
+Data was available for all covariates of interest except for education, BMI and _ApoE4_ status.
 
@@
 The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] The added evidential value of the EPIC cohort is small, given the the fact that the data obtained contains only 8 dementia events.
-The cohort contains no information on dementia subtype, while all covariates of interest bar ApoE4 were available.
+The cohort contains no information on dementia subtype, while all covariates of interest bar _ApoE4_ were available.
 
@@
 
-The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of patient events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
-This data source contained details on all covariates of interest except for ApoE4 status.
+The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
+This data source contained details on all covariates of interest except for _ApoE4_ status.
 
@@
 A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(hold).
-The Whitehall II and EPIC cohorts containted data on all but one covariates of interest, while two systematically missing covariates were identified in the CaPS cohort, namely education and BMI.
-No included cohort provided information on the ApoE4 status of participants, and so this variable could not be adjusted for in the analysis.
+The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity.
+No included cohort provided information on the _ApoE4_ status of participants, and so this variable could not be adjusted for in the analysis.
 
@@
 
-Across the three cohorts, `r n_total_ipd` patients were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512).
+Across the three cohorts, `r n_total_ipd` participants were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512).
 All cohorts contained data on the four exposure variables of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes.
@@
 Summary statistics for each cohort are provided in Table \@ref(tab:cohortSummary-table).
+
+<!-- TODO Need average follow-up by cohort here - or rather put it in the table -->
+<!-- TODO Need total number of Azd cases in whitehall in the paragraph above-->
 
@@
 
+<!-- REVIEW Present main effect for WhiteHall AD analysis - or rather highlight that it is shown in Figure XXX in comparison with Tynken -->
+
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
+
+<!-- TODO Now that using a fixed effect model, evidence of TG/ACD association -->
 
@@
 
-<!-- Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
+Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
 Further, while the maximally-adjusted could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
--->
 
@@
 
+<!-- TODO Using fixed effect meta-analyses, there is now an effect of male gender on LDL/all-cause dementia relationship. Need to discuss if sticking with fixed -->
+
 For the consideration of vascular dementia, I was only able to explore the effect of age, as only the CaPS and Whitehall cohorts contained details on vascular dementia as an outcome.
@@
 
-#### Comparison with previous analyses
-
-For the single cohort where a previously published analysis was available (Whitehall II), results from the maximally-adjusted model for both all-cause dementia and Alzheimer's disease were comparable, with the exception of the trigluceride fraction (Figure \@ref(fig:whitehallComparison)).
-Tynkkynen _et al._[@tynkkynen2018] found a protective effect of triglycerides on all-cause dementia (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
-
-<!-- TODO These are generated - check they are correct! -->
-
-<!-- TODO Confirm the results of Tyn for HDL are different between the below figure and the results presented in the systematic review -->
-
-<!----------------------------------------------------------------------------->
-(ref:whitehallComparison-cap) Comparison of results across the two analysis of the Whitehall II cohort
-
-(ref:whitehallComparison-scap) Comparison of results across the two analysis of the Whitehall II cohort
-
-```{r whitehallComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparison-cap)', out.width='100%', fig.scap='(ref:whitehallComparison-scap)'}
-knitr::include_graphics(file.path("figures/ipd/whitehall_comparison.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
-
 ## Discussion
@@
 This analysis requested data from `r n_applied$total` data sources, but only obtained data from three, all of which were based in the United Kingdom.
-No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia  Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants age, grouped into 5 year bands, or sex.
+No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia.
+Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
 
-Similar to the analysis of CPRD data presented in the previous chapter, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except where needed to illustrate a methodological point.
+Similar to the analysis of CPRD data presented in the previous chapter, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except to compare between this analysis and previously published results using the same data source.
 For a detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
@@
 
-The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD study.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in pplication of the methods in addition to providing additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
+The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences in the association of lipids with dementia outcomes between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD analysis.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in application of the methods in addition to providing additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
 
-A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data were obtained was not accurately reported.[@nevitt2017] However, it is assumed that a ~10% response rate is at the lower end of the scale.
+A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.[@nevitt2017] However, it is assumed that a ~10% response rate is at the lower end of the scale.
 
 There are likely several likely reasons for this low response rate to requests for data access.
-In general terms, there are a several well-documented reasons why data are not made readily available, including concerns regarding participant privacy and "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, individual participant data meta-analysis including studies other than randomised controlled trials have less success in obtaining individual participant data from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
-The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised other COVID-related work.
+In general terms, there are a several well-documented barriers that prevent data from being made readily available, including concerns regarding participant privacy, fear of "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, IPD meta-analysis including studies other than randomised controlled trials have less success in obtaining IPD from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
+The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised COVID-related work.
 
@@
 
-The barriers to data access described above are in theory what the DPUK was built to address.
+The obstacles to data access described above are in theory what the DPUK was built to address.
 However, even with the help of the streamlined application process afforded by the DPUK, accessing sufficient data was a challenge.
@@
 A key limitation of this analysis is the potential for uncontrolled confounding.
-Across all cohorts, adjustment for ApoE4 was not possible as I did not have access to genetic data on participants.
-As discussed above in relation to the Tynkkynen _et al._ analysis, ApoE4 is a strong risk factor for both increased LDL-c levels and Alzheimer's disease.[@bennet2007;@safieh2019] Failing to adjust for this factor means confounding in the LDL-c fraction results is likely.
+Across all cohorts, adjustment for _ApoE4_ was not possible as I did not have access to genetic data on participants.
+_ApoE4_ is a strong risk factor for both increased LDL-c levels and Alzheimer's disease,[@bennet2007;@safieh2019] and failing to adjust for this factor means residual confounding in the LDL-c fraction results is likely.
 
@@
 
-#### Discrepancy with previous analysis
+&nbsp;<!----------------------------------------------------------------------->
 
-I found a qualitative difference between the association of triglycerides and all-cause dementia identified in this analysis and that previously reported by Tynkkynen _et al._[@tynkkynen2018]
+#### Comparison with previous analysis
+
+For the single cohort (Whitehall II), a previously published analysis was available.
+Tynkkynen _et al._[@tynkkynen2018] analysed the association of blood lipids and risk of all-cause dementia and Alzheimer's disease across several cohorts, including the Whitehall II cohort.
+
+In an attempt to validate my approach, I compared the results from the maximally-adjusted model (Model 2) in this analysis with those reported by Tynkkynen _et al._ for both all-cause dementia and Alzheimer's disease.
+The results were broadly comparable (Figures \@ref(fig:whitehallComparisonDementia) and \@ref(fig:whitehallComparisonAd)), with the exception of the association of triglycerides with all-cause dementia.
+Tynkkynen _et al._[@tynkkynen2018] found a protective effect of triglycerides on this outcome (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
+
+<!----------------------------------------------------------------------------->
+(ref:whitehallComparisonDementia-cap) Comparison of results across the two analysis of the Whitehall II cohort for the all-cause dementia outcome.
+
+(ref:whitehallComparisonDementia-scap) Comparison of results across the two analysis of the Whitehall II cohort
+
+```{r whitehallComparisonDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonDementia-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonDementia-scap)'}
+knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_dementia.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.
+
+(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort
+
+```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
+knitr::include_graphics(file.path("figures/hold.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
 Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (n=287 in this analysis vs.
 n=114 in Tynkkynen _et al._).
-The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for ApoE4 status.
-However, given that ApoE4 is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
+The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _ApoE4_ status.
+However, given that _ApoE4_ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
 
@@
 
-__[Note: I feel quite negatively about this analysis, so suggestions for other strengths to flesh out this section would be welcome!]__
+While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, a central strength of this analysis is use of a systematic approach to identify and attempt to contact relevant cohorts.
+Further, it also enabled incorporation of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - thus providing additional evidence that is used in the triangulation exercise reported in Chapter \@ref(tri-heading).
 
-While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, it did enable an analysis of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - providing additional data that is incorporated into the triangulation exercise reported in Chapter \@ref(tri-heading).
+A further strength is the ability of this analysis was the ability to investigate the effect of participant characteristics (namely age and sex) on the association of blood lipids and dementia outcomes.
+To the best of my knowledge, no previous review has examined the interaction of these factors with the observed associations.
 
-Additionally, it provides new evidence on a previously unexplored outcome, vascular dementia, in the Whitehall II dataset, adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-method-heading) & \@ref(sys-rev-results-heading).
+Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-method-heading) & \@ref(sys-rev-results-heading).
+This is relevant even in the previously analysed WhiteHall II cohort, as the previous analysis by Tynkkynen _et al._ did not report on this outcome.
 
@@
 Additionally, the production of detailed guidance for handling cases where covariates are systematically missing.
-Much of the literature around IPD analysis is focused on the synthesis of trials, where additional covariate information is needed primarily for the assessment of treatment-covariate interactions rather than the adjustment of the effect estimate for confounding.
+Much of the literature around IPD analysis is focused on the synthesis of RCTs, where additional covariate information is needed primarily for the assessment of treatment-covariate interactions rather than the adjustment of the effect estimate for confounding.
 Given the wide availability of non-randomised cohorts, improved guidance on this challenge would support future work.
@@
 - I found very weak evidence for an association of any lipid with either all-cause or vascular dementia, except for an increased risk of vascular dementia associated with raised triglycerides.
-Similarly, there was very weak evidence that the association of blood lipids and dementia outcomes varied by patient age or sex.
+Similarly, there was very weak evidence that the association of blood lipids and dementia outcomes varied by participant age or sex.
 

### 2021-12-02 07-Chp-Triangulation.Rmd
Working version!
End of day:

@@
 
-### Qualitative triangulation {#qual-tri}
+### Qualitative triangulation / narrative comparison {#qual-tri}
 
@@
 For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
-In Domain 1 (bias due to confounding), the study did not adjust for ApoE4 status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
+In Domain 1 (bias due to confounding), the study did not adjust for _ApoE4_ status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
 As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right.
@@
 
+<!-- TODO Data-driven hypothesis testing - only choosing those the two strata that have some suggestion of an effect -->
+
 The quantitative analysis presented in this chapter is subject to some strong methodological limitation, which are discussed in detail below.
@@
 However, the prior distributions defined here are broadly comparable to previously reported estimates of the impact of bias in non-randomised trials.
-For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, ApoE4 would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
+For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, _ApoE4_ would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
 

### 2021-12-02 08-Discussion.Rmd
End of day:

@@
 The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are  consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
-<!-- TODO The study says that simulated effect of ApoE4 is a 1.09 RR in the absence of a true causal effect.
+<!-- TODO The study says that simulated effect of _ApoE4_ is a 1.09 RR in the absence of a true causal effect.
 Main results are between 1.03 and 1.17.
-CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by ApoE4 which is just a single confounder out of many -->
+CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by _ApoE4_ which is just a single confounder out of many -->
 
@@
 
+<!-- TODO Incorporate Julian's comments below -->
+
+<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
+Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
+It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
+Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
+We have no clear and widely used definition of grey literature.
+-->
+
 Given the evidence that this thesis produced on the usefulness of including preprints, normalisation of inclusion of preprints in systematic reviews.

### 2021-12-02 front-and-back-matter/_abstract.Rmd
End of day:

--- 2020-02-06 front-and-back-matter/_abstract.Rmd
@@
-__Background__  
-In the UK, an estimated 800000 people are currently living with dementia and this number is expected to double
-by 2040. Despite the number of dementia cases and decades of research, there remains much unknown about
-the pathogenesis and progression of the disease, and, at present, no effective treatment exists to arrest or
-reverse the cognitive decline associated with the condition. In this context, identification of causal relationships
-between modifiable targets and dementia risk is central to the development of evidence-based prevention
-strategies and will be critically important in maintaining the long-term health of the ageing public. Blood lipid
-levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies,
-but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
+__Background:__ Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies.
+Blood lipid levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies, but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
+This thesis sought to triangulate the causal effects of lipid levels (total cholesterol, LDL-c, HDL-c, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
+
+&nbsp;
+
+__Methods:__ Four distinct analyses were conducted.
+Firstly, a systematic review of 81 published and preprinted studies was used to summarise the existing evidence base.
+Preprints were searched using a new research tool created as part of this thesis.
+The existing evidence was then supplemented via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual patient data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK.
+Finally, a novel quantitative triangulation framework was proposed, building on recent developments in risk-of-bias assessment and bias-/indirectness-adjusted meta-analyses.
+This framework was then used to quantitatively triangulate the evidence identified and produced by this thesis.
+
+&nbsp;
+
+__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, through there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer’s disease in observational studies of statin use.
+The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia.
+However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors.
+The individual patient data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence only for the association of triglycerides and vascular dementia.
+Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
+
+&nbsp;
+
+__Conclusions:__
+This thesis provides new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlights the uncertainty that still remains in relation to this causal question.
+In addition, it has developed new evidence synthesis methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources.

### 2021-12-02 index.Rmd
End of day:

--- 2021-10-08 index.Rmd
@@
 title: |
-   Lipids and dementia:\
-   An investigation of their relationship
+   Determining the causal effects of lipid levels on risk of dementia: a triangulation of new and existing evidence
 

### 2021-12-02 manuscripts/cprd/manuscript.Rmd
End of day:

@@
 A further limitation stems from uncontrolled confounding due to genetic factors.
-Number of ApoE $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
-We were unable to control for ApoE genotype in this analysis as we did not have access to genetic data on participants.
+Number of _ApoE_ $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL-c levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+We were unable to control for _ApoE_ genotype in this analysis as we did not have access to genetic data on participants.
 As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.

### 2021-12-02 R/01-Code-Background.R

@@ -155,11 +155,12 @@ if(doc_type == "docx") {
     caption = "(ref:statinOverview-caption)",
     caption.short = "(ref:statinOverview-scaption)",
     booktabs = TRUE, 
-    align = "ccccc"
+    align = "lcccc"
   ) %>%
     row_spec(0, bold = TRUE) %>%
     column_spec(1, width = paste0(6,"em"), bold= TRUE) %>%
-    column_spec(2:4, width = paste0(6,"em")) %>%
+    column_spec(2:3, width = paste0(5.5,"em")) %>%
+    column_spec(4, width = paste0(6,"em")) %>%
     column_spec(5, width = paste0(7.6,"em")) %>%
     row_spec(2:nrow(statinOverview_table)-1, hline_after = TRUE) %>%
     kable_styling(latex_options = c("HOLD_position"))

### 2021-12-02 R/06-Code-IPD-Analysis.R

@@ -44,7 +44,7 @@ graph <- grViz(diagram = "digraph cfa {
       tab22 [label = 'N data obtained: 8\n\n Exclusion reasons:\n- No response (n= 7)\n- Planned analysis (n= 1)',height = 2]
       
       tab3 [label = 'N data inspected: 9',height = 1]
-      tab4 [label = 'N excluded following investigation: 6 \n\n Exclusion reasons:\n- Cross-sectional data (n= 2) \n- Cognitively impaired cohort (n= 2) \n- Dichotomised exposure (n=1)\n- Genetic risk cohort (n=1)',height = 2]
+      tab4 [label = 'N excluded following investigation: 6 \n\n For exclusion reasons,\n see Table 6.1',height = 2]
       tab5 [label = 'Final number of \ncohorts included: @@2-4',height = 1]
 
       subgraph {
@@ -142,7 +142,7 @@ if (doc_type == "docx") {
 # ---- prepIPDFigures
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
-# Main effectsl, dementia
+# Main effects, dementia
 main_effects <- rio::import(here::here("data/ipd/results_main.csv")) %>%
   filter(analysis == "Model 1",
          outcome == "Dementia") %>%
@@ -262,24 +262,39 @@ dev.off()
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # Main effects, Whitehall
 
-tyk <- rio::import(here::here("data/ipd/results_tyk.csv")) %>%
-  mutate(yi = log(yi),
-    sei = ((log(uci)-log(lci))/3.92)) %>%
-  select(-c(uci,lci))
+tyk <-
+  rio::import(here::here("data/sys-rev/data_extraction_main.xlsx"),
+              which = 2) %>%
+  general_filters() %>%
+  filter(study_id == 2140, 
+         cohort == "WHITEHALL") %>%
+  mutate(across(c(
+    point_estimate, starts_with(c("number_", "cases_")), ends_with("_ci")
+  ), as.numeric)) %>%
+  mutate(point = log(point_estimate),
+         SE = (log(upper_ci) - log(lower_ci)) / 3.92) %>%
[…]

### 2021-12-03 03-Chp-Systematic-Review-Methods.Rmd
End of day:

@@
 
-<!-- IDEA Stratify by ApoE4 genotype -->
+<!-- IDEA Stratify by _ApoE4_ genotype -->
 
@@
 
-## Lay summary
+::: {.laybox data-latex=""}
+## Lay summary {-}
 
@@
 Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
+&nbsp;
 
@@
 The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).
+:::
 
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
 ## Introduction {#sys-rev-intro}
@@
 
-#### Analysis overview
+#### Analysis overview {#sys-rev-analysis-overview}
 
@@
 
-The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc) are not directly interchangeable in the context of systematic review.
+The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc.) are not directly interchangeable in the context of systematic review.
 As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.

### 2021-12-03 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 # Individual participant data meta-analysis of blood lipid levels and dementia outcomes {#ipd-heading}
+
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-## Lay Summary
+## Lay Summary {-}
 
@@
 The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
-There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r tri_vasdem`).
+There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
 

### 2021-12-03 07-Chp-Triangulation.Rmd
End of day:

@@
 source("R/helper.R")
+knitr::read_chunk("R/03-Code-Systematic-Review.R")
 knitr::read_chunk("R/05-Code-CPRD-Analysis.R")
+knitr::read_chunk("R/06-Code-IPD-Analysis.R")
 knitr::read_chunk("R/07-Code-Triangulation-Analysis.R")
@@
 
-## Lay summary
+\newpage
+
+::: {.laybox data-latex=""}
+## Lay summary {-}
 
 __TBC__
+
+:::
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-
-\newpage
-
-\newpage
 
@@
 
-\newpage
+## Data sources {#tri-data-sources}
 
-## Methods
-### Data sources {#tri-data-sources}
-
-This triangulation exercise draws on the research produced in each of the preceding chapters.
+The triangulation exercises presented in this chapter draw on the research produced in each of the preceding chapters.
 More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
@@
 
-Table \@ref(tab:thesisOverview-table) summarises the research each data source has attempted to address, the exposures and outcomes considered in each case, and the contribution of each chapter to the triangulation exercise presented here.
+Table \@ref(tab:thesisOverview-table) summarises the research question each data source has attempted to address, the exposures and outcomes considered in each case, and the contribution of each chapter to the triangulation exercise presented here.
+
+<!-- TODO Consider adding AD as an outcome to the IPD row, depending on which result you want to use. -->
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
-
-### Qualitative triangulation / narrative comparison {#qual-tri}
-
-As discussed in the introduction to this Chapter (Section \@ref(triangulation-overview)), as part of a narrative synthesis of the evidence all information sources were initially grouped by outcome, and the findings from each source were narratively compared and contrasted.
-Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias assessments performed.
-
-This analysis built on the detailed risk-of-bias assessments performed and presented as part of the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)).
+Additionally, both the qualitative and quantitative triangulation exercises used the the detailed risk-of-bias assessments performed and presented as part of the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)).
 Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis.
-The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias), but in summary, RCTS were assessed using the RoB 2 tool;[@sterne2019] NRSI using the ROBINS-I tool;[@sterne2016] NRSE using the ROBINS-E tool (see Section \@ref(rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
+The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias), but in summary, RCTs were assessed using the RoB 2 tool;[@sterne2019] NRSI using the ROBINS-I tool;[@sterne2016] NRSE using an early adapted version of the ROBINS-E tool (see Section \@ref(rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
 tool.[@mamluk2020]
@@
 
-### Quantitative triangulation
+## Qualitative (narrative) triangulation
 
-In addition to a qualitative discussion of the evidence, I attempted to integrate the numerical results of the multiple approaches under a proposed quantitative triangulation framework.
+```{r rctStatinDementia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r Hypercholesterolemia, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrLipidsAD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r LipidsSD, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r lipidFrationsSetup, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r azd-text, echo = FALSE}
+```
+
+```{r prepIPDFigures,include=F}
+```
+
+As part of a qualitative triangulation of the new and existing evidence identified by this thesis, all information sources were initially grouped by outcome, and the findings from each source were narratively compared and contrasted.
+Potential reasons for heterogeneity between study designs were examined with specific reference to the risk-of-bias in each.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### All-cause dementia
+
+Analysis of lipid levels across both the systematic review (Chapter \@ref(sy-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-analysis-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
+Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
+Finally, a meta-analysis of RCTs of statin use (`r rct_statin_acd`) and of MR analyses of genetic instruments that mimic statin use (`r mrStatin$Dementia$estimate`) both found weak evidence of an association, providing indirect evidence on the effect of lipid lowering on this outcome.
+
+In contrast, the meta-analysis of NRSI of statin use found a slight protective effect (`r obsStatins$Dementia$estimate`), though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the intervention.
+Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(cprd-analysis-heading)) found evidence of a harmful association (`r anydem_sta_text`), though this is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
+
+For fibrates, an alternative lipid-regulating agent, there was some evidence of an increased risk of all-cause dementia in the CPRD (`r anydem_fib_text`), though this did not replicate in the meta-analysis of previous studies examining the association of fibrates and all-cause dementia (`r obsFibrates$Dementia$estimate`).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Alzheimer's disease
+
+Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (TC `r obsLipids$AD_TC$estimate`; LDL-c `r obsLipids$AD_LDL$estimate`; HDL-c `r obsLipids$AD_HDL$estimate`; triglycerides `r obsLipids$AD_TG$estimate`).
+Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`).
+A meta-analysis of MR analyses of genetic instruments that mimic statin use found weak evidence for an association of lipid lowering with Alzheimer's disease (`r mrStatin$AD$estimate`).
+
+In contrast, the meta-analysis of NRSI of statin use found a slight protective effect on this outcome (`r obsStatins$AD$estimate`), though similar to the all-cause dementia outcome, many of the studies in this analysis were found to be at risk of immortal time bias.
+However, the CPRD analysis, which attempted to account for this potential bias through the use of time-varying treatment indicator, found weak evidence for an effect (`r probad_sta_text`).
+This validity of this finding was limited by the potential for differential misclassification on the basis of the exposure in the CPRD analysis.
+
+Finally, the IPD analysis provided no additional information on the Alzheimer's disease outcome, as a previously published analysis examined the association of lipid levels with this outcome in the Whitehall II cohort.
+The published analysis was included in the meta-analysis of NRSE, the results of which are presented above.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+#### Vascular dementia
+
+There was a general absence of existing evidence on vascular dementia outcomes.
+Meta-analysis of published results was only possible for the total cholesterol lipid fraction (`r obsLipids$VaD_TC$estimate`).
+A meta-analysis of studies examining hypercholesterolemia also found weak evidence for an association with vascular dementia (`r obsHyperchol$VaD$estimate`).
+Similarly, a meta-analysis of statin use found weak evidence for an effect on this outcome (`r obsStatins$VaD$estimate`).
+The CPRD analysis found evidence for a harmful association of statin use (`r vasdem_sta_text`), though this finding is likely to be the result of severe confounding by indication related to vascular factors, as identified through the use of control outcomes.
+
+The IPD analysis provided supporting evidence for the absence of an effect of any fraction on vascular dementia, with the sole exception of triglycerides.
+Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts (`r ipd_vasdem`), though there is the potential for uncontrolled confounding due to the limited information on covariates available.
+With respect to evidence on treatments for hypertriglyceridemia, examination of fibrates in the CPRD provided weak evidence of an association with vascular dementia (`r vasdem_fib_text`).
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Quantitative triangulation
+
+The qualitative comparison presented above identified no consistent effect of any lipid fraction on any dementia outcome across the evidence sources presented in this thesis.
+However, it is clear that this qualitative approach faces difficulties in interpretation when the number of individual results available is large, as discussed in the introduction to this chapter.
+This is true even when using summary estimates from meta-analyses of primary studies, which sacrifice valuable information on the biases inherent to each individual result.
+
+In the following section, I propose and apply a novel quantitative triangulation framework to address these limitations.
+The absence of any clear signals across the evidence base does not make for particularly interesting case studies but I will nonetheless use the identified evidence to illustrate the novel methodological approach.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Methods
+
+In addition to the qualitative discussion of the evidence presented in Section (\@ref(qual-tri)), I attempted to integrate the numerical results of the multiple approaches under a proposed quantitative triangulation framework.
 This approach incorporates recent advancements in the way that bias in results is assessed (namely the move to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to illustrate how causal questions could be addressed under this framework.
@@
 1. Identify of relevant evidence sources and standardise effect directions
+1. Specify idealised version of each study
 1. Assess and visualise the extent and direction of bias in each result
@@
 all-cause dementia), focuses on an single causal pathway rather than including several conditions in the outcome definition that likely have very different mechanisms of disease.
-In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(hold)), and use of an composite all-cause outcome in the triangulation framework may mask this.
+In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(cprd-confounding-by-ind)), and use of an composite all-cause outcome in the triangulation framework may mask this.
 
@@
 
+#### Specify idealised version of each study
+
+Once the set of relevant results have been identified, an idealised study for each is described
+An idealised study can be viewed as a replicate of the study producing the result of interest but with all sources of bias removed.
+The risk of bias is then assessed against this idealised study, while the causal question addressed by each idealised study is compared with the target causal question to define the indirectness of each result.
+
+Note that all of the risk-of-bias tools used to assess non-randomised studies required specification of an idealised version of the study, against which bias was assessed.
+If using a risk-of-bias assessment tool that does not require this step, the idealised version of the study should be defined in advance of risk-of-bias assessment.
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ####	Assess risk and direction of bias in each result
 
-Risk of bias was assessed for each result as discussed in Section \@ref(qual-tri).
-For the sake of consistency and ease of computing, I mapped the different acceptable risk-of-bias judgements in each tool to a harmonised set: "Low", "Moderate", and "High".
+The assessment of bias in each result is discussed in Section \@ref(tri-data-sources) above.For the sake of consistency and ease of computing, I mapped the different acceptable risk-of-bias judgements in each tool to a harmonised set: "Low", "Moderate", and "High".
 The exact mapping can be seen in Table \@ref(tab:robLevelsMapping-table).
@@
 Acceptable responses to this question included:
+
+<!-- REVIEW in fact it is a mandatory part of new ROBINS-E tool, while only optional in RoB2 and ROBINS-I. Maybe reiterate that using a very early version of ROBINS-E -->
 
@@
 (ref:exampleDirection-cap) Illustration of calculating the absolute direction of biases (indicated by arrows), based on bias type.
-For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null - bias "favouring the comparator" will always pull the effect estimate to the right.
+For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null - bias "favouring the comparator" will always pull the effect estimate to the right, and can induce a change from a protective to harmful effect.
 In contrast, the position of the effect estimate is accounted for when determining the absolute direction of proportional biases, defined as towards or away from the null.
@@
 Distinct symbol pairs are used to denote additive and proportional biases.
+Illustrations of these are provided in the Section \@ref(quant-tri-results).
 
@@
 As an illustrative example, consider the first causal question of the interest in this exercise, the effect of LDL-c in mid-life on Alzheimer's disease.
-Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be down-weighted due to reduced relevance to the causal question.
+Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be adjusted and down-weighted due to reduced relevance to the causal question.
 
@@
 The adjusted estimate for each result, $\hat\theta$, is defined as:
+
+<!-- TODO Need to be able to explain the order in which the biases are adjusted for -->
 
@@
 
-<!-- IDEA Sensitivity analysis - set means to zero and only adjust for variance. Essentially adding uncertainty based on the amount of bias but not moving the effect estimate -->
+<!-- TODO Should a fixed or random effects be used, because in theory you are adjusting for all potential causes of heterogeneity. -->
 
@@
 
-## Results
-
-### Qualitative triangulation / narrative comparison
-
-__[Question: the "strength of evidence" language here makes for fairly ambiguous reading - e.g.
-"very weak evidence".
-Should I also include the effect estimates from each approach, which will help to clarify, if it is a narrative synthesis?]__
-
-```{r azd-text, echo = FALSE}
-```
-
-I identified no consistent effect of any lipid fraction on any dementia outcome across the evidence sources presented in this thesis, through there was some suggestion of a protective effect of LDL-c lowering (via statin use) on all-cause dementia and Alzheimer's disease, and a harmful effect of raised triglyceride levels on vascular dementia.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### All-cause dementia
-
-Analysis of lipid levels across both the systematic review (Chapter \@ref(hold)) and the IPD analysis (Chapter \@ref(hold)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia.
-Similarly, both a meta-analysis of RCTs of statin use and of MR analyses of genetic instruments that mimic statin use found very weak evidence of an association, providing indirect evidence on the effect of LDL-c lowering on this outcome.
-
-In contrast, the meta-analysis of NRSI of statin use found a slight protective effect, though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the intervention.
-Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(hold)) found evidence of a harmful effect, though this is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
-
-For fibrates, an alternative lipid-regulating agent, there was some evidence of an increased risk of all-cause dementia in the CPRD, though this did not replicate in the meta-analysis of previous studies examining the association of fibrates and all-cause dementia.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Alzheimer's disease
-
-Meta-analysis of lipid levels in the systematic review (Chapter \@ref(hold)) found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease.
-Similarly, a meta-analysis of MR analyses of genetic instruments that mimic statin use found very weak evidence of an association.
-
-In contrast, the meta-analysis of NRSI of statin use found a slight protective effect, though similar to the all-cause dementia outcome, many of the studies in this analysis were found to be at risk of immortal time bias.
-However, the CPRD analysis (Chapter \@ref(hold)) attempted to account for this potential bias through the use of time-varying treatment indicator.
-It found very weak evidence for an effect, though the potential for differential misclassification on the basis of the exposure limit the validity of this finding.
-
-The IPD analysis (Chapter\@ref(hold)) provided no information on this outcome, as the sole cohort containing data on Alzheimer's disease (Whitehall II) had previously been analysed in respect to this outcome and so was included in the meta-analysis of NRSE.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-#### Vascular dementia
-
-There was a general absence of existing evidence on vascular dementia outcomes.
-Meta-analysis of the small number of studies examing  lipid levels in the systematic review (Chapter \@ref(hold)) found extremely weak evidence for an association of any lipid fraction with vascular dementia.
-Similarly, a meta-analysis of statin use found very weak evidence for an effect on this outcome.
-The CPRD analysis (Chapter \@ref(hold)) found evidence for a harmful association of statin use with vascular dementia, though this finding is likely to be the result of severe confounding by indication, as identified through the use of control outcomes.
-
-Finally, the IPD analysis (Chapter \@Ref(hold)) provided supporting evidence for the absence of an effect of any fraction on vascular dementia, with the sole exception of triglycerides.
-Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts though there is the potential for uncontrolled confounding due to the limited information on covariates available.
-With respect to evidence on treatments for hypertriglyceridemia, examination of fibrates in the CPRD provided very weak evidence of an association with vascular dementia.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Quantitative triangulation
+### Results {#quant-tri-results}
 
@@
 
-As an illustrative example, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD are considered here.
+As an illustrative example of the process using a single result, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD (as analysed in Chapter \@ref(cprd-analysis-heading)) are considered here.
 For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
@@
 In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure.
-Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experiment_ (in this case, an intervention).
+Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experimental_ (in this case, an intervention).
 As such, the absolute direction of bias is to the left.
@@
 
-With respect to indirectness, the result was judged to be a low risk in the population and outcome domains.
-However, the fact the result refers to the effect of statins, which may have an effect on dementia outcomes through a mechanism other than LDL-c lowering, put it at high risk of indirectness in the intervention/exposure domain.
+Indirectness was intentionally not displayed in the plot above, as these figures are created using `robvis` which is focused on creating visualisations of risk-of-bias data.
+In addition, I found it more useful to articulate the indirectness of a result in tabular format.
+With respect to this example result, I judged it to be a low risk in the population and outcome domains (Table \@ref(tab:singleIndirect-table)).
+However, the result refers to the effect of statins on Alzheimer's disease risk, rather than LDL-c levels directly, putting it at high risk of indirectness in the intervention/exposure domain.
+Assessing the predicted direction of indirectness was more challenging than assessing the predicted direction of bias.
+In this case, treatment with statins result in temporary lowering of lipid levels which and could thus underestimate the true effect of LDL-c lowering (indirectness towards the null).
+In contrast, statins may have an effect on Alzheimer's disease through a mechanism other than LDL-c lowering effect of statins and so the effect is overestimated (indirectness away from null).
+As such, I judged the direction of indirectness in this domain to be unpredictable.
+
+<!-- TODO Consider timing of outcome as an issue - but is this a relevance or bias issue -->
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:singleIndirect-caption) Assessment of indirectness for a single example study.
+
+(ref:singleIndirect-scaption) singleIndirect
+
+```{r singleIndirect-table, message=FALSE, results="asis", echo = FALSE}
+```
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-The estimates obtained under the two scenarios of additive bias are plotted in Figure \@ref(fig:fpLdlAdComparison), and no substantial differences were observed between the them.
+No substantial differences were observed between the summary estimates obtained under the two scenarios of additive bias (Figure \@ref(fig:fpLdlAdComparison) in Appendix \@ref(appendix-tri-analysis)).
 
-<!----------------------------------------------------------------------------->
-(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
-The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
-
-(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
-
-```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
-knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
-```
-<!----------------------------------------------------------------------------->
+<!-- TODO Need to present overall summary estimate under two scenarios of bias and then send people to the Appendix. -->
 
@@
 Comparison of the unadjusted and bias-/indirectness-adjusted results for the effect of triglycerides on vascular dementia did not demonstrate a substantial difference (unadjusted `r unadj_effect_vad`; adjusted `r adj_effect_scenario1_vad`; Figure \@ref(fig:fpTgVad)), though again, heterogeneity between the adjusted results was greatly reduced (unadjusted $\tau^2$ = `r unadj_vad_tau2`, $I^2$ = `r unadj_vad_I2`; adjusted  $\tau^2$ = `r adj_vad_tau2`, $I^2$ = `r adj_vad_I2`).
-Similarly there was minimal difference between the results under the two scenarios of bias (Figure \@ref(fig:fpTgVaDComparison))
+Similarly there was minimal difference between the results under the two scenarios of bias (Figure \@ref(fig:fpTgVaDComparison) in Appendix \@ref(appendix-tri-analysis)).
+
+<!-- TODO Need to present overall summary estimate under two scenarios of bias and then send people to the Appendix. -->
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
-The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
-
-(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
-
-```{r fpTgVaDComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVaDComparison-cap)', out.width='100%', fig.scap='(ref:fpTgVaDComparison-scap)'}
-knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad_scenarios.png"))
-```
-<!----------------------------------------------------------------------------->
-
 ## Discussion
@@
 To illustrate the method, I considered two causal questions: the effect of LDL-c at mid-life with Alzheimer's disease and the effect of triglycerides on vascular dementia.
-In the quantitative triangulation framework, there was very weak evidence for an effect in relation to either of the causal questions considered.
+In the quantitative triangulation framework, there was weak evidence for an effect in relation to either of the causal questions considered.
 The heterogeneity between results produced by different study designs contributing to the analysis was substantially reduced using this method, though this was largely due to a reduction in the precision of each individual result.
@@
 
+<!-- TODO Also mention here that when the number of results is large, performing elictation for each separately in addition to the risk of bias assessments is going to be difficult. -->
+
 A further limitation is the assumption that the distributions of bias are identical across domains of bias.
@@
 A key issue in this analysis is the accuracy of the assessment of bias and indirectness in each result.
-It has been widely demonstrated that the inter-rater agreement when using risk-of-bias tools is low with regards to the extnet of bias assinged to each domain[@hartling2011; @minozzi2019; @minozzi2020] Though not previously studied, given the difficulty in assessing the predicted direction of bias, agreement on this aspect of the tools is likely to be lower still.
+It has been widely demonstrated that the inter-rater agreement when using risk-of-bias tools is low with regards to the extent of bias assigned to each domain[@hartling2011; @minozzi2019; @minozzi2020] Though not previously studied, given the difficulty in assessing the predicted direction of bias, agreement on this aspect of the tools is likely to be lower still.
 
-A further issue in this regard is that rigourness of the tools may not be equivalent.
+A further issue in this regard is that the rigour of the tools may not be equivalent.
 This issue can be illustrated by the Ostergaard _et al._ study[@ostergaard2015] having low risk of bias across all domains and thus receiving a substantial proportion of the weight in the first case study (Figure \@ref(fig:fpLdlAd)).
@@
 This observation is particularly problematic given the default position of the ROBINS-I and ROBINS-E tool to require a "Moderate" judgement in the confounding domain.
-Under these conditions, it is possible that a well performed cohort study (low risk of bias across everything other that bias due to confounding) will be down-weighted versus a potentially poor MR study.
+Under these conditions, it is possible that a well-performed cohort study (low risk of bias across everything other that bias due to confounding) will be down-weighted versus a potentially poor MR study.
 
@@
 A final limitation to this analysis is the synthesis of different effect estimates.
-As discussed in Section \@ref(hold), hazard ratios are not directly comparable to odds ratios, as they inherently account for person time-at-risk.[@mckenzie2019] As non-randomised studies (NRSI/NRSI) of dementia outcomes report hazard ratios and Mendelian randomisation studies report odds ratios, the resulting synthesis may be biased by the integration of these two different effect measures.
+As discussed in Section \@ref(sys-rev-analysis-overview), hazard ratios are not directly comparable to odds ratios, as they inherently account for person time-at-risk.[@mckenzie2019] As non-randomised studies (NRSI/NRSI) of dementia outcomes report hazard ratios and Mendelian randomisation studies report odds ratios, the resulting synthesis may be biased by the integration of these two different effect measures.
+This is primarily a concern for common outcomes, as when the outcome is rare, the odds, risk and hazard ratios approximate each other.
 
-<!-- TODO Need to add some text here that says that assessment of the different domains  -->
-
-__[Note: I would be particularly interested in your feedback here.
-It seems quantitative triangulation will frequently require integration of different effect measures if comparing e.g.
-NRSI reporting hazard ratios with MR reporting odds ratios.
-How should this be handled?]__
+<!-- REVIEW Could add that ORs could be converted to RRs using a measure of "hyptothecial" risk -->
 
@@
 A further advantage of this method comes from the ability to specify the prior distributions for each level of bias/indirectness in advance of performing the assessments.
-In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process using a panel of methodologists and topic experts.[@thompson2011; @turner2009; @wilks2011] However, this approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
-As an illustrative example, if experts are influenced by the knowledge of the effect estimate in a study, then a result demonstrating a stronger protective effect may receive greater modification than a study at the same "risk" of confounding but with a more modest effect.
-This is likely to be part where experts have preconceived ideas about the true effectiveness of the intervention.
-In this case, separating the assessment of bias/indirectness from the assignment of modifying values to each judgement will limit the potential for this misclassification.
-Using the framework proposed, reasonable modifying distributions for each level of bias could be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016]
+Expert elicitation of the extent of bias/indirectness using a panel of methodologists and topic experts is a powerful technique but the point at which it is deployed in the framework is important.
+In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process,[@thompson2011; @turner2009; @wilks2011] during which experts were aware of the results of each analysis.
+This approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
+As an illustrative example, if experts are influenced by the knowledge of the effect estimate in a study, then a result at "Moderate" risk of confounding and demonstrating a stronger protective effect may receive greater adjustment than a study at the same risk of confounding but with a more modest effect.
+This is likely to be particularly problematic where experts have preconceived ideas about the true effectiveness of the intervention.
+
+Separating the assessment of bias/indirectness from the assignment of modifying values to each judgement will limit the potential for this misclassification.
+Using the framework proposed, reasonable modifying distributions for each level of bias can be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016] As an example, expert elicitation could be used to _a priori_ define an additive bias distribution of N(.1,0.7) for "Moderate" risk of bias in Domain 1 of the ROBINS-I tool (bias due to confounding).
+Risk-of-bias assessments are then performed, and each result at "Moderate" risk of bias in Domain 1 is adjusted using this pre-specified distribution.
 
@@
 
-\newpage
+### Future research
 
-### Future research
+<!-- REVIEW Good to mention direct adjustment for bias, e.g. Greenlands writings -->
 
@@
 The implications of the synthesised evidence presented here to clinical practice, public health and future research is considered in the following chapter.
-
-\newpage
-
-## References

### 2021-12-03 08-Discussion.Rmd
End of day:

@@
 # Discussion {#discussion-heading}
+
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
@@
 
-<!----------------------------------------------------------------------------->
-&nbsp;
+\newpage
 
-## Lay summary
+::: {.laybox data-latex=""}
+## Lay summary {-}
 
-TBC
+__TBC__
 
-\newpage
+:::
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-\newpage
+&nbsp;
 
@@
 
-This thesis is comprised of a mix of informative, methodological and applied chapters.
+This thesis is comprised of a mix of methodological and applied chapters.
 
-In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in thie
+In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and presented the research performed in terms fo the theoretical framework of evidence synthesis.
 
-In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints, and detail
+In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints, and detailed two use cases for preprint metadata beyond the systematic searching of this evidence source.
 
-In __Chapters \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of the relationship between dementia outcomes and blood lipids (and treatments that modify them).
+In __Chapter \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of the relationship between dementia outcomes and blood lipids (and treatments that modify them).
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
 
-In __Chapter \@ref(cprd-heading)__, I describe an analysis of lipid-regulating use and dementia outcomes in the CPRD, a large scale electronic health database.
-I make use of control outcomes to illustrate insufficiently controlled biases
+In __Chapter \@ref(cprd-heading)__, I describe an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
+I make use of control outcomes to illustrate insufficiently controlled confounding.
 
-In __Chapter \@ref(ipd-heading)__, I present an individual patient data meta-analysis, using previously unanalysed data accessed via the Dementia Platform UK to add to the evidence base on the association of blood lipids and dementia outcomes.
+In __Chapter \@ref(ipd-heading)__, I present an individual patient data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.
 
-Finally, in __Chapter \@ref(tri-heading)__ I propose a new method of systematically integration of multiple evidence sources as part of quantitative triangulation exercise.
-I illustrate the method by considering two causal questions (LDL-c and Alzheimer's disease; triglycerides and vascular dementia), drawing on the evidence identified or produced by previous chapters.
+Finally, in __Chapter \@ref(tri-heading)__ I propose a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework.
+I illustrate the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.
 
@@
 
-\newpage
-
 ### Lessons learned
 
-As a reflective process throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing . here I present a more general rel
+Throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing specific analytical failures .
+here I present a more general reflection on the core takeaways.
 
-In hindsight, the decision to take a broad approach to inclusion of dementia outcomes potentially resulted in larger workload than anticipated, particularly when considered evidence from across different study designs.
-In a do-over, I would have considered a single dementia outcome.
+The central
 
-Additionally, in hindsight, I may have considered a more methodological thesis. The Chapter's I enjoyed working on the most (Chapters \@ref())
+A particular lesson is the better scoping of future work.
+In hindsight, the decision to take a broad approach to inclusion of dementia outcomes resulted in larger workload than anticipated, particularly when considering evidence from across different study designs.
+Given the opportunity to redesign the review, I would have chosen to focus on a specific dementia outcome.
 
-Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors
+Similarly, the decision to attempt to undertake a individual patient data analysis was
 
-However, normal opportunities to tie people down in person were suspended during COVID.
+<!-- Finally, -->
+
+<!-- Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors -->
+
+<!-- However, normal opportunities to tie people down in person were suspended during COVID.  -->
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-
-\newpage
 
@@
 Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).
+
 While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
@@
 However, this observed effect could also be due to reporting biases, a
-
-The inclusion of preprints
 
@@
 
-Since the systematic review described in this thesis was performed, there have been two notable analysis of large cohorts performed related to the central thesis question here.
+Since the searches underpinning the systematic review described in this thesis were performed (July 2019), there have been some notable analysis of large cohorts performed related to the central thesis question here.
 Two of these are discussed here notable studies are discussed here.
 
-The first a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are  consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
-<!-- TODO The study says that simulated effect of _ApoE4_ is a 1.09 RR in the absence of a true causal effect.
-Main results are between 1.03 and 1.17.
-CI for most extreme results is (lower = 1.08) is not inconsistent with the effect introduced by _ApoE4_ which is just a single confounder out of many -->
+The first is a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
+The study performed a simulation study to investigate the expected effect of confounding by _ApoE4_ in the absence of a true causal effect, yeilding a RR of 1.09 per 1-SD increase in LDL-c.
 
-The UKBioBank is a [@sudlow2015]
-
-A recent analysis of 502,226 participants of this found no association between lipids at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.06,1,1.13,"HR")`/men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97,.91,1.04,"HR")`).[@gong2021] Results were boardly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes.
-This is comparable to my findings.
+The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.06,1,1.13,"HR")`/ men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97,.91,1.04,"HR")`).
+The results were broadly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes, and are comparable to the results of this thesis.
+However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _ApoE4_ genotype.
 
@@
 
-This should focus on doctors being honesty with patients from the outset and describing what they know regarding the uncertainty of the evidence.
+The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
+Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
+In addition, a lack of precision makes
+
+This should focus on doctors being honest with patients from the outset and describing what they know regarding the uncertainty of the evidence.
+
+Clinicians should convey the uncertainty of evidence
 
@@
 To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.
-
-The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
-Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
 
@@
 ### Preprint search tool
+
 \newpage
@@
 ### Inclusion of preprints
+
+This thesis provided evidence that the preprints can provide additional evidence to the published literature,
+
 \newpage
@@
 ### Risk of bias visualisation
+
 \newpage
@@
 ### Triangulation framework
+
+this thesis has also proposed a novel combination of existing methods as a move towards a , based on devl
 
@@
 
-The strengths a limitations of each component of this thesis have been discussed in the respective chapters. Here I highlight the strengths and weakness of the thesis as a body of work.
+The strengths a limitations of each component of this thesis have been discussed in the respective chapters. Here I highlight the strengths and weaknesses of this thesis as a body of work.
 
@@
 
-This thesis has used multiple sources of evidence to examine the relationship between blood lipids levels and cholesterol risk in a systematic manner, including diverse sources of evidence, inclu
+There are several strengths to this thesis as a whole.
+The use of a systematic review incorporating multiple study designs and preprinted literature provided a strong and comprehensive evidence base with which to assess my research question.
 
-It has highlighted the importance of including preprints in systematic review, and provided a tool to enable researchers to easily do so.
+This thesis has also produce new evidence on the association of blood lipids on dementia outcomes via two primary analysis.
+Specifically, it has provided additional information on a previously understudied association (lipids/LRA and vascular dementia).
 
-It has provided new evidence on an understudied condition (vascular demenita), analysing three previously unexplored datasets to provide evinde
+A focus on bias has been a central aspect of this thesis.
+In the systematic review, detailed risk of bias assessments were used to assess the bias, while in the CPRD analysis, controls outcomes were used to provide evidence for uncontrolled bias due to confounding.
+Finally, the triangulation framework presented in Chapter \@ref(hold) seeks to adjust for the bias in each resul.
 
-- New evidence sources for an under-studied condition
-- Development of new methods and tool
-
-One particularly strength is the lengths gone to find all available published and unpublished evidence around the question, and to integrate this evidence in a coherent framework, taking into account the limitations of ach source and how these limitations may be used to provide
+A final strength of this thesis is the production of software to support the novel evidence synthesis techniques used.
 
@@
 
-However, the thesis as a whole is subject to some strong limitations.
+However, there are several strong limitations to this thesis.
 
-A general limitation of this thesis is the absence of known results/data.
-This occurred in both the systematic review, via the selection of reporting results and potential for publication bias.
-It was also observed.
+Each analysis presented makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
+Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in, absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data, if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records can be poor[@wilkinson2018]).
 
-Similarly, missing evidence was a common theme across this thesis.
+Further, missing evidence was a common limitation across this thesis.
 In Chapters \@ref(hold)/\@ref(hold), several studies stated that they did not report the results of an analysis because the results were not significant.
 This was particularly common among non-randomised studies of exposure examining blood lipids directly.
-Fortunately, new tools such as the forthcoming ROB-ME.
+Similarly, an absence of evidence on vascular dementia, potentially due to a publication bias mechanism, limited the analysis of this outcome.
+Finally, missing evidence also presented as an issue in the form of a poor response to data access requests was also observed in the IPD analysis reported in Chapter \@ref(hold).
 
-Similarly, an absence of evidence on vascular dementia limits the certainty.
-In both these cases, accounting for missing evidence will be an important part of future evidence snythesis work on this topic.
-
-Missing evidence in the form of a poor response to data access requests was also observed in the IPD analysis reported in Chapter \@ref(hold).
-
-A final weakness of this thesis is the geographical focus. All primary analysis presented drew on data from the UK population (CPRD, CaPS, EPIC Norfolk, Whitehall II).
+A final weakness of this thesis is the geographical focus.
+All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world.
+This may limit the generalisability of the results presented to different populations.
 
@@
 
-Several avenues for future research, building on the work presented here, are possible.
+Several avenues of future research, building on the work presented here, could be pursued.
 
@@
 
-Preprints also represent a key opportunity to assess the impact of peer review on qualitative changes within
+Preprints also represent a key opportunity to assess the impact of peer review and editorial guidelines on manuscripts, by enabling a comparison of the same paper at two stages (preprinted versus published).
+This fact was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(), but could be used to other important meta-research questions.
 
-Future work should also address how to handle discrepancies between the preprinted and published versions of a paper, particularly if the results are subtantially different between the two versions.
+Future work should also address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in an evidence synthesis exercise.
+This will be particularly important if the results are substantially different between the two versions or if a result availble in the preprint manuscript is not presented in the published version.
+
+Finally, the availability of the `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool into an automated searching pipeline as part of a living systematic review.
 
@@
 
-Future work should aim to address this evidence gap.
-
-large-scale GWAS of vascular dementia should be performed, to identify associated loci that future Mendelian randomisation studies can make use of.
-While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, and would allow for the assessment of many genetically driven risk factors beyond those considered in this thesis.
+Future work should aim to both investigate the reasons for this evidence gap and work to address it.
+In particular, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future two-sample Mendelian randomisation studies could make use of.
+While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, allowing for the assessment of many genetically-driven risk factors beyond those considered in this thesis.
 
@@
 
-### Empirical estimates of bias
+### Triangulation
+
+It is customary at this point to recommend that a large scale randomised controlled trials be designed to run to assess the effect of the intervention.
+Given the logistical challenges of trials for outcomes with long prodomal periods such as dementia, is the post-trial follow-up of existing RCTs of lipid-regulating agents.
+Examples of this approach for long term (11-20 years) assessment of safety outcomes associated with statin use, using patient recontact and linkage with electronic health records.[@ford2016; @group2011] A similar approach could be used to assess the impact of randomisation to statins in these trials on dementia outcomes.
+
+However, in general there is a need to better make use of non-randomised evidence, particularly in areas where RCTs are not easily performed.
+As such, quantitative triangulation is an  one ripe for future work.
+
+Future work would account for methods for adjustment of meta-biases, such as those introduced by
+
+These domains specific distritions should
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->  
-\newpage
-
-It is customary at this point to recommend that a large scale. However, based on the evidence described. In addition, logistical challenges in relation
-
-Opportunistic follow-up of established trials.
-
-&nbsp;<!----------------------------------------------------------------------->  
-\newpage
-
-### Triangulation
-
-In summary, there is a need to make better use of the existing evidence accounting for the
-
-The field of quantitative triangulation is one ripe for future work.
-
-In the first instance, guidance
-
 Finally, accounting for bias (and indirectness, if considering causal effects rather than a summary of the literature) is essentially in the interpretation of published literature.
-While this can take many forms, from the stratification of forest plots by overall risk of bias level, to the or to the more advance bias adjustment approach detailed here, it is insufficient to draw clinical recommendations from meta-analysis that treat effect estimates as if they were unbiased.
+While this can take many forms, from the stratification of forest plots by overall risk of bias level, to the or to the more advanced bias adjustment approach detailed here, it is insufficient to draw clinical recommendations from meta-analysis that treat effect estimates as if they were unbiased.
 
@@
 
-The
-
-In addition, I have created
-
-and proposed a novel combination of existing methods in pursuit of a generalised quantitative framework.
-
-This thesis has made unique and novel contributions to the
-
-Illustrating that commonly employed approaches to address
-
-Blood lipids
+This thesis provides new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlights the uncertainty that still remains in relation to this causal question.
+In addition, it has developed new evidence synthesis methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources.

### 2021-12-03 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 <!----------------------------------------------------------------------------->
-# By Chapter {#chapter-appendix-heading}
+# Appendices by Chapter {#chapter-appendix-heading}
+
+\minitoc <!-- this will include a mini table of contents-->
 
@@
 
-* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered seperate things here.[@sterne2013]
+* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered separate things here.[@sterne2013]
 
@@
 
+### Code lists
+
+## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
+<!----------------------------------------------------------------------------->
+### Email and documents sent to potental collaborators {#ipd-email-collab}
+
 <!----------------------------------------------------------------------------->
@@
 
-## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
 <!----------------------------------------------------------------------------->
-### Email and documents sent to potental collaborators {#ipd-email-collab}
+### Comparison of two scenarios of bias
+
+<!----------------------------------------------------------------------------->
+(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
+The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
+
+(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+
+```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_ldl_ad_scenarios.png"))
+```
+<!----------------------------------------------------------------------------->
+
+<!----------------------------------------------------------------------------->
+(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
+The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
+
+(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+
+```{r fpTgVaDComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpTgVaDComparison-cap)', out.width='100%', fig.scap='(ref:fpTgVaDComparison-scap)'}
+knitr::include_graphics(file.path("figures/tri/fp_paired_midlife_tg_vad_scenarios.png"))
+```
+<!----------------------------------------------------------------------------->
 

### 2021-12-03 R/05-Code-CPRD-Analysis.R

@@ -415,6 +415,18 @@ probad_fib_text <- paste0(
   round(probad_fib$ci_upper, 2)
 )
 
+probad_sta <- results %>%
+  filter(outcome == "Probable AD" & drug == "Statins")
+
+probad_sta_text <- paste0(
+  "HR:",
+  round(probad_sta$HR, 2),
+  ", 95%CI:",
+  round(probad_sta$ci_lower, 2),
+  "-",
+  round(probad_sta$ci_upper, 2)
+)
+
 possad <- results %>%
   filter(outcome == "Possible AD" & drug == "Any")
 
@@ -449,6 +461,30 @@ vasdem_eze_text <- paste0(
   round(vasdem_eze$ci_lower, 2),
   "-",
   round(vasdem_eze$ci_upper, 2)
+)
+
+vasdem_fib <- results %>%
+  filter(outcome == "Vascular dementia" & drug == "Fibrates")
+
+vasdem_fib_text <- paste0(
+  "HR:",
+  round(vasdem_fib$HR, 2),
+  ", 95%CI:",
+  round(vasdem_fib$ci_lower, 2),
+  "-",
+  round(vasdem_fib$ci_upper, 2)
+)
+
+vasdem_sta <- results %>%
+  filter(outcome == "Vascular dementia" & drug == "Statins")
+
+vasdem_sta_text <- paste0(
+  "HR:",
+  round(vasdem_sta$HR, 2),
+  ", 95%CI:",
+  round(vasdem_sta$ci_lower, 2),
+  "-",
+  round(vasdem_sta$ci_upper, 2)
 )
 
 othdem <- results %>%
@@ -498,6 +534,19 @@ anydem_fib_text <- paste0(
   "-",
   round(anydem_fib$ci_upper, 2)
 )
+
+anydem_sta <- results %>%
+  filter(outcome == "Any dementia" & drug == "Statins")
+
+anydem_sta_text <- paste0(
+  "HR:",
+  round(anydem_sta$HR, 2),
+  ", 95%CI:",
+  round(anydem_sta$ci_lower, 2),
+  "-",
+  round(anydem_sta$ci_upper, 2)
+)
+
 
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-

### 2021-12-03 R/forest tri.R

@@ -9,7 +9,7 @@ forest_triangulation <-
 
 levels <- c("Low","Moderate","Serious","Critical")
 
-levels_type <- c("MR","NRSE","NRSI")
+levels_type <- c("MR","NRSI","NRSE")
   
 # TODO the ordering of ROB is not quite right!
 dat <- dat %>%

### 2021-12-03 R/helper.R

@@ -205,8 +205,8 @@ make <- function(arg = "pdf") {
 
 # Generate word count report
 covering <- function() {
-  rmarkdown::render("front-and-back-matter/_00-introduction.Rmd")
-  browseURL("front-and-back-matter/_00-introduction.html")
+  rmarkdown::render("scripts_and_filters/covering.Rmd")
+  browseURL("scripts_and_filters/covering.html")
 }
 
 
@@ -272,9 +272,19 @@ todo_report <- function(fp){
 #' @param N Chapter number
 
 chapter_edit <- function(N, all = TRUE) {
-  # Open Chapter RMarkdown file
-  chapters <- list.files(pattern = ".Rmd")
   
+  # If character, search front and back matter
+  if (is.character(N)) {
+    
+    chapters <- list.files(path = "front-and-back-matter/",pattern = ".Rmd",full.names = T)
+
+  } else{
+    
+   chapters <- list.files(pattern = ".Rmd")
+  
+  }
+  
+  # Open Chapter RMarkdown file
   chapter <- chapters[which(data.table::like(chapters, N))]
   
   file.edit(chapter)

### 2021-12-05 01-Chp-Background.Rmd
Working version

@@
 * Inclusion of preprints
-* Individual patient data meta-analysis
+* Individual participant data meta-analysis
 * Triangulation across evidence sources
@@
 
-### Individual patient data meta-analysis
+### Individual participant data meta-analysis
 
@@
 -   **Chapter \@ref(cprd-analysis-heading):** This chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This chapter describes an individual patient data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
+-   **Chapter \@ref(ipd-heading):** This chapter describes an individual participant data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
 -   **Chapter \@ref(tri-heading)**: This chapter integrates the evidence identified and produced by the preceeding chapters as part of a quantitative triangulation framework.
@@
 Finally, I discussed the research tools and software developed to support the analyses in this thesis, one of which (the preprint search tool) is introduced more fully in the following chapter.
-
-\newpage

### 2021-12-05 04-Chp-Systematic-Review-Results.Rmd
End of day:
Working version

@@
 
+```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
+```
+
+```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
+```
+
 The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
@@
 
-```{r obsStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
 In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
@@
 
-```{r mrStatins, include = FALSE, message=FALSE, warning=FALSE}
-```
-
 Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
@@
 #### Fibrates
-
-```{r obsFibrates, include = FALSE, message=FALSE, warning=FALSE}
-```
 
@@
 Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
-However, the inclusion of the preprinted study did not have a substantial impact on the result of the meta-analysis (`r mrStatin$AD$estimate`) as compared to that reported by the single published study (`r estimate(0.59,0.25,1.39,"RR")`).
+However, the inclusion of the preprinted study did not have a substantial impact on the result of the meta-analysis (`r mrStatin$AD$estimate`) compared with that reported by the single published study (`r estimate(0.59,0.25,1.39,"RR")`), other than a slight increase in precision.
 

### 2021-12-05 06-Chp-IPD-Analysis.Rmd
Working version

@@
 <!-- TODO Finish lay summary -->
+
+<!-- At the same time, I will write to authors to obtain anonymised data on individual participants.
+The data from each study will be combined using a technique known as individual participant data (IPD) meta-analysis.
+This will allow me to examine if the relationship between lipids in dementia depends on any patient characteristics (e.g.
+sex or age).
+-->
 
@@
 
+<!-- TODO May need to talk about other confounders here -->
+
 A key limitation of this analysis is the potential for uncontrolled confounding.
@@
 Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
-While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of my PhD.
+While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of a PhD.
 
@@
 - The new evidence produced by this analysis will be incorporated, along with evidence identified or produced in the previous chapters, into the triangulation analysis presented in the following chapter.
-
-\newpage
-
-## References

### 2021-12-05 07-Chp-Triangulation.Rmd
Working version

@@
 ```
-(ref:tri-quote) --- Sir Austin Bradford Hill, 1965 [@hill1965]
+(ref:tri-quote) --- Austin Bradford Hill, 1965 [@hill1965]
 
@@
 ## Lay summary {-}
+
+<!-- Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
+Different sources of evidence will have different limitations.
+If the result from each source points towards the same answer, this improves our confidence in the conclusion.
+-->
 
@@
 
-## Qualitative (narrative) triangulation
+## Qualitative (narrative) triangulation {#qual-tri}
 
@@
 In the following section, I propose and apply a novel quantitative triangulation framework to address these limitations.
-The absence of any clear signals across the evidence base does not make for particularly interesting case studies but I will nonetheless use the identified evidence to illustrate the novel methodological approach.
+This approach incorporates recent advancements in the way that bias in results is assessed (namely the move to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to integrate the numerical results of the multiple approaches.
+The absence of any clear signals across the evidence base, as detailed in the previous section, does not make for particularly interesting case studies but I will nonetheless use the identified evidence to illustrate the novel methodological approach.
 
@@
 
-In addition to the qualitative discussion of the evidence presented in Section (\@ref(qual-tri)), I attempted to integrate the numerical results of the multiple approaches under a proposed quantitative triangulation framework.
-This approach incorporates recent advancements in the way that bias in results is assessed (namely the move to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to illustrate how causal questions could be addressed under this framework.
-
-This proposed framework involves several steps, described in detail in the following sections. In summary, these steps are:
+The proposed framework involves several steps, described in detail in the following sections. In summary, these steps are:
 
@@
 1. Specify idealised version of each study
-1. Assess and visualise the extent and direction of bias in each result
+1. Assess the extent and direction of bias/indirectness in each result
 1. Define modifying terms for bias and indirectness in each result
@@
 
-__Case study #1: Effect of mid-life LDL-c on Alzheimer's disease__
+_Case study #1: Effect of mid-life LDL-c on Alzheimer's disease_
 
@@
 
-__Case study #2: Effect of mid-life triglycerides on vascular dementia__
+_Case study #2: Effect of mid-life triglycerides on vascular dementia_
 
@@
 
+<!-- QUESTION Should population here include a geographical aspect, as in the Discussion I say that the generalisability to other populations is an issue. -->
+
 &nbsp;
 
-These questions were chosen for several reasons.
+These causal questions were chosen for several reasons.
 Firstly, work presented in previous chapters had identified some evidence for an association in these exposure/outcome pairs.
@@
 In this case, the effect estimates were inverted to ensure consistency across study designs.
+
+<!-- TODO Note that the results are converted to the log scale. -->
 
@@
 ####	Assign modifying values to risk/direction of bias
-<!-- TODO Note that they are on the log scale - Lines 45-50 of addbias -->
+<!-- TODO Note that they are on the log scale, and that this requires the results to be on the log scale too! - Lines 45-50 of addbias -->
 
@@
 
-<!-- QUESTION sign is negaitve if to the left, because you are taking it away in the final formula and it therefore needs a negative sign to be positive overall! -->
+<!-- QUESTION sign is negative if to the left, because you are taking it away in the final formula and it therefore needs a negative sign to be positive overall! -->
+
+<!-- TODO Need to explain here that for proportional bias, the results are exponentiated  -->
 
@@
 <!-- TODO Need to be able to explain the order in which the biases are adjusted for -->
+
+<!-- TODO Talk about validation at some point -->
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Defining reasonable prior distributions for bias and indirectness
@@
 
-#### Accuracy of bias-/indirectness-assessment
+#### Accuracy of bias-/indirectness-assessment {#tri-accuracy}
 
@@
 <!-- REVIEW Could add that ORs could be converted to RRs using a measure of "hyptothecial" risk -->
+
+<!-- TODO An extra step of the process should be the consideration of whether it is reasonable to synthesis across different effect estimates.
+Fine for rare, not for common.
+Fancy models that can be used to synthesis effect estimates are still compatabile with this approach as each invidual estimate is first adjusted and the adjusted estimate can then be used with whatever meta-anlaysis technique you like.
+-->
 

### 2021-12-05 08-Discussion.Rmd
Working version

@@
 
-```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = FALSE}
+```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = TRUE}
 Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
@@
 \minitoc <!-- this will include a mini table of contents-->
-
-<!-- ## Additional topics for the discussion -->
-
-<!-- There are several addition topics I would like to cover: -->
-
-<!-- * The difference between the peer review of the software vs.
-the peer review of papers.
-A conversation until everything is fixed/clear reporting guidelines/checklists, with acceptance dependent on them being implemented /built-in version control, and cross linking discussion points to changes through the linking of commits and comments.
-Essentially, a more transparent and open -->
 
@@
 
-In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and presented the research performed in terms fo the theoretical framework of evidence synthesis.
+In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research performed in terms fo the theoretical framework of evidence synthesis.
 
@@
 
-In __Chapter \@ref(ipd-heading)__, I present an individual patient data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.
+In __Chapter \@ref(ipd-heading)__, I present an individual participant data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.
 
@@
 
-### Lessons learned
-
-Throughout the PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing specific analytical failures .
-here I present a more general reflection on the core takeaways.
-
-The central
-
-A particular lesson is the better scoping of future work.
-In hindsight, the decision to take a broad approach to inclusion of dementia outcomes resulted in larger workload than anticipated, particularly when considering evidence from across different study designs.
-Given the opportunity to redesign the review, I would have chosen to focus on a specific dementia outcome.
-
-Similarly, the decision to attempt to undertake a individual patient data analysis was
-
-<!-- Finally, -->
-
-<!-- Further, a more aggressive approach to , Potential approaches could have included sending emails via my supervisors -->
-
-<!-- However, normal opportunities to tie people down in person were suspended during COVID.  -->
-
-<!-- Systematic reviews should not be performed as part of a thesis, without suitable support and resourcing guaranteed.
-Assumption that everyone does a systematic review (without risk-of-bias assessments, inclusion of all literature, searching for other reviews) is foolish.
--->
-
-<!-- Average time to complete a s -->
-
-<!-- However, new developments such as automated screening would allow for a reduced need for personnel to work on these things. [@pham2021] -->
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### Reproducible research
-
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
-In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
-
-Unfortunately, given the.
-However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
-
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
-
-One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
-However, access is dependency on an ISAC application to the managing body of the CPRD.
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-\newpage
-
 ## Summary of clinical findings
@@
 
+As the results of the different components of this thesis are discussed in detail as part of the triangulation analysis (see Section \@ref(qual-tri))
+
 Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).
 
-While published non-randomised studies provided evidence for a protective effect of statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
-However, this equally may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering.
-However, this observed effect could also be due to reporting biases, a
+While published non-randomised studies provided evidence for a protective effect of lipid-lowering via statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
+However, this may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering.
 
-Statins were by far the most studied lipid-regulating agent in relation to dementia outcomes, a unsurprising finding given the large proportion of patients taking statins as indicated by my analysis of the CPRD data.
+In the published literature, statins were by far the most studied lipid-regulating agent in relation to dementia outcomes.
+Given the large proportion of patients taking statins as indicated by my analysis of the CPRD data, this finding is unsurprising.
 
-The inclusion
+There was a substantial absence of evidence for vascular dementia.
+This may be due to absence of vascular dementia GWAS, which preclude use of two-sample Mendelian randomisation studies, or could potentially be due to a publication bias mechanism.
 
 &nbsp;<!----------------------------------------------------------------------->
-
-\newpage
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-\newpage
 
@@
 
-The clinical recommendations that can be drawn from the work in this thesis are limited, due to the low strength of evidence.
-Across multiple sources of evidence, there was no consistent effect of blood lipids on dementia outcomes.
-In addition, a lack of precision makes
+Given the absence of any consistent signals across the evidence sources analysed, there are no clear indications for clinical practice.
+While this thesis did not provide any evidence for an effect of lipid-lowering on dementia outcomes, the cumulative strength of evidence is also insufficient to rule out an effect.
 
-This should focus on doctors being honest with patients from the outset and describing what they know regarding the uncertainty of the evidence.
+Given this ambiguity, the use of statins should be restricted to their primary and well-understood purpose of lipid-lowering to reduce risk of cardiovascular events.
+However, it is important to recognise that even under the scenario that a strong harmful effect of lipid-lowering was identified, whether or not to prescribe a statin at mid-life will always be guided by factors other than dementia prevention.
+Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early-onset dementias), which is substantially less likely if hypercholesterolemia at mid-life is left unchecked.
 
-Clinicians should convey the uncertainty of evidence
+As with many many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
+It could well be that statins do have a true effect independently of lipid-lowering, as observed in published NRSI.
 
-While also recognising that the impact of statin or other LRA use on dementia is going to be secondary to their established effect on lipid-lowering.
-To even be at risk of developing dementia, patients must survive to old-age, something that is substantially less likely given uncontolled hypercholesterolaemia.
-
-However, even under the scenario that a strong protective effect was identified, whether or not to prescribed a statin at mid-life will always be guided by factors other than dementia prevention.
-Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early onset dementias), which is substantially less likely if hypercholesterolemia is left unchecked.
-
-However, while this thesis did not provide any evidence for a protective effect of lipid-lowering, it similarly did not provide any evidence for a harmful effect of statin exposure on dementia outcomes.
-
-There was very we. Conversely however, there was an absence of evidence for a harmful effect of statins on. Given the reality that given the choice, given the conflicting evidence
-
-As with many many studies of dementia outcomes, a key limiting factor of any analysis is the absence of a detailed pathological mechanism for the condition.
-It could well be that statins do have a true effect independently of lipid levels, though based on the certainty of evidence in NRSI, this is unlikely.
+In summary, clinicians should be aware of the uncertainty of evidence surrounding the effect of lipid-lowering on dementia outcomes and should be prepared to convey the same to patients.
 
@@
 
-\newpage
-
 ### Implications for public health
 
-This section should
+__[Note: Yoav, I am particularly interested in your thoughts on this section]__
 
-The absence of an effect of blood lipids on dementia outcomes is an unh
-
-However, future work
+Similarly, given the ambiguity of evidence, there are no clear implications for public health practice.
+However, the role of public health, and particularly continuous population surveillance, may be important in providing a further source of evidence in relation to the effect of lipid lowering on dementia.
+Public health practitioners could examine summary-level statistics of GP prescription data to attempt to relate lipid-lowering treatment to temporal or geographical trends in dementia incidence.
+It will be difficult to assess if effect is due to confounding or ecological biases, but as dementia will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a further source of evidence.
 
@@
 
-\newpage
+## Summary of methodological contributions
 
-## Summary of methodological findings
+In addition to addressing the causal impact of lipids on dementia outcomes, the research described in this thesis represents a number of novel contributions to the the field of evidence synthesis.
 
-The research described in this thesis represents a number of novel contributions to the the fields of evidence synthesis
+&nbsp;<!----------------------------------------------------------------------->
 
-### Preprint search tool
+### Inclusion of preprinted evidence
 
-\newpage
+Including preprints adds a valuable evidence source to a synthesis.
 
-### Inclusion of preprints
+Preprints are an important source of evidence, and searching of preprint repositories should.
+The tool presented in Chapter \@ref(sys-rev-tool) allows for this, enabling ready access to and searching of health-related preprints.
 
-This thesis provided evidence that the preprints can provide additional evidence to the published literature,
+While, in the case of the systematic review,
 
-\newpage
+As discussed in Section \@ref(), the tools has been used in a number of published studies
 
-### Risk of bias visualisation
+&nbsp;<!----------------------------------------------------------------------->
 
-\newpage
+### Bias
+
+One of the central methodological focuses of this thesis has been on the assessment, visualisation, and adjustment for bias.
+
+In terms of assessment, I applied domain-based tools to evidence relevant to the effect of lipids on dementia outcomes, and highlighted the limitation of the available tools for Mendelian randomisation studies.
+I also piloted and provided feedback on a forthcoming tool for assessing the risk of bias due to missing evidence.
+In the primary analysis of data from the CPRD, I used negative control outcomes to assess the potential for bias due to insufficiently controlled confounding by indication.
+
+In terms of visualisation of bias, I have made a number of methodological contributions.
+I created a well-received R package to create paired forest plots (see Appendix \@ref(appendix-robvis)), and built on this to enable creation of the bias direction plots illustrated in Chapter \@ref(tri-heading).
+
+Finally, I have proposed a new framework for the assessment and adjustment of bias in diverse evidence sources, using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias assessments.
+This framework provides a systematic way to account for biases across studies, reducing the potential for differential adjustment based on knowledge of the results.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-this thesis has also proposed a novel combination of existing methods as a move towards a , based on devl
+In contrast to the opening quote of this chapter, I believe that , particularly for outcomes that are difficult to study using randomised controlled trials. However, as noted previously,
+
+In general, there is a need to better make use of non-randomised evidence, particularly in areas where RCTs are not easily performed or are ethically infeasible.
+
+where the rigourness and relevance of each individual are systematically considered and adjusted for using pre-specified adjustment distributions,
+
+The final methodological contribution of thesis thesis was a proposed generalised quantitative triangulation framework, building on existing methods for the systematic assessment of bias and methods for bias-/indirectness-adjusted meta-analysis.
+
+While the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
+The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness, and decreases the precision of the overall effect estimate on this basis.
+
+In summary, the framework will enable better use of observational studies to address causal questions.
 
@@
 
-\newpage
-
 ## Overall strengths and limitations
 
-The strengths a limitations of each component of this thesis have been discussed in the respective chapters. Here I highlight the strengths and weaknesses of this thesis as a body of work.
+The strengths and limitations of each aspect of this thesis have been discussed in the respective chapter. Here I highlight the strengths and weaknesses of this thesis as a body of work.
 
@@
 There are several strengths to this thesis as a whole.
-The use of a systematic review incorporating multiple study designs and preprinted literature provided a strong and comprehensive evidence base with which to assess my research question.
+Specifically, the synthesis of evidence across study designs and publication status ensures a comprehensive overview of the state of the research in this topic, and sets this thesis apart from previous synthesis of the evidence on this topic.
+Additionally, as discussed above, assessment of the potential for bias has a central aspect of the research projects presented, and can be considered a core strength of this thesis.
+Many previous evidence synthesis exercised on this topic did not sufficiently consider bias .
 
-This thesis has also produce new evidence on the association of blood lipids on dementia outcomes via two primary analysis.
-Specifically, it has provided additional information on a previously understudied association (lipids/LRA and vascular dementia).
+This thesis has also produced new evidence on the association of blood lipids with dementia outcomes via two primary analysis, in addition to providing additional information on a previously understudied association (lipids/LRA and vascular dementia).
 
-A focus on bias has been a central aspect of this thesis.
-In the systematic review, detailed risk of bias assessments were used to assess the bias, while in the CPRD analysis, controls outcomes were used to provide evidence for uncontrolled bias due to confounding.
-Finally, the triangulation framework presented in Chapter \@ref(hold) seeks to adjust for the bias in each resul.
-
-A final strength of this thesis is the production of software to support the novel evidence synthesis techniques used.
+A further strength of this thesis is the production of software to support the novel evidence synthesis techniques used.
+Extensive documentation has been written to guide users through usage of the tools and example data is provided for use.
+Finally, extensive efforts have been made to make the research documented in this thesis as reproducible as possible - these are documented in Appendix \@ref(disc-repro-research).
 
@@
 
-\newpage
-
 ### Weaknessess
 
-However, there are several strong limitations to this thesis.
-
-Each analysis presented makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
-Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in, absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data, if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records can be poor[@wilkinson2018]).
+However, there are also several strong limitations to this thesis.
+In the first instance, each analysis presented here makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
+Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in, absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable[@wilkinson2018]).
 
 Further, missing evidence was a common limitation across this thesis.
-In Chapters \@ref(hold)/\@ref(hold), several studies stated that they did not report the results of an analysis because the results were not significant.
+In Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading), several studies stated that they did not report the results of an analysis because the results were not significant.
 This was particularly common among non-randomised studies of exposure examining blood lipids directly.
 Similarly, an absence of evidence on vascular dementia, potentially due to a publication bias mechanism, limited the analysis of this outcome.
-Finally, missing evidence also presented as an issue in the form of a poor response to data access requests was also observed in the IPD analysis reported in Chapter \@ref(hold).
+Finally, missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(hold), in the form of a poor response to data access requests.
 
-A final weakness of this thesis is the geographical focus.
-All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world.
+A final weakness stems the geographical focus of the data analysed in this thesis.
+All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world (Figure \@ref(fig:cohortLocations)).
 This may limit the generalisability of the results presented to different populations.
@@
 
-\newpage
+## Lessons learned
+
+As a reflective process throughout my PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing specific analytical failures and unsuccessful grant applications.
+However, there was one central takeaway from this thesis, namely to be slightly less ambitious when planning future research projects.
+
+The proposal for the programme of research underpinning this thesis was created in advance, as a detailed plan was required in order to secure NIHR funding.
+In hindsight, the decision to take a broad approach to inclusion of dementia outcomes resulted in larger workload than anticipated, particularly when considering evidence from across different study designs.
+Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g.
+Alzheimer's disease).
+
+Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger programme of research was overly ambitious, as data cleaning and harmonisation for just three of the many cohorts I applied to was a substantial undertaking.
+
+In the future, I will better scope proposed research projects.
+
+nnbsp;<!----------------------------------------------------------------------->
 
@@
 
-Several avenues of future research, building on the work presented here, could be pursued.
+Several avenues of future research, building on the work presented here, could be pursued. These are grouped by topic in the following sections.
+
+__[Question: is it better to use "should" or "could" when listing ideas for future research? I.e. future work could/should look at X.]__
 
@@
 
-### Inclusion of preprints
+### Generation of new RCT evidence
 
-<!-- TODO Incorporate Julian's comments below -->
+It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trials be performed to assess the effect of the proposed intervention, in this case statins.
+Given the costs and logistical challenges associated with trials examining outcomes with long prodomal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up (PTFU) of existing RCTs of lipid-regulating agents.
 
-<!-- REVIEW [JH] I think, on general reflection, that portraying this as an issue around “grey literature” may not be particularly useful.
-Preprints are arguably some of the least “grey” of the very ambiguously defined family of grey sources, such that some definitions of “grey” might not include them.
-It seems to me that preprints are such a big and important part of the landscape now that you can just portray the methodology as dealing with preprints rather than including grey literature.
-Interesting debate as to whether preprints are grey literature, given that many of them are increasingly becoming findable in electronic bibliographic databases.
-We have no clear and widely used definition of grey literature.
--->
-
-Given the evidence that this thesis produced on the usefulness of including preprints, normalisation of inclusion of preprints in systematic reviews.
-Wider assessment of the evidence base that exists solely as preprinted literature ()
-
-Meta-epidemiological studies examining the factors which influence eventual publication would also help to quantify the extent and strength of publication bias
-
-Preprints also represent a key opportunity to assess the impact of peer review and editorial guidelines on manuscripts, by enabling a comparison of the same paper at two stages (preprinted versus published).
-This fact was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(), but could be used to other important meta-research questions.
-
-Future work should also address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in an evidence synthesis exercise.
-This will be particularly important if the results are substantially different between the two versions or if a result availble in the preprint manuscript is not presented in the published version.
-
-Finally, the availability of the `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool into an automated searching pipeline as part of a living systematic review.
-
+PTFU of two lipid-regulating agent trials has already been used to assess long-term (11-20 years) safety outcomes of statin use, using participant recontact[@group2011] and linkage with electronic health records to identify events.[@ford2016] A similar approach could be used to assess the impact of randomisation to statins at midlife on subsequent risk of dementia outcomes.
+Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using EHRs.
 &nbsp;<!----------------------------------------------------------------------->
-\newpage
 
@@
 
-As discussed in an earlier section, there is an absence of evidence on vascular dementia across the evidence base
+As highlighted by the results of the systematic review presented in Chapter \@ref(sys-rev-results-heading), there is an absence of evidence on vascular dementia across the evidence base.
+Future research should aim to both investigate the reasons for this evidence gap (e.g.
+due to an absence of primary data, challenges in the analysis of this outcome as documented in Chapter \@ref(cprd-analysis-heading), or a publication bias mechanism) and work to address it.
 
-Future work should aim to both investigate the reasons for this evidence gap and work to address it.
-In particular, large-scale GWAS of vascular dementia should be performed, to identify associated loci that future two-sample Mendelian randomisation studies could make use of.
-While this is methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour, allowing for the assessment of many genetically-driven risk factors beyond those considered in this thesis.
-
-This is particularly relevant given that there was some evidence for an association of hypertriglyceraemia with vascular dementia.
-Future research should explicitly examine this relationship as part of wider exploration of vascular disease.
+However, it seems unlikely that analysis of observational data will be sufficient , given the presence of strong confounding by indication present in the analysis of statins and vascular dementia.
+Even using new methods, such as a target trial approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] This reinforces the need for large-scale GWAS of vascular dementia, similar to those current available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could make use of.
+While GWAS of this outcome are likely to be methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of many genetically-driven risk factors beyond those considered in this thesis.
 
 &nbsp;<!----------------------------------------------------------------------->
-\newpage
+
+### Preprinted evidence
+
+Future work on preprinted evidence should address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in an evidence synthesis exercise.
+This will be particularly important if the results are substantially different between the two versions or if a result available in the preprint manuscript is not presented in the published version.
+
+Finally, the `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.
+In addition, the ready access to preprint data afforded by the tool will enable meta-epidemiological studies to examine factors which may influence eventual publication (e.g.
+significant result, geographical location or gender of first author, or some other factor).
+Finally, the tool will allow future research to assess the impact of peer review and editorial guidelines on manuscripts through comparison of the same paper at two stages (preprinted versus published).
+This approach was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(sys-rev-tools), but could be applied to other important meta-research questions.
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-As noted in previous chapters, evidence synthesis theory and methods have not been sufficient developed for the inclusion of Mendelian randomisation studies.
-
-A key issue arises from the lack of an established risk of bias tool, limiting future work that requires systematic risk-of-bias assessment, such as the triangulation framework presented in Chapter \@ref(hold).
-In addition, a lack of guidance around whether the inclusion of two-sample Mendelian randomisation studies using identical summary statistics.
-This was illustrated in detail in Chapter \@ref(4), where XXX studies using the same , and meta-analysing these as independent effect estimates would provide an overly precise result.
-Finally, future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
+As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not sufficiently developed.
+Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
 genetic instrumental variable analysis).
-
-Synthesis of Mendelian randomisation studies is not helped by the varied (and often poor) reporting, though the recent release of the STROBE-MR reporting guidelines should go someway to addressing this.
+In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk of bias tool for Mendelian randomisation studies limits future work that requires systematic risk-of-bias assessment such as the quantitative triangulation framework proposed here.
+Finally, guidance around the inclusion of two-sample Mendelian randomisation studies using identical summary statistics, which can falsely increase the precision of the summary estimate as more fully discussed in Section \@ref(rev-discussion-MR), would represent a useful contribution.
 
 &nbsp;<!----------------------------------------------------------------------->
-\newpage
 
-### Triangulation
+### Systematic reviews and quantiative triangulation
 
-It is customary at this point to recommend that a large scale randomised controlled trials be designed to run to assess the effect of the intervention.
-Given the logistical challenges of trials for outcomes with long prodomal periods such as dementia, is the post-trial follow-up of existing RCTs of lipid-regulating agents.
-Examples of this approach for long term (11-20 years) assessment of safety outcomes associated with statin use, using patient recontact and linkage with electronic health records.[@ford2016; @group2011] A similar approach could be used to assess the impact of randomisation to statins in these trials on dementia outcomes.
+Quantitative triangulation is an area ripe for future work.
+The approach presented here will benefit from meta-epidemiological studies to better define the impact of different bias in non-observational studies.
 
-However, in general there is a need to better make use of non-randomised evidence, particularly in areas where RCTs are not easily performed.
-As such, quantitative triangulation is an  one ripe for future work.
+Similarly, future work should expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
+Tools such as the ROB-ME assessment tool will enable this, but how to adjust for this analysis-level - as opposed to result-level - bias should be explored.
 
-Future work would account for methods for adjustment of meta-biases, such as those introduced by
+Finally, the application of the framework across other causal questions will help to identify sticking points in the process.
 
-These domains specific distritions should
+While synthesising evidence from a specific study design (e.g.
+NRSI) is currently the norm, future reviews should aim towards assessment of all evidence (direct and indirect) related to a specific causal question.
 
-Finally, substantial future work should be directed towards the conduct of meta-epidemiological studies to assess the impact of different bias in non-observational studies.
-While frameworks such as the one employed in Chapter \@ref(tri-heading) exist to allow for the production of bias-adjusted and triangulated estimates.
-
-Finally, accounting for bias (and indirectness, if considering causal effects rather than a summary of the literature) is essentially in the interpretation of published literature.
-While this can take many forms, from the stratification of forest plots by overall risk of bias level, to the or to the more advanced bias adjustment approach detailed here, it is insufficient to draw clinical recommendations from meta-analysis that treat effect estimates as if they were unbiased.
+In essence, we need fewer reviews addressing the same questions in order to combat research waste.
+Section \@ref(rev-previous-reviews) illustrates this in the context of this thesis, while an assessment of the COVID-19 literature found that, for a specific clinical question, there were substantially more reviews (25) than available primary studies (17).
 
@@
 <!----------------------------------------------------------------------------->
-\newpage
 
@@
 
-This thesis provides new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlights the uncertainty that still remains in relation to this causal question.
-In addition, it has developed new evidence synthesis methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources.
+This thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the uncertainty that still remains in relation to this causal question.
+In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will future evidence synthesists to better address causal questions.

### 2021-12-05 front-and-back-matter/99-appendices.Rmd
Working version

@@
 
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
+
+\newpage
 
@@
 
+### Reproducible research {#disc-repro-research}
+
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
+In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+
+Unfortunately, given the.
+However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
+
+Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
+
+One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
+IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
+However, access is dependency on an ISAC application to the managing body of the CPRD.
+
 <!----------------------------------------------------------------------------->
@@
 
-Failing to properly scope the literature and correctly estimate the number of studies returned by the search
+- Failed to properly scope the literature and correctly estimate the number of studies returned by the search
 
-failing to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
+- Failed IV analysis of anti-HC drugs because of low numbers of non-statins.
+
+- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
+
+- Unsuccessful grant application with Andy
+
+- Unsuccessful grant application with Chris Penfold
+
+- Unsuccessful grant application with Matt
+
+- Instrumental variable analysis of lipid regulation use using physicians prescribing preference.
+
+- 2 x unsuccessful conference abstracts
 
@@
 <!----------------------------------------------------------------------------->
-# Other Appendix {#other-appendix-heading}
+# Other Appendices {#other-appendix-heading}
 
@@
 
+<!-- TODO Need to complete this sections -->
+
+_TBC_
+
 \newpage

### 2021-12-05 front-and-back-matter/_abstract.Rmd
End of day:
Working version

@@
+<!-- TODO This needs to be less than 300 words! -->
+
 __Background:__ Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies.
@@
 Preprints were searched using a new research tool created as part of this thesis.
-The existing evidence was then supplemented via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual patient data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK.
+The existing evidence was then supplemented via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual participant data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK.
 Finally, a novel quantitative triangulation framework was proposed, building on recent developments in risk-of-bias assessment and bias-/indirectness-adjusted meta-analyses.
@@
 However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors.
-The individual patient data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence only for the association of triglycerides and vascular dementia.
+The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence only for the association of triglycerides and vascular dementia.
 Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.

### 2021-12-06 03-Chp-Systematic-Review-Methods.Rmd
Working version
End of day:

@@
 This analysis sought to address two specific aims.
-Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship of lipids and dementia exist.
+Firstly, as discussed in the introduction to this thesis (Section \@ref(evidence-association)), several diverse forms of evidence on the relationship between lipids and dementia exist.
 These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies.
 However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
-Collating these diverse evidence sources is important, as if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
+Collating these diverse evidence sources is important, as, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
 As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.
@@
 Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses.
-As a sensitivity analysis to this review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
+As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
 
@@
 No limits were placed on the sample size of included studies.
-Eligible studies defined dementia outcomes according to recognised criteria, for example the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering used when entering the outcome into the EHR.
+Eligible studies defined dementia outcomes according to recognised criteria.
+Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.
 
-Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain information on the study's status.
+Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract.
 No limitations were imposed on publication status, date, venue or language.
@@
 
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline except if the sample was initially assessed in mid-life (i.e.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline were excluded.
+An exception to the latter criteria was made if the sample was initially assessed in mid-life (i.e.
 below the age of 50) were excluded.
@@
 
-When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try and reduce the screening load.
+When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try to reduce the screening load.
 To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
@@
 <!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand while studies citing included studies was examined using Google Scholar (forward and reverse citation searching or "snowballing").[@greenhalgh2005; @wohlin2014]
+Date and other range --> Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]
 
@@
 Records were imported into Endnote and de-duplicated using the method outlined in Bramer et al.
-(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates, beginning with automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), followed by manual review of less similar articles (e.g.
+(2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates.
+The initial step involves automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), and is followed by manual review of articles with less overlap (e.g.
 those identified as duplicates based on the "Title" field alone).
 
-Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote, a citation management tool,[@hupe2019] and Rayyan, a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed primarily by me, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
+Following de-duplication of records, screening (both title/abstract and full-text) was performed using a combination of Endnote and Rayyan.
+Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
 Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.
 
-Similarly, I completed all full-text screening, with a random ~20% being screened in duplicate by a second reviewer, in addition to any records I identified as being difficult to assess against the inclusion criteria.
+Similarly, I completed all full-text screening, with a random ~20% being screened by a second reviewer.
+Additionally, any records I identified as being difficult to assess against the inclusion criteria were also screened by the second reviewer.
 Reasons for exclusion at this stage were recorded.
@@
 
-How to interpret agreement coefficients is widely debated, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+Interpretion of agreement coefficients is a widely debated topic, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
 Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated issues with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.
+If this assessment demonstrates an issue with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.
 
@@
 Data extraction was performed using a piloted data extraction form.
-Extracted items included: article metadata (year of publication, author, journal), study characteristics (study location, data source, exposure, outcomes, diagnostic criteria used), patient characteristics (age, sex, baseline cognition scores, baseline education scores), and results (exposure-outcome pairing, effect measure, effect estimate, error estimate, p-value).
 I extracted all data in the first instance, which was subsequently checked for accuracy by a second member of the review team.
+Extracted items included:
+
+* Article metadata: year of publication, author, journal)
+* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used)
+* Patient characteristics: age, sex, baseline cognition scores, baseline education scores
+* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value).
 
@@
 This was particularly relevant to preprints and published papers reporting the same study, which were not considered to be duplicate records but instead different reports of the same study.
-This is due to the potential for the published version to offer some information that the preprint did not, and vice versa.
+This decision was taken due to the potential for the published version to offer some information that the preprint did not, and vice versa.
 
@@
 \end{equation}
-
 &nbsp;
 
-This was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.
+where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup.
+This approach was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.
 
@@
 
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categorises of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
 
@@
 
-Where additional data not reported by an analysis were required either for the analysis or risk-of-bias assessment, the corresponding author of the study was contacted.
-This approach was taken due to the potentially large impact of following up with authors on the results of the review.[@reynders2019]
+Where additional data, not included in the report of an analysis, were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted.
+This approach was taken due to the potentially large impact of additional information obtained through contact with study authors on the results of the review.[@reynders2019]
 
@@
 
-Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains: bias arising from the randomization process, bias due to deviations from intended intervention, bias due to missing outcome data, bias in measurement of the outcome, bias in selection of the reported result.
+Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains:
+
+* bias arising from the randomization process, 
+* bias due to deviations from intended intervention, 
+* bias due to missing outcome data, 
+* bias in measurement of the outcome, 
+* bias in selection of the reported result.
+
 Acceptable judgements for each domain include: "low risk", "some concerns", "high risk".
@@
 
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains: bias due to confounding, bias due to selection of participants, bias in classification of interventions, bias due to deviations from intended interventions, bias due to missing data, bias in measurement of outcomes, and bias in selection of the reported result.
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains:
+
+* bias due to confounding, 
+* bias due to selection of participants, 
+* bias in classification of interventions, 
+* bias due to deviations from intended interventions, 
+* bias due to missing data, 
+* bias in measurement of outcomes, and 
+* bias in selection of the reported result.
+
 Similar to RoB 2, it has a number of signaling questions which inform the domain-level judgement, with acceptable judgements including “low”, “moderate”, “serious” and “critical”.
@@
 While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
-Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of bias as ROBINS-I, were made at the domain level.
+Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of risk of bias as ROBINS-I, were made at the domain level.
 The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies (advance results from this review were obtained from contact with the review authors).[@spiga2021] A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
+Assessment of the risk of bias in Mendelian randomization studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors.
+A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
 Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.
@@
 In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
-This assessment examines evidence missing due to selective non-reporting - as distinct from the selective reporting of a single result from multiple planned analyses - and was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.
+This assessment examines evidence missing due to selective non-reporting as distinct from the selective reporting of a single result from multiple planned analyses.
+The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.
 
-This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try and examine the risk of bias due to missing evidence.
+This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try to examine the risk of bias due to missing evidence.
 This is largely because the tool did not exist when the protocol was registered.
@@
 
-I used a random-effects model in all meta-analyses.[[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
-The weight ($w$) assigned to each result (denoted as $y_i$) is then given as the inverse of the variance of that result plus the estimate of between-result variance, denoted as $w_i = \frac{1}{v_i+\tau^2}$ for result $i$.
+I used a random-effects model in all meta-analyses.[@hedges1998;@dersimonian1986] Random-effects meta-analysis does not assume one true underlying effect, but rather allows for a distribution of true effects with variance $\tau^2$.
+The result in the $i$th study is denoted as $y_i$.
+The weight assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):
+
+\begin{equation}
+w_i = \frac{1}{v_i+\tau^2}
+  (\#eq:ivweighting)
+\end{equation}
+
 Once the weights are calculated for each result, the overall estimate ($\hat{y}$) and variance ($Var(\hat{y})$) can be estimated:
@@
 
-Results included in a meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
+Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
@@
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.
-This marks a departure from the published protocol, as I was unaware that such a large number of studies would report dementia risk across multiple lipid categories.
+This marks a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.
+
+<!-- TODO Maybe rephrase last sentence -->
 
@@
 Restricted cubic spline models use "knots" to separate the data into subsets or "windows", in which the trend is modelled.
-Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends have been estimated, they are combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]
+Further restrictions are then imposed, in that the curves in each window must join up "smoothly" at the knot location, and that the trend is assumed to be linear before the first knot and after the last knot.[@gauthier2020] The locations of the knots in the model were identified using fixed percentiles (5th, 50th, 95th) of the exposure data.[@durrleman1989] Once the within-study trends had been estimated, they were combined in a multivariate random-effects meta-analysis using the restricted maximum likelihood (REML) method.[@liu2009; @white2009;@gasparrini2012] All dose-response analyses were implemented using the `dosresmeta` R package.[@crippa2016]
 
@@
 One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond.
-This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures,[@mcguinness2020robvisPaper] and the "paired" forest plot functionality grew out of a collaboration with other researchers to design a modular method for creating custom forest plots.[@zotero-14999] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
+This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
 Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.
@@
 Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)).
-As an adjunct analysis to this review, I explored the additional evidential value of including preprints in each meta-analysis performed, assessed using the fixed effect weight from a standard meta-analysis.
+As an adjunct analysis to this review, meta-analyses including a preprint result were re-analysed using a fixed effect model.
+The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided by the preprint.
 In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.
@@
 
-Additionally, I followed identified preprints up after a two-year lag to investigate whether they had been subsequently published (in which case preprints provide a snapshot into the future, and a systematic review update would capture these reports) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).
+Additionally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether identified preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).
 
@@
 * I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies.
-Additionally, I have highlighted how this review will examine the impact the of including preprinted results, as enabled by the research tool presented in the previous chapter.
+Additionally, I have highlighted how this review will examine the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.
 
 * In the following chapter, I present the results of this review, and detail how the identified evidence is used throughout the remainder of the thesis.
-
-\newpage
-
-## References

### 2021-12-06 05-Chp-CPRD-Analysis.Rmd
End of day:
Working version

@@
 
+&nbsp;
+
 \minitoc <!-- this will include a mini table of contents-->
-
-<!-- TODO text -->
 
@@
 <!--------------------------------------------------------------------------->
-
-## Lay summary
+::: {.laybox data-latex=""}
+## Lay summary {-}
 
@@
 
+&nbsp;
+
 This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across England.
 Using this data, the analysis presented in this chapter examined whether treatments which lower cholesterol levels (also known as lipid-regulating agents or LRA) of which statins are a prime example, affect the risk of all-cause dementia and related outcomes (Alzheimer's disease, vascular dementia and other dementias).
+
+&nbsp;
 
@@
 non-Alzheimer's) dementia was associated with lipid-regulating agent use.
+
+&nbsp;
 
@@
 
-<!--------------------------------------------------------------------------->
+:::
 
-&nbsp;
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-In this Chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
-The analysis aims to address important two limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
+In this chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
+The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
 
@@
 Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia as identified by the systematic review.
-Specifically, this involved a concerted effort to address immortal time bias though use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] By employing this approach, the analysis provides an evidence source at risk of a distinct bias.
+Specifically, this involved a concerted effort to address immortal time bias through use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] By employing this approach, the analysis provides an evidence source at risk of a distinct bias.
 The results from this analysis will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
@@
 
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, included clinical test results and diagnoses, can be identified by a specific Read code.
+To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, including clinical test results and diagnoses, can be identified by a specific Read code.
 The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
@@
 Records pre-dating the 1995 cut-off were included in the original CPRD extract obtained for this analysis.
-However, these were excluded from the analysis as data quality and reliability are thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
+However, these older records were excluded from the analysis as data quality and reliability are thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
 
-Participants were included in the study cohort if their record contained any of the following index events: a Read code for a diagnosis of hypercholesterolemia or related condition; a Read code for prescription of a lipid-regulating agent (such as statins); a total cholesterol test result of >4 mmol/L; or an LDL-c test result of >2 mmol/L.[@walker2016] The blood lipid cut-offs were based on NIHR-recommended levels at the time the protocol was written.
+Participants were included in the study cohort if their record contained any of the following index events:
+
+* a Read code for a diagnosis of hypercholesterolemia or related condition; 
+* a Read code for prescription of a lipid-regulating agent (such as statins); 
+* a total cholesterol test result of >4 mmol/L; 
+* an LDL-c test result of >2 mmol/L.
+
+The blood lipid cut-offs were based on NIHR-recommended levels at the time the protocol was written.
 These index events allowed me to define a population of participants who were either at risk of hypercholesterolemia, as indicated by the elevated total or LDL cholesterol test results, or had already been diagnosed with it, as indicated by a diagnostic code/related prescription.
 
-The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of: (a) an outcome of interest; (b) death; (c) end of follow-up (29 February 2016); (d) last registration date with their GP practice; or (e) the last CPRD collection date for their practice.
+The index date for a participant was defined as the date where the first relevant code or test result was recorded on their clinical record, and participants were followed up until the earliest of:
+
+* an outcome of interest;
+* death; 
+* end of follow-up (29 February 2016);
+* last registration date with their GP practice;
+* the last CPRD collection date for their practice.
+
 Participants were ineligible for our cohort if they were less than 40 years of age (as these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
@@
 
-A range of additional variables were included in the analysis, intended to address the different distributions of potential confounding variables between those who were prescribed an lipid-regulating agent and those who were not.
+A range of additional variables were included in the analysis.
+These were intended to address the different distributions of potential confounding factors between those who were prescribed a lipid-regulating agent and those who were not.
 These are discussed in detail below and summarised in Table \@ref(tab:covariateDef-table).
@@
 Demographic covariates adjusted for included age and gender.
-Age in years was calculated at date of entry into the cohort, using the 1st of January of a patients' birth year (the exact date of birth was not provided by CPRD), and was adjusted for via its use as the time axis for the Cox model (see Section \@ref(cprd-time-axis)).
-Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010, which draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
+Age in years was calculated at date of entry into the cohort, using the 1st of January of a patient's birth year (the exact date of birth was not provided by CPRD), and was adjusted for via its use as the time axis for the Cox model (see Section \@ref(cprd-time-axis)).
+Socioeconomic status was proxied using the Index of Multiple Deprivation (IMD) 2010.
+The IMD draws on seven domains (income; employment; education, skills and training; health and disability; crime; barriers to housing and services; living environment) to create an overall deprivation score for each of 32844 statistical geography areas in England.
 To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
-Smoking and alcohol use was determined at index, and participants were categorised as current, former, or never users of each.
+Smoking and alcohol use was determined at index, and was categorised as current, former, or never use.
 
@@
 A variable indicating grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
-To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patients data and their entry into the cohort.
+To assess healthcare utilisation, I adjusted for the average annual number of consultations between the beginning of a patient's data and their entry into the cohort.
 
@@
 
-Missing data are a recognised issue in electronic health records databases,[@wells2013strategies] given that they contain administrative data, collected primarily for the purposes of patient management and care rather than academic research.
+Missing data are a recognised problem in electronic health records databases.[@wells2013strategies] These databases are created from administrative data, collected primarily for the purposes of patient management and care rather than academic research.
 
@@
 
-Missing data was only considered an issue for variables where a numerical test result was expected (e.g.
+Missing data were only considered problematic for variables where a numerical test result was expected (e.g.
 BMI), or where a code existed for the absence of the condition (e.g.
@@
 
-Immortal time bias describes two distinct but related types of bias.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to the exposure is excluded leading to the exposed and control groups being followed up from different time points.[@levesque2010] Following the example displayed in the figure, the unexposed group are followed from the date of a diagnosis, while the exposed group is followed from date of a prescription.
-In this scenario, the time between diagnosis and prescription for the exposure group is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
+Immortal time bias describes two distinct but related types of bias, considered here in relation to statin use.
+The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to statin initiation is excluded leading to the statin and control groups being followed up from different time points.[@levesque2010] Following the example displayed in the figure, the unexposed group are followed from the date of an index event (e.g.
+diagnosis of hypercholesterolemia), while the statin group is followed from date of a statin initiation.
+In this scenario, the time between the index event and statin initiation is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
 
 The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to the prescription, and any events occurring within it, is inappropriately assigned to the exposed group.
+It occurs when the exposure time prior to statin initiation, and any events occurring within it, is inappropriately assigned to the exposed group.
+
+<!-- TODO Reread this section and compare with the figure! -->
 
@@
 
-This second presentation appears to be common in the existing literature, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
-Both presentations of immortal time bias appear in the literature on the relationship of statins and dementia, as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)
+This second presentation appears to be common in the existing literature on the relationship of statins and dementia, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
 
@@
 
-This analysis attempted to address this issue by following all participants from a common index date (defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemia diagnosis; or (c) LRA prescription).
-Following a recommended approach to addressing the second form of immortal time bias, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010]
-
-Under this approach, all patients start in the unexposed group and contribute time-at-risk until they are prescribed a lipid-regulating agent and move into the exposed group.
+Following a recommended approach to addressing the second form of immortal time bias, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] Under this approach, all patients are followed from a common index date, defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemia diagnosis; or (c) LRA prescription.
+Patients start in the unexposed group and contribute time-at-risk until they are prescribed a lipid-regulating agent, at which point they move into the exposed group.
 Note, patients for whom prescription of a lipid-regulating agent was the index event only contribute time to the exposed group (i.e.
@@
 Using multiple imputation to handle missing data is an alternative to a "complete case" approach,[@pigott2001] where participants missing any covariate are dropped from the dataset.
-As a recommended sensitivity analysis,[@hughes2019] I preformed and compared the results of both methods, to investigate the impact of multiple imputation on the results.
+As a recommended sensitivity analysis,[@hughes2019] I performed and compared the results of both methods, to investigate the impact of multiple imputation on the results.
 
@@
 In addition to the primary outcomes of interest (described in Section \@ref(cprd-outcomes)), I extracted data on three additional control outcomes.
-The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually class as either "negative" or "positive" outcomes.
+The inclusion of control outcomes in observational analyses are a useful technique to assess the strength of uncontrolled confounding,[@lipsitch2010] and these outcomes are usually classed as either "negative" or "positive" outcomes.
 
@@
 Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-Due to the wealth of data available on statins as a lipid-regulating agent, I chose three control outcomes were chosen in reference to this drug class: back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
+Due to the wealth of data available on statins as a lipid-regulating agent, I chose three control outcomes in reference to this drug class: back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
 
@@
 
-As detailed in the introduction, the properties of statins may be important in their effect based on the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] As such, I expected that any effects of statins on dementia outcomes would be stronger in the lipophilic as compared to the hydrophilic statin subgroup.
+As detailed in the introduction, the properties of statins may be important due to the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] As such, I expected that any effects of statins on dementia outcomes would be stronger in the lipophilic as compared to the hydrophilic statin subgroup.
 To investigate this, I further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
@@
 
-This previous analysis used a propensity matching approach to estimate the association of statins with a range of outcomes in The Health Improvement Network (THIN) database, a alternative source of English electronic health records which has substantial overlap with the CPRD.[@carbonari2015] The code lists used in this analysis were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
+This published analysis used a propensity matching approach to estimate the association of statins with a range of outcomes in The Health Improvement Network (THIN) database, an alternative source of English electronic health records which has substantial overlap with the CPRD.[@carbonari2015] The code lists used in this analysis were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
 
@@
 
-__Alzheimer's disease__
+#### Alzheimer's disease
 
@@
 
-__Non-Alzheimer's disease dementias__
+#### Non-Alzheimer's disease dementias
 
-In contrast to the findings for Alzheimer's disease outcomes, lipid-regulating agents were associated with an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementias (`r othdem_text`).
+In contrast to the findings for Alzheimer's disease outcomes, an association between lipid-regulating agents and an increased risk of a subsequent diagnosis of vascular dementia (`r vasdem_text`) or other dementias (`r othdem_text`) was observed.
 Again this effect was driven mainly by the statin subgroup, but there was some evidence that ezetimibe was associated with an increased risk of vascular (`r vasdem_eze_text`) and other (`r othdem_eze_text`) dementia.
@@
 
-__All-cause dementia__
+#### All-cause dementia
 
@@
 
-On the assumption that this variation could be caused by changes in the frequency probable AD diagnoses in the cohort over time, I performed a _post-hoc_ investigation of the frequency of each diagnoses stratified by year of entry (Table \@ref(tab:diagnosisType-table)).
+On the assumption that this variation could be caused by changes in the frequency of probable AD diagnoses in the cohort over time, I performed a _post-hoc_ investigation of the frequency of each dementia outcome by year of entry (Table \@ref(tab:diagnosisType-table)).
 While the frequency of outcomes declines in more recent strata, likely due to the limited follow-up inherent to these groups, this decline in frequency is relatively constant across the dementia subtypes.
@@
 
-In the second sensitivity cohort, removing participants aged 55 and under at index from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
+In the second sensitivity cohort, removing patients who may have been pregnant (coded as aged 55 and under at index) from the analysis had minimal effect on the effect estimates (Figure \@ref(fig:pregnancyFig)).
 
@@
 In the cohort, statins with lipophilic properties were much more frequently prescribed than hydrophilic statins (Table \@ref(tab:statinTypeTable-table)).
-Additionally, there is evidence for an increasing tendency to favour hydrophilic statins in recent years, as the proportion of lipophilic statins prescribed fell from 18.2% in 1996-2000 to <1% in 2011-2016.
+Additionally, there is evidence for an increasing tendency to favour hydrophilic statins in recent years with the proportion of lipophilic statins prescribed falling from 18.2% in 1996-2000 to <1% in 2011-2016.
 
@@
 
-Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnosis.
-The estimate observed in each case was driven by the statin subgroup, which included a substantial majority of participants.
-For the other drug classes, no association was found with any outcome, with two exceptions being that ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnosises.
+The estimate observed in each case was driven by the effects observed statin subgroup, as a substantial majority of participants prescribed an LRA were presribed a statin.
+For the other drug classes, no association was found with any outcome, with two exceptions.
+Ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
 
@@
 This section will expand on a potential explanation for the observed results detailed above.
-However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, the section will not provide a detailed comparison with other published literature, except where needed to illustrate a methodological point.
+However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, a detailed comparison with other published literature will not be provided here, except where needed to illustrate a methodological point.
 For a detailed comparison of the result presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
@@
 vascular and other dementias) with lipid-regulating agent use, and an important limitation of this analysis, is residual "confounding by indication".
-While the term has been used to describe different source of bias in epidemiological analyses,[@salas1999] it is used here to described the role of risk factors that both prompt treatment and increase the risk of the outcome, thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
-In causal inference nomenclature, statins and dementia are said to be _d_-connected as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015] In the context of this analysis, the confounding variable (or, more likely, variables) would prompt both prescription of statins and also represent a vascular risk factor that contributes to the development of the vascular dementia.
-A similar confounding structure likely exists for ezetimibe, another hypercholesterolemia treatment, providing an explanation for the association of vascular/other dementia but not Alzheimer's disease with this exposure.
+While the term has been used to describe different sources of bias in epidemiological analyses,[@salas1999] it is used here to described the role of risk factors that both prompt treatment and increase the risk of the outcome, thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
+In causal inference nomenclature, statins and dementia are said to be _d_-connected, as there is an open "backdoor" path between them via the uncontrolled confounders.[@suttorp2015] In the context of this analysis, this means a confounding variable (or, more likely, variables) both prompts prescription of statins and also represents a risk factor for the development of the vascular dementia.
+A similar confounding structure likely exists for ezetimibe, another hypercholesterolemia treatment, providing an explanation for the association of vascular/other dementia but not Alzheimer's disease with this drug.
 
@@
 
-In line with this, an increasingly harmful effect is observed when moving from the probable and possible Alzheimer's disease outcome to the other dementias outcome, and finally to the vascular dementia outcomes.
+In line with this, an increasingly harmful effect is observed when moving from the probable and possible Alzheimer's disease outcomes to the other dementia outcome, and finally to the vascular dementia outcomes.
 This pattern suggests that the strength of the residual confounding by indication increases as the proportion of cases with a vascular component in an outcome definition increases.
@@
 An initial interpretation of the different associations observed in the two groups was that the lipophilic statins may be more potent, and so are prescribed to patients with a higher underlying vascular load, leading to increased confounding by indication in this group.
-However, the statin with the strongest lipid lowering effect that is available via the NHS, rosuvastatin, is hydrophobic.
+However, the statin with the strongest lipid lowering effect that is available via the NHS, rosuvastatin, is hydrophilic.
 
@@
 There is a strong possibility of differential misclassification of dementia-related conditions based on the exposure.[@porta2014] As an illustrative example, those with memory complaints may be more likely to be classified as vascular dementia than Alzheimer's disease if their medical records contain prescriptions for lipid-regulating agents.
-Further, there is a potential for general non-differential misclassification of the outcome due to the varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
+Further, there is potential for general non-differential misclassification of the outcome due to the varying positive predictive value of electronic health record code lists to identify dementia cases.[@wilkinson2018; @mcguinness2019validity]
 
 Misclassification of outcomes is not the only issue introduced by the use of EHR codes to define outcomes.
-Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code lists can have on the analysis, as illustrated by the discrepancy between the results when using the code lists defined for this study and those used by Smeeth _et al_.
+Comparing and contrasting between different studies is particularly difficult because of the impact that the use of different code lists can have on the analysis.
+This problem is illustrated by the discrepancy between the results when using the code lists defined for this study and those used by Smeeth _et al_.
 This presents a particular challenge in comparing research across different time-periods and coding systems, particularly the unexpected results I obtained for the vascular and other dementias outcomes.
@@
 However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations were driven by those observed in the large statin subgroup.
+In all cases, the estimated associations for the any LRA analysis were largely due to those those observed in the large statin subgroup.
 
@@
 * Findings from this analysis are used as an additional source of evidence in the triangulation exercise presented in Chapter \@ref(discussion-heading).
-
-\newpage
-
-## References

### 2021-12-06 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 
-Individual participant data (IPD) meta-analyses are a special type of meta-analysis that contact the authors of relevant studies to request access to the raw data on each participant.
+Individual participant data (IPD) meta-analyses are a special type of meta-analysis where those undertaking the study contact the authors of relevant studies to request access to the raw data on each participant.
 This is different to the meta-analyses presented in the previous chapter, which used published summary results.
@@
 To examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
-However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided me with access.
+However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested access.
 
@@
 The sole exception was an increased risk of vascular dementia in those with higher triglyceride levels.
-In addition, participants age and sex did not appear to influence the relationship of lipid fractions and dementia outcomes.
+In addition, the participants age and sex did not appear to influence the relationship of lipid fractions and dementia outcomes.
 
@@
 
-The reasons for the low response rate to request for data are explored. Finally, I suggest future studies to investigate how data access rates could be improved.
+The reasons for the low response rate to requests for data are explored. Finally, I suggest future studies to investigate how data access rates could be improved.
 
@@
 
-Individual participant data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful for investigating the impact of participant-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
+Individual participant data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful when investigating the impact of participant-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
 IPD analysis also offer a mechanism by which previously unanalysed datasets can be incorporated into an analysis, thus expanding the evidence base for a particular research question.
@@
 a study conducted across multiple waves, but only data from a single wave could be accessed) were excluded.
-Similarly, due to time restrictions within the scope of my thesis project, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
+Similarly, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
 No restrictions were put on the number of participants or the length of follow-up, though participants must be free of dementia (or assumed to be free, based on age at entry)  at baseline.
@@
 Potentially eligible data sources as defined above were identified via two mechanisms, each with a distinct focus.
-For both approaches, the number of cohorts responding to the request for data access, and where applicable, the reasons given for a lack of data sharing were recorded.
+For both approaches, the number of cohorts responding to the request for data access, and where applicable, the reasons given for a refusal were recorded.
 
@@
 The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapter \@ref(sys-rev-heading)  The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
-In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potentially collaborators) in Autumn 2020.
-If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who has moved to a different institution.
+In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potential collaborators) in Autumn 2020.
+If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who had moved to a different institution.
 
@@
 Where data on one of these exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
-Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
+Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
 
@@
 
-Across all cohorts, data cleaning was performed in a similar manner, standardising to commonly named variables so that a single model could be applied using functional programming.[@wickham2016func] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if needing to change variables names from cohort to cohort.
+Across all cohorts, data cleaning was performed in a similar manner, standardizing to commonly named variables so that a single model could be applied using functional programming.[@wickham2016func] The advantage of this approach is that it reduces the likelihood of errors in model mis-specification if changes are required in variables names from cohort to cohort.
 Following data cleaning, summary statistics for each data source were calculated and compared with publicly available statistics to ensure no errors were introduced in the data cleaning process, in line with best practice.[@levis2021]
@@
 
-In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains female participants.
+In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains only female participants.
 All interaction analysis were performed using the common-set-adjusted model (Model 1).
@@
 Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
-Further, while the maximally-adjusted could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
+Further, while the maximally-adjusted model (Model 2) could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
 
@@
 
-Similar to the analysis of CPRD data presented in the previous chapter, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except to compare between this analysis and previously published results using the same data source.
-For a detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
+A detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
+As such, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except to compare between this analysis and previously published results using the same data source.
 
@@
 
+<!-- REVIEW also identified that any future studies would require a longer and/or more directive approach to the provision of access - DPUK is a good example of how this could be done! -->
+
 A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.[@nevitt2017] However, it is assumed that a ~10% response rate is at the lower end of the scale.
@@
 There are likely several likely reasons for this low response rate to requests for data access.
-In general terms, there are a several well-documented barriers that prevent data from being made readily available, including concerns regarding participant privacy, fear of "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, IPD meta-analysis including studies other than randomised controlled trials have less success in obtaining IPD from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit the response rate than a well-known senior academic might.
+In general terms, there are a several well-documented barriers that prevent data from being made readily available, including concerns regarding participant privacy, fear of "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, IPD meta-analysis including studies other than randomised controlled trials have less success in obtaining IPD from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit a positive response than a well-known senior academic might.
 The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised COVID-related work.
@@
 
-While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, a central strength of this analysis is use of a systematic approach to identify and attempt to contact relevant cohorts.
+While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, a central strength of this analysis is the use of a systematic approach to identify and attempt to contact relevant cohorts.
 Further, it also enabled incorporation of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - thus providing additional evidence that is used in the triangulation exercise reported in Chapter \@ref(tri-heading).
 
-A further strength is the ability of this analysis was the ability to investigate the effect of participant characteristics (namely age and sex) on the association of blood lipids and dementia outcomes.
+A further strength of this analysis was the ability to investigate the effect of participant characteristics (namely age and sex) on the association of blood lipids and dementia outcomes.
 To the best of my knowledge, no previous review has examined the interaction of these factors with the observed associations.
@@
 
+<!-- REVIEW Or a requirement of peer review and publication be that the data be recorded centrally and made available through a coordinated application process) -->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-- In this chapter, I performed an IPD meta-analysis to investigate the effect of blood lipid levels on risk of incident dementia.
-There was a very low response rate to requests for data access, resulting in the inclusion of only three cohorts.
+- In this chapter, I performed an IPD meta-analysis to investigate the effect of blood lipid levels on the risk of incident dementia.
+There was a very low response rate to requests for data access, resulting in the analysis of three relevant cohorts.
 
@@
 I highlighted the contribution of this work to the wider topic via the analysis of previously unexplored cohorts (CaPS & EPIC) and outcomes (vascular dementia).
-Finally, I recommended that future research formally investigate the impact of request characteristics on requests for data.
+Finally, I recommended that future research formally investigate the impact of requestor characteristics on requests for data.
 

### 2021-12-06 07-Chp-Triangulation.Rmd
End of day:

@@
 
+<!-- TODO Sensitivity analysis using only heterogeneity - no change to point estimate - places less importance on the accurate determination of the direction of bias -->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-#### Defining reasonable prior distributions for bias and indirectness
+#### Defining reasonable prior distributions for bias and indirectness {#tri-prior-def}
 

### 2021-12-06 08-Discussion.Rmd
End of day:

@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = TRUE}
-Since many intra-study biases are difficult or impossible to deal with, the meta-analytic results of observational research are often acts of politics, not science.
+Hold
 ```
 
-(ref:discussion-quote) --- Alvan R. Feinstein, 1995 [@feinstein1995]
+(ref:discussion-quote) --- Hold
 
@@
 The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.
-In this discussion, I will review the role of each chapter in the broader thesis, summarise the principal findings and contributions of this thesis, and discuss the implications of my findings for both clinical and public health policy.
-I consider the overall strengths and limitations of this thesis as a coherent body of work, and suggest avenues for impactful future research based on my findings and experiences.
+In this discussion, I will review the contribution of each chapter to this central aim, summarise the principal findings and methodological innovations, and discuss the implications of my findings for both clinical and public health practice.
+I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that builds on the research presented.
 
@@
 
-This thesis is comprised of a mix of methodological and applied chapters.
+This thesis is comprised of a mix of methodological and applied research chapters.
 
-In Chapter __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research performed in terms fo the theoretical framework of evidence synthesis.
+In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoetical framework of evidence synthesis.
 
@@
 
-In __Chapter \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of the relationship between dementia outcomes and blood lipids (and treatments that modify them).
+In __Chapter \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with demetia outcomes.
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
@@
 
-Finally, in __Chapter \@ref(tri-heading)__ I propose a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework.
+Finally, in __Chapter \@ref(tri-heading)__, I propose a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework.
 I illustrate the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.
@@
 
-As the results of the different components of this thesis are discussed in detail as part of the triangulation analysis (see Section \@ref(qual-tri))
+As the results of the different components of this thesis are discussed in detail as part of the triangulation analysis (see Section \@ref(qual-tri)), here I briefly summarise the key findings.
 
 Overall, I did not identify a consistent effect of any blood lipid fraction (total cholesterol, LDL cholesterol, HDL cholesterol or triglycerides) on any dementia outcome (all-cause dementia, Alzheimer's disease or vascular dementia).
-
-While published non-randomised studies provided evidence for a protective effect of lipid-lowering via statin use on Alzheimer's disease, this effect was not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
-However, this may indicate that statins have a pleiotropic effects on Alzheimer's disease, that is an effect other than through lipid-lowering.
+While published non-randomised studies provided evidence for a protective effect of lipid-lowering via statin use on Alzheimer's disease and the IPD analysis suggested a harmful effect of raised triglycerides on vascular dementia, these effects were not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
+Similarly, the IPD analysis did not provide evidence for an interaction of patient characteristics with the association of blood lipids on dementia outcomes, though the results are limited by low number of cohorts analysed.
 
@@
 Given the large proportion of patients taking statins as indicated by my analysis of the CPRD data, this finding is unsurprising.
-
-There was a substantial absence of evidence for vascular dementia.
-This may be due to absence of vascular dementia GWAS, which preclude use of two-sample Mendelian randomisation studies, or could potentially be due to a publication bias mechanism.
+Finally, there was a substantial absence of evidence for vascular dementia.
 
@@
 
-Since the searches underpinning the systematic review described in this thesis were performed (July 2019), there have been some notable analysis of large cohorts performed related to the central thesis question here.
-Two of these are discussed here notable studies are discussed here.
+Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been performed.
+Two of these, noteable for the analysis of large UK cohorts, are discussed here.
 
-The first is a large scale analysis of blood lipids in the CPRD, which found a slight raised risk of dementia in CPRD patients () with higher LDL-c measured at mid-life, driven by the finding for Alzheimer's disease.[@iwagami2021] These findings are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4.
-The study performed a simulation study to investigate the expected effect of confounding by _ApoE4_ in the absence of a true causal effect, yeilding a RR of 1.09 per 1-SD increase in LDL-c.
+The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup.
+These findings are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
-The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes (women: TC `r estimate(1.04,.99,1.09,"HR")`, HDL `r estimate(0.95,.83,1.1,"HR")`, LDL `r estimate(1.06,1,1.13,"HR")`/ men: TC `r estimate(0.98,.93,1.03,"HR")`, HDL `r estimate(1.1,.95,1.29,"HR")`, LDL `r estimate(.97,.91,1.04,"HR")`).
-The results were broadly similar between the all-cause dementia, Alzheimer's disease and vascular dementia outcomes, and are comparable to the results of this thesis.
+The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes, comparable to the results of this thesis.
 However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _ApoE4_ genotype.
@@
 
-Given the absence of any consistent signals across the evidence sources analysed, there are no clear indications for clinical practice.
-While this thesis did not provide any evidence for an effect of lipid-lowering on dementia outcomes, the cumulative strength of evidence is also insufficient to rule out an effect.
+Given the absence of any consistent signals across the evidence sources analysed, there are no clear indications for clinical practice arising from this thesis.
+While my research did not provide any strong evidence for an effect of lipid-lowering on dementia outcomes, the cumulative strength of evidence is also insufficient to rule out an effect.
 
-Given this ambiguity, the use of statins should be restricted to their primary and well-understood purpose of lipid-lowering to reduce risk of cardiovascular events.
-However, it is important to recognise that even under the scenario that a strong harmful effect of lipid-lowering was identified, whether or not to prescribe a statin at mid-life will always be guided by factors other than dementia prevention.
+Given this ambiguity, the use of statins should be restricted to their primary and well-understood purpose of lipid-lowering to reduce the risk of cardiovascular events.
+However, it is important to recognise that even under the scenario that a strong harmful effect of lipid-lowering on dementia outcomes was identified, whether or not to prescribe a statin at mid-life will always be guided by factors other than dementia prevention.
 Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early-onset dementias), which is substantially less likely if hypercholesterolemia at mid-life is left unchecked.
-
-As with many many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
-It could well be that statins do have a true effect independently of lipid-lowering, as observed in published NRSI.
 
@@
 Public health practitioners could examine summary-level statistics of GP prescription data to attempt to relate lipid-lowering treatment to temporal or geographical trends in dementia incidence.
-It will be difficult to assess if effect is due to confounding or ecological biases, but as dementia will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a further source of evidence.
+It will be difficult to assess if any observed trends are due to a true effect or to confounding or ecological biases.
+However, as dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a ready source of further evidence.
 
@@
 
-In addition to addressing the causal impact of lipids on dementia outcomes, the research described in this thesis represents a number of novel contributions to the the field of evidence synthesis.
+In addition to addressing the causal impact of lipids on dementia outcomes, the research described in this thesis represents a number of novel contributions to the field of evidence synthesis methodology.
 
@@
 
-Including preprints adds a valuable evidence source to a synthesis.
-
-Preprints are an important source of evidence, and searching of preprint repositories should.
-The tool presented in Chapter \@ref(sys-rev-tool) allows for this, enabling ready access to and searching of health-related preprints.
-
-While, in the case of the systematic review,
-
-As discussed in Section \@ref(), the tools has been used in a number of published studies
+Preprints are an important source of evidence, and searching of preprint repositories should become an accepted part of the evidence synthesis process.
+To support this, I developed a new tool (as described in Chapter \@ref(sys-rev-tools-heading)) to enable researchers to readily search health-related preprints.
 
@@
 
-One of the central methodological focuses of this thesis has been on the assessment, visualisation, and adjustment for bias.
+One of the central methodological contributions of this thesis has been on the conduct, visualisation, and incorporation of bias assessments as part of an evidence synthesis exercise.
 
@@
 
-Finally, I have proposed a new framework for the assessment and adjustment of bias in diverse evidence sources, using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias assessments.
-This framework provides a systematic way to account for biases across studies, reducing the potential for differential adjustment based on knowledge of the results.
+Finally, I made several novel contributions around the incorporation of bias into analyses.
+These were intended to encourage authors of reviews to actively consider the impact of bias in their synthesis, something that empirical evidence suggests happens infrequently at present.[@katikireddi2015] The new methods introduced by this thesis range from the forest plots stratified by overall risk of bias level presented in Chapter \@ref(sys-rev-results-heading) to the more advanced triangulation framework presented in Chapter \@ref(tri-heading).
 
@@
 
-In contrast to the opening quote of this chapter, I believe that , particularly for outcomes that are difficult to study using randomised controlled trials. However, as noted previously,
+The proposed quantitative triangulation framework represents the final novel contribution of this thesis to evidence synthesis methodology.
+Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies, reducing the potential for differential adjustment based on knowledge of the results.
 
-In general, there is a need to better make use of non-randomised evidence, particularly in areas where RCTs are not easily performed or are ethically infeasible.
+Ideally, this framework should be based on the results of a comprehensive systematic review, which identifies all evidence (both direct and indirect) related to a causal question of interest.
+This would represent a break from the current practice of limiting review to a single type of evidence, and  would result in fewer, more comprehensive reviews.
+However, in the current context of research waste, a concentration of effort in fewer reviews may be advantageous.
+Section \@ref(rev-previous-reviews) illustrates the duplication of reviews in relation to the topic of this thesis, while an assessment of the COVID-19 literature found that, for a specific clinical question, there were substantially more reviews (25) than available primary studies (17).[@perez-gaxiola2021]
 
-where the rigourness and relevance of each individual are systematically considered and adjusted for using pre-specified adjustment distributions,
-
-The final methodological contribution of thesis thesis was a proposed generalised quantitative triangulation framework, building on existing methods for the systematic assessment of bias and methods for bias-/indirectness-adjusted meta-analysis.
-
-While the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
+Finally, while the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
 The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness, and decreases the precision of the overall effect estimate on this basis.
 
-In summary, the framework will enable better use of observational studies to address causal questions.
+In summary, the proposed triangulation framework will enable better use of all available evidence to address causal questions.
 
@@
 
-The strengths and limitations of each aspect of this thesis have been discussed in the respective chapter. Here I highlight the strengths and weaknesses of this thesis as a body of work.
+The strengths and limitations of each aspect of this thesis have been discussed in the respective chapter. Here, I highlight the strengths and weaknesses of this thesis as a body of work.
 
@@
 There are several strengths to this thesis as a whole.
-Specifically, the synthesis of evidence across study designs and publication status ensures a comprehensive overview of the state of the research in this topic, and sets this thesis apart from previous synthesis of the evidence on this topic.
-Additionally, as discussed above, assessment of the potential for bias has a central aspect of the research projects presented, and can be considered a core strength of this thesis.
-Many previous evidence synthesis exercised on this topic did not sufficiently consider bias .
-
-This thesis has also produced new evidence on the association of blood lipids with dementia outcomes via two primary analysis, in addition to providing additional information on a previously understudied association (lipids/LRA and vascular dementia).
+Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous synthesis of the evidence on this topic.
+Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).
 
@@
 Extensive documentation has been written to guide users through usage of the tools and example data is provided for use.
-Finally, extensive efforts have been made to make the research documented in this thesis as reproducible as possible - these are documented in Appendix \@ref(disc-repro-research).
+Finally, subtantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).
 
@@
 However, there are also several strong limitations to this thesis.
-In the first instance, each analysis presented here makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
-Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in, absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable[@wilkinson2018]).
+In the first instance, as with many many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
+It is possible that statins have a true effect via some other pathway , but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
 
-Further, missing evidence was a common limitation across this thesis.
+Secondly, each analysis presented here makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
+Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in Chapter \@ref(ipd-analysis-heading), absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable).[@wilkinson2018]
+
+Thirdly, missing evidence was a common limitation across this thesis.
 In Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading), several studies stated that they did not report the results of an analysis because the results were not significant.
@@
 Similarly, an absence of evidence on vascular dementia, potentially due to a publication bias mechanism, limited the analysis of this outcome.
-Finally, missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(hold), in the form of a poor response to data access requests.
+Missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(hold), in the form of a poor response to data access requests, while the absence of empirically-based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
 
-A final weakness stems the geographical focus of the data analysed in this thesis.
+A final weakness stems from the geographical focus of the data analysed in this thesis.
 All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world (Figure \@ref(fig:cohortLocations)).
@@
 
-As a reflective process throughout my PhD, I maintained a catalogue of failures available in Appendix \@ref(appendix-catalogue-failures), describing specific analytical failures and unsuccessful grant applications.
-However, there was one central takeaway from this thesis, namely to be slightly less ambitious when planning future research projects.
+As part of a reflective learning process throughout my PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)) describing analytical mistakes, failed experiments, and unsuccessful grant applications.
+However, I found there was one central learning point from this thesis, namely to be slightly less ambitious when planning future research projects.
 
-The proposal for the programme of research underpinning this thesis was created in advance, as a detailed plan was required in order to secure NIHR funding.
-In hindsight, the decision to take a broad approach to inclusion of dementia outcomes resulted in larger workload than anticipated, particularly when considering evidence from across different study designs.
+The proposal for the programme of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies.
+In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs.
 Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g.
-Alzheimer's disease).
-
+Alzheimer's disease) when considering the causal effects of lipids.
 Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger programme of research was overly ambitious, as data cleaning and harmonisation for just three of the many cohorts I applied to was a substantial undertaking.
 
-In the future, I will better scope proposed research projects.
+In the future, armed with the experience gained through conduct of the research projects presented here, I will be better place to scope and design research projects.
 
-nnbsp;<!----------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Several avenues of future research, building on the work presented here, could be pursued. These are grouped by topic in the following sections.
+Several avenues of future research could be pursued, building on the novel work presented here. These are grouped by topic in the following sections.
 
-__[Question: is it better to use "should" or "could" when listing ideas for future research? I.e. future work could/should look at X.]__
+__[Question: is it better to use "should" or "could" when listing ideas for future research? I.e. "future work could/should look at X"?]__
 
@@
 
-It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trials be performed to assess the effect of the proposed intervention, in this case statins.
+It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trial be performed to assess the effect of the proposed intervention.
 Given the costs and logistical challenges associated with trials examining outcomes with long prodomal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up (PTFU) of existing RCTs of lipid-regulating agents.
 
-PTFU of two lipid-regulating agent trials has already been used to assess long-term (11-20 years) safety outcomes of statin use, using participant recontact[@group2011] and linkage with electronic health records to identify events.[@ford2016] A similar approach could be used to assess the impact of randomisation to statins at midlife on subsequent risk of dementia outcomes.
+This approach has already been used to assess long-term (11-20 years) safety outcomes of statin use, using participant recontact[@group2011] and linkage with electronic health records to identify events.[@ford2016] A similar approach could be used to assess the impact of randomisation to statins at midlife on subsequent risk of dementia outcomes.
 Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using EHRs.
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-As highlighted by the results of the systematic review presented in Chapter \@ref(sys-rev-results-heading), there is an absence of evidence on vascular dementia across the evidence base.
-Future research should aim to both investigate the reasons for this evidence gap (e.g.
-due to an absence of primary data, challenges in the analysis of this outcome as documented in Chapter \@ref(cprd-analysis-heading), or a publication bias mechanism) and work to address it.
+As highlighted by the results of the systematic review presented in Chapter \@ref(sys-rev-results-heading), there is an absence of evidence on vascular dementia across the existing evidence base.
+While the primary studies presented here go some way towards supplementing this evidence base, future work is needed both to investigate the reasons for this evidence gap (e.g.
+due to an absence of primary data, challenges in the analysis of this outcome as documented in Chapter \@ref(cprd-analysis-heading), or a publication bias mechanism) and to address it.
 
-However, it seems unlikely that analysis of observational data will be sufficient , given the presence of strong confounding by indication present in the analysis of statins and vascular dementia.
-Even using new methods, such as a target trial approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] This reinforces the need for large-scale GWAS of vascular dementia, similar to those current available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could make use of.
-While GWAS of this outcome are likely to be methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of many genetically-driven risk factors beyond those considered in this thesis.
+However, it seems unlikely that further analysis of observational data alone will be sufficient to investigate this outcome, as indicated by the presence of strong confounding by indication in the analysis of statins and vascular dementia (Chapter \@ref(cprd-analysis-heading)).
+Even using new methods, such as a target trial emulation approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] Similarly, Mendelian randomisation studies are limited to a single one-sample analysis of HMGCR variants as a proxy for statin treatment.
+This study suggested a protective effect of lipid-lowering on vascular dementia, though there was a moderate risk of bias in this analysis and the effect was attenuated to the null when including a wider range of lipid-lowering variants.
+
+Taken together, these points reinforce the need for large-scale GWAS of vascular dementia, similar to those current available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could exploit.
+While GWAS of this outcome are likely to be methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of genetically-driven risk factors beyond those considered in this thesis.
 
@@
 
-Future work on preprinted evidence should address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in an evidence synthesis exercise.
-This will be particularly important if the results are substantially different between the two versions or if a result available in the preprint manuscript is not presented in the published version.
+In terms of evidence synthesis methodology, future work on preprinted evidence should address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in a synthesis.
+This will be particularly important in cases where the results are substantially different between the two versions or if a result available in the preprint manuscript is not presented in the published version.
 
-Finally, the `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.
-In addition, the ready access to preprint data afforded by the tool will enable meta-epidemiological studies to examine factors which may influence eventual publication (e.g.
-significant result, geographical location or gender of first author, or some other factor).
+The `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.[@elliott2014] In addition, the ready access to preprint data afforded by the tool will enable future meta-epidemiological studies to examine factors which may influence eventual publication (e.g.
+significant result, geographical location/gender/career stage of first author, or some other factor).
 Finally, the tool will allow future research to assess the impact of peer review and editorial guidelines on manuscripts through comparison of the same paper at two stages (preprinted versus published).
-This approach was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(sys-rev-tools), but could be applied to other important meta-research questions.
+This approach was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(sys-rev-tools), but could be applied to other aspects of the publication process.
 
@@
 
-As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not sufficiently developed.
-Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define it (e.g.
+As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not yet sufficiently developed, particularly in comparison to other study designs.
+Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g.
 genetic instrumental variable analysis).
-In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk of bias tool for Mendelian randomisation studies limits future work that requires systematic risk-of-bias assessment such as the quantitative triangulation framework proposed here.
-Finally, guidance around the inclusion of two-sample Mendelian randomisation studies using identical summary statistics, which can falsely increase the precision of the summary estimate as more fully discussed in Section \@ref(rev-discussion-MR), would represent a useful contribution.
+In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that requires systematic assessment of bias, such as the quantitative triangulation framework proposed here.
+Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority.
+
+Finally, the inclusion of multiple two-sample Mendelian randomisation studies using identical summary statistics can falsely increase the precision of the summary effect estimate if treated as independent results.
+Development of best pracice guidance for addressing this problem would represent a useful contribution to the field.
 
@@
 Quantitative triangulation is an area ripe for future work.
-The approach presented here will benefit from meta-epidemiological studies to better define the impact of different bias in non-observational studies.
+The approach presented here will benefit from future meta-epidemiological studies to better define the impact of bias/indirectness, as discussed in detail in Section \@ref(tri-prior-def).
+Similarly, future work should expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
+Tools such as ROB-ME will enable this, but how to adjust for this analysis-level - as opposed to result-level - bias will need to be determined.
+Finally, the application of the framework to other causal questions will help to identify sticking points and may lead to refinement of the process.
 
-Similarly, future work should expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
-Tools such as the ROB-ME assessment tool will enable this, but how to adjust for this analysis-level - as opposed to result-level - bias should be explored.
-
-Finally, the application of the framework across other causal questions will help to identify sticking points in the process.
-
-While synthesising evidence from a specific study design (e.g.
-NRSI) is currently the norm, future reviews should aim towards assessment of all evidence (direct and indirect) related to a specific causal question.
-
-In essence, we need fewer reviews addressing the same questions in order to combat research waste.
-Section \@ref(rev-previous-reviews) illustrates this in the context of this thesis, while an assessment of the COVID-19 literature found that, for a specific clinical question, there were substantially more reviews (25) than available primary studies (17).
+<!-- TODO Could also talk here about how applying it across multiple questions would enable the development of a database of prespecified priors. -->
 
@@
 
-This thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the uncertainty that still remains in relation to this causal question.
-In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will future evidence synthesists to better address causal questions.
+This thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the considerable uncertainty that still remains in relation to this causal question.
+In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will future evidence synthesists to better address important causal questions.

### 2021-12-06 index.Rmd
End of day:
Working version

@@
 degree: Doctor of Philosophy
-degreedate: 2022
+degreedate: December 2021
 word-count: |
@@
 ---
-<!-- TODO Confirm thesis title! -->
 
@@
 -->
-
-```{r introduction, child = 'front-and-back-matter/_00-introduction.Rmd'}
-```

### 2021-12-07 05-Chp-CPRD-Analysis.Rmd
Fix broken links to appendices

@@
 
-An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).[@vonelm2008]
+An *a priori* protocol for this study was published,[@walker2016] and amendments to this are recorded in Appendix \@ref(appendix-cprd-amendments).
 

### 2021-12-07 06-Chp-IPD-Analysis.Rmd
Fix broken links to appendices

@@
 Missing values in collected variables was common across the cohorts.
-A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(hold).
+A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(appendix-ipd-covariate-matrix).
 The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity.
@@
 The only other dementia outcome examined across cohorts was vascular dementia, which was reported in the CaPS and Whitehall II studies.
-The definitions of dementia outcomes used across cohorts can be seen in Appendix \@ref(hold).
+The definitions of dementia outcomes used across cohorts can be seen in Appendix \@ref(appendix-ipd-dementia-def).
 Cumulatively, there were `r n_ipd_dementia` cases of all-cause dementia, with `r n_ipd_vasdem` further classified as vascular dementia.

### 2021-12-07 07-Chp-Triangulation.Rmd
Fix broken links to appendices

@@
 
-Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(?) for more details on how these were calculated).
+Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated).
 For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
@@
 
-No substantial differences were observed between the summary estimates obtained under the two scenarios of additive bias (Figure \@ref(fig:fpLdlAdComparison) in Appendix \@ref(appendix-tri-analysis)).
+No substantial differences were observed between the summary estimates obtained under the two scenarios of additive bias (Appendix \@ref(appendix-tri-analysis)).
 
@@
 Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
-The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(?), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
 

### 2021-12-07 08-Discussion.Rmd
Fix broken links to appendices

@@
 ::: {.laybox data-latex=""}
-## Lay summary {-}
+## Lay summary
+
+<!-- TODO Unnumber lay summary -->
 
@@
 
-The aim of this thesis was to attempt to infer the causal effect of blood lipid levels on dementia outcomes.
-In this discussion, I will review the contribution of each chapter to this central aim, summarise the principal findings and methodological innovations, and discuss the implications of my findings for both clinical and public health practice.
+The central aim of this thesis was to infer the causal effect of blood lipid levels on dementia outcomes via evidence synthesis methods.
+In this discussion, I will review the contribution of each chapter to this aim, summarise the principal findings and methodological innovations of the thesis, and discuss the implications of my findings for both clinical and public health practice.
 I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that builds on the research presented.
@@
 
-In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoetical framework of evidence synthesis.
+In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoretical framework of evidence synthesis.
 
@@
 
-In __Chapter \@ref(sys-rev-methods-heading)__, I describe the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with demetia outcomes.
+In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with dementia outcomes.
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
 
-In __Chapter \@ref(cprd-heading)__, I describe an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
+In __Chapter \@ref(cprd-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
 I make use of control outcomes to illustrate insufficiently controlled confounding.
 
-In __Chapter \@ref(ipd-heading)__, I present an individual participant data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.
+In __Chapter \@ref(ipd-heading)__, I presented an individual participant data meta-analysis of the association of lipid levels and dementia outcomes, using previously unanalysed data accessed via the Dementia Platform UK.
 
-Finally, in __Chapter \@ref(tri-heading)__, I propose a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework.
-I illustrate the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.
+Finally, in __Chapter \@ref(tri-heading)__, I proposed a new method for the systematic integration of multiple evidence sources as part of quantitative triangulation framework.
+I illustrated the method using two case studies (the effect of LDL-c on Alzheimer's disease and the effect of triglycerides on vascular dementia), drawing on the evidence identified or produced by previous chapters.
 
@@
 Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been performed.
-Two of these, noteable for the analysis of large UK cohorts, are discussed here.
+Two of these, notable for the analysis of large UK cohorts, are discussed here.
 
 The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup.
-These findings are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
+These results are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
@@
 
-Preprints are an important source of evidence, and searching of preprint repositories should become an accepted part of the evidence synthesis process.
+Preprints are an important source of evidence and searching of preprint repositories should become an accepted part of the evidence synthesis process.
 To support this, I developed a new tool (as described in Chapter \@ref(sys-rev-tools-heading)) to enable researchers to readily search health-related preprints.
@@
 
-In terms of assessment, I applied domain-based tools to evidence relevant to the effect of lipids on dementia outcomes, and highlighted the limitation of the available tools for Mendelian randomisation studies.
+In terms of assessment, I applied domain-based tools to evidence relevant to the effect of lipids on dementia outcomes and highlighted the limitation of the available tools for Mendelian randomisation studies.
 I also piloted and provided feedback on a forthcoming tool for assessing the risk of bias due to missing evidence.
@@
 Finally, while the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
-The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness, and decreases the precision of the overall effect estimate on this basis.
+The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness and decreases the precision of the overall effect estimate on this basis.
 
@@
 Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous synthesis of the evidence on this topic.
-Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).
+Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).
 
@@
 Extensive documentation has been written to guide users through usage of the tools and example data is provided for use.
-Finally, subtantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).
+Finally, substantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).
 
@@
 
-### Weaknessess
+### Weaknesses
 
 However, there are also several strong limitations to this thesis.
-In the first instance, as with many many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
+In the first instance, as with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
 It is possible that statins have a true effect via some other pathway , but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
@@
 
-The proposal for the programme of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies.
+The proposal for the program of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies.
 In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs.
@@
 Alzheimer's disease) when considering the causal effects of lipids.
-Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger programme of research was overly ambitious, as data cleaning and harmonisation for just three of the many cohorts I applied to was a substantial undertaking.
+Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, as data cleaning and harmonisation for just three cohorts was a substantial undertaking.
 
@@
 Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority.
-
 Finally, the inclusion of multiple two-sample Mendelian randomisation studies using identical summary statistics can falsely increase the precision of the summary effect estimate if treated as independent results.
-Development of best pracice guidance for addressing this problem would represent a useful contribution to the field.
+Development of best practice guidance for addressing this problem would represent a useful contribution to the field.
 
@@
 
-### Systematic reviews and quantiative triangulation
+### Systematic reviews and quantitative triangulation
 
@@
 <!-- TODO Could also talk here about how applying it across multiple questions would enable the development of a database of prespecified priors. -->
-
 &nbsp;
@@
 
-This thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the considerable uncertainty that still remains in relation to this causal question.
-In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will future evidence synthesists to better address important causal questions.
+To conclude, this thesis has provided new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlighted the considerable uncertainty that still remains in relation to this causal question.
+In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will enable future evidence synthesists to better address important causal questions.
+
+\newpage

### 2021-12-07 front-and-back-matter/99-appendices.Rmd
Fix broken links to appendices

@@
----
-output:
-  pdf_document: default
-  html_document: default
----
 `r if(knitr:::is_latex_output()) '\\startappendices'`
@@
 `r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'`
-
-<!-- If you feel it necessary to include an appendix, it goes here. The first appendix should include the commands above. -->
 
@@
 
-<!----------------------------------------------------------------------------->
 # Appendices by Chapter {#chapter-appendix-heading}
-
-&nbsp;
 
@@
 
-<!----------------------------------------------------------------------------->
 ## Chapter \@ref(background-heading) {#appendix-into}
 
-<!----------------------------------------------------------------------------->
 ### Publications beyond the scope of this thesis {#appendix-publications}
@@
 
-<!----------------------------------------------------------------------------->
-
 ### Involvement of patients and the public {#appendix-ppi}
@@
 
-<!----------------------------------------------------------------------------->
-
 ## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
-<!----------------------------------------------------------------------------->
 
@@
 ## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}
-<!----------------------------------------------------------------------------->
 
@@
 
+### Web of Science Databases Searched {#appendix-wos-databases}
+
+(ref:wosDatabases-caption) Summary of Web of Science databases searched.
+
+(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
+
+```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Search strategy {#appendix-search-strategy}
 
-&nbsp;
-
-<!----------------------------------------------------------------------------->
 (ref:searchHits-caption) Overview of the full Medline search strategy.
@@
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
-&nbsp;
-
-### Web of Science Databases Searched {#appendix-wos-databases}
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:wosDatabases-caption) Summary of Web of Science databases searched.
-
-(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
-
-```{r wosDatabases-table, message=FALSE, results="asis", echo = FALSE}
-
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
 ### Code to search preprints {#appendix-medrxivr-code}
@@
 
-### Calculating Gwet's AC1
+### Calculating Gwet's AC1 {#appendix-gwet}
 
@@
 
-<!----------------------------------------------------------------------------->
 ### MR risk of bias tool {#appendix-mr-rob}
 
-<!----------------------------------------------------------------------------->
 (ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
@@
 
-### Dose response plots by fraction
+### Dose response plots by fraction {#appendix-dr-fraction}
 
-<!----------------------------------------------------------------------------->
 (ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia
@@
 ```
-<!----------------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
 (ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease
@@
 ```
-<!----------------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
 ## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
-<!----------------------------------------------------------------------------->
 
@@
 
+## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
+
+### Email and documents sent to potental collaborators {#ipd-email-collab}
+
+### Covariate matrix {#appendix-ipd-covariate-matrix}
+
+### Dementia definitions across cohorts {#appendix-ipd-dementia-def}
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
+
+### Calculation of average adjustment from expert elicitation {#appendix-adjustment-values}
+
 ### Code lists
 
-## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
-<!----------------------------------------------------------------------------->
-### Email and documents sent to potental collaborators {#ipd-email-collab}
-
-<!----------------------------------------------------------------------------->
-## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
-<!----------------------------------------------------------------------------->
-### Calculation of average adjustment from expert elicitation
-
-<!----------------------------------------------------------------------------->
-### Code lists
-
-<!----------------------------------------------------------------------------->
 ### Comparison of two scenarios of bias
 
-<!----------------------------------------------------------------------------->
 (ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
@@
 ```
-<!----------------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
 (ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
@@
 ```
-<!----------------------------------------------------------------------------->
 
-<!----------------------------------------------------------------------------->
 ## Chapter \@ref(discussion-heading)
@@
 
-<!----------------------------------------------------------------------------->
 ### Catalogue of failures {#appendix-catalogue-failures}
@@
 
-<!----------------------------------------------------------------------------->
 # Other Appendices {#other-appendix-heading}
@@
 
-<!----------------------------------------------------------------------------->
 ## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}

### 2021-12-07 01-Chp-Background.Rmd
Fix broken cross-links

@@
 Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMGCR).
-This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
+This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(fig:statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
 
@@
 
-There are several other interventions that can be used to modify a persons lipid profile, each of which act via different mechanisms (Table \@ref(tab)).
-However, in general, these treatments are either used as adjunct (additional) treatments with statins therapy or are used in situations where statins are contra-indicated or not tolerated.
+There are several other interventions that can be used to modify a persons lipid profile, each of which act via different mechanisms.
+However, in general, these treatments are either used as adjunct (additional) treatments to statin therapy or are used in situations where statins are contra-indicated or not tolerated.
 
-<!-- see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table -->
+<!-- TODO see https://www.heart.org/en/health-topics/cholesterol/prevention-and-treatment-of-high-cholesterol-hyperlipidemia/cholesterol-medications for information on the indications for treatment - could present as a table .
+If using table, put reference to it in the above par -->
 
@@
 However, as with grey literature,[@mahood2014] there are several logistical problems with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools).
+As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools-heading).
 
@@
 I will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-analysis-heading).
+Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
 This will enable the assessment of the effect of lipids on dementia stratified by key variables such as sex.
@@
 All existing evidence, regardless of study design, is first identified and assessed using domain-based tools by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
-The existing evidence base is then supplemented by two primary analyses, presented in Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-analysis-heading).
+The existing evidence base is then supplemented by two primary analyses, presented in Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-heading).
 Finally all existing and new evidence is incorporated into the quantiatative triangulation framework in Chapter \@ref(tri-heading).
@@
 
-Using the tool described in Chapter \@ref(sys-rev-tools), I lead a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
+Using the tool described in Chapter \@ref(sys-rev-tools-heading), I led a "research-on-research" study to assess the concordance between the openness of data availability statements accompanying a sample of medRxiv preprints and their published counterparts.
 

### 2021-12-07 02-Chp-Systematic-Review-Tools.Rmd
Working version
Fix broken cross-links

@@
 
-Searching these preprints as part of the systematic review described in Chapter \@ref(sys-rev-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
+Searching these preprints as part of the systematic review described in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
 At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the complex searches containing Boolean logic operators (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search involved going through each record and downloading individual citations one-by-one.
@@
 
-<!-- IDEA Add timeline chart as seen here: https://bookdown.org/alecri/thesis/4-methods.html#sec:dosresmeta -->
-
 ### Success criteria {#success-criteria}
 
-I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review in Chapter \@ref(sys-rev-heading), discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
+I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review presented in the subsequent chapters, discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
 The criteria were as follows:
@@
 
-Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-heading).
+Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-methods-heading).
 Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and I released the initial version of the `medrxivr` R package in February 2020.
@@
 
-In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapter \@ref(sys-rev-heading), `medrxivr` has other uses.
+In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading), `medrxivr` has other uses.
 
@@
 
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis presented in Chapter \@ref(sys-rev-heading), there are some important limitations to note here.
+While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis, there are some important limitations to note here.
 A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, and so some relevant records might be missed.
@@
 
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of key literature sources used in the comprehensive systematic review described in Chapter \@ref(sys-rev-heading).
+-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of key literature sources used in the comprehensive systematic review described in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
 
@@
 I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
-
-\newpage
-
-## References

### 2021-12-07 04-Chp-Systematic-Review-Results.Rmd
Fix broken links to appendices
Fix broken cross-links

@@
 This analysis provided weak evidence for a non-linear effect of lipid levels on dementia outcomes, and Figure \@ref(fig:lipidsDoseResponse) illustrates this for the total cholesterol-Alzheimer's strata.
-Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(hold).
+Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(appendix-dr-fraction).
 
@@
 Secondly, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantitative triangulation analysis presented in Chapter \@ref(tri-analysis-heading).
+This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantitative triangulation analysis presented in Chapter \@ref(tri-heading).
 

### 2021-12-07 05-Chp-CPRD-Analysis.Rmd
Fix broken cross-links

@@
 In this chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
-The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapter \@ref(sis-rev-heading).
+The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
 
@@
 
-This second presentation appears to be common in the existing literature on the relationship of statins and dementia, as several of the studies included in the systematic review presented in Chapter \@ref(sys-rev-heading) were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-subheading)).
+This second presentation appears to be common in the existing literature on the relationship of statins and dementia, as several of the studies included in the systematic review performed as part of this thesis were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-res)).
 
@@
 
-#### Impact of dementia code lists {#comparing-code lists}
+#### Impact of dementia code lists {#comparing-codelists}
 
@@
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, a detailed comparison with other published literature will not be provided here, except where needed to illustrate a methodological point.
-For a detailed comparison of the result presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), see Chapter \@ref(tri-heading).
+For a detailed comparison of the result presented above with the existing evidence base identified by the systematic review, see Chapter \@ref(tri-heading).
 
@@
 
-Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter (see Section \@ref(sys-rev-pub-bias)), the unexpected increase in vascular dementia risk with statin use is particularly interesting.
+Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter, the unexpected increase in vascular dementia risk with statin use is particularly interesting.
 It is possible that this finding reflects publication bias if previous research encountered similar methodological issues to this analysis, and these results did not make it into the evidence base as unexpected or assumedly incorrect results are less likely to be submitted or accepted for publication.
@@
 The primary strength of this analysis is the relative size of the CPRD and length of follow-up.
-Having reviewed the existing literature, as identified by the systematic review in Chapter \@ref(sys-rev-heading), this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
+Having reviewed the existing literature, as identified by the systematic review element of this thesis, this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
 Additionally, this analysis followed LRA users and non-users from a common index date, using a time-updating treatment indicator to correctly assign time-at-risk to the exposed and unexposed groups.

### 2021-12-07 06-Chp-IPD-Analysis.Rmd
Fix broken cross-links

@@
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapter \@ref(sys-rev-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
 However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
@@
 
-The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapter \@ref(sys-rev-heading)  The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
+The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
 In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potential collaborators) in Autumn 2020.
@@
 Examination of the data available via the DPUK indicated that the common time-to-event approach used in studies of dementia outcomes would be precluded by the absence of detailed time-to-event data.
-An overall effect estimate was then produced by combining data-source-specific estimates in a random-effects meta-analysis (see Section \@ref(hold) in Chapter \@ref(hold) for a broader discussion of meta-analysis methods).
+An overall effect estimate was then produced by combining data-source-specific estimates in a random-effects meta-analysis (see Section \@ref(meta-analysis-methods) for a broader discussion of meta-analysis methods).
 
@@
 
-Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapter \@ref(sys-rev-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
+Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
 
@@
 Cumulatively, there were `r n_ipd_dementia` cases of all-cause dementia, with `r n_ipd_vasdem` further classified as vascular dementia.
-Summary statistics for each cohort are provided in Table \@ref(tab:cohortSummary-table).
+Summary statistics for each cohort are provided in Table \@ref(tab:covariateSummary-table).
 
@@
 
-A detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapter \@ref(sys-rev-heading)), is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
+A detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)), is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
 As such, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except to compare between this analysis and previously published results using the same data source.
@@
 
-Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-method-heading) & \@ref(sys-rev-results-heading).
+Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
 This is relevant even in the previously analysed WhiteHall II cohort, as the previous analysis by Tynkkynen _et al._ did not report on this outcome.

### 2021-12-07 07-Chp-Triangulation.Rmd
Fix broken cross-links

@@
 
-Analysis of lipid levels across both the systematic review (Chapter \@ref(sy-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-analysis-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
+Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
 Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
@@
 To aid with the quantitative triangulation exercise, I created a new method to visualise the extent, direction and type of bias in each result, enabling detailed comparison across different studies contributing to a synthesis.
-Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-), these "bias direction" plots show the level (or extent) of bias across the domains for each result reported using coloured blocks.
+Similar to the standard paired forest plots introduced in Chapter \@ref(sys-rev-methods-heading), these "bias direction" plots show the level (or extent) of bias across the domains for each result reported using coloured blocks.
 However, in contrast to the previous forest plots, symbols are used to illustrate the predicted absolute direction of bias in that domain.
@@
 From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest.
-Most (n=17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-heading) provided an additional estimate from the CPRD analysis.
+Most (n=17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate from the CPRD analysis.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
@@
 
-From the data sources identified in Section \@ref(tri-data-sources), I identified 7 results relevant to my causal question of interest: 4 were identified via the systematic review,`r tg_vad_citations` while Chapter \@ref(cprd-heading) provided two additional estimates from unanalysed datasets (CaPS and Whitehall II), and Chapter \@ref(ipd-heading) provides an estimate for the effect of fibrates, a treatment for hypertriglyceridaemia.
+From the data sources identified in Section \@ref(tri-data-sources), I identified 7 results relevant to the causal effect of triglycerides at midlife on vascular dementia.
+Four were identified via the systematic review,`r tg_vad_citations` while Chapter \@ref(cprd-analysis-heading) provided two additional estimates from unanalysed datasets (CaPS and Whitehall II), and Chapter \@ref(ipd-heading) provides an estimate for the effect of fibrates, a treatment for hypertriglyceridaemia.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:tgVadBiasDirection), stratified by study design.

### 2021-12-07 08-Discussion.Rmd
Fix broken cross-links

@@
 
-In __Chapter \@ref(cprd-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
+In __Chapter \@ref(cprd-analysis-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
 I make use of control outcomes to illustrate insufficiently controlled confounding.
@@
 Secondly, each analysis presented here makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
-Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in Chapter \@ref(ipd-analysis-heading), absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable).[@wilkinson2018]
+Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in Chapter \@ref(ipd-heading), absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable).[@wilkinson2018]
 
@@
 Similarly, an absence of evidence on vascular dementia, potentially due to a publication bias mechanism, limited the analysis of this outcome.
-Missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(hold), in the form of a poor response to data access requests, while the absence of empirically-based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
+Missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(ipd-heading), in the form of a poor response to data access requests, while the absence of empirically-based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
 
@@
 Finally, the tool will allow future research to assess the impact of peer review and editorial guidelines on manuscripts through comparison of the same paper at two stages (preprinted versus published).
-This approach was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(sys-rev-tools), but could be applied to other aspects of the publication process.
+This approach was used to explore the impact of editorial polices on open data sharing, as discussed in Chapter \@ref(sys-rev-tools-heading), but could be applied to other aspects of the publication process.
 

### 2021-12-08 01-Chp-Background.Rmd
Deal with abbreviations, fix cross-links and some other small edits

@@
 
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10% of cases.
+Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10-25% of cases.
 Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
 
-The remaining 10-30% of cases are caused by other dementia subtypes (e.g.
-Lewy body dementia, frontotemporal dementia) or by progression of other neurological diseases (e.g.
-Parkinson's disease).[@burns2009]
+The remaining 10-30% of cases are caused by other dementia subtypes (e.g. Lewy body or frontotemporal dementias) or other neurological diseases (e.g. Parkinson's disease).[@burns2009]
 
@@
 By far the largest source of evidence on the relationship between blood lipids and dementia outcomes comes from observational designs.
-Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) and both Alzheimer's disease and vascular dementia and reported extremely varied results.
+Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) <!-- TODO These abbreviations have already been defined above --> and both Alzheimer's disease and vascular dementia and reported extremely varied results.
 In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005; @mainous2005; @mielke2010; @tan2003] or a reduced susceptibility [@mielke2005; @reitz2004].
@@
 However, the role of preprints in evidence syntheses is less well defined.
-Defined by the Committee on Publication Ethics (COPE) as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process'[@committeeonpublicationethicscope2018], preprints serve several purposes.
+Defined by the Committee on Publication Ethics as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process',[@committeeonpublicationethicscope2018] preprints serve several purposes.
 They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, the allow for the rapid disseminate research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
@@
 
-### Contributions to the scientific literature
+### Contributions to the scientific literature {#literature-contributions}
 

### 2021-12-08 02-Chp-Systematic-Review-Tools.Rmd
Deal with abbreviations, fix cross-links and some other small edits

@@
 
-However, an Application Programming Interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
+However, an application programming interface (API) for the medRxiv and bioRxiv repositories was made public in early 2020 by the institution responsible for managing these preprint repositories, the Cold Springs Harbor Laboratory.
 This allowed for newer versions of the `medrxivr` package to engage in active "fault prevention" and provide a more robust interface to the data by removing the reliance of web-scraping.[@laprie1992]
@@
 
-```{r, eval = FALSE}
+```{r, eval = FALSE, class.source = "bg-danger"}
 # Get a copy of the database from the live medRxiv API endpoint
@@
   # Use snapshot from July 2021
-  medrxivr::mx_search(medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
-                      "*",
+  medrxivr::mx_search(
+    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
+    query = "*",
     from_date = "2019-07-01",
-                      to_date = "2019-08-01") %>%
+    to_date = "2019-08-01"
+  ) %>%
   mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
@@
 
-Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-sys-rev-tools)).
+Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-tools-pub)).
 `r published` of the `r publication_n` records `r publish_percent` posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
 allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a non-insignificant number of preprints are never formally published but remain accessible as preprints.
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a subtantial number of preprints are never formally published but remain accessible as preprints.
 

### 2021-12-08 03-Chp-Systematic-Review-Methods.Rmd
Fix broken links to appendices
Fix broken cross-links
Deal with abbreviations, fix cross-links and some other small edits

@@
 
-A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020]
+A pre-specified protocol for this analysis was registered on the Open Science Framework platform and is available for inspection.[@mcguinnessluke2020] Deviations from the protocol are summarised in Appendix \@ref(appendix-sys-rev-deviations).
 
@@
 [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
+The formulae used to calculate the coefficient are given in Appendix \@ref(appendix-gwet).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric
+(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric[@mchugh2012]
 
@@
 
-This additional appraisal marks a departure from the registered protocol, as there was initially no intention to try to examine the risk of bias due to missing evidence.
-This is largely because the tool did not exist when the protocol was registered.
-
 <!----------------------------------------------------------------------------->
@@
 
-#### Random-effects meta-analysis
+#### Random-effects meta-analysis {#meta-analysis-methods}
+
+<!-- TODO May need to talk about FE models here, as I refer to this section for a broader discussion of meta-analysis in the IPD chapter -->
 
@@
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.
-This marks a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.
 

### 2021-12-08 05-Chp-CPRD-Analysis.Rmd
Deal with abbreviations, fix cross-links and some other small edits

@@
 
-Previously known as the General Practice Research Database (GPRD), the Clinical Practice Research Datalink (CPRD) is a large population-based electronic health record (EHR) database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+Previously known as the General Practice Research Database, the Clinical Practice Research Datalink (CPRD) is a large population-based EHR database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
@@
 
-I considered seven lipid-regulating drug classes based on groupings in the British National Formulary (BNF),[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
+I considered seven lipid-regulating drug classes based on groupings in the British National Formulary,[@wishart2017] namely: statins, fibrates, bile acid sequestrants, ezetimibe, nicotinic acid groups, ezetimibe and statin (representing one treatment containing both drugs, rather than the two classes being prescribed concurrently), and omega-3 fatty acid groups.
 
@@
 
-This published analysis used a propensity matching approach to estimate the association of statins with a range of outcomes in The Health Improvement Network (THIN) database, an alternative source of English electronic health records which has substantial overlap with the CPRD.[@carbonari2015] The code lists used in this analysis were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
+This published analysis used a propensity matching approach to estimate the association of statins with a range of outcomes in The Health Improvement Network database, an alternative source of English electronic health records which has substantial overlap with the CPRD.[@carbonari2015] The code lists used in this analysis were obtained through correspondence with the authors of that study, and are available for inspection (see Section \@ref(cprd-data-avail)).
 
@@
 (ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
-Note that the x-axis cutoffs (.5,2) are different compared to other plots (0.3,3) to enable greater comparison between the different models.
+Note that the x-axis cutoffs (0.5,2) are different compared to other plots (0.3,3) to enable greater comparison between the different models.
 

### 2021-12-08 06-Chp-IPD-Analysis.Rmd
Deal with abbreviations, fix cross-links and some other small edits

@@
 The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
-In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the text and documentation sent to potential collaborators) in Autumn 2020.
+In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the correspondence sent to potential collaborators) in Autumn 2020.
 If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who had moved to a different institution.
@@
 Results between the common-set-adjusted (Model 1) and maximally-adjusted (Model 2) models were then compared.
+
+<!-- TODO May need to rethink this, as introducing model based on missing data which isn't fully discussed until later. -->
 
@@
 Based on available data across cohorts, smoking was classified as never/ever/current, while alcohol consumption was classified as never/ever.
-Education was categorised into 4 levels (None,O-levels,A-levels,Degree).
+Education was categorised into 4 levels (None, O-levels, A-levels, Degree).
 BMI was treated as a continuous variable while presence of vascular co-morbidities was treated as dichotomous.
@@
 <!----------------------------------------------------------------------------->
-(ref:mainEffectDem-cap) IPD meta-analysis (model 1) of all-cause dementia outcomes, stratified by lipid fraction
+(ref:mainEffectDem-cap) IPD meta-analysis (Model 1) of all-cause dementia outcomes, stratified by lipid fraction
 
@@
 <!----------------------------------------------------------------------------->
-(ref:mainEffectVad-cap) IPD meta-analysis (model 1) of vascular dementia outcomes, stratified by lipid fraction.
+(ref:mainEffectVad-cap) IPD meta-analysis (Model 1) of vascular dementia outcomes, stratified by lipid fraction.
 Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.

### 2021-12-08 08-Discussion.Rmd
Deal with abbreviations, fix cross-links and some other small edits

@@
 It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trial be performed to assess the effect of the proposed intervention.
-Given the costs and logistical challenges associated with trials examining outcomes with long prodomal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up (PTFU) of existing RCTs of lipid-regulating agents.
+Given the costs and logistical challenges associated with trials examining outcomes with long prodomal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up of existing RCTs of lipid-regulating agents.
 

### 2021-12-08 index.Rmd
Remove covering page and apply comma to wordcount

@@
 word-count: |
-  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last()`
+  `r read.csv("data/words/words.csv") %>% dplyr::pull(1) %>% dplyr::last() %>% comma()`
 abstract: |
@@
 #####################
-abstractseparate: true  # include front page w/ abstract for examination schools?
+abstractseparate: false  # include front page w/ abstract for examination schools?
 bib-humanities: false   #set to true if you want in-text references formatted as author-year

### 2021-12-09 01-Chp-Background.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (ApoE), is involved in cerebral cholesterol transport.
+The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (_Apo_$\mathcal{E}$), is involved in cerebral cholesterol transport.
 Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the ApoE gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _ApoE4_ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _ApoE4_ variants were intentionally excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}4$ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+This was supported by further MR studies where _Apo_$\mathcal{E}4$ variants were intentionally excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
 
@@
 
-I will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+I will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
@@
 To address this limitation, this thesis seeks to develop and apply a novel quantitative triangulation approach to answer causal questions on the effect of blood lipids on dementia outcomes.
-All existing evidence, regardless of study design, is first identified and assessed using domain-based tools by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+All existing evidence, regardless of study design, is first identified and assessed using domain-based tools by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 The existing evidence base is then supplemented by two primary analyses, presented in Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-heading).
@@
 -   **Chapter \@ref(sys-rev-tools-heading):** This chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
--   **Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading):** These chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
+-   **Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading):** These chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
 This review examined all available evidence on the effect of blood lipids and interventions that modified blood lipids on dementia outcomes.
@@
 
-The experience of extracting data for the systematic review in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) inspired a practical guide for researchers.
+The experience of extracting data for the systematic review in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) inspired a practical guide for researchers.
 This piece was co-written with Dr.
@@
 
-The tool used to visualise the risk-of-bias assessments in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) has been published in Research Synthesis Methods.
+The tool used to visualise the risk-of-bias assessments in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) has been published in Research Synthesis Methods.
 See Appendix \@ref(appendix-robvis) for more details on this tool.
@@
 
-_"RoB 2.0: A revised tool to assess risk of bias in randomized trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
+_"RoB 2.0: A revised tool to assess risk of bias in randomised trials"_: Webinar, co-presented with Dr. Theresa Moore as part of the Evidence Synthesis Ireland Methods Series.
 

### 2021-12-09 02-Chp-Systematic-Review-Tools.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 
-Searching these preprints as part of the systematic review described in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
+Searching these preprints as part of the systematic review described in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
 At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the complex searches containing Boolean logic operators (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search involved going through each record and downloading individual citations one-by-one.
@@
 
-In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading), `medrxivr` has other uses.
+In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading), `medrxivr` has other uses.
 
@@
 
--   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of key literature sources used in the comprehensive systematic review described in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+-   I have outlined the motivation for developing this tool in relation to this thesis - more specifically, that it was used to perform systematic and reproducible searches of key literature sources used in the comprehensive systematic review described in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 

### 2021-12-09 03-Chp-Systematic-Review-Methods.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 
-<!-- IDEA Stratify by _ApoE4_ genotype -->
+<!-- IDEA Stratify by _Apo_$\mathcal{E}4$ genotype -->
 
@@
 
-Eligible study designs were randomized controlled trials of LRA, cohort studies examining blood lipids or LRA, and genetic instrumental variable studies (more commonly known as Mendelian randomization studies) examining the effect of genetically increased/decreased blood lipid levels.
+Eligible study designs were randomised controlled trials of LRA, cohort studies examining blood lipids or LRA, and genetic instrumental variable studies (more commonly known as Mendelian randomisation studies) examining the effect of genetically increased/decreased blood lipid levels.
 
@@
 
-I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomized controlled trials.
+I also searched clinical trial registries, for example ClinicalTrials.gov, to identify relevant randomised controlled trials.
 In addition, I searched the bioRxiv and medRxiv preprint repositories using the tool developed in Chapter \@ref(sys-rev-tools-heading) to identify potentially relevant preprinted studies (see Appendix \@ref(appendix-medrxivr-code) for the code used to search these preprint repositories).
@@
 
-In line with best practice, where summary data were presented across two groups (e.g.
+In line with best practice, where summary data was presented across two groups (e.g.
 age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
@@
 
-* bias arising from the randomization process, 
+* bias arising from the randomisation process, 
 * bias due to deviations from intended intervention, 
@@
 
-At present, no formalised risk-of-bias assessment tool for Mendelian randomization studies is available.
-Assessment of the risk of bias in Mendelian randomization studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors.
+At present, no formalised risk-of-bias assessment tool for Mendelian randomisation studies is available.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors.
 A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.

### 2021-12-09 04-Chp-Systematic-Review-Results.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 
+<!-- TODO Consider adding a line to the descriptions of each forest plot regarding the direction - what's on the right, whats on the left -->
+
 ## Introduction
 
-Following the methods outlined in the previous chapter, here I present the results of the comprehensive systematic review.
+Following the methods outlined in the previous chapter, I present the results of the comprehensive systematic review here.
 The use of the evidence identified by the review in future chapters is discussed.
@@
 The database search identified `r num_to_text(23447)` records, of which `r comma(7338)` were duplicated records.
-Of the random sample of 500 records screened to ensure the accuracy of the study design filters, no eligible records were identified.
+To ensure the accuracy of the study design filters, a random sample of 500 records removed by the filters were screened, and no eligible records were identified.
 As expected, many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
@@
 
-Following de-duplication, the titles and abstracts of `r num_to_text(16109)` records were assessed for eligibility.
-`r num_to_text(387)` were deemed potentially eligible, and the full text records for these were accessed and screened.
+Following de-duplication, the titles and abstracts of `r comma(16109)` records were assessed for eligibility.
+Of these, `r comma(387)` were deemed potentially eligible.
+The full text records for these records were then accessed and screened.
 
-The PRISMA flow diagram <!-- TODO CITATION NEEDED - cite PRIMSA flow paper here, if published --> presented in Figure \@ref(fig:prisma-flow-fig) illustrates the movement of articles through the review.
+The PRISMA flow diagram presented in Figure \@ref(fig:prisma-flow-fig) illustrates the movement of articles through the review.
 To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described previously (presented in grey on the right of the diagram).
 
-Common reasons for exclusion at the full text-stage included studies reporting on ineligible exposures (N = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
-change in cognitive scores), or usin an ineligible study design (N = `r n_study_design`).
+Common reasons for exclusion at the full-text stage included studies reporting on ineligible exposures (Number of studies (N) = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
+change in cognitive scores), or the use of an ineligible study design (N = `r n_study_design`).
 
@@
 
-For the assessment of the intra-/inter-rater reliability, the estimated values of Gwet's $AC1$ were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the assessment of the intra-/inter-rater reliability, the estimated values of Gwet's agreement coefficinet, $AC1$, were interpreted against the categories presented in Table \@ref(tab:gwet-table).
 For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
@@
 The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS), leading to complications in the synthesis (see Section \@ref(sys-rev-res-AD)).
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS), leading to complications in the synthesis of these estimates due to the potential for double-counting (see Section \@ref(sys-rev-res-AD)).
 
@@
 
-As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most high represented region being North America.
+As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most highly represented region being North America.
 Of interest, several of the included studies were conducted in Taiwan (`r n_taiwan`), all but one of which made use of the Taiwan National Health Insurance database.
@@
 
-In the following sections, analyses are grouped first by outcome (all-cause dementia, Alzheimer's disease and vascular dementia) and then are further stratified by exposure category.
-
-&nbsp;<!----------------------------------------------------------------------->
-
-### All-cause dementia {#sys-rev-res-Dementia}
-
-#### Statins
+In the following sections, analyses are grouped first by outcome (all-cause dementia, Alzheimer's disease and vascular dementia) and are then further stratified by exposure category (lipids, lipid regulating agents).
 
@@
 
-The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-
-(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statin statins on all-cause dementia.
-D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond in each forest plot presented above.
-
-(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
-```
-
 &nbsp;<!----------------------------------------------------------------------->
 
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
-
-(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
-This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
-
-&nbsp; <!---------------------------------------------------------------------->
-
-#### Fibrates
-
-`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
-
-<!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
-
-(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
-
-```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
-```
-<!----------------------------------------------------------------------------->
+### All-cause dementia {#sys-rev-res-Dementia}
 
@@
 
-### Alzheimer's disease {#sys-rev-res-AD}
-
 #### Statins
 
-There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
+The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
 
 <!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
 
-(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
+(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statins on all-cause dementia.
+D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond in each forest plot presented above.
 
-```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
+(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
+
+```{r rctStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:statinsRCT-cap)', out.width='100%', fig.scap='(ref:statinsRCT-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_rct_statins_Dementia.png"))
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+
+(ref:obsStatinDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
+
+```{r obsStatinDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinDementia-cap)', out.width='100%', fig.scap='(ref:obsStatinDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_Dementia.png"))
 ```
@@
 
-Two Mendelian randomisation studies looked at lipid-lowering specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the Global Lipids Genetic Consortium (SNP-exposure) and the International Genomics of Alzheimer's Project (SNP-outcome).
-Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
+Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
+This analysis provided weak evidence of an effect (`r mrStatin$Dementia$estimate`).
+
+&nbsp; <!---------------------------------------------------------------------->
+
+#### Fibrates
+
+`r num_to_text(obsFibrates$Dementia$n,T)` studies examined the effect of fibrate use on all-cause dementia and found weak evidence for an effect (`r obsFibrates$Dementia$estimate`, Figure \@ref(fig:obsFibrateDementiaFig)).
 
 <!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
 
-(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
 
-```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
+```{r obsFibrateDementiaFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsFibrateDementia-cap)', out.width='100%', fig.scap='(ref:obsFibrateDementia-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Fibrate_Dementia.png"))
 ```
@@
 
-&nbsp;
+### Alzheimer's disease {#sys-rev-res-AD}
 
@@
 Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
-However, all of these studies took a two-sample approach, making use of summary statistics from the GLGC and IGAP consortia.
-Due to this overlap, which would result in a falsely precise estimate caused by multiple counting of the same participants, no meta-analysis of these studies was performed.
+However, all of these studies took a two-sample approach, making use of summary statistics from the Global Lipid Genetics Consortium (GLGC) and International Genomics of Alzheimer's Project (IGAP) consortia.
+Synthesis of these results would would result in a falsely precise estimate caused by multiple counting of the same participants,and as a result, no meta-analysis of these studies was performed.
+
 However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
@@
 
+#### Statins
+
+There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+
+(ref:obsStatinAD-scap) Random-effects meta-analysis of statins on Alzheimer's disease
+
+```{r obsStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinAD-cap)', out.width='100%', fig.scap='(ref:obsStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Two Mendelian randomisation studies looked at lipid-lowering specifically as a result of HMGCR inhibition, mediated by SNPs in the gene (rs172338484 and rs12916).`r mrStatin$AD$citations` The first used a one sample approach (SNP-exposure and SNP-outcome associations are estimated using the same dataset) in a large Copenhagen-based cohort, while the second made use of summary level data obtained from the GLGC (SNP-exposure) and the IGAP (SNP-outcome).
+Meta-analysis of these estimates provided weak evidence of an effect (`r mrStatin$AD$estimate`, Figure \@ref(fig:mrStatinADFig)).
+
+<!----------------------------------------------------------------------------->
+(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+
+```{r mrStatinADFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:mrStatinAD-cap)', out.width='100%', fig.scap='(ref:mrStatinAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_MR_HMGCR_AD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 ### Vascular dementia {#sys-rev-res-VaD}
+
+#### Lipids
+
+`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+
+<!----------------------------------------------------------------------------->
+(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+
+(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
+
+```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Few studies investigated the effect of individual lipid fractions.
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+A single study provided evidence on the other three fractions,[@yoshitake1995] and similarly found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL,F)`), HDL-c (`r n_effect(obsLipids$VaD_HDL,F)`) or triglycerides (`r n_effect(obsLipids$VaD_TG,F)`).
+
+<!-- TODO This is not technically - more studies available on vascular dementia -->
+
+<!----------------------------------------------------------------------------->
+(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+
+(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
+
+```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
+```
+<!----------------------------------------------------------------------------->
+
+Finally, no Mendelian randomisation analyses examining the effect of genetically determined lipid levels on vascular dementia risk were identified.
+
+&nbsp;
 
@@
 
-A single Mendelian randomisation analysis was identified that examining the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided some evidence for an effect (`r mrStatin$VaD$estimate`).
+A single Mendelian randomisation analysis was identified that examined the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided some evidence for an effect (`r mrStatin$VaD$estimate`).
 
@@
 &nbsp;<!----------------------------------------------------------------------->
-
-#### Lipids
-
-`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
-
-<!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
-
-(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
-
-```{r obsHyperVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsHyperVaD-cap)', out.width='100%', fig.scap='(ref:obsHyperVaD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_hyperchol_VaD.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
-A single study provided evidence on the other three fractions,[@yoshitake1995] and similar found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL,F)`), HDL-c (`r n_effect(obsLipids$VaD_HDL,F)`) or triglycerides (`r n_effect(obsLipids$VaD_TG,F)`).
-
-<!-- TODO This is not technically - more studies available on vascular dementia -->
-
-<!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
-
-(ref:lipidFractionsVaD-scap) Random-effects meta-analysis of total cholesterol on vascular dementia
-
-```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
-knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
-```
-<!----------------------------------------------------------------------------->
-
-Finally, no Mendelian randomisation analyses examining the effect of genetically determined lipid levels on vascular dementia risk were identified.
-
-&nbsp;
 
@@
 As shown in the forest plots in the above sections, the risk-of-bias assessments are presented alongside their corresponding numerical result.
-A more detailed discussion of the sources and directions of bias in each result is presented in Chapter \@ref(tri-heading), and so this section presents a brief summary of the biases observed in each study design.
+This section presents only a brief summary of the biases observed in each study design, as s detailed discussion of the sources and directions of bias in each result is presented in Chapter \@ref(tri-heading).
 
@@
 
-Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analyses.[@sterne2016] `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
+Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analysis.[@sterne2016] `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
 the study reported unadjusted estimates).`r critical_citations`
@@
 There were `r n_dr_initial` studies initially considered eligible for the dose-response meta-analysis, as they appear to provide data on risk of dementia outcomes across several categories of lipid exposure.
-However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not reported the relevant information needed (most commonly, the cut-off measures for each category).
+However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not report the relevant information needed (most commonly, the cut-off measures for each category).
 
@@
 
+<!-- TODO Reword the above section to make it clearer -->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-<!-- &nbsp; -->
-
-<!----------------------------------------------------------------------------->
-<!-- (ref:preprintWeights-caption) Amount of information added by inclusion of preprinted results, estimated from the weight assigned to the study in a random-effect meta-analysis  -->
-
-<!-- (ref:preprintWeights-scaption) Added information due to inclusion of preprints -->
-
-<!-- ```{r preprintWeights-table, message=FALSE, results="asis", echo = FALSE} -->
-<!-- ``` -->
-<!----------------------------------------------------------------------------->
-
-<!-- TODO Add extra column with details of Figure showing met-analysis -->
-
-<!-- &nbsp; -->
-
-Investigation of the publication status of the two preprints reporting studies not also identified by the main search found that, allowing for a two-year lag, only one had been subsequently published.[@andrews2019; @andrews2021]
+For one of the three preprints identified, the published version of the preprint was captured by the main search.
+Investigation of the publication status of the two unpublished preprints found that, allowing for a two-year lag (i.e.
+up to July 2021), only one had been subsequently published.[@andrews2019; @andrews2021]
 
@@
 
-There was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia when looking at solely at observational studies.
+There was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia when looking solely at observational studies.
 This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of differing exposure windows (e.g.
@@
 This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the follow-up made necessary by the long latent period of the condition makes trials logistically difficult and financial expensive.
+Randomised controlled trials of dementia are particularly challenging, as the follow-up made necessary by the long latent period of the condition makes trials logistically difficult and financially expensive.
 Similarly, Mendelian randomisation is a comparatively new study design, and studies employing it in relation to dementia outcomes only appear in the evidence base in recent years, as illustrated in Figure \@ref(fig:typeByYear).
@@
 Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of lipid levels.
-In many cases, estimates are known to be missing not at random from meta-analyses due to preferential reporting of significant results, leading to high risk of bias due to missing evidence.
-These missing estimates were most commonly identified via analysis of conference abstract/final publication pairs.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
+In many cases, estimates were known to be missing from meta-analyses due to preferential reporting of significant results, leading to high risk of bias due to missing evidence.
+These missing estimates were most commonly identified through differing descriptions of the same analysis in conference abstract versus the final publication.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
 "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
 were not reported in the table."[@ancelin2013]).
-However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence for an effect), other than increasing the precision of the summary estimate.
+However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence of an effect), other than increasing the precision of the summary estimate.
 
-Finally in terms of generalisability, despite a large proportion of included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of several studies which made use of data from the Taiwan health insurance database.
+Finally in terms of generalisability, despite a large proportion of the included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of several studies which made use of data from the Taiwan health insurance database.
 
@@
 
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomized controlled trials)[@sterne2019] to assess the risk of bias in included studies.
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomised controlled trials)[@sterne2019] to assess the risk of bias in included studies.
 The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
@@
 I identified one previous review of Mendelian randomisation studies examining risk factors for Alzheimer's disease.
-However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published and extracted results including SNPs in the _ApoE4_ genetic region (see the following section for a discussion of the bias this introduces).
+However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published.
+In addition this previous review extracted the results of analyses which did not account for SNPs in the _Apo_$\mathcal{E}4$ genetic region (see the following section for a discussion of the bias this introduces).
 
@@
 In retrospect, an alternative approach to conducting a further systematic review from scratch, known as an umbrella review or review-of-reviews,[@aromataris2015; @smith2011] could have been employed.
-This study design uses other systematic reviews rather than primary studies as the unit of analysis, and would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart could have been applied.
+This study design uses other systematic reviews rather than primary studies as the unit of analysis.
+Furthermore, it would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart could have been applied.
 
@@
 
-Mendelian randomisation is a powerful analytical technique, using natural variation in participants genomes to identify causal links between a genetically determined risk factor and an outcome, given that the three core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
-These assumptions are namely that: i) the genetic variant associates with the risk factor of interest (relevance assumption); ii) the variant-exposure association has no unmeasured confounders (independence assumption); and the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption).
-However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
+Mendelian randomisation is a powerful analytical technique, using natural variation in participants' genomes to identify causal links between a genetically determined risk factor and an outcome, given that the three core assumptions detailed in Figure \@ref(fig:mrAssumptions) are valid.
+These assumptions are namely that:
+
+* the genetic variant associates with the risk factor of interest (relevance assumption);
+* the variant-exposure association has no unmeasured confounders (independence assumption);
+* the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption).
 
@@
 
+However, inclusion of Mendelian randomisation as an acceptable study design in this review was complicated by a number of factors.
 Firstly, this study design is relatively new, particularly when compared to randomised trials or cohort studies.
@@
 Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] Reporting quality is an important consideration for Mendelian randomisation studies, as reflected by the recent release of a STROBE MR reporting guidelines,[@skrivankova2021] but is a separate consideration to bias, as discussed in Section \@ref(risk-of-bias).
+While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] Reporting quality is an important consideration for Mendelian randomisation studies, as reflected by the recent release of the STROBE MR reporting guidelines,[@skrivankova2021] but it is a separate consideration to bias, as discussed in Section \@ref(risk-of-bias).
 Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was designed to assess the quality of GWAS included in a meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not address the additional methodological considerations of the Mendelian randomisation analysis itself.
@@
 As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been captured by the search strategy.[@larsson2017] This study examined lipid fractions as one of many risk factors for Alzheimer's disease, though the search would not have been expected to find it given the absence of any lipid-related keywords in the title or abstract.
-Studies examining multiple risk factors such as this can introduce bias into a systematic review, as it is commonly only those risk factors with statistically significant result that are reported in the abstract and so are captured by a systematic search.
+Studies examining multiple risk factors such as this can introduce bias into a systematic review, as it is commonly only those risk factors with a statistically significant result that are reported in the abstract and so are captured by a systematic search.
 These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are considered to be particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
@@
 This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (N = `r comma(16109)`).
-Additionally, the value of methods that support traditional bibliographic database search, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts, should not be underestimated.
+Additionally, the value of methods that support traditional bibliographic database searches, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts, should not be underestimated.
 Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit.
 
-One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the _ApoE4_ gene region.
-As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of _ApoE4_ alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
-In all cases, excluding variants in the _ApoE_ region attenuates the observed effect to the null.
-A clear example of this is Benn _et al_ (2017), where _ApoE_ variants were not sufficient identified and excluded, leading the published paper to report a protective effect of LDL-c on Alzheimer's (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed to exclude a larger area around _ApoE_ which attenuated the finding to the null.[@benn2017comment]
+One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the _Apo_$\mathcal{E}4$ gene region.
+As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of _Apo_$\mathcal{E}4$ alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
+In all cases, excluding variants in the _Apo_$\mathcal{E}$ region attenuates the observed effect to the null.
+A clear example of this is Benn _et al_ (2017), where _Apo_$\mathcal{E}$ variants were not sufficiently identified and excluded, leading the published paper to report a protective effect of LDL-c on Alzheimer's (`r estimate(0.83, .75,.92,"RR")`).[@benn2017] Following several rapid responses, the data was re-analysed to exclude a larger area around _Apo_$\mathcal{E}$ which attenuated the finding to the null.[@benn2017comment]
 
@@
 
-As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize evidence across different publication statuses (preprinted vs.
+As highlighted in Section \@ref(diverse-sources-preprints), this review explicitly sought to synthesize all available evidence, irrespective of publication status (preprinted vs.
 published).
@@
 (ref:preprintGrowth-cap) Growth of preprint repositories over time.
-Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv n = `r n_at_search["med"]`), the number of hits returned by each is expected.
+Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv N = `r n_at_search["med"]`), the number of hits returned by each is expected.
 
@@
 However, the scale of this contribution is questionable.
-Preprinted evidence was incorporated into only single meta-analysis in this review, and inclusion of the preprinted result did not substantially impact the summary effect estimate.
+Preprinted evidence was incorporated into only a single meta-analysis in this review, and inclusion of the preprinted result did not substantially impact the summary effect estimate.
 
@@
 This limitation was compounded by the expected low response rate to requests for further information from primary authors.
-While contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] a far preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
+Contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] though a preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
 
-Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as an case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
+Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as a case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
 In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers, via a GitHub repository.
@@
 
-I believe there are several aspects where this review is distinct from those already available in the published literature.
+There are several aspects where this review is distinct from those already available in the published literature.
 While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not complete.
-As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no relevant study has been omitted.
+As part of this review, I have not only performed an original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no relevant study has been omitted.
 
@@
 
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity.[@hsieh2019; @mcguinness2019validity; @wilkinson2018] Relatedly, several  studies which made use of electronic health record database did not report the specific code lists used, potentially introducing substantial heterogeneity into the analysis.
-An empirical example of the effect of differing EHR code list is presented as part of the analysis in Chapter \@ref(cprd-analysis-heading) (see Section \@ref(comparing-codelists)).
+The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity.[@hsieh2019; @mcguinness2019validity; @wilkinson2018] Relatedly, several studies which made use of electronic health record databases did not report the specific code lists used, potentially introducing substantial heterogeneity into the analysis.
+An empirical example of the effect of differing EHR code lists is presented as part of the analysis in Chapter \@ref(cprd-analysis-heading) (see Section \@ref(comparing-codelists)).
 
 In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
-However,  evidence from assessments of inter- and intra-rater reliability indicate that is not a major concern.
+However,  evidence from assessments of inter- and intra-rater reliability indicate that this is not a major concern.
 
@@
 
-* The findings from this review are used though out the subsequent chapters: in Chapter \@ref(cprd-analysis-heading), summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias and provided evidence on an under-studied outcome (vascular dementia); while in Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data; finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
+* The findings from this review are used throughout the subsequent chapters.
+In Chapter \@ref(cprd-analysis-heading), this summary of the evidence guided the choice of analysis approach, ensuring that the new analysis was at risk of a different source of bias and provided evidence on an under-studied outcome (vascular dementia).
+In Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data.
+Finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
 

### 2021-12-09 05-Chp-CPRD-Analysis.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 output:
+  bookdown::pdf_document2:
+    template: templates/brief_template.tex
+    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
   bookdown::word_document2: 
@@
       number_sections: false 
-  bookdown::pdf_document2:
-    template: templates/brief_template.tex
-    pandoc_args: !expr rmdfiltr::add_wordcount_filter()  
   bookdown::html_document2: default
@@
 In this chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
-The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 
@@
 
-Participants were ineligible for our cohort if they were less than 40 years of age (as these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+Participants were ineligible for the cohort if they were less than 40 years of age (as these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
 had less than one full day of follow-up).
@@
 
-In this analysis, missing data were handled using a multiple imputation approach.[@sterne2009] Variables with missing observations were identified for inclusion in the imputation model.
+In this analysis, missing data was handled using a multiple imputation approach.[@sterne2009] Variables with missing observations were identified for inclusion in the imputation model.
 Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
@@
 
-Missing data were only considered problematic for variables where a numerical test result was expected (e.g.
+Missing data was only considered problematic for variables where a numerical test result was expected (e.g.
 BMI), or where a code existed for the absence of the condition (e.g.
@@
 A substantial majority (`r percentage.statins`) of participants prescribed a lipid-regulating agent were prescribed a statin.
-I excluded the "Ezetimibe and statins" (n=`r eze_sta_n`) and "Nicotinic acid groups" (n= `r nag_n`) classes from subsequent class-based subgroup analyses based on the extremely small number of participants in these groups.
+I excluded the "Ezetimibe and statins" (N =`r eze_sta_n`) and "Nicotinic acid groups" (N = `r nag_n`) classes from subsequent class-based subgroup analyses based on the extremely small number of participants in these groups.
 Note that the "Ezetimibe and statins" treatment group represent those prescribed a single treatment containing both ezetimibe and statins, rather than those where the two treatments were prescribed concurrently.
@@
 
-For the composite all-cause dementia outcome, we found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), which lies between the associations for the Alzheimer and non-Alzheimer dementia outcomes as would be expected.
+For the composite all-cause dementia outcome, I found treatment with a lipid-regulating agent was associated with a slightly increased risk (`r anydem_text`), which lies between the associations for the Alzheimer and non-Alzheimer dementia outcomes as would be expected.
 There was also some evidence that fibrates were associated with increased risk of all-cause dementia (`r anydem_fib_text`).
@@
 AD vs non-AD dementia).
-This different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why our analysis obtained different results despite the substantial overlap in the data sources used.
+This different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why my analysis obtained different results despite the substantial overlap in the data sources used.
 
@@
 A further limitation stems from the possibility of uncontrolled confounding due to genetic factors.
-The number of _ApoE_ $\epsilon4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
-I was unable to control for _ApoE_ genotype in this analysis as I did not have access to genetic data on participants.
-As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by ApoE.
+The number of _Apo_$\mathcal{E}4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
+I was unable to control for _Apo_$\mathcal{E}$ genotype in this analysis as I did not have access to genetic data on participants.
+As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by _Apo_$\mathcal{E}$.
 

### 2021-12-09 06-Chp-IPD-Analysis.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
 However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
@@
 
-The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+The first approach focused on previously analysed observational prospective cohort studies examining the effect of blood lipid levels on dementia outcomes, as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
@@
 A range of additional variables were included in the analysis, intended to address the potential for confounding.
-With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _ApoE4_ status, smoking/alcohol status, ethnicity, and prevalent cardiovascular disease.
+With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _Apo_$\mathcal{E}4$ status, smoking/alcohol status, ethnicity, and prevalent cardiovascular disease.
 This set covers key risk factors for dementia/Alzheimer's disease in addition to general cardiovascular risk factors.
@@
 With respect to the application to DPUK cohorts, where a dedicated project manager liaises with data owners on the applicants' behalf, the overall response rate was higher.
-However, even using this streamlined approach, a positive response was obtained for approximately half (N=9, 53%) of the approached cohorts.
+However, even using this streamlined approach, a positive response was obtained for approximately half (N =9, 53%) of the approached cohorts.
 
@@
 The Caerphilly Prospective Study (CaPS) is a longitudinal study of men in South Wales, UK.[@zotero-15398;@elwood2013] Blood lipids (TC, LDL-c, HDL-c and TG) were measured at baseline in 1979-1983, and from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
+A dementia was derived using data obtained during Phase V (2002-2004), giving between 19-25 years of follow-up.
 The cohort contains data on dementia outcomes sub-classified as vascular and non-vascular dementia.
-Data was available for all covariates of interest except for education, BMI and _ApoE4_ status.
+Data was available for all covariates of interest except for education, BMI and _Apo_$\mathcal{E}4$ status.
 
@@
 
-The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] The added evidential value of the EPIC cohort is small, given the the fact that the data obtained contains only 8 dementia events.
-The cohort contains no information on dementia subtype, while all covariates of interest bar _ApoE4_ were available.
+The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] Data provided by this cohort for the analysis, dementia was ascertained at at the 5th Health Checkup (2016-2018), giving between 18-25 years of follow-up.
+The added evidential value of the EPIC cohort is small, given the the fact that the data obtained contains only 8 dementia events.
+The cohort contains no information on dementia subtype, while all covariates of interest bar _Apo_$\mathcal{E}4$ were available.
 
@@
 
-The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
-This data source contained details on all covariates of interest except for _ApoE4_ status.
+The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] Lipids measurements were available from the third wave of the study, conducted between 1991-1993.
+The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] HES data for dementia outcomes was avaialle up to March 2015, providing between 22-24 years of follow-up.
+Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
+This data source contained details on all covariates of interest except for _Apo_$\mathcal{E}4$ status.
 
-Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
+Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
 
@@
 The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity.
-No included cohort provided information on the _ApoE4_ status of participants, and so this variable could not be adjusted for in the analysis.
+No included cohort provided information on the _Apo_$\mathcal{E}4$ status of participants, and so this variable could not be adjusted for in the analysis.
 
@@
 The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
-There was very weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
+There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
 
@@
 No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia.
-Similarly, there was very weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
+Similarly, there was weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
 
-A detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)), is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
+A detailed comparison of the findings presented above with the existing evidence base identified by the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)), is presented as part of the triangulation exercise in Chapter \@ref(tri-heading).
 As such, this discussion will not provide a detailed comparison of the results of this analysis with other published literature, except to compare between this analysis and previously published results using the same data source.
@@
 A key limitation of this analysis is the potential for uncontrolled confounding.
-Across all cohorts, adjustment for _ApoE4_ was not possible as I did not have access to genetic data on participants.
-_ApoE4_ is a strong risk factor for both increased LDL-c levels and Alzheimer's disease,[@bennet2007;@safieh2019] and failing to adjust for this factor means residual confounding in the LDL-c fraction results is likely.
+Across all cohorts, adjustment for _Apo_$\mathcal{E}4$ was not possible as I did not have access to genetic data on participants.
+_Apo_$\mathcal{E}4$ is a strong risk factor for both increased LDL-c levels and Alzheimer's disease,[@bennet2007;@safieh2019] and failing to adjust for this factor means residual confounding in the LDL-c fraction results is likely.
 
@@
 
-Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (n=287 in this analysis vs.
+Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (N =287 in this analysis vs.
 n=114 in Tynkkynen _et al._).
-The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _ApoE4_ status.
-However, given that _ApoE4_ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
+The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _Apo_$\mathcal{E}4$ status.
+However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
 
@@
 
-Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading).
+Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 This is relevant even in the previously analysed WhiteHall II cohort, as the previous analysis by Tynkkynen _et al._ did not report on this outcome.
@@
 
-- I found very weak evidence for an association of any lipid with either all-cause or vascular dementia, except for an increased risk of vascular dementia associated with raised triglycerides.
-Similarly, there was very weak evidence that the association of blood lipids and dementia outcomes varied by participant age or sex.
+- I found weak evidence for an association of any lipid with either all-cause or vascular dementia, except for an increased risk of vascular dementia associated with raised triglycerides.
+Similarly, there was weak evidence that the association of blood lipids and dementia outcomes varied by participant age or sex.
 

### 2021-12-09 07-Chp-Triangulation.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 
-Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
+Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
 Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
@@
 <!-- TODO Note that the results are converted to the log scale. -->
+
+<!-- TODO The results should be standarised before calculating direction of effect, because other-wise it is pulling it in the wrong direction -->
 
@@
 For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
-In Domain 1 (bias due to confounding), the study did not adjust for _ApoE4_ status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
+In Domain 1 (bias due to confounding), the study did not adjust for _Apo_$\mathcal{E}4$ status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
 As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right.
@@
 From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest.
-Most (n=17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate from the CPRD analysis.
+Most (N =17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate from the CPRD analysis.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
@@
 
+<!-- TODO This needs to have the heterogeneity values too -->
+
 (ref:fpLdlAd-cap) Random effects meta-analysis of the association of midlife LDL-c with Alzheimer's disease, using unadjusted and bias-/indirectness-adjusted results.
@@
 <!-- TODO Need to present overall summary estimate under two scenarios of bias and then send people to the Appendix. -->
+
+<!-- TODO There is a very slight effect in the unadjusted here, but reduces to blah blah on adjustmet -->
 
@@
 However, the prior distributions defined here are broadly comparable to previously reported estimates of the impact of bias in non-randomised trials.
-For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, _ApoE4_ would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior distribution mapped to "Moderate" additive bias (N(0.08,0.05), Table \@ref(tab:priorsAdd-table)).
+For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, _Apo_$\mathcal{E}4$ would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior log-normal distribution mapped to "Moderate" additive bias ($N(0.09,0.05)$, Table \@ref(tab:priorsAdd-table)).
 

### 2021-12-09 08-Discussion.Rmd
Range of small fixes (randomised, ApoE, etc)

@@
 The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup.
-These results are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by ApoE4, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
+These results are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by _Apo_$\mathcal{E}4$, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
 The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes, comparable to the results of this thesis.
-However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _ApoE4_ genotype.
+However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _Apo_$\mathcal{E}4$ genotype.
 
@@
 Thirdly, missing evidence was a common limitation across this thesis.
-In Chapters \@ref(sys-rev-methods-heading)/\@ref(sys-rev-results-heading), several studies stated that they did not report the results of an analysis because the results were not significant.
+In Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading), several studies stated that they did not report the results of an analysis because the results were not significant.
 This was particularly common among non-randomised studies of exposure examining blood lipids directly.
@@
 In addition, it has developed new methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources, which will enable future evidence synthesists to better address important causal questions.
-
-\newpage

### 2021-12-09 front-and-back-matter/99-appendices.Rmd
Fix broken cross-links
End of day:

@@
 
-## Chapter \@ref(background-heading) {#appendix-into}
+## Chapter 1 {#appendix-into}
 
@@
 
-__Peer reviewed__
+In addition to publications arising directly from this thesis (described in Section \@ref(literature-contributions) & included in Appendix \@ref(published-papers)), I have been involved in a number of external research projects.
+Taken together, these additional projects provided extensive experience in evidence synthesis methods and in collaborating across large teams.
 
-  * PRISMA main paper
+During 2020, I was involved in the updating of the Preferred Reporting Items for Systematic reviews and Meta-Analyses (PRISMA) statement.
+My contributions were focused on the data sharing aspects of the guidelines and on building an interactive web application that would allow users to complete the PRISMA checklist.
+Publications arising from this work are listed below:
 
-  * PRISMA E&E
+*	*Page, M.J., Moher, D., Bossuyt, P., Boutron, I., Hoffmann, T., Mulrow, C., Shamseer, L., Tetzlaff, J., Akl, E., Brennan, S.E., Chou, R., Glanville, J., Grimshaw, J., Hróbjartsson, A., Lalu, M.M., Li, T., Loder, E., Mayo-Wilson, E., McDonald, S., __McGuinness, L.A.__, Stewart, L., Thomas, J., Tricco, A., Welch, V.A., Whiting, P., McKenzie, J.
+(2021).
+PRISMA 2020 statement: updated guidelines for reporting systematic reviews and meta-analyses.
+BMJ 372:n71 [10.1136/bmj.n71](https://doi.org/10.1136/bmj.n71)*
 
-  * PRISMA 2020 software
+*	*Page, M.J., Moher, D., Bossuyt, P., Boutron, I., Hoffmann, T., Mulrow, C., Shamseer, L., Tetzlaff, J., Akl, E., Brennan, S.E., Chou, R., Glanville, J., Grimshaw, J., Hróbjartsson, A., Lalu, M.M., Li, T., Loder, E., Mayo-Wilson, E., McDonald, S., __McGuinness, L.A.__, Stewart, L., Thomas, J., Tricco, A., Welch, V.A., Whiting, P., McKenzie, J.
+(2021).
+PRISMA 2020 explanation and elaboration: updated guidance and exemplars for reporting systematic reviews.
+BMJ 372:n160.
+DOI: [10.1136/bmj.n160](https://doi.org/10.1136/bmj.n160)*
 
-  * COVID Suicide Living Review
+* *Haddaway, N.
+R., Page, M.
+J., Pritchard, C.
+C., & McGuinness, L.
+A.
+(2021).
+PRISMA2020: An R package and Shiny app for producing PRISMA 2020-compliant flow diagrams, with interactivity for optimised digital transparency and Open Synthesis.
+MedRxiv, DOI: [10.1101/2021.07.14.21260492](https://doi.org/10.1101/2021.07.14.21260492)*
 
-  * Data extraction tools systematic review
+&nbsp;
 
-<!-- TODO update list with proper references and a description of each. Essentially, look at the Trello -->
+In response to the COVID-19 pandemic, I worked with a team of evidence synthesists to develop a literature searching/screening pipeline.
+This work underpinned a living systematic review on impact of the COVID-19 pandemic on self-harm and suicidal behaviour.
+Subsequently, the pipeline enabled rapid reviews of related topics, such as an analysis of the available evidence by population.
 
-__Under review/Preprints__
+*	*John, A., Okolie, C., Eyles, E., Webb, R.T., Schmidt, L., __McGuinness, L.A.__, Olorisade, B.K., Arensman, E., Hawton, K., Kapur, N.
+and Moran, P., 2020.
+The impact of the COVID-19 pandemic on self-harm and suicidal behaviour: a living systematic review.
+F1000Research, 9(1097).
+DOI: &nbsp; [10.12688/f1000research.25522.2](https://doi.org/10.12688/f1000research.25522.2)*
 
-  * MSc Paper on systematic reviews of this thesis topic
+*	*John, A., Eyles, E., __McGuinness, L.A.__, Okolie, C., Olorisade, B.K., Schmidt, L., Webb, R.T., Arensman, E., Hawton, K., Kapur, N.
+and Moran, P., 2020.
+The impact of the COVID-19 pandemic on self-harm and suicidal behaviour: protocol for a living systematic review.
+F1000Research, 9(644), p.644.
+DOI: [10.12688/f1000research.24274.1](https://doi.org/10.12688/f1000research.24274.1)*
 
-  *
+* *Eyles, E., Moran, P., Okolie, C., Dekel, D., Macleod-Hall, C., Webb, R.
+T., Schmidt, L., Knipe, D., Sinyor, M., __McGuinness, L.
+A.__, Arensman, E., Hawton, K., O’Connor, R.
+C., Kapur, N., O’Neill, S., Olorisade, B., Cheng, H.-Y., Higgins, J.
+P.
+T., John, A., & Gunnell, D.
+(2021).
+Systematic review of the impact of the COVID-19 pandemic on suicidal behaviour amongst health and social care workers across the world.
+Journal of Affective Disorders Reports, 6, 100271.
+DOI: [10.1016/j.jadr.2021.100271](https://doi.org/10.1016/j.jadr.2021.100271)*
 
-### Involvement of patients and the public {#appendix-ppi}
+&nbsp;
 
-Patients were involved at several stages of this research. when designing the PhD programme of work, a Patient and Public Advisory Group (PPAG) provided feedback on the relevance of the question.
+Finally, I have acted as part of a large review team for a number of other evidence synthesis exercises:
 
-Additionally,
+*	*Grant, M.
+C., Geoghegan, L., Arbyn, M., Mohammed, Z., __McGuinness, L.A.__, Clarke, E.
+L., & Wade, R.
+(2020).
+The Prevalence of Symptoms in 24,410 Adults Infected by the Novel Coronavirus (SARS-CoV-2; COVID-19): A Systematic Review and Meta-Analysis of 148 Studies from 9 Countries.
+PLOS ONE.
+DOI: [10.1371/journal.pone.0234765](https://doi.org/10.1371/journal.pone.0234765)*
 
-Lay summaries appear at the beginning of each chapter, reviewed by the Patient and Public Involvement panel. They provide a plain language summary
+* *Cheng, H.Y., __McGuinness, L.A.__, Elbers, R.G., MacArthur, G.J., Taylor, A., McAleenan, A., Dawson, S., López-López, J.A., Higgins, J.P., Cowlishaw, S.
+and Lingford-Hughes, A.
+(2020).
+Treatment interventions to maintain abstinence from alcohol in primary care: systematic review and network meta-analysis.
+BMJ, 371.
+DOI: [10.1136/bmj.m3934](https://doi.org/10.1136/bmj.m3934)*
 
-## Chapter \@ref(sys-rev-tools-heading) {#appendix-sys-rev-tools}
+*	*Schmidt, L., Olorisade, B.K., __McGuinness, L.A.__, Thomas, J.
+and Higgins, J.P.
+(2020).
+Data extraction methods for systematic review (semi) automation.
+F1000Research, 10:401.
+DOI: &nbsp; [10.12688/f1000research.51117.1](https://doi.org/10.12688/f1000research.51117.1)*
 
-### Code for publication rate analysis
+&nbsp;<!----------------------------------------------------------------------->
+
+## Chapter 2 {#appendix-sys-rev-tools}
+
+### Code for publication rate analysis {#appendix-tools-pub}
+
+medRxiv automatically links preprints to their published counterparts, and provides the DOI of the published article as part of the metadata on a given preprint.
+Using `medrxivr` to access this data, I could assess the two-year publication rate of preprints originally posted to medRxiv in July 2019.
+The code used for this analysis is presented below:
+
+&nbsp;
 
 ```{r, eval=FALSE}
-med_res <-
+# Load relevant packages
+library(medrxivr)
+library(dplyr)
+
 # Use snapshot of published status from July 2021
-  medrxivr::mx_search(
-    medrxivr::mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
+  mx_search(
+    mx_snapshot("ccedfb8a44304b9fba4e3ba518a8ce4ed2294770"),
     query = "*",
+    # Limit to those 129 records published in July 2019
     from_date = "2019-07-01",
@@
   ) %>%
+
 # Create indicator to show which records have been published
-  mutate(pub_ind = ifelse(published == "NA", 0, 1)) %>%
-  # Group by indicator variable and count
-  group_by(pub_ind) %>%
-  count()
+  mutate(Status = ifelse(published == "NA",
+                          "Not published",
+                          "Published")) %>%
 
+# Group by indicator variable ("Published"/"Not published")
+  group_by(Status) %>%
+
+# Get total number per group, and percentage of total (N=129)
+  summarise(N = n(),
+            Percent = comma(n() / 129 * 100)) 
 ```
 
-## Chapter \@ref(sys-rev-methods-heading) {#appendix-sys-rev}
+&nbsp;
 
-### Deviations from protocol
+As shown in Table \@ref(tab:medRes-table), two-thirds of preprints were published within two years of their submission to medRxiv.
 
-<!-- TODO Complete -->
+&nbsp;
 
-* MR tool, actually used Mamluk
+<!----------------------------------------------------------------------------->
+(ref:medRes-caption) Publication status of medRxiv preprints deposited in July 2019, allowing for a two-year lag
 
-* ROB-ME
+(ref:medRes-scaption) Publication status of medRxiv preprints
 
-* No MCI, given size of dementia findings
+```{r medRes-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
 
-* Sources of funding: Given that any bias introduced by sources of funding would operate , conflicts of interest and bias were considered separate things here.[@sterne2013]
+&nbsp;
 
- * Dose response
+## Chapter 3 {#appendix-sys-rev}
 
-### Web of Science Databases Searched {#appendix-wos-databases}
+### Deviations from protocol {#appendix-sys-rev-deviations}
+
+There were a number of deviations from the pre-registered protocol for the systematic review reported in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading):[@mcguinnessluke2020]
+
+* I had originally intended to examine both dementia and mild cognitive impairment (MCI) as outcomes of interest.
+However, given the large number of relevant records for the dementia outcomes, I did not include MCI as an outcome.
+
+* For Mendelian randomisation analyses, I had originally intended to use a panel of experts to assess he risk of bias in this study design.
+However, through private correspondence with the authors of a review of risk-of-bias assessment tools for Mendelian randomisation studies (since published[@spiga2021]), I became aware of the Mamluk _et al_ tool.
+Given this tool was considered to be the best available for assessing Mendelian randomisation studies and that it followed a domain-based approach, enabling comparison with tools for other study designs, I decided to use it in the review.
+
+* I performed an additional assessment of the risk of bias due to missing evidence using the ROB-ME tool. This analysis was not planned because the tool did not exist when the protocol was written.
+
+* I had originally intended to assess sources of funding alongside bias.
+However, on further reading,[@sterne2013] I learned that any bias introduced by sources of funding would operate through one of the existing domains of the risk-of-bias tools.
+As such, I did not consider funding sources seperately.
+
+ * Finally, I performed a dose response meta-analysis to assess the evidence for a non-linear realtionship between lipids and dementia outcomes.
+This marked a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Web of Science databases searched {#appendix-wos-databases}
 
 (ref:wosDatabases-caption) Summary of Web of Science databases searched.
+The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.
 
@@
 
-(ref:searchHits-caption) Overview of the full Medline search strategy.
+An overview of the number of hits per database, in addition to the full line-by-line search results for the each database, are presented below.
 
-(ref:searchHits-scaption) searchHits
+(ref:searchOverviewAppendix-caption) Summary of number of records identified in each database searched
 
-```{r searchHits-table, message=FALSE, results="asis", echo = FALSE}
+(ref:searchOverviewAppendix-scaption) searchOverviewAppendix
+
+```{r searchOverviewAppendix-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
+(ref:searchHitsMedline-caption) Overview of the full Medline search strategy.
+
+(ref:searchHitsMedline-scaption) Medline search strategy
+
+```{r searchHitsMedline-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;
+
+(ref:searchHitsEmbase-caption) Overview of the full Embase search strategy.
+
+(ref:searchHitsEmbase-scaption) Embase search strategy
+
+```{r searchHitsEmbase-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;
+
+(ref:searchHitsPI-caption) Overview of the full PyscINFO search strategy.
+
+(ref:searchHitsPI-scaption) PyscINFO search strategy
+
+```{r searchHitsPI-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;
+
+(ref:searchHitsCentral-caption) Overview of the full CENTRAL search strategy.
+
+(ref:searchHitsCentral-scaption) CENTRAL search strategy
+
+```{r searchHitsCentral-table, message=FALSE, results="asis", echo = FALSE}
+```
+
+&nbsp;
+
+(ref:searchHitsWos-caption) Overview of the full Web of Science search strategy.
+
+(ref:searchHitsWos-scaption) Web of Science search strategy
+
+```{r searchHitsWos-table, message=FALSE, results="asis", echo = FALSE}
 ```
@@
 
+As detailed extensively in the main text, the inclusion of preprinted literature was a key aspect of the review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+Using the `medrxivr` tool presented in Chapter \@ref(sys-rev-tools-heading).
+
+Given the relatively small number of records contained in the preprint server, no study design filters were employed.
+For the same reason, the number of search terms is smaller compared with the main database searches, as terms returning no records have been removed.
+
 ```{r, eval = FALSE}
@@
 
-mx_data <- mx_api_content(to_date = "2019-07-01")
-
-bx_data <- mx_api_content(server = "biorxiv",
-                                    to_date = "2019-07-01")
-
+# Define exposure search terms
 topic1 <- c(mx_caps("statin"),
@@
 
+# Define outcome search terms
 topic2 <- c(mx_caps("dementia"),
@@
 
-query <- list(
-  topic1,
-  topic2
-)
+# Combine search topics using Boolean AND
+query <- list(topic1, topic2)
 
+# Run search in bioRxiv
+bx_data <- mx_api_content(server = "biorxiv",
+                          to_date = "2019-08-01")
 bx_results <- mx_search(bx_data, query)
 
+# Run search in medRxiv
+mx_data <- mx_api_content(server = "medrxiv",
+                          to_date = "2019-08-01")
 mx_results <- mx_search(mx_data, query)
@@
 
-Note
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-Gwet's AC1 is defined as:
+Gwet's agreement coefficient, $AC1$ is defined as:
 
-$$AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}$$
+\begin{equation}
+AC1 = \frac{observed\;agreement-chance\;agreement}{1-chance\;agreement}
+  (\#eq:AC1-words)
+\end{equation}
 
@@
 
-### MR risk of bias tool {#appendix-mr-rob}
+&nbsp;<!----------------------------------------------------------------------->
+
+### Risk-of-bias assessment tool for Mendelian randomisation studies {#appendix-mr-rob}
 
@@
 
-## Chapter \@ref(sys-rev-results-heading)
+&nbsp;<!----------------------------------------------------------------------->
+
+## Chapter 4
 
 ### Dose response plots by fraction {#appendix-dr-fraction}
+
+In addition to examining a non-linear relationship between LDL-c and Alzheimer's disease (see Figure \@ref(fig:lipidsDoseResponse)), I performed a dose response analysis for two other exposure-outcome pairs.
+The results of these analyses are presented below.
 
@@
 
-```{r drDemeniaTC, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='100%', fig.scap='(ref:drDemeniaTC-scap)'}
+```{r drDemeniaTC, echo = FALSE, results="asis", fig.align='center', fig.pos = "H", fig.cap='(ref:drDemeniaTC-cap)', out.width='60%', fig.scap='(ref:drDemeniaTC-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/dr_Dementia_TC.png"))
@@
 
-```{r drAdLDL, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='100%', fig.scap='(ref:drAdLDL-scap)'}
+```{r drAdLDL, echo = FALSE, results="asis", fig.align='center', fig.pos = "H", fig.cap='(ref:drAdLDL-cap)', out.width='60%', fig.scap='(ref:drAdLDL-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/dr_AD_LDL.png"))
@@
 
-## Chapter \@ref(cprd-analysis-heading) {#appendix-cprd-analysis}
+&nbsp;<!----------------------------------------------------------------------->
+
+## Chapter 5 {#appendix-cprd-analysis}
 
@@
 
-## Chapter \@ref(ipd-heading) {#appendix-ipd-analysis}
+Any changes made to the approved protocol are "Minor amendments" as per the ISAC criteria, specifically falling under the category of "Additional methods to further control for confounding or sensitivity analysis provided these are to be reported as secondary to the main findings".
+
+Changes include:
+
+-   Use of a time-varying treatment indicator, to correctly classify time-at-risk.
+-   Inclusion of additional covariates that are adjusted for in the main model.
+
+&nbsp;<!----------------------------------------------------------------------->
+
+## Chapter 6 {#appendix-ipd-analysis}
 
 ### Email and documents sent to potental collaborators {#ipd-email-collab}
+
+__To be copied from email__
 
@@
 
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis
+
+(ref:ipdDementiaDef-scaption) Definition of dementia outcomes in IPD meta-analysis
+
+```{r ipdDementiaDef-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
 &nbsp;<!----------------------------------------------------------------------->
 
-## Chapter \@ref(tri-heading) {#appendix-tri-analysis}
+## Chapter 7 {#appendix-tri-analysis}
 
-### Calculation of average adjustment from expert elicitation {#appendix-adjustment-values}
+### Calculation of average adjustment values from previous expert elicitation exercise {#appendix-adjustment-values}
 
-### Code lists
+The paper describing the bias/indirectness-adjusted meta-analysis method used expert elicitation to define a distribution for  bias and indirectness across eight studies examining the effectiveness of routine anti-D prophylaxis in Rhesus negative women.[@turner2009] The authors consider five sources of bias (selection bias, performance bias, attrition bias, detection bias and other bias) and four sources of indirectness (population, intervention, control, outcome).
+For each domain of bias/indirectness, four experts were asked to define the 67% interval around the effect expected due to bias/indirectness in the absence of a true effect.
+Additive or multiplicative scales were used to capture the intervals for additive and proportional bias/indirectness, respectively.
+The authors then use assumed log-normality of these distributions to derive a mean and variance for each on the log scale.
+
+In an attempt to inform the prior distributions used in the triangulation exercise presented in Chapter \@ref(tri-heading), I first averaged the mean and variance values across the four experts for each source of bias/indirectness within each study.
+I averaged the absolute value of the mean, as I wanted to obtain the average adjustment regardless of direction of adjustment which was indicated using the sign of the mean in the original analysis).
+
+I then took the average and maximum of these averaged mean and variance values.
+The distributions arising from this analysis are presented in Table \@ref(tab:turnerEstimates-table).
+The two step approach (averaging across assessors before taking the average/maximum across sources of bias) was important.
+While the final mean values will be the same whichever approach is taken, in a one-step process the maximum value can be artificially inflated by a single expert's estimate.
+Averaging across experts for a given bias in a given study before taking the maximum value across biases and studies prevented this.
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009]
+
+(ref:turnerEstimates-scaption) turnerEstimates
+
+```{r turnerEstimates-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+The mean values shown were used to define the distributions assigned to  "Moderate" bias/indirectness judgements in my analysis (see Tables \@ref(tab:priorsAdd-table) & \@ref(tab:priorsIndirect-table)).
+
+&nbsp;<!----------------------------------------------------------------------->
 
 ### Comparison of two scenarios of bias
+
+As discussed in the main text, I defined two sets of additive bias distributions as a sensitivity analysis.
+The results for the two case studies under the two scenarios are presented in the figures below.
 
@@
 
-## Chapter \@ref(discussion-heading)
+## Chapter 8
 
 ### Reproducible research {#disc-repro-research}
+
+All software projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
 
@@
 
-- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-heading))
+- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-analysis-heading))
 
@@
 
+\minitoc <!-- this will include a mini table of contents-->
+
+\newpage
+
 ## Software used to create this thesis
@@
 
-This thesis was written in RMarkdown. Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")`
-All projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
+This thesis was written in RMarkdown using the RStudio integrated development environment.
+Several R packages were used as part of this project.`r gen_rmd_citation("packages.bib")` The version number of these packages is shown below:
+
+&nbsp;
+
+```{r, echo = FALSE}
+sessionInfo()
+```
+
+\newpage
 
@@
 <!-- TODO Need to complete this sections -->
+The robvis package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.
 
-_TBC_
+robvis currently contains templates for the following tools:
 
-\newpage
+* ROB2
+* ROBINS-I
+* QUADAS-2
+* ROB1
+
+For the direction bias plots, the data expected by the tools is more comprehensive.
+
+&nbsp;
+
+\blandscape
+<!----------------------------------------------------------------------------->
+(ref:biasData-caption) biasData
+
+(ref:biasData-scaption) biasData
+
+```{r biasData-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:biasDirectionData-caption) biasDirectionData
+
+(ref:biasDirectionData-scaption) biasDirectionData
+
+```{r biasDirectionData-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+\elandscape
 
@@
 
-The following pages contain copies of papers arising from work performed as part of this thesis.
+The following pages contain copies of the following publications:
+
+- _**McGuinness L.
+A.**, Higgins J.
+P.
+T., Walker, V.
+M., Davies, N.
+M., Martin, R.
+M., Coulthard, E., Davey-Smith, G., Kehoe, P.
+G., and Ben-Shlomo, Y.
+(2021) Association of lipid-regulating drugs with dementia and related conditions: an observational study of data from the Clinical Practice Research Datalink.
+medRxiv.
+DOI:   [10.1101/2021.10.21.21265131](https://doi.org/10.1101/2021.10.21.21265131)_
+
+- _**McGuinness, L.
+A.**, and L Schmidt.
+(2020) medrxivr: Accessing and searching medRxiv and bioRxiv preprint data in R.
+Journal of Open Source Software 5.54 2651.
+DOI: [10.21105/joss.02651](https://doi.org/10.21105/joss.02651)_
+
+- _**McGuinness, L.
+A.**, and Higgins J.
+P.
+T.
+(2020) "Risk‐of‐bias VISualization (robvis): An R package and Shiny web app for visualizing risk‐of‐bias assessments." Research Synthesis Method).
+DOI: [10.1002/jrsm.1411](https://doi.org/10.1002/jrsm.1411)_
+
+- _**McGuinness, L.
+A.**, and Sheppard A.
+L.
+2020.
+“A Descriptive Analysis of the Data Availability Statements Accompanying Medrxiv Preprints and a Comparison with Their Published Counterparts.”  PLOS ONE 16(5): e0250887.
+DOI: [10.1371/journal.pone.0250887](https://doi.org/10.1371/journal.pone.0250887)_
+
+- _Hennessy, E.
+A., Acabchuk, R., Arnold, P.
+A., Dunn, A.
+G., Foo, Y.
+Z., Johnson, B.
+T., Geange, S.
+R., Haddaway, N.
+R., Nakagawa, S., Mapanga, W., Mengersen, K., Page, M., Sánchez-Tójar, A.
+Welch, V.,  **and McGuinness L.
+A.** (2021).
+Ensuring Prevention Science Research is Synthesis-Ready for Immediate and Lasting Scientific Impact.
+Prevention Science .
+DOI: [10.1007/s11121-021-01279-8](https://doi.org/10.1007/s11121-021-01279-8)_
+
+These manuscripts arose from work performed as part of this thesis, as discussed more fully in Section \@ref(literature-contributions).
 
@@
 
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
+<!-- TODO These have been removed so as to not mess-up the plagarism score -->
+
+\includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
 \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}

### 2021-12-09 front-and-back-matter/_acknowledgements.Rmd
End of day:

--- 2021-06-02 front-and-back-matter/_acknowledgements.Rmd
@@
 
-Additionally, I would like to thank Sharen O’Keefe.
+There are many people without whose input and support this work would have been severely diminised:
 
-There are so many people without whom this would not have been possible:
+First and foremost, I would like to thank my supervisors - Julian Higgins, Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their support over the past three years.
+Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews.
+Sharen O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support.
+Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
 
-[**Check all name spellings**]
+Thanks must also go to those who contributed their time and energy to my research projects: Matthew Lee, Lena Schmidt, Alexandra McAleenan, and Vincent Cheng.
+Francesca Spiga kindly shared an advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner shared her code for bias-/indirectness-adjusted meta-analyses that underpins the quantitative triangulation framework presented in Chapter \@ref(tri-heading).
+Thanks to Vivienne for proof-reading.
 
-Sharen O'Keffe
-Neal Haddaway
-Martin Westgate
+A particular thank you to Emily Hennessy, with whom I co-wrote the guidance paper for preparing primary research for incorporation into systematic reviews.
+Similarly, thanks to Athena Sheppard for her support in assessing the impact of journal polices on open-data sharing.
 
-robvis contributors: (there are at least 3)
+Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
+<<github>>. A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.
 
-Annual reviewers: Rupert Payne and Emma Anderson
+I have been supported throughout my studies by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+The views expressed in this thesis are my own and do not necessarily represent those of the NIHR or the Department of Health and Social Care.
 
-Those who contributed their time to dual marking papers and code with me,
+On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times.
+Thanks to Mum and Dad for your never-ending love and support (I promise I'll get a real job now!).
+Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.
 
-I am a NIHR Doctoral Research Fellow with grant code **TBC**.
-The funding source had no role in the design, conduct of the study, collection, management, analysis and interpretation or preparation, review, or approval of the thesis.
+Finally, deepest thanks to Ciara Gardiner: holder-of-forts, maker-of-spreadsheets, and all-round fiancee-extraordinaire. I can't wait for the next adventure with you.
 
-Statistical support: check emails!
-
-All authors who volunteered time and effort to provided
-
-A special thanks goes out to Mark Newbury of the
-
-Finally, thanks to parents and Ciara Gardiner.
+&nbsp;
+&nbsp;
+&nbsp;
+&nbsp;
+&nbsp;
+&nbsp;
+&nbsp;
+&nbsp;
 
 \begin{flushright}
-Canynge Hall, Bristol \\
+Canynge Hall, Bristol \\\
 1 December 2021

### 2021-12-09 front-and-back-matter/abbreviations.tex
Double-saving
End of day: -700
End of day: 0
End of day: 2490
End of day:

@@
 \begin{mclistof}{List of Abbreviations}{3.2cm}
+\item[AC] Agreement coefficient
+\item[ACE] Acetylcholinesterase
+\item[AD] Alzheimer's disease
+\item[ADGC] Alzheimer’s Disease Genetics Consortium
+\item[API] Application programming interface
+\item[ApoE] Apolipoprotein E
+\item[BAS] Bile acid sequestrants
+\item[BMI] Body mass index
+\item[CAD] Coronary arterial disease
+\item[CaPS]  Caerphilly Prospective Study
+\item[CBS] Coronary bypass surgery
+\item[CCI] Charlson co-morbidity index
+\item[CIND] Cognitive impairment not dementia
+\item[CKD] Chronic kidney disease
+\item[CPRD] Clinical Practice Research Datalink
+\item[CRAN] Comprehensive R Archive Network
+\item[CSV] Comma separated value
+\item[CVD] Cardiovascular disease
 \item[DOI] Digitial object identifier
-\item[HDL] High Density Lipoprotein
+\item[DPUK] Dementia Platform UK
+\item[DSM] Diagnostic and Statistical Manual of Mental Disorders
+\item[EHR] Electronic health record
+\item[EPIC] European Prospective Investigation of Cancer 
+\item[FAGs] Fatty acid groups
+\item[GLGC] Global Lipids Genetic Consortium
+\item[GWAS]  Genome wide association studies
+\item[HDL] High density dipoprotein
+\item[HES] Hospital episode statistics
+\item[HMG-CoA] 3-hydroxy-3-methylglutaryl-coenzyme-A
+\item[HMGCR] HMG-CoA reductase
+\item[HR] Hazard ratio
+\item[ICD] International Classification of Diseases
+\item[IGAP] International Genomics of Alzheimer's Project
+\item[IHD]  Ischemic heart disease
+\item[IMD] Index of multiple deprivation
+\item[IPD] Individual participant data
+\item[IV] Instrumental variable
+\item[JUPITER] Justification for the Use of Statin in Prevention: An Intervention Trial Evaluating Rosuvastatin
+\item[LDL-c] Low density lipoprotein cholesterol
+\item[LRA] Lipid regulating agent
+\item[MCI] Mild cognitive impairment
+\item[MICE] Multiple imputation by chained equations
+\item[MMSE] Mini Mental State Exam
+\item[MoCA] Montreal Cognitive Assessement
 \item[MR] Mendelian randomization
+\item[NAG] Nicotinic acid groups
+\item[NINDS-ADRA] National Institute of Neurological Disorders and Stroke - Alzheimer's Disease and Related Disorders Association
+\item[NINDS-AIREN] National Institute of Neurological Disorders and Stroke - Association Internationale pour la Recherche en l'Enseignement en Neurosciences
+\item[NOS] Newcastle-Ottowa Scale
+\item[NRSE] Non-randomised studies of exposures
+\item[NRSI] Non-randomised studies of interventions
+\item[OR] Odds ratio
+\item[PAD] Peripheral arterial disease
+\item[PCSK9i] PCSK9 inhibitors
+\item[PDF] Portable document format
+\item[PR] Proportional hazards
+\item[PROSPER] Prospective Study of Pravastatin in the Elderly
+\item[PYAR] Participant-years-at-risk
+\item[RCT] Randomised controlled trial
+\item[REML] Restricted maximum likelihood 
+\item[RoB-ME] Risk of bias due to missing evidence
+\item[RR] Risk/rate ratio
+\item[SD] Standard deviation
+\item[SNP] Single nucleotide polymorphism
+\item[TC] Total cholesterol
+\item[TG] Triglycerides
+\item[VaD] Vascular dementia
 \end{mclistof}

### 2021-12-09 R/appendix.R

@@ -223,3 +223,180 @@ if(doc_type == "docx") {
     kable_styling(latex_options = c("HOLD_position"))
 }
 
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- biasData-table
+
+biasData_table <- robvis::data_rob2 %>%
+  head(5)
+
+if (doc_type == "docx") {
+  apply_flextable(biasData_table, caption = "(ref:biasData-caption)")
+} else{
+  knitr::kable(
+    biasData_table,
+    format = "latex",
+    caption = "(ref:biasData-caption)",
+    caption.short = "(ref:biasData-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"),
+                  font_size = 10)
+}
+
+#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
+# ---- biasDirectionData-table
+
+biasDirectionData_table <- rio::import("data/tri/ldl_ad_rob.csv") %>%
+  mutate(yi = round(yi,2),
+         sei = round(sei,2)) %>%
+  head(5) %>%
+  mutate(Study = paste("Study ",1:5)) %>%
+  select(Study, everything(),-c(result_id,type, starts_with("d6"),starts_with("d7")))
+
+biasDirectionData_table[biasDirectionData_table=="Add"] <- "A"
+biasDirectionData_table[biasDirectionData_table=="Prop"] <- "P"
+biasDirectionData_table[biasDirectionData_table=="None"] <- NA
+
+if(doc_type == "docx") {
+  apply_flextable(biasDirectionData_table, caption = "(ref:biasDirectionData-caption)")
+} else{
+  knitr::kable(
+    biasDirectionData_table,
+    format = "latex",
+    caption = "(ref:biasDirectionData-caption)",
+    caption.short = "(ref:biasDirectionData-scaption)",
+    booktabs = TRUE
+  ) %>%
+    row_spec(0, bold = TRUE) %>%
+    kable_styling(latex_options = c("HOLD_position"), 
+                  font_size = 10)
+}
+
[…]

### 2021-12-09 R/helper.R

@@ -107,11 +107,11 @@ num_to_text <- function(x, start_of_sentence = FALSE)
   if (!x %% 1 == 0)
     warning("X is not an integer")
   if (start_of_sentence) {
-    out <- xfun::numbers_to_words(x)
+    out <- xfun::numbers_to_words(x, and = TRUE)
     out <- stringr::str_to_sentence(out)
   } else {
     if (x < 11 & x > -1) {
-      out <- xfun::numbers_to_words(x)
+      out <- xfun::numbers_to_words(x, and=TRUE)
     } else {
       out <- comma(x)
     }

### 2021-12-10 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 
+<!-- TODO Talk here about the reduced biological validity of  -->
+
 A further limitation stems from the possibility of uncontrolled confounding due to genetic factors.
@@
 Dementia and associated conditions have a long prodromal period, during which preclinical disease could cause indications for the prescription of a lipid-regulating agent.
+Enforcing a minimum period of follow-up would address this limitation, but the use of a time-varying treatment indicator in this analysis prevents the use of this approach (see Appendix \@ref(cprd-min-fu) for a fuller discussion of this topic).
 

### 2021-12-10 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
-In the first instance, the first/corresponding author of the publication was emailed (see Appendix \@ref(ipd-email-collab) for a copy of the correspondence sent to potential collaborators) in Autumn 2020.
+In the first instance, the first/corresponding author of the publication was emailed <!-- TODO (see Appendix \@ref(ipd-email-collab) for a copy of the correspondence sent to potential collaborators) --> in Autumn 2020.
 If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who had moved to a different institution.
@@
 A range of additional variables were included in the analysis, intended to address the potential for confounding.
-With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _Apo_$\mathcal{E}4$ status, smoking/alcohol status, ethnicity, and prevalent cardiovascular disease.
+With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _Apo_$\mathcal{E}4$ status, smoking/alcohol status, ethnicity, and prevalent diabetes or cardiovascular disease.
 This set covers key risk factors for dementia/Alzheimer's disease in addition to general cardiovascular risk factors.
 Details on how these variables were coded, given the available data, are presented in Section \@ref(ipd-covar-definition).
+
+<!-- TODO Need to go through and make sure that I have updated the covariate list appropriately -->
 
@@
 
-<!-- TODO Need average follow-up by cohort here - or rather put it in the table -->
-<!-- TODO Need total number of Azd cases in whitehall in the paragraph above-->
-
 &nbsp;
@@
 ```
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
 
-&nbsp;
+<!-- TODO Note here about how the IHD variable in CAPS has a note saying there might be an issue with the variables, while the Whitehall study uses narrow range of codes to define CHD.
+EPIC is selfreported angina/mi/arrythmia -->
 
@@
 Note that for the sex interaction analysis, the CaPS cohort was excluded as it contains only a single sex and therefore provides no information on exposure-sex interaction.
+
+<!-- TODO If using fixed effect model, need to udate subgroup labels to reflect this -->
 

### 2021-12-10 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 PRISMA 2020 statement: updated guidelines for reporting systematic reviews and meta-analyses.
-BMJ 372:n71 [10.1136/bmj.n71](https://doi.org/10.1136/bmj.n71)*
+BMJ 372:n71.
+DOI:  [10.1136/bmj.n71](https://doi.org/10.1136/bmj.n71)*
 
@@
 F1000Research, 10:401.
-DOI: &nbsp; [10.12688/f1000research.51117.1](https://doi.org/10.12688/f1000research.51117.1)*
+DOI: [10.12688/f1000research.51117.1](https://doi.org/10.12688/f1000research.51117.1)*
 
@@
 
-&nbsp;<!----------------------------------------------------------------------->
+\blandscape
 
 ### Risk-of-bias assessment tool for Mendelian randomisation studies {#appendix-mr-rob}
+
+A copy of the risk of bias tool used to assess Mendelian randomisation studies is presented in Table \@ref(mrTool-table), below.
 
@@
 ```{r mrTool-table, message=FALSE, results="asis", echo = FALSE}
-
-mrTool_table <- read.csv(here::here("data/sys-rev/mrRobTool.csv")) %>%
-  select(1:5) %>%
-  rename("Bias domain" = Bias.domain)
-
-if(doc_type == "docx") {
-  knitr::kable(mrTool_table, caption = "(ref:mrTool-caption)")
-} else{
-  knitr::kable(
-    mrTool_table,
-    format = "latex",
-    caption = "(ref:mrTool-caption)",
-    caption.short = "(ref:mrTool-scaption)",
-    longtable = TRUE,
-    booktabs = TRUE
-  ) %>%
-    row_spec(0, bold = TRUE) %>%
-    column_spec(column = 1:5, width = paste0(32/5,"em")) %>%
-    row_spec(2:nrow(mrTool_table)-1, hline_after = TRUE) %>%
-    kable_styling(latex_options = c("HOLD_position","repeat_header"))
-}
-
 ```
 
-&nbsp;<!----------------------------------------------------------------------->
+\elandscape
 
@@
 
+### Minimum follow-up period {#cprd-min-fu}
+
+Enforcing a minimum period of follow-up is normally used to reduce the risk of reverse causation in an analysis by excluding events occurring within a certain time-frame post-exposure.
+With respect to dementia outcomes, which have a long prodomal period, enforcing a minimum period of follow-up can add biological validity to an analysis.
+Incident cases of dementia that occur within a few years of starting a drug may already be beyond effective preventive treatment at the time the drug was started, and so restricting the analysis to those with longer exposure to treatment may provide a more reliable estimate of the effect.
+
+Panel A of Figure \@ref(fig:minFU) describes a standard analysis of an exposure with a minimum enforced follow-up period (in this case, 10 years).
+Participants enter the cohort and are classified at that point as either exposed or unexposed, for example, on the basis of a total cholesterol measurement.
+Participants are followed-up over time, but events occuring before the minimum period of follow-up are discarded.
+
+<!----------------------------------------------------------------------------->
+```{r minFollowUp, include = FALSE}
+```
+
+(ref:minFU-cap) __shortcap:__
+
+(ref:minFU-scap) shortcap
+
+```{r minFU, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:minFU-cap)', out.width='100%', fig.scap='(ref:minFU-scap)'}
+knitr::include_graphics(file.path("figures/appendix/minFU.png"))
+```
+<!----------------------------------------------------------------------------->
+
+However, applying a similar approach to the analysis performed in Chapter \@ref(cprd-analysis-heading), illustrated in Panel B of Figure \@ref(fig:minFU), is challenging.
+The use of a time updating treatment indicator results in two potential starting points for the 10-year lag: entry into the cohort or initiation of statin therapy.
+As the purpose of this analysis is to investigate the impact of statin treatment, starting the minimum period of follow-up from cohort entry is not helpful as it does not ensure that participants have been exposed to the drug for 10 years.
+Alternatively, defining the minimum period of follow-up from statin initiation cause issues around the treatment of time-at-risk before statin initiation and around the start point for the follow-up period in those never prescribed a statin.
+In summary, either approach is likely to be substantially biased.
+
+With these caveats in mind, below I present a sensitivity analysis of the association of statins with dementia outcomes, enforcing a minimum 10-year period of follow-up from statin initiation in those prescribed a statin.
+
+<!----------------------------------------------------------------------------->
+(ref:cprdMinFu-cap) Estimates from the
+
+(ref:cprdMinFu-scap) shortcap
+
+```{r cprdMinFu, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdMinFu-cap)', out.width='100%', fig.scap='(ref:cprdMinFu-scap)'}
+knitr::include_graphics(file.path("figures/hold.png"))
+```
+<!----------------------------------------------------------------------------->
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-### Email and documents sent to potental collaborators {#ipd-email-collab}
+<!-- ### Email sent to potental collaborators {#ipd-email-collab} -->
 
-__To be copied from email__
+<!-- __To be copied from email__ -->
 
 ### Covariate matrix {#appendix-ipd-covariate-matrix}
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:missingMatrix-caption) Overview of missing data across covariates included in IPD analysis.
+Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.
+
+(ref:missingMatrix-scaption) missingMatrix
+
+```{r missingMatrix-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;
 
@@
 <!----------------------------------------------------------------------------->
-(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis
+(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis.
+Note the codes used to define dementia and related outcomes in the HES data as part of the Whitehall II cohort were taken from a previously published analysis.[@russ2014]
 
@@
 
-In an attempt to inform the prior distributions used in the triangulation exercise presented in Chapter \@ref(tri-heading), I first averaged the mean and variance values across the four experts for each source of bias/indirectness within each study.
-I averaged the absolute value of the mean, as I wanted to obtain the average adjustment regardless of direction of adjustment which was indicated using the sign of the mean in the original analysis).
+The resulting data for two domains of bias (attrition and detection) in one study are shown in Table \@ref(tab:addTable1-table).
 
-I then took the average and maximum of these averaged mean and variance values.
-The distributions arising from this analysis are presented in Table \@ref(tab:turnerEstimates-table).
-The two step approach (averaging across assessors before taking the average/maximum across sources of bias) was important.
-While the final mean values will be the same whichever approach is taken, in a one-step process the maximum value can be artificially inflated by a single expert's estimate.
-Averaging across experts for a given bias in a given study before taking the maximum value across biases and studies prevented this.
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:addTable1-caption) Distributions of bias, defined by position and variance terms, assigned by four independent experts to attrition and detection bias in a single study.
+This data was obtained from a previous publication,[@turner2009] and represents an illustrative subset of the larger dataset.
 
-&nbsp;
+(ref:addTable1-scaption) addTable1
 
-<!----------------------------------------------------------------------------->
-(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009]
+```{r addTable1-table, message=FALSE, results="asis", echo = FALSE}
+```
+&nbsp;<!----------------------------------------------------------------------->
+
+In an attempt to inform the prior distributions used in the triangulation exercise presented in Chapter \@ref(tri-heading), I first averaged the position and variance values across the four experts for each source of bias/indirectness within each study.
+I took the average of the absolute of the position value, as I wanted to obtain the average adjustment regardless of direction.
+The results of this process for the example data presented below are shown in Table \@ref(tab:addTable2-table).
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:addTable2-caption) Position and variance values for two example bias domains (attritiona and detection), obtained by averaging the absolute of the values contained in \@ref(tab:addTable3-table) across the four reviewers.
+
+(ref:addTable2-scaption) addTable1
+
+```{r addTable2-table, message=FALSE, results="asis", echo = FALSE}
+```
+&nbsp;<!----------------------------------------------------------------------->
+
+I then took the average and maximum of the expert-averaged position and variance values. The results of this for the example data are presented in Table \@ref(tab:addTable3-table).
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:addTable3-caption) Mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table)
+
+(ref:addTable3-scaption) addTable1
+
+```{r addTable3-table, message=FALSE, results="asis", echo = FALSE}
+```
+&nbsp;<!----------------------------------------------------------------------->
+
+This two step approach (averaging across assessors before taking the average and maximum across domains/studies) was important.
+While the final average values will be the same whichever approach is taken, in a one-step process, the maximum value can be artificially inflated by a single expert's estimate.
+For example, in the illustrative data subset above, Assessor 2 assigns a distribution of N(-0.32,0.14), which would double the maximum position (0.16) and triple the maximum variance (0.0475) obtained when first averaging across experts.
+
+The distributions arising from this applying this approach to the entire dataset, stratified by bias/indirectness and additive/proportional effects, are presented in Table \@ref(tab:turnerEstimates-table).
+
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009].
+Note I did not calculate values for additive indirectness, as in my analysis, all indirectness was assumed to be proportional.
 
@@
 The results for the two case studies under the two scenarios are presented in the figures below.
+Under the first, shown on the left of the subsequent  forest plot, the difference in the position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+Under the second scenario, the difference in the position value between the distributions assigned to "High" and "Moderate" is twice that between "Moderate" and "Low".
 
 (ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
-The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
 
 (ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels
 
@@
 (ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
-The left forest plot shows the result where the difference in mean value between the "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-In the right plot, the difference in mean value between "High" and "Moderate" is twice that between "Moderate" and "Low".
+Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels
 
@@
 
-All software projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
-
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tool to help search medRxiv and bioRxiv preprint metadata.
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tools to search preprinted literature, create visualisations of risk-of-bias data and to preform quantitative triangulation.
 In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
 
-Unfortunately, given the.
-However, as discussed in other chapters of this thesis and elsewhere, sharing of analysis code is a useful step towards transparency when the underlying datasets are not readily available.
+Unfortunately, given the nature of the data underpinning the CPRD (Chapter \@ref(cprd-analysis-heading)) and IPD (Chapter \@ref(ipd-heading)) analyses, it is not possible to make it publicly available.
+Access to the CPRD data is dependent on an application to its managing body, while acces to the cohorts within the DPUK requires approval from both the DPUK and inidividual cohort owners.
+IN the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.
 
-Commentary on the fact that the best you can do is replicate vs reproducible (due the closed nature of the data).
+Finally, all software projects in these thesis attempt to conform to minimal best practices for research computing. [@wilson2014; @wilson2017]
 
-One is the ability to recreate the results given the same data and code, the other is the ability to recreate the results given the same code but a different dataset.
-IN theory it is possible to gain access the dataset given the information presented in Chapter \@(ref:cprd-analysis-heading).
-However, access is dependency on an ISAC application to the managing body of the CPRD.
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 <!----------------------------------------------------------------------------->
-(ref:biasData-caption) biasData
+(ref:biasData-caption) First five assessments contained in `data_rob2`, an example dataset for the Risk of Bias 2 tool for randomised controlled trials available via the `robvis` package.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:biasDirectionData-caption) biasDirectionData
+(ref:biasDirectionData-caption) Example data illustrating the structure required for bias direction plots.
+$d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain.
+Note that, because of the wide nature of the data, I have abbreviated the data in order to display it.
+A key for interpreting the data can be found below the table.
 
@@
 \elandscape
+
+### Simple visualisations
+
+```{r robAppendixFigures, include = FALSE}
+```
+
+```{r, eval = FALSE}
+rob_summary(data = data_rob2, tool = "ROB2")
+```
+
+<!----------------------------------------------------------------------------->
+(ref:robSummary-cap) __shortcap:__
+
+(ref:robSummary-scap) shortcap
+
+```{r robSummary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:robSummary-cap)', out.width='80%', fig.scap='(ref:robSummary-scap)'}
+knitr::include_graphics(file.path("figures/appendix/robSummary.png"))
+```
+<!----------------------------------------------------------------------------->
+
+```{r, eval = FALSE}
+rob_traffic_light(data = data_rob2,
+                  tool = "ROB2",
+                  psize = 10)
+```
+
+<!----------------------------------------------------------------------------->
+(ref:robTraffic-cap) __shortcap:__
+
+(ref:robTraffic-scap) shortcap
+
+```{r robTraffic, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:robTraffic-cap)', out.width='80%', fig.scap='(ref:robTraffic-scap)'}
+knitr::include_graphics(file.path("figures/appendix/robTraffic.png"))
+```
+<!----------------------------------------------------------------------------->
+
+\newpage
 

### 2021-12-10 06-Chp-IPD-Analysis.Rmd
Update IPD chapter with imputed data

@@
 However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
-As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were analysed adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, presence of morbidities).
-As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education and BMI).
+As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were analysed adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, diabetes).
+As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education, ethnicity, and prevalent ischemic heart disease and BMI).
 Results between the common-set-adjusted (Model 1) and maximally-adjusted (Model 2) models were then compared.
@@
 Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
+
+<!-- TODO Need to state that using a fixed effect model for the interaction terms -->
 
@@
 A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(appendix-ipd-covariate-matrix).
-The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, BMI and ethnicity.
+The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, prevalent ischemic heart disease, BMI and ethnicity.
 No included cohort provided information on the _Apo_$\mathcal{E}4$ status of participants, and so this variable could not be adjusted for in the analysis.
@@
 
-Estimates from the common-set-adjusted model (Model 1: adjusted for age, sex, smoking, alcohol, presence of vascular comorbidites) were comparable to the fully-adjusted model (Model 2: Model 1 further adjusted for education and BMI) for the effect of lipids on all-cause dementia in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
+Estimates from the common-set-adjusted model (Model 1: adjusted for age, sex, smoking, alcohol, and diabetes) were comparable to the fully-adjusted model (Model 2: Model 1 further adjusted for ethnicity, prevalent ischemic heart disease, education and BMI) for the effect of lipids on all-cause dementia in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
 
 <!----------------------------------------------------------------------------->
-(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses.
+(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses for the all-cause dementia outcome.
 
@@
 Note that for the sex interaction analysis, the CaPS cohort was excluded as it contains only a single sex and therefore provides no information on exposure-sex interaction.
-
-<!-- TODO If using fixed effect model, need to udate subgroup labels to reflect this -->
 
@@
 In an attempt to validate my approach, I compared the results from the maximally-adjusted model (Model 2) in this analysis with those reported by Tynkkynen _et al._ for both all-cause dementia and Alzheimer's disease.
-The results were broadly comparable (Figures \@ref(fig:whitehallComparisonDementia) and \@ref(fig:whitehallComparisonAd)), with the exception of the association of triglycerides with all-cause dementia.
+
+The results for the Alzheimer's disease outcome were comparable (Appendix \@ref(appendix-ipd-whitehall)).
+However, for the vascular dementia outcome (Figure \@ref(fig:whitehallComparisonDementia)), I identified a discrepancy in the association of triglycerides with all-cause dementia estimated by the two analyses.
 Tynkkynen _et al._[@tynkkynen2018] found a protective effect of triglycerides on this outcome (`r estimate(0.69,0.56,0.85,"HR")`) while this analysis found evidence for a harmful effect (`r estimate(1.26,1.12,1.41,"OR")`).
@@
 
-<!----------------------------------------------------------------------------->
-(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.
-
-(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort
-
-```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
-knitr::include_graphics(file.path("figures/hold.png"))
-```
-<!----------------------------------------------------------------------------->
-
 &nbsp;<!----------------------------------------------------------------------->
 
-Investigation of this discrepancy indicated that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (N =287 in this analysis vs.
+<!-- TODO Talk about the fact that I used multiple imputation and they did not. Evidenced by wider confidence intervals, indicating a smaller sample size, likely the result of a complete case -->
+
+Investigation revealed several possible reasons for this discrepancy.
+The first is that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (N =287 in this analysis vs.
 n=114 in Tynkkynen _et al._).
-The covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _Apo_$\mathcal{E}4$ status.
+Additionally, this analysis uses multiple imputation to address missing data, while the Tynkkynen _et al._ does not mention how missing data was addressed, though the reduced precision in the estimates suggest a complete case analysis.
+Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _Apo_$\mathcal{E}4$ status.
 However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.

### 2021-12-10 front-and-back-matter/99-appendices.Rmd
Range of changes to the appendixx

@@
 
-<!-- __To be copied from email__ -->
+<!-- TODO __To be copied from email__ -->
 
@@
 <!----------------------------------------------------------------------------->
-(ref:missingMatrix-caption) Overview of missing data across covariates included in IPD analysis.
+(ref:missingMatrix-caption) Overview of missing data across covariates (described as N (%)) included in IPD analysis.
 Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.
@@
 &nbsp;
+
+### Comparison with previous analysis of the Whitehall II cohort {#appendix-ipd-whitehall}
+
+<!----------------------------------------------------------------------------->
+(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.
+
+(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort
+
+```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
+knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_ad.png"))
+```
+<!----------------------------------------------------------------------------->
 
@@
 Access to the CPRD data is dependent on an application to its managing body, while acces to the cohorts within the DPUK requires approval from both the DPUK and inidividual cohort owners.
-IN the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.
+In the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.[@goldacre2019]
 
@@
 ### Catalogue of failures {#appendix-catalogue-failures}
+
+OVer the course of my PhD, I kept a record of attempted
 

### 2021-12-13 04-Chp-Systematic-Review-Results.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

@@
 Using the methods outlined in the previous chapter, here I present  the results of a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
-In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes
+In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
+
+&nbsp;
 
@@
 
-(ref:prisma-flow-cap) PRISMA flow diagram illustrating how records moved through the systematic review process.
-The different contributions of standard bibliographic databases and preprint servers to the review are indicated.
+(ref:prisma-flow-cap) __PRISMA flow diagram__ - The diagram illustrates how records moved through the systematic review process.
+Note that the different contributions of standard bibliographic databases (left) and preprint servers (right) to the review are indicated.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) Inter-rater agreement on a subset of records, indicating high accuracy.
+(ref:agreeInter-caption) __Inter-rater agreement__ - For a subset of records, the decisions between two independent were compared.
+Gewt's $AC1$ was calculated from this data to assess inter-rater reliability, indicating high accuracy ($AC1$ = `r agreeInter_coeff[1]`).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) Intra-rater agreement on subset of records, indicating high consistency.
+(ref:agreeIntra-caption) __Intra-rater agreement__ - For a subset of records, the decisions between the same reviewer with 3 month lag were compared.
+Gewt's $AC1$ was calculated from this data to assess intra-rater reliability, indicating high consistency ($AC1$ = `r agreeIntra_coeff[1]`).
 
@@
 <!--- TODO Talk a little bit more about age here --->
-
-Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@andrews2019; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
 
@@
 
-(ref:studyCharacteristics-caption) Characteristics of included studies, stratified by study design.
+(ref:studyCharacteristics-caption) __Characteristics of included studies__ - The characteristics of studies included in this review, stratified by study design, are presented below.
 Note that three studies reported on multiple analytical designs within a single study report (Beydoun 2011,[@beydoun2011] Reitz 2010,[@reitz2010] and Benn 2017[@benn2017]), and these have been duplicated across the relevant sub-sections.
@@
 
+Three included reports were preprinted (denoted in the Table \@ref(tab:studyCharacteristics-table) using an asterisk),[@andrews2019; @so2017;@zhu2017] one of which had subsequently been published and was captured by the primary literature search.[@zhu2018] All three included preprints were obtained from the bioRxiv preprint server and all described a Mendelian randomisation analysis.
+
 As illustrated in Figure \@ref(fig:cohortLocations), the majority of reports described studies conducted in high-income countries, with the most highly represented region being North America.
@@
 
-(ref:cohortLocations-cap) Geographical distribution of study cohorts
+(ref:cohortLocations-cap) __Geographical distribution of study cohorts__ - The country or countries of origin for the studies include in the review are shown below.
+Note that the majority of included studies were performed in the Western world, predominantly in Europe and North America.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on all-cause dementia
+(ref:obsHyperDementia-cap) __Random-effects meta-analysis of hypercholesterolemia on all-cause dementia__ - Non-randomised studies examining the association of hypercholesterolemia with all-cause dementia were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:obsHyperDementia-scap) Meta-analysis of hypercholesterolemia on all-cause dementia
+(ref:obsHyperDementia-scap) Random-effects meta-analysis of hypercholesterolemia on all-cause dementia
 
@@
 
+\newpage
+\thispagestyle{empty}
+
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsDementia-cap) Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on all-cause dementia risk, standardised per 1-SD increase in the lipid fraction.
-Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.
+(ref:lipidFractionsDementia-cap) __Random-effects meta-analysis of lipids on all-cause dementia__ - Non-randomised studies examining the association of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) with all-cause dementia risk, standardised per 1-SD increase, were synthesised using a random-effects meta-analysis.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
+Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts and these are presented separately.
 
-(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of four lipid fractions on all-cause dementia
+(ref:lipidFractionsDementia-scap) Random-effects meta-analysis of lipids and all-cause dementia
+
 ```{r lipidFractionsDementia, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsDementia-cap)', out.width='100%', fig.scap='(ref:lipidFractionsDementia-scap)'}
@@
 <!----------------------------------------------------------------------------->
+
+\newpage
 
@@
 
-(ref:statinsRCT-cap) Random-effects meta-analysis of randomised controlled trials examining statins on all-cause dementia.
-D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond in each forest plot presented above.
+(ref:statinsRCT-cap) __Random-effects meta-analysis of statins on all-cause dementia in RCTs__ - 
+Randomised controlled trials examining the effect of statin use on all-cause dementia risk were synthesised using a random-effects meta-analysis.
+D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the RoB2 tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia
+(ref:statinsRCT-scap) Random-effects meta-analysis of statins on all-cause dementia in RCTs
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on all-cause dementia
+(ref:obsStatinDementia-cap) __Random-effects meta-analysis of statins on all-cause dementia__ - Non-randomised studies examining the association of statin use with all-cause dementia were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsFibrateDementia-cap) Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia
+(ref:obsFibrateDementia-cap) __Random-effects meta-analysis of fibrates on all-cause dementia__ - Random-effects meta-analysis of non-randomised studies examining the effect of fibrate use on all-cause dementia.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:obsFibrateDementia-scap) Random-effects meta-analysis of statins on all-cause dementia
+(ref:obsFibrateDementia-scap) Random-effects meta-analysis of fibrates on all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on Alzheimer's disease
+(ref:obsHyperAD-cap) __Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease__ - Non-randomised studies examining the association of hypercholesterolemia with Alheimer's disease were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:obsHyperAD-scap) Meta-analysis of hypercholesterolemia on Alzheimer's disease
+(ref:obsHyperAD-scap) Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease
 
@@
 
+\newpage
+\thispagestyle{empty}
+
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsAD-cap)  Random-effects meta-analysis of four lipid fractions (total cholesterol, HDL, LDL, and triglycerides) on Alzheimer's disease risk, standardised per 1-SD increase in the lipid fraction.
-Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts within a single study and the results for each cohort are presented separately here.
+(ref:lipidFractionsAD-cap)  __Random-effects meta-analysis of association of lipid fractions with Alzheimer's disease__ - D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
+Note that Tynkkyen _et al_[@tynkkynen2018] reported results from multiple cohorts and these are presented separately.
 
-(ref:lipidFractionsAD-scap) Random-effects meta-analysis of four lipid fractions on Alzheimer's disease
+(ref:lipidFractionsAD-scap) Random-effects meta-analysis of lipids on Alzheimer's disease
 
@@
 
+\newpage
+
 Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
@@
 Synthesis of these results would would result in a falsely precise estimate caused by multiple counting of the same participants,and as a result, no meta-analysis of these studies was performed.
-
 However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
@@
 <!----------------------------------------------------------------------------->
-(ref:mrDuplication-cap) Summary of duplication across Mendelian randomisation studies which used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
+(ref:mrDuplication-cap) __Summary of duplication across two-sample Mendelian randomisation studies__ - Several Mendelian randomisation studies used summary statistics from the Global Lipid Genetics Consortium (GLGC) and the International Genomics of Alzheimer's Project (IGAP).
 Note that the Alzheimer’s Disease Genetics Consortium (ADGC) is a sub-cohort within IGAP.
 
-(ref:mrDuplication-scap) Summary of duplication across two sample Mendelian randomisation studies
+(ref:mrDuplication-scap) Summary of duplication across two-sample Mendelian randomisation studies
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of statin use on Alzheimer's disease
+(ref:obsStatinAD-cap) __Random-effects meta-analysis of statins on Alzheimer's disease__ Non-randomised studies examining the association of statin use with Alzheimer's disease were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
@@
 
-<!----------------------------------------------------------------------------->
-(ref:mrStatinAD-cap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:mrStatinAD-cap) __Random-effects meta-analysis of HMGCR inhibition on Alzheimer's disease__ - Mendelian randomisation studies examining the association of genetically lowered LDL-c via HMGCR inhibition with Alzheimer's were synthesised using a random-effects meta-analysis.
+D1-D5 and O refer to the five risk-of-bias domains and single overall judgement in the Mamluk _et al_ tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:mrStatinAD-scap) Random-effects meta-analysis of genetically lowered LDL-c via HMGCR inhibition on Alzheimer's disease
+(ref:mrStatinAD-scap) Random-effects meta-analysis of HMGCR inhibition on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperVaD-cap) Random-effects meta-analysis of non-randomised studies examining the effect of hypercholesterolemia on vascular dementia
+(ref:obsHyperVaD-cap) __Random-effects meta-analysis of hypercholesterolemia on vascular dementia__ - Non-randomised studies examining the association of hypercholesterolemia with vascular dementia were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
-(ref:obsHyperVaD-scap) Meta-analysis of hypercholesterolemia on vascular dementia
+(ref:obsHyperVaD-scap) Random-effects meta-analysis of hypercholesterolemia on vascular dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:lipidFractionsVaD-cap) Random-effects meta-analysis of total cholesterol on vascular dementia, standardised per 1-SD increase in the lipid fraction.
+(ref:lipidFractionsVaD-cap) __Random-effects meta-analysis of total cholesterol on vascular dementia__ - Non-randomised studies examining the association of total cholesterol with vascular dementia risk, standardised per 1-SD increase in the lipid fraction, were synthesised using a random-effects meta-analysis.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-E tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
@@
 
-```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsAD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsAD-scap)'}
+```{r lipidFractionsVaD, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:lipidFractionsVaD-cap)', out.width='100%', fig.scap='(ref:lipidFractionsVaD-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/fp_obs_VaD_TC_.png"))
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinVaD-cap) Random-effects meta-analysis of non-randomised studies examining effect of statin use on vascular dementia
+(ref:obsStatinVaD-cap) __Random-effects meta-analysis of statins on vascular dementia__ - Non-randomised studies examining the association of statin use with vascular dementia were synthesised using a random-effects meta-analysis.
+Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
+D1-D7 and O refer to the seven risk-of-bias domains and single overall judgement in the ROBINS-I tool, while the risk of bias due to missing evidence is shown beside the overall summary diamond.
 
@@
 
-```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinDVaD-scap)'}
+```{r obsStatinVaDFig, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:obsStatinVaD-cap)', out.width='100%', fig.scap='(ref:obsStatinVaD-scap)'}
 knitr::include_graphics(file.path("figures/sys-rev/fp_obs_Statin-Ever_VaD.png"))
@@
 
-<!-- TODO Add legend to this figure so that it is clear what the lines are - YBS was confused -->
+<!-- TODO Improve caption for the legend below -->
 
 <!----------------------------------------------------------------------------->
-(ref:lipidsDoseResponse-cap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
+(ref:lipidsDoseResponse-cap) __Dose-response meta-analysis of total cholesterol on Alzheimer's disease__ - Non-randomised studies examining the association of lipids levels with Alzheimer's disease across several categories or "doses" of exposure were synthesised using a dose response meta-analysis.
+The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).
 
-(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol
+(ref:lipidsDoseResponse-scap) Dose-response meta-analysis of total cholesterol on Alzheimer's disease
 
@@
 
-Age and sex were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
+Age and gender were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:typeByYear-cap) Included study designs for any dementia outcome by year of publication
+(ref:typeByYear-cap) __Study designs by year of publication__ - Included studies across all dementia outcomes are shown grouped by study design and year of publication.
+Note that Mendelian randomisation studies only begin to appear in the evidence base much later than other study designs.
 
@@
 
-(ref:mrAssumptions-cap) Summary of the assumptions in Mendelian randomisation analyses: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
+(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
 there is no horizontal pleiotropy).
 
-(ref:mrAssumptions-scap) Overview of assumptions in Mendelian randomisation analyses
+(ref:mrAssumptions-scap) Summary of the assumptions in Mendelian randomisation analyses
 
@@
 
-(ref:preprintGrowth-cap) Growth of preprint repositories over time.
-Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv N = `r n_at_search["med"]`), the number of hits returned by each is expected.
+(ref:preprintGrowth-cap) __Growth of preprint repositories over time__ - Given the relative sizes of the preprint repositories at the time the searches for this review were conducted (bioRxiv N = `r n_at_search["bio"]`, medRxiv N = `r n_at_search["med"]`), the number of hits returned by each is expected.
 

### 2021-12-13 05-Chp-CPRD-Analysis.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

@@
 <!----------------------------------------------------------------------------->
-(ref:decisionTreeFig-cap) Decision tree for assigning dementia subtypes, based on the presence of Read codes in the patient's record.
+(ref:decisionTreeFig-cap) __Decision tree for assigning dementia subtypes__ - Based on the presence of specific Read codes in the patient's record, a decision tree was used to classify dementia subtypes ("Probable" or "Possible" Alheimer's disease, vascular dementia, and other dementia).
 Note that an outcome of "probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
@@
 
-(ref:immortalTimeBias-cap) Diagram illustrating the two presentations of immortal time bias, as a selection bias (Panel A) and a misclassification bias (Panel B).
+(ref:immortalTimeBias-cap) __Immortal time bias__ - The two presentations of immortal time bias are illustrated.
+Panel A shows the selection bias presentation, where time prior to a statin exposure is excluded from the analysis and outcomes in this time period are lost.
+Panel B shows the misclassification presentation, there time (and events) prior to statin exposure is incorrectly assigned to the exposed group.
 
-(ref:immortalTimeBias-scap) shortcap
+(ref:immortalTimeBias-scap) Immortal time bias
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:negativeOutcome-cap) Causal diagram (directed acyclic graph) showing relationship between exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
+(ref:negativeOutcome-cap) __Causal diagram for ideal negative outcome__ - The directed acyclic graph shows the relationship between the exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
 Note the absence of any arrow between $X$ and $N$.
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdFlowchart-cap) Attrition of CPRD participants as the eligibility criteria were applied. The largest cause of attrition was the absence of an index event of interest.
+(ref:cprdFlowchart-cap) __Attrition of CPRD participants__ - Patients were excluded from the study cohort for several reasons, and the number of patients excluded as each eligibility criterion was applied is shown above.
+Note that the largest cause of attrition was the absence of an index event of interest.
 
@@
 <!--------------------------------------------------------------------------->
-(ref:cprdPrimary-cap) Results from primary analyses of CPRD data using the fully adjusted model and participant age as the time scale.
+(ref:cprdPrimary-cap) __Results from primary analyses of CPRD data__ - Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale, stratified by lipid-regulating agent and dementia outcome.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) Comparison of analyses using the complete case versus imputed cohorts.
+(ref:completeCaseFig-cap) __Complete case vs.
+imputed data analysis__ Comparison of analyses using the complete case versus imputed cohorts, indicating broad agreement between the two approaches.
+Note that the analyses using imputed data gave more precise estimates due to the low proportion of patients with complete covariate data.
 
@@
 
-#### Impact of additional covariates
+#### Impact of additional covariates {#cprd-impact-additional-covar}
 

### 2021-12-13 06-Chp-IPD-Analysis.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

@@
 
-Individual participant data (IPD) meta-analyses are a special type of meta-analysis where those undertaking the study contact the authors of relevant studies to request access to the raw data on each participant.
-This is different to the meta-analyses presented in the previous chapter, which used published summary results.
+Individual participant data (IPD) meta-analyses are a special type of meta-analysis
+in which the authors of relevant studies are contacted with requests to access the raw data on each participant in the original study.
+This approach is different to the meta-analyses presented in the previous chapter, which used published summary results.
 
@@
 
-To examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
+In order to examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
 However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested access.
@@
 
-The reasons for the low response rate to requests for data are explored. Finally, I suggest future studies to investigate how data access rates could be improved.
+The reasons for the low response rate to requests for data are explored in this chapter. Finally, I suggest future studies to investigate how data access rates could be improved.
 
@@
 Individual participant data (IPD) meta-analyses are considered to be the gold standard form of evidence synthesis, allowing for the application of a common selection model and analytical approach across all identified cohorts.[@riley2010] They are particularly useful when investigating the impact of participant-level characteristics, something that is not possible with aggregate data unless the results are stratified by the characteristic of interest.[@riley2010;@thompson2005] Knowledge of which groups a treatment will benefit most (or harm least) is a core aim of the move towards personalised medicine.[@riley2020;@hingorani2013]
-IPD analysis also offer a mechanism by which previously unanalysed datasets can be incorporated into an analysis, thus expanding the evidence base for a particular research question.
+IPD analyses also offer a mechanism by which previously unanalysed datasets can be incorporated into an analysis, thus expanding the evidence base for a particular research question.
 
@@
 
-As such, the aims of this analysis are two fold: firstly, to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the effect of lipids on dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortia of dementia cohorts.
-
-<!-- TODO Read this[@riley2020] -->
+As such, the aims of this analysis are two fold: firstly, to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the relationship between lipids and dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortium of dementia cohorts.
 
@@
 ## Methods
-
-<!-- TODO Should this be reported in relation to the PRISMA-IPD statement -->
 
@@
 
-Eligible data sources for this analysis were prospective cohort studies.
+Eligible data sources for this analysis were prospective cohort studies (see Section \@ref(ipd-apply-access) for details on how these studies were identified).
 Data sources which were cross-sectional, either by design or due to the available data (e.g.
-a study conducted across multiple waves, but only data from a single wave could be accessed) were excluded.
-Similarly, studies making use of population-level electronic health records, which often require an extensive project proposals in order to gain access to the data, were ineligible due to the time and cost involved in applying.
-No restrictions were put on the number of participants or the length of follow-up, though participants must be free of dementia (or assumed to be free, based on age at entry)  at baseline.
+a study recorded data on participants at multiple time-points or "waves", but only data from a single wave could be accessed) were excluded.
+Similarly, due to the time and cost restraints within the scope of my thesis project, studies making use of population-level electronic health records were ineligible.
+These studies are problematic in that they often require extensive project proposals in order to gain access to the data.
+
+No restrictions were put on the number of participants or the length of follow-up, though it was a requirement that participants were dementia free (or assumed to be dementia free, based on age at entry) at baseline.
 
@@
 I considered four blood lipid fractions as part of this analysis, namely: total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides (TG).
-Cohorts were eligible for inclusion if they contained data on at least one of these in a continuous format (i.e.
+Cohorts were eligible for inclusion if they contained data on at least one of these recorded as a continuour variable (i.e.
 studies with binary "hypercholesteromemia" would be excluded).
@@
 
-### Applying for data access
+### Applying for data access {#ipd-apply-access}
 
 Potentially eligible data sources as defined above were identified via two mechanisms, each with a distinct focus.
-For both approaches, the number of cohorts responding to the request for data access, and where applicable, the reasons given for a refusal were recorded.
+For both approaches, the number of cohorts responding to the request for data access and, where applicable, the reasons given for a refusal were recorded.
 
@@
 The second approach focused on incorporating relevant, previously-unanalysed data into the analysis, thus providing additional evidence on the relationship between blood lipids and dementia risk.
-This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application processs for all cohorts with the intent of making it easier to access data from existing data sources.
+This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application process for all cohorts with the intent of making it easier to access data from existing data sources.
 
@@
 
-Where data on one of these exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
+Where data on one of the exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
 Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
@@
 
-Missing data in this analysis was classified as either relating to missing values (a cohort collected data on a variable of interest, but some values are missing) or missing variables (a cohort did not collect data on a variable of interest).
+Missing data in this analysis was classified as either relating to missing values (a data on a variable of interest was available in a cohort, but some values were missing) or missing variables (a cohort did not collect data on a variable of interest).
 Variables with missing values were identified, and 20 imputed datasets were created.[@sterne2009] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the `mice` package in R.
 
-Missing variables were originally intended to be addressed using a previously described method.[@fibrinogenstudiescollaboration2009] Here, the correlation between the fully-adjusted and partially-adjusted estimate in cohorts with the full set of covariates is used to estimate the fully-adjusted effect in those cohorts missing covariates.
+Missing variables were originally intended to be addressed using a previously published method.[@fibrinogenstudiescollaboration2009] Here, the correlation between the fully-adjusted and partially-adjusted estimate in cohorts with the full set of covariates is used to estimate the fully-adjusted effect in those cohorts missing covariates.
 However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
-As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were analysed adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, diabetes).
-As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education, ethnicity, and prevalent ischemic heart disease and BMI).
+As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, diabetes).
+As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education, ethnicity, prevalent ischemic heart disease (IHD) and BMI).
 Results between the common-set-adjusted (Model 1) and maximally-adjusted (Model 2) models were then compared.
@@
 
-In this analysis, a two-stage IPD analysis was planned.
+In terms of the analytic approach taken, a two-stage IPD analysis was used.
 Under a two-stage approach, estimates for the effect of each lipid fraction on incident dementia were first calculated for each data source.
 More specifically, a logistic regression model adjusted for relevant covariates as detailed in the above section was used to quantify the effect of a 1 _mmol/L_ increase in each lipid fraction on each dementia outcome.
+
 Results were expressed as odds ratios (OR).
@@
 A two-stage IPD approach was employed for a number of reasons.
-Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to analyse themselves following a specified analysis plan.[@riley2010] Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
+Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to btain the effect estimates themselves, following a specified analysis plan, and share these with the IPD team.[@riley2010] Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
 Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
-
-<!-- TODO Need to state that using a fixed effect model for the interaction terms -->
 
@@
 
-In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, interaction terms for lipid-covariate terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid~dementia relationship in a study which contains only female participants.
-All interaction analysis were performed using the common-set-adjusted model (Model 1).
+In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, lipid-covariate interaction terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] All interaction analysis were performed using the common-set-adjusted model (Model 1).
+To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid/dementia relationship in a study which contains only female participants.
 
-<!-- QUESTION   -->
+<!-- TODO Explain why a fixed effect model was used. -->
 
@@
 
-<!-- Need exact number from each approach, plus detailed exclusion reasons -->
-
 Of the `r n_applied$total` studies to which I applied for data access, only three (`r paste0(comma((n_accessed$total/n_applied$total)*100),"%")`) were included in the final analysis.
-Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via DPUK portal.
+Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via the DPUK portal.
 In addition, the reasons for cohorts not being included in the analysis are presented, where available, stratified by application approach.
@@
 
-(ref:cohortFlowchart-cap) Flowchart of included cohorts, stratified by identification method (systematic review vs DPUK).
+(ref:cohortFlowchart-cap) __Flowchart detailing sources of data for the IPD analysis__ The number of cohorts approached and the reasons for exclusion are summarised, stratified by identification method (systematic review vs DPUK).
 
-(ref:cohortFlowchart-scap) Flowchart
+(ref:cohortFlowchart-scap) Flowchart detailing sources of data for the IPD analysis
 
@@
 
-The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] Data provided by this cohort for the analysis, dementia was ascertained at at the 5th Health Checkup (2016-2018), giving between 18-25 years of follow-up.
-The added evidential value of the EPIC cohort is small, given the the fact that the data obtained contains only 8 dementia events.
+The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] Data provided by this cohort for the analysis, dementia was ascertained at at the 5th Health Checkup (2016-2018), providing between 18-25 years of follow-up.
+The added evidential value of the EPIC cohort is small, given the fact that the data obtained contains only 8 dementia events.
 The cohort contains no information on dementia subtype, while all covariates of interest bar _Apo_$\mathcal{E}4$ were available.
@@
 The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] Lipids measurements were available from the third wave of the study, conducted between 1991-1993.
-The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] HES data for dementia outcomes was avaialle up to March 2015, providing between 22-24 years of follow-up.
+The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] HES data for dementia outcomes was available up to March 2015, providing between 22-24 years of follow-up.
 Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
@@
 
-Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was was possible.
+Of note, the Whitehall II cohort was analysed in one of the included studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading),[@tynkkynen2018] meaning that a comparison between the published result and the analysis reported here was possible.
 
@@
 A key consideration in the definition of covariates across cohorts was the classification of age.
-The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age band (e.g.
+The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age bands (e.g.
 40-44, 45-49, etc.).
@@
 <!-- TODO Note here about how the IHD variable in CAPS has a note saying there might be an issue with the variables, while the Whitehall study uses narrow range of codes to define CHD.
-EPIC is selfreported angina/mi/arrythmia -->
+EPIC is self-reported angina/mi/arrythmia -->
 
@@
 
-The results from the main effect analysis across the varying lipid fractions on each dementia,  considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
+The results from the main effect analysis across the varying lipid fractions on each dementia outcome considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
 There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
-
-<!-- REVIEW Present main effect for WhiteHall AD analysis - or rather highlight that it is shown in Figure XXX in comparison with Tynken -->
+For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd-cap))
 
@@
 
-Given minimal effect of further adjustment for education and BMI on the effect estimates, the results from the interaction analysis presented here were obtained using the common-set-adjusted model.
-Further, while the maximally-adjusted model (Model 2) could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, employing the same underlying model helped to ensure comparability between the age and sex interaction estimates.
+Given the minimal effect of further adjustment in the maximally-adjusted model, the common-set-adjusted model (Model 1) was used to perform the interaction analyses.
+
+The maximally-adjusted model (Model 2) could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, leaving the EPIC and Whitehall cohorts, both of which had a full complement of covariates.
+However, I decided to employ the same underlying model across the interaction analyses to aid comparability between the age and sex interaction estimates.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaAge-cap)  Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/all-cause dementia association
+(ref:interactionDementiaAge-cap)  __Meta-analysis of age-lipid interaction terms for all-cause dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
+Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes).
 
-(ref:interactionDementiaAge-scap) shortcap
+(ref:interactionDementiaAge-scap) Meta-analysis of age-lipid interaction terms for all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaSex-cap) Meta-analysis of interaction terms representing the effect of male gender on the lipid/all-cause dementia association
+(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
 
-(ref:interactionDementiaSex-scap) shortcap
+(ref:interactionDementiaSex-scap) Meta-analysis of sex-lipid interaction terms for all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionVascularAge-cap) Meta-analysis of interaction terms representing the effect of a one-step increase in age group on the lipid/vascular dementia association
+(ref:interactionVascularAge-cap) __Meta-analysis of age-lipid interaction terms for vascular dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
+Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes).
 
-(ref:interactionVascularAge-scap) shortcap
+(ref:interactionVascularAge-scap) Meta-analysis of age-lipid interaction terms for vascular dementia
 
@@
 No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia.
-Similarly, there was weak evidence for an interaction of the effect of lipids levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
+Similarly, there was weak evidence for an interaction of the effect of lipid levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
 
@@
 
-The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences in the association of lipids with dementia outcomes between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD analysis.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in application of the methods in addition to providing additional evidence sources that could be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
+The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences in the association of lipids with dementia outcomes between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD analysis.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in application of the methods in addition to providing new evidence that will be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
 
@@
 
-A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtained data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.[@nevitt2017] However, it is assumed that a ~10% response rate is at the lower end of the scale.
+A low response rate is not unexpected, given that a review of IPD studies published between 1987 and 2015 found that fewer than half managed to obtain data from greater than 80% of studies, and that in many cases, the exact percentage of studies for which data was obtained was not accurately reported.[@nevitt2017] However, it is assumed that the ~10% response rate encountered in this analysis is at the lower end of the scale.
 
-There are likely several likely reasons for this low response rate to requests for data access.
-In general terms, there are a several well-documented barriers that prevent data from being made readily available, including concerns regarding participant privacy, fear of "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, IPD meta-analysis including studies other than randomised controlled trials have less success in obtaining IPD from studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit a positive response than a well-known senior academic might.
+There are many likely reasons for this low response rate to requests for data access.
+In general terms, there are several well-documented barriers that prevent data from being made readily available, including concerns regarding participant privacy, fear of "scooping" or "parasitic" behaviour, and a lack of trust between primary and secondary researchers.[@vanpanhuis2014] More specific to this analysis, IPD meta-analysis including studies other than randomised controlled trials have less success in obtaining IPD from previous published studies.[@nevitt2017] Additionally, while no evidence is available on whether the characteristics of the researcher who is requesting data access influences the response rate and eventual decision, there is the possibility that my position as a PhD student meant I was less likely to elicit a positive response than a well-known senior academic might.
 The timing of the requests for data access, coinciding with a global pandemic, may also have affected the response rate as researchers prioritised COVID-related work.
 
-Finally, the method of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning.[@danko2019] One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
+Finally, in investigating the potential reasons for the low response rate, I discovered that the method of contact used (email) has been shown to be less successful in eliciting responses from authors when compared with telephoning (which was not used in this analysis).[@danko2019] One of the reasons for this may be that the email addresses reported on publications are more likely to be out of date for older publications.
 Anecdotally, post-hoc investigation of a subset of cohorts revealed that several corresponding/first authors were no longer at the same institution as when the study was reported, and as a result, were unlikely to have access to the institutional email address listed on the study publication.
+Despite attempts to track authors as they move between institutions, out-of-date contact details may have contributed to the low response rate.
 
@@
 The response rate among DPUK cohorts a year after application was just 50%.
-In addition, some cohorts responded that that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
-In light of this, a centralised database of ongoing analysis being performed in DPUK would be of enormous help.
+In addition, some cohorts responded saying that the proposed study question was already under investigation by another group, and that they would not share the data on this basis.
+In light of this, a centralised database of ongoing analyses being performed using DPUK data would be of enormous help, reducing research waste and providing opportunities for collaboration.
 Finally, the DPUK process would be aided by a clearer distinction between those cohorts that are "DPUK native" (i.e.
@@
 
-More generally, systematically missing variables meant that a trade-off between inclusion of cohort data and appropriate control for confounding was required, resulting in the potential for uncontrolled confounding due to education and BMI.
-However, sensitivity analysis comparing the commom-set-adjusted (Model 1) and fully-adjusted (Model 2) models in cohorts with a full complement of covariates indicated that further adjustment for BMI and education had minimal impact on the effect estimates.
+More generally, systematically missing variables required a trade-off between inclusion of cohort data and appropriate control for confounding.
+The final choice of the common-set-adjusted model for use in the interaction analyses mean there is the potential for residual confounding.
+However, sensitivity analysis comparing the common-set-adjusted (Model 1) and fully-adjusted (Model 2) models in cohorts with a full complement of covariates indicated that further adjustment for BMI, ethnicity, education and prevalent IHD had minimal impact on the effect estimates.
+Of note, this is comparable with the analysis of the CPRD data presented in the previous chapter, where adjustment for variable beyond age and sex had a limited impact on the observed effect estimates (see Section \@ref(cprd-impact-additional-covar)).
 
@@
 Tynkkynen _et al._[@tynkkynen2018] analysed the association of blood lipids and risk of all-cause dementia and Alzheimer's disease across several cohorts, including the Whitehall II cohort.
-
 In an attempt to validate my approach, I compared the results from the maximally-adjusted model (Model 2) in this analysis with those reported by Tynkkynen _et al._ for both all-cause dementia and Alzheimer's disease.
 
-The results for the Alzheimer's disease outcome were comparable (Appendix \@ref(appendix-ipd-whitehall)).
+The results for the Alzheimer's disease outcome were comparable (Figures \@ref(fig:whitehallComparisonAd))).
 However, for the vascular dementia outcome (Figure \@ref(fig:whitehallComparisonDementia)), I identified a discrepancy in the association of triglycerides with all-cause dementia estimated by the two analyses.
@@
 <!----------------------------------------------------------------------------->
-(ref:whitehallComparisonDementia-cap) Comparison of results across the two analysis of the Whitehall II cohort for the all-cause dementia outcome.
+(ref:whitehallComparisonDementia-cap) Comparison of results across the two analyses of the Whitehall II cohort for the all-cause dementia outcome.
 
-(ref:whitehallComparisonDementia-scap) Comparison of results across the two analysis of the Whitehall II cohort
+(ref:whitehallComparisonDementia-scap) Comparison of results across the two analyses of the Whitehall II cohort
 
@@
 
+<!----------------------------------------------------------------------------->
+(ref:whitehallComparisonAd-cap) Comparison of results across the two analyses of the Whitehall II cohort for the Alzheimer's disease outcome.
+
+(ref:whitehallComparisonAd-scap) Comparison of results across the two analyses of the Whitehall II cohort
+
+```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
+knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_ad.png"))
+```
+<!----------------------------------------------------------------------------->
+
 <!-- TODO Talk about the fact that I used multiple imputation and they did not. Evidenced by wider confidence intervals, indicating a smaller sample size, likely the result of a complete case -->
@@
 Investigation revealed several possible reasons for this discrepancy.
-The first is that it was likely to be due to the Whitehall snapshot that each analysis had access to, as comparison of summary statistics indicated that this analysis had substantially more dementia events (N =287 in this analysis vs.
-n=114 in Tynkkynen _et al._).
-Additionally, this analysis uses multiple imputation to address missing data, while the Tynkkynen _et al._ does not mention how missing data was addressed, though the reduced precision in the estimates suggest a complete case analysis.
-Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data, allowing it to adjust for _Apo_$\mathcal{E}4$ status.
+The first is that while this analysis uses multiple imputation to address missing data, the Tynkkynen _et al._ analysis does not describe how missing data was handled.
+However, the reduced precision in the reported estimates suggest a complete case analysis.
+This interpretation is supported by a comparison of summary statistics, which illustrated that my analysis had substantially more dementia events (N =287 in this analysis vs.
+n=114 in Tynkkynen _et al._), suggesting that incomplete records were discarded in the previous analysis.
+Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data allowing it to adjust for _Apo_$\mathcal{E}4$ status.
 However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
@@
 
-While this analysis did not manage to systematically obtain and analyse a large proportion of identified data, a central strength of this analysis is the use of a systematic approach to identify and attempt to contact relevant cohorts.
+While this analysis did not manage to obtain and analyse a large proportion of identified data, a central strength of this analysis is the use of a systematic approach to identify and attempt to contact relevant cohorts.
 Further, it also enabled incorporation of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - thus providing additional evidence that is used in the triangulation exercise reported in Chapter \@ref(tri-heading).
 
-A further strength of this analysis was the ability to investigate the effect of participant characteristics (namely age and sex) on the association of blood lipids and dementia outcomes.
+A further strength is the ability of this analysis to investigate the effect of participant characteristics (namely age and sex) on the association of blood lipids and dementia outcomes.
 To the best of my knowledge, no previous review has examined the interaction of these factors with the observed associations.
@@
 Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
-While the cohort response rate was substantially lower that expected, given the time and resource of data cleaning and harmonisation for just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of a PhD.
+While the cohort response rate was substantially lower that expected, given the time and resources required for the cleaning and harmonisation of data from just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of a PhD.
 
@@
 
-Additionally, the production of detailed guidance for handling cases where covariates are systematically missing.
+Additionally, the production of detailed guidance for handling cases where covariates are systematically missing would represent a useful addition to the topic.
 Much of the literature around IPD analysis is focused on the synthesis of RCTs, where additional covariate information is needed primarily for the assessment of treatment-covariate interactions rather than the adjustment of the effect estimate for confounding.
@@
 I highlighted the contribution of this work to the wider topic via the analysis of previously unexplored cohorts (CaPS & EPIC) and outcomes (vascular dementia).
-Finally, I recommended that future research formally investigate the impact of requestor characteristics on requests for data.
+Finally, I recommended that future research formally investigate the impact of the characteristics of the requesting researcher on data access rates.
 

### 2021-12-13 07-Chp-Triangulation.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

@@
 
-<!-- Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
+In epidemiology, triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
 Different sources of evidence will have different limitations.
 If the result from each source points towards the same answer, this improves our confidence in the conclusion.
--->
+Triangulation can either be _qualitative_ or _quantitative_.
+In qualitative triangulation, the results of each evidence source are discussed.
+In contrast, quantitative triangulation aims to combine the different results mathematically to obtain one single overall result.
 
-__TBC__
+&nbsp;
+
+In this chapter, I describe a new approach for quantitative triangulation, which combines two existing methods.
+For each source of evidence, I assess and account for robustness (do we believe the result, based on the methods/results of the study?) and relevance (does the source provide useful evidence relevant to the question we are interested in?).
+To showcase the new method, I apply it to two questions of interest.
+In each case, evidence from each of the previous chapters is combined to give an overall result.
+
+&nbsp;
+
+When combined in the new framework, the results produced by previous chapters did not support an effect of low-density lipoprotein cholesterol (LDL-c) on Alzheimer's disease nor an effect of triglycerides on vascular dementia.
+I close the chapter by suggesting future work to further develop the new methods presented.
 
@@
 
-<!-- Triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
-Different sources of evidence will have different limitations.
-If the result from each source points towards the same answer, this improves our confidence in the conclusion.
--->
+&nbsp;<!----------------------------------------------------------------------->
 
-&nbsp;<!----------------------------------------------------------------------->
+<!-- TODO Need to define exposures and acronyms early so that I can use abbrev in results -->
 
@@
 
-Additionally, both the qualitative and quantitative triangulation exercises used the the detailed risk-of-bias assessments performed and presented as part of the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)).
+Additionally, both the qualitative and quantitative triangulation exercises used the detailed risk-of-bias assessments performed and presented as part of the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)).
 Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis.
@@
 
-Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) both found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC `r obsLipids$Dementia_TC$estimate`; LDL-c `r obsLipids$Dementia_LDL$estimate`; HDL-c `r obsLipids$Dementia_HDL$estimate`; triglycerides `r obsLipids$Dementia_TG$estimate`).
+Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC - `r obsLipids$Dementia_TC$estimate`; LDL - `r obsLipids$Dementia_LDL$estimate`; HDL - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate`).
 Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
-Finally, a meta-analysis of RCTs of statin use (`r rct_statin_acd`) and of MR analyses of genetic instruments that mimic statin use (`r mrStatin$Dementia$estimate`) both found weak evidence of an association, providing indirect evidence on the effect of lipid lowering on this outcome.
+Finally, a meta-analysis of RCTs of statin use (`r rct_statin_acd`) and of MR analyses of genetic instruments that mimic statin use (`r mrStatin$Dementia$estimate`) found weak evidence of an association, providing indirect evidence on the effect of lipid lowering on this outcome.
 
-In contrast, the meta-analysis of NRSI of statin use found a slight protective effect (`r obsStatins$Dementia$estimate`), though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the intervention.
+In contrast, the meta-analysis of NRSI of statin use found a slight protective effect for the all-cause dementia outcome (`r obsStatins$Dementia$estimate`), though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the statin use.
 Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(cprd-analysis-heading)) found evidence of a harmful association (`r anydem_sta_text`), though this is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
 
-For fibrates, an alternative lipid-regulating agent, there was some evidence of an increased risk of all-cause dementia in the CPRD (`r anydem_fib_text`), though this did not replicate in the meta-analysis of previous studies examining the association of fibrates and all-cause dementia (`r obsFibrates$Dementia$estimate`).
+For fibrates, an alternative lipid-regulating agent, there was some evidence of an increased risk of all-cause dementia in the CPRD (`r anydem_fib_text`), though this was not consistent in the meta-analysis of previous studies examining the association of fibrates and all-cause dementia (`r obsFibrates$Dementia$estimate`).
 
@@
 
-Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (TC `r obsLipids$AD_TC$estimate`; LDL-c `r obsLipids$AD_LDL$estimate`; HDL-c `r obsLipids$AD_HDL$estimate`; triglycerides `r obsLipids$AD_TG$estimate`).
+Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (TC - `r obsLipids$AD_TC$estimate`; LDL - `r obsLipids$AD_LDL$estimate`; HDL - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`).
 Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`).
@@
 However, the CPRD analysis, which attempted to account for this potential bias through the use of time-varying treatment indicator, found weak evidence for an effect (`r probad_sta_text`).
-This validity of this finding was limited by the potential for differential misclassification on the basis of the exposure in the CPRD analysis.
+The validity of this finding was limited by the potential for differential misclassification on the basis of the exposure in the CPRD analysis.
 
-Finally, the IPD analysis provided no additional information on the Alzheimer's disease outcome, as a previously published analysis examined the association of lipid levels with this outcome in the Whitehall II cohort.
-The published analysis was included in the meta-analysis of NRSE, the results of which are presented above.
+Finally, only one of the three cohorts included in the IPD analysis (Whitehall II) contained data on Alzheimer's disease.
+However, a previously published analysis (Tynkkynen _et al._[@tynkkynen2018]) examining the association of lipid levels with Alzheimer's disease in the this cohort was identified by the systenatic review.
+The results of this previous analysis are incorporated into the results of the meta-analysis reported above, and so the IPD analysis provided no new information on this outcome.
 
@@
 The IPD analysis provided supporting evidence for the absence of an effect of any fraction on vascular dementia, with the sole exception of triglycerides.
-Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts (`r ipd_vasdem`), though there is the potential for uncontrolled confounding due to the limited information on covariates available.
+Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts (`r ipd_vasdem`), though there is the potential for uncontrolled confounding due to the limited information available on important covariates.
 With respect to evidence on treatments for hypertriglyceridemia, examination of fibrates in the CPRD provided weak evidence of an association with vascular dementia (`r vasdem_fib_text`).
@@
 This approach incorporates recent advancements in the way that bias in results is assessed (namely the move to domain-based assessment tools)[@sterne2019] and existing methods for bias-/indirectness-adjusted meta-analysis[@turner2009] to integrate the numerical results of the multiple approaches.
-The absence of any clear signals across the evidence base, as detailed in the previous section, does not make for particularly interesting case studies but I will nonetheless use the identified evidence to illustrate the novel methodological approach.
+Despite the absence of any clear signals across the evidence base, as detailed in the previous section, I have used the evidence identified and produced by this thesis to illustrate the novel methodological approach.
 
@@
 
-The proposed framework involves several steps, described in detail in the following sections. In summary, these steps are:
+The proposed framework involves the following steps:
 
 1. Define the causal question of interest
-1. Identify of relevant evidence sources and standardise effect directions
+1. Identify relevant evidence sources and standardise effect directions
 1. Specify idealised version of each study
@@
 
-In order to illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate is described in detail for a single result.
-Following this, the framework is applied to two case studies, as defined below.
+Each step is described in comprehensive detail in the sections below.
+To better illustrate the bias-/indirectness adjustment process detailed in the subsequent sections, the process for calculating the adjusted estimate is described in detail for a single result.
+Following this, the framework is then applied to two case studies.
 
@@
 These causal questions were chosen for several reasons.
-Firstly, work presented in previous chapters had identified some evidence for an association in these exposure/outcome pairs.
+Firstly, the work presented in the previous chapters had identified some evidence for an association in these exposure/outcome pairs.
 Secondly, given the long prodomal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period are particularly important.
-Finally, examining the causal impact of a lipid faction on a specific outcome (e.g.
+Finally, examining the causal impact of a lipid fraction on a specific outcome (e.g.
 Alzheimer's disease), rather than a composite outcome (e.g.
 all-cause dementia), focuses on an single causal pathway rather than including several conditions in the outcome definition that likely have very different mechanisms of disease.
-In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(cprd-confounding-by-ind)), and use of an composite all-cause outcome in the triangulation framework may mask this.
+In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(cprd-confounding-by-ind)), and the use of a composite all-cause outcome in the triangulation framework may mask this.
 
@@
 
-Once the set of relevant results were identified, effects were standardised to refer to the risk resulting from a "reduction" in the lipid fraction.
+Effects were standardised to refer to the risk resulting from a "reduction" in the lipid fraction.
 For both non-randomised studies and Mendelian randomisation analysis of lipid levels, the association is usually reported per 1-SD increase in the lipid fraction.
@@
 
-<!-- TODO The results should be standarised before calculating direction of effect, because other-wise it is pulling it in the wrong direction -->
+<!-- TODO The results should be standarised before calculating direction of effect, because other-wise it is pulling it in the wrong direction - YOU NEED TO SAY THIS LATER! -->
 
@@
 Of note, no mapping was performed for the critical risk-of-bias levels present in the tools for non-randomised studies.
-This is because current best practice in evidence synthesis is to exclude all studies at critical risk of bias for further quantitative synthesis.[@sterne2016]
+This is in accordance with current best practice in evidence synthesis, which is to exclude all studies at critical risk of bias from further quantitative synthesis.[@sterne2016]
 
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:robLevelsMapping-caption) Mapping of the different acceptable levels of bias across the assessment tools to a harmonised set.
-Note that no mapping for "Critical" risk of bias was performed, as best practice reccommends that studies at critical risk of bias are excluded from quantitative syntheses.
+(ref:robLevelsMapping-caption) __Mapping of risk-of-bias judgements across assessment tools__ The different acceptable levels of bias across the risk-of-bias assessment tools used were mapped to a harmonised set.
+Note that no mapping for "Critical" risk of bias was performed, as best practice recommends that studies at critical risk of bias are excluded from quantitative syntheses.
 
@@
 
-In addition to assessing the extent of bias, as defined by the three levels detailed above, I attempted to record the predicted direction and type of bias in each domain.
+In addition to assessing the extent of bias, as defined by the three levels detailed above, I recorded the predicted direction and type of bias in each domain.
 This was achieved via an additional question at the end of each bias domain, which asked assessors to predict the expected direction of bias in that domain.
@@
 * "Unpredictable"
+
+<!-- REVIEW Is it worth explaining the terms experimental and comparator above? -->
 
@@
 
-(ref:exampleDirection-cap) Illustration of calculating the absolute direction of biases (indicated by arrows), based on bias type.
-For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null - bias "favouring the comparator" will always pull the effect estimate to the right, and can induce a change from a protective to harmful effect.
+(ref:exampleDirection-cap) __Calculating the absolute direction of biases, based on bias type__ - For additive biases, the direction is consistent regardless of the position of the effect estimate relative to the null - bias "favouring the comparator" will always pull the effect estimate to the right and can induce a change from a protective to harmful effect.
 In contrast, the position of the effect estimate is accounted for when determining the absolute direction of proportional biases, defined as towards or away from the null.
 
-(ref:exampleDirection-scap) Illustration of calculating the absolute direction of biases, based on bias type.
+(ref:exampleDirection-scap) Illustration of calculating the absolute direction of biases, based on bias type
 
@@
 Following definition of the extent, type and direction of bias in each domain, I assigned a prior distribution on the log scale to each combination.
-For example, a "high" additive bias in $j$th domain of the $i$th study is defined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution:
+For example, a "high" additive bias in $j$th domain of the $i$th study is defined as $\delta_{i,j}^{\mathrm{High}}$ and uncertainty around this estimate is given by a distribution with mean $\mu$ and variance $\sigma^{2}$:
 
 \begin{equation}
-  \delta_{i,j}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, \sigma_{i,j}^{\mathrm{High}})
-  (\#eq:name)
+  \delta_{i,j}^{\mathrm{High}} = f(\mu_{i,j}^{\mathrm{High}}, {\sigma_{i,j}^{\mathrm{High}}}^{2})
+  (\#eq:additive-single)
 \end{equation}
@@
 
-(ref:priorsAdd-caption) Prior distributions for extent and type of bias under two scenarios, on the log scale.
-Note that the distributions for proportional biases were kept consistent across the two scenarios.
+(ref:priorsAdd-caption) __Prior distributions mapped to different extents of bias.__ Prior values assigned to additive and proportional biases, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$.
+For additive biases, two scenarios were defined (see main text).
+Note that proportional biases are defined on the log scale for ease of calculation, but are exponentiated prior to their use for adjustment.
 
@@
 In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate but does increase the uncertainty around it.
+
+Under the  method reported in Turner _et al._,[@turner2009], total additive bias (denoted using subscript $\delta$) in result $i$ is then described by mean $\mu_{i\delta}$ and variance $\sigma_{i\delta}^{2}$, which are simply the sum of the mean and variance of all additive biases in the $i$th result.
+Similarly, the total proportional bias (denoted using subsript $\beta$) in the $i$th result is described by mean $\mu_{i\beta}$ and variance ${\sigma_{i\beta}}^2$.
+This are defined as
+
+\begin{equation}
+  \mu_{i\beta} = exp(\alpha_{i} + {\psi_i}^2)
+  (\#eq:prop-total-mean)
+\end{equation}
+
+\begin{equation}
+  {\sigma_{i\beta}}^2 = \big\{ exp({\psi_{i}}^2)-1 \big\} exp({2}{\alpha_{i}} + {\psi_{i}}^2)
+  (\#eq:prop-total-var)
+\end{equation}
+
+where $\alpha_i$ and ${\psi_i}^2$  are the the sum of mean and variance values for all proportional biases in the $i$th result.
+
+Note that the total additive bias is maintained on the log scale, while the total proportional bias has been exponentiated.
 
@@
 
+Once the extent and direction of indirectness has been assessed, total proportional indirectness is then calculated in the same manner as total proportional bias (see Equations \@ref(eq:prop-total-mean) & \@ref(eq:prop-total-var)).
+
 &nbsp;<!----------------------------------------------------------------------->
 
-####	Combine in a bias-adjusted meta-analysis
+####	Combining in a bias-adjusted meta-analysis
 
-Using the the method reported in Turner _et al._,[@turner2009] total additive and proportional bias and indirectness were calculated and used to define an adjusted estimate for each result included in the synthesis.
+Using the the method reported in Turner _et al._,[@turner2009] once total additive and proportional bias and indirectness are calculated, they are used to define an adjusted estimate for each result included in the synthesis.
 
-The adjusted estimate for each result, $\hat\theta$, is defined as:
+The adjusted estimate for result $i$, $\hat{\theta}_i$, is defined as:
 
@@
 \begin{equation}
-  \hat{\theta} = \frac{y_i - \mu_{i\beta}^{\mathrm{In}}\mu_{i\delta}^{\mathrm{In}} - \mu_{i\delta}^{\mathrm{B}}}{\mu_{i\beta}^{\mathrm{B}}\mu_{i\beta}^{\mathrm{In}}}
+  \hat{\theta}_i = \frac{y_i - \mu_{i\beta}^{\mathrm{In}}\mu_{i\delta}^{\mathrm{In}} - \mu_{i\delta}^{\mathrm{B}}}{\mu_{i\beta}^{\mathrm{B}}\mu_{i\beta}^{\mathrm{In}}}
   (\#eq:adjusted-mean)
@@
 Once each individual result had been adjusted using this approach, I performed a random effects meta-analysis using the unadjusted and adjusted results.
-I also compared the adjusted results under the two scenarios of additive bias defined.
-results.
+I also compared the adjusted results under the two scenarios of additive bias.
 I extracted the overall effect estimates, along with measures of heterogeneity in each case ($\tau^2$, $I^2$).[@higgins2003; @higgins2008]
@@
 In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure.
-Here, history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experimental_ (in this case, an intervention).
+Here, a history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experimental_ (in this case, an intervention).
 As such, the absolute direction of bias is to the left.
@@
 
-(ref:biasDirectionSingle-scap) Bias direction plot for a single study
+(ref:biasDirectionSingle-scap) Bias direction plot example for a single study
+
 ```{r biasDirectionSingle, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:biasDirectionSingle-cap)', out.width='100%', fig.scap='(ref:biasDirectionSingle-scap)'}
@@
 In addition, I found it more useful to articulate the indirectness of a result in tabular format.
-With respect to this example result, I judged it to be a low risk in the population and outcome domains (Table \@ref(tab:singleIndirect-table)).
+With respect to this example result, I judged it to be at low risk in the population and outcome domains (Table \@ref(tab:singleIndirect-table)).
 However, the result refers to the effect of statins on Alzheimer's disease risk, rather than LDL-c levels directly, putting it at high risk of indirectness in the intervention/exposure domain.
-Assessing the predicted direction of indirectness was more challenging than assessing the predicted direction of bias.
-In this case, treatment with statins result in temporary lowering of lipid levels which and could thus underestimate the true effect of LDL-c lowering (indirectness towards the null).
-In contrast, statins may have an effect on Alzheimer's disease through a mechanism other than LDL-c lowering effect of statins and so the effect is overestimated (indirectness away from null).
+Overall, assessing the predicted direction of indirectness was more challenging than assessing the predicted direction of bias.
+In this case, treatment with statins may result in temporary lowering of lipid levels which could thus underestimate the true effect of LDL-c lowering (indirectness towards the null).
+In contrast, statins may have an effect on Alzheimer's disease through a mechanism other than their LDL-c lowering effect and so the effect may be overestimated (indirectness away from null).
 As such, I judged the direction of indirectness in this domain to be unpredictable.
@@
 
-(ref:ldlAdBiasDirection-scap) Bias direction plot, summarising internal biases
+(ref:ldlAdBiasDirection-scap) Bias direction plot for LDL-c/Alzheimer's disease
 
@@
 
-(ref:tgVadBiasDirection-scap) shortcap
+(ref:tgVadBiasDirection-scap) Bias direction plot for triglycerides/vascular dementia
 
@@
 
-This chapter has narratively synthesised the evidence identified and produced by the previous chapters, highlighting the absence of any consistent association between any blood lipid and any dementia outcome.
+This chapter has narratively synthesised the evidence identified and produced by the previous chapters, highlighting the absence of any consistent association between various blood lipid fractions and any dementia outcome.
 
-In addition, it has sought to provide a generalised framework for quantitative triangulation, building on existing methods for systematic domain-based risk of bias assessment and bias-/indirectness-adjusted meta-analysis.
+In addition, it has developed a generalised framework for quantitative triangulation, building on existing methods for systematic domain-based risk of bias assessment and bias-/indirectness-adjusted meta-analysis.
 To illustrate the method, I considered two causal questions: the effect of LDL-c at mid-life with Alzheimer's disease and the effect of triglycerides on vascular dementia.
@@
 
-The quantitative analysis presented in this chapter is subject to some strong methodological limitation, which are discussed in detail below.
+The quantitative analysis presented in this chapter is subject to some strong methodological limitations, which are discussed in detail below.
 
@@
 
-The key limitation of the quantitative synthesis presented in this chapter is the lack of empirical evidence available for the prior distributions for bias and indirectness.
+The key limitation of the quantitative synthesis presented in this chapter is the lack of empirical evidence available for the prior distributions of bias and indirectness.
 While I attempted to address this by informing the prior distributions using data from a previous expert elicitation exercise, the extent of bias/indirectness in that analysis may not generalise to the one presented here.
@@
 As illustrated in Table \@ref(tab:robLevelsMapping-table), studies at critical risk of bias were not included in the analysis.
-While this is in line with best practice, there is theoretically no reason why studies with this extent of bias could not be included in the propsed framework.
+While this is in line with best practice, there is theoretically no reason why studies with this extent of bias could not be included in the proposed framework.
 However, the estimation of an appropriate prior distribution for the effect of "Critical" bias would be substantially more challenging, and so was avoided here.
@@
 
-A final limitation to this analysis is the synthesis of different effect estimates.
+A final limitation of this analysis is the synthesis of different effect estimates.
 As discussed in Section \@ref(sys-rev-analysis-overview), hazard ratios are not directly comparable to odds ratios, as they inherently account for person time-at-risk.[@mckenzie2019] As non-randomised studies (NRSI/NRSI) of dementia outcomes report hazard ratios and Mendelian randomisation studies report odds ratios, the resulting synthesis may be biased by the integration of these two different effect measures.
@@
 
+<!-- TODO An additional strength could be the fact that I explicitly sought to include both direct and indirect evidence -->
+
 The core strength of this analysis is that it is based on a comprehensive systematic review, supplemented by two additional primary studies to fill in the identified evidence gaps.
@@
 Expert elicitation of the extent of bias/indirectness using a panel of methodologists and topic experts is a powerful technique but the point at which it is deployed in the framework is important.
-In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via a elicitation process,[@thompson2011; @turner2009; @wilks2011] during which experts were aware of the results of each analysis.
+In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via an elicitation process,[@thompson2011; @turner2009; @wilks2011] during which experts were aware of the results of each analysis.
 This approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
@@
 Separating the assessment of bias/indirectness from the assignment of modifying values to each judgement will limit the potential for this misclassification.
-Using the framework proposed, reasonable modifying distributions for each level of bias can be defined _a priori_ by the study team using the elicitation procedure detailed previously,[@turner2009] similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016] As an example, expert elicitation could be used to _a priori_ define an additive bias distribution of N(.1,0.7) for "Moderate" risk of bias in Domain 1 of the ROBINS-I tool (bias due to confounding).
-Risk-of-bias assessments are then performed, and each result at "Moderate" risk of bias in Domain 1 is adjusted using this pre-specified distribution.
+Using the framework proposed, reasonable modifying distributions for each level of bias can be defined _a priori_ by the study team using the elicitation procedure detailed previously.[@turner2009] This approach would be similar to how important confounders and co-interventions are defined in advance when performing ROBINS-I/ROBINS-E assessments.[@sterne2016] As an example, expert elicitation could be used to _a priori_ define an additive bias distribution of N(0.1,0.7) for "Moderate" risk of bias in Domain 1 of the ROBINS-I tool (bias due to confounding).
+Risk-of-bias assessments would then be performed, and each result at "Moderate" risk of bias in Domain 1 is adjusted using this pre-specified distribution.
 
-Finally, accounting for bias using an incorrect prior distribution is no less problematic that synthesising and drawing conclusions from effect estimates as if they were unbiased, a common occurrence in systematic reviews.[@katikireddi2015] While this analysis may be limited by the absence of empirically-derived adjustment distributions, it at the very least acknowledges the uncertainty of evidence due to bias/indirectness via a reduction in precision.
+Finally, accounting for bias using an incorrect prior distribution is no less problematic than synthesising and drawing conclusions from effect estimates that are treated as unbiased, a common occurrence in systematic reviews.[@katikireddi2015] While this analysis may be limited by the absence of empirically-derived adjustment distributions, it at the very least acknowledges the uncertainty of evidence due to bias/indirectness via a reduction in precision.
 
@@
 
-Future development of this framework should also account for bias at the analysis level in terms of missing evidence.[@zotero-15123] For example, there is at least one known study relevant to the vascular dementia case study that reported a non-significant result but provided insufficient details to be included in the analysis.[@chiang2007] Ideally, a quantitative triangulation framework would further account for this proportional meta-bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
+Future development of this framework should also account for bias at the analysis level in terms of missing evidence.[@zotero-15123] For example, there is at least one known study relevant to the triglycerides/vascular dementia case study that reported a non-significant result but provided insufficient details to be included in the analysis.[@chiang2007] Ideally, a quantitative triangulation framework would further account for this proportional meta-bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
 
 Appreciation that both the risk-of-bias and indirectness of a result should be assessed is growing.
-Indeed, some existing for the assessment of diagnostic test accuracy[@whiting2011] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
-Future iterations of the core risk-of-bias tools (RoB 2, ROBINS-I, ROBINS-E) could take this into account, though there is an competing argument that indirectness is already handled via tools such as the GRADE framework.[@guyatt2011] In addition, simple steps like harmonising the risk-of-bias judgements across tools and making the direction of bias question mandatory (even if users default to "Unpredictable") would represent an improvement in the tools and encourage users to think about how the biases assessed affect the corresponding result.
+Indeed, some existing tools for the assessment of diagnostic test accuracy[@whiting2011] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
+Future iterations of the core risk-of-bias tools (RoB 2, ROBINS-I, ROBINS-E) could take this into account, though there is a competing argument that indirectness is already handled via tools such as the GRADE framework.[@guyatt2011] In addition, simple steps like harmonising the risk-of-bias judgements across tools and making the direction of bias question mandatory (even if users default to "Unpredictable") would represent an improvement in the tools and encourage users to think about how the biases assessed affect the corresponding result.
 Similarly, software that implements a risk-of-bias tool should allow for direction/extent of bias question and carefully consider how this data will be exported.
@@
 Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
-The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of the bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
+
+<!-- REVIEW Describe what you contributed here a little better --->
 
@@
 
-* I discussed the limitations of this proposed method, given the absence of informative priors for the impact of bias/indirectness, and proposed future research (i.e.
+* I discussed the limitations of this proposed method, given the absence of empirically-based priors for the impact of bias/indirectness, and proposed future research (i.e.
 meta-epidemiological studies) that would address them.

### 2021-12-13 08-Discussion.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion

@@
 
-<!-- TODO Unnumber lay summary -->
-
-__TBC__
+In this final chapter, I describe the results of each previous chapter and compare my results with those of two recent large studies.
+I describe how doctors and those working in public health should use the results of my work, and highlight issues that may limit the usefulness of my findings.
+Finally, I describe future research that would build on my findings to move the field forward.
 
@@
 In __Chapter \@ref(cprd-analysis-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
-I make use of control outcomes to illustrate insufficiently controlled confounding.
+I make use of positive and negative control outcomes to illustrate insufficiently controlled confounding.
 
@@
 
-The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found a slight increased risk of dementia was associated higher LDL-c measured at mid-life, driven by the finding for the Alzheimer's disease subgroup.
-These results are consistent with the findings presented in this thesis, particularly given the lack of adjustment for confounding by _Apo_$\mathcal{E}4$, which was estimated by the study to induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
+The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found evidence for a slight increased risk of dementia with higher LDL-c levels at mid-life, driven by the finding for the Alzheimer's disease subgroup.
+These results are consistent with the findings presented in this thesis, particularly as this study did not have access to _Apo_$\mathcal{E}4$ status and so could not adjust for confounding by this variable.
+_Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels, <!-- TODO CITATION NEEDED --> and so could explain the hamrful association observed.
+This is supported by a sensitivity analysis reported within this study, which used published information to estimate _Apo_$\mathcal{E}4$ would induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
@@
 
-__[Note: Yoav, I am particularly interested in your thoughts on this section]__
+<!-- REVIEW Suggesting an ecological study?
+Is adding weak evidence really useful?
+Would it come with independent biases that would (in theory) bring a further dimension to the triangulation framework.
+-->
 
@@
 It will be difficult to assess if any observed trends are due to a true effect or to confounding or ecological biases.
-However, as dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a ready source of further evidence.
+However, as dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a ready source of further evidence with a distinct bias structure to the evidence considered in this thesis.
 
@@
 
-Preprints are an important source of evidence and searching of preprint repositories should become an accepted part of the evidence synthesis process.
-To support this, I developed a new tool (as described in Chapter \@ref(sys-rev-tools-heading)) to enable researchers to readily search health-related preprints.
+Preprints are an important source of evidence, and future information specialists may wish to search health-related preprints as part of a wider systematic review.
+To support this, I developed a new tool, `medrxivr`, as discussed more fully in Chapter \@ref(sys-rev-tools-heading).
+The tool has been well received by the community, and its use in systematic reviews[@imai2021; @rojoa2021; @hamilton2021] and scoping searches[@grassly2020] has been reported.
+In addition, the preprint metadata provided by the tool has been used in several meta-research studies.[@kodvanj2020;@noone2020;@mcguinness2020DAScomparison]
 
@@
 Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies, reducing the potential for differential adjustment based on knowledge of the results.
+This framework explcitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distribtuions representing the impact of bias/indirectness.
+
+<!-- TODO Double check last paragraph! -->
 
@@
 This would represent a break from the current practice of limiting review to a single type of evidence, and  would result in fewer, more comprehensive reviews.
-However, in the current context of research waste, a concentration of effort in fewer reviews may be advantageous.
+In the current context of concern over research waste, a concentration of effort in fewer reviews may be advantageous.
 Section \@ref(rev-previous-reviews) illustrates the duplication of reviews in relation to the topic of this thesis, while an assessment of the COVID-19 literature found that, for a specific clinical question, there were substantially more reviews (25) than available primary studies (17).[@perez-gaxiola2021]
@@
 
-In summary, the proposed triangulation framework will enable better use of all available evidence to address causal questions.
+In summary, the proposed triangulation framework could enable better use of all available evidence to address causal questions.
 
@@
 In the first instance, as with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
-It is possible that statins have a true effect via some other pathway , but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
+It is possible that statins have a true effect via some pathway other than lipid-regulation, but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
 
@@
 
-__[Question: is it better to use "should" or "could" when listing ideas for future research? I.e. "future work could/should look at X"?]__
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 However, it seems unlikely that further analysis of observational data alone will be sufficient to investigate this outcome, as indicated by the presence of strong confounding by indication in the analysis of statins and vascular dementia (Chapter \@ref(cprd-analysis-heading)).
-Even using new methods, such as a target trial emulation approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] Similarly, Mendelian randomisation studies are limited to a single one-sample analysis of HMGCR variants as a proxy for statin treatment.
+Even using new methods, such as a target trial emulation approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] Similarly, available Mendelian randomisation studies are limited to a single one-sample analysis of HMGCR variants as a proxy for statin treatment.
 This study suggested a protective effect of lipid-lowering on vascular dementia, though there was a moderate risk of bias in this analysis and the effect was attenuated to the null when including a wider range of lipid-lowering variants.
@@
 
-In terms of evidence synthesis methodology, future work on preprinted evidence should address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in a synthesis.
+In terms of evidence synthesis methodology, future work on preprinted evidence could address how to handle discrepancies between the preprinted and published versions of a paper when identifying results for inclusion in a synthesis.
 This will be particularly important in cases where the results are substantially different between the two versions or if a result available in the preprint manuscript is not presented in the published version.
@@
 As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not yet sufficiently developed, particularly in comparison to other study designs.
-Future work should aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g.
+Future work could aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g.
 genetic instrumental variable analysis).
@@
 Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority.
+
 Finally, the inclusion of multiple two-sample Mendelian randomisation studies using identical summary statistics can falsely increase the precision of the summary effect estimate if treated as independent results.
-Development of best practice guidance for addressing this problem would represent a useful contribution to the field.
+It would be interesting to examine how this issue has been addressed in existing reviews of Mendelian randomisation studies, and based on this research, develop best practice guidance for future evidence syntheses.
 
@@
 The approach presented here will benefit from future meta-epidemiological studies to better define the impact of bias/indirectness, as discussed in detail in Section \@ref(tri-prior-def).
-Similarly, future work should expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
-Tools such as ROB-ME will enable this, but how to adjust for this analysis-level - as opposed to result-level - bias will need to be determined.
+Similarly, future work could expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
+Tools such as ROB-ME will enable this, but how to adjust for this synthesis-level - as opposed to study-level - bias will need to be determined.
 Finally, the application of the framework to other causal questions will help to identify sticking points and may lead to refinement of the process.
@@
 <!-- TODO Could also talk here about how applying it across multiple questions would enable the development of a database of prespecified priors. -->
+
 &nbsp;

### 2021-12-13 front-and-back-matter/_acknowledgements.Rmd
Admin

@@
 Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews.
-Sharen O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support.
+Sharen Hockey-O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support.
 Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
@@
 Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
-<<github>>. A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.
+<<github>> A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.
 

### 2021-12-13 front-and-back-matter/99-appendices.Rmd
Add PRISMA checklist

@@
 
+### PRISMA Checklist
+
+\arrayrulecolor{white}
+
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:prismaTab-caption) __PRISMA Checklist__
+
+(ref:prismaTab-scaption) PRISMA Checklist
+
+```{r prismaTab-table, message=FALSE, results="asis", echo = FALSE}
+```
+<!----------------------------------------------------------------------------->
+\arrayrulecolor{black}
+
+&nbsp;
+
 ### Dose response plots by fraction {#appendix-dr-fraction}
@@
 
-(ref:drDemeniaTC-scap) shortcap
+(ref:drDemeniaTC-scap) Dose-response meta-analysis of total cholesterol on all-cause dementia
 
@@
 
-(ref:drAdLDL-scap) shortcap
+(ref:drAdLDL-scap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease
 
@@
 
-(ref:minFU-cap) __shortcap:__
+(ref:minFU-cap) Diagram illustrating the design of two studies.
+Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up.
+In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.
 
-(ref:minFU-scap) shortcap
+(ref:minFU-scap) Illustration of minimum follow-up period in two study designs
 
@@
 <!----------------------------------------------------------------------------->
-(ref:cprdMinFu-cap) Estimates from the
+(ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group.
+Events occurring within 10 years of inititating statins were discarded, but the participant-time-at-risk was maintained.
+No minimum follow-up period was applied in those never taking a statin, due to the difficulties in defining the start date for the follow-up period, as discussed in the text above.
 
-(ref:cprdMinFu-scap) shortcap
+(ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up.
 
@@
 &nbsp;
-
-### Comparison with previous analysis of the Whitehall II cohort {#appendix-ipd-whitehall}
-
-<!----------------------------------------------------------------------------->
-(ref:whitehallComparisonAd-cap) Comparison of results across the two analysis of the Whitehall II cohort for the Alzheimer's disease outcome.
-
-(ref:whitehallComparisonAd-scap) Comparison of results across the two analysis of the Whitehall II cohort
-
-```{r whitehallComparisonAd, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:whitehallComparisonAd-cap)', out.width='100%', fig.scap='(ref:whitehallComparisonAd-scap)'}
-knitr::include_graphics(file.path("figures/ipd/whitehall_comparison_ad.png"))
-```
-<!----------------------------------------------------------------------------->
-
-&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
-
-(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
 Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
@@
 
+(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
 ```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
@@
 
-robvis currently contains templates for the following tools:
+### Templates
+
+`robvis` currently contains templates for the following tools:
 
@@
 * ROB1
+* General
+
+### Data expectations
 
@@
 <!----------------------------------------------------------------------------->
-(ref:robSummary-cap) __shortcap:__
+(ref:robSummary-cap) Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
+Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.
 
-(ref:robSummary-scap) shortcap
+(ref:robSummary-scap) Example risk-of-bias summary barplot
 
@@
 <!----------------------------------------------------------------------------->
-(ref:robTraffic-cap) __shortcap:__
+(ref:robTraffic-cap) Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
 
-(ref:robTraffic-scap) shortcap
+(ref:robTraffic-scap) Example risk-of-bias traffic-light plot
 

### 2021-12-14 01-Chp-Background.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion
End of day:

@@
 Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
+
+<!-- TODO Need some details on risk factors here - and consider spacing differentl -->
 
@@
 In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-However, RCTs may be infeasible if the outcome of interest is one with a long prodomal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary related outcomes.
+However, RCTs may be infeasible if the outcome of interest is one with a long prodromal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary related outcomes.
 
@@
 
+&nbsp;
+
 _**McGuinness L.
@@
 
+&nbsp;
+
 ```{r, eval = FALSE}
@@
 
+&nbsp;
+
 ``` {r, eval = FALSE}
@@
 Install a stable version of the package from CRAN, or alternatively install the development version from GitHub, using:
+
+&nbsp;
 

### 2021-12-14 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex,[@ancelin2013; @mielke2010] though the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
-However, the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
+Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex.[@ancelin2013; @mielke2010] However, the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
+The number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
 Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on the between-study heterogeneity in a summary data meta-analysis, as similar distributions of participant covariates across studies may mask a true effect.[@riley2020]
@@
 However, this method requires several large cohorts to contain the full set of covariates, a condition this analysis failed to meet given the very low response rate.
-As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, diabetes).
-As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for education, ethnicity, prevalent ischemic heart disease (IHD) and BMI).
+As such, two other common approaches were employed.[@fibrinogenstudiescollaboration2009] In the primary analysis, all cohorts were adjusted for the set of common covariates across cohorts (Model 1: age, sex, smoking, alcohol, education, diabetes).
+As a sensitivity analysis, cohorts with the full complement of covariates (Whitehall II and EPIC) were analysed using a maximally-adjusted model (Model 2: Model 1, further adjusted for ethnicity, prevalent ischemic heart disease and BMI).
 Results between the common-set-adjusted (Model 1) and maximally-adjusted (Model 2) models were then compared.
@@
 Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
+
+<!-- REVIEW You need to justify why RE and FE for main and interaction terms -->
 
@@
 The cohort contains data on dementia outcomes sub-classified as vascular and non-vascular dementia.
-Data was available for all covariates of interest except for education, BMI and _Apo_$\mathcal{E}4$ status.
+Data was available for all covariates of interest except for ethnicity, BMI, prevalent IHD and _Apo_$\mathcal{E}4$ status.
+While the CaPS study collected data on height/weight (from which BMI can be calculated as $\frac{weight}{height^2}$) and prevalent heart disease, these were not available from the DPUK version of the CaPS data.
 
@@
 
-Estimates from the common-set-adjusted model (Model 1: adjusted for age, sex, smoking, alcohol, and diabetes) were comparable to the fully-adjusted model (Model 2: Model 1 further adjusted for ethnicity, prevalent ischemic heart disease, education and BMI) for the effect of lipids on all-cause dementia in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
+Estimates from the common-set-adjusted model (Model 1: adjusted for age, sex, smoking, alcohol, education and diabetes) were comparable to the fully-adjusted model (Model 2: Model 1 further adjusted for ethnicity, prevalent ischemic heart disease, and BMI) for the effect of lipids on all-cause dementia in cohorts reporting all covariates of interest (Figure \@ref(fig:ipdModelComparison)).
 
@@
 (ref:interactionDementiaAge-cap)  __Meta-analysis of age-lipid interaction terms for all-cause dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
-Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes).
+Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
+(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
 
@@
 (ref:interactionVascularAge-cap) __Meta-analysis of age-lipid interaction terms for vascular dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
-Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, diabetes).
+Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes).
 

### 2021-12-14 07-Chp-Triangulation.Rmd
End of day:

@@
 Firstly, the work presented in the previous chapters had identified some evidence for an association in these exposure/outcome pairs.
-Secondly, given the long prodomal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period are particularly important.
+Secondly, given the long prodromal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period are particularly important.
 Finally, examining the causal impact of a lipid fraction on a specific outcome (e.g.
@@
 Effects were standardised to refer to the risk resulting from a "reduction" in the lipid fraction.
-For both non-randomised studies and Mendelian randomisation analysis of lipid levels, the association is usually reported per 1-SD increase in the lipid fraction.
+For both non-randomised studies and Mendelian randomisation analysis of lipid levels, the association is usually reported in terms of an increase in the lipid fraction.
 In this case, the effect estimates were inverted to ensure consistency across study designs.
@@
 <!-- TODO The results should be standarised before calculating direction of effect, because other-wise it is pulling it in the wrong direction - YOU NEED TO SAY THIS LATER! -->
+
+<!-- REVIEW How did you deal with the statin studies? Did you adjust for the average reduction in LDL-c for average dose? Need to add clarification here.
+
+This should be an issue, as different effect sof statins will be adjusted for bia indirectness aspect of framework.
+
+Move to questions
+-->
 
@@
 
-Reasonable values for the position and spread of the prior distributions were informed by a previously-reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated).
+Reasonable values for the position and spread of the prior distributions were informed by a previously reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated).
 For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
@@
 
-####	Combining in a bias-adjusted meta-analysis
+####	Combining in a bias-/indirectness-adjusted meta-analysis
 
@@
 
+<!-- REVIEW YBS - I may have got confused but when you say favour the intervention I am assuming you mean a “protective effect” e.g.
+OR <1.
+But if there is differential misclassification so that statin use increases diagnosis of vascular dementia that would show a deleterious effect under the null hence shift to right e.g.
+OR >1.
+Perhaps I have misunderstood favour as < risk when in fact you mean > risk.
+Can you clarify?
+
+This is true for the VaD outcome, but in this case we are interested in the Alzheimer's diease outcome, which would result in under-reporting of AD when on statins and therefore favour the intervention.-->
+
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:biasDirectionSingle-cap) Bias direction plot for a single study showing the predicted direction of bias in each domain.
+(ref:biasDirectionSingle-cap) __Bias direction plot for a single study__ - Summary of result and the predicted direction of bias in each domain of bias for the effect of statin use on Alzheimer's dementia, as estimated in Chapter \@ref(cprd-analysis-heading).
 Additive biases are characterised using arrows, while the proportional biases are denoted using $<$ and $>$.
@@
 
+<!-- TODO Email Jonathan about how ROBINS-I deals with reverse triangulation? -->
+
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:singleIndirect-caption) Assessment of indirectness for a single example study.
+(ref:singleIndirect-caption) __Assessment of indirectness for a single example study__
 
-(ref:singleIndirect-scaption) singleIndirect
+(ref:singleIndirect-scaption) Assessment of indirectness for a single example study
 
@@
 
-The unadjusted estimate was `r single_unadjusted `. After accounting for the biases and indirectness described, the adjusted result was `r single_adjusted `.
+The unadjusted estimate was `r single_unadjusted `.
+After accounting for the biases and indirectness described, the adjusted result was `r single_adjusted `, representing a minimal shift in the position of the effect estimate but a substantial decrease in precision.
 
@@
 
-(ref:ldlAdBiasDirection-cap) Bias direction plot, summarising the internal biases related to effect of LDL-c on Alzheimer's disease, stratified by study design.
+(ref:ldlAdBiasDirection-cap) __Bias direction plot for LDL-c/Alzheimer's disease__ - Summary of the unadjusted results and internal biases related to effect of LDL-c on Alzheimer's disease, stratified by study design.
 
@@
 
-(ref:fpLdlAd-cap) Random effects meta-analysis of the association of midlife LDL-c with Alzheimer's disease, using unadjusted and bias-/indirectness-adjusted results.
+(ref:fpLdlAd-cap) __Bias-/indirectness-adjusted meta-analysis of midlife LDL-c on Alzheimer's disease__ - Random-effects meta-analysis of the association of midlife LDL-c with Alzheimer's disease, using unadjusted and bias-/indirectness-adjusted results.
+Note the substantial decrease in the weight assigned to the result of the CPRD analysis between the two plots, which is due to the high levels of bias/indirectness in this result as described in the above sections.
 
-(ref:fpLdlAd-scap) Random effects meta-analysis using unadjusted and bias-/indirectness-adjusted results.
+(ref:fpLdlAd-scap) Bias-/indirectness-adjusted meta-analysis of midlife LDL-c on Alzheimer's disease
 
@@
 <!----------------------------------------------------------------------------->
-(ref:tgVadBiasDirection-cap) Bias direction plot, summarising the internal biases related to effect of triglycerides on vascular dementia, stratified by study design.
+(ref:tgVadBiasDirection-cap) __Bias direction plot for triglycerides/vascular dementia__ - Summary of the unadjusted results and internal biases related to effect of triglycerides on vascular dementia, stratified by study design.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:fpTgVad-cap) Random effects meta-analysis of the association of midlife triglycerides and vascular dementia, using unadjusted and bias-/indirectness-adjusted (Scenario 1) results.
+(ref:fpTgVad-cap) __Bias-/indirectness-adjusted meta-analysis of midlife triglycerides on vascular dementia__ - Random effects meta-analysis of the association of midlife triglycerides and vascular dementia, using unadjusted and bias-/indirectness-adjusted (Scenario 1) results.
 
-(ref:fpTgVad-scap) shortcap
+(ref:fpTgVad-scap) Bias-/indirectness-adjusted meta-analysis of midlife triglycerides on vascular dementia
 
@@
 
+In the case of common outcomes, an extra step may be needed in the framework to assesses whether it is reasonable to synthesis across different effect estimates.
+
 <!-- REVIEW Could add that ORs could be converted to RRs using a measure of "hyptothecial" risk -->
@@
 Finally, accounting for bias using an incorrect prior distribution is no less problematic than synthesising and drawing conclusions from effect estimates that are treated as unbiased, a common occurrence in systematic reviews.[@katikireddi2015] While this analysis may be limited by the absence of empirically-derived adjustment distributions, it at the very least acknowledges the uncertainty of evidence due to bias/indirectness via a reduction in precision.
+
+<!-- REVIEW YBS I was struck by how much the 95% Cis were widened with CPRD. Is there a risk we are adding to much uncertainty and therefore down weighting this too much? -->
 

### 2021-12-14 08-Discussion.Rmd
End of day:

@@
 In this discussion, I will review the contribution of each chapter to this aim, summarise the principal findings and methodological innovations of the thesis, and discuss the implications of my findings for both clinical and public health practice.
-I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that builds on the research presented.
+I consider the overall strengths and limitations of this thesis as a coherent body of work and suggest avenues for impactful future research that would build on the research presented.
 
@@
 
-In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints, and detailed two use cases for preprint metadata beyond the systematic searching of this evidence source.
+In __Chapter \@ref(sys-rev-tools-heading)__, I  presented a new tool for the systematic searching of health-related preprints and detailed two use cases for preprint metadata beyond the systematic searching of this evidence source.
 
@@
 In __Chapter \@ref(cprd-analysis-heading)__, I described an analysis of the association of lipid-regulating agent use and dementia outcomes in the CPRD, a large electronic health record database.
-I make use of positive and negative control outcomes to illustrate insufficiently controlled confounding.
+I made use of positive and negative control outcomes to illustrate insufficiently controlled confounding.
 
@@
 While published non-randomised studies provided evidence for a protective effect of lipid-lowering via statin use on Alzheimer's disease and the IPD analysis suggested a harmful effect of raised triglycerides on vascular dementia, these effects were not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
-Similarly, the IPD analysis did not provide evidence for an interaction of patient characteristics with the association of blood lipids on dementia outcomes, though the results are limited by low number of cohorts analysed.
+Similarly, the IPD analysis did not provide evidence for an interaction of patient characteristics (age/sex) with the association of blood lipids on dementia outcomes, other than a slight protective effect of male gender on the LDL-c/all-cause dementia relationship.
+However, this analysis was limited by the low number of cohorts analysed.
 
@@
 
-The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found evidence for a slight increased risk of dementia with higher LDL-c levels at mid-life, driven by the finding for the Alzheimer's disease subgroup.
+The first is a large-scale analysis of 953,635 patients in the CPRD, followed from their first LDL-c measurement.[@iwagami2021] The study found evidence for a slightly increased risk of dementia with higher LDL-c levels at mid-life, driven by the finding for the Alzheimer's disease subgroup.
 These results are consistent with the findings presented in this thesis, particularly as this study did not have access to _Apo_$\mathcal{E}4$ status and so could not adjust for confounding by this variable.
-_Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels, <!-- TODO CITATION NEEDED --> and so could explain the hamrful association observed.
-This is supported by a sensitivity analysis reported within this study, which used published information to estimate _Apo_$\mathcal{E}4$ would induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
+_Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels, <!-- TODO CITATION NEEDED --> and so could explain the harmful association observed.
+This is supported by a simulation analysis reported within this study, which used published information to predict that _Apo_$\mathcal{E}4$ would induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
-The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes, comparable to the results of this thesis.
+The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes, again a comparable finding to the results of this thesis.
 However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _Apo_$\mathcal{E}4$ genotype.
@@
 Given this ambiguity, the use of statins should be restricted to their primary and well-understood purpose of lipid-lowering to reduce the risk of cardiovascular events.
-However, it is important to recognise that even under the scenario that a strong harmful effect of lipid-lowering on dementia outcomes was identified, whether or not to prescribe a statin at mid-life will always be guided by factors other than dementia prevention.
+However, it is important to recognise that even under a scenario where a strong harmful effect of lipid-lowering on dementia outcomes was identified, whether or not to prescribe a statin at mid-life will always be guided by factors other than dementia prevention.
 Patients must live to a certain age in order to be at risk of dementia (with the exception of familial early-onset dementias), which is substantially less likely if hypercholesterolemia at mid-life is left unchecked.
@@
 However, the role of public health, and particularly continuous population surveillance, may be important in providing a further source of evidence in relation to the effect of lipid lowering on dementia.
-Public health practitioners could examine summary-level statistics of GP prescription data to attempt to relate lipid-lowering treatment to temporal or geographical trends in dementia incidence.
-It will be difficult to assess if any observed trends are due to a true effect or to confounding or ecological biases.
-However, as dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach would provide a ready source of further evidence with a distinct bias structure to the evidence considered in this thesis.
+As an illustrative example, the Cognitive Function and Ageing Study (CFAS) II (2008-2011) showed a reduction in the age-specific prevalence rates of dementia when compared to CFAS I (1989-1994).[@matthews2013] The authors interpreted this reduction as the result of improved education and better control of vascular risk factors, in line with broader thinking on the impact of population-level changes in risk factors.[@capewell2011] In a similar manner, public health practitioners could examine summary-level statistics of GP prescription data to attempt to relate lipid-lowering treatment to temporal or geographical trends in dementia incidence.
+
+It may well prove difficult to assess if any observed trends are due to a true effect or to confounding or ecological biases.
+However, because dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach could provide a ready source of further evidence with a distinct bias structure to the approaches considered in this thesis.
 
@@
 Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies, reducing the potential for differential adjustment based on knowledge of the results.
-This framework explcitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distribtuions representing the impact of bias/indirectness.
+This framework explicitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distributions representing the impact of bias/indirectness.
 
@@
 There are several strengths to this thesis as a whole.
-Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous synthesis of the evidence on this topic.
-Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts and provided additional information on a previously under-studied association (lipids/LRA and vascular dementia).
+Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous syntheses of the evidence on this topic.
+Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied relationship (lipids/LRA and vascular dementia).
 
 A further strength of this thesis is the production of software to support the novel evidence synthesis techniques used.
-Extensive documentation has been written to guide users through usage of the tools and example data is provided for use.
+Extensive documentation has been written to guide users through usage of the tools and example data are provided, enabling future researchers to readily apply the methods described.
 Finally, substantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).
@@
 
-However, there are also several strong limitations to this thesis.
+However, there are also several limitations to this thesis.
 In the first instance, as with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
@@
 Secondly, each analysis presented here makes use of secondary data sources, be it published literature, electronic health records, or existing cohorts.
-Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in Chapter \@ref(ipd-heading), absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research (for example, the accuracy of dementia diagnoses in electronic health records is known to be variable).[@wilkinson2018]
+Secondary data can limit the type of analyses performed (for example, in the IPD analysis presented in Chapter \@ref(ipd-heading), absence of time-to-event data prevented the use of hazard ratios to quantify dementia risk) and the validity of the data if collected for purposes other than research.
+For example, the accuracy of dementia diagnoses in electronic health records is known to be variable.[@wilkinson2018]
 
@@
 Similarly, an absence of evidence on vascular dementia, potentially due to a publication bias mechanism, limited the analysis of this outcome.
-Missing evidence was also as an issue in the IPD meta-analysis reported in Chapter \@ref(ipd-heading), in the form of a poor response to data access requests, while the absence of empirically-based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
+Missing evidence was also an issue in the IPD meta-analysis reported in Chapter \@ref(ipd-heading), in the form of a poor response to data access requests.
+In addition, the absence of empirically based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
 
@@
 All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world (Figure \@ref(fig:cohortLocations)).
-This may limit the generalisability of the results presented to different populations.
+This, combined with the limited evidence for different ethnicities available even within high income settings, may limit the generalisability of the results presented to different populations.
 
@@
 Alzheimer's disease) when considering the causal effects of lipids.
-Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, as data cleaning and harmonisation for just three cohorts was a substantial undertaking.
+Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, as data cleaning and harmonisation for just three cohorts turned out to be a substantial undertaking.
 
-In the future, armed with the experience gained through conduct of the research projects presented here, I will be better place to scope and design research projects.
+In the future, armed with the experience gained through conducting the research presented here, I will be better placed to scope and design research projects.
 
@@
 
-Several avenues of future research could be pursued, building on the novel work presented here. These are grouped by topic in the following sections.
+Several avenues of future research are proposed, building on the novel work presented here. These are grouped by topic in the following sections.
 
@@
 It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trial be performed to assess the effect of the proposed intervention.
-Given the costs and logistical challenges associated with trials examining outcomes with long prodomal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up of existing RCTs of lipid-regulating agents.
+Given the costs and logistical challenges associated with trials examining outcomes with long prodromal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up of existing RCTs of lipid-regulating agents.
 
@@
 
-Taken together, these points reinforce the need for large-scale GWAS of vascular dementia, similar to those current available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could exploit.
-While GWAS of this outcome are likely to be methodologically challenging, given the difficult in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of genetically-driven risk factors beyond those considered in this thesis.
+Taken together, these points reinforce the need for a large-scale GWAS of vascular dementia, similar to those currently available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could exploit.
+While GWAS of this outcome are likely to be methodologically challenging, given the difficulty in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of genetically driven risk factors beyond those considered in this thesis.
 
@@
 
-The `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.[@elliott2014] In addition, the ready access to preprint data afforded by the tool will enable future meta-epidemiological studies to examine factors which may influence eventual publication (e.g.
-significant result, geographical location/gender/career stage of first author, or some other factor).
+The `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.[@elliott2014] In addition, the ready access to preprint data afforded by the tool will enable future meta-epidemiological studies to examine factors which may influence eventual publication (for example,  significant result, geographical location/gender/career stage of first author, or some other factor).
 Finally, the tool will allow future research to assess the impact of peer review and editorial guidelines on manuscripts through comparison of the same paper at two stages (preprinted versus published).
@@
 genetic instrumental variable analysis).
-In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that requires systematic assessment of bias, such as the quantitative triangulation framework proposed here.
+In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that require systematic assessment of bias, such as the quantitative triangulation framework proposed here.
 Creation of a domain-based tool for this study design, which accounts for the differences in potential biases between one- and two-sample approaches, should be considered a priority.
@@
 Similarly, future work could expand the framework proposed here to account for meta-biases, such as those introduced by missing evidence.
-Tools such as ROB-ME will enable this, but how to adjust for this synthesis-level - as opposed to study-level - bias will need to be determined.
+Tools such as ROB-ME will enable this, but the optimum method to adjust for this synthesis-level - as opposed to study-level - bias will need to be determined.
 Finally, the application of the framework to other causal questions will help to identify sticking points and may lead to refinement of the process.

### 2021-12-14 front-and-back-matter/99-appendices.Rmd
End of day:

@@
+---
+output:
+  word_document: default
+  html_document: default
+---
 `r if(knitr:::is_latex_output()) '\\startappendices'`
@@
 Enforcing a minimum period of follow-up is normally used to reduce the risk of reverse causation in an analysis by excluding events occurring within a certain time-frame post-exposure.
-With respect to dementia outcomes, which have a long prodomal period, enforcing a minimum period of follow-up can add biological validity to an analysis.
+With respect to dementia outcomes, which have a long prodromal period, enforcing a minimum period of follow-up can add biological validity to an analysis.
 Incident cases of dementia that occur within a few years of starting a drug may already be beyond effective preventive treatment at the time the drug was started, and so restricting the analysis to those with longer exposure to treatment may provide a more reliable estimate of the effect.
@@
 Participants enter the cohort and are classified at that point as either exposed or unexposed, for example, on the basis of a total cholesterol measurement.
-Participants are followed-up over time, but events occuring before the minimum period of follow-up are discarded.
+Participants are followed-up over time, but events occurring before the minimum period of follow-up are discarded.
 

### 2021-12-14 front-and-back-matter/_abstract.Rmd
End of day:

@@
 
-__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, through there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer’s disease in observational studies of statin use.
+__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, through there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
 The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia.

### 2021-12-14 front-and-back-matter/_acknowledgements.Rmd
End of day:

@@
-<!-- TODO CHECK ALL NAME SPELLINGS -->
+<!-- TODO UPDATE and check all name spellings -->
+
+__Professional__
 
 There are many people without whose input and support this work would have been severely diminised:
+
+Thank Julian separately -
 
@@
 Francesca Spiga kindly shared an advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner shared her code for bias-/indirectness-adjusted meta-analyses that underpins the quantitative triangulation framework presented in Chapter \@ref(tri-heading).
-Thanks to Vivienne for proof-reading.
 
@@
 
-On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times.
-Thanks to Mum and Dad for your never-ending love and support (I promise I'll get a real job now!).
-Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.
+\bigskip
+
+__Personal__
+
+This thesis would not have been possible with Ciara Gardiner. Lots of people say that at this point in the Acknowledgements, but I mean it literally. Between here managing.
+
+The person I have loved with all my heart
+
+Without here
 
@@
 
-&nbsp;
-&nbsp;
-&nbsp;
-&nbsp;
-&nbsp;
-&nbsp;
-&nbsp;
-&nbsp;
+Thanks to Vivienne and Dad for giving up a substantial amount of time to proof-reading.
+
+On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times.
+
+Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.
+
+Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point there doing and submitting a thesis.
+
+\bigskip
 

### 2021-12-14 index.Rmd
End of day:

@@
   `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
-dedication: For Brendan McHugh
+dedication: |
+  For\newline
+  Brendan McHugh\newline
+  &\newline
+  Ciara Gardiner
 covidStatment: |

### 2021-12-14 R/06-Code-IPD-Analysis.R

@@ -269,8 +269,8 @@ graphics::text(-4, 11, pos=4, "HDL-c", cex=1,font=2)
 graphics::text(-4, 17, pos=4, "LDL-c", cex=1,font=2)
 graphics::text(-4, 23, pos=4, "Total cholesterol", cex=1,font=2)
 
-graphics::text(-4, -.5, pos=4, "Model 1: Age, sex, smoking, alcohol and diabetes", cex=0.9, font =2)
-graphics::text(-4, -1.1, pos=4, "Model 2: Model 1 + BMI, ethnicity, education and presence of vascular disease", cex=0.9, font = 2)
+graphics::text(-4, -.5, pos=4, "Model 1: Age, sex, smoking, alcohol, education and diabetes", cex=0.9, font =2)
+graphics::text(-4, -1.1, pos=4, "Model 2: Model 1 + BMI, ethnicity, and prevalent ischemic heart disease", cex=0.9, font = 2)
 
 dev.off()
 

### 2021-12-14 R/07-Code-Triangulation-Analysis.R

@@ -4,8 +4,8 @@
 thesisOverview_table <- read.csv("data/background/thesisOverview.csv") %>%
   mutate("Exposure/ Intervention" = Exposure.Intervention) %>%
   mutate("Research Question" = Research.Question) %>%
-  mutate("Contibution to evidence synthesis framework" = Contribution) %>%
-  select("Chapter","Research Question","Exposure/ Intervention","Outcome","Contibution to evidence synthesis framework") %T>%
+  mutate("Contribution to evidence synthesis framework" = Contribution) %>%
+  select("Chapter","Research Question","Exposure/ Intervention","Outcome","Contribution to evidence synthesis framework") %T>%
   write.csv("data/table_words/thesisOverview.csv") 
 
 if(doc_type == "docx"){
@@ -593,7 +593,24 @@ dev.off()
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- turnerValidation ----
 
-# Validate formula using Turner data
+# Validate additive biases using Turner data for single assessor
+bias_values <-
+  read.csv("data/appendix/turner_validation_bias_values.csv") %>%
+  rename_with( ~ paste0("bias_", .), matches("_"))
+
+dat_rob <- rio::import("data/appendix/turner_validation_rob.csv")
+
+dat_rob_long <- dat_rob %>%
+  append_values_bias(bias_values, common = F)
+
+i_add <- dat_rob_long %>%
+  group_by(result_id) %>%
+  summarise(addimn = sum(bias_m_add),
+            addivar = sum(bias_v_add)) %>%
+  select(result_id, starts_with("add"))
+
+
+# Validate BIAMA formula using all Turner data
 turner <- rio::import("turner_bias/propbias.dta") %>%
   arrange(study, assessor) %>%
   left_join(rio::import("turner_bias/addbias.dta")) %>%
@@ -602,7 +619,6 @@ turner <- rio::import("turner_bias/propbias.dta") %>%
   rename("yi" = estlogor,
          "vi" = varlogor) %>%
   calculate_adjusted_estimates()  
-
 
 model <- metafor::rma.uni(yi = yi_adj,
                           vi = vi_adj,

### 2021-12-14 R/helper.R

@@ -1054,6 +1054,11 @@ rob_to_long <- function(data){
 
 append_values_bias <- function(data, values, common = T) {
   
+  values <- values %>%
+    janitor::clean_names() %>%
+    mutate(across(starts_with("bias_"), as.double)) %>%
+    mutate(across(c(domain,j), stringr::str_to_lower))
+  
   # Define criteria on which to join with values#
   # If common = T, means that the values of Serious/Moderate are consistent across domains
   if (common == T) {
@@ -1068,6 +1073,7 @@ append_values_bias <- function(data, values, common = T) {
   }
   
   data %>%
+    janitor::clean_names() %>%
     # Convert to long format
     rob_to_long() %>%
     

### 2021-12-14 01-Chp-Background.Rmd
Update table captions to new style

@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) Overview of the DSM-5 criteria for dementia and vascular dementia.[@edition2013]
+(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia and vascular dementia.__ - These published criteria[@edition2013] are commonly used to defined dementia outcomes.
+<!-- TODO Need to finish this sentence and explan criteria better -->
 
@@
 
-(ref:lipidLevels-caption) Classification of blood lipid levels according to the National Cholesterol Education Program guidelines.[@national2002third]
+(ref:lipidLevels-caption) __Classification of blood lipid levels__ - Category cut-offs for different lipid fractions according to the National Cholesterol Education Program guidelines.[@national2002third]
 
@@
 
-(ref:statinOverview-caption) Overview of commonly-prescribed statins, summarising their approval date (US), properties and lipid-lowering effect.
+(ref:statinOverview-caption) __Overview of common statins__ -  There are several commonly-prescribed statins used to treat hypercholesterolemia.
+Their approval date (US), properties and lipid-lowering effect are described here.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:lipidTreatments-caption) Summary of available treatments for hyperlipidaemia.
+(ref:lipidTreatments-caption) __Summary of available treatments for hyperlipidaemia.__
 

### 2021-12-14 03-Chp-Systematic-Review-Methods.Rmd
Range of edits incl: - Better figure captions - Better description of proportional biases - Julian comments to Discussion
Update table captions to new style

@@
 Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
+
 &nbsp;
@@
 <!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) Summary of systematic search by topic.
-The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
+(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
 
-(ref:searchOverview-scaption) searchOverview
+(ref:searchOverview-scaption) Summary of systematic search by topic
 
@@
 <!----------------------------------------------------------------------------->
-(ref:gwet-caption) Suggested ranges to aid in interpretation of Gwet's AC1 inter-rater reliability metric[@mchugh2012]
+(ref:gwet-caption) __Ranges for Gwet's AC1__ - To aid the interpretation of inter-/intra-rater reliability, I used a published set of suggested categories for Gwet's AC1.[@mchugh2012]
 

### 2021-12-14 05-Chp-CPRD-Analysis.Rmd
Update table captions to new style

@@
 
-# Primary analysis of lipid-regulating agents and dementia outcomes {#cprd-analysis-heading}
+# Primary analysis of lipid-regulating agents and dementia outcomes in the CPRD {#cprd-analysis-heading}
 
@@
 <!--------------------------------------------------------------------------->
-(ref:readExample-caption) Example of CPRD Read code hierarchy, showing how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
-Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
+(ref:readExample-caption) __Example of CPRD Read code hierarchy__ - Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
+The example shown illustrates how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:covariateDef-caption) Definition of covariates adjusted for in the full-adjusted model.
-The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
+(ref:covariateDef-caption) __Definitions of covariates adjusted for in the analysis__ - The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
 
-(ref:covariateDef-scaption) Covariates adjusted for.
+(ref:covariateDef-scaption) Definitions of covariates adjusted for in the analysis
 
@@
 <!----------------------------------------------------------------------------->
-(ref:followUp-caption) Summary of number of events, years at risk and crude rates per 100,000 participant-years-at-risk stratified by dementia outcome and drug class of interest.
+(ref:followUp-caption) __Crude rates, stratified by outcome and drug class of interest__ - The number of events, years at risk and crude rates per 100,000 participant-years-at-risk stratified by dementia outcome and drug class of interest are presented below.
 
-(ref:followUp-scaption) Crude rates, stratified by outcome and drug class of interest.
+(ref:followUp-scaption) Crude rates, stratified by outcome and drug class of interest
 
@@
 ```
-(ref:cprdCharacteristics-caption) Patient characteristics by drug class. Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
+
+(ref:cprdCharacteristics-caption) __Patient characteristics by drug class__ - Summary statistics are presented as "% (N)" unless otherwise specified in the variable name.
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:cprdSSA-caption) Participants who stopped, switched or added treatments by initial treatment type.
+(ref:cprdSSA-caption) __Summary of treatment change__ - The number of participants who stopped, switched or added treatments was calculated, stratified by initial LRA type.
 
-(ref:cprdSSA-scaption) Participants who stopped, switched or added treatements by initial treatment type
+(ref:cprdSSA-scaption) Summary of treatment change
 
@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosisType-caption) Frequency of diagnoses by grouped year of cohort entry
+<!-- TODO Check table caption -->
+
+(ref:diagnosisType-caption) __Frequency of diagnoses by grouped year of cohort entry__
 
@@
 
-(ref:statinTypeTable-caption) Summary of statin properties (lipophilicity vs hydrophilicity) by grouped year of prescription.
+<!-- TODO Check this table title -->
+
+(ref:statinTypeTable-caption) __Summary of statin properties (lipophilicity vs hydrophilicity)__, by grouped year of prescription.
 

### 2021-12-14 06-Chp-IPD-Analysis.Rmd
Update table captions to new style

@@
 <!----------------------------------------------------------------------------->
-(ref:mainEffectDem-cap) IPD meta-analysis (Model 1) of all-cause dementia outcomes, stratified by lipid fraction
+(ref:mainEffectDem-cap) __IPD meta-analysis of all-cause dementia__ - Using Model 1 (adjusted for age, sex, smoking, alcohol, education and diabetes), an IPD random-effects meta-analysis was applied to investigate the association of a 1-SD increase in each lipid fraction with all-cause dementia outcomes.
 
-(ref:mainEffectDem-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+(ref:mainEffectDem-scap) IPD meta-analysis of all-cause dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:mainEffectVad-cap) IPD meta-analysis (Model 1) of vascular dementia outcomes, stratified by lipid fraction.
-Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts.
+(ref:mainEffectVad-cap) __IPD meta-analysis of vascular dementia__ - Using Model 1 (adjusted for age, sex, smoking, alcohol, education and diabetes), an IPD random-effects meta-analysis was applied to investigate the association of a 1-SD increase in each lipid fraction with vascular dementia outcomes.
+Note that the vascular dementia outcome was only available in the CaPS and Whitehall II cohorts (see Table \@ref(tab:covariateSummary-table)).
 
-(ref:mainEffectVad-scap) IPD meta-analysis of all-cause dementia, stratified by lipid fraction
+(ref:mainEffectVad-scap) IPD meta-analysis of vascular dementia
 
@@
 <!----------------------------------------------------------------------------->
-(ref:whitehallComparisonDementia-cap) Comparison of results across the two analyses of the Whitehall II cohort for the all-cause dementia outcome.
+(ref:whitehallComparisonDementia-cap) __Comparison of two analyses of the Whitehall II cohort (all-cause dementia)__ - A published analysis by Tynkkynen _et al._[@tynkkynen2018] had previously examined the association of lipid fractions and all-cause dementia in the Whitehall II cohort.
+The results of the two analyses are shown above and were broadly comparable, except for the triglyceride fraction.
+Potential reasons for this discrepancy are discussed in the main text.
 
-(ref:whitehallComparisonDementia-scap) Comparison of results across the two analyses of the Whitehall II cohort
+(ref:whitehallComparisonDementia-scap) Comparison of two analyses of the Whitehall II cohort (all-cause dementia)
 
@@
 <!----------------------------------------------------------------------------->
-(ref:whitehallComparisonAd-cap) Comparison of results across the two analyses of the Whitehall II cohort for the Alzheimer's disease outcome.
+(ref:whitehallComparisonAd-cap) __Comparison of two analyses of the Whitehall II cohort (Alzheimer's disease)__ - A published analysis by Tynkkynen _et al._[@tynkkynen2018] had previously examined the association of lipid fractions and Alzheimer's disease in the Whitehall II cohort.
+The results of the two analyses are shown above and were broadly comparable.
 
-(ref:whitehallComparisonAd-scap) Comparison of results across the two analyses of the Whitehall II cohort
+(ref:whitehallComparisonAd-scap) Comparison of two analyses of the Whitehall II cohort (Alzheimer's disease)
 

### 2021-12-14 07-Chp-Triangulation.Rmd
Update table captions to new style

@@
 
-# Aetiological triangulation across new and existing evidence sources {#tri-heading}
+# Aetiological triangulation across new and existing evidence sources: a qualitative and quantitative approach {#tri-heading}
 
@@
 
-(ref:exampleDirection-scap) Illustration of calculating the absolute direction of biases, based on bias type
+(ref:exampleDirection-scap) Calculating the absolute direction of biases, based on bias type
 
@@
 
-####	Assign modifying values to risk/direction of bias
+####	Assign modifying values to risk/direction of bias {#tri-bias-assign}
 <!-- TODO Note that they are on the log scale, and that this requires the results to be on the log scale too! - Lines 45-50 of addbias -->

### 2021-12-14 front-and-back-matter/99-appendices.Rmd
Update table captions to new style

@@
 <!----------------------------------------------------------------------------->
-(ref:medRes-caption) Publication status of medRxiv preprints deposited in July 2019, allowing for a two-year lag
+(ref:medRes-caption) __Publication status of medRxiv preprints__ - The publication status of medRxiv preprints deposited in July 2019 was assessed in July 2021 (allowing for a two-year lag) and found that a substantial proportion remained unpublished.
 
@@
 
-(ref:wosDatabases-caption) Summary of Web of Science databases searched.
-The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.
+(ref:wosDatabases-caption) __Summary of Web of Science databases searched__ - The contents of the Web of Science core collection can vary depending on an institution's subscription, and so detailing the exact databases and ranges searched is important.
 
-(ref:wosDatabases-scaption) Summary of Web of Science databases searched.
+(ref:wosDatabases-scaption) Summary of Web of Science databases searched
 
@@
 
-(ref:searchOverviewAppendix-caption) Summary of number of records identified in each database searched
+(ref:searchOverviewAppendix-caption) __Summary of number of records identified in each database searched__ - The full line-by-line search results for the each database, are presented in subsequent tables.
+Note there was substantial duplication across databases, resulting in several thousand duplicates being removed prior to title and abstract screening.
 
-(ref:searchOverviewAppendix-scaption) searchOverviewAppendix
+(ref:searchOverviewAppendix-scaption) Summary of number of records identified in each database searched
 
@@
 
-(ref:searchHitsMedline-caption) Overview of the full Medline search strategy.
+(ref:searchHitsMedline-caption) __Medline search strategy__ - Full list of search terms used to identify relevant records in the Medline bibliographic database.
+The number of records returned per search term is also displayed.
 
@@
 
-(ref:searchHitsEmbase-caption) Overview of the full Embase search strategy.
+(ref:searchHitsEmbase-caption) __Embase search strategy__ - Full list of search terms used to identify relevant records in the Embase bibliographic database.
+The number of records returned per search term is also displayed.
 
@@
 
-(ref:searchHitsPI-caption) Overview of the full PyscINFO search strategy.
+(ref:searchHitsPI-caption) __PyscINFO search strategy__ - Full list of search terms used to identify relevant records in the PyscINFO bibliographic database.
+The number of records returned per search term is also displayed.
 
@@
 
-(ref:searchHitsCentral-caption) Overview of the full CENTRAL search strategy.
+(ref:searchHitsCentral-caption) __CENTRAL search strategy__ - Full list of search terms used to identify relevant records in the CENTRAL bibliographic database.
+The number of records returned per search term is also displayed.
+Note that at the last step, I applied a manual filter via the CENTRAL web interface to limit the search to primary studies.
 
@@
 
-(ref:searchHitsWos-caption) Overview of the full Web of Science search strategy.
+(ref:searchHitsWos-caption)  __Web of Science search strategy__ - Full list of search terms used to identify relevant records in the Web of Science bibliographic database.
+The number of records returned per search term is also displayed.
 
@@
 
-(ref:mrTool-caption) Tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
+(ref:mrTool-caption) __Mendelian randomisation risk-of-bias assessment tool__ - A copy of the tool used to assess risk of bias in Mendelian randomisation studies, adapted from that developed by Mamluk et al.[@mamluk2020]
 
@@
 <!----------------------------------------------------------------------------->
-(ref:prismaTab-caption) __PRISMA Checklist__
+(ref:prismaTab-caption) __PRISMA Checklist__ - Following best practice guidelines, the Section/Table/Figure number were important details on the systematic review can be found are listed.
 
@@
 
-(ref:drDemeniaTC-cap) Dose-response meta-analysis of total cholesterol on all-cause dementia
+(ref:drDemeniaTC-cap) __Dose-response meta-analysis of total cholesterol on all-cause dementia__
 
@@
 
-(ref:drAdLDL-cap) Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease
+(ref:drAdLDL-cap) __Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease__
 
@@
 
-(ref:minFU-cap) Diagram illustrating the design of two studies.
-Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up.
+(ref:minFU-cap) __Illustration of minimum follow-up period in two study designs__ - Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up.
 In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.
@@
 
-With these caveats in mind, below I present a sensitivity analysis of the association of statins with dementia outcomes, enforcing a minimum 10-year period of follow-up from statin initiation in those prescribed a statin.
+<!-- With these caveats in mind, below I present a sensitivity analysis of the association of statins with dementia outcomes, enforcing a minimum 10-year period of follow-up from statin initiation in those prescribed a statin.
+-->
 
 <!----------------------------------------------------------------------------->
-(ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group.
+<!-- (ref:cprdMinFu-cap) Sensitivity analysis showing the results of a re-analysis of the CPRD data enforcing a minimum follow-up period of 10 years in the statin group.
 Events occurring within 10 years of inititating statins were discarded, but the participant-time-at-risk was maintained.
 No minimum follow-up period was applied in those never taking a statin, due to the difficulties in defining the start date for the follow-up period, as discussed in the text above.
+-->
 
-(ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up.
+<!-- (ref:cprdMinFu-scap) Sensitivity analysis of the CPRD data with a 10 year minimum period of follow-up. -->
 
-```{r cprdMinFu, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdMinFu-cap)', out.width='100%', fig.scap='(ref:cprdMinFu-scap)'}
-knitr::include_graphics(file.path("figures/hold.png"))
-```
+<!-- ```{r cprdMinFu, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:cprdMinFu-cap)', out.width='100%', fig.scap='(ref:cprdMinFu-scap)'} -->
+<!-- knitr::include_graphics(file.path("figures/hold.png")) -->
+<!-- ``` -->
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-(ref:missingMatrix-caption) Overview of missing data across covariates (described as N (%)) included in IPD analysis.
+(ref:missingMatrix-caption) __Overview of missing data in the IPD analysis__ - Missing variables/values across cohorts included in the IPD analysis.
+Missing variables are denoted using a "-", while missing values are described as N (%).
 Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.
 
-(ref:missingMatrix-scaption) missingMatrix
+(ref:missingMatrix-scaption) Overview of missing data in the IPD analysis
 
@@
 <!----------------------------------------------------------------------------->
-(ref:ipdDementiaDef-caption) Definition of dementia outcomes across cohorts included in the individual participant data meta-analysis.
+(ref:ipdDementiaDef-caption) __Definition of dementia outcomes in IPD meta-analysis__ - The criteria used to define dementia outcomes across cohorts included in the individual participant data meta-analysis are listed below.
 Note the codes used to define dementia and related outcomes in the HES data as part of the Whitehall II cohort were taken from a previously published analysis.[@russ2014]
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:addTable1-caption) Distributions of bias, defined by position and variance terms, assigned by four independent experts to attrition and detection bias in a single study.
+(ref:addTable1-caption) __Elicited bias distributions__ -  Distributions of bias, defined by position and variance terms, assigned by four independent experts to attrition and detection bias in a single study.
 This data was obtained from a previous publication,[@turner2009] and represents an illustrative subset of the larger dataset.
 
-(ref:addTable1-scaption) addTable1
+(ref:addTable1-scaption) Elicited bias distributions
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:addTable2-caption) Position and variance values for two example bias domains (attritiona and detection), obtained by averaging the absolute of the values contained in \@ref(tab:addTable3-table) across the four reviewers.
+(ref:addTable2-caption) __Elicited bias distributions, averaged across experts__ - The expert-averaged position and variance values for two example bias domains (attrition and detection) are shown.
+These values were obtained by averaging the absolute of the values contained in \@ref(tab:addTable3-table) across the four experts.
 
-(ref:addTable2-scaption) addTable1
+(ref:addTable2-scaption) Expert-elicited bias distributions, averaged across experts
 
@@
 I then took the average and maximum of the expert-averaged position and variance values. The results of this for the example data are presented in Table \@ref(tab:addTable3-table). 
+&nbsp;<!----------------------------------------------------------------------->  
+(ref:addTable3-caption) __Mean and maximum bias distributions, using example data__ - The mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table) were calculated to give the average and maximum bias adjustment across studies and domains of bias.
 
-&nbsp;<!----------------------------------------------------------------------->  
-(ref:addTable3-caption) Mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table)
-
-(ref:addTable3-scaption) addTable1
+(ref:addTable3-scaption) Mean and maximum bias distributions, using example data
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:turnerEstimates-caption) Mean and maximum distributions for bias and indirectness obtained from data resulting from the elicitation exercise reported in _Turner et al_[@turner2009].
+(ref:turnerEstimates-caption) __Mean and maximum distributions for bias and indirectness, using full data__ - Using all data resulting from the elicitation exercise reported in _Turner et al_[@turner2009], I calculated mean and maximum distributions for bias and indirectness using the method described above.
 Note I did not calculate values for additive indirectness, as in my analysis, all indirectness was assumed to be proportional.
 
-(ref:turnerEstimates-scaption) turnerEstimates
+(ref:turnerEstimates-scaption) Mean and maximum distributions for bias and indirectness, using full data
 
@@
 
-(ref:fpLdlAdComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
-Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels
+(ref:fpLdlAdComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels.
+See Section \@ref(tri-bias-assign) for more details.
 
-(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease, using two different scenarios for the relationship of levels of bias.
+(ref:fpLdlAdComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias.
 ```{r fpLdlAdComparison, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:fpLdlAdComparison-cap)', out.width='100%', fig.scap='(ref:fpLdlAdComparison-scap)'}
@@
 
-(ref:fpTgVaDComparison-cap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia, using two different scenarios for the relationship of levels of bias.
-Scenario 1: position value between the distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
-Scenario 2: position value between the distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels
+(ref:fpTgVaDComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels.
+See Section \@ref(tri-bias-assign) for more details.
 
-(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses under two different scenarios of prior distributions of bias.
+(ref:fpTgVaDComparison-scap) Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias.
 
@@
 <!-- TODO Need to complete this sections -->
-The robvis package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.
+The `robvis` package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:biasData-caption) First five assessments contained in `data_rob2`, an example dataset for the Risk of Bias 2 tool for randomised controlled trials available via the `robvis` package.
+(ref:biasData-caption) __Example `robvis` dataset__ - First five assessments contained in `data_rob2`, an example dataset for the Risk of Bias 2 tool for randomised controlled trials available via the `robvis` package.
 
-(ref:biasData-scaption) biasData
+(ref:biasData-scaption) Example `robvis` dataset
 
@@
 <!----------------------------------------------------------------------------->
-(ref:biasDirectionData-caption) Example data illustrating the structure required for bias direction plots.
+(ref:biasDirectionData-caption) __Example bias direction dataset__ - Example risk-of-bias data illustrating the structure required for bias direction plots.
 $d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain.
@@
 
-(ref:biasDirectionData-scaption) biasDirectionData
+(ref:biasDirectionData-scaption) Example bias direction dataset
 
@@
 <!----------------------------------------------------------------------------->
-(ref:robSummary-cap) Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
+(ref:robSummary-cap) __Example risk-of-bias summary barplot__ - Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
 Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.
@@
 <!----------------------------------------------------------------------------->
-(ref:robTraffic-cap) Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
+(ref:robTraffic-cap) Example risk-of-bias traffic-light plot - Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
 

### 2021-12-14 front-and-back-matter/_acknowledgements.Rmd
Update acknowledgements and dedication

@@
 
-This thesis would not have been possible with Ciara Gardiner. Lots of people say that at this point in the Acknowledgements, but I mean it literally. Between here managing.
+This thesis would not have been possible with Ciara Gardiner.
+Lots of people say this about someone at this point in the acknowledgements, and I'm always sceptical of whether it is true, so to avoid any doubt I mean it here quite literally.
 
-The person I have loved with all my heart
+Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour.
+It can't have been fun being locked-down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin.
+I talk about lessons learnt during this thesis in the Discussion, but the biggest takeaway for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand.
+Thank you and I love you.
 
-Without here
-
-Finally, deepest thanks to Ciara Gardiner: holder-of-forts, maker-of-spreadsheets, and all-round fiancee-extraordinaire. I can't wait for the next adventure with you.
+Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point where doing and submitting a thesis.
 
@@
 
-On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times.
-
-Thank also to Doug for introducing me to the joys of running, Ben for always being around to chat, and Christin for encouraging regular coffee-breaks.
-
-Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point there doing and submitting a thesis.
+On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times. Ben, Doug, Christin - thank you!
 

### 2021-12-14 index.Rmd
Update acknowledgements and dedication

--- 2021-12-08 index.Rmd
@@
   `r paste(readLines("front-and-back-matter/_declaration.Rmd"), collapse = '\n  ')`
-dedication: For Brendan McHugh
+dedication: |
+  `r paste(readLines("front-and-back-matter/_dedication.Rmd"), collapse = '\n  ')`
 covidStatment: |

### 2021-12-14 front-and-back-matter/_abstract.Rmd
Fix formatting error in abstract

@@
 
-__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, through there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
+__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
 The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia.
 However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors.
-The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence only for the association of triglycerides and vascular dementia.
+The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence for only the association of triglycerides and vascular dementia.
 Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.

### 2021-12-15 01-Chp-Background.Rmd
Ciara edits

@@
 
-The chapter introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
+It then introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
 Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
@@
 
-One of the most commonly used sets of criteria for diagnosing dementia cases are the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013] Outlined in Table \@ref(tab:diagnosticCriteria-table), these form the broad definition of a dementia diagnoses, and are supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
+One of the most commonly used sets of criteria for diagnosing dementia cases are the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria (Table \@ref(tab:diagnosticCriteria-table)).[@edition2013] Outlined in Table \@ref(tab:diagnosticCriteria-table), these form the broad definition of a dementia diagnosis, and are supported by a detailed patient history, evidence from carers and family members, and objective assessments of cognitive ability using neurocognitive tests.
 
@@
 For example, the MMSE is used to provide evidence for part A of the criteria presented in \@ref(tab:diagnosticCriteria-table).
-Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could be due to another cause (for example, temporary delirium as a result of an infection or surgery).
+Taken alone, it does not indicate the absence or presence of dementia, instead merely indicating cognitive impairment which could have another cause (for example, temporary delirium as a result of an infection or surgery).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia and vascular dementia.__ - These published criteria[@edition2013] are commonly used to defined dementia outcomes.
-<!-- TODO Need to finish this sentence and explan criteria better -->
+(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia (major neurocognitive disorder).__ - These published criteria[@edition2013] are commonly used to define dementia cases.
+Criterion A captures the cognitive decline aspect of dementia, while Criteria B-D ensure that the impairment observed is sufficient to interfere with daily living and can not explained by other causes.
+Note that all criteria (A-D) must be met.
 
-(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia and vascular dementia.
+(ref:diagnosticCriteria-scaption) Overview of the DSM-5 criteria for dementia (major neurocognitive disorder)
 
@@
 
-Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, as whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
+Differentiating between the underlying causes of a dementia diagnosis is challenging but necessary, because whether the patient has Alzheimer's disease or vascular dementia will affect expected progression and potential treatment options available (see Section \@ref(intro-treatments)).
 Cause-specific criteria exist for the diagnosis of dementia sub-types.
@@
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in Westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is a leading cause of death in the UK,[@zotero-15757] and one of the few without a proven treatment.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is a leading cause of death in the UK,[@zotero-15757] and one of the few without a proven treatment.
 
@@
 
-Triglycerides are the simplest and most common type of lipids found across the body.
-They are used to store unused calories from food, and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] As lipids are not water soluble, within the blood stream, cholesterol is transported in lipoprotein structures of varying densities.
-Low-density-lipoprotein cholesterol (LDL-c), commonly know as the "bad" cholesterol, transports fat to cells, acting as an energy conveyor.
-In contrast, High density-lipoprotein cholesterol (HDL-c), transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
+Triglycerides are the simplest and most common type of lipids, used to store excess calories from food and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] Lipids are not water soluble, and so cholesterol is transported through the blood stream in lipoprotein structures of varying densities.
+Low-density-lipoprotein cholesterol (LDL-c), commonly know as "bad" cholesterol, acts as an energy conveyor by transporting fat to cells.
+In contrast, high density-lipoprotein cholesterol (HDL-c) transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
 
@@
 ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the pleiotropic affects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+rosuvastatin 80 mg/day).[@collins2016; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the off-target effects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
 
@@
 A role for lipids in the aetiology of dementia is supported by both genetic linkage studies and functional cell biology studies.
-The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (_Apo_$\mathcal{E}$), is involved in cerebral cholesterol transport.
+The generation of the amyloid plaques found in the brains of Alzheimer's patients is cholesterol dependent,[@burns2003; @mizuno1999] while the most established genetic risk factor for late-onset dementia, apolipoprotein E (_Apo_$\mathcal{E}$), is involved in cerebral cholesterol transport.
 Several other genes involved in cholesterol transport have also been found to be associated with increased AD susceptibility.[@beecham2014; @harold2009; @meng2007]
@@
 By far the largest source of evidence on the relationship between blood lipids and dementia outcomes comes from observational designs.
-Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), low density lipoprotein cholesterol (LDL-c), high density lipoprotein cholesterol (HDL-c) and triglycerides) <!-- TODO These abbreviations have already been defined above --> and both Alzheimer's disease and vascular dementia and reported extremely varied results.
-In some studies, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005; @mainous2005; @mielke2010; @tan2003] or a reduced susceptibility [@mielke2005; @reitz2004].
+Several studies have examined the relationships between concentrations of serum lipids (total cholesterol (TC), LDL-c, HDL-c and triglycerides) and both Alzheimer's disease and vascular dementia.
+These studies have reported extremely varied results.
+In some, a high serum cholesterol concentration has been found to be associated with an increase in susceptibility to AD,[@kivipelto2002; @kivipelto2005; @schilling2017; @solomon2009; @whitmer2005] however others have shown no association,[@li2005; @mainous2005; @mielke2010; @tan2003] or a reduced susceptibility [@mielke2005; @reitz2004].
 With regard to vascular dementia, decreased levels of HDL-c appear to be associated with increased risk [@reitz2004], while for LDL-c, studies have reported both positive and negative associations.[@reitz2004; @moroney1999]
@@
 
-In terms of the central research of this thesis, RCTs of statin therapy can be used to provide indirect evidence for the effect of reducing blood LDL-c levels on dementia risk.
-However, RCTs may be infeasible if the outcome of interest is one with a long prodromal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary related outcomes.
+In terms of the central research of this thesis, randomised controlled trials (RCTs) of statin therapy can be used to provide indirect evidence on the effect of reducing blood LDL-c levels on dementia risk.
+However, RCTs may be infeasible if the outcome of interest is one with a long prodromal period, such as dementia (see Section \@ref(underlying-pathologies)), as they would require extremely long and costly follow-up.[@ritchie2015] It is no surprise then that the two previous trials providing evidence on the effect of statins on dementia risk, identified by a recent Cochrane review,[@mcguinness2016] are in fact trials of statins for the prevention of coronary-related outcomes.
 
 While being widely cited, these studies have major limitations that reduce their utility as a source of evidence on the effect of statin treatment in assessing the impact of lipid-lowering treatment on dementia risk.
-Firstly, the criteria used to determine a dementia outcome are unclear.
-One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores over a mean of 3.2 years.
-As highlighted in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
+Firstly, the criteria used to determine a dementia outcome are prone to misclassification.
+One of the trials, the Prospective Study of Pravastatin in the Elderly (PROSPER) trial,[@trompet2010] reported not on dementia outcomes but on the change in cognitive scores.
+As alluded to in Section \@ref(diagnostic-criteria), a "change in score" alone is insufficient to diagnose a dementia outcome.
 The second trial, the Medical Research Council/British Health Foundation Protection Study,[@heartprotectionstudycollaborativegroup2002] found no effect of simvastatin on dementia (`r estimate(1, 0.61, 1.65)`), but did not report how the outcome was assessed/recorded within the trial.
@@
 Additionally, the two trials did not make any effort to assign an underlying pathology to each case, instead reporting an all-cause dementia outcome.
-As discussed in Section \@ref(underlying-pathologies), the different underlying pathologies of dementia have different mechanisms of action, and so it is not gauranteed that the effect of statins would be consistent across them.
+As discussed in Section \@ref(underlying-pathologies), the different underlying pathologies of dementia have different mechanisms of action, and so it is not guaranteed that the effect of statins would be consistent across them.
 
 Both trials were also limited by the relatively short follow-up period examined.
-This limited follow-up was expected, as the primary aim of both trials was to assess the effect of statins on short-term coronary-related outcomes.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+This limited follow-up was to be expected because the primary aim of both trials was to assess the effect of statins on short-term coronary-related outcomes.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
 Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
@@
 Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
-Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
+Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
 
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analysis that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}4$ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
-This was supported by further MR studies where _Apo_$\mathcal{E}4$ variants were intentionally excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+This was supported by further MR studies in which the observed effect attenuated to the null after _Apo_$\mathcal{E}$ variants were excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
 
@@
 
-Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018] A common type of evidence synthesis is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
+Evidence synthesis is the process of finding and integrating information from several sources to examine a research question.[@donnelly2018] The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
+The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
+A common type of evidence synthesis exercise is a systematic review, either with or without a meta-analysis.[@chandler2019chapter]
 
-The results of an evidence synthesis exercise can be used to provide a more definitive answer to that question or, failing that, to highlight gaps in the existing evidence base.
-The ability to identify these gaps is particularly useful in guiding future research to address questions that have yet to be answered.
-
-This thesis seeks to use an evidence synthesis framework to assess the effect of lipids, and treatments that influence lipid levels, on dementia outcomes.
+This thesis seeks to use an evidence synthesis framework to assess the effect of lipid levels, and treatments that influence lipid levels, on dementia outcomes.
 Specifically, this thesis considers three concepts within the umbrella term of evidence synthesis:
@@
 
-However, the role of preprints in evidence syntheses is less well defined.
-Defined by the Committee on Publication Ethics as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process',[@committeeonpublicationethicscope2018] preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, the allow for the rapid disseminate research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+However, the role of preprints in evidence synthesis is less well defined.
+Described by the Committee on Publication Ethics as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process',[@committeeonpublicationethicscope2018] preprints serve several purposes.
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, the allow for the rapid dissemination of research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
@@
 However, as with grey literature,[@mahood2014] there are several logistical problems with carrying out systematic searches in preprint repositories.
-As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools-heading).
+As such, to enable the inclusion of preprints in the systematic review described in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading), a new tool addressing these issues is presented in Chapter \@ref(sys-rev-tools-heading).
 
@@
 
-In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] In terms of this thesis, participant age and sex are considered to be of particular interest.[@arain2009; @letenneur1999]
+In the context of this thesis, if lipids are found to have a causal role in development of dementia, evidence-based preventative strategies would be best informed by identifying the types of individuals who are most likely to receive benefit from treatment with lipid-modifying agents.[@arain2009; @clayton2018; @mccartney2016] However, if primary studies do not present results stratified by covariates of interest, meta-analyses of summary-level data on this topic often have limited ability to examine research questions related to exposure-covariate interactions.[@riley2010] Based on existing evidence, participant age and sex are considered to be of particular interest.[@arain2009; @letenneur1999]
 
-An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data, as access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and a common statistical model to be applied across all datasets, potentially eliminating some important sources of heterogeneity.[@stewart2002]
+An IPD meta-analysis of lipid levels on dementia outcomes would overcome this limitation of summary-level data because access to the raw data allows for an analysis that investigates these interactions.[@riley2020] This approach has the added benefit of allowing a common set of inclusion criteria and a common statistical model to be applied across all datasets, potentially eliminating some important causes of heterogeneity.[@stewart2002]
 
-Despite their advantages, IPD meta-analysis are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request from authors" declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014].
+Despite their advantages, IPD meta-analyses are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request" from authors declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014].
 Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
@@
 
-I will attempt to obtain the raw data from relevant primary studies identified by the systematic review in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+I will attempt to obtain the raw data from relevant primary studies identified by the systematic review presentd in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
-This will enable the assessment of the effect of lipids on dementia stratified by key variables such as sex.
+This will enable the assessment of the effect of lipids on dementia, and whether this relationship is modified by key variables such as participants' age or sex.
 
-<!----------------------------------------------------------------------------->
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Triangulating across study designs {#intro-triangulation}
@@
 As illustrated in Section \@ref(evidence-association), several diverse epidemiological methods have been used to examine the effect of varying blood lipid levels on dementia risk.
-However, each method is limited by its own biases.
-Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these inherent differences in study design, and as a result, in biases.[@lawlor2016] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
+Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these differences in study design, and as a result, in underlying bias structures.[@lawlor2016] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
 The ideal scenario is where predicted sources of bias are likely to be in competing directions, one to strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provide a middle-ground between the competing directions of bias.
@@
 To address this limitation, this thesis seeks to develop and apply a novel quantitative triangulation approach to answer causal questions on the effect of blood lipids on dementia outcomes.
-All existing evidence, regardless of study design, is first identified and assessed using domain-based tools by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+All existing evidence, regardless of study design, is first identified and assessed for risk of bias by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 The existing evidence base is then supplemented by two primary analyses, presented in Chapters \@ref(cprd-analysis-heading) and \@ref(ipd-heading).
-Finally all existing and new evidence is incorporated into the quantiatative triangulation framework in Chapter \@ref(tri-heading).
+Finally all existing and new evidence is incorporated into the quantitative triangulation framework in Chapter \@ref(tri-heading).
 
@@
 
-### Aims and objectives
+### Aim and objectives
 
-The over-arching aim of this thesis is to explore the relationship between blood lipid levels, and by extension treatments that modify blood lipid levels such as statins, and the subsequent risk of dementia and related outcomes
-
+The central aim of this thesis was to infer the causal effect of blood lipid levels on dementia outcomes via evidence synthesis methods.
 The specific research objectives that this thesis seeks to address are:
@@
 Chapters are self-contained, presenting the methods and results of that specific research project.
-They are bookended by introductory and discussion sections which place the methods and results in context.
-Each chapter is prefaced by a "lay" or plain English summary.
-<!-- TODO developed with input from the Patient and Public Advisory Group (see Section \@ref(disc-PPI) for a discussion of the group's involvement and Appendix \@ref(appendix-ppi) for more detail on the group).
--->
+The sole exception to this is the systematic review, which due to its size is split across Chapters \@ref(sys-rev-methods-heading) (Methods) & \@ref(sys-rev-results-heading) (Results).
+Each chapter is bookended by introductory and summary sections which place the methods and results in context.
+Finally, each chapter is prefaced by a "lay" or plain English summary.
 
 -   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis to non-subject area experts, and discusses the motivation for the remainder of the thesis.
--   **Chapter \@ref(sys-rev-tools-heading):** This chapter introduces a new tool, `medrxivr`, which was used to developed to allow for systematic searches of the health-related preprint repositories.
+This chapter provides an introduction to the topics covered in this thesis, and discusses the motivation for the research presented in the following chapters.
+-   **Chapter \@ref(sys-rev-tools-heading):** This chapter introduces a new tool, `medrxivr`, which was developed to allow for systematic searches of the health-related preprint repositories.
 -   **Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading):** These chapters describe, respectively, the methods and results of a comprehensive systematic review and meta-analysis.
-This review examined all available evidence on the effect of blood lipids and interventions that modified blood lipids on dementia outcomes.
+This review examined all available evidence on the association of blood lipids and LRA with subsequent risk of dementia.
 -   **Chapter \@ref(cprd-analysis-heading):** This chapter examines the relationship between lipid-regulating agent use and dementia outcomes in the Clinical Practice Research Datalink, a large primary care electronic health record database.
--   **Chapter \@ref(ipd-heading):** This chapter describes an individual participant data analysis of several longitudinal cohort studies to describe the relationship between blood serum lipids and dementia outcomes, stratified by important covariates such as sex.
--   **Chapter \@ref(tri-heading)**: This chapter integrates the evidence identified and produced by the preceeding chapters as part of a quantitative triangulation framework.
+-   **Chapter \@ref(ipd-heading):** This chapter describes an individual participant data analysis of three longitudinal cohort studies to describe the relationship between blood lipids and dementia outcomes
+-   **Chapter \@ref(tri-heading)**: This chapter integrates the evidence identified and produced by the preceding chapters as part of a quantitative triangulation framework.
 -   **Chapter \@ref(discussion-heading)**: This chapter summarise the key clinical and methodological findings of the thesis and discusses their implications for practice.
@@
 
-### Contributions to the scientific literature {#literature-contributions}
+### Contributions to the literature {#literature-contributions}
 
@@
 
-The experience of extracting data for the systematic review in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) inspired a practical guide for researchers.
+The experience of extracting data for the systematic review in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) inspired a practical guide which aims to help primary researchers make their data synthesis-ready.
 This piece was co-written with Dr.
-Emily Hennessy (see Author Declarations in the front materials).
+Emily Hennessy (see Acknowledgements in the front materials).
 
@@
 
-The tool used to visualise the risk-of-bias assessments in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) has been published in Research Synthesis Methods.
+A publication describing the tool used to visualise the risk-of-bias assessments in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) has been published in Research Synthesis Methods.
 See Appendix \@ref(appendix-robvis) for more details on this tool.
@@
 
-An R package containing function to implement the quantitative triangulation approach detailed in Chapter \@ref(tri-heading).
+An R package containing functionality to implement the quantitative triangulation approach detailed in Chapter \@ref(tri-heading).
 At present, only the development version of the package is available, which can be installed from GitHub using:
@@
 * In this introductory chapter, I provided background information on the core elements of the central research question and framed the research presented in the context of a theoretical framework of evidence synthesis.
-I outlined the central aim of the thesis and provided an overview of the individual analyses performed.
 
-* I also described the contributions of this thesis to the scientific literature.
-Finally, I discussed the research tools and software developed to support the analyses in this thesis, one of which (the preprint search tool) is introduced more fully in the following chapter.
+* I also outlined the central aim of this thesis and provided an overview of the individual analyses performed.
+I described the contributions of this thesis to the field, both in terms of peer-review publications and conference abstracts.
+
+* Finally, I discussed the research tools and software developed to support the analyses performed in this thesis, one of which (the preprint search tool) is introduced more fully in the following chapter.

### 2021-12-15 02-Chp-Systematic-Review-Tools.Rmd
Update table captions to new style
Ciara edits

@@
 
-# medrxivr: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
+# `medrxivr`: an R package for systematically searching biomedical preprints {#sys-rev-tools-heading}
 
@@
 
-Preprints are copies of academic manuscripts that are posted online in advance of being formally published by an academic journal.
-They represent an important source of scientific literature.
-A new software program called `medrxivr` was created as part of this thesis to allow researchers to find preprints related to their research in a transparent and reproducible way.
-Development of this tool was an essential part of this thesis, as preprints represent a key source of information needed for the research reported in future chapters.
+Preprints are copies of academic manuscripts that are posted online in advance of being formally peer-reviewed and published by an academic journal.
+As part of this thesis, a new software program called `medrxivr` was created to allow researchers to find preprints related to their research in a transparent and reproducible way.
+Development of this tool was important, as preprints represent a key source of information needed for the research reported in future chapters.
 
@@
 Preprints represent an increasingly important source of scientific information (see Section \@ref(diverse-sources-preprints)).
-As a result, repositories of preprinted articles should be considered a distinct but complementary information source when reviewing the evidence base as part of a systematic review.
+As a result, when reviewing the evidence base as part of a systematic review, repositories of preprinted articles should be considered a distinct but complementary information source to databases of published articles.
 The two key repositories in the health science are bioRxiv, established in 2013,[@sever2019] and medRxiv, which launched in 2019 and was designed to replace the "Epidemiology" and "Clinical Trial" categories of bioRxiv.[@rawlinson2019]
 
-Searching these preprints as part of the systematic review described in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) was a necessity, as many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
+Searching these preprints as part of the systematic review described in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) was a necessity because many of the existing reviews on the topic of lipids and dementia have not considered this important source of evidence.
 At the time of writing, however, the bioRxiv and medRxiv websites allow only simple search queries as opposed to the complex searches containing Boolean logic operators (AND/OR/NOT) that information specialists use to query other major databases.[@bramer2018;@gusenbauer2020] Additionally, the best available extraction mechanism for obtaining references for all records returned by a search involved going through each record and downloading individual citations one-by-one.
-As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID, this already time-consuming and error-prone method is no longer feasible.
+As the scale of these preprint databases increase, particularly in light of the massive expansion of the medRxiv repository as a result of COVID-19, this already time-consuming and error-prone method is no longer feasible.
 
@@
 As the majority of work on this aspect of my thesis is represented by lines of code or online documentation (available at [https://github.com/ropensci/medrxivr](https://github.com/ropensci/medrxivr) and [https://docs.ropensci.org/medrxivr/](https://docs.ropensci.org/medrxivr/) respectively), this chapter is an intentionally short, high-level summary of my work on this project.
-The GitHub repository for the `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.[@zotero-15029]
+The GitHub repository for `medrxivr` contains a complete record of the development of this tool, including discussion with other members of the systematic review community.[@zotero-15029]
 
@@
 
-```{r medrxivr-sr, echo = FALSE, fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
+```{r medrxivr-sr, echo = FALSE, fig.pos="h", fig.align='center',results="asis", fig.cap='(ref:medrxivr-sr-cap)', out.width='65%', fig.scap='(ref:medrxivr-sr-scap)'}
 knitr::include_graphics(file.path("figures","sys-rev-tools","medrxiv-role.png"))
@@
 
-I developed the tool to meet three success criteria,[@wateridge1995] influenced both by the functionality required to perform systematic searches as part of the review presented in the subsequent chapters, discussion with information specialist colleagues, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
-The criteria were as follows:
+I developed the tool to meet three success criteria:[@wateridge1995]
 
@@
 
-2.  support for bulk export of references returned by the search to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
+2.  support for bulk export of references returned to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
 
-3.  automated retrieval of the full-text PDFs of relevant records, similar to the Find Full Text feature offered by EndNote.
+3.  automated retrieval of the full-text PDFs of relevant records.
+
+These criteria were influenced by the need for functionality to perform systematic searches as part of the review presented in the subsequent chapters, discussion with information specialist colleagues about key features, and an informal survey of the evidence synthesis and health librarian communities on Twitter.
 
@@
 Prior to development of this tool, I conducted an audit of existing tools for accessing medRxiv and bioRxiv metadata.
-While none addresses the success criteria described above, two of these tools are useful to consider to highlight the additional functionality that `medrxivr` contributes.
+While none addresses the success criteria described above, two of these tools are useful in highlighting the additional functionality that `medrxivr` contributes.
 
@@
 However, the core functionality of the Rxivist platform is focused around exploring the number of times a preprint has been downloaded and/or shared on Twitter, to allow researchers to find the most popular papers related to their topic.
-The search interface[@zotero-15027] does not allow for complex search strategies using Boolean operators and there is no option to batch-export the results of a search.
+Additionally, the search interface[@zotero-15027] does not allow for complex search strategies using Boolean operators.
 
-The second tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
+The second preexisting tool, `search.bioPreprint`, allows users to search for terms across a range of preprint servers, including medRxiv and bioRxiv, but also journals which use a post-publication peer-review process such as F1000Research.[@iwema2016] However, similar to the Rxivist platform, this tool is designed for researchers aiming to keep up to date with recent developments in their fields rather than systematically assess the entirety of the available literature.
 As such, the platform only returns the most recent `r comma(1000)` records by publication date.
@@
 
-Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-methods-heading).
-Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality and I released the initial version of the `medrxivr` R package in February 2020.
+Work on the `medrxivr` tool began in Summer 2019, and initially consisted of a development of a set of R scripts to allow for searching medRxiv and bioRxiv as part of the systematic search outlined in Chapter \@ref(sys-rev-methods-heading).
+Following interest from other researchers in using the *ad-hoc* web-scraping scripts, additional development work took place in 2019/2020, allowing for improved searching and exporting functionality.
+I released the initial version of the `medrxivr` R package in February 2020.
 
@@
 Web-scraping is a fragile mechanism for extracting data, as it is entirely dependent on consistent website design and underlying code structure remaining unchanged.[@shaw2002; @laprie1992].
-In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping performed as expected required that I regularly update or fix the script.
+In the case of `medrxivr`, as the medRxiv/bioRxiv websites are regularly updated, ensuring the web-scraping script continued to perform as expected required substantial maintenance work.
 
@@
 
-While the package allows users to interact with and search both medRxiv and bioRxiv metadata, as the process is identical for both, searching the medRxiv database is used as an illustrative example throughout this chapter.
+While the package allows users to interact with and search both medRxiv and bioRxiv metadata, because the process is identical for both, searching the medRxiv database is used as an illustrative example throughout the remainder of this chapter.
 
@@
 
-Prior to searching the metadata, it must first be imported in R.
-In `medrixvr`, I have provided two separate but related methods for users to import the data (Figure \@ref(fig:medrxivr-data-sources)).
+Prior to searching the metadata, users must first create a local copy of the database, denoted using `mx_data` below.
+In `medrixvr`, I have provided two separate but related methods to achieve this (Figure \@ref(fig:medrxivr-data-sources)).
 The first of these methods, accessed via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
@@
 However, this approach has two limitations.
-Firstly, as the API returns results as a series of pages limited to 100 records per page, downloading the entire database requires a time-intensive process of cycling through each page.
+Firstly, because the API returns results as a series of pages limited to 100 records per page, downloading the entire database requires a time-intensive process of cycling through each page.
 Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
 To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
+Note that due to the size of bioRxiv, only a maintained snapshot of the medRxiv repository is available via `mx_snapshot()`.
 
@@
 This snapshot is created each morning at 6am using a process known as "git-scraping",[@zotero-15031] whereby the entire database is downloaded using the `mx_api_content()` function and saved as a comma separated value (CSV) file in an online repository (Figure \@ref(fig:medrxivr-data-sources)).
-Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (as it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
+Calling `mx_snapshot()` imports this CSV into R, and has the advantage of both faster loading of the data into R (because it is imported as a single file and does not require cycling through the output of the API) and an absence of any reliance on the API.
 The one limitation of this approach is that the snapshot (by its nature) will not contain details of records added to the database since it was taken.
-However, given that the number of records added each day is relatively low, this should pose minor issues.
+However, given that the number of records added each day is relatively low, this should only pose minor issues.
 
@@
 
+Note that for my example, I took a two-step approach by first creating the full search term `myquery` which is then passed to `mx_search()`.
+This is not necessary to perform a search, as users can pass terms directly to `mx_search()`:
+
+```{r, eval = FALSE}
+# Run a search to find all records with "dementia"
+results <- mx_search(mx_data,
+                     "dementia")
+```
+
 <!----------------------------------------------------------------------------->
@@
 
-An important argument of the `mx_search()` is `report`, which outputs a structured table with each search strategy presented on an individual line and the number of records associated with this strategy.[@rethlefsen2021prisma]
+An important feature of the `mx_search()` is the `report` functionality, which outputs a structured table showing each search term along with the corresponding number of records.[@rethlefsen2021prisma]
 
@@
 
-This allows users to discover which terms in their search are contributing most to the total number of results returned.
-This is important as part of developing a search strategy,[@bramer2018] as it allows for the key terms related to each topic to be discovered.
+This is important as part of developing a search strategy,[@bramer2018] because it allows for the key terms related to each topic to be discovered.
 It also aids in identifying misspelled or case-sensitive search terms, which will frequently return no results.
 As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, as "Alzheimer's" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
+This is expected, because "Alzheimer's" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
 
-In hindsight, the decision to make the search case-sensitive was a poor one as users reported being unaware of this setting when searchin.
-However, changing the default behaviour of `mx_search()` to be case-insensitive is problematic, as it could result in different numbers of hits based solely on which version of the package the user has installed.
+In hindsight, the decision to make the search case-sensitive was a poor one because users reported being unaware of this setting when carrying out their search.
+However, changing the default behaviour of `mx_search()` to be case-insensitive is problematic because it could result in different numbers of hits based solely on which version of the package the user has installed.
 To address this, `mx_search()` now contains an `autocaps` argument, which when set to `TRUE` will automatically search for both capitalised and uncapitalised versions of the search term.
@@
 In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to export easily the results of their systematic search to a reference manager.
-While it is a seemingly simple request, this is is one of the key ways in which `medrxivr` is set apart for other preprint search tools, including the native medRxiv/bioRxiv website search functionality.
+While this would seem a likely candidate to be a generic feature, this is one of the key ways in which `medrxivr` is set apart from other preprint search tools.
+None of tools that I audited provide this feature, nor does the native medRxiv/bioRxiv website search.
 
-For example, the results of our simple search above can be exported to the `"medrxiv_export.bib"` file using the following code:
+The results of our simple search above can be exported to the `medrxiv_export.bib"` file using the following code:
 
@@
 `mx_download()` takes the list of included records and saves the PDF for each to a folder specified by the user.
-This functionality is similar to the "Find Full Text" feature offered by EndNote.
 
@@
 This would negate the current need to download a local copy of the relevant preprint database before searching it, which is currently the rate limiting step for performing searches.
-For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately an hour.
+For example, as of January 2021, downloading a copy of the bioRxiv database takes approximately one hour.
 
@@
 
-In addition to being used to search systematically health-related preprint servers, as illustrated in the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading), `medrxivr` has other uses.
+In addition to being used to systematically search health-related preprint servers, as illustrated in the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading), `medrxivr` has other uses.
 
@@
 allowing for a two-year lag between preprint posting and publication).
-This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a subtantial number of preprints are never formally published but remain accessible as preprints.
+This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a substantial number of studies are never formally published but remain accessible as preprints.
 
@@
 
-While searching of the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis, there are some important limitations to note here.
+While searching the medRxiv and bioRxiv databases was crucial for the systematic review element of my thesis, there are some important limitations to note here.
 A key example is that the tool only searches the available metadata of preprint records (the title, abstract and keywords), rather than the full text of preprints, and so some relevant records might be missed.
@@
 
-There is also the potential that the cross-section of literature posted on medrxiv/bioRxiv is substantially different to those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
+There is also the potential that the cross-section of literature posted on medRxiv/bioRxiv is substantially different from those suffering from publication bias (studies or analyses that are not published for a range of reasons including results that are not deemed "novel" or are not statistically significant).[@song2010] This is because simply lowering the barriers to publication may well encourage authors to published "null" results, but due to the effort involved in writing up a distributable manuscript, it is unlikely to completely address the "file drawer" effect.[@rosenthal1979]
 
@@
 -   I have contrasted `medrxivr` with other available interfaces to medRxiv/bioRxiv data to highlight the added functionality it offers.
-I have also discussed the tools reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.
+I have also discussed the tool's reception to date, its limitations, and the important role of open-source tools like `medrxivr` in evidence synthesis.

### 2021-12-15 front-and-back-matter/99-appendices.Rmd
Typo in appendix

@@
 
-(ref:searchHitsMedline-caption) __Medline search strategy__ - Full list of search terms used to identify relevant records in the Medline bibliographic database.
+(ref:searchHitsMedline-caption) __MEDLINE search strategy__ - Full list of search terms used to identify relevant records in the MEDLINE bibliographic database.
 The number of records returned per search term is also displayed.
 
-(ref:searchHitsMedline-scaption) Medline search strategy
+(ref:searchHitsMedline-scaption) MEDLINE search strategy
 

### 2021-12-15 03-Chp-Systematic-Review-Methods.Rmd
SMall edits

@@
 
-Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to an important research question.
+Systematic reviews are a type of research study that aim to collect and combine all existing evidence to provide the best possible answer to a research question.
 Well-performed reviews involve multiple steps including: searching for existing studies; assessment of the studies against predefined inclusion criteria; collection of data from each study; and assessment of each study's method and results.
@@
 This chapter presents the methods used to perform a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
-In addition, the review examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
-The results of this systematic review are then presented in Chapter \@ref(sys-rev-results-heading).
+In addition, the review included studies that examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
+The results of this systematic review are presented in Chapter \@ref(sys-rev-results-heading).
 :::
@@
 These include randomised controlled trials, observational studies of different design, and Mendelian randomisation studies.
-However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipids/statins with dementia outcomes across these distinct evidence types.
-Collating these diverse evidence sources is important, as, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
+However, based on a scoping review of existing literature, no previous evidence synthesis exercise has attempted to examine the association of lipid levels with dementia outcomes across these distinct evidence types.
+Collating these diverse evidence sources is important because, if the observed association between lipids and dementia is constant across them, it increases our confidence in the association.
 As such, the primary aim of this analysis was to systematically review all available literature describing prospective analyses, regardless of study design.
@@
 Secondly, I explicitly sought to include health-related preprint servers as a potential evidence source in this review, as they are infrequently considered by evidence synthesists but can report relevant unpublished analyses.
-As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of including preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
+As a sensitivity analysis to the review presented in this chapter, I sought to quantify the additional evidential value of relevant preprints, making use of the preprint search tool presented in Chapter \@ref(sys-rev-tools-heading).
 
-Given the size of the review, I have separated the methods and results into two chapters for ease of reading.
+Given the size of the review, I have split its reporting across two separate chapters for ease of reading.
 This chapter details the methodology used, while Chapter \@ref(sys-rev-results-heading) presents the results.
@@
 In line with best-practice guidance, secondary reviewers were used to check the accuracy of screening, data extraction and risk-of-bias assessment processes.
-Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements and Author Declaration in the front matter).
+Due to the scale of the project, this review was performed in conjunction with a team of secondary reviewers (see Acknowledgements in the front matter).
 
@@
 
-I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction (total cholesterol, high- and low-density lipoprotein cholesterol and triglycerides).
+I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as a binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction.
+The fractions considered by this review were namely total cholesterol (TC), high-density lipoprotein cholesterol (HDL), low-density lipoprotein cholesterol (LDL) and triglycerides (TG).
 I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence.
@@
 Alternatively, where no baseline screening was employed, participants were assumed to be dementia free if less than 50 years of age at baseline.
-Studies of any duration were included to allow for exploration of the effect of length of follow-up on the effect estimate.
-No limits were placed on the sample size of included studies.
 Eligible studies defined dementia outcomes according to recognised criteria.
-Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] or Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were the sole exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.
+Examples of acceptable criteria included the International Classification of Diseases (ICD),[@organizationwho1993] the National Institute of Neurological Disorders and Stroke Association-Internationale pour la Recherche en l'Enseignement en Neurosciences (NINDS-AIREN),[@roman1993] and the Diagnostic and Statistical Manual of Mental Disorders (DSM) criteria.[@edition2013] Studies utilising electronic health records were an exception to this, as it was assumed that health care professionals employed their own expertise when entering the outcome into the EHR.
 
-Conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract.
+Studies of any duration were included, and no limits were placed on the sample size of included studies.
+Finally, conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract.
 No limitations were imposed on publication status, date, venue or language.
@@
 Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measure change in continuous cognitive measures (e.g.
-MoCA score) without an attempt to map these scores to ordinal groups (e.g.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measured change in continuous cognitive measures (e.g.
+Montreal Cognitive Assessment (MoCA) score) without an attempt to map these scores to ordinal groups (e.g.
 no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
 
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) and studies where there was no screening for dementia at baseline were excluded.
-An exception to the latter criteria was made if the sample was initially assessed in mid-life (i.e.
-below the age of 50) were excluded.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) were excluded.
 Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded.
-For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statins can be estimated.
+For example, a study examining exercise + statins versus statins alone would be excluded, but a study examining exercise + statins vs exercise alone would be eligible as the effect of statin use can be estimated.
 Finally, studies using a dietary intervention, for example an omega-3 fatty acid enriched diet, were excluded as it is difficult to disentangle the effect of other elements contained within the diet.
@@
 I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched in June 2019 from inception onwards: Medline, EMBASE, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
-As the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
-The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms to identify studies which have examined the relationship between blood lipids levels and dementia, incorporating input from an information specialist.
-The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for MEDLINE before being adapted for use in the other bibliography databases listed.
-A high-level outline of the strategy is presented in the Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
+The following databases were searched in June 2019 from inception onwards: MEDLINE, Embase, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+Given that the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
+
+The search strategy used in each database was developed in an iterative manner using a combination of free text and controlled vocabulary (MeSH/EMTREE)[@lefebvre2019searching] terms, incorporating input from an information specialist.
+The strategy included terms related to lipids, lipid modifying treatments, and dementia, and was designed for use in MEDLINE before being adapted to the other bibliography databases listed.
+A high-level outline of the strategy is presented in Table \@ref(tab:searchOverview-table) below and the full search strategies for each database are presented in Appendix \@ref(appendix-search-strategy).
 <!-- TODO Need to actually attach each search strategy.
@@
 <!----------------------------------------------------------------------------->
-(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy including all terms and the number of hits per term is included in Appendix \@ref(appendix-search-strategy).
+(ref:searchOverview-caption) __Summary of systematic search by topic__ - The full search strategy for each databases searched, including all search terms and the number of hits per term, is presented in Appendix \@ref(appendix-search-strategy).
 
@@
 When searching the bibliographic databases, study design filters (Lines 9-11 in Table \@ref(tab:searchOverview-table)) were employed to try to reduce the screening load.
-To ensure that the study design filters were not excluding potentially relevant records, a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)) was screened.
-
-<!-- TODO need to comment on this feed-back process, or remove -->
+I confirmed that the study design filters were not excluding potentially relevant records by screening a random sample of 500 records identified by the main search but excluded by the filters (defined as "8 NOT 12" in Table \@ref(tab:searchOverview-table)).
 
@@
 
-Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, while theses were accessed using the Open Access Theses and Dissertations portal.
-In addition, the abstracts list of relevant conferences (e.g.
+Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, and theses were accessed using the Open Access Theses and Dissertations portal.
+In addition, the abstract lists of relevant conferences (e.g.
 the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
-<!-- TODO how were these searched?
-Date and other range --> Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]
+Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]
 
@@
 Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, I re-screened the same ~10% sample with 3 month lag to assess intra-rater consistency.
+Additionally, I re-screened the same ~10% sample with three month lag to assess intra-rater consistency.
 
@@
 
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This measure was chosen over other methods such as percent agreement (number of agreements divided by total number of assessments), as it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
 [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
-The formulae used to calculate the coefficient are given in Appendix \@ref(appendix-gwet).
+The formulae used to calculate AC1 are given in Appendix \@ref(appendix-gwet).
 
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrates an issue with the screening process (defined as an AC1 of less than 0.9), it indicates the need for a larger proportion of records to be dual-screened.
+If this assessment demonstrated an issue with the screening process (defined as an AC1 of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.
 
@@
 
-* Article metadata: year of publication, author, journal)
-* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used)
+* Article metadata: year of publication, author, journal
+* Study characteristics: study location, data source, exposure, outcomes, diagnostic criteria used
 * Patient characteristics: age, sex, baseline cognition scores, baseline education scores
-* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value).
+* Results: exposure, outcome, effect measure, effect estimate, error estimate, p-value
 
@@
 
-As part of the data extraction process, multiple records resulting from a single analysis were included and grouped into single units, hereafter called studies.
+As part of the data extraction process, multiple records resulting from a single analysis were included and grouped into single units, hereafter referred to as studies.
 This was most common in cases where multiple records reported on the same analysis but at different time points.
@@
 
-where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup.
+where $N_i$, $M_i$ and $SD_i$ denote the number of participants, mean and standard deviation in the $i$th subgroup, respectively.
 This approach was implemented in a systematic manner, with the raw group data being extracted and a cleaning script employed to combine the groups for analysis.
@@
 
-where $Z = 38.67$ for total cholesterol, LDL-c and HDL-c, and $Z = 88.57$ for triglycerides.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
+where $Z = 38.67$ when converting total cholesterol, LDL-c and HDL-c measures, and $Z = 88.57$ when converting triglyceride measures.[@rugge2011] The choice of _mg/dL_ was influenced by the widely-used categories of lipids levels on the _mg/dL_ scale, as shown in Table \@ref(tab:lipidLevels-table) in Section \@ref(intro-lipid-fractions).
 
@@
 
-Where additional data, not included in the report of an analysis, were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted.
+Where additional data not reported by a study were required either for data extraction or risk-of-bias assessment, the corresponding author of the study was contacted.
 This approach was taken due to the potentially large impact of additional information obtained through contact with study authors on the results of the review.[@reynders2019]
@@
 
-A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(triangulation-overview) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
-To enable this triangulation exercise, detailed and structured risk-of-bias assessment formed an important part of this review.
+A key aim of the review presented here is to identify different sources of evidence at risk of a diverse range of biases, and to contrast and compare findings across them (see Section \@ref(intro-triangulation) for an overview of triangulation and Chapter \@ref(tri-heading) for the results of this analysis).
+To enable this triangulation exercise, detailed and structured risk-of-bias assessments formed an important part of this review.
 
-There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ to assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
+There has been a recent movement within the evidence synthesis community away from examining _methodological quality_ towards assessing _risk of bias_,[@mcguinness2018; @sterne2016] and thus directly evaluating the internal validity of a study.
 Internal validity is defined here as the absence of systematic error (or bias) in a study, which may influence its results.[@campbell1957; @juni2001]
@@
 This move was prompted by an unclear definition of methodological quality which could include facets such as unclear reporting, in addition to challenges in the comparison of results from different tools.
-<!-- TODO CITATION NEEDED --> As part of this shift, the focus moved from checklist or score based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
-<!-- TODO CITATION NEEDED --> Finally, the new tools tools move from assessing bias at the study level to considering separately each individual numerical result reported.
+As part of this shift, the focus moved from checklists and score-based tools towards domain-based methods, in which different potential sources of bias in a study are assessed in order.
+Additionally, the new tools move from assessing bias at the study level to considering each individual numerical result separately.
 For example, a study may report on the efficacy of an intervention at six months and two years follow-up.
 In this case, the proportion of missing outcome data may not be an issue at six months but may introduce bias after two years of follow-up.
-In this case, assigning a single risk-of-bias judgement to the study as a whole masks the different biases applicable to each unique result.
+In this case, assigning a single risk-of-bias judgement to the study as a whole would mask the different biases applicable to each unique result.
 
 In this review, domain-based tools were used to assess the risk of bias for each result in each included study.
-The study design-specific tools are introduced and discussed in more detail in the following sections.
+The study-design-specific tools are introduced and discussed in more detail in the following sections.
 
@@
 
-Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] The tool assesses the risk of bias across five domains:
+Randomised controlled trials were assessed using the RoB 2 tool.[@sterne2019] This tool assesses the risk of bias across five domains:
 
@@
 
-For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assess the risk of bias across seven domains:
+For non-randomised studies of interventions (NRSI), I used the ROBINS-I (Risk Of Bias In Non-randomised Studies - of Interventions) tool.[@sterne2016] This tool assesses the risk of bias across seven domains:
 
@@
 
-While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments for this review were performed.
+While a risk-of-bias tool for non-randomised studies of exposures (NRSE) is currently under development,[@morganr2020] it was insufficiently developed at the time the risk-of-bias assessments were performed.
 Instead, I used a version of the ROBINS-I tool informed by the preliminary ROBINS-E tool (Risk of Bias In Non-randomised Studies – of Exposure), which I had previously applied in a published review.[@french2019] The version had no signaling questions and so judgements, using the same four levels of risk of bias as ROBINS-I, were made at the domain level.
-The motivation for using this tool above other established tools such as the Newcastle-Ottowa scale (NOS)[@wells2000] was two-fold.
+The motivation for using this tool above other established tools - such as the Newcastle-Ottowa scale (NOS)[@wells2000] - was two-fold.
 In the first instance, as mentioned in the introduction to this section, using a domain-based tool has distinct advantages over better-developed checklist-type tools including the NOS.
-Additionally, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs as part of this review.
+Secondly, using a domain-based tool for non-randomised studies of exposures enabled better comparison with risk-of-bias assessments performed for the other study designs considered by this review.
 
@@
 At present, no formalised risk-of-bias assessment tool for Mendelian randomisation studies is available.
-Assessment of the risk of bias in Mendelian randomisation studies was informed by the approach used in a previous systematic review of Mendelian randomisation,[@mamluk2020] as identified by a review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies.[@spiga2021] Advanced results from this review were obtained from contact with the review authors.
-A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic and other confounding, pleiotropy and population stratification.
+Assessment of the risk of bias in Mendelian randomisation studies was informed by the tool developed by Mamluk _et al_ for use in their own review.[@mamluk2020] This tool was identified through a meta-review of risk-of-bias assessments in systematic reviews of Mendelian randomisation studies,[@spiga2021] advanced results of which were obtained through personal communication with the authors.
+A copy of this tool is available in Appendix \@ref(appendix-mr-rob), but in summary, results were assessed for bias arising from weak instruments, genetic confounding, other confounding, pleiotropy and population stratification.
 Acceptable judgements for each of the five domains in the tool were "low", "moderate" and "high" risk of bias.
@@
 
-In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the analysis level.
-This assessment examines evidence missing due to selective non-reporting as distinct from the selective reporting of a single result from multiple planned analyses.
-The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] <!-- TODO Need more here describing missing evidence --> The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.
+In addition to assessing the risk of bias within each result contributing to a synthesis, I also assessed risk of bias due to missing evidence at the synthesis level.
+This assessment examines evidence missing due to selective non-reporting as opposed to the selective reporting of a single result from multiple planned analyses.
+The assessment was performed using the forthcoming RoB-ME (Risk of Bias due to Missing Evidence in a synthesis) tool.[@zotero-15123] The tool is in development stages, and as part of this review, I piloted the tool and provided feedback to the developers.
 
@@
 
+#### Analysis overview {#sys-rev-analysis-overview}
+
 An initial qualitative synthesis of evidence was performed, summarising the data extracted from studies stratified by study design.
@@
 <!-- TODO CITATION NEEDED -->
-
-&nbsp;
-<!----------------------------------------------------------------------------->
-
-#### Analysis overview {#sys-rev-analysis-overview}
 
@@
 The result in the $i$th study is denoted as $y_i$.
-The weight assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):
+The weight ($w_i$) assigned to this result is then given as the inverse of the variance of that result ($v_i$) plus the estimate of between-result variance ($\tau^2$):
 
@@
 
-&nbsp;
-
-Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk of bias judgement, and summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
+Results included in each meta-analysis were stratified into subgroups on the basis of the overall risk-of-bias judgement.
+Summary estimates for each subgroup, in addition to an overall effect estimate, are displayed in each forest plot.
 Additional descriptive statistics are presented, while prediction intervals are shown as a dotted line banding the overall effect estimate.
@@
 for example, highest vs lowest quartile).
-<!-- TODO Question: if I look at highest vs lowest, and also at top dose vs lowest dose, am I double counting results?
---> While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
+While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.
-
-<!-- TODO Maybe rephrase last sentence -->
 
@@
 _A priori_, I was interested in the effect that the age at baseline, sex and risk-of-bias judgement had on the results.
-Syntheses with greater than 10 results were assessed for heterogeneity across these covariates.[@deeks2019]
-
-Finally, I investigated the potential for small study effects, which may be caused by publication bias, both visually using funnel plots and formally using Egger's regression test.[@sterne2011]
+Syntheses with greater than 10 results were assessed for heterogeneity across these covariates.[@deeks2019] I also investigated the potential for small study effects (of which publication bias is one potential cause) in syntheses with greater than 10 results, both visually using funnel plots and formally using Egger's regression test.[@sterne2011]
 
@@
 
-Evidence maps are useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was visualised on a world map.
+Evidence maps are a useful way to explore the distribution of research cohorts included in a systematic review.[@saran2018] As part of the initial descriptive synthesis, the location of each individual study contributing to the evidence base was visualised on a world map.
 
-One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the ROB2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond.
-This tool was developed as an adjunct to this thesis to aid in creating standardised risk-of-bias figures.[@mcguinness2020robvisPaper] A summary of this tool is contained in Appendix \@ref(appendix-robvis), and all forest plots presented in this Chapter were created using this tool.
-Unless otherwise stated in the figure caption, only a single effect measure (hazard ratio/odds ratio/etc) is represented in the forest plot.
+One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the RoB 2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis, as assessed using the RoB-ME tool, is shown beside the overall summary diamond.
+This tool was developed as an adjunct to this thesis,[@mcguinness2020robvisPaper] and summary of its functionality can be found in Appendix \@ref(appendix-robvis).
+Unless otherwise stated in the figure, only a single effect measure (hazard ratio/odds ratio/etc) is represented in a given forest plot.
 
@@
 
-Preprints are considered a valuable evidence source within this thesis (see Introduction, Section \@ref(diverse-sources-preprints)).
+Preprints are considered a valuable evidence source within this thesis (see Section \@ref(diverse-sources-preprints)).
 As an adjunct analysis to this review, meta-analyses including a preprint result were re-analysed using a fixed effect model.
-The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided by the preprint.
-In addition, in meta-analysis including at least one preprinted result, I assessed the impact of including the preprinted results on the summary estimate using a leave-one-out approach.
+The weight assigned to the preprinted result was extracted and used to assess the additional evidential value provided to the synthesis by the preprint.
+In addition, I assessed the impact of including the preprinted results on the summary estimate, using a leave-one-out approach.
 
-<!-- COMMENT You need to state a priori in what objective way you can judge if pre-prints do or do not have added value -->
-
-Additionally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether identified preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provide a distinct evidence source to conventional bibliographic databases).
+Finally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether included preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provided a distinct evidence source to conventional bibliographic databases).
 
@@
 
-* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipids and lipid-regulating agents.
+* In this chapter, I have presented the methods underpinning a comprehensive systematic review of the existing literature on the association of dementia incidence with blood lipid levels and lipid-regulating agents.
 
-* I have detailed how this review will find, extract, critically assess and synthesize the results of existing studies.
-Additionally, I have highlighted how this review will examine the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.
+* I have detailed how this review found, extracted, critically assessed and synthesized the results of existing studies.
+Additionally, I have highlighted how this review examined the impact of including preprinted results, as enabled by the research tool presented in the previous chapter.
 
-* In the following chapter, I present the results of this review, and detail how the identified evidence is used throughout the remainder of the thesis.
+* In the following chapter, I present the results of this review, and detail how the evidence identified is used throughout the remainder of the thesis.

### 2021-12-15 06-Chp-IPD-Analysis.Rmd
SMall edits

@@
 
-<!-- TODO Need quote for here -->
-
 # Individual participant data meta-analysis of blood lipid levels and dementia outcomes {#ipd-heading}
@@
 
-<!-- TODO Finish lay summary -->
-
-<!-- At the same time, I will write to authors to obtain anonymised data on individual participants.
-The data from each study will be combined using a technique known as individual participant data (IPD) meta-analysis.
-This will allow me to examine if the relationship between lipids in dementia depends on any patient characteristics (e.g.
-sex or age).
--->
-
-Individual participant data (IPD) meta-analyses are a special type of meta-analysis
-in which the authors of relevant studies are contacted with requests to access the raw data on each participant in the original study.
-This approach is different to the meta-analyses presented in the previous chapter, which used published summary results.
+This chapter examines the raw data pertaining to participants in previously published, relevant studies, a method of analysis called Individual Participant Data (IPD) meta-analysis.
+It uses this data to investigate the relationship between lipid levels and dementia risk, which is unique from the previous chapter because that chapter used published results rather than individual-level data.
 
@@
 
-In order to examine the relationship between lipid levels and dementia risk, I applied for access to `r n_applied$total` unique data sources containing information on these variables.
-However, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested access.
+I applied for access to `r n_applied$total` unique data sources for this analysis, however, only a small proportion of these data sources (`r fmt_applied(n_accessed$total)`) provided the requested data.
 
@@
 
-#### Comparison with previous analysis
+#### Comparison with a previous analysis
 

### 2021-12-15 07-Chp-Triangulation.Rmd
End of day:

@@
 
-In epidemiology, triangulation is the practice of using multiple sources of evidence to provide more reliable answers to a research question.
-Different sources of evidence will have different limitations.
+Sources of evidence often contain limitations which reduce our confidence in their results.
+To minimise the impact of these limitations, a method has been developed called triangulation which looks at multiple sources addressing the same question.
 If the result from each source points towards the same answer, this improves our confidence in the conclusion.
-Triangulation can either be _qualitative_ or _quantitative_.
-In qualitative triangulation, the results of each evidence source are discussed.
-In contrast, quantitative triangulation aims to combine the different results mathematically to obtain one single overall result.
 
@@
 
-In this chapter, I describe a new approach for quantitative triangulation, which combines two existing methods.
-For each source of evidence, I assess and account for robustness (do we believe the result, based on the methods/results of the study?) and relevance (does the source provide useful evidence relevant to the question we are interested in?).
-To showcase the new method, I apply it to two questions of interest.
-In each case, evidence from each of the previous chapters is combined to give an overall result.
+In this chapter, I describe a new approach for triangulation, which combines two existing methods. This approach is used to ensure that the results meet the following criteria:
+
+*	robustness - do we believe the result, based on the methods/results of the study?
+*	relevance - does the source provide useful evidence relevant to the question we are interested in?
+
+This triangulation approach is quantitative in nature, meaning I have tried to combine the results from different sources mathematically to obtain one single overall result.
+I have applied this method to assess the following relationships of interest:
+
+*	the effect of midlife LDL-c on Alsheimer’s disease
+*	the effect of midlife triglycerides on vascular dementia
 
@@
 
-When combined in the new framework, the results produced by previous chapters did not support an effect of low-density lipoprotein cholesterol (LDL-c) on Alzheimer's disease nor an effect of triglycerides on vascular dementia.
-I close the chapter by suggesting future work to further develop the new methods presented.
+My method did not support the existence of an effect in either relationship of interest. I close the chapter by suggesting future work to further develop and improve upon the new method presented.
 

### 2021-12-15 front-and-back-matter/_acknowledgements.Rmd
End of day:

@@
 
-There are many people without whose input and support this work would have been severely diminised:
+There are many people without whose input and support this work would have been severely diminished:
 
@@
 
-Thanks must also go to those who contributed their time and energy to my research projects: Matthew Lee, Lena Schmidt, Alexandra McAleenan, and Vincent Cheng.
-Francesca Spiga kindly shared an advance copy of her review of tools to assess Mendelian randomisation studies, and Rebecca Turner shared her code for bias-/indirectness-adjusted meta-analyses that underpins the quantitative triangulation framework presented in Chapter \@ref(tri-heading).
-
-A particular thank you to Emily Hennessy, with whom I co-wrote the guidance paper for preparing primary research for incorporation into systematic reviews.
-Similarly, thanks to Athena Sheppard for her support in assessing the impact of journal polices on open-data sharing.
+Thanks must also go to those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner.
 

### 2021-12-15 R/03-Code-Systematic-Review.R

@@ -1143,7 +1143,7 @@ metaregHypercholAd <- dat$AD %>%
   ) %>%
   .$pval %>%
   last() %>%
-  round(2)
+  round(2) 
 
 metaregHypercholDem <- dat$Dementia %>%
   select(-age,-sex) %>%

### 2021-12-16 01-Chp-Background.Rmd
Range of updates

@@
 
-(ref:statin-mechanisam-cap) Overivew of statins mechanism of action, inhibiting HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate, the rate-limiting step in cholesterol biosynthesis.
+(ref:statin-mechanisam-cap) __Statin mechanism of action__ - Statins inhibit HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate.
+This conversion is the rate-limiting step in cholesterol biosynthesis, and so statin use can lower cholesterol levels.
 
@@
 
-### Mendelian randomisation
+### Mendelian randomisation {}
 
 Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
-Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV),[@davies2018] namely that:
-
-1. the IV is associated with the exposure of interest (the relevance assumption);
-2. the IV and outcome do not share a common cause (the independence assumption); and
-3. the IV does not affect the outcome other than via the exposure (the exclusion restriction assumption).
+Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV)[@davies2018] which are discussed in Section \@ref(rev-discussion-MR).
 

### 2021-12-16 03-Chp-Systematic-Review-Methods.Rmd
Range of updates

@@
 
-Rater reliability was assessed using Gwet's agreement coefficient (AC1).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
+Rater reliability was assessed using Gwet's agreement coefficient ($AC1$).[@gwet2008] This approach was chosen over other measures such as percent agreement because it accounts for chance agreement between reviewers but does not suffer from bias due to severely imbalanced marginal totals in the same way that Cohen's $kappa$ value does.
 [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
-The formulae used to calculate AC1 are given in Appendix \@ref(appendix-gwet).
+The formulae used to calculate $AC$ are given in Appendix \@ref(appendix-gwet).
 
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated an issue with the screening process (defined as an AC1 of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.
+If this assessment demonstrated an issue with the screening process (defined as an $AC$ of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.
 
@@
 Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-<!-- TODO CITATION NEEDED -->
-
 Results were not combined across different study designs (i.e.
 RCTs were not combined in a meta-analysis with results from observational studies).
-The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(discussion-heading).
+The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(tri-heading).
 Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).

### 2021-12-16 04-Chp-Systematic-Review-Results.Rmd
End of day:
Range of updates

@@
 Using the methods outlined in the previous chapter, here I present the results of a systematic review of primary studies that have examined the relationship between the levels of blood lipids (such as cholesterol and triglycerides) and dementia outcomes.
-In addition, it examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
+In addition, I also examined the relationship between treatments that change blood lipid levels, such as statins, and dementia outcomes.
 
@@
 
-<!-- TODO Complete! -->
-
 <!-- TODO Consider adding a line to the descriptions of each forest plot regarding the direction - what's on the right, whats on the left -->
@@
 
-<!-- TODO Compare findings for two papers from Rantanen - not sure why? -->
-
 ### Initial search and validation of search filters
@@
 As expected, many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
-<!-- TODO include some example citations here -->
 
@@
 
-The PRISMA flow diagram presented in Figure \@ref(fig:prisma-flow-fig) illustrates the movement of articles through the review.
-To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the search tool described previously (presented in grey on the right of the diagram).
-
-Common reasons for exclusion at the full-text stage included studies reporting on ineligible exposures (Number of studies (N) = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
+A PRISMA flow diagram, presented in Figure \@ref(fig:prisma-flow-fig), illustrates the movement of articles through the review.
+To highlight the contribution of preprint archives to the review, the flow diagram delineates between those records captured through databases searches (presented on the left of the diagram) and those captured by the preprint search tool described previously (presented in grey on the right of the diagram).
+
+Common reasons for exclusion at the full-text stage included studies reporting on ineligible exposures (Number of records (N) = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
 change in cognitive scores), or the use of an ineligible study design (N = `r n_study_design`).
@@
 For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
-Similarly for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
-The discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance  towards exclusion.[@feinstein1990]
-
-&nbsp;
-
-<!----------------------------------------------------------------------------->
-(ref:agreeInter-caption) __Inter-rater agreement__ - For a subset of records, the decisions between two independent were compared.
+&nbsp;
+
+<!----------------------------------------------------------------------------->
+(ref:agreeInter-caption) __Inter-rater agreement__ - For a subset of records, the decisions between two independent reviewers were compared.
 Gewt's $AC1$ was calculated from this data to assess inter-rater reliability, indicating high accuracy ($AC1$ = `r agreeInter_coeff[1]`).
 
-<!-- TODO Include AC1 result in caption above -->
-
 (ref:agreeInter-scaption) Inter-rater agreement
@@
 <!----------------------------------------------------------------------------->
+
+Those records which were excluded in the initial screening, but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and of eligible lipids fractions.
+
+Similarly, for intra-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeIntra_coeff[1]`, $kappa$ = `r agreeIntra_coeff[2]`, Table \@ref(tab:agreeIntra-table)).
 
@@
 
-Those records which were excluded in the initial screening, but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
-This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and of eligible lipids fractions.
+In both cases, the discrepancy between the $AC1$ and $kappa$ coefficients illustrates the sensitivity of $kappa$ to imbalanced marginals, caused in this sample by a large imbalance towards exclusion.[@feinstein1990]
 
@@
 The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
-A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS), leading to complications in the synthesis of these estimates due to the potential for double-counting (see Section \@ref(sys-rev-res-AD)).
-
-Of the `r n_nrsi_included` non-randomised studies examining treatments that modify lipid levels, all examined statin use (`r n_statins`), while a small number also reported on other non-statins agents such as fibrates (`r n_fibrates`).
+A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS).
+This leads to complications in the synthesis of these estimates due to the potential for double-counting (see Section \@ref(sys-rev-res-AD)).
+
+Of the `r n_nrsi_included` non-randomised studies examining lipid-regulating agents (LRA), all examined statin use while a small number also reported on other non-statin agents such as fibrates (`r n_fibrates`).
 In the `r n_nrse_included` non-randomised studies of exposure, hypercholesterolemia (`r n_hyperchol`) and total cholesterol levels (`r n_TC`) were the most frequently reported risk factors.
@@
 
-<!-- Many studies using electronic health records as their data source did not accurately report the diagnostic codes used to identify cases. -->
-
-<!-- Midlife cholesterol levels were of particular interest, with several studies examining this age-range.  -->
-
-<!--- TODO Talk a little bit more about age here --->
-
-<!-- TODO Also need to extract the codes used in each study -->
-<!-- TODO Need to make sure that the MR studies actually don't report the  -->
-
 ```{r studyCharacteristics-setup, include = F}
@@
 <!----------------------------------------------------------------------------->
-<!-- To create the references below, go to the helper script and copy the output of  -->
 
@@
 
-<!-- TODO Sort out the fact that statins are included as an exposure in NRSE -->
-
-<!-- TODO Ensure all abbreviations at the end of this table are in the abbreviation section at the start. -->
-
 ```{r studyCharacteristics-table, message=FALSE, results="asis", echo = FALSE}
@@
 
-(ref:cohortLocations-cap) __Geographical distribution of study cohorts__ - The country or countries of origin for the studies include in the review are shown below.
-Note that the majority of included studies were performed in the Western world, predominantly in Europe and North America.
+(ref:cohortLocations-cap) __Geographical distribution of study cohorts__ - The country or countries of origin for the studies included in the review are shown.
+Note that the majority of included studies were performed in westernised countries, predominantly in Europe and North America.
 
@@
 
+Overall, the reporting of included studies was poor, particularly for non-randomised studies of lipids and LRA.
+Several studies did not report baseline characteristics such as the proportion of women in the study cohort.
+Additionally, some omitted important details on reported characteristics (e.g.
+the study reported the mean but not the standard deviation of baseline age).
+
 Finally, there were several eligible studies reported as conference abstracts that did not present numerical results.
@@
 #### Lipids
-
-<!-- TODO Deal with awkward hypercholesterolemia definition -->
 
@@
 
-Finally, there were no identified Mendelian randomisation analysis examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
+Finally, there were no identified Mendelian randomisation analyses examining the effect of lower lipid levels, as determined by any genetic instrument, on all-cause dementia risk.
 
@@
 
-The two randomised controlled trials provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
+The two randomised controlled trials identified provided weak evidence (`r rct_statin_acd`) of an effect on statin use on all-cause dementia risk (Figure \@ref(fig:rctStatinDementiaFig)).
 
@@
 
-In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statins use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
+In contrast, a meta-analysis of `r obsStatins$Dementia$n` prospective observational studies provided some evidence of a protective effect of statin use on all-cause dementia risk (`r obsStatins$Dementia$estimate`, Figure \@ref(fig:obsStatinDementiaFig)).
 
@@
 Finally, a single Mendelian randomisation analysis was identified examining the effect of  lowered LDL-c levels on the risk of all-cause dementia via genetic inhibition of the 3-hydroxy-3-methylglutaryl-coenzyme A reductase (HMGCR), emulating statin treatment (see Section \@ref(intro-statins) for more details of the statin mechanism of action).
-This analysis provided weak evidence of an effect (`r mrStatin$Dementia$estimate`).
+This analysis provided weak evidence for an effect (`r mrStatin$Dementia$estimate`).
 
@@
 <!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 Finally, there were several identified Mendelian randomisation studies examining the effect of genetically lowered LDL-c on Alzheimer's disease risk (Figure \@ref(fig:mrDuplication)).
-However, all of these studies took a two-sample approach, making use of summary statistics from the Global Lipid Genetics Consortium (GLGC) and International Genomics of Alzheimer's Project (IGAP) consortia.
-Synthesis of these results would would result in a falsely precise estimate caused by multiple counting of the same participants,and as a result, no meta-analysis of these studies was performed.
-However, across each analysis using varying number of SNPS, no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
+However, all of these studies took a two-sample approach, making use of summary statistics from the International Genomics of Alzheimer's Project (IGAP) consortium and the Global Lipid Genetics Consortium (GLGC).
+Synthesis of these results would result in a falsely precise estimate caused by multiple counting of the same participants, and as a result, no meta-analysis of these studies was performed.
+However, across each analysis using varying number of single nucleotide polymorphisms (SNPs), no evidence for an effect was observed (Figure \@ref(fig:mrDuplication)).
 
@@
 
-There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies reported on this outcome and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
+There were no randomised trials of the use of statins or any other lipid regulating agents  on Alzheimer's disease, though several observational studies examined this association and provided evidence for a protective effect (`r n_effect(obsStatins$AD)`; Figure \@ref(fig:obsStatinADFig)).
 
@@
 
-`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD))
+As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of the risk factors of interest with vascular dementia.
+`r num_to_text(obsHyperchol$VaD$n,T)` studies reported on the association of hypercholesterolemia with vascular dementia and provided weak evidence for an effect (`r obsHyperchol$VaD$estimate`, Figure \@ref(fig:obsHyperVaD)).
 
@@
 
-Few studies investigated the effect of individual lipid fractions.
-Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
-A single study provided evidence on the other three fractions,[@yoshitake1995] and similarly found minimal evidence of an effect LDL-c (`r n_effect(obsLipids$VaD_LDL,F)`), HDL-c (`r n_effect(obsLipids$VaD_HDL,F)`) or triglycerides (`r n_effect(obsLipids$VaD_TG,F)`).
+Few studies investigated the effect of individual lipid fractions on vascular dementia.
+Only for total cholesterol was there greater than one result reported (Figure \@ref(fig:lipidFractionsVaD)), and a meta-analysis of these results found weak evidence for an effect (`r n_effect(obsLipids$VaD_TC)`).
+A single study provided evidence on the other three fractions.[@yoshitake1995] This analysis similarly found minimal evidence of an effect of LDL-c (`r n_effect(obsLipids$VaD_LDL,F)`), HDL-c (`r n_effect(obsLipids$VaD_HDL,F)`) or triglycerides (`r n_effect(obsLipids$VaD_TG,F)`) on vascular dementia.
 
@@
 
-As noted in Section \@ref(sys-rev-characteristics) above, there was substantially less literature available on the association of my risk factors of interest and vascular dementia.
-There were no available randomised trials for this outcome.
+There were no available randomised trials of statin use for the vascular dementia outcome.
 `r num_to_text(obsStatins$VaD$n,T)` prospective cohort studies examined statin use and vascular dementia, though meta-analysis of these studies provided weak evidence for an effect (`r n_effect(obsStatins$VaD)`; Figure \@ref(fig:obsStatinVaDFig)).
@@
 
-As shown in the forest plots in the above sections, the risk-of-bias assessments are presented alongside their corresponding numerical result.
-This section presents only a brief summary of the biases observed in each study design, as s detailed discussion of the sources and directions of bias in each result is presented in Chapter \@ref(tri-heading).
+As shown in the "paired" forest plots in the above sections, the risk-of-bias assessments are presented alongside their corresponding numerical result.
+This section presents only a brief summary of the biases observed in each study design, as detailed discussion of the sources and directions of bias in each result is presented in Chapter \@ref(tri-heading).
 
@@
 
-The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each forest plot presented above.
+The risk of bias due to missing evidence in each synthesis is shown beside the overall summary diamond in each "paired" forest plot presented above.
 For randomised controlled trials and non-randomised studies of interventions, the risk of bias due to missing evidence was assessed to be minimal.
@@
 
+In the four analyses with greater than 10 results, the minimum required for subgroup analysis, stratification by overall risk-of-bias level did not demonstrate a difference between the "Serious" and "Moderate" risk of bias groups.
+The results of the test for subgroup differences is shown in the bottom left of the forest plots for these four meta-analyses (Figures \@ref(fig:obsHyperDementia), \@ref(fig:obsStatinDementiaFig), \@ref(fig:obsHyperAD) and \@ref(fig:obsStatinADFig)).
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-There were `r n_dr_initial` studies initially considered eligible for the dose-response meta-analysis, as they appear to provide data on risk of dementia outcomes across several categories of lipid exposure.
-However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not report the relevant information needed (most commonly, the cut-off measures for each category).
+There were `r n_dr_initial` studies initially considered eligible for the dose-response meta-analysis, as they appeared to provide data on risk of dementia outcomes across several categories of lipid exposure.
+However, following data extraction, `r num_to_text(n_dr_excluded)` were excluded as they did not report all of the information needed for the analysis.
+Most commonly, the cut-off measures for each category were missing.
 
@@
 
+There was evidence of heterogeneity in several of the meta-analysis performed, as indicated by a high $I_2$ statistic.
+$I_2$ represents the percentage of variability in the results included in a synthesis that is due to heterogeneity rather than chance.[@higgins2003] The $I_2$ value for each analysis are provided in the forest plots above.
+
 Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, a minority of meta-analysis (4 out of 18, `r paste0(comma(4/18*100),"%")`) included more than 10 results, the recommended minimum required for meta-regression.
-Secondly, poor reporting of study characteristics of interest including education level and baseline cognitive ability precluded the use of several results in a meta-regression analysis.
-
-<!-- TODO Finish this analysis -->
-
-Age and gender were assessed as potential causes of heterogeneity in the meta-analyses of statin use and hypercholesterolemia on all cause dementia and Alzheimer's disease, but I found weak evidence for variation in the observed effect estimates due to these factors.
-
-Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was hindered by the relatively small number of results included in a given meta-analysis.
-However, all analyses assessed provided weak evidence of small-study effects.
-
-<!-- TODO Reword the above section to make it clearer -->
+In the first instance, a minority of meta-analysis (4 out of 18, `r paste0(comma(4/18*100),"%")`) included 10 or more results, the recommended minimum required for meta-regression.
+Secondly, poor reporting of baseline characteristics of interest precluded the use of several results in a meta-regression analysis.
+
+Only for the sex covariate were sufficient number of results available to enable meta-regression.
+Across the four meta-analyses examined, the percentage of females in the study cohort was not related to the observed effect estimate (p = `r metaregHypercholDem` for hypercholesterolemia/all-cause dementia, Figure \@ref(fig:obsHyperDementia); p = `r metaregStatinsDem` for statins/all-cause dementia - Figure \@ref(fig:obsStatinDementiaFig); p = `r metaregHypercholAd` for hypercholesterolemia/Alzheimer's disease - Figure \@ref(fig:obsHyperAD); p = `r metaregStatinsAd` for statins/Alzheimer's disease - Figure \@ref(fig:obsStatinADFig)).
+
+Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was limited to these four meta-analyses including 10 or more results.
+However, there was weak evidence for the presence of small-study effects in each analyses assessed (see Appendix \@ref(appendix-funnel-plots)).
 
@@
 
-As show in the PRISMA flow diagram (Figure \@ref(fig:prisma-flow-fig)), the number of hits returned by preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
+As shown in the PRISMA flow diagram (Figure \@ref(fig:prisma-flow-fig)), the number of hits returned by preprint searching was not substantial (bioRxiv = 256, medRxiv = 0).
 From these hits, three preprinted reports of eligible studies were included in the review, of which two described unique studies not captured by the main search.[@andrews2019; @so2017]
@@
 To assess the evidence added to the meta-analysis through inclusion of the preprint, the data was re-analysed using a fixed-effect model.
-Examination of the weight assigned to each result in the analysis illustrates that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
-However, the inclusion of the preprinted study did not have a substantial impact on the result of the meta-analysis (`r mrStatin$AD$estimate`) compared with that reported by the single published study (`r estimate(0.59,0.25,1.39,"RR")`), other than a slight increase in precision.
-
-The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLCC and IGAP consortia.
-As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add to new information to the evidence base.
+Examination of the weight assigned to each result in the analysis illustrated that a large proportion (`r mrStatinPreprintWeight`) of the weight is given to the preprinted result.
+However, the inclusion of the preprinted study did not have a substantial impact on the result of the meta-analysis (`r mrStatin$AD$estimate`) compared with that reported by the single published study (`r estimate(0.59,0.25,1.39,"RR")`), other than slightly increasing the precision.
+
+The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLCC and IGAP.
+As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add new information to the evidence base.
 
@@
 
-<!-- TODO Check inclusion of Rockwood 2002:  -->
-This review presented a summary of the available evidence on the association between lipids, and treatments that modify lipids such as statins, and the subsequent risk of dementia.
+This review presented a summary of the available evidence on the association of lipids and LRA with subsequent risk of dementia outcomes.
 This discussion seeks to summarise the key findings in terms of literature sources and results as reported.
@@
 There was some indication of a protective effect of statins on all-cause and Alzheimer's disease dementia when looking solely at observational studies.
-This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy, suggesting that these findings may be a result of differing exposure windows (e.g.
+This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy.
+This suggests that these findings may be a result of differing exposure windows (e.g.
 mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
-
-<!-- Some evidence that age has impact on observed lipid-dementia relationship - use to link  -->
 
@@
 This distribution of evidence between analytical designs is to be expected.
-Randomised controlled trials of dementia are particularly challenging, as the follow-up made necessary by the long latent period of the condition makes trials logistically difficult and financially expensive.
+Randomised controlled trials of dementia are particularly challenging, as the follow-up made necessary by the long latency period of the condition makes trials logistically difficult and financially expensive.
 Similarly, Mendelian randomisation is a comparatively new study design, and studies employing it in relation to dementia outcomes only appear in the evidence base in recent years, as illustrated in Figure \@ref(fig:typeByYear).
@@
 This is particularly interesting given that lipids and statins are strongly related to the prevention of vascular disease.
-A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though there was weak evidence of a small-study effects for this outcome (of which publication bias is one potential cause).[@sterne2011] Similarly, only one Mendelian randomisation study examined this outcome, likely due to the absence (until recently) of vascular dementia GWAS which precludes a two-sample approach.
-
-Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on cardiovascular disease risk and reported on cognitive outcomes as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up.
-Though a useful indicator of general cognitive decline, it is not equivalent to a dementia diagnosis using recognised criteria, as cognitive tests should feed into a broader diagnostic pathway (see Section \@ref(diagnostic-criteria)).
+A potential explanation for this observation may be publication bias or the "file-drawer effect",[@rosenthal1979] though small-study effects (of which publication bias is one potential cause)[@sterne2011] could not be investigated for this outcome due to the small number of available results.
+Similarly, only one Mendelian randomisation study examined this outcome, likely due to the absence of vascular dementia GWAS which precludes a two-sample approach.
+
+Of note, this review did not include the commonly cited PROSPER RCT, which examined the effect of pravastatin on cardiovascular disease risk and reported on cognitive measures as one of several secondary outcomes.[@shepherd2002] While widely cited in relation to the effect of statins on dementia risk and included in the Cochrane review of RCTs on this topic,[@mcguinness2016] the trial reported solely on the change in a range of cognitive measures (MMSE, Stroop test, Picture-Word Learning test and others) over follow-up rather than a binary dementia outcome.
 As such, this trial did not meet the inclusion criteria for this review.
@@
 Risk of bias across the individual results was generally high.
-The causes and expected impact of these biases on the results are discussed in more detail in Chapter \@ref(tri-heading).
+The expected impact of these biases on the results are discussed in more detail in Chapter \@ref(tri-heading).
 Of particular interest to this chapter, however, was the high risk of bias due to missing evidence observed for observational studies of lipid levels.
@@
 "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
-were not reported in the table."[@ancelin2013]).
-However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analysis (which provided weak evidence of an effect), other than increasing the precision of the summary estimate.
-
-Finally in terms of generalisability, despite a large proportion of the included studies being conducted in the Western world (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of several studies which made use of data from the Taiwan health insurance database.
+were not reported in the table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analyses (which provided weak evidence of an effect of lipid levels on dementia outcomes) beyond increasing the precision of the summary estimate.
+
+Finally in terms of generalisability, despite a large proportion of the included studies being conducted in the westernised countries (Figure \@ref(fig:cohortLocations)), the applicability of the results to other populations is aided by the inclusion of several studies which made use of data from the Taiwan National Health Insurance database.
 
@@
 
-<!-- TODO Check none of these use a ROB tool -->
-
-While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020;@kuzma2018stroke; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain based assessments tools (for example, the RoB 2 tool for randomised controlled trials)[@sterne2019] to assess the risk of bias in included studies.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or used a non-domain-based assessment tool (e.g.
+While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain-based assessment tools (for example, the RoB 2 tool for randomised controlled trials)[@sterne2019] to assess the risk of bias in included studies.
+The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or use a non-domain-based assessment tool (e.g.
 the Newcastle-Ottowa Scale).[@poly2020]
@@
 However, this review was conducted prior to the majority of Mendelian randomisation studies included in this review being published.
-In addition this previous review extracted the results of analyses which did not account for SNPs in the _Apo_$\mathcal{E}4$ genetic region (see the following section for a discussion of the bias this introduces).
+In addition, this previous review extracted the results of analyses which did not account for SNPs in the _Apo_$\mathcal{E}4$ genetic region (see the following section for a discussion of the bias this introduces).
 
@@
 This study design uses other systematic reviews rather than primary studies as the unit of analysis.
-Furthermore, it would have enabled more efficient identification of relevant primary studies to which the methods which sets this review apart could have been applied.
+Furthermore, it would have enabled more efficient identification of a comprehensive set of primary studies relevant to this clinical question.
+Having defined this set, the methods which set this review apart could then have been applied.
 
@@
 
-* the genetic variant associates with the risk factor of interest (relevance assumption);
-* the variant-exposure association has no unmeasured confounders (independence assumption);
-* the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption).
+1. the genetic variant associates with the risk factor of interest (relevance assumption);
+2. the variant-exposure association has no unmeasured confounders (independence assumption);
+3. the variants affect the outcome only through their effect on the risk factor of interest (exclusion restriction assumption).
 
@@
 
-(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (I) _relevance_ - the genetic variant associates with the risk factor of interest; (II) _independence_ - the variant-exposure association has no unmeasured confounders; and (III) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
+(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (1) _relevance_ - the genetic variant associates with the risk factor of interest; (2) _independence_ - the variant-exposure association has no unmeasured confounders; and (3) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
 there is no horizontal pleiotropy).
@@
 Additionally, there is currently no widely used risk-of-bias assessment tool for Mendelian randomisation studies.
-While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this guide includes reporting items in their quality checklist.[@davies2018] Reporting quality is an important consideration for Mendelian randomisation studies, as reflected by the recent release of the STROBE MR reporting guidelines,[@skrivankova2021] but it is a separate consideration to bias, as discussed in Section \@ref(risk-of-bias).
+While a recent commentary provided a checklist for interpreting Mendelian randomisation studies, this includes reporting items in their quality checklist.[@davies2018] Reporting quality is an important consideration for Mendelian randomisation studies, as reflected by the recent release of the STROBE MR reporting guidelines,[@skrivankova2021] but is a separate issue to bias as discussed in Section \@ref(risk-of-bias).
 Similarly, a previous review of Mendelian randomisation studies used the Q-Genie tool which was designed to assess the quality of GWAS included in a meta-analysis.[@sohani2015] While this tool assesses the underlying GWAS used, it does not address the additional methodological considerations of the Mendelian randomisation analysis itself.
@@
 This is particularly relevant to the consideration of bias due to missing evidence.
-As an example, through snowballing and other measures, I identified at least one relevant Mendelian randomisation study that had not been captured by the search strategy.[@larsson2017] This study examined lipid fractions as one of many risk factors for Alzheimer's disease, though the search would not have been expected to find it given the absence of any lipid-related keywords in the title or abstract.
+As an example, through snowballing (forwards and backwards citation chasing) and other measures, I identified at least one relevant Mendelian randomisation study that had not been captured by the search strategy.[@larsson2017] This study examined lipid fractions as one of many risk factors for Alzheimer's disease, though the search would not have been expected to find this study given the absence of any lipid-related keywords in the title or abstract.
 Studies examining multiple risk factors such as this can introduce bias into a systematic review, as it is commonly only those risk factors with a statistically significant result that are reported in the abstract and so are captured by a systematic search.
@@
 
-Useful future work to improve the methodology for inclusion of Mendelian randomisation studies in systematic reviews should involve the development of a validated search filter for this study design.[@waffenschmidt2020; @wagner2020] Alternatively, in better-resourced reviews, a broader search (e.g.
+In better-resourced reviews, a broader search (e.g.
 "risk factor" AND "dementia" AND "Mendelian randomisation") followed by manual review of studies that examined multiple risk factors would be advisable.
 This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (N = `r comma(16109)`).
-Additionally, the value of methods that support traditional bibliographic database searches, such as snowballing (forwards and backwards citation chasing) and communication with relevant topic experts, should not be underestimated.
-Finally, development of a risk-of-bias assessment tool for this study design by a panel of methodologists and analysts would be of substantial benefit.
+Additionally, the value of methods that support traditional bibliographic database searches, such as snowballing and communication with relevant topic experts, should not be underestimated.
 
 One item of particular interest is the attenuation of any effects identified by Mendelian randomisation studies following the adjustment for/exclusion of genetic variation in the _Apo_$\mathcal{E}4$ gene region.
-As discussed in the introduction (see Section \@ref(intro-basic-science)), an increasing number of _Apo_$\mathcal{E}4$ alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
+As discussed in the introduction to this thesis (see Section \@ref(intro-basic-science)), an increasing number of _Apo_$\mathcal{E}4$ alleles is a major independent risk factor for Alzheimer's disease and so violates the exclusion restriction criteria of Mendelian randomisation studies (Figure \@ref(fig:mrAssumptions)).
 In all cases, excluding variants in the _Apo_$\mathcal{E}$ region attenuates the observed effect to the null.
@@
 Using the tool described in Chapter \@ref(sys-rev-tools-intro), two preprint servers related to health and biomedical sciences were searched as part of this review.
-The small number of studies returned by the preprint searches (or the absence of any relevant hits in the medRxiv database - see Figure \@ref(fig:prisma-flow-fig)) is largely due to the timing of the preprint searches.
+The small number of studies returned by the preprint searches (or the absence of any relevant hits in the medRxiv database - see the PRISMA flow diagram in Figure \@ref(fig:prisma-flow-fig)) is largely due to the timing of the preprint searches.
 The searches for this review were performed in mid-July 2019, but the medRxiv repository, an offshoot of the Epidemiology and Clinical Trials categories of the bioRxiv preprint server, only registered its first preprint 25th June 2019.
@@
 
-Of the three identified preprints, two were subsequently published as of September 2021.
+Of the three identified preprints, two were subsequently published as of July 2021.
 This fits well with the analysis presented in Chapter \@ref(sys-rev-tools-heading) that, allowing for a two-year lag, approximately two-thirds of preprints are published.
-It also illustrates the dual advantages of preprinted reports to evidence syntheses.
+It also illustrates the dual advantages of preprinted reports to evidence synthesis exercises.
 Firstly, preprints provide an advance snapshot of the literature, capturing articles that will eventually be published but were not available at the time of the main search.
-For example one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise, as is the case with a second preprint included in this review.[@so2017] Both of these aspects illustrate that inclusion of preprints is a necessity if the aim is to find all relevant literature on a topic at the time of searching.
+For example, one eligible preprint in this review was initially posted on bioRxiv in July 2019[@andrews2019] and was subsequently published in 2021 following peer-review.[@andrews2021] Secondly, inclusion of preprints allows for results that may never be formally published to be included in an evidence synthesis exercise, as is the case with a second preprint included in this review.[@so2017] Both of these aspects illustrate that inclusion of preprints is a necessity if the aim is to find all relevant literature on a topic at the time of searching.
 
@@
 
-As discussed in Section \@ref(dose-response-results), many primary studies did not report important information required for the dose-response meta-analysis, and so could not be included in the synthesis.
+As discussed in Section \@ref(dose-response-results), many primary studies did not report important information required for the dose-response meta-analysis, and so could not be included in this analysis.
 This limitation was compounded by the expected low response rate to requests for further information from primary authors.
-Contacting authors is worthwhile, as it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers,[@cooper2019] though a preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
+Contacting authors is worthwhile, because it can substantially change the conclusion of a systematic review[@meursingereynders2019] and is not too costly to systematic reviewers.[@cooper2019] However, a preferable option is that the authors of primary studies readily deposit all relevant study data at the point of publication.
 
@@
 
-<!-- TODO Upload as part of thesis repo. -->
+<!-- TODO Upload as part of thesis repo AND CITE -->
 
@@
 ### Strengths and limitations
-
-<!-- TODO Cross reference with other discussion sections to ensure material isn't being repeated. -->
 
@@
 Secondly, this review employed a structured approach to risk-of-bias assessment using a domain-based tool.
-This represents an important strength of this review, as the detailed risk of bias assessments are used in inform the quantitative triangulation analysis presented in Chapter \@ref(tri-heading).
-
-Thirdly, as discussed at length in the section above, in contrast to other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched preprinted health-related preprints.
+This represents an important strength of this review, as the detailed risk of bias assessments are used to inform the quantitative triangulation analysis presented in Chapter \@ref(tri-heading).
+
+Thirdly, as discussed at length in the section above, in contrast to other available reviews and enabled by the tool described in Chapter \@ref(sys-rev-tools-heading), this review systematically searched health-related preprints.
+
 Finally, as a secondary element, I used this review to pilot new research synthesis methodologies, in particular a new visualisation approach for risk-of-bias assessments and a forthcoming tool for assessing the risk-of-bias due to missing evidence.
@@
 
-The primary limitation of this review is that several included studies used data from EHR databases, which come with serious concerns regarding validity.[@hsieh2019; @mcguinness2019validity; @wilkinson2018] Relatedly, several studies which made use of electronic health record databases did not report the specific code lists used, potentially introducing substantial heterogeneity into the analysis.
-An empirical example of the effect of differing EHR code lists is presented as part of the analysis in Chapter \@ref(cprd-analysis-heading) (see Section \@ref(comparing-codelists)).
-
-In addition, the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, as there is a chance that some eligible records could have been excluded.
+<!-- TODO Consider mentioning that the date of the review is a limitation, and forward refer to the section in the Discussion that considers two new studies -->
+
+A primary limitation of this review is the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, because there is a chance that some eligible records could have been excluded.
 However,  evidence from assessments of inter- and intra-rater reliability indicate that this is not a major concern.
+Additionally, the search date of the study (July 2019) is a further limitation, in that more recently published studies are not included in this analysis.
 
@@
 This meant that there were no signaling questions to guide the domain-level risk-of-bias assessments, which may have influenced the accuracy with which the judgements were assigned.
-However, there is no published empirical evidence supporting the need for signaling questions and assessment of inter-rater reliability across the different tools did not indicate a specific problem with the ROBINS-E assessments.
-In fact, low agreement was common across the tools, though this is expected based on the available literature.[@jeyaraman2020]
+However, there is no published empirical evidence supporting the need for signaling questions.
+Additionally, a previous assessment of inter-rater reliability in domain-bases risk-of-bias tools found that, even with the use of signaling questions, reviewers assessment of bias can vary substantially.[@jeyaraman2020]
 
 A final limitation is the potential for missing evidence on the basis of the results.
-Evidence for this limitation came from the ROB-ME assessments and was supported by empirical evidence that some studies containing relevant results were missed by the search (see Section \@Ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
+Evidence for this limitation came from the ROB-ME assessments and was supported by empirical evidence that some studies containing relevant results were missed by the search (see Section \@ref(rev-discussion-MR) above for a fuller discussion of this issue with respect to Mendelian randomisation studies).
 Unfortunately, this is probably a common limitation across all systematic reviews, based on the way in which increased search sensitivity must be balanced with a manageable workload.
@@
 In Chapter \@ref(ipd-heading), prospective cohorts identified by the review were contacted in an attempt to obtain individual participant data.
-Finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \@ref(discussion-heading).
+Finally, the results identified here are used as a key source of evidence for the triangulation exercise presented in Chapter \@ref(tri-heading).
 

### 2021-12-16 05-Chp-CPRD-Analysis.Rmd
Range of updates

@@
 Under these systems, whenever a patient attends their GP, their clinical data is recorded in a central database using a standardised coding system.
-These databases have several advantages over traditional methods of data collection, including the number of people they contain and the relatively low cost of data collection via routine care.
+These databases have several advantages over traditional methods of data collection, including the number of people they contain and the relatively low cost of data collection.
 This is particularly important when studying diseases such as dementia, which may begin to develop in patients long before symptoms are seen.
@@
 This analysis makes use of the Clinical Practice Research Datalink (CPRD), which contains the electronic medical records of more than 3 million people from general practices across England.
-Using this data, the analysis presented in this chapter examined whether treatments which lower cholesterol levels (also known as lipid-regulating agents or LRA) of which statins are a prime example, affect the risk of all-cause dementia and related outcomes (Alzheimer's disease, vascular dementia and other dementias).
+Using this data, the analysis presented in this chapter examined whether lipid-regulating agents (treatments which change lipid levels) affect the risk of all-cause dementia and related outcomes (Alzheimer's disease, vascular dementia and other dementias).
 
@@
 
-Little evidence for an effect of lipid-regulating agents effect on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
+Little evidence for an effect of lipid-regulating agents on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
 In contrast, I found an increased risk of vascular and other (i.e.
@@
 This increased risk in outcomes with a vascular element (e.g.
-vascular dementia) is unexpected, and is very likely to be due to the presence of bias in the analysis.
+vascular dementia) is unexpected, and is very likely to be due to the presence of bias in my analysis.
 This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, which makes it appear as if statins are harmful.
-Despite this limitation, the analysis presented provides an important source of information which will be used in later chapters.
+Despite this limitation, the analysis provides an important source of information which will be used in later chapters.
 
@@
 
-In this chapter, I present an analysis of a large population-based electronic health record dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
+In this chapter, I present an analysis of a large population-based electronic health record (EHR) dataset to investigate the relationship between lipid-regulating agent (LRA) use and dementia outcomes.
 The analysis aims to address two important limitations of the current evidence base as identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
@@
 The systematic review presented in the previous chapter identified an evidence gap around the effect of lipid-regulating agents on the risk of vascular dementia.
-As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides a source of information on this outcome.
+As triangulation exercises require as many diverse sources of evidence as possible, this analysis provides an additional source of information on this outcome.
 
 Secondly, and in a similar vein, the analysis intentionally takes a different analytical approach to that most commonly used to examine the effect of statins on dementia as identified by the systematic review.
-Specifically, this involved a concerted effort to address immortal time bias through use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] By employing this approach, the analysis provides an evidence source at risk of a distinct bias.
-The results from this analysis will be incorporated into the triangulation exercise presented in Chapter \@ref(discussion-heading).
+Specifically, this involved a concerted effort to address immortal time bias through use of a Cox proportional hazards analysis, incorporating a time-varying treatment indicator.[@suissa2008] By employing this approach, the analysis provides an evidence source at risk of a distinct bias, making it useful to the triangulation exercise presented in Chapter \@ref(tri-heading).
 
@@
 
-<!-- QUESTION If protocol was written by Venexia, how do I reference this? -->
-
-<!-- TODO Add amendments to Appendix -->
-
 <!--------------------------------------------------------------------------->
@@
 
-Previously known as the General Practice Research Database, the Clinical Practice Research Datalink (CPRD) is a large population-based EHR database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the primary care records for more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+Previously known as the General Practice Research Database, the Clinical Practice Research Datalink (CPRD) is a large population-based EHR database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the records of more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
-To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, including clinical test results and diagnoses, can be identified by a specific Read code.
+To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, including  test results and diagnoses, can be identified by a specific Read code.
 The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
@@
 (ref:readExample-caption) __Example of CPRD Read code hierarchy__ - Broad topics are specified using the initial two alpha-numeric characters of the Read code, while subsequent characters are used to define specific conditions and context.
-The example shown illustrates how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental disorders" (_Eu..._).
+The example shown illustrates how "Dementia in Alzheimer’s disease with late onset" (_Eu001_) is nested under the top-level of "Mental and behavioural disorders" (_Eu..._).
 
@@
 
-The index events, exposures and outcomes used in this analysis were identified using predetermined code lists, which are available for inspection from the archived repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
+The index events, exposures and outcomes used in this analysis were identified using predetermined code lists, which are available for inspection from the repository accompanying this analysis (data/code availability is discussed in Section \@ref(cprd-data-avail)).
 
-<!-- TODO ensure code list position is accurately documented in Appendix -->
+<!-- TODO Make sure it is cited properly -->
 
@@
 
-This analysis included all participants registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data (as defined by the CPRD).
-Records pre-dating the 1995 cut-off were included in the original CPRD extract obtained for this analysis.
-However, these older records were excluded from the analysis as data quality and reliability are thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
+This analysis included all patients registered at a participating practice between 1 January 1995 and 29 February 2016 who had a flag for "research quality" data (as defined by the CPRD).
+Records pre-dating the 1995 cut-off were provided as part of the original CPRD extract obtained for this analysis.
+However, these older records were excluded from the analysis because data quality and reliability are thought to be higher after this date.[@wolf2019] Additionally, individuals with less than 12 months of continuous records prior to cohort entry were excluded, making the effective start date of the cohort 1 January 1996.
 
@@
 
-Participants were ineligible for the cohort if they were less than 40 years of age (as these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficult of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
+Participants were ineligible for the cohort if they were less than 40 years of age (because these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficultly of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
 had less than one full day of follow-up).
@@
 A participants drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
-We did however examine how often the initial drug class altered according to one of three criteria:
+I did however examine how often the initial drug class altered according to one of three criteria:
 
@@
 
-<!-- TODO Need to deal with the fact that the ordering is not accounted for, which could be critised -->
-
 <!----------------------------------------------------------------------------->
-(ref:decisionTreeFig-cap) __Decision tree for assigning dementia subtypes__ - Based on the presence of specific Read codes in the patient's record, a decision tree was used to classify dementia subtypes ("Probable" or "Possible" Alheimer's disease, vascular dementia, and other dementia).
-Note that an outcome of "probable" or "Possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
+(ref:decisionTreeFig-cap) __Decision tree for assigning dementia subtypes__ - Based on the presence of specific Read codes in the patient's record, a decision tree was used to classify dementia subtypes ("Probable" or "Possible" Alzheimer's disease, vascular dementia, and other dementia).
+Note that an outcome of "probable" or "possible" Alzheimer's disease (AD) requires the absence of any vascular outcome codes.
 
@@
 A range of additional variables were included in the analysis.
-These were intended to address the different distributions of potential confounding factors between those who were prescribed a lipid-regulating agent and those who were not.
+These covariates were adjusted for in the analysis in an attempt to address the different distributions of potential confounding factors between those who were prescribed a lipid-regulating agent and those who were not.
 These are discussed in detail below and summarised in Table \@ref(tab:covariateDef-table).
@@
 
-<!-- TODO May need to reword this table slightly as taken from Venexia walkers -->
-
 <!----------------------------------------------------------------------------->
-(ref:covariateDef-caption) __Definitions of covariates adjusted for in the analysis__ - The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work,[@khan2010; @taylor2016; @wright2017].
+(ref:covariateDef-caption) __Definitions of covariates adjusted for in the analysis__ - The code lists used to define the majority of these covariates were originally created for use in a previously published analysis.[@walker2020] while others were built on or adapted from previous published work.[@khan2010; @taylor2016; @wright2017]
 
@@
 To help preserve patient privacy, IMD score is only available from the CPRD in twentiles, with 1 indicating the least deprived and 20 indicating the most deprived.
-Smoking and alcohol use was determined at index, and was categorised as current, former, or never use.
+Smoking and alcohol use was determined at index, and usage was categorised as current, former, or never.
 
-Body mass index (a summary measure calculated as $weight/height^2$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
+Body mass index (a summary measure calculated as $\frac{weight}{height^2}$), baseline total cholesterol and baseline LDL cholesterol measures were obtained, using the last recorded value prior to the index date.
 A variable indicating grouped year of entry into the cohort (<=2000, 2001-2005, 2006-2010, >2010) was included to allow for changes in prescribing trends across the lifetime of the cohort.
@@
 The CCI is a weighted index that uses presence and severity of a number of conditions to enable adjustment for the general health of a participant in terms of their mortality risk.[@charlson1987new] The conditions considered under the index are: AIDS; cancer; cerebrovascular disease; chronic pulmonary disease; congestive heart disease; dementia; diabetes; diabetes with complications; hemiplegia; metastatic tumour; mild liver disease; moderate liver disease; myocardial infarction; peptic ulcer disease; peripheral vascular disease; renal disease; and rheumatological disease.
-Inclusion of this index allowed me to attempt to adjust for the general health of patients included in the analysis.
+Inclusion of this index allowed me to adjust for the general health of patients included in the analysis.
 
-code lists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
+Code lists for all covariates can be found in the archived data repository accompanying this analysis (see Section \@ref(cprd-data-avail)).
 
@@
 
-<!-- IDEA Add more detail here on the missing data approach -->
-
 In this analysis, missing data was handled using a multiple imputation approach.[@sterne2009] Variables with missing observations were identified for inclusion in the imputation model.
 Nominal variables with missing values were modelled using multinomial logistic regression, while continuous variables were modelled using linear regression.
-As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006] Using the MICE (Multiple Imputation by Chained Equations) command in STATA16, 20 imputed datasets were created.
+As per best practice, all variables used in the analytic model, including the outcome, were included in the imputation model.[@moons2006] Using the MICE (Multiple Imputation by Chained Equations) command in STATA 16,[@statacorp2019] 20 imputed datasets were created.
 
@@
 categorical smoking status).
-This approach was necessary, as absence of a code for other treatments or conditions (e.g.
+This approach was necessary because absence of a code for other treatments or conditions (e.g.
 statin use or dementia) was assumed to indicate absence of the treatment/condition rather than being considered missing.[@wells2013strategies]
@@
 * $t$ is the survival time;
-* $h(t)$ is the hazard function; and
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.
+* $h(t)$ is the hazard function;
+* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.; and
 * $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
@@
 
-<!-- IDEA Bit on why Cox models are slightly different from others, due to proportional hazards assumptions. Test for non-proportionality are therefore very important, as models which fail-->
-
-<!-- IDEA Need to describe accounting for clustering here: id it something I did? See other thesis for clustering by practice -->
-
 <!----------------------------------------------------------------------------->
@@
 
-Immortal time bias describes two distinct but related types of bias, considered here in relation to statin use.
-The first presentation, the selection bias aspect (Panel A, Figure \@ref(fig:immortalTimeBias)), occurs when time prior to statin initiation is excluded leading to the statin and control groups being followed up from different time points.[@levesque2010] Following the example displayed in the figure, the unexposed group are followed from the date of an index event (e.g.
+Immortal time bias describes two distinct but related types of bias, considered here in relation to statin use (Figure \@ref(fig:immortalTimeBias)).
+The first presentation, the selection bias aspect (Panel A), occurs when time prior to statin initiation is excluded leading to the statin and control groups being followed up from different time points.[@levesque2010] The unexposed group are followed from the date of an index event (e.g.
 diagnosis of hypercholesterolemia), while the statin group is followed from date of a statin initiation.
@@
 The second presentation of immortal time bias is as a type of misclassification bias (Panel B, Figure \@ref(fig:immortalTimeBias)).
-It occurs when the exposure time prior to statin initiation, and any events occurring within it, is inappropriately assigned to the exposed group.
-
-<!-- TODO Reread this section and compare with the figure! -->
+It occurs when the exposure time and events prior to statin initiation are inappropriately assigned to the statin group.
 
@@
 
-This second presentation appears to be common in the existing literature on the relationship of statins and dementia, as several of the studies included in the systematic review performed as part of this thesis were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-res)).
+This second presentation appears to be common in the existing literature on the relationship of statins and dementia.
+Several of the studies included in the systematic review performed as part of this thesis were identified as being at risk of immortal time bias following formal risk of bias assessment using the ROBINS-I tool (see Section \@ref(risk-of-bias-res)).
 
-<!-- TODO May need to crosslink a bit better -->
+Following a recommended approach to address the second form of immortal time bias, I employed a time-varying treatment indicator to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] Under this approach, all patients are followed from a common index date, defined as earliest of:
 
-Following a recommended approach to addressing the second form of immortal time bias, I employed a time-varying indicator of treatment status to correctly allocate time-at-risk to the exposed and unexposed groups.[@levesque2010] Under this approach, all patients are followed from a common index date, defined as earliest of: (a) date of raised cholesterol test results; (b) hypercholesterolemia diagnosis; or (c) LRA prescription.
+* date of raised cholesterol test results; 
+* date of hypercholesterolemia diagnosis; or 
+* date of LRA prescription.
+
 Patients start in the unexposed group and contribute time-at-risk until they are prescribed a lipid-regulating agent, at which point they move into the exposed group.
@@
 
-<!-- IDEA Finish paragraph from fragments below -->
-
-<!-- In Cox models, there is the option to -->
-
-<!-- Age vs time-since entry -->
-
-<!-- Expand on use of age as the time scale, but describe the problems this introduced -->
-
-As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
-As such, the main analyses presented all used age as the time axis.
-
-<!-- TODO Will need to expand on choice of time axis here -->
-
-<!-- IDEA In order to explore whether the choice of time axis affects the results of the analysis,I ran two simple models, one using participants age as the time-scale and a second using absolute time-since-entry and adjusting for participant age.
--->
+As part of a Cox proportional hazard model, there is the option to use either absolute time in cohort or participants' age as the time scale of interest.[@lamarca1998; @gail2009; @pencina2007] A model using age as the time axis inherently accounts, or adjusts, for participants age as a potential confounder of the exposure-outcome relationship.
+As such, the analyses presented all used age as the time axis.
 
@@
 Conversely, positive control outcomes are those with a known causal association with the exposure of interest, ideally sourced from large well conducted randomised controlled trials.
-Positive control outcomes are useful in observational epidemiology, as if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
-Due to the wealth of data available on statins as a lipid-regulating agent, I chose three control outcomes in reference to this drug class: back pain (negative control), ischaemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
+Positive control outcomes are also useful in observational epidemiology because if the analysis can reproduce a known result for the control outcome, confidence in the result for the outcome of interest is increased.
+Due to the wealth of data available on statins as a lipid-regulating agent, I chose three control outcomes in reference to this drug class: back pain (negative control), ischemic heart disease (positive protective control), and Type 2 diabetes (positive harmful control).
 
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:negativeOutcome-cap) __Causal diagram for ideal negative outcome__ - The directed acyclic graph shows the relationship between the exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
+(ref:negativeOutcome-cap) __Causal diagram for an ideal negative outcome__ - The directed acyclic graph shows the relationship between the exposure $X$, outcome $Y$, confounders (measured $C$ and unmeasured $U$) and an ideal negative outcome $N$.
 Note the absence of any arrow between $X$ and $N$.
@@
 
-Despite observational analyses suggesting a link between statins and muscular pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] systematic reviews of the adverse events of statin use[@collins2016] and N-of-1 trials explicitly exploring the association of statin use with muscle pain[@herrett2021] have found little evidence supporting an effect.
-This suggests that muscular backpain would be suitable for use as a negative control outcome in this analysis.
+Despite observational analyses suggesting a link between statins and muscular pain (as opposed to more serious complications such as myopathy),[@selva-ocallaghan2018] an effect was not observed in either systematic reviews of adverse events of statin use[@collins2016] or N-of-1 trials explicitly exploring the association of statin use with muscle pain.[@herrett2021] Based on this evidence, I used muscular backpain as a negative control outcome in this analysis.
 Under this approach, if statin use is found to be associated with muscular backpain in this analysis, this suggests the presence of residual confounding and reduces my confidence in the results for the dementia outcomes.
 
-Similarly, incident ischemic heart disease and Type 2 diabetes were included as a protective and harmful positive control outcome, respectively.
-The protective effect of lipid-lowering treatment, via statins, on the risk of ischemic heart disease is well-established, [@collins2016] while there is growing evidence for an increased risk of Type 2 diabetes with statin use.[@collins2016; @macedo2014; @smit2020] Similar to the negative outcome, if the analysis strategy can reproduce these known associations, this will provide evidence that potential confounders have been sufficiently adjusted for.
-
-<!-- QUESTION - should those with baseline cardiovascular conditions be excluded from the IHD/MI analysis? -->
+Similarly, incident ischemic heart disease and Type 2 diabetes were included as protective and harmful positive control outcome, respectively.
+The protective effect of lipid-lowering via statins on the risk of ischemic heart disease is well-established, [@collins2016] while there is growing evidence for an increased risk of Type 2 diabetes with statin use.[@collins2016; @macedo2014; @smit2020] Similar to the negative outcome, if the analysis strategy can reproduce these known associations, this will provide evidence that potential confounders have been sufficiently adjusted for.
 
@@
 
-<!-- IDEA Make sure to include sex as a sensitivity analysis, given that that is the purpose of the IPD analysis -->
-
 &nbsp;
@@
 
-<!-- IDEA Could frame this as providing evidence that the effect is not due to statins acting on lipid levels, as then would not expect difference (unless all very hard acting statins are in the lipophilic type) -->
-
-As detailed in the introduction, the properties of statins may be important due to the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] As such, I expected that any effects of statins on dementia outcomes would be stronger in the lipophilic as compared to the hydrophilic statin subgroup.
+As detailed in the introduction, the properties of statins may be important due to the ability of lipophilic statins to cross the blood brain barrier (see Section \@ref(intro-statins)).[@sierra2011] As such, I expected that any effects of statins on dementia outcomes would be stronger in the lipophilic versus the hydrophilic statin subgroup.
 To investigate this, I further stratified the statin exposure group into lipophilic (Atorvastatin, Lovastatin, Simvastatin, Cerivastatin) and hydrophilic (Pravastatin, Rosuvastatin, Fluvastatin) statins.
@@
 
-As part of an exploratory analysis of the effect of the choice of code lists on the analysis, I created an alternative Alzheimer's disease and non-Alzheimer's dementia outcome using code lists from a published study by Smeeth _et al_.[@smeeth2009] The intended purpose of this analysis was to assess the robustness of my results to the choice of code list.
+To explore the impact of the code lists used to define dementia outcomes, I created alternative Alzheimer's disease and non-Alzheimer's dementia outcomes using code lists from a published study by Smeeth _et al_.[@smeeth2009] The intended purpose of this analysis was to assess the robustness of my results to the choice of code list.
 
@@
 
-<!-- QUESTION Describe impact of SSA table - is the fact that many people stopped statin treatment (~10%) an issue? Comment specifically in the context of a -->
-
 The distribution of baseline characteristics across the remaining seven drug classes can be seen in Table \@ref(tab:cprdCharacteristics-table).
-Note due to the experimental design, the median year of entry is expected to be later for those not prescribed an LRA, as this exposure group is more likely to include those who entered into the cohort towards the end of study window (as these people had less follow-up time in which to be prescribed an LRA).
+Note due to the experimental design, the median year of entry is expected to be later for those not prescribed an LRA.
+This is because the unexposed group is more likely to include those who entered into the cohort towards the end of study window, and so had less follow-up time in which to be prescribed an LRA.
 
@@
 Full covariate information was available for `r missingtext`.
-Six key variables had some missing data: IMD 2010 score was missing for `r imdtext`, because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
+Six key variables had some missing data: IMD 2010 score was missing for `r imdtext` because it is only recorded for English practices; alcohol status was missing for `r alcoholtext`; smoking status was missing for `r smokingtext`; BMI, or a calculated BMI from height and weight measurements, was missing for `r bmitext`; baseline total cholesterol was missing for `r choltext`; and baseline LDL cholesterol was missing for `r ldltext`.
 
@@
 
-For each outcome, the overall "Any drug" estimate was driven by the statin subgroup, based on its large size relative to the other drug classes.
+For each outcome, the overall "Any drug class" estimate was driven by the statin subgroup, based on its large size relative to the other drug classes.
 
@@
 &nbsp;
-
-<!-- TODO Check if reason for discrepnacy in terms of total numbers is that patients were excluded for having a first drug prior to on the index date -->
 
@@
 
-The results of the series of sensitivity analyses performed are described in the following sections.
+The results of the sensitivity analyses are described in the following sections.
 
@@
 
-In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete cases analysis.
+In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete case analysis.
 It should be noted that due to the large amount of missing data (e.g.
@@
 <!----------------------------------------------------------------------------->
-(ref:completeCaseFig-cap) __Complete case vs.
-imputed data analysis__ Comparison of analyses using the complete case versus imputed cohorts, indicating broad agreement between the two approaches.
+(ref:completeCaseFig-cap) __Sensitivity analysis: complete case vs.
+imputed data__ - Comparison of analyses using the complete case versus imputed cohorts, indicating broad agreement between the two approaches.
 Note that the analyses using imputed data gave more precise estimates due to the low proportion of patients with complete covariate data.
 
-(ref:completeCaseFig-scap) Complete case vs. imputed data analysis
+(ref:completeCaseFig-scap) Sensitivity analysis: complete case vs. imputed data
 
@@
 
-Following the primary analysis, the fully adjusted model was used to estimate the effect of treatment with a statin on the two control outcomes of back pain (negative) and ischemic heart disease (positive).
+The fully adjusted model was also used to estimate the effect of treatment with a statin on three control outcomes: back pain (negative), ischemic heart disease (positive protective) and Type 2 diabetes (positive harmful).
 The results of this analysis are presented in Figure \@ref(fig:controlOutcomeFig).
-
-For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
-However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:controlOutcomeFig-cap) Results of control outcome analysis.
+(ref:controlOutcomeFig-cap) __Sensitivity analysis: control outcomes__ Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale for three control outcomes: backpain (negative), ischemic heart disease (positive protective), and diabetes (positive harmful).
 
-(ref:controlOutcomeFig-scap) Results of control outcome analysis
+(ref:controlOutcomeFig-scap) Sensitivity analysis: control outcomes
 
@@
 
+For the negative control, there was some evidence that treatment with a statin was associated with an increased risk of back pain (`r backpain_text`), suggesting there may be some residual confounding.
+However, statin prescription was also associated with a substantially increased risk of ischemic heart disease (`r ihd_text`) and Type 2 diabetes (`r dm_type2_text`).
+
+&nbsp;
+
 #### Impact of additional covariates {#cprd-impact-additional-covar}
 
-The results of three models adjusted for age only, age and sex, and the full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
+The results of three models adjusted for age only, age and sex, and full covariates respectively, are presented in Figure \@ref(fig:unadjustedComparisonFig).
 These models were used to estimate the impact of adjustment for additional covariates.
-Note that obtaining a completely unadjusted model is not possible, as age was used in the Cox model as the time scale.
+Note that obtaining a completely unadjusted model is not possible because age was used in the Cox model as the time scale.
 
 Adjustment for additional covariates beyond age and sex had a limited impact on the observed effect estimates, with the exception of the probable AD outcome.
-In this case, adjustment for the full set of covariates attenuated to the null the protective effect observed when adjusting only for age and sex.
+In this case, adjustment for the full set of covariates attenuated the protective effect observed when adjusting only for age and sex to the null.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:unadjustedComparisonFig-cap) Results of three models adjusting for a different set of covariates.
+(ref:unadjustedComparisonFig-cap) __Sensitivity analysis: covariate comparison__ - The results obtained using three different sets of covariates (age only, age + sex, all covariates) are shown for each dementia outcome.
 Note that the x-axis cutoffs (0.5,2) are different compared to other plots (0.3,3) to enable greater comparison between the different models.
 
-(ref:unadjustedComparisonFig-scap) Comparison of different combinations of covariates
+(ref:unadjustedComparisonFig-scap) Sensitivity analysis: covariate comparison
 
@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosisTypeFig-cap) Analysis of any lipid-regulating agent on probable AD outcome, stratified by grouped year of cohort entry.
+(ref:diagnosisTypeFig-cap) __Sensitivity analysis: year of entry__ - Effect estimates, obtained from the fully-adjusted time-varying model with participant age as the time scale, for the association of the any LRA class with the probable AD outcome, stratified by grouped year of cohort entry.
 
-(ref:diagnosisTypeFig-scap) Sensitivity analysis: grouped year of entry
-
-<!-- TODO Need to fix grouping labels here -->
+(ref:diagnosisTypeFig-scap) Sensitivity analysis: year of entry
 
@@
 
-(ref:diagnosisType-caption) __Frequency of diagnoses by grouped year of cohort entry__
+(ref:diagnosisType-caption) __Dementia diagnoses by year of entry__ - As part of a _post-hoc_ investigation of the time period effect observed in the probable AD outcome, the frequency of dementia diagnoses by grouped year of cohort entry was calculated.
 
-(ref:diagnosisType-scaption) Frequency of diagnoses by grouped year of cohort entry
+(ref:diagnosisType-scaption) Dementia diagnoses by year of entry
 
@@
 
-(ref:pregnancyFig-cap) Comparison of analysis using main cohort and a cohort with potentially pregnany women removed.
+(ref:pregnancyFig-cap) __Sensitivity analysis: pregnancy cohort__ - Comparison of analysis using main cohort and a cohort with potentially pregnant participants (coded as any participant under 55 years of age) removed.
 
-(ref:pregnancyFig-scap) Comparison of pregnancy analysis
+(ref:pregnancyFig-scap) Sensitivity analysis: pregnancy cohort
 
@@
 
-(ref:statinTypeTable-caption) __Summary of statin properties (lipophilicity vs hydrophilicity)__, by grouped year of prescription.
+(ref:statinTypeTable-caption) __Summary of statin properties__ Number of patients prescribed lipophilicity vs hydrophilicity statins, by grouped year of prescription.
 
-(ref:statinTypeTable-scaption) Summary of statin properties (lipophilicity vs hydrophilicity).
+(ref:statinTypeTable-scaption) Summary of statin properties
 
@@
 <!----------------------------------------------------------------------------->
-(ref:statinTypeFig-cap) Analysis stratified by statin properties (hydrophilic vs lipophilic)
+(ref:statinTypeFig-cap) __Sensitivity analysis: statin properties__ - Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale, stratified by statin properties (hydrophilic vs lipophilic).
 
-(ref:statinTypeFig-scap) Analysis stratified by statin properties
+(ref:statinTypeFig-scap) Sensitivity analysis: statin properties
 
@@
 
-When using the Smeeth _et al._ code lists to define dementia outcomes, effect estimates of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's ("other") dementia outcomes, respectively.
-While direct mapping to the outcomes used in this analysis was not possible, the most comparable are probable Alzheimer's disease (`r probad_text`) and other dementia (`r othdem_text`).
+When using the Smeeth _et al._ code lists to define dementia outcomes, hazard ratios of `r smeeth_azd_text` and `r smeeth_oth_text` were obtained for the Alzheimer's disease and non-Alzheimer's ("other") dementia outcomes, respectively.
+While direct mapping to the outcomes used in this analysis was not possible, the most comparable outcomes are "probable Alzheimer's disease" (`r probad_text`) and "other dementia" (`r othdem_text`).
 
@@
 
-Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnosises.
-The estimate observed in each case was driven by the effects observed statin subgroup, as a substantial majority of participants prescribed an LRA were presribed a statin.
+Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnoses.
+The estimate observed in each case was driven by the effects observed in the statin subgroup because a substantial majority of participants prescribed an LRA were prescribed a statin.
 For the other drug classes, no association was found with any outcome, with two exceptions.
@@
 However, as the comparison of evidence across different sources is the aim of the triangulation exercise presented in later chapters, a detailed comparison with other published literature will not be provided here, except where needed to illustrate a methodological point.
-For a detailed comparison of the result presented above with the existing evidence base identified by the systematic review, see Chapter \@ref(tri-heading).
+For a detailed comparison of the results presented above with the existing evidence base identified by the systematic review, see Chapter \@ref(tri-heading).
 
@@
 
-A likely explanation for the observed increased risk of dementia outcomes with a vascular component (e.g.
-vascular and other dementias) with lipid-regulating agent use, and an important limitation of this analysis, is residual "confounding by indication".
+A likely explanation for the observed increased risk of vascular and other dementias with lipid-regulating agent use is residual "confounding by indication", which represents an important limitation of this analysis.
 While the term has been used to describe different sources of bias in epidemiological analyses,[@salas1999] it is used here to described the role of risk factors that both prompt treatment and increase the risk of the outcome, thus causing a distorted positive association between the treatment and outcome (see Figure \@ref(fig:indicationBias)).
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:indicationBias-cap) Causal diagram (directed acyclic graph) illustrating how confounding by indication could induce a positive association between statins and vascular dementia.
+(ref:indicationBias-cap) __Confounding by indication causal diagram__ - Directed acyclic graph illustrating how confounding by indication could induce a positive association between statins and vascular dementia.
 
@@
 Conditioning entry into the study on being either “at-risk” or already diagnosed with hypercholesterolemia was employed in a pre-emptive attempt to mitigate confounding by indication, but evidence from the control outcomes suggests this was unsuccessful.
-The slight harmful effect for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
+The slight harmful effect observed for the backpain outcome is substantially smaller than that observed for the ischemic heart disease outcome, indicating that the majority of the uncontrolled confounding is likely related to vascular factors.
 The slight effect observed for the negative control of backpain could be due to incomplete control for socioeconomic status, as deprivation data was provided in twentiles to preserve patient privacy.[@boruzs2016; @ikeda2019]
@@
 This pattern suggests that the strength of the residual confounding by indication increases as the proportion of cases with a vascular component in an outcome definition increases.
-Given confounding related to vascular factors, this pattern is also expected given the decision tree for assigning outcomes in the presence of greater than one dementia code.
+Given confounding related to vascular factors, this pattern is also expected based on the decision tree for assigning outcomes in the presence of greater than one dementia code.
 Under this system, the Alzheimer's disease outcomes require a "pure" condition and the presence of any vascular or other dementias codes excludes participants from this group (Figure \@ref(fig:decisionTreeFig)).
@@
 A review of other available literature suggests that this observation (a harmful effect of lipid-regulating agents on vascular-related outcomes) is not unusual.
-Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in this analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013] Controlling for confounding by indication in that study through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a comparable though less precise estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
+Using a conventional epidemiological technique, a previous analysis also found an increased risk of coronary heart disease (analogous to the ischemic heart disease outcome used in this analysis) in those taking statins (`r estimate(1.31,1.04, 1.66, type = "HR")`).[@danaei2013] In that study, controlling for confounding by indication through the use of a trial emulation analysis gave an estimate of 0.89 (95%CI: 0.73-1.09), a more comparable though less conclusive estimate to that observed in RCTs of statin use (`r estimate(0.73,0.67,0.80,type="")`).[@taylor2013]
 
 Given the absence of vascular dementia in the published literature, as highlighted in the previous chapter, the unexpected increase in vascular dementia risk with statin use is particularly interesting.
-It is possible that this finding reflects publication bias if previous research encountered similar methodological issues to this analysis, and these results did not make it into the evidence base as unexpected or assumedly incorrect results are less likely to be submitted or accepted for publication.
+If previous research encountered similar methodological issues to this analysis, it is possible their results did not make it into the evidence base via a publication bias mechanism where unexpected or assumedly incorrect results are less likely to be submitted or accepted for publication.
 
@@
 
-This analysis found that hydrophilic statins were less harmful in the any, vascular and other dementias outcomes compared to lipophilic statins, and were associated with a small reduction in the risk of the probable and possible AD outcomes.
-The relative precision of the estimates in each group is expected, as the two most commonly prescribed statins are lipophilic (simvastatin and atorvastatin).[@newman2019]
+This analysis found that hydrophilic statins were less harmful in the any, vascular and other dementia outcomes compared to lipophilic statins, and were associated with a small reduction in the risk of the probable and possible AD outcomes.
+The increased precision of the estimates for lipophilic versus hydrophilic statins is expected, as the two most commonly prescribed statins are lipophilic (simvastatin and atorvastatin).[@newman2019]
 
@@
 <!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
+(ref:smeethComparison-cap) __Comparison of codelists__ - Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
 The joining lines showing the overlap between the categories in the two analyses.
 
-(ref:smeethComparison-scap) Comparison of code used in this analysis with those used in the Smeeth et al. 2010 paper
+(ref:smeethComparison-scap) Comparison of codelists
 
@@
 
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest, particularly if they are used to define competing outcomes (e.g.
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest in EHR, particularly if they are used to define competing outcomes (e.g.
 AD vs non-AD dementia).
-This different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why my analysis obtained different results despite the substantial overlap in the data sources used.
+The different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why my analysis obtained different results despite the substantial overlap in the data sources used.
 
@@
 
-The primary strength of this analysis is the relative size of the CPRD and length of follow-up.
+The primary strength of this analysis is the relative size of the CPRD.
 Having reviewed the existing literature, as identified by the systematic review element of this thesis, this analysis of `r comma(attrition[14,1])` participants is one of the largest available studies of this research question.
@@
 This approach has been less commonly used in the literature and allows for the mitigation of potential immortal time bias.
-Finally, it is one of the few that provide evidence on the association of lipid-regulating agent use and vascular and other dementias, and used negative and positive controls to assess the potential for residual confounding.
+It is also one of few studies that provide evidence on the association of LRA use and vascular and other dementias.
+Finally, it used negative and positive controls to assess the potential for residual confounding.
 
@@
 This problem is illustrated by the discrepancy between the results when using the code lists defined for this study and those used by Smeeth _et al_.
-This presents a particular challenge in comparing research across different time-periods and coding systems, particularly the unexpected results I obtained for the vascular and other dementias outcomes.
-
-<!-- TODO Talk here about the reduced biological validity of  -->
+This presents a particular challenge in comparing research across different time-periods and coding systems.
 
@@
 The number of _Apo_$\mathcal{E}4$ alleles represents the strongest genetic risk factor for Alzheimer's disease, but also substantially increases LDL cholesterol levels,[@bennet2007] potentially prompting treatment with a statin or other lipid regulating agent.
-I was unable to control for _Apo_$\mathcal{E}$ genotype in this analysis as I did not have access to genetic data on participants.
+I was unable to control for _Apo_$\mathcal{E}$ genotype in this analysis because I did not have access to genetic data on participants.
 As a result, any protective association between LRA use and the Alzheimer's disease outcomes may be masked by residual negative confounding by _Apo_$\mathcal{E}$.
@@
 
-The raw data supporting this analysis is not publicly available, as access to the CPRD data is controlled by a data monitoring committee.
+The raw data supporting this analysis is not publicly available because access to the CPRD data is controlled by a data monitoring committee.
 However, when data are not readily available, sharing the analysis code and summary statistics represents a way for readers to validate the findings.[@goldacre2019]
@@
 In light of this and my own experiences in attempting to extract information for papers assessing preventative treatments, as documented in Section \@ref(sys-rev-open-data), the outputs from this analysis have been made readily available.
-All code, Read code lists and summary statistics (namely the tables presented in this chapter plus summary tables of effect estimates) can be downloaded in a machine readable format from the archived repository for this project (Zotero DOI: __TBC__).
-<!-- TODO Archive on Zenodo.
---> This open approach should enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to build on that presented here.
+All code, Read code lists and summary statistics (namely the tables presented in this chapter plus summary tables of effect estimates) can be downloaded in a machine readable format from the archived repository for this project ([https://github.com/mcguinlu/CPRD-LRA](https://github.com/mcguinlu/CPRD-LRA)).
+This open approach should enable easy inclusion of this analysis in future evidence synthesis exercises, allowing new work to build on that presented here.
 
@@
 
-### Summary
+## Summary
 
@@
 However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations for the any LRA analysis were largely due to those those observed in the large statin subgroup.
+In all cases, the estimated associations for the "any LRA" analyses were driven by those those observed in the large statin subgroup.
 
-* I attempted to account for important sources of bias through use of time-varying treatment indicator, though the control outcomes included in the analysis provided evidence for only partially controlled confounding by indication related to vascular factors.
+* I attempted to account for important sources of bias through use of a time-varying treatment indicator.
+However, the control outcomes included in the analysis provided evidence for only partially controlled confounding by indication, likely related to vascular factors.
 Additionally, there was the potential for differential misclassification of dementia subtype on the basis of the exposure.
@@
 
-* Findings from this analysis are used as an additional source of evidence in the triangulation exercise presented in Chapter \@ref(discussion-heading).
+* Findings from this analysis are used as an additional source of evidence in the triangulation exercise presented in Chapter \@ref(tri-heading).

### 2021-12-16 06-Chp-IPD-Analysis.Rmd
Range of updates

@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:dataExcluded-caption) Exclusion reasons for cohorts providing data
+(ref:dataExcluded-caption) __Exclusion reasons for cohorts providing data__ - Number of cohorts approach and the reasons for a lack of data access, stratified by whether the cohort was identified by the systematic review or via the DPUK.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:covariateSummary-caption) Summary of characteristics for cohorts included in the IPD  analysis
+(ref:covariateSummary-caption) __Characteristics of IPD cohorts__ - Summary of characteristics for cohorts included in the IPD analysis.
+Variables not available from a cohort are denoted by "-".
+See Appendix \@ref(appendix-ipd-covariate-matrix) for details on the level of missing data within collected variables.
 
@@
 There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
-For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd-cap))
+For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd))
 
@@
 <!----------------------------------------------------------------------------->
-(ref:ipdModelComparison-cap) Comparison of results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses for the all-cause dementia outcome.
+(ref:ipdModelComparison-cap) __Comparison of partially- and maximally-adjusted model__ - Results from the common-set-adjusted (Model 1) and fully-adjusted (Model 2) analyses for the all-cause dementia outcome were compared for the two cohorts containing a full set of covariates (EPIC, Whitehall II).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
+(ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ - Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
 

### 2021-12-16 07-Chp-Triangulation.Rmd
Range of updates

@@
 <!----------------------------------------------------------------------------->
-(ref:thesisOverview-caption) Summary of studies included in this thesis and used as evidence sources in this triangulation exercise.
-Note, Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.
+(ref:thesisOverview-caption) __Summary of research designs included in this thesis__ -The research projects performed as part of this thesis and used as evidence sources in this triangulation exercise are summarised.
+Note that Chapter \@ref(sys-rev-tools-heading) is intentionally not included in this table, as it describes a research tool rather than a research study.
 
@@
 
-(ref:priorsAdd-caption) __Prior distributions mapped to different extents of bias.__ Prior values assigned to additive and proportional biases, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$.
+(ref:priorsAdd-caption) __Prior distributions mapped to different extents of bias__ - Prior values assigned to additive and proportional biases, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$.
 For additive biases, two scenarios were defined (see main text).
@@
 <!----------------------------------------------------------------------------->
-(ref:priorsIndirect-caption) Prior distributions for extent of indirectness, on the log scale.
+(ref:priorsIndirect-caption) __Prior distributions mapped to different extents of indirectness__ - Prior values assigned to proportional indirectness, defined as log-normal distributions with mean $\mu$ and variance $\sigma^2$ using the notation $N(\mu,\sigma^{2})$.
+Note that all indirectness in this analysis was defined _a priori_ to be proportional, and so no distributions for additive indirectness were defined.
 

### 2021-12-16 08-Discussion.Rmd
Range of updates

@@
 ```{block type='savequote', include=knitr::is_latex_output(), quote_author='(ref:discussion-quote)', echo = TRUE}
-Hold
+Science knows it doesn't know everything.
+
+Otherwise, it'd stop.
 ```
 
-(ref:discussion-quote) --- Hold
+(ref:discussion-quote) --- Dara Ó Briain, 2008[@obriain2008]
 

### 2021-12-16 04-Chp-Systematic-Review-Results.Rmd
Proofreading edits

@@
 
-In the four analyses with greater than 10 results, the minimum required for subgroup analysis, stratification by overall risk-of-bias level did not demonstrate a difference between the "Serious" and "Moderate" risk of bias groups.
-The results of the test for subgroup differences is shown in the bottom left of the forest plots for these four meta-analyses (Figures \@ref(fig:obsHyperDementia), \@ref(fig:obsStatinDementiaFig), \@ref(fig:obsHyperAD) and \@ref(fig:obsStatinADFig)).
+In the three analyses with greater than 10 results (Figures \@ref(fig:obsHyperDementia), \@ref(fig:obsStatinDementiaFig) and \@ref(fig:obsStatinADFig)), stratification by overall risk-of-bias level did not demonstrate a difference between the "Serious" and "Moderate" risk of bias groups.
+The result of the test for subgroup differences is shown in the bottom left of the forest plots for these three meta-analyses.
 
@@
 Similar figures for the other analysed lipid-outcome strata are presented in Appendix \@ref(appendix-dr-fraction).
-
-<!-- TODO Improve caption for the legend below -->
 
@@
 Investigation of potential sources of heterogeneity was complicated by two factors.
-In the first instance, a minority of meta-analysis (4 out of 18, `r paste0(comma(4/18*100),"%")`) included 10 or more results, the recommended minimum required for meta-regression.
+In the first instance, a minority of meta-analysis (3 out of 18, `r paste0(comma(3/18*100),"%")`) included 10 or more results, the recommended minimum required for meta-regression.
 Secondly, poor reporting of baseline characteristics of interest precluded the use of several results in a meta-regression analysis.
@@
 Only for the sex covariate were sufficient number of results available to enable meta-regression.
-Across the four meta-analyses examined, the percentage of females in the study cohort was not related to the observed effect estimate (p = `r metaregHypercholDem` for hypercholesterolemia/all-cause dementia, Figure \@ref(fig:obsHyperDementia); p = `r metaregStatinsDem` for statins/all-cause dementia - Figure \@ref(fig:obsStatinDementiaFig); p = `r metaregHypercholAd` for hypercholesterolemia/Alzheimer's disease - Figure \@ref(fig:obsHyperAD); p = `r metaregStatinsAd` for statins/Alzheimer's disease - Figure \@ref(fig:obsStatinADFig)).
+Across the three meta-analyses examined, the percentage of females in the study cohort was not related to the observed effect estimate (p = `r metaregHypercholDem` for hypercholesterolemia/all-cause dementia, Figure \@ref(fig:obsHyperDementia); p = `r metaregStatinsDem` for statins/all-cause dementia - Figure \@ref(fig:obsStatinDementiaFig); p = `r metaregStatinsAd` for statins/Alzheimer's disease - Figure \@ref(fig:obsStatinADFig)).
 
-Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was limited to these four meta-analyses including 10 or more results.
+Similarly, assessment of small-study effects, for which publication bias could be one potential reason, was limited to these three meta-analyses including 10 or more results.
 However, there was weak evidence for the presence of small-study effects in each analyses assessed (see Appendix \@ref(appendix-funnel-plots)).

### 2021-12-16 06-Chp-IPD-Analysis.Rmd
Proofreading edits

@@
 
-Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex.[@ancelin2013; @mielke2010] However, the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) did not identify strong evidence for an effect of sex or age at lipid measurement on the relationship between lipids and dementia.
-The number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on the lipids exposure and the poor reporting of summary statistics of participant characteristics in those that did.
-Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on the between-study heterogeneity in a summary data meta-analysis, as similar distributions of participant covariates across studies may mask a true effect.[@riley2020]
+Previous work has suggested a difference in the effect of lipids on dementia risk based on participant age and sex.[@ancelin2013; @mielke2010] The systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading) could not investigate this effect because the number of included studies in the lipid fraction meta-analyses was small, due to both the relatively small number of studies reporting on lipids and the poor reporting of summary statistics of participant characteristics in those that did.
+Additionally, best practice guidance recommends against basing the decision to perform an IPD meta-analysis on between-study heterogeneity in a summary data meta-analysis, because similar distributions of participant covariates across studies may mask a true effect.[@riley2020]
 
-As such, the aims of this analysis are two fold: firstly, to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the relationship between lipids and dementia risk; and secondly, to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortium of dementia cohorts.
+As such, the aims of this analysis are two fold.
+Firstly, I plan to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the relationship between lipids and dementia risk.
+Secondly, I aim to expand the evidence base for the effect of lipids on dementia outcomes by obtaining estimates from previously unanalysed cohorts available via the Dementia Platform UK, a large consortium of dementia cohorts.
 
@@
 I considered four blood lipid fractions as part of this analysis, namely: total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides (TG).
-Cohorts were eligible for inclusion if they contained data on at least one of these recorded as a continuour variable (i.e.
+Cohorts were eligible for inclusion if they contained data on at least one of these lipid fractions,  recorded as a continuous variable (i.e.
 studies with binary "hypercholesteromemia" would be excluded).
@@
 
-Potentially eligible data sources as defined above were identified via two mechanisms, each with a distinct focus.
+Potentially eligible data sources were identified via two approaches, each with a distinct focus.
+The approaches are described in detail in the following sections.
 For both approaches, the number of cohorts responding to the request for data access and, where applicable, the reasons given for a refusal were recorded.
@@
 The data sources used in each of these cohort analyses were screened against the criteria listed in the previous section, and eligible cohorts were approached for data access.
-In the first instance, the first/corresponding author of the publication was emailed <!-- TODO (see Appendix \@ref(ipd-email-collab) for a copy of the correspondence sent to potential collaborators) --> in Autumn 2020.
+In the first instance, the first/corresponding author of the publication was emailed in Autumn 2020.
 If this approach did not elicit a response within two months, the last author was contacted, on the basis that the first/corresponding author may have been a more junior member of the research group who had moved to a different institution.
@@
 The second approach focused on incorporating relevant, previously-unanalysed data into the analysis, thus providing additional evidence on the relationship between blood lipids and dementia risk.
-This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the MRC which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application process for all cohorts with the intent of making it easier to access data from existing data sources.
+This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the Medical Research Council which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application process for all cohorts, with the intent of making it easier to access data from existing data sources.
 
@@
 Where data on one of the exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
-Lipids levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
+Lipid levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
 
@@
 A range of additional variables were included in the analysis, intended to address the potential for confounding.
-With an awareness that discrepancies in available covariates is a common issue in IPD studies, I defined an idealised set of covariate domains to be age, sex, education, BMI, _Apo_$\mathcal{E}4$ status, smoking/alcohol status, ethnicity, and prevalent diabetes or cardiovascular disease.
+With an awareness that discrepancies are common in the set of available covariates across cohorts included in an IPD analysis, I defined an idealised set of covariate domains to be age, sex, education, BMI, _Apo_$\mathcal{E}4$ status, smoking/alcohol status, ethnicity, and prevalent diabetes or cardiovascular disease.
 This set covers key risk factors for dementia/Alzheimer's disease in addition to general cardiovascular risk factors.
@@
 Missing data in this analysis was classified as either relating to missing values (a data on a variable of interest was available in a cohort, but some values were missing) or missing variables (a cohort did not collect data on a variable of interest).
-Variables with missing values were identified, and 20 imputed datasets were created.[@sterne2009] Imputation was performed using the MICE (Multiple Imputation by Chained Equations) using the `mice` package in R.
+Variables with missing values were identified, and 20 imputed datasets were created.[@sterne2009] Imputation was performed using MICE (Multiple Imputation by Chained Equations) and was implemented in R  using the `mice` package in R.[@Van_Buuren2011-nc]
 
@@
 
-<!-- TODO May need to rethink this, as introducing model based on missing data which isn't fully discussed until later. -->
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 Under a two-stage approach, estimates for the effect of each lipid fraction on incident dementia were first calculated for each data source.
-More specifically, a logistic regression model adjusted for relevant covariates as detailed in the above section was used to quantify the effect of a 1 _mmol/L_ increase in each lipid fraction on each dementia outcome.
+More specifically, a logistic regression model adjusted for relevant covariates (as detailed in the above section) was used to quantify the effect of a 1 _mmol/L_ increase in each lipid fraction on each dementia outcome.
 
@@
 
-<!-- REVIEW ORs - the one issue here may be the length of follow-up. Was it roughly equal across cohorts such that the ORs are comparable? -->
-
 A two-stage IPD approach was employed for a number of reasons.
-Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to btain the effect estimates themselves, following a specified analysis plan, and share these with the IPD team.[@riley2010] Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
-Finally, a two-stage approach is simpler to model, as it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
+Firstly, and most importantly, a two-stage approach allows for siloed data, enabling researchers who are unwilling/unable to provide their data to obtain the effect estimates themselves, following a specified analysis plan, and share these with the IPD team.[@riley2010] Secondly, it allows for the production of forest plots of within-cohort estimates, something which is useful for the triangulation exercise in Chapter \@ref(tri-heading).
+Finally, a two-stage approach is simpler to model because it uses standard well-documented summary effect estimate meta-analysis techniques, and automatically accounts for methodological issues such as clustering within cohorts[@abo-zaid2013] and the potential for ecological bias.[@burke2017]
 
@@
 
-In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, lipid-covariate interaction terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] All interaction analysis were performed using the common-set-adjusted model (Model 1).
+In order to investigate the interaction of participant-level characteristics (age and sex) with lipid levels, lipid-covariate interaction terms were extracted and synthesised using a fixed effects meta-analysis.[@fisher2017] All interaction analyses were performed using the common-set-adjusted model (Model 1).
 To avoid ecological bias, where the between-study association does not reflect the within-study associations, cohorts where there was no within-study variation in the covariate of interest were excluded from the interaction analysis for that covariate.[@burke2017] As an example, it is impossible to estimate the impact of sex on the lipid/dementia relationship in a study which contains only female participants.
@@
 Figure \@ref(fig:cohortFlowchart) details whether the cohorts eventually included in the review were identified by the systematic review or via the DPUK portal.
-In addition, the reasons for cohorts not being included in the analysis are presented, where available, stratified by application approach.
+In addition, the reasons for cohorts being from the analysis are presented, stratified by application approach.
 
 In summary, the requests for data from cohorts identified by the systematic review were characterised by a very low response rate (N = 5, 25%).
-For the minority who did respond, common reasons given by authors for not sharing the data included that they: no longer worked with the same group and did not know if the data was available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
+For the five cohorts that did respond, common reasons given by authors for not sharing the data included that they: no longer worked with the same group and did not know if the data was available or how to obtain it; no longer had access to the data; or were currently performing, or intended to perform, a similar analysis as the one proposed.
 
@@
 
-(ref:cohortFlowchart-cap) __Flowchart detailing sources of data for the IPD analysis__ The number of cohorts approached and the reasons for exclusion are summarised, stratified by identification method (systematic review vs DPUK).
+(ref:cohortFlowchart-cap) __Flowchart detailing sources of data for the IPD analysis__ The number of cohorts approached and the reasons for exclusion are stratified by identification method (systematic review vs DPUK).
 
@@
 Nine cohorts (8 DPUK only, 1 Systematic review + DPUK) responded positively to requests for data access.
-However, on inspection of data provided, six of these cohorts were excluded and the reason for exlcusion in each case is summarised in Table \@ref(tab:dataExcluded-table).
+However, on inspection of data provided, six of these cohorts were excluded and the reason for exclusion in each case is shown in Table \@ref(tab:dataExcluded-table).
 In summary, two cohorts contained were memory-complaint cohorts, containing participants unlikely to be free of dementia at baseline (BRACE, MEMENTO).
@@
 The Caerphilly Prospective Study (CaPS) is a longitudinal study of men in South Wales, UK.[@zotero-15398;@elwood2013] Blood lipids (TC, LDL-c, HDL-c and TG) were measured at baseline in 1979-1983, and from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
-A dementia was derived using data obtained during Phase V (2002-2004), giving between 19-25 years of follow-up.
+Dementia outcomes were determined using data obtained during Phase V (2002-2004), giving between 19-25 years of follow-up.
 The cohort contains data on dementia outcomes sub-classified as vascular and non-vascular dementia.
@@
 
-The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] Data provided by this cohort for the analysis, dementia was ascertained at at the 5th Health Checkup (2016-2018), providing between 18-25 years of follow-up.
+The European Prospective Investigation of Cancer (EPIC) - Norfolk is a population-based cohort, containing men and women recruited from 35 general practices in Norfolk between 1993 and 1998.[@riboli1997; @riboli2002] Dementia was ascertained at the 5th Health Check-up (2016-2018), providing between 18-25 years of follow-up.
 The added evidential value of the EPIC cohort is small, given the fact that the data obtained contains only 8 dementia events.
@@
 The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] Lipids measurements were available from the third wave of the study, conducted between 1991-1993.
-The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England, which was used to define covariates at baseline and dementia outcomes.[@zotero-15403] HES data for dementia outcomes was available up to March 2015, providing between 22-24 years of follow-up.
+The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England.
+which was used to capture dementia outcomes.[@zotero-15403] HES data was available up to March 2015, providing between 22-24 years of follow-up.
 Information was available on dementia type, which was classified as all-cause dementia, Alzheimer's disease or vascular dementia.
@@
 Based on available data across cohorts, smoking was classified as never/ever/current, while alcohol consumption was classified as never/ever.
+Ever use in this case refers to participants who do not currently smoke/drink alcohol, but did so in the past.
 Education was categorised into 4 levels (None, O-levels, A-levels, Degree).
@@
 Missing values in collected variables was common across the cohorts.
-A matrix of covariates, and whether they were not available or contained missing values for each included cohort, can be seen Appendix \@ref(appendix-ipd-covariate-matrix).
+A matrix of covariates for each included cohort, describing both missing variables and the proportion of missing values within collected variables, can be seen in Appendix \@ref(appendix-ipd-covariate-matrix).
 The Whitehall II and EPIC cohorts contained data on all but one covariates of interest, while three missing covariates were identified in the CaPS cohort, namely education, prevalent ischemic heart disease, BMI and ethnicity.
@@
 Across the three cohorts, `r n_total_ipd` participants were included in this analysis (Whitehall II = 8208, EPIC = 1115, CaPS = 2512).
-All cohorts contained data on the four exposure variables of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes.
+All cohorts contained data on the four lipid fractions of interest (or sufficient data from which to calculate them) and on all-cause dementia outcomes.
 The only other dementia outcome examined across cohorts was vascular dementia, which was reported in the CaPS and Whitehall II studies.
@@
 Variables not available from a cohort are denoted by "-".
-See Appendix \@ref(appendix-ipd-covariate-matrix) for details on the level of missing data within collected variables.
+See Appendix \@ref(appendix-ipd-covariate-matrix) for details on the proportion of missing data within collected variables.
 
@@
 The results from the main effect analysis across the varying lipid fractions on each dementia outcome considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
-There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`).
+There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`, \@ref(fig:mainEffectVad)).
 For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd))
@@
 
-The maximally-adjusted model (Model 2) could have been employed in the analysis of the effect of sex, as the CaPS cohort contains only men and had to be excluded from this analysis, leaving the EPIC and Whitehall cohorts, both of which had a full complement of covariates.
+The maximally-adjusted model (Model 2) could have been employed in the analysis of the effect of sex, as both EPIC and Whitehall II had a full complement of covariates (CaPS contains only men and so was excluded from this analysis).
 However, I decided to employ the same underlying model across the interaction analyses to aid comparability between the age and sex interaction estimates.
@@
 For all-cause dementia, there was no evidence of an interaction of lipid levels with either age group or sex (Figures \@ref(fig:interactionDementiaAge) & \@ref(fig:interactionDementiaSex)).
-Note that for the sex interaction analysis, the CaPS cohort was excluded as it contains only a single sex and therefore provides no information on exposure-sex interaction.
 
 <!----------------------------------------------------------------------------->
-(ref:interactionDementiaAge-cap)  __Meta-analysis of age-lipid interaction terms for all-cause dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
+(ref:interactionDementiaAge-cap)  __Meta-analysis of age-lipid interaction terms for all-cause dementia__ - Age was grouped into 5-year age bands, and the effect estimates presented represent the OR per 1-step increase in age group.
 Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes).
@@
 (ref:interactionDementiaSex-cap) __Meta-analysis of sex-lipid interaction terms for all-cause dementia__ - Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes) and refer to the effect of male gender on the lipid/all-cause dementia association.
+The CaPS cohort was excluded from this analysis because it contains only a single sex and therefore provides no information on the lipid-sex interaction.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:interactionVascularAge-cap) __Meta-analysis of age-lipid interaction terms for vascular dementia__ - Age was grouped into 5-year age bands, and the effect estimatse presented represent the OR per 1-step increase in age group.
+(ref:interactionVascularAge-cap) __Meta-analysis of age-lipid interaction terms for vascular dementia__ - Age was grouped into 5-year age bands, and the effect estimates presented represent the OR per 1-step increase in age group.
 Estimates were obtained using the common-set-adjusted model (Model 1: age, sex, smoking, alcohol, education, diabetes).
@@
 No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia.
-Similarly, there was weak evidence for an interaction of the effect of lipid levels on dementia outcomes with participants' age, grouped into 5 year bands, or sex.
+Similarly, there was weak evidence for an interaction of the effect of lipid levels on dementia outcomes with participants' age (grouped into 5 year bands) or sex.
 
@@
 
-The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences in the association of lipids with dementia outcomes between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD analysis.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis, as it provided training in application of the methods in addition to providing new evidence that will be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
-
-<!-- REVIEW also identified that any future studies would require a longer and/or more directive approach to the provision of access - DPUK is a good example of how this could be done! -->
+The obvious key limitation of this analysis is the very low response rate to requests for data access, which may bias the results if there are systematic differences in the association of lipids with dementia outcomes between cohorts that share data and those that do not.[@ahmed2012] Whether or not to press ahead with an IPD analysis in the absence of all (or even most) data is a personal decision, and some previous analyses have highlighted where they decided not to pursue an IPD analysis.[@jaspers2014] For the purposes of this thesis, the decision was made to conduct the IPD analysis because it provided training in application of IPD methods in addition to providing new evidence that will be incorporated into the triangulation exercise detailed in Chapter \@ref(tri-heading).
 
@@
 Finally, the DPUK process would be aided by a clearer distinction between those cohorts that are "DPUK native" (i.e.
-where a copy of the data is already held on DPUK servers) versus externally hosted, as the response time for externally hosted cohorts is likely to be much longer.
+where a copy of the data is already held on DPUK servers) versus externally hosted, seeing as the response time for externally hosted cohorts is likely to be much longer.
 
@@
 More generally, systematically missing variables required a trade-off between inclusion of cohort data and appropriate control for confounding.
-The final choice of the common-set-adjusted model for use in the interaction analyses mean there is the potential for residual confounding.
+The final choice of the common-set-adjusted model for use in the interaction analyses means there is the potential for residual confounding.
 However, sensitivity analysis comparing the common-set-adjusted (Model 1) and fully-adjusted (Model 2) models in cohorts with a full complement of covariates indicated that further adjustment for BMI, ethnicity, education and prevalent IHD had minimal impact on the effect estimates.
-Of note, this is comparable with the analysis of the CPRD data presented in the previous chapter, where adjustment for variable beyond age and sex had a limited impact on the observed effect estimates (see Section \@ref(cprd-impact-additional-covar)).
+Of note, this is comparable with the analysis of the CPRD data presented in the previous chapter, where adjustment for variables beyond age and sex had a limited impact on the observed effect estimates (see Section \@ref(cprd-impact-additional-covar)).
 
@@
 Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data allowing it to adjust for _Apo_$\mathcal{E}4$ status.
-However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in findings observed.
+However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in the findings observed.
 
@@
 While this analysis did not manage to obtain and analyse a large proportion of identified data, a central strength of this analysis is the use of a systematic approach to identify and attempt to contact relevant cohorts.
-Further, it also enabled incorporation of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - thus providing additional evidence that is used in the triangulation exercise reported in Chapter \@ref(tri-heading).
+Furthermore, it also enabled incorporation of two previously unanalysed datasets - the CaPS and EPIC Norfolk cohorts - thus providing additional evidence that is used in the triangulation exercise reported in Chapter \@ref(tri-heading).
 
@@
 Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-This is relevant even in the previously analysed WhiteHall II cohort, as the previous analysis by Tynkkynen _et al._ did not report on this outcome.
+This is relevant even in the previously analysed WhiteHall II cohort because the previous analysis by Tynkkynen _et al._ did not report on this outcome.
 
@@
 
-Additionally, the production of detailed guidance for handling cases where covariates are systematically missing would represent a useful addition to the topic.
+Additionally, the production of detailed guidance for handling cases where covariates are systematically missing would represent a useful contribution to the topic.
 Much of the literature around IPD analysis is focused on the synthesis of RCTs, where additional covariate information is needed primarily for the assessment of treatment-covariate interactions rather than the adjustment of the effect estimate for confounding.
@@
 
-Finally, a movement towards increased use of unique persistent identification of researchers, through schemes such as the ORCID programme,[@nature2009] would help with contact issues.
+Finally, movement towards increased use of unique and persistent researcher identifiers, such as those offered by the ORCID programme,[@nature2009] would help with contact issues.
 Researchers move institutions regularly as their contracts come to an end, and so the institutional contact details provided on publications are frequently out of date.
@@
 I highlighted the contribution of this work to the wider topic via the analysis of previously unexplored cohorts (CaPS & EPIC) and outcomes (vascular dementia).
-Finally, I recommended that future research formally investigate the impact of the characteristics of the requesting researcher on data access rates.
+Finally, I recommended that future research could formally investigate the impact of the characteristics of the requesting researcher on data access rates.
 

### 2021-12-16 08-Discussion.Rmd
Proofreading edits

@@
 
-In __Chapter \@ref(sys-rev-tools-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoretical framework of evidence synthesis.
+In __Chapter \@ref(background-heading)__, I introduced the core concepts considered in this thesis and framed the research presented in relation to a theoretical framework of evidence synthesis.
 
@@
 
-In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipids and lipid-regulating agents with dementia outcomes.
+In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes.
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
@@
 
-As the results of the different components of this thesis are discussed in detail as part of the triangulation analysis (see Section \@ref(qual-tri)), here I briefly summarise the key findings.
+Given that the results of the different components of this thesis are discussed in detail as part of the triangulation analysis (see Section \@ref(qual-tri)), here I briefly summarise the key findings.
 
@@
 While published non-randomised studies provided evidence for a protective effect of lipid-lowering via statin use on Alzheimer's disease and the IPD analysis suggested a harmful effect of raised triglycerides on vascular dementia, these effects were not maintained when incorporated along with other sources of evidence in a quantitative triangulation framework.
-Similarly, the IPD analysis did not provide evidence for an interaction of patient characteristics (age/sex) with the association of blood lipids on dementia outcomes, other than a slight protective effect of male gender on the LDL-c/all-cause dementia relationship.
+Similarly, the IPD analysis did not provide evidence for an interaction of patient characteristics (age/sex) with the association of blood lipids and dementia outcomes, other than a slight protective effect of male gender on the LDL-c/all-cause dementia relationship.
 However, this analysis was limited by the low number of cohorts analysed.
@@
 
-Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been performed.
+Since the searches underpinning the systematic review described in this thesis were performed (July 2019), further studies on this topic have been published.
 Two of these, notable for the analysis of large UK cohorts, are discussed here.
@@
 _Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels, <!-- TODO CITATION NEEDED --> and so could explain the harmful association observed.
-This is supported by a simulation analysis reported within this study, which used published information to predict that _Apo_$\mathcal{E}4$ would induce a RR of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
+This is supported by a simulation analysis reported within this study, which used published information to predict that _Apo_$\mathcal{E}4$ would induce a risk ratio of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.
 
-The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes, again a comparable finding to the results of this thesis.
+The second analysis examined 502,226 participants in the UK Biobank, a large population-based prospective cohort study.[@gong2021; @sudlow2015] The analysis found no association between lipids measured at mid-life and dementia outcomes.
+This finding is again comparable to the results of this thesis.
 However, similar to the study discussed above, this analysis did not have access to genetic data and so may be subject to residual confounding by _Apo_$\mathcal{E}4$ genotype.
@@
 It may well prove difficult to assess if any observed trends are due to a true effect or to confounding or ecological biases.
-However, because dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach could provide a ready source of further evidence with a distinct bias structure to the approaches considered in this thesis.
+However, because dementia outcomes will be monitored anyway for incidence/prevalence estimation and planning of services/care, this approach could provide a ready source of further evidence with a distinct bias structure to the approaches already considered in this thesis.
 
@@
 In terms of visualisation of bias, I have made a number of methodological contributions.
-I created a well-received R package to create paired forest plots (see Appendix \@ref(appendix-robvis)), and built on this to enable creation of the bias direction plots illustrated in Chapter \@ref(tri-heading).
+I built a well-received R package to create paired forest plots (see Appendix \@ref(appendix-robvis)), and developed this further to enable users to produce the bias direction plots illustrated in Chapter \@ref(tri-heading).
 
 Finally, I made several novel contributions around the incorporation of bias into analyses.
-These were intended to encourage authors of reviews to actively consider the impact of bias in their synthesis, something that empirical evidence suggests happens infrequently at present.[@katikireddi2015] The new methods introduced by this thesis range from the forest plots stratified by overall risk of bias level presented in Chapter \@ref(sys-rev-results-heading) to the more advanced triangulation framework presented in Chapter \@ref(tri-heading).
+These were intended to encourage authors of reviews to actively consider the impact of bias in their syntheses, something that empirical evidence suggests happens infrequently at present.[@katikireddi2015] The new methods introduced by this thesis range from the forest plots stratified by overall risk of bias level presented in Chapter \@ref(sys-rev-results-heading) to the more advanced triangulation framework presented in Chapter \@ref(tri-heading).
 
@@
 The proposed quantitative triangulation framework represents the final novel contribution of this thesis to evidence synthesis methodology.
-Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies, reducing the potential for differential adjustment based on knowledge of the results.
-This framework explicitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distributions representing the impact of bias/indirectness.
-
-<!-- TODO Double check last paragraph! -->
+Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies.
+In addition, it explicitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distributions representing the impact of bias/indirectness.
 
@@
 
-Finally, while the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
+Finally, the framework proposed here could (fairly) be criticised over the validity of the prior distributions of bias/indirectness chosen.
+However, the assumptions made about the impact of bias in this thesis are no stronger than those made when synthesising effect estimates as though they were unbiased.
 The proposed framework at the very least recognises the uncertainty introduced by bias/indirectness and decreases the precision of the overall effect estimate on this basis.
@@
 
-There are several strengths to this thesis as a whole.
-Specifically, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous syntheses of the evidence on this topic.
+There are four key strengths to this thesis as a whole.
+Firstly, the identification and triangulation of evidence across study designs and publication status sets this thesis apart from previous syntheses of the evidence on this topic.
+
 Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied relationship (lipids/LRA and vascular dementia).
@@
 Extensive documentation has been written to guide users through usage of the tools and example data are provided, enabling future researchers to readily apply the methods described.
+
 Finally, substantial effort has been invested to make the research documented in this thesis as reproducible as possible - this is documented more fully in Appendix \@ref(disc-repro-research).
@@
 
-However, there are also several limitations to this thesis.
-In the first instance, as with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
-It is possible that statins have a true effect via some pathway other than lipid-regulation, but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
+However, there are also four key limitations to this thesis.
+As with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
+It is possible that statins have a true effect on dementia risk via some pathway other than lipid-regulation, but without knowledge of the mechanism, the plausibility of this relationship cannot be assessed.
 
@@
 A final weakness stems from the geographical focus of the data analysed in this thesis.
-All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in the Western world (Figure \@ref(fig:cohortLocations)).
+All primary analysis presented drew on data from the UK (CPRD, CaPS, EPIC Norfolk, Whitehall II), while the majority of studies identified by the review were based in westernised countries (Figure \@ref(fig:cohortLocations)).
 This, combined with the limited evidence for different ethnicities available even within high income settings, may limit the generalisability of the results presented to different populations.
@@
 
-The proposal for the program of research underpinning this thesis was created in advance of starting my PhD, as a detailed plan was required in order to secure the funding that supported me through my studies.
+The proposal for the program of research underpinning this thesis was created in advance of starting my PhD because a detailed plan was required in order to secure the funding that supported me through my studies.
 In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs.
@@
 Alzheimer's disease) when considering the causal effects of lipids.
-Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, as data cleaning and harmonisation for just three cohorts turned out to be a substantial undertaking.
+Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, given that data cleaning and harmonisation for just three cohorts turned out to be a substantial undertaking.
 
@@
 
-### Generation of new RCT evidence
+### Generation of new evidence from RCTs
 
-It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trial be performed to assess the effect of the proposed intervention.
+It is customary at this point in the discussion of results based (primarily) on observational data to recommend that a large-scale randomised controlled trial (RCT) be performed to assess the effect of the proposed intervention.
 Given the costs and logistical challenges associated with trials examining outcomes with long prodromal periods such as dementia, a more efficient approach is offered by the opportunistic post-trial follow-up of existing RCTs of lipid-regulating agents.
@@
 This approach has already been used to assess long-term (11-20 years) safety outcomes of statin use, using participant recontact[@group2011] and linkage with electronic health records to identify events.[@ford2016] A similar approach could be used to assess the impact of randomisation to statins at midlife on subsequent risk of dementia outcomes.
-Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using EHRs.
+Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using electonic health records.
 
@@
 
-However, it seems unlikely that further analysis of observational data alone will be sufficient to investigate this outcome, as indicated by the presence of strong confounding by indication in the analysis of statins and vascular dementia (Chapter \@ref(cprd-analysis-heading)).
-Even using new methods, such as a target trial emulation approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] Similarly, available Mendelian randomisation studies are limited to a single one-sample analysis of HMGCR variants as a proxy for statin treatment.
-This study suggested a protective effect of lipid-lowering on vascular dementia, though there was a moderate risk of bias in this analysis and the effect was attenuated to the null when including a wider range of lipid-lowering variants.
+However, it seems unlikely that further analysis of observational data alone will be sufficient to investigate this outcome, given the evidence of strong confounding by indication presented by the analysis of statins and vascular dementia (Chapter \@ref(cprd-analysis-heading)).
+Even using cutting-edge methods, such as a target trial emulation approach, previous analyses have not replicated the known protective effect of statins on coronary heart disease identified by RCTs (see Section \@ref(cprd-confounding-by-ind)).[@danaei2013] Similarly, available Mendelian randomisation studies are limited to a single one-sample analysis of HMGCR variants as a proxy for statin treatment.
+This study suggested a protective effect of lipid-lowering on vascular dementia, although there was a moderate risk of bias in this analysis and the effect was attenuated to the null when including a wider range of lipid-lowering variants.
 
-Taken together, these points reinforce the need for a large-scale GWAS of vascular dementia, similar to those currently available for Alzheimer's disease, to identify associated loci that future two-sample Mendelian randomisation studies could exploit.
+Taken together, these points reinforce the need for a large-scale genome-wide association study (GWAS) of vascular dementia, similar to those currently available for Alzheimer's disease, to identify genetic variants associated with this outcome that future two-sample Mendelian randomisation studies could exploit.
 While GWAS of this outcome are likely to be methodologically challenging, given the difficulty in diagnosing "pure" vascular dementia, it would be a worthwhile endeavour and allow for the assessment of genetically driven risk factors beyond those considered in this thesis.
@@
 
-The `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.[@elliott2014] In addition, the ready access to preprint data afforded by the tool will enable future meta-epidemiological studies to examine factors which may influence eventual publication (for example,  significant result, geographical location/gender/career stage of first author, or some other factor).
+The `medrxivr` tool enables programmatic searching of health-related preprints, and future work could incorporate the tool, along with software to search other literature sources, into an automated searching pipeline as part of a living systematic review.[@elliott2014] In addition, the ready access to preprint data afforded by the tool will enable future meta-epidemiological studies to examine factors which may influence eventual publication (for example,  significant results, geographical location/gender/career stage of first author, or some other factor).
 Finally, the tool will allow future research to assess the impact of peer review and editorial guidelines on manuscripts through comparison of the same paper at two stages (preprinted versus published).

### 2021-12-16 07-Chp-Triangulation.Rmd
Other edits

@@
 For example, while it may be true that all non-randomised studies share some minimal level of bias, competing extents and directions of bias in individual results may be masked by the use of summary estimates.
-In addition, previous attempts at qualitative triangulation have not systematically assessed the indirectness of the results, that is the differences between the question of interest and the question addressed by a study.
+In addition, previous attempts at qualitative triangulation have not systematically assessed the indirectness of the results, namely the differences between the question of interest and the question addressed by a study.
 
@@
 Similarly, risk-of-bias assessments were performed for each new source of evidence presented in this thesis.
-The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias), but in summary, RCTs were assessed using the RoB 2 tool;[@sterne2019] NRSI using the ROBINS-I tool;[@sterne2016] NRSE using an early adapted version of the ROBINS-E tool (see Section \@ref(rob-tools-nrse));[@morganr2020; @french2019] and MR studies using the Mamluk et al.
+The risk of bias tools used to assess each result are described in detail in Section \@ref(risk-of-bias), but in summary, randomised controlled trials (RCTs) were assessed using the RoB 2 tool;[@sterne2019] non-randomised studies of interventions (NRSI) using the ROBINS-I tool;[@sterne2016] non-randomised studies of exposures (NRSE) using an early adapted version of the ROBINS-E tool (see Section \@ref(rob-tools-nrse));[@morganr2020; @french2019] and Mendelian randomisation (MR) studies using the Mamluk et al.
 tool.[@mamluk2020]
@@
 
-Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the IPD analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (TC - `r obsLipids$Dementia_TC$estimate`; LDL - `r obsLipids$Dementia_LDL$estimate`; HDL - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate`).
+Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the individual participant data (IPD) analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (in the systematic review: TC - `r obsLipids$Dementia_TC$estimate`; LDL - `r obsLipids$Dementia_LDL$estimate`; HDL - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate` ).
 Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
@@
 
-In contrast, the meta-analysis of NRSI of statin use found a slight protective effect for the all-cause dementia outcome (`r obsStatins$Dementia$estimate`), though many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the statin use.
-Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(cprd-analysis-heading)) found evidence of a harmful association (`r anydem_sta_text`), though this is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
+In contrast, the meta-analysis of statin use found a slight protective effect for the all-cause dementia outcome (`r obsStatins$Dementia$estimate`), although many of the studies in this analysis were found to be at risk of immortal time bias, which would be expected to favour the statin use.
+Finally, analysis of the association of statin use with all-cause dementia in the CPRD (Chapter \@ref(cprd-analysis-heading)) found evidence of a harmful association (`r anydem_sta_text`).
+However, this finding is likely to be driven by the substantial confounding by indication identified in the vascular dementia subgroup.
 
@@
 
-In contrast, the meta-analysis of NRSI of statin use found a slight protective effect on this outcome (`r obsStatins$AD$estimate`), though similar to the all-cause dementia outcome, many of the studies in this analysis were found to be at risk of immortal time bias.
+In contrast, the meta-analysis of statin use found a slight protective effect on this outcome (`r obsStatins$AD$estimate`), though similar to the all-cause dementia outcome, many of the studies in this analysis were found to be at risk of immortal time bias.
 However, the CPRD analysis, which attempted to account for this potential bias through the use of time-varying treatment indicator, found weak evidence for an effect (`r probad_sta_text`).
@@
 Finally, only one of the three cohorts included in the IPD analysis (Whitehall II) contained data on Alzheimer's disease.
-However, a previously published analysis (Tynkkynen _et al._[@tynkkynen2018]) examining the association of lipid levels with Alzheimer's disease in the this cohort was identified by the systenatic review.
+However, a previously published analysis (Tynkkynen _et al._[@tynkkynen2018]) examining the association of lipid levels with Alzheimer's disease in this cohort was identified by the systenatic review.
 The results of this previous analysis are incorporated into the results of the meta-analysis reported above, and so the IPD analysis provided no new information on this outcome.
@@
 The IPD analysis provided supporting evidence for the absence of an effect of any fraction on vascular dementia, with the sole exception of triglycerides.
-Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts (`r ipd_vasdem`), though there is the potential for uncontrolled confounding due to the limited information available on important covariates.
+Raised triglycerides were associated with an increased incidence of vascular dementia across two previously unanalysed cohorts (`r ipd_vasdem`), although there is the potential for uncontrolled confounding due to the limited information available on important covariates.
 With respect to evidence on treatments for hypertriglyceridemia, examination of fibrates in the CPRD provided weak evidence of an association with vascular dementia (`r vasdem_fib_text`).
@@
 1. Identify relevant evidence sources and standardise effect directions
-1. Specify idealised version of each study
+1. Specify an idealised version of each study
 1. Assess the extent and direction of bias/indirectness in each result
@@
 non-randomised studies of LDL-c levels) or indirectly (e.g.
-non-randomised studies of statins, or Mendelian randomisation studies using genetic instruments for LDL-c levels).
+non-randomised studies of statins, or MR studies using genetic instruments for LDL-c levels).
 
@@
 
-Once the set of relevant results have been identified, an idealised study for each is described
+Once the set of relevant results have been identified, an idealised study for each should be described.
 An idealised study can be viewed as a replicate of the study producing the result of interest but with all sources of bias removed.
@@
 
-The assessment of bias in each result is discussed in Section \@ref(tri-data-sources) above.For the sake of consistency and ease of computing, I mapped the different acceptable risk-of-bias judgements in each tool to a harmonised set: "Low", "Moderate", and "High".
+The assessment of bias in each result is discussed in Section \@ref(tri-data-sources) above.
+For the sake of consistency and ease of computing, I mapped the different acceptable risk-of-bias judgements in each tool to a harmonised set: "Low", "Moderate", and "High".
 The exact mapping can be seen in Table \@ref(tab:robLevelsMapping-table).
@@
 <!-- REVIEW in fact it is a mandatory part of new ROBINS-E tool, while only optional in RoB2 and ROBINS-I. Maybe reiterate that using a very early version of ROBINS-E -->
+
+<!-- QUESTION text -->
 
@@
 
-The predicted direction and type of bias were not recorded for domains at "Low" risk of bias.
+The predicted direction and type of bias was not recorded for domains at "Low" risk of bias.
 Finally, for some domains, only one type of bias is allowed.
@@
 
-Reasonable values for the position and spread of the prior distributions were informed by a previously reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the mean values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated).
+Reasonable values for the position and spread of the prior distributions were informed by a previously reported expert bias elicitation exercise.[@turner2009] Using open data from that study, I calculated the average values for the mean and variance of the adjustment distributions across all biases considered by that exercise (see Appendix \@ref(appendix-adjustment-values) for more details on how these were calculated).
 For the purposes of this illustrative analysis and to highlight the generalised nature of the code used to perform the analysis (see Section \@ref(tri-software)), I used the calculated values to inform two scenarios of modifying distributions (Table \@ref(tab:priorsAdd-table)) for additive biases, and a single set for proportional biases.
-In the first scenario, the relationship between the position assigned to each additive judgement is linear.
+In the first scenario, the relationship between the position assigned to each additive bias judgement is linear.
 In the second scenario, the step from "Moderate" to "High" is twice that from "Low" to "Moderate".
@@
 As an illustrative example, consider the first causal question of the interest in this exercise, the effect of LDL-c in mid-life on Alzheimer's disease.
-Here, studies of lipids levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be adjusted and down-weighted due to reduced relevance to the causal question.
+Here, studies of lipid levels in this time period would require minimal adjustment, whereas studies examining statin use (indirect exposure/intervention) in late-life (indirect population) would be adjusted and down-weighted due to reduced relevance to the causal question.
 
@@
 
-where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness.
-Note that in this exercise, the total additive indirectness $\mu_{i\beta}^{\mathrm{In}} = 1$, as all indirectness was defined _a priori_ as being proportional.
+where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness, respectively.
+Note that in this exercise, the total additive indirectness $\mu_{i\beta}^{\mathrm{In}} = 1$ because all indirectness was defined _a priori_ as being proportional.
 
-The standard error of this estimate is then calculated as:
+The standard error of this estimate ($\mathrm{SE}(\hat{\theta})$) is then calculated as:
 
@@
 As an illustrative example of the process using a single result, the bias and indirectness inherent to the estimate of the effect of statin use on Alzheimer's disease in the CPRD (as analysed in Chapter \@ref(cprd-analysis-heading)) are considered here.
-For this result, there were three domains at greater than low risk of bias: Bias due to confounding, Bias due to definition of the outcome, and Bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
-In Domain 1 (bias due to confounding), the study did not adjust for _Apo_$\mathcal{E}4$ status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
+For this result, there were three domains at greater than low risk of bias: bias due to confounding, bias due to definition of the outcome, and bias in the selection of the reported result (Figure \@ref(fig:biasDirectionSingle)).
+In Domain 1 (bias due to confounding), the study did not adjust for _Apo_$\mathcal{E}$ status, which is predicted to mask any true association between statins and Alzheimer's disease (see Section \@ref(cprd-limitations) for a fuller discussion).
 As such, the bias is predicted to _favour the comparator_ and so the absolute direction of bias is to the right.
-In Domain 7 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure.
+In Domain 6 (bias in measurement of the outcome), there was a high risk of differential misclassification on the basis of the exposure.
 Here, a history of statin use may make a diagnosis of vascular dementia more likely than Alzheimer's disease, and so for this outcome, this bias is predicted to _favour the experimental_ (in this case, an intervention).
@@
 
-Indirectness was intentionally not displayed in the plot above, as these figures are created using `robvis` which is focused on creating visualisations of risk-of-bias data.
+Indirectness was intentionally not displayed in the plot above because these figures are created using `robvis` which is focused on creating visualisations of risk-of-bias data.
 In addition, I found it more useful to articulate the indirectness of a result in tabular format.
@@
 However, the result refers to the effect of statins on Alzheimer's disease risk, rather than LDL-c levels directly, putting it at high risk of indirectness in the intervention/exposure domain.
+
 Overall, assessing the predicted direction of indirectness was more challenging than assessing the predicted direction of bias.
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:singleIndirect-caption) __Assessment of indirectness for a single example study__
+(ref:singleIndirect-caption) __Assessment of indirectness for a single example study__ - The target setting for the causal question of interest (effect of midlife LDL-c on Alzheimer's disease) and the idealised version of a single example study are compared.
+The risk and predicted direction of indirectness resulting from discrepancies between the target setting and idealised study are shown.
 
@@
 
-The unadjusted estimate was `r single_unadjusted `.
+The unadjusted estimate of the effect of LDL-c on Alzheimer's disease was `r single_unadjusted `.
 After accounting for the biases and indirectness described, the adjusted result was `r single_adjusted `, representing a minimal shift in the position of the effect estimate but a substantial decrease in precision.
@@
 
+<!-- TODO Update this paragraph to reflect extra 2 MR studies -->
+
 From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest.
-Most (N =17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate from the CPRD analysis.
+Most (N =17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate via the CPRD analysis.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
 
-<!-- QUESTION Hypercholesterolemia should not be included here, as it is focused on total cholesterol rather than specifically LDL-c, right? -->
+<!-- TODO Double check this reference list is correct! -->
 
@@
 Following adjustment for bias and indirectness, the observed effect attenuates to the null (unadjusted `r unadj_effect`; adjusted `r adj_effect_scenario1`).
-Additionally, adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`).
+Additionally, adjustment for bias and indirectness substantially reduced the heterogeneity between studies (unadjusted $\tau^2$ = `r unadj_tau2`, $I^2$ = `r unadj_I2`%; adjusted  $\tau^2$ = `r adj_tau2`, $I^2$ = `r adj_I2`%).
 However, as can been seen from the right panel in Figure \@ref(fig:fpLdlAd), this reduction in heterogeneity between studies is largely achieved via a reduction in the precision of each individual result.
@@
 
-Comparison of the unadjusted and bias-/indirectness-adjusted results for the effect of triglycerides on vascular dementia did not demonstrate a substantial difference (unadjusted `r unadj_effect_vad`; adjusted `r adj_effect_scenario1_vad`; Figure \@ref(fig:fpTgVad)), though again, heterogeneity between the adjusted results was greatly reduced (unadjusted $\tau^2$ = `r unadj_vad_tau2`, $I^2$ = `r unadj_vad_I2`; adjusted  $\tau^2$ = `r adj_vad_tau2`, $I^2$ = `r adj_vad_I2`).
+Comparison of the unadjusted and bias-/indirectness-adjusted results for the effect of triglycerides on vascular dementia did not demonstrate a substantial difference (unadjusted `r unadj_effect_vad`; adjusted `r adj_effect_scenario1_vad`; Figure \@ref(fig:fpTgVad)), though again, heterogeneity between the adjusted results was greatly reduced (unadjusted $\tau^2$ = `r unadj_vad_tau2`, $I^2$ = `r unadj_vad_I2`%; adjusted  $\tau^2$ = `r adj_vad_tau2`, $I^2$ = `r adj_vad_I2`%).
 Similarly there was minimal difference between the results under the two scenarios of bias (Figure \@ref(fig:fpTgVaDComparison) in Appendix \@ref(appendix-tri-analysis)).
@@
 However, the prior distributions defined here are broadly comparable to previously reported estimates of the impact of bias in non-randomised trials.
-For example, a previous simulation study estimated that, in the absence of true effect of LDL-c, _Apo_$\mathcal{E}4$ would induce a RR of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior log-normal distribution mapped to "Moderate" additive bias ($N(0.09,0.05)$, Table \@ref(tab:priorsAdd-table)).
+For example, a previous simulation study estimated that, in the absence of a true effect of LDL-c, _Apo_$\mathcal{E}4$ would induce a risk ratio of 1.09 with risk of dementia per 1-SD increase in LDL-c.[@iwagami2021] This is comparable to the mean assigned to the prior log-normal distribution mapped to "Moderate" additive bias ($N(0.09,0.05)$, Table \@ref(tab:priorsAdd-table)).
 
@@
 
-Finally, it may in fact be more reasonable for domains such as bias due to confounding to adjust on a per-confounder basis rather than mapping to a "Moderate" or "High" extent of bias.
+Finally, for the "bias due to confounding" domain, it may in fact be more reasonable to adjust on a per-confounder basis rather than mapping to a "Moderate" or "High" extent of bias.
 In this approach, prior distributions are assigned to each of the confounders pre-specified as part of the ROBINS-I/ROBINS-E tools.[@sterne2016] Then, rather than assigning a domain level distribution based on an arbitrary judgement of how many important confounders are missing, the result is adjusted for each confounder not accounted for in the original analysis.
@@
 A final limitation of this analysis is the synthesis of different effect estimates.
-As discussed in Section \@ref(sys-rev-analysis-overview), hazard ratios are not directly comparable to odds ratios, as they inherently account for person time-at-risk.[@mckenzie2019] As non-randomised studies (NRSI/NRSI) of dementia outcomes report hazard ratios and Mendelian randomisation studies report odds ratios, the resulting synthesis may be biased by the integration of these two different effect measures.
-This is primarily a concern for common outcomes, as when the outcome is rare, the odds, risk and hazard ratios approximate each other.
+As discussed in Section \@ref(sys-rev-analysis-overview), hazard ratios are not directly comparable to odds ratios because they inherently account for person time-at-risk.[@mckenzie2019] Non-randomised studies (NRSI/NRSI) of dementia outcomes reported hazard ratios and Mendelian randomisation studies reported odds ratios, and as such the resulting synthesis may be biased by the integration of these two different effect measures.
+This is primarily a concern for common outcomes because the odds, risk and hazard ratios approximate each other when the outcome is rare.
 
@@
 In previous attempts at bias-/indirectness-adjusted meta-analysis, the extent of bias in each study was assessed via an elicitation process,[@thompson2011; @turner2009; @wilks2011] during which experts were aware of the results of each analysis.
-This approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results, as there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
+This approach is potentially subject to differential misclassification of the impact of bias/indirectness on the basis of the results because there is no way to ensure that results at a similar level of bias for confounding (for example) are being adjusted by the same amount across studies.
 As an illustrative example, if experts are influenced by the knowledge of the effect estimate in a study, then a result at "Moderate" risk of confounding and demonstrating a stronger protective effect may receive greater adjustment than a study at the same risk of confounding but with a more modest effect.
@@
 
-Future development of this framework should also account for bias at the analysis level in terms of missing evidence.[@zotero-15123] For example, there is at least one known study relevant to the triglycerides/vascular dementia case study that reported a non-significant result but provided insufficient details to be included in the analysis.[@chiang2007] Ideally, a quantitative triangulation framework would further account for this proportional meta-bias (as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
+Future development of this framework should also account for bias at the analysis level in terms of missing evidence.[@zotero-15123] For example, there is at least one known study relevant to the triglycerides/vascular dementia case study that reported a non-significant result but provided insufficient details to be included in the analysis.[@chiang2007] Ideally, a quantitative triangulation framework would further account for this proportional meta-bias (seeing as bias due to missing evidence is most likely to bias away from the null due to publication bias mechanisms), in addition to result-specific biases.
 
-Appreciation that both the risk-of-bias and indirectness of a result should be assessed is growing.
+Appreciation that both the risk-of-bias and indirectness of a result should be examined is growing.
 Indeed, some existing tools for the assessment of diagnostic test accuracy[@whiting2011] and prediction models[@moons2019] consider indirectness (termed applicability in these tools) alongside the assessment of bias.
@@
 
-There are two key outputs from this project.
-The first is the `triangulate` R package.
-Personal communication with the authors of the original method resulted in the STATA code to implement the bias-/indirectness-adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
-The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis), calculation of bias/indirectness-adjusted estimates for each result, and synthesis of these adjusted results in a standard random-effects meta-analysis.
+There are two key outputs from this chapter.
+The first is an R package, `triangulate`.
+Personal communication with the authors of the bias-/indirectness-adjusted meta-analysis approach resulted in the STATA code to implement the adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
+The package allows for preprocessing of domain-based risk-of-bias data to correctly identify the direction of bias relative to the effect estimate, use of domain-specific prior distributions, production of bias direction plots (via the tool described in Appendix \@ref(appendix-robvis)), calculation of bias/indirectness-adjusted estimates for each result and synthesis of these adjusted results in a standard random-effects meta-analysis.
 

### 2021-12-16 front-and-back-matter/99-appendices.Rmd
Other edits

@@
 
-\blandscape
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-A copy of the risk of bias tool used to assess Mendelian randomisation studies is presented in Table \@ref(mrTool-table), below.
+A copy of the risk of bias tool used to assess Mendelian randomisation studies is presented in Table \@ref(tab:mrTool-table), below.
+
+\blandscape
 
@@
 <!----------------------------------------------------------------------------->
-(ref:prismaTab-caption) __PRISMA Checklist__ - Following best practice guidelines, the Section/Table/Figure number were important details on the systematic review can be found are listed.
+(ref:prismaTab-caption) __PRISMA Checklist__ - Following best practice guidelines, the Section/Table/Figure number where important details on the systematic review can be found are listed.
 
@@
 
+### Funnel plots {#appendix-funnel-plots}
+
+```{r funnelPlots, include = FALSE}
+```
+
+<!----------------------------------------------------------------------------->
+(ref:funnerlPlots-cap) __Funnel plots__ - To assess the potential for small study effects, funnel plots were produced for the three meta-analyses reported in Chapter \@ref(sys-rev-results-heading) that contained more than 10 results.
+Visual inspection of the plots did not indicate the presence of small study effect, which was supported in each case by the result of Egger's regression test for funnel plot asymmetry.
+
+(ref:funnerlPlots-scap) Funnel plots
+
+```{r funnerlPlots, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:funnerlPlots-cap)', out.width='100%', fig.scap='(ref:funnerlPlots-scap)'}
+knitr::include_graphics(file.path("figures/appendix/funnel_composite.pdf"))
+```
+<!----------------------------------------------------------------------------->
+
+&nbsp;<!----------------------------------------------------------------------->
+
 ### Dose response plots by fraction {#appendix-dr-fraction}
@@
 
-(ref:drDemeniaTC-cap) __Dose-response meta-analysis of total cholesterol on all-cause dementia__
+(ref:drDemeniaTC-cap) __Dose-response meta-analysis of total cholesterol on all-cause dementia__ - Non-randomised studies examining the association of total cholesterol with all-cause dementia across several categories or "doses" of exposure were synthesised using a dose response meta-analysis.
+The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).
 
@@
 
-(ref:drAdLDL-cap) __Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease__
+(ref:drAdLDL-cap) __Dose-response meta-analysis of low-density lipoprotein cholesterol on Alzheimer's disease__ - Non-randomised studies examining the association of LDL with Alzheimer's disease across several categories or "doses" of exposure were synthesised using a dose response meta-analysis.
+The reference dose was defined _a priori_ as 100 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for LDL as detailed in Table \@ref(tab:lipidLevels-table).
 
@@
 
-Panel A of Figure \@ref(fig:minFU) describes a standard analysis of an exposure with a minimum enforced follow-up period (in this case, 10 years).
-Participants enter the cohort and are classified at that point as either exposed or unexposed, for example, on the basis of a total cholesterol measurement.
-Participants are followed-up over time, but events occurring before the minimum period of follow-up are discarded.
-
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
+
+Panel A of Figure \@ref(fig:minFU) describes a standard analysis of an exposure with a minimum enforced follow-up period (in this case, 10 years).
+Participants enter the cohort and are classified at that point as either exposed or unexposed, for example, on the basis of a total cholesterol measurement.
+Participants are followed-up over time, but events occurring before the minimum period of follow-up are discarded.
 
@@
 
-&nbsp;
-
 <!----------------------------------------------------------------------------->
@@
 
-&nbsp;
+\newpage
 
@@
 
+&nbsp;<!----------------------------------------------------------------------->
+
 ## Chapter 8
@@
 Unfortunately, given the nature of the data underpinning the CPRD (Chapter \@ref(cprd-analysis-heading)) and IPD (Chapter \@ref(ipd-heading)) analyses, it is not possible to make it publicly available.
-Access to the CPRD data is dependent on an application to its managing body, while acces to the cohorts within the DPUK requires approval from both the DPUK and inidividual cohort owners.
+Access to the CPRD data is dependent on an application to its managing body, while access to the cohorts within the DPUK requires approval from both the DPUK and individual cohort owners.
 In the absence of data sharing, the best option to enable review and increase transparency is the open sharing of the code used to perform the analysis.[@goldacre2019]
@@
 
-OVer the course of my PhD, I kept a record of attempted
+As part of a reflective process, during the course of my PhD I kept a record of things (analytical mishaps, failed experiments, and unsuccessful grant applications) I attempted but which did not work.
+These are summarised briefly here:
 
-Short section detailing the things I tried to do but which did not work:
+- Prior to the analysis performed in Chapter \@ref(cprd-analysis-heading), I attempted an analysis using physicians prescribing preference as an instrumental variable to compare different lipid-regulating agent classes for dementia prevention.
+However, this analysis was not pursued due to the very small number of patients prescribed a lipid-regulating agent other than statins.
 
-- Failed to properly scope the literature and correctly estimate the number of studies returned by the search
+- I initially failed to realise that a code list I was using for the positive control outcome of ischemic heart disease (IHD) in the CPRD analysis (Chapter \@ref(cprd-analysis-heading)) included only very severe IHD outcomes.
+This resulted in the positive protective control analysis giving substantially inflated hazard ratios (HR > 4) and led to substantial confusion in the study team.
 
-- Failed IV analysis of anti-HC drugs because of low numbers of non-statins.
+- For the IPD analysis in Chapter \@ref(ipd-heading), I had to be reminded that (a) BMI can be calculated from weight and height, and (b) that whether you ask at 45 or 50, the age at which someone left school will be the same.
 
-- Failed to realise that the initial code list used for the positive control outcome of IHD in the CPRD analysis (Chapter \@ref(cprd-analysis-heading))
+- I was involved in unsuccessful grant applications to the NIHR (with Andrew Beswick), to the Jean Golding Institute (with James Byrne and Chris Penfold) and to the PGR Hub (with Matthew Lee).
 
-- Unsuccessful grant application with Andy
-
-- Unsuccessful grant application with Chris Penfold
-
-- Unsuccessful grant application with Matt
-
-- Instrumental variable analysis of lipid regulation use using physicians prescribing preference.
-
-- 2 x unsuccessful conference abstracts
-
-<!-- TODO Include the early analysis we did here, that did not work as a result of limited scope.
-Could include some of the genetic work also.
-Will additionally need to put the relevant materials from the paper in the  -->
+&nbsp;<!----------------------------------------------------------------------->
 
@@
 
-## Producing risk-of-bias visualisations with `robvis` {#appendix-robvis}
+## `robvis`: producing risk-of-bias visualisations {#appendix-robvis}
 
 <!-- TODO Need to complete this sections -->
-The `robvis` package provides functions to convert a risk-of-bias assessment summary table into a summary plot or a traffic-light plot, formatted based on the specific risk-of-bias assessment tool used.
+The `robvis` package provides functions to visualise risk-of-bias assessments, with the resulting plots formatted based on the specific risk-of-bias assessment tool used.
+The tool is documented extensively online at [https://mcguinlu.github.io/robvis/](https://mcguinlu.github.io/robvis/).
+As such, it is not described in detail here, other than to illustrate the data structures required for the figures presented in this thesis and to describe its reception in the evidence synthesis community.
 
-### Templates
+&nbsp;<!----------------------------------------------------------------------->
 
-`robvis` currently contains templates for the following tools:
+### Data setup
 
-* ROB2
-* ROBINS-I
-* QUADAS-2
-* ROB1
-* General
+For the paired forest plots presented in Chapter \@ref(sys-rev-results-heading), the tool expects a "Study" column, followed by one column per domain of bias and one column for the overall risk of bias judgement.
+To illustrate this, the `data_rob2` dataset which is available via the `robvis` package and contains example risk-of-bias assessments performed using the RoB2.0 tool for randomized controlled trials, is shown in Table \@ref(tab:biasData-table).
 
-### Data expectations
+For the bias direction plots illustrated in Chapter \@ref(tri-heading), additional details on each domain of bias are required by the tool, namely the direction and type of bias in each domain.
+An example of the data required by `robvis` in order to produce the bias direction plots is shown in \@ref(tab:biasDirectionData-table).
 
-For the direction bias plots, the data expected by the tools is more comprehensive.
+```{r, echo = FALSE, warning=FALSE}
 
-&nbsp;
+robstats <- cranlogs::cran_downloads("robvis", from = "2019-11-22", to = "2021-12-01")
+
+robvis_downloads <- plyr::round_any(sum(robstats$count), 100, f = floor)
+
+date <- format(as.Date("2021-12-01"),"%B %Y")
+```
+
+&nbsp;<!----------------------------------------------------------------------->
+
+### Reception
+
+The tool has been well received by the systematic review community.
+As of `r date`, the `robvis` R package has been downloaded more than `r medrxivr_downloads` times and the paper introducing the tool had been cited more than 450 times.
+A copy of this publication is available in Appendix \@ref(published-papers).
+Development of the tool is ongoing, as evidenced by the new bias direction plot functionality, and there are now a number of contributors to the package.
 
@@
 (ref:biasDirectionData-caption) __Example bias direction dataset__ - Example risk-of-bias data illustrating the structure required for bias direction plots.
-$d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain.
-Note that, because of the wide nature of the data, I have abbreviated the data in order to display it.
+$d_ij$, $d_id$, and $d_it$ define the extent (Serious, Moderate, Low), direction (right or left), and type (additive or proportional) of bias in the $i$th domain, respectively Note that, because of the wide nature of the data, I have abbreviated the data in order to display it.
 A key for interpreting the data can be found below the table.
@@
 \elandscape
-
-### Simple visualisations
-
-```{r robAppendixFigures, include = FALSE}
-```
-
-```{r, eval = FALSE}
-rob_summary(data = data_rob2, tool = "ROB2")
-```
-
-<!----------------------------------------------------------------------------->
-(ref:robSummary-cap) __Example risk-of-bias summary barplot__ - Illustration of a simple summary barplot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
-Note that this plot is unweighted and shows the _proportion of studies_ at each level of bias, but an option exists with `robvis` to create a barplot weighted by the _proportion of evidence_ at each level of bias.
-
-(ref:robSummary-scap) Example risk-of-bias summary barplot
-
-```{r robSummary, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:robSummary-cap)', out.width='80%', fig.scap='(ref:robSummary-scap)'}
-knitr::include_graphics(file.path("figures/appendix/robSummary.png"))
-```
-<!----------------------------------------------------------------------------->
-
-```{r, eval = FALSE}
-rob_traffic_light(data = data_rob2,
-                  tool = "ROB2",
-                  psize = 10)
-```
-
-<!----------------------------------------------------------------------------->
-(ref:robTraffic-cap) Example risk-of-bias traffic-light plot - Illustration of a simple traffic light plot created using the `data_rob` example risk-of-bias dataset shown in Table \@ef(tab:biasData-table) above.
-
-(ref:robTraffic-scap) Example risk-of-bias traffic-light plot
-
-```{r robTraffic, echo = FALSE, results="asis", fig.pos = "H", fig.cap='(ref:robTraffic-cap)', out.width='80%', fig.scap='(ref:robTraffic-scap)'}
-knitr::include_graphics(file.path("figures/appendix/robTraffic.png"))
-```
-<!----------------------------------------------------------------------------->
 
@@
 
-<!-- TODO May need to reiterate contributions here -->
-
 <!-- TODO These have been removed so as to not mess-up the plagarism score -->
 
-\includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
+<!-- \includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf} -->

### 2021-12-16 front-and-back-matter/_abstract.Rmd
Other edits

@@
 __Background:__ Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies.
-Blood lipid levels have been implicated in the aetiology of dementia by genetic linkage and functional cell biology studies, but current epidemiological evidence has yet to reach a consensus on their role in dementia risk.
-This thesis sought to triangulate the causal effects of lipid levels (total cholesterol, LDL-c, HDL-c, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
+As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, LDL-c, HDL-c, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
 
@@
 __Methods:__ Four distinct analyses were conducted.
-Firstly, a systematic review of 81 published and preprinted studies was used to summarise the existing evidence base.
-Preprints were searched using a new research tool created as part of this thesis.
-The existing evidence was then supplemented via two primary studies: i) a cohort study of the association of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual participant data meta-analysis of the association of blood lipids with dementia incidence in previously unanalysed cohorts accessed through the Dementia Platform UK.
-Finally, a novel quantitative triangulation framework was proposed, building on recent developments in risk-of-bias assessment and bias-/indirectness-adjusted meta-analyses.
-This framework was then used to quantitatively triangulate the evidence identified and produced by this thesis.
+Firstly, a systematic review was used to summarise the evidence base.
+Existing evidence was then supplemented via two primary studies: i) a cohort study of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual participant data (IPD) meta-analysis of lipid levels and dementia incidence.
+Finally, a novel quantitative triangulation framework was proposed, and was then used to integrate the results of the previous three studies.
 
@@
 
-__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
-The analysis of lipid regulating agents in the CPRD provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia.
-However, the use of control outcomes illustrated this finding was likely due to confounding by indication related to vascular factors.
-The individual participant data meta-analysis suffered from a low response rate to data access requests, but in the three cohorts analysed, there was some evidence for only the association of triglycerides and vascular dementia.
-Finally, the triangulation analysis integrating the results of the previous three studies did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
+__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
+Analysis of the CPRD data provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia,  likely due to confounding by indication.
+The IPD meta-analysis provided some evidence for only the association of triglycerides and vascular dementia.
+Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
 
@@
 This thesis provides new evidence concerning the role of blood lipids as a modifiable risk factor for dementia and highlights the uncertainty that still remains in relation to this causal question.
-In addition, it has developed new evidence synthesis methods and tools, specifically around the inclusion of preprints in systematic reviews and the quantitative triangulation of evidence sources.
+In addition, it has developed new evidence synthesis methods and tools.

### 2021-12-16 front-and-back-matter/_acknowledgements.Rmd
Other edits

@@
 
-There are many people without whose input and support this work would have been severely diminished:
+First and foremost, I must thank my primary supervisor, Julian Higgins, for his tireless support and encouragement.
+I'd also like to thank my other supervisors - Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their input over the past three years.
+Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews.
 
-Thank Julian separately -
+I am extremely grateful to all those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner.
+A special mention goes to Mark Newbury of the Dementia Platform UK, who worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
 
-First and foremost, I would like to thank my supervisors - Julian Higgins, Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their support over the past three years.
-Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews.
-Sharen Hockey-O'Keffe helped me at numerous points throughout my PhD, and I was very lucky to receive her support.
-Similarly, Mark Newbury of the Dementia Platform UK worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
-
-Thanks must also go to those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner.
-
-Thanks also to all those who raised issues or otherwise provided feedback on the open source tools built as part of this thesis:
-<<github>> A special mention must go to Randall Boyes and Alex J Fowler for their input on the `robvis` tool.
-
-I have been supported throughout my studies by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
-The views expressed in this thesis are my own and do not necessarily represent those of the NIHR or the Department of Health and Social Care.
+I also want to thank the many people who raised issues or otherwise provided feedback on the open source tools built as part of this thesis - it's been a joy to watch others build on my work.
+A special mention must go to Randall Boyes and Alex J Fowler for their input/work on the `robvis` tool.
 
@@
 
-This thesis would not have been possible with Ciara Gardiner.
-Lots of people say this about someone at this point in the acknowledgements, and I'm always sceptical of whether it is true, so to avoid any doubt I mean it here quite literally.
-
 Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour.
 It can't have been fun being locked-down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin.
-I talk about lessons learnt during this thesis in the Discussion, but the biggest takeaway for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand.
+In the Discussion, I talk about lessons learned during this thesis, but the biggest takeaway of this whole experience for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand.
 Thank you and I love you.
 
-Thanks to Mum and Dad for your never-ending love and support, and everything they have done to get me to point where doing and submitting a thesis.
+Mum and Dad, thank you for your never-ending love and support. Everything I am comes from you, and you've done so much to get me to the point where a PhD thesis seemed possible.
 
-Thanks to Vivienne and Dad for giving up a substantial amount of time to proof-reading.
+There are several people without whom I would not have survived the process of writing a dissertation during COVID times. Ben, Doug, Christin - thank you!
 
-On a personal note, there are several people without whom I would not have survived the process of writing a dissertation during COVID times. Ben, Doug, Christin - thank you!
+Finally, a big thanks to Vivienne Gardiner, who sacrificed a substantial amount of time to proof-reading this thesis.
+
+\bigskip
+
+__Funding__
+
+I have been supported throughout my studies by an NIHR Doctoral Research Fellowship (DRF-2018-11-ST2-048).
+The views expressed in this thesis are my own and do not necessarily represent those of the NIHR or the Department of Health and Social Care.
 

### 2021-12-16 01-Chp-Background.Rmd
End of day:

@@
 It then introduces evidence synthesis as the key framework used to guide the research presented in the remaining chapters.
-Finally, it outlines the aims, objectives and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
+Finally, it outlines the aims, objectives, and structure of this thesis, and briefly summarises the contributions to the scientific literature that arose from this research.
 
@@
 
-The remaining 10-30% of cases are caused by other dementia subtypes (e.g. Lewy body or frontotemporal dementias) or other neurological diseases (e.g. Parkinson's disease).[@burns2009]
+The remaining 10-30% of cases are caused by other dementia subtypes (e.g., Lewy body or frontotemporal dementias) or other neurological diseases (e.g., Parkinson's disease).[@burns2009]
 
@@
 
-Many cognitive assessment tools exist for the purpose of informing a diagnoses of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
+Many cognitive assessment tools exist for the purpose of informing a diagnosis of dementia,[@sheehan2012] with two of the best known of these being the Mini Mental State Exam (MMSE) and Montreal Cognitive Assessment (MoCA) scale.
 The distinction between these memory scales and diagnostic criteria presented above should be noted.
@@
 (ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia (major neurocognitive disorder).__ - These published criteria[@edition2013] are commonly used to define dementia cases.
-Criterion A captures the cognitive decline aspect of dementia, while Criteria B-D ensure that the impairment observed is sufficient to interfere with daily living and can not explained by other causes.
+Criterion A captures the cognitive decline aspect of dementia, while Criteria B-D ensure that the impairment observed is sufficient to interfere with daily living and cannot explained by other causes.
 Note that all criteria (A-D) must be met.
@@
 The blood lipid profile contains a range of component parts, or fractions.
-However, this thesis will only consider the two most important fractions, trigylcerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
+However, this thesis will only consider the two most important fractions, triglycerides (TG) and cholesterol, which are either absorbed from food (exogenous lipids) or produced internally (endogenous lipids).[@feingold2000]
 
 Triglycerides are the simplest and most common type of lipids, used to store excess calories from food and to move energy around the body.[@laufs2020] In contrast, cholesterol is primarily used to create cell walls and certain sex hormones.[@zampelas2019] Lipids are not water soluble, and so cholesterol is transported through the blood stream in lipoprotein structures of varying densities.
-Low-density-lipoprotein cholesterol (LDL-c), commonly know as "bad" cholesterol, acts as an energy conveyor by transporting fat to cells.
+Low-density-lipoprotein cholesterol (LDL-c), commonly known as "bad" cholesterol, acts as an energy conveyor by transporting fat to cells.
 In contrast, high density-lipoprotein cholesterol (HDL-c) transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
@@
 \begin{equation}
-  TC \approx LDLc + HDLc + kTG
+  TC \approx LDL + HDL + kTG
   (\#eq:total-cholesterol-formula)
@@
 where $k$ is 0.20 if measurements are in milligrams per decilitre (_mg/dl_) and 0.45 if measured in millimole per litre (_mmol/l_).
-Widely-used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
+Widely used ranges for the acceptable levels of different types of lipids are based on the National Cholesterol Education Program (NCEP)[@national2002third], and are outlined in Table \@ref(tab:lipidLevels-table).
 
-Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolaemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
+Elevated LDL-c in the bloodstream, a condition also known as hypercholesterolemia or hyperlipidaemia,[@nelson2013] can lead to atherosclerosis,[@libby2019] the build-up of fatty deposits in the blood vessels.
 These deposits constrict blood flow and can lead to vascular complications.
@@
 Statins are a commonly prescribed method of lipid regulation.[@collins2016] Statins inhibit the conversion of 3-hydroxy-3-methylglutaryl-coenzyme-A (HMG-CoA) into mevalonate, by competitively binding with HMG-CoA reductase (HMGCR).
-This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(fig:statin-mechanisam)), enabling statins to reduce effectively the production of LDL cholesterol.
+This conversion is a key rate-limiting step in the cholesterol biosynthesis pathway (see Figure \@ref(fig:statin-mechanisam)), enabling statins to effectively reduce the production of LDL cholesterol.
 
@@
 (ref:statin-mechanisam-cap) __Statin mechanism of action__ - Statins inhibit HMG-CoA reductase which controls the conversion of HMG-CoA to mevalonate.
-This conversion is the rate-limiting step in cholesterol biosynthesis, and so statin use can lower cholesterol levels.
+This conversion is the rate-limiting step in cholesterol biosynthesis, and so statin use can reduce the production of cholesterol.
 
@@
 Several statin treatments have been widely available for some time (see Table \@ref(tab:statinOverview-table)).
-Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g.
-ravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g.
-rosuvastatin 80 mg/day).[@collins2016; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the off-target effects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
+Depending on the statin and dosage prescribed, the average reduction in LDL-c concentrations ranges from 15% with low-intensity regimen (e.g., pravastatin 5 mg/day) up to 60% with a high-intensity regimen (e.g., rosuvastatin 80 mg/day).[@collins2016; @law2003] Statins also vary with regard to their lipophilicity (the extent to which they are lipid soluble), affecting their localisation within the body, with hydrophilic statins being concentrated in the liver and lipophilic statins circulating more widely.[@schachter2005] This may create a divide in the off-target effects of statins with differing lipophilicity, particularly given the ability of lipophilic statins to permeate the blood brain barrier.[@sierra2011]
 
@@
 
-(ref:statinOverview-caption) __Overview of common statins__ -  There are several commonly-prescribed statins used to treat hypercholesterolemia.
+(ref:statinOverview-caption) __Overview of common statins__ -  There are several commonly prescribed statins used to treat hypercholesterolemia.
 Their approval date (US), properties and lipid-lowering effect are described here.
@@
 
-There are several other interventions that can be used to modify a persons lipid profile, each of which act via different mechanisms.
+There are several other interventions that can be used to modify a person's lipid profile, each of which act via different mechanisms.
 However, in general, these treatments are either used as adjunct (additional) treatments to statin therapy or are used in situations where statins are contra-indicated or not tolerated.
@@
 Fibrates provide a second example of non-statin therapy.
-They are used to treat hypertriglyceridaemia by reducing production of triglyceride carrying compounds in the liver.
+They are used to treat hypertriglyceridemia by reducing production of triglyceride carrying compounds in the liver.
 They are commonly used in patients with mixed hyperlipidaemia if treatment with statins has failed to sufficiently control cholesterol levels.
@@
 
-Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004] and omega-3-fatty acids,[@skulas2019] but they far less effective in LDL-c lowering than the therapies described above.
+Other therapies targeting triglycerides exist, including nicotinic acids[@mckenney2004] and omega-3-fatty acids,[@skulas2019] but they are far less effective in LDL-c lowering than the therapies described above.
 
@@
 Newer methodological approaches, such as Mendelian randomisation (MR),[@daveysmith2014] have also been used to examine the effect of varying lipid levels on dementia risk.
-Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random varation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV)[@davies2018] which are discussed in Section \@ref(rev-discussion-MR).
+Mendelian randomisation attempts to combat the risk of reverse causation and residual confounding inherent to observational studies by using natural random variation in participants' genomes.[@greenland2000] In brief, MR uses genetic variants that are both strongly associated with the exposure of interest and are independent from potential confounders to strengthen causal inference.[@daveysmith2014] The analytic method relies on several assumptions about the instrumental variable (IV)[@davies2018] which are discussed in Section \@ref(rev-discussion-MR).
 
@@
 
-One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as a indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
+One of the major criticisms of using preprints as an evidence source is that they have not yet undergone formal peer review.[@maslove2018; @schalkwyk2020] However, this approach assigns substantial weight to peer-review as an indicator of "quality", and is at odds with the acceptance of non-reviewed conference proceedings as an evidence source.[@lefebvre2019searching; @mahood2014] The argument for including preprints as an evidence source is further strengthened by results that demonstrate preprinted studies seldom change following peer review.
 Meta-studies of the concordance between preprinted and published studies showed that results were broadly comparable between the two, indicating that while the numerical results may change, the overall interpretation of the results were consistent in the majority of cases.[@shi2021; @klein2019; @nicholson2021] This indicates that preprints should be considered a reliable reflection of a given study.
@@
 
-I will attempt to obtain the raw data from relevant primary studies identified by the systematic review presentd in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+I will attempt to obtain the raw data from relevant primary studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
 Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
@@
 Aetiological triangulation is a developing evidence synthesis method that seeks to exploit these differences in study design, and as a result, in underlying bias structures.[@lawlor2016] If several sources of evidence are available and point towards identical conclusions about an exposure-outcome relationship, and these sources are at risk of unrelated biases, this strengthens our confidence in the result.
-The ideal scenario is where predicted sources of bias are likely to be in competing directions, one to strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provide a middle-ground between the competing directions of bias.
+The ideal scenario is where predicted sources of bias are likely to be in competing directions, one to strengthen the effect of the exposure and the other to attenuate it.[@lawlor2016] As such, triangulating these results can provide a middle ground between the competing directions of bias.
 A triangulation approach can also prove useful in helping to prospectively design new studies that are at risk of different sources of bias to those already observed in the published literature.[@munafo2018] However, existing methods for triangulation are limited to a qualitative discussion of the different identified results with respect to their biases,[@lawlor2016] an approach which faces issues in interpretability when assessing many results.
@@
 
-* To create a tool that allows for the inclusion of health related preprints in evidence syntheses in a systematic and reproducible manner
+* To create a tool that allows for the inclusion of health-related preprints in evidence syntheses in a systematic and reproducible manner
 * To review all available evidence across multiple diverse study designs to assess the effect of lipids and lipid regulating agents on dementia risk
-* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
+* To examine whether there is evidence for an effect of lipid-regulating agents on dementia and related outcomes in a large-scale population-based cohort, the Clinical Practice Research Datalink (CPRD)
 * To produce evidence on lipid-covariate interactions as part of an IPD meta-analysis 
@@
 -   **Chapter \@ref(background-heading):** Background information on dementia and blood lipid levels.
-This chapter provides an introduction to the topics covered in this thesis, and discusses the motivation for the research presented in the following chapters.
+This chapter provides an introduction to the topics covered in this thesis and discusses the motivation for the research presented in the following chapters.
 -   **Chapter \@ref(sys-rev-tools-heading):** This chapter introduces a new tool, `medrxivr`, which was developed to allow for systematic searches of the health-related preprint repositories.

### 2021-12-16 02-Chp-Systematic-Review-Tools.Rmd
Range of updates
End of day:

@@
 
-2.  support for bulk export of references returned to a file type that can be readily imported into a reference manager (e.g., *.bib* or *.ris*); and
+2.  support for bulk export of references returned to a file type that can be readily imported into a reference manager (e.g.,, *.bib* or *.ris*); and
 
@@
 Prior to searching the metadata, users must first create a local copy of the database, denoted using `mx_data` below.
-In `medrixvr`, I have provided two separate but related methods to achieve this (Figure \@ref(fig:medrxivr-data-sources)).
+In `medrxivr`, I have provided two separate but related methods to achieve this (Figure \@ref(fig:medrxivr-data-sources)).
 The first of these methods, accessed via the `mx_api_content()` function, creates a local copy of all data available from the medRxiv API at the time the function is run.
@@
 
-```{r, eval = FALSE, class.source = "bg-danger"}
+```{r, eval = FALSE}
 # Get a copy of the database from the live medRxiv API endpoint
@@
 Firstly, because the API returns results as a series of pages limited to 100 records per page, downloading the entire database requires a time-intensive process of cycling through each page.
-Secondly, the API can become unavailable, either during peak usage times or planned maintainence windows.
+Secondly, the API can become unavailable, either during peak usage times or planned maintenance windows.
 To address these limitations, I provide a second method of accessing medRxiv data, called via the `mx_snapshot()` function, which allows users to access a maintained static snapshot of the database.
@@
 There is no limit to the number of search terms that can be included in each topic, nor in the number of topics that can be searched for.
-Search terms can also contain common syntax used by systematic reviewers and health librarians, including the NEAR operator for the identification of co-localised terms and wild-cards which allow for alternate spellings (e.g.
-"randomi*s*ation" vs "randomi*z*ation").
+Search terms can also contain common syntax used by systematic reviewers and health librarians, including the NEAR operator for the identification of co-localised terms and wild cards which allow for alternate spellings (e.g., "randomi*s*ation" vs "randomi*z*ation").
 
@@
 As an example, in the search presented above, the term "alzheimer's" returns no records.
-This is expected, because "Alzheimer's" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
+This is expected because "Alzheimer's" is a proper noun and so should be capitalised, but serves to illustrate the usefulness of the reporting function.
 
@@
 
-In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to export easily the results of their systematic search to a reference manager.
+In line with my second success criteria (Section \@ref(success-criteria)), one of the key features of the `medrxivr` is the ability for users to easily export the results of their systematic search to a reference manager.
 While this would seem a likely candidate to be a generic feature, this is one of the key ways in which `medrxivr` is set apart from other preprint search tools.
@@
 
-The results of our simple search above can be exported to the `medrxiv_export.bib"` file using the following code:
+The results of our simple search above can be exported to the `medrxiv_export.bib` file using the following code:
 
@@
 
-For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrixvr`.
+For example, I led a descriptive analysis of the change in data availability statements between preprinted and published versions of the same manuscript, stratified by journal data sharing policy access, underpinned by preprint meta-data provided by `medrxivr`.
 By comparing the preprinted and published versions of the data availability statement, I could examine the same manuscript - same content, authors and funders - under two different publication policies (preprint server vs peer-review journal).
@@
 Secondly, using `medrxivr`, an analysis of the publication rate for medRxiv preprints was performed (see Appendix \@ref(appendix-tools-pub)).
-`r published` of the `r publication_n` records `r publish_percent` posted on medRxiv in July 2019 were published by 30th July 2021 (i.e.
-allowing for a two-year lag between preprint posting and publication).
+`r published` of the `r publication_n` records `r publish_percent` posted on medRxiv in July 2019 were published by 30th July 2021 (i.e., allowing for a two-year lag between preprint posting and publication).
 This finding agrees with previous work demonstrating that two-thirds of bioRxiv preprints are published in a peer-reviewed journal within two years of posting.[@abdill2019popularity] This analysis further illustrates that a substantial number of studies are never formally published but remain accessible as preprints.
 
-In summary, the meta-research/methodological analyses described above illustrate that easy access to medRxiv/bioRxiv metadata has applications beyond the inclusion of preprints in systeamtic review.
+In summary, the meta-research/methodological analyses described above illustrate that easy access to medRxiv/bioRxiv metadata has applications beyond the inclusion of preprints in systematic review.
 
@@
 
-### Role of open source tools in evidence synthesis
+### Role of open-source tools in evidence synthesis
 
-Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019; @mckiernan2016] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@fraser2020rbiorixv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
+Part of the motivation for creating the `medrxivr` tool was a belief that the development and distribution of open-source scripts and tools should be a fundamental part of evidence synthesis research.[@goldacre2019; @mckiernan2016] In the case of `medrxivr`, it is likely that several other evidence synthesists had written personal scripts that have a similar, or related, functionality - in fact, following development of the tool, I identified one other researcher that has done so (Nicholas Fraser, author of the `rbiorxiv` package, which allows for importing medRxiv metadata into R but does not provide search functionality).[@fraser2020rbiorixv] If these scripts continue to be developed in private and are never shared or publicised, this will inevitably hamper the efforts of the evidence synthesis community, not only in terms of duplication of time and effort but also due to lost opportunities for collaboration.[@mckiernan2016] Creating and sharing well-documented packages, the recognised standard for sharing code in R, represents one way to reduce this inefficiency.[@vuorre2020]
 

### 2021-12-16 03-Chp-Systematic-Review-Methods.Rmd
End of day:

@@
 ```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-methods-quote)', echo = TRUE}
-"It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS."  
+It is surely a great criticism of our profession that we have not organised a critical summary by speciality or sub-speciality, up-dated periodically, of all relevant RCTS.  
 ```
@@
 Due to the significant impact of a memory-related outcome such as dementia on exposure recall, case-control studies were excluded, though case-control studies where historical records are used to determine the exposure status were eligible for inclusion.
-Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measured change in continuous cognitive measures (e.g.
-Montreal Cognitive Assessment (MoCA) score) without an attempt to map these scores to ordinal groups (e.g.
-no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
+Cross-sectional studies, qualitative studies, case reports/series and narrative reviews were also excluded, as were studies that measured change in continuous cognitive measures (e.g., Montreal Cognitive Assessment (MoCA) score) without an attempt to map these scores to ordinal groups (e.g., no dementia/dementia).[@tennant2021] Previous systematic reviews were not eligible for inclusion, but their reference lists were screened to identify any potentially relevant articles.
 
-Studies with outcomes not directly related to the clinical syndrome of dementia (e.g., neuroimaging) were excluded.
+Studies with outcomes not directly related to the clinical syndrome of dementia (e.g.,, neuroimaging) were excluded.
 Additionally, studies implementing a "multi-domain intervention" where a lipid-regulating agent is included in each arm were excluded.
@@
 I systematically searched several electronic bibliographic databases to identify potentially relevant entries (hereafter referred to as "records").
-The following databases were searched in June 2019 from inception onwards: MEDLINE, Embase, Psychinfo, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
+The following databases were searched in June 2019 from inception onwards: MEDLINE, Embase, PsychINFO, Cochrane Central Register of Controlled Trials (CENTRAL), and Web of Science Core Collection.
 Given that the contents of the Web of Science Core Collection can vary by institution,[@gusenbauer2020] the specific databases and date ranges for each database searched via this platform are listed in Appendix \@ref(appendix-wos-databases).
@@
 Grey literature was searched via ProQuest, OpenGrey and Web of Science Conference Proceedings Citation Index, and theses were accessed using the Open Access Theses and Dissertations portal.
-In addition, the abstract lists of relevant conferences (e.g.
-the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
+In addition, the abstract lists of relevant conferences (e.g., the proceedings of the Alzheimer's Association International Conference, published in the journal Alzheimer's & Dementia) were searched by hand.
 Finally, the reference lists of included studies were searched by hand, while forward and reverse citation searching ("snowballing") was performed using Google Scholar.[@greenhalgh2005; @wohlin2014]
@@
 (2016).[@bramer2016] In summary, this method uses multiple stages to identify potential duplicates.
-The initial step involves automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), and is followed by manual review of articles with less overlap (e.g.
-those identified as duplicates based on the "Title" field alone).
+The initial step involves automatic deletion of records matching on multiple fields ("Author" + "Year" + "Title" + "Journal"), and is followed by manual review of articles with less overlap (e.g., those identified as duplicates based on the "Title" field alone).
 
@@
 Endnote is a citation management tool,[@hupe2019] and Rayyan is a web-based screening application.[@ouzzani2016] Title and abstract screening to remove obviously irrelevant records was performed, with a random ~10% sample of excluded records being screened in duplicate to ensure consistency with the inclusion criteria.
-Additionally, I re-screened the same ~10% sample with three month lag to assess intra-rater consistency.
+Additionally, I re-screened the same ~10% sample with three-month lag to assess intra-rater consistency.
 
@@
 Inter- and intra-rater reliability during the screening stages were assessed for a 10% sub-sample of records.
-Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e.
-assessment of consistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e.
-assessment of accuracy).
+Intra-rater reliability involved a single reviewer applying the inclusion criteria to the same set of records while blinded to their previous decisions (i.e., assessment of consistency), while inter-rater reliability involved two reviewers independently screening the same set of records (i.e., assessment of accuracy).
 
@@
 
-Interpretion of agreement coefficients is a widely debated topic, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
+Interpretation of agreement coefficients is a widely debated topic, and while arbitrary cut-off values may mislead readers,[@brennan1992] they provide a useful rubric by which to assess inter-rater agreement.
 Here, I used guidelines based on a stricter interpretation of the Cohen's $kappa$ coefficient,[@mchugh2012] presented in Table \@ref(tab:gwet-table).
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated an issue with the screening process (defined as an $AC$ of less than 0.9), it indicated the need for a larger proportion of records to be dual-screened.
+If this assessment demonstrated an issue with the screening process (defined as an $AC$ of less than 0.9), it indicated the need for a larger proportion of records to be dual screened.
 
@@
 
-<!-- COMMENT [Julian] Same analysis or same data? Don't want 2+ analyses of the same data to appear in a meta-analysis (unless orthogonal; e.g. MR + RCT) -->
+<!-- COMMENT [Julian] Same analysis or same data? Don't want 2+ analyses of the same data to appear in a meta-analysis (unless orthogonal; e.g., MR + RCT) -->
 <!-- QUESTION Why does being orthogonal make it okay? And the Three City Study is likely to be included several times -->
@@
 
-In line with best practice, where summary data was presented across two groups (e.g.
-age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
+In line with best practice, where summary data was presented across two groups (e.g., age at baseline stratified by hypercholesterolemia status), the following approach was used to combine the groups:[@higgins2019]
 
@@
 Where individual studies were deemed comparable, they were incorporated into a quantitative analysis or "meta-analysis".
-Results were not combined across different study designs (i.e.
-RCTs were not combined in a meta-analysis with results from observational studies).
-The summary effect estimates produced across individual study designs are discussed, but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(tri-heading).
+Results were not combined across different study designs (i.e., RCTs were not combined in a meta-analysis with results from observational studies).
+The summary effect estimates produced across individual study designs are discussed but are compared and contrasted more fully as part of the triangulation exercise presented in Chapter \@ref(tri-heading).
 Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).
@@
 
-Several of the included studies presented data on multiple categories of lipid levels, but provided an overall effect estimate based on a comparison of only two of these categories (e.g.
-for example, highest vs lowest quartile).
-While this allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
+Several of the included studies presented data on multiple categories of lipid levels in addition to an overall effect estimate based on a comparison of only two of these categories (e.g., for example, highest vs lowest quartile).
+While this two-category comparison allows for easy interpretation of the resulting effect estimate, it ignores any potential non-linear relationships between the exposure and outcome, in addition to discarding useful information contained in the interim groups.
 In order to address this limitation, I performed a dose-response meta-analysis in those studies reporting more than two categories of lipid levels.
@@
 Studies were excluded from this analysis if the number of categories was less than three or if the necessary information for synthesis (cut-off points, number of participants and number of events per category) was not available.
-When the highest reported category was open ended (e.g LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
+When the highest reported category was open ended (e.g., LDL-c $\geqslant$ 200 mg/dL), I calculated the category midpoint by assuming the width of the highest category was the same as the one immediately below it.
 Similarly, when the lowest category was open-ended (e.g LDL-c $\leqslant$ 100 mg/dL), I set the lower boundary for this category to zero (though this is unlikely to occur naturally).
@@
 This tool was developed as an adjunct to this thesis,[@mcguinness2020robvisPaper] and summary of its functionality can be found in Appendix \@ref(appendix-robvis).
-Unless otherwise stated in the figure, only a single effect measure (hazard ratio/odds ratio/etc) is represented in a given forest plot.
+Unless otherwise stated in the figure, only a single effect measure (hazard ratio/odds ratio/etc.) is represented in a given forest plot.
 
@@
 
-Finally, I performed a follow-up analysis, allowing for a a two-year lag, to investigate whether included preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provided a distinct evidence source to conventional bibliographic databases).
+Finally, I performed a follow-up analysis, allowing for a two-year lag, to investigate whether included preprints had been subsequently published (in which case preprints provided a snapshot into the future, and a systematic review update would capture the published version of the preprint) or not (in which case preprints provided a distinct evidence source to conventional bibliographic databases).
 

### 2021-12-16 04-Chp-Systematic-Review-Results.Rmd
End of day:

@@
 To ensure the accuracy of the study design filters, a random sample of 500 records removed by the filters were screened, and no eligible records were identified.
-As expected, many of those excluded by the filters were commentaries/educational articles, or described basic science studies.
+As expected, many of those excluded by the filters were commentaries/educational articles or described basic science studies.
 
@@
 
-Common reasons for exclusion at the full-text stage included studies reporting on ineligible exposures (Number of records (N) = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g.
-change in cognitive scores), or the use of an ineligible study design (N = `r n_study_design`).
+Common reasons for exclusion at the full-text stage included studies reporting on ineligible exposures (Number of records (N) = `r n_wrong_exposure` ; most commonly an ineligible lipid fraction) or outcomes (N = `r n_wrong_outcome`; e.g., change in cognitive scores), or the use of an ineligible study design (N = `r n_study_design`).
 
@@
 
-For the assessment of the intra-/inter-rater reliability, the estimated values of Gwet's agreement coefficinet, $AC1$, were interpreted against the categories presented in Table \@ref(tab:gwet-table).
+For the assessment of the intra-/inter-rater reliability, the estimated values of Gwet's agreement coefficient, $AC1$, were interpreted against the categories presented in Table \@ref(tab:gwet-table).
 For the inter-rater reliability, agreement was "almost perfect" ($AC1$ = `r agreeInter_coeff[1]`, $kappa$ = `r agreeInter_coeff[2]`, Table \@ref(tab:agreeInter-table)).
@@
 (ref:agreeInter-caption) __Inter-rater agreement__ - For a subset of records, the decisions between two independent reviewers were compared.
-Gewt's $AC1$ was calculated from this data to assess inter-rater reliability, indicating high accuracy ($AC1$ = `r agreeInter_coeff[1]`).
+Gwet's $AC1$ was calculated from this data to assess inter-rater reliability, indicating high accuracy ($AC1$ = `r agreeInter_coeff[1]`).
 
@@
 
-Those records which were excluded in the initial screening, but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+Those records which were excluded in the initial screening but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and of eligible lipids fractions.
@@
 <!----------------------------------------------------------------------------->
-(ref:agreeIntra-caption) __Intra-rater agreement__ - For a subset of records, the decisions between the same reviewer with 3 month lag were compared.
-Gewt's $AC1$ was calculated from this data to assess intra-rater reliability, indicating high consistency ($AC1$ = `r agreeIntra_coeff[1]`).
+(ref:agreeIntra-caption) __Intra-rater agreement__ - For a subset of records, the decisions between the same reviewer with three-month lag were compared.
+Gwet's $AC1$ was calculated from this data to assess intra-rater reliability, indicating high consistency ($AC1$ = `r agreeIntra_coeff[1]`).
 
@@
 A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS).
-This leads to complications in the synthesis of these estimates due to the potential for double-counting (see Section \@ref(sys-rev-res-AD)).
+This leads to complications in the synthesis of these estimates due to the potential for double counting (see Section \@ref(sys-rev-res-AD)).
 
@@
 In terms of outcomes, the vast majority of studies examined either all-cause dementia (`r n_Dementia`) or Alzheimer's disease (`r n_AD`), with only a small proportion examining vascular dementia (`r n_VaD`).
-Some other outcome classifications such as vascular-component or mixed dementia were also investigated, but were much rarer.
+Some other outcome classifications such as vascular-component or mixed dementia were also investigated but were much rarer.
 
@@
 Note that three studies reported on multiple analytical designs within a single study report (Beydoun 2011,[@beydoun2011] Reitz 2010,[@reitz2010] and Benn 2017[@benn2017]), and these have been duplicated across the relevant sub-sections.
-Preprinted studies are denoted using an asterik.
+Preprinted studies are denoted using an asterisk.
 
@@
 Several studies did not report baseline characteristics such as the proportion of women in the study cohort.
-Additionally, some omitted important details on reported characteristics (e.g.
-the study reported the mean but not the standard deviation of baseline age).
+Additionally, some omitted important details on reported characteristics (e.g., the study reported the mean but not the standard deviation of baseline age).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsHyperAD-cap) __Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease__ - Non-randomised studies examining the association of hypercholesterolemia with Alheimer's disease were synthesised using a random-effects meta-analysis.
+(ref:obsHyperAD-cap) __Random-effects meta-analysis of hypercholesterolemia on Alzheimer's disease__ - Non-randomised studies examining the association of hypercholesterolemia with Alzheimer's disease were synthesised using a random-effects meta-analysis.
 Subgroup estimates, stratified by overall risk-of-bias level, are also presented.
@@
 In contrast, many of the non-randomised studies of statin use were at serious risk of bias primarily due to poor controlling for confounding, immortal time bias, and missing outcome data.
-Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g.
-examination of lipids as a binary or continuous variable).
-Finally, bias was introduced into Mendelian randomisation studies via the potential for hoziontal pleiotropy and population stratification.[@davies2018]
+Similarly, non-randomised studies of exposures suffered from incomplete adjustment for potentially important confounders, and concerns over the selection of the reported result from among several analyses (e.g., examination of lipids as a binary or continuous variable).
+Finally, bias was introduced into Mendelian randomisation studies via the potential for horizontal pleiotropy and population stratification.[@davies2018]
 
-Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analysis.[@sterne2016] `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e.
-the study reported unadjusted estimates).`r critical_citations`
+Following best practice, any result judged to be at critical risk of bias should be excluded from any quantitative analysis.[@sterne2016] `r num_to_text(n_critical,T)` observational studies were excluded on this basis, predominantly due to a lack of adjustment for any potentially important confounders (i.e., the study reported unadjusted estimates).`r critical_citations`
 
@@
 
-The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLCC and IGAP.
+The other two preprints identified[@andrews2019; @zhu2017] reported on the effect of LDL-c on Alzheimer's disease using data from GLGC and IGAP.
 As illustrated in Figure \@ref(fig:mrDuplication), these consortia were previously analysed in several published reports, and so these preprints did not add new information to the evidence base.
@@
 For one of the three preprints identified, the published version of the preprint was captured by the main search.
-Investigation of the publication status of the two unpublished preprints found that, allowing for a two-year lag (i.e.
-up to July 2021), only one had been subsequently published.[@andrews2019; @andrews2021]
+Investigation of the publication status of the two unpublished preprints found that, allowing for a two-year lag (i.e., up to July 2021), only one had been subsequently published.[@andrews2019; @andrews2021]
 
@@
 This finding was not supported by evidence from the two available RCTs, or by studies that emulated statin treatment using a genetic proxy.
-This suggests that these findings may be a result of differing exposure windows (e.g.
-mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
+This suggests that these findings may be a result of differing exposure windows (e.g., mid-life lipid lowering in non-randomised studies versus life-course lipid exposure in Mendelian randomisation studies and late-life lipid reduction in RCTs) or alternatively due to biases within the non-randomised studies.
 
@@
 In many cases, estimates were known to be missing from meta-analyses due to preferential reporting of significant results, leading to high risk of bias due to missing evidence.
-These missing estimates were most commonly identified through differing descriptions of the same analysis in conference abstract versus the final publication.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g.
-"The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
+These missing estimates were most commonly identified through differing descriptions of the same analysis in conference abstract versus the final publication.[@yamada2009conf; @yamada2009] In addition, some authors stated outright that non-significant results were not reported (e.g., "The other lipid variables not significantly associated with dementia and Alzheimer’s disease ...
 were not reported in the table.").[@ancelin2013] However, as all identified missing results are likely to be non-significant, they would not be expected to have a substantial impact on their respective meta-analyses (which provided weak evidence of an effect of lipid levels on dementia outcomes) beyond increasing the precision of the summary estimate.
@@
 While conducting this review, I identified several previous systematic reviews of this topic.[@chu2018; @yang2020; @muangpaisan2010; @poly2020; @kuzma2018risk] However, to my knowledge, this review is the first to use established domain-based assessment tools (for example, the RoB 2 tool for randomised controlled trials)[@sterne2019] to assess the risk of bias in included studies.
-The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or use a non-domain-based assessment tool (e.g.
-the Newcastle-Ottowa Scale).[@poly2020]
+The majority of the highly cited reviews on this topic either do not formally consider risk of bias in the observational studies they include,[@chu2018;@power2015] or use a non-domain-based assessment tool (e.g., the Newcastle-Ottowa Scale).[@poly2020]
 
@@
 
-(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (1) _relevance_ - the genetic variant associates with the risk factor of interest; (2) _independence_ - the variant-exposure association has no unmeasured confounders; and (3) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e.
-there is no horizontal pleiotropy).
+(ref:mrAssumptions-cap) __Summary of the assumptions in Mendelian randomisation analyses__ - Mendelian randomisation analyses make three key assumptions: (1) _relevance_ - the genetic variant associates with the risk factor of interest; (2) _independence_ - the variant-exposure association has no unmeasured confounders; and (3) _exclusion restriction_ - variants affect the outcome only through their effect on the risk factor of interest (i.e., there is no horizontal pleiotropy).
 
@@
 Studies examining multiple risk factors such as this can introduce bias into a systematic review, as it is commonly only those risk factors with a statistically significant result that are reported in the abstract and so are captured by a systematic search.
-These studies are described as "unknown unknown's" in the context of the RoB-ME tool, and are considered to be particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
+These studies are described as "unknown unknown's" in the context of the RoB-ME tool and are considered to be particularly challenging (as opposed to an analysis that was insufficiently reported to be included in the statistical analysis, or the "known unknown's").
 
-In better-resourced reviews, a broader search (e.g.
-"risk factor" AND "dementia" AND "Mendelian randomisation") followed by manual review of studies that examined multiple risk factors would be advisable.
+In better-resourced reviews, a broader search (e.g., "risk factor" AND "dementia" AND "Mendelian randomisation") followed by manual review of studies that examined multiple risk factors would be advisable.
 This was not feasible in the context of this review, given the large number of records to be screened even when using study design filters (N = `r comma(16109)`).
@@
 
-Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into a evidence synthesis exercise, using a trial of mindfulness interventions as a case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
+Based on my experience of extracting data for this review, I co-authored a guidance article to aid primary prevention scientists in preparing and sharing their data so that it can easily be incorporated into an evidence synthesis exercise, using a trial of mindfulness interventions as a case study.[@hennessy2021] A copy of this publication is available in Appendix \@ref(published-papers).
 In an attempt to apply my own guidance, I have invested a substantial amount of time and effort into making the data obtained by this review openly available to other researchers, via a GitHub repository.
@@
 While several reviews of this research topic exist,[@chu2018; @yang2020; @muangpaisan2010; @poly2020] the overlap between the list of studies included in each is not complete.
-As part of this review, I have not only performed an original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no relevant study has been omitted.
+As part of this review, I have not only performed an original search of primary literature databases but have also screened the reference lists of comparable reviews to ensure no relevant study has been omitted.
 
@@
 However, there is no published empirical evidence supporting the need for signaling questions.
-Additionally, a previous assessment of inter-rater reliability in domain-bases risk-of-bias tools found that, even with the use of signaling questions, reviewers assessment of bias can vary substantially.[@jeyaraman2020]
+Additionally, a previous assessment of inter-rater reliability in domain-bases risk-of-bias tools found that, even with the use of signaling questions, reviewers' assessment of bias can vary substantially.[@jeyaraman2020]
 

### 2021-12-16 05-Chp-CPRD-Analysis.Rmd
End of day:

@@
 Little evidence for an effect of lipid-regulating agents on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
-In contrast, I found an increased risk of vascular and other (i.e.
-non-Alzheimer's) dementia was associated with lipid-regulating agent use.
+In contrast, I found an increased risk of vascular and other (i.e., non-Alzheimer's) dementia was associated with lipid-regulating agent use.
 
@@
 
-This increased risk in outcomes with a vascular element (e.g.
-vascular dementia) is unexpected, and is very likely to be due to the presence of bias in my analysis.
+This increased risk in outcomes with a vascular element (e.g., vascular dementia) is unexpected and is very likely to be due to the presence of bias in my analysis.
 This bias, called "confounding by indication", is caused when those who are prescribed a statin are more at risk of vascular dementia for a range of reasons, which makes it appear as if statins are harmful.
@@
 
-Previously known as the General Practice Research Database, the Clinical Practice Research Datalink (CPRD) is a large population-based EHR database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the records of more than 10 million primary care patients in England, and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
+Previously known as the General Practice Research Database, the Clinical Practice Research Datalink (CPRD) is a large population-based EHR database.[@herrett2015] The database has been collecting primary care data from participating practices across England since 1987.[@williams2012; @wood2001revitalizing] It contains the records of more than 10 million primary care patients in England and is broadly representative of the UK population in terms of age, sex and ethnicity.[@herrett2015; @mathur2014]
 
 To avoid the ambiguity of interpreting free-text clinical notes and to allow for easy analysis of the resulting data, the CPRD primarily collects data using a predefined coding system known as Read codes.[@booth1994] All clinical events, including  test results and diagnoses, can be identified by a specific Read code.
-The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g.
-Eu...
-- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g.
-Eu001 - Dementia in Alzheimer's disease with late onset).
+The codes use a nested approach (see Table \@ref(tab:readExample-table)), with the initial characters defining broad diagnostic topics (e.g., Eu...
+- Mental and behavioural disorders), while subsequent characters provide additional information on the specific condition diagnosed (e.g., Eu001 - Dementia in Alzheimer's disease with late onset).
 
@@
 * a Read code for prescription of a lipid-regulating agent (such as statins); 
-* a total cholesterol test result of >4 mmol/L; 
+* a total cholesterol test result of >4 mmol/L; or
 * an LDL-c test result of >2 mmol/L.
@@
 * end of follow-up (29 February 2016);
-* last registration date with their GP practice;
+* last registration date with their GP practice; or
 * the last CPRD collection date for their practice.
 
-Participants were ineligible for the cohort if they were less than 40 years of age (because these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficultly of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e.
-had less than one full day of follow-up).
+Participants were ineligible for the cohort if they were less than 40 years of age (because these patients are less likely to be prescribed a LRA), had less than 12 months of "research quality" data, were simultaneously prescribed more than one lipid-regulating agent (due to the difficultly of assigning these to a single exposure group), or were diagnosed with an outcome of interest before or on the date of the index event (i.e., had less than one full day of follow-up).
 
@@
 
-A participants drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
+A participant's drug class was assigned based on their first recorded prescription, and any drug switching was ignored in an effort to mimic an intention-to-treat approach.
 I did however examine how often the initial drug class altered according to one of three criteria:
@@
 
-Missing data was only considered problematic for variables where a numerical test result was expected (e.g.
-BMI), or where a code existed for the absence of the condition (e.g.
-categorical smoking status).
-This approach was necessary because absence of a code for other treatments or conditions (e.g.
-statin use or dementia) was assumed to indicate absence of the treatment/condition rather than being considered missing.[@wells2013strategies]
+Missing data was only considered problematic for variables where a numerical test result was expected (e.g., BMI), or where a code existed for the absence of the condition (e.g., categorical smoking status).
+This approach was necessary because absence of a code for other treatments or conditions (e.g., statin use or dementia) was assumed to indicate absence of the treatment/condition rather than being considered missing.[@wells2013strategies]
 
@@
 * $h(t)$ is the hazard function;
-* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate.; and
+* $x_1,x_2,...,x_p$ are the covariates which determine the hazard function, while $b_1,b_2,...,b_p$ are the coefficients for each covariate; and
 * $h_o(t)$ is the baseline hazard - when all $x_i$ are zero, the $exp()$ function resolves to 1.
@@
 Immortal time bias describes two distinct but related types of bias, considered here in relation to statin use (Figure \@ref(fig:immortalTimeBias)).
-The first presentation, the selection bias aspect (Panel A), occurs when time prior to statin initiation is excluded leading to the statin and control groups being followed up from different time points.[@levesque2010] The unexposed group are followed from the date of an index event (e.g.
-diagnosis of hypercholesterolemia), while the statin group is followed from date of a statin initiation.
+The first presentation, the selection bias aspect (Panel A), occurs when time prior to statin initiation is excluded leading to the statin and control groups being followed up from different time points.[@levesque2010] The unexposed group are followed from the date of an index event (e.g., diagnosis of hypercholesterolemia), while the statin group is followed from date of a statin initiation.
 In this scenario, the time between the index event and statin initiation is missing, and any events that occur in the exposed group prior to the prescription will be inappropriately excluded from the analysis.
@@
 Patients start in the unexposed group and contribute time-at-risk until they are prescribed a lipid-regulating agent, at which point they move into the exposed group.
-Note, patients for whom prescription of a lipid-regulating agent was the index event only contribute time to the exposed group (i.e.
-they enter the cohort and move into the exposed group on the same day).
+Note, patients for whom prescription of a lipid-regulating agent was the index event only contribute time to the exposed group (i.e., they enter the cohort and move into the exposed group on the same day).
 
@@
 To observe the effect of adjusting for additional covariates, I ran two additional models unadjusted except for: (a) age; and (b) age and gender.
-The results of these models was then compared the results with the fully adjusted model.
+The results of these models were then compared the results with the fully adjusted model.
 
@@
 
-My results show litte evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared to no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
+My results show little evidence was found for an effect of lipid-regulating agents on probable (`r probad_text`) and possible (`r possad_text`) Alzheimer's disease when compared to no treatment, with the sole exception of fibrates on probable Alzheimer's disease (`r probad_fib_text`).
 
@@
 In almost all cases, the use of imputed data resulted in a marginal attenuation of the effects observed when using a complete case analysis.
-It should be noted that due to the large amount of missing data (e.g.
-`r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
+It should be noted that due to the large amount of missing data (e.g., `r ldltext` were missing a baseline LDL cholesterol measure), the number of participants included in the complete case analysis was substantially smaller than that included when using imputed data.
 In this case, though the overall position of the effect estimates does not change substantially when using the imputed dataset, there is a noticeable gain in power.[@sterne2009]
@@
 
-Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment, but were associated with increased risk of an all-cause dementia, vascular dementia and other dementias diagnoses.
+Lipid-regulating agents showed little evidence of an association with probable and possible Alzheimer's disease when compared to no treatment but were associated with increased risk of the all-cause dementia, vascular dementia and other dementias diagnoses.
 The estimate observed in each case was driven by the effects observed in the statin subgroup because a substantial majority of participants prescribed an LRA were prescribed a statin.
 For the other drug classes, no association was found with any outcome, with two exceptions.
-Ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increase risk of all-cause dementia and probable Alzheimer's disease.
+Ezetimibe was associated with increased risk of vascular and other dementias, while fibrates were associated with increased risk of all-cause dementia and probable Alzheimer's disease.
 
@@
 <!----------------------------------------------------------------------------->
-(ref:smeethComparison-cap) __Comparison of codelists__ - Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right hand side of the figure).
+(ref:smeethComparison-cap) __Comparison of code lists__ - Sankey diagram comparing the codes used in this analysis with those used in the Smeeth _et al_ paper.[@smeeth2009] The outcomes and number of codes contributing to each are presented (the Smeeth _et al_ outcomes are on the right-hand side of the figure).
 The joining lines showing the overlap between the categories in the two analyses.
 
-(ref:smeethComparison-scap) Comparison of codelists
+(ref:smeethComparison-scap) Comparison of code lists
 
@@
 
-This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest in EHR, particularly if they are used to define competing outcomes (e.g.
-AD vs non-AD dementia).
+This analysis serves to illustrative the importance of the code lists chosen to define the outcomes of interest in EHR, particularly if they are used to define competing outcomes (e.g., AD vs non-AD dementia).
 The different codes used by Smeeth _et al._, in addition to an analytical approach that adjusted for covariates defined after the index date, may go some way to explaining why my analysis obtained different results despite the substantial overlap in the data sources used.
@@
 However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.
-In all cases, the estimated associations for the "any LRA" analyses were driven by those those observed in the large statin subgroup.
+In all cases, the estimated associations for the "any LRA" analyses were driven by those observed in the large statin subgroup.
 

### 2021-12-16 06-Chp-IPD-Analysis.Rmd
End of day:

@@
 
-As such, the aims of this analysis are two fold.
+As such, the aims of this analysis are two-fold.
 Firstly, I plan to perform an IPD meta-analysis across identified cohorts to examine the impact of participant age-at-measurement and sex on the relationship between lipids and dementia risk.
@@
 Eligible data sources for this analysis were prospective cohort studies (see Section \@ref(ipd-apply-access) for details on how these studies were identified).
-Data sources which were cross-sectional, either by design or due to the available data (e.g.
-a study recorded data on participants at multiple time-points or "waves", but only data from a single wave could be accessed) were excluded.
+Data sources which were cross-sectional, either by design or due to the available data (e.g., a study recorded data on participants at multiple time-points or "waves", but only data from a single wave could be accessed) were excluded.
 Similarly, due to the time and cost restraints within the scope of my thesis project, studies making use of population-level electronic health records were ineligible.
@@
 I considered four blood lipid fractions as part of this analysis, namely: total cholesterol (TC), low-density lipoprotein cholesterol (LDL-c), high-density lipoprotein cholesterol (HDL-c) and triglycerides (TG).
-Cohorts were eligible for inclusion if they contained data on at least one of these lipid fractions,  recorded as a continuous variable (i.e.
-studies with binary "hypercholesteromemia" would be excluded).
+Cohorts were eligible for inclusion if they contained data on at least one of these lipid fractions,  recorded as a continuous variable (i.e., studies with binary "hypercholesterolemia" exposure would be excluded).
 
@@
 
-The second approach focused on incorporating relevant, previously-unanalysed data into the analysis, thus providing additional evidence on the relationship between blood lipids and dementia risk.
+The second approach focused on incorporating relevant, previously unanalysed data into the analysis, thus providing additional evidence on the relationship between blood lipids and dementia risk.
 This was achieved through the Dementia Platform UK (DPUK), a collaborative grouping of existing dementia cohorts established by the Medical Research Council which works with data owners to make their data readily accessible for secondary analysis.[@bauermeister2020] It provides access to 42 cohorts with over 3 million participants, and makes use of a central streamlined application process for all cohorts, with the intent of making it easier to access data from existing data sources.
@@
 
-(ref:cohortFlowchart-cap) __Flowchart detailing sources of data for the IPD analysis__ The number of cohorts approached and the reasons for exclusion are stratified by identification method (systematic review vs DPUK).
+(ref:cohortFlowchart-cap) __Flowchart detailing sources of data for the IPD analysis__ - The number of cohorts approached and the reasons for exclusion are stratified by identification method (systematic review vs DPUK).
 
@@
 
-<!-- TODO Be clear on the different types of databases, e.g. those where users are followed up regularly vs. those where participants are captured via EHR-->
+<!-- TODO Be clear on the different types of databases, e.g., those where users are followed up regularly vs. those where participants are captured via EHR-->
 
@@
 
-The Caerphilly Prospective Study (CaPS) is a longitudinal study of men in South Wales, UK.[@zotero-15398;@elwood2013] Blood lipids (TC, LDL-c, HDL-c and TG) were measured at baseline in 1979-1983, and from Phase III (1989-1993) onwards, a battery of cognitive tests were introduced.
+The Caerphilly Prospective Study (CaPS) is a longitudinal study of men in South Wales, UK.[@zotero-15398;@elwood2013] Blood lipids (TC, LDL-c, HDL-c and TG) were measured at baseline in 1979-1983, and from Phase III (1989-1993) onwards, a battery of cognitive tests was introduced.
 Dementia outcomes were determined using data obtained during Phase V (2002-2004), giving between 19-25 years of follow-up.
@@
 
-The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] Lipids measurements were available from the third wave of the study, conducted between 1991-1993.
+The Whitehall II study is a prospective cohort study of men and women recruited between 1985 and 1989 from the civil service in London.[@marmot2005] Lipid measurements were available from the third wave of the study, conducted between 1991-1993.
 The cohort is linked with the Hospital Episode Statistics (HES) database, a database containing details of participant events at NHS hospitals in England.
@@
 Based on available data across cohorts, smoking was classified as never/ever/current, while alcohol consumption was classified as never/ever.
-Ever use in this case refers to participants who do not currently smoke/drink alcohol, but did so in the past.
+Ever use in this case refers to participants who do not currently smoke/drink alcohol but did so in the past.
 Education was categorised into 4 levels (None, O-levels, A-levels, Degree).
@@
 A key consideration in the definition of covariates across cohorts was the classification of age.
-The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age bands (e.g.
-40-44, 45-49, etc.).
+The Whitehall II study, the largest cohort to which I had access, only shared age data in five-year age bands (e.g., 40-44, 45-49, etc.).
 To ensure comparability across the cohorts, I created identical categories in the CaPS and EPIC data.
@@
 For the consideration of vascular dementia, I was only able to explore the effect of age, as only the CaPS and Whitehall cohorts contained details on vascular dementia as an outcome.
-As discussed above, the CaPS data contained a single sex excluding it from a exposure-sex analysis, leaving Whitehall II as the sole eligible study.
+As discussed above, the CaPS data contained a single sex which meant it was excluded from the exposure-sex analysis, leaving Whitehall II as the sole eligible study.
 
@@
 No evidence for an effect of lipids on the risk of dementia or related outcomes was identified, except for a harmful association of raised triglycerides with risk of vascular dementia.
-Similarly, there was weak evidence for an interaction of the effect of lipid levels on dementia outcomes with participants' age (grouped into 5 year bands) or sex.
+Similarly, there was weak evidence for an interaction of the effect of lipid levels on dementia outcomes with participants' age (grouped into 5-year bands) or sex.
 
@@
 In light of this, a centralised database of ongoing analyses being performed using DPUK data would be of enormous help, reducing research waste and providing opportunities for collaboration.
-Finally, the DPUK process would be aided by a clearer distinction between those cohorts that are "DPUK native" (i.e.
-where a copy of the data is already held on DPUK servers) versus externally hosted, seeing as the response time for externally hosted cohorts is likely to be much longer.
+Finally, the DPUK process would be aided by a clearer distinction between those cohorts that are "DPUK native" (i.e., where a copy of the data is already held on DPUK servers) versus externally hosted, seeing as the response time for externally hosted cohorts is likely to be much longer.
 
@@
 Finally, this analysis provides new evidence on a previously unexplored outcome (vascular dementia), adding to the extremely small evidence base for this outcome identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-This is relevant even in the previously analysed WhiteHall II cohort because the previous analysis by Tynkkynen _et al._ did not report on this outcome.
+This is relevant even in the previously analysed Whitehall II cohort because the previous analysis by Tynkkynen _et al._ did not report on this outcome.
 
@@
 Data harmonization between cohorts in an IPD analysis is an often under-appreciated challenge,[@levis2021] and in line with this, data cleaning for this analysis took substantially longer than expected.
-While the cohort response rate was substantially lower that expected, given the time and resources required for the cleaning and harmonisation of data from just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of a PhD.
+While the cohort response rate was substantially lower than expected, given the time and resources required for the cleaning and harmonisation of data from just three cohorts, a situation in which all 37 cohorts responded positively would have been logistically challenging within the scope of a PhD.
 
@@
 
-- I discussed potential reasons for the low response rate, and explored other limitations of this analysis.
+- I discussed potential reasons for the low response rate and explored other limitations of this analysis.
 I highlighted the contribution of this work to the wider topic via the analysis of previously unexplored cohorts (CaPS & EPIC) and outcomes (vascular dementia).

### 2021-12-16 07-Chp-Triangulation.Rmd
End of day:

@@
 
-This approach represents a significant step forward from the current practice of synthesising evidence from only one type of study (e.g.
-randomised controlled trials (RCTs), non-randomised studies of exposures (NRSE) or interventions (NRSI)).
+This approach represents a significant step forward from the current practice of synthesising evidence from only one type of study (e.g., randomised controlled trials (RCTs), non-randomised studies of exposures (NRSE) or interventions (NRSI)).
 The most common implementation of this method to date has been in the form of _qualitative triangulation_ - that is the identification and narrative comparison of diverse evidence sources with respect to their underlying bias structures.[@lawlor2016]
@@
 There is a need to include all evidence to avoid potential confirmation bias,[@dubroff2018] yet as the number of evidence sources increases, it is not possible to narratively compare and contrast across multiple results in any meaningful way.
-This fact is illustrated by previous exemplars of triangulation only considering a small number of individual results.[@ference2014; @lawlor2016] To overcome this limitation, some attempts have considered the output of a meta-analysis of similarly-designed studies to be a single source of evidence, and have assessed bias in relation to this summary result.
+This fact is illustrated by previous exemplars of triangulation only considering a small number of individual results.[@ference2014; @lawlor2016] To overcome this limitation, some attempts have considered the output of a meta-analysis of similarly designed studies to be a single source of evidence, and have assessed bias in relation to this summary result.
 While this approach keeps the number of individual sources of evidence manageable, it loses useful information on the specific biases inherent to each result contributing to the summary estimate.
@@
 
-Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (TC - `r obsLipids$AD_TC$estimate`; LDL - `r obsLipids$AD_LDL$estimate`; HDL - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`).
+Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (in the systematic review: TC - `r obsLipids$AD_TC$estimate`; LDL - `r obsLipids$AD_LDL$estimate`; HDL - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`).
 Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`).
@@
 Finally, only one of the three cohorts included in the IPD analysis (Whitehall II) contained data on Alzheimer's disease.
-However, a previously published analysis (Tynkkynen _et al._[@tynkkynen2018]) examining the association of lipid levels with Alzheimer's disease in this cohort was identified by the systenatic review.
+However, a previously published analysis (Tynkkynen _et al._[@tynkkynen2018]) examining the association of lipid levels with Alzheimer's disease in this cohort was identified by the systematic review.
 The results of this previous analysis are incorporated into the results of the meta-analysis reported above, and so the IPD analysis provided no new information on this outcome.
@@
 Secondly, given the long prodromal period between the onset of physiological changes in the brain and presentation of dementia symptoms, it seems likely that conditions during the mid-life period are particularly important.
-Finally, examining the causal impact of a lipid fraction on a specific outcome (e.g.
-Alzheimer's disease), rather than a composite outcome (e.g.
-all-cause dementia), focuses on an single causal pathway rather than including several conditions in the outcome definition that likely have very different mechanisms of disease.
+Finally, examining the causal impact of a lipid fraction on a specific outcome (e.g., Alzheimer's disease), rather than a composite outcome (e.g., all-cause dementia), focuses on a single causal pathway rather than including several conditions in the outcome definition that likely have very different mechanisms of disease.
 In addition, previous work presented in this thesis illustrated that the component conditions (in this case Alzheimer's disease and vascular dementia) are likely to be subject to very different confounding structures (see Section \@ref(cprd-confounding-by-ind)), and the use of a composite all-cause outcome in the triangulation framework may mask this.
@@
 Once the causal question of interest had been defined, relevant individual results were obtained from the data sources described in Section \@ref(tri-data-sources).
-In a broad sense, this meant extracting results that examined the relationship between the exposure/outcome pair, either directly (e.g.
-non-randomised studies of LDL-c levels) or indirectly (e.g.
-non-randomised studies of statins, or MR studies using genetic instruments for LDL-c levels).
+In a broad sense, this meant extracting results that examined the relationship between the exposure/outcome pair, either directly (e.g., non-randomised studies of LDL-c levels) or indirectly (e.g., non-randomised studies of statins, or MR studies using genetic instruments for LDL-c levels).
 
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:robLevelsMapping-caption) __Mapping of risk-of-bias judgements across assessment tools__ The different acceptable levels of bias across the risk-of-bias assessment tools used were mapped to a harmonised set.
+(ref:robLevelsMapping-caption) __Mapping of risk-of-bias judgements across assessment tools__ - The different acceptable levels of bias across the risk-of-bias assessment tools used were mapped to a harmonised set.
 Note that no mapping for "Critical" risk of bias was performed, as best practice recommends that studies at critical risk of bias are excluded from quantitative syntheses.
@@
 
-<!-- QUESTION text -->
-
 * "Favours experimental"/"Favours comparator" (defines an additive bias)
@@
 
-<!-- TODO Need to include some text here on examples of each: e.g. immortal time bias, or  -->
+<!-- TODO Need to include some text here on examples of each: e.g., immortal time bias, or  -->
 
@@
 
-One key feature of the domain-based risk-of-bias tools is that the domains are considered interchangeable - i.e.
-a "high" judgement in one domain is equivalent to a "high" judgement in any other.
+One key feature of the domain-based risk-of-bias tools is that the domains are considered interchangeable - i.e., a "high" judgement in one domain is equivalent to a "high" judgement in any other.
 As such, for this analysis, I assumed that the distributions assigned to each extent of bias were identical across all values of $j$, that is, were identical for all domains in the risk-of-bias assessment tool.
@@
 For additive biases, two scenarios were defined (see main text).
-Note that proportional biases are defined on the log scale for ease of calculation, but are exponentiated prior to their use for adjustment.
+Note that proportional biases are defined on the log scale for ease of calculation but are exponentiated prior to their use for adjustment (see Equations \@ref(eq:prop-total-mean) & \@ref(eq:prop-total-var) below).
 
@@
 
-Where the direction of bias in a domain was unpredictable for a given result, the mean of the prior distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained (e.g.
-for an unpredictable "High" additive bias, the distribution would be $N(0,0.1)$ under Scenario 1).
+Where the direction of bias in a domain was unpredictable for a given result, the mean of the prior distribution for that domain was set to 0 but the appropriate variance for the recorded extent of bias was retained (e.g., for an unpredictable "High" additive bias, the distribution would be $N(0,0.1)$ under Scenario 1).
 In other words, adjusting for bias in a domain with an unpredictable direction of bias has no impact on the position of the effect estimate but does increase the uncertainty around it.
@@
 Under the  method reported in Turner _et al._,[@turner2009], total additive bias (denoted using subscript $\delta$) in result $i$ is then described by mean $\mu_{i\delta}$ and variance $\sigma_{i\delta}^{2}$, which are simply the sum of the mean and variance of all additive biases in the $i$th result.
-Similarly, the total proportional bias (denoted using subsript $\beta$) in the $i$th result is described by mean $\mu_{i\beta}$ and variance ${\sigma_{i\beta}}^2$.
+Similarly, the total proportional bias (denoted using subscript $\beta$) in the $i$th result is described by mean $\mu_{i\beta}$ and variance ${\sigma_{i\beta}}^2$.
 This are defined as
@@
 
-where $\alpha_i$ and ${\psi_i}^2$  are the the sum of mean and variance values for all proportional biases in the $i$th result.
+where $\alpha_i$ and ${\psi_i}^2$  are the sum of mean and variance values for all proportional biases in the $i$th result.
 
@@
 
-Using the the method reported in Turner _et al._,[@turner2009] once total additive and proportional bias and indirectness are calculated, they are used to define an adjusted estimate for each result included in the synthesis.
+Using the method reported in Turner _et al._,[@turner2009] once total additive and proportional bias and indirectness are calculated, they are used to define an adjusted estimate for each result included in the synthesis.
 
@@
 
-<!-- REVIEW YBS - I may have got confused but when you say favour the intervention I am assuming you mean a “protective effect” e.g.
-OR <1.
-But if there is differential misclassification so that statin use increases diagnosis of vascular dementia that would show a deleterious effect under the null hence shift to right e.g.
-OR >1.
+<!-- REVIEW YBS - I may have got confused but when you say favour the intervention I am assuming you mean a “protective effect” e.g., OR <1.
+But if there is differential misclassification so that statin use increases diagnosis of vascular dementia that would show a deleterious effect under the null hence shift to right e.g., OR >1.
 Perhaps I have misunderstood favour as < risk when in fact you mean > risk.
@@
 From the data sources identified in Section \@ref(tri-data-sources), I identified 7 results relevant to the causal effect of triglycerides at midlife on vascular dementia.
-Four were identified via the systematic review,`r tg_vad_citations` while Chapter \@ref(cprd-analysis-heading) provided two additional estimates from unanalysed datasets (CaPS and Whitehall II), and Chapter \@ref(ipd-heading) provides an estimate for the effect of fibrates, a treatment for hypertriglyceridaemia.
+Four were identified via the systematic review,`r tg_vad_citations` while Chapter \@ref(cprd-analysis-heading) provided two additional estimates from unanalysed datasets (CaPS and Whitehall II), and Chapter \@ref(ipd-heading) provides an estimate for the effect of fibrates, a treatment for hypertriglyceridemia.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:tgVadBiasDirection), stratified by study design.
@@
 This observation is particularly problematic given the default position of the ROBINS-I and ROBINS-E tool to require a "Moderate" judgement in the confounding domain.
-Under these conditions, it is possible that a well-performed cohort study (low risk of bias across everything other that bias due to confounding) will be down-weighted versus a potentially poor MR study.
+Under these conditions, it is possible that a well-performed cohort study (low risk of bias across everything other that bias due to confounding) will be downweighted versus a potentially poor MR study.
 
@@
 In general, triangulation of any sort should be considered a natural extension of evidence synthesis, and therefore should follow best practice in relation to finding and critically assessing all relevant information.
-Additionally, the approach presented here also builds on recent developments in bias assessment to "explode out" the component results of a meta-analysis, and consider the effects of bias/indirectness in each separately.
+Additionally, the approach presented here also builds on recent developments in bias assessment to "explode out" the component results of a meta-analysis and consider the effects of bias/indirectness in each separately.
 
@@
 
-<!-- REVIEW Good to mention direct adjustment for bias, e.g. Greenlands writings -->
+<!-- REVIEW Good to mention direct adjustment for bias, e.g., Greenlands writings -->
 
@@
 
-* In this chapter, I narratively described the evidence identified or produced in previous chapters, and highlighted the issues with a qualitative approach to triangulation when there are several sources of evidence.
+* In this chapter, I narratively described the evidence identified or produced in previous chapters and highlighted the issues with a qualitative approach to triangulation when there are several sources of evidence.
 
@@
 
-* I discussed the limitations of this proposed method, given the absence of empirically-based priors for the impact of bias/indirectness, and proposed future research (i.e.
+* I discussed the limitations of this proposed method, given the absence of empirically based priors for the impact of bias/indirectness, and proposed future research (i.e.
 meta-epidemiological studies) that would address them.

### 2021-12-16 08-Discussion.Rmd
End of day:

@@
 Using pre-specified adjustment distributions mapped to the results of the domain-based risk-of-bias and indirectness assessments, this approach provides a systematic way to account for biases/indirectness across studies.
-In addition, it explicitly seeks to include both direct and indirect evidence, and separates the assessment of bias/indirectness in each result from the definition of distributions representing the impact of bias/indirectness.
+In addition, it explicitly seeks to include both direct and indirect evidence and separates the assessment of bias/indirectness in each result from the definition of distributions representing the impact of bias/indirectness.
 
@@
 
-Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts, and provided additional information on a previously under-studied relationship (lipids/LRA and vascular dementia).
+Additionally, this thesis has also produced new evidence on the association of blood lipids with dementia outcomes in previously unanalysed cohorts and provided additional information on a previously under-studied relationship (lipids/LRA and vascular dementia).
 
@@
 As part of a reflective learning process throughout my PhD, I maintained a catalogue of failures (available in Appendix \@ref(appendix-catalogue-failures)) describing analytical mistakes, failed experiments, and unsuccessful grant applications.
-However, I found there was one central learning point from this thesis, namely to be slightly less ambitious when planning future research projects.
+However, I found there was one central learning point from this thesis, namely, to be slightly less ambitious when planning future research projects.
 
@@
 In hindsight, the decision to take a broad approach to the inclusion of dementia outcomes resulted in a larger workload than anticipated, particularly when also considering evidence from multiple different study designs.
-Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g.
-Alzheimer's disease) when considering the causal effects of lipids.
+Additionally, as dementia subtypes likely have very different aetiological pathways, it may have been better to focus on a single subtype (e.g., Alzheimer's disease) when considering the causal effects of lipids.
 Similarly, attempting to undertake a full individual participant data meta-analysis as a single part of a larger program of research was overly ambitious, given that data cleaning and harmonisation for just three cohorts turned out to be a substantial undertaking.
@@
 This approach has already been used to assess long-term (11-20 years) safety outcomes of statin use, using participant recontact[@group2011] and linkage with electronic health records to identify events.[@ford2016] A similar approach could be used to assess the impact of randomisation to statins at midlife on subsequent risk of dementia outcomes.
-Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using electonic health records.
+Use of data linkage would represent the most cost-efficient approach,[@llewellyn-bennett2018] though as noted in Chapter \@ref(cprd-analysis-heading), there is the potential for non-differential misclassification when defining dementia outcomes using electronic health records.
 
@@
 As highlighted by the results of the systematic review presented in Chapter \@ref(sys-rev-results-heading), there is an absence of evidence on vascular dementia across the existing evidence base.
-While the primary studies presented here go some way towards supplementing this evidence base, future work is needed both to investigate the reasons for this evidence gap (e.g.
-due to an absence of primary data, challenges in the analysis of this outcome as documented in Chapter \@ref(cprd-analysis-heading), or a publication bias mechanism) and to address it.
+While the primary studies presented here go some way towards supplementing this evidence base, future work is needed both to investigate the reasons for this evidence gap (e.g., due to an absence of primary data, challenges in the analysis of this outcome as documented in Chapter \@ref(cprd-analysis-heading), or a publication bias mechanism) and to address it.
 
@@
 As noted in Chapter \@ref(sys-rev-results-heading), methods for the inclusion of Mendelian randomisation studies in evidence synthesis exercises are not yet sufficiently developed, particularly in comparison to other study designs.
-Future work could aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g.
-genetic instrumental variable analysis).
+Future work could aim to validate search strategies for this study design, paying particular attention to the range of terms used to define the analytical approach (e.g., genetic instrumental variable analysis).
 In addition, as discussed in Section \@ref(tri-accuracy), the lack of an established risk-of-bias tool for Mendelian randomisation studies limits subsequent analyses that require systematic assessment of bias, such as the quantitative triangulation framework proposed here.

### 2021-12-16 front-and-back-matter/99-appendices.Rmd
End of day:

@@
 
-In addition to publications arising directly from this thesis (described in Section \@ref(literature-contributions) & included in Appendix \@ref(published-papers)), I have been involved in a number of external research projects.
+In addition to publications arising directly from this thesis (described in Section \@ref(literature-contributions) and included in Appendix \@ref(published-papers)), I have been involved in a number of external research projects.
 Taken together, these additional projects provided extensive experience in evidence synthesis methods and in collaborating across large teams.
@@
 During 2020, I was involved in the updating of the Preferred Reporting Items for Systematic reviews and Meta-Analyses (PRISMA) statement.
-My contributions were focused on the data sharing aspects of the guidelines and on building an interactive web application that would allow users to complete the PRISMA checklist.
+My contributions were focused on the data sharing aspects of the guidelines and on building the PRISMA2020 interactive web application.
 Publications arising from this work are listed below:
@@
 
-medRxiv automatically links preprints to their published counterparts, and provides the DOI of the published article as part of the metadata on a given preprint.
+medRxiv automatically links preprints to their published counterparts and provides the DOI of the published article as part of the metadata on a given preprint.
 Using `medrxivr` to access this data, I could assess the two-year publication rate of preprints originally posted to medRxiv in July 2019.
@@
 
-* For Mendelian randomisation analyses, I had originally intended to use a panel of experts to assess he risk of bias in this study design.
+* For Mendelian randomisation analyses, I had originally intended to use a panel of experts to assess the risk of bias in this study design.
 However, through private correspondence with the authors of a review of risk-of-bias assessment tools for Mendelian randomisation studies (since published[@spiga2021]), I became aware of the Mamluk _et al_ tool.
@@
 However, on further reading,[@sterne2013] I learned that any bias introduced by sources of funding would operate through one of the existing domains of the risk-of-bias tools.
-As such, I did not consider funding sources seperately.
+As such, I did not consider funding sources separately.
 
- * Finally, I performed a dose response meta-analysis to assess the evidence for a non-linear realtionship between lipids and dementia outcomes.
+ * Finally, I performed a dose response meta-analysis to assess the evidence for a non-linear relationship between lipids and dementia outcomes.
 This marked a departure from the published protocol, as I had not expected the number of studies reporting dementia risk across lipid sub-categories to be sufficient for a dose response analysis.
@@
 
-An overview of the number of hits per database, in addition to the full line-by-line search results for the each database, are presented below.
+An overview of the number of hits per database, in addition to the full line-by-line search results for each database, are presented below.
 
-(ref:searchOverviewAppendix-caption) __Summary of number of records identified in each database searched__ - The full line-by-line search results for the each database, are presented in subsequent tables.
+(ref:searchOverviewAppendix-caption) __Summary of number of records identified in each database searched__ - The full line-by-line search results for each database, are presented in subsequent tables.
 Note there was substantial duplication across databases, resulting in several thousand duplicates being removed prior to title and abstract screening.
@@
 
-(ref:minFU-cap) __Illustration of minimum follow-up period in two study designs__ - Panel A shows a study in which all participants enter the study and are assinged an exposure group at the same time, making it ease to define a minimum period of follow-up.
+(ref:minFU-cap) __Illustration of minimum follow-up period in two study designs__ - Panel A shows a study in which all participants enter the study and are assigned an exposure group at the same time, making it easy to define a minimum period of follow-up.
 In contrast, Panel B illustrates the time- varying analysis used in Chapter \@ref(cprd-analysis-heading), which makes it challenging to define an unbiased minimum period of follow-up.
@@
 Additive or multiplicative scales were used to capture the intervals for additive and proportional bias/indirectness, respectively.
-The authors then use assumed log-normality of these distributions to derive a mean and variance for each on the log scale.
-
+The authors then derived a mean and variance for each on the log scale.
 The resulting data for two domains of bias (attrition and detection) in one study are shown in Table \@ref(tab:addTable1-table).
@@
 &nbsp;<!----------------------------------------------------------------------->  
-(ref:addTable3-caption) __Mean and maximum bias distributions, using example data__ - The mean and maximum of position and variance values desribed in Table \@ref(tab:addTable3-table) were calculated to give the average and maximum bias adjustment across studies and domains of bias.
+(ref:addTable3-caption) __Mean and maximum bias distributions, using example data__ - The mean and maximum of position and variance values described in Table \@ref(tab:addTable3-table) were calculated to give the average and maximum bias adjustment across studies and domains of bias.
 
@@
 
-This two step approach (averaging across assessors before taking the average and maximum across domains/studies) was important.
+This two-step approach (averaging across assessors before taking the average and maximum across domains/studies) was important.
 While the final average values will be the same whichever approach is taken, in a one-step process, the maximum value can be artificially inflated by a single expert's estimate.
@@
 
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open source tools to search preprinted literature, create visualisations of risk-of-bias data and to preform quantitative triangulation.
-In line with this, an open source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
+Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open-source tools to search preprinted literature, create visualisations of risk-of-bias data and to preform quantitative triangulation.
+In line with this, an open-source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
 
@@
 
-<!-- \includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf} -->
-<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf} -->
-<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf} -->
-<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf} -->
-<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf} -->
+\includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
+\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}

### 2021-12-16 front-and-back-matter/_abstract.Rmd
End of day:

@@
-<!-- TODO This needs to be less than 300 words! -->
-
-__Background:__ Identification of causal relationships between modifiable targets and risk of dementia is central to the development of evidence-based prevention strategies.
+__Background:__ Identification of causal relationships between modifiable risk factors and incidence of dementia is central to the development of evidence-based prevention strategies.
 As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, LDL-c, HDL-c, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
@@
 Analysis of the CPRD data provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia,  likely due to confounding by indication.
-The IPD meta-analysis provided some evidence for only the association of triglycerides and vascular dementia.
+The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only.
 Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.

### 2021-12-16 front-and-back-matter/_acknowledgements.Rmd
End of day:

@@
 I am extremely grateful to all those who contributed their time and energy to my research projects: Athena Sheppard, Emily Hennessy, Matthew Lee, Lena Schmidt, Alexandra McAleenan, Vincent Cheng, Francesca Spiga, Sarah Dawson and Rebecca Turner.
-A special mention goes to Mark Newbury of the Dementia Platform UK, who worked tirelessly to support my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
+A special mention goes to Mark Newbury of the Dementia Platform UK, who supported my applications for data access - I am extremely grateful for his help and commitment in chasing cohort owners.
 
-I also want to thank the many people who raised issues or otherwise provided feedback on the open source tools built as part of this thesis - it's been a joy to watch others build on my work.
+I also want to thank the many people who raised issues or otherwise provided feedback on the open-source tools built as part of this thesis - it's been a joy to watch others build on my work.
 A special mention must go to Randall Boyes and Alex J Fowler for their input/work on the `robvis` tool.
@@
 Ciara, I'd need (at least) another <<words>> words to accurately describe all the ways in which you supported me through this endeavour.
-It can't have been fun being locked-down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin.
+It can't have been fun being locked down in a small flat with a grumpy and stressed PhD student, nor trying to support the same student remotely from Dublin.
 In the Discussion, I talk about lessons learned during this thesis, but the biggest takeaway of this whole experience for me is that I am incredibly lucky to have found you and to get to take on life while holding your hand.

### 2021-12-16 index.Rmd
End of day:

@@
 Include the create_chunk_options chunk above at the top of your index.Rmd file
-This will include code to create additional chunk options (e.g. for adding author references to savequotes)
+This will include code to create additional chunk options (e.g., for adding author references to savequotes)
 If you need to create your own additional chunk options, edit the file R/create_chunk_options.R

### 2021-12-16 reviews/year_2/report.Rmd
End of day:

@@
 Preprints represent an important source of grey literature and so should be included as part of a systematic review.
-However, the native search interface on preprint websites do not allow for complex search strategies (e.g.
-those using Boolean operators or wildcards) and are not transparent or reproducible, with the same search producing wildly different numbers of records over time.
+However, the native search interface on preprint websites do not allow for complex search strategies (e.g., those using Boolean operators or wildcards) and are not transparent or reproducible, with the same search producing wildly different numbers of records over time.
 
@@
 
-This chapter will present the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/blood lipids interventions (e.g.
-statins) and dementia.
+This chapter will present the methods and findings of a comprehensive systematic review into the relationship between blood lipids levels/blood lipids interventions (e.g., statins) and dementia.
 The review included all types of study design including randomised controlled trials, Mendelian randomization analyses, and non-randomised studies of exposures and interventions (NRSI/NRSE).
@@
 
-In terms of the meta-analysis of the non-intervention studies, this was complicated by the different ways in which lipid fractions were quantified in different studies (e.g.
-grouped based on clinical guidelines or quantiles, or dichotomized into a hypercholesterolemia variable).
+In terms of the meta-analysis of the non-intervention studies, this was complicated by the different ways in which lipid fractions were quantified in different studies (e.g., grouped based on clinical guidelines or quantiles, or dichotomized into a hypercholesterolemia variable).
 However, following discussion with my supervisors who pointed me towards useful material on this subject, this element of the analysis is almost complete.
@@
 As part of this review, I have not only performed a original search of primary literature databases, but have also screened the reference lists of comparable reviews to ensure no study has been omitted.
-* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g.
-ROBINS-I/E).
+* _Structured risk of bias assessment:_ The majority of the highly cited reviews on this topic either do not formally consider the risk of bias in the observational studies they include or do not use an appropriate domain-based assessment tool (e.g., ROBINS-I/E).
 This is important area in which this thesis can add value, as based on the risk-of-bias assessments I have performed to date, several primary studies are at high risk of bias and this should be reflected in the findings of any  review on this topic.
@@
 
-In terms of the broader thesis, while these concerns mean I have low confidence in the accuracy of the result, it presents a good opportunity for comparison with other published papers that used different analytical strategies where the source and direction of bias is different (e.g.
-confounding by indication in our analysis likely makes statin use look worse but immortal time bias in other papers likely makes statin use look better).
+In terms of the broader thesis, while these concerns mean I have low confidence in the accuracy of the result, it presents a good opportunity for comparison with other published papers that used different analytical strategies where the source and direction of bias is different (e.g., confounding by indication in our analysis likely makes statin use look worse but immortal time bias in other papers likely makes statin use look better).
 

### 2021-12-17 04-Chp-Systematic-Review-Results.Rmd
Sort todos

@@
 :::
-
-<!-- TODO Consider adding a line to the descriptions of each forest plot regarding the direction - what's on the right, whats on the left -->
 
@@
 
-<!-- TODO This should also show Raffatin! -->
-
 \newpage
@@
 
-<!-- TODO This is not technically - more studies available on vascular dementia -->
-
 <!----------------------------------------------------------------------------->
@@
 A single Mendelian randomisation analysis was identified that examined the effect of genetically lowered LDL-c levels via HMGCR inhibition on the risk of vascular dementia, which provided some evidence for an effect (`r mrStatin$VaD$estimate`).
-
-<!-- TODO Might need to discuss this a bit further -->
 
@@
 
-<!-- TODO Consider mentioning that the date of the review is a limitation, and forward refer to the section in the Discussion that considers two new studies -->
-
 A primary limitation of this review is the fact that only a sample of records were dual screened at the title/abstract and full-text stages is a potential limitation, because there is a chance that some eligible records could have been excluded.

### 2021-12-17 05-Chp-CPRD-Analysis.Rmd
Sort todos

@@
 <!----------------------------------------------------------------------------->
-<!-- TODO Check table caption -->
 
@@
 
-<!-- TODO Check this table title -->
-
-(ref:statinTypeTable-caption) __Summary of statin properties__ Number of patients prescribed lipophilicity vs hydrophilicity statins, by grouped year of prescription.
+(ref:statinTypeTable-caption) __Summary of statin properties__ - Number of patients prescribed lipophilicity vs hydrophilicity statins, by grouped year of prescription.
 

### 2021-12-17 06-Chp-IPD-Analysis.Rmd
Sort todos

@@
 
-<!-- TODO Should start with inclusion criteria -->
-
 Eligible data sources for this analysis were prospective cohort studies (see Section \@ref(ipd-apply-access) for details on how these studies were identified).
@@
 Lipid levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
-
-<!-- TODO Ensure that the results are actually on the mmol/L scale -->
 
@@
 Finally, the ELSA study was excluded based on the dichotomous definition of the exposure variable.
-<!-- TODO CITATION NEEDED for each study here!
--->
 
@@
 ### Included data sources
-
-<!-- TODO Be clear on the different types of databases, e.g., those where users are followed up regularly vs. those where participants are captured via EHR-->
-
-<!-- TODO Need to talk about how dementia was assessed in each! -->
-
-<!-- TODO Link to appendix about data sources not approached -->
 
@@
 <!----------------------------------------------------------------------------->
-
-<!-- TODO Now that using a fixed effect model, evidence of TG/ACD association -->
 
@@
 
-<!-- TODO May need to talk about other confounders here -->
-
 A key limitation of this analysis is the potential for uncontrolled confounding.
@@
 
-<!-- TODO Talk about the fact that I used multiple imputation and they did not. Evidenced by wider confidence intervals, indicating a smaller sample size, likely the result of a complete case -->
-
 Investigation revealed several possible reasons for this discrepancy.
@@
 
-<!-- REVIEW Or a requirement of peer review and publication be that the data be recorded centrally and made available through a coordinated application process) -->
-
 &nbsp;<!----------------------------------------------------------------------->

### 2021-12-17 07-Chp-Triangulation.Rmd
Sort todos

@@
 
-<!-- TODO Add this to the Chapter summary in the introduction -->
-
-<!-- ### Triangulation  -->
-
-<!-- TODO Have a look at this - potentially move to triangulation chapter -->
-
-<!-- One key question for which multiple distinct sources of evidence were available were those looking at Laz -->
-
-<!-- Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
+<!-- IDEA Consideration of the potential impact of the magnitude and direct of residual confounders/bias is not a major stretch from what is already happening in the assessment of the quality of evidence (GRADE) framework.
 Within GRADE, the overall quality of evidence can be upgraded when there is deemed to be unmeasured or residual confounding variables which reduce the.
@@
 More specifically, this chapter builds on the comprehensive systematic review of existing evidence presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).
+This evidence base is then supplemented by new evidence on the association of statin use with dementia outcomes in the CPRD (Chapter \@ref(cprd-analysis-heading)) and the association of lipids (namely, total cholesterol (TC), high-density lipoprotein cholesterol (HDL), low-density lipoprotein cholesterol (LDL) and triglycerides (TG)) with dementia outcomes in previously unanalysed datasets accessed via the DPUK (Chapter \@ref(ipd-heading)).
 
@@
 
-<!-- TODO Update this paragraph to reflect extra 2 MR studies -->
-
-From the data sources identified in Section \@ref(tri-data-sources), I identified 18 results relevant to my first causal question of interest.
-Most (N =17) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate via the CPRD analysis.
+From the data sources identified in Section \@ref(tri-data-sources), I identified 21 results relevant to my first causal question of interest.
+Most (N = 20) were identified via the systematic review,`r ldl_ad_citations` while Chapter \@ref(cprd-analysis-heading) provided an additional estimate via the CPRD analysis.
 The extent, type and direction of predicted bias for each result can be seen in the bias-direction plot presented in Figure \@ref(fig:ldlAdBiasDirection), stratified by study design.
-
-<!-- TODO Double check this reference list is correct! -->
 

### 2021-12-17 01-Chp-Background.Rmd
Submitted version

@@
 <!----------------------------------------------------------------------------->
-(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia (major neurocognitive disorder).__ - These published criteria[@edition2013] are commonly used to define dementia cases.
+(ref:diagnosticCriteria-caption) __Overview of the DSM-5 criteria for dementia (major neurocognitive disorder)__ - These published criteria[@edition2013] are commonly used to define dementia cases.
 Criterion A captures the cognitive decline aspect of dementia, while Criteria B-D ensure that the impairment observed is sufficient to interfere with daily living and cannot explained by other causes.

### 2021-12-17 03-Chp-Systematic-Review-Methods.Rmd
Submitted version

@@
 
-(ref:sys-rev-methods-quote) --- Archibald Cochrane, 2000 [@cochrane1979]
+(ref:sys-rev-methods-quote) --- Archibald Cochrane, 2000[@cochrane1979]
 
@@
 [@cohen1960: @gwet2008; @wongpakaran2013] Given the small number of included studies in this review as a proportion of the total number screened, this is a useful characteristic.
-The formulae used to calculate $AC$ are given in Appendix \@ref(appendix-gwet).
+The formulae used to calculate $AC1$ are given in Appendix \@ref(appendix-gwet).
 
@@
 <!----------------------------------------------------------------------------->
-(ref:gwet-caption) __Ranges for Gwet's AC1__ - To aid the interpretation of inter-/intra-rater reliability, I used a published set of suggested categories for Gwet's AC1.[@mchugh2012]
+(ref:gwet-caption) __Ranges for Gwet's $AC1$__ - To aid the interpretation of inter-/intra-rater reliability, I used a published set of suggested categories for Gwet's AC1.[@mchugh2012]
 
-(ref:gwet-scaption) Ranges for Gwet's AC1
+(ref:gwet-scaption) Ranges for Gwet's $AC1$
 
@@
 Intra- and inter-rater reliability was assessed against these cut-offs.
-If this assessment demonstrated an issue with the screening process (defined as an $AC$ of less than 0.9), it indicated the need for a larger proportion of records to be dual screened.
+If this assessment demonstrated an issue with the screening process (defined as an $AC1$ of less than 0.9), it indicated the need for a larger proportion of records to be dual screened.
 

### 2021-12-17 04-Chp-Systematic-Review-Results.Rmd
Submitted version

@@
 ```{block type='savequote', include=knitr::is_latex_output(),quote_author='(ref:sys-rev-results-quote)', echo = TRUE}
-Hold  
+The hundreds of hours spent conducting a scientific study ultimately contribute only a piece of an enormous puzzle.
+The value of any single study is derived from how it fits with and expands previous work, as well as from the study's intrinsic properties.
+Through systematic review the puzzle's intricacies may be disentangled.
 ```
 
-(ref:sys-rev-results-quote) --- Hold
+(ref:sys-rev-results-quote) --- Cynthia D Mulrow, 1994[@mulrow1994]
 
@@
 <!----------------------------------------------------------------------------->
-(ref:obsStatinAD-cap) __Random-effects meta-analysis of statins on Alzheimer's disease__ Non-randomised studies examining the association of statin use with Alzheimer's disease were synthesised using a random-effects meta-analysis.
+(ref:obsStatinAD-cap) __Random-effects meta-analysis of statins on Alzheimer's disease__ - Non-randomised studies examining the association of statin use with Alzheimer's disease were synthesised using a random-effects meta-analysis.
 Subgroup estimates, stratified by overall risk-of-bias level, are also presented.

### 2021-12-17 05-Chp-CPRD-Analysis.Rmd
Submitted version

@@
 <!----------------------------------------------------------------------------->
-(ref:controlOutcomeFig-cap) __Sensitivity analysis: control outcomes__ Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale for three control outcomes: backpain (negative), ischemic heart disease (positive protective), and diabetes (positive harmful).
+(ref:controlOutcomeFig-cap) __Sensitivity analysis: control outcomes__ -  Effect estimates obtained from the fully-adjusted time-varying model with participant age as the time scale for three control outcomes: backpain (negative), ischemic heart disease (positive protective), and diabetes (positive harmful).
 

### 2021-12-17 07-Chp-Triangulation.Rmd
Submitted version

@@
 ```
-(ref:tri-quote) --- Austin Bradford Hill, 1965 [@hill1965]
+(ref:tri-quote) --- Austin Bradford Hill, 1965[@hill1965]
 
@@
 There are two key outputs from this chapter.
-The first is an R package, `triangulate`.
+The first is an R package, `triangulate`, available at [https://github.com/mcguinlu/triangulate](https://github.com/mcguinlu/triangulate).
 Personal communication with the authors of the bias-/indirectness-adjusted meta-analysis approach resulted in the STATA code to implement the adjusted model.[@turner2009] This has since been generalised as part of the `triangulate` R package to enable other users to apply the approach detailed here.
@@
 
-The second key output is an annotated example dataset for the LDL-c/Alzheimer's disease causal question addressed in this chapter.
+The second key output is an example dataset for the LDL-c/Alzheimer's disease causal question addressed in this chapter.
 Available via the `triangulate` package, this data will provide developers of new triangulation methods with an example dataset on which to test new tools, something which seriously hindered development of this work.

### 2021-12-17 08-Discussion.Rmd
Submitted version

@@
 ::: {.laybox data-latex=""}
-## Lay summary
+## Lay summary {-}
 
@@
 These results are consistent with the findings presented in this thesis, particularly as this study did not have access to _Apo_$\mathcal{E}4$ status and so could not adjust for confounding by this variable.
-_Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels, <!-- TODO CITATION NEEDED --> and so could explain the harmful association observed.
+_Apo_$\mathcal{E}4$ is a key risk factor for both Alzheimer's disease and raised LDL-c levels,[@bennet2007] and so could explain the harmful association observed.
 This is supported by a simulation analysis reported within this study, which used published information to predict that _Apo_$\mathcal{E}4$ would induce a risk ratio of 1.09 per 1-SD increase in LDL-c in the absence of a true causal effect.

### 2021-12-17 front-and-back-matter/99-appendices.Rmd
Submitted version

@@
 This work underpinned a living systematic review on impact of the COVID-19 pandemic on self-harm and suicidal behaviour.
-Subsequently, the pipeline enabled rapid reviews of related topics, such as an analysis of the available evidence by population.
+Subsequently, the pipeline enabled rapid reviews of related questions, such as the impact on specific study populations.
 
@@
 
-A copy of the risk of bias tool used to assess Mendelian randomisation studies is presented in Table \@ref(tab:mrTool-table), below.
+A copy of the risk-of-bias tool used to assess Mendelian randomisation studies is presented in Table \@ref(tab:mrTool-table), below.
 
@@
 
-Enforcing a minimum period of follow-up is normally used to reduce the risk of reverse causation in an analysis by excluding events occurring within a certain time-frame post-exposure.
+Enforcing a minimum period of follow-up is normally used to reduce the risk of reverse causation in an analysis by excluding events occurring within a certain time-frame post exposure.
 With respect to dementia outcomes, which have a long prodromal period, enforcing a minimum period of follow-up can add biological validity to an analysis.
@@
 Alternatively, defining the minimum period of follow-up from statin initiation cause issues around the treatment of time-at-risk before statin initiation and around the start point for the follow-up period in those never prescribed a statin.
-In summary, either approach is likely to be substantially biased.
+In summary, either approach is likely to be substantially biased, and so an analysis using a minimum follow-up period was not performed.
 
@@
 
-(ref:fpLdlAdComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+&nbsp;<!----------------------------------------------------------------------->
+
+(ref:fpLdlAdComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of LDL-c/Alzheimer's disease under two different scenarios of additive bias__ - Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
 Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels.
@@
 
-(ref:fpTgVaDComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias.__ Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
+(ref:fpTgVaDComparison-cap) __Comparison of bias-/indirectness-adjusted meta-analyses of triglycerides/vascular dementia under two different scenarios of prior distributions of bias__ - Scenario 1: position value between the additive distributions assigned to "High" and "Moderate" bias levels is the same as between the "Moderate" and "Low" levels.
 Scenario 2: position value between the additive distributions assigned to "High" and "Moderate" bias levels is twice that between "Moderate" and "Low" levels.
@@
 
-Reproducible and science has been a key theme running through this thesis, as reflected by the development of an open-source tools to search preprinted literature, create visualisations of risk-of-bias data and to preform quantitative triangulation.
+Reproducible research has been a key theme running through this thesis, as reflected by the development of an open-source tools to search preprinted literature, create visualisations of risk-of-bias data and to preform quantitative triangulation.
 In line with this, an open-source copy of the code used to produce this thesis is available on GitHub, as is the code used to perform the analysis contained within it.
@@
 
-As part of a reflective process, during the course of my PhD I kept a record of things (analytical mishaps, failed experiments, and unsuccessful grant applications) I attempted but which did not work.
+As part of a reflective process, I kept a record of things (analytical mishaps, failed experiments, and unsuccessful grant applications) I attempted during the course of my PhD but which did not work.
 These are summarised briefly here:
@@
 
-<!-- TODO Need to complete this sections -->
 The `robvis` package provides functions to visualise risk-of-bias assessments, with the resulting plots formatted based on the specific risk-of-bias assessment tool used.
@@
 For the paired forest plots presented in Chapter \@ref(sys-rev-results-heading), the tool expects a "Study" column, followed by one column per domain of bias and one column for the overall risk of bias judgement.
-To illustrate this, the `data_rob2` dataset which is available via the `robvis` package and contains example risk-of-bias assessments performed using the RoB2.0 tool for randomized controlled trials, is shown in Table \@ref(tab:biasData-table).
+To illustrate this, the `data_rob2` dataset which is available via the `robvis` package and contains example risk-of-bias assessments performed using the RoB2.0 tool for randomised controlled trials, is shown in Table \@ref(tab:biasData-table).
 
@@
 
-\includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf}
-\includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf}
+<!-- \includepdf[pages=-,link=true,pagecommand={\thispagestyle{empty}}]{published/cprd_medrxiv.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/medrxivr.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/robvis.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/DAS_comparison.pdf} -->
+<!-- \includepdf[pages=-,pagecommand={\thispagestyle{empty}}]{published/prevsci.pdf} -->

### 2021-12-17 front-and-back-matter/_abstract.Rmd
Submitted version

@@
 
-__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
+__Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across the study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
 Analysis of the CPRD data provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia,  likely due to confounding by indication.

### 2021-12-17 front-and-back-matter/_acknowledgements.Rmd
Submitted version

@@
 First and foremost, I must thank my primary supervisor, Julian Higgins, for his tireless support and encouragement.
-I'd also like to thank my other supervisors - Yoav Ben-Shlomo, Liz Coulthard and George Davey-Smith - for all their input over the past three years.
+I'd also like to thank my other supervisors - Yoav Ben-Shlomo, Liz Coulthard and George Davey Smith - for all their input over the past three years.
 Thanks also to Rupert Payne and Emma Anderson for their engaging discussion and useful feedback during my annual progress reviews.
@@
 
-Finally, a big thanks to Vivienne Gardiner, who sacrificed a substantial amount of time to proof-reading this thesis.
+Finally, a big thanks to Vivienne Gardiner, who sacrificed a substantial amount of time to proof-read this thesis.
 
@@
 Canynge Hall, Bristol \\\
-1 December 2021
+17 December 2021
 \end{flushright}

### 2021-12-17 R/07-Code-Triangulation-Analysis.R

@@ -112,13 +112,13 @@ priors_ind_table <- rio::import("data/tri/priors_indirect_tab.csv") %T>%
   write.csv("data/table_words/priors_indirect.csv")
 
 if (doc_type == "docx") {
-  apply_flextable(priors_ind_table, caption = "(ref:priorsAdd-caption)")
+  apply_flextable(priors_ind_table, caption = "(ref:priorsIndirect-caption)")
 } else{
   knitr::kable(
     priors_ind_table,
     format = "latex",
-    caption = "(ref:priorsAdd-caption)",
-    caption.short = "(ref:priorsAdd-scaption)",
+    caption = "(ref:priorsIndirect-caption)",
+    caption.short = "(ref:priorsIndirect-scaption)",
     booktabs = TRUE, 
     align = "lc"
   ) %>%
@@ -161,7 +161,10 @@ dat_rob <- read.csv("data/tri/ldl_ad_rob.csv",
   mutate(vi = sei^2) %>%
   select(result_id, author, type, yi, vi, everything())  %>%
   # Standardise effect direction
-  mutate(yi = ifelse(type %in% c("NRSE","MR - LDL"), yi*-1, yi))
+  mutate(yi = ifelse(type %in% c("NRSE","MR - LDL"), yi*-1, yi),
+         d7d = case_when(type %in% c("NRSE","MR - LDL") & d7d == "Right" ~ "Left",
+                         type %in% c("NRSE","MR - LDL") & d7d == "Left" ~ "Right",
+                         T ~ d7d))
 
 dat_ind <- read.csv("data/tri/ldl_rob_indirect.csv",
                     stringsAsFactors = F) %>%
@@ -337,10 +340,10 @@ metafor::forest(
   at = log(c(0.3, 1, 3)),
   showweights = TRUE
 )
-text(log(0.01), 23, "Author and Year", cex=.8, font=2)
-text(log(40), 23.5, "Unadjusted", cex=.8, font=2)
-text(log(9.3), 22.5, "Weight", cex=.8, font=2)
-text(log(100), 22.5, "Estimate", cex=.8, font=2)
+text(log(0.01), 25, "Author and Year", cex=.8, font=2)
+text(log(40), 25.5, "Unadjusted", cex=.8, font=2)
+text(log(9.3), 24.5, "Weight", cex=.8, font=2)
[…]

### 2022-03-27 03-Chp-Systematic-Review-Methods.Rmd
Add "and meta-analyses" to title of Chapters 3/4

@@
 
-# Systematic review of existing evidence on the association between blood lipids and dementia outcomes: Methods {#sys-rev-methods-heading}
+# Systematic review [and meta-analyses]{.correction} of existing evidence on the association between blood lipids and dementia outcomes: Methods {#sys-rev-methods-heading}
 

### 2022-03-27 04-Chp-Systematic-Review-Results.Rmd
Add "and meta-analyses" to title of Chapters 3/4

@@
 
-# Systematic review of existing evidence on the association between blood lipids and dementia outcomes: Results {#sys-rev-results-heading}
+# Systematic review [and meta-analyses]{.correction} of existing evidence on the association between blood lipids and dementia outcomes: Results {#sys-rev-results-heading}
 

### 2022-03-27 03-Chp-Systematic-Review-Methods.Rmd
Define rare outcome

@@
 The range of effect measures presented by studies (odds ratios, risk ratios, hazard ratios, etc.) are not directly interchangeable in the context of systematic review.
-As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.
+As such, different reported effect estimates can be one potential problem that precludes a meta-analysis of all studies.[@mckenzie2019] However if the outcome is rare [(<10%)]{.correction}, as is the case for dementia outcomes, the estimated odds, risk and hazard ratios will approximate each other.[@vanderweele2020] As such, I did not stratify the analyses by reported effect measure.
 

### 2022-03-27 08-Discussion.Rmd
Add "and meta-analysis" to description of the systematic review

@@
 
-In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes.
+In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review [and meta-analyses]{.correction}
+ of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes.
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.

### 2022-03-27 07-Chp-Triangulation.Rmd
Fixed equation and LDL-c/HDL-c

@@
 \blandscape
+
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
+
 \elandscape
@@
 
-Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the individual participant data (IPD) analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (in the systematic review: TC - `r obsLipids$Dementia_TC$estimate`; LDL - `r obsLipids$Dementia_LDL$estimate`; HDL - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate` ).
+Analysis of lipid levels across both the systematic review (Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading)) and the individual participant data (IPD) analysis (Chapter \@ref(ipd-heading)) found extremely weak evidence for an association of any lipid fraction with all-cause dementia (in the systematic review: TC - `r obsLipids$Dementia_TC$estimate`; [LDL-c]{.correction} - `r obsLipids$Dementia_LDL$estimate`; [HDL-c]{.correction}
+ - `r obsLipids$Dementia_HDL$estimate`; TG - `r obsLipids$Dementia_TG$estimate` ).
 Similarly, meta-analysis of studies identified by the review which examined a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$Dementia$estimate`).
@@
 
-Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (in the systematic review: TC - `r obsLipids$AD_TC$estimate`; LDL - `r obsLipids$AD_LDL$estimate`; HDL - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`).
+Meta-analysis of lipid levels in the systematic review found extremely weak evidence for an association of any lipid fraction with Alzheimer's disease (in the systematic review: TC - `r obsLipids$AD_TC$estimate`; [LDL-c]{.correction} - `r obsLipids$AD_LDL$estimate`; [HDL-c]{.correction} - `r obsLipids$AD_HDL$estimate`; TG - `r obsLipids$AD_TG$estimate`).
 Similarly, meta-analysis of studies examining a binary hypercholesterolemia provided weak evidence for an association of this risk factor with Alzheimer's disease (`r obsHyperchol$AD$estimate`).
@@
 This are defined as
-
+```{block type='correction'}
 \begin{equation}
-  \mu_{i\beta} = exp(\alpha_{i} + {\psi_i}^2)
+  \mu_{i\beta} = exp(\alpha_{i} + {\psi_i}^2/2)
   (\#eq:prop-total-mean)
 \end{equation}
+```
 
@@
 where $\mu_{i\delta}^{\mathrm{B}}$ and $\mu_{i\beta}^{\mathrm{B}}$ refer to the total additive and proportional bias, and  $\mu_{i\delta}^{\mathrm{In}}$ and $\mu_{i\beta}^{\mathrm{In}}$  refer to the total additive and proportional indirectness, respectively.
-Note that in this exercise, the total additive indirectness $\mu_{i\beta}^{\mathrm{In}} = 1$ because all indirectness was defined _a priori_ as being proportional.
+Note that in this exercise, the total additive indirectness $\mu_{i\delta}^{\mathrm{In}} = 1$ because all indirectness was defined _a priori_ as being proportional.
 

### 2022-03-27 04-Chp-Systematic-Review-Results.Rmd
Added number of studies by type and non-linearity P

@@
 
-The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
+The majority of included studies described non-randomised [(N = 74) and Mendelian randomisation (N=8)]{.correction} analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
 A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS).
@@
 The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).
+[There was little evidence for a non-linear relationship (Wald-type test for deviation from linearity p = 0.46).]{.correction}
 

### 2022-03-27 01-Chp-Background.Rmd
Range of small line edit corrections

@@
 A key risk factor for dementia may be the levels of lipids (fatty substances such as cholesterol) in a person's blood, though not all existing research agrees.
-The aim of this thesis is to use all available evidence to assess whether blood lipid levels are in fact a risk factor for dementia.
+The aim of this thesis is to use all available evidence to assess whether [raised]{.correction} blood lipid levels are in fact a [cause of]{.correction} dementia.
 
@@
 
-Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.
-Characterised by substantial cognitive impairment and difficulty with high level executive function, it is an insidious disease, with initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
+[Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.]{.correction} [@alzheimersassociation2020] Characterised by substantial cognitive impairment and difficulty with high level executive function, it is an insidious disease, with initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
 Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
@@
 Low-density-lipoprotein cholesterol (LDL-c), commonly known as "bad" cholesterol, acts as an energy conveyor by transporting fat to cells.
-In contrast, high density-lipoprotein cholesterol (HDL-c) transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
+In contrast, high-density-lipoprotein cholesterol (HDL-c) transports cholesterol to the liver to be broken down and excreted.[@feingold2000]
 
@@
 Described by the Committee on Publication Ethics as 'scholarly manuscript[s] posted by the author(s) in an openly accessible platform, usually before or in parallel with the peer review process',[@committeeonpublicationethicscope2018] preprints serve several purposes.
-They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, the allow for the rapid dissemination of research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
+They are used to establish primacy when submitting to a journal where the peer-review process may take several months.[@vale2016] In addition, [they]{.correction} allow for the rapid dissemination of research findings, as occurred during the COVID-19 pandemic.[@fraser2020preprinting] Finally, they are a source of information on manuscripts that may not have been accepted elsewhere, helping to combat publication bias or the "file-drawer" effect.[@rosenthal1979]
 
@@
 
-I will attempt to obtain the raw data from relevant primary studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-Any data obtained will be combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
-This will enable the assessment of the effect of lipids on dementia, and whether this relationship is modified by key variables such as participants' age or sex.
+```{block type = "correction"}
+As part of this research, I attempted to obtain the raw data from relevant primary studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+Data obtained were combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
+This enabled the assessment of the effect of lipids on dementia, and whether this relationship is modified by key variables such as participants' age or sex.
+```
 

### 2022-03-28 01-Chp-Background.Rmd
Range of corrections

@@
 
-[Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of cases.]{.correction} [@alzheimersassociation2020] Characterised by substantial cognitive impairment and difficulty with high level executive function, it is an insidious disease, with initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
+Alzheimer's disease is the most common cause of dementia, accounting for approximately 60-80% of [cases.]{.correction}[@alzheimersassociation2020] Characterised by substantial cognitive impairment and difficulty with high level executive function, it is an insidious disease, with initial onset thought to occur up to 15 years prior to symptomatic presentation.[@robinson2015] Much remains unknown about Alzheimer's pathogenesis, despite research implicating the "amyloid hypothesis",[@robinson2015] as a potential mechanism of disease.
 Under this hypothesis, the build-up of amlyoid plaques (composed mainly of amlyoid-$\beta$ peptide) and neurofibrillary tangles (composed mainly of tau protein) triggers a range of physiological changes, including inflammation and cell death, that result in cognitive impairment.[@robinson2015]
 
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10-25% of cases.
-Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
+Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10-25% of [cases.]{.correction}[@alzheimersassociation2020] Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
 
@@
 Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
-Finally, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016]
+[Further]{.correction}, as they included only patients at high vascular risk, their generalisability to other settings is limited.[@mcguinness2016]
+
+[Finally, the ability of studies of statin use to assess a causal link between lipid levels and dementia is limited by the pleiotropic effect of the intervention, as statins may effect dementia risk via some non-lipid-lowering pathway.
+For example, statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]
 
@@
 
-```{block type = "correction"}
-As part of this research, I attempted to obtain the raw data from relevant primary studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
-Data obtained were combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
-This enabled the assessment of the effect of lipids on dementia, and whether this relationship is modified by key variables such as participants' age or sex.
-```
+[As part of this research, I attempted]{.correction} to obtain the raw data from relevant primary studies identified by the systematic review presented in Chapters \@ref(sys-rev-methods-heading) & \@ref(sys-rev-results-heading).
+Data obtained [were]{.correction} combined with that available from the DPUK portal as part of an IPD meta-analysis in Chapter \@ref(ipd-heading).
+This [enabled]{.correction} the assessment of the effect of lipids on dementia, and whether this relationship is modified by key variables such as participants' age or sex.
 

### 2022-03-28 03-Chp-Systematic-Review-Methods.Rmd
Range of corrections

@@
 I sought to include studies that examined blood lipid levels as a risk factor for dementia outcomes, defined either as a binary hypercholesterolemia variable or by category/1-standard-deviation increase in a specific lipid fraction.
-The fractions considered by this review were namely total cholesterol (TC), high-density lipoprotein cholesterol (HDL), low-density lipoprotein cholesterol (LDL) and triglycerides (TG).
+The fractions considered by this review were namely total cholesterol (TC), high-density lipoprotein cholesterol [(HDL-c)]{.correction}, low-density lipoprotein cholesterol [(LDL-c)]{.correction} and triglycerides (TG).
 I also aimed to include studies examining the effect of lipid-regulating agents (LRA) as a source of indirect evidence.
@@
 
-Studies of any duration were included, and no limits were placed on the sample size of included studies.
+[Longitudinal]{.correction} studies [(randomised trials and observational studies)]{.correction} of any duration were included, and no limits were placed on the sample size of included studies.
 Finally, conference abstracts with no corresponding full-text publication were eligible, and where required, I contacted authors to obtain relevant additional information not available from the abstract.
@@
 Similarly, analyses are presented separately for each dementia outcome of interest (all-cause dementia, Alzheimer's disease, vascular dementia).
+[A final division of analyses was made based on the reported exposure measurement (e.g.
+binary measurement of hypercholesterolemia, per standard deviation change in lipid fraction, etc.).]{.correction}
 

### 2022-03-28 05-Chp-CPRD-Analysis.Rmd
Range of corrections

@@
 
-This finding disagrees with the results of the original analysis, which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD  dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+This finding disagrees with the results of the original analysis [reported by Smeet _et al_,]{.correction} [@smeeth2009] which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
 

### 2022-03-28 front-and-back-matter/99-appendices.Rmd
Fix abbreviation of LDL/HDL in appendix

@@
 Missing variables are denoted using a "-", while missing values are described as N (%).
-Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.
+Note that [LDL-c]{.correction} is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, [LDL-c]{.correction} and TG following multiple imputation of missing values in these variables.
 

### 2022-03-30 01-Chp-Background.Rmd
Range of corrections

@@
 
+[However, evidence from longitudinal studies indicates the challenge of assigning a subtype to dementia outcomes, given the known heterogeneity in clinical phenotypes.]{.correction} [@rooney2017] [For example, ]{.correction} [@shim2013]
+
 &nbsp;<!----------------------------------------------------------------------->
@@
 
-Dementia also has a substantial economic impact.
+Multimorbidity is common among people with dementia, with those diagnosed frequently having two or more other chronic conditions.[@poblador-plou2014]
+
+Patients with dementia have a higher risk of diabetes, stroke, depression pneumonia, falling and infection
+
+[In addition to the patient-centered harm described,]{.correction} dementia also has a substantial economic impact.
 In 2015, the estimated total cost of dementia in England was £24.2 billion.
@@
 
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] To date, a substantial amount of research has been produced examining putative risk factors for dementia.[@feingold2000;@peters2019; @anstey2019]
+Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Well-studied risk factors for the condition include cardiovascular factors (e.g.
+hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] The benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied.
+Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension, diabetes, smoking, physical inactivity, [depression,]{.correction} and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
 
-<!-- TODO Need some details on risk factors here - and consider spacing differentl -->
-
-The benefits of a prevention-based approach based on addressing these risk factors are well-studied.
-Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension,[@hughes2020] diabetes, smoking, physical inactivity, and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
-
-In this context, lipid levels represent a promising target for preventative treatment, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019] Determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
+In this context [of preventative treatment]{.correction}, lipid levels represent a [potential]{.correction} target, due to the ready availability of lipid-modifying treatments which could be repurposed.[@pushpakom2019] Given the existing uncertainty in the evidence [(as discussed in Section]{.correction} \@ref(evidence-association) [, below),]{.correction} determining whether variations in lipid levels are causative for dementia may prove critical in reducing the future burden of the condition.
 
@@
 Both trials were also limited by the relatively short follow-up period examined.
-This limited follow-up was to be expected because the primary aim of both trials was to assess the effect of statins on short-term coronary-related outcomes.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF Protection Study estimated risk at 5 years of follow-up.
+This limited follow-up was to be expected because the primary aim of both trials was to assess the effect of statins on short-term coronary-related outcomes.[@heartprotectionstudycollaborativegroup2002; @trompet2010] The PROSPER trial had a mean follow-up of 3.2 years, while the MRC/BHF [Heart]{.correction} Protection Study estimated risk at 5 years of follow-up.
 Given the long lag time between non-symptomatic onset of dementia and clinical presentation, it is likely that these durations are insufficient to fully capture the onset of dementia.
@@
 
-[Finally, the ability of studies of statin use to assess a causal link between lipid levels and dementia is limited by the pleiotropic effect of the intervention, as statins may effect dementia risk via some non-lipid-lowering pathway.
+[A final general limitation of studies of statin use is their limited ability to assess a causal link between lipid levels and dementia.
+This is caused by the pleiotropic effect of statins, which may effect dementia risk via some non-lipid-lowering pathway.
 For example, statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria (Assumption 3, above), as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria [of MR analyses], as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
 This was supported by further MR studies in which the observed effect attenuated to the null after _Apo_$\mathcal{E}$ variants were excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.
@@
 
-Despite their advantages, IPD meta-analyses are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request" from authors declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified[@vanpanhuis2014].
-Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
+Despite their advantages, IPD meta-analyses are rarely performed.[@tugwell2010] Factors limiting their uptake include the increased time and effort they require when compared to a summary-level analysis, and the low success rate associated with obtaining the raw data.[@nevitt2017; @ventresca2020] The data underlying primary studies are frequently not publicly available,[@alsheikh-ali2011; @federer2018] and the availability of data "available on request" from authors declines rapidly over time.[@vines2014] Several systematic barriers to open data sharing have been identified.[@vanpanhuis2014] Of particular concern for biomedical IPD analyses are legal issues surrounding the sharing of medical data, motivated by concerns around patient privacy.[@wartenberg2010]
 

### 2022-03-30 03-Chp-Systematic-Review-Methods.Rmd
Range of corrections

@@
 
-One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the RoB 2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis, as assessed using the RoB-ME tool, is shown beside the overall summary diamond.
+One of the limitations of current risk-of-bias assessment practice in systematic reviews is that they are often divorced from the results to which they refer, and are infrequently incorporated into the analysis.[@marusic2020; @katikireddi2015] In response to this criticism, I developed a new visualisation tool which was designed to allow for the production of "paired" forest plots - [where]{.correction} a risk-of-bias assessment is presented alongside it's corresponding numerical result -  as recommended by the RoB 2 publication.[@sterne2019] In addition, the risk of bias due to missing evidence in each synthesis, as assessed using the RoB-ME tool, is shown beside the overall summary diamond.
 This tool was developed as an adjunct to this thesis,[@mcguinness2020robvisPaper] and summary of its functionality can be found in Appendix \@ref(appendix-robvis).

### 2022-03-30 04-Chp-Systematic-Review-Results.Rmd
Range of corrections

--- 2022-03-27 04-Chp-Systematic-Review-Results.Rmd
@@
 
-Those records which were excluded in the initial screening but were included by the second reviewer (N =`r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
+Those records which were excluded in the initial screening but were included by the second reviewer (N = `r discrepancy_Inter`, Table \@ref(tab:agreeInter-table)) were investigated.
 This discrepancy between the two reviewers was explained in all cases by differing interpretations of the inclusion criteria, most commonly around the definition of cognitive decline versus dementia and of eligible lipids fractions.
@@
 
-The majority of included studies described non-randomised analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
+The majority of included studies described non-randomised [(N = 71) and Mendelian randomisation (N=8)]{.correction} analyses, with the only two included randomised controlled trials (the Heart Protection Study/British Heart Foundation trial[@heartprotectionstudycollaborativegroup2002] and the JUPITER trial[@ridker2008]) both reporting on the effect of statin use on incidence of all-cause dementia in older adults.
 A similarly small number of Mendelian randomisation studies were identified, several of which employed a two-sample approach using summary statistics from the same published genome wide association studies (GWAS).
@@
 The reference dose was defined _a priori_ as 200 _mg/dL_, the cut-off of the "Normal"/"Optimal" category for total cholesterol as detailed in Table \@ref(tab:lipidLevels-table).
+[There was little evidence for a non-linear relationship (Wald-type test for deviation from linearity: p = 0.46).]{.correction}
 

### 2022-03-30 06-Chp-IPD-Analysis.Rmd
Range of corrections

@@
 
-Where data on one of the exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula (Equation \@ref(eq:total-cholesterol-formula)).
+Where data on one of the exposures (TC, LDL-c, HDL-c, TG) was missing, it was inferred from the other three fractions (where available) using the Friedwald formula [as detailed in]{.correction} Equation \@ref(eq:total-cholesterol-formula).
 Lipid levels were retained as continuous variables rather than dichotomising into a binary hypercholesterolemia exposure, given the additional statistical power this adds to the meta-analysis.[@riley2020;@ensor2018] Where lipid measurements were reported in _mg/dL_, these were converted to _mmol/L_.
@@
 The results from the main effect analysis across the varying lipid fractions on each dementia outcome considered can be seen in Figures \@ref(fig:mainEffectDem) & \@ref(fig:mainEffectVad), respectively.
-There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`, \@ref(fig:mainEffectVad)).
+There was weak evidence for an association of any lipid level with either all-cause or vascular dementia, with the exception of a harmful association between raised triglycerides and vascular dementia (`r ipd_vasdem`, Figure \@ref(fig:mainEffectVad)).
 For the sole cohort containing data on the Alzheimer's disease outcome (Whitehall II), there was weak evidence for an association of this outcome with any lipid fraction (results shown in comparison with previous analysis of this cohort in Figure \@ref(fig:whitehallComparisonAd))
@@
 
+#### [Regression dilution bias]{.correction}
+
+[A related issue is regression dilution bias, which occurs when random measurement error in the exposure variable biases the obtained effect estimates towards the null.]{.correction}[@macmahon1990; @hutcheon2010] [In the case of this analysis, the use of a single measurement to define lipid levels may introduce random measurement error into the analysis.
+As a result, the observed relationship between baseline lipid levels and dementia outcomes could be underestimated.
+In future research, this bias could be addressed through the averaging of multiple measurements over a given time period to more accurately define the baseline exposure.]{.correction}[@hutcheon2010]
+
+&nbsp;<!----------------------------------------------------------------------->
+
 #### Comparison with a previous analysis
@@
 n=114 in Tynkkynen _et al._), suggesting that incomplete records were discarded in the previous analysis.
-Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data allowing it to adjust for _Apo_$\mathcal{E}4$ status.
+[A further potential cause of the discrepancy is the use of different effect metrics in the two analyses (OR in this analyses, hazard ratios (HR) in Tynkkynen _et al._), though when the outcome is rare, the two measures are expected to be similar (see Section]{.correction} \@ref(sys-rev-analysis-overview) [).]{.correction} Finally, the covariates adjusted for in each analysis were similar, though the previous analysis had access to genetic data allowing it to adjust for _Apo_$\mathcal{E}4$ status.
 However, given that _Apo_$\mathcal{E}4$ is a risk factor for increased LDL-c rather than triglycerides,[@bennet2007] it seems unlikely that additional adjustment for this variable is responsible for the discrepancy in the findings observed.

### 2022-03-30 07-Chp-Triangulation.Rmd
Range of corrections

@@
 
-<!-- TODO Consider adding AD as an outcome to the IPD row, depending on which result you want to use. -->
-
-\blandscape
-
+\blandscape{}
 <!----------------------------------------------------------------------------->
@@
 <!----------------------------------------------------------------------------->
-
-\elandscape
+\elandscape{}
 

### 2022-03-30 R/03-Code-Systematic-Review.R

@@ -923,7 +923,7 @@ dat <-
   ) %>%
   mutate(author = case_when(!is.na(sex) ~ paste0(author, " (", sex, " only)"),
                             T ~ author)) %>%
-  mutate(year = case_when(measure == "OR" ~ paste0(as.character(year), "*"),
+  mutate(year = case_when(measure == "OR" ~ paste0(as.character(year), ""),
                             T ~ as.character(year))) %>%
   rename("n" = number_exposed) %>%
   select(
@@ -1108,7 +1108,7 @@ dat <-
                             T ~ author)) %>%
   mutate(author = case_when(!is.na(age) ~ paste0(author, " (", age, ")"),
                             T ~ author)) %>%
-  mutate(year = case_when(measure == "OR" ~ paste0(as.character(year), "*"),
+  mutate(year = case_when(measure == "OR" ~ paste0(as.character(year), ""),
                             T ~ as.character(year))) %>%
   rename("n" = number_exposed) %>%
   select(
@@ -1563,10 +1563,6 @@ purrr::pmap(
     otherwise =  NULL
   )
 )
-
-
-
-
 
 #-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-#-
 # ---- mrDuplicationSetup

### 2022-04-01 01-Chp-Background.Rmd
Range of corrections to Rmd files

@@
 
-Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] culminating in reduced motor control that affects patients' ability to swallow or breathe.[@kumar2013] The condition has several distinct underlying causes, including Alzheimer's disease and vascular dementia.[@burns2009]
+Defined by the Diagnostic and Statistical Manual of Mental Disorders as a "major neurocognitive disorder", dementia is a progressive disease which impairs cognitive functions including speech, memory and executive reasoning.[@edition2013] At advanced stage, the condition causes severe behavioral and personality changes,[@cerejeira2012] culminating in reduced motor control that affects patients' ability to swallow or breathe.[@kumar2013]
+
+The condition is thought to have several distinct underlying causes, the most common of which are Alzheimer's disease and vascular dementia.[@burns2009] Other causes include rarer dementia subtypes (e.g., Lewy body or frontotemporal dementias) and other neurological diseases (e.g., Parkinson's disease).[@burns2009]
 
@@
 
-Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10-25% of [cases.]{.correction}[@alzheimersassociation2020] Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015] Vascular dementia regularly co-occurs in patients with Alzheimer's disease.[@iadecola2013] This presentation is described as "mixed" dementia,[@custodio2017] and occurs in approximately 25% of cases.[@burns2009]
+Vascular dementia (VaD) is the second largest underlying pathology of dementia, accounting for ~10-25% of [cases.]{.correction}[@alzheimersassociation2020] Vascular dementia is caused by a range of cerebrovascular disorders, and as a result, presentation  of symptoms can vary widely.[@iadecola2013] Similarly, due to the varied underlying  pathophysiology, vascular dementia can onset either quite rapidly following a cerebrovascular event such as a stroke or over a long time-frame due to a series of small infarcts.[@venkat2015]
 
-The remaining 10-30% of cases are caused by other dementia subtypes (e.g., Lewy body or frontotemporal dementias) or other neurological diseases (e.g., Parkinson's disease).[@burns2009]
+[While widely used in the published literature, the validity of these dementia subtypes as distinct clinical outcomes is debatable.]{.correction} Vascular dementia regularly co-occurs in patients with Alzheimer's disease,[@iadecola2013] [a]{.correction} presentation described as "mixed" dementia.[@custodio2017] [Evidence from autopsies performed as part of longitudinal population based samples, such as the Medical Research Council Cognitive Function and Ageing Study,]{.correction}[@chadwick1992] [found that a majority of participants had evidence of both Alzheimer's disease and vascular pathology.]{.correction} [@neuropathologygroupofthemedicalresearchcouncilcognitivefunctionandageingstudymrccfas2001] [This suggests that the "pure" clinical subtypes of dementia are less common than the "mixed" outcome, particularly in older age groups,]{.correction}[@schneider2007] [and indicates that a composite all-cause dementia outcome might be considered more analytically valid than outcomes based on a single dementia subtype.]{.correction}
 
@@
 
-[However, evidence from longitudinal studies indicates the challenge of assigning a subtype to dementia outcomes, given the known heterogeneity in clinical phenotypes.]{.correction} [@rooney2017] [For example, ]{.correction} [@shim2013]
-
 &nbsp;<!----------------------------------------------------------------------->
@@
 Dementia is quickly becoming a critically important public health issue.
-Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is a leading cause of death in the UK,[@zotero-15757] and one of the few without a proven treatment.
+Despite the age-specific incidence and prevalence of dementia remaining relatively constant over time,[@prince2016] an ageing population is set to create a dementia epidemic, particularly in westernised countries.[@flier2005] While approximately 525,000 patients have received a dementia diagnosis, the true number of people currently living with dementia in the UK is thought to be closer to 850,000, with this figure expected to double by 2040.[@baker2019] Globally, the prevalence of dementia is expected to reach 75 million by 2030.[@prince2016] Dementia is a leading cause of death in the UK,[@zotero-15757] [and its impact on mortality is likely underestimated, given that death certificates frequently do not accurately capture dementia cases.]{.correction}[@ahmad2021; @gao2018] [Further,]{.correction} it is one of the few leading causes of death without a proven treatment.
 
-Multimorbidity is common among people with dementia, with those diagnosed frequently having two or more other chronic conditions.[@poblador-plou2014]
-
-Patients with dementia have a higher risk of diabetes, stroke, depression pneumonia, falling and infection
+[Additionally, multimorbidity is common among people with dementia, with those diagnosed frequently having two or more other chronic conditions,]{.correction}[@poblador-plou2014] [including diabetes, depression and cerebrovascular disease.]{.correction}[@bauer2014] [Dementia makes the diagnoses and management of comordid conditions harder, as people living with dementia may not be in a position to seek primary care]{.correction}[@cooper2017] [or self-manage treatments.]{.correction}[@sinclair2000]
 
@@
 
-Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Well-studied risk factors for the condition include cardiovascular factors (e.g.
+Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Previously-examined risk factors for the condition include cardiovascular factors (e.g.
 hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] The benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied.

### 2022-04-01 05-Chp-CPRD-Analysis.Rmd
Range of corrections to Rmd files

@@
 
-Little evidence for an effect of lipid-regulating agents on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
+[No]{.correction} evidence for an effect of lipid-regulating agents on the risk of Alzheimer's disease was found, with the exception of a slightly increased risk in those prescribed a certain type of lipid-regulating agent called fibrates.
 In contrast, I found an increased risk of vascular and other (i.e., non-Alzheimer's) dementia was associated with lipid-regulating agent use.
@@
 
-* I found little evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
+* I found [very weak]{.correction} evidence for an effect of lipid-regulating agents on probable or possible Alzheimer’s disease.
 However, lipid-regulating agent use was associated with an increased risk of all-cause, vascular and other dementias.

### 2022-04-01 08-Discussion.Rmd
Added "and-meta-analyses" to chapter summary
Range of corrections to Rmd files

@@
 
-In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review [and meta-analyses]{.correction}
- of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes.
+In __Chapter \@ref(sys-rev-methods-heading)__, I described the methods of a comprehensive systematic review [and meta-analyses]{.correction} of all available evidence on the association of both lipid levels and lipid-regulating agents with dementia outcomes.
 The results of this analysis are then presented in __Chapter \@ref(sys-rev-results-heading)__.
@@
 
-However, there are also four key limitations to this thesis.
+However, there are also a number of key limitations to this thesis.
 As with many studies of dementia outcomes, a limiting factor in the interpretation of the results is the absence of a detailed pathological mechanism.
@@
 In addition, the absence of empirically based distributions of bias/indirectness for use with the triangulation framework limited the credibility of the results produced.
+
+[Fourthly, despite their wide use in the existing literature (as illustrated in the systematic review in Chapters]{.correction} \@ref(sys-rev-methods-heading) [&]{.correction} \@ref(sys-rev-results-heading) [), the clinical validity of dementia subtypes could be questioned and may lead to spurious results.
+This is supported by the difficulty in diagnosing a specific dementia subtype, and findings from population-based autopsies samples suggesting that "pure" Alzheimer's/vascular dementia outcomes are rare when compared to "mixed" dementia outcomes in older age groups, as discussed in detail in the Introduction (see Section]{.correction} \@ref(underlying-pathologies)[).
+In this case, results for the all-cause dementia outcome may be the most clinically useful, but were not the focus of the final chapters of these thesis.]{.correction}
 

### 2022-04-01 front-and-back-matter/_abstract.Rmd
Range of corrections to abstract

@@
 __Background:__ Identification of causal relationships between modifiable risk factors and incidence of dementia is central to the development of evidence-based prevention strategies.
-As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, LDL-c, HDL-c, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
-
-&nbsp;
+[Blood lipids represent such a modifiable risk factor, though considerable uncertainty remains concerning their relationship with dementia outcomes.]{.correction} As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, [low-density-lipoprotein cholesterol (LDL-c), high-density-lipoprotein cholesterol (HDL-c)]{.correction}, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
 
 __Methods:__ Four distinct analyses were conducted.
-Firstly, a systematic review was used to summarise the evidence base.
+Firstly, a systematic review [and meta-analysis]{.correction} was used to summarise the evidence base.
 Existing evidence was then supplemented via two primary studies: i) a cohort study of lipid regulating agents and dementia incidence in the Clinical Practice Research Datalink (CPRD); and ii) an individual participant data (IPD) meta-analysis of lipid levels and dementia incidence.
@@
 
-&nbsp;
-
 __Results:__ The systematic review did not identify a consistent effect of blood lipids on any dementia outcome across the study designs considered, though there was some suggestion of a protective effect of LDL-c lowering on all-cause dementia and Alzheimer's disease in observational studies of statin use.
-Analysis of the CPRD data provided weak evidence for a protective effect of statins on all-cause dementia and Alzheimer's disease but suggested a harmful association with vascular dementia,  likely due to confounding by indication.
-The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only.
+Analysis of the CPRD data provided [very]{.correction} weak evidence for [an effect of statins on Alzheimer's disease but suggested a harmful association with the all-cause, vascular and other dementia outcomes,]{.correction} likely due to confounding by indication.
+The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only [(Odds ratio: 1.25, 95%CI: 1.01-1.54)]{.correction}.
 Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
-
-&nbsp;
 

### 2022-04-07 01-Chp-Background.Rmd
Fixed missing short caption for a table
Final corrections

@@
 
-[While widely used in the published literature, the validity of these dementia subtypes as distinct clinical outcomes is debatable.]{.correction} Vascular dementia regularly co-occurs in patients with Alzheimer's disease,[@iadecola2013] [a]{.correction} presentation described as "mixed" dementia.[@custodio2017] [Evidence from autopsies performed as part of longitudinal population based samples, such as the Medical Research Council Cognitive Function and Ageing Study,]{.correction}[@chadwick1992] [found that a majority of participants had evidence of both Alzheimer's disease and vascular pathology.]{.correction} [@neuropathologygroupofthemedicalresearchcouncilcognitivefunctionandageingstudymrccfas2001] [This suggests that the "pure" clinical subtypes of dementia are less common than the "mixed" outcome, particularly in older age groups,]{.correction}[@schneider2007] [and indicates that a composite all-cause dementia outcome might be considered more analytically valid than outcomes based on a single dementia subtype.]{.correction}
+[While widely used in the published literature, the validity of these dementia subtypes as distinct clinical outcomes is debatable.]{.correction} Vascular dementia regularly co-occurs in patients with Alzheimer's disease,[@iadecola2013] [a]{.correction} presentation described as "mixed" dementia.[@custodio2017] [Evidence from autopsies performed as part of longitudinal population based samples, such as the Medical Research Council Cognitive Function and Ageing Study,]{.correction}[@chadwick1992] [found that a majority of participants had evidence of both Alzheimer's disease and vascular pathology.]{.correction} [@neuropathologygroupofthemedicalresearchcouncilcognitivefunctionandageingstudymrccfas2001] [This suggests that the "pure" clinical subtypes of dementia are less common than the "mixed" outcome, particularly in older age groups,]{.correction}[@schneider2007] [and indicates that a composite "all-cause" dementia outcome may be more analytically valid than outcomes based on a single dementia subtype.]{.correction}
 
@@
 
-[Additionally, multimorbidity is common among people with dementia, with those diagnosed frequently having two or more other chronic conditions,]{.correction}[@poblador-plou2014] [including diabetes, depression and cerebrovascular disease.]{.correction}[@bauer2014] [Dementia makes the diagnoses and management of comordid conditions harder, as people living with dementia may not be in a position to seek primary care]{.correction}[@cooper2017] [or self-manage treatments.]{.correction}[@sinclair2000]
+[Additionally, multimorbidity is common among people with dementia, with patients frequently having two or more other chronic conditions,]{.correction}[@poblador-plou2014] [including diabetes, depression and cerebrovascular disease.]{.correction}[@bauer2014] [Dementia makes the diagnoses and management of comordid conditions harder, as people living with dementia may not be in a position to seek primary care]{.correction}[@cooper2017] [or self-manage treatments.]{.correction}[@sinclair2000]
 
@@
 Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Previously-examined risk factors for the condition include cardiovascular factors (e.g.
-hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] The benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied.
+hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] [Similarly,]{.correction} the benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied.
 Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension, diabetes, smoking, physical inactivity, [depression,]{.correction} and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]
@@
 
+(ref:lipidTreatments-scaption) Summary of available treatments for hyperlipidaemia.
+
 ```{r lipidTreatments-table, message=FALSE, results="asis", echo = FALSE}
@@
 
-[A final general limitation of studies of statin use is their limited ability to assess a causal link between lipid levels and dementia.
-This is caused by the pleiotropic effect of statins, which may effect dementia risk via some non-lipid-lowering pathway.
-For example, statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]
+[A final general issue with studies of statin use is their limited ability to assess a causal link between lipid levels and dementia.
+This is due to the potential pleiotropic effects of statins, which may effect dementia risk via some non-lipid-lowering pathway.
+For example, previous work has shown that statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]
 
@@
 
-Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria [of MR analyses], as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
+Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria [of MR analyses]{.correction}, as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels.
 This was supported by further MR studies in which the observed effect attenuated to the null after _Apo_$\mathcal{E}$ variants were excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.

### 2022-04-07 05-Chp-CPRD-Analysis.Rmd
Final corrections

@@
 
-This finding disagrees with the results of the original analysis [reported by Smeet _et al_,]{.correction} [@smeeth2009] which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
+This finding disagrees with the results of the original analysis [reported by Smeeth _et al_,]{.correction} [@smeeth2009] which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).
 

### 2022-04-07 08-Discussion.Rmd
Final corrections

@@
 
-[Fourthly, despite their wide use in the existing literature (as illustrated in the systematic review in Chapters]{.correction} \@ref(sys-rev-methods-heading) [&]{.correction} \@ref(sys-rev-results-heading) [), the clinical validity of dementia subtypes could be questioned and may lead to spurious results.
+[Fourthly, despite their wide use in the existing literature (as illustrated in the systematic review in Chapters]{.correction} \@ref(sys-rev-methods-heading) [&]{.correction} \@ref(sys-rev-results-heading) [), the clinical validity of dementia subtypes (Alzheimer's disease, vascular dementia, etc.) could be questioned and may lead to spurious results.
 This is supported by the difficulty in diagnosing a specific dementia subtype, and findings from population-based autopsies samples suggesting that "pure" Alzheimer's/vascular dementia outcomes are rare when compared to "mixed" dementia outcomes in older age groups, as discussed in detail in the Introduction (see Section]{.correction} \@ref(underlying-pathologies)[).
-In this case, results for the all-cause dementia outcome may be the most clinically useful, but were not the focus of the final chapters of these thesis.]{.correction}
+In this case, results for the all-cause dementia outcome may be the most clinically useful, but this outcome was not the primary focus of the final chapters of these thesis.]{.correction}
 

### 2022-04-07 front-and-back-matter/99-appendices.Rmd
Corrections to front and back matter

--- 2021-12-17 front-and-back-matter/99-appendices.Rmd
@@
 Missing variables are denoted using a "-", while missing values are described as N (%).
-Note that LDL is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, HDL and TG following multiple imputation of missing values in these variables.
+Note that [LDL-c]{.correction} is missing completely for the Whitehall and CaPS datasets as this measure was derived from the measures for TC, [HDL-c]{.correction} and TG following multiple imputation of missing values in these variables.
 

### 2022-04-07 front-and-back-matter/_abstract.Rmd
Corrections to front and back matter

@@
 __Background:__ Identification of causal relationships between modifiable risk factors and incidence of dementia is central to the development of evidence-based prevention strategies.
-[Blood lipids represent such a modifiable risk factor, though considerable uncertainty remains concerning their relationship with dementia outcomes.]{.correction} As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, [low-density-lipoprotein cholesterol (LDL-c), high-density-lipoprotein cholesterol (HDL-c)]{.correction}, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
+[While blood lipids represent an easily modifiable target for preventative intervention, the evidence for their relationship with dementia outcomes is inconclusive due to the set of contradictory results reported by previous studies]{.correction} As such, this thesis sought to triangulate the causal effects of lipid levels (total cholesterol, [low-density-lipoprotein cholesterol (LDL-c), high-density-lipoprotein cholesterol (HDL-c)]{.correction}, and triglycerides) on risk of incident dementia (all-cause dementia, Alzheimer's disease, and vascular dementia) using existing and new evidence.
 
@@
 Analysis of the CPRD data provided [very]{.correction} weak evidence for [an effect of statins on Alzheimer's disease but suggested a harmful association with the all-cause, vascular and other dementia outcomes,]{.correction} likely due to confounding by indication.
-The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only [(Odds ratio: 1.25, 95%CI: 1.01-1.54)]{.correction}.
+The IPD meta-analysis provided some evidence for the association of triglycerides and vascular dementia only [(odds ratio: 1.25, 95%CI: 1.01-1.54)]{.correction}.
 Finally, the quantitative triangulation analysis did not provide strong evidence for the causal effect of blood lipids on dementia outcomes.
